### 2017-03-26 slides/athenatalk.tex
[ slides ] .tex skeleton added.

\documentclass[hyperref={pdfpagelabels=false}]{beamer}
\beamertemplatenavigationsymbolsempty
\usepackage[utf8x]{inputenc}
\newcommand{\textdf}[1]{\textbf{\textsf{#1}}\index{#1}}
\newcommand{\agda}[0]{\textbf{\texttt{Agda}\,}}
\newcommand{\keyword}[1]{\textit{#1}}
\newcommand{\miss}[0]{{\colorbox{amber}{\textdf{?}}}}
\newcommand{\ttgray}[1]{\texttt{\color{gray} #1}}
\newcommand{\shell}[1]{\texttt{\color{gray} #1}}
\newcommand{\highlight}[1]{\texttt{\color{bondiblue} #1}}
\let\Tiny=\tiny
\usepackage{lmodern}
\usepackage{url}
\usepackage{bussproofs}
\definecolor{amethyst}{rgb}{0.6, 0.4, 0.8}
\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
\definecolor{blue(munsell)}{rgb}{0.0, 0.5, 0.69}
\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\definecolor{cadet}{rgb}{0.33, 0.41, 0.47}
\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
\definecolor{amber}{rgb}{1.0, 0.75, 0.0}

\hypersetup{linktocpage}
\hypersetup{
colorlinks,
citecolor=amethyst,
filecolor=black,
linkcolor=blue(munsell),
urlcolor=blue(munsell)
}

\usepackage{graphicx}
\usepackage{bm}
\usepackage{amsmath, amsthm, amssymb}

\title{Proof Reconstruction with Athena\\(Work in Progress)}
% \date{\small{\jobname}}
\date{9th May}
\author{By Jonathan Prieto-Cubides}
\institute{
EAFIT University\\
Medell\'in, Colombia
}

\begin{document}

\setcounter{page}{1}
\maketitle

\begin{frame}{References}

\end{frame}

\end{document}

### 2017-03-26 src/Athena/Main.hs
minor changes in the headers.

@@ -1,5 +1,5 @@
 
--- | Main module
+-- | Main module.
 
 {-# LANGUAGE MultiWayIf    #-}
 {-# LANGUAGE UnicodeSyntax #-}

### 2017-03-26 src/Athena/Options.hs

@@ -1,5 +1,5 @@
 
--- | Options module.
+-- | Athena.Options module.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-26 src/Athena/TSTP.hs

@@ -1,4 +1,4 @@
--- | TSTP module.
+-- | Athena.TSTP module.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-26 src/Athena/TSTP/Base.hs

@@ -1,5 +1,5 @@
 
--- | TSTP.Base module.
+-- | Athena.TSTP.Base module.
 
 {-# OPTIONS_HADDOCK hide   #-}
 {-# LANGUAGE UnicodeSyntax #-}

### 2017-03-26 src/Athena/Translation/Core.hs

@@ -1,5 +1,5 @@
 
--- | Athena.Translation.Core module
+-- | Athena.Translation.Core module.
 
 {-# LANGUAGE ScopedTypeVariables #-}
 {-# LANGUAGE UnicodeSyntax       #-}

### 2017-03-26 src/Athena/Utils/Monad.hs

@@ -1,5 +1,5 @@
 
--- | Monads utilities.
+-- | Athena.Utils.Monads utilities.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-26 src/Athena/Utils/PrettyPrint.hs

@@ -7,7 +7,7 @@
 module Athena.Utils.PrettyPrint
   ( module Text.PrettyPrint.HughesPJ
   , cquotes
-  , Pretty(pretty)
+  , Pretty ( pretty )
   , prettyShow
   , scquotes
   , spaces

### 2017-03-26 src/Athena/Utils/Show.hs

@@ -1,5 +1,5 @@
 
--- | Utilities related to 'Show'.
+-- | Athena.Utils.Show module.
 
 {-# LANGUAGE CPP           #-}
 {-# LANGUAGE UnicodeSyntax #-}

### 2017-03-26 src/Athena/Utils/Version.hs

@@ -1,5 +1,6 @@
 
--- | Utilities related to representation of versions.
+-- | Athena.Utils.Version module.
+-- Utilities related to representation of versions.
 
 {-# LANGUAGE CPP           #-}
 {-# LANGUAGE UnicodeSyntax #-}

### 2017-03-26 src/Data/Proof.hs

@@ -1,5 +1,5 @@
 
--- | Data.Proof module
+-- | Data.Proof module.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-26 src/Data/Proof/ProofTreeGen.hs

@@ -1,5 +1,5 @@
 
--- | Data.Proof.ProofTreeGen module
+-- | Data.Proof.ProofTreeGen module.
 
 module Data.Proof.ProofTreeGen where
 

### 2017-03-26 src/Data/TSTP.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP module
+-- | Data.TSTP module.
 
 {-# LANGUAGE FlexibleInstances    #-}
 {-# LANGUAGE UnicodeSyntax        #-}

### 2017-03-26 src/Data/TSTP/AtomicWord.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.AtomicWord module
+-- | Data.TSTP.AtomicWord module.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-26 src/Data/TSTP/BinOp.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.BinOp module
+-- | Data.TSTP.BinOp module.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-26 src/Data/TSTP/F.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.F module
+-- | Data.TSTP.F module.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-26 src/Data/TSTP/Formula.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.Formula module
+-- | Data.TSTP.Formula module.
 
 {-# OPTIONS -fno-warn-incomplete-patterns #-}
 {-# LANGUAGE UnicodeSyntax                #-}

### 2017-03-26 src/Data/TSTP/GData.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.GData module
+-- | Data.TSTP.GData module.
 
 module Data.TSTP.GData where
 

### 2017-03-26 src/Data/TSTP/InfixPred.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.InfixPred module
+-- | Data.TSTP.InfixPred module.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-26 src/Data/TSTP/IntroType.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.IntroType module
+-- | Data.TSTP.IntroType module.
 
 module Data.TSTP.IntroType where
 

### 2017-03-26 src/Data/TSTP/Parent.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.Parent module
+-- | Data.TSTP.Parent module.
 
 module Data.TSTP.Parent where
 

### 2017-03-26 src/Data/TSTP/Quant.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.Quant module
+-- | Data.TSTP.Quant module.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-26 src/Data/TSTP/Role.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.Role module
+-- | Data.TSTP.Role module.
 
 module Data.TSTP.Role where
 

### 2017-03-26 src/Data/TSTP/Rule.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.Rule module
+-- | Data.TSTP.Rule module.
 
 module Data.TSTP.Rule where
 

### 2017-03-26 src/Data/TSTP/Source.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.Source module
+-- | Data.TSTP.Source module.
 
 module Data.TSTP.Source where
 

### 2017-03-26 src/Data/TSTP/Status.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.Status module
+-- | Data.TSTP.Status module.
 
 module Data.TSTP.Status where
 

### 2017-03-26 src/Data/TSTP/Term.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.Term module
+-- | Data.TSTP.Term module.
 
 module Data.TSTP.Term where
 

### 2017-03-26 src/Data/TSTP/Theory.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.Theory module
+-- | Data.TSTP.Theory module.
 
 module Data.TSTP.Theory where
 

### 2017-03-26 src/Data/TSTP/V.hs

@@ -1,5 +1,5 @@
 
--- | Data.TSTP.V module
+-- | Data.TSTP.V module.
 
 module Data.TSTP.V where
 

### 2017-03-26 src/Athena/Translation/Core.hs
[ Translation.Core ] leaving the essential.

@@ -13,25 +13,14 @@ import Athena.Translation.Functions
   , getConjeture
   , getRefutes
   , getSubGoals
-  , printAxiom
   , printAxioms
   , printConjecture
   , printPreamble
-  -- , printSubGoals
-  -- , printVar
+  , printPremises
+  , printProof
+  , printSubGoals
   , printVars
   )
-import Athena.Translation.Rules
-  (
-    -- atpCanonicalize
-  -- , atpClausify
-    atpConjunct
-  -- , atpNegate
-  , atpResolve
-  -- , atpSimplify
-  -- , atpStrip
-  )
-import Athena.Translation.Utils ( Ident, getIdent, stdName)
 import Athena.Utils.Monad       ( stdout2file )
 import Athena.Options
   ( Options
@@ -41,30 +30,22 @@ import Athena.Options
   )
 import Athena.TSTP              ( parseFile )
 
-import Data.List
-import qualified Data.Map as Map
-import Data.Maybe               ( fromJust, fromMaybe, Maybe )
+import Data.Maybe               ( fromJust, fromMaybe )
 
 import Data.Proof
   ( buildProofMap
   , buildProofTree
   , ProofMap
   , ProofTree
-  , ProofTreeGen(..)
   )
 import Data.TSTP
   ( F(..)
   , Formula(..)
-  , Rule(..)
-  , Role(..)
   )
 import Data.TSTP.Formula        ( getFreeVars )
 import Data.TSTP.V              ( V(..) )
 
 ------------------------------------------------------------------------------
-
-debug :: Bool
-debug = True
 
 mainCore ∷ Options → IO ()
 mainCore opts = do
@@ -99,234 +80,13 @@ mainCore opts = do
   let freevars ∷ [V]
       freevars = getFreeVars formulas
 
-  printPreamble (length freevars)
+  printPreamble $ length freevars
 
   putStrLn "-- Vars"
   _ <- printVars freevars 0
 
   printAxioms axioms
-
   printPremises axioms
-
   printConjecture conj
-
-  printSubGoals' subgoals
-
+  printSubGoals subgoals
   printProof axioms subgoals conj rulesMap rulesTrees
-
-
-
-printPremises ∷ [F] → IO ()
-printPremises premises = do
[…]

### 2017-03-26 src/Athena/Translation/Functions.hs

@@ -13,25 +13,48 @@ module Athena.Translation.Functions
    , printAxioms
    , printConjecture
    , printPreamble
+   , printPremises
+   , printProof
    , printSubGoals
-   , printVar
    , printVars
    ) where
 
 ------------------------------------------------------------------------------
 
-import Athena.Translation.Utils ( stdName )
+import Athena.Translation.Rules
+  (
+  -- atpCanonicalize
+  -- , atpClausify
+    atpConjunct
+  -- , atpNegate
+  , atpResolve
+  -- , atpSimplify
+  -- , atpStrip
+  )
+import Athena.Translation.Utils  ( Ident, getIdent, stdName )
+import Athena.Utils.Version      ( progNameVersion )
+
+import Data.Proof
+  ( ProofMap
+  , ProofTree
+  , ProofTreeGen(..)
+  )
 
 import Data.List                ( isPrefixOf, intercalate )
+import Data.Maybe               ( fromJust, Maybe )
+import qualified Data.Map as Map
 
 import Data.TSTP
   ( F    ( name, role, formula )
+  , Formula(..)
   , Role ( Axiom, Conjecture )
+  , Rule(..)
   )
-
 import Data.TSTP.V              ( V(..) )
-
 ------------------------------------------------------------------------------
+
+debug :: Bool
+debug = True
 
 -- Vars.
 
@@ -69,6 +92,7 @@ printAxiom f =
     ,  axiom , " = " ,  show (formula f) , "\n"
     ]
 
+-- | Print out in the Agda file the axioms.
 printAxioms ∷ [F] → IO ()
 printAxioms []  = return ()
 printAxioms [a] = do
@@ -89,6 +113,7 @@ getConjeture rules =
     [l] → Just l
     _   → Nothing
 
+-- | Print out in the Agda file the conjecture.
 printConjecture ∷ F → IO ()
 printConjecture f = putStrLn $
   concat
@@ -96,12 +121,19 @@ printConjecture f = putStrLn $
     , printAxiom f , "\n"
     ]
 
+-- Refutes.
+
+-- | Extract refuting steps from a list of formulae.
+getRefutes ∷ [F] → [F]
+getRefutes = filter (isPrefixOf "refute"  . name)
+
 -- Subgoals.
 
[…]

### 2017-03-26 src/Data/TSTP/Formula.hs
[ Data/TSTP/Formula ] show pattern completed.

@@ -43,16 +43,18 @@ data Formula = BinOp Formula BinOp Formula    -- ^ Binary connective application
 
 -- TODO: use of PrettyPrinter
 instance Show Formula where
+  show ((:~:) f )            = "(" ++ "¬" ++ show f ++ ")"
   show (BinOp f₁ (:=>:) f₂)  = "(" ++ show f₁ ++ "⇒" ++ show f₂ ++ ")"
   show (BinOp f₁ (:<=>:) f₂) = "(" ++ show f₁ ++ "⇔" ++ show f₂ ++ ")"
   show (BinOp f₁ op f₂)      = "(" ++ show f₁ ++ show op ++ show f₂ ++ ")"
   show (InfixPred t₁ r t₂)   = "(" ++ show t₁ ++ show r  ++ show t₂ ++ ")"
   show (PredApp (AtomicWord "$false") []) = "⊥"
   show (PredApp (AtomicWord "$true")  []) = "⊤"
-  show (PredApp ρ []) = show ρ
+  show (PredApp (AtomicWord p)  [])       = show p
   show (PredApp ρ ϕ ) = "(" ++ show ρ ++ ":" ++ show ϕ ++ "⇒ ⊤" ++ ")"
-  show ((:~:)f )      = "(" ++ "¬" ++ show f ++ ")"
-
+  show (Quant     All []     _ ) = "-- not supported yet."
+  show (Quant     All _      _ ) = "-- not supported yet."
+  show (Quant     Exists _   _ ) = "-- not supported yet."
 
 -- | 'freeVarsF' 'f', returns a 'Set' of all free variables of 'f'.
 freeVarsF ∷ Formula → Set V

### 2017-03-26 src/Athena/Translation/Functions.hs
[ Translation.Functions ] fixed header in Agda file.

@@ -146,7 +146,7 @@ printSubGoals subgoals = putStrLn $
 printPreamble ∷ Int → IO ()
 printPreamble n = do
   version <- progNameVersion
-  putStrLn $ "\n-- Athena v" ++ version ++ " reconstructs this proof.\n"
+  putStrLn $ "\n-- " ++ version ++ " reconstructed this proof.\n"
   putStrLn $ "open import Data.Prop " ++ show n ++ " public"
   putStrLn $ "open import ATP.Metis " ++ show n ++ " public\n"
 

### 2017-03-26 src/Data/TSTP/Formula.hs
[ Data.TSTP.Formula ] fixed a miss whitespace.

@@ -43,7 +43,7 @@ data Formula = BinOp Formula BinOp Formula    -- ^ Binary connective application
 
 -- TODO: use of PrettyPrinter
 instance Show Formula where
-  show ((:~:) f )            = "(" ++ "¬" ++ show f ++ ")"
+  show ((:~:) f )            = "(" ++ "¬ " ++ show f ++ ")"
   show (BinOp f₁ (:=>:) f₂)  = "(" ++ show f₁ ++ "⇒" ++ show f₂ ++ ")"
   show (BinOp f₁ (:<=>:) f₂) = "(" ++ show f₁ ++ "⇔" ++ show f₂ ++ ")"
   show (BinOp f₁ op f₂)      = "(" ++ show f₁ ++ show op ++ show f₂ ++ ")"

### 2017-03-26 src/Data/TSTP/Formula.hs
[ Data.TSTP.Formula ] fixed print of literals.

@@ -50,7 +50,7 @@ instance Show Formula where
   show (InfixPred t₁ r t₂)   = "(" ++ show t₁ ++ show r  ++ show t₂ ++ ")"
   show (PredApp (AtomicWord "$false") []) = "⊥"
   show (PredApp (AtomicWord "$true")  []) = "⊤"
-  show (PredApp (AtomicWord p)  [])       = show p
+  show (PredApp (AtomicWord p)  [])       = p
   show (PredApp ρ ϕ ) = "(" ++ show ρ ++ ":" ++ show ϕ ++ "⇒ ⊤" ++ ")"
   show (Quant     All []     _ ) = "-- not supported yet."
   show (Quant     All _      _ ) = "-- not supported yet."

### 2017-03-26 src/Data/TSTP/Formula.hs
[ Data.TSTP.Formula ] added whitespaces in general.

@@ -44,14 +44,14 @@ data Formula = BinOp Formula BinOp Formula    -- ^ Binary connective application
 -- TODO: use of PrettyPrinter
 instance Show Formula where
   show ((:~:) f )            = "(" ++ "¬ " ++ show f ++ ")"
-  show (BinOp f₁ (:=>:) f₂)  = "(" ++ show f₁ ++ "⇒" ++ show f₂ ++ ")"
-  show (BinOp f₁ (:<=>:) f₂) = "(" ++ show f₁ ++ "⇔" ++ show f₂ ++ ")"
-  show (BinOp f₁ op f₂)      = "(" ++ show f₁ ++ show op ++ show f₂ ++ ")"
-  show (InfixPred t₁ r t₂)   = "(" ++ show t₁ ++ show r  ++ show t₂ ++ ")"
+  show (BinOp f₁ (:=>:) f₂)  = "(" ++ show f₁ ++ " ⇒ " ++ show f₂ ++ ")"
+  show (BinOp f₁ (:<=>:) f₂) = "(" ++ show f₁ ++ " ⇔ " ++ show f₂ ++ ")"
+  show (BinOp f₁ op f₂)      = "(" ++ show f₁ ++ " " ++ show op ++ " " ++ show f₂ ++ ")"
+  show (InfixPred t₁ r t₂)   = "(" ++ show t₁ ++ " " ++ show r  ++ " " ++ show t₂ ++ ")"
   show (PredApp (AtomicWord "$false") []) = "⊥"
   show (PredApp (AtomicWord "$true")  []) = "⊤"
   show (PredApp (AtomicWord p)  [])       = p
-  show (PredApp ρ ϕ ) = "(" ++ show ρ ++ ":" ++ show ϕ ++ "⇒ ⊤" ++ ")"
+  show (PredApp ρ ϕ )            = "-- not supported yet."
   show (Quant     All []     _ ) = "-- not supported yet."
   show (Quant     All _      _ ) = "-- not supported yet."
   show (Quant     Exists _   _ ) = "-- not supported yet."

### 2017-03-26 src/Athena/Translation/Functions.hs
[ Translation ] headers fixed.

@@ -146,10 +146,12 @@ printSubGoals subgoals = putStrLn $
 printPreamble ∷ Int → IO ()
 printPreamble n = do
   version <- progNameVersion
-  putStrLn $ "\n-- " ++ version ++ " reconstructed this proof.\n"
-  putStrLn $ "open import Data.Prop " ++ show n ++ " public"
+  putStrLn $ "\n-- " ++ version ++ "\n"
+  putStrLn $ replicate 78 '-'
+  putStrLn $ "\nopen import Data.Prop " ++ show n ++ " public"
   putStrLn $ "open import ATP.Metis " ++ show n ++ " public\n"
-
+  putStrLn $ replicate 78 '-'
+  putStrLn ""
 
 -- | Print out the premises in the Agda file.
 printPremises ∷ [F] → IO ()
@@ -180,7 +182,11 @@ printInnerFormula n dict tag ctxt =
 printProof ∷ [F] → [F] → F → ProofMap → [ProofTree] → IO ()
 printProof _ _  _ _ [] = return ()
 printProof axioms subgoals goal rmap rtree = do
-  putStrLn "-- Metis Proof."
+  putStrLn ""
+  putStrLn $ replicate 78 '-'
+  putStrLn "-- Proof"
+  putStrLn $ replicate 78 '-'
+  putStrLn "\n"
   printProofSubgoal 0 axioms subgoals goal rmap rtree
   printProofGoal subgoals goal rmap rtree
 

### 2017-03-26 src/Data/TSTP/Formula.hs

@@ -51,7 +51,7 @@ instance Show Formula where
   show (PredApp (AtomicWord "$false") []) = "⊥"
   show (PredApp (AtomicWord "$true")  []) = "⊤"
   show (PredApp (AtomicWord p)  [])       = p
-  show (PredApp ρ ϕ )            = "-- not supported yet."
+  show (PredApp _ _ )            = "-- not supported yet."
   show (Quant     All []     _ ) = "-- not supported yet."
   show (Quant     All _      _ ) = "-- not supported yet."
   show (Quant     Exists _   _ ) = "-- not supported yet."

### 2017-03-26 src/Athena/Options.hs
[ Options ] removed standard output. Now, file+.agda generated.

@@ -85,7 +85,7 @@ options =
   [ Option ['h'] ["help"] (NoArg helpOpt)
       "Prints help message"
   , Option ['o'] ["output"] (ReqArg outputFileOpt "FILE")
-      "Output to file      (default: STDOUT)"
+      "Output to file"
   , Option ['p'] ["proof-name"] (ReqArg proofNameOpt "NAME")
       "Main proof name     (default: proof)"
   , Option []    ["version"] (NoArg versionOpt)

### 2017-03-26 src/Athena/Translation/Core.hs

@@ -45,6 +45,7 @@ import Data.TSTP
 import Data.TSTP.Formula        ( getFreeVars )
 import Data.TSTP.V              ( V(..) )
 
+import System.FilePath          ( replaceExtension )
 ------------------------------------------------------------------------------
 
 mainCore ∷ Options → IO ()
@@ -72,7 +73,10 @@ mainCore opts = do
   let rulesTrees ∷ [ProofTree]
       rulesTrees = fmap (buildProofTree rulesMap) refutes
 
-  stdout2file $ optOutputFile opts
+  stdout2file $ Just (fromMaybe
+    (replaceExtension (fromJust (optInputFile opts)) ".agda")
+    (optOutputFile opts)
+    )
 
   let formulas ∷ [Formula]
       formulas = fmap formula tstp

### 2017-03-29 src/Athena/TSTP.hs
Adding information about the adapted code.

@@ -1,4 +1,6 @@
+
 -- | Athena.TSTP module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-29 src/Athena/TSTP/Base.hs

@@ -1,5 +1,6 @@
 
 -- | Athena.TSTP.Base module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 {-# OPTIONS_HADDOCK hide   #-}
 {-# LANGUAGE UnicodeSyntax #-}

### 2017-03-29 src/Athena/Utils/PrettyPrint.hs

@@ -1,5 +1,6 @@
 
 -- | Athena.Utils.PrettyPrint module.
+-- Adapted from https://github.com/asr/apia.
 
 {-# LANGUAGE FlexibleInstances #-}
 {-# LANGUAGE UnicodeSyntax     #-}

### 2017-03-29 src/Data/Proof/ProofTreeGen.hs

@@ -1,5 +1,6 @@
 
 -- | Data.Proof.ProofTreeGen module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.Proof.ProofTreeGen where
 

### 2017-03-29 src/Athena/TSTP.hs
[ TSTP parsing ] fixed #3.

@@ -1,8 +1,9 @@
-
 -- | Athena.TSTP module.
 -- Adapted from https://github.com/agomezl/tstp2agda.
 
-{-# LANGUAGE UnicodeSyntax #-}
+{-# LANGUAGE ScopedTypeVariables #-}
+{-# LANGUAGE UnicodeSyntax       #-}
+
 
 module Athena.TSTP
   ( parse
@@ -15,6 +16,8 @@ import  Athena.TSTP.Lexer  ( alexScanTokens )
 import  Athena.TSTP.Parser ( parseTSTP )
 
 import  Data.TSTP.F
+
+import Data.List           ( isPrefixOf )
 
 ------------------------------------------------------------------------------
 
@@ -44,4 +47,10 @@ parse ∷ String → [F]
 parse = parseTSTP . fmap snd . alexScanTokens
 
 parseFile ∷ FilePath → IO [F]
-parseFile path = parse <$> readFile path
+parseFile path = do
+  contents ∷ String ← readFile path
+
+  let vlines ∷ String
+      vlines = unlines . filter (not . isPrefixOf "%") . lines $ contents
+
+  return $ parse vlines

### 2017-03-30 src/Athena/TSTP.hs
[ Data.TSTP ] added "Adapted" in the modules.

@@ -12,12 +12,12 @@ module Athena.TSTP
 
 ------------------------------------------------------------------------------
 
-import  Athena.TSTP.Lexer  ( alexScanTokens )
-import  Athena.TSTP.Parser ( parseTSTP )
+import Athena.TSTP.Lexer  ( alexScanTokens )
+import Athena.TSTP.Parser ( parseTSTP )
 
-import  Data.TSTP.F
+import Data.TSTP.F
 
-import Data.List           ( isPrefixOf )
+import Data.List          ( isPrefixOf )
 
 ------------------------------------------------------------------------------
 

### 2017-03-30 src/Data/TSTP/AtomicWord.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.AtomicWord module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-30 src/Data/TSTP/BinOp.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.BinOp module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 {-# LANGUAGE UnicodeSyntax #-}
 
@@ -8,9 +9,9 @@ module Data.TSTP.BinOp where
 ------------------------------------------------------------------------------
 
 -- | Binary formula connectives.
-data BinOp = (:<=>:)  -- ^ ↔ /Equivalence/
-           | (:=>:)   -- ^ → /Implication/
-           | (:<=:)   -- ^ ← /Reverse Implication/
+data BinOp = (:<=>:)  -- ^ ⇔ /Equivalence/
+           | (:=>:)   -- ^ ⇒ /Implication/
+           | (:<=:)   -- ^ ⇐ /Reverse Implication/
            | (:&:)    -- ^ ∧ /AND/
            | (:|:)    -- ^ ∨ /OR/
            | (:~&:)   -- ^ ⊼ /NAND/
@@ -19,9 +20,9 @@ data BinOp = (:<=>:)  -- ^ ↔ /Equivalence/
            deriving (Eq, Ord, Read)
 
 instance Show BinOp where
-  show (:<=>:) = "↔"
-  show (:=>:)  = "→"
-  show (:<=:)  = "←"
+  show (:<=>:) = "⇔"
+  show (:=>:)  = "⇒"
+  show (:<=:)  = "⇐"
   show (:&:)   = "∧"
   show (:|:)   = "∨"
   show (:~&:)  = "⊼"

### 2017-03-30 src/Data/TSTP/F.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.F module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 {-# LANGUAGE UnicodeSyntax #-}
 
@@ -7,9 +8,9 @@ module Data.TSTP.F where
 
 ------------------------------------------------------------------------------
 
-import Data.TSTP.Formula    ( Formula(..) )
-import Data.TSTP.Role       ( Role(..) )
-import Data.TSTP.Source     ( Source(..) )
+import Data.TSTP.Formula ( Formula(..) )
+import Data.TSTP.Role    ( Role(..) )
+import Data.TSTP.Source  ( Source(..) )
 
 ------------------------------------------------------------------------------
 

### 2017-03-30 src/Data/TSTP/Formula.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.Formula module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 {-# OPTIONS -fno-warn-incomplete-patterns #-}
 {-# LANGUAGE UnicodeSyntax                #-}
@@ -27,11 +28,6 @@ import Data.TSTP.Term       ( Term(..))
 import Data.TSTP.V          ( V(..) )
 
 ------------------------------------------------------------------------------
-
--- The following code is based on:
--- https://github.com/DanielSchuessler/logic-TPTP
--- and is just a simplified version of the the datatypes
--- (without the Indirect composite)
 
 -- | first-order logic formula.
 data Formula = BinOp Formula BinOp Formula    -- ^ Binary connective application

### 2017-03-30 src/Data/TSTP/GData.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.GData module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.TSTP.GData where
 

### 2017-03-30 src/Data/TSTP/InfixPred.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.InfixPred module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-30 src/Data/TSTP/IntroType.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.IntroType module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.TSTP.IntroType where
 

### 2017-03-30 src/Data/TSTP/Parent.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.Parent module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.TSTP.Parent where
 

### 2017-03-30 src/Data/TSTP/Quant.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.Quant module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 {-# LANGUAGE UnicodeSyntax #-}
 

### 2017-03-30 src/Data/TSTP/Role.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.Role module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.TSTP.Role where
 

### 2017-03-30 src/Data/TSTP/Rule.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.Rule module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.TSTP.Rule where
 

### 2017-03-30 src/Data/TSTP/Source.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.Source module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.TSTP.Source where
 

### 2017-03-30 src/Data/TSTP/Status.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.Status module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.TSTP.Status where
 

### 2017-03-30 src/Data/TSTP/Term.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.Term module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.TSTP.Term where
 

### 2017-03-30 src/Data/TSTP/Theory.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.Theory module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.TSTP.Theory where
 

### 2017-03-30 src/Data/TSTP/V.hs

@@ -1,5 +1,6 @@
 
 -- | Data.TSTP.V module.
+-- Adapted from https://github.com/agomezl/tstp2agda.
 
 module Data.TSTP.V where
 

### 2017-03-30 src/Athena/Translation/Functions.hs
[ Makefile ] fixed targets, and fixed name translation.

@@ -324,15 +324,15 @@ printSteps _ n [Leaf Conjecture gname] _ _ _ =
 printSteps sname n [Leaf Axiom gname] _ _ _ =
   concat
     [ getIdent n , "weaken (atp-neg " , stdName sname , ") $\n"
-    , getIdent (n+1) , "(assume {Γ = ∅} " , gname , ")\n"
+    , getIdent (n+1) , "(assume {Γ = ∅} " , stdName gname , ")\n"
     ]
 printSteps _ n _ _ _ _ = getIdent n ++ "? -- no supported yet\n"
 
 
 andIntroSubgoals ∷ Ident → Int → [F] → String
-andIntroSubgoals _ _ []       = ""
-andIntroSubgoals m n [_]      = getIdent m ++ "subgoal" ++ stdName (show n)
-andIntroSubgoals m n [_,_]    =
+andIntroSubgoals _ _ []    = ""
+andIntroSubgoals m n [_]   = getIdent m ++ "subgoal" ++ stdName (show n)
+andIntroSubgoals m n [_,_] =
   concat
     [ getIdent m , "subgoal" , stdName (show n) , "\n"
     , getIdent m , "subgoal" , stdName (show (n+1)) , "\n"

### 2017-04-12 src/Athena/Translation/AgdaFile.hs
[ Translation ] the number of the subgoal is available now in docSteps.

@@ -304,6 +304,9 @@ getRefutes = filter (isPrefixOf "refute" . name)
 -- Proof.
 ------------------------------------------------------------------------------
 
+subgoalName ∷ Int → Doc
+subgoalName n = pretty "subgoal" <> (pretty . stdName . show) n
+
 docProof ∷ AgdaFile → Doc
 docProof agdaFile =
      hypenline
@@ -316,16 +319,13 @@ docProof agdaFile =
 
 docProofSubgoal ∷ Int → ProofTree → AgdaFile → Doc
 docProofSubgoal n tree agdaFile =
-     pName <+> colon <+> pretty "Γ ⊢" <+> pretty sName <> line
+     pName <+> colon <+> pretty "Γ ⊢" <+> pretty (subgoalName n) <> line
   <> pName <+> equals <> line
   <> indent 2  (parens (pretty "RAA" <> line <>
-              indent 2 (docSteps sName tree agdaFile))) <> line
+              indent 2 (docSteps n tree agdaFile))) <> line
   where
     pName ∷  Doc
     pName = pretty "proof" <> (pretty . stdName . show) n
-
-    sName ∷ Doc
-    sName = pretty "subgoal" <> (pretty . stdName . show) n
 
 docProofSubgoals ∷ AgdaFile → Doc
 docProofSubgoals agdaFile =
@@ -334,8 +334,8 @@ docProofSubgoals agdaFile =
       (\(n, tree) → docProofSubgoal n tree agdaFile)
       (zip [0..] trees)
   where
-      trees ∷ [ProofTree]
-      trees = fileTrees agdaFile
+    trees ∷ [ProofTree]
+    trees = fileTrees agdaFile
 
 docProofGoal ∷ AgdaFile → Doc
 docProofGoal agdaFile =
@@ -373,17 +373,22 @@ docProofGoal agdaFile =
 
 -- | docSteps generates the document with the proof making recursion
 -- over the deduction tree.
-docSteps ∷ Doc → ProofTree → AgdaFile → Doc
+
+docSteps ∷ Int        -- ^ The number of the subgoal.
+         → ProofTree  -- ^ Deduction tree.
+         → AgdaFile   -- ^ Agda file.
+         → Doc        -- ^ Doc of the step.
 
 ------------------------------------------------------------------------------
 -- Axiom.
 ------------------------------------------------------------------------------
 
-docSteps sName (Leaf Axiom axiom) agdaFile =
[…]

### 2017-04-18 slides/athenatalk.tex
[ Makefile ] fixed targets, and fixed name translation.
[ slides ] minor changes.
[ slides ] init.

@@
 \usepackage[utf8x]{inputenc}
-\newcommand{\textdf}[1]{\textbf{\textsf{#1}}\index{#1}}
-\newcommand{\agda}[0]{\textbf{\texttt{Agda}\,}}
-\newcommand{\keyword}[1]{\textit{#1}}
-\newcommand{\miss}[0]{{\colorbox{amber}{\textdf{?}}}}
-\newcommand{\ttgray}[1]{\texttt{\color{gray} #1}}
-\newcommand{\shell}[1]{\texttt{\color{gray} #1}}
-\newcommand{\highlight}[1]{\texttt{\color{bondiblue} #1}}
-\let\Tiny=\tiny
+\usepackage{amsmath, amsthm, amssymb}
+%\usepackage{bm}
+\usepackage{bussproofs}
+\usepackage{graphicx}
+\usepackage{listings}
 \usepackage{lmodern}
 \usepackage{url}
-\usepackage{bussproofs}
-\definecolor{amethyst}{rgb}{0.6, 0.4, 0.8}
-\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
-\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
-\definecolor{blue(munsell)}{rgb}{0.0, 0.5, 0.69}
-\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
-\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
+\usepackage[T1]{fontenc}
+
+\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
 \definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
 \definecolor{cadet}{rgb}{0.33, 0.41, 0.47}
-\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
-\definecolor{amber}{rgb}{1.0, 0.75, 0.0}
 
-\hypersetup{linktocpage}
-\hypersetup{
-colorlinks,
-citecolor=amethyst,
-filecolor=black,
-linkcolor=blue(munsell),
-urlcolor=blue(munsell)
+\lstset{
+    aboveskip=10pt
+  , backgroundcolor=\color{aliceblue}
+  , basicstyle=\ttfamily
+  , belowskip=9pt
+  , frame=trbl
+  , keywords=[2]{axiom, conjecture,inference, negated_conjecture, plain}
+  , keywords=[3]{fof, cnf}
+  , keywords=[4]{canonicalize, resolve, conjunct, strip, simplify, negate, clausify}
+  , keywordstyle=[2]\color{cadet}%\underbar,%\bfseries
+  , keywordstyle=[3]\color{bondiblue}\bfseries
+  , keywordstyle=[4]\bfseries
+  , showstringspaces=false
 }
 
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{amsmath, amsthm, amssymb}
+\newcommand{\problemtptp}[3][c]{\lstinputlisting[caption=#2, firstline=#3, label=custom#1]{#2}}
+\newcommand{\solutiontstp}[2][c]{\lstinputlisting[caption=#2, firstline=5, label=custom#1]{#2}}
 
 \title{Proof Reconstruction with Athena\\(Work in Progress)}
-% \date{\small{\jobname}}
-\date{9th May}
-\author{By Jonathan Prieto-Cubides}
+
+\date{Agda Implementors’ Meeting XXV}
+
+\author{Jonathan Prieto-Cubides}
+
 \institute{
+Advisor: Andr\'es Sicard-Ram\'irez\\[3mm]
 EAFIT University\\
-Medell\'in, Colombia
-}
+Medell\'in, Colombia}
 
@@
 
+% Context
+% - SledgeHammer
+% - Metis
+% - Problem with Wallmeinster finding the code.
+% - equinox (intuisionistic version)
+
+\begin{frame}{Keywords}
+  \begin{block}{Proof Assistant}
+  is a software program that work together with a human in order to give formal proofs to problems in a wide range of topics.\footnote{Matita development team, Matita website, http://matita.cs.unibo.it/index.shtml}
+  \end{block}
+  \begin{block}{ATP}
+  An \text{A}utomatic \textbf{T}heorem \textbf{P}rover is software program 
+  \end{block}
+\end{frame}
+
+\begin{frame}{Athena}
+  Is a Haskell program that translates proofs given by Metis ATP in TSTP format
+  to Agda code.
+
+  \begin{figure}
+    \includegraphics[scale=0.85]{diagram.pdf}
+    \label{im:athena}
+    \caption{Proof reconstruction work flow.}
+  \end{figure}
+\end{frame}
+
+\begin{frame}{TPTP}
+  Is a text format to encode problems in different theories. Its goal is provide
+  a standard for all ATPs in the input file format. The version for derivations
+  is named TSTP but this one is not a standard yet.\\[2mm]
+
+  A TPTP file looks like:
+
+  \problemtptp[basic-4.tptp]{../test/prop-pack/problems/basic/basic-4.tptp}{2}
+
+\end{frame}
+
+\begin{frame}{TSTP}
+  A derivation of the previous problem output by Metis ATP.
+{\footnotesize
+  \problemtptp[basic-4.tstp]{../test/prop-pack/problems/basic/basic-4.tstp}{0}
+}
+\end{frame}
+
+%% \begin{frame}{Agda}
+%%   A proof verified of the previous derivation output by Athena.
+%% {\footnotesize
+%%   \problemtptp[basic-4.agda]{../test/prop-pack/problems/basic/basic-4.agda}{0}
+%% }
+%% \end{frame}
+
+% The tool : Athena.
+% Its components:
+% - agda-prop (logic framework)
+% - agda-metis (ATP rules)
+% - prop-pack (problems)
+
+\begin{frame}{Future work}
+
+  \begin{itemize}
+  \item
+    Extend the libraries Agda-Prop and Agda-Metis to handle predicated logic
+  \item
+    Reconstruct proofs of eprover in Agda-EProver
+  \item
+    Support more versions of GHC in Athena
+  \end{itemize}
+
+\end{frame}
+
 \begin{frame}{References}

### 2017-04-19 slides/athenatalk.tex
[ slides ] tstp, tptp explanation.

@@
   \begin{block}{Proof Assistant}
-  is a software program that work together with a human in order to give formal proofs to problems in a wide range of topics.\footnote{Matita development team, Matita website, http://matita.cs.unibo.it/index.shtml}
+    is a software program that work together with a human in order to give formal proofs to problems in a wide range of topics.\\
+    - Agda, Isabelle/HOL, HOL Light, Coq.
   \end{block}
-  \begin{block}{ATP}
-  An \text{A}utomatic \textbf{T}heorem \textbf{P}rover is software program 
+  \begin{block}{\text{A}utomatic \textbf{T}heorem \textbf{P}rover}
+    Is software program that tries to prove conjecture based on a list of hypothesis.\\
+    - Metis, Z3, Vampire, EProver, iProver, SPSS.
   \end{block}
@@
 
-%% \begin{frame}{Agda}
-%%   A proof verified of the previous derivation output by Athena.
-%% {\footnotesize
-%%   \problemtptp[basic-4.agda]{../test/prop-pack/problems/basic/basic-4.agda}{0}
-%% }
-%% \end{frame}
+\begin{frame}{Agda}
+   A verified proof of the previous derivation output by Athena.
 
+  \begin{figure}
+    \includegraphics[scale=0.35]{basic-4}
+    \label{im:basic}
+    \caption{Type-checked Proof.}
+  \end{figure}
+
+\end{frame}
+
+\begin{frame}{Natural deduction tree}
+  $\Gamma , p \vdash p$
+\begin{proof}\hfill
+\label{basic-der}
+\begin{prooftree}
+\AxiomC{$\Gamma \vdash a_1$}
+\RightLabel{\scriptsize({\bfseries weaken $\neg\ \text{subgoal}_0$})}
+\UnaryInfC{$\Gamma, \neg\ \text{subgoal}_0\,\vdash a_1$}
+\RightLabel{\scriptsize({\bfseries canonicalize})}
+\UnaryInfC{$\Gamma, \neg\ \text{subgoal}_0\,\vdash p$}
+\AxiomC{$\Gamma \vdash p$}
+\RightLabel{\scriptsize({\bfseries assume})}
+\UnaryInfC{$\Gamma, \neg\ \text{subgoal}_0\,\vdash \neg p$}
+\RightLabel{\scriptsize({\bfseries canonicalize})}
+\UnaryInfC{$\Gamma, \neg\ \text{subgoal}_0\,\vdash \neg p$}
+\RightLabel{\scriptsize({\bfseries simplify})}
+\UnaryInfC{$\Gamma, \neg\ \text{subgoal}_0\,\vdash \neg p$}
+\BinaryInfC{$\bot$}
+\RightLabel{\scriptsize({\bfseries RAA})}
+\UnaryInfC{$\Gamma \vdash p$}
+\end{prooftree}
+% A tree deduction of problem \ref{prob1}
+\end{proof}
+\end{frame}
 % The tool : Athena.

### 2017-04-21 slides/slides.tex
[ slides ] playing with fonts.

--- 2017-04-19 slides/athenatalk.tex
@@
-\documentclass[hyperref={pdfpagelabels=false}]{beamer}
+\documentclass[xetex, mathserif, serif,hyperref={pdfpagelabels=false}]{beamer}
+
+% --------------------------------------------------------------------------
+% Color definitions.
+% --------------------------------------------------------------------------
+\usepackage{xcolor}
+\definecolor{amethyst}{rgb}{0.6, 0.4, 0.8}
+\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
+\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
+\definecolor{blue(munsell)}{rgb}{0.0, 0.5, 0.69}
+\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
+\definecolor{blu}{RGB}{1,0,102}
+\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
+\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
+\definecolor{cadet}{rgb}{0.33, 0.41, 0.47}
+\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
+\definecolor{amber}{rgb}{1.0, 0.75, 0.0}
+\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
+% --------------------------------------------------------------------------
+
+% --------------------------------------------------------------------------
+% Beamer configuration.
+% --------------------------------------------------------------------------
+\usetheme{default}
+\usecolortheme{default}
 \beamertemplatenavigationsymbolsempty
-\usepackage[utf8x]{inputenc}
+\hypersetup{pdfpagemode=UseNone}
+
+\setbeamertemplate{footline}{
+  \leavevmode%
+  \hbox{%
+  \begin{beamercolorbox}[wd=.8\paperwidth,ht=2.25ex,dp=1ex,left]{headFoot}%
+    \hspace*{2ex}\insertshorttitle
+  \end{beamercolorbox}%
+  \begin{beamercolorbox}[wd=.2\paperwidth,ht=2.25ex,dp=1ex,right]{headFoot}%
+    \insertframenumber{}/\inserttotalframenumber\hspace*{2ex}
+  \end{beamercolorbox}}%
+  \vskip0pt%
+}
+
+\setbeamercolor{headFoot}{fg=gray,bg=aliceblue}
+\setbeamercolor{institute}{fg=blu}
+\setbeamercolor{normal text}{fg=blu}
+\setbeamercolor{subtitle}{fg=blu}
+\setbeamercolor{titlelike}{fg=blu}
+\setbeamerfont{footnote}{size=\tiny}
+\setbeamercolor{block title}{bg=blue,fg=blu}
+\setbeamercolor{block body}{bg=aliceblue}
+\setbeamercolor{item}{fg=blu} % color of bullets
+\setbeamercolor{subitem}{fg=blu}
+\setbeamercolor{itemize/enumerate subbody}{fg=blu}
+\setbeamertemplate{itemize subitem}{{\textendash}}
+\setbeamerfont{itemize/enumerate subbody}{size=\footnotesize}
+\setbeamerfont{itemize/enumerate subitem}{size=\footnotesize}
+% --------------------------------------------------------------------------
+
+\usepackage[english]{babel}
 \usepackage{amsmath, amsthm, amssymb}
-%\usepackage{bm}
 \usepackage{bussproofs}
+\usepackage{geometry}
 \usepackage{graphicx}
-\usepackage{listings}
 \usepackage{lmodern}
 \usepackage{url}
-\usepackage[T1]{fontenc}
+\usepackage{lstagda}
 
-\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
-\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
-\definecolor{cadet}{rgb}{0.33, 0.41, 0.47}
+\usefonttheme{professionalfonts}
+\usefonttheme{serif}
+\usepackage{fontspec}
+\setmainfont[ExternalLocation=fonts/
+  , BoldFont=Vollkorn-Bold.ttf
+  , ItalicFont=Vollkorn-Italic.ttf
+  , BoldItalicFont=Vollkorn-BoldItalic.ttf
+  ]{Vollkorn-Regular.ttf}
 
-\lstset{
-    aboveskip=10pt
-  , backgroundcolor=\color{aliceblue}
-  , basicstyle=\ttfamily
-  , belowskip=9pt
-  , frame=trbl
-  , keywords=[2]{axiom, conjecture,inference, negated_conjecture, plain}
-  , keywords=[3]{fof, cnf}
-  , keywords=[4]{canonicalize, resolve, conjunct, strip, simplify, negate, clausify}
-  , keywordstyle=[2]\color{cadet}%\underbar,%\bfseries
-  , keywordstyle=[3]\color{bondiblue}\bfseries
-  , keywordstyle=[4]\bfseries
-  , showstringspaces=false
-}
+\usepackage{mathtools}
+\usepackage{unicode-math}
 
-\newcommand{\problemtptp}[3][c]{\lstinputlisting[caption=#2, firstline=#3, label=custom#1]{#2}}
-\newcommand{\solutiontstp}[2][c]{\lstinputlisting[caption=#2, firstline=5, label=custom#1]{#2}}
+%\setmainfont{xits-regular.otf}
+\setmathfont{xits-mathbold.otf}
+
+\newfontfamily\SourceCode{SourceCodePro-Semibold.ttf}
+\newfontfamily\SourceCodeIt{SourceCodePro-It.ttf}
+\setmonofont{SourceCodePro-Semibold.ttf}
+
+\newcommand{\problemtptp}[3][c]{\lstinputlisting[style=tptp,caption=#2, firstline=#3, label=custom#1]{#2}}
+\newcommand{\solutiontstp}[2][c]{\lstinputlisting[style=tptp,caption=#2, firstline=5, label=custom#1]{#2}}
 
 \title{Proof Reconstruction with Athena\\(Work in Progress)}
-
 \date{Agda Implementors’ Meeting XXV}
-
 \author{Jonathan Prieto-Cubides}

### 2017-04-23 slides/slides.tex
[ slides ] tptp, and tstp slides added.

--- 2017-04-18 slides/athenatalk.tex
@@
-\documentclass[hyperref={pdfpagelabels=false}]{beamer}
-\beamertemplatenavigationsymbolsempty
-\usepackage[utf8x]{inputenc}
-\usepackage{amsmath, amsthm, amssymb}
-%\usepackage{bm}
-\usepackage{bussproofs}
-\usepackage{graphicx}
-\usepackage{listings}
-\usepackage{lmodern}
-\usepackage{url}
-\usepackage[T1]{fontenc}
+\documentclass[xetex,hyperref={pdfpagelabels=false}]{beamer}
 
+% --------------------------------------------------------------------------
+% Color definitions.
+% --------------------------------------------------------------------------
+\usepackage{xcolor}
 \definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
+\definecolor{amber}{rgb}{1.0, 0.75, 0.0}
+\definecolor{amethyst}{rgb}{0.6, 0.4, 0.8}
+\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
+\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
+\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
+\definecolor{blue(munsell)}{rgb}{0.0, 0.5, 0.69}
+\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
+\definecolor{blu}{RGB}{1,0,102}
 \definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
+\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
 \definecolor{cadet}{rgb}{0.33, 0.41, 0.47}
 
-\lstset{
-    aboveskip=10pt
-  , backgroundcolor=\color{aliceblue}
-  , basicstyle=\ttfamily
-  , belowskip=9pt
-  , frame=trbl
-  , keywords=[2]{axiom, conjecture,inference, negated_conjecture, plain}
-  , keywords=[3]{fof, cnf}
-  , keywords=[4]{canonicalize, resolve, conjunct, strip, simplify, negate, clausify}
-  , keywordstyle=[2]\color{cadet}%\underbar,%\bfseries
-  , keywordstyle=[3]\color{bondiblue}\bfseries
-  , keywordstyle=[4]\bfseries
-  , showstringspaces=false
+% --------------------------------------------------------------------------
+% My palette.
+% --------------------------------------------------------------------------
+\definecolor{energy}{RGB}{49,247,250}
+\definecolor{delicate}{RGB}{67,179,223}
+\definecolor{faded}{RGB}{76,117,195}
+\definecolor{plum}{RGB}{87,78,164}
+\definecolor{petunias}{RGB}{109,80,139}
+% --------------------------------------------------------------------------
+
+% --------------------------------------------------------------------------
+% Beamer configuration.
+% --------------------------------------------------------------------------
+\usetheme{default}
+\usecolortheme{default}
+\usefonttheme{serif}
+
+\beamertemplatenavigationsymbolsempty
+\setbeamertemplate{navigation symbols}{}
+\hypersetup{pdfpagemode=UseNone}
+
+% footer.
+\setbeamercolor{headFoot}{fg=white, bg=plum!80!black}
+\setbeamertemplate{footline}{
+  \leavevmode%
+  \hbox{%
+  \begin{beamercolorbox}
+    [wd=.8\paperwidth,ht=2.3ex,dp=1ex,left]{headFoot}%
+    \hspace*{2ex}\insertshorttitle\hspace*{2mm}(\insertshortauthor)
+  \end{beamercolorbox}%
+  \begin{beamercolorbox}
+    [wd=.2\paperwidth,ht=2.3ex,dp=1ex,right]{headFoot}%
+    \insertframenumber{}/\inserttotalframenumber\hspace*{2ex}
+  \end{beamercolorbox}}%
+  \vskip0pt%
 }
 
-\newcommand{\problemtptp}[3][c]{\lstinputlisting[caption=#2, firstline=#3, label=custom#1]{#2}}
-\newcommand{\solutiontstp}[2][c]{\lstinputlisting[caption=#2, firstline=5, label=custom#1]{#2}}
+% title in the frame
+\setbeamerfont{frametitle}{size=\small,series=\bfseries}
+\setbeamercolor{frametitle}{fg=white,bg=plum}
 
-\title{Proof Reconstruction with Athena\\(Work in Progress)}
+\setbeamerfont{framesubtitle}{size=\normalfont\tiny\itshape}
+\setbeamercolor{framesubtitle}{fg=white, bg=plum}
 
-\date{Agda Implementors’ Meeting XXV}
+\setbeamercolor{background canvas}{bg=white}
+\setbeamercolor{normal text}{fg=black}
 
+\setbeamercolor{institute}{fg=blu}
+% \setbeamercolor{subtitle}{fg=blu}
+% \setbeamercolor{titlelike}{fg=blu}
+% \setbeamerfont{footnote}{size=\tiny}
+% \setbeamercolor{block title}{bg=blue,fg=blu}
+% \setbeamercolor{block body}{bg=aliceblue}
+% \setbeamercolor{item}{fg=blu} % color of bullets
+% \setbeamercolor{subitem}{fg=blu}
+% \setbeamercolor{itemize/enumerate subbody}{fg=blu}
+% \setbeamertemplate{itemize subitem}{{\textendash}}
+% \setbeamerfont{itemize/enumerate subbody}{size=\footnotesize}
+% \setbeamerfont{itemize/enumerate subitem}{size=\footnotesize}
+
+% --------------------------------------------------------------------------
+
+\usepackage[english]{babel}
+\usepackage{amsmath, amsthm, amssymb}
+\usepackage{bussproofs}
+\usepackage{geometry}
+\usepackage{graphicx}
+\usepackage{lmodern}
+\usepackage{lstagda}
+\usepackage{tikz}
+\usepackage{url}
+
+\usefonttheme{professionalfonts}
+\usefonttheme{serif}
+\usepackage{fontspec}
+\usepackage{mathtools}
+\usepackage{unicode-math}
+
+\setmathfont[ExternalLocation=fonts/
+  , BoldFont=xits-mathbold.otf
+  ]{xits-math.otf}
+
+\setmainfont[ExternalLocation=fonts/
+  , BoldFont=SourceSansPro-Semibold.otf
+  , BoldItalicFont=SourceSansPro-SemiboldIt.otf
+  , ItalicFont=SourceSansPro-It.otf
+  ]{SourceSansPro-Regular.otf}
+
+\setmonofont[ExternalLocation=fonts/
+  , BoldFont=SourceCodePro-Semibold.ttf
+  , BoldItalicFont=SourceCodePro-SemiboldIt.ttf
+  , ItalicFont=SourceCodePro-It.ttf
+  ]{SourceCodePro-Semibold.ttf}
+\newfontfamily\SourceCodeIt{fonts/SourceCodePro-It.ttf}
+\newfontfamily\SourceCode{fonts/SourceCodePro-Regular.ttf}
+
+\newcommand{\problemtptp}[3][c]
+  {\lstinputlisting[style=tptp,caption=#2, firstline=#3, label=custom#1]{#2}}
+\newcommand{\solutiontstp}[2][c]
+  {\lstinputlisting[style=tptp,caption=#2, firstline=5, label=custom#1]{#2}}
+
+% --------------------------------------------------------------------------
+% Title Page
+\title{\textbf{Proof Reconstruction in Classical Propositional Logic}}
+\date{Agda Implementors’ Meeting XXV\\
+May 9-15th
+}
 \author{Jonathan Prieto-Cubides}
@@
 Advisor: Andr\'es Sicard-Ram\'irez\\[3mm]
-EAFIT University\\
+Universidad EAFIT\\
 Medell\'in, Colombia}
+% --------------------------------------------------------------------------
 
@@
 \setcounter{page}{1}
-\maketitle
 
-% Context
-% - SledgeHammer
-% - Metis
-% - Problem with Wallmeinster finding the code.
-% - equinox (intuisionistic version)
-
-\begin{frame}{Keywords}
-  \begin{block}{Proof Assistant}
-  is a software program that work together with a human in order to give formal proofs to problems in a wide range of topics.\footnote{Matita development team, Matita website, http://matita.cs.unibo.it/index.shtml}
-  \end{block}
-  \begin{block}{ATP}
-  An \text{A}utomatic \textbf{T}heorem \textbf{P}rover is software program 
-  \end{block}
+\begin{frame}[plain]
+  \titlepage
 \end{frame}
 
-\begin{frame}{Athena}
-  Is a Haskell program that translates proofs given by Metis ATP in TSTP format
-  to Agda code.
-
-  \begin{figure}
-    \includegraphics[scale=0.85]{diagram.pdf}
-    \label{im:athena}
-    \caption{Proof reconstruction work flow.}
-  \end{figure}
+\begin{frame}
+  \frametitle{Outline}
+  \tableofcontents
 \end{frame}
 
-\begin{frame}{TPTP}
-  Is a text format to encode problems in different theories. Its goal is provide
-  a standard for all ATPs in the input file format. The version for derivations
-  is named TSTP but this one is not a standard yet.\\[2mm]
+\section{Introduction}
+\subsection{Motivation}
 
-  A TPTP file looks like:
+\begin{frame}
+Proof Term Reconstruction
 
-  \problemtptp[basic-4.tptp]{../test/prop-pack/problems/basic/basic-4.tptp}{2}
+At the moment, the communication between Agda and
+the ATPs is unidirectional because we use the ATPs as oracles
 
@@
 
-\begin{frame}{TSTP}
-  A derivation of the previous problem output by Metis ATP.
-{\footnotesize
-  \problemtptp[basic-4.tstp]{../test/prop-pack/problems/basic/basic-4.tstp}{0}
-}
+% \subsection{Proof Reconstruction}
+
+% \subsubsection{Sledgehammer}
+% \subsubsection{Waldemesiter}
+
+\subsection{Automatic Provers}
+
+\subsubsection{TPTP Syntax}
+
+\begin{frame}[fragile]{TPTP Syntax}{Thousands of Problems for Theorem Provers}
+
+ \tikz[overlay,remember picture]
+  \node at (0.92\textwidth, 0cm)
+    {\includegraphics[width=0.15\textwidth]{figures/tptp}};
+
+  \begin{itemize}
+  \item Is a language\footnote{Is available at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} to encode problems in text files
+  \item Is the input of the ATPs
+  \item his problems contains formulas with the form
+   \begin{center}
+\begin{verbatim}
+language(name, role, formula).
+\end{verbatim}
+    \end{center}
+    \begin{itemize}
+      \item[\texttt{language}] THF, TFF, FOF, or CNF
+      \item[\texttt{name}] to identify the formula within the problem
+      \item[\texttt{role}] axiom, definition, hypothesis, conjecture, among others
+      \item[\texttt{formula}] the logic formula in the language
+    \end{itemize}
+  \end{itemize}
 \end{frame}
 
-%% \begin{frame}{Agda}
-%%   A proof verified of the previous derivation output by Athena.
-%% {\footnotesize
-%%   \problemtptp[basic-4.agda]{../test/prop-pack/problems/basic/basic-4.agda}{0}
-%% }
-%% \end{frame}
+\begin{frame}[fragile]{TPTP Examples}{Prop-Pack Repository}
+Problems in Propositional Logic:
+  \begin{itemize}
+    \item $p ⊢ p$
+\begin{tptp}
+$ cat basic-4.tptp
+fof(a, axiom, p).
+fof(goal, conjecture, p).
+\end{tptp}
+    \item $p ∧ q ⊢ q ∧ p$
+\begin{tptp}
+$ cat conj-3.tptp
+fof(a, axiom, p & q).
+fof(goal, conjecture, q & p).
+\end{tptp}
+    \item $⊢ ¬ (p ∧ ¬ p) ∨ (q ∧ ¬ q)$
+\begin{tptp}
+$ cat neg-7.tptp
+fof(goal, conjecture, ~ ((p & ~ p) | (q & ~ q))).
+\end{tptp}
+    \end{itemize}
+\end{frame}
 
-% The tool : Athena.
-% Its components:
-% - agda-prop (logic framework)
-% - agda-metis (ATP rules)
-% - prop-pack (problems)
+\subsubsection{TSTP Derivations}
 
-\begin{frame}{Future work}
+\begin{frame}[fragile]{TSTP Syntax}
+ \tikz[overlay,remember picture]
+  \node at (0.92\textwidth, -0.5cm)
+    {\includegraphics[width=0.15\textwidth]{figures/tstp}};
+
+A TSTP derivation\footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/QuickGuide/Derivations.html}}
+\begin{itemize}
+  \item Is a Directed Acyclic Graph where
+  \begin{itemize}
+    \item[\texttt{leaf}] is a formulae from the TPTP input
+    \item[\texttt{node}] is a formulae inferred from parent formulae
+    \item[\texttt{root}] the final derived formulae
+  \end{itemize}
+  \item Is a list of annotated formulae:
+  {\footnotesize
+    \begin{center}
+\begin{verbatim}
+language(name,role,formula,source[,useful info]).
+\end{verbatim}
+  \end{center}}
+\begin{itemize}
+  \item[\texttt{source}] typically is a inference record:
+  {\footnotesize \begin{verbatim}
+  inference(rule, [], [])
+  \end{verbatim}}
+  % Where each slot corresponds to
+\begin{itemize}
+    \item[-] The inference rule name,
+    \item[-] a list of useful inference information, and
+    \item[-] a list of references to its parent formulae.
+\end{itemize}
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]{TSTP Example}
+ \tikz[overlay,remember picture]
+  \node at (0.93\textwidth, -0.3cm)
+    {\includegraphics[width=0.15\textwidth]{figures/metis}};
 
 \begin{itemize}
-  \item
-    Extend the libraries Agda-Prop and Agda-Metis to handle predicated logic
-  \item
-    Reconstruct proofs of eprover in Agda-EProver
-  \item
-    Support more versions of GHC in Athena
+  \item Proof found by \texttt{Metis} ATP for the problem $p ⊢ p$
+\begin{tptp}
+$ metis --show proof basic-4.tptp
+fof(a, axiom, (p)).
+fof(goal, conjecture, (p)).
+fof(subgoal_0, plain, (p),
+  inference(strip, [], [goal])).
+fof(negate_0_0, plain, (~ p),
+  inference(negate, [], [subgoal_0])).
+fof(normalize_0_0, plain, (~ p),
+  inference(canonicalize, [], [negate_0_0])).
+fof(normalize_0_1, plain, (p),
+  inference(canonicalize, [], [a])).
+fof(normalize_0_2, plain, ($false),
+  inference(simplify, [],
+    [normalize_0_0, normalize_0_1])).
+cnf(refute_0_0, plain, ($false),
+  inference(canonicalize, [], [normalize_0_2])).
+\end{tptp}
 \end{itemize}
-
 \end{frame}
 
-\begin{frame}{References}
-
+\begin{frame}[fragile]{DAG for the previous TSTP derivation found by \texttt{Metis} ATP}
+\vfill
+\begin{center}
+\includegraphics[height=0.8\textheight]{figures/derivation.png}
+\end{center}
 \end{frame}

### 2017-04-24 slides/ideas.tex
[ slides ] diagrams added.

--- 2017-04-19 slides/athenatalk.tex
@@
-\documentclass[hyperref={pdfpagelabels=false}]{beamer}
-\beamertemplatenavigationsymbolsempty
-\usepackage[utf8x]{inputenc}
-\usepackage{amsmath, amsthm, amssymb}
-%\usepackage{bm}
-\usepackage{bussproofs}
-\usepackage{graphicx}
-\usepackage{listings}
-\usepackage{lmodern}
-\usepackage{url}
-\usepackage[T1]{fontenc}
+\begin{frame}{Keywords}
 
-\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
-\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
-\definecolor{cadet}{rgb}{0.33, 0.41, 0.47}
+ \tikz[overlay,remember picture]
+  \node[opacity=0.2]at (0.8\textwidth, 0.5cm)
+    {\includegraphics[width=0.3\textwidth]{figures/metis}};
 
-\lstset{
-    aboveskip=10pt
-  , backgroundcolor=\color{aliceblue}
-  , basicstyle=\ttfamily
-  , belowskip=9pt
-  , frame=trbl
-  , keywords=[2]{axiom, conjecture,inference, negated_conjecture, plain}
-  , keywords=[3]{fof, cnf}
-  , keywords=[4]{canonicalize, resolve, conjunct, strip, simplify, negate, clausify}
-  , keywordstyle=[2]\color{cadet}%\underbar,%\bfseries
-  , keywordstyle=[3]\color{bondiblue}\bfseries
-  , keywordstyle=[4]\bfseries
-  , showstringspaces=false
-}
-
-\newcommand{\problemtptp}[3][c]{\lstinputlisting[caption=#2, firstline=#3, label=custom#1]{#2}}
-\newcommand{\solutiontstp}[2][c]{\lstinputlisting[caption=#2, firstline=5, label=custom#1]{#2}}
-
-\title{Proof Reconstruction with Athena\\(Work in Progress)}
-
-\date{Agda Implementors’ Meeting XXV}
-
-\author{Jonathan Prieto-Cubides}
-
-\institute{
-Advisor: Andr\'es Sicard-Ram\'irez\\[3mm]
-EAFIT University\\
-Medell\'in, Colombia}
-
-\begin{document}
-
-\setcounter{page}{1}
-\maketitle
-
-% Context
-% - SledgeHammer
-% - Metis
-% - Problem with Wallmeinster finding the code.
-% - equinox (intuisionistic version)
-
-\begin{frame}{Keywords}
   \begin{block}{Proof Assistant}
-    is a software program that work together with a human in order to give formal proofs to problems in a wide range of topics.\\
+    Is a software program that work together with a human in order to give formal proofs to problems in a wide range of topics.\\
     - Agda, Isabelle/HOL, HOL Light, Coq.
@@
 
-\begin{frame}{Athena}
+\begin{frame}{Athena}{asdf}
   Is a Haskell program that translates proofs given by Metis ATP in TSTP format
@@
   \begin{figure}
-    \includegraphics[scale=0.85]{diagram.pdf}
+    \includegraphics[scale=0.85]{figures/diagram.pdf}
     \label{im:athena}
@@
 \end{frame}
-
-\begin{frame}{References}
-
-\end{frame}
-
-\end{document}

### 2017-04-24 slides/slides.tex
[ slides ] diagrams added.

@@
 \definecolor{petunias}{RGB}{109,80,139}
+\definecolor{letour}{RGB}{101,41,105}
+
 % --------------------------------------------------------------------------
@@
 
-\setbeamercolor{institute}{fg=blu}
+% \setbeamercolor{institute}{fg=blu}
 % \setbeamercolor{subtitle}{fg=blu}
 % \setbeamercolor{titlelike}{fg=blu}
-% \setbeamerfont{footnote}{size=\tiny}
+\setbeamerfont{footnote}{size=\tiny}
+\setbeamercolor{footnote}{fg=gray}
 % \setbeamercolor{block title}{bg=blue,fg=blu}
@@
 \usepackage{bussproofs}
+\usepackage{fancyvrb}
 \usepackage{geometry}
@@
 % --------------------------------------------------------------------------
+% References
+\usepackage[autostyle]{csquotes}
+\usepackage[
+    backend=biber
+  , style=authoryear-icomp
+  , sortlocale=en_US
+  , natbib=true
+  , url=false
+  , doi=true
+  , eprint=false
+]{biblatex}
+\addbibresource{ref.bib}
+\renewcommand*{\nameyeardelim}{\addcomma\addspace}
+\usepackage{silence}
+\WarningFilter{biblatex}{Patching footnotes failed}
+
+% --------------------------------------------------------------------------
 % Title Page
@@
 \date{Agda Implementors’ Meeting XXV\\
-May 9-15th
-}
+May 9-15th}
 \author{Jonathan Prieto-Cubides}
@@
 
+\newsavebox\agdapragma
+
 \begin{document}
@@
 \begin{frame}[plain]
+% \tikz[overlay,remember picture] \node[opacity=0.05, at=(6,6)] {
+% $Γ ⊢ ϕ$
+% };
 \titlepage
@@
 
-\begin{frame}
-Proof Term Reconstruction
+\begin{lrbox}{\agdapragma}
+\begin{lstlisting}
+$ cat Or.agda
+module Or where
 
-At the moment, the communication between Agda and
-the ATPs is unidirectional because we use the ATPs as oracles
+data _or_ (A B : Set) : Set where
+  inj1 : A -> A or B
+  inj2 : B -> A or B
+
+postulate
+  A B    : Set
+  or-comm : A or B -> B or A
+{-# ATP prove or-comm #-}
+\end{lstlisting}
+\end{lrbox}
+
+\begin{frame}[fragile]{Translation}
+
+\only<1-2>{At the moment, the communication between Agda and
+the ATPs is unidirectional because the ATPs are being used as oracles.\citep{Sicard2015}.}
+\only<1-2>{\vfill}
+
+\begin{tikzpicture}[scale=2]
+\only<1->{ \node(agda-pragmas) at (0,0){\includegraphics{figures/agda-pragmas.pdf}}};
+\only<1>{
+  \node[fill=aliceblue, rectangle](atp-pragma) at (3,0){
+  \scalebox{0.7}{\usebox\agdapragma}
+  }};
+
+\only<2->{ \node(eagda) at (2,0){
+  \includegraphics{figures/eagda.pdf}
+  \footnote{Development version of Agda in order to handle a new built-in ATP-pragma.
+    \url{https://github.com/asr/eagda}}
+  }};
+
+\only<3->{ \node(apia) at (4,0){
+  \includegraphics{figures/apia.pdf}
+  \footnote{Haskell program for proving first-order theorems written in Agda using ATPs.
+    \url{https://github.com/asr/apia}}}
+  };
+
+\only<3->{ \node(tptp) at (2,-2){\includegraphics{figures/tptp.pdf}}};
+
+\only<3->{ \node(atp) at (4,-2){\includegraphics{figures/atp.pdf}}};
+
+\only<2->{\draw[->,ultra thick] (agda-pragmas) to (eagda)};
+
+\only<3->{\draw[->,ultra thick] (eagda) to (apia)};
+\only<3->{\draw[->, very thick, dashed, gray] (apia) to (tptp)};
+\only<3->{\draw[->, very thick, dashed, gray] (tptp) to (atp)};
+\only<3->{\draw[->, very thick, dashed, gray] (atp) to (apia)};
+
+\end{tikzpicture}
 
@@
 \begin{frame}[fragile]{TPTP Syntax}{Thousands of Problems for Theorem Provers}
-
+\label{tptp-syntax}
  \tikz[overlay,remember picture]
@@
   \begin{itemize}
-  \item Is a language\footnote{Is available at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} to encode problems in text files
+  \item Is a language\footnote{Is available at
+        \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}}
+        to encode problems in text files
   \item Is the input of the ATPs
@@
 \begin{frame}[fragile]{TPTP Examples}{Prop-Pack Repository}
+\label{tptp-examples}
 Problems in Propositional Logic:
@@
 \begin{frame}[fragile]{TSTP Syntax}
+\label{tstp-syntax}
  \tikz[overlay,remember picture]
@@
 
-A TSTP derivation\footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/QuickGuide/Derivations.html}}
+A TSTP derivation
+\footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/QuickGuide/Derivations.html}}
 \begin{itemize}
@@
   \item[\texttt{source}] typically is a inference record:
-  {\footnotesize \begin{verbatim}
+    {\footnotesize
+\begin{verbatim}
   inference(rule, [], [])
   \end{verbatim}}
-  % Where each slot corresponds to
 \begin{itemize}
@@
 \begin{frame}[fragile]{TSTP Example}
+\label{tstp-example}
  \tikz[overlay,remember picture]
@@
 \begin{frame}[fragile]{DAG for the previous TSTP derivation found by \texttt{Metis} ATP}
+\label{tstp-dag}
 \vfill
@@
 
+\begin{frame}{Design decisions for the Reconstruction Tool}
+\label{agda}
+
+ \tikz[overlay,remember picture]
+  \node at (0.93\textwidth, 0cm)
+    {\includegraphics[width=0.2\textwidth]{figures/athena}};
+
+\textbf{Programming Languages}
+\begin{itemize}
+\item \texttt{Haskell} is a standardized, general-purpose purely functional programming language.\\
+Our usages:
+\begin{itemize}
+    \item Parsing
+    \item AST construction
+    \item Creation and analysis of DAG derivations
+    \item Analysis of inference rules used
+    \item Generation of Agda code of the proof
+\end{itemize}
+
+\item \texttt{Agda} is dependently typed functional programming language and it also a proof assistant.\\
+Our usages:
+    \begin{itemize}
+    \item Logic framework for Classical Propositional Logic
+    \item Type-Checker for the Agda code of the proofs generated
+    \end{itemize}
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{References}
+\label{references}
+\printbibliography
+\end{frame}
+
 \end{document}

### 2017-04-24 slides/slides.tex
[ slides ] clickeable items in the diagram.

@@
-\documentclass[xetex,hyperref={pdfpagelabels=false}]{beamer}
+\documentclass[xetex, hyperref={pdfpagelabels=false}]{beamer}
 
@@
 % \setbeamercolor{institute}{fg=blu}
+\setbeamercolor{title}{fg=plum}
 % \setbeamercolor{subtitle}{fg=blu}
+
 % \setbeamercolor{titlelike}{fg=blu}
@@
 \usepackage{lmodern}
-\usepackage{lstagda}
+\usepackage{mylst}
 \usepackage{tikz}
+\usetikzlibrary{positioning}
+\usetikzlibrary{calc}
+
 \usepackage{url}
@@
 \begin{document}
-
 \setcounter{page}{1}
 
-\begin{frame}[plain]
-% \tikz[overlay,remember picture] \node[opacity=0.05, at=(6,6)] {
-% $Γ ⊢ ϕ$
-% };
+\tikzset{
+    hyperlink node/.style={
+        alias=sourcenode,
+        append after command={
+            let     \p1 = (sourcenode.north west),
+                \p2=(sourcenode.south east),
+                \n1={\x2-\x1},
+                \n2={\y1-\y2} in
+            node [inner sep=0pt, outer sep=0pt,anchor=north west,at=(\p1)] {\hyperlink{#1}{\XeTeXLinkBox{\phantom{\rule{\n1}{\n2}}}}}
+                    %xelatex needs \XeTeXLinkBox, won't create a link unless it
+                    %finds text --- rules don't work without \XeTeXLinkBox.
+                    %Still builds correctly with pdflatex and lualatex
+        }
+    }
+}
+
+\begin{frame}
 \titlepage
+\begin{tikzpicture}[overlay,remember picture, scale=0.5]
+\foreach \x in {0,4,..., \textwidth}
+  \foreach \y in {0,1,..., 20} {
+    \node[opacity=0.05](tptp) at (\x,\y){$Γ ⊢ ϕ$};
+  }
+\end{tikzpicture}
 \end{frame}
@@
 \section{Introduction}
+
+\begin{frame}[fragile, label=reconstruction]{Proof Reconstruction}
+
+\begin{tikzpicture}
+\node(problem) at (0,0)
+   {\includegraphics[scale=0.7]{figures/problem}};
+
+\node[right = 0.8cm of problem, hyperlink node=tptp-syntax](tptp){
+\includegraphics[scale=0.7]{figures/tptp}
+};
+
+\node[right= 0.8cm of tptp, hyperlink node=metis] (metis)
+  {\includegraphics[scale=0.7]{figures/metis}};
+
+\node[right= 0.8cm of metis, hyperlink node=tstp-syntax] (tstp)
+  {\includegraphics[scale=0.7]{figures/tstp}};
+
+\node[below= 2cm of tstp, hyperlink node=athena] (athena)
+  {\includegraphics[scale=0.7]{figures/athena}};
+
+\node[left = 0.5cm of athena, hyperlink node=agda-file] (agdafile)
+  {\includegraphics[scale=0.7]{figures/agdafile}};
+
+\node[left = 0.5cm of agdafile, hyperlink node=agda] (agda)
+  {\includegraphics[scale=0.7]{figures/agda}};
+
+\node[below = 0.2cm of problem, hyperlink node=verified-example] (verified)
+  {\includegraphics[scale=0.7]{figures/verified}};
+
+\node[below = 0.2cm of verified, opacity=0.5] (failure)
+  {\includegraphics[scale=0.7]{figures/failure}};
+
+\draw[->, thick] (problem) to (tptp);
+\draw[->, thick] (tptp) to (metis);
+\draw[->, thick] (metis) to (tstp);
+\draw[->, thick] (tstp) to (athena);
+\draw[->, thick] (athena) to (agdafile);
+\draw[->, thick] (agdafile) to (agda);
+\draw[->, thick] (agda) to (verified);
+\draw[->, thick, gray] (agda) to (failure);
+\end{tikzpicture}
+\vfill
+\end{frame}
+
 \subsection{Motivation}
@@
 
-\begin{frame}[fragile]{Translation}
+\begin{frame}[fragile]{Previous Work: Apia}{Proving first-order theorems written in Agda using automatic theorem provers for first-order logic}
 
 \only<1-2>{At the moment, the communication between Agda and
-the ATPs is unidirectional because the ATPs are being used as oracles.\citep{Sicard2015}.}
+the ATPs is unidirectional because the ATPs are being used as oracles \citep{Sicard2015}.}
 \only<1-2>{\vfill}
@@
 \begin{tikzpicture}[scale=2]
-\only<1->{ \node(agda-pragmas) at (0,0){\includegraphics{figures/agda-pragmas.pdf}}};
+\only<1->{ \node(agda-pragmas) at (0,0){\includegraphics{figures/agda-pragmas}}};
 \only<1>{
@@
 \only<2->{ \node(eagda) at (2,0){
-  \includegraphics{figures/eagda.pdf}
+  \includegraphics{figures/eagda}
   \footnote{Development version of Agda in order to handle a new built-in ATP-pragma.
@@
 \only<3->{ \node(apia) at (4,0){
-  \includegraphics{figures/apia.pdf}
+  \includegraphics{figures/apia}
   \footnote{Haskell program for proving first-order theorems written in Agda using ATPs.
@@
 
-\only<3->{ \node(tptp) at (2,-2){\includegraphics{figures/tptp.pdf}}};
+\only<3->{ \node(tptp) at (2,-2){\includegraphics{figures/tptp}}};
 
-\only<3->{ \node(atp) at (4,-2){\includegraphics{figures/atp.pdf}}};
+\only<3->{ \node(atp) at (4,-2){\includegraphics{figures/atp}}};
 
@@
 
-\subsection{Automatic Provers}
+% \subsection{Automatic Provers}
 
-\subsubsection{TPTP Syntax}
+% \subsubsection{TPTP Syntax}
 
-\begin{frame}[fragile]{TPTP Syntax}{Thousands of Problems for Theorem Provers}
-\label{tptp-syntax}
+\begin{frame}{}
+{\Huge Bonus Slides}
+\end{frame}
+
+\begin{frame}[fragile, label=tptp-syntax]{TPTP Syntax}{Thousands of Problems for Theorem Provers}
+
  \tikz[overlay,remember picture]
@@
     \begin{itemize}
-      \item[\texttt{language}] THF, TFF, FOF, or CNF
+      \item[\texttt{language}] FOF, or CNF %THF, TFF,
       \item[\texttt{name}] to identify the formula within the problem
@@
   \end{itemize}
+
+\hyperlink{reconstruction}{Go to Reconstruction}
 \end{frame}
 
-\begin{frame}[fragile]{TPTP Examples}{Prop-Pack Repository}
+\begin{frame}[fragile]{TPTP Examples}{From Prop-Pack repository\footnote{Is available at \url{http://github.com/jonaprieto/pro-pack}}}
 \label{tptp-examples}
@@
 
-\begin{frame}[fragile]{TSTP Syntax}
-\label{tstp-syntax}
+\begin{frame}[fragile, label=tstp-syntax]{TSTP Syntax}
+
  \tikz[overlay,remember picture]
@@
   \item Is a list of annotated formulae:
-  {\footnotesize
+  \end{itemize}
+
 \begin{center}
-\begin{verbatim}
-language(name,role,formula,source[,useful info]).
-\end{verbatim}
-  \end{center}}
-\begin{itemize}
-  \item[\texttt{source}] typically is a inference record:
   {\footnotesize
 \begin{verbatim}
-  inference(rule, [], [])
+language(name, role, formula, source [,useful info]).
 \end{verbatim}}
-\begin{itemize}
-    \item[-] The inference rule name,
-    \item[-] a list of useful inference information, and
-    \item[-] a list of references to its parent formulae.
-\end{itemize}
-\end{itemize}
-\end{itemize}
+\end{center}
+
+where \textbf{source} typically is a inference record:
+\begin{center}
+{\footnotesize
+\begin{verbatim}
+inference(rule, useful information, parents)
+\end{verbatim}
+}
+\end{center}
+
 \end{frame}
 
-\begin{frame}[fragile]{TSTP Example}
-\label{tstp-example}
+\begin{frame}[fragile, label=tstp-example]{TSTP Example}
+
  \tikz[overlay,remember picture]
@@
 
-\begin{frame}[fragile]{DAG for the previous TSTP derivation found by \texttt{Metis} ATP}
-\label{tstp-dag}
+\begin{frame}[fragile, label=tstp-dag]{DAG for the previous TSTP derivation found by \texttt{Metis} ATP}
+
 \vfill
@@
 
-\begin{frame}{Design decisions for the Reconstruction Tool}
-\label{agda}
-
+\begin{frame}[label=haskell]{Design Decisions for the Reconstruction Tool}
  \tikz[overlay,remember picture]
@@
 
-\textbf{Programming Languages}
-\begin{itemize}
-\item \texttt{Haskell} is a standardized, general-purpose purely functional programming language.\\
-Our usages:
+\texttt{Haskell} % is a standardized, general-purpose purely functional programming language.\\ Our usages: 
 \begin{itemize}
@@
 \end{itemize}
+\end{frame}
 
-\item \texttt{Agda} is dependently typed functional programming language and it also a proof assistant.\\
+\begin{frame}[label=agda]{Design Decisions for the Reconstruction Tool}{Programming Languages}
+\texttt{Agda} is a dependently typed functional programming language and it also a proof assistant.\\
 Our usages:
@@
     \end{itemize}
-\end{itemize}
 
@@
 
-\begin{frame}{References}
+\begin{frame}[label=references]{References}
 \label{references}

### 2017-04-25 slides/slides.tex

@@
 \documentclass[xetex, hyperref={pdfpagelabels=false}]{beamer}
+
+% --------------------------------------------------------------------------
+% Packages
+% --------------------------------------------------------------------------
+\usepackage[english]{babel}
+\usepackage{amsmath, amsthm, amssymb}
+\usepackage{bussproofs}
+\usepackage{fancyvrb}
+\usepackage{geometry}
+\usepackage{graphicx}
+\usepackage{lmodern}
+\usepackage{mylst}
+\usepackage{url}
+
+% --------------------------------------------------------------------------
+% Tikz Configuration
+% --------------------------------------------------------------------------
+\usepackage{tikz}
+\usetikzlibrary{positioning}
+\usetikzlibrary{calc}
+\usepackage{rotating}
+
+\tikzset{
+    hyperlink node/.style={
+        alias=sourcenode,
+        append after command={
+            let     \p1 = (sourcenode.north west),
+                \p2=(sourcenode.south east),
+                \n1={\x2-\x1},
+                \n2={\y1-\y2} in
+            node [inner sep=0pt, outer sep=0pt,anchor=north west,at=(\p1)]
+            {\hyperlink{#1}{\XeTeXLinkBox{\phantom{\rule{\n1}{\n2}}}}}
+                    %xelatex needs \XeTeXLinkBox, won't create a link unless it
+                    %finds text --- rules don't work without \XeTeXLinkBox.
+                    %Still builds correctly with pdflatex and lualatex
+        }
+    }
+}
+% \usetikzlibrary{shapes.geometric,shapes.symbols,shadows}
+
+\newcommand{\gobackreconstruction}{
+  \begin{tikzpicture}[overlay, remember picture, scale=0.5]
+    \tikzset{shift={(current page.center)}, xshift=11.6cm,yshift=-8.3cm}
+    \node[fill=plum,text=white, hyperlink node = reconstruction] (go) at (0,0) {\tiny Go Back};
+  \end{tikzpicture}}
 
@@
   \end{beamercolorbox}}%
-  \vskip0pt%
+  \vskip 0pt%
+  % \vspace*{1mm}%
 }
@@
 % --------------------------------------------------------------------------
-
-\usepackage[english]{babel}
-\usepackage{amsmath, amsthm, amssymb}
-\usepackage{bussproofs}
-\usepackage{fancyvrb}
-\usepackage{geometry}
-\usepackage{graphicx}
-\usepackage{lmodern}
-\usepackage{mylst}
-\usepackage{tikz}
-\usetikzlibrary{positioning}
-\usetikzlibrary{calc}
-
-\usepackage{url}
+% Fonts
+% --------------------------------------------------------------------------
 
@@
 % References
+% --------------------------------------------------------------------------
+
 \usepackage[autostyle]{csquotes}
@@
 % --------------------------------------------------------------------------
-% Title Page
-\title{\textbf{Proof Reconstruction in Classical Propositional Logic}}
+% Title and Author
+% --------------------------------------------------------------------------
+
+\title[Proof Reconstruction in Classical Propositional Logic]
+  {\textbf{Proof Reconstruction in Classical Propositional Logic}
+}
+\subtitle{(Work in Progress)}
 \date{Agda Implementors’ Meeting XXV\\
 May 9-15th}
-\author{Jonathan Prieto-Cubides}
-
+\author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides\\
+(Joint work with Andr\'es Sicard-Ram\'irez)}
 \institute{
-Advisor: Andr\'es Sicard-Ram\'irez\\[3mm]
 Universidad EAFIT\\
@@
 
-\tikzset{
-    hyperlink node/.style={
-        alias=sourcenode,
-        append after command={
-            let     \p1 = (sourcenode.north west),
-                \p2=(sourcenode.south east),
-                \n1={\x2-\x1},
-                \n2={\y1-\y2} in
-            node [inner sep=0pt, outer sep=0pt,anchor=north west,at=(\p1)] {\hyperlink{#1}{\XeTeXLinkBox{\phantom{\rule{\n1}{\n2}}}}}
-                    %xelatex needs \XeTeXLinkBox, won't create a link unless it
-                    %finds text --- rules don't work without \XeTeXLinkBox.
-                    %Still builds correctly with pdflatex and lualatex
-        }
-    }
-}
-
-\begin{frame}
+\begin{frame}[plain]
 \titlepage
-\begin{tikzpicture}[overlay,remember picture, scale=0.5]
-\foreach \x in {0,4,..., \textwidth}
-  \foreach \y in {0,1,..., 20} {
-    \node[opacity=0.05](tptp) at (\x,\y){$Γ ⊢ ϕ$};
-  }
-\end{tikzpicture}
+% \begin{tikzpicture}[overlay,remember picture, scale=0.5]
+% \foreach \x in {0,4,..., \textwidth}
+%   \foreach \y in {0,1,..., 20} {
+%     \node[opacity=0.05](tptp) at (\x,\y){$Γ ⊢ ϕ$};
+%   }
+% \end{tikzpicture}
 \end{frame}
 
-\begin{frame}
-  \frametitle{Outline}
-  \tableofcontents
-\end{frame}
+% \begin{frame}
+%   \frametitle{Outline}
+%   \tableofcontents
+% \end{frame}
 
@@
 
-\begin{frame}[fragile, label=reconstruction]{Proof Reconstruction}
+\begin{frame}[fragile, label=reconstruction]{Proof Reconstruction: Overview}
 
 \begin{tikzpicture}
-\node(problem) at (0,0)
+\only<1->{\node(problem) at (0,0)
    {\includegraphics[scale=0.7]{figures/problem}};
+}
 
-\node[right = 0.8cm of problem, hyperlink node=tptp-syntax](tptp){
+\only<2->{\node[right = 0.8cm of problem, hyperlink node=tptp-syntax](tptp){
 \includegraphics[scale=0.7]{figures/tptp}
 };
-
+}
+\only<3->{
 \node[right= 0.8cm of tptp, hyperlink node=metis] (metis)
-  {\includegraphics[scale=0.7]{figures/metis}};
-
+  {\includegraphics[scale=0.7]{figures/metis}\,
+  \footnote{It is available at \url{http://www.gilith.com/software/metis}}
+  };
+}
+\only<4->{
 \node[right= 0.8cm of metis, hyperlink node=tstp-syntax] (tstp)
   {\includegraphics[scale=0.7]{figures/tstp}};
+}
+\only<5->{
+\node[below= 1.5cm of tstp, hyperlink node=athena] (athena)
+  {\includegraphics[scale=0.7]{figures/athena}
+  \footnote{It is available at \url{http://github.com/jonaprieto/athena}}
+  };
+}
+\only<6->{
+\node[left = 0.5cm of athena, hyperlink node=agda-file] (agdafile)
+  {\includegraphics[scale=0.7]{figures/agdafile}
+  };
+}
+\only<7->{
+\node[left = 0.5cm of agdafile, hyperlink node=agda] (agda)
+  {\includegraphics[scale=0.7]{figures/agda}
+  \footnote{It is available at \url{http://github.com/agda/agda}}
+  };
+}
+\only<8->{
+\node[below = 0.18cm of problem, hyperlink node=verified-example] (verified)
+  {\includegraphics[scale=0.7]{figures/verified}};
+}
+\only<8->{
+\node[below = 0.18cm of verified, opacity=0.5, hyperlink node=failure-example] (failure)
+  {\includegraphics[scale=0.7]{figures/failure}};
+}
 
-\node[below= 2cm of tstp, hyperlink node=athena] (athena)
-  {\includegraphics[scale=0.7]{figures/athena}};
-
-\node[left = 0.5cm of athena, hyperlink node=agda-file] (agdafile)
-  {\includegraphics[scale=0.7]{figures/agdafile}};
-
-\node[left = 0.5cm of agdafile, hyperlink node=agda] (agda)
-  {\includegraphics[scale=0.7]{figures/agda}};
-
-\node[below = 0.2cm of problem, hyperlink node=verified-example] (verified)
-  {\includegraphics[scale=0.7]{figures/verified}};
-
-\node[below = 0.2cm of verified, opacity=0.5] (failure)
-  {\includegraphics[scale=0.7]{figures/failure}};
-
-\draw[->, thick] (problem) to (tptp);
-\draw[->, thick] (tptp) to (metis);
-\draw[->, thick] (metis) to (tstp);
-\draw[->, thick] (tstp) to (athena);
-\draw[->, thick] (athena) to (agdafile);
-\draw[->, thick] (agdafile) to (agda);
-\draw[->, thick] (agda) to (verified);
-\draw[->, thick, gray] (agda) to (failure);
+\only<2->{ \draw[->, thick] (problem) to (tptp)};
+\only<3->{ \draw[->, thick] (tptp) to (metis)};
+\only<4->{ \draw[->, thick] (metis) to (tstp)};
+\only<5->{ \draw[->, thick] (tstp) to (athena)};
+\only<6->{ \draw[->, thick] (athena) to (agdafile)};
+\only<7->{ \draw[->, thick] (agdafile) to (agda)};
+\only<8->{ \draw[->, thick] (agda) to (verified)};
+\only<8->{ \draw[->, thick, gray] (agda) to (failure)};
 \end{tikzpicture}
@@
 
-\begin{frame}[fragile]{Previous Work: Apia}{Proving first-order theorems written in Agda using automatic theorem provers for first-order logic}
+\begin{frame}[fragile, label=hammer]{Related Work}
+\begin{block}{SledgeHammer}
+\begin{itemize}
+\item Isabelle/HOL tool
+\item Metis ported within Isabelle
+\item Reconstruct proofs of well-known ATPs: EProver, Vampire, among others
+\end{itemize}
+\end{block}
+
+\begin{block}{Integrating Waldmeister and Agda}
+\begin{itemize}
+  \item Source code not available
+  \item Equational Logic
+  \item Reflection Layers
+  \end{itemize}
+\end{block}
+\end{frame}
+
+\begin{frame}[fragile]{Related Work: Apia}
+  {Proving first-order theorems written in Agda using automatic theorem provers for first-order logic}
 
@@
 
-\begin{frame}{}
-{\Huge Bonus Slides}
+\begin{frame}{Bonus Slides}
 \end{frame}
@@
         \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}}
-        to encode problems in text files
+        to encode problems
   \item Is the input of the ATPs
-  \item his problems contains formulas with the form
+  \item Annotated formulas with the form
    \begin{center}
-\begin{verbatim}
+\begin{tptp}
 language(name, role, formula).
-\end{verbatim}
+\end{tptp}
     \end{center}
     \begin{itemize}
-      \item[\texttt{language}] FOF, or CNF %THF, TFF,
+      \item[\texttt{language}] FOF or CNF %THF, TFF,
       \item[\texttt{name}] to identify the formula within the problem
       \item[\texttt{role}] axiom, definition, hypothesis, conjecture, among others
-      \item[\texttt{formula}] the logic formula in the language
+      \item[\texttt{formula}] version in TPTTP format
     \end{itemize}
@@
 
-\hyperlink{reconstruction}{Go to Reconstruction}
+\gobackreconstruction
 \end{frame}
 
-\begin{frame}[fragile]{TPTP Examples}{From Prop-Pack repository\footnote{Is available at \url{http://github.com/jonaprieto/pro-pack}}}
-\label{tptp-examples}
+\begin{frame}[fragile, label=tptp-examples]{TPTP Examples}{From Prop-Pack repository
+  \footnote{Is available at \url{http://github.com/jonaprieto/pro-pack}}}
 Problems in Propositional Logic:
+
 \begin{itemize}
@@
 \end{tptp}
+
   \item $p ∧ q ⊢ q ∧ p$
@@
 \end{tptp}
+
   \item $⊢ ¬ (p ∧ ¬ p) ∨ (q ∧ ¬ q)$
@@
   \end{itemize}
+\gobackreconstruction
 \end{frame}
@@
 \begin{itemize}
-  \item Is a Directed Acyclic Graph where
+  \item Is a \hyperlink{tstp-dag}{Directed Acyclic Graph} where
   \begin{itemize}
-    \item[\texttt{leaf}] is a formulae from the TPTP input
+    \item[\texttt{leaf}] is a formulae from the \hyperlink{tptp-syntax}{TPTP} input
     \item[\texttt{node}] is a formulae inferred from parent formulae
@@
   {\footnotesize
-\begin{verbatim}
+\begin{tptp}
 language(name, role, formula, source [,useful info]).
-\end{verbatim}}
+\end{tptp}}
 \end{center}
@@
 {\footnotesize
-\begin{verbatim}
+\begin{tptp}
 inference(rule, useful information, parents)
-\end{verbatim}
+\end{tptp}
 }
 \end{center}
-
+\gobackreconstruction
 \end{frame}
@@
 \end{itemize}
+\gobackreconstruction
 \end{frame}
@@
 \end{center}
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[fragile, label=athena]{Athena}
+ \tikz[overlay,remember picture]
+  \node at (0.92\textwidth, 1cm)
+    {\includegraphics[width=0.15\textwidth]{figures/athena}};
+\begin{block}{Athena} Is a Haskell program that translates proofs given by Metis Prover
+in TSTP format to Agda code.\\
+It depends on:
+\begin{itemize}
+  \item \texttt{agda-prop} Classical Logic within Agda: Axioms + Theorems
+  \item \texttt{agda-metis} Theorems of the inference rules of Metis Prover
+\end{itemize}
+\end{block}
+\gobackreconstruction
 \end{frame}
@@
 
-\texttt{Haskell} % is a standardized, general-purpose purely functional programming language.\\ Our usages: 
+\begin{block}{Haskell} % is a standardized, general-purpose purely functional programming language.\\ Our usages:
 \begin{itemize}
@@
     \item AST construction
-    \item Creation and analysis of DAG derivations
+    \item Creation and analysis of \hyperlink{tstp-dag}{DAG} derivations
     \item Analysis of inference rules used
@@
 \end{itemize}
+\end{block}
+\gobackreconstruction
 \end{frame}
@@
 \begin{frame}[label=agda]{Design Decisions for the Reconstruction Tool}{Programming Languages}
-\texttt{Agda} is a dependently typed functional programming language and it also a proof assistant.\\
-Our usages:
+
+ \tikz[overlay,remember picture]
+  \node at (0.92\textwidth, 1cm)
+    {\includegraphics[width=0.15\textwidth]{figures/agda}};
+
+\begin{block}{Agda}
+Is a dependently typed functional programming language and it also a proof assistant.\\
+We used it to type-check the proofs found by Metis Prover
     \begin{itemize}
-    \item Logic framework for Classical Propositional Logic
-    \item Type-Checker for the Agda code of the proofs generated
+    \item Agda-Prop Libary: Logic framework for Classical Propositional Logic
+    \item Agda-Metis Library: theorems based on the inference rules of Metis Prover
     \end{itemize}
+\end{block}
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[label=metis]{Metis Theorem Prover}{\url{http://www.gilith.com/software/metis/}}
+ \tikz[overlay,remember picture]
+  \node at (0.92\textwidth, 0.5cm)
+    {\includegraphics[width=0.15\textwidth]{figures/metis}};
+
+Metis is an automatic theorem prover for First-Order Logic with equality
+\begin{block}{Why Metis?}
+  \begin{itemize}
+    \item \href{https://github.com/gilith/metis}{Open source} implemented in Standard ML
+    \item Reads problem in \hyperlink{tptp-syntax}{\texttt{TPTP} format}
+    \item Outputs detailed proofs in \hyperlink{tstp-format}{\texttt{TSTP} format}
+    \item Each refutation step is one of
+      \href{http://www.gilith.com/software/metis/logical-kernel.txt}{\textbf{6 simple rules}}
+  \end{itemize}
+\end{block}
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[fragile, label=metis-rules]{Inference Rules of Metis}
+With Classical Propositional Logic, \hyperlink{tstp-example}{TSTP} derivations exhibit
+these inferences:
+\begin{itemize}
+\item \hyperlink{atp-canonicalize}
+  {\texttt{Canonicalize} transforms formulas to CNF or NNF}
+\item \hyperlink{atp-clausify}
+  {\texttt{Clausify} performs clausification}
+\item \hyperlink{atp-conjunct}
+  {\texttt{Conjunct} extracts a formula from a conjunction}
+\item \hyperlink{atp-negate}
+  {\texttt{Negate} applies negation to the formula}
+\item \hyperlink{atp-resolve}
+  {\texttt{Resolve} applies theorems of resolution}
+\item \hyperlink{atp-simplify}
+  {\texttt{Simplify} applies over a list of formula to simplify them}
+% \item[\texttt{Skolemize}] ...
+% \item[\texttt{Specialize}] ...
+\item \hyperlink{atp-strip}{\texttt{Strip} splits a formula into subgoals}
+\end{itemize}
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[fragile, label=atp-canonicalize]{Canonicalize}{Inference Rule}
+\begin{block}{canonicalize}
+
+\end{block}
+\end{frame}
+
+\begin{frame}[fragile, label=atp-clausify]{Clausify}{Inference Rule}
+\begin{block}{clausify}
+
+\end{block}
+\end{frame}
+
+\begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Inference Rule}
+\begin{block}{conjunct}
+\begin{lstlisting}
+$ cat ~/agda-metis/src/ATP/Metis/Rules/Conjunct.agda
+...
+conjunct : Prop -> Prop -> Prop
+conjunct (φ ∧ ψ) ω with ⌊ eq φ ω ⌋ | ⌊ eq ψ ω ⌋
+... | true  | _     = φ
+... | false | true  = ψ
+... | false | false = conjunct φ ω
+conjunct φ ω        = φ
+
+atp-conjunct
+  : ∀ {Γ} {φ}
+  -> (ω : Prop)
+  -> Γ ⊢ φ
+  -> Γ ⊢ conjunct φ ω
+\end{lstlisting}
+\end{block}
 
@@
 
+\begin{frame}[fragile, label=atp-negate]{Negate}{Inference Rule}
+\begin{block}{negate}
+
+\end{block}
+\end{frame}
+
+\begin{frame}[fragile, label=atp-resolve]{Resolve}{Inference Rule}
+\begin{block}{resolve}
+
+\end{block}
+\end{frame}
+
+\begin{frame}[fragile, label=atp-simplify]{Simplify}{Inference Rule}
+\begin{block}{simplify}
+
+\end{block}
+\end{frame}
+
+\begin{frame}[fragile, label=atp-strip]{Strip}{Inference Rule}
+\begin{block}{strip}
+\end{block}
+\end{frame}
+
+\begin{frame}[fragile, label=agda-file]{Agda Code}{Generated by Athena Tool}
+Example goes here
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[fragile, label=verified-example]{Type-checked Proof}
+Verified Example goes here
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[fragile, label=failure-example]{Type-checked Proof}
+Failure Example goes here
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[label=future-work]{Future Work}
+\begin{itemize}
+  \item Add shallow embedding in order to work with Apia
+  \item Support First-Order Logic
+  \item Support another prover like EProver
+  \item Support a Intuitionistic Prover
+\end{itemize}
+\end{frame}
+
 \begin{frame}[label=references]{References}
-\label{references}
 \printbibliography

### 2017-04-25 slides/slides.tex
[ slides ] fixed mistakes.

@@
   \begin{tikzpicture}[overlay, remember picture, scale=0.5]
-    \tikzset{shift={(current page.center)}, xshift=11.6cm,yshift=-8.3cm}
+    \tikzset{shift={(current page.center)}, xshift=11.7cm,yshift=-8.4cm}
     \node[fill=plum,text=white, hyperlink node = reconstruction] (go) at (0,0) {\tiny Go Back};
@@
 May 9-15th}
-\author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides\\
+\author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides
 (Joint work with Andr\'es Sicard-Ram\'irez)}
@@
   \footnote{Is available at \url{http://github.com/jonaprieto/pro-pack}}}
-Problems in Propositional Logic:
 
@@
 \begin{tptp}
-$ cat basic-4.tptp
 fof(a, axiom, p).
@@
 
-  \item $p ∧ q ⊢ q ∧ p$
-\begin{tptp}
-$ cat conj-3.tptp
-fof(a, axiom, p & q).
-fof(goal, conjecture, q & p).
-\end{tptp}
-
   \item $⊢ ¬ (p ∧ ¬ p) ∨ (q ∧ ¬ q)$
 \begin{tptp}
-$ cat neg-7.tptp
 fof(goal, conjecture, ~ ((p & ~ p) | (q & ~ q))).
@@
 \begin{itemize}
-  \item Is a \hyperlink{tstp-dag}{Directed Acyclic Graph} where
+  \item Is a \hyperlink{tstp-dag}{\textbf{D}irected \textbf{A}cyclic \textbf{G}raph} where
   \begin{itemize}
-    \item[\texttt{leaf}] is a formulae from the \hyperlink{tptp-syntax}{TPTP} input
-    \item[\texttt{node}] is a formulae inferred from parent formulae
-    \item[\texttt{root}] the final derived formulae
+    \item[\texttt{leaf}] is a formula from the \hyperlink{tptp-syntax}{TPTP} input
+    \item[\texttt{node}] is a formula inferred from parent formula
+    \item[\texttt{root}] the final derived formula
   \end{itemize}
-  \item Is a list of annotated formulae:
+  \item Is a list of annotated formulas with the form:
   \end{itemize}
@@
 
-where \textbf{source} typically is a inference record:
+where \textbf{source} typically is an inference record:
 \begin{center}
@@
 \begin{tptp}
-inference(rule, useful information, parents)
+inference(rule, useful info, parents)
 \end{tptp}
@@
   \item Proof found by \texttt{Metis} ATP for the problem $p ⊢ p$
+{\small
 \begin{tptp}
@@
 \end{tptp}
+}
 \end{itemize}
@@
 \begin{frame}[fragile, label=metis-rules]{Inference Rules of Metis}
-With Classical Propositional Logic, \hyperlink{tstp-example}{TSTP} derivations exhibit
-these inferences:
-\begin{itemize}
-\item \hyperlink{atp-canonicalize}
-  {\texttt{Canonicalize} transforms formulas to CNF or NNF}
-\item \hyperlink{atp-clausify}
-  {\texttt{Clausify} performs clausification}
-\item \hyperlink{atp-conjunct}
-  {\texttt{Conjunct} extracts a formula from a conjunction}
-\item \hyperlink{atp-negate}
-  {\texttt{Negate} applies negation to the formula}
-\item \hyperlink{atp-resolve}
-  {\texttt{Resolve} applies theorems of resolution}
-\item \hyperlink{atp-simplify}
-  {\texttt{Simplify} applies over a list of formula to simplify them}
-% \item[\texttt{Skolemize}] ...
-% \item[\texttt{Specialize}] ...
-\item \hyperlink{atp-strip}{\texttt{Strip} splits a formula into subgoals}
-\end{itemize}
+\hyperlink{tstp-example}{TSTP} derivations exhibit these inferences:
+\vfill
+\begin{table}[!ht]
+\begin{center}
+\scalebox{0.8}{
+{\renewcommand{\arraystretch}{1.3}%
+\begin{tabular}{|cl| }
+\hline
+\textbf{Rule} & \textbf{Task} \\
+\hline
+\hyperlink{atp-canonicalize}{\texttt{canonicalize}} & transforms formulas to CNF, DNF or NNF\\
+\hyperlink{atp-clausify}{\texttt{clausify}} & performs clausification\\
+\hyperlink{atp-conjunct}{\texttt{conjunct}} & extracts a formula from a conjunction\\
+\hyperlink{atp-negate}{\texttt{negate}} & applies negation to the formula\\
+\hyperlink{atp-resolve}{\texttt{resolve}} & applies theorems of resolution\\
+\hyperlink{atp-simplify}{\texttt{simplify}} & applies over a list of formula to simplify them\\
+\hyperlink{atp-strip}{\texttt{strip}} & splits a formula into subgoals\\[1ex]
+\hline
+\end{tabular}}
+}
+\end{center}
+\label{tab:label}
+\end{table}
+\vfill
 \gobackreconstruction
@@
 \begin{itemize}
-  \item Add shallow embedding in order to work with Apia
-  \item Support First-Order Logic
-  \item Support another prover like EProver
-  \item Support a Intuitionistic Prover
-\end{itemize}
+  \item Add shallow embedding in order to work with \texttt{Apia}
+  \item Support First-Order Logic with Equality
+  \item Support another prover like \texttt{EProver}\textbf{
+}\end{itemize}
 \end{frame}

### 2017-04-26 slides/slides.tex
[ slides ] minor changes.

@@
     \tikzset{shift={(current page.center)}, xshift=11.7cm,yshift=-8.4cm}
-    \node[fill=plum,text=white, hyperlink node = reconstruction] (go) at (0,0) {\tiny Go Back};
+    \node[fill=plum,text=white, hyperlink node = after-reconstruction] (go) at (0,0) {\tiny Go Back};
   \end{tikzpicture}}
@@
 May 9-15th}
-\author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides
+\author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides\\
 (Joint work with Andr\'es Sicard-Ram\'irez)}
@@
 \end{lrbox}
+
+\begin{frame}[fragile, label=after-reconstruction]
+\end{frame}
 

### 2017-04-27 slides/slides.tex
[ slides ] minor changes.

@@
   ]{xits-math.otf}
+\newfontfamily\mathfont{fonts/xits-math.otf}
 
@@
 \WarningFilter{biblatex}{Patching footnotes failed}
+\WarningFilter{hyperref}{Token not allowed in a PDF string}
 
@@
 \titlepage
-% \begin{tikzpicture}[overlay,remember picture, scale=0.5]
-% \foreach \x in {0,4,..., \textwidth}
-%   \foreach \y in {0,1,..., 20} {
-%     \node[opacity=0.05](tptp) at (\x,\y){$Γ ⊢ ϕ$};
-%   }
-% \end{tikzpicture}
+  \begin{tikzpicture}[overlay, remember picture] (eafit) at (current page.center)
+    \node[xshift=0cm,yshift=0cm]
+      {\includegraphics[width=0.25\textwidth]{figures/eafit}};
+    \node[xshift=3cm,yshift=-2cm] (chalmers) at (current page.center)
+      {\includegraphics[width=0.25\textwidth]{figures/chalmers}};
+  \end{tikzpicture}
 \end{frame}
-
-% \begin{frame}
-%   \frametitle{Outline}
-%   \tableofcontents
-% \end{frame}
 
@@
 }
-\only<8->{
+\only<9->{
 \node[below = 0.18cm of verified, opacity=0.5, hyperlink node=failure-example] (failure)
@@
 \only<8->{ \draw[->, thick] (agda) to (verified)};
-\only<8->{ \draw[->, thick, gray] (agda) to (failure)};
+\only<9->{ \draw[->, thick, gray] (agda) to (failure)};
 \end{tikzpicture}
@@
 \subsection{Motivation}
-
-\begin{lrbox}{\agdapragma}
-\begin{lstlisting}
-$ cat Or.agda
-module Or where
-
-data _or_ (A B : Set) : Set where
-  inj1 : A -> A or B
-  inj2 : B -> A or B
-
-postulate
-  A B    : Set
-  or-comm : A or B -> B or A
-{-# ATP prove or-comm #-}
-\end{lstlisting}
-\end{lrbox}
-
-\begin{frame}[fragile, label=after-reconstruction]
-\end{frame}
-
-\begin{frame}[fragile, label=hammer]{Related Work}
-\begin{block}{SledgeHammer}
-\begin{itemize}
-\item Isabelle/HOL tool
-\item Metis ported within Isabelle
-\item Reconstruct proofs of well-known ATPs: EProver, Vampire, among others
-\end{itemize}
-\end{block}
-
-\begin{block}{Integrating Waldmeister and Agda}
-\begin{itemize}
-  \item Source code not available
-  \item Equational Logic
-  \item Reflection Layers
-  \end{itemize}
-\end{block}
-\end{frame}
-
-\begin{frame}[fragile]{Related Work: Apia}
-  {Proving first-order theorems written in Agda using automatic theorem provers for first-order logic}
-
-\only<1-2>{At the moment, the communication between Agda and
-the ATPs is unidirectional because the ATPs are being used as oracles \citep{Sicard2015}.}
-\only<1-2>{\vfill}
-
-\begin{tikzpicture}[scale=2]
-\only<1->{ \node(agda-pragmas) at (0,0){\includegraphics{figures/agda-pragmas}}};
-\only<1>{
-  \node[fill=aliceblue, rectangle](atp-pragma) at (3,0){
-  \scalebox{0.7}{\usebox\agdapragma}
-  }};
-
-\only<2->{ \node(eagda) at (2,0){
-  \includegraphics{figures/eagda}
-  \footnote{Development version of Agda in order to handle a new built-in ATP-pragma.
-    \url{https://github.com/asr/eagda}}
-  }};
-
-\only<3->{ \node(apia) at (4,0){
-  \includegraphics{figures/apia}
-  \footnote{Haskell program for proving first-order theorems written in Agda using ATPs.
-    \url{https://github.com/asr/apia}}}
-  };
-
-\only<3->{ \node(tptp) at (2,-2){\includegraphics{figures/tptp}}};
-
-\only<3->{ \node(atp) at (4,-2){\includegraphics{figures/atp}}};
-
-\only<2->{\draw[->,ultra thick] (agda-pragmas) to (eagda)};
-
-\only<3->{\draw[->,ultra thick] (eagda) to (apia)};
-\only<3->{\draw[->, very thick, dashed, gray] (apia) to (tptp)};
-\only<3->{\draw[->, very thick, dashed, gray] (tptp) to (atp)};
-\only<3->{\draw[->, very thick, dashed, gray] (atp) to (apia)};
-
-\end{tikzpicture}
-
-\end{frame}
 
@@
         \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}}
-        to encode problems
+        to encode problems \citep{Sut09}
   \item Is the input of the ATPs
@@
 \begin{frame}[fragile, label=tptp-examples]{TPTP Examples}{From Prop-Pack repository
-  \footnote{Is available at \url{http://github.com/jonaprieto/pro-pack}}}
+  \footnote{Is available at \url{http://github.com/jonaprieto/prop-pack}}}
 
@@
 \hline
-\hyperlink{atp-canonicalize}{\texttt{canonicalize}} & transforms formulas to CNF, DNF or NNF\\
-\hyperlink{atp-clausify}{\texttt{clausify}} & performs clausification\\
+\texttt{canonicalize} & transforms formulas to CNF, DNF or NNF\\
+\texttt{clausify} & performs clausification\\
 \hyperlink{atp-conjunct}{\texttt{conjunct}} & extracts a formula from a conjunction\\
-\hyperlink{atp-negate}{\texttt{negate}} & applies negation to the formula\\
-\hyperlink{atp-resolve}{\texttt{resolve}} & applies theorems of resolution\\
-\hyperlink{atp-simplify}{\texttt{simplify}} & applies over a list of formula to simplify them\\
-\hyperlink{atp-strip}{\texttt{strip}} & splits a formula into subgoals\\[1ex]
+\texttt{negate} & applies negation to the formula\\
+\texttt{resolve} & applies theorems of resolution\\
+\texttt{simplify} & applies over a list of formula to simplify them\\
+\texttt{strip} & splits a formula into subgoals\\[1ex]
 \hline
@@
 
-\begin{frame}[fragile, label=atp-canonicalize]{Canonicalize}{Inference Rule}
-\begin{block}{canonicalize}
-
-\end{block}
-\end{frame}
-
-\begin{frame}[fragile, label=atp-clausify]{Clausify}{Inference Rule}
-\begin{block}{clausify}
-
-\end{block}
-\end{frame}
-
 \begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Inference Rule}
 \begin{block}{conjunct}
-\begin{lstlisting}
-$ cat ~/agda-metis/src/ATP/Metis/Rules/Conjunct.agda
-...
-conjunct : Prop -> Prop -> Prop
+\begin{agda}
+conjunct : Prop → Prop → Prop
 conjunct (φ ∧ ψ) ω with ⌊ eq φ ω ⌋ | ⌊ eq ψ ω ⌋
@@
   : ∀ {Γ} {φ}
-  -> (ω : Prop)
-  -> Γ ⊢ φ
-  -> Γ ⊢ conjunct φ ω
-\end{lstlisting}
-\end{block}
-
-\end{frame}
-
-\begin{frame}[fragile, label=atp-negate]{Negate}{Inference Rule}
-\begin{block}{negate}
-
-\end{block}
-\end{frame}
-
-\begin{frame}[fragile, label=atp-resolve]{Resolve}{Inference Rule}
-\begin{block}{resolve}
-
-\end{block}
-\end{frame}
-
-\begin{frame}[fragile, label=atp-simplify]{Simplify}{Inference Rule}
-\begin{block}{simplify}
-
-\end{block}
-\end{frame}
-
-\begin{frame}[fragile, label=atp-strip]{Strip}{Inference Rule}
-\begin{block}{strip}
+  → (ω : Prop)
+  → Γ ⊢ φ
+  → Γ ⊢ conjunct φ ω
+\end{agda}
 \end{block}
@@
 
+\begin{frame}[fragile, label=hammer]{Related Work}
+\begin{block}{SledgeHammer}
+\begin{itemize}
+\item Isabelle/HOL tool
+\item Metis ported within Isabelle
+\item Reconstruct proofs of well-known ATPs: EProver, Vampire, among others
+\end{itemize}
+\end{block}
+
+\begin{block}{Integrating Waldmeister and Agda}
+\begin{itemize}
+  \item Source code not available
+  \item Equational Logic
+  \item Reflection Layers
+  \end{itemize}
+\end{block}
+\end{frame}
+
+\begin{lrbox}{\agdapragma}
+\begin{agda}
+module Or where
+
+data _OR_ (A B : Set) : Set where
+  inj1 : A → A OR B
+  inj2 : B → A OR B
+
+postulate
+  A B    : Set
+  OR-comm : A OR B → B OR A
+{-# ATP prove OR-comm #-}
+\end{agda}
+\end{lrbox}
+
+\begin{frame}[fragile, label=after-reconstruction]
+\end{frame}
+
+\begin{frame}[fragile]{Related Work: Apia}
+  {Proving first-order theorems written in Agda using automatic theorem provers for first-order logic}
+
+\only<1-2>{At the moment, the communication between Agda and
+the ATPs is unidirectional because the ATPs are being used as oracles \citep{Sicard2015}.}
+\only<1-2>{\vfill}
+
+\begin{tikzpicture}
+\only<1->{ \node(agdafile) at (0,0){
+  \includegraphics[scale=0.8]{figures/agda-pragmas}}};
+\only<1>{
+  \node[fill=aliceblue, rectangle, right = 2.5cm of agdafile] (atp-pragmas){
+  \scalebox{0.7}{\usebox\agdapragma}
+  }
+  };
+
+\only<2->{
+  \node[right=1cm of agdafile] (eagda){
+  \includegraphics[scale=0.8]{figures/eagda}
+  \footnote{Development version of Agda in order to handle a new built-in ATP-pragma.
+    \url{https://github.com/asr/eagda}}
+  }
+};
+
+\only<2->{
+\node[right=1cm of eagda] (agdai){
+  \includegraphics[scale=0.8]{figures/agdai}
+  }
+};
+
+\only<3->{
+  \node[below=0.4cm of agdai] (apia){
+  \includegraphics[scale=0.8]{figures/apia}
+  \footnote{Haskell program for proving first-order theorems written in Agda using ATPs.
+    \url{https://github.com/asr/apia}}}
+  };
+
+\only<4->{
+  \node[left= 1cm of apia] (tptp)
+    {\includegraphics[scale=0.8]{figures/tptp}}};
+
+\only<5->{ \node[below = 0.8cm of apia] (atp)
+  {\includegraphics[scale=0.8]{figures/atp}}};
+
+\only<7->{ \node[below = 2.4 of agdafile, rectangle, text=white,fill=black, align=left, font=\tiny] (proved)
+{
+\texttt{\$ agda Or.agda}\\
+\texttt{\$ apia Or.agda --atp=online-metis}\\
+\texttt{Metis---2.3 proved the conjecture}
+  }
+};
+
+\only<2->{\draw[->, ultra thick] (agdafile) to (eagda)};
+\only<2->{\draw[->, ultra thick] (eagda) to (agdai)};
+\only<3->{\draw[->, ultra thick] (agdai) to (apia)};
+\only<4->{\draw[->, very thick, dashed, gray] (apia) to (tptp)};
+\only<5->{\draw[->, very thick, dashed, gray] (tptp) to (atp)};
+\only<6->{\draw[->, very thick, dashed, gray] (atp) to (apia)};
+
+\end{tikzpicture}
+\end{frame}
+
 \begin{frame}[label=future-work]{Future Work}

### 2017-04-27 slides/slides.tex
[ slides ] Makefile added, and many changes.

@@
     [wd=.8\paperwidth,ht=2.3ex,dp=1ex,left]{headFoot}%
-    \hspace*{2ex}\insertshorttitle\hspace*{2mm}(\insertshortauthor)
+    \hspace*{2ex}\textbf\insertshorttitle\hspace*{2mm}|\hspace*{2mm}\textbf\insertshortauthor
   \end{beamercolorbox}%
@@
 % \setbeamercolor{institute}{fg=blu}
-\setbeamercolor{title}{fg=plum}
+\setbeamercolor{title}{fg=plum!80!black}
 % \setbeamercolor{subtitle}{fg=blu}
@@
 \author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides\\
-(Joint work with Andr\'es Sicard-Ram\'irez)}
+Joint work with Andr\'es Sicard-Ram\'irez}
 \institute{
@@
 \titlepage
-  \begin{tikzpicture}[overlay, remember picture] (eafit) at (current page.center)
-    \node[xshift=0cm,yshift=0cm]
-      {\includegraphics[width=0.25\textwidth]{figures/eafit}};
-    \node[xshift=3cm,yshift=-2cm] (chalmers) at (current page.center)
-      {\includegraphics[width=0.25\textwidth]{figures/chalmers}};
+  \begin{tikzpicture}[overlay, remember picture]
+   \tikzset{shift={(current page.center)}}
+    \node[xshift=-4.5cm,yshift=-3.5cm] (eafit)
+      {\includegraphics[width=0.2\textwidth]{figures/eafit}};
+    \node[xshift=4.5cm,yshift=-3cm] (chalmers)
+      {\includegraphics[width=0.18\textwidth]{figures/chalmers}};
   \end{tikzpicture}
@@
 \begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Inference Rule}
-\begin{block}{conjunct}
+\begin{itemize}
+\item In \hyperlink{tstp-syntax}{TSTP}
+\begin{tptp}
+\end{tptp}
+\item Function:
 \begin{agda}
 conjunct : Prop → Prop → Prop
-conjunct (φ ∧ ψ) ω with ⌊ eq φ ω ⌋ | ⌊ eq ψ ω ⌋
-... | true  | _     = φ
-... | false | true  = ψ
-... | false | false = conjunct φ ω
-conjunct φ ω        = φ
-
+conjunct $(φ \wedge ψ)$ $ω$ with $⌊$ eq $φ$ $ω$ $⌋$ | $⌊$ eq ψ $ω$ $⌋$
+... | true  | _     = $φ$
+... | false | true  = $ψ$
+... | false | false = conjunct $φ$ $ω$
+conjunct $φ$ $ω$       = $φ$
+\end{agda}
+\item Theorem
+\begin{agda}
 atp-conjunct
-  : ∀ {Γ} {φ}
-  → (ω : Prop)
-  → Γ ⊢ φ
-  → Γ ⊢ conjunct φ ω
+  : ∀ $\{Γ\}$ $\{φ\}$
+  → $(ω : Prop)$
+  → $Γ \vdash φ$
+  → $Γ \vdash$ conjunct $φ$ $ω$
 \end{agda}
-\end{block}
+\end{itemize}
 \end{frame}
@@
   \node[fill=aliceblue, rectangle, right = 2.5cm of agdafile] (atp-pragmas){
-  \scalebox{0.7}{\usebox\agdapragma}
+  \scalebox{0.9}{\usebox\agdapragma}
   }

### 2017-04-27 slides/slides.tex
Update

@@
 \usepackage{bussproofs}
+\EnableBpAbbreviations
 \usepackage{fancyvrb}
@@
 }
+
+\tikzstyle{vertex}=[auto=left,circle,fill=black!25,minimum size=5pt,inner sep=0pt]
+
 % \usetikzlibrary{shapes.geometric,shapes.symbols,shadows}
@@
     \tikzset{shift={(current page.center)}, xshift=11.7cm,yshift=-8.4cm}
-    \node[fill=plum,text=white, hyperlink node = after-reconstruction] (go) at (0,0) {\tiny Go Back};
+    \node[fill=plum,text=white, hyperlink node = reconstruction] (go) at (0,0) {\tiny Go Back};
   \end{tikzpicture}}
@@
 
-\begin{frame}[fragile, label=reconstruction]{Proof Reconstruction: Overview}
-
+\begin{frame}[fragile, label=overview]{Proof Reconstruction: Overview}
+\vfill
 \begin{tikzpicture}
@@
 \only<9->{ \draw[->, thick, gray] (agda) to (failure)};
+\end{tikzpicture}
+\vfill
+\end{frame}
+
+\begin{frame}[fragile, label=reconstruction]{Proof Reconstruction: Overview}
+\vfill
+\begin{tikzpicture}
+\node(problem) at (0,0)
+   {\includegraphics[scale=0.7]{figures/problem}};
+\node[right = 0.8cm of problem, hyperlink node=tptp-syntax](tptp){
+\includegraphics[scale=0.7]{figures/tptp}
+};
+\node[right= 0.8cm of tptp, hyperlink node=metis] (metis)
+  {\includegraphics[scale=0.7]{figures/metis}\,
+  \footnote{It is available at \url{http://www.gilith.com/software/metis}}
+  };
+\node[right= 0.8cm of metis, hyperlink node=tstp-syntax] (tstp)
+  {\includegraphics[scale=0.7]{figures/tstp}};
+\node[below= 1.5cm of tstp, hyperlink node=athena] (athena)
+  {\includegraphics[scale=0.7]{figures/athena}
+  \footnote{It is available at \url{http://github.com/jonaprieto/athena}}
+  };
+\node[left = 0.5cm of athena, hyperlink node=agda-file] (agdafile)
+  {\includegraphics[scale=0.7]{figures/agdafile}
+  };
+\node[left = 0.5cm of agdafile, hyperlink node=agda] (agda)
+  {\includegraphics[scale=0.7]{figures/agda}
+  \footnote{It is available at \url{http://github.com/agda/agda}}
+  };
+\node[below = 0.18cm of problem, hyperlink node=verified-example] (verified)
+  {\includegraphics[scale=0.7]{figures/verified}};
+\node[below = 0.18cm of verified, opacity=0.5, hyperlink node=failure-example] (failure)
+  {\includegraphics[scale=0.7]{figures/failure}};
+
+\draw[->, thick] (problem) to (tptp);
+\draw[->, thick] (tptp) to (metis);
+\draw[->, thick] (metis) to (tstp);
+\draw[->, thick] (tstp) to (athena);
+\draw[->, thick] (athena) to (agdafile);
+\draw[->, thick] (agdafile) to (agda);
+\draw[->, thick] (agda) to (verified);
+\draw[->, thick, gray] (agda) to (failure);
 \end{tikzpicture}
@@
 \begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Inference Rule}
+
 \begin{itemize}
-\item In \hyperlink{tstp-syntax}{TSTP}
-\begin{tptp}
-\end{tptp}
+\item Definition
+  \begin{equation*}
+  conjunct (ϕ₁ ∧  ϕ₂ ∧ ⋯ ∧ \mathbf{ϕᵢ} ∧ ⋯ ∧ ϕₙ, \mathbf{ϕᵢ}) ⟶ \mathbf{ϕᵢ}
+  \end{equation*}
+
 \item Function:
@@
 
-\begin{frame}[fragile, label=agda-file]{Agda Code}{Generated by Athena Tool}
-Example goes here
+\begin{frame}[fragile, label=agda-file]{Agda Code Example}{Generated by Athena Tool}
+\begin{tikzpicture}[overlay, remember picture]
+ \tikzset{shift={(current page.north)}, xshift=5cm,yshift=-2cm}
+\node[vertex, fill=black] (d1) {};
+\node[vertex, fill=black, right=0.5cm of d1 ] (d2) {};
+\node[vertex, fill=black, below=0.2cm of d1] (d3) {};
+\node[vertex, fill=black, below=0.2cm of d2] (d4) {};
+\node[vertex, fill=black, below right= 0.2cm and  0.25cm of d3] (d5) {};
+\draw[-, thick] (d1) to (d3);
+\draw[-, thick] (d2) to (d4);
+\draw[-, thick] (d3) to (d5);
+\draw[-, thick] (d4) to (d5);
+\end{tikzpicture}
+
+\begin{itemize}
+  \item The problem is $p ∧ q ⊢ q ∧ p$
+  \item TSTP derivation
+\begin{tptp}
+fof(a, axiom, p & q).
+fof(goal, conjecture, q & p).
+\end{tptp}
+  \item A natural deduction proof
+  \begin{prooftree}
+  \AxiomC{$ϕ ∧ ψ$}
+  \RightLabel{$∧$-\texttt{proj}$₁$}
+  \UnaryInfC{$ϕ$}
+
+  \AxiomC{$ϕ ∧ ψ$}
+  \RightLabel{$∧$-\texttt{proj}$₂$}
+  \UnaryInfC{$ψ$}
+  \RightLabel{$∧$-\texttt{intro}}
+  \BinaryInfC{$ψ ∧ ϕ$}
+  \end{prooftree}
+\end{itemize}
 \gobackreconstruction
@@
 \begin{frame}[fragile, label=verified-example]{Type-checked Proof}
-Verified Example goes here
+\begin{agda}
+proof$₀$ : $Γ ⊢$ subgoal$₀$
+proof$₀$ =
+  (RAA
+    (atp-canonicalize
+      (atp-simplify
+        (atp-canonicalize
+          (atp-strip
+            (assume $\{Γ = Γ\}$
+              (atp-negate subgoal$₀$))))
+        (atp-conjunct (q)
+          (atp-canonicalize
+            (weaken (atp-negate subgoal$₀$)
+              (assume $\{Γ = ∅\}$ a)))))))
+\end{agda}
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[fragile, label=verified-example-2]{Type-checked Proof}
+\begin{agda}
+proof$₁$ : $Γ ⊢$ subgoal$₁$
+proof$₁$ =
+  (RAA
+    (atp-canonicalize
+      (atp-simplify
+        (atp-conjunct (q)
+          (atp-canonicalize
+            (weaken (atp-negate subgoal$₁$)
+              (assume $\{Γ = ∅\}$ a))))
+        (atp-simplify
+          (atp-canonicalize
+            (atp-strip
+              (assume $\{Γ = Γ\}$
+                (atp-negate subgoal$₁$))))
+          (atp-conjunct (p)
+            (atp-canonicalize
+              (weaken (atp-negate subgoal$₁$)
+                (assume $\{Γ = ∅\}$ a))))))))
+\end{agda}
 \gobackreconstruction

### 2017-04-27 slides/slides.tex
[ slides ] alejandro no deja trabajar.

@@
 
-\begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Inference Rule}
+\begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Metis Inference Rule}
 
@@
 
-\item Function:
+\item Function\footnote{\label{note-conjunct}It is available in \texttt{agda-metis} library in \texttt{ATP.Metis.Rules.Conjunct} module.}:
 \begin{agda}
@@
 \end{agda}
-\item Theorem
+\item Theorem\textsuperscript{\ref{note-conjunct}}
 \begin{agda}
@@
 \begin{frame}[fragile, label=agda-file]{Agda Code Example}{Generated by Athena Tool}
-\begin{tikzpicture}[overlay, remember picture]
- \tikzset{shift={(current page.north)}, xshift=5cm,yshift=-2cm}
-\node[vertex, fill=black] (d1) {};
-\node[vertex, fill=black, right=0.5cm of d1 ] (d2) {};
-\node[vertex, fill=black, below=0.2cm of d1] (d3) {};
-\node[vertex, fill=black, below=0.2cm of d2] (d4) {};
-\node[vertex, fill=black, below right= 0.2cm and  0.25cm of d3] (d5) {};
-\draw[-, thick] (d1) to (d3);
-\draw[-, thick] (d2) to (d4);
-\draw[-, thick] (d3) to (d5);
-\draw[-, thick] (d4) to (d5);
-\end{tikzpicture}
 
@@
   \item The problem is $p ∧ q ⊢ q ∧ p$
-  \item TSTP derivation
+  \item TPTP derivation
 \begin{tptp}
@@
   \item A natural deduction proof
+\begin{columns}
+\begin{column}{0.8\textwidth}
  \begin{prooftree}
@@
   \end{prooftree}
+\end{column}
+\begin{column}{0.2\textwidth}  %%<--- here
+   \begin{tikzpicture}[overlay, remember picture]
+% \tikzset{shift={(current page.north)}, xshift=cm,yshift=-2cm}
+\node[vertex, fill=black] (d1) {};
+\node[vertex, fill=black, right=0.5cm of d1 ] (d2) {};
+\node[vertex, fill=black, below=0.2cm of d1] (d3) {};
+\node[vertex, fill=black, below=0.2cm of d2] (d4) {};
+\node[vertex, fill=black, below right= 0.2cm and  0.25cm of d3] (d5) {};
+\draw[-, thick] (d1) to (d3);
+\draw[-, thick] (d2) to (d4);
+\draw[-, thick] (d3) to (d5);
+\draw[-, thick] (d4) to (d5);
+\end{tikzpicture}
+\end{column}
+\end{columns}
+
 \end{itemize}
@@
 
+% \begin{frame}[fragile, label=verified-example1]{TPTP}
+
+% \end{frame}
+
 \begin{frame}[fragile, label=verified-example]{Type-checked Proof}
+\vfill
 \begin{agda}
@@
 \end{agda}
+\vfill
 \gobackreconstruction
@@
 \begin{frame}[fragile, label=verified-example-2]{Type-checked Proof}
+\vfill
 \begin{agda}

### 2017-04-28 slides/slides.tex
[ slides ] example proof added.

@@
 \EnableBpAbbreviations
+\def\extraVskip{3pt}
+
 \usepackage{fancyvrb}
@@
   , url=false
-  , doi=true
+  , doi=false
+  , isbn=false
   , eprint=false
@@
 \node[right= 0.8cm of tptp, hyperlink node=metis] (metis)
-  {\includegraphics[scale=0.7]{figures/metis}\,
-  \footnote{It is available at \url{http://www.gilith.com/software/metis}}
-  };
+  {\includegraphics[scale=0.7]{figures/metis}};
 \node[right= 0.8cm of metis, hyperlink node=tstp-syntax] (tstp)
@@
 \node[below= 1.5cm of tstp, hyperlink node=athena] (athena)
-  {\includegraphics[scale=0.7]{figures/athena}
-  \footnote{It is available at \url{http://github.com/jonaprieto/athena}}
-  };
+  {\includegraphics[scale=0.7]{figures/athena}};
 \node[left = 0.5cm of athena, hyperlink node=agda-file] (agdafile)
-  {\includegraphics[scale=0.7]{figures/agdafile}
-  };
+  {\includegraphics[scale=0.7]{figures/agdafile}};
 \node[left = 0.5cm of agdafile, hyperlink node=agda] (agda)
-  {\includegraphics[scale=0.7]{figures/agda}
-  \footnote{It is available at \url{http://github.com/agda/agda}}
-  };
+  {\includegraphics[scale=0.7]{figures/agda}};
 \node[below = 0.18cm of problem, hyperlink node=verified-example] (verified)
@@
 
-\subsubsection{TSTP Derivations}
-
-\begin{frame}[fragile, label=tstp-syntax]{TSTP Syntax}
-
- \tikz[overlay,remember picture]
-  \node at (0.92\textwidth, -0.5cm)
-    {\includegraphics[width=0.15\textwidth]{figures/tstp}};
-
-A TSTP derivation
-\footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/QuickGuide/Derivations.html}}
-\begin{itemize}
-  \item Is a \hyperlink{tstp-dag}{\textbf{D}irected \textbf{A}cyclic \textbf{G}raph} where
-  \begin{itemize}
-    \item[\texttt{leaf}] is a formula from the \hyperlink{tptp-syntax}{TPTP} input
-    \item[\texttt{node}] is a formula inferred from parent formula
-    \item[\texttt{root}] the final derived formula
-  \end{itemize}
-  \item Is a list of annotated formulas with the form:
-  \end{itemize}
-
-\begin{center}
-  {\footnotesize
-\begin{tptp}
-language(name, role, formula, source [,useful info]).
-\end{tptp}}
-\end{center}
-
-where \textbf{source} typically is an inference record:
-\begin{center}
-{\footnotesize
-\begin{tptp}
-inference(rule, useful info, parents)
-\end{tptp}
-}
-\end{center}
-\gobackreconstruction
-\end{frame}
-
-\begin{frame}[fragile, label=tstp-example]{TSTP Example}
-
- \tikz[overlay,remember picture]
-  \node at (0.93\textwidth, -0.3cm)
-    {\includegraphics[width=0.15\textwidth]{figures/metis}};
-
-\begin{itemize}
-  \item Proof found by \texttt{Metis} ATP for the problem $p ⊢ p$
-{\small
-\begin{tptp}
-$ metis --show proof basic-4.tptp
-fof(a, axiom, (p)).
-fof(goal, conjecture, (p)).
-fof(subgoal_0, plain, (p),
-  inference(strip, [], [goal])).
-fof(negate_0_0, plain, (~ p),
-  inference(negate, [], [subgoal_0])).
-fof(normalize_0_0, plain, (~ p),
-  inference(canonicalize, [], [negate_0_0])).
-fof(normalize_0_1, plain, (p),
-  inference(canonicalize, [], [a])).
-fof(normalize_0_2, plain, ($false),
-  inference(simplify, [],
-    [normalize_0_0, normalize_0_1])).
-cnf(refute_0_0, plain, ($false),
-    inference(canonicalize, [], [normalize_0_2])).
-\end{tptp}
-}
-\end{itemize}
-\gobackreconstruction
-\end{frame}
-
-\begin{frame}[fragile, label=tstp-dag]{DAG for the previous TSTP derivation found by \texttt{Metis} ATP}
-
-\vfill
-\begin{center}
-\includegraphics[height=0.8\textheight]{figures/derivation.png}
-\end{center}
-\gobackreconstruction
-\end{frame}
-
-\begin{frame}[fragile, label=athena]{Athena}
- \tikz[overlay,remember picture]
-  \node at (0.92\textwidth, 1cm)
-    {\includegraphics[width=0.15\textwidth]{figures/athena}};
-\begin{block}{Athena} Is a Haskell program that translates proofs given by Metis Prover
-in TSTP format to Agda code.\\
-It depends on:
-\begin{itemize}
-  \item \texttt{agda-prop} Classical Logic within Agda: Axioms + Theorems
-  \item \texttt{agda-metis} Theorems of the inference rules of Metis Prover
-\end{itemize}
-\end{block}
-\gobackreconstruction
-\end{frame}
-
-\begin{frame}[label=haskell]{Design Decisions for the Reconstruction Tool}
- \tikz[overlay,remember picture]
-  \node at (0.93\textwidth, 0cm)
-    {\includegraphics[width=0.2\textwidth]{figures/athena}};
-
-\begin{block}{Haskell} % is a standardized, general-purpose purely functional programming language.\\ Our usages:
-\begin{itemize}
-    \item Parsing
-    \item AST construction
-    \item Creation and analysis of \hyperlink{tstp-dag}{DAG} derivations
-    \item Analysis of inference rules used
-    \item Generation of Agda code of the proof
-\end{itemize}
-\end{block}
-\gobackreconstruction
-\end{frame}
-
-\begin{frame}[label=agda]{Design Decisions for the Reconstruction Tool}{Programming Languages}
-
- \tikz[overlay,remember picture]
-  \node at (0.92\textwidth, 1cm)
-    {\includegraphics[width=0.15\textwidth]{figures/agda}};
-
-\begin{block}{Agda}
-Is a dependently typed functional programming language and it also a proof assistant.\\
-We used it to type-check the proofs found by Metis Prover
-    \begin{itemize}
-    \item Agda-Prop Libary: Logic framework for Classical Propositional Logic
-    \item Agda-Metis Library: theorems based on the inference rules of Metis Prover
-    \end{itemize}
-\end{block}
-\gobackreconstruction
-\end{frame}
-
 \begin{frame}[label=metis]{Metis Theorem Prover}{\url{http://www.gilith.com/software/metis/}}
@@
     \item \href{https://github.com/gilith/metis}{Open source} implemented in Standard ML
-    \item Reads problem in \hyperlink{tptp-syntax}{\texttt{TPTP} format}
-    \item Outputs detailed proofs in \hyperlink{tstp-format}{\texttt{TSTP} format}
     \item Each refutation step is one of
       \href{http://www.gilith.com/software/metis/logical-kernel.txt}{\textbf{6 simple rules}}
+    \item Reads problem in \hyperlink{tptp-syntax}{\texttt{TPTP} format}
+    \item Outputs detailed proofs in \hyperlink{tstp-syntax}{\texttt{TSTP} format}
   \end{itemize}
@@
 \begin{frame}[fragile, label=metis-rules]{Inference Rules of Metis}
-\hyperlink{tstp-example}{TSTP} derivations exhibit these inferences:
+\hyperlink{tstp-example}{TSTP} derivations by Metis exhibit these inferences
+\footnote{Inference rules found in proofs of Propositional Logic theorems}:
 \vfill
@@
 \hline
-\textbf{Rule} & \textbf{Task} \\
+\textbf{Rule} & \textbf{Purpose} \\
 \hline
@@
 \texttt{clausify} & performs clausification\\
-\hyperlink{atp-conjunct}{\texttt{conjunct}} & extracts a formula from a conjunction\\
+\hyperlink{atp-conjunct}{\texttt{conjunct}} & takes a formula from a conjunction\\
 \texttt{negate} & applies negation to the formula\\
@@
 
-\begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Metis Inference Rule}
+\subsubsection{TSTP Derivations}
 
+\begin{frame}[fragile, label=tstp-syntax]{TSTP Syntax}
+
+ \tikz[overlay,remember picture]
+  \node at (0.92\textwidth, -0.5cm)
+    {\includegraphics[width=0.15\textwidth]{figures/tstp}};
+
+A TSTP derivation
+\footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/QuickGuide/Derivations.html}}
+\begin{itemize}
+  \item Is a \hyperlink{tstp-dag}{\textbf{D}irected \textbf{A}cyclic \textbf{G}raph} where
+  \begin{itemize}
+    \item[\texttt{leaf}] is a formula from the \hyperlink{tptp-syntax}{\texttt{TPTP}} input
+    \item[\texttt{node}] is a formula inferred from parent formula
+    \item[\texttt{root}] the final derived formula
+  \end{itemize}
+  \item Is a list of annotated formulas with the form:
+  \end{itemize}
+
+\begin{center}
+  {\footnotesize
+\begin{tptp}
+language(name, role, formula, source [,useful info]).
+\end{tptp}}
+\end{center}
+
+where \textbf{\color{plum} source} typically is an inference record:
+\begin{center}
+{\footnotesize
+\begin{tptp}
+inference(rule, useful info, parents)
+\end{tptp}
+}
+\end{center}
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[fragile, label=tstp-example]{\texttt{TSTP} Example}
+
+ \tikz[overlay,remember picture]
+  \node at (0.93\textwidth, -0.3cm)
+    {\includegraphics[width=0.15\textwidth]{figures/metis}};
+
+\begin{itemize}
+  \item Proof found by \texttt{Metis} Prover for the problem $p ⊢ p$
+{\small
+\begin{tptp}
+$ metis --show proof basic-4.tptp
+fof(a, axiom, p).
+fof(goal, conjecture, p).
+fof(subgoal_0, plain, p),
+  inference(strip, [], [goal])).
+fof(negate_0_0, plain, ~ p,
+  inference(negate, [], [subgoal_0])).
+fof(normalize_0_0, plain, ~ p,
+  inference(canonicalize, [], [negate_0_0])).
+fof(normalize_0_1, plain, p,
+  inference(canonicalize, [], [a])).
+fof(normalize_0_2, plain, $false,
+  inference(simplify, [],
+    [normalize_0_0, normalize_0_1])).
+cnf(refute_0_0, plain, $false,
+    inference(canonicalize, [], [normalize_0_2])).
+\end{tptp}
+}
+\end{itemize}
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[fragile, label=tstp-dag]{DAG for the previous TSTP derivation found by \texttt{Metis} Prover}
+
+\vfill
+By refutation, we proved $p ⊢ p$:
+\begin{center}
+\begin{prooftree}
+\AxiomC{$p$}
+\RightLabel{\texttt{assume}}
+\UnaryInfC{$p$}
+\RightLabel{\texttt{strip}}
+\UnaryInfC{$p$}
+\RightLabel{\texttt{negate}}
+\UnaryInfC{$¬ p$}
+\AxiomC{$p$}
+\RightLabel{\texttt{canonicalize}}
+\UnaryInfC{$p$}
+\RightLabel{\texttt{simplify}}
+\BinaryInfC{$⊥$}
+\RightLabel{\texttt{canonicalize}}
+\UnaryInfC{$⊥$}
+
+\end{prooftree}
+% \includegraphics[height=0.8\textheight]{figures/derivation.png}
+\end{center}
+\vfill
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[fragile, label=athena]{Athena}
+  {\url{http://github.com/jonaprieto/athena}}
+
+ \begin{tikzpicture}[overlay,remember picture]
+ \tikzset{shift={(current page.north)}, xshift=0cm,yshift=0cm}
+  \node[] at (0.92\textwidth, 1cm)
+    {\includegraphics[width=0.15\textwidth]{figures/athena}};
+\end{tikzpicture}
+
+Is a Haskell program
+that translates proofs given by Metis Prover
+in \texttt{TSTP} format to Agda code.\\
+
+\begin{itemize}
+    \item Parsing of \texttt{TSTP} language
+    \item Creation and analysis of \hyperlink{tstp-dag}{\textbf{DAG}} derivations
+    \item Analysis of inference rules used in the \texttt{TSTP} derivation
+    \item Agda code generation
+\begin{table}[!ht]
+\begin{center}
+\scalebox{0.8}{
+{\renewcommand{\arraystretch}{1.3}%
+\begin{tabular}{|cl| }
+\hline
+\textbf{Library} & \textbf{Purpose} \\
+\hline
+\texttt{\hyperlink{agda-prop}{Agda-Prop}}& axioms and theorems of Classical Propositional Logic\\
+\texttt{\hyperlink{agda-metis}{Agda-Metis}} & versions of the inference rules used by Metis\\
+\hline
+\end{tabular}}
+}
+\end{center}
+\label{tab:library}
+\end{table}
+
+\end{itemize}
+\gobackreconstruction
+\end{frame}
+
+\begin{frame}[fragile, label=agda-prop-2]{Agda-Prop Library}
+  {\url{https://github.com/jonaprieto/agda-prop}}
+\begin{itemize}
+  \item Propositional Logic + PEM ($Γ ⊢ ϕ ∨ ¬ ϕ$)
+  \item A data type for formulas
+\begin{agda}
+data Prop : Set where
+  Var  : Fin n → Prop           -- Variables.
+  $⊤$    : Prop                   -- Top (truth).
+  $⊥$    : Prop                   -- Bottom (falsum).
+  _$∧$_  : ($φ$ $ψ$ : Prop) → Prop    -- Conjunction.
+  _$∨$_  : ($φ$ $ψ$ : Prop) → Prop    -- Disjunction.
+  _$⇒$_  : ($φ$ $ψ$ : Prop) → Prop    -- Implication.
+  _$⇔$_  : ($φ$ $ψ$ : Prop) → Prop    -- Biimplication.
+  $¬$_   : ($φ$ : Prop) → Prop      -- Negation.
+\end{agda}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile, label=agda-prop]{Agda-Prop Library}
+  {\url{https://github.com/jonaprieto/agda-prop}}
+\begin{itemize}
+  \item A data type for theorems
+\begin{agda}
+data _$⊢$_ : ($Γ$ : Ctxt)($φ$ : Prop) → Set
+\end{agda}
+
+\item Constructors
+\begin{agda}
+assume, axiom, weaken, $⊤$-intro, $⊥$-elim, $¬$-intro,
+$¬$-elim, $∧$-intro, $∧$-proj$₁$, $∧$-proj$₂$, $∨$-intro$₁$,
+$∨$-intro$₂$, $∨$-elim, $⇒$-intro, $⇒$-elim, $⇔$-intro,
+$⇔$-elim$₁$, $⇔$-elim$₂$
+\end{agda}
+  \item Natural deduction proofs for more than 71 theorems
+\begin{agda}
+$⇔$-equiv, $⇔$-assoc, $⇔$-comm, $⇒-⇔-¬∨$, $⇔-¬$-to-$¬$,
+$¬⇔$-to-$¬$, $¬¬$-equiv, $⇒⇒-⇔-∧⇒$, $⇔$-trans, $∧$-assoc,
+$∧$-comm, $∧$-dist, $¬∧$-to-$¬∨¬$, $¬∨¬$-to-$¬∧$, $¬∨¬-⇔-¬∧$,
+subst$⊢∧₁$, subst$⊢∧₂$, $∨$-assoc, $∨$-comm, $∨$-dist,
+$∨$-equiv, $¬∨$-to-$¬∧¬$, $¬∧¬$-to-$¬∨$, $∨$-dmorgan,
+$¬¬∨¬¬$-to-$∨$, cnf, nnf, dnf, RAA, ...
+\end{agda}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile, label=agda-metis]{Agda-Metis Library}
+  {\url{https://github.com/jonaprieto/agda-metis}}
+\vfill
+\begin{table}[!ht]
+\begin{center}
+\scalebox{0.7}{
+{\renewcommand{\arraystretch}{1.3}%
+\begin{tabular}{|clc|}
+\hline
+\textbf{Rule} & \textbf{Purpose} &\textbf{Theorem}\\
+\hline
+\texttt{canonicalize} & transforms formulas to CNF, DNF or NNF &\texttt{atp-canonicalize}\\
+\texttt{clausify} & performs clausification &\texttt{atp-clausify}\\
+\hyperlink{atp-conjunct}{\texttt{conjunct}} & takes a formula from a conjunction &\hyperlink{atp-conjunct}{\texttt{atp-conjunct}}\\
+\texttt{negate} & applies negation to the formula &\texttt{atp-negate}\\
+\texttt{resolve} & applies theorems of resolution &\texttt{atp-resolve}\\
+\texttt{simplify} & applies over a list of formula to simplify them &\texttt{atp-simplify}\\
+\texttt{strip} & splits a formula into subgoals &\texttt{strip}\\[1ex]
+\hline
+\end{tabular}}
+}
+\end{center}
+\label{tab:agda-metis-table}
+\end{table}
+\vfill
+\end{frame}
+
+\begin{frame}[fragile, label=atp-conjunct]{Agda-Metis: Conjunct Inference}
+   {\url{https://github.com/jonaprieto/agda-metis}}
 \begin{itemize}
@@
   \begin{equation*}
-  conjunct (ϕ₁ ∧  ϕ₂ ∧ ⋯ ∧ \mathbf{ϕᵢ} ∧ ⋯ ∧ ϕₙ, \mathbf{ϕᵢ}) ⟶ \mathbf{ϕᵢ}
+  conjunct (ϕ₁ ∧  ϕ₂ ∧ ⋯ ∧ \mathbf{ϕᵢ} ∧ ⋯ ∧ ϕ\_n, \mathbf{ϕᵢ}) ⟶ \mathbf{ϕᵢ}
   \end{equation*}
 
-\item Function\footnote{\label{note-conjunct}It is available in \texttt{agda-metis} library in \texttt{ATP.Metis.Rules.Conjunct} module.}:
+\item Function\footnote{\label{note-conjunct}Excerpt from the \texttt{Agda-Metis} library available in  \texttt{ATP.Metis.Rules.Conjunct} module.}:
 \begin{agda}
@@
 
+\begin{frame}[fragile, label=atp-conjunct-proof]{A proof of \texttt{atp-conjunct} theorem}
+\vfill
+\begin{agda}
+atp-conjunct
+  : $∀ \{Γ\} \{φ\}$
+  → ($ω$ : Prop)
+  → $Γ ⊢ φ$
+  → $Γ ⊢$ conjunct $φ\ ω$
+
+atp-conjunct $\{Γ\}$ $\{φ ∧ ψ\}$ $ω$ $Γ⊢φ$ with $⌊$ eq $φ$ $ω$ $⌋$ | $⌊$ eq $ψ$ $ω$ $⌋$
+... | true  | _     = $∧$-proj$₁$ $Γ⊢φ$
+... | false | true  = $∧$-proj$₂$ $Γ⊢φ$
+... | false | false =
+    atp-conjunct $\{Γ = Γ\}$ $\{φ = φ\}$ $ω$ ($∧$-proj$₁$ $Γ⊢φ$)
+atp-conjunct {_} {Var x} _ = id
+atp-conjunct {_} {$⊤$} _     = id
+atp-conjunct {_} {$⊥$} _     = id
+atp-conjunct {_} {$φ ∨ φ₁$} _ = id
+atp-conjunct {_} {$φ ⇒ φ₁$} _ = id
+atp-conjunct {_} {$φ ⇔ φ₁$} _ = id
+atp-conjunct {_} {$¬ φ$} _    = id
+\end{agda}
+\vfill
+
+\end{frame}
+
 \begin{frame}[fragile, label=agda-file]{Agda Code Example}{Generated by Athena Tool}
@@
   \item The problem is $p ∧ q ⊢ q ∧ p$
-  \item TPTP derivation
+  \item In TPTP format
 \begin{tptp}
@@
 
-% \begin{frame}[fragile, label=verified-example1]{TPTP}
+\begin{frame}[fragile, allowframebreaks]{TSTP derivation}
+\begin{tptp}
+fof(a, axiom, p & q).
+fof(goal, conjecture, q & p).
+fof(subgoal_0, plain, q,
+    inference(strip, [], [goal])).
+fof(subgoal_1, plain, q => p,
+    inference(strip, [], [goal])).
+fof(negate_0_0, plain, ~ q,
+inference(negate, [], [subgoal_0])).
+fof(normalize_0_0, plain, (~ q),
+    inference(canonicalize, [], [negate_0_0])).
+fof(normalize_0_1, plain, p & q,
+    inference(canonicalize, [], [a])).
+fof(normalize_0_2, plain, q,
+    inference(conjunct, [], [normalize_0_1])).
+fof(normalize_0_3, plain, $false,
+    inference(simplify, [],
+        [normalize_0_0, normalize_0_2])).
+cnf(refute_0_0, plain, $false,
+    inference(canonicalize, [], [normalize_0_3])).
+fof(negate_1_0, plain, ~ (q => p),
+    inference(negate, [], [subgoal_1])).
+fof(normalize_1_0, plain, ~ p & q,
+    inference(canonicalize, [], [negate_1_0])).
+fof(normalize_1_1, plain, p & q,
+     inference(canonicalize, [], [a])).
+fof(normalize_1_2, plain, p,
+    inference(conjunct, [], [normalize_1_1])).
+fof(normalize_1_3, plain, q,
+    inference(conjunct, [], [normalize_1_1])).
+fof(normalize_1_4, plain, $false,
+    inference(simplify, [],
+      [normalize_1_0, normalize_1_2, normalize_1_3])).
+cnf(refute_1_0, plain, ($false),
+    inference(canonicalize, [], [normalize_1_4])).
+\end{tptp}
+\end{frame}
 
-% \end{frame}
+\begin{frame}[fragile, label=verified-example]{$p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
+\vfill
+Definitions
+\begin{agda}
+p : Prop
+p = Var (# 0)
+q : Prop
+q = Var (# 1)
+-- Axiom.
+a : Prop
+a = (p $∧$ q)
+-- Premise.
+$Γ$ : Ctxt
+$Γ$ = [ a ]
+-- Conjecture.
+goal : Prop
+goal = (q $∧$ p)
+-- Subgoals.
+subgoal$₀$ : Prop
+subgoal$₀$ = q
+subgoal$₁$ : Prop
+subgoal$₁$ = (q $⇒$ p)
+\end{agda}
+\end{frame}
 
-\begin{frame}[fragile, label=verified-example]{Type-checked Proof}
+\begin{frame}[fragile, label=verified-example-2]{$p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
 \vfill
 \begin{agda}
+-- Axiom.
+a : Prop
+a = (p $∧$ q)
+-- Subgoal.
+subgoal$₀$ : Prop
+subgoal$₀$ = q
+
 proof$₀$ : $Γ ⊢$ subgoal$₀$
@@
           (atp-strip
-            (assume $\{Γ = Γ\}$
-              (atp-negate subgoal$₀$))))
+            (assume $\{Γ = Γ\}$ (atp-negate subgoal$₀$))))
         (atp-conjunct (q)
@@
 \vfill
-\gobackreconstruction
 \end{frame}
 
-\begin{frame}[fragile, label=verified-example-2]{Type-checked Proof}
+\begin{frame}[fragile, label=verified-example-3]{$p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
 \vfill
 \begin{agda}
+subgoal$₁$ : Prop
+subgoal$₁$ = (q $⇒$ p)
+
 proof$₁$ : $Γ ⊢$ subgoal$₁$
@@
             (atp-strip
-              (assume $\{Γ = Γ\}$
-                (atp-negate subgoal$₁$))))
+              (assume $\{Γ = Γ\}$ (atp-negate subgoal$₁$))))
           (atp-conjunct (p)
@@
 \vfill
+\end{frame}
+
+\begin{frame}[fragile, label=verified-example-4]{$p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
+\begin{agda}
+proof : $Γ ⊢$ goal
+proof =
+  $⇒$-elim
+    atp-splitGoal
+    ($∧$-intro proof$₀$ proof$₁$)
+\end{agda}
 \gobackreconstruction
@@
 
-\begin{frame}[fragile, label=failure-example]{Type-checked Proof}
-Failure Example goes here
-\gobackreconstruction
+\begin{frame}[fragile, label=failure-example]{Bug in the Printing of the Proof}
+  {Metis' Issue: \url{https://github.com/gilith/metis/issues/2}}
+% {}
+% \begin{tptp}
+% $ cat problem.tptp
+% fof(goal, conjecture,
+%   ((p <=> q) <=> r) <=> (p <=> (q <=> r))).
+% \end{tptp}
+\begin{tptp}
+$ metis --version
+metis 2.3 (release 20161108)
+$ metis --show proof problem.tptp
+...
+fof(normalize_2_0, plain,
+  (~ p & (~ q <=> ~ r) & (~ p <=> (~ q <=> ~ r))),
+  inference(canonicalize, [], [negate_2_0])).
+fof(normalize_2_1, plain, ~ p <=> (~ q <=> ~ r),
+    inference(conjunct, [], [normalize_2_0])).
+fof(normalize_2_2, plain, ~ q <=> ~ r,
+    inference(conjunct, [], [normalize_2_0])).
+fof(normalize_2_3, plain, ~ p,
+  inference(conjunct, [], [normalize_2_0])).
+fof(normalize_2_4, plain, $false,
+    inference(simplify, [],
+      [normalize_2_1, normalize_2_2, normalize_2_3])).
+...
+\end{tptp}
 \end{frame}
@@
 \begin{frame}[fragile, label=hammer]{Related Work}
-\begin{block}{SledgeHammer}
+\begin{block}{SledgeHammer} \citep{Paulson2007}
 \begin{itemize}
-\item Isabelle/HOL tool
+\item Isabelle/HOL mature tool
 \item Metis ported within Isabelle
-\item Reconstruct proofs of well-known ATPs: EProver, Vampire, among others
+\item Reconstruct proofs of well-known ATPs: \texttt{EProver}, \texttt{Vampire},
+among others using SystemOnTPTP server
 \end{itemize}
@@
 
-\begin{block}{Integrating Waldmeister and Agda}
+\begin{block}{Integrating Waldmeister into Agda} \citep{Foster2011}
 \begin{itemize}
-  \item Source code not available
+  \item Framework for a integration between Agda and ATPs
+  \begin{itemize}
     \item Equational Logic
     \item Reflection Layers
+  \end{itemize}
+  \item Source code is not available\footnote{\url{http://simon-foster.staff.shef.ac.uk/agdaatp}}
   \end{itemize}
@@
 \end{lrbox}
-
-\begin{frame}[fragile, label=after-reconstruction]
-\end{frame}
 
@@
 \only<4->{
-  \node[left= 1cm of apia] (tptp)
+  \node[below= 0.4cm of eagda] (tptp)
     {\includegraphics[scale=0.8]{figures/tptp}}};
@@
 
-\only<7->{ \node[below = 2.4 of agdafile, rectangle, text=white,fill=black, align=left, font=\tiny] (proved)
+\only<7->{ \node[left= 2.75cm of atp, rectangle, text=white,fill=black, align=left, font=\tiny] (proved)
 {
@@
 
+\begin{frame}[label=pending-work]{Pending Work}
+\begin{itemize}
+\item There are missing cases with the \texttt{simplify} inference
+\item Is not clear, how  \texttt{canonicalize} inference choose what
+normal form use to transform the formulas
+\item When Metis prove a goal, it first splits that goal in a list of
+subgoal, then we are working on verification of such splitting.
+\end{itemize}
+\end{frame}
+
 \begin{frame}[label=future-work]{Future Work}
@@
   \item Support First-Order Logic with Equality
-  \item Support another prover like \texttt{EProver}\textbf{
-}\end{itemize}
+  \item Support another prover like EProver or Vampire
+\end{itemize}
 \end{frame}

### 2017-04-29 slides/slides.tex
[ slides ] minor changes.

@@
 \definecolor{letour}{RGB}{101,41,105}
-
 % --------------------------------------------------------------------------
@@
 \institute{
+Master in Applied Mathematics\\
 Universidad EAFIT\\
@@
   {\includegraphics[scale=0.7]{figures/metis}\,
-  \footnote{It is available at \url{http://www.gilith.com/software/metis}}
+  \footnote{\url{http://www.gilith.com/software/metis}}
   };
@@
   {\includegraphics[scale=0.7]{figures/athena}
-  \footnote{It is available at \url{http://github.com/jonaprieto/athena}}
+  \footnote{\url{http://github.com/jonaprieto/athena}}
   };
@@
   {\includegraphics[scale=0.7]{figures/agda}
-  \footnote{It is available at \url{http://github.com/agda/agda}}
+  \footnote{\url{http://github.com/agda/agda}}
   };
@@
   \begin{itemize}
-  \item Is a language\footnote{Is available at
-        \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}}
+  \item Is a language\footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}}
         to encode problems \citep{Sut09}
@@
 \begin{frame}[fragile, label=tptp-examples]{TPTP Examples}{From Prop-Pack repository
-  \footnote{Is available at \url{http://github.com/jonaprieto/prop-pack}}}
+  \footnote{\url{http://github.com/jonaprieto/prop-pack}}}
 
@@
   \begin{equation*}
-  conjunct (ϕ₁ ∧  ϕ₂ ∧ ⋯ ∧ \mathbf{ϕᵢ} ∧ ⋯ ∧ ϕ\_n, \mathbf{ϕᵢ}) ⟶ \mathbf{ϕᵢ}
+  conjunct (ϕ₁ ∧  ϕ₂ ∧ ⋯ ∧ \mathbf{ϕᵢ} ∧ ⋯ ∧ \phi_n, \mathbf{ϕᵢ}) ⟶ \mathbf{ϕᵢ}
   \end{equation*}
@@
 \vfill
-
+\gobackreconstruction
 \end{frame}
@@
   \includegraphics[scale=0.8]{figures/apia}
-  \footnote{Haskell program for proving first-order theorems written in Agda using ATPs.
-    \url{https://github.com/asr/apia}}}
+  \footnote{\url{https://github.com/asr/apia}}}
   };
@@
 normal form use to transform the formulas
-\item When Metis prove a goal, it first splits that goal in a list of
-subgoal, then we are working on verification of such splitting.
+\item Splitting a goal in a list of subgoals is not verified yet
 \end{itemize}
@@
 \begin{itemize}
-  \item Add shallow embedding in order to work with \texttt{Apia}
+  \item Add a shallow embedding in order to work with \texttt{Apia}
   \item Support First-Order Logic with Equality

### 2017-04-30 slides/slides.tex
[ slides ] djvu fonts added.

@@
     \tikzset{shift={(current page.center)}, xshift=11.7cm,yshift=-8.4cm}
-    \node[fill=plum,text=white, hyperlink node = reconstruction] (go) at (0,0) {\tiny Go Back};
+    \node[fill=plum,text=white, hyperlink node = reconstruction]
+      (go) at (0,0) {\tiny Go Back};
   \end{tikzpicture}}
@@
   , ItalicFont=SourceCodePro-It.ttf
-  ]{SourceCodePro-Semibold.ttf}
+  ]{SourceCodePro-Regular.ttf}
 \newfontfamily\SourceCodeIt{fonts/SourceCodePro-It.ttf}
@@
 \date{Agda Implementors’ Meeting XXV\\
-May 9-15th}
-\author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides\\
+May 9-15th 2017}
+\author[Jonathan Prieto-Cubides]{Jonathan Prieto-Cubides\\
 Joint work with Andr\'es Sicard-Ram\'irez}
@@
 
-% \subsection{Proof Reconstruction}
-
-% \subsubsection{Sledgehammer}
-% \subsubsection{Waldemesiter}
-
-% \subsection{Automatic Provers}
-
-% \subsubsection{TPTP Syntax}
-
-\begin{frame}{Bonus Slides}
-\end{frame}
-
-\begin{frame}[fragile, label=tptp-syntax]{TPTP Syntax}{Thousands of Problems for Theorem Provers}
+\begin{frame}[fragile, label=tptp-syntax]{\texttt{TPTP} Syntax}
+  {Thousands of Problems for Theorem Provers}
 
@@
       \item[\texttt{name}] to identify the formula within the problem
-      \item[\texttt{role}] axiom, definition, hypothesis, conjecture, among others
-      \item[\texttt{formula}] version in TPTTP format
+      \item[\texttt{role}] axiom, definition, hypothesis, conjecture
+      \item[\texttt{formula}] version in \texttt{TPTP} format
     \end{itemize}
@@
 
-\begin{frame}[fragile, label=tptp-examples]{TPTP Examples}{From Prop-Pack repository
-  \footnote{\url{http://github.com/jonaprieto/prop-pack}}}
+\begin{frame}[fragile, label=tptp-examples]{\texttt{TPTP} Examples}
 
@@
 
-\begin{frame}[label=metis]{Metis Theorem Prover}{\url{http://www.gilith.com/software/metis/}}
+\begin{frame}[label=metis]{\texttt{Metis} Theorem Prover
+  \footnote{\url{http://www.gilith.com/software/metis/}}}
  \tikz[overlay,remember picture]
@@
 
-Metis is an automatic theorem prover for First-Order Logic with equality
+\texttt{Metis} is an automatic theorem prover for First-Order Logic with Equality
+\citep{hurd2003first}
 \begin{block}{Why Metis?}
   \begin{itemize}
-    \item \href{https://github.com/gilith/metis}{Open source} implemented in Standard ML
+    \item \href{https://github.com/gilith/metis}{Open source} implemented in
+       \texttt{Standard ML}
     \item Each refutation step is one of
-      \href{http://www.gilith.com/software/metis/logical-kernel.txt}{\textbf{6 simple rules}}
+      \href{http://www.gilith.com/software/metis/logical-kernel.txt}{\textit{6 rules}}
     \item Reads problem in \hyperlink{tptp-syntax}{\texttt{TPTP} format}
@@
 
-\begin{frame}[fragile, label=metis-rules]{Inference Rules of Metis}
-\hyperlink{tstp-example}{TSTP} derivations by Metis exhibit these inferences
-\footnote{Inference rules found in proofs of Propositional Logic theorems}:
+\begin{frame}[fragile, label=metis-rules]{Inference Rules of \texttt{Metis}}
+\hyperlink{tstp-example}{TSTP} derivations by \texttt{Metis} exhibit these inferences
+\footnote{Inference rules found in proofs of Propositional Logic theorems}
 \vfill
@@
 {\renewcommand{\arraystretch}{1.3}%
-\begin{tabular}{|cl| }
+\begin{tabular}{|ll| }
 \hline
@@
 
-\subsubsection{TSTP Derivations}
-
-\begin{frame}[fragile, label=tstp-syntax]{TSTP Syntax}
+\begin{frame}[fragile, label=tstp-syntax]{\texttt{TSTP} Syntax}
 
@@
 
-A TSTP derivation
+A \texttt{TSTP} derivation
 \footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/QuickGuide/Derivations.html}}
@@
   \end{itemize}
-  \item Is a list of annotated formulas with the form:
+  \item Is a list of annotated formulas with the form
   \end{itemize}
@@
 
-where \textbf{\color{plum} source} typically is an inference record:
+where \texttt{\color{plum} source} typically is an inference record
 \begin{center}
@@
 \begin{tptp}
-$ metis --show proof basic-4.tptp
+$ metis --show proof problem.tptp
 fof(a, axiom, p).
@@
 
-\begin{frame}[fragile, label=tstp-dag]{DAG for the previous TSTP derivation found by \texttt{Metis} Prover}
+\begin{frame}[fragile, label=tstp-dag]{DAG Example}
 
@@
 \AxiomC{$p$}
-\RightLabel{\texttt{assume}}
+\RightLabel{\texttt{\tiny assume}}
 \UnaryInfC{$p$}
-\RightLabel{\texttt{strip}}
+\RightLabel{\texttt{\tiny strip}}
 \UnaryInfC{$p$}
-\RightLabel{\texttt{negate}}
+\RightLabel{\texttt{\tiny negate}}
 \UnaryInfC{$¬ p$}
 \AxiomC{$p$}
-\RightLabel{\texttt{canonicalize}}
+\RightLabel{\texttt{\tiny canonicalize}}
 \UnaryInfC{$p$}
-\RightLabel{\texttt{simplify}}
+\RightLabel{\texttt{\tiny simplify}}
 \BinaryInfC{$⊥$}
-\RightLabel{\texttt{canonicalize}}
+\RightLabel{\texttt{\tiny canonicalize}}
 \UnaryInfC{$⊥$}
@@
 
-\begin{frame}[fragile, label=athena]{Athena}
-  {\url{http://github.com/jonaprieto/athena}}
+\begin{frame}[fragile, label=athena]{\texttt{Athena}
+  \footnote{\url{http://github.com/jonaprieto/athena}}}
 
@@
 
-Is a Haskell program
-that translates proofs given by Metis Prover
-in \texttt{TSTP} format to Agda code.\\
+Is a \texttt{Haskell} program
+that translates proofs given by \texttt{Metis} Prover
+in \texttt{TSTP} format to \texttt{Agda} code\\
 
@@
     \item Analysis of inference rules used in the \texttt{TSTP} derivation
-    \item Agda code generation
+    \item \texttt{Agda} code generation
 \begin{table}[!ht]
@@
 \hline
-\texttt{\hyperlink{agda-prop}{Agda-Prop}}& axioms and theorems of Classical Propositional Logic\\
-\texttt{\hyperlink{agda-metis}{Agda-Metis}} & versions of the inference rules used by Metis\\
+\texttt{\hyperlink{agda-prop}{\texttt{Agda-Prop}}}& axioms and theorems of Classical Propositional Logic\\
+\texttt{\hyperlink{agda-metis}{\texttt{Agda-Metis}}} & versions of the inference rules used by \texttt{Metis}\\
 \hline
@@
 
-\begin{frame}[fragile, label=agda-prop-2]{Agda-Prop Library}
-  {\url{https://github.com/jonaprieto/agda-prop}}
-\begin{itemize}
-  \item Propositional Logic + PEM ($Γ ⊢ ϕ ∨ ¬ ϕ$)
+\begin{frame}[fragile, label=agda-prop-2]{\texttt{Agda-Prop} Library
+  \footnote{\url{https://github.com/jonaprieto/agda-prop}}}
+\begin{itemize}
+  \item Intuitionistic Propositional Logic + PEM ($Γ ⊢ ϕ ∨ ¬ ϕ$)
   \item A data type for formulas
@@
 
-\begin{frame}[fragile, label=agda-prop]{Agda-Prop Library}
-  {\url{https://github.com/jonaprieto/agda-prop}}
+\begin{frame}[fragile, label=agda-prop]{\texttt{Agda-Prop} Library
+  \footnote{\url{https://github.com/jonaprieto/agda-prop}}}
 \begin{itemize}
@@
 $∨$-intro$₂$, $∨$-elim, $⇒$-intro, $⇒$-elim, $⇔$-intro,
-$⇔$-elim$₁$, $⇔$-elim$₂$
+$⇔$-elim$₁$, $⇔$-elim$₂$.
 \end{agda}
@@
 $∨$-equiv, $¬∨$-to-$¬∧¬$, $¬∧¬$-to-$¬∨$, $∨$-dmorgan,
-$¬¬∨¬¬$-to-$∨$, cnf, nnf, dnf, RAA, ...
-\end{agda}
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile, label=agda-metis]{Agda-Metis Library}
-  {\url{https://github.com/jonaprieto/agda-metis}}
+$¬¬∨¬¬$-to-$∨$, cnf, nnf, dnf, RAA, $\cdots$
+\end{agda}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile, label=agda-metis]{\texttt{Agda-Metis} Library
+  \footnote{\url{https://github.com/jonaprieto/agda-metis}}}
 \vfill
@@
 {\renewcommand{\arraystretch}{1.3}%
-\begin{tabular}{|clc|}
+\begin{tabular}{|lll|}
 \hline
@@
 \texttt{simplify} & applies over a list of formula to simplify them &\texttt{atp-simplify}\\
-\texttt{strip} & splits a formula into subgoals &\texttt{strip}\\[1ex]
+\texttt{strip} & splits a formula into subgoals &\texttt{atp-strip}\\[1ex]
 \hline
@@
 
-\begin{frame}[fragile, label=atp-conjunct]{Agda-Metis: Conjunct Inference}
-   {\url{https://github.com/jonaprieto/agda-metis}}
+\begin{frame}[fragile, label=atp-conjunct]{\texttt{Agda-Metis}: Conjunct Inference
+  \footnote{\url{https://github.com/jonaprieto/agda-metis}}}
 \begin{itemize}
@@
 
-\item Function\footnote{\label{note-conjunct}Excerpt from the \texttt{Agda-Metis} library available in  \texttt{ATP.Metis.Rules.Conjunct} module.}:
+\item Function\footnote{\label{note-conjunct}Excerpt from the \texttt{Agda-Metis}
+library available in  \texttt{ATP.Metis.Rules.Conjunct} module}:
 \begin{agda}
@@
 atp-conjunct {_} {$φ ⇔ φ₁$} _ = id
-atp-conjunct {_} {$¬ φ$}    _ = id
+atp-conjunct {_} {$¬\,φ$}   _ = id
 \end{agda}
@@
 
-\begin{frame}[fragile, label=agda-file]{Agda Code Example}{Generated by Athena Tool}
+\begin{frame}[fragile, label=agda-file]{\texttt{Agda} Code Example}
+  {Generated by \texttt{Athena} Tool}
 
@@
   \item The problem is $p ∧ q ⊢ q ∧ p$
-  \item In TPTP format
+  \item In \texttt{TPTP} format
 \begin{tptp}
@@
 \begin{column}{0.2\textwidth}  %%<--- here
-   \begin{tikzpicture}[overlay, remember picture]
+   \begin{tikzpicture}[overlay, remember picture, scale=2]
 % \tikzset{shift={(current page.north)}, xshift=cm,yshift=-2cm}
@@
 
-\begin{frame}[fragile, allowframebreaks]{TSTP derivation}
+\begin{frame}[fragile, allowframebreaks]{\texttt{TSTP} Derivation}
 \begin{tptp}
@@
 
-\begin{frame}[fragile, label=verified-example]{$p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
+\begin{frame}[fragile, label=verified-example]{$p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
 \vfill
@@
 \begin{agda}
-p : Prop
-p = Var (# 0)
-q : Prop
-q = Var (# 1)
+p, q, a, goal, subgoal$₀$, subgoal$₁$ : Prop
+
+-- Axiom.
+a = (p $∧$ q)
+
+-- Premise.
+$Γ$ : Ctxt
+$Γ$ = [ a ]
+
+-- Conjecture.
+goal = (q $∧$ p)
+
+-- Subgoals.
+
+subgoal$₀$ = q
+
+subgoal$₁$ = (q $⇒$ p)
+\end{agda}
+\end{frame}
+
+\begin{frame}[fragile, label=verified-example-2]{$p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
+\vfill
+\begin{agda}
 -- Axiom.
@@
 a = (p $∧$ q)
--- Premise.
-$Γ$ : Ctxt
-$Γ$ = [ a ]
--- Conjecture.
-goal : Prop
-goal = (q $∧$ p)
--- Subgoals.
-subgoal$₀$ : Prop
-subgoal$₀$ = q
-subgoal$₁$ : Prop
-subgoal$₁$ = (q $⇒$ p)
-\end{agda}
-\end{frame}
-
-\begin{frame}[fragile, label=verified-example-2]{$p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
-\vfill
-\begin{agda}
--- Axiom.
-a : Prop
-a = (p $∧$ q)
+
 -- Subgoal.
@@
 
-\begin{frame}[fragile, label=verified-example-3]{$p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
+\begin{frame}[fragile, label=verified-example-3]{$p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
 \vfill
@@
 \begin{frame}[fragile, label=failure-example]{Bug in the Printing of the Proof}
-  {Metis' Issue: \url{https://github.com/gilith/metis/issues/2}}
+  {\texttt{Metis}' Issue: \url{https://github.com/gilith/metis/issues/2}}
 % {}
@@
 \begin{itemize}
-\item Isabelle/HOL mature tool
-\item Metis ported within Isabelle
+\item \texttt{Isabelle}/\texttt{HOL} mature tool
+\item \texttt{Metis} ported within \texttt{Isabelle}
 \item Reconstruct proofs of well-known ATPs: \texttt{EProver}, \texttt{Vampire},
-among others using SystemOnTPTP server
+among others using \texttt{SystemOnTPTP} server
 \end{itemize}
@@
 
-\begin{block}{Integrating Waldmeister into Agda} \citep{Foster2011}
-\begin{itemize}
-  \item Framework for a integration between Agda and ATPs
+\begin{block}{Integrating \texttt{Waldmeister} into \texttt{Agda}} \citep{Foster2011}
+\begin{itemize}
+  \item Framework for a integration between \texttt{Agda} and ATPs
   \begin{itemize}
@@
 
-\begin{frame}[fragile]{Related Work: Apia}
-  {Proving first-order theorems written in Agda using automatic theorem provers for first-order logic}
-
-\only<1-2>{At the moment, the communication between Agda and
-the ATPs is unidirectional because the ATPs are being used as oracles \citep{Sicard2015}.}
-\only<1-2>{\vfill}
+\begin{frame}[fragile]{Related Work: \texttt{Apia}}
+  {Proving First-Order theorems written in \texttt{Agda} using automatic theorem provers for First-Order Logic}
+
+\only<1>{At the moment, the communication between \texttt{Agda} and
+the ATPs is unidirectional because the ATPs are being used as oracles \citep{Sicard2015}
+\vfill
+}
 
@@
   \includegraphics[scale=0.8]{figures/eagda}
-  \footnote{Development version of Agda in order to handle a new built-in ATP-pragma.
-    \url{https://github.com/asr/eagda}}
+  \footnote{\url{https://github.com/asr/eagda}}
   }
@@
 \begin{itemize}
-  \item Add a shallow embedding in order to work with \texttt{Apia}
+  \item Integration with \texttt{Apia}
   \item Support First-Order Logic with Equality
-  \item Support another prover like EProver or Vampire
-\end{itemize}
+  \item Support another prover like \texttt{EProver} or \texttt{Vampire}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
 \end{frame}

### 2017-05-03 slides/slides.tex
[ slides ] new use of pygments-cagda.

@@
-\documentclass[xetex, hyperref={pdfpagelabels=false}]{beamer}
+\documentclass[10pt, xetex, hyperref={pdfpagelabels=false}]{beamer}
 
@@
 \usepackage{lmodern}
+
 \usepackage{mylst}
@@
 
-% \usetikzlibrary{shapes.geometric,shapes.symbols,shadows}
-
 \newcommand{\gobackreconstruction}{
   \begin{tikzpicture}[overlay, remember picture, scale=0.5]
-    \tikzset{shift={(current page.center)}, xshift=11.7cm,yshift=-8.4cm}
+    \tikzset{shift={(current page.center)}, xshift=11.8cm,yshift=-8.4cm}
     \node[fill=plum,text=white, hyperlink node = reconstruction]
@@
   \vskip 0pt%
-  % \vspace*{1mm}%
-}
-
-% title in the frame
+}
+
 \setbeamerfont{frametitle}{size=\small,series=\bfseries}
@@
 % --------------------------------------------------------------------------
-
 \usefonttheme{professionalfonts}
@@
 
+\newfontfamily\djvu[ExternalLocation=fonts/
+  , BoldFont=DejaVuSansMono-Bold.ttf
+  , BoldItalicFont=DejaVuSansMono-BoldOblique.ttf
+  , ItalicFont=DejaVuSansMono-Oblique.ttf
+  ]{DejaVuSansMono.ttf}
+
+\setmonofont[ExternalLocation=fonts/
+, BoldFont=DejaVuSansMono-Bold.ttf
+, BoldItalicFont=DejaVuSansMono-BoldOblique.ttf
+, ItalicFont=DejaVuSansMono-Oblique.ttf
+]{DejaVuSansMono.ttf}
+
 \setmathfont[ExternalLocation=fonts/
-  , BoldFont=xits-mathbold.otf
-  ]{xits-math.otf}
-\newfontfamily\mathfont{fonts/xits-math.otf}
+  ]{DejaVuMathTeXGyre.ttf}
+\newfontfamily\mathfont{fonts/DejaVuMathTeXGyre.ttf}
 
@@
 
-\setmonofont[ExternalLocation=fonts/
+% \setmonofont[ExternalLocation=fonts/
+%   , BoldFont=SourceCodePro-Semibold.ttf
+%   , BoldItalicFont=SourceCodePro-SemiboldIt.ttf
+%   , ItalicFont=SourceCodePro-It.ttf
+%   ]{SourceCodePro-Regular.ttf}
+
+\newfontfamily\sourcecode[ExternalLocation=fonts/
   , BoldFont=SourceCodePro-Semibold.ttf
@@
   ]{SourceCodePro-Regular.ttf}
-\newfontfamily\SourceCodeIt{fonts/SourceCodePro-It.ttf}
-\newfontfamily\SourceCode{fonts/SourceCodePro-Regular.ttf}
-
-\newcommand{\problemtptp}[3][c]
-  {\lstinputlisting[style=tptp,caption=#2, firstline=#3, label=custom#1]{#2}}
-\newcommand{\solutiontstp}[2][c]
-  {\lstinputlisting[style=tptp,caption=#2, firstline=5, label=custom#1]{#2}}
+
+\usepackage{minted}
+\setminted[cagda]{
+  bgcolor   = aliceblue
+, fontsize  = \footnotesize
+, frame     = none
+% , framerule = 0.4pt
+% , framesep  = 0pt
+, style     = cagda
+}
 
@@
     backend=biber
+  , doi=false
+  , eprint=false
+  , isbn=false
+  , natbib=true
+  , sortlocale=en_US
   , style=authoryear-icomp
-  , sortlocale=en_US
-  , natbib=true
   , url=false
-  , doi=false
-  , isbn=false
-  , eprint=false
 ]{biblatex}
@@
 \title[Proof Reconstruction in Classical Propositional Logic]
-  {\textbf{Proof Reconstruction in Classical Propositional Logic}
-}
+  {\textbf{Proof Reconstruction in Classical Propositional Logic}}
 \subtitle{(Work in Progress)}
@@
 \author[Jonathan Prieto-Cubides]{Jonathan Prieto-Cubides\\
-Joint work with Andr\'es Sicard-Ram\'irez}
+(Joint work with Andr\'es Sicard-Ram\'irez)}
 \institute{
@@
 
-\section{Introduction}
-
 \begin{frame}[fragile, label=overview]{Proof Reconstruction: Overview}
@@
 \only<6->{
-\node[left = 0.5cm of athena, hyperlink node=agda-file] (agdafile)
+\node[left = 0.6cm of athena, hyperlink node=agda-file] (agdafile)
   {\includegraphics[scale=0.7]{figures/agdafile}
@@
   {\includegraphics[scale=0.7]{figures/athena}};
-\node[left = 0.5cm of athena, hyperlink node=agda-file] (agdafile)
+\node[left = 0.6cm of athena, hyperlink node=agda-file] (agdafile)
   {\includegraphics[scale=0.7]{figures/agdafile}};
@@
 
-\subsection{Motivation}
-
 \begin{frame}[fragile, label=tptp-syntax]{\texttt{TPTP} Syntax}
@@
     \begin{itemize}
-      \item[\texttt{language}] FOF or CNF %THF, TFF,
+      \item[\texttt{language}] FOF or CNF
       \item[\texttt{name}] to identify the formula within the problem
@@
 
- \tikz[overlay,remember picture]
-  \node at (0.93\textwidth, -0.3cm)
-    {\includegraphics[width=0.15\textwidth]{figures/metis}};
+ % \tikz[overlay,remember picture]
+ %  \node at (0.93\textwidth, -0.3cm)
+ %    {\includegraphics[width=0.15\textwidth]{figures/metis}};
 
@@
   \item A data type for formulas
-\begin{agda}
+  \vspace*{1mm}
+
+\begin{minted}{cagda}
 data Prop : Set where
   Var  : Fin n → Prop           -- Variables.
-  $⊤$    : Prop                   -- Top (truth).
-  $⊥$    : Prop                   -- Bottom (falsum).
-  _$∧$_  : ($φ$ $ψ$ : Prop) → Prop    -- Conjunction.
-  _$∨$_  : ($φ$ $ψ$ : Prop) → Prop    -- Disjunction.
-  _$⇒$_  : ($φ$ $ψ$ : Prop) → Prop    -- Implication.
-  _$⇔$_  : ($φ$ $ψ$ : Prop) → Prop    -- Biimplication.
-  $¬$_   : ($φ$ : Prop) → Prop      -- Negation.
-\end{agda}
+  ⊤    : Prop                   -- Top (truth).
+  ⊥    : Prop                   -- Bottom (falsum).
+  _∧_  : (φ ψ : Prop) → Prop    -- Conjunction.
+  _∨_  : (φ ψ : Prop) → Prop    -- Disjunction.
+  _⇒_  : (φ ψ : Prop) → Prop    -- Implication.
+  _⇔_  : (φ ψ : Prop) → Prop    -- Biimplication.
+  ¬_   : (φ : Prop)   → Prop    -- Negation.
+\end{minted}
 \end{itemize}
@@
   \item A data type for theorems
-\begin{agda}
-data _$⊢$_ : ($Γ$ : Ctxt)($φ$ : Prop) → Set
-\end{agda}
+  \vspace*{1mm}
+\begin{minted}{cagda}
+data _⊢_ : (Γ : Ctxt)(φ : Prop) → Set
+\end{minted}
 
 \item Constructors
-\begin{agda}
-assume, axiom, weaken, $⊤$-intro, $⊥$-elim, $¬$-intro,
-$¬$-elim, $∧$-intro, $∧$-proj$₁$, $∧$-proj$₂$, $∨$-intro$₁$,
-$∨$-intro$₂$, $∨$-elim, $⇒$-intro, $⇒$-elim, $⇔$-intro,
-$⇔$-elim$₁$, $⇔$-elim$₂$.
-\end{agda}
+  \vspace*{1mm}
+
+\begin{minted}{cagda}
+assume, axiom, weaken, ⊤-intro, ⊥-elim, ¬-intro,
+¬-elim, ∧-intro, ∧-proj₁, ∧-proj₂, ∨-intro₁,
+∨-intro₂, ∨-elim, ⇒-intro, ⇒-elim, ⇔-intro,
+⇔-elim₁, ⇔-elim₂.
+\end{minted}
   \item Natural deduction proofs for more than 71 theorems
-\begin{agda}
-$⇔$-equiv, $⇔$-assoc, $⇔$-comm, $⇒-⇔-¬∨$, $⇔-¬$-to-$¬$,
-$¬⇔$-to-$¬$, $¬¬$-equiv, $⇒⇒-⇔-∧⇒$, $⇔$-trans, $∧$-assoc,
-$∧$-comm, $∧$-dist, $¬∧$-to-$¬∨¬$, $¬∨¬$-to-$¬∧$, $¬∨¬-⇔-¬∧$,
-subst$⊢∧₁$, subst$⊢∧₂$, $∨$-assoc, $∨$-comm, $∨$-dist,
-$∨$-equiv, $¬∨$-to-$¬∧¬$, $¬∧¬$-to-$¬∨$, $∨$-dmorgan,
-$¬¬∨¬¬$-to-$∨$, cnf, nnf, dnf, RAA, $\cdots$
-\end{agda}
+  \vspace*{1mm}
+\begin{minted}{cagda}
+⇔-equiv, ⇔-assoc, ⇔-comm, ⇒-⇔-¬∨, ⇔-¬-to-¬,
+¬⇔-to-¬, ¬¬-equiv, ⇒⇒-⇔-∧⇒, ⇔-trans, ∧-assoc,
+∧-comm, ∧-dist, ¬∧-to-¬∨¬, ¬∨¬-to-¬∧, ¬∨¬-⇔-¬∧,
+subst⊢∧₁, subst⊢∧₂, ∨-assoc, ∨-comm, ∨-dist,
+∨-equiv, ¬∨-to-¬∧¬, ¬∧¬-to-¬∨, ∨-dmorgan,
+¬¬∨¬¬-to-∨, cnf, nnf, dnf, RAA, ...
+\end{minted}
 \end{itemize}
@@
 library available in  \texttt{ATP.Metis.Rules.Conjunct} module}:
-\begin{agda}
+\vspace*{1mm}
+\begin{minted}{cagda}
 conjunct : Prop → Prop → Prop
-conjunct $(φ \wedge ψ)$ $ω$ with $⌊$ eq $φ$ $ω$ $⌋$ | $⌊$ eq ψ $ω$ $⌋$
-... | true  | _     = $φ$
-... | false | true  = $ψ$
-... | false | false = conjunct $φ$ $ω$
-conjunct $φ$ $ω$       = $φ$
-\end{agda}
+conjunct (φ ∧ ψ) ω with ⌊ eq φ ω ⌋ | ⌊ eq ψ ω ⌋
+... | true  | _     = φ
+... | false | true  = ψ
+... | false | false = conjunct φ ω
+conjunct φ ω        = φ
+\end{minted}
 \item Theorem\textsuperscript{\ref{note-conjunct}}
-\begin{agda}
+\vspace*{1mm}
+\begin{minted}{cagda}
 atp-conjunct
-  : ∀ $\{Γ\}$ $\{φ\}$
-  → $(ω : Prop)$
-  → $Γ \vdash φ$
-  → $Γ \vdash$ conjunct $φ$ $ω$
-\end{agda}
+  : ∀ {Γ} {φ}
+  → (ω :Prop)
+  → Γ ⊢ φ
+  → Γ ⊢ conjunct φ ω
+\end{minted}
 \end{itemize}
@@
 \vfill
-\begin{agda}
+\begin{minted}{cagda}
 atp-conjunct
-  : $∀ \{Γ\} \{φ\}$
-  → ($ω$ : Prop)
-  → $Γ ⊢ φ$
-  → $Γ ⊢$ conjunct $φ\ ω$
-
-atp-conjunct $\{Γ\}$ $\{φ ∧ ψ\}$ $ω$ $Γ⊢φ$ with $⌊$ eq $φ$ $ω$ $⌋$ | $⌊$ eq $ψ$ $ω$ $⌋$
-... | true  | _     = $∧$-proj$₁$ $Γ⊢φ$
-... | false | true  = $∧$-proj$₂$ $Γ⊢φ$
+  : ∀ {Γ} {φ}
+  → (ω : Prop)
+  → Γ ⊢ φ
+  → Γ ⊢ conjunct φ ω
+
+atp-conjunct {Γ} {φ ∧ ψ} ω Γ⊢φ
+  with ⌊ eq φ ω ⌋ | ⌊ eq ψ ω ⌋
+... | true  | _     = ∧-proj₁ Γ⊢φ
+... | false | true  = ∧-proj₂ Γ⊢φ
 ... | false | false =
-  atp-conjunct $\{Γ = Γ\}$ $\{φ = φ\}$ $ω$ ($∧$-proj$₁$ $Γ⊢φ$)
+  atp-conjunct {Γ = Γ} {φ = φ} ω (∧-proj₁ Γ⊢φ)
 atp-conjunct {_} {Var x}  _ = id
-atp-conjunct {_} {$⊤$}      _ = id
-atp-conjunct {_} {$⊥$}      _ = id
-atp-conjunct {_} {$φ ∨ φ₁$} _ = id
-atp-conjunct {_} {$φ ⇒ φ₁$} _ = id
-atp-conjunct {_} {$φ ⇔ φ₁$} _ = id
-atp-conjunct {_} {$¬\,φ$}   _ = id
-\end{agda}
+atp-conjunct {_} {⊤}      _ = id
+atp-conjunct {_} {⊥}      _ = id
+atp-conjunct {_} {φ ∨ ψ}  _ = id
+atp-conjunct {_} {φ ⇒ ψ}  _ = id
+atp-conjunct {_} {φ ⇔ ψ}  _ = id
+atp-conjunct {_} {¬ φ}    _ = id
+\end{minted}
 \vfill
@@
 \begin{frame}[fragile, label=verified-example]{$p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
-\vfill
-Definitions
-\begin{agda}
-p, q, a, goal, subgoal$₀$, subgoal$₁$ : Prop
+\begin{minted}{cagda}
+p, q, a, goal, subgoal₀, subgoal₁ : Prop
 
 -- Axiom.
-a = (p $∧$ q)
+
+a = (p ∧ q)
 
 -- Premise.
-$Γ$ : Ctxt
-$Γ$ = [ a ]
+
+Γ : Ctxt
+Γ = [ a ]
 
 -- Conjecture.
-goal = (q $∧$ p)
+
+goal = (q ∧ p)
 
@@
 
-subgoal$₀$ = q
-
-subgoal$₁$ = (q $⇒$ p)
-\end{agda}
+subgoal₀ = q
+subgoal₁ = (q ⇒ p)
+\end{minted}
 \end{frame}
@@
 \vfill
-\begin{agda}
--- Axiom.
+\begin{minted}{cagda}
 a : Prop
-a = (p $∧$ q)
-
--- Subgoal.
-subgoal$₀$ : Prop
-subgoal$₀$ = q
-
-proof$₀$ : $Γ ⊢$ subgoal$₀$
-proof$₀$ =
+a = (p ∧ q)
+
+subgoal₀ : Prop
+subgoal₀ = q
+
+proof₀ : Γ ⊢ subgoal₀
+proof₀ =
   (RAA
@@
           (atp-strip
-            (assume $\{Γ = Γ\}$ (atp-negate subgoal$₀$))))
+            (assume {Γ = Γ} (atp-negate subgoal₀))))
         (atp-conjunct (q)
           (atp-canonicalize
-            (weaken (atp-negate subgoal$₀$)
-              (assume $\{Γ = ∅\}$ a)))))))
-\end{agda}
+            (weaken (atp-negate subgoal₀)
+              (assume {Γ = ∅} a)))))))
+\end{minted}
 \vfill
@@
 \vfill
-\begin{agda}
-subgoal$₁$ : Prop
-subgoal$₁$ = (q $⇒$ p)
-
-proof$₁$ : $Γ ⊢$ subgoal$₁$
-proof$₁$ =
+\begin{minted}{cagda}
+subgoal₁ : Prop
+subgoal₁ = (q ⇒ p)
+
+proof₁ : Γ ⊢ subgoal₁
+proof₁ =
   (RAA
@@
           (atp-canonicalize
-            (weaken (atp-negate subgoal$₁$)
-              (assume $\{Γ = ∅\}$ a))))
+            (weaken (atp-negate subgoal₁)
+              (assume {Γ = ∅} a))))
         (atp-simplify
@@
             (atp-strip
-              (assume $\{Γ = Γ\}$ (atp-negate subgoal$₁$))))
+              (assume {Γ = Γ} (atp-negate subgoal₁))))
           (atp-conjunct (p)
             (atp-canonicalize
-              (weaken (atp-negate subgoal$₁$)
-                (assume $\{Γ = ∅\}$ a))))))))
-\end{agda}
+              (weaken (atp-negate subgoal₁)
+                (assume {Γ = ∅} a))))))))
+\end{minted}
 \vfill
@@
 \begin{frame}[fragile, label=verified-example-4]{$p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
-\begin{agda}
-proof : $Γ ⊢$ goal
+\begin{minted}{cagda}
+Γ : Ctxt
+Γ = [ a ]
+
+proof₀ : Γ ⊢ subgoal₀
+proof₁ : Γ ⊢ subgoal₁
+
+proof : Γ ⊢ goal
 proof =
-  $⇒$-elim
+  ⇒-elim
     atp-splitGoal
-    ($∧$-intro proof$₀$ proof$₁$)
-\end{agda}
+    (∧-intro proof₀ proof₁)
+\end{minted}
 \gobackreconstruction
@@
 
-\begin{lrbox}{\agdapragma}
-\begin{agda}
-module Or where
-
-data _OR_ (A B : Set) : Set where
-  inj1 : A → A OR B
-  inj2 : B → A OR B
-
-postulate
-  A B    : Set
-  OR-comm : A OR B → B OR A
-{-# ATP prove OR-comm #-}
-\end{agda}
-\end{lrbox}
-
 \begin{frame}[fragile]{Related Work: \texttt{Apia}}
@@
 }
+\only<1>{
+\inputminted{cagda}{Or.agda}
+}
 
 \begin{tikzpicture}
-\only<1->{ \node(agdafile) at (0,0){
+
+\only<2->{ \node(agdafile) at (0,0){
   \includegraphics[scale=0.8]{figures/agda-pragmas}}};
-\only<1>{
-  \node[fill=aliceblue, rectangle, right = 2.5cm of agdafile] (atp-pragmas){
-  \scalebox{0.9}{\usebox\agdapragma}
-  }
-  };
 
@@
 
-\begin{frame}[label=references]{References}
+\begin{frame}[label=references, allowframebreaks]{References}
 \printbibliography

### 2017-05-09 slides/slides.tex
[ slides ] last corrections.

@@
     [wd=.8\paperwidth,ht=2.3ex,dp=1ex,left]{headFoot}%
-    \hspace*{2ex}\textbf\insertshorttitle\hspace*{2mm}|\hspace*{2mm}\textbf\insertshortauthor
+    \hspace*{2ex}\textbf\insertshorttitle\hspace*{2mm}|
+    \hspace*{2mm}\textbf\insertshortauthor
   \end{beamercolorbox}%
@@
 
-\setbeamerfont{framesubtitle}{size=\normalfont\tiny\itshape}
-\setbeamercolor{framesubtitle}{fg=white, bg=plum}
+\setbeamerfont{framesubtitle}{size=\normalfont\tiny}
+\setbeamercolor{framesubtitle}{fg=white, bg=plum!80!black}
 
@@
     \item Each refutation step is one of
-      \href{http://www.gilith.com/software/metis/logical-kernel.txt}{\textit{6 rules}}
+      \hyperlink{metis-inference-rules}{\textit{six rules}}
     \item Reads problem in \hyperlink{tptp-syntax}{\texttt{TPTP} format}
@@
   \begin{equation*}
-  conjunct (ϕ₁ ∧  ϕ₂ ∧ ⋯ ∧ \mathbf{ϕᵢ} ∧ ⋯ ∧ \phi_n, \mathbf{ϕᵢ}) ⟶ \mathbf{ϕᵢ}
+  \text{conjunct}(ϕ₁ ∧  ϕ₂ ∧ ⋯ ∧ \mathbf{ϕᵢ} ∧ ⋯ ∧ \phi_n, \mathbf{ϕᵢ}) ⟶ \mathbf{ϕᵢ}
   \end{equation*}
@@
 \begin{minted}{cagda}
+-- Premise.
+
 Γ : Ctxt
 Γ = [ a ]
+
+-- Conjecture.
+
+goal = (q ∧ p)
+
+-- Subgoals.
+
+subgoal₀ = q
+subgoal₁ = (q ⇒ p)
+
+-- Proof
 
@@
 \begin{frame}[fragile, label=failure-example]{Bug in the Printing of the Proof}
-  {\texttt{Metis}' Issue: \url{https://github.com/gilith/metis/issues/2}}
+  {\texttt{Metis}' v2.3 (release 20161108) - Issue\footnote{\url{https://github.com/gilith/metis/issues/2}}}
 % {}
-% \begin{tptp}
-% $ cat problem.tptp
-% fof(goal, conjecture,
-%   ((p <=> q) <=> r) <=> (p <=> (q <=> r))).
-% \end{tptp}
 \begin{tptp}
-$ metis --version
-metis 2.3 (release 20161108)
+$ cat problem.tptp
+fof(goal, conjecture,
+  ((p <=> q) <=> r) <=> (p <=> (q <=> r))).
+\end{tptp}
+\begin{tptp}
 $ metis --show proof problem.tptp
@@
 
+\begin{frame}[fragile, label=failure-example]{Bug in the Printing of the Proof}
+  {\texttt{Metis}' v2.3 (release 20161108) - Issue\footnote{\url{https://github.com/gilith/metis/issues/2}}}
+
+\[ φ := ¬ p ∧ (¬ q ⇔ ¬ r) ∧ (¬ p ⇔ (¬ q ⇔ ¬ r))\]
+
+\begin{prooftree}
+\AxiomC{$\vdots$}
+\RightLabel{\scriptsize{canonicalize}}
+\UnaryInfC{$φ$}
+\RightLabel{\scriptsize{conjunct}}
+\UnaryInfC{$¬ p ⇔ (¬ q ⇔ ¬ r)$}
+
+\AxiomC{$\vdots$}
+\RightLabel{\scriptsize{canonicalize}}
+\UnaryInfC{$φ$}
+\RightLabel{\scriptsize{conjunct}}
+\UnaryInfC{$¬ q ⇔ ¬ r$}
+
+\AxiomC{$\vdots$}
+\RightLabel{\scriptsize{canonicalize}}
+\UnaryInfC{$φ$}
+\RightLabel{\scriptsize{conjunct}}
+\UnaryInfC{$¬ p$}
+
+\RightLabel{\scriptsize{simplify}}
+\TrinaryInfC{$\bot$}
+\end{prooftree}
+\pause
+The bug was caused by the conversion of \texttt{Xor} sets to \texttt{Iff} lists.
+After reporting this, Joe fixed the printing of \texttt{canonicalize} inference rule
+\[ φ := ¬ p ∧ (¬ q ⇔ ¬ r) ∧ (¬ p ⇔ (¬ q ⇔ {\color{red} r}))\]
+
+\end{frame}
+
 \begin{frame}[fragile, label=hammer]{Related Work}
@@
 \begin{frame}[fragile]{Related Work: \texttt{Apia}}
-  {Proving First-Order theorems written in \texttt{Agda} using automatic theorem provers for First-Order Logic}
+  {Proving First-Order theorems written in \texttt{Agda} using automatic
+  theorem provers for First-Order Logic}
 
@@
 \only<5->{ \node[below = 0.8cm of apia] (atp)
-  {\includegraphics[scale=0.8]{figures/atp}}};
+  {\includegraphics[scale=0.8]{figures/atp}
+  \footnote{\url{http://github.com/jonaprieto/online-atps}}}
+  };
 
@@
 \only<6->{\draw[->, very thick, dashed, gray] (atp) to (apia)};
-
 \end{tikzpicture}
@@
 
-\begin{frame}[label=future-work]{Future Work}
+\begin{frame}[label=future-work]{Contributions and Future Work}
+\vfill
+\begin{table}[!ht]
+\begin{center}
+\scalebox{0.8}{
+{\renewcommand{\arraystretch}{1.3}%
+\begin{tabular}{|ll|}
+\hline
+\textbf{Name} & \textbf{Purpose} \\
+\hline
+\href{http://github.com/jonaprieto/agda-prop}{\texttt{Agda-Prop}}     & lib. for syntax and theorems of Clasical Propositional Logic\\
+\href{http://github.com/jonaprieto/agda-metis}{\texttt{Agda-Metis}}   & lib. for versions of the inference rules used by \texttt{Metis}\\
+\href{http://github.com/jonaprieto/athena}{\texttt{Athena}}           & soft. Translator in Haskell for \texttt{Metis'} \texttt{TSTP} files to \texttt{Agda}\\
+\href{http://github.com/jonaprieto/online-atps}{\texttt{OnlineATPs}}  & soft. A client in Haskell for \texttt{SystemOnTPTP} of \texttt{TPTP} World\\[1ex]
+\hline
+\end{tabular}}
+}
+\end{center}
+\label{tab:library}
+\end{table}
+\vfill
+
 \begin{itemize}
@@
 
-\begin{frame}
-\end{frame}
-
-\begin{frame}[label=references, allowframebreaks]{References}
+\begin{frame}[fragile, label=references, allowframebreaks]{References}
 \printbibliography
@@
 
+\begin{frame}[fragile,label=metis-inference-rules]{\texttt{Metis}' Inference Rules}
+\vfill
+\begin{prooftree}
+\AxiomC{}
+\RightLabel{axiom}
+\UnaryInfC{$C$}
+\end{prooftree}
+\vfill
+\begin{prooftree}
+\AxiomC{}
+\RightLabel{assume $L$}
+\UnaryInfC{$L ∨ ¬ L$}
+\end{prooftree}
+\vfill
+\begin{prooftree}
+\AxiomC{$C$}
+\RightLabel{subst $σ$}
+\UnaryInfC{$σC$}
+\end{prooftree}
+\vfill
+\begin{prooftree}
+\AxiomC{$L ∨ C$}
+\AxiomC{$¬ L ∨ D$}
+\RightLabel{resolve $L$}
+\BinaryInfC{$C ∨ D$}
+\end{prooftree}
+\vfill
+\begin{prooftree}
+\AxiomC{}
+\RightLabel{refl $t$}
+\UnaryInfC{$t = t$}
+\end{prooftree}
+\vfill
+\begin{prooftree}
+\AxiomC{}
+\RightLabel{eq $L$ $p$ $t$}
+\UnaryInfC{$¬ (L[p] = t) ∨ ¬ L ∨ L[ p ↦ t]$}
+\end{prooftree}
+\vfill
+\end{frame}
+ \begin{tikzpicture}[overlay, remember picture, scale=0.5]
+    \tikzset{shift={(current page.center)}, xshift=11.8cm,yshift=-8.4cm}
+    \node[fill=plum,text=white, hyperlink node = metis]
+      (go) at (0,0) {\tiny Go Back};
+  \end{tikzpicture}
 \end{document}

### 2017-05-09 slides/slides.tex
[ slides ] added more footnotes.

@@
 \only<7->{
-\node[left = 0.5cm of agdafile, hyperlink node=agda] (agda)
+\node[left = 0.5cm of agdafile] (agda)
   {\includegraphics[scale=0.7]{figures/agda}
@@
   {\includegraphics[scale=0.7]{figures/agdafile}};
-\node[left = 0.5cm of agdafile, hyperlink node=agda] (agda)
+\node[left = 0.5cm of agdafile] (agda)
   {\includegraphics[scale=0.7]{figures/agda}};
@@
 \begin{itemize}
-    \item Parsing of \texttt{TSTP} language
-    \item Creation and analysis of \hyperlink{tstp-dag}{\textbf{DAG}} derivations
+    \item Parsing of \texttt{TSTP} language\footnote{\label{parsing}\url{https://github.com/agomezl/tstp2agda}}\textsuperscript{,}\footnote{\url{https://github.com/jonaprieto/tstp2agda}}
+    \item Creation\textsuperscript{\ref{parsing}} and analysis of \hyperlink{tstp-dag}{\textbf{DAG}} derivations
     \item Analysis of inference rules used in the \texttt{TSTP} derivation
@@
 
-Γ : Ctxt
 Γ = [ a ]
@@
   ⇒-elim
-    atp-splitGoal
+    atp-splitGoal            -- q ∧ (q ⇒ p) ⇒ p
     (∧-intro proof₀ proof₁)
@@
 
-\begin{frame}[fragile, label=failure-example]{Bug in the Printing of the Proof}
-  {\texttt{Metis}' v2.3 (release 20161108) - Issue\footnote{\url{https://github.com/gilith/metis/issues/2}}}
+\begin{frame}[fragile, label=failure-example]{Bug\footnote{\url{https://github.com/gilith/metis/issues/2}} in the Printing of the Proof}
+  {\texttt{Metis}' v2.3 (release 20161108)}
 % {}
@@
 \[ φ := ¬ p ∧ (¬ q ⇔ ¬ r) ∧ (¬ p ⇔ (¬ q ⇔ {\color{red} r}))\]
-
+\gobackreconstruction
 \end{frame}
@@
 \inputminted{cagda}{Or.agda}
+\begin{tikzpicture}[overlay, remember picture, scale=0.5]
+\tikzset{shift={(current page.center)}, xshift=6cm,yshift=-2cm}
+\node(agdafile) at (0,0){
+  \includegraphics[scale=0.8]{figures/agda-pragmas}};
+\end{tikzpicture}
 }
@@
 
-\only<7->{ \node[left= 2.75cm of atp, rectangle, text=white,fill=black, align=left, font=\tiny] (proved)
+\only<7->{ \node[left= 3cm of atp, rectangle, text=white,fill=black, align=left, font=\tiny] (proved)
 {
@@
 \begin{itemize}
-\item There are missing cases with the \texttt{simplify} inference
-\item Is not clear, how  \texttt{canonicalize} inference choose what
+\item Complete implementation for \texttt{simplify} inference\footnote{\url{https://github.com/gilith/metis/issues/3}}
+\item Complete implementation for \texttt{canonicalize} inference: what
 normal form use to transform the formulas
-\item Splitting a goal in a list of subgoals is not verified yet
+\item Complete implementation for Splitting a goal in a list of subgoals
 \end{itemize}
@@
 \hline
-\href{http://github.com/jonaprieto/agda-prop}{\texttt{Agda-Prop}}     & lib. for syntax and theorems of Clasical Propositional Logic\\
-\href{http://github.com/jonaprieto/agda-metis}{\texttt{Agda-Metis}}   & lib. for versions of the inference rules used by \texttt{Metis}\\
-\href{http://github.com/jonaprieto/athena}{\texttt{Athena}}           & soft. Translator in Haskell for \texttt{Metis'} \texttt{TSTP} files to \texttt{Agda}\\
-\href{http://github.com/jonaprieto/online-atps}{\texttt{OnlineATPs}}  & soft. A client in Haskell for \texttt{SystemOnTPTP} of \texttt{TPTP} World\\[1ex]
+\href{http://github.com/jonaprieto/agda-metis}{\texttt{Agda-Metis}}   & Implementation of \texttt{Metis}' inference rules\\
+\href{http://github.com/jonaprieto/agda-prop}{\texttt{Agda-Prop}}     & Syntax and theorems of Classical Propositional Logic\\
+\href{http://github.com/jonaprieto/athena}{\texttt{Athena}}           & Translator for \texttt{Metis'} \texttt{TSTP} files to \texttt{Agda}\\
+\href{http://github.com/jonaprieto/online-atps}{\texttt{OnlineATPs}}  & Client to use ATPs from \texttt{SystemOnTPTP} of \texttt{TPTP} World\\
+\href{http://github.com/jonaprieto/prop-pack}{\texttt{Prop-Pack}}     & Collection of \texttt{TPTP} problems to test \texttt{Athena}\\[1ex]
 \hline
@@
 \vfill
-\end{frame}
  \begin{tikzpicture}[overlay, remember picture, scale=0.5]
@@
   \end{tikzpicture}
+\end{frame}
 \end{document}

### 2017-05-10 slides/slides.tex
[ slides ] last changes.

@@
 
-\setbeamerfont{framesubtitle}{size=\normalfont\tiny}
+\setbeamerfont{framesubtitle}{size=\normalfont\scriptsize}
 \setbeamercolor{framesubtitle}{fg=white, bg=plum!80!black}
@@
   {\textbf{Proof Reconstruction in Classical Propositional Logic}}
-\subtitle{(Work in Progress)}
+\subtitle{(work in progress)}
 \date{Agda Implementors’ Meeting XXV\\
-May 9-15th 2017}
+Teknikparken, Chalmers, Gothenburg, Sweden\\
+May 11 2017\\
+}
 \author[Jonathan Prieto-Cubides]{Jonathan Prieto-Cubides\\
-(Joint work with Andr\'es Sicard-Ram\'irez)}
+(joint work with Andr\'es Sicard-Ram\'irez)}
 \institute{
@@
    \tikzset{shift={(current page.center)}}
-    \node[xshift=-4.5cm,yshift=-3.5cm] (eafit)
+    \node[xshift=-4.7cm,yshift=-3.2cm] (eafit)
       {\includegraphics[width=0.2\textwidth]{figures/eafit}};
-    \node[xshift=4.5cm,yshift=-3cm] (chalmers)
-      {\includegraphics[width=0.18\textwidth]{figures/chalmers}};
+    \node[xshift=4.7cm,yshift=-3cm] (chalmers)
+      {\includegraphics[width=0.17\textwidth]{figures/chalmers}};
   \end{tikzpicture}
@@
   {\includegraphics[scale=0.7]{figures/metis}\,
-  \footnote{\url{http://www.gilith.com/software/metis}}
+  \footnote{\url{http://www.gilith.com/software/metis}.}
   };
@@
   {\includegraphics[scale=0.7]{figures/athena}
-  \footnote{\url{http://github.com/jonaprieto/athena}}
+  \footnote{\url{http://github.com/jonaprieto/athena}.}
   };
@@
   {\includegraphics[scale=0.7]{figures/agda}
-  \footnote{\url{http://github.com/agda/agda}}
+  \footnote{\url{http://github.com/agda/agda}.}
   };
@@
   \begin{itemize}
-  \item Is a language\footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}}
+  \item Is a language\footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}.}
         to encode problems \citep{Sut09}
@@
       \item[\texttt{role}] axiom, definition, hypothesis, conjecture
-      \item[\texttt{formula}] version in \texttt{TPTP} format
+      \item[\texttt{formula}] formula in \texttt{TPTP} format
     \end{itemize}
@@
 \begin{tptp}
-fof(a, axiom, p).
+fof(myaxiom, axiom, p).
 fof(goal, conjecture, p).
@@
 \begin{frame}[label=metis]{\texttt{Metis} Theorem Prover
-  \footnote{\url{http://www.gilith.com/software/metis/}}}
+  \footnote{\url{http://www.gilith.com/software/metis/}.}}
  \tikz[overlay,remember picture]
@@
     \item Reads problem in \hyperlink{tptp-syntax}{\texttt{TPTP} format}
-    \item Outputs detailed proofs in \hyperlink{tstp-syntax}{\texttt{TSTP} format}
+    \item Outputs \textit{detailed} proofs in \hyperlink{tstp-syntax}{\texttt{TSTP} format}
   \end{itemize}
@@
 \begin{frame}[fragile, label=metis-rules]{Inference Rules of \texttt{Metis}}
-\hyperlink{tstp-example}{TSTP} derivations by \texttt{Metis} exhibit these inferences
-\footnote{Inference rules found in proofs of Propositional Logic theorems}
+\hyperlink{tstp-example}{\texttt{TSTP}} derivations by \texttt{Metis} exhibit these inferences\footnote{Inference rules found in proofs of Propositional Logic theorems.}
 \vfill
@@
 
-A \texttt{TSTP} derivation
-\footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/QuickGuide/Derivations.html}}
+A \texttt{TSTP} derivation\footnote{\url{http://www.cs.miami.edu/~tptp/TPTP/QuickGuide/Derivations.html}.}
 \begin{itemize}
@@
 \begin{tptp}
-inference(rule, useful info, parents)
+inference(rule, useful info, parents).
 \end{tptp}
@@
 \begin{itemize}
-  \item Proof found by \texttt{Metis} Prover for the problem $p ⊢ p$
+  \item Proof found by \texttt{Metis} for the problem $p ⊢ p$
 {\small
@@
 \begin{frame}[fragile, label=tstp-dag]{DAG Example}
-
 \vfill
@@
 \AxiomC{$p$}
-\RightLabel{\texttt{\tiny assume}}
+\RightLabel{\texttt{\scriptsize assume}}
 \UnaryInfC{$p$}
-\RightLabel{\texttt{\tiny strip}}
+\RightLabel{\texttt{\scriptsize strip}}
 \UnaryInfC{$p$}
-\RightLabel{\texttt{\tiny negate}}
+\RightLabel{\texttt{\scriptsize negate}}
 \UnaryInfC{$¬ p$}
 \AxiomC{$p$}
-\RightLabel{\texttt{\tiny canonicalize}}
+\RightLabel{\texttt{\scriptsize canonicalize}}
 \UnaryInfC{$p$}
-\RightLabel{\texttt{\tiny simplify}}
+\RightLabel{\texttt{\scriptsize simplify}}
 \BinaryInfC{$⊥$}
-\RightLabel{\texttt{\tiny canonicalize}}
+\RightLabel{\texttt{\scriptsize canonicalize}}
 \UnaryInfC{$⊥$}
@@
 \begin{frame}[fragile, label=athena]{\texttt{Athena}
-  \footnote{\url{http://github.com/jonaprieto/athena}}}
+  \footnote{\url{http://github.com/jonaprieto/athena}.}}
 
@@
 Is a \texttt{Haskell} program
-that translates proofs given by \texttt{Metis} Prover
+that translates proofs given by \texttt{Metis}
 in \texttt{TSTP} format to \texttt{Agda} code\\
@@
 \begin{itemize}
-    \item Parsing of \texttt{TSTP} language\footnote{\label{parsing}\url{https://github.com/agomezl/tstp2agda}}\textsuperscript{,}\footnote{\url{https://github.com/jonaprieto/tstp2agda}}
+    \item Parsing of \texttt{TSTP} language\footnote{\label{parsing}\url{https://github.com/agomezl/tstp2agda}.}\textsuperscript{,}\footnote{\url{https://github.com/jonaprieto/tstp2agda}.}
     \item Creation\textsuperscript{\ref{parsing}} and analysis of \hyperlink{tstp-dag}{\textbf{DAG}} derivations
@@
 \begin{frame}[fragile, label=agda-prop-2]{\texttt{Agda-Prop} Library
-  \footnote{\url{https://github.com/jonaprieto/agda-prop}}}
+  \footnote{\url{https://github.com/jonaprieto/agda-prop}.}}
 \begin{itemize}
@@
 data Prop : Set where
-  Var  : Fin n → Prop           -- Variables.
-  ⊤    : Prop                   -- Top (truth).
-  ⊥    : Prop                   -- Bottom (falsum).
-  _∧_  : (φ ψ : Prop) → Prop    -- Conjunction.
-  _∨_  : (φ ψ : Prop) → Prop    -- Disjunction.
-  _⇒_  : (φ ψ : Prop) → Prop    -- Implication.
-  _⇔_  : (φ ψ : Prop) → Prop    -- Biimplication.
-  ¬_   : (φ : Prop)   → Prop    -- Negation.
+  Var  : Fin n → Prop
+  ⊤    : Prop
+  ⊥    : Prop
+  _∧_  : (φ ψ : Prop) → Prop
+  _∨_  : (φ ψ : Prop) → Prop
+  _⇒_  : (φ ψ : Prop) → Prop
+  _⇔_  : (φ ψ : Prop) → Prop
+  ¬_   : (φ : Prop)   → Prop
 \end{minted}
@@
 \begin{frame}[fragile, label=agda-prop]{\texttt{Agda-Prop} Library
-  \footnote{\url{https://github.com/jonaprieto/agda-prop}}}
+  \footnote{\url{https://github.com/jonaprieto/agda-prop}.}}
 \begin{itemize}
@@
 \begin{frame}[fragile, label=agda-metis]{\texttt{Agda-Metis} Library
-  \footnote{\url{https://github.com/jonaprieto/agda-metis}}}
+  \footnote{\url{https://github.com/jonaprieto/agda-metis}.}}
 \vfill
@@
 \begin{frame}[fragile, label=atp-conjunct]{\texttt{Agda-Metis}: Conjunct Inference
-  \footnote{\url{https://github.com/jonaprieto/agda-metis}}}
+  \footnote{\url{https://github.com/jonaprieto/agda-metis}.}}
 \begin{itemize}
@@
 
-\item Function\footnote{\label{note-conjunct}Excerpt from the \texttt{Agda-Metis}
-library available in  \texttt{ATP.Metis.Rules.Conjunct} module}:
+\item Function
 \vspace*{1mm}
@@
 \end{minted}
-\item Theorem\textsuperscript{\ref{note-conjunct}}
+\item Theorem
 \vspace*{1mm}
@@
   : ∀ {Γ} {φ}
-  → (ω :Prop)
+  → (ω : Prop)
   → Γ ⊢ φ
@@
 \begin{frame}[fragile, label=verified-example]{$p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
+\vfill
 \begin{minted}{cagda}
@@
 -- Axiom.
-
 a = (p ∧ q)
@@
 -- Premise.
-
 Γ : Ctxt
@@
 -- Conjecture.
-
 goal = (q ∧ p)
@@
 -- Subgoals.
-
 subgoal₀ = q
@@
 \end{minted}
+\vfill
 \end{frame}
@@
 \begin{frame}[fragile, label=verified-example-4]{$p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
+\vfill
 \begin{minted}{cagda}
 -- Premise.
-
 Γ = [ a ]
@@
 -- Proof
-
 proof₀ : Γ ⊢ subgoal₀
@@
 \end{minted}
+\vfill
 \gobackreconstruction
@@
 
-\begin{frame}[fragile, label=failure-example]{Bug\footnote{\url{https://github.com/gilith/metis/issues/2}} in the Printing of the Proof}
-  {\texttt{Metis}' v2.3 (release 20161108)}
+\begin{frame}[fragile, label=failure-example]{Bug\footnote{\url{https://github.com/gilith/metis/issues/2}.} in the Printing of the Proof}
+  {\texttt{Metis} v2.3 (release 20161108)}
 % {}
@@
 
-\begin{frame}[fragile, label=failure-example]{Bug in the Printing of the Proof}
-  {\texttt{Metis}' v2.3 (release 20161108) - Issue\footnote{\url{https://github.com/gilith/metis/issues/2}}}
+\begin{frame}[fragile, label=failure-example-2]{Bug in the Printing of the Proof}
+  {\texttt{Metis} v2.3 (release 20161108)}
 
@@
 The bug was caused by the conversion of \texttt{Xor} sets to \texttt{Iff} lists.
-After reporting this, Joe fixed the printing of \texttt{canonicalize} inference rule
+After reporting this, Hurd fixed the printing of \texttt{canonicalize} inference rule
 \[ φ := ¬ p ∧ (¬ q ⇔ ¬ r) ∧ (¬ p ⇔ (¬ q ⇔ {\color{red} r}))\]
@@
 \item \texttt{Isabelle}/\texttt{HOL} mature tool
-\item \texttt{Metis} ported within \texttt{Isabelle}
+\item \texttt{Metis} ported within \texttt{Isabelle/HOL}
 \item Reconstruct proofs of well-known ATPs: \texttt{EProver}, \texttt{Vampire},
@@
   \end{itemize}
-  \item Source code is not available\footnote{\url{http://simon-foster.staff.shef.ac.uk/agdaatp}}
+  \item Source code is not available\footnote{\url{http://simon-foster.staff.shef.ac.uk/agdaatp}.}
   \end{itemize}
@@
   \includegraphics[scale=0.8]{figures/eagda}
-  \footnote{\url{https://github.com/asr/eagda}}
+  \footnote{\url{https://github.com/asr/eagda}.}
   }
@@
   \includegraphics[scale=0.8]{figures/apia}
-  \footnote{\url{https://github.com/asr/apia}}}
+  \footnote{\url{https://github.com/asr/apia}.}}
   };
@@
   {\includegraphics[scale=0.8]{figures/atp}
-  \footnote{\url{http://github.com/jonaprieto/online-atps}}}
+  \footnote{\url{http://github.com/jonaprieto/online-atps}.}}
   };
 
-\only<7->{ \node[left= 3cm of atp, rectangle, text=white,fill=black, align=left, font=\tiny] (proved)
+\only<7->{ \node[left= 2cm of atp, rectangle, text=white,fill=black, align=left, font=\small] (proved)
 {
@@
 
-\begin{frame}[label=pending-work]{Pending Work}
-\begin{itemize}
-\item Complete implementation for \texttt{simplify} inference\footnote{\url{https://github.com/gilith/metis/issues/3}}
+\begin{frame}[label=pending-work]{TODO}
+\begin{itemize}
+\item Complete implementation for \texttt{simplify} inference\footnote{\url{https://github.com/gilith/metis/issues/3}.}
 \item Complete implementation for \texttt{canonicalize} inference: what
@@
 
-\begin{frame}[label=future-work]{Contributions and Future Work}
+\begin{frame}[label=contributions]{Contributions}
 \vfill
@@
 \hline
-\href{http://github.com/jonaprieto/agda-metis}{\texttt{Agda-Metis}}   & Implementation of \texttt{Metis}' inference rules\\
+\href{http://github.com/jonaprieto/agda-metis}{\texttt{Agda-Metis}}   & Implementation of \texttt{Metis} inference rules\\
 \href{http://github.com/jonaprieto/agda-prop}{\texttt{Agda-Prop}}     & Syntax and theorems of Classical Propositional Logic\\
-\href{http://github.com/jonaprieto/athena}{\texttt{Athena}}           & Translator for \texttt{Metis'} \texttt{TSTP} files to \texttt{Agda}\\
+\href{http://github.com/jonaprieto/athena}{\texttt{Athena}}           & Translator for \texttt{Metis} \texttt{TSTP} files to \texttt{Agda}\\
 \href{http://github.com/jonaprieto/online-atps}{\texttt{OnlineATPs}}  & Client to use ATPs from \texttt{SystemOnTPTP} of \texttt{TPTP} World\\
@@
 \vfill
-
+\end{frame}
+
+\begin{frame}[label=future-work]{Future Work}
 \begin{itemize}
@@
 
-\begin{frame}[fragile,label=metis-inference-rules]{\texttt{Metis}' Inference Rules}
+\begin{frame}[fragile,label=metis-inference-rules]{\texttt{Metis} Inference Rules}
 \vfill

### 2017-05-11 src/Athena/TSTP/Parser.hs
[ Parser.hs ] removing unnecessary file.

@@ -1,6713 +1,0 @@
-{-# OPTIONS_GHC -w #-}
--- | Athena.TSTP.Parser module
--- Adapted from https://github.com/agomezl/tstp2agda.
-
-{-# OPTIONS -fno-warn-incomplete-patterns       #-}
-{-# OPTIONS -fno-warn-incomplete-uni-patterns   #-}
-{-# OPTIONS -fno-warn-missing-signatures        #-}
-{-# OPTIONS -fno-warn-monomorphism-restriction  #-}
-{-# OPTIONS -fno-warn-name-shadowing            #-}
-{-# OPTIONS -fno-warn-unused-matches            #-}
-
-module Athena.TSTP.Parser where
-
-------------------------------------------------------------------------------
-
-import Athena.TSTP.Base
-import Athena.TSTP.Lexer
-
-import Control.Monad
-import Control.Monad.Identity
-
-import Data.Char
-import Data.Data
-import Data.List as L
-import Data.Ratio
-import Data.Set as S
-
-import Data.TSTP
-  ( AtomicWord (..)
-  , BinOp (..)
-  , F (..)
-  , Formula (..)
-  , GData (..)
-  , GTerm (..)
-  , InfixPred (..)
-  , Info (..)
-  , IntroType (..)
-  , Parent (..)
-  , Quant (..)
-  , Role (..)
-  , Rule (..)
-  , Source (..)
-  , Status (..)
-  , Term (..)
-  , Theory (..)
-  , V (..)
-  )
-
-import System.IO
-import System.IO.Unsafe
-
-------------------------------------------------------------------------------
-import Control.Applicative(Applicative(..))
-import Control.Monad (ap)
-
--- parser produced by Happy Version 1.19.5
-
-data HappyAbsSyn 
-	= HappyTerminal (Token)
-	| HappyErrorToken Int
-	| HappyAbsSyn4 ([F])
-	| HappyAbsSyn5 (F)
-	| HappyAbsSyn9 (Source)
-	| HappyAbsSyn10 (Role)
-	| HappyAbsSyn11 (Formula)
-	| HappyAbsSyn16 ([Formula])
-	| HappyAbsSyn21 ([V])
-	| HappyAbsSyn28 (Quant)
-	| HappyAbsSyn29 (BinOp)
-	| HappyAbsSyn35 (InfixPred)
[…]

### 2017-05-11 slides/slides.tex
Slides for Agda Implementors' Meeting XXV
* [ Makefile ] type-checked impl-11.agda.

* [ slides ] init.

* [ slides ] tstp, tptp explanation.

* [ slides ] playing with fonts.

* [ slides ] images PDF files added.

* [ slides ] put some order.

* [ slides ] updated files.

* [ slides ] tptp, and tstp slides added.

* [ slides ] diagrams added.

* [ slides ] clickeable items in the diagram.

* [ agda-prop ] updated.

* [ agda-prop ] fixed import of Weakening module.

* [ slides ] fixed typos.

* [ slides ] fixed mistakes.

* [ slides ] minor changes.

* [ slides ] minor changes.

* [ slides ] M

@@
 \vfill
+\end{frame}
+
+\begin{frame}{Obstacles to Reconstruction with Automatic Provers \citep{Paulson2007}}
+\begin{itemize}
+\item \textit{Ambiguities}: their output typically omits crucial information,
+such as which term is affected by rewriting.
+\item \textit{Lack of standards}: automatic provers generate different output formats
+and employ a variety of inference systems
+\item \textit{Complexity}: a single automatic prover may use numerous inference rules with
+complicated behaviors
+\item \textit{Problem transformations}: ATPs re-order literals and make other changes to the clauses
+they are given
+\end{itemize}
+
 \end{frame}
@@
   \end{itemize}
-
-\gobackreconstruction
 \end{frame}
@@
 \end{block}
-\gobackreconstruction
 \end{frame}
@@
 \end{center}
-\gobackreconstruction
 \end{frame}
@@
 \end{itemize}
-\gobackreconstruction
 \end{frame}
@@
 By refutation, we proved $p ⊢ p$:
-\begin{center}
+
+\begin{columns}
+\begin{column}{0.5\textwidth}
+
 \begin{prooftree}
-\AxiomC{$p$}
+\AxiomC{}
 \RightLabel{\texttt{\scriptsize assume}}
+\UnaryInfC{$¬ p$}
+\RightLabel{\texttt{\scriptsize strip}}
+\UnaryInfC{$¬ p$}
+\AxiomC{}
+\RightLabel{\texttt{\scriptsize axiom}}
 \UnaryInfC{$p$}
-\RightLabel{\texttt{\scriptsize strip}}
-\UnaryInfC{$p$}
-\RightLabel{\texttt{\scriptsize negate}}
-\UnaryInfC{$¬ p$}
-\AxiomC{$p$}
 \RightLabel{\texttt{\scriptsize canonicalize}}
@@
 \UnaryInfC{$⊥$}
-
 \end{prooftree}
-% \includegraphics[height=0.8\textheight]{figures/derivation.png}
+\end{column}
+\begin{column}{0.5\textwidth}  %%<--- here
+    \begin{center}
+    \includegraphics[height=0.8\textwidth]{figures/derivation.png}
      \end{center}
+\end{column}
+\end{columns}
 \vfill

### 2017-06-16 slides/slides.tex
[ slides ] last version.
[ slides ] conjunct and atp-conjuncted fixed.

@@
 % \setbeamercolor{institute}{fg=blu}
-\setbeamercolor{title}{fg=plum!80!black}
+\setbeamercolor{title}{fg=blu}
 % \setbeamercolor{subtitle}{fg=blu}
@@
   , style=authoryear-icomp
-  , url=false
+  , url=true
 ]{biblatex}
@@
 \subtitle{(work in progress)}
-\date{Agda Implementors’ Meeting XXV\\
-Teknikparken, Chalmers, Gothenburg, Sweden\\
-May 11 2017\\
+\date{May 11, 2017
 }
@@
 \end{frame}
+
+\begin{frame}[fragile, label=reconstruction]{Proof Reconstruction: Overview}
+\vfill
+\begin{tikzpicture}
+\node(problem) at (0,0)
+   {\includegraphics[scale=0.7]{figures/problem}};
+\node[right = 0.8cm of problem, hyperlink node=tptp-syntax](tptp){
+\includegraphics[scale=0.7]{figures/tptp}
+};
+\node[right= 0.8cm of tptp, hyperlink node=metis] (metis)
+  {\includegraphics[scale=0.7]{figures/metis}};
+\node[right= 0.8cm of metis, hyperlink node=tstp-syntax] (tstp)
+  {\includegraphics[scale=0.7]{figures/tstp}};
+\node[below= 1.5cm of tstp, hyperlink node=athena] (athena)
+  {\includegraphics[scale=0.7]{figures/athena}};
+\node[left = 0.6cm of athena, hyperlink node=agda-file] (agdafile)
+  {\includegraphics[scale=0.7]{figures/agdafile}};
+\node[left = 0.5cm of agdafile] (agda)
+  {\includegraphics[scale=0.7]{figures/agda}};
+\node[below = 0.18cm of problem, hyperlink node=verified-example] (verified)
+  {\includegraphics[scale=0.7]{figures/verified}};
+\node[below = 0.18cm of verified, opacity=0.5, hyperlink node=failure-example] (failure)
+  {\includegraphics[scale=0.7]{figures/failure}};
+
+\draw[->, thick] (problem) to (tptp);
+\draw[->, thick] (tptp) to (metis);
+\draw[->, thick] (metis) to (tstp);
+\draw[->, thick] (tstp) to (athena);
+\draw[->, thick] (athena) to (agdafile);
+\draw[->, thick] (agdafile) to (agda);
+\draw[->, thick] (agda) to (verified);
+\draw[->, thick, gray] (agda) to (failure);
+\end{tikzpicture}
+\vfill
+\end{frame}
+
+% Now each step paused.
 
@@
 
-\begin{frame}[fragile, label=athena]{\texttt{Athena}
-  \footnote{\url{http://github.com/jonaprieto/athena}.}}
+\begin{frame}[fragile, label=athena]{\texttt{Athena}~\citep{Athena}}
 
@@
 \begin{itemize}
-    \item Parsing of \texttt{TSTP} language\footnote{\label{parsing}\url{https://github.com/agomezl/tstp2agda}.}\textsuperscript{,}\footnote{\url{https://github.com/jonaprieto/tstp2agda}.}
+    \item Parsing of \texttt{TSTP} language\footnote{\label{parsing}\url{https://github.com/agomezl/tstp2agda}.}
     \item Creation\textsuperscript{\ref{parsing}} and analysis of \hyperlink{tstp-dag}{\textbf{DAG}} derivations
@@
 
-\begin{frame}[fragile, label=agda-prop]{\texttt{Agda-Prop} Library
-  \footnote{\url{https://github.com/jonaprieto/agda-prop}.}}
+\begin{frame}[fragile, label=agda-prop]{\texttt{Agda-Prop} Library~\citep{AgdaProp}}
 \begin{itemize}
@@
 \begin{frame}[fragile, label=agda-metis]{\texttt{Agda-Metis} Library
-  \footnote{\url{https://github.com/jonaprieto/agda-metis}.}}
+  ~\citep{AgdaMetis}}
 \vfill
@@
 \hyperlink{atp-conjunct}{\texttt{conjunct}} & takes a formula from a conjunction &\hyperlink{atp-conjunct}{\texttt{atp-conjunct}}\\
-\texttt{negate} & applies negation to the formula &\texttt{atp-negate}\\
+\texttt{negate} & append negation symbol to the formula &\texttt{atp-negate}\\
 \texttt{resolve} & applies theorems of resolution &\texttt{atp-resolve}\\
@@
 \begin{frame}[fragile, label=atp-conjunct]{\texttt{Agda-Metis}: Conjunct Inference
-  \footnote{\url{https://github.com/jonaprieto/agda-metis}.}}
+  \footnote{\url{https://github.com/jonaprieto/agda-metis}.}
+  }
+
+\vfill
 \begin{itemize}
@@
 \begin{equation*}
-  \text{conjunct}(ϕ₁ ∧  ϕ₂ ∧ ⋯ ∧ \mathbf{ϕᵢ} ∧ ⋯ ∧ \phi_n, \mathbf{ϕᵢ}) ⟶ \mathbf{ϕᵢ}
+\text{\color{plum!40!black}conjunct}(ϕ₁ ∧ ⋯ ∧ \phi_n, \omega)
+= \begin{cases}
+\phi_{i} \ \ \ \ \text{if }\omega\text{ is equal to some }\phi_i\\
+\phi    \ \ \ \ \text{otherwise}
+\end{cases}
 \end{equation*}
 
-\item Function
-\vspace*{1mm}
+\pause
+\item Inference rules involved
+\begin{center}
+\begin{columns}
+\begin{column}{0.45\textwidth}
+
+ \begin{prooftree}
+  \AxiomC{$ϕ ∧ ψ$}
+  \RightLabel{\scriptsize $∧$-\texttt{proj}$₁$}
+  \UnaryInfC{$ϕ$}
+  \end{prooftree}
+\end{column}
+
+\begin{column}{0.45\textwidth}
+ \begin{prooftree}
+  \AxiomC{$ϕ ∧ ψ$}
+  \RightLabel{\scriptsize $∧$-\texttt{proj}$₂$}
+  \UnaryInfC{$ψ$}
+  \end{prooftree}
+\end{column}
+
+\begin{column}{0.1\textwidth}  %%<--- here
+   \begin{tikzpicture}[overlay, remember picture, scale=2]
+% \tikzset{shift={(current page.north)}, xshift=cm,yshift=-2cm}
+\node[vertex, fill=black] (d1) {};
+\node[vertex, fill=black, below left=0.2cm and 0.1cm of d1] (d2) {};
+\node[vertex, fill=black, below right=0.2cm and 0.1cm of d1] (d3) {};
+
+\node[vertex, fill=black, below left=0.2cm and 0.1cm of d3] (q) {};
+\node[vertex, fill=black, below right=0.2cm and 0.1cm of d3] (w) {};
+
+\node[vertex, fill=black, below right=0.2cm and 0.1cm of q] (s) {};
+
+\draw[-, thick] (d1) to (d2);
+\draw[-, thick] (d1) to (d3);
+\draw[-, thick] (d3) to (q);
+\draw[-, thick] (d3) to (w);
+\draw[-, thick] (q) to (s);
+\end{tikzpicture}
+\end{column}
+\end{columns}
+\end{center}
+\vskip 2mm
+
+\item Target example
+\[ φ := (¬ p ∧ (¬ q ⇔ ¬ r)) ∧ (p ∧ (¬ q ⇔ ¬r))\]
+
+\begin{itemize}
+
+\item
 \begin{minted}{cagda}
-conjunct : Prop → Prop → Prop
-conjunct (φ ∧ ψ) ω with ⌊ eq φ ω ⌋ | ⌊ eq ψ ω ⌋
-... | true  | _     = φ
-... | false | true  = ψ
-... | false | false = conjunct φ ω
-conjunct φ ω        = φ
+ conjunct(φ , ¬ q) ≡ ϕ
 \end{minted}
-\item Theorem
-\vspace*{1mm}
+\vskip 3mm
+\item
 \begin{minted}{cagda}
+ conjunct(φ , ¬ q ⇔ ¬ r) ≡ ¬ q ⇔ ¬ r
+\end{minted}
+\vskip 3mm
+
+\item
+\begin{minted}{cagda}
+ conjunct(φ , p)   ≡ p
+\end{minted}
+
+\end{itemize}
+
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile, label=atp-conjunct]
+
+\begin{minted}{cagda}
+data ConjView : Prop → Set where
+  conj  : (φ₁ φ₂ : Prop) → ConjView (φ₁ ∧ φ₂)
+  other : (φ : Prop)     → ConjView φ
+
+conj-view : (φ : Prop) → ConjView φ
+conj-view (φ ∧ ψ) = conj _ _
+conj-view φ       = other _
+
+data Step  : Set where
+  pick  : Step
+  proj₁ : Step
+  proj₂ : Step
+
+Path : Set
+Path = List Step
+
+conjunct-path : (φ : Prop) → (ω : Prop) → Path → Path
+conjunct-path φ ω path with ⌊ eq φ ω ⌋
+... | true  = path ∷ʳ pick
+... | false with conj-view φ
+...   | other _   = []
+...   | conj φ₁ φ₂ with conjunct-path φ₁ ω []
+...     | subpath@(_ ∷ _) = (path ∷ʳ proj₁) ++ subpath
+...     | [] with conjunct-path φ₂ ω []
+...         | subpath@(_ ∷ _) = (path ∷ʳ proj₂) ++ subpath
+...         | []              = []
+\end{minted}
+
+\end{frame}
+
+\begin{frame}[fragile, label=atp-conjunct-proof]{The \texttt{conjunct} function and its theorem, \texttt{atp-conjunct}}
+\vfill
+\begin{minted}{cagda}
+conjunct : (φ : Prop) → (ω : Prop) → Prop
+conjunct φ ω with conj-view φ | conjunct-path φ ω []
+... | _          | []           = φ
+... | conj φ₁ φ₂ | pick  ∷ path = φ
+... | conj φ₁ φ₂ | proj₁ ∷ path = conjunct φ₁ ω
+... | conj φ₁ φ₂ | proj₂ ∷ path = conjunct φ₂ ω
+... | other .φ   | _            = φ
+
 atp-conjunct
@@
   → Γ ⊢ conjunct φ ω
-\end{minted}
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile, label=atp-conjunct-proof]{A proof of \texttt{atp-conjunct} theorem}
-\vfill
-\begin{minted}{cagda}
-atp-conjunct
-  : ∀ {Γ} {φ}
-  → (ω : Prop)
-  → Γ ⊢ φ
-  → Γ ⊢ conjunct φ ω
-
-atp-conjunct {Γ} {φ ∧ ψ} ω Γ⊢φ
-  with ⌊ eq φ ω ⌋ | ⌊ eq ψ ω ⌋
-... | true  | _     = ∧-proj₁ Γ⊢φ
-... | false | true  = ∧-proj₂ Γ⊢φ
-... | false | false =
-  atp-conjunct {Γ = Γ} {φ = φ} ω (∧-proj₁ Γ⊢φ)
-atp-conjunct {_} {Var x}  _ = id
-atp-conjunct {_} {⊤}      _ = id
-atp-conjunct {_} {⊥}      _ = id
-atp-conjunct {_} {φ ∨ ψ}  _ = id
-atp-conjunct {_} {φ ⇒ ψ}  _ = id
-atp-conjunct {_} {φ ⇔ ψ}  _ = id
-atp-conjunct {_} {¬ φ}    _ = id
+
+atp-conjunct {Γ} {φ} ω Γ⊢φ
+  with conj-view φ | conjunct-path φ ω []
+...  | _          | []           = Γ⊢φ
+...  | conj φ₁ φ₂ | pick  ∷ path = Γ⊢φ
+...  | conj φ₁ φ₂ | proj₁ ∷ path = atp-conjunct ω (∧-proj₁ Γ⊢φ)
+...  | conj φ₁ φ₂ | proj₂ ∷ path = atp-conjunct ω (∧-proj₂ Γ⊢φ)
+...  | other .φ   | (_ ∷ _)      = Γ⊢φ
 \end{minted}
@@
 \begin{tptp}
+$ cat problem.tptp
 fof(a, axiom, p & q).
@@
 \end{tptp}
-  \item A natural deduction proof
-\begin{columns}
-\begin{column}{0.8\textwidth}
- \begin{prooftree}
-  \AxiomC{$ϕ ∧ ψ$}
-  \RightLabel{$∧$-\texttt{proj}$₁$}
-  \UnaryInfC{$ϕ$}
-
-  \AxiomC{$ϕ ∧ ψ$}
-  \RightLabel{$∧$-\texttt{proj}$₂$}
-  \UnaryInfC{$ψ$}
-  \RightLabel{$∧$-\texttt{intro}}
-  \BinaryInfC{$ψ ∧ ϕ$}
-  \end{prooftree}
-\end{column}
-\begin{column}{0.2\textwidth}  %%<--- here
-   \begin{tikzpicture}[overlay, remember picture, scale=2]
-% \tikzset{shift={(current page.north)}, xshift=cm,yshift=-2cm}
-\node[vertex, fill=black] (d1) {};
-\node[vertex, fill=black, right=0.5cm of d1 ] (d2) {};
-\node[vertex, fill=black, below=0.2cm of d1] (d3) {};
-\node[vertex, fill=black, below=0.2cm of d2] (d4) {};
-\node[vertex, fill=black, below right= 0.2cm and  0.25cm of d3] (d5) {};
-\draw[-, thick] (d1) to (d3);
-\draw[-, thick] (d2) to (d4);
-\draw[-, thick] (d3) to (d5);
-\draw[-, thick] (d4) to (d5);
+  \item How to use Athena with your problem
+  \vspace*{5mm}
+\begin{tikzpicture}
+\node[rectangle, text=white,fill=black, align=left, font=\small]
+{
+\texttt{\$ metis --show proof problem.tptp > problem.tstp}\hspace{1cm}\\
+\texttt{\$ athena problem.tstp}\\
+\texttt{\$ agda problem.agda}
+  };
 \end{tikzpicture}
-\end{column}
-\end{columns}
 
@@
 \hline
-\textbf{Name} & \textbf{Purpose} \\
+\textbf{Name} & \textbf{References} \\
 \hline
-\href{http://github.com/jonaprieto/agda-metis}{\texttt{Agda-Metis}}   & Implementation of \texttt{Metis} inference rules\\
-\href{http://github.com/jonaprieto/agda-prop}{\texttt{Agda-Prop}}     & Syntax and theorems of Classical Propositional Logic\\
-\href{http://github.com/jonaprieto/athena}{\texttt{Athena}}           & Translator for \texttt{Metis} \texttt{TSTP} files to \texttt{Agda}\\
-\href{http://github.com/jonaprieto/online-atps}{\texttt{OnlineATPs}}  & Client to use ATPs from \texttt{SystemOnTPTP} of \texttt{TPTP} World\\
-\href{http://github.com/jonaprieto/prop-pack}{\texttt{Prop-Pack}}     & Collection of \texttt{TPTP} problems to test \texttt{Athena}\\[1ex]
+\href{http://github.com/jonaprieto/agda-metis}{\texttt{Agda-Metis}}   & \citep{AgdaMetis}\\
+\href{http://github.com/jonaprieto/agda-prop}{\texttt{Agda-Prop}}     & \citep{AgdaProp}\\
+\href{http://github.com/jonaprieto/athena}{\texttt{Athena}}           & \citep{Athena}\\
+\href{http://github.com/jonaprieto/online-atps}{\texttt{OnlineATPs}}  & \citep{OnlineATPs}\\
+\href{http://github.com/jonaprieto/prop-pack}{\texttt{Prop-Pack}}     & \citep{ProPack}\\[1ex]
 \hline
@@
 
-\begin{frame}[fragile, label=references, allowframebreaks]{References}
+\begin{frame}[allowframebreaks]{References}
 \printbibliography

### 2017-06-16 slides/Jonathan-Proof-Reconstruction.tex
[ slides ] Renamed slides. Fixed atp-conjunct explanation.

--- 2017-06-16 slides/slides.tex
@@
 \usetikzlibrary{positioning}
+\usetikzlibrary{arrows}
+\usetikzlibrary{automata}
 \usetikzlibrary{calc}
@@
 
-\begin{frame}[fragile, label=reconstruction]{Proof Reconstruction: Overview}
+\begin{frame}[fragile]{Proof Reconstruction: Overview}
 \vfill
@@
 \begin{equation*}
-\text{\color{plum!40!black}conjunct}(ϕ₁ ∧ ⋯ ∧ \phi_n, \omega)
+\text{\color{plum!40!black}conjunct}(\overbrace{ϕ₁ ∧ ⋯ ∧ \phi_n}^{\phi}, \psi)
 = \begin{cases}
-\phi_{i} \ \ \ \ \text{if }\omega\text{ is equal to some }\phi_i\\
+\phi_{i} \ \ \ \ \text{if }\psi\text{ is equal to some }\phi_i\\
 \phi    \ \ \ \ \text{otherwise}
@@
 \begin{columns}
-\begin{column}{0.45\textwidth}
+\begin{column}{0.42\textwidth}
 
  \begin{prooftree}
-  \AxiomC{$ϕ ∧ ψ$}
+  \AxiomC{$ϕ₁ ∧ φ₂$}
   \RightLabel{\scriptsize $∧$-\texttt{proj}$₁$}
-  \UnaryInfC{$ϕ$}
+  \UnaryInfC{$ϕ₁$}
   \end{prooftree}
@@
 
-\begin{column}{0.45\textwidth}
+\begin{column}{0.42\textwidth}
  \begin{prooftree}
-  \AxiomC{$ϕ ∧ ψ$}
+  \AxiomC{$ϕ₁ ∧ φ₂$}
   \RightLabel{\scriptsize $∧$-\texttt{proj}$₂$}
-  \UnaryInfC{$ψ$}
+  \UnaryInfC{$φ₂$}
   \end{prooftree}
@@
 
-\begin{column}{0.1\textwidth}  %%<--- here
-   \begin{tikzpicture}[overlay, remember picture, scale=2]
-% \tikzset{shift={(current page.north)}, xshift=cm,yshift=-2cm}
-\node[vertex, fill=black] (d1) {};
-\node[vertex, fill=black, below left=0.2cm and 0.1cm of d1] (d2) {};
-\node[vertex, fill=black, below right=0.2cm and 0.1cm of d1] (d3) {};
-
-\node[vertex, fill=black, below left=0.2cm and 0.1cm of d3] (q) {};
-\node[vertex, fill=black, below right=0.2cm and 0.1cm of d3] (w) {};
-
-\node[vertex, fill=black, below right=0.2cm and 0.1cm of q] (s) {};
-
-\draw[-, thick] (d1) to (d2);
-\draw[-, thick] (d1) to (d3);
-\draw[-, thick] (d3) to (q);
-\draw[-, thick] (d3) to (w);
-\draw[-, thick] (q) to (s);
+\begin{column}{0.2\textwidth}  %%<--- here
+  \begin{tikzpicture}[
+    ->
+  , >=stealth'
+  , shorten >=1pt
+  , auto
+%  , node distance=2.8cm
+  , thick
+  , every state/.style={fill=plum!45!black,draw=none,text=white}
+  , overlay
+  , remember picture
+    , transform canvas={scale=.75}
+    ]
+  \tikzset{shift={(current page.center)}, xshift=4.5cm,yshift=1cm}
+
+  \node[state]  (phi)                     {$φ$};
+  \node[state]  (phi1) [below left =1.3cm and 0.1cm of phi]  {$φ₁$};
+  \node[state]  (phi2) [below right=1.3cm and 0.1cm of phi]  {$φ₂$};
+  \node[state]  (phi3)  [below left =1.3cm and 0.1cm of phi2]  {$φ₃$};
+  \node[state]  (phi4)  [below right =1.3cm and 0.1cm of phi2]  {$φ₄$};
+
+  \path[every node/.style={sloped,anchor=south,auto=false}]
+        (phi) edge node {\tiny $∧$-\texttt{proj}$₁$} (phi1)            
+        (phi) edge node {\tiny $∧$-\texttt{proj}$₂$} (phi2)
+        (phi2) edge node {\tiny $∧$-\texttt{proj}$₁$} (phi3)
+        (phi2) edge node {\tiny $∧$-\texttt{proj}$₂$} (phi4);
+
 \end{tikzpicture}
@@
 
-\item Target example
-\[ φ := (¬ p ∧ (¬ q ⇔ ¬ r)) ∧ (p ∧ (¬ q ⇔ ¬r))\]
+\item Example
+\[ φ := φ₁ ∧ \overbrace{(φ₃ ∧ φ₄)}^{φ₂}\]
 
@@
 \item
-\begin{minted}{cagda}
- conjunct(φ , ¬ q) ≡ ϕ
-\end{minted}
+\texttt{conjunct}$(φ , φ₃ ∧ φ₁) ≡ ϕ$
 \vskip 3mm
 \item
-\begin{minted}{cagda}
- conjunct(φ , ¬ q ⇔ ¬ r) ≡ ¬ q ⇔ ¬ r
-\end{minted}
+\texttt{conjunct}$(φ , φ₃)      ≡ ϕ₃$
 \vskip 3mm
-
 \item
-\begin{minted}{cagda}
- conjunct(φ , p)   ≡ p
-\end{minted}
-
-\end{itemize}
-
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile, label=atp-conjunct]
+\texttt{conjunct}$(φ , φ₂)      ≡ ϕ₂$
+\vskip 3mm
+\end{itemize}
+
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
 
@@
 
-conjunct-path : (φ : Prop) → (ω : Prop) → Path → Path
-conjunct-path φ ω path with ⌊ eq φ ω ⌋
+conjunct-path : (φ ψ : Prop) → Path → Path
+conjunct-path φ ψ path with ⌊ eq φ ψ ⌋
 ... | true  = path ∷ʳ pick
@@
 ...   | other _   = []
-...   | conj φ₁ φ₂ with conjunct-path φ₁ ω []
+...   | conj φ₁ φ₂ with conjunct-path φ₁ ψ []
 ...     | subpath@(_ ∷ _) = (path ∷ʳ proj₁) ++ subpath
-...     | [] with conjunct-path φ₂ ω []
+...     | [] with conjunct-path φ₂ ψ []
 ...         | subpath@(_ ∷ _) = (path ∷ʳ proj₂) ++ subpath
@@
 \begin{minted}{cagda}
-conjunct : (φ : Prop) → (ω : Prop) → Prop
-conjunct φ ω with conj-view φ | conjunct-path φ ω []
+conjunct : (φ ψ : Prop) → Prop
+conjunct φ ψ with conj-view φ | conjunct-path φ ψ []
 ... | _          | []           = φ
-... | conj φ₁ φ₂ | pick  ∷ path = φ
-... | conj φ₁ φ₂ | proj₁ ∷ path = conjunct φ₁ ω
-... | conj φ₁ φ₂ | proj₂ ∷ path = conjunct φ₂ ω
+... | conj _ _ | pick  ∷ path = φ
+... | conj φ₁ _ | proj₁ ∷ path = conjunct φ₁ ψ
+... | conj _ φ₂ | proj₂ ∷ path = conjunct φ₂ ψ
 ... | other .φ   | _            = φ
@@
   : ∀ {Γ} {φ}
-  → (ω : Prop)
   → Γ ⊢ φ
-  → Γ ⊢ conjunct φ ω
-
-atp-conjunct {Γ} {φ} ω Γ⊢φ
-  with conj-view φ | conjunct-path φ ω []
+  → (ψ : Prop)
+  → Γ ⊢ conjunct φ ψ
+
+atp-conjunct {Γ} {φ} Γ⊢φ ψ
+  with conj-view φ | conjunct-path φ ψ []
 ...  | _          | []           = Γ⊢φ
 ...  | conj φ₁ φ₂ | pick  ∷ path = Γ⊢φ
-...  | conj φ₁ φ₂ | proj₁ ∷ path = atp-conjunct ω (∧-proj₁ Γ⊢φ)
-...  | conj φ₁ φ₂ | proj₂ ∷ path = atp-conjunct ω (∧-proj₂ Γ⊢φ)
+...  | conj φ₁ φ₂ | proj₁ ∷ path = atp-conjunct ψ (∧-proj₁ Γ⊢φ)
+...  | conj φ₁ φ₂ | proj₂ ∷ path = atp-conjunct ψ (∧-proj₂ Γ⊢φ)
 ...  | other .φ   | (_ ∷ _)      = Γ⊢φ
@@
   \item How to use Athena with your problem
-  \vspace*{5mm}
-\begin{tikzpicture}
-\node[rectangle, text=white,fill=black, align=left, font=\small]
-{
-\texttt{\$ metis --show proof problem.tptp > problem.tstp}\hspace{1cm}\\
-\texttt{\$ athena problem.tstp}\\
-\texttt{\$ agda problem.agda}
-  };
-\end{tikzpicture}
-
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile, allowframebreaks]{\texttt{TSTP} Derivation}
+
+\begin{tptp}
+$ metis --show proof problem.tptp > problem.tstp
+$ athena problem.tstp
+$ agda problem.tstp
+\end{tptp}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile, allowframebreaks]{\texttt{TSTP} Derivation given by \texttt{Metis}}
 \begin{tptp}
@@
 
-\begin{frame}[fragile, label=verified-example]{$p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
+\begin{frame}[fragile, label=verified-example]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof generated with \texttt{Athena}}
 \vfill
@@
 
-\begin{frame}[fragile, label=verified-example-2]{$p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
+\begin{frame}[fragile, label=verified-example-2]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
 \vfill
@@
 
-\begin{frame}[fragile, label=verified-example-3]{$p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
+\begin{frame}[fragile, label=verified-example-3]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
 \vfill
@@
 
-\begin{frame}[fragile, label=verified-example-4]{$p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
+\begin{frame}[fragile, label=verified-example-4]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed proof}
 \vfill
@@
 \end{center}
-\label{tab:library}
 \end{table}

### 2017-06-17 slides/Jonathan-Proof-Reconstruction.tex
[ slides ] updated info added and fixed phi symbols.

@@
 \subtitle{(work in progress)}
-\date{May 11, 2017
-}
+\date{May 11, 2017\\Updated: \today}
 \author[Jonathan Prieto-Cubides]{Jonathan Prieto-Cubides\\
@@
 \begin{equation*}
-\text{\color{plum!40!black}conjunct}(\overbrace{ϕ₁ ∧ ⋯ ∧ \phi_n}^{\phi}, \psi)
+\text{\color{plum!40!black}conjunct}(\overbrace{\varphi_1 ∧ ⋯ ∧ \varphi_n}^{\varphi}, \psi)
 = \begin{cases}
-\phi_{i} \ \ \ \ \text{if }\psi\text{ is equal to some }\phi_i\\
-\phi    \ \ \ \ \text{otherwise}
+\varphi_{i} \ \ \ \ \text{if }\psi\text{ is equal to some }\varphi_i\\
+\varphi    \ \ \ \ \text{otherwise}
 \end{cases}
@@
  \begin{prooftree}
-  \AxiomC{$ϕ₁ ∧ φ₂$}
+  \AxiomC{$\varphi_1 ∧ \varphi_2$}
   \RightLabel{\scriptsize $∧$-\texttt{proj}$₁$}
-  \UnaryInfC{$ϕ₁$}
+  \UnaryInfC{$\varphi_1$}
   \end{prooftree}
@@
  \begin{prooftree}
-  \AxiomC{$ϕ₁ ∧ φ₂$}
+  \AxiomC{$\varphi_1 ∧ \varphi_2$}
   \RightLabel{\scriptsize $∧$-\texttt{proj}$₂$}
-  \UnaryInfC{$φ₂$}
+  \UnaryInfC{$\varphi₂$}
   \end{prooftree}
@@
     ]
-  \tikzset{shift={(current page.center)}, xshift=4.5cm,yshift=1cm}
-
-  \node[state]  (phi)                     {$φ$};
-  \node[state]  (phi1) [below left =1.3cm and 0.1cm of phi]  {$φ₁$};
-  \node[state]  (phi2) [below right=1.3cm and 0.1cm of phi]  {$φ₂$};
-  \node[state]  (phi3)  [below left =1.3cm and 0.1cm of phi2]  {$φ₃$};
-  \node[state]  (phi4)  [below right =1.3cm and 0.1cm of phi2]  {$φ₄$};
+  \tikzset{shift={(current page.center)}, xshift=4.5cm,yshift=0cm}
+
+  \node[state]  (phi)                     {$\varphi$};
+  \node[state]  (phi1) [below left =1.3cm and 0.1cm of phi]  {$\varphi_1$};
+  \node[state]  (phi2) [below right=1.3cm and 0.1cm of phi]  {$\varphi_2$};
+  \node[state]  (phi3)  [below left =1.3cm and 0.1cm of phi2]  {$\varphi_3$};
+  \node[state]  (phi4)  [below right =1.3cm and 0.1cm of phi2]  {$\varphi_4$};
 
@@
 \item Example
-\[ φ := φ₁ ∧ \overbrace{(φ₃ ∧ φ₄)}^{φ₂}\]
+\[ \varphi := \varphi_1 ∧ \overbrace{(\varphi_3 ∧ \varphi_4)}^{\varphi_2}\]
 
@@
 \item
-\texttt{conjunct}$(φ , φ₃ ∧ φ₁) ≡ ϕ$
+\texttt{conjunct}$(\varphi , \varphi_3 ∧ \varphi_1) ≡ \varphi$
 \vskip 3mm
 \item
-\texttt{conjunct}$(φ , φ₃)      ≡ ϕ₃$
+\texttt{conjunct}$(\varphi , \varphi_3)      ≡ \varphi_3$
 \vskip 3mm
 \item
-\texttt{conjunct}$(φ , φ₂)      ≡ ϕ₂$
+\texttt{conjunct}$(\varphi , \varphi_2)      ≡ \varphi_2$
 \vskip 3mm
@@
 ... | _          | []        = φ
-... | conj _ _ | pick  ∷ path = φ
-... | conj φ₁ _ | proj₁ ∷ path = conjunct φ₁ ψ
-... | conj _ φ₂ | proj₂ ∷ path = conjunct φ₂ ψ
+... | conj _ _   | pick  ∷ _ = φ
+... | conj φ₁ _  | proj₁ ∷ _ = conjunct φ₁ ψ
+... | conj _ φ₂  | proj₂ ∷ _ = conjunct φ₂ ψ
 ... | other .φ   | _         = φ
@@
   : ∀ {Γ} {φ}
+  → (ψ : Prop)
   → Γ ⊢ φ
-  → (ψ : Prop)
   → Γ ⊢ conjunct φ ψ
 
-atp-conjunct {Γ} {φ} Γ⊢φ ψ
+atp-conjunct {Γ} {φ} ψ Γ⊢φ
   with conj-view φ | conjunct-path φ ψ []
 ...  | _           | []        = Γ⊢φ
-...  | conj φ₁ φ₂ | pick  ∷ path = Γ⊢φ
-...  | conj φ₁ φ₂ | proj₁ ∷ path = atp-conjunct ψ (∧-proj₁ Γ⊢φ)
-...  | conj φ₁ φ₂ | proj₂ ∷ path = atp-conjunct ψ (∧-proj₂ Γ⊢φ)
-...  | other .φ   | (_ ∷ _)      = Γ⊢φ
+...  | conj _ _    | pick  ∷ _ = Γ⊢φ
+...  | conj _ _    | proj₁ ∷ _ = atp-conjunct ψ (∧-proj₁ Γ⊢φ)
+...  | conj _ _    | proj₂ ∷ _ = atp-conjunct ψ (∧-proj₂ Γ⊢φ)
+...  | other _     | (_ ∷ _)   = Γ⊢φ
 \end{minted}
@@
 -- Axiom.
-a = (p ∧ q)
+a = p ∧ q
 
@@
 -- Conjecture.
-goal = (q ∧ p)
+goal = q ∧ p
 
@@
 subgoal₀ = q
-subgoal₁ = (q ⇒ p)
+subgoal₁ = q ⇒ p
 \end{minted}
@@
 a : Prop
-a = (p ∧ q)
+a = p ∧ q
 
@@
 subgoal₁ : Prop
-subgoal₁ = (q ⇒ p)
+subgoal₁ = q ⇒ p
 
@@
 subgoal₀ = q
-subgoal₁ = (q ⇒ p)
+subgoal₁ = q ⇒ p
 

### 2017-07-25 src/Athena/Translation/Rules/Strip.hs
minor changes in Strip.hs

@@ -43,6 +43,7 @@ split (BinOp φ₁ (:|:) φ₂)           =
   unshunt (BinOp ((:~:) φ₁) (:=>:) (split φ₂))
 
 split (BinOp φ₁ (:=>:) φ₂)          = unshunt (BinOp φ₁ (:=>:) (split φ₂))
+
 split (BinOp φ₁ (:<=>:) φ₂)         =
   BinOp
     (unshunt (BinOp φ₁ (:=>:) (split φ₂)))
@@ -50,6 +51,7 @@ split (BinOp φ₁ (:<=>:) φ₂)         =
     (unshunt (BinOp φ₂ (:=>:) (split φ₁)))
 split ((:~:) (BinOp φ₁ (:&:) φ₂))   =
   unshunt (BinOp φ₁ (:=>:) (split ((:~:) φ₂)))
+
 split ((:~:) (BinOp φ₁ (:|:) φ₂))   =
   BinOp
     (unshunt (split ((:~:) φ₁)))

### 2017-07-25 paper/llncsdoc/typeinst.tex
working on inferences rules.

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\usepackage{url}
\urldef{\mailsc}\path|{jprieto9, asr}@eafit.edu.co|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Towards Proof-Reconstruction of Problems in Classical Propositional Logic}

% a short form should be given in case it is too long for the running head
\titlerunning{Towards Proof-Reconstruction of Problems in Classical Propositional Logic}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Jonathan Prieto-Cubides%
\and Andr\'es Sicard-Ram\'irez}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Universidad EAFIT, Escuela de Ciencias e Ingenier\'ia,\\
Medell\'in, Colombia\\
\mailsc}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.

\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

\section{Introduction}

\subsection{Copyright Forms}

The copyright form may be downloaded from the ``For Authors"
(Information for LNCS Authors) section of the LNCS Website:
\texttt{www.springer.com/lncs}. Please send your signed copyright form
to the Contact Volume Editor, either as a scanned pdf or by fax or by
courier. One author may sign on behalf of all of the other authors of a
particular paper. Digital signatures are acceptable.

\section{Paper Preparation}

Springer provides you with a complete integrated \LaTeX{} document class
(\texttt{llncs.cls}) for multi-author books such as those in the LNCS
series. Papers not complying with the LNCS style will be reformatted.
This can lead to an increase in the overall number of pages. We would
therefore urge you not to squash your paper.

Please always cancel any superfluous definitions that are
not actually used in your text. If you do not, these may conflict with
the definitions of the macro package, causing changes in the structure
of the text and leading to numerous mistakes in the proofs.

If you wonder what \LaTeX{} is and where it can be obtained, see the
``\textit{LaTeX project site}'' (\url{http://www.latex-project.org})
and especially the webpage ``\textit{How to get it}''
(\url{http://www.latex-project.org/ftp.html}) respectively.

When you use \LaTeX\ together with our document class file,
\texttt{llncs.cls},
your text is typeset automatically in Computer Modern Roman (CM) fonts.
Please do
\emph{not} change the preset fonts. If you have to use fonts other
than the preset fonts, kindly submit these with your files.

Please use the commands \verb+\label+ and \verb+\ref+ for
cross-references and the commands \verb+\bibitem+ and \verb+\cite+ for
references to the bibliography, to enable us to create hyperlinks at
these places.

For preparing your figures electronically and integrating them into
your source file we recommend using the standard \LaTeX{} \verb+graphics+ or
\verb+graphicx+ package. These provide the \verb+\includegraphics+ command.
In general, please refrain from using the \verb+\special+ command.

Remember to submit any further style files and
fonts you have used together with your source files.

\subsubsection{Headings.}

Headings should be capitalized
(i.e., nouns, verbs, and all other words
except articles, prepositions, and conjunctions should be set with an
initial capital) and should,
with the exception of the title, be aligned to the left.
Words joined by a hyphen are subject to a special rule. If the first
word can stand alone, the second word should be capitalized.

Here are some examples of headings: ``Criteria to Disprove
Context-Freeness of Collage Language", ``On Correcting the Intrusion of
Tracing Non-deterministic Programs by Software", ``A User-Friendly and
Extendable Data Distribution System", ``Multi-flip Networks:
Parallelizing GenSAT", ``Self-determinations of Man".

\subsubsection{Lemmas, Propositions, and Theorems.}

The numbers accorded to lemmas, propositions, and theorems, etc. should
appear in consecutive order, starting with Lemma 1, and not, for
example, with Lemma 11.

\subsection{Figures}

For \LaTeX\ users, we recommend using the \emph{graphics} or \emph{graphicx}
package and the \verb+\includegraphics+ command.

Please check that the lines in line drawings are not
interrupted and are of a constant width. Grids and details within the
figures must be clearly legible and may not be written one on top of
the other. Line drawings should have a resolution of at least 800 dpi
(preferably 1200 dpi). The lettering in figures should have a height of
2~mm (10-point type). Figures should be numbered and should have a
caption which should always be positioned \emph{under} the figures, in
contrast to the caption belonging to a table, which should always appear
\emph{above} the table; this is simply achieved as matter of sequence in
your source.

Please center the figures or your tabular material by using the \verb+\centering+
declaration. Short captions are centered by default between the margins
and typeset in 9-point type (Fig.~\ref{fig:example} shows an example).
The distance between text and figure is preset to be about 8~mm, the
distance between figure and caption about 6~mm.

To ensure that the reproduction of your illustrations is of a reasonable
quality, we advise against the use of shading. The contrast should be as
pronounced as possible.

If screenshots are necessary, please make sure that you are happy with
the print quality before you send the files.
\begin{figure}
\centering
\includegraphics[height=6.2cm]{eijkel2}
\caption{One kernel at $x_s$ (\emph{dotted kernel}) or two kernels at
$x_i$ and $x_j$ (\textit{left and right}) lead to the same summed estimate
at $x_s$. This shows a figure consisting of different types of
lines. Elements of the figure described in the caption should be set in
italics, in parentheses, as shown in this sample caption.}
\label{fig:example}
\end{figure}

Please define figures (and tables) as floating objects. Please avoid
using optional location parameters like ``\verb+[h]+" for ``here".

\paragraph{Remark 1.}

In the printed volumes, illustrations are generally black and white
(halftones), and only in exceptional cases, and if the author is
prepared to cover the extra cost for color reproduction, are colored
pictures accepted. Colored pictures are welcome in the electronic
version free of charge. If you send colored figures that are to be
printed in black and white, please make sure that they really are
legible in black and white. Some colors as well as the contrast of
converted colors show up very poorly when printed in black and white.

\subsection{Formulas}

Displayed equations or formulas are centered and set on a separate
line (with an extra line or halfline space above and below). Displayed
expressions should be numbered for reference. The numbers should be
consecutive within each section or within the contribution,
with numbers enclosed in parentheses and set on the right margin --
which is the default if you use the \emph{equation} environment, e.g.,
\begin{equation}
  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt \;  .
\end{equation}

Equations should be punctuated in the same way as ordinary
text but with a small space before the end punctuation mark.

\subsection{Footnotes}

The superscript numeral used to refer to a footnote appears in the text
either directly after the word to be discussed or -- in relation to a
phrase or a sentence -- following the punctuation sign (comma,
semicolon, or period). Footnotes should appear at the bottom of
the
normal text area, with a line of about 2~cm set
immediately above them.\footnote{The footnote numeral is set flush left
and the text follows with the usual word spacing.}

\subsection{Program Code}

Program listings or program commands in the text are normally set in
typewriter font, e.g., CMTT10 or Courier.

\medskip

\noindent
{\it Example of a Computer Program}
\begin{verbatim}
program Inflation (Output)
  {Assuming annual inflation rates of 7%, 8%, and 10%,...
   years};
   const
     MaxYears = 10;
   var
     Year: 0..MaxYears;
     Factor1, Factor2, Factor3: Real;
   begin
     Year := 0;
     Factor1 := 1.0; Factor2 := 1.0; Factor3 := 1.0;
     WriteLn('Year  7% 8% 10%'); WriteLn;
     repeat
       Year := Year + 1;
       Factor1 := Factor1 * 1.07;
       Factor2 := Factor2 * 1.08;
       Factor3 := Factor3 * 1.10;
       WriteLn(Year:5,Factor1:7:3,Factor2:7:3,Factor3:7:3)
     until Year = MaxYears
end.
\end{verbatim}
%
\noindent
{\small (Example from Jensen K., Wirth N. (1991) Pascal user manual and
report. Springer, New York)}

\subsection{Citations}

For citations in the text please use
square brackets and consecutive numbers: \cite{jour}, \cite{lncschap},
\cite{proceeding1} -- provided automatically
by \LaTeX 's \verb|\cite| \dots\verb|\bibitem| mechanism.

\subsection{Page Numbering and Running Heads}

There is no need to include page numbers. If your paper title is too
long to serve as a running head, it will be shortened. Your suggestion
as to how to shorten it would be most welcome.

\section{LNCS Online}

The online version of the volume will be available in LNCS Online.
Members of institutes subscribing to the Lecture Notes in Computer
Science series have access to all the pdfs of all the online
publications. Non-subscribers can only read as far as the abstracts. If
they try to go beyond this point, they are automatically asked, whether
they would like to order the pdf, and are given instructions as to how
to do so.

Please note that, if your email address is given in your paper,
it will also be included in the meta data of the online version.

\section{BibTeX Entries}

The correct BibTeX entries for the Lecture Notes in Computer Science
volumes can be found at the following Website shortly after the
publication of the book:
\url{http://www.informatik.uni-trier.de/~ley/db/journals/lncs.html}

\subsubsection*{Acknowledgments.} The heading should be treated as a
subsubsection heading and should not be assigned a number.

\section{The References Section}\label{references}

In order to permit cross referencing within LNCS-Online, and eventually
between different publishers and their online databases, LNCS will,
from now on, be standardizing the format of the references. This new
feature will increase the visibility of publications and facilitate
academic research considerably. Please base your references on the
examples below. References that don't adhere to this style will be
reformatted by Springer. You should therefore check your references
thoroughly when you receive the final pdf of your paper.
The reference section must be complete. You may not omit references.
Instructions as to where to find a fuller version of the references are
not permissible.

We only accept references written using the latin alphabet. If the title
of the book you are referring to is in Russian or Chinese, then please write
(in Russian) or (in Chinese) at the end of the transcript or translation
of the title.

The following section shows a sample reference list with entries for
journal articles \cite{jour}, an LNCS chapter \cite{lncschap}, a book
\cite{book}, proceedings without editors \cite{proceeding1} and
\cite{proceeding2}, as well as a URL \cite{url}.
Please note that proceedings published in LNCS are not cited with their
full titles, but with their acronyms!

\begin{thebibliography}{4}

\bibitem{jour} Smith, T.F., Waterman, M.S.: Identification of Common Molecular
Subsequences. J. Mol. Biol. 147, 195--197 (1981)

\bibitem{lncschap} May, P., Ehrlich, H.C., Steinke, T.: ZIB Structure Prediction Pipeline:
Composing a Complex Biological Workflow through Web Services. In: Nagel,
W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006. LNCS, vol. 4128,
pp. 1148--1158. Springer, Heidelberg (2006)

\bibitem{book} Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing
Infrastructure. Morgan Kaufmann, San Francisco (1999)

\bibitem{proceeding1} Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid
Information Services for Distributed Resource Sharing. In: 10th IEEE
International Symposium on High Performance Distributed Computing, pp.
181--184. IEEE Press, New York (2001)

\bibitem{proceeding2} Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The Physiology of the
Grid: an Open Grid Services Architecture for Distributed Systems
Integration. Technical report, Global Grid Forum (2002)

\bibitem{url} National Center for Biotechnology Information, \url{http://www.ncbi.nlm.nih.gov}

\end{thebibliography}

\section*{Appendix: Springer-Author Discount}

LNCS authors are entitled to a 33.3\% discount off all Springer
publications. Before placing an order, the author should send an email, 
giving full details of his or her Springer publication,
to \url{orders-HD-individuals@springer.com} to obtain a so-called token. This token is a
number, which must be entered when placing an order via the Internet, in
order to obtain the discount.

\section{Checklist of Items to be Sent to Volume Editors}
Here is a checklist of everything the volume editor requires from you:

\begin{itemize}
\settowidth{\leftmargin}{{\Large$\square$}}\advance\leftmargin\labelsep
\itemsep8pt\relax
\renewcommand\labelitemi{{\lower1.5pt\hbox{\Large$\square$}}}

\item The final \LaTeX{} source files
\item A final PDF file
\item A copyright form, signed by one author on behalf of all of the
authors of the paper.
\item A readme giving the name and email address of the
corresponding author.
\end{itemize}
\end{document}

### 2017-07-25 paper/main.tex
working on inferences rules.

\documentclass[runningheads,a4paper]{llncs}

\usepackage{bussproofs}
\newenvironment{bprooftree}
  {\leavevmode\hbox\bgroup}
  {\DisplayProof\egroup}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{multicol}

\usepackage{url}
\urldef{\mailsc}\path|{jprieto9, asr}@eafit.edu.co|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

% --------------------------------------------------------------------------
% Tikz Configuration
% --------------------------------------------------------------------------
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows}
\usetikzlibrary{automata}
\usetikzlibrary{calc}
\usepackage{rotating}

\tikzset{
    hyperlink node/.style={
        alias=sourcenode,
        append after command={
            let     \p1 = (sourcenode.north west),
                \p2=(sourcenode.south east),
                \n1={\x2-\x1},
                \n2={\y1-\y2} in
            node [inner sep=0pt, outer sep=0pt,anchor=north west,at=(\p1)]
            {\hyperlink{#1}{\XeTeXLinkBox{\phantom{\rule{\n1}{\n2}}}}}
                    %xelatex needs \XeTeXLinkBox, won't create a link unless it
                    %finds text --- rules don't work without \XeTeXLinkBox.
                    %Still builds correctly with pdflatex and lualatex
        }
    }
}

\tikzstyle{vertex}=[auto=left,circle,fill=black!25,minimum size=5pt,inner sep=0pt]

% --------------------------------------------------------------------------
% Minted Configuration
% --------------------------------------------------------------------------
%% \usepackage{minted}
%% \setminted[cagda]{
%% , fontsize  = \footnotesize
%% , frame     = none
%% % , framerule = 0.4pt
%% % , framesep  = 0pt
%% , style     = cagda
%% }

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Towards Proof-Reconstruction of Problems in Classical Propositional Logic}

% a short form should be given in case it is too long for the running head
\titlerunning{Towards Proof-Reconstruction of Problems in Classical Propositional Logic}

\author{Jonathan Prieto-Cubides%
\and Andr\'es Sicard-Ram\'irez}
%
\authorrunning{Proof-Reconstruction in Classical Propositional Logic}

\institute{EAFIT University, School of Sciences and Engineering,\\
Medell\'in, Colombia\\
\mailsc}

% \toctitle{Lecture Notes in Computer Science}
% \tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
...
\keywords{Proof reconstruction, Agda, Automatic theorem prover, Classical Propositional Logic, Metis }
\end{abstract}

\section{Introduction}
Proof reconstruction is a hard labor, it depends on the integration of two complex systems. On one hand, we have the automatic theorem provers (henceforth ATPs), these are programs designed to answer automatically if a statement, the conjecture, is a theorem, is counter-feasible or is unknown based on a set of hypothesis. Provers often deal with problems in First-Order Logic with or without equality, High-Order Logic, Intuitionistic Logic, and other logics or background theories.

For proof reconstruction, we are interested in ATP tools that can deliver proof objects in a consistent format to work with, that is, a full   script  describing  step-by-step the table of the derivation to get the proof. Unfortunately, just a few of the ATPs can give us such a proof object. For problems in Classical Propositional Logic (henceforth CPL), from a list of at least forty\footnote{ATPs available in the website  \texttt{SystemOnTPTP} from the TPTP World} ATPs, just a few can deliver proofs (e.g. \verb!CVC4!~\cite{Barrett2011}, \verb!SPASS!~\cite{Weidenbach2009}, \verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less deliver proofs in the TSTP file format (e.g. \verb!E!~\cite{Schulz:AICOM-2002}, \verb!Metis!~\cite{hurd2003first}, \verb!Vampire!~\cite{Riazanov1999}, \verb!Z3!).

On the other hand, we have the proof checkers, Interactive Theorem Provers
%(henceforth ITP)
or proof assistants (e.g. \verb!Agda!~\cite{agdateam}, \verb!Coq!~\cite{coqteam}, \verb!Isabelle!~\cite{paulson1994isabelle}, \verb!HOL4!~\cite{norrish2007hol}). These programs allow us to define the formal language for the problems like operators, logic variables, axioms, and theorems. They can assist us to check and validate the proof script delivered by the provers. Because the formalism in the source (the proof generated by the ATP) is not necessarily the same formalism in the target (proof reconstructed in the proof assistant), then the reconstruction of a proof involves a deep understanding around the deduction process done by the ATP, for translating that deduction later into the proof assistant.

Many approaches have been proposed and some tools have been implemented for proof reconstruction in the last decades, we mention some of them in the following.

\subsection*{Related Work.}\label{Related Work}
\par
\verb!Sledgehammer! is a tool for \verb!Isabelle! proof assistant~\cite{paulson1994isabelle} that provides a full integration of automatic theorem provers including ATPs (see, for example, \cite{meng2006automation} and~\cite{blanchette2013extending}) and SMT solvers (see, for example,~\cite{blanchette2013extending}) with \verb!Isabelle/HOL!~\cite{nipkow2002isabelle}, the specialization of \verb!Isabelle! for Higher-Order Logic.

\verb!Waldmeister! is an automatic theorem prover for Unit Equational Logic \cite{hillenbrand1997}. Foster and Struth \cite{foster2011integrating} integrate \verb!Waldmeister! into \verb!Agda!~\cite{agdateam}. This integration requires a proof reconstruction step but authors' approach is restricted to Pure Equational Logic --also called Identity Theory \cite{humberstone2011}-- that is, First-Order Logic with Equality but no other predicate symbols and no functions symbols \cite{appel1959}.

An integration between SMT Solvers and \verb!Agda! in \cite{kanso2016light} use a \emph{oracle and reflection} approach to give certificates for propositional problems.

\verb!SMTCoq! \cite{armand2011} is a tool for the \verb!Coq! proof assistant \cite{coqteam} which provides a certified checker for proof witness coming from the SMT solver \verb!veriT! \cite{bouton2009} and adds a new tactic named verit, that calls \verb!veriT! on any \verb!Coq! goal.

Given a fixed but arbitrary First-Order signature, in \cite{bezem2002automated} transform a proof produced by the first-order automatic theorem prover \verb!Bliksem! \cite{deNivelle2003} in a \verb!Coq! proof term.

We structure the paper as follows. In section \ref{sec2}, we briefly introduce the \verb!Metis! Prover. In section \ref{secproofrecon}, we present our approach to reconstruct proofs deliver by \verb!Metis! in \verb!Agda!. In section 4, we present a complete example of a proof reconstructed with our tool for a CPL problem. In section \ref{secconclusion}, we discuss some limitations and conclusions, for ending up with the future work.

\section{Metis: Language and Proof Terms}\label{sec2}
\verb!Metis! is an automatic theorem prover for First-order Logic with Equality~\cite{hurd2003first}.

\subsection{Input and Output Language}
The \verb!TPTP! language --which includes the First-Order Form (FOF) and Clause Normal Form (CNF) formats \cite{sutcliffe2009} -- is de facto input standard language and the \verb!TSTP! language is de facto output standard language~\cite{sutcliffe2004tstp}.

\subsection{Proof Terms}

\verb!Metis!' proof terms encode natural deduction proofs. Its deduction system uses six simple inference rules and it proves conjectures by refutation.

\[
\begin{bprooftree}
\AxiomC{}
\RightLabel{axiom}
\UnaryInfC{$C$}
\end{bprooftree}
\qquad
\begin{bprooftree}
\AxiomC{}
\RightLabel{assume $L$}
\UnaryInfC{$L \vee \neg L$}
\end{bprooftree}
\qquad
\begin{bprooftree}
\AxiomC{}
\RightLabel{refl $t$}
\UnaryInfC{$t = t$}
\end{bprooftree}
\qquad
\begin{bprooftree}
\AxiomC{$C$}
\RightLabel{subst $\sigma$}
\UnaryInfC{$\sigma\,C$}
\end{bprooftree}
\qquad
\]

\[
\begin{bprooftree}
\AxiomC{}
\RightLabel{equality $L$ $p$ $t$}
\UnaryInfC{$\neg (L[p] = t) \vee \neg L \vee L[ p \mapsto t]$}
\end{bprooftree}
\qquad
\begin{bprooftree}
\AxiomC{$L \vee C$}
\AxiomC{$\neg L \vee D$}
\RightLabel{resolve $L$}
\BinaryInfC{$C \vee D$}
\end{bprooftree}
\]

Metis’ proofs are directed acyclic graphs (henceforth DAG), refutations trees. Each node stands for an application of an inference rule and the leaves in the tree represent formulas in the given problem. Each node is labeled with an axiom or an inference rule name (e.g. \verb!resolve!). Each edge links a premise with one conclusion. All proof graphs have in their root the conclusion ⊥ si
nce Metis uses refutation in each deduction step.

\subsection{Proof Rules}
Using \verb!Metis! to prove CPL problems, we found that their TSTP derivations showed six inference rules, \verb!canonicalize!, \verb!conjunct!, \verb!negate!, \verb!simplify!,  \verb!strip! and \verb!resolve!.

The \verb!canonicalize! rule transforms a formula to one of its normal form, CNF, NNF, and DNF.
This rule also performs simple simplification in the process, applying for instance some of the following theorems assuming commutative properties.

\[
\begin{bprooftree}
  \AxiomC{$P \vee \bot$}
  \UnaryInfC{$P$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$P \vee \top$}
\UnaryInfC{$P$}
\end{bprooftree}
\begin{bprooftree}
\AxiomC{$P \vee \neg P$}
\UnaryInfC{$\top$}
\end{bprooftree}
\begin{bprooftree}
  \AxiomC{$P \wedge \bot$}
  \UnaryInfC{$\bot$}
\end{bprooftree}
\begin{bprooftree}
  \AxiomC{$P \wedge \top$}
  \UnaryInfC{$P$}
\end{bprooftree}
\begin{bprooftree}
  \AxiomC{$P \wedge \neg P$}
  \UnaryInfC{$\bot$}
\end{bprooftree}
\]

The \verb!strip! rule extracts a subgoal from a goal. The splitting process
takes a goal and recursively recolects all hypotesis required in order to prove the goal.
At the end, the final hypotesis represent the subgoals.

\section{Proof Reconstruction in Agda}
\label{secproofrecon}
As a proof checker, we choose the proof-assistant Agda without a clear reason in mind
rather than its syntax language shares similarity with Haskell, the programming language
of our proof-reconstruction tool, Athena.

\subsection{LCF-Style Theorem Proving}

\subsection{The Translation Method}
\subsection{Reconstruction Work-flow}
Explain in a diagram like we did in the slides for the AIM ...

\subsection{Emulation of Inference Rules in Agda}

% \subsection{Limitations}
%

% \section{Experimental Results}
% We could be able to reconstruct 88 problems in CPL.

\subsection{Implementation}
...
\subsection{Examples}
...

\section{Conclusions}
\label{secconclusion}
\verb!simplify! and \verb!canonicalize! coverage.
Proof-reconstruction can be done in Agda from the Metis' proofs.
...

\subsubsection*{Future Work.}
First-Order Logic support.

\subsubsection*{Acknowledgments.}
We thank EAFIT University in Medell\'in, Colombia for funding support.

\bibliographystyle{splncs03}
\bibliography{ref}

\end{document}

### 2017-07-27 paper/main.tex
Working on the introduction.

@@
 % first the title is needed
-\title{Towards Proof-Reconstruction of Problems in Classical Propositional Logic}
+\title{Towards Proof-Reconstruction of Problems in Classical Propositional Logic
+in Agda}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{Towards Proof-Reconstruction of Problems in Classical Propositional Logic}
+\titlerunning{Towards Proof-Reconstruction of Problems in Classical
+  Propositional Logic in Agda}
 
@@
 \section{Introduction}
-Proof reconstruction is a hard labor, it depends on the integration of two complex systems.
-On one hand, we have the automatic theorem provers (henceforth ATPs), these are programs designed to answer automatically if a statement, the conjecture, is a theorem, is counter-feasible or is unknown based on a set of hypothesis.
-Provers often deal with problems in First-Order Logic with or without equality, High-Order Logic, Intuitionistic Logic, and other logics or background theories.
+Proof reconstruction is a hard labor, it integrates two
+complex systems. On one hand, we have the automatic theorem provers (henceforth
+ATPs) that depending on the specification logic and background theories exist
+many alternatives. They are SAT solvers (e.g. \verb!zChaff!~\cite{Moskewicz2001} and \verb!MiniSat!~\cite{Een2004}) to prove unsatisfiability of CNF formulas,
+QBF solvers (e.g.~\verb!GhostQ!~\cite{Klieber2014} and ~\verb!DepQBF!~\cite{Lonsing2017}) to prove satisfiability and invalidity of quantified Boolean
+formulas, SMT solvers (e.g \verb!CVC4!~\cite{Barrett2011}, \verb!veriT!~\cite{bouton2009}, \verb!Z3!~\cite{DeMoura2008}) to
+prove unsatisfiability of formulas from first-order logic with theories,  and
+finally, the ATPs to prove validity of formulas from first-order logic with
+equality (e.g.~\verb!E!~\cite{Schulz:AICOM-2002},~\verb!Gandalf!~\cite{Tammet1997},~\verb!leanCoP!~\cite{Otten2008},~\verb!Metis!~\cite{hurd2003first},~\verb!SPASS!~\cite{Weidenbach2009} and ~\verb!Vampire!~\cite{Riazanov1999}),
+high-order logic (e.g.~\verb!Leo-II!,~\verb!Satallax!), intuitonistic logic
+(e.g.~\verb!ileanCoP!~\cite{Otten2008},~\verb!JProver!~\cite{Schmitt2001},~\verb!Gandalf!~\cite{Tammet1997}), among others.
 
-For proof reconstruction, we are interested in ATP tools that can deliver proof objects in a consistent format to work with, that is, a full   script  describing  step-by-step the table of the derivation to get the proof.
-Unfortunately, just a few of the ATPs can give us such a proof object.
-For problems in Classical Propositional Logic (henceforth CPL), from a list of at least forty\footnote{ATPs available in the website  \texttt{SystemOnTPTP} from the TPTP World} ATPs, just a few can deliver proofs (e.g.
-\verb!CVC4!~\cite{Barrett2011}, \verb!SPASS!~\cite{Weidenbach2009}, \verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less deliver proofs in the TSTP file format (e.g.
-\verb!E!~\cite{Schulz:AICOM-2002}, \verb!Metis!~\cite{hurd2003first}, \verb!Vampire!~\cite{Riazanov1999}, \verb!Z3!).
+For proof reconstruction, we are interested in ATP tools that can deliver proof
+objects in a consistent format to work with, that is, a full script describing
+step-by-step the table of the derivation to get the actual proof. Unfortunately,
+just a few of the ATPs generate in their outputs a proof object.
+
+For problems in classical propositional logic (henceforth CPL), from a list of
+at least forty\footnote{ATPs available in the website  \texttt{SystemOnTPTP}
+  from the TPTP World} ATPs, just a few deliver proofs (e.g.
+\verb!CVC4!~\cite{Barrett2011}, \verb!SPASS!~\cite{Weidenbach2009},
+\verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less proofs in file
+format like TSTP (e.g. \verb!E!~\cite{Schulz:AICOM-2002}, \verb!Metis!~\cite{hurd2003first}, \verb!Vampire!~\cite{Riazanov1999}, \verb!Z3!).
 
@@
 \par
-\verb!Sledgehammer!
-is a tool for \verb!Isabelle!
-proof assistant~\cite{paulson1994isabelle} that provides a full integration of automatic theorem provers including ATPs (see, for example, \cite{meng2006automation} and~\cite{blanchette2013extending}) and SMT solvers (see, for example,~\cite{blanchette2013extending}) with \verb!Isabelle/HOL!~\cite{nipkow2002isabelle}, the specialization of \verb!Isabelle!
-for Higher-Order Logic.
+\verb!Sledgehammer! is a tool for \verb!Isabelle! proof
+assistant~\cite{paulson1994isabelle} that provides a full integration of
+automatic theorem provers including ATPs (see, for example,
+\cite{meng2006automation}, ~\cite{blanchette2013extending} and \cite{Fleury2014}) and SMT solvers (see, for
+example,~\cite{blanchette2013extending},~\cite{bohme2010} and \cite{Fleury2014}) with \verb!Isabelle/HOL!~\cite{nipkow2002isabelle}, the specialization of \verb!Isabelle! for Higher-Order Logic.
 
@@
 \verb!SMTCoq!
-\cite{armand2011} is a tool for the \verb!Coq!
+(see \cite{armand2011} and \cite{Ekici2017} for more details) is a tool for the \verb!Coq!
 proof assistant \cite{coqteam} which provides a certified checker for proof witness coming from the SMT solver \verb!veriT!

### 2017-07-28 paper/main.tex
minor changes
minor changes.

@@
 many alternatives. They are SAT solvers (e.g. \verb!zChaff!~\cite{Moskewicz2001} and \verb!MiniSat!~\cite{Een2004}) to prove unsatisfiability of CNF formulas,
-QBF solvers (e.g.~\verb!GhostQ!~\cite{Klieber2014} and ~\verb!DepQBF!~\cite{Lonsing2017}) to prove satisfiability and invalidity of quantified Boolean
-formulas, SMT solvers (e.g \verb!CVC4!~\cite{Barrett2011}, \verb!veriT!~\cite{bouton2009}, \verb!Z3!~\cite{DeMoura2008}) to
+QBF solvers (e.g. \verb!GhostQ!~\cite{Klieber2014} and~\verb!DepQBF!~\cite{Lonsing2017}) to prove satisfiability and invalidity of quantified Boolean
+formulas, SMT solvers (e.g \verb!CVC4!~\cite{Barrett2011}, \verb!veriT!~\cite{bouton2009}, and \verb!Z3!~\cite{DeMoura2008}) to
 prove unsatisfiability of formulas from first-order logic with theories,  and
 finally, the ATPs to prove validity of formulas from first-order logic with
-equality (e.g.~\verb!E!~\cite{Schulz:AICOM-2002},~\verb!Gandalf!~\cite{Tammet1997},~\verb!leanCoP!~\cite{Otten2008},~\verb!Metis!~\cite{hurd2003first},~\verb!SPASS!~\cite{Weidenbach2009} and ~\verb!Vampire!~\cite{Riazanov1999}),
-high-order logic (e.g.~\verb!Leo-II!,~\verb!Satallax!), intuitonistic logic
-(e.g.~\verb!ileanCoP!~\cite{Otten2008},~\verb!JProver!~\cite{Schmitt2001},~\verb!Gandalf!~\cite{Tammet1997}), among others.
+equality (e.g.
+\verb!E!~\cite{Schulz:AICOM-2002},~\verb!Gandalf!~\cite{Tammet1997},~\verb!leanCoP!~\cite{Otten2008},~\verb!Metis!~\cite{hurd2003first},~\verb!SPASS!~\cite{Weidenbach2009} and ~\verb!Vampire!~\cite{Riazanov1999}),
+high-order logic (e.g. \verb!Leo-II!~\cite{Benzmuller2008} and \verb!Satallax!~\cite{Brown2012}), intuitonistic logic
+(e.g. \verb!ileanCoP!~\cite{Otten2008},~\verb!JProver!~\cite{Schmitt2001}, and \verb!Gandalf!~\cite{Tammet1997}), among others.
 
-For proof reconstruction, we are interested in ATP tools that can deliver proof
-objects in a consistent format to work with, that is, a full script describing
+For proof reconstruction, we need from the ATP tools proof objects in a consistent format to work with, that is, a full script describing
 step-by-step the table of the derivation to get the actual proof. Unfortunately,
-just a few of the ATPs generate in their outputs a proof object.
-
+not all ATPs can deliver proofs or some useful output for reconstruct a proof.
 For problems in classical propositional logic (henceforth CPL), from a list of
-at least forty\footnote{ATPs available in the website  \texttt{SystemOnTPTP}
-  from the TPTP World} ATPs, just a few deliver proofs (e.g.
-\verb!CVC4!~\cite{Barrett2011}, \verb!SPASS!~\cite{Weidenbach2009},
-\verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less proofs in file
-format like TSTP (e.g. \verb!E!~\cite{Schulz:AICOM-2002}, \verb!Metis!~\cite{hurd2003first}, \verb!Vampire!~\cite{Riazanov1999}, \verb!Z3!).
+at least forty\footnote{ATPs available in the website  \texttt{SystemOnTPTP} from the TPTP World} ATPs, just a few were able to deliver proofs (e.g.
+\verb!CVC4!~\cite{Barrett2011}, \verb!SPASS!, and
+\verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less generate proofs in a file
+format like TSTP~\cite{sutcliffe2004tstp} (e.g. \verb!E!~\cite{Schulz:AICOM-2002}, \verb!Metis!~\cite{hurd2003first}, \verb!Vampire!, and \verb!Z3!) or LFSC~\cite{Stump2008}.
 
@@
 They can assist us to check and validate the proof script delivered by the provers.
-Because the formalism in the source (the proof generated by the ATP) is not necessarily the same formalism in the target (proof reconstructed in the proof assistant), then the reconstruction of a proof involves a deep understanding around the deduction process done by the ATP, for translating that deduction later into the proof assistant.
+Because the formalism in the source (the proof generated by the ATP) is not necessarily the same formalism in the target (proof reconstructed in the proof assistant), the reconstruction of a proof involves a deep understanding around the deduction process done by the ATP, for translating that deduction later into the proof assistant, the so called ``reverse engineering''.
 

### 2017-07-28 paper/main.tex
minor changes.

@@
 formulas, SMT solvers (e.g \verb!CVC4!~\cite{Barrett2011}, \verb!veriT!~\cite{bouton2009}, and \verb!Z3!~\cite{DeMoura2008}) to
-prove unsatisfiability of formulas from first-order logic with theories,  and
-finally, the ATPs to prove validity of formulas from first-order logic with
+prove unsatisfiability of formulas from first-order logic with theories, and the ATPs to prove validity of formulas from first-order logic with
 equality (e.g.
 \verb!E!~\cite{Schulz:AICOM-2002},~\verb!Gandalf!~\cite{Tammet1997},~\verb!leanCoP!~\cite{Otten2008},~\verb!Metis!~\cite{hurd2003first},~\verb!SPASS!~\cite{Weidenbach2009} and ~\verb!Vampire!~\cite{Riazanov1999}),
-high-order logic (e.g. \verb!Leo-II!~\cite{Benzmuller2008} and \verb!Satallax!~\cite{Brown2012}), intuitonistic logic
+high-order logic (e.g. \verb!Leo-II!~\cite{Benzmuller2008} and
+\verb!Satallax!~\cite{Brown2012}) or  intuitonistic logic
 (e.g. \verb!ileanCoP!~\cite{Otten2008},~\verb!JProver!~\cite{Schmitt2001}, and \verb!Gandalf!~\cite{Tammet1997}), among others.
 
-For proof reconstruction, we need from the ATP tools proof objects in a consistent format to work with, that is, a full script describing
-step-by-step the table of the derivation to get the actual proof. Unfortunately,
-not all ATPs can deliver proofs or some useful output for reconstruct a proof.
-For problems in classical propositional logic (henceforth CPL), from a list of
-at least forty\footnote{ATPs available in the website  \texttt{SystemOnTPTP} from the TPTP World} ATPs, just a few were able to deliver proofs (e.g.
+For proof reconstruction, what we need from the ATP tools is a proof object in a consistent format to work with, that is, a full script describing
+step-by-step with exhaustive details and without ambiguities, the table of the
+derivation to get the actual proof. For problems in classical propositional logic (henceforth CPL), from a list of
+at least forty\footnote{ATPs available from the web service \texttt{SystemOnTPTP} of the TPTP World.} ATPs, just a few are able to deliver proofs (e.g.
 \verb!CVC4!~\cite{Barrett2011}, \verb!SPASS!, and
-\verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less generate proofs in a file
-format like TSTP~\cite{sutcliffe2004tstp} (e.g. \verb!E!~\cite{Schulz:AICOM-2002}, \verb!Metis!~\cite{hurd2003first}, \verb!Vampire!, and \verb!Z3!) or LFSC~\cite{Stump2008}.
+\verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less reply with a proof in a file
+format like TSTP~\cite{sutcliffe2004tstp} (e.g. \verb!E!, \verb!Metis!, \verb!Vampire!, and \verb!Z3!) or LFSC~\cite{Stump2008}.
 
-On the other hand, we have the proof checkers, Interactive Theorem Provers
-%(henceforth ITP)
-or proof assistants (e.g.
-\verb!Agda!~\cite{agdateam}, \verb!Coq!~\cite{coqteam}, \verb!Isabelle!~\cite{paulson1994isabelle}, \verb!HOL4!~\cite{norrish2007hol}).
-These programs allow us to define the formal language for the problems like operators, logic variables, axioms, and theorems.
-They can assist us to check and validate the proof script delivered by the provers.
-Because the formalism in the source (the proof generated by the ATP) is not necessarily the same formalism in the target (proof reconstructed in the proof assistant), the reconstruction of a proof involves a deep understanding around the deduction process done by the ATP, for translating that deduction later into the proof assistant, the so called ``reverse engineering''.
+On the other hand, we have the proof checkers, interactive theorem provers
+(henceforth ITP) or proof assistants (e.g. \verb!Agda!~\cite{agdateam},
+\verb!Coq!~\cite{coqteam}, \verb!Isabelle!~\cite{paulson1994isabelle},
+\verb!HOL4!~\cite{norrish2007hol}) and their specification logic. The ITPs allow us to define the formal
+language for the problems like operators, logic variables, axioms, and theorems.
+With ITPs tools, we can check and validate proof scripts delivered by provers
+with or without any guidance.
+Because the logic of the source (the proof generated by the
+ATP) is not necessarily the same logic in the target, the reconstruction turns
+out in a ``reverse engineering'' task. Reconstructing a proof involves a deep
+understanding around the deduction process done by the ATP and the specification
+logic in the ITP.
 
@@
 
-\verb!Metis!' proof terms encode natural deduction proofs. Its deduction system uses six simple inference rules and it proves conjectures by refutation.
+\verb!Metis!'' proof terms encode natural deduction proofs. Its deduction system uses six simple inference rules and it proves conjectures by refutation.
 
@@
 The \verb!strip! rule extracts a subgoal from a goal. The splitting process
-takes a goal and recursively recolects all hypotesis required in order to prove the goal.
-At the end, the final hypotesis represent the subgoals.
+takes a goal and recursively recollects all hypothesis required in order to prove the goal.
+At the end, the final hypothesis represent the subgoals.
 
@@
 \subsubsection*{Acknowledgments.}
-We thank EAFIT University in Medell\'in, Colombia for funding support.
+We thank EAFIT University of Medell\'in, Colombia for funding support.
+This is part of Jonathan Prieto-Cubides's Master thesis in Applied
+Mathematics, written under the supervision of Andr\'es Sicard-Ram\'irez
+for the Logic and Computation Research Group at the EAFIT University.
+
+We also acknowledge the work~\cite{Gomez-Londono2015} done by
+Alejandro G\'omez-Londo\~no that deserves as the basis for our parsing module
+for TSTP files.
+And last but not least, we gratefully acknowledge Andreas Abel and Chalmers University of Gothenburg, Sweden for inviting us to be part of the Agda Implementors’ Meeting XXV where we presented part of this paper.
 

### 2017-07-31 paper/main.tex
testing incorporating Agda code for theorems.

@@
 
+\setcounter{tocdepth}{3}
+\usepackage{graphicx}
+\usepackage{array}
 \usepackage{bussproofs}
@@
   {\DisplayProof\egroup}
-
-\usepackage{amssymb}
-\setcounter{tocdepth}{3}
-\usepackage{graphicx}
-\usepackage{multicol}
-
-\usepackage{url}
-\urldef{\mailsc}\path|{jprieto9, asr}@eafit.edu.co|
-\newcommand{\keywords}[1]{\par\addvspace\baselineskip
-\noindent\keywordname\enspace\ignorespaces#1}
 
@@
 
-% --------------------------------------------------------------------------
-% Minted Configuration
-% --------------------------------------------------------------------------
-%% \usepackage{minted}
-%% \setminted[cagda]{
-%% , fontsize  = \footnotesize
-%% , frame     = none
-%% % , framerule = 0.4pt
-%% % , framesep  = 0pt
-%% , style     = cagda
-%% }
+%\usepackage[utf8]{inputenc}
+\usepackage{ucs}
+\usepackage{autofe}
+\usepackage{afterpage}
+\usepackage{comment}
+\usepackage{url}
+%\usepackage{times}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{stmaryrd}
+\usepackage{color}
+\usepackage{verbatim}
+\usepackage{fancyvrb}
+
+\DefineVerbatimEnvironment
+  {code}{Verbatim}
+  {} % {fontfamily=\tt} %freemodo
+
+\setcounter{secnumdepth}{5}
+
+%% ODER: format ==         = "\mathrel{==}"
+%% ODER: format /=         = "\neq "
+%
+%
+\makeatletter
+\@ifundefined{lhs2tex.lhs2tex.sty.read}%
+  {\@namedef{lhs2tex.lhs2tex.sty.read}{}%
+   \newcommand\SkipToFmtEnd{}%
+   \newcommand\EndFmtInput{}%
+   \long\def\SkipToFmtEnd#1\EndFmtInput{}%
+  }\SkipToFmtEnd
+
+\newcommand\ReadOnlyOnce[1]{\@ifundefined{#1}{\@namedef{#1}{}}\SkipToFmtEnd}
+\usepackage{amstext}
+\usepackage{amssymb}
+\usepackage{stmaryrd}
+\DeclareFontFamily{OT1}{cmtex}{}
+\DeclareFontShape{OT1}{cmtex}{m}{n}
+  {<5><6><7><8>cmtex8
+   <9>cmtex9
+   <10><10.95><12><14.4><17.28><20.74><24.88>cmtex10}{}
+\DeclareFontShape{OT1}{cmtex}{m}{it}
+  {<-> ssub * cmtt/m/it}{}
+\newcommand{\texfamily}{\fontfamily{cmtex}\selectfont}
+\DeclareFontShape{OT1}{cmtt}{bx}{n}
+  {<5><6><7><8>cmtt8
+   <9>cmbtt9
+   <10><10.95><12><14.4><17.28><20.74><24.88>cmbtt10}{}
+\DeclareFontShape{OT1}{cmtex}{bx}{n}
+  {<-> ssub * cmtt/bx/n}{}
+\newcommand{\tex}[1]{\text{\texfamily#1}}	% NEU
+
+\newcommand{\Sp}{\hskip.33334em\relax}
+
+\newcommand{\Conid}[1]{\mathit{#1}}
+\newcommand{\Varid}[1]{\mathit{#1}}
+\newcommand{\anonymous}{\kern0.06em \vbox{\hrule\@width.5em}}
+\newcommand{\plus}{\mathbin{+\!\!\!+}}
+\newcommand{\bind}{\mathbin{>\!\!\!>\mkern-6.7mu=}}
+\newcommand{\rbind}{\mathbin{=\mkern-6.7mu<\!\!\!<}}% suggested by Neil Mitchell
+\newcommand{\sequ}{\mathbin{>\!\!\!>}}
+\renewcommand{\leq}{\leqslant}
+\renewcommand{\geq}{\geqslant}
+\usepackage{polytable}
+
+%mathindent has to be defined
+\@ifundefined{mathindent}%
+  {\newdimen\mathindent\mathindent\leftmargini}%
+  {}%
+
+\def\resethooks{%
+  \global\let\SaveRestoreHook\empty
+  \global\let\ColumnHook\empty}
+\newcommand*{\savecolumns}[1][default]%
+  {\g@addto@macro\SaveRestoreHook{\savecolumns[#1]}}
+\newcommand*{\restorecolumns}[1][default]%
+  {\g@addto@macro\SaveRestoreHook{\restorecolumns[#1]}}
+\newcommand*{\aligncolumn}[2]%
+  {\g@addto@macro\ColumnHook{\column{#1}{#2}}}
+
+\resethooks
+
+\newcommand{\onelinecommentchars}{\quad-{}- }
+\newcommand{\commentbeginchars}{\enskip\{-}
+\newcommand{\commentendchars}{-\}\enskip}
+
+\newcommand{\visiblecomments}{%
+  \let\onelinecomment=\onelinecommentchars
+  \let\commentbegin=\commentbeginchars
+  \let\commentend=\commentendchars}
+
+\newcommand{\invisiblecomments}{%
+  \let\onelinecomment=\empty
+  \let\commentbegin=\empty
+  \let\commentend=\empty}
+
+\visiblecomments
+
+\newlength{\blanklineskip}
+\setlength{\blanklineskip}{0.66084ex}
+
+\newcommand{\hsindent}[1]{\quad}% default is fixed indentation
+\let\hspre\empty
+\let\hspost\empty
+\newcommand{\NB}{\textbf{NB}}
+\newcommand{\Todo}[1]{$\langle$\textbf{To do:}~#1$\rangle$}
+
+\EndFmtInput
+\makeatother
+%
+
+%
+%
+%
+%
+%
+% This package provides two environments suitable to take the place
+% of hscode, called "plainhscode" and "arrayhscode". 
+%
+% The plain environment surrounds each code block by vertical space,
+% and it uses \abovedisplayskip and \belowdisplayskip to get spacing
+% similar to formulas. Note that if these dimensions are changed,
+% the spacing around displayed math formulas changes as well.
+% All code is indented using \leftskip.
+%
+% Changed 19.08.2004 to reflect changes in colorcode. Should work with
+% CodeGroup.sty.
+%
+\ReadOnlyOnce{polycode.fmt}%
+\makeatletter
+
+\newcommand{\hsnewpar}[1]%
+  {{\parskip=0pt\parindent=0pt\par\vskip #1\noindent}}
+
+% can be used, for instance, to redefine the code size, by setting the
+% command to \small or something alike
+\newcommand{\hscodestyle}{}
+
+% The command \sethscode can be used to switch the code formatting
+% behaviour by mapping the hscode environment in the subst directive
+% to a new LaTeX environment.
+
+\newcommand{\sethscode}[1]%
+  {\expandafter\let\expandafter\hscode\csname #1\endcsname
+   \expandafter\let\expandafter\endhscode\csname end#1\endcsname}
+
+% "compatibility" mode restores the non-polycode.fmt layout.
+
+\newenvironment{compathscode}%
+  {\par\noindent
+   \advance\leftskip\mathindent
+   \hscodestyle
+   \let\\=\@normalcr
+   \let\hspre\(\let\hspost\)%
+   \pboxed}%
+  {\endpboxed\)%
+   \par\noindent
+   \ignorespacesafterend}
+
+\newcommand{\compaths}{\sethscode{compathscode}}
+
+% "plain" mode is the proposed default.
+% It should now work with \centering.
+% This required some changes. The old version
+% is still available for reference as oldplainhscode.
+
+\newenvironment{plainhscode}%
+  {\hsnewpar\abovedisplayskip
+   \advance\leftskip\mathindent
+   \hscodestyle
+   \let\hspre\(\let\hspost\)%
+   \pboxed}%
+  {\endpboxed%
+   \hsnewpar\belowdisplayskip
+   \ignorespacesafterend}
+
+\newenvironment{oldplainhscode}%
+  {\hsnewpar\abovedisplayskip
+   \advance\leftskip\mathindent
+   \hscodestyle
+   \let\\=\@normalcr
+   \(\pboxed}%
+  {\endpboxed\)%
+   \hsnewpar\belowdisplayskip
+   \ignorespacesafterend}
+
+% Here, we make plainhscode the default environment.
+
+\newcommand{\plainhs}{\sethscode{plainhscode}}
+\newcommand{\oldplainhs}{\sethscode{oldplainhscode}}
+\plainhs
+
+% The arrayhscode is like plain, but makes use of polytable's
+% parray environment which disallows page breaks in code blocks.
+
+\newenvironment{arrayhscode}%
+  {\hsnewpar\abovedisplayskip
+   \advance\leftskip\mathindent
+   \hscodestyle
+   \let\\=\@normalcr
+   \(\parray}%
+  {\endparray\)%
+   \hsnewpar\belowdisplayskip
+   \ignorespacesafterend}
+
+\newcommand{\arrayhs}{\sethscode{arrayhscode}}
+
+% The mathhscode environment also makes use of polytable's parray 
+% environment. It is supposed to be used only inside math mode 
+% (I used it to typeset the type rules in my thesis).
+
+\newenvironment{mathhscode}%
+  {\parray}{\endparray}
+
+\newcommand{\mathhs}{\sethscode{mathhscode}}
+
+% texths is similar to mathhs, but works in text mode.
+
+\newenvironment{texthscode}%
+  {\(\parray}{\endparray\)}
+
+\newcommand{\texths}{\sethscode{texthscode}}
+
+% The framed environment places code in a framed box.
+
+\def\codeframewidth{\arrayrulewidth}
+\RequirePackage{calc}
+
+\newenvironment{framedhscode}%
+  {\parskip=\abovedisplayskip\par\noindent
+   \hscodestyle
+   \arrayrulewidth=\codeframewidth
+   \tabular{@{}|p{\linewidth-2\arraycolsep-2\arrayrulewidth-2pt}|@{}}%
+   \hline\framedhslinecorrect\\{-1.5ex}%
+   \let\endoflinesave=\\
+   \let\\=\@normalcr
+   \(\pboxed}%
+  {\endpboxed\)%
+   \framedhslinecorrect\endoflinesave{.5ex}\hline
+   \endtabular
+   \parskip=\belowdisplayskip\par\noindent
+   \ignorespacesafterend}
+
+\newcommand{\framedhslinecorrect}[2]%
+  {#1[#2]}
+
+\newcommand{\framedhs}{\sethscode{framedhscode}}
+
+% The inlinehscode environment is an experimental environment
+% that can be used to typeset displayed code inline.
+
+\newenvironment{inlinehscode}%
+  {\(\def\column##1##2{}%
+   \let\>\undefined\let\<\undefined\let\\\undefined
+   \newcommand\>[1][]{}\newcommand\<[1][]{}\newcommand\\[1][]{}%
+   \def\fromto##1##2##3{##3}%
+   \def\nextline{}}{\) }%
+
+\newcommand{\inlinehs}{\sethscode{inlinehscode}}
+
+% The joincode environment is a separate environment that
+% can be used to surround and thereby connect multiple code
+% blocks.
+
+\newenvironment{joincode}%
+  {\let\orighscode=\hscode
+   \let\origendhscode=\endhscode
+   \def\endhscode{\def\hscode{\endgroup\def\@currenvir{hscode}\\}\begingroup}
+   %\let\SaveRestoreHook=\empty
+   %\let\ColumnHook=\empty
+   %\let\resethooks=\empty
+   \orighscode\def\hscode{\endgroup\def\@currenvir{hscode}}}%
+  {\origendhscode
+   \global\let\hscode=\orighscode
+   \global\let\endhscode=\origendhscode}%
+
+\makeatother
+\EndFmtInput
+%
+%
+\ReadOnlyOnce{agda.fmt}%
+
+\RequirePackage[T1]{fontenc}
+\RequirePackage[utf8x]{inputenc}
+\RequirePackage{ucs}
+\RequirePackage{amsfonts}
+
+\providecommand\mathbbm{\mathbb}
+
+% TODO: Define more of these ...
+\DeclareUnicodeCharacter{737}{\textsuperscript{l}}
+\DeclareUnicodeCharacter{8718}{\ensuremath{\blacksquare}}
+\DeclareUnicodeCharacter{8759}{::}
+\DeclareUnicodeCharacter{9669}{\ensuremath{\triangleleft}}
+\DeclareUnicodeCharacter{8799}{\ensuremath{\stackrel{\scriptscriptstyle ?}{=}}}
+\DeclareUnicodeCharacter{10214}{\ensuremath{\llbracket}}
+\DeclareUnicodeCharacter{10215}{\ensuremath{\rrbracket}}
+
+% TODO: This is in general not a good idea.
+\providecommand\textepsilon{$\epsilon$}
+\providecommand\textmu{$\mu$}
+
+%Actually, varsyms should not occur in Agda output.
+
+% TODO: Make this configurable. IMHO, italics doesn't work well
+% for Agda code.
+
+\renewcommand\Varid[1]{\mathord{\textsf{#1}}}
+\let\Conid\Varid
+\newcommand\Keyword[1]{\textsf{\textbf{#1}}}
+\EndFmtInput
+
+%%format : = "\in"
+
+\renewcommand*\rmdefault{cmr}
+
+\usepackage{url}
+% \urldef{\mailsc}\path|{jprieto9, asr}@eafit.edu.co|
+\newcommand{\keywords}[1]{\par\addvspace\baselineskip
+\noindent\keywordname\enspace\ignorespaces#1}
 
@@
 
-\institute{EAFIT University, School of Sciences and Engineering,\\
+\institute{EAFIT University, \emph{School of Sciences and Engineering},\\
 Medell\'in, Colombia\\
-\mailsc}
+\text{\tt \char123{}jprieto9\char44{}~asr\char125{}\char64{}eafit\char46{}edu\char46{}co}}
 
@@
 ...
-\keywords{Proof reconstruction, Agda, Automatic theorem prover, Classical Propositional Logic, Metis }
+\keywords{Proof reconstruction, Agda, Automatic theorem prover,
+  Classical Propositional Logic, Metis }
 \end{abstract}
@@
 \section{Introduction}
-Proof reconstruction is a hard labor, it integrates two
-complex systems. On one hand, we have the automatic theorem provers (henceforth
-ATPs) that depending on the specification logic and background theories exist
-many alternatives. They are SAT solvers (e.g. \verb!zChaff!~\cite{Moskewicz2001} and \verb!MiniSat!~\cite{Een2004}) to prove unsatisfiability of CNF formulas,
-QBF solvers (e.g. \verb!GhostQ!~\cite{Klieber2014} and~\verb!DepQBF!~\cite{Lonsing2017}) to prove satisfiability and invalidity of quantified Boolean
-formulas, SMT solvers (e.g \verb!CVC4!~\cite{Barrett2011}, \verb!veriT!~\cite{bouton2009}, and \verb!Z3!~\cite{DeMoura2008}) to
-prove unsatisfiability of formulas from first-order logic with theories, and the ATPs to prove validity of formulas from first-order logic with
-equality (e.g.
-\verb!E!~\cite{Schulz:AICOM-2002},~\verb!Gandalf!~\cite{Tammet1997},~\verb!leanCoP!~\cite{Otten2008},~\verb!Metis!~\cite{hurd2003first},~\verb!SPASS!~\cite{Weidenbach2009} and ~\verb!Vampire!~\cite{Riazanov1999}),
-high-order logic (e.g. \verb!Leo-II!~\cite{Benzmuller2008} and
-\verb!Satallax!~\cite{Brown2012}) or  intuitonistic logic
-(e.g. \verb!ileanCoP!~\cite{Otten2008},~\verb!JProver!~\cite{Schmitt2001}, and \verb!Gandalf!~\cite{Tammet1997}), among others.
-
-For proof reconstruction, what we need from the ATP tools is a proof object in a consistent format to work with, that is, a full script describing
-step-by-step with exhaustive details and without ambiguities, the table of the
-derivation to get the actual proof. For problems in classical propositional logic (henceforth CPL), from a list of
-at least forty\footnote{ATPs available from the web service \texttt{SystemOnTPTP} of the TPTP World.} ATPs, just a few are able to deliver proofs (e.g.
-\verb!CVC4!~\cite{Barrett2011}, \verb!SPASS!, and
-\verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less reply with a proof in a file
-format like TSTP~\cite{sutcliffe2004tstp} (e.g. \verb!E!, \verb!Metis!, \verb!Vampire!, and \verb!Z3!) or LFSC~\cite{Stump2008}.
+Proof reconstruction is a hard labor since it depends on the integration of two
+complex system. On one hand, we have the automatic theorem provers
+(henceforth ATP) and their specification logic. These tools are usually
+classified in at least one of the following categories.
+A SAT solver (e.g. \text{\tt zChaff}~\cite{Moskewicz2001} and \text{\tt MiniSat}
+~\cite{Een2004}) to prove unsatisfiability of CNF formulas, a QBF solver
+(e.g. \text{\tt GhostQ}~\cite{Klieber2014} and \text{\tt DepQBF}~\cite{Lonsing2017})
+to prove satisfiability and invalidity of quantified Boolean formulas, a SMT
+solver (e.g \text{\tt CVC4}~\cite{Barrett2011}, \text{\tt veriT}~\cite{bouton2009}, and
+\text{\tt Z3}~\cite{DeMoura2008}) to prove unsatisfiability of formulas from
+first-order logic with theories, and a prover for validity of formulas from
+first-order logic with equality (e.g. \text{\tt E}~\cite{Schulz:AICOM-2002},
+\text{\tt leanCoP}~\cite{Otten2008}, \text{\tt Metis}~\cite{hurd2003first}, \text{\tt SPASS}
+~\cite{Weidenbach2009} and \text{\tt Vampire}~\cite{Riazanov1999}), high-order logic
+(e.g. \text{\tt Leo\char45{}II}~\cite{Benzmuller2008} and \text{\tt Satallax}~\cite{Brown2012})
+or intuitionistic logic (e.g. \text{\tt ileanCoP}~\cite{Otten2008},
+\text{\tt JProver}~\cite{Schmitt2001}, and \text{\tt Gandalf}~\cite{Tammet1997}), among others.
 
 On the other hand, we have the proof checkers, interactive theorem provers
-(henceforth ITP) or proof assistants (e.g. \verb!Agda!~\cite{agdateam},
-\verb!Coq!~\cite{coqteam}, \verb!Isabelle!~\cite{paulson1994isabelle},
-\verb!HOL4!~\cite{norrish2007hol}) and their specification logic. The ITPs allow us to define the formal
-language for the problems like operators, logic variables, axioms, and theorems.
-With ITPs tools, we can check and validate proof scripts delivered by provers
-with or without any guidance.
-Because the logic of the source (the proof generated by the
-ATP) is not necessarily the same logic in the target, the reconstruction turns
-out in a ``reverse engineering'' task. Reconstructing a proof involves a deep
-understanding around the deduction process done by the ATP and the specification
-logic in the ITP.
+(henceforth ITP) or proof assistants (e.g. \text{\tt Agda}~\cite{agdateam},
+\text{\tt Coq}~\cite{coqteam}, \text{\tt Isabelle}~\cite{paulson1994isabelle}, and
+\text{\tt HOL4}~\cite{norrish2007hol}). The ITP tools provide us the logic framework
+to check and validate the reply of the ATPs, since they allow us to define the
+formal language for the problems like operators, logic variables, axioms, and
+theorems.
 
-Many approaches have been proposed and some tools have been implemented for proof reconstruction in the last decades, we mention some of them in the following.
+A proof reconstruction tool provides such an integration in one direction, the
+bridge between ATPs to ITPs. This is mostly a translation of the reply delivered
+by the prover into the formalism of the proof assistant.
+Because the formalism of the source (the proof generated by the ATP) is not
+necessarily the same logic in the target, the reconstruction turns out in a
+``reverse engineering'' task. Then, reconstructing a proof involves a deep
+understanding of the algorithms in the ATP and the specification logic in the ITP.
+
+What we need from the ATP tools is a proof object in a consistent format to work
+with, that is, a full script describing step-by-step with exhaustive details and
+without ambiguities, the table of the derivation to get the actual proof.
+For problems in classical propositional logic (henceforth CPL), from a list of
+at least forty\footnote{ATPs available from the web service \texttt{SystemOnTPTP}
+of the TPTP World.} ATPs, just a few provers are able to deliver proofs (e.g.
+\text{\tt CVC4}~\cite{Barrett2011}, \text{\tt SPASS}, and \text{\tt Waldmeister}
+~\cite{hillenbrand1997}) and a little bit less reply with a proof in a file
+format like TSTP~\cite{sutcliffe2004tstp} (e.g. \text{\tt E}, \text{\tt Metis},
+\text{\tt Vampire}, and \text{\tt Z3}), LFSC~\cite{Stump2008}, or the SMT-LIB
+~\cite{Bohme2011} format.
+
+Many approaches have been proposed and some tools have been implemented for
+proof reconstruction in the last decades. These programs are relevant not only
+because it helps to spread their usage but they also increase the confidence of
+their users about their algorithms and their correctness (see, for example, bugs
+in ATPs~\cite{Keller2013}, \cite{Bohme2011}, and \cite{Fleury2014}).
+We mention some tools in the following.
 
 \subsection*{Related Work.}\label{Related Work}
-\par
-\verb!Sledgehammer! is a tool for \verb!Isabelle! proof
-assistant~\cite{paulson1994isabelle} that provides a full integration of
-automatic theorem provers including ATPs (see, for example,
-\cite{meng2006automation}, ~\cite{blanchette2013extending} and \cite{Fleury2014}) and SMT solvers (see, for
-example,~\cite{blanchette2013extending},~\cite{bohme2010} and \cite{Fleury2014}) with \verb!Isabelle/HOL!~\cite{nipkow2002isabelle}, the specialization of \verb!Isabelle! for Higher-Order Logic.
 
-\verb!Waldmeister!
-is an automatic theorem prover for Unit Equational Logic \cite{hillenbrand1997}.
-Foster and Struth \cite{foster2011integrating} integrate \verb!Waldmeister!
-into \verb!Agda!~\cite{agdateam}.
-This integration requires a proof reconstruction step but authors' approach is restricted to Pure Equational Logic --also called Identity Theory \cite{humberstone2011}-- that is, First-Order Logic with Equality but no other predicate symbols and no functions symbols \cite{appel1959}.
+\text{\tt Sledgehammer} is a tool for \text{\tt Isabelle} proof assistant
+~\cite{paulson1994isabelle} that provides a full integration of automatic
+theorem provers including ATPs (see, for example, \cite{meng2006automation},
+\cite{blanchette2013extending} and \cite{Fleury2014}) and SMT solvers (see,
+for example, \cite{hurlin07practical}, \cite{bohme2010},
+\cite{blanchette2013extending}, and \cite{Fleury2014}) with \text{\tt Isabelle\char47{}HOL}
+\cite{nipkow2002isabelle}, the specialization of \text{\tt Isabelle} for
+higher-order logic. Sultana, Benzm{\"{u}}ller, and Paulson~\cite{Een2004}
+integrates \text{\tt Leo\char45{}II} and \text{\tt Satallax}, two theorem provers for high-order
+logic with \text{\tt Isabelle\char47{}HOL} proposing a modular proof reconstruction work flow.
 
-An integration between SMT Solvers and \verb!Agda! in \cite{kanso2016light} use a \emph{oracle and reflection} approach to give certificates for propositional problems.
+\text{\tt SMTCoq}~\cite{armand2011,Ekici2017} is a tool for the \text{\tt Coq} proof
+assistant \cite{coqteam} which provides a certified checker for proof witness
+coming from the SMT solver \text{\tt veriT} \cite{bouton2009} and adds a new tactic
+named verit, that calls \text{\tt veriT} on any \text{\tt Coq} goal.
+In \cite{bezem2002automated}, given a fixed but arbitrary first-order signature,
+the authors transform a proof produced by the first-order automatic theorem
+prover \text{\tt Bliksem} \cite{deNivelle2003} in a \text{\tt Coq} proof term.
 
-\verb!SMTCoq!
-(see \cite{armand2011} and \cite{Ekici2017} for more details) is a tool for the \verb!Coq!
-proof assistant \cite{coqteam} which provides a certified checker for proof witness coming from the SMT solver \verb!veriT!
-\cite{bouton2009} and adds a new tactic named verit, that calls \verb!veriT!
-on any \verb!Coq!
-goal.
+Hurd~\cite{Hurd1999} integrates the first-order resolution prover \text{\tt Gandalf}
+with \text{\tt HOL}~\cite{norrish2007hol}, a high-order theorem prover, following a
+LCF model implementing the tactic \text{\tt GANDALF\char95{}TAC}. The SMT solver \text{\tt CVC4}
+was integrated with \text{\tt HOL~Light}, a version of \text{\tt HOL} but with a simpler
+logic core. \text{\tt PRocH}~ tool by Kaliszyk and Urban~\cite{kaliszyk2013}
+reconstruct proofs from different ATPs to \text{\tt HOL~Light}, replaying the
+detailed inference steps from the ATPs with internal inference methods
+implemented in the ITP.
 
-Given a fixed but arbitrary First-Order signature, in \cite{bezem2002automated} transform a proof produced by the first-order automatic theorem prover \verb!Bliksem!
-\cite{deNivelle2003} in a \verb!Coq!
-proof term.
+\text{\tt Waldmeister} is an automatic theorem prover for unit equational logic
+\cite{hillenbrand1997}. Foster and Struth~\cite{foster2011integrating} integrate
+\text{\tt Waldmeister} into \text{\tt Agda}~\cite{agdateam}. This integration requires a
+proof reconstruction step but authors' approach is restricted to pure equational
+logic --also called identity theory~\cite{humberstone2011}-- that is,
+first-order logic with equality but no other predicate symbols and no functions
+symbols~\cite{appel1959}.
 
-We structure the paper as follows.
-In section \ref{sec2}, we briefly introduce the \verb!Metis!
-Prover.
-In section \ref{secproofrecon}, we present our approach to reconstruct proofs deliver by \verb!Metis!
-in \verb!Agda!.
-In section 4, we present a complete example of a proof reconstructed with our tool for a CPL problem.
-In section \ref{secconclusion}, we discuss some limitations and conclusions, for ending up with the future work.
+Kanso and Setzer~\cite{kanso2016light} integrate as SAT solvers (\text{\tt iProver},
+\text{\tt E}, and \text{\tt Z3}) in \text{\tt Agda} using an approach that they call
+\emph{oracle and reflection}.
+
+% replaying the Otter/Prover9 proofs in Mizar, and
+
+In this paper, we describe the integration of \text{\tt Metis} prover with the proof
+assistant \text{\tt Agda}. We structure the paper as follows. In section \ref{sec2},
+we briefly introduce the \text{\tt Metis} prover. In section \ref{secproofrecon},
+we present our approach to reconstruct proofs deliver by \text{\tt Metis} in
+\text{\tt Agda}. In section 4, we present a complete example of a proof
+reconstructed with our tool for a CPL problem. In section \ref{secconclusion},
+we discuss some limitations and conclusions, for ending up with the future work.
 
 \section{Metis: Language and Proof Terms}\label{sec2}
-\verb!Metis! is an automatic theorem prover for First-order Logic with Equality~\cite{hurd2003first}.
+\text{\tt Metis} is an automatic theorem prover for first-order logic with
+equality~\cite{hurd2003first}.
 
 \subsection{Input and Output Language}
-The \verb!TPTP!
-language --which includes the First-Order Form (FOF) and Clause Normal Form (CNF) formats \cite{sutcliffe2009} -- is de facto input standard language and the \verb!TSTP!
-language is de facto output standard language~\cite{sutcliffe2004tstp}.
+The \text{\tt TPTP} language --which includes the First-Order Form (FOF) and Clause
+Normal Form (CNF) formats \cite{sutcliffe2009} -- is de facto input standard
+language and the \text{\tt TSTP} language is de facto output standard
+language~\cite{sutcliffe2004tstp}.
 
@@
 
-\verb!Metis!'' proof terms encode natural deduction proofs. Its deduction system uses six simple inference rules and it proves conjectures by refutation.
+\text{\tt Metis}' proof terms encode natural deduction proofs. Its deduction system
+uses six simple inference rules and it proves conjectures by refutation.
 
 \[
+\scalebox{0.9}{
 \begin{bprooftree}
@@
 \qquad
+}
 \]
-
 \[
+\scalebox{0.9}{
 \begin{bprooftree}
@@
 \end{bprooftree}
+}
 \]
 
-Metis’ proofs are directed acyclic graphs (henceforth DAG), refutations trees.
-Each node stands for an application of an inference rule and the leaves in the tree represent formulas in the given problem.
-Each node is labeled with an axiom or an inference rule name (e.g.
-\verb!resolve!).
-Each edge links a premise with one conclusion.
-All proof graphs have in their root the conclusion ⊥ si
-nce Metis uses refutation in each deduction step.
+\text{\tt Metis}’ proofs are directed acyclic graphs (henceforth DAG), refutations
+trees. Each node stands for an application of an inference rule and the leaves
+in the tree represent formulas in the given problem. Each node is labeled with
+an axiom or an inference rule name (e.g. \text{\tt resolve}). Each edge links a
+premise with one conclusion. All proof graphs have in their root the conclusion
+⊥ since \text{\tt Metis} uses refutation in each deduction step.
 
 \subsection{Proof Rules}
-Using \verb!Metis!
-to prove CPL problems, we found that their TSTP derivations showed six inference rules, \verb!canonicalize!, \verb!conjunct!, \verb!negate!, \verb!simplify!,  \verb!strip!
-and \verb!resolve!.
+Using \text{\tt Metis} to prove CPL problems, we found that their TSTP derivations
+showed six inference rules, \text{\tt canonicalize}, \text{\tt conjunct}, \text{\tt negate},
+\text{\tt simplify}, \text{\tt strip} and \text{\tt resolve}.
 
-The \verb!canonicalize! rule transforms a formula to one of its normal form, CNF, NNF, and DNF.
-This rule also performs simple simplification in the process, applying for instance some of the following theorems assuming commutative properties.
+The \text{\tt canonicalize} rule transforms a formula to one of its normal form,
+CNF, NNF, and DNF. This rule also performs simple simplification in the process,
+applying for instance some of the following theorems assuming commutative
+properties.
 
@@
 
-The \verb!strip! rule extracts a subgoal from a goal. The splitting process
+The \text{\tt strip} rule extracts a subgoal from a goal. The splitting process
 takes a goal and recursively recollects all hypothesis required in order to prove the goal.
@@
 \label{secproofrecon}
-As a proof checker, we choose the proof-assistant Agda without a clear reason in mind
-rather than its syntax language shares similarity with Haskell, the programming language
-of our proof-reconstruction tool, Athena.
+As a proof checker, we choose the proof-assistant \text{\tt Agda}.
+
+Such TPTP proofs produced by ATPs on the type-annotated input are the
+starting point for the HOL proof reconstruction.
 
@@
 
+The propositional formulas are represented using the \text{\tt Prop} data type.
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{20}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{35}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{Prop}\;\mathbin{:}\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Conid{Var}\;{}\<[20]%
+\>[20]{}\mathbin{:}\;\Conid{Fin}\;\Varid{n}\;\rightarrow\;\Conid{Prop}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\top\;{}\<[20]%
+\>[20]{}\mathbin{:}\;\Conid{Prop}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\bot\;{}\<[20]%
+\>[20]{}\mathbin{:}\;\Conid{Prop}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{\char95 ∧\char95 }\;\Varid{\char95 ∨\char95 }\;\Varid{\char95 ⇒\char95 }\;\Varid{\char95 ⇔\char95 }\;{}\<[20]%
+\>[20]{}\mathbin{:}\;(\Varid{$\phi$}\;\psi\;\mathbin{:}\;\Conid{Prop})\;\rightarrow\;\Conid{Prop}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{¬\char95 }\;{}\<[20]%
+\>[20]{}\mathbin{:}\;(\Varid{$\phi$}\;\mathbin{:}\;\Conid{Prop})\;{}\<[35]%
+\>[35]{}\rightarrow\;\Conid{Prop}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+The theorems in CPL are represented using an abstract data type to implement
+a natural deduction calculus. Theorems represent the \emph{sequents} $\Gamma \vdash \phi$,
+where $\Gamma$ is a set of hypothesis --using for the implementation the list data type
+from the \text{\tt Agda} standard library version-- and $\phi$ is the
+sequent's conclusion.
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{13}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{43}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Varid{\char95 ⊢\char95 }\;\mathbin{:}\;(\Gamma\;\mathbin{:}\;\Conid{Ctxt})\;(\Varid{$\phi$}\;\mathbin{:}\;\Conid{Prop})\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{assume}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\rightarrow\;(\Varid{$\phi$}\;\mathbin{:}\;\Conid{Prop})\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{,}\;\Varid{$\phi$}\;\Varid{⊢}\;\Varid{$\phi$}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{axiom}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\rightarrow\;(\Varid{$\phi$}\;\mathbin{:}\;\Conid{Prop})\;{}\<[43]%
+\>[43]{}\rightarrow\;\Varid{$\phi$}\;\Varid{∈}\;\Gamma\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{weaken}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\mskip1.5mu\}\;\rightarrow\;(\psi\;\mathbin{:}\;\Conid{Prop})\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{,}\;\psi\;\Varid{⊢}\;\Varid{$\phi$}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{weaken₂}\;{}\<[13]%
+\>[13]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\mskip1.5mu\}\;\rightarrow\;(\psi\;\mathbin{:}\;\Conid{Prop})\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\psi\;\Varid{∷}\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⊤-intro}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\top{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⊥-elim}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\rightarrow\;(\Varid{$\phi$}\;\mathbin{:}\;\Conid{Prop})\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\bot\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{¬-intro}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{,}\;\Varid{$\phi$}\;\Varid{⊢}\;\bot\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{¬}\;\Varid{$\phi$}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{¬-elim}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{¬}\;\Varid{$\phi$}\;\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\bot{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{∧-intro}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\;\psi\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\rightarrow\;\Gamma\;\Varid{⊢}\;\psi\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\Varid{∧}\;\psi{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{∧-proj₁}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\;\psi\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\Varid{∧}\;\psi\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{∧-proj₂}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\;\psi\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\Varid{∧}\;\psi\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\psi{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{∨-intro₁}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\mskip1.5mu\}\;\rightarrow\;(\psi\;\mathbin{:}\;\Conid{Prop})\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\Varid{∨}\;\psi{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{∨-intro₂}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \psi\mskip1.5mu\}\;\rightarrow\;(\Varid{$\phi$}\;\mathbin{:}\;\Conid{Prop})\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\psi\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\Varid{∨}\;\psi{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{∨-elim}\;{}\<[11]%
+\>[11]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\;\psi\;\chi\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{,}\;\Varid{$\phi$}\;\Varid{⊢}\;\chi\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{,}\;\psi\;\Varid{⊢}\;\chi\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{,}\;\Varid{$\phi$}\;\Varid{∨}\;\psi\;\Varid{⊢}\;\chi{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⇒-intro}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\;\psi\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{,}\;\Varid{$\phi$}\;\Varid{⊢}\;\psi\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\Varid{⇒}\;\psi{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⇒-elim}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\;\psi\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\Varid{⇒}\;\psi\;\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\psi{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⇔-intro}\;{}\<[12]%
+\>[12]{}\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\;\psi\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{,}\;\Varid{$\phi$}\;\Varid{⊢}\;\psi\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{,}\;\psi\;\Varid{⊢}\;\Varid{$\phi$}\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\Varid{⇔}\;\psi{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⇔-elim₁}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\;\psi\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\Varid{⇔}\;\psi\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\psi{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⇔-elim₂}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;\{\mskip1.5mu \Varid{$\phi$}\;\psi\mskip1.5mu\}\;{}\<[43]%
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\psi\;\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}\;\Varid{⇔}\;\psi\;{}\<[E]%
+\\
+\>[43]{}\rightarrow\;\Gamma\;\Varid{⊢}\;\Varid{$\phi$}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
 \subsection{The Translation Method}
+
 \subsection{Reconstruction Work-flow}
@@
 \label{secconclusion}
-\verb!simplify! and \verb!canonicalize! coverage.
+\text{\tt simplify} and \text{\tt canonicalize} coverage.
 Proof-reconstruction can be done in Agda from the Metis' proofs.
@@
 \subsubsection*{Acknowledgments.}
-We thank EAFIT University of Medell\'in, Colombia for funding support.
-This is part of Jonathan Prieto-Cubides's Master thesis in Applied
-Mathematics, written under the supervision of Andr\'es Sicard-Ram\'irez
-for the Logic and Computation Research Group at the EAFIT University.
+We thank EAFIT University of Medell\'in, Colombia for funding support. This is
+part of first author's Master thesis in Applied Mathematics, written under the
+supervision of Andr\'es Sicard-Ram\'irez for the Logic and Computation Research
+Group at the EAFIT University.
 
-We also acknowledge the work~\cite{Gomez-Londono2015} done by
-Alejandro G\'omez-Londo\~no that deserves as the basis for our parsing module
+We thank Joe Leslie-Hurd for supporting comments about \text{\tt Metis}.
+We also acknowledge the work done by Alejandro G\'omez-Londo\~no~
+\cite{Gomez-Londono2015} that deserves as the basis code for our parsing module
 for TSTP files.
-And last but not least, we gratefully acknowledge Andreas Abel and Chalmers University of Gothenburg, Sweden for inviting us to be part of the Agda Implementors’ Meeting XXV where we presented part of this paper.
+And last but not least, we gratefully acknowledge Andreas Abel and Chalmers
+University of Gothenburg, Sweden for inviting us to be part of the Agda
+Implementors’ Meeting XXV where we presented part of this paper.
 
@@
 \bibliography{ref}
+\addcontentsline{toc}{section}{References}
 

### 2017-08-14 slides/Jonathan-Proof-Reconstruction.tex
[ slides ] fixed conjunct function.
[ paper ] adding ndeduction tree example.

@@
 
-% \setmonofont[ExternalLocation=fonts/
-%   , BoldFont=SourceCodePro-Semibold.ttf
-%   , BoldItalicFont=SourceCodePro-SemiboldIt.ttf
-%   , ItalicFont=SourceCodePro-It.ttf
-%   ]{SourceCodePro-Regular.ttf}
-
 \newfontfamily\sourcecode[ExternalLocation=fonts/
@@
 
-\usepackage{minted}
-\setminted[cagda]{
-  bgcolor   = aliceblue
-, fontsize  = \footnotesize
-, frame     = none
-% , framerule = 0.4pt
-% , framesep  = 0pt
-, style     = cagda
-}
+,
 
@@
 \subtitle{(work in progress)}
-\date{May 11, 2017\\Updated: \today}
+\date{Agda Implementors’ Meeting XXV\\
+Teknikparken, Chalmers, Gothenburg, Sweden\\
+May 11 2017\\[2mm]
+Updated: \today}
 \author[Jonathan Prieto-Cubides]{Jonathan Prieto-Cubides\\
@@
 \begin{minted}{cagda}
-conjunct : (φ ψ : Prop) → Prop
+conjunct : Prop → Prop → Prop
 conjunct φ ψ with conj-view φ | conjunct-path φ ψ []
@@
 
-\begin{frame}[fragile, label=verified-example]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof generated with \texttt{Athena}}
+\begin{frame}[fragile, label=verified-example]{Problem $p ∧ q ⊢ q ∧ p$}{Proof generated with \texttt{Athena}}
 \vfill
@@
   (RAA
-    (atp-canonicalize
-      (atp-simplify
-        (atp-canonicalize
-          (atp-strip
-            (assume {Γ = Γ} (atp-negate subgoal₀))))
-        (atp-conjunct (q)
-          (atp-canonicalize
-            (weaken (atp-negate subgoal₀)
-              (assume {Γ = ∅} a)))))))
+    (atp-simplify ⊥
+      (assume {Γ = Γ}
+        (¬ subgoal₀))
+      (atp-conjunct q
+        (atp-canonicalize (p ∧ q)
+          (weaken (¬ subgoal₀)
+            (assume {Γ = ∅} a))))))
 \end{minted}
@@
 
-\begin{frame}[fragile, label=verified-example-3]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
+\begin{frame}[fragile, label=verified-example-3]
+  {Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
 \vfill
@@
   (RAA
-    (atp-canonicalize
-      (atp-simplify
-        (atp-conjunct (q)
-          (atp-canonicalize
-            (weaken (atp-negate subgoal₁)
+    (atp-simplify ⊥
+      (atp-conjunct q
+        (atp-canonicalize (p ∧ q)
+          (weaken (¬ subgoal₁)
             (assume {Γ = ∅} a))))
-        (atp-simplify
-          (atp-canonicalize
-            (atp-strip
-              (assume {Γ = Γ} (atp-negate subgoal₁))))
-          (atp-conjunct (p)
-            (atp-canonicalize
-              (weaken (atp-negate subgoal₁)
-                (assume {Γ = ∅} a))))))))
+      (atp-simplify ⊥
+        (atp-canonicalize ((¬ p) ∧ q)
+          (assume {Γ = Γ}
+            (¬ subgoal₁)))
+        (atp-conjunct p
+          (atp-canonicalize (p ∧ q)
+            (weaken (¬ subgoal₁)
+              (assume {Γ = ∅} a)))))))
 \end{minted}

### 2017-09-01 paper/main.tex
[ paper ] using subfiles, sections is a new directory.

--- 2017-07-28 paper/main.tex
@@
 
+\usepackage{subfiles}
+
+\setcounter{tocdepth}{5}
+\usepackage{graphicx}
+\usepackage{array}
 \usepackage{bussproofs}
@@
   {\DisplayProof\egroup}
-
-\usepackage{amssymb}
-\setcounter{tocdepth}{3}
-\usepackage{graphicx}
-\usepackage{multicol}
-
-\usepackage{url}
-\urldef{\mailsc}\path|{jprieto9, asr}@eafit.edu.co|
-\newcommand{\keywords}[1]{\par\addvspace\baselineskip
-\noindent\keywordname\enspace\ignorespaces#1}
+\def\extraVskip{3pt}
+\def\labelSpacing{3pt}
+\def\defaultHypSeparation{\hskip.2in}
+\def\EnableBpAbbreviations{true}
 
@@
 % --------------------------------------------------------------------------
+
 \usepackage{tikz}
@@
 \usetikzlibrary{arrows}
-\usetikzlibrary{automata}
 \usetikzlibrary{calc}
@@
 
-\tikzstyle{vertex}=[auto=left,circle,fill=black!25,minimum size=5pt,inner sep=0pt]
+\tikzstyle{vertex}=[
+    auto=left
+  , circle
+  , fill=black!25
+  , minimum size=5pt
+  , inner sep=0pt
+  ]
 
 % --------------------------------------------------------------------------
-% Minted Configuration
+% Listings
 % --------------------------------------------------------------------------
-%% \usepackage{minted}
-%% \setminted[cagda]{
-%% , fontsize  = \footnotesize
-%% , frame     = none
-%% % , framerule = 0.4pt
-%% % , framesep  = 0pt
-%% , style     = cagda
-%% }
+
+\usepackage{listings}
+\usepackage{lstautogobble}
+
+\lstdefinestyle{TPTP}{
+    aboveskip=10pt
+  , basicstyle=\tt
+  , belowskip=10pt
+  , keywords=[2]{axiom, conjecture,inference, negated_conjecture, plain, source}
+  , keywords=[3]{fof, cnf}
+  , keywords=[4]{canonicalize, resolve, conjunct,
+    strip, simplify, negate, clausify}
+  , keywordstyle=[2]\bfseries
+  , keywordstyle=[3]\bfseries
+  , keywordstyle=[4]\bfseries
+  , showstringspaces=false
+  , keepspaces=true
+}
+
+\lstnewenvironment{tptp}
+  {\lstset{style=TPTP,columns=fullflexible}\csname lst@SetFirstLabel\endcsname}
+  {\csname lst@SaveFirstLabel\endcsname}
+
+%\usepackage[utf8]{inputenc}
+\usepackage{ucs}
+\usepackage{autofe}
+\usepackage{afterpage}
+\usepackage{comment}
+\usepackage{url}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{stmaryrd} %new symbol font for tcs
+\usepackage{color}
+\usepackage{fancybox}
+
+\usepackage{verbatim}
+\usepackage{relsize}
+\usepackage{fancyvrb}
+% \DefineVerbatimEnvironment
+%   {code}{Verbatim}
+%   { fontsize=\relsize{-2}
+%   , fontfamily=freemodo
+%   , frame =single
+%   , framesep=5mm
+%   , showspaces=true
+%   , obeytabs=true
+%   } % {}
+
+\setcounter{secnumdepth}{5}
+
+\renewcommand*\rmdefault{cmr}
+
+% --------------------------------------------------------------------------
+% New commands
+% --------------------------------------------------------------------------
+
+\newcommand{\name}{\textsc}
+\newcommand{\Agda}{\name{Agda}}
+
+% --------------------------------------------------------------------------
+% Rest.
+% --------------------------------------------------------------------------
+
+\usepackage{url}
+% \urldef{\mailsc}\path|{jprieto9, asr}@eafit.edu.co|
+\newcommand{\keywords}[1]{\par\addvspace\baselineskip
+\noindent\keywordname\enspace\ignorespaces#1}
 
@@
 
-\mainmatter  % start of an individual contribution
+\mainmatter
 
-% first the title is needed
-\title{Towards Proof-Reconstruction of Problems in Classical Propositional Logic
-in Agda}
+\title{Towards Proof-Reconstruction of Problems
+in Classical Propositional Logic in Agda}
 
-% a short form should be given in case it is too long for the running head
-\titlerunning{Towards Proof-Reconstruction of Problems in Classical
-  Propositional Logic in Agda}
+\titlerunning{Proof-Reconstruction in Classical
+Propositional Logic}
 
@@
 
-\institute{EAFIT University, School of Sciences and Engineering,\\
+\institute{Universidad EAFIT, \emph{School of Sciences and Engineering},\\
 Medell\'in, Colombia\\
-\mailsc}
+\email{jprieto9,asr@eafit.edu.co}}
 
@@
 
-\begin{abstract}
-...
-\keywords{Proof reconstruction, Agda, Automatic theorem prover, Classical Propositional Logic, Metis }
-\end{abstract}
-
-\section{Introduction}
-Proof reconstruction is a hard labor, it integrates two
-complex systems. On one hand, we have the automatic theorem provers (henceforth
-ATPs) that depending on the specification logic and background theories exist
-many alternatives. They are SAT solvers (e.g. \verb!zChaff!~\cite{Moskewicz2001} and \verb!MiniSat!~\cite{Een2004}) to prove unsatisfiability of CNF formulas,
-QBF solvers (e.g. \verb!GhostQ!~\cite{Klieber2014} and~\verb!DepQBF!~\cite{Lonsing2017}) to prove satisfiability and invalidity of quantified Boolean
-formulas, SMT solvers (e.g \verb!CVC4!~\cite{Barrett2011}, \verb!veriT!~\cite{bouton2009}, and \verb!Z3!~\cite{DeMoura2008}) to
-prove unsatisfiability of formulas from first-order logic with theories,  and
-finally, the ATPs to prove validity of formulas from first-order logic with
-equality (e.g.
-\verb!E!~\cite{Schulz:AICOM-2002},~\verb!Gandalf!~\cite{Tammet1997},~\verb!leanCoP!~\cite{Otten2008},~\verb!Metis!~\cite{hurd2003first},~\verb!SPASS!~\cite{Weidenbach2009} and ~\verb!Vampire!~\cite{Riazanov1999}),
-high-order logic (e.g. \verb!Leo-II!~\cite{Benzmuller2008} and \verb!Satallax!~\cite{Brown2012}), intuitonistic logic
-(e.g. \verb!ileanCoP!~\cite{Otten2008},~\verb!JProver!~\cite{Schmitt2001}, and \verb!Gandalf!~\cite{Tammet1997}), among others.
-
-For proof reconstruction, we need from the ATP tools proof objects in a consistent format to work with, that is, a full script describing
-step-by-step the table of the derivation to get the actual proof. Unfortunately,
-not all ATPs can deliver proofs or some useful output for reconstruct a proof.
-For problems in classical propositional logic (henceforth CPL), from a list of
-at least forty\footnote{ATPs available in the website  \texttt{SystemOnTPTP} from the TPTP World} ATPs, just a few were able to deliver proofs (e.g.
-\verb!CVC4!~\cite{Barrett2011}, \verb!SPASS!, and
-\verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less generate proofs in a file
-format like TSTP~\cite{sutcliffe2004tstp} (e.g. \verb!E!~\cite{Schulz:AICOM-2002}, \verb!Metis!~\cite{hurd2003first}, \verb!Vampire!, and \verb!Z3!) or LFSC~\cite{Stump2008}.
-
-On the other hand, we have the proof checkers, Interactive Theorem Provers
-%(henceforth ITP)
-or proof assistants (e.g.
-\verb!Agda!~\cite{agdateam}, \verb!Coq!~\cite{coqteam}, \verb!Isabelle!~\cite{paulson1994isabelle}, \verb!HOL4!~\cite{norrish2007hol}).
-These programs allow us to define the formal language for the problems like operators, logic variables, axioms, and theorems.
-They can assist us to check and validate the proof script delivered by the provers.
-Because the formalism in the source (the proof generated by the ATP) is not necessarily the same formalism in the target (proof reconstructed in the proof assistant), the reconstruction of a proof involves a deep understanding around the deduction process done by the ATP, for translating that deduction later into the proof assistant, the so called ``reverse engineering''.
-
-Many approaches have been proposed and some tools have been implemented for proof reconstruction in the last decades, we mention some of them in the following.
-
-\subsection*{Related Work.}\label{Related Work}
-\par
-\verb!Sledgehammer! is a tool for \verb!Isabelle! proof
-assistant~\cite{paulson1994isabelle} that provides a full integration of
-automatic theorem provers including ATPs (see, for example,
-\cite{meng2006automation}, ~\cite{blanchette2013extending} and \cite{Fleury2014}) and SMT solvers (see, for
-example,~\cite{blanchette2013extending},~\cite{bohme2010} and \cite{Fleury2014}) with \verb!Isabelle/HOL!~\cite{nipkow2002isabelle}, the specialization of \verb!Isabelle! for Higher-Order Logic.
-
-\verb!Waldmeister!
-is an automatic theorem prover for Unit Equational Logic \cite{hillenbrand1997}.
-Foster and Struth \cite{foster2011integrating} integrate \verb!Waldmeister!
-into \verb!Agda!~\cite{agdateam}.
-This integration requires a proof reconstruction step but authors' approach is restricted to Pure Equational Logic --also called Identity Theory \cite{humberstone2011}-- that is, First-Order Logic with Equality but no other predicate symbols and no functions symbols \cite{appel1959}.
-
-An integration between SMT Solvers and \verb!Agda! in \cite{kanso2016light} use a \emph{oracle and reflection} approach to give certificates for propositional problems.
-
-\verb!SMTCoq!
-(see \cite{armand2011} and \cite{Ekici2017} for more details) is a tool for the \verb!Coq!
-proof assistant \cite{coqteam} which provides a certified checker for proof witness coming from the SMT solver \verb!veriT!
-\cite{bouton2009} and adds a new tactic named verit, that calls \verb!veriT!
-on any \verb!Coq!
-goal.
-
-Given a fixed but arbitrary First-Order signature, in \cite{bezem2002automated} transform a proof produced by the first-order automatic theorem prover \verb!Bliksem!
-\cite{deNivelle2003} in a \verb!Coq!
-proof term.
-
-We structure the paper as follows.
-In section \ref{sec2}, we briefly introduce the \verb!Metis!
-Prover.
-In section \ref{secproofrecon}, we present our approach to reconstruct proofs deliver by \verb!Metis!
-in \verb!Agda!.
-In section 4, we present a complete example of a proof reconstructed with our tool for a CPL problem.
-In section \ref{secconclusion}, we discuss some limitations and conclusions, for ending up with the future work.
-
-\section{Metis: Language and Proof Terms}\label{sec2}
-\verb!Metis! is an automatic theorem prover for First-order Logic with Equality~\cite{hurd2003first}.
-
-\subsection{Input and Output Language}
-The \verb!TPTP!
-language --which includes the First-Order Form (FOF) and Clause Normal Form (CNF) formats \cite{sutcliffe2009} -- is de facto input standard language and the \verb!TSTP!
-language is de facto output standard language~\cite{sutcliffe2004tstp}.
-
-\subsection{Proof Terms}
-
-\verb!Metis!' proof terms encode natural deduction proofs. Its deduction system uses six simple inference rules and it proves conjectures by refutation.
-
-\[
-\begin{bprooftree}
-\AxiomC{}
-\RightLabel{axiom}
-\UnaryInfC{$C$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-\AxiomC{}
-\RightLabel{assume $L$}
-\UnaryInfC{$L \vee \neg L$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-\AxiomC{}
-\RightLabel{refl $t$}
-\UnaryInfC{$t = t$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-\AxiomC{$C$}
-\RightLabel{subst $\sigma$}
-\UnaryInfC{$\sigma\,C$}
-\end{bprooftree}
-\qquad
-\]
-
-\[
-\begin{bprooftree}
-\AxiomC{}
-\RightLabel{equality $L$ $p$ $t$}
-\UnaryInfC{$\neg (L[p] = t) \vee \neg L \vee L[ p \mapsto t]$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-\AxiomC{$L \vee C$}
-\AxiomC{$\neg L \vee D$}
-\RightLabel{resolve $L$}
-\BinaryInfC{$C \vee D$}
-\end{bprooftree}
-\]
-
-Metis’ proofs are directed acyclic graphs (henceforth DAG), refutations trees.
-Each node stands for an application of an inference rule and the leaves in the tree represent formulas in the given problem.
-Each node is labeled with an axiom or an inference rule name (e.g.
-\verb!resolve!).
-Each edge links a premise with one conclusion.
-All proof graphs have in their root the conclusion ⊥ si
-nce Metis uses refutation in each deduction step.
-
-\subsection{Proof Rules}
-Using \verb!Metis!
-to prove CPL problems, we found that their TSTP derivations showed six inference rules, \verb!canonicalize!, \verb!conjunct!, \verb!negate!, \verb!simplify!,  \verb!strip!
-and \verb!resolve!.
-
-The \verb!canonicalize! rule transforms a formula to one of its normal form, CNF, NNF, and DNF.
-This rule also performs simple simplification in the process, applying for instance some of the following theorems assuming commutative properties.
-
-\[
-\begin{bprooftree}
-  \AxiomC{$P \vee \bot$}
-  \UnaryInfC{$P$}
-\end{bprooftree}
-\begin{bprooftree}
-\AxiomC{$P \vee \top$}
-\UnaryInfC{$P$}
-\end{bprooftree}
-\begin{bprooftree}
-\AxiomC{$P \vee \neg P$}
-\UnaryInfC{$\top$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$P \wedge \bot$}
-  \UnaryInfC{$\bot$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$P \wedge \top$}
-  \UnaryInfC{$P$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$P \wedge \neg P$}
-  \UnaryInfC{$\bot$}
-\end{bprooftree}
-\]
-
-The \verb!strip! rule extracts a subgoal from a goal. The splitting process
-takes a goal and recursively recolects all hypotesis required in order to prove the goal.
-At the end, the final hypotesis represent the subgoals.
-
-\section{Proof Reconstruction in Agda}
-\label{secproofrecon}
-As a proof checker, we choose the proof-assistant Agda without a clear reason in mind
-rather than its syntax language shares similarity with Haskell, the programming language
-of our proof-reconstruction tool, Athena.
-
-\subsection{LCF-Style Theorem Proving}
-
-\subsection{The Translation Method}
-\subsection{Reconstruction Work-flow}
-Explain in a diagram like we did in the slides for the AIM ...
-
-\subsection{Emulation of Inference Rules in Agda}
-
-% \subsection{Limitations}
-%
-
-% \section{Experimental Results}
-% We could be able to reconstruct 88 problems in CPL.
-
-\subsection{Implementation}
-...
-\subsection{Examples}
-...
-
-\section{Conclusions}
-\label{secconclusion}
-\verb!simplify! and \verb!canonicalize! coverage.
-Proof-reconstruction can be done in Agda from the Metis' proofs.
-...
-
-\subsubsection*{Future Work.}
-First-Order Logic support.
-
-\subsubsection*{Acknowledgments.}
-We thank EAFIT University in Medell\'in, Colombia for funding support.
+\subfile{sections/abstract.tex}
+\subfile{sections/introduction.tex}
+\subfile{sections/metis-language-and-proofs.tex}
+\subfile{sections/proof-reconstruction.tex}
+\subfile{sections/related-work.tex}
+\subfile{sections/conclusions.tex}
+\subfile{sections/acknowledgements.tex}
 

### 2017-09-01 paper/sections/abstract.tex
[ paper ] using subfiles, sections is a new directory.

% -*- root: main.tex -*-
\documentclass[../main.tex]{subfiles}
\begin{document}

% ============================================================================

\begin{abstract}
...
\keywords{Proof reconstruction, Agda, Automatic theorem prover,
  Classical Propositional Logic, Metis }
\end{abstract}

\end{document}

### 2017-09-01 paper/sections/acknowledgements.tex
[ paper ] using subfiles, sections is a new directory.

% -*- root: main.tex -*-
\documentclass[main.tex]{subfiles}
\begin{document}

% ============================================================================

\subsubsection*{Acknowledgments.}

We thank Universidad EAFIT of Medell\'in, Colombia for funding support.
This project was a product of the Logic and Computation Research
Group at the Universidad EAFIT.
%This is part of first author's Master thesis in Applied Mathematics, written under the
% supervision of Andr\'es Sicard-Ram\'irez for the Logic and Computation Research
% Group at the Universidad EAFIT.

We thank Joe Leslie-Hurd for all support with \verb!Metis! prover.
We also acknowledge the work carry out by Alejandro G\'omez-Londo\~no~
\cite{Gomez-Londono2015} that was used as the basis code for our TSTP parsing
module.
And last but not least, we gratefully acknowledge Andreas Abel and Chalmers
University of Goteborg, Sweden for inviting us to be part of the Agda
Implementors’ Meeting XXV where we presented part of this paper.

\end{document}

### 2017-09-01 paper/sections/conclusions.tex
[ paper ] using subfiles, sections is a new directory.

--- 2017-09-01 paper/sections/acknowledgements.tex
@@
 
-\subsubsection*{Acknowledgments.}
+\section{Conclusions}
+\label{sec:conclusions}
 
-We thank Universidad EAFIT of Medell\'in, Colombia for funding support.
-This project was a product of the Logic and Computation Research
-Group at the Universidad EAFIT.
-%This is part of first author's Master thesis in Applied Mathematics, written under the
-% supervision of Andr\'es Sicard-Ram\'irez for the Logic and Computation Research
-% Group at the Universidad EAFIT.
+Amazing conclusions.
+...
+\cite{}
 
-We thank Joe Leslie-Hurd for all support with \verb!Metis! prover.
-We also acknowledge the work carry out by Alejandro G\'omez-Londo\~no~
-\cite{Gomez-Londono2015} that was used as the basis code for our TSTP parsing
-module.
-And last but not least, we gratefully acknowledge Andreas Abel and Chalmers
-University of Goteborg, Sweden for inviting us to be part of the Agda
-Implementors’ Meeting XXV where we presented part of this paper.
+\subsubsection*{Future Work.}
+\label{ssec:future-work}
 

### 2017-09-01 paper/sections/introduction.tex
[ paper ] using subfiles, sections is a new directory.

% -*- root: main.tex -*-
\documentclass[main.tex]{subfiles}
\begin{document}

% ============================================================================

\section{Introduction}
\label{sec:introduction}

Proof reconstruction is a hard labor since it depends on the integration
of two complex system. On one hand, we have the automatic theorem provers
(henceforth ATP) and their specification logic. These tools are usually
classified in at least one of the following categories. A SAT solver
(e.g. \verb!zChaff!~\cite{Moskewicz2001} and \verb!MiniSat!~\cite{Een2004})
to prove unsatisfiability of CNF formulas, a QBF solver
(e.g. \verb!GhostQ!~\cite{Klieber2014} and \verb!DepQBF!~\cite{Lonsing2017})
to prove satisfiability and invalidity of quantified Boolean formulas, a SMT
solver (e.g \verb!CVC4!~\cite{Barrett2011}, \verb!veriT!~\cite{bouton2009},
and \verb!Z3!~\cite{DeMoura2008}) to prove unsatisfiability of formulas
from first-order logic with theories, and a prover for validity of
formulas from first-order logic with equality
(e.g. \verb!E!~\cite{Schulz:AICOM-2002}, \verb!leanCoP!~\cite{Otten2008},
\verb!Metis!~\cite{hurd2003first}, \verb!SPASS! ~\cite{Weidenbach2009} and
\verb!Vampire!~\cite{Riazanov1999}), high-order logic (e.g. \verb!Leo-II!
\cite{Benzmuller2008} and \verb!Satallax!~\cite{Brown2012}) or intuitonistic
logic (e.g. \verb!ileanCoP!~\cite{Otten2008}, \verb!JProver!
\cite{Schmitt2001}, and \verb!Gandalf!~\cite{Tammet1997}), among others.
On the other hand, we have the proof checkers, interactive theorem provers
(henceforth ITP) or proof assistants (e.g. \verb!Agda!~\cite{agdateam},
\verb!Coq!~\cite{coqteam}, \verb!Isabelle!~\cite{paulson1994isabelle}, and
\verb!HOL4!~\cite{norrish2007hol}).
The ITP tools provide us the logic framework to check and validate the
reply of the ATPs, since they allow us to define the formal language for
the problems like operators, logic variables, axioms, and theorems.

A proof reconstruction tool provides such an integration in one
direction, the bridge between ATPs to ITPs. This is mostly a translation
of the reply delivered by the prover into the formalism of the proof
assistant. Because the formalism of the source (the proof generated by
the ATP) is not necessarily the same logic in the target, the
reconstruction turns out in a ``reverse engineering'' task. Then,
reconstructing a proof involves a deep understanding of the algorithms in
the ATP and the specification logic in the ITP.

What we need from the ATP tools is a proof object in a consistent format
to work with, that is, a full script describing step-by-step with
exhaustive details and without ambiguities, the table of the derivation
to get the actual proof. For problems in classical propositional logic
(henceforth CPL), from a list of at least forty\footnote{ATPs available
from the web service \texttt{SystemOnTPTP} of the TPTP World.} ATPs, just
a few provers were able to deliver proofs (e.g. \verb!CVC4!~
\cite{Barrett2011}, \verb!SPASS!, and
\verb!Waldmeister!~\cite{hillenbrand1997})
and a little bit less replied with a proof in a
file format like \verb!TSTP!~\cite{sutcliffe2004tstp} (e.g. \verb!E!, \verb!Metis!,
\verb!Vampire!, and \verb!Z3!), LFSC~\cite{Stump2008}, or the
SMT-LIB~\cite{Bohme2011} format.

Many approaches have been proposed and some tools have been implemented
for proof reconstruction in the last decades. These programs are relevant
not only because it helps to spread their usage but they also increase
the confidence of their users about their algorithms and their
correctness (see, for example, bugs in ATPs~\cite{Keller2013},
\cite{Bohme2011}, \cite{Fleury2014} and \cite{Kanso2012}).
% We mention some tools in the following.

In this paper, we describe the integration of \verb!Metis! prover with the
proof assistant \verb!Agda! by parsing \verb!TSTP! derivations to generate
\verb!Agda! code of the proofs. We structure the paper as follows.
In section \ref{sec:metis-language-and-proofs} we briefly introduce
the \verb!Metis! prover. In section \ref{sec:proof-reconstruction}, we
present our approach to reconstruct proofs deliver by \verb!Metis! in
\verb!Agda!.
%In section \ref{sec:example}, we present a complete example of a proof reconstructed with our tool for a CPL problem.
We list related work in proof reconstruction in section \ref{sec:related-work}
In section~\ref{sec:conclusions}, we discuss some limitations, advantages
and disadvantages with other similar proof reconstruction tools and
conclusions for ending up with the future work.

\end{document}

### 2017-09-01 paper/sections/metis-language-and-proofs.tex
[ paper ] using subfiles, sections is a new directory.

% % -*- root: main.tex -*-
\documentclass[../main.tex]{subfiles}
\begin{document}

% ===========================================================================

\section{Metis: Language and Proofs}
\label{sec:metis-language-and-proofs}

\verb!Metis! is an automatic theorem prover written in Standard ML for
first-order logic with equality developed by John Hurd~\cite{hurd2003first}.
As we show later this prover is suitable for proof reconstruction task since
it provides well-documented proof-objects with enough information to justify
the deduction steps.

\verb!Metis! has been integrated to \verb!Isabelle/HOL! as a macro-step reconstruction
tool for justifying proof steps (usually CNF goals) replied from other ATPs like
\verb!CVC4!, \verb!Vampire!, or \verb!Z3!.
In \cite{Farber2015}, \verb!Metis! was used to provide a tactic for
\verb!HOL Light!, this tactic challenges others like \verb!MESON! tactic or the
\verb!leanCoP! tactic that reconstructs proofs delivered by
\verb!leanCoP!~\cite{Farber2016}.

In this paper, we ported a subset of \verb!Metis!' inference rules to \verb!Agda!,
the propositional fragmented, to allow us justify step-by-step the proofs
delivered in \verb!TSTP! format generated by \verb!Metis!.

% ---------------------------------------------------------------------------

\subsection{Input and Output Language}
\label{ssec:input-and-output-language}

\textit{Input.}~The \verb!TPTP! language  --which includes the first-order
form (denoted by \verb!fof!) and clause normal form (denoted by \verb!cnf!)
formats~\cite{sutcliffe2009} -- is de
facto input standard language to encode problems for many ATPs.
The \verb!TPTP! syntax describes a well-defined grammar to handle annotated
formulas with the following form

\begin{verbatim}
language(name, role, formula).
\end{verbatim}

The \verb!language! can be \verb!fof! or \verb!cnf!. The \verb!name!
serves to identify the formula within the problem. Each formula assumes one
\verb!role!, this could be an \verb!axiom!, \verb!conjecture!,
\verb!definition!, or a \verb!hypothesis!. The formulas include Boolean
connectives (\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!, $\tt\sim$) and logic
constants \verb!$true! and \verb!$false!.

For instance, we express the problem
$p\, \vdash \neg (p \wedge \neg p) \vee (q \vee \neg q)$
in \verb!TPTP! syntax as follows.

\begin{verbatim}
fof(h, axiom, p).
fof(goal, conjecture, ~ ((p & ~ p) | (q & ~ q))).
\end{verbatim}

\textit{Output.}~\verb!TSTP! language is de facto output standard language
for derivations of ATPs~\cite{sutcliffe2004tstp}.
A \verb!TSTP! derivation is a directed acyclic graph, a proof tree, where each leaf
is a formula from the \verb!TPTP! input. A node is a formula inferred from the parent
formulas. The root is the final derived formula. Such a derivation is a list of
annotated formulas with the form

\begin{verbatim}
language(name, role, formula, source [,useful info]).
\end{verbatim}

The \verb!source! field is an inference record with the following pattern
\begin{verbatim}
inference(rule, useful info, parents).
\end{verbatim}

The \verb!rule! stands for the inference name, the other fields are
auxiliary arguments or useful information to apply the inference, and
the list of parents nodes.
For instance, in Fig.~\ref{fig:metis-proof-tstp}, \verb!strip! is the name of one
of the inference and it has no arguments and only one parent node, \verb!goal!.

\begin{figure}
\begin{verbatim}
fof(a, axiom, p) .
fof(goal, conjecture, p) .
fof(subgoal_0, plain, p, inference (strip, [], [goal])) .
fof(negate_0_0, plain, ~ p, inference (negate, [], [subgoal_0])) .
fof(normalize_0_0, plain, ∼ p, inference (canonicalize, [], [negate_0_0])) .
fof(normalize_0_1, plain, p, inference (canonicalize, [], [a])) .
fof(normalize_0_2, plain, $false, inference (simplify, [],
  [normalize_0_0, normalize_0_1]))
cnf(refute_0_0, plain, $false, inference (canonicalize, [], [normalize_0_2])) .
\end{verbatim}
\caption{A simple \texttt{Metis}' \texttt{TSTP} derivation for the problem $p\vdash p$.}
\label{fig:metis-proof-tstp}
\end{figure}

% ---------------------------------------------------------------------------

\subsection{Proof Terms}
\label{ssec:proof-terms}

A proof-object delivered in a \verb!Metis!' proof encodes a natural
deduction proof. Its deduction system uses six simple inference rules
(see Fig.~\ref{fig:metis-inferences}) to attempt to prove conjectures
by refutation (see. e.g. Fig.~\ref{fig:metis-example}).

\begin{figure}
\[
% \scalebox{0.9}{
\begin{bprooftree}
  \AxiomC{}
  \RightLabel{axiom}
  \UnaryInfC{$C$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{}
  \RightLabel{assume $L$}
  \UnaryInfC{$L \vee \neg L$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{}
  \RightLabel{refl $t$}
  \UnaryInfC{$t = t$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{$C$}
  \RightLabel{subst $\sigma$}
  \UnaryInfC{$\sigma\,C$}
\end{bprooftree}
\qquad
% }
\]
\[
% \scalebox{0.9}{
\begin{bprooftree}
  \AxiomC{}
  \RightLabel{equality $L$ $p$ $t$}
  \UnaryInfC{$\neg (L[p] = t) \vee \neg L \vee L[ p \mapsto t]$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{$L \vee C$}
  \AxiomC{$\neg L \vee D$}
  \RightLabel{resolve $L$}
  \BinaryInfC{$C \vee D$}
\end{bprooftree}
% }
\]
\caption{Inference rules of the \texttt{Metis} prover.}
\label{fig:metis-inferences}
\end{figure}

These proofs are directed acyclic graphs, trees of refutations. Each node stands
for an application of an inference rule and the
leaves in the tree represent formulas in the given problem. Each node is
labeled with a name of the inference rule
(e.g. \verb!canonicalize! in Fig.~\ref{fig:metis-example}). Each
edge links a premise with one conclusion. The proof graphs have in their
root the conclusion $\bot$ since \verb!Metis! delivers proof by refutation.

% \begin{figure}
% \centering
% \begin{bprooftree}
%   \centering\tt
%   \AxiomC{}
%   \RightLabel{\scriptsize negate}
%   \UnaryInfC{$\neg p$}
%   \RightLabel{\scriptsize strip}
%   \UnaryInfC{$\neg p$}
%   \AxiomC{}
%   \RightLabel{\scriptsize axiom}
%   \UnaryInfC{$p$}
%   \RightLabel{\scriptsize canonicalize}
%   \UnaryInfC{$p$}
%   \RightLabel{\scriptsize simplify}
%   \BinaryInfC{$\bot$}
%   \RightLabel{\scriptsize canonicalize}
%   \UnaryInfC{$\bot$}
% \end{bprooftree}
% % \caption{The \verb!Metis!' refutation tree for $p \vdash p$ from the
% % derivation in Fig.~\ref{fig:metis-proof-tstp}}
% \label{fig:metis-example}
% \end{figure}

% ---------------------------------------------------------------------------

\subsection{Proof Rules}
\label{ssec:proof-rules}

Despite the six simple rules in the \verb!Metis!' logic
kernel (see~Fig. \ref{fig:metis-inferences}), we found in \verb!TSTP!
derivations for CPL problems other inference rules.
They are \verb!canonicalize!, \verb!conjunct!, \verb!negate!, \verb!simplify!,
\verb!strip! and \verb!resolve!. We briefly review each of these rules
following no order except maybe by their frequency in the \verb!TSTP! derivations.

% ...........................................................................

\textit{Splitting}.
To prove a goal, \verb!Metis! splits the goal into disjoint cases. This
process produces a list of new subgoals, the conjunction of these subgoals
implies the goal as we show later in subsection~\ref{ssec:emulating-inferences}.
Then, a proof of the goal becomes in smaller proofs, one
refutation for each subgoal. These subgoals are introduced in the \verb!TSTP!
derivation with the \verb!strip! inference rule.

\begin{verbatim}
fof(goal, conjecture, p & r & q).
fof(subgoal_0, plain, p, inference(strip, [], [goal])).
fof(subgoal_1, plain, p => r, inference(strip, [], [goal])).
fof(subgoal_2, plain, (p & r) => q, inference(strip, [], [goal])).
\end{verbatim}

% ...........................................................................

\textit{Clausification.} The \verb!clausify! rule transforms a
propositional formula in clausal normal form or CNF,
a conjunction of clauses. Where a clause is the disjunction of zero or
more literals and a literal is an atom (positive literal) or a negation of an
atom (negative literal). This conversion is not unique and \verb!Metis! performs
this transformation using its own criteria.

% ...........................................................................

\textit{Normalization.}
\verb!Metis! uses the \verb!canonicalize! rule to normalize a
propositional formula that comes from an axiom or a definition.
It often converts the formula in one of its normal form,
the conjunctive normal form,%as \verb!clausify! does
the negative normal form or the disjunctive normal form.
Posterior, this rule simplifies the formula with some definitions, applying
recursively on the structure's formula conjunctions and disjunctions simplifications
to remove tautologies
(see Fig.~\ref{fig:conjunctive-disjunctive-simplification} with a list
of these theorems. We had assumed the commutative property for conjunction and
disjunction connectives).

\begin{figure}
\[%\scalebox{0.9}{
  \begin{bprooftree}
    \AxiomC{$\varphi \wedge \bot$}
    \UnaryInfC{$\bot$}
  \end{bprooftree}
  \qquad
  \begin{bprooftree}
    \AxiomC{$\varphi \wedge \top$}
    \UnaryInfC{$\varphi$}
  \end{bprooftree}
  \qquad
  \begin{bprooftree}
    \AxiomC{$\varphi \wedge \neg \varphi$}
    \UnaryInfC{$\bot$}
  \end{bprooftree}
  \qquad
  \begin{bprooftree}
    \AxiomC{$\varphi \wedge \varphi$}
    \UnaryInfC{$\varphi$}
  \end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
  \begin{bprooftree}
    \AxiomC{$\varphi \vee \bot$}
    \UnaryInfC{$\varphi$}
  \end{bprooftree}
  \qquad
  \begin{bprooftree}
    \AxiomC{$\varphi \vee \top$}
    \UnaryInfC{$\top$}
  \end{bprooftree}
  \qquad
  \begin{bprooftree}
    \AxiomC{$\varphi \vee \neg \varphi$}
    \UnaryInfC{$\top$}
  \end{bprooftree}
  \qquad
  \begin{bprooftree}
    \AxiomC{$\varphi \vee \varphi$}
    \UnaryInfC{$\varphi$}
  \end{bprooftree}
%}
\]
% \caption{Some rules of \verb!canonicalize! inference.}
\label{fig:conjunctive-disjunctive-simplification}
\end{figure}

% ...........................................................................

\textit{Resolution.} The \verb!resolve! rule (see, for example,
Fig.~\ref{fig:resolve-inference}) is the resolution
theorem with two argument, the positive literal for resolution and two
formulas from their own derivations. The positive literal $p$ must occur in
the first formula of the input and the negative literal must occur in the second
formula of the input
(see the resolve rule in \verb!Metis!' logic core in
Fig.~\ref{fig:metis-inferences}).

\begin{verbatim}
cnf(refute_0_0, plain, p | q, inference(canonicalize, [], [normalize_0_0])).
cnf(refute_0_1, plain, ~ p, inference(canonicalize, [], [normalize_0_4])).
cnf(refute_0_2, plain, q,
  inference(resolve, [$cnf(p)], [refute_0_0, refute_0_1])).
\end{verbatim}

% ...........................................................................

\textit{Splitting a conjunct.}
The \verb!conjunct! rule extracts from a conjunction one of its conjuncts, it is
a generalization of the projection rules for the conjunction connective as
we can see in the following \verb!TSTP! derivation.

\begin{verbatim}
fof(normalize_1, plain, p & q & r, inference(canonicalize, [], [x])).
fof(normalize_2, plain, q, inference(conjunct, [], [normalize_1])).
\end{verbatim}

\textit{Negate.}
Each subgoal proof is a refutation, thereby each proof assumes
the negation of its subgoal. The \verb!negate! rule
introduces the negation of a subgoal that results
after applies the \verb!strip! inference to the goal.

\begin{verbatim}
fof(subgoal_0, plain, p, inference(strip, [], [goal])).
fof(negate_0_0, plain, ~ p, inference(negate, [], [subgoal_0])).
\end{verbatim}

% ...........................................................................

\textit{Simplification.} %abbreviate formulas
The \verb!simplify! rule is an $n$-ary rule that performs simplification
of definitions. This rule transverses a list of formulas by
applying different theorems (e.g.\emph{modus pones}, \emph{modus tollens},
or \emph{disjunctive syllogism}) including the list of theorems used by
\verb!canonicalize! in Fig.~\ref{fig:conjunctive-disjunctive-simplification}
and the resolution theorem of \verb!resolve! rule.
Moreover, many things happen inside this \verb!Metis!' procedure and
it is fairly complex to grasp it completely.

\end{document}

### 2017-09-01 paper/sections/proof-reconstruction.tex
[ paper ] using subfiles, sections is a new directory.

% -*- root: main.tex -*-
\documentclass[../main.tex]{subfiles}
\begin{document}

% ============================================================================

\section{Proof Reconstruction}
\label{sec:proof-reconstruction}

\subsection{The Translation Method}

Our system (see Fig~\ref{fig:proof-reconstruction-overview}) translates a \verb!TSTP!
file into an \verb!Agda! proof by parsing it with a \verb!Haskell! tool.
This tool reconstructs the proof tree, removing redundancies and
cutting unnecessary steps (see for example repetitions in the derivation shown in
Fig~\ref{fig:metis-example}). The output is \verb!Agda! code.
Then, we use \verb!Agda! as a proof checker to type-check the proof.
If type-checking succeed, then our proof is verified. Else, we have a failure
proof due by three possible actors. First, a soundness bug in the ATP or a bug
in the output printing. Second, a bug in the translation process in our \verb!TSTP! parsing
module, the inner algorithms in the analysis of the proof tree, the pretty printer
module, or a bug in \verb!Haskell!. Lastly, a bug in our proof checker \verb!Agda!.

% ---------------------------------------------------------------------------

\subsection{Reconstruction Work-flow}

\begin{figure}
\begin{tikzpicture}
\node[text width=2cm, align=center](problem) at (0,0)
  {CPL \\ Problem};

\node[right = 1.2cm of problem, text width=2cm, align=center]
  (tptp){\verb!TPTP! \\ Problem};

\node[right= 1.2cm of tptp, text width=2cm, align=center]
   (metis) {\verb!Metis! \\ Prover};

\node[right= 1.2cm of metis, text width=2cm, align=center, inner sep=10pt]
   (tstp) {\verb!TSTP! \\ Derivation};

\node[below= 0.5cm of tstp, text width=2cm, align=center, inner sep=10pt]
  (athena) {\verb!Haskell! \\ Traslator};

\node[left = 1.2cm of athena, text width=2cm, align=center]
   (agdafile) {\verb!Agda! \\ Proof};

\node[left = 1.2cm of agdafile, text width=2cm, align=center]
   (agda) {Proof Checker};

\node[below = 0.5cm of problem, text width=2cm, align=center]
   (verified) {Checked};

\node[below = 0.5cm of verified, text width=2cm, align=center]
   (failure) {Error};

% node[below] {send to}
\draw[->, thick] (problem) to
  % node[below] {\tiny encoding}
  (tptp);
\draw[->, thick] (tptp) to
  % node[below] {\tiny }
  (metis);
\draw[->, thick] (metis) to
  % node[below] {\tiny replies on}
  (tstp);
\draw[->, thick] (tstp) to
  % node[right] {\tiny parsing}
  (athena);
\draw[->, thick] (athena) to
  % node[below] {\tiny traslation}
  (agdafile);
\draw[->, thick] (agdafile) to
  % node[below] {\tiny type-checking}
  (agda);
\draw[->, thick] (agda) to (verified);
\draw[->, thick, gray] (agda) to (failure);
\end{tikzpicture}
\caption{Proof reconstruction overview.}
\label{fig:proof-reconstruction-overview}
\end{figure}

% ---------------------------------------------------------------------------

\subsection{Proof Cheker}
\label{ssec:agda}\

\verb!Agda! is an interactive system for constructing proofs and programs,
based on Martin-L\"{o}f's type theory and extended with records, parametrised
modules, among other features.
One of the main strengths of \verb!Agda! is its support for writing proofs,
which we shall call \verb!Agda!'s proof engine and it consists of: support for
inductively defined types, including inductive families, and function
definitions using pattern matching on such types, normalisation during type-
checking, commands for refining proof terms, coverage checker and termination
checker.
The inductive approach for representing classical propositional logic
is better because we benefit from \verb!Agda!'s proof engine and its Unicode
support that allows us writing proofs similar as we find in math text books.

% ---------------------------------------------------------------------------

\subsection{LCF-Style Theorem Proving}
\label{ssec:lcf-style-theormem-proving}

A propositional formula is a string of indivisible propositional atoms,
logical connectives $\{\wedge, \vee, \Rightarrow, \Leftrightarrow, \neg\}$
and logic constants $\{\top, \bot\}$.
In \verb!Agda!, we define the formula
as an inductive type using the keyword \texttt{data} and including every
connective as a constructor. We represent propositional formulas with
\verb!Prop! data type using the following definition.

%an extension of the syntax definition used in \cite{Altenkirch2015}.

\begin{verbatim}
data Prop : Set where
  Var              : Fin n → Prop
  ⊤                : Prop
  ⊥                : Prop
  _∧_ _∨_ _⇒_ _⇔_  : (φ ψ : Prop) → Prop
  ¬_               : (φ : Prop)   → Prop
\end{verbatim}

On the other hand, we represent theorems in CPL using an abstract data type
to implement a natural deduction calculus.

\begin{verbatim}
data _⊢_ : (Γ : Ctxt)(φ : Prop) → Set where
\end{verbatim}

The sequents  $\Gamma \vdash \phi$ represent theorems,
where $\Gamma$ is a set of premises and $\phi$ is the
sequent's conclusion. Strictly speaking, we define the set of premises
$\Gamma$ with \verb!List! data type
% \footnote{We use the \verb!Agda! standard library's implementation of the List data type.}.

Our CPL system define all inference rules for intuitonistic propositional logic
(see Fig.~\ref{fig:theorem-constructors}) as constructors of the theorem
data type, and we postulate the principle of the excluded middle (PEM).

\begin{verbatim}
postulate  PEM : ∀ {Γ} {φ} → Γ ⊢ φ ∨ ¬ φ
\end{verbatim}

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt assume $\varphi$}
\UnaryInfC{$\Gamma , \varphi \vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt weaken $\psi$}
\UnaryInfC{$\Gamma , \psi \vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt $\top$-intro}
\UnaryInfC{$\Gamma \vdash \top$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \bot$}
\RightLabel{\scriptsize\tt $\bot$-elim $\varphi$}
\UnaryInfC{$\Gamma \vdash \varphi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \bot$}
\RightLabel{\scriptsize\tt $\neg$-intro}
\UnaryInfC{$\Gamma \vdash \neg \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg \varphi$}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\neg$-elim}
\BinaryInfC{$\Gamma \vdash \bot$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \psi$}
\RightLabel{\scriptsize\tt $\wedge$-intro}
\BinaryInfC{$\Gamma \vdash \varphi \wedge \psi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
\RightLabel{\scriptsize\tt $\wedge$-proj$_1$}
\UnaryInfC{$\Gamma\vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
\RightLabel{\scriptsize\tt $\wedge$-proj$_2$}
\UnaryInfC{$\Gamma\vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\vee$-intro$_1$ $\psi$}
\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \psi$}
\RightLabel{\scriptsize\tt $\vee$-intro$_2$ $\varphi$}
\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma ,\varphi \vdash \gamma $}
\AxiomC{$\Gamma , \psi  \vdash \gamma$}
\RightLabel{\scriptsize\tt $\vee$-elim}
\BinaryInfC{$\Gamma , \varphi \vee \psi \vdash \gamma$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \psi$}
\RightLabel{\scriptsize\tt $\Rightarrow$-intro}
\UnaryInfC{$\Gamma \vdash \varphi \Rightarrow \psi$}
\end{bprooftree}
%}
\]

\[
%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\Rightarrow$-elim}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \psi$}
\AxiomC{$\Gamma , \psi \vdash \varphi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-intro}
\BinaryInfC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\end{bprooftree}
%}
\]

\[
%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_1$}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_2$}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}
%}
\]

\caption{Inference rules for CPL system.}
\label{fig:theorem-constructors}
\end{figure}

% ---------------------------------------------------------------------------

% ---------------------------------------------------------------------------

\subsection{Emulation of Inference Rules in Agda}
\label{ssec:emulating-inferences}

\textit{Normalization.}

\begin{figure}
\[ \scalebox{0.9}{
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi$}

  \UnaryInfC{$\Gamma \vdash \texttt{cnf}~\varphi$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi$}
  \UnaryInfC{$\Gamma \vdash \texttt{nnf}~\varphi$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi$}
  \UnaryInfC{$\Gamma \vdash \texttt{dnf}~\varphi$}
\end{bprooftree}
}\]
\end{figure}

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \wedge \bot$}
  \UnaryInfC{$\Gamma \vdash \bot$}
\end{bprooftree}
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \wedge \top$}
  \UnaryInfC{$\Gamma \vdash \varphi$}
\end{bprooftree}
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \wedge \neg \varphi$}
  \UnaryInfC{$\Gamma \vdash \bot$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \vee \bot$}
  \UnaryInfC{$\Gamma \vdash \varphi$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \vee \top$}
  \UnaryInfC{$\Gamma \vdash \top$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \vee \neg \varphi$}
  \UnaryInfC{$\Gamma \vdash \top$}
\end{bprooftree}
%}
\]
\end{figure}

\textit{Resolution.}

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\delta_{\phi} := \Gamma \vdash \varphi$}
\AxiomC{$\delta_{\psi} := \Gamma \vdash \psi$}
\RightLabel{\texttt{resolve} $p$}
\BinaryInfC{$\Gamma \vdash$ \texttt{resolve} $\phi\ \psi\ p$}
\end{bprooftree}
%}
\]
% \caption{Resolution in \verb!Metis!.}
\label{fig:resolution-rule}
\end{figure}

\textit{Splitting a conjunct.}
In the following theorem, we see the definition for the \verb!conjunct! rule.
It extracts the $\varphi_i$ conjunct from the conjunction given by $\varphi$.

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi := \varphi_1 \wedge \cdots\wedge\varphi_i
\wedge\cdots\wedge \varphi_n$}
\AxiomC{$\varphi_i \equiv \psi$}
\RightLabel{\footnotesize\tt conjunct $\psi$}
\BinaryInfC{$\Gamma\vdash\varphi_i$}
\end{bprooftree}
}
\]

\textit{Splitting a goal}

\begin{figure}
\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi_1 \wedge \varphi_2$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi_1) \wedge \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi_1 \vee \varphi_2$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\neg \varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi_1 \Rightarrow \varphi_2$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
\end{bprooftree}\qquad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg \neg \varphi$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$ \Gamma \vdash \varphi_1 \Leftrightarrow \varphi_2$}
\UnaryInfC{$\Gamma\vdash\texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2) \wedge \texttt{unshunt}~(\varphi_2 \Rightarrow \texttt{split}~\varphi_1)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg \top$}
\UnaryInfC{$\Gamma \vdash \bot$}
\end{bprooftree}\qquad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg \bot$}
\UnaryInfC{$\Gamma \vdash \top$}
\end{bprooftree}\qquad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg (\varphi_1 \wedge \varphi_2)$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt} (\varphi_1 \Rightarrow \texttt{split}~ \neg \varphi_2)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg (\varphi_1 \vee \varphi_2)$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\neg \varphi_1) \wedge  \texttt{unshunt}~(\neg \varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg (\varphi_1 \Rightarrow \varphi_2)$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi_1) \wedge \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2)$}
\end{bprooftree}\qquad
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg (\varphi_1 \Leftrightarrow \varphi_2)$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2) \wedge \texttt{unshunt}~(\neg \varphi_2 \Rightarrow \texttt{split}~\varphi_1)$}
\end{bprooftree}
}\]
\caption{Split a goal in an equivalent conjunction of subgoals.}
\label{split}
\end{figure}

In the theorems above appear two recursive functions \texttt{unshunt} and \texttt{split}. They have the following definitions.

\begin{verbatim}
unshunt : Prop → Prop
unshunt (φ₁ ⇒ (φ₂ ⇒ φ₃)) = unshunt ((φ₁ ∧ φ₂) ⇒ φ₃)
unshunt (φ₁ ⇒ (φ₂ ∧ φ₃)) = unshunt (φ₁ ⇒ φ₂)) ∧ (unshunt(φ₁ ⇒ φ₃)
unshunt φ                = φ
\end{verbatim}

\begin{verbatim}
split : Prop → Prop
split (φ₁ ∧ φ₂)     = {!!}
split (φ₁ ∨ φ₂)     = {!!}
split (φ₁ ⇒ φ₂)     = {!!}
split (φ₁ ⇔ φ₂)     = {!!}
split (¬ ⊤)         = {!!}
split (¬ ⊥)         = {!!}
split (¬ (φ₁ ∧ φ₂)) = {!!}
split (¬ (φ₁ ∨ φ₂)) = {!!}
split (¬ (φ₁ ⇒ φ₂)) = {!!}
split (¬ (φ₁ ⇔ φ₂)) = {!!}
split (¬ (¬ φ))     = {!!}
split φ₁            = {!!}
\end{verbatim}

...

\textit{Simplification.}

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
  \AxiomC{$\Gamma \vdash \psi$}
  \RightLabel{\footnotesize\tt $\Leftrightarrow$-elim}
  \BinaryInfC{$\Gamma \vdash \varphi$}
\end{bprooftree}
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
  \AxiomC{$\Gamma \vdash \varphi$}
  \RightLabel{\footnotesize\tt $\Rightarrow$-elim}
  \BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}
\]
\[
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \vee \neg \psi$}
  \AxiomC{$\Gamma \vdash \neg \varphi$}
  \BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}
%}
\]

\caption{Additional simplification theorems.}
\label{fig:simplify-rule}
\end{figure}

\end{document}

### 2017-09-01 paper/sections/related-work.tex
[ paper ] using subfiles, sections is a new directory.

% -*- root: main.tex -*-
\documentclass[main.tex]{subfiles}
\begin{document}

% ============================================================================

\section{Related Work}
\label{sec:related-work}

\verb!Sledgehammer! is a tool for \verb!Isabelle! proof assistant
~\cite{paulson1994isabelle} that provides a full integration of automatic
theorem provers including ATPs
(see, for example, \cite{meng2006automation}, \cite{blanchette2013extending}
and \cite{Fleury2014}) and SMT solvers (see, for example,
\cite{hurlin07practical}, \cite{bohme2010},
\cite{blanchette2013extending}, and \cite{Fleury2014}) with
\verb!Isabelle/HOL! \cite{nipkow2002isabelle}, the specialization of
\verb!Isabelle! for higher-order logic. Sultana, Benzm{\"{u}}ller, and
Paulson~\cite{Een2004} integrates \verb!Leo-II! and \verb!Satallax!, two
theorem provers for high-order logic with \verb!Isabelle/HOL! proposing a
modular proof reconstruction work flow.

\verb!SMTCoq!~\cite{armand2011,Ekici2017} is a tool for the \verb!Coq!
proof assistant \cite{coqteam} which provides a certified checker for
proof witness coming from the SMT solver \verb!veriT! \cite{bouton2009}
and adds a new tactic named verit, that calls \verb!veriT! on any
\verb!Coq! goal. In \cite{bezem2002automated}, given a fixed but arbitrary
first-order signature, the authors transform a proof produced by the
first-order automatic theorem prover \verb!Bliksem! \cite{deNivelle2003}
in a \verb!Coq! proof term.

Hurd~\cite{Hurd1999} integrates the first-order resolution prover
\verb!Gandalf! with \verb!HOL!~\cite{norrish2007hol}, a high-order theorem
prover, following a LCF model implementing the tactic \verb!GANDALF_TAC!.
For \verb!HOL Light!, a version of \verb!HOL! but with a simpler logic core,
the SMT solver \verb!CVC4! was integrated and Kaliszyk and
Urban~\cite{kaliszyk2013} reconstruct proofs from different ATPs with their
\verb!PRocH! tool, replaying the detailed inference steps from the ATPs with
internal inference methods implemented in \verb!HOL Light!.

% Taken from: % Färber, M., & Kaliszyk, C. (2015). Metis-based
% Paramodulation Tactic for HOL

% Light. In GCAI 2015. Global Conference on Artificial Intelligence
% Metis-based

%(Vol. 36, pp. 127–136).

% HOL(y)Hammer [KU15] is an automated deduction framework for HOL4 and
% HOL Light.

% Given a conjecture, it attempts to find suitable premises, then calls
% external ATPs such as E[Sch13], Vampire [KV13], or Z3 [dMB08], and
% attempts to reconstruct the proof using the premises used by the ATP.
% To reconstruct proofs, it uses tactics such as MESON, simplification,
% and a
% few other decision procedures, however, these are sometimes not p
% owerful
% enough to reconstruct proofs found by the external ATPs.

\verb!Waldmeister! is an automatic theorem prover for unit equational
logic \cite{hillenbrand1997}.
Foster and Struth~\cite{foster2011integrating} integrate \verb!Waldmeister! into
\verb!Agda!~\cite{agdateam}. This integration requires a proof
reconstruction step but authors' approach is restricted to pure
equational logic --also called identity theory~\cite{humberstone2011}--
that is, first-order logic with equality but no other predicate symbols
and no functions symbols~\cite{appel1959}.

Kanso and Setzer~\cite{kanso2016light} integrate \verb!Z3! in \verb!Agda!
but they also integrate the propositional fragment of the \verb!E! prover in
\cite{Kanso2012}. They cataloged these two integration as
\emph{Oracle and Reflection} and \emph{Oracle and Justification}, respectively.
Their integration with the \verb!E! prover is the most related work with our
apporach found at the moment while we write this document. Besides the use
of the same ITP, crucial differences easily arise like decidability of
propositional logic using semantics that we do not take into account for the
reason we describe later on in section~\ref{sec:conclusions}.

\end{document}

### 2017-09-04 paper/sections/introduction.tex
[ paper ] minor changes.

@@
 Proof reconstruction is a hard labor since it depends on the integration
-of two complex system. On one hand, we have the automatic theorem provers
+of two complex systems. On the one hand, we have the automatic theorem provers
 (henceforth ATP) and their specification logic. These tools are usually
 classified in at least one of the following categories. A SAT solver
-(e.g. \verb!zChaff!~\cite{Moskewicz2001} and \verb!MiniSat!~\cite{Een2004})
+(e.g., \verb!zChaff!~\cite{Moskewicz2001} and \verb!MiniSat!~\cite{Een2004})
 to prove unsatisfiability of CNF formulas, a QBF solver
-(e.g. \verb!GhostQ!~\cite{Klieber2014} and \verb!DepQBF!~\cite{Lonsing2017})
+(e.g., \verb!GhostQ!~\cite{Klieber2014} and \verb!DepQBF!~\cite{Lonsing2017})
 to prove satisfiability and invalidity of quantified Boolean formulas, a SMT
@@
 formulas from first-order logic with equality
-(e.g. \verb!E!~\cite{Schulz:AICOM-2002}, \verb!leanCoP!~\cite{Otten2008},
+(e.g., \verb!E!~\cite{Schulz:AICOM-2002}, \verb!leanCoP!~\cite{Otten2008},
 \verb!Metis!~\cite{hurd2003first}, \verb!SPASS! ~\cite{Weidenbach2009} and
-\verb!Vampire!~\cite{Riazanov1999}), high-order logic (e.g. \verb!Leo-II!
+\verb!Vampire!~\cite{Riazanov1999}), high-order logic (e.g., \verb!Leo-II!
 \cite{Benzmuller2008} and \verb!Satallax!~\cite{Brown2012}) or intuitonistic
-logic (e.g. \verb!ileanCoP!~\cite{Otten2008}, \verb!JProver!
+logic (e.g., \verb!ileanCoP!~\cite{Otten2008}, \verb!JProver!
 \cite{Schmitt2001}, and \verb!Gandalf!~\cite{Tammet1997}), among others.
 On the other hand, we have the proof checkers, interactive theorem provers
-(henceforth ITP) or proof assistants (e.g. \verb!Agda!~\cite{agdateam},
+(henceforth ITP) or proof assistants (e.g., \verb!Agda!~\cite{agdateam},
 \verb!Coq!~\cite{coqteam}, \verb!Isabelle!~\cite{paulson1994isabelle}, and
@@
 The ITP tools provide us the logic framework to check and validate the
-reply of the ATPs, since they allow us to define the formal language for
+reply of the ATPs since they allow us to define the formal language for
 the problems like operators, logic variables, axioms, and theorems.
 
-A proof reconstruction tool provides such an integration in one
-direction, the bridge between ATPs to ITPs. This is mostly a translation
-of the reply delivered by the prover into the formalism of the proof
-assistant. Because the formalism of the source (the proof generated by
-the ATP) is not necessarily the same logic in the target, the
-reconstruction turns out in a ``reverse engineering'' task. Then,
-reconstructing a proof involves a deep understanding of the algorithms in
-the ATP and the specification logic in the ITP.
+A proof reconstruction tool provides such an integration in one direction,
+the bridge between ATPs to ITPs. This is mostly a translation of the reply
+delivered by the prover into the formalism of the proof assistant.
+Because the formalism of the source (the evidence generated by the ATP) is
+not necessarily the same logic in the target, the reconstruction turns out
+in a ``reverse engineering'' task. Then, reconstructing a proof involves an
+in-depth understanding deep understanding of the algorithms in the ATP and
+the specification logic in the ITP.
 
-What we need from the ATP tools is a proof object in a consistent format
+What we need from the ATP tools is a proof-object in a consistent format
 to work with, that is, a full script describing step-by-step with
@@
 from the web service \texttt{SystemOnTPTP} of the TPTP World.} ATPs, just
-a few provers were able to deliver proofs (e.g. \verb!CVC4!~
+a few provers were able to deliver proofs (e.g., \verb!CVC4!~
 \cite{Barrett2011}, \verb!SPASS!, and
@@
 and a little bit less replied with a proof in a
-file format like \verb!TSTP!~\cite{sutcliffe2004tstp} (e.g. \verb!E!, \verb!Metis!,
+file format like \verb!TSTP!~\cite{sutcliffe2004tstp} (e.g., \verb!E!, \verb!Metis!,
 \verb!Vampire!, and \verb!Z3!), LFSC~\cite{Stump2008}, or the
@@
 proof assistant \verb!Agda! by parsing \verb!TSTP! derivations to generate
-\verb!Agda! code of the proofs. We structure the paper as follows.
+\verb!Agda! proof-terms. We structure the paper as follows.
 In section \ref{sec:metis-language-and-proofs} we briefly introduce
-the \verb!Metis! prover. In section \ref{sec:proof-reconstruction}, we
+the \verb!Metis! prover. In section \ref{sec:proof-reconstruction}; we
 present our approach to reconstruct proofs deliver by \verb!Metis! in
@@
 We list related work in proof reconstruction in section \ref{sec:related-work}
-In section~\ref{sec:conclusions}, we discuss some limitations, advantages
+In section~\ref{sec:conclusions}, we discuss some limitations, advantages,
 and disadvantages with other similar proof reconstruction tools and

### 2017-09-04 paper/sections/metis-language-and-proofs.tex
[ paper ] minor changes.

@@
 first-order logic with equality developed by John Hurd~\cite{hurd2003first}.
-As we show later this prover is suitable for proof reconstruction task since
-it provides well-documented proof-objects with enough information to justify
-the deduction steps.
+This prover is suitable for proof reconstruction task since it provides
+well-documented proof-objects with enough information to justify his deduction
+steps and it also has been used by other proof-reconstruction tools.
 
-\verb!Metis! has been integrated to \verb!Isabelle/HOL! as a macro-step reconstruction
-tool for justifying proof steps (usually CNF goals) replied from other ATPs like
+\verb!Isabelle/HOL! integrated !Metis! as a macro-step reconstruction
+tool for explaining proof steps (usually CNF goals) replied from other ATPs like
 \verb!CVC4!, \verb!Vampire!, or \verb!Z3!.
 In \cite{Farber2015}, \verb!Metis! was used to provide a tactic for
-\verb!HOL Light!, this tactic challenges others like \verb!MESON! tactic or the
+\verb!HOL Light!; this tactic challenges others like \verb!MESON! tactic or the
 \verb!leanCoP! tactic that reconstructs proofs delivered by
@@
 In this paper, we ported a subset of \verb!Metis!' inference rules to \verb!Agda!,
-the propositional fragmented, to allow us justify step-by-step the proofs
+the propositional fragmented, to allow us to justify step-by-step the proofs
 delivered in \verb!TSTP! format generated by \verb!Metis!.

### 2017-09-04 paper/main.tex
[ paper ] todo notes added.

@@
 \def\EnableBpAbbreviations{true}
+
+% --------------------------------------------------------------------------
+% TODO notes
+% --------------------------------------------------------------------------
+
+\usepackage{xargs}
+\usepackage[pdftex,dvipsnames]{xcolor}
+\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
+\newcommandx{\unsure}[2][1=]
+  {\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
+\newcommandx{\change}[2][1=]
+  {\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
+\newcommandx{\info}[2][1=]
+  {\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25
+        ,bordercolor=OliveGreen,#1]{#2}}
+\newcommandx{\improvement}[2][1=]
+  {\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
+\newcommandx{\thiswillnotshow}[2][1=]
+  {\todo[disable,#1]{#2}}
 
@@
 % \tocauthor{Authors' Instructions}
+
+\listoftodos[Notes]
+
+% TODO commands!
+% \unsure
+% \change
+% \info
+% \improvement
+% \thiswillnotshow
+
+\subfile{TODO.tex}
+
 \maketitle

### 2017-09-04 paper/sections/acknowledgements.tex
[ paper ] todo notes added.

@@
 We thank Joe Leslie-Hurd for all support with \verb!Metis! prover.
-We also acknowledge the work carry out by Alejandro G\'omez-Londo\~no~
-\cite{Gomez-Londono2015} that was used as the basis code for our TSTP parsing
+We also acknowledge the work carried out by Alejandro G\'omez-Londo\~no~
+\cite{Gomez-Londono2015} used as the basis code for our TSTP parsing
 module.
-And last but not least, we gratefully acknowledge Andreas Abel and Chalmers
+And last but not least, we thankfully acknowledge Andreas Abel and Chalmers
 University of Goteborg, Sweden for inviting us to be part of the Agda

### 2017-09-04 paper/sections/introduction.tex
[ paper ] todo notes added.

@@
 \verb!Vampire!~\cite{Riazanov1999}), high-order logic (e.g., \verb!Leo-II!
-\cite{Benzmuller2008} and \verb!Satallax!~\cite{Brown2012}) or intuitonistic
+\cite{Benzmuller2008} and \verb!Satallax!~\cite{Brown2012}) or intuitionistic
 logic (e.g., \verb!ileanCoP!~\cite{Otten2008}, \verb!JProver!
@@
 A proof reconstruction tool provides such an integration in one direction,
-the bridge between ATPs to ITPs. This is mostly a translation of the reply
-delivered by the prover into the formalism of the proof assistant.
-Because the formalism of the source (the evidence generated by the ATP) is
-not necessarily the same logic in the target, the reconstruction turns out
-in a ``reverse engineering'' task. Then, reconstructing a proof involves an
-in-depth understanding deep understanding of the algorithms in the ATP and
-the specification logic in the ITP.
-
+is a translator of the reply delivered by the prover into the formalism of
+the proof assistant. Because the formalism of the source (the evidence
+generated by the ATP) is not necessarily the same logic in the target, the
+reconstruction turns out in a ``reverse engineering'' task.
+Then, reconstructing a proof involves an in-depth understanding of the
+algorithms in the ATP and the specification logic in the ITP.
 What we need from the ATP tools is a proof-object in a consistent format

### 2017-09-04 paper/sections/metis-language-and-proofs.tex
[ paper ] todo notes added.

@@
 
-\verb!Isabelle/HOL! integrated !Metis! as a macro-step reconstruction
+\verb!Isabelle/HOL! integrated \verb!Metis! as a macro-step reconstruction
 tool for explaining proof steps (usually CNF goals) replied from other ATPs like
@@
 
-The \verb!rule! stands for the inference name, the other fields are
-auxiliary arguments or useful information to apply the inference, and
+The \verb!rule! stands for the inference name; the other fields are
+supporting arguments or useful information to apply the reasoning step, and
 the list of parents nodes.
 For instance, in Fig.~\ref{fig:metis-proof-tstp}, \verb!strip! is the name of one
-of the inference and it has no arguments and only one parent node, \verb!goal!.
+of the inference with no arguments and only one parent node, the \verb!goal!.
 
@@
 fof(negate_0_0, plain, ~ p, inference (negate, [], [subgoal_0])) .
-fof(normalize_0_0, plain, ∼ p, inference (canonicalize, [], [negate_0_0])) .
-fof(normalize_0_1, plain, p, inference (canonicalize, [], [a])) .
-fof(normalize_0_2, plain, $false, inference (simplify, [],
-  [normalize_0_0, normalize_0_1]))
-cnf(refute_0_0, plain, $false, inference (canonicalize, [], [normalize_0_2])) .
+fof(normalize_0_0, plain, ∼ p,
+  inference (canonicalize, [], [negate_0_0])) .
+fof(normalize_0_1, plain, p,
+  inference (canonicalize, [], [a])) .
+fof(normalize_0_2, plain, $false,
+  inference (simplify, [], [normalize_0_0, normalize_0_1]))
+cnf(refute_0_0, plain, $false,
+  inference (canonicalize, [], [normalize_0_2])) .
 \end{verbatim}
@@
 
-\subsection{Proof Terms}
-\label{ssec:proof-terms}
+\subsection{Proofs}
+\label{ssec:metis-proofs}
 
 A proof-object delivered in a \verb!Metis!' proof encodes a natural
-deduction proof. Its deduction system uses six simple inference rules
-(see Fig.~\ref{fig:metis-inferences}) to attempt to prove conjectures
-by refutation (see. e.g. Fig.~\ref{fig:metis-example}).
+deduction proof. The deduction system uses six inference rules
+\cite{hurd2003first} (see Fig.~\ref{fig:metis-inferences}) to attempt to
+prove conjectures by refutation (see. e.g., the last conclusion
+in the TSTP derivation Fig.~\ref{fig:metis-example} is \emph{falsium}).
 
@@
 labeled with a name of the inference rule
-(e.g. \verb!canonicalize! in Fig.~\ref{fig:metis-example}). Each
-edge links a premise with one conclusion. The proof graphs have in their
+(e.g., \verb!canonicalize! in Fig.~\ref{fig:metis-example}). Each
+edge links a premise with one conclusion. The proof graphs have at their
 root the conclusion $\bot$ since \verb!Metis! delivers proof by refutation.
 
-% \begin{figure}
-% \centering
-% \begin{bprooftree}
-%   \centering\tt
-%   \AxiomC{}
-%   \RightLabel{\scriptsize negate}
-%   \UnaryInfC{$\neg p$}
-%   \RightLabel{\scriptsize strip}
-%   \UnaryInfC{$\neg p$}
-%   \AxiomC{}
-%   \RightLabel{\scriptsize axiom}
-%   \UnaryInfC{$p$}
-%   \RightLabel{\scriptsize canonicalize}
-%   \UnaryInfC{$p$}
-%   \RightLabel{\scriptsize simplify}
-%   \BinaryInfC{$\bot$}
-%   \RightLabel{\scriptsize canonicalize}
-%   \UnaryInfC{$\bot$}
-% \end{bprooftree}
-% % \caption{The \verb!Metis!' refutation tree for $p \vdash p$ from the
-% % derivation in Fig.~\ref{fig:metis-proof-tstp}}
-% \label{fig:metis-example}
-% \end{figure}
+\begin{figure}
+\centering
+\begin{bprooftree}\tt
+  \AxiomC{}
+  \RightLabel{\scriptsize negate}
+  \UnaryInfC{$\neg p$}
+  \RightLabel{\scriptsize strip}
+  \UnaryInfC{$\neg p$}
+  \AxiomC{}
+  \RightLabel{\scriptsize axiom}
+  \UnaryInfC{$p$}
+  \RightLabel{\scriptsize canonicalize}
+  \UnaryInfC{$p$}
+  \RightLabel{\scriptsize simplify}
+  \BinaryInfC{$\bot$}
+  \RightLabel{\scriptsize canonicalize}
+  \UnaryInfC{$\bot$}
+\end{bprooftree}
+% \caption{The \verb!Metis!' refutation tree for $p \vdash p$ from the
+% derivation in Fig.~\ref{fig:metis-proof-tstp}}
+\label{fig:metis-example}
+\end{figure}
 
@@
 
-Despite the six simple rules in the \verb!Metis!' logic
-kernel (see~Fig. \ref{fig:metis-inferences}), we found in \verb!TSTP!
+Despite the six rules in the \verb!Metis!' logic
+kernel (see~Fig. \ref{fig:metis-inferences}), we observed in \verb!TSTP!
 derivations for CPL problems other inference rules.
@@
 more literals and a literal is an atom (positive literal) or a negation of an
-atom (negative literal). This conversion is not unique and \verb!Metis! performs
-this transformation using its own criteria.
+atom (negative literal). This conversion is not unique, and \verb!Metis! performs
+this transformation using its criteria.
 
@@
 propositional formula that comes from an axiom or a definition.
-It often converts the formula in one of its normal form,
-the conjunctive normal form,%as \verb!clausify! does
-the negative normal form or the disjunctive normal form.
+It often converts each expression in one of its normal form,
+the conjunctive normal form, the negative normal form or the disjunctive normal form.
 Posterior, this rule simplifies the formula with some definitions, applying
@@
 
-\textit{Resolution.} The \verb!resolve! rule (see, for example,
-Fig.~\ref{fig:resolve-inference}) is the resolution
-theorem with two argument, the positive literal for resolution and two
-formulas from their own derivations. The positive literal $p$ must occur in
-the first formula of the input and the negative literal must occur in the second
-formula of the input
-(see the resolve rule in \verb!Metis!' logic core in
-Fig.~\ref{fig:metis-inferences}).
+\textit{Resolution.} The \verb!resolve! rule is the resolution
+theorem showed in Fig.~\ref{fig:metis-inferences}. Its applications
+needs the positive literal for resolution and two
+derivations to deduce the \emph{resolvent}.
+The positive literal $p$ must occur in the formula from the first derivation,
+and the negative literal must occur in the formula from the second derivation
+(this follows the same pattern in \verb!Metis!' logic core in
+Fig.~\ref{fig:metis-inferences} for the resolve inference).
 
 \begin{verbatim}
-cnf(refute_0_0, plain, p | q, inference(canonicalize, [], [normalize_0_0])).
-cnf(refute_0_1, plain, ~ p, inference(canonicalize, [], [normalize_0_4])).
+cnf(refute_0_0, plain, p | q,
+  inference(canonicalize, [], [normalize_0_0])).
+cnf(refute_0_1, plain, ~ p,
+  inference(canonicalize, [], [normalize_0_4])).
 cnf(refute_0_2, plain, q,
@@
 \textit{Splitting a conjunct.}
-The \verb!conjunct! rule extracts from a conjunction one of its conjuncts, it is
+The \verb!conjunct! rule extracts from a conjunction one of its conjuncts; it is
 a generalization of the projection rules for the conjunction connective as
@@
 \begin{verbatim}
-fof(normalize_1, plain, p & q & r, inference(canonicalize, [], [x])).
-fof(normalize_2, plain, q, inference(conjunct, [], [normalize_1])).
+fof(normalize_1, plain, p & q & r,
+  inference(canonicalize, [], [x])).
+fof(normalize_2, plain, q,
+  inference(conjunct, [], [normalize_1])).
 \end{verbatim}
@@
 \begin{verbatim}
-fof(subgoal_0, plain, p, inference(strip, [], [goal])).
-fof(negate_0_0, plain, ~ p, inference(negate, [], [subgoal_0])).
+fof(subgoal_0, plain, p,
+  inference(strip, [], [goal])).
+fof(negate_0_0, plain, ~ p,
+  inference(negate, [], [subgoal_0])).
 \end{verbatim}
@@
 \textit{Simplification.} %abbreviate formulas
-The \verb!simplify! rule is an $n$-ary rule that performs simplification
+The \verb!simplify! rule is a $n$-ary inference that performs simplification
 of definitions. This rule transverses a list of formulas by
-applying different theorems (e.g.\emph{modus pones}, \emph{modus tollens},
+applying different theorems (e.g., \emph{modus pones}, \emph{modus tollens},
 or \emph{disjunctive syllogism}) including the list of theorems used by
@@
 and the resolution theorem of \verb!resolve! rule.
-Moreover, many things happen inside this \verb!Metis!' procedure and
-it is fairly complex to grasp it completely.
+Moreover, many things happen inside this \verb!Metis!' procedure, and
+it is somewhat complicated to grasp it completely.
 

### 2017-09-04 paper/sections/proof-reconstruction.tex
[ paper ] todo notes added.

@@
 Then, we use \verb!Agda! as a proof checker to type-check the proof.
-If type-checking succeed, then our proof is verified. Else, we have a failure
-proof due by three possible actors. First, a soundness bug in the ATP or a bug
+If type-checking succeed, then our proof is checked. Else, we have a failure
+proof due to three possible factors. First, a soundness bug in the ATP or a bug
 in the output printing. Second, a bug in the translation process in our \verb!TSTP! parsing
@@
 One of the main strengths of \verb!Agda! is its support for writing proofs,
-which we shall call \verb!Agda!'s proof engine and it consists of: support for
+which we shall call \verb!Agda!'s proof engine. It consists of: support for
 inductively defined types, including inductive families, and function
@@
 
-A propositional formula is a string of indivisible propositional atoms,
+A propositional formula is a experssion of indivisible propositional atoms,
 logical connectives $\{\wedge, \vee, \Rightarrow, \Leftrightarrow, \neg\}$

### 2017-09-04 paper/sections/related-work.tex
[ paper ] todo notes added.

@@
 (see, for example, \cite{meng2006automation}, \cite{blanchette2013extending}
-and \cite{Fleury2014}) and SMT solvers (see, for example,
+and \cite{Fleury2014}) and SMT solvers (see, for instance,
 \cite{hurlin07practical}, \cite{bohme2010},
@@
 \verb!Gandalf! with \verb!HOL!~\cite{norrish2007hol}, a high-order theorem
-prover, following a LCF model implementing the tactic \verb!GANDALF_TAC!.
+prover, following an LCF model implementing the tactic \verb!GANDALF_TAC!.
 For \verb!HOL Light!, a version of \verb!HOL! but with a simpler logic core,
-the SMT solver \verb!CVC4! was integrated and Kaliszyk and
+the SMT solver \verb!CVC4! was integrated, and Kaliszyk and
 Urban~\cite{kaliszyk2013} reconstruct proofs from different ATPs with their
@@
 \verb!Agda!~\cite{agdateam}. This integration requires a proof
-reconstruction step but authors' approach is restricted to pure
+reconstruction step, but authors' approach is restricted to pure
 equational logic --also called identity theory~\cite{humberstone2011}--

### 2017-09-05 paper/sections/introduction.tex
[ paper ] new commands for programs and langs.

@@
 % -*- root: main.tex -*-
-\documentclass[main.tex]{subfiles}
+\documentclass[../main.tex]{subfiles}
 \begin{document}
@@
 of two complex systems. On the one hand, we have the automatic theorem provers
-(henceforth ATP) and their specification logic. These tools are usually
-classified in at least one of the following categories. A SAT solver
-(e.g., \verb!zChaff!~\cite{Moskewicz2001} and \verb!MiniSat!~\cite{Een2004})
-to prove unsatisfiability of CNF formulas, a QBF solver
-(e.g., \verb!GhostQ!~\cite{Klieber2014} and \verb!DepQBF!~\cite{Lonsing2017})
-to prove satisfiability and invalidity of quantified Boolean formulas, a SMT
-solver (e.g \verb!CVC4!~\cite{Barrett2011}, \verb!veriT!~\cite{bouton2009},
-and \verb!Z3!~\cite{DeMoura2008}) to prove unsatisfiability of formulas
+(henceforth \ATP) and their specification logic. These tools are usually
+classified in at least one of the following categories. A \SAT solver
+(e.g., \name{zChaff}~\cite{Moskewicz2001} and \name{MiniSat}~\cite{Een2004})
+to prove unsatisfiability of \CNF formulas, a \abbre{QBF} solver
+(e.g., \name{GhostQ}~\cite{Klieber2014} and \name{DepQBF}~\cite{Lonsing2017})
+to prove satisfiability and invalidity of quantified Boolean formulas, a \SMT
+solver (e.g \name{CVC4}~\cite{Barrett2011}, \name{veriT}~\cite{bouton2009},
+and \name{Z3}~\cite{DeMoura2008}) to prove unsatisfiability of formulas
 from first-order logic with theories, and a prover for validity of
 formulas from first-order logic with equality
-(e.g., \verb!E!~\cite{Schulz:AICOM-2002}, \verb!leanCoP!~\cite{Otten2008},
-\verb!Metis!~\cite{hurd2003first}, \verb!SPASS! ~\cite{Weidenbach2009} and
-\verb!Vampire!~\cite{Riazanov1999}), high-order logic (e.g., \verb!Leo-II!
-\cite{Benzmuller2008} and \verb!Satallax!~\cite{Brown2012}) or intuitionistic
-logic (e.g., \verb!ileanCoP!~\cite{Otten2008}, \verb!JProver!
-\cite{Schmitt2001}, and \verb!Gandalf!~\cite{Tammet1997}), among others.
+(e.g., \name{E}~\cite{Schulz:AICOM-2002}, \name{leanCoP}~\cite{Otten2008},
+\Metis~\cite{hurd2003first}, \name{SPASS} ~\cite{Weidenbach2009} and
+\name{Vampire}~\cite{Riazanov1999}), high-order logic (e.g., \name{Leo-II}
+\cite{Benzmuller2008} and \name{Satallax}~\cite{Brown2012}) or intuitionistic
+logic (e.g., \name{ileanCoP}~\cite{Otten2008}, \name{JProver}
+\cite{Schmitt2001}, and \name{Gandalf}~\cite{Tammet1997}), among others.
 On the other hand, we have the proof checkers, interactive theorem provers
-(henceforth ITP) or proof assistants (e.g., \verb!Agda!~\cite{agdateam},
-\verb!Coq!~\cite{coqteam}, \verb!Isabelle!~\cite{paulson1994isabelle}, and
-\verb!HOL4!~\cite{norrish2007hol}).
-The ITP tools provide us the logic framework to check and validate the
-reply of the ATPs since they allow us to define the formal language for
+(henceforth \ITP) or proof assistants (e.g., \Agda~\cite{agdateam},
+\name{Coq}~\cite{coqteam}, \name{Isabelle}~\cite{paulson1994isabelle}, and
+\name{HOL4}~\cite{norrish2007hol}).
+The \ITP tools provide us the logic framework to check and validate the
+reply of the \ATPs since they allow us to define the formal language for
 the problems like operators, logic variables, axioms, and theorems.
@@
 the proof assistant. Because the formalism of the source (the evidence
-generated by the ATP) is not necessarily the same logic in the target, the
+generated by the \ATP) is not necessarily the same logic in the target, the
 reconstruction turns out in a ``reverse engineering'' task.
 Then, reconstructing a proof involves an in-depth understanding of the
-algorithms in the ATP and the specification logic in the ITP.
-What we need from the ATP tools is a proof-object in a consistent format
+algorithms in the \ATP and the specification logic in the \ITP.
+What we need from the \ATP tools is a proof-object in a consistent format
 to work with, that is, a full script describing step-by-step with
@@
 to get the actual proof. For problems in classical propositional logic
-(henceforth CPL), from a list of at least forty\footnote{ATPs available
-from the web service \texttt{SystemOnTPTP} of the TPTP World.} ATPs, just
-a few provers were able to deliver proofs (e.g., \verb!CVC4!~
-\cite{Barrett2011}, \verb!SPASS!, and
-\verb!Waldmeister!~\cite{hillenbrand1997})
-and a little bit less replied with a proof in a
-file format like \verb!TSTP!~\cite{sutcliffe2004tstp} (e.g., \verb!E!, \verb!Metis!,
-\verb!Vampire!, and \verb!Z3!), LFSC~\cite{Stump2008}, or the
-SMT-LIB~\cite{Bohme2011} format.
+(henceforth \CPL), from a list of at least forty\footnote{\ATPs available
+from the web service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just
+a few provers were able to deliver proofs (e.g., \name{CVC4}~
+\cite{Barrett2011}, \name{SPASS}, and \name{Waldmeister}~\cite{hillenbrand1997})
+and a little bit less replied with a proof in a file format like
+\TSTP~\cite{sutcliffe2004tstp} (e.g., \name{E}, \Metis,
+\name{Vampire}, and \name{Z3}), \len{LFSC}~\cite{Stump2008}, or the
+\len{SMT-LIB}~\cite{Bohme2011} format.
 
@@
 the confidence of their users about their algorithms and their
-correctness (see, for example, bugs in ATPs~\cite{Keller2013},
+correctness (see, for example, bugs in \ATPs~\cite{Keller2013},
 \cite{Bohme2011}, \cite{Fleury2014} and \cite{Kanso2012}).
@@
 
-In this paper, we describe the integration of \verb!Metis! prover with the
-proof assistant \verb!Agda! by parsing \verb!TSTP! derivations to generate
-\verb!Agda! proof-terms. We structure the paper as follows.
+In this paper, we describe the integration of \Metis prover with the
+proof assistant \Agda by parsing \TSTP derivations to generate
+\Agda proof-terms. We structure the paper as follows.
 In section \ref{sec:metis-language-and-proofs} we briefly introduce
-the \verb!Metis! prover. In section \ref{sec:proof-reconstruction}; we
-present our approach to reconstruct proofs deliver by \verb!Metis! in
-\verb!Agda!.
-%In section \ref{sec:example}, we present a complete example of a proof reconstructed with our tool for a CPL problem.
+the \Metis prover. In section \ref{sec:proof-reconstruction}; we
+present our approach to reconstruct proofs deliver by \Metis in
+\Agda.
 We list related work in proof reconstruction in section \ref{sec:related-work}

### 2017-09-05 paper/sections/metis-language-and-proofs.tex
[ paper ] new commands for programs and langs.

@@
 
-\verb!Metis! is an automatic theorem prover written in Standard ML for
+\Metis is an automatic theorem prover written in \len{Standard ML} for
 first-order logic with equality developed by John Hurd~\cite{hurd2003first}.
-This prover is suitable for proof reconstruction task since it provides
-well-documented proof-objects with enough information to justify his deduction
-steps and it also has been used by other proof-reconstruction tools.
+This prover is suitable for proof reconstruction since it provides
+well-documented proof-objects to justify its deduction steps from the basis
+of only six inference rules. Exists tools that perform proof
+reconstruction with \Metis, some of these systems are the following.
 
-\verb!Isabelle/HOL! integrated \verb!Metis! as a macro-step reconstruction
-tool for explaining proof steps (usually CNF goals) replied from other ATPs like
-\verb!CVC4!, \verb!Vampire!, or \verb!Z3!.
-In \cite{Farber2015}, \verb!Metis! was used to provide a tactic for
-\verb!HOL Light!; this tactic challenges others like \verb!MESON! tactic or the
-\verb!leanCoP! tactic that reconstructs proofs delivered by
-\verb!leanCoP!~\cite{Farber2016}.
+\name{Isabelle/HOL} incorporated \Metis as a macro-step reconstruction
+tool for explaining proof steps (usually \CNF goals) replied from other \ATPs like
+\name{CVC4}, \name{Vampire}, or \name{Z3}
+(more details in Ref.~\cite{paulson2007source}).
+In \cite{Farber2015}, \Metis was used to provide a tactic for
+\name{HOL Light}; this tactic challenges others like \name{MESON} tactic or the
+\name{leanCoP} tactic that reconstructs proofs delivered by
+\name{leanCoP}~\cite{Farber2016}.
 
-In this paper, we ported a subset of \verb!Metis!' inference rules to \verb!Agda!,
+In this paper, we ported a subset of \Metis' inference rules to \Agda,
 the propositional fragmented, to allow us to justify step-by-step the proofs
-delivered in \verb!TSTP! format generated by \verb!Metis!.
+delivered in \TSTP format generated by \Metis.
 
@@
 
-\textit{Input.}~The \verb!TPTP! language  --which includes the first-order
-form (denoted by \verb!fof!) and clause normal form (denoted by \verb!cnf!)
+\textit{Input.}~The \TPTP language --which includes the first-order
+form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf})
 formats~\cite{sutcliffe2009} -- is de
-facto input standard language to encode problems for many ATPs.
-The \verb!TPTP! syntax describes a well-defined grammar to handle annotated
+facto input standard language to encode problems for many \ATPs.
+The \TPTP syntax describes a well-defined grammar to handle annotated
 formulas with the following form
@@
 
-The \verb!language! can be \verb!fof! or \verb!cnf!. The \verb!name!
+The \name{language} can be \name{fof} or \name{cnf}. The \name{name}
 serves to identify the formula within the problem. Each formula assumes one
-\verb!role!, this could be an \verb!axiom!, \verb!conjecture!,
-\verb!definition!, or a \verb!hypothesis!. The formulas include Boolean
-connectives (\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!, $\tt\sim$) and logic
+\name{role}, this could be an \name{axiom}, \name{conjecture},
+\name{definition}, or a \name{hypothesis}. The formulas include Boolean
+connectives (\verb!&!, \verb!|!, \verb!=>!, \verb!{<=>!, $\tt\sim$) and logic
 constants \verb!$true! and \verb!$false!.
@@
 $p\, \vdash \neg (p \wedge \neg p) \vee (q \vee \neg q)$
-in \verb!TPTP! syntax as follows.
+in \TPTP syntax as follows.
 
@@
 
-\textit{Output.}~\verb!TSTP! language is de facto output standard language
+\textit{Output.}~\TSTP language is de facto output standard language
 for derivations of ATPs~\cite{sutcliffe2004tstp}.
-A \verb!TSTP! derivation is a directed acyclic graph, a proof tree, where each leaf
-is a formula from the \verb!TPTP! input. A node is a formula inferred from the parent
+A \TSTP derivation is a directed acyclic graph, a proof tree, where each leaf
+is a formula from the \TPTP input. A node is a formula inferred from the parent
 formulas. The root is the final derived formula. Such a derivation is a list of
@@
 
-The \verb!source! field is an inference record with the following pattern
+The \name{source} field is an inference record with the following pattern
 \begin{verbatim}
@@
 
-The \verb!rule! stands for the inference name; the other fields are
+The \name{rule} stands for the inference name; the other fields are
 supporting arguments or useful information to apply the reasoning step, and
 the list of parents nodes.
-For instance, in Fig.~\ref{fig:metis-proof-tstp}, \verb!strip! is the name of one
-of the inference with no arguments and only one parent node, the \verb!goal!.
+For instance, in Fig.~\ref{fig:metis-proof-tstp}, \strip is the name of one
+of the inference with no arguments and only one parent node, the \name{goal}.
 
@@
 \end{verbatim}
-\caption{A simple \texttt{Metis}' \texttt{TSTP} derivation for the problem $p\vdash p$.}
+\caption{The \texttt{Metis}' \texttt{TSTP} derivation for the problem $p\vdash p$.}
 \label{fig:metis-proof-tstp}
@@
 
-A proof-object delivered in a \verb!Metis!' proof encodes a natural
+A proof-object delivered in a \Metis' proof encodes a natural
 deduction proof. The deduction system uses six inference rules
@@
 prove conjectures by refutation (see. e.g., the last conclusion
-in the TSTP derivation Fig.~\ref{fig:metis-example} is \emph{falsium}).
+in the \TSTP derivation Fig.~\ref{fig:metis-example} is \emph{falsium}).
 
@@
 labeled with a name of the inference rule
-(e.g., \verb!canonicalize! in Fig.~\ref{fig:metis-example}). Each
+(e.g., \canonicalize in Fig.~\ref{fig:metis-example}). Each
 edge links a premise with one conclusion. The proof graphs have at their
-root the conclusion $\bot$ since \verb!Metis! delivers proof by refutation.
+root the conclusion $\bot$ since \Metis delivers proof by refutation.
 
@@
 \end{bprooftree}
-% \caption{The \verb!Metis!' refutation tree for $p \vdash p$ from the
+% \caption{The \Metis' refutation tree for $p \vdash p$ from the
 % derivation in Fig.~\ref{fig:metis-proof-tstp}}
@@
 
-Despite the six rules in the \verb!Metis!' logic
-kernel (see~Fig. \ref{fig:metis-inferences}), we observed in \verb!TSTP!
-derivations for CPL problems other inference rules.
-They are \verb!canonicalize!, \verb!conjunct!, \verb!negate!, \verb!simplify!,
-\verb!strip! and \verb!resolve!. We briefly review each of these rules
-following no order except maybe by their frequency in the \verb!TSTP! derivations.
+Despite the six rules in the \Metis' logic
+kernel (see~Fig. \ref{fig:metis-inferences}), we observed in \TSTP
+derivations for\CPL problems other inference rules.
+They are \canonicalize, \conjunct, \negate, \simplify,
+\strip and \resolve. We briefly review each of these rules
+following no order except maybe by their frequency in the \TSTP derivations.
 
@@
 \textit{Splitting}.
-To prove a goal, \verb!Metis! splits the goal into disjoint cases. This
+To prove a goal, \Metis splits the goal into disjoint cases. This
 process produces a list of new subgoals, the conjunction of these subgoals
@@
 Then, a proof of the goal becomes in smaller proofs, one
-refutation for each subgoal. These subgoals are introduced in the \verb!TSTP!
-derivation with the \verb!strip! inference rule.
+refutation for each subgoal. These subgoals are introduced in the \TSTP
+derivation with the \strip inference rule.
 
@@
 
-\textit{Clausification.} The \verb!clausify! rule transforms a
-propositional formula in clausal normal form or CNF,
+\textit{Clausification.} The \clausify rule transforms a
+propositional formula in clausal normal form or \CNF,
 a conjunction of clauses. Where a clause is the disjunction of zero or
 more literals and a literal is an atom (positive literal) or a negation of an
-atom (negative literal). This conversion is not unique, and \verb!Metis! performs
+atom (negative literal). This conversion is not unique, and \Metis performs
 this transformation using its criteria.
@@
 \textit{Normalization.}
-\verb!Metis! uses the \verb!canonicalize! rule to normalize a
+\Metis uses the \canonicalize rule to normalize a
 propositional formula that comes from an axiom or a definition.
@@
 \]
-% \caption{Some rules of \verb!canonicalize! inference.}
+% \caption{Some rules of \canonicalize inference.}
 \label{fig:conjunctive-disjunctive-simplification}
@@
 
-\textit{Resolution.} The \verb!resolve! rule is the resolution
+\textit{Resolution.} The \resolve rule is the resolution
 theorem showed in Fig.~\ref{fig:metis-inferences}. Its applications
@@
 and the negative literal must occur in the formula from the second derivation
-(this follows the same pattern in \verb!Metis!' logic core in
+(this follows the same pattern in \Metis' logic core in
 Fig.~\ref{fig:metis-inferences} for the resolve inference).
@@
 \textit{Splitting a conjunct.}
-The \verb!conjunct! rule extracts from a conjunction one of its conjuncts; it is
+The \conjunct rule extracts from a conjunction one of its conjuncts; it is
 a generalization of the projection rules for the conjunction connective as
-we can see in the following \verb!TSTP! derivation.
+we can see in the following \TSTP derivation.
 
@@
 Each subgoal proof is a refutation, thereby each proof assumes
-the negation of its subgoal. The \verb!negate! rule
+the negation of its subgoal. The \negate rule
 introduces the negation of a subgoal that results
-after applies the \verb!strip! inference to the goal.
+after applies the \strip inference to the goal.
 
@@
 \textit{Simplification.} %abbreviate formulas
-The \verb!simplify! rule is a $n$-ary inference that performs simplification
+The \simplify rule is a $n$-ary inference that performs simplification
 of definitions. This rule transverses a list of formulas by
@@
 or \emph{disjunctive syllogism}) including the list of theorems used by
-\verb!canonicalize! in Fig.~\ref{fig:conjunctive-disjunctive-simplification}
-and the resolution theorem of \verb!resolve! rule.
-Moreover, many things happen inside this \verb!Metis!' procedure, and
+\canonicalize in Fig.~\ref{fig:conjunctive-disjunctive-simplification}
+and the resolution theorem of \resolve rule.
+Moreover, many things happen inside this \Metis' procedure, and
 it is somewhat complicated to grasp it completely.

### 2017-09-05 paper/sections/proof-reconstruction.tex
[ paper ] new commands for programs and langs.

@@
 
-Our system (see Fig~\ref{fig:proof-reconstruction-overview}) translates a \verb!TSTP!
-file into an \verb!Agda! proof by parsing it with a \verb!Haskell! tool.
+Our system (see Fig~\ref{fig:proof-reconstruction-overview}) translates a \TSTP
+file into an \Agda proof by parsing it with a \Haskell tool.
 This tool reconstructs the proof tree, removing redundancies and
 cutting unnecessary steps (see for example repetitions in the derivation shown in
-Fig~\ref{fig:metis-example}). The output is \verb!Agda! code.
-Then, we use \verb!Agda! as a proof checker to type-check the proof.
+Fig~\ref{fig:metis-example}). The output is \Agda code.
+Then, we use \Agda as a proof checker to type-check the proof.
 If type-checking succeed, then our proof is checked. Else, we have a failure
 proof due to three possible factors. First, a soundness bug in the ATP or a bug
-in the output printing. Second, a bug in the translation process in our \verb!TSTP! parsing
+in the output printing. Second, a bug in the translation process in our \TSTP parsing
 module, the inner algorithms in the analysis of the proof tree, the pretty printer
-module, or a bug in \verb!Haskell!. Lastly, a bug in our proof checker \verb!Agda!.
+module, or a bug in \Haskell. Lastly, a bug in our proof checker \Agda.
 
@@
 \node[right = 1.2cm of problem, text width=2cm, align=center]
-  (tptp){\verb!TPTP! \\ Problem};
+  (tptp){\TPTP \\ Problem};
 
 \node[right= 1.2cm of tptp, text width=2cm, align=center]
-   (metis) {\verb!Metis! \\ Prover};
+   (metis) {\Metis \\ Prover};
 
 \node[right= 1.2cm of metis, text width=2cm, align=center, inner sep=10pt]
-   (tstp) {\verb!TSTP! \\ Derivation};
+   (tstp) {\TSTP \\ Derivation};
 
 \node[below= 0.5cm of tstp, text width=2cm, align=center, inner sep=10pt]
-  (athena) {\verb!Haskell! \\ Traslator};
+  (athena) {\Haskell \\ Traslator};
 
 \node[left = 1.2cm of athena, text width=2cm, align=center]
-   (agdafile) {\verb!Agda! \\ Proof};
+   (agdafile) {\Agda \\ Proof};
 
@@
 
-\verb!Agda! is an interactive system for constructing proofs and programs,
+\Agda is an interactive system for constructing proofs and programs,
 based on Martin-L\"{o}f's type theory and extended with records, parametrised
 modules, among other features.
-One of the main strengths of \verb!Agda! is its support for writing proofs,
-which we shall call \verb!Agda!'s proof engine. It consists of: support for
+One of the main strengths of \Agda is its support for writing proofs,
+which we shall call \Agda's proof engine. It consists of: support for
 inductively defined types, including inductive families, and function
@@
 The inductive approach for representing classical propositional logic
-is better because we benefit from \verb!Agda!'s proof engine and its Unicode
+is better because we benefit from \Agda's proof engine and its Unicode
 support that allows us writing proofs similar as we find in math text books.
@@
 
-\subsection{LCF-Style Theorem Proving}
-\label{ssec:lcf-style-theormem-proving}
+% \subsection{LCF-Style Theorem Proving}
+% \label{ssec:lcf-style-theormem-proving}
 
-A propositional formula is a experssion of indivisible propositional atoms,
-logical connectives $\{\wedge, \vee, \Rightarrow, \Leftrightarrow, \neg\}$
-and logic constants $\{\top, \bot\}$.
-In \verb!Agda!, we define the formula
-as an inductive type using the keyword \texttt{data} and including every
-connective as a constructor. We represent propositional formulas with
-\verb!Prop! data type using the following definition.
+% A propositional formula is a experssion of indivisible propositional atoms,
+% logical connectives $\{\wedge, \vee, \Rightarrow, \Leftrightarrow, \neg\}$
+% and logic constants $\{\top, \bot\}$.
+% In \Agda, we define the formula
+% as an inductive type using the keyword \texttt{data} and including every
+% connective as a constructor. We represent propositional formulas with
+% \name{Prop} data type using the following definition.
 
-%an extension of the syntax definition used in \cite{Altenkirch2015}.
+% %an extension of the syntax definition used in \cite{Altenkirch2015}.
 
-\begin{verbatim}
-data Prop : Set where
-  Var              : Fin n → Prop
-  ⊤                : Prop
-  ⊥                : Prop
-  _∧_ _∨_ _⇒_ _⇔_  : (φ ψ : Prop) → Prop
-  ¬_               : (φ : Prop)   → Prop
-\end{verbatim}
+% \begin{verbatim}
+% data Prop : Set where
+%   Var              : Fin n → Prop
+%   ⊤                : Prop
+%   ⊥                : Prop
+%   _∧_ _∨_ _⇒_ _⇔_  : (φ ψ : Prop) → Prop
+%   ¬_               : (φ : Prop)   → Prop
+% \end{verbatim}
 
-On the other hand, we represent theorems in CPL using an abstract data type
-to implement a natural deduction calculus.
+% On the other hand, we represent theorems in\CPLusing an abstract data type
+% to implement a natural deduction calculus.
 
-\begin{verbatim}
-data _⊢_ : (Γ : Ctxt)(φ : Prop) → Set where
-\end{verbatim}
+% \begin{verbatim}
+% data _⊢_ : (Γ : Ctxt)(φ : Prop) → Set where
+% \end{verbatim}
 
-The sequents  $\Gamma \vdash \phi$ represent theorems,
-where $\Gamma$ is a set of premises and $\phi$ is the
-sequent's conclusion. Strictly speaking, we define the set of premises
-$\Gamma$ with \verb!List! data type
-% \footnote{We use the \verb!Agda! standard library's implementation of the List data type.}.
+% The sequents  $\Gamma \vdash \phi$ represent theorems,
+% where $\Gamma$ is a set of premises and $\phi$ is the
+% sequent's conclusion. Strictly speaking, we define the set of premises
+% $\Gamma$ with \name{List} data type
+% % \footnote{We use the \Agda standard library's implementation of the List data type.}.
 
-Our CPL system define all inference rules for intuitonistic propositional logic
-(see Fig.~\ref{fig:theorem-constructors}) as constructors of the theorem
-data type, and we postulate the principle of the excluded middle (PEM).
+% Our\CPLsystem define all inference rules for intuitonistic propositional logic
+% (see Fig.~\ref{fig:theorem-constructors}) as constructors of the theorem
+% data type, and we postulate the principle of the excluded middle (PEM).
 
-\begin{verbatim}
-postulate  PEM : ∀ {Γ} {φ} → Γ ⊢ φ ∨ ¬ φ
-\end{verbatim}
+% \begin{verbatim}
+% postulate  PEM : ∀ {Γ} {φ} → Γ ⊢ φ ∨ ¬ φ
+% \end{verbatim}
 
-\begin{figure}
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{}
-\RightLabel{\scriptsize\tt assume $\varphi$}
-\UnaryInfC{$\Gamma , \varphi \vdash \varphi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt weaken $\psi$}
-\UnaryInfC{$\Gamma , \psi \vdash \varphi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{}
-\RightLabel{\scriptsize\tt $\top$-intro}
-\UnaryInfC{$\Gamma \vdash \top$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \bot$}
-\RightLabel{\scriptsize\tt $\bot$-elim $\varphi$}
-\UnaryInfC{$\Gamma \vdash \varphi$}
-\end{bprooftree}
-%}
-\]
+% \begin{figure}
+% \[%\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{}
+% \RightLabel{\scriptsize\tt assume $\varphi$}
+% \UnaryInfC{$\Gamma , \varphi \vdash \varphi$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi$}
+% \RightLabel{\scriptsize\tt weaken $\psi$}
+% \UnaryInfC{$\Gamma , \psi \vdash \varphi$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{}
+% \RightLabel{\scriptsize\tt $\top$-intro}
+% \UnaryInfC{$\Gamma \vdash \top$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \bot$}
+% \RightLabel{\scriptsize\tt $\bot$-elim $\varphi$}
+% \UnaryInfC{$\Gamma \vdash \varphi$}
+% \end{bprooftree}
+% %}
+% \]
 
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma , \varphi \vdash \bot$}
-\RightLabel{\scriptsize\tt $\neg$-intro}
-\UnaryInfC{$\Gamma \vdash \neg \varphi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg \varphi$}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\neg$-elim}
-\BinaryInfC{$\Gamma \vdash \bot$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\AxiomC{$\Gamma \vdash \psi$}
-\RightLabel{\scriptsize\tt $\wedge$-intro}
-\BinaryInfC{$\Gamma \vdash \varphi \wedge \psi$}
-\end{bprooftree}
-%}
-\]
+% \[%\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma , \varphi \vdash \bot$}
+% \RightLabel{\scriptsize\tt $\neg$-intro}
+% \UnaryInfC{$\Gamma \vdash \neg \varphi$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \neg \varphi$}
+% \AxiomC{$\Gamma \vdash \varphi$}
+% \RightLabel{\scriptsize\tt $\neg$-elim}
+% \BinaryInfC{$\Gamma \vdash \bot$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi$}
+% \AxiomC{$\Gamma \vdash \psi$}
+% \RightLabel{\scriptsize\tt $\wedge$-intro}
+% \BinaryInfC{$\Gamma \vdash \varphi \wedge \psi$}
+% \end{bprooftree}
+% %}
+% \]
 
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
-\RightLabel{\scriptsize\tt $\wedge$-proj$_1$}
-\UnaryInfC{$\Gamma\vdash \varphi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
-\RightLabel{\scriptsize\tt $\wedge$-proj$_2$}
-\UnaryInfC{$\Gamma\vdash \psi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\vee$-intro$_1$ $\psi$}
-\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
-\end{bprooftree}
-%}
-\]
+% \[%\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
+% \RightLabel{\scriptsize\tt $\wedge$-proj$_1$}
+% \UnaryInfC{$\Gamma\vdash \varphi$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
+% \RightLabel{\scriptsize\tt $\wedge$-proj$_2$}
+% \UnaryInfC{$\Gamma\vdash \psi$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi$}
+% \RightLabel{\scriptsize\tt $\vee$-intro$_1$ $\psi$}
+% \UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
+% \end{bprooftree}
+% %}
+% \]
 
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \psi$}
-\RightLabel{\scriptsize\tt $\vee$-intro$_2$ $\varphi$}
-\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma ,\varphi \vdash \gamma $}
-\AxiomC{$\Gamma , \psi  \vdash \gamma$}
-\RightLabel{\scriptsize\tt $\vee$-elim}
-\BinaryInfC{$\Gamma , \varphi \vee \psi \vdash \gamma$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma , \varphi \vdash \psi$}
-\RightLabel{\scriptsize\tt $\Rightarrow$-intro}
-\UnaryInfC{$\Gamma \vdash \varphi \Rightarrow \psi$}
-\end{bprooftree}
-%}
-\]
+% \[%\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \psi$}
+% \RightLabel{\scriptsize\tt $\vee$-intro$_2$ $\varphi$}
+% \UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma ,\varphi \vdash \gamma $}
+% \AxiomC{$\Gamma , \psi  \vdash \gamma$}
+% \RightLabel{\scriptsize\tt $\vee$-elim}
+% \BinaryInfC{$\Gamma , \varphi \vee \psi \vdash \gamma$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma , \varphi \vdash \psi$}
+% \RightLabel{\scriptsize\tt $\Rightarrow$-intro}
+% \UnaryInfC{$\Gamma \vdash \varphi \Rightarrow \psi$}
+% \end{bprooftree}
+% %}
+% \]
 
-\[
-%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\Rightarrow$-elim}
-\BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma , \varphi \vdash \psi$}
-\AxiomC{$\Gamma , \psi \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\Leftrightarrow$-intro}
-\BinaryInfC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
-\end{bprooftree}
-%}
-\]
+% \[
+% %\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
+% \AxiomC{$\Gamma \vdash \varphi$}
+% \RightLabel{\scriptsize\tt $\Rightarrow$-elim}
+% \BinaryInfC{$\Gamma \vdash \psi$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma , \varphi \vdash \psi$}
+% \AxiomC{$\Gamma , \psi \vdash \varphi$}
+% \RightLabel{\scriptsize\tt $\Leftrightarrow$-intro}
+% \BinaryInfC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
+% \end{bprooftree}
+% %}
+% \]
 
-\[
-%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
-\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_1$}
-\BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
-\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_2$}
-\BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}
-%}
-\]
+% \[
+% %\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi$}
+% \AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
+% \RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_1$}
+% \BinaryInfC{$\Gamma \vdash \psi$}
+% \end{bprooftree}\quad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi$}
+% \AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
+% \RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_2$}
+% \BinaryInfC{$\Gamma \vdash \psi$}
+% \end{bprooftree}
+% %}
+% \]
 
-\caption{Inference rules for CPL system.}
-\label{fig:theorem-constructors}
-\end{figure}
+% \caption{Inference rules for\CPLsystem.}
+% \label{fig:theorem-constructors}
+% \end{figure}
 
-% ---------------------------------------------------------------------------
+% % ---------------------------------------------------------------------------
 
-% ---------------------------------------------------------------------------
+% % ---------------------------------------------------------------------------
 
-\subsection{Emulation of Inference Rules in Agda}
-\label{ssec:emulating-inferences}
+% \subsection{Emulation of Inference Rules in Agda}
+% \label{ssec:emulating-inferences}
 
-\textit{Normalization.}
+% \textit{Normalization.}
 
-\begin{figure}
-\[ \scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi$}
+% \begin{figure}
+% \[ \scalebox{0.9}{
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi$}
 
-  \UnaryInfC{$\Gamma \vdash \texttt{cnf}~\varphi$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi$}
-  \UnaryInfC{$\Gamma \vdash \texttt{nnf}~\varphi$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi$}
-  \UnaryInfC{$\Gamma \vdash \texttt{dnf}~\varphi$}
-\end{bprooftree}
-}\]
-\end{figure}
+%   \UnaryInfC{$\Gamma \vdash \texttt{cnf}~\varphi$}
+% \end{bprooftree}
+% \qquad
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi$}
+%   \UnaryInfC{$\Gamma \vdash \texttt{nnf}~\varphi$}
+% \end{bprooftree}
+% \qquad
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi$}
+%   \UnaryInfC{$\Gamma \vdash \texttt{dnf}~\varphi$}
+% \end{bprooftree}
+% }\]
+% \end{figure}
 
-\begin{figure}
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \wedge \bot$}
-  \UnaryInfC{$\Gamma \vdash \bot$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \wedge \top$}
-  \UnaryInfC{$\Gamma \vdash \varphi$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \wedge \neg \varphi$}
-  \UnaryInfC{$\Gamma \vdash \bot$}
-\end{bprooftree}
-%}
-\]
+% \begin{figure}
+% \[%\scalebox{0.9}{
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi \wedge \bot$}
+%   \UnaryInfC{$\Gamma \vdash \bot$}
+% \end{bprooftree}
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi \wedge \top$}
+%   \UnaryInfC{$\Gamma \vdash \varphi$}
+% \end{bprooftree}
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi \wedge \neg \varphi$}
+%   \UnaryInfC{$\Gamma \vdash \bot$}
+% \end{bprooftree}
+% %}
+% \]
 
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \vee \bot$}
-  \UnaryInfC{$\Gamma \vdash \varphi$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \vee \top$}
-  \UnaryInfC{$\Gamma \vdash \top$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \vee \neg \varphi$}
-  \UnaryInfC{$\Gamma \vdash \top$}
-\end{bprooftree}
-%}
-\]
-\end{figure}
+% \[%\scalebox{0.9}{
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi \vee \bot$}
+%   \UnaryInfC{$\Gamma \vdash \varphi$}
+% \end{bprooftree}
+% \qquad
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi \vee \top$}
+%   \UnaryInfC{$\Gamma \vdash \top$}
+% \end{bprooftree}
+% \qquad
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi \vee \neg \varphi$}
+%   \UnaryInfC{$\Gamma \vdash \top$}
+% \end{bprooftree}
+% %}
+% \]
+% \end{figure}
 
-\textit{Resolution.}
+% \textit{Resolution.}
 
-\begin{figure}
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\delta_{\phi} := \Gamma \vdash \varphi$}
-\AxiomC{$\delta_{\psi} := \Gamma \vdash \psi$}
-\RightLabel{\texttt{resolve} $p$}
-\BinaryInfC{$\Gamma \vdash$ \texttt{resolve} $\phi\ \psi\ p$}
-\end{bprooftree}
-%}
-\]
-% \caption{Resolution in \verb!Metis!.}
-\label{fig:resolution-rule}
-\end{figure}
+% \begin{figure}
+% \[%\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\delta_{\phi} := \Gamma \vdash \varphi$}
+% \AxiomC{$\delta_{\psi} := \Gamma \vdash \psi$}
+% \RightLabel{\texttt{resolve} $p$}
+% \BinaryInfC{$\Gamma \vdash$ \texttt{resolve} $\phi\ \psi\ p$}
+% \end{bprooftree}
+% %}
+% \]
+% % \caption{Resolution in \Metis.}
+% \label{fig:resolution-rule}
+% \end{figure}
 
-\textit{Splitting a conjunct.}
-In the following theorem, we see the definition for the \verb!conjunct! rule.
-It extracts the $\varphi_i$ conjunct from the conjunction given by $\varphi$.
+% \textit{Splitting a conjunct.}
+% In the following theorem, we see the definition for the \name{conjunct} rule.
+% It extracts the $\varphi_i$ conjunct from the conjunction given by $\varphi$.
 
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi := \varphi_1 \wedge \cdots\wedge\varphi_i
-\wedge\cdots\wedge \varphi_n$}
-\AxiomC{$\varphi_i \equiv \psi$}
-\RightLabel{\footnotesize\tt conjunct $\psi$}
-\BinaryInfC{$\Gamma\vdash\varphi_i$}
-\end{bprooftree}
-}
-\]
+% \[\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi := \varphi_1 \wedge \cdots\wedge\varphi_i
+% \wedge\cdots\wedge \varphi_n$}
+% \AxiomC{$\varphi_i \equiv \psi$}
+% \RightLabel{\footnotesize\tt conjunct $\psi$}
+% \BinaryInfC{$\Gamma\vdash\varphi_i$}
+% \end{bprooftree}
+% }
+% \]
 
-\textit{Splitting a goal}
+% \textit{Splitting a goal}
 
-\begin{figure}
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi_1 \wedge \varphi_2$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi_1) \wedge \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
-\end{bprooftree}
-}\]
+% \begin{figure}
+% \[\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi_1 \wedge \varphi_2$}
+% \UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi_1) \wedge \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
+% \end{bprooftree}
+% }\]
 
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi_1 \vee \varphi_2$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\neg \varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
-\end{bprooftree}
-}\]
+% \[\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi_1 \vee \varphi_2$}
+% \UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\neg \varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
+% \end{bprooftree}
+% }\]
 
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi_1 \Rightarrow \varphi_2$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg \neg \varphi$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi)$}
-\end{bprooftree}
-}\]
+% \[\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \varphi_1 \Rightarrow \varphi_2$}
+% \UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
+% \end{bprooftree}\qquad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \neg \neg \varphi$}
+% \UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi)$}
+% \end{bprooftree}
+% }\]
 
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$ \Gamma \vdash \varphi_1 \Leftrightarrow \varphi_2$}
-\UnaryInfC{$\Gamma\vdash\texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2) \wedge \texttt{unshunt}~(\varphi_2 \Rightarrow \texttt{split}~\varphi_1)$}
-\end{bprooftree}
-}\]
+% \[\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$ \Gamma \vdash \varphi_1 \Leftrightarrow \varphi_2$}
+% \UnaryInfC{$\Gamma\vdash\texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2) \wedge \texttt{unshunt}~(\varphi_2 \Rightarrow \texttt{split}~\varphi_1)$}
+% \end{bprooftree}
+% }\]
 
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg \top$}
-\UnaryInfC{$\Gamma \vdash \bot$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg \bot$}
-\UnaryInfC{$\Gamma \vdash \top$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg (\varphi_1 \wedge \varphi_2)$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt} (\varphi_1 \Rightarrow \texttt{split}~ \neg \varphi_2)$}
-\end{bprooftree}
-}\]
+% \[\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \neg \top$}
+% \UnaryInfC{$\Gamma \vdash \bot$}
+% \end{bprooftree}\qquad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \neg \bot$}
+% \UnaryInfC{$\Gamma \vdash \top$}
+% \end{bprooftree}\qquad
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \neg (\varphi_1 \wedge \varphi_2)$}
+% \UnaryInfC{$\Gamma \vdash \texttt{unshunt} (\varphi_1 \Rightarrow \texttt{split}~ \neg \varphi_2)$}
+% \end{bprooftree}
+% }\]
 
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg (\varphi_1 \vee \varphi_2)$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\neg \varphi_1) \wedge  \texttt{unshunt}~(\neg \varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2)$}
-\end{bprooftree}
-}\]
+% \[\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \neg (\varphi_1 \vee \varphi_2)$}
+% \UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\neg \varphi_1) \wedge  \texttt{unshunt}~(\neg \varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2)$}
+% \end{bprooftree}
+% }\]
 
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg (\varphi_1 \Rightarrow \varphi_2)$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi_1) \wedge \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2)$}
-\end{bprooftree}\qquad
-}\]
+% \[\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \neg (\varphi_1 \Rightarrow \varphi_2)$}
+% \UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi_1) \wedge \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2)$}
+% \end{bprooftree}\qquad
+% }\]
 
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg (\varphi_1 \Leftrightarrow \varphi_2)$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2) \wedge \texttt{unshunt}~(\neg \varphi_2 \Rightarrow \texttt{split}~\varphi_1)$}
-\end{bprooftree}
-}\]
-\caption{Split a goal in an equivalent conjunction of subgoals.}
-\label{split}
-\end{figure}
+% \[\scalebox{0.9}{
+% \begin{bprooftree}
+% \AxiomC{$\Gamma \vdash \neg (\varphi_1 \Leftrightarrow \varphi_2)$}
+% \UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2) \wedge \texttt{unshunt}~(\neg \varphi_2 \Rightarrow \texttt{split}~\varphi_1)$}
+% \end{bprooftree}
+% }\]
+% \caption{Split a goal in an equivalent conjunction of subgoals.}
+% \label{split}
+% \end{figure}
 
-In the theorems above appear two recursive functions \texttt{unshunt} and \texttt{split}. They have the following definitions.
+% In the theorems above appear two recursive functions \texttt{unshunt} and \texttt{split}. They have the following definitions.
 
-\begin{verbatim}
-unshunt : Prop → Prop
-unshunt (φ₁ ⇒ (φ₂ ⇒ φ₃)) = unshunt ((φ₁ ∧ φ₂) ⇒ φ₃)
-unshunt (φ₁ ⇒ (φ₂ ∧ φ₃)) = unshunt (φ₁ ⇒ φ₂)) ∧ (unshunt(φ₁ ⇒ φ₃)
-unshunt φ                = φ
-\end{verbatim}
+% \begin{verbatim}
+% unshunt : Prop → Prop
+% unshunt (φ₁ ⇒ (φ₂ ⇒ φ₃)) = unshunt ((φ₁ ∧ φ₂) ⇒ φ₃)
+% unshunt (φ₁ ⇒ (φ₂ ∧ φ₃)) = unshunt (φ₁ ⇒ φ₂)) ∧ (unshunt(φ₁ ⇒ φ₃)
+% unshunt φ                = φ
+% \end{verbatim}
 
-\begin{verbatim}
-split : Prop → Prop
-split (φ₁ ∧ φ₂)     = {!!}
-split (φ₁ ∨ φ₂)     = {!!}
-split (φ₁ ⇒ φ₂)     = {!!}
-split (φ₁ ⇔ φ₂)     = {!!}
-split (¬ ⊤)         = {!!}
-split (¬ ⊥)         = {!!}
-split (¬ (φ₁ ∧ φ₂)) = {!!}
-split (¬ (φ₁ ∨ φ₂)) = {!!}
-split (¬ (φ₁ ⇒ φ₂)) = {!!}
-split (¬ (φ₁ ⇔ φ₂)) = {!!}
-split (¬ (¬ φ))     = {!!}
-split φ₁            = {!!}
-\end{verbatim}
+% \begin{verbatim}
+% split : Prop → Prop
+% split (φ₁ ∧ φ₂)     = {!!}
+% split (φ₁ ∨ φ₂)     = {!!}
+% split (φ₁ ⇒ φ₂)     = {!!}
+% split (φ₁ ⇔ φ₂)     = {!!}
+% split (¬ ⊤)         = {!!}
+% split (¬ ⊥)         = {!!}
+% split (¬ (φ₁ ∧ φ₂)) = {!!}
+% split (¬ (φ₁ ∨ φ₂)) = {!!}
+% split (¬ (φ₁ ⇒ φ₂)) = {!!}
+% split (¬ (φ₁ ⇔ φ₂)) = {!!}
+% split (¬ (¬ φ))     = {!!}
+% split φ₁            = {!!}
+% \end{verbatim}
 
-...
+% ...
 
-\textit{Simplification.}
+% \textit{Simplification.}
 
-\begin{figure}
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
-  \AxiomC{$\Gamma \vdash \psi$}
-  \RightLabel{\footnotesize\tt $\Leftrightarrow$-elim}
-  \BinaryInfC{$\Gamma \vdash \varphi$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
-  \AxiomC{$\Gamma \vdash \varphi$}
-  \RightLabel{\footnotesize\tt $\Rightarrow$-elim}
-  \BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}
-\]
-\[
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \vee \neg \psi$}
-  \AxiomC{$\Gamma \vdash \neg \varphi$}
-  \BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}
-%}
-\]
+% \begin{figure}
+% \[%\scalebox{0.9}{
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
+%   \AxiomC{$\Gamma \vdash \psi$}
+%   \RightLabel{\footnotesize\tt $\Leftrightarrow$-elim}
+%   \BinaryInfC{$\Gamma \vdash \varphi$}
+% \end{bprooftree}
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
+%   \AxiomC{$\Gamma \vdash \varphi$}
+%   \RightLabel{\footnotesize\tt $\Rightarrow$-elim}
+%   \BinaryInfC{$\Gamma \vdash \psi$}
+% \end{bprooftree}
+% \]
+% \[
+% \begin{bprooftree}
+%   \AxiomC{$\Gamma \vdash \varphi \vee \neg \psi$}
+%   \AxiomC{$\Gamma \vdash \neg \varphi$}
+%   \BinaryInfC{$\Gamma \vdash \psi$}
+% \end{bprooftree}
+% %}
+% \]
 
-\caption{Additional simplification theorems.}
-\label{fig:simplify-rule}
-\end{figure}
+% \caption{Additional simplification theorems.}
+% \label{fig:simplify-rule}
+% \end{figure}
 

### 2017-09-05 paper/sections/related-work.tex
[ paper ] new commands for programs and langs.

@@
 
-\verb!Sledgehammer! is a tool for \verb!Isabelle! proof assistant
+\name{Sledgehammer} is a tool for \name{Isabelle} proof assistant
 ~\cite{paulson1994isabelle} that provides a full integration of automatic
@@
 (see, for example, \cite{meng2006automation}, \cite{blanchette2013extending}
-and \cite{Fleury2014}) and SMT solvers (see, for instance,
+and \cite{Fleury2014}) and\SMTsolvers (see, for instance,
 \cite{hurlin07practical}, \cite{bohme2010},
 \cite{blanchette2013extending}, and \cite{Fleury2014}) with
-\verb!Isabelle/HOL! \cite{nipkow2002isabelle}, the specialization of
-\verb!Isabelle! for higher-order logic. Sultana, Benzm{\"{u}}ller, and
-Paulson~\cite{Een2004} integrates \verb!Leo-II! and \verb!Satallax!, two
-theorem provers for high-order logic with \verb!Isabelle/HOL! proposing a
+\name{Isabelle/HOL} \cite{nipkow2002isabelle}, the specialization of
+\name{Isabelle} for higher-order logic. Sultana, Benzm{\"{u}}ller, and
+Paulson~\cite{Een2004} integrates \name{Leo-II} and \name{Satallax}, two
+theorem provers for high-order logic with \name{Isabelle/HOL} proposing a
 modular proof reconstruction work flow.
 
-\verb!SMTCoq!~\cite{armand2011,Ekici2017} is a tool for the \verb!Coq!
+\name{SMTCoq}~\cite{armand2011,Ekici2017} is a tool for the \name{Coq}
 proof assistant \cite{coqteam} which provides a certified checker for
-proof witness coming from the SMT solver \verb!veriT! \cite{bouton2009}
-and adds a new tactic named verit, that calls \verb!veriT! on any
-\verb!Coq! goal. In \cite{bezem2002automated}, given a fixed but arbitrary
+proof witness coming from the\SMTsolver \name{veriT} \cite{bouton2009}
+and adds a new tactic named verit, that calls \name{veriT} on any
+\name{Coq} goal. In \cite{bezem2002automated}, given a fixed but arbitrary
 first-order signature, the authors transform a proof produced by the
-first-order automatic theorem prover \verb!Bliksem! \cite{deNivelle2003}
-in a \verb!Coq! proof term.
+first-order automatic theorem prover \name{Bliksem} \cite{deNivelle2003}
+in a \name{Coq} proof term.
 
 Hurd~\cite{Hurd1999} integrates the first-order resolution prover
-\verb!Gandalf! with \verb!HOL!~\cite{norrish2007hol}, a high-order theorem
+\name{Gandalf} with \name{HOL}~\cite{norrish2007hol}, a high-order theorem
 prover, following an LCF model implementing the tactic \verb!GANDALF_TAC!.
-For \verb!HOL Light!, a version of \verb!HOL! but with a simpler logic core,
-the SMT solver \verb!CVC4! was integrated, and Kaliszyk and
+For \name{HOL Light}, a version of \name{HOL} but with a simpler logic core,
+the\SMTsolver \name{CVC4} was integrated, and Kaliszyk and
 Urban~\cite{kaliszyk2013} reconstruct proofs from different ATPs with their
-\verb!PRocH! tool, replaying the detailed inference steps from the ATPs with
-internal inference methods implemented in \verb!HOL Light!.
+\name{PRocH} tool, replaying the detailed inference steps from the ATPs with
+internal inference methods implemented in \name{HOL Light}.
 
@@
 
-\verb!Waldmeister! is an automatic theorem prover for unit equational
+\name{Waldmeister} is an automatic theorem prover for unit equational
 logic \cite{hillenbrand1997}.
-Foster and Struth~\cite{foster2011integrating} integrate \verb!Waldmeister! into
-\verb!Agda!~\cite{agdateam}. This integration requires a proof
+Foster and Struth~\cite{foster2011integrating} integrate \name{Waldmeister} into
+\Agda~\cite{agdateam}. This integration requires a proof
 reconstruction step, but authors' approach is restricted to pure
@@
 
-Kanso and Setzer~\cite{kanso2016light} integrate \verb!Z3! in \verb!Agda!
-but they also integrate the propositional fragment of the \verb!E! prover in
+Kanso and Setzer~\cite{kanso2016light} integrate \name{Z3} in \Agda
+but they also integrate the propositional fragment of the \name{E} prover in
 \cite{Kanso2012}. They cataloged these two integration as
 \emph{Oracle and Reflection} and \emph{Oracle and Justification}, respectively.
-Their integration with the \verb!E! prover is the most related work with our
+Their integration with the \name{E} prover is the most related work with our
 apporach found at the moment while we write this document. Besides the use

### 2017-09-05 paper/sections/introduction.tex
minor changes.

@@
 
-A proof reconstruction tool provides such an integration in one direction,
-is a translator of the reply delivered by the prover into the formalism of
+A proof reconstruction tool provides such an integration translating 
+the reply delivered by the prover into the formalism of
 the proof assistant. Because the formalism of the source (the evidence

### 2017-09-05 paper/sections/related-work.tex
minor changes.

@@
 ~\cite{paulson1994isabelle} that provides a full integration of automatic
-theorem provers including ATPs
+theorem provers including \ATPs
 (see, for example, \cite{meng2006automation}, \cite{blanchette2013extending}
-and \cite{Fleury2014}) and\SMTsolvers (see, for instance,
+and \cite{Fleury2014}) and \SMT solvers (see, for instance,
 \cite{hurlin07practical}, \cite{bohme2010},
@@
 proof assistant \cite{coqteam} which provides a certified checker for
-proof witness coming from the\SMTsolver \name{veriT} \cite{bouton2009}
+proof witness coming from the \SMT solver \name{veriT} \cite{bouton2009}
 and adds a new tactic named verit, that calls \name{veriT} on any
@@
 \name{Gandalf} with \name{HOL}~\cite{norrish2007hol}, a high-order theorem
-prover, following an LCF model implementing the tactic \verb!GANDALF_TAC!.
+prover, following an \abbre{LCF} model implementing the tactic \verb!GANDALF_TAC!.
 For \name{HOL Light}, a version of \name{HOL} but with a simpler logic core,
-the\SMTsolver \name{CVC4} was integrated, and Kaliszyk and
+the \SMT solver \name{CVC4} was integrated, and Kaliszyk and
 Urban~\cite{kaliszyk2013} reconstruct proofs from different ATPs with their
@@
 Their integration with the \name{E} prover is the most related work with our
-apporach found at the moment while we write this document. Besides the use
-of the same ITP, crucial differences easily arise like decidability of
+approach found at the moment while we write this document. Besides the use
+of the same \ITP, crucial differences easily arise like decidability of
 propositional logic using semantics that we do not take into account for the

### 2017-09-06 paper/sections/metis-language-and-proofs.tex
[ paper ] section 2 improvements.

@@
 The \TPTP syntax describes a well-defined grammar to handle annotated
-formulas with the following form
+formulas with the following form,
 
@@
 \name{definition}, or a \name{hypothesis}. The formulas include Boolean
-connectives (\verb!&!, \verb!|!, \verb!=>!, \verb!{<=>!, $\tt\sim$) and logic
+connectives (\verb!&!, \verb!|!, \verb!=>!, \verb!{<=>!, \verb!~!) and logic
 constants \verb!$true! and \verb!$false!.
@@
 $p\, \vdash \neg (p \wedge \neg p) \vee (q \vee \neg q)$
-in \TPTP syntax as follows.
+in \TPTP syntax as follows, declaring an \tptpaxiom $p$, and the expected
+conclusion, the  \tptpconjecture \verb!~ ((p & ~ p) | (q & ~ q))!.
 
@@
 formulas. The root is the final derived formula. Such a derivation is a list of
-annotated formulas with the form
+annotated formulas with the form,
 
@@
 
-The \name{source} field is an inference record with the following pattern
+The \name{source} field is an inference record with the following pattern,
 \begin{verbatim}
@@
 deduction proof. The deduction system uses six inference rules
-\cite{hurd2003first} (see Fig.~\ref{fig:metis-inferences}) to attempt to
-prove conjectures by refutation (see. e.g., the last conclusion
-in the \TSTP derivation Fig.~\ref{fig:metis-example} is \emph{falsium}).
+\cite{hurd2003first} listed in Fig.~\ref{fig:metis-inferences}.
+With these inference rules as the only valid deduction steps, \Metis attempts to
+prove conjectures by refutation (see. e.g., \emph{falsium} in the last conclusion
+of the \TSTP derivation in Fig.~\ref{fig:metis-example}).
 
@@
   \AxiomC{}
-  \RightLabel{\scriptsize negate}
+  \RightLabel{\footnotesize negate}
   \UnaryInfC{$\neg p$}
-  \RightLabel{\scriptsize strip}
+  \RightLabel{\footnotesize strip}
   \UnaryInfC{$\neg p$}
   \AxiomC{}
-  \RightLabel{\scriptsize axiom}
+  \RightLabel{\footnotesize axiom}
   \UnaryInfC{$p$}
-  \RightLabel{\scriptsize canonicalize}
+  \RightLabel{\footnotesize canonicalize}
   \UnaryInfC{$p$}
-  \RightLabel{\scriptsize simplify}
+  \RightLabel{\footnotesize simplify}
   \BinaryInfC{$\bot$}
-  \RightLabel{\scriptsize canonicalize}
+  \RightLabel{\footnotesize canonicalize}
   \UnaryInfC{$\bot$}
 \end{bprooftree}
-% \caption{The \Metis' refutation tree for $p \vdash p$ from the
-% derivation in Fig.~\ref{fig:metis-proof-tstp}}
+\caption{The \Metis' refutation tree for $p \vdash p$ from the
+derivation in Fig.~\ref{fig:metis-proof-tstp}}
 \label{fig:metis-example}
@@
 
-Despite the six rules in the \Metis' logic
-kernel (see~Fig. \ref{fig:metis-inferences}), we observed in \TSTP
-derivations for\CPL problems other inference rules.
-They are \canonicalize, \conjunct, \negate, \simplify,
-\strip and \resolve. We briefly review each of these rules
-following no order except maybe by their frequency in the \TSTP derivations.
+We noted in \TSTP derivations that \Metis do not take into account some
+inference rules for the \Metis' official documentation; we refer to
+the \Metis' logic kernel. Besides the figure that shows us the six
+\Metis' inference rules, its proof-objects, the \TSTP derivations,
+exhibit an entirely different set of rules.
+
+For instance, for the propositional logic fragment without equality,
+we know only three rules are valid from the \Metis' Logic Kernel:
+\emph{assume}, \emph{axiom}, and \emph{resolve}.
+Nevertheless, as we observed in \TSTP derivations, for such a propositional
+fragment, \Metis uses in his deductions steps, six rules where only the
+resolve inference persists from the original list. In the case of \resolve,
+it differs from its original version since, in \TSTP,  this rules comes with
+an argument, a literal. The other undocumented rules found in \TSTP
+derivations are: \canonicalize, \clausify, \conjunct, \negate, \simplify,
+and \strip.
+
+This lack of the \Metis' documentation was an important matter for us in the
+proof reconstruction and certainty for other implementors (see a comment
+related on the presenting of \name{Sledgehammer}
+\info{cite here Paulson and Metis Paramodulation' paper}).
+We faced the ambiguity and lack of clearness of some rules like \canonicalize
+or \simplify. For example, we believe that with these last inferences, \Metis
+summarized many essential steps in the conversion or deduction from one formula
+or a list of formulas to another as we show in Example X.
+\unsure{Should I give an Example?}
+That is inconvenient since, our proof reconstruction approach needs take into
+account any assumption or consideration as ordering for literals, application
+of simplification theorems, reductions, among other valid transformations.
+\unsure{Should I give an Example?}
+In this part, our job\improvement{job or purpose?} mainly consists of giving
+a response to these rules looking at the \Metis' source code while inspecting
+a representative set of solutions of \CPL problems generated by \Metis.
+\unsure{Should I mention the Prop-Pack Collection?}
+Therefore, this is an attempt to help and fulfill this difficulty, describing
+our understanding of each rule, to later on in section
+\ref{sec:proof-reconstruction}, formalize them effectively in \Agda.
 
@@
 \]
-% \caption{Some rules of \canonicalize inference.}
+\caption{Defintions of \canonicalize inference.}
 \label{fig:conjunctive-disjunctive-simplification}

### 2017-09-07 paper/main.tex
[ paper ] new commands for programs and langs.
minor changes.
[ paper ] section 2 improvements.
[ paper ] major changes, abstract, conclusions was added.

@@
 \usepackage{xargs}
-\usepackage[pdftex,dvipsnames]{xcolor}
+\usepackage[dvipsnames]{xcolor}
+% \usepackage[pdftex,dvipsnames]{xcolor}
 \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
@@
 % --------------------------------------------------------------------------
+\usepackage{xspace}
 
-\newcommand{\name}{\textsc}
-\newcommand{\Agda}{\name{Agda}}
+\newcommand{\abbre}[1]{\textsc{#1}\xspace}
+\newcommand{\ATP}{\abbre{ATP}}
+\newcommand{\ATPs}{\abbre{ATPs}}
+\newcommand{\SAT}{\abbre{SAT}}
+\newcommand{\SMT}{\abbre{SMT}}
+\newcommand{\ITP}{\abbre{ITP}}
+\newcommand{\CPL}{\abbre{CPL}}
+\newcommand{\CNF}{\abbre{CNF}}
+
+\newcommand{\name}[1]{\texttt{#1}\xspace}
+\newcommand{\canonicalize}{\name{canonicalize}}
+\newcommand{\clausify}{\name{clausify}}
+\newcommand{\conjunct}{\name{conjunct}}
+\newcommand{\negate}{\name{negate}}
+\newcommand{\resolve}{\name{resolve}}
+\newcommand{\simplify}{\name{simplify}}
+\newcommand{\strip}{\name{strip}}
+\newcommand{\tptpaxiom}{\name{axiom}}
+\newcommand{\tptpconjecture}{\name{conjecture}}
+
+\newcommand{\prg}[1]{\texttt{#1}\xspace}
+\newcommand{\Agda}{\prg{Agda}}
+\newcommand{\Metis}{\prg{Metis}}
+\newcommand{\IsabelleHOL}{\prg{IsabelleHOL}}
+
+\newcommand{\len}[1]{\texttt{#1}\xspace}
+\newcommand{\Haskell}{\len{Haskell}}
+\newcommand{\TPTP}{\len{TPTP}}
+\newcommand{\TSTP}{\len{TSTP}}
 
@@
 \title{Towards Proof-Reconstruction of Problems
-in Classical Propositional Logic in Agda}
+in Classical Propositional Logic}
 
@@
 
-\institute{Universidad EAFIT, \emph{School of Sciences and Engineering},\\
-Medell\'in, Colombia\\
-\email{jprieto9,asr@eafit.edu.co}}
+\institute{Universidad EAFIT, Logic and Computation Research Group,\\
+Department of Mathematics, Medell\'in, Colombia\\
+\email{\{jprieto9,asr\}@eafit.edu.co}}
 
@@
 
-\subfile{TODO.tex}
-
 \maketitle
@@
 \subfile{sections/metis-language-and-proofs.tex}
-\subfile{sections/proof-reconstruction.tex}
+% \subfile{sections/proof-reconstruction.tex}
 \subfile{sections/related-work.tex}

### 2017-09-07 paper/sections/abstract.tex
[ paper ] new commands for programs and langs.
[ paper ] major changes, abstract, conclusions was added.

@@
 
-% ============================================================================
+% ===================================================================
 
 \begin{abstract}
-...
-\keywords{Proof reconstruction, Agda, Automatic theorem prover,
-  Classical Propositional Logic, Metis }
+In this paper, we describe our approach to reconstruct and verify in
+\Agda, a  proof assistant,  solutions obtained by \Metis, an
+automatic theorem prover, to problems in classical propositional
+logic. The translation method consists of justifying step-by-step
+each deduction found in the prover's solution. To carry out this
+plan, we emulate the inference rules of the prover, providing a
+version of them in the proof assistant. Finally, we parse the output
+of the prover,  constructing the respective tree associated with the
+proof, ending up with an \Agda code for type-checking.
+
+\keywords{proof reconstruction, \Agda, automatic theorem prover, classical propositional logic, \Metis.}
 \end{abstract}

### 2017-09-07 paper/sections/acknowledgements.tex
[ paper ] new commands for programs and langs.
[ paper ] major changes, abstract, conclusions was added.

@@
 
-% ============================================================================
+% ===================================================================
 
@@
 
-We thank Universidad EAFIT of Medell\'in, Colombia for funding support.
-This project was a product of the Logic and Computation Research
-Group at the Universidad EAFIT.
-%This is part of first author's Master thesis in Applied Mathematics, written under the
-% supervision of Andr\'es Sicard-Ram\'irez for the Logic and Computation Research
-% Group at the Universidad EAFIT.
+We thank Universidad EAFIT of Medell\'in, Colombia for funding
+support. This project was a product of the Logic and Computation
+Research Group at the Universidad EAFIT.
 
-We thank Joe Leslie-Hurd for all support with \verb!Metis! prover.
-We also acknowledge the work carried out by Alejandro G\'omez-Londo\~no~
-\cite{Gomez-Londono2015} used as the basis code for our TSTP parsing
-module.
-And last but not least, we thankfully acknowledge Andreas Abel and Chalmers
-University of Goteborg, Sweden for inviting us to be part of the Agda
-Implementors’ Meeting XXV where we presented part of this paper.
+We thank Joe Leslie-Hurd for his support with \Metis prover. We also
+acknowledge the work carried out by Alejandro G\'omez-Londo\~no~
+\cite{Gomez-Londono2015} used as the basis code for our \TSTP
+parsing module.
+\improvement{We should consider thank Kanso and Anton, to provide us
+their thesis, discussion, and source code to compare with our work?}
+
+Last but not least, we thankfully acknowledge
+Andreas Abel and Chalmers University of Goteborg, Sweden for
+inviting us to be part of the \Agda Implementors’ Meeting XXV where
+we presented part of this paper.
 

### 2017-09-07 paper/sections/conclusions.tex
[ paper ] major changes, abstract, conclusions was added.

@@
 
-Amazing conclusions.
-...
-\cite{}
+Besides our scope in this document, propositional logic without
+equality, is straightforward compared with other logics like
+first-order or high-order logic; the proof reconstruction task is
+far from trivial. Depending on the systems involved in the
+translation, some difficulties can arise. We listed some of them in
+section \ref{sec:metis-language-and-proofs} and section
+\ref{sec:proof-reconstruction}.
 
-\subsubsection*{Future Work.}
-\label{ssec:future-work}
+For instance, just showing equality between Normal Forms for the
+same formula in the output of the \canonicalize inference and a
+common implementation for this kind of conversion; we observed that
+\Metis performs reordering for each expression mainly in the
+presence of negative literals. Another example was the \Metis'
+convention for conjunctions and disjunction as right associative and
+binary operators in the \TSTP format. We had to update the \TSTP
+parser module introduced in \cite{Gomez-Londono2015} to include some
+feature like this.
+
+However, we believe one of our biggest obstacles was dealing with
+the Equality between formulas since, in our approach, we only work
+with the syntactic treatment of the logic without considering the
+semantics. One of the main reasons for such a restriction resides in
+our plans to support further first-order logic where a semantic
+treatment is not viable.\unsure{Please confirm this assumption.}
+
+Nevertheless, the proof reconstruction is certainly possible, and
+the verification of solutions of \CPL problems can be carried out
+successful in \Agda. Our tool is capable of translating \Metis
+derivations in \TSTP format to deliver \Agda code of the proof, and
+this proof can be type-checked by \Agda.
+
+We believe the source code of our tool can be extended to support
+other \ATPs for \CPL like \name{E}. For example, we incorporate the
+inferences rules of \name{E} or \name{Z3} from the description in
+Kanso's Thesis~\cite{Kanso2012}.
+
+Trying to justify output from a theorem prover has a real impact,
+increasing the trustworthy of the prover. For instance, we found a
+soundness bug, a bug in the printing out of the \TSTP derivations,
+and a bug in the parsing for \TPTP problem in \Metis.
+Fortunately, all these bugs were fixed quickly by Hurd\footnote{
+Issues No. 4, No. 2, and the commit \name{8a3f11e} from the
+\Metis' official repository \url{https://github.com/gilith/metis}},
+and a new version of \Metis was released
+(version 2.3, release 20170810).
+
+% \subsubsection*{Future Work.}
+% \label{ssec:future-work}
 

### 2017-09-07 paper/sections/introduction.tex
[ paper ] major changes, abstract, conclusions was added.

@@
 
-Proof reconstruction is a hard labor since it depends on the integration
-of two complex systems. On the one hand, we have the automatic theorem provers
-(henceforth \ATP) and their specification logic. These tools are usually
-classified in at least one of the following categories. A \SAT solver
-(e.g., \name{zChaff}~\cite{Moskewicz2001} and \name{MiniSat}~\cite{Een2004})
-to prove unsatisfiability of \CNF formulas, a \abbre{QBF} solver
-(e.g., \name{GhostQ}~\cite{Klieber2014} and \name{DepQBF}~\cite{Lonsing2017})
-to prove satisfiability and invalidity of quantified Boolean formulas, a \SMT
-solver (e.g \name{CVC4}~\cite{Barrett2011}, \name{veriT}~\cite{bouton2009},
-and \name{Z3}~\cite{DeMoura2008}) to prove unsatisfiability of formulas
-from first-order logic with theories, and a prover for validity of
-formulas from first-order logic with equality
-(e.g., \name{E}~\cite{Schulz:AICOM-2002}, \name{leanCoP}~\cite{Otten2008},
-\Metis~\cite{hurd2003first}, \name{SPASS} ~\cite{Weidenbach2009} and
-\name{Vampire}~\cite{Riazanov1999}), high-order logic (e.g., \name{Leo-II}
-\cite{Benzmuller2008} and \name{Satallax}~\cite{Brown2012}) or intuitionistic
-logic (e.g., \name{ileanCoP}~\cite{Otten2008}, \name{JProver}
-\cite{Schmitt2001}, and \name{Gandalf}~\cite{Tammet1997}), among others.
-On the other hand, we have the proof checkers, interactive theorem provers
-(henceforth \ITP) or proof assistants (e.g., \Agda~\cite{agdateam},
-\name{Coq}~\cite{coqteam}, \name{Isabelle}~\cite{paulson1994isabelle}, and
-\name{HOL4}~\cite{norrish2007hol}).
-The \ITP tools provide us the logic framework to check and validate the
-reply of the \ATPs since they allow us to define the formal language for
-the problems like operators, logic variables, axioms, and theorems.
+Proof reconstruction is a hard labor since it depends on the
+integration of two complex systems. On the one hand, we have the
+automatic theorem provers (henceforth \ATP) and their specification
+logic. These tools are usually classified in at least one of the
+following categories. A \SAT solver (e.g., \name{zChaff}
+\cite{Moskewicz2001} and \name{MiniSat}~\cite{Een2004}) to prove
+unsatisfiability of \CNF formulas, a \abbre{QBF} solver (e.g.,
+\name{GhostQ}~\cite{Klieber2014} and \name{DepQBF}
+\cite{Lonsing2017}) to prove satisfiability and invalidity of
+quantified Boolean formulas, a \SMT solver (e.g \name{CVC4}
+\cite{Barrett2011}, \name{veriT}~\cite{bouton2009}, and \name{Z3}
+\cite{DeMoura2008}) to prove unsatisfiability of formulas from
+first-order logic with theories, and a prover for validity of
+formulas from first-order logic with equality (e.g., \name{E}
+\cite{Schulz:AICOM-2002}, \name{leanCoP}~\cite{Otten2008}, \Metis
+\cite{hurd2003first}, \name{SPASS} ~\cite{Weidenbach2009} and
+\name{Vampire}~\cite{Riazanov1999}), high-order logic (e.g.,
+\name{Leo-II} \cite{Benzmuller2008} and \name{Satallax}
+\cite{Brown2012}) or intuitionistic logic (e.g., \name{ileanCoP}
+\cite{Otten2008}, \name{JProver} \cite{Schmitt2001}, and
+\name{Gandalf}~\cite{Tammet1997}), among others. On the other hand,
+we have the proof checkers, interactive theorem provers (henceforth
+\ITP) or proof assistants (e.g., \Agda~\cite{agdateam}, \name{Coq}
+\cite{coqteam}, \name{Isabelle}~\cite{paulson1994isabelle}, and
+\name{HOL4}~\cite{norrish2007hol}). The \ITP tools provide us the
+logic framework to check and validate the reply of the \ATPs since
+they allow us to define the formal language for the problems like
+operators, logic variables, axioms, and theorems.
 
 A proof reconstruction tool provides such an integration translating
-the reply delivered by the prover into the formalism of
-the proof assistant. Because the formalism of the source (the evidence
-generated by the \ATP) is not necessarily the same logic in the target, the
-reconstruction turns out in a ``reverse engineering'' task.
-Then, reconstructing a proof involves an in-depth understanding of the
-algorithms in the \ATP and the specification logic in the \ITP.
-What we need from the \ATP tools is a proof-object in a consistent format
-to work with, that is, a full script describing step-by-step with
-exhaustive details and without ambiguities, the table of the derivation
-to get the actual proof. For problems in classical propositional logic
-(henceforth \CPL), from a list of at least forty\footnote{\ATPs available
-from the web service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just
-a few provers were able to deliver proofs (e.g., \name{CVC4}~
-\cite{Barrett2011}, \name{SPASS}, and \name{Waldmeister}~\cite{hillenbrand1997})
-and a little bit less replied with a proof in a file format like
-\TSTP~\cite{sutcliffe2004tstp} (e.g., \name{E}, \Metis,
-\name{Vampire}, and \name{Z3}), \len{LFSC}~\cite{Stump2008}, or the
-\len{SMT-LIB}~\cite{Bohme2011} format.
+the reply delivered by the prover into the formalism of the proof
+assistant. Because the formalism of the source (the evidence
+generated by the \ATP) is not necessarily the same logic in the
+target, the reconstruction turns out in a ``reverse engineering''
+task. Then, reconstructing a proof involves an in-depth
+understanding of the algorithms in the \ATP and the specification
+logic in the \ITP. What we need from the \ATP tools is a
+proof-object in a consistent format to work with, that is, a full
+script describing step-by-step with exhaustive details and without
+ambiguities, the table of the derivation to get the actual proof.
+For problems in classical propositional logic (henceforth \CPL),
+from a list of at least forty\footnote{\ATPs available from the web
+service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
+provers were able to deliver proofs (e.g., \name{CVC4}
+\cite{Barrett2011}, \name{SPASS}, and \name{Waldmeister}
+\cite{hillenbrand1997}) and a little bit less replied with a proof
+in a file format like \TSTP~\cite{sutcliffe2004tstp} (e.g.,
+\name{E}, \Metis, \name{Vampire}, and \name{Z3}), \len{LFSC}
+\cite{Stump2008}, or the \len{SMT-LIB}~\cite{Bohme2011} format.
 
-Many approaches have been proposed and some tools have been implemented
-for proof reconstruction in the last decades. These programs are relevant
-not only because it helps to spread their usage but they also increase
-the confidence of their users about their algorithms and their
-correctness (see, for example, bugs in \ATPs~\cite{Keller2013},
-\cite{Bohme2011}, \cite{Fleury2014} and \cite{Kanso2012}).
-% We mention some tools in the following.
+Many approaches have been proposed and some tools have been
+implemented for proof reconstruction in the last decades. These
+programs are relevant not only because it helps to spread their
+usage but they also increase the confidence of their users about
+their algorithms and their correctness (see, for example, bugs in
+\ATPs~\cite{Keller2013}, \cite{Bohme2011}, \cite{Fleury2014} and
+\cite{Kanso2012}). % We mention some tools in the following.
 
 In this paper, we describe the integration of \Metis prover with the
-proof assistant \Agda by parsing \TSTP derivations to generate
-\Agda proof-terms. We structure the paper as follows.
-In section \ref{sec:metis-language-and-proofs} we briefly introduce
-the \Metis prover. In section \ref{sec:proof-reconstruction}; we
-present our approach to reconstruct proofs deliver by \Metis in
-\Agda.
-We list related work in proof reconstruction in section \ref{sec:related-work}
-In section~\ref{sec:conclusions}, we discuss some limitations, advantages,
-and disadvantages with other similar proof reconstruction tools and
-conclusions for ending up with the future work.
+proof assistant \Agda by parsing \TSTP derivations to generate \Agda
+proof-terms. We structure the paper as follows. In section
+\ref{sec:metis-language-and-proofs} we briefly introduce the \Metis
+prover. In section \ref{sec:proof-reconstruction}; we present our
+approach to reconstruct proofs deliver by \Metis in \Agda. We list
+related work in proof reconstruction in section
+\ref{sec:related-work} In section~\ref{sec:conclusions}, we discuss
+some limitations, advantages, and disadvantages with other similar
+proof reconstruction tools and conclusions for ending up with the
+future work.
 

### 2017-09-07 paper/sections/metis-language-and-proofs.tex
[ paper ] major changes, abstract, conclusions was added.

@@
 
-% ===========================================================================
+% ===================================================================
 
@@
 
-\Metis is an automatic theorem prover written in \len{Standard ML} for
-first-order logic with equality developed by John Hurd~\cite{hurd2003first}.
-This prover is suitable for proof reconstruction since it provides
-well-documented proof-objects to justify its deduction steps from the basis
-of only six inference rules. Exists tools that perform proof
-reconstruction with \Metis, some of these systems are the following.
+\Metis is an automatic theorem prover written in \len{Standard ML}
+for first-order logic with equality developed by John Hurd
+\cite{hurd2003first}. This prover is suitable for proof
+reconstruction since it provides well-documented proof-objects to
+justify its deduction steps from the basis of only six inference
+rules. Exists tools that perform proof reconstruction with \Metis,
+some of these systems are the following.
 
-\name{Isabelle/HOL} incorporated \Metis as a macro-step reconstruction
-tool for explaining proof steps (usually \CNF goals) replied from other \ATPs like
-\name{CVC4}, \name{Vampire}, or \name{Z3}
-(more details in Ref.~\cite{paulson2007source}).
+\name{Isabelle/HOL} incorporated \Metis as a macro-step
+reconstruction tool for explaining proof steps (usually \CNF goals)
+replied from other \ATPs like \name{CVC4}, \name{Vampire}, or
+\name{Z3} (more details in Ref.~\cite{paulson2007source}).
 In \cite{Farber2015}, \Metis was used to provide a tactic for
-\name{HOL Light}; this tactic challenges others like \name{MESON} tactic or the
-\name{leanCoP} tactic that reconstructs proofs delivered by
-\name{leanCoP}~\cite{Farber2016}.
+\name{HOL Light}; this tactic challenges others like \name{MESON}
+tactic or the \name{leanCoP} tactic that reconstructs proofs
+delivered by \name{leanCoP}~\cite{Farber2016}.
 
-In this paper, we ported a subset of \Metis' inference rules to \Agda,
-the propositional fragmented, to allow us to justify step-by-step the proofs
-delivered in \TSTP format generated by \Metis.
+In this paper, we ported a subset of \Metis' inference rules to
+\Agda, the propositional fragmented, to allow us to justify
+step-by-step the proofs delivered in \TSTP format generated
+by \Metis.
 
-% ---------------------------------------------------------------------------
+% -------------------------------------------------------------------
 
@@
 \textit{Input.}~The \TPTP language --which includes the first-order
-form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf})
-formats~\cite{sutcliffe2009} -- is de
-facto input standard language to encode problems for many \ATPs.
-The \TPTP syntax describes a well-defined grammar to handle annotated
-formulas with the following form,
+form (denoted by \name{fof}) and clause normal form (denoted by
+\name{cnf}) formats~\cite{sutcliffe2009} -- is de facto input
+standard language to encode problems for many \ATPs. The \TPTP
+syntax describes a well-defined grammar to handle annotated formulas
+with the following form,
 
@@
 The \name{language} can be \name{fof} or \name{cnf}. The \name{name}
-serves to identify the formula within the problem. Each formula assumes one
-\name{role}, this could be an \name{axiom}, \name{conjecture},
-\name{definition}, or a \name{hypothesis}. The formulas include Boolean
-connectives (\verb!&!, \verb!|!, \verb!=>!, \verb!{<=>!, \verb!~!) and logic
-constants \verb!$true! and \verb!$false!.
+serves to identify the formula within the problem. Each formula
+assumes one \name{role}, this could be an \name{axiom},
+\name{conjecture}, \name{definition}, or a \name{hypothesis}.
+The formulas include Boolean connectives (\verb!&!, \verb!|!,
+\verb!=>!, \verb!{<=>!, \verb!~!) and logic constants \verb!$true!
+and \verb!$false!.
 
@@
 $p\, \vdash \neg (p \wedge \neg p) \vee (q \vee \neg q)$
-in \TPTP syntax as follows, declaring an \tptpaxiom $p$, and the expected
-conclusion, the  \tptpconjecture \verb!~ ((p & ~ p) | (q & ~ q))!.
+in \TPTP syntax as follows, declaring an \tptpaxiom $p$, and the
+expected conclusion, the  \tptpconjecture
+\verb!~ ((p & ~ p) | (q & ~ q))!.
 
@@
 \textit{Output.}~\TSTP language is de facto output standard language
-for derivations of ATPs~\cite{sutcliffe2004tstp}.
-A \TSTP derivation is a directed acyclic graph, a proof tree, where each leaf
-is a formula from the \TPTP input. A node is a formula inferred from the parent
-formulas. The root is the final derived formula. Such a derivation is a list of
-annotated formulas with the form,
+for derivations of ATPs~\cite{sutcliffe2004tstp}. A \TSTP derivation
+is a directed acyclic graph, a proof tree, where each leaf is a
+formula from the \TPTP input. A node is a formula inferred from the
+parent formulas. The root is the final derived formula. Such a
+derivation is a list of annotated formulas with the form,
 
@@
 
-The \name{source} field is an inference record with the following pattern,
+The \name{source} field is an inference record with the following
+pattern,
+
 \begin{verbatim}
@@
 The \name{rule} stands for the inference name; the other fields are
-supporting arguments or useful information to apply the reasoning step, and
-the list of parents nodes.
-For instance, in Fig.~\ref{fig:metis-proof-tstp}, \strip is the name of one
-of the inference with no arguments and only one parent node, the \name{goal}.
+supporting arguments or useful information to apply the reasoning
+step, and the list of parents nodes. For instance, in Fig.
+\ref{fig:metis-proof-tstp}, \strip is the name of one of the
+inference with no arguments and only one parent node, the
+\name{goal}.
 
@@
 \end{verbatim}
-\caption{The \texttt{Metis}' \texttt{TSTP} derivation for the problem $p\vdash p$.}
+\caption{The \texttt{Metis}' \texttt{TSTP} derivation for the
+problem $p\vdash p$.}
 \label{fig:metis-proof-tstp}
@@
 
-% ---------------------------------------------------------------------------
+% -------------------------------------------------------------------
 
@@
 \cite{hurd2003first} listed in Fig.~\ref{fig:metis-inferences}.
-With these inference rules as the only valid deduction steps, \Metis attempts to
-prove conjectures by refutation (see. e.g., \emph{falsium} in the last conclusion
-of the \TSTP derivation in Fig.~\ref{fig:metis-example}).
+With these inference rules as the only valid deduction steps, \Metis
+attempts to prove conjectures by refutation (see. e.g.,
+\emph{falsium} in the last conclusion of the \TSTP derivation in
+Fig.\ref{fig:metis-example}).
 
@@
 
-These proofs are directed acyclic graphs, trees of refutations. Each node stands
-for an application of an inference rule and the
-leaves in the tree represent formulas in the given problem. Each node is
-labeled with a name of the inference rule
-(e.g., \canonicalize in Fig.~\ref{fig:metis-example}). Each
-edge links a premise with one conclusion. The proof graphs have at their
-root the conclusion $\bot$ since \Metis delivers proof by refutation.
+These proofs are directed acyclic graphs, trees of refutations. Each
+node stands for an application of an inference rule and the leaves
+in the tree represent formulas in the given problem. Each node is
+labeled with a name of the inference rule (e.g., \canonicalize in
+Fig.~\ref{fig:metis-example}). Each edge links a premise with one
+conclusion. The proof graphs have at their root the conclusion $\bot$
+since \Metis delivers proof by refutation.
 
@@
 
-We noted in \TSTP derivations that \Metis do not take into account some
-inference rules for the \Metis' official documentation; we refer to
-the \Metis' logic kernel. Besides the figure that shows us the six
-\Metis' inference rules, its proof-objects, the \TSTP derivations,
-exhibit an entirely different set of rules.
+We noted in \TSTP derivations that \Metis do not take into account
+some inference rules for the \Metis' official documentation; we
+refer to the \Metis' logic kernel.
+Besides the six \Metis' inference rules from the Fig.
+\ref{fig:metis-inferences}, its proof-objects, the \TSTP
+derivations, exhibit an entirely different set of rules.
 
@@
 we know only three rules are valid from the \Metis' Logic Kernel:
-\emph{assume}, \emph{axiom}, and \emph{resolve}.
-Nevertheless, as we observed in \TSTP derivations, for such a propositional
-fragment, \Metis uses in his deductions steps, six rules where only the
-resolve inference persists from the original list. In the case of \resolve,
-it differs from its original version since, in \TSTP,  this rules comes with
-an argument, a literal. The other undocumented rules found in \TSTP
-derivations are: \canonicalize, \clausify, \conjunct, \negate, \simplify,
-and \strip.
+\emph{assume}, \emph{axiom}, and \emph{resolve}. Nevertheless, as we
+observed in \TSTP derivations, for such a propositional fragment,
+\Metis uses in his deductions steps, six rules where only the
+\emph{resolve} inference persists from the original list. In the
+case of \resolve, it differs from its original version since, in
+\TSTP, this rules comes with an argument, a literal. The other
+undocumented rules found in \TSTP derivations are: \canonicalize,
+\clausify, \conjunct, \negate, \simplify, and \strip.
 
-This lack of the \Metis' documentation was an important matter for us in the
-proof reconstruction and certainty for other implementors (see a comment
-related on the presenting of \name{Sledgehammer}
-\info{cite here Paulson and Metis Paramodulation' paper}).
-We faced the ambiguity and lack of clearness of some rules like \canonicalize
-or \simplify. For example, we believe that with these last inferences, \Metis
-summarized many essential steps in the conversion or deduction from one formula
-or a list of formulas to another as we show in Example X.
+This lack of the \Metis' documentation was an important matter for
+us in the proof reconstruction and certainty for other implementors
+(see a comment related on the presenting of \name{Sledgehammer}
+in \cite{paulson2007source} and \cite{Farber2015}). We faced
+the ambiguity and lack of clearness of some rules like \canonicalize
+or \simplify. For example, we believe that with these last
+inferences, \Metis summarized many essential steps in the conversion
+or deduction from one formula or a list of formulas to another.
+That is inconvenient since, our proof reconstruction approach needs
+take into account any assumption or consideration as ordering for
+literals, application of simplification theorems, reductions, among
+other valid transformations.
+
 \unsure{Should I give an Example?}
-That is inconvenient since, our proof reconstruction approach needs take into
-account any assumption or consideration as ordering for literals, application
-of simplification theorems, reductions, among other valid transformations.
-\unsure{Should I give an Example?}
-In this part, our job\improvement{job or purpose?} mainly consists of giving
-a response to these rules looking at the \Metis' source code while inspecting
-a representative set of solutions of \CPL problems generated by \Metis.
-\unsure{Should I mention the Prop-Pack Collection?}
-Therefore, this is an attempt to help and fulfill this difficulty, describing
-our understanding of each rule, to later on in section
+
+In this part, our main purpose consists of giving a response to
+these rules looking at the \Metis' source code while inspecting a
+representative set of solutions of \CPL problems
+\cite{Prieto-Cubides2017}generated by \Metis.
+This is an attempt to fulfill the \Metis's documentation,
+describing our understanding of each rule, to later on in section
 \ref{sec:proof-reconstruction}, formalize them effectively in \Agda.
 
-% ...........................................................................
+\vskip 2mm
 
-\textit{Splitting}.
-To prove a goal, \Metis splits the goal into disjoint cases. This
-process produces a list of new subgoals, the conjunction of these subgoals
-implies the goal as we show later in subsection~\ref{ssec:emulating-inferences}.
-Then, a proof of the goal becomes in smaller proofs, one
-refutation for each subgoal. These subgoals are introduced in the \TSTP
-derivation with the \strip inference rule.
+% ...................................................................
+
+\textit{Splitting}. To prove a goal, \Metis splits the goal into
+disjoint cases. This process produces a list of new subgoals, the
+conjunction of these subgoals implies the goal as we show later in
+subsection~\ref{ssec:emulating-inferences}. Then, a proof of the
+goal becomes in smaller proofs, one refutation for each subgoal.
+These subgoals are introduced in the \TSTP derivation with the \strip
+inference rule.
 
@@
 
-% ...........................................................................
+% ...................................................................
 
 \textit{Clausification.} The \clausify rule transforms a
-propositional formula in clausal normal form or \CNF,
-a conjunction of clauses. Where a clause is the disjunction of zero or
-more literals and a literal is an atom (positive literal) or a negation of an
-atom (negative literal). This conversion is not unique, and \Metis performs
-this transformation using its criteria.
+propositional formula in clausal normal form or \CNF, a conjunction
+of clauses. Where a clause is the disjunction of zero or more
+literals and a literal is an atom (positive literal) or a negation
+of an atom (negative literal). This conversion is not unique, and
+\Metis performs this transformation using its criteria.
 
-% ...........................................................................
+% ...................................................................
 
-\textit{Normalization.}
-\Metis uses the \canonicalize rule to normalize a
-propositional formula that comes from an axiom or a definition.
-It often converts each expression in one of its normal form,
-the conjunctive normal form, the negative normal form or the disjunctive normal form.
-Posterior, this rule simplifies the formula with some definitions, applying
-recursively on the structure's formula conjunctions and disjunctions simplifications
-to remove tautologies
-(see Fig.~\ref{fig:conjunctive-disjunctive-simplification} with a list
-of these theorems. We had assumed the commutative property for conjunction and
-disjunction connectives).
+\textit{Normalization.} \Metis uses the \canonicalize rule to
+normalize a propositional formula that comes from an axiom or a
+definition. It often converts each expression in one of its normal
+form, the conjunctive normal form, the negative normal form or the
+disjunctive normal form. Posterior, this rule simplifies the formula
+with some definitions, applying recursively on the structure's
+formula conjunctions and disjunctions simplifications to remove
+tautologies (see Fig.~\ref{fig:conjunctive-disjunctive-simpl} with a
+list of these theorems. We had assumed the commutative property for
+conjunction and disjunction connectives).
 
@@
 \caption{Defintions of \canonicalize inference.}
-\label{fig:conjunctive-disjunctive-simplification}
+\label{fig:conjunctive-disjunctive-simpl}
 \end{figure}
 
-% ...........................................................................
+% ...................................................................
 
-\textit{Resolution.} The \resolve rule is the resolution
-theorem showed in Fig.~\ref{fig:metis-inferences}. Its applications
-needs the positive literal for resolution and two
-derivations to deduce the \emph{resolvent}.
-The positive literal $p$ must occur in the formula from the first derivation,
-and the negative literal must occur in the formula from the second derivation
-(this follows the same pattern in \Metis' logic core in
-Fig.~\ref{fig:metis-inferences} for the resolve inference).
+\textit{Resolution.} The \resolve rule is the resolution theorem
+showed in Fig.~\ref{fig:metis-inferences}. Its applications needs
+the positive literal for resolution and two derivations to deduce
+the \emph{resolvent}. The positive literal $p$ must occur in the
+formula from the first derivation, and the negative literal must
+occur in the formula from the second derivation (this follows the
+same pattern in \Metis' logic core in Fig.~\ref{fig:metis-inferences}
+for the resolve inference).
 
@@
 
-% ...........................................................................
+% ...................................................................
 
-\textit{Splitting a conjunct.}
-The \conjunct rule extracts from a conjunction one of its conjuncts; it is
-a generalization of the projection rules for the conjunction connective as
-we can see in the following \TSTP derivation.
+\textit{Splitting a conjunct.} The \conjunct rule extracts from a
+conjunction one of its conjuncts; it is a generalization of the
+projection rules for the conjunction connective as we can see in the
+following \TSTP derivation.
 
@@
 
-% ...........................................................................
+% ...................................................................
 
-\textit{Simplification.} %abbreviate formulas
-The \simplify rule is a $n$-ary inference that performs simplification
-of definitions. This rule transverses a list of formulas by
-applying different theorems (e.g., \emph{modus pones}, \emph{modus tollens},
-or \emph{disjunctive syllogism}) including the list of theorems used by
-\canonicalize in Fig.~\ref{fig:conjunctive-disjunctive-simplification}
-and the resolution theorem of \resolve rule.
-Moreover, many things happen inside this \Metis' procedure, and
-it is somewhat complicated to grasp it completely.
+\textit{Simplification.}
+The \simplify rule is a $n$-ary inference that performs
+simplification of definitions. This rule transverses a list of
+formulas by applying different theorems (e.g., \emph{modus pones},
+\emph{modus tollens}, or \emph{disjunctive syllogism}) including the
+list of theorems used by \canonicalize in
+Fig.\ref{fig:conjunctive-disjunctive-simpl} and the resolution
+theorem of \resolve rule. Moreover, many things happen inside this
+\Metis' procedure, and it is somewhat complicated to grasp it
+completely.
 

### 2017-09-07 paper/sections/related-work.tex
[ paper ] major changes, abstract, conclusions was added.

@@
 \name{Sledgehammer} is a tool for \name{Isabelle} proof assistant
-~\cite{paulson1994isabelle} that provides a full integration of automatic
-theorem provers including \ATPs
-(see, for example, \cite{meng2006automation}, \cite{blanchette2013extending}
-and \cite{Fleury2014}) and \SMT solvers (see, for instance,
-\cite{hurlin07practical}, \cite{bohme2010},
-\cite{blanchette2013extending}, and \cite{Fleury2014}) with
+\cite{paulson1994isabelle} that provides a full integration of
+automatic theorem provers including \ATPs (see, for example,
+\cite{meng2006automation}, \cite{blanchette2013extending} and
+\cite{Fleury2014}) and \SMT solvers (see, for instance,
+\cite{hurlin07practical}, \cite{bohme2010}, \cite{blanchette2013extending}, and \cite{Fleury2014}) with
 \name{Isabelle/HOL} \cite{nipkow2002isabelle}, the specialization of
-\name{Isabelle} for higher-order logic. Sultana, Benzm{\"{u}}ller, and
-Paulson~\cite{Een2004} integrates \name{Leo-II} and \name{Satallax}, two
-theorem provers for high-order logic with \name{Isabelle/HOL} proposing a
-modular proof reconstruction work flow.
+\name{Isabelle} for higher-order logic. Sultana, Benzm{\"{u}}ller,
+and Paulson~\cite{Een2004} integrates \name{Leo-II} and
+\name{Satallax}, two theorem provers for high-order logic with
+\name{Isabelle/HOL} proposing a modular proof reconstruction work
+flow.
 
-\name{SMTCoq}~\cite{armand2011,Ekici2017} is a tool for the \name{Coq}
-proof assistant \cite{coqteam} which provides a certified checker for
-proof witness coming from the \SMT solver \name{veriT} \cite{bouton2009}
-and adds a new tactic named verit, that calls \name{veriT} on any
-\name{Coq} goal. In \cite{bezem2002automated}, given a fixed but arbitrary
-first-order signature, the authors transform a proof produced by the
-first-order automatic theorem prover \name{Bliksem} \cite{deNivelle2003}
-in a \name{Coq} proof term.
+\name{SMTCoq}~\cite{armand2011,Ekici2017} is a tool for the
+\name{Coq} proof assistant \cite{coqteam} which provides a certified checker for proof witness coming from the \SMT solver \name{veriT}
+\cite{bouton2009} and adds a new tactic named verit, that calls
+\name{veriT} on any \name{Coq} goal. In \cite{bezem2002automated},
+given a fixed but arbitrary first-order signature, the authors
+transform a proof produced by the first-order automatic theorem
+prover \name{Bliksem} \cite{deNivelle2003} in a \name{Coq} proof
+term.
 
 Hurd~\cite{Hurd1999} integrates the first-order resolution prover
-\name{Gandalf} with \name{HOL}~\cite{norrish2007hol}, a high-order theorem
-prover, following an \abbre{LCF} model implementing the tactic \verb!GANDALF_TAC!.
-For \name{HOL Light}, a version of \name{HOL} but with a simpler logic core,
-the \SMT solver \name{CVC4} was integrated, and Kaliszyk and
-Urban~\cite{kaliszyk2013} reconstruct proofs from different ATPs with their
-\name{PRocH} tool, replaying the detailed inference steps from the ATPs with
-internal inference methods implemented in \name{HOL Light}.
+\name{Gandalf} with \name{HOL}~\cite{norrish2007hol}, a high-order
+theorem prover, following an \abbre{LCF} model implementing the
+tactic \verb!GANDALF_TAC!. For \name{HOL Light}, a version of
+\name{HOL} but with a simpler logic core, the \SMT solver \name{CVC4}
+was integrated, and Kaliszyk and Urban~\cite{kaliszyk2013}
+reconstruct proofs from different ATPs with their \name{PRocH} tool,
+replaying the detailed inference steps from the ATPs with internal
+inference methods implemented in \name{HOL Light}.
 
@@
 
-%(Vol. 36, pp. 127–136).
+% (Vol. 36, pp. 127–136).
 
@@
 
-% Given a conjecture, it attempts to find suitable premises, then calls
-% external ATPs such as E[Sch13], Vampire [KV13], or Z3 [dMB08], and
-% attempts to reconstruct the proof using the premises used by the ATP.
-% To reconstruct proofs, it uses tactics such as MESON, simplification,
-% and a
-% few other decision procedures, however, these are sometimes not p
-% owerful
-% enough to reconstruct proofs found by the external ATPs.
+% Given a conjecture, it attempts to find suitable premises, then
+% calls external ATPs such as E[Sch13], Vampire [KV13], or Z3 [dMB08],
+% and attempts to reconstruct the proof using the premises used by the
+% ATP. To reconstruct proofs, it uses tactics such as MESON,
+% simplification, and a few other decision procedures, however, these
+% are sometimes not p owerful enough to reconstruct proofs found by
+% the external ATPs.
 
-\name{Waldmeister} is an automatic theorem prover for unit equational
-logic \cite{hillenbrand1997}.
-Foster and Struth~\cite{foster2011integrating} integrate \name{Waldmeister} into
-\Agda~\cite{agdateam}. This integration requires a proof
-reconstruction step, but authors' approach is restricted to pure
-equational logic --also called identity theory~\cite{humberstone2011}--
-that is, first-order logic with equality but no other predicate symbols
-and no functions symbols~\cite{appel1959}.
+\name{Waldmeister} is an automatic theorem prover for unit
+equational logic \cite{hillenbrand1997}. Foster and Struth
+\cite{foster2011integrating} integrate \name{Waldmeister} into \Agda
+\cite{agdateam}. This integration requires a proof reconstruction
+step, but authors' approach is restricted to pure equational logic
+--also called identity theory~\cite{humberstone2011}-- that is,
+first-order logic with equality but no other predicate symbols and
+no functions symbols~\cite{appel1959}.
 
-Kanso and Setzer~\cite{kanso2016light} integrate \name{Z3} in \Agda
-but they also integrate the propositional fragment of the \name{E} prover in
-\cite{Kanso2012}. They cataloged these two integration as
-\emph{Oracle and Reflection} and \emph{Oracle and Justification}, respectively.
-Their integration with the \name{E} prover is the most related work with our
-approach found at the moment while we write this document. Besides the use
-of the same \ITP, crucial differences easily arise like decidability of
-propositional logic using semantics that we do not take into account for the
-reason we describe later on in section~\ref{sec:conclusions}.
+% Kanso and Setzer~\cite{kanso2016light} integrate \name{Z3} in \Agda
+% but they also integrate the propositional fragment of the \name{E} prover in
+% \cite{Kanso2012}. They cataloged these two integration as
+% \emph{Oracle and Reflection} and \emph{Oracle and Justification}, respectively.
+% Their integration with the \name{E} prover is the most related work with our
+% approach found at the moment while we write this document. Besides the use
+% of the same \ITP, crucial differences easily arise like decidability of
+% propositional logic using semantics that we do not take into account for the
+% reason we describe later on in section~\ref{sec:conclusions}.
 

### 2017-09-07 paper/sections/abstract.tex
[ paper ] minor changes, title and abstract.

@@
 of the prover, constructing the respective tree associated with the
-proof, ending up with an \Agda code for type-checking.
+proof, for ending up with an \Agda code for type-checking.
 

### 2017-09-07 paper/sections/introduction.tex
[ paper ] fixing some mistakes.

@@
 proof-terms. We structure the paper as follows. In section
-\ref{sec:metis-language-and-proofs} we briefly introduce the \Metis
+\ref{sec:metis-language-and-proofs}, we briefly introduce the \Metis
 prover. In section \ref{sec:proof-reconstruction}; we present our
@@
 related work in proof reconstruction in section
-\ref{sec:related-work} In section~\ref{sec:conclusions}, we discuss
+\ref{sec:related-work}. In section~\ref{sec:conclusions}, we discuss
 some limitations, advantages, and disadvantages with other similar

### 2017-09-07 paper/sections/metis-language-and-proofs.tex
[ paper ] fixing some mistakes.

@@
 In \cite{Farber2015}, \Metis was used to provide a tactic for
-\name{HOL Light}; this tactic challenges others like \name{MESON}
-tactic or the \name{leanCoP} tactic that reconstructs proofs
+\name{HOL Light}; this challenges others like \name{MESON}
+or the \name{leanCoP} tactic that reconstructs proofs
 delivered by \name{leanCoP}~\cite{Farber2016}.
@@
 
-We noted in \TSTP derivations that \Metis do not take into account
+We noted in \TSTP derivations that \Metis does not take into account
 some inference rules for the \Metis' official documentation; we
@@
 For instance, for the propositional logic fragment without equality,
-we know only three rules are valid from the \Metis' Logic Kernel:
+only three rules are valid from the \Metis' Logic Kernel:
 \emph{assume}, \emph{axiom}, and \emph{resolve}. Nevertheless, as we
@@
 case of \resolve, it differs from its original version since, in
-\TSTP, this rules comes with an argument, a literal. The other
+\TSTP, this rules come with an argument, a literal. The other
 undocumented rules found in \TSTP derivations are: \canonicalize,
@@
 inferences, \Metis summarized many essential steps in the conversion
-or deduction from one formula or a list of formulas to another.
+or deduction from one formula or a list of formulas to another as we see in the following example.
+\improvement{Add an example showing a deduction where metis do a lot 
+between two steps}
 That is inconvenient since, our proof reconstruction approach needs
@@
 representative set of solutions of \CPL problems
-\cite{Prieto-Cubides2017}generated by \Metis.
+\cite{Prieto-Cubides2017} generated by \Metis.
 This is an attempt to fulfill the \Metis's documentation,
@@
 \textit{Simplification.}
-The \simplify rule is a $n$-ary inference that performs
-simplification of definitions. This rule transverses a list of
-formulas by applying different theorems (e.g., \emph{modus pones},
-\emph{modus tollens}, or \emph{disjunctive syllogism}) including the
-list of theorems used by \canonicalize in
-Fig.\ref{fig:conjunctive-disjunctive-simpl} and the resolution
-theorem of \resolve rule. Moreover, many things happen inside this
-\Metis' procedure, and it is somewhat complicated to grasp it
-completely.
-
+The \simplify rule is inference that performs simplification of 
+definitions or tautologies over a list of derivations. This rule 
+transverses a list of formulas by applying different theorems (e.g.,
+\emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
+syllogism}) including the list of theorems used by \canonicalize in Fig.
+\ref{fig:conjunctive-disjunctive-simpl} and the resolution theorem of
+\resolve rule. Moreover, many things happen inside this \Metis'procedure, 
+and it is somewhat complicated to grasp it completely.
 \end{document}

### 2017-09-07 paper/sections/proof-reconstruction.tex
[ paper ] major changes, abstract, conclusions was added.
[ paper ] fixing some mistakes.

--- 2017-09-04 paper/sections/proof-reconstruction.tex
@@
 
-\subsection{The Translation Method}
-
-Our system (see Fig~\ref{fig:proof-reconstruction-overview}) translates a \verb!TSTP!
-file into an \verb!Agda! proof by parsing it with a \verb!Haskell! tool.
-This tool reconstructs the proof tree, removing redundancies and
-cutting unnecessary steps (see for example repetitions in the derivation shown in
-Fig~\ref{fig:metis-example}). The output is \verb!Agda! code.
-Then, we use \verb!Agda! as a proof checker to type-check the proof.
-If type-checking succeed, then our proof is checked. Else, we have a failure
-proof due to three possible factors. First, a soundness bug in the ATP or a bug
-in the output printing. Second, a bug in the translation process in our \verb!TSTP! parsing
-module, the inner algorithms in the analysis of the proof tree, the pretty printer
-module, or a bug in \verb!Haskell!. Lastly, a bug in our proof checker \verb!Agda!.
-
-% ---------------------------------------------------------------------------
-
-\subsection{Reconstruction Work-flow}
-
 \begin{figure}
@@
 \node[text width=2cm, align=center](problem) at (0,0)
-  {CPL \\ Problem};
+  {1. CPL \\ Problem.};
 
 \node[right = 1.2cm of problem, text width=2cm, align=center]
-  (tptp){\verb!TPTP! \\ Problem};
+  (tptp){2. \TPTP \\ Problem.};
 
 \node[right= 1.2cm of tptp, text width=2cm, align=center]
-   (metis) {\verb!Metis! \\ Prover};
+   (metis) {3. \Metis \\ Prover.};
 
 \node[right= 1.2cm of metis, text width=2cm, align=center, inner sep=10pt]
-   (tstp) {\verb!TSTP! \\ Derivation};
+   (tstp) {4. \TSTP \\ Derivation.};
 
 \node[below= 0.5cm of tstp, text width=2cm, align=center, inner sep=10pt]
-  (athena) {\verb!Haskell! \\ Traslator};
+  (athena) {5. \Haskell \\ Traslator.};
 
 \node[left = 1.2cm of athena, text width=2cm, align=center]
-   (agdafile) {\verb!Agda! \\ Proof};
+   (agdafile) {6. \Agda \\ Proof.};
 
 \node[left = 1.2cm of agdafile, text width=2cm, align=center]
-   (agda) {Proof Checker};
+   (agda) {7. Proof Checker.};
 
 \node[below = 0.5cm of problem, text width=2cm, align=center]
-   (verified) {Checked};
+   (verified) {8.1 Proof \\ Checked.};
 
 \node[below = 0.5cm of verified, text width=2cm, align=center]
-   (failure) {Error};
+   (failure) {8.2 Error.};
 
@@
 
-% ---------------------------------------------------------------------------
-
-\subsection{Proof Cheker}
-\label{ssec:agda}\
-
-\verb!Agda! is an interactive system for constructing proofs and programs,
-based on Martin-L\"{o}f's type theory and extended with records, parametrised
-modules, among other features.
-One of the main strengths of \verb!Agda! is its support for writing proofs,
-which we shall call \verb!Agda!'s proof engine. It consists of: support for
-inductively defined types, including inductive families, and function
-definitions using pattern matching on such types, normalisation during type-
-checking, commands for refining proof terms, coverage checker and termination
-checker.
-The inductive approach for representing classical propositional logic
-is better because we benefit from \verb!Agda!'s proof engine and its Unicode
-support that allows us writing proofs similar as we find in math text books.
-
-% ---------------------------------------------------------------------------
-
-\subsection{LCF-Style Theorem Proving}
-\label{ssec:lcf-style-theormem-proving}
-
-A propositional formula is a experssion of indivisible propositional atoms,
-logical connectives $\{\wedge, \vee, \Rightarrow, \Leftrightarrow, \neg\}$
-and logic constants $\{\top, \bot\}$.
-In \verb!Agda!, we define the formula
-as an inductive type using the keyword \texttt{data} and including every
-connective as a constructor. We represent propositional formulas with
-\verb!Prop! data type using the following definition.
-
-%an extension of the syntax definition used in \cite{Altenkirch2015}.
-
-\begin{verbatim}
-data Prop : Set where
-  Var              : Fin n → Prop
-  ⊤                : Prop
-  ⊥                : Prop
-  _∧_ _∨_ _⇒_ _⇔_  : (φ ψ : Prop) → Prop
-  ¬_               : (φ : Prop)   → Prop
-\end{verbatim}
-
-On the other hand, we represent theorems in CPL using an abstract data type
-to implement a natural deduction calculus.
-
-\begin{verbatim}
-data _⊢_ : (Γ : Ctxt)(φ : Prop) → Set where
-\end{verbatim}
-
-The sequents  $\Gamma \vdash \phi$ represent theorems,
-where $\Gamma$ is a set of premises and $\phi$ is the
-sequent's conclusion. Strictly speaking, we define the set of premises
-$\Gamma$ with \verb!List! data type
-% \footnote{We use the \verb!Agda! standard library's implementation of the List data type.}.
-
-Our CPL system define all inference rules for intuitonistic propositional logic
-(see Fig.~\ref{fig:theorem-constructors}) as constructors of the theorem
-data type, and we postulate the principle of the excluded middle (PEM).
-
-\begin{verbatim}
-postulate  PEM : ∀ {Γ} {φ} → Γ ⊢ φ ∨ ¬ φ
-\end{verbatim}
-
-\begin{figure}
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{}
-\RightLabel{\scriptsize\tt assume $\varphi$}
-\UnaryInfC{$\Gamma , \varphi \vdash \varphi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt weaken $\psi$}
-\UnaryInfC{$\Gamma , \psi \vdash \varphi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{}
-\RightLabel{\scriptsize\tt $\top$-intro}
-\UnaryInfC{$\Gamma \vdash \top$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \bot$}
-\RightLabel{\scriptsize\tt $\bot$-elim $\varphi$}
-\UnaryInfC{$\Gamma \vdash \varphi$}
-\end{bprooftree}
-%}
-\]
-
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma , \varphi \vdash \bot$}
-\RightLabel{\scriptsize\tt $\neg$-intro}
-\UnaryInfC{$\Gamma \vdash \neg \varphi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg \varphi$}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\neg$-elim}
-\BinaryInfC{$\Gamma \vdash \bot$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\AxiomC{$\Gamma \vdash \psi$}
-\RightLabel{\scriptsize\tt $\wedge$-intro}
-\BinaryInfC{$\Gamma \vdash \varphi \wedge \psi$}
-\end{bprooftree}
-%}
-\]
-
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
-\RightLabel{\scriptsize\tt $\wedge$-proj$_1$}
-\UnaryInfC{$\Gamma\vdash \varphi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
-\RightLabel{\scriptsize\tt $\wedge$-proj$_2$}
-\UnaryInfC{$\Gamma\vdash \psi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\vee$-intro$_1$ $\psi$}
-\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
-\end{bprooftree}
-%}
-\]
-
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \psi$}
-\RightLabel{\scriptsize\tt $\vee$-intro$_2$ $\varphi$}
-\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma ,\varphi \vdash \gamma $}
-\AxiomC{$\Gamma , \psi  \vdash \gamma$}
-\RightLabel{\scriptsize\tt $\vee$-elim}
-\BinaryInfC{$\Gamma , \varphi \vee \psi \vdash \gamma$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma , \varphi \vdash \psi$}
-\RightLabel{\scriptsize\tt $\Rightarrow$-intro}
-\UnaryInfC{$\Gamma \vdash \varphi \Rightarrow \psi$}
-\end{bprooftree}
-%}
-\]
-
-\[
-%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\Rightarrow$-elim}
-\BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma , \varphi \vdash \psi$}
-\AxiomC{$\Gamma , \psi \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\Leftrightarrow$-intro}
-\BinaryInfC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
-\end{bprooftree}
-%}
-\]
-
-\[
-%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
-\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_1$}
-\BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}\quad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
-\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_2$}
-\BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}
-%}
-\]
-
-\caption{Inference rules for CPL system.}
-\label{fig:theorem-constructors}
-\end{figure}
-
-% ---------------------------------------------------------------------------
-
-% ---------------------------------------------------------------------------
-
-\subsection{Emulation of Inference Rules in Agda}
-\label{ssec:emulating-inferences}
-
-\textit{Normalization.}
-
-\begin{figure}
-\[ \scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi$}
-
-  \UnaryInfC{$\Gamma \vdash \texttt{cnf}~\varphi$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi$}
-  \UnaryInfC{$\Gamma \vdash \texttt{nnf}~\varphi$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi$}
-  \UnaryInfC{$\Gamma \vdash \texttt{dnf}~\varphi$}
-\end{bprooftree}
-}\]
-\end{figure}
-
-\begin{figure}
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \wedge \bot$}
-  \UnaryInfC{$\Gamma \vdash \bot$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \wedge \top$}
-  \UnaryInfC{$\Gamma \vdash \varphi$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \wedge \neg \varphi$}
-  \UnaryInfC{$\Gamma \vdash \bot$}
-\end{bprooftree}
-%}
-\]
-
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \vee \bot$}
-  \UnaryInfC{$\Gamma \vdash \varphi$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \vee \top$}
-  \UnaryInfC{$\Gamma \vdash \top$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \vee \neg \varphi$}
-  \UnaryInfC{$\Gamma \vdash \top$}
-\end{bprooftree}
-%}
-\]
-\end{figure}
-
-\textit{Resolution.}
-
-\begin{figure}
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\delta_{\phi} := \Gamma \vdash \varphi$}
-\AxiomC{$\delta_{\psi} := \Gamma \vdash \psi$}
-\RightLabel{\texttt{resolve} $p$}
-\BinaryInfC{$\Gamma \vdash$ \texttt{resolve} $\phi\ \psi\ p$}
-\end{bprooftree}
-%}
-\]
-% \caption{Resolution in \verb!Metis!.}
-\label{fig:resolution-rule}
-\end{figure}
-
-\textit{Splitting a conjunct.}
-In the following theorem, we see the definition for the \verb!conjunct! rule.
-It extracts the $\varphi_i$ conjunct from the conjunction given by $\varphi$.
-
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi := \varphi_1 \wedge \cdots\wedge\varphi_i
-\wedge\cdots\wedge \varphi_n$}
-\AxiomC{$\varphi_i \equiv \psi$}
-\RightLabel{\footnotesize\tt conjunct $\psi$}
-\BinaryInfC{$\Gamma\vdash\varphi_i$}
-\end{bprooftree}
-}
-\]
-
-\textit{Splitting a goal}
-
-\begin{figure}
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi_1 \wedge \varphi_2$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi_1) \wedge \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
-\end{bprooftree}
-}\]
-
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi_1 \vee \varphi_2$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\neg \varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
-\end{bprooftree}
-}\]
-
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi_1 \Rightarrow \varphi_2$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg \neg \varphi$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi)$}
-\end{bprooftree}
-}\]
-
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$ \Gamma \vdash \varphi_1 \Leftrightarrow \varphi_2$}
-\UnaryInfC{$\Gamma\vdash\texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2) \wedge \texttt{unshunt}~(\varphi_2 \Rightarrow \texttt{split}~\varphi_1)$}
-\end{bprooftree}
-}\]
-
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg \top$}
-\UnaryInfC{$\Gamma \vdash \bot$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg \bot$}
-\UnaryInfC{$\Gamma \vdash \top$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg (\varphi_1 \wedge \varphi_2)$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt} (\varphi_1 \Rightarrow \texttt{split}~ \neg \varphi_2)$}
-\end{bprooftree}
-}\]
-
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg (\varphi_1 \vee \varphi_2)$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\neg \varphi_1) \wedge  \texttt{unshunt}~(\neg \varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2)$}
-\end{bprooftree}
-}\]
-
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg (\varphi_1 \Rightarrow \varphi_2)$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi_1) \wedge \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2)$}
-\end{bprooftree}\qquad
-}\]
-
-\[\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg (\varphi_1 \Leftrightarrow \varphi_2)$}
-\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2) \wedge \texttt{unshunt}~(\neg \varphi_2 \Rightarrow \texttt{split}~\varphi_1)$}
-\end{bprooftree}
-}\]
-\caption{Split a goal in an equivalent conjunction of subgoals.}
-\label{split}
-\end{figure}
-
-In the theorems above appear two recursive functions \texttt{unshunt} and \texttt{split}. They have the following definitions.
-
-\begin{verbatim}
-unshunt : Prop → Prop
-unshunt (φ₁ ⇒ (φ₂ ⇒ φ₃)) = unshunt ((φ₁ ∧ φ₂) ⇒ φ₃)
-unshunt (φ₁ ⇒ (φ₂ ∧ φ₃)) = unshunt (φ₁ ⇒ φ₂)) ∧ (unshunt(φ₁ ⇒ φ₃)
-unshunt φ                = φ
-\end{verbatim}
-
-\begin{verbatim}
-split : Prop → Prop
-split (φ₁ ∧ φ₂)     = {!!}
-split (φ₁ ∨ φ₂)     = {!!}
-split (φ₁ ⇒ φ₂)     = {!!}
-split (φ₁ ⇔ φ₂)     = {!!}
-split (¬ ⊤)         = {!!}
-split (¬ ⊥)         = {!!}
-split (¬ (φ₁ ∧ φ₂)) = {!!}
-split (¬ (φ₁ ∨ φ₂)) = {!!}
-split (¬ (φ₁ ⇒ φ₂)) = {!!}
-split (¬ (φ₁ ⇔ φ₂)) = {!!}
-split (¬ (¬ φ))     = {!!}
-split φ₁            = {!!}
-\end{verbatim}
-
-...
-
-\textit{Simplification.}
-
-\begin{figure}
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
-  \AxiomC{$\Gamma \vdash \psi$}
-  \RightLabel{\footnotesize\tt $\Leftrightarrow$-elim}
-  \BinaryInfC{$\Gamma \vdash \varphi$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
-  \AxiomC{$\Gamma \vdash \varphi$}
-  \RightLabel{\footnotesize\tt $\Rightarrow$-elim}
-  \BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}
-\]
-\[
-\begin{bprooftree}
-  \AxiomC{$\Gamma \vdash \varphi \vee \neg \psi$}
-  \AxiomC{$\Gamma \vdash \neg \varphi$}
-  \BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}
-%}
-\]
-
-\caption{Additional simplification theorems.}
-\label{fig:simplify-rule}
-\end{figure}
-
 \end{document}

### 2017-09-08 paper/sections/abstract.tex
[ paper ] fixing error grammars and adding notes.

--- 2017-09-07 paper/sections/abstract.tex
@@
 In this paper, we describe our approach to reconstruct and verify in
-\Agda, a  proof assistant,  solutions obtained by \Metis, an
+\Agda, a  proof assistant for type theory, solutions obtained by \Metis, an
 automatic theorem prover, to problems in classical propositional
@@
 version of them in the proof assistant. Finally, we parse the output
-of the prover,  constructing the respective tree associated with the
-proof, ending up with an \Agda code for type-checking.
+of the prover, build and analize the respective tree associated with the
+proof, for ending up with an \Agda code of the proof for type-checking.
 
-\keywords{proof reconstruction, \Agda, automatic theorem prover, classical propositional logic, \Metis.}
+\keywords{proof reconstruction
+\unsure{proof reconstruction or proof-reconstruction},
+\Agda, automatic theorem prover, classical propositional logic, \Metis.}
+
 \end{abstract}

### 2017-09-08 paper/sections/acknowledgements.tex
[ paper ] fixing error grammars and adding notes.

@@
 
-We thank Universidad EAFIT of Medell\'in, Colombia for funding
+We thank Universidad EAFIT in Medell\'in, Colombia for funding
 support. This project was a product of the Logic and Computation
-Research Group at the Universidad EAFIT.
+Research Group at Universidad EAFIT.
 

### 2017-09-08 paper/sections/conclusions.tex
[ paper ] fixing error grammars and adding notes.

--- 2017-09-01 paper/sections/conclusions.tex
@@
 
-Amazing conclusions.
-...
-\cite{}
+Besides the logic and its complexity, the proof reconstruction task is
+far from trivial. In this document, we attempt to reconstruct proofs
+of propositional logic without equality deliverd by \Metis successfully.
 
-\subsubsection*{Future Work.}
-\label{ssec:future-work}
+From our experience building a proof reconstruction tool, depending on
+the systems involved in thetranslation, some difficulties can arise.
+We listed some of them in section \ref{sec:metis-language-and-proofs}
+and in the section \ref{sec:proof-reconstruction}.
+
+For instance, just showing equality between Normal Forms for the
+same formula in the output of the \canonicalize inference and a
+common implementation for this kind of conversion; we observed that
+\Metis performs reordering for each inner expression mainly in the
+presence of negative literals. Another aspect to take into account
+is the \Metis' treatment for conjunctions and disjunction;
+these connectives were treated as right associative and binary
+operators in the \TSTP format but that assumptons is not a standard.
+We had to update the \TSTP parser module introduced in
+\cite{Gomez-Londono2015} to include features like these.
+
+However, one of our biggest obstacles
+\improvement{Remove the use of the \emph{biggest obstacules}.}
+was dealing with
+the Equality between formulas since, in our approach, we only work
+with the syntactic treatment of the logic without considering the
+semantics.
+One of the main reasons for such a restriction relay on our plans to
+support further first-order logic, where a semantic treatment is not
+viable.\unsure{Please confirm this.}
+
+Nevertheless, the proof reconstruction is certainly possible, and
+the verification of solutions of \CPL problems can be carried out
+successful in \Agda. Our tool is able to translate \Metis
+derivations in \TSTP format to deliver \Agda code of the proof,
+\change{Better uses \emph{proof-terms}?}
+and this proof can be type-checked by \Agda.
+
+The source code of our tool can be extended to support
+other \ATPs for \CPL like \name{E}. This work can be carried out
+may following the description in Kanso' Ph.D. Thesis~\cite{Kanso2012}
+for the inference rules of \name{E} or \name{Z3}.
+
+Trying to justify a proof-object of a theorem prover has a
+significant impact, may increase the trustworthiness of the prover
+proving its correctness, or contrary, revealing important issues to
+improve the system. In both cases, there is a benefit for both
+sides, the user of this technology, and their developers.
+
+For instance, while writing this document, we found a soundness bug,
+a bug in the printing out of the \TSTP derivations, and a bug in the
+parsing for \TPTP problem in \Metis. Fortunately, all these bugs
+were fixed quickly by Hurd\footnote{Issues No. 4, No. 2, and the
+commit \name{8a3f11e} from the \Metis' official repository
+\url{https://github.com/gilith/metis}}, and a new version of \Metis
+was released (version 2.3, release 20170810).
+
+% \subsubsection*{Future Work.}
+% \label{ssec:future-work}
 

### 2017-09-08 paper/sections/introduction.tex
[ paper ] fixing error grammars and adding notes.

@@
 understanding of the algorithms in the \ATP and the specification
-logic in the \ITP. What we need from the \ATP tools is a
-proof-object in a consistent format to work with, that is, a full
-script describing step-by-step with exhaustive details and without
-ambiguities, the table of the derivation to get the actual proof.
+logic in the \ITP. To begin with the proof reconstruction, it is
+necessary to have a proof-object from the \ATP in a consistent
+format to work with, that is, a full script describing step-by-step
+with exhaustive details and without ambiguities, the derivation to
+get the actual proof.
 For problems in classical propositional logic (henceforth \CPL),
@@
 \ATPs~\cite{Keller2013}, \cite{Bohme2011}, \cite{Fleury2014} and
-\cite{Kanso2012}). % We mention some tools in the following.
+\cite{Kanso2012}). We mention some of these tools in the related work,
+section \ref{sec:related-work}.
 
@@
 \ref{sec:metis-language-and-proofs}, we briefly introduce the \Metis
-prover. In section \ref{sec:proof-reconstruction}; we present our
-approach to reconstruct proofs deliver by \Metis in \Agda. We list
-related work in proof reconstruction in section
-\ref{sec:related-work}. In section~\ref{sec:conclusions}, we discuss
+prover. In section \ref{sec:proof-reconstruction}, we present our
+approach to reconstruct proofs deliver by \Metis in type theory.
+In section~\ref{sec:conclusions}, we discuss
 some limitations, advantages, and disadvantages with other similar
-proof reconstruction tools and conclusions for ending up with the
-future work.
+proof reconstruction tools for ending up with some conclusions and the
+future work. Finally, we list some related works in proof reconstruction
+in section \ref{sec:related-work}.
 

### 2017-09-08 paper/sections/metis-language-and-proofs.tex
[ paper ] fixing error grammars and adding notes.

@@
 justify its deduction steps from the basis of only six inference
-rules. Exists tools that perform proof reconstruction with \Metis,
-some of these systems are the following.
+rules. There are already some tools that perform proof reconstruction
+with \Metis, some of these systems are the following.
 
@@
 
-In this paper, we ported a subset of \Metis' inference rules to
-\Agda, the propositional fragmented, to allow us to justify
-step-by-step the proofs delivered in \TSTP format generated
-by \Metis.
+In this paper, we ported a subset of the \Metis' inference rules to
+\Agda, the propositional fragmented without equality.
+That allows us to justify step-by-step the proofs delivered in
+\TSTP format generated by the prover \Metis.
 
@@
 
-For instance, we express the problem
+For instance, let us express the problem
 $p\, \vdash \neg (p \wedge \neg p) \vee (q \vee \neg q)$
@@
 Fig.~\ref{fig:metis-example}). Each edge links a premise with one
-conclusion. The proof graphs have at their root the conclusion $\bot$
-since \Metis delivers proof by refutation.
+conclusion. The proof graphs have at their root the conclusion
+$\bot$, since \Metis delivers proofs by refutation.
 
@@
 case of \resolve, it differs from its original version since, in
-\TSTP, this rules come with an argument, a literal. The other
+\TSTP, this rule has by definition an argument, a literal. The other
 undocumented rules found in \TSTP derivations are: \canonicalize,
@@
 
-This lack of the \Metis' documentation was an important matter for
+This lack of the \Metis' documentation is an important matter for
 us in the proof reconstruction and certainty for other implementors
@@
 the ambiguity and lack of clearness of some rules like \canonicalize
-or \simplify. For example, we believe that with these last
-inferences, \Metis summarized many essential steps in the conversion
-or deduction from one formula or a list of formulas to another as we see in the following example.
-\improvement{Add an example showing a deduction where metis do a lot 
-between two steps}
-That is inconvenient since, our proof reconstruction approach needs
-take into account any assumption or consideration as ordering for
-literals, application of simplification theorems, reductions, among
-other valid transformations.
+or \simplify.
+For example, we believe by applying these last
+inferences, \Metis summarized many essential steps to deduce a
+formula from a list a list of formulas as we see in the following
+example.
+\improvement{Add an example here to show a deduction where \Metis do
+a lot between two steps.}
+That inference' behavior has become a drawback since, our approach
+to reconstruct proofs needs take into account any assumption or
+consideration as ordering for literals, application of
+simplification theorems, reductions, among other valid
+transformations.
 
@@
 \cite{Prieto-Cubides2017} generated by \Metis.
-This is an attempt to fulfill the \Metis's documentation,
-describing our understanding of each rule, to later on in section
-\ref{sec:proof-reconstruction}, formalize them effectively in \Agda.
+This is an attempt to fulfill the \Metis's documentation, by
+describing our each rule from our perspective. Later on, in section
+\ref{sec:proof-reconstruction}, we present a formal description of
+such rules.
 
@@
 definition. It often converts each expression in one of its normal
-form, the conjunctive normal form, the negative normal form or the
-disjunctive normal form. Posterior, this rule simplifies the formula
+form: the conjunctive normal form, the negative normal form or the
+disjunctive normal form. Next, this rule simplifies the formula
 with some definitions, applying recursively on the structure's
 formula conjunctions and disjunctions simplifications to remove
-tautologies (see Fig.~\ref{fig:conjunctive-disjunctive-simpl} with a
-list of these theorems. We had assumed the commutative property for
+tautologies (see Fig.~\ref{fig:conjunctive-disjunctive-simpl} for a
+list of these theorems. We assume the commutative property for the
 conjunction and disjunction connectives).
@@
 \textit{Resolution.} The \resolve rule is the resolution theorem
-showed in Fig.~\ref{fig:metis-inferences}. Its applications needs
-the positive literal for resolution and two derivations to deduce
-the \emph{resolvent}. The positive literal $p$ must occur in the
-formula from the first derivation, and the negative literal must
+showed in Fig.~\ref{fig:metis-inferences}. For its application, we
+need the positive literal for resolution and two derivations to
+deduce the \emph{resolvent}. The positive literal $p$ must occur in
+the formula from the first derivation, and the negative literal must
 occur in the formula from the second derivation (this follows the
@@
 conjunction one of its conjuncts; it is a generalization of the
-projection rules for the conjunction connective as we can see in the
-following \TSTP derivation.
+projection rules for the conjunction connective as the
+following \TSTP derivation shows.
 
@@
 \emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
-syllogism}) including the list of theorems used by \canonicalize in Fig.
-\ref{fig:conjunctive-disjunctive-simpl} and the resolution theorem of
-\resolve rule. Moreover, many things happen inside this \Metis'procedure, 
-and it is somewhat complicated to grasp it completely.
+syllogism}) including the list of theorems used by \canonicalize in
+Fig. \ref{fig:conjunctive-disjunctive-simpl} and the resolution
+theorem of \resolve rule.
+
+Moreover, we are not completely sure about the exact behavior for
+all \Metis' inference rules. It is somewhat complicated to grasp it
+completely since the source code is around the 10.000 lines of code.
+
 \end{document}

### 2017-09-08 paper/sections/abstract.tex
[ paper ] section 3 introduction added.

@@
 In this paper, we describe our approach to reconstruct and verify in
-\Agda, a  proof assistant for type theory, solutions obtained by \Metis, an
-automatic theorem prover, to problems in classical propositional
-logic. The translation method consists of justifying step-by-step
-each deduction found in the prover's solution. To carry out this
-plan, we emulate the inference rules of the prover, providing a
-version of them in the proof assistant. Finally, we parse the output
-of the prover, build and analize the respective tree associated with the
-proof, for ending up with an \Agda code of the proof for type-checking.
+\Agda, a  proof assistant for type theory, solutions obtained by
+\Metis, an automatic theorem prover, to problems in classical 
+propositional logic. The translation method consists of justifying 
+step-by-step each deduction found in the prover's solution. To carry 
+out this plan, we emulate the inference rules of the prover, 
+providing a version of them in the proof assistant. Finally, we 
+parse the output of the prover, build and analyze the respective 
+tree associated with the proof, for ending up with an \Agda code of 
+the proof for type-checking.
 

### 2017-09-08 paper/sections/conclusions.tex
[ paper ] section 3 introduction added.

@@
 
-Besides the logic and its complexity, the proof reconstruction task is
-far from trivial. In this document, we attempt to reconstruct proofs
-of propositional logic without equality deliverd by \Metis successfully.
+In this document, we attempted to reconstruct proofs
+of propositional logic without equality deliver by \Metis successfully.
 
-From our experience building a proof reconstruction tool, depending on
-the systems involved in thetranslation, some difficulties can arise.
-We listed some of them in section \ref{sec:metis-language-and-proofs}
-and in the section \ref{sec:proof-reconstruction}.
+From our experience building a proof reconstruction tool, depending 
+on the systems involved in the translation, some difficulties can 
+arise. We listed some of them in section
+\ref{sec:metis-language-and-proofs} and in the section
+\ref{sec:proof-reconstruction}.
 
@@
 these connectives were treated as right associative and binary
-operators in the \TSTP format but that assumptons is not a standard.
+operators in the \TSTP format but that assumptions is not a standard.
 We had to update the \TSTP parser module introduced in
@@
 However, one of our biggest obstacles
-\improvement{Remove the use of the \emph{biggest obstacules}.}
+\improvement{Remove the use of the \emph{biggest obstacles}.}
 was dealing with

### 2017-09-08 paper/sections/proof-reconstruction.tex
[ paper ] section 3 introduction added.

@@
 \begin{figure}
-\begin{tikzpicture}
+\centering
+
+\begin{tikzpicture}[scale=0.9]
 \node[text width=2cm, align=center](problem) at (0,0)
@@
 
-\node[right = 1.2cm of problem, text width=2cm, align=center]
+\node[right = 1.1cm of problem, text width=2cm, align=center]
   (tptp){2. \TPTP \\ Problem.};
 
-\node[right= 1.2cm of tptp, text width=2cm, align=center]
+\node[right= 1.1cm of tptp, text width=2cm, align=center]
    (metis) {3. \Metis \\ Prover.};
 
-\node[right= 1.2cm of metis, text width=2cm, align=center, inner sep=10pt]
+\node[right= 1.1cm of metis, text width=2cm, align=center, inner sep=10pt]
    (tstp) {4. \TSTP \\ Derivation.};
@@
 
-\node[left = 1.2cm of athena, text width=2cm, align=center]
+\node[left = 1.1cm of athena, text width=2cm, align=center]
    (agdafile) {6. \Agda \\ Proof.};
 
-\node[left = 1.2cm of agdafile, text width=2cm, align=center]
-   (agda) {7. Proof Checker.};
+\node[left = 1.1cm of agdafile, text width=2cm, align=center]
+   (agda) {7. Proof Checking.};
 
@@
 \node[below = 0.5cm of verified, text width=2cm, align=center]
-   (failure) {8.2 Error.};
+   (failure) {8.2 Failure.};
 
@@
 \caption{Proof reconstruction overview.}
-\label{fig:proof-reconstruction-overview}
+\label{fig:proof-reconstruction-workflow}
 \end{figure}
 
+The proof reconstruction approach proposed here consists of a series 
+of steps similar to the workflow presented by Sultana in
+\cite{sultana2015}. This process is a translation from a source 
+system to a target system. In our case, the system of origin, the 
+automatic theorem prover, is \Metis; the target system is the proof 
+assistant, \Agda. We choose \Agda, but another proof assistant with 
+support of type theory and features similar like \Agda is valid; our 
+results do not depend on the proof assistant but the support of inductive data types, and termination checking, and type-checking.
+\improvement{Make this statement stronger and clear.}
+
+Following the diagram in Fig.
+\ref{fig:proof-reconstruction-workflow}, the process can begin with 
+a problem in \CPL that we encode in \TPTP format to be sent as the 
+input of the \Metis prover.
+The proof-search algorithms of \Metis in step No. 3 perform a 
+search for a solution; if they success, \Metis 
+replies a derivation in \TSTP format of the proof, else \Metis may 
+no stop running forever or replies the problem is counter feasible.
+
+With such a derivation, we process it with our \Haskell translator 
+tool, \Athena. \Athena parses the \TSTP format, analyze the 
+derivation and generates a representation of the natural deduction 
+proof using a version of a tree data structure (see the properties 
+of this tree in subsection \ref{ssec:metis-proofs}). As a result,
+\Athena generates an \Agda file with such a proof. We have included 
+in this file, imports for \Agda libraries that give the support for 
+the logic~\cite{AgdaProp}, and versions of the \Metis' inference 
+rules~\cite{AgdaMetis}.
+
+Finally, we use the proof assistant in step No. 7 to type-check the 
+proof and verify its correctness. We have only one answer from two 
+possible answers: the type-checking success (i.e., the proof is 
+valid) or not. If the type-check fails, one of the three actors are 
+responsible: \Metis, \Athena, or \Agda. We are responsible for 
+errors committed in the translation from \TSTP to \Agda; lack of the 
+coverage of the \Metis' inference rules, or bad assumptions about 
+them.
+
+In the rest of this section, we provide a formal description using 
+type theory to build definitions and theorems for the functions 
+necessary to emulate the \Metis' inference rules.
+
 \end{document}

### 2017-09-08 paper/main.tex
[ paper ] minor changes, title and abstract.
[ paper ] fixing some mistakes.
[ paper ] fixing error grammars and adding notes.
[ paper ] section 3 introduction added.
[ paper ] appendix added.

@@
-\documentclass[runningheads,a4paper]{llncs}
-
+\documentclass[runningheads, a4paper]{llncs}
 \usepackage{subfiles}
@@
 
-% --------------------------------------------------------------------------
+\usepackage[title]{appendix}
+
+% -------------------------------------------------------------------
 % TODO notes
-% --------------------------------------------------------------------------
+% -------------------------------------------------------------------
 
@@
 
-% --------------------------------------------------------------------------
+% -------------------------------------------------------------------
 % Tikz Configuration
-% --------------------------------------------------------------------------
+% -------------------------------------------------------------------
 
@@
 
-% --------------------------------------------------------------------------
+% -------------------------------------------------------------------
 % Listings
-% --------------------------------------------------------------------------
+% -------------------------------------------------------------------
 
@@
   , belowskip=10pt
-  , keywords=[2]{axiom, conjecture,inference, negated_conjecture, plain, source}
+  , keywords=[2]{axiom
+    , conjecture
+    , inference
+    , negated_conjecture
+    , plain
+    , source}
   , keywords=[3]{fof, cnf}
@@
 
-%\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
 \usepackage{ucs}
@@
 \usepackage{amsmath}
-\usepackage{stmaryrd} %new symbol font for tcs
+%\usepackage{stmaryrd} %new symbol font for tcs
 \usepackage{color}
 \usepackage{fancybox}
+
+\usepackage{textcomp}
+\usepackage[verbose]{newunicodechar}
+\newunicodechar{∧}{\ensuremath{\wedge}}
+\newunicodechar{∨}{\ensuremath{\vee}}
+\newunicodechar{¬}{\ensuremath{\neg}}
+\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
+\newunicodechar{⇔}{\ensuremath{\Leftrightarrow}}
+\newunicodechar{∼}{\ensuremath{\sim}}
+\newunicodechar{₀}{\ensuremath{{}_{0}}}
+\newunicodechar{₁}{\ensuremath{{}_{1}}}
+\newunicodechar{₃}{\ensuremath{{}_{2}}}
+\newunicodechar{₄}{\ensuremath{{}_{3}}}
+\newunicodechar{₅}{\ensuremath{{}_{4}}}
+\newunicodechar{₆}{\ensuremath{{}_{5}}}
+\newunicodechar{₇}{\ensuremath{{}_{6}}}
+\newunicodechar{₈}{\ensuremath{{}_{7}}}
+\newunicodechar{₉}{\ensuremath{{}_{8}}}
+\newunicodechar{∅}{\ensuremath{\emptyset}}
+\newunicodechar{⊢}{\ensuremath{\vdash}}
+\newunicodechar{⊥}{\ensuremath{\bot}}
+\newunicodechar{Γ}{\ensuremath{\Gamma}}
+
+%\DeclareUnicodeCharacter{00A0}{~}
 
@@
 
-% --------------------------------------------------------------------------
+% -------------------------------------------------------------------
 % New commands
-% --------------------------------------------------------------------------
+% -------------------------------------------------------------------
 \usepackage{xspace}
@@
 \newcommand{\Metis}{\prg{Metis}}
+\newcommand{\Athena}{\prg{Athena}}
 \newcommand{\IsabelleHOL}{\prg{IsabelleHOL}}
@@
 
-% --------------------------------------------------------------------------
+% -------------------------------------------------------------------
 % Rest.
-% --------------------------------------------------------------------------
+% -------------------------------------------------------------------
 
@@
 
-\institute{Universidad EAFIT, Logic and Computation Research Group,\\
-Department of Mathematics, Medell\'in, Colombia\\
+\institute{Logic and Computation Research Group,\\
+Universidad EAFIT, Medell\'in, Colombia\\
 \email{\{jprieto9,asr\}@eafit.edu.co}}
@@
 \subfile{sections/metis-language-and-proofs.tex}
-% \subfile{sections/proof-reconstruction.tex}
+\subfile{sections/proof-reconstruction.tex}
+\subfile{sections/conclusions.tex}
 \subfile{sections/related-work.tex}
-\subfile{sections/conclusions.tex}
 \subfile{sections/acknowledgements.tex}
@@
 
+\newpage
+\subfile{sections/appendices.tex}
+
 \end{document}

### 2017-09-08 paper/sections/conclusions.tex
[ paper ] appendix added.

@@
 
-In this document, we attempted to reconstruct proofs
-of propositional logic without equality deliver by \Metis successfully.
+In this document, we reconstruct proofs
+of propositional logic without equality deliver by \Metis 
+successfully.
 
-From our experience building a proof reconstruction tool, depending 
-on the systems involved in the translation, some difficulties can 
-arise. We listed some of them in section
+Despite the fact, our logic domain is more straightforward than 
+first-order or high-order logic where there are many 
+proof-reconstruction tools (see a list of some of them in the 
+related work, section \ref{sec:related-work}), we found some issues 
+around the reconstruction that show this task is far from trivial.
+Depending  on the systems involved in the translation, some 
+difficulties can arise. We listed some of them in section
 \ref{sec:metis-language-and-proofs} and in the section
@@
 
-However, one of our biggest obstacles
-\improvement{Remove the use of the \emph{biggest obstacles}.}
-was dealing with
-the Equality between formulas since, in our approach, we only work
+An important matter was how dealing with
+the equality between formulas since, in our approach, we only work
 with the syntactic treatment of the logic without considering the
 semantics.
-One of the main reasons for such a restriction relay on our plans to
-support further first-order logic, where a semantic treatment is not
-viable.\unsure{Please confirm this.}
+One of the main reasons for such a restriction relay on our plans 
+further to support first-order logic, where a semantic treatment is 
+not viable since it computational complexity.\unsure{Please confirm this.}
 

### 2017-09-08 paper/sections/proof-reconstruction.tex
[ paper ] appendix added.

@@
 With such a derivation, we process it with our \Haskell translator 
-tool, \Athena. \Athena parses the \TSTP format, analyze the 
+tool, \Athena~\cite{Athena}.
+\Athena parses the \TSTP format, analyze the 
 derivation and generates a representation of the natural deduction 
@@
 proof and verify its correctness. We have only one answer from two 
-possible answers: the type-checking success (i.e., the proof is 
-valid) or not. If the type-check fails, one of the three actors are 
+possible answers: type-checking succeed (i.e., the proof is 
+valid) or type-checking failed.
+If the type-check fails, one of the three actors are 
 responsible: \Metis, \Athena, or \Agda. We are responsible for 

### 2017-09-10 paper/sections/conclusions.tex
added text.

@@
 
-Nevertheless, the proof reconstruction is certainly possible, and
+Nevertheless, the proof-reconstruction is certainly possible, and
 the verification of solutions of \CPL problems can be carried out

### 2017-09-10 paper/sections/introduction.tex
[ paper ] section 3 introduction added.
added text.

@@
 
-Proof reconstruction is a hard labor since it depends on the
+proof-reconstruction is a hard labor since it depends on the
 integration of two complex systems. On the one hand, we have the
@@
 
-A proof reconstruction tool provides such an integration translating
+A proof-reconstruction tool provides such an integration translating
 the reply delivered by the prover into the formalism of the proof
@@
 understanding of the algorithms in the \ATP and the specification
-logic in the \ITP. To begin with the proof reconstruction, it is
+logic in the \ITP. To begin with the proof-reconstruction, it is
 necessary to have a proof-object from the \ATP in a consistent
@@
 Many approaches have been proposed and some tools have been
-implemented for proof reconstruction in the last decades. These
+implemented for proof-reconstruction in the last decades. These
 programs are relevant not only because it helps to spread their
@@
 some limitations, advantages, and disadvantages with other similar
-proof reconstruction tools for ending up with some conclusions and the
-future work. Finally, we list some related works in proof reconstruction
-in section \ref{sec:related-work}.
+proof-reconstruction tools for ending up with some conclusions and
+the future work. Finally, we list some related works in proof
+reconstruction in section \ref{sec:related-work}.
 

### 2017-09-10 paper/sections/metis-language-and-proofs.tex
added text.

@@
 justify its deduction steps from the basis of only six inference
-rules. There are already some tools that perform proof reconstruction
+rules. There are already some tools that perform proof-reconstruction
 with \Metis, some of these systems are the following.
@@
 This lack of the \Metis' documentation is an important matter for
-us in the proof reconstruction and certainty for other implementors
+us in the proof-reconstruction and certainty for other implementors
 (see a comment related on the presenting of \name{Sledgehammer}

### 2017-09-10 paper/sections/related-work.tex
[ paper ] appendix added.
added text.

@@
 \cite{Fleury2014}) and \SMT solvers (see, for instance,
-\cite{hurlin07practical}, \cite{bohme2010}, \cite{blanchette2013extending}, and \cite{Fleury2014}) with
+\cite{hurlin07practical}, \cite{bohme2010},
+\cite{blanchette2013extending}, and \cite{Fleury2014}) with
 \name{Isabelle/HOL} \cite{nipkow2002isabelle}, the specialization of
@@
 \name{Satallax}, two theorem provers for high-order logic with
-\name{Isabelle/HOL} proposing a modular proof reconstruction work
+\name{Isabelle/HOL} proposing a modular proof-reconstruction work
 flow.
@@
 \name{SMTCoq}~\cite{armand2011,Ekici2017} is a tool for the
-\name{Coq} proof assistant \cite{coqteam} which provides a certified checker for proof witness coming from the \SMT solver \name{veriT}
+\name{Coq} proof assistant \cite{coqteam} which provides a certified
+checker for proof witness coming from the \SMT solver \name{veriT}
 \cite{bouton2009} and adds a new tactic named verit, that calls
@@
 \cite{foster2011integrating} integrate \name{Waldmeister} into \Agda
-\cite{agdateam}. This integration requires a proof reconstruction
+\cite{agdateam}. This integration requires a proof-reconstruction
 step, but authors' approach is restricted to pure equational logic

### 2017-09-11 paper/sections/metis-language-and-proofs.tex
[ paper ] perliminaries added.

@@
 In \cite{Farber2015}, \Metis was used to provide a tactic for
-\name{HOL Light}; this challenges others like \name{MESON}
-or the \name{leanCoP} tactic that reconstructs proofs
+\name{HOL Light}; this challenges others like \emph{MESON}
+or the \emph{leanCoP} tactic that reconstructs proofs
 delivered by \name{leanCoP}~\cite{Farber2016}.
@@
 The formulas include Boolean connectives (\verb!&!, \verb!|!,
-\verb!=>!, \verb!{<=>!, \verb!~!) and logic constants \verb!$true!
-and \verb!$false!.
+\verb!=>!, \verb!<=>!, \verb!~!) and logic constants \verb!$true!
+and \verb!$false!, for the symbols (∧, ∨, ⇒, ⇔, ¬, ⊤, ⊥), respectively.
 
@@
 \emph{falsium} in the last conclusion of the \TSTP derivation in
-Fig.\ref{fig:metis-example}).
+Fig.~\ref{fig:metis-example}).
 
@@
 
+% -------------------------------------------------------------------
+
+\subsection{Proof Rules}
+\label{ssec:proof-rules}
+
+We noted in \TSTP derivations that \Metis does not take into account
+some inference rules for the \Metis' official documentation; we
+refer to the \Metis' logic kernel.
+Besides the six \Metis' inference rules from the Fig.
+\ref{fig:metis-inferences}, its proof-objects, the \TSTP
+derivations, exhibit an entirely different set of rules.
+
+For instance, for the propositional logic fragment without equality,
+only three rules are valid from the \Metis' Logic Kernel:
+\emph{assume}, \emph{axiom}, and \emph{resolve}. Nevertheless, as we
+observed in \TSTP derivations, for such a propositional fragment,
+\Metis uses in his deductions steps, six rules where only the
+\emph{resolve} inference persists from the original list. In the
+case of \resolve, it differs from its original version since, in
+\TSTP, this rule has by definition an argument, a literal. The other
+undocumented rules found in \TSTP derivations are: \canonicalize,
+\clausify, \conjunct, \negate, \simplify, and \strip.
+
 \begin{figure}
@@
 
-% -------------------------------------------------------------------
-
-\subsection{Proof Rules}
-\label{ssec:proof-rules}
-
-We noted in \TSTP derivations that \Metis does not take into account
-some inference rules for the \Metis' official documentation; we
-refer to the \Metis' logic kernel.
-Besides the six \Metis' inference rules from the Fig.
-\ref{fig:metis-inferences}, its proof-objects, the \TSTP
-derivations, exhibit an entirely different set of rules.
-
-For instance, for the propositional logic fragment without equality,
-only three rules are valid from the \Metis' Logic Kernel:
-\emph{assume}, \emph{axiom}, and \emph{resolve}. Nevertheless, as we
-observed in \TSTP derivations, for such a propositional fragment,
-\Metis uses in his deductions steps, six rules where only the
-\emph{resolve} inference persists from the original list. In the
-case of \resolve, it differs from its original version since, in
-\TSTP, this rule has by definition an argument, a literal. The other
-undocumented rules found in \TSTP derivations are: \canonicalize,
-\clausify, \conjunct, \negate, \simplify, and \strip.
-
 This lack of the \Metis' documentation is an important matter for
@@
 a lot between two steps.}
-That inference' behavior has become a drawback since, our approach
+That inference' behavior is a drawback since, our approach
 to reconstruct proofs needs take into account any assumption or

### 2017-09-11 paper/sections/preliminaries.tex
[ paper ] perliminaries added.

% -*- root: main.tex -*-
\documentclass[../main.tex]{subfiles}
\begin{document}

% ===================================================================

\section{Preliminaries}
\label{sec:preliminaries}

Before describe the proof reconstruction, we need some definitions
and some convention notations.

\subsection{Classical Propositional Logic}
\label{ssec:CPL}

\textit{Propositions.}
We define the classical propositional logic as usual.
A proposition is an expression of indivisible propositional atoms
(e.g., symbols $φ₀, φ₁, \cdots$),
binary logic connectives ($∧, ∨, ⇒, ⇔)$,
propositional negation $(\neg)$, and logic constants $\bot$
and $\top$. We use the inductive definition of the set \PROP
defined in \cite{VanDalen1994} as the mechanism to produce any
propositional formula.
Then, $ϕ_i \in \PROP$ for all $i \in \mathbb{N}$.
If $(\phi\ \square\ \psi)$ stands for a proposition that use a
binary connective where is the symbol $\square$; when $\phi, \psi\in
\PROP$, then $(\phi\ \square\ \psi) \in \PROP$.
If $\phi \in \PROP$, then $(\neg \phi) \in \PROP$.
Finally, $\bot, \top \in \PROP$.

\emph{Derivations.}
A derivation of $φ$ is a mechanism to obtain the conclusion φ from
the application of some deduction steps. Such a deduction step has
the form of a set of propositional \emph{premises} that conclude the
result: one or more propositions. As we show in the following
figure, the premises are always above the line, and the conclusions
are below it. As a notation convention, if the name of a rule used
in the derivation step is typed using verbatim, that means, it is
available in our implementation for the CPL (see the syntax module in
\cite{AgdaProp}) used in the proof reconstruction latter.

\[
\label{eq:derivation}
\begin{bprooftree}
\AxiomC{φ}
\AxiomC{ψ}
\BinaryInfC{φ ∧ ψ}
\end{bprooftree}\qquad
\begin{bprooftree}
\AxiomC{[¬ φ]}
\noLine
\UnaryInfC{$\vdots$}
\noLine
\UnaryInfC{⊥}
\RightLabel{\abbre{RAA}}
\UnaryInfC{φ}
\end{bprooftree}
\]

\vskip 2mm

\emph{Theorems.}
A sequent $Γ ⊢ φ$ represents a theorem, but we
define it as a relation between a set of propositions premises $Γ$,
and $φ$ as the sequent's conclusion.
The symbol $⊢$ is called turnstile.
If $Γ = ∅$, we write $⊢ φ$, and we say that $φ$ is a theorem
Then, a theorem, $Γ ⊢ φ$ , means that there is a derivation with
conclusion $φ$ and with all (uncancelled) hypotheses in $Γ$.

\emph{Postulates.}
We only postulate the principle of excluded third
(\abbre{PEM}), $φ ∨ ¬ φ$. From there, we derive the
\emph{reductio ad absurdum} rule (\abbre{RAA}) as the
formulation of the principle of proof by contradiction: a derivation
of a contradiction, $⊥$, from the hypothesis $(¬ φ)$, is a
derivation of $φ$.

\[
\label{eq:PEM-RAA}
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt PEM}
\UnaryInfC{Γ ⊢ φ ∨ ¬ φ}
\end{bprooftree}\qquad
\begin{bprooftree}
\AxiomC{Γ, ¬ φ ⊢ ⊥}
\RightLabel{\scriptsize\tt RAA}
\UnaryInfC{Γ ⊢ φ}
\end{bprooftree}
\]

\emph{Natural Deductions.}
The natural deduction designed by Gentzen \improvement{Cite the work
by Gentzen.} defines a formal system for derivations that uses a set
of inference rules as the only way to obtain a conclusion.
We use this system to refer to formal proofs as natural deduction
proofs and conversely, in the latter.
We define our inference rules for \CPL in the Fig.
\ref{fig:CPL-inference-rules}. These rules give us the complete
meaning of the connectives; how to introduce them and
how they can be remove them in the conclusion side of the theorems.

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt assume $\varphi$}
\UnaryInfC{$\Gamma , \varphi \vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt weaken $\psi$}
\UnaryInfC{$\Gamma , \psi \vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt $\top$-intro}
\UnaryInfC{$\Gamma \vdash \top$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \bot$}
\RightLabel{\scriptsize\tt $\bot$-elim $\varphi$}
\UnaryInfC{$\Gamma \vdash \varphi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \bot$}
\RightLabel{\scriptsize\tt $\neg$-intro}
\UnaryInfC{$\Gamma \vdash \neg \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg \varphi$}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\neg$-elim}
\BinaryInfC{$\Gamma \vdash \bot$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \psi$}
\RightLabel{\scriptsize\tt $\wedge$-intro}
\BinaryInfC{$\Gamma \vdash \varphi \wedge \psi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
\RightLabel{\scriptsize\tt $\wedge$-proj$_1$}
\UnaryInfC{$\Gamma\vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
\RightLabel{\scriptsize\tt $\wedge$-proj$_2$}
\UnaryInfC{$\Gamma\vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\vee$-intro$_1$ $\psi$}
\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \psi$}
\RightLabel{\scriptsize\tt $\vee$-intro$_2$ $\varphi$}
\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma ,\varphi \vdash \gamma $}
\AxiomC{$\Gamma , \psi  \vdash \gamma$}
\RightLabel{\scriptsize\tt $\vee$-elim}
\BinaryInfC{$\Gamma , \varphi \vee \psi \vdash \gamma$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \psi$}
\RightLabel{\scriptsize\tt $\Rightarrow$-intro}
\UnaryInfC{$\Gamma \vdash \varphi \Rightarrow \psi$}
\end{bprooftree}
%}
\]

\[
%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\Rightarrow$-elim}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \psi$}
\AxiomC{$\Gamma , \psi \vdash \varphi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-intro}
\BinaryInfC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\end{bprooftree}
%}
\]

\[
%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_1$}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_2$}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}
%}
\]

\caption{Inference rules in classical propositional logic.}
\label{fig:CPL-inference-rules}
\end{figure}

\emph{Proof Trees.} We use trees to represent derivations and
natural deduction proofs. In a proof tree, the root is the
conclusion of the entire derivation. The nodes labeled with
the name of the inference rules contains the result of applying the
rule to their parents. The leaves in the tree become the premises,
not all necessary canceled (see a better discussion on cancellation
of hypotheses in \cite{VanDalen1994}).
\improvement{Include a tree of a proof tree.}
\end{document}

### 2017-09-11 paper/sections/proof-reconstruction.tex
added text.
[ paper ] perliminaries added.

@@
 
-\section{Proof Reconstruction}
+\section{Proof-Reconstruction}
 \label{sec:proof-reconstruction}
+
+\subsection{Workflow}
+\label{ssec:workflow}
 
@@
 \end{tikzpicture}
-\caption{Proof reconstruction overview.}
+\caption{proof-reconstruction overview.}
 \label{fig:proof-reconstruction-workflow}
@@
 
-The proof reconstruction approach proposed here consists of a series 
+The proof-reconstruction approach proposed here consists of a series
 of steps similar to the workflow presented by Sultana in
@@
 support of type theory and features similar like \Agda is valid; our
-results do not depend on the proof assistant but the support of inductive data types, and termination checking, and type-checking.
-\improvement{Make this statement stronger and clear.}
+results do not depend on the proof assistant but the support of
+inductive data types, termination checking, and type-checking.
 
@@
 Finally, we use the proof assistant in step No. 7 to type-check the
-proof and verify its correctness. We have only one answer from two 
-possible answers: type-checking succeed (i.e., the proof is 
-valid) or type-checking failed.
-If the type-check fails, one of the three actors are 
+proof and verify its correctness. Next, we only have one answer:
+type-checking succeed (i.e., the proof is valid) or type-checking failed.
+If the type-check fails, one of the three actors in the process are
 responsible: \Metis, \Athena, or \Agda. We are responsible for
@@
 coverage of the \Metis' inference rules, or bad assumptions about
-them.
+them. \improvement{Make this statement stronger and clear.}
 
@@
 
+% ...................................................................
+
+% \footnote{We use the \Agda standard library's implementation of the List data type.}.
+
+\subsection{A Brief Review of Agda}
+\label{ssec:agda-definition}
+
+\Agda is an interactive system for constructing proofs and programs,
+based on Martin-L\"{o}f's type theory and extended with records, parametrised
+modules, among other features.
+One of the main strengths of \Agda is its support for writing proofs,
+which we shall call \Agda's proof engine. It consists of: support for
+inductively defined types, including inductive families, and function
+definitions using pattern matching on such types, normalisation during type-
+checking, commands for refining proof terms, coverage checker and termination
+checker.
+
+The inductive approach for representing classical propositional logic
+is better because we benefit from \Agda's proof engine and its Unicode
+support that allows us writing proofs similar as we find in math text books.
+
+In \Agda, we define a proposition formula
+as an inductive type using the keyword \texttt{data}.
+The \name{PropFormula} data type stands for propositions,\cite{Altenkirch2015}.
+We include every connective, logic constant as a constructor.
+We also define the constructor for atomic propositions \verb!Var!
+to represent based on a natural number $i$, the atomic proposition
+$p_i$ for a finite universe of them ($i \leq n$), this is $Fin n$ in the
+definition.
+
+\begin{verbatim}
+data PropFormula : Set where
+  Var : Fin n → PropFormula
+  ⊤ : PropFormula
+  ⊥ : PropFormula
+  _∧_ _∨_ _⇒_ _⇔_ : (φ ψ : PropFormula) → PropFormula
+  ¬_ : (φ : PropFormula) → PropFormula
+\end{verbatim}
+
+\begin{remark}
+In the above definition, we defined all connectives, execept negation, as
+a binary connective. In \Agda, we named constructors for those functions
+that inhabit the data type, for example, the boolean connecetives and
+the function for atomic propositions, \verb!Var!, are constructors.
+The underscores in a definition like
+\begin{verbatim}
+_⇔_ : (φ ψ : PropFormula) → PropFormula
+\end{verbatim}
+stands for an argument, and \verb!(φ ψ : PropFormula)! intend for the
+uncurryfied version of the type:
+$$PropFormula → PropFormula → PropFormula$$
+\end{remark}
+
+\begin{definition}(Negative Normal Form (NNF))
+Una forma normal negativa para la formula $\varphi$ es aquella
+en la cual negaciones aparecen solamente en los literales y
+la expresión se encuentra en términos unicamente
+de los operadores booleanos ($\neg$, $\wedge$, $\vee$).
+\end{definition}
+
+Para transformar una formula $\varphi$ a su forma equivalente NNF,
+aplicamos recursivamente las siguientes ecuaciones que definen
+la función \name{nnf}.
+
+\begin{equation}
+\label{eq:nnf-definition}
+\nnf(φ) =
+\begin{cases}
+\nnf(φ₁) ∧ \nnf(φ₂)
+   & φ := φ₁ ∧ φ₂  \\
+
+\nnf(φ₁) ∨ \nnf(φ₂)
+   & φ := φ₁ ∨ φ₂  \\
+
+\nnf(¬ φ₁ ∨ φ₂)
+   & φ := φ₁ ⇒ φ₂  \\
+
+\nnf(φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁)
+   & φ := φ₁ ⇔ φ₂\\
+
+\nnf(¬ φ₁ ∨ ¬ φ₂)
+   & φ := ¬ (φ₁ ∧ φ₂) \\
+
+\nnf(¬ φ₁ ∧ ¬ φ₂)
+   & φ := ¬ (φ₁ ∨ φ₂) \\
+
+\nnf(φ₁)
+   & φ := ¬ ¬ φ₁     \\
+
+\nnf(¬ (φ₂ ∨ ¬ φ₁))
+   & φ := ¬ (φ₁ ⇒ φ₂)  \\
+
+\nnf(¬ (φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁))
+   & φ := ¬ (φ₁ ⇔ φ₂) \\
+
+⊥  & φ := ¬ ⊤        \\
+
+⊤  & φ := ¬ ⊥        \\
+
+φ  & \text{otherwise}
+\end{cases}
+\end{equation}
+
+\begin{definition}
+Una funcion recursiva se dice bien estructura, si el tamaño de los argumentos
+con que con esta se define se reducen en tamaño por cada llamada a la
+funcion.
+\end{definition}
+
+De la anterior definincion, sintacticamente la funcion nnf no es recursivamente
+bien estructurado. El problem que no lo sea esta en nuestra traducion
+de este tipo de funciones a la teoria de tipos.
+
+Veamos otros ejemplos de funciones con el mismo problema que utilizaremos mas
+adelante para formalizar la inferencia strip.
+
+\begin{equation}
+\label{eq:unshunt-definition}
+\unshunt(φ) =
+\begin{cases}
+\unshunt((φ₁ ∧ φ₂) ⇒ φ₃)
+  & φ := φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+
+\unshunt(φ₁ ⇒ φ₂) ∧ \unshunt(φ₁ ⇒ φ₃)
+  & φ := φ₁ ⇒ (φ₂ ∧ φ₃)\\
+
+φ &\text{otherwise}
+\end{cases}
+\end{equation}
+
+Para traducir las funciones en un manera que esten bien definidas,
+utilizamos el metodo propuesto por Ana Bove, el cual basicamente consiste
+
+una funcion general recursiva $f:\sigma \to \tau$, su formalizacion en
+teoria de tipos consiste en definir un predicado inductivo $Ind$,
+$P:\sigma \to Ind$
+
+En nuestro caso, el conjunto de los numeros servira como nuestro
+conjunto inductivo y como segundo argumento para nueva funcion.
+De manera, que la funcion g estara definida por recursion estructural en
+su segundo termino.
+
+Para aplicar la tecnica antes mencionada para nuestras funciones,
+veamos su aplicación con la funcion \unshunt porque para las demas,
+seguiremos un camino similar, f con tipo:
+
+\[
+\unshunt^{*} : PROP \to \mathcal{N} \to PROP
+\]
+
+\begin{equation}
+\label{eq:unshunt-structured}
+\unshunt^{*}(φ, n) =
+\begin{cases}
+\unshunt^{*}((φ₁ ∧ φ₂) ⇒ φ₃, n-1)
+  & φ := φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+
+\unshunt^{*}(φ₁ ⇒ φ₂, n-1) ∧ \unshunt^{*}(φ₁ ⇒ φ₃,n-1)
+  & φ := φ₁ ⇒ (φ₂ ∧ φ₃)\\
+
+φ & n := 0
+\end{cases}
+\end{equation}
+
+\begin{definition}
+El rango $rank(\phi)$ de una proposition $\phi$ es definido como
+
+\begin{equation}
+\label{eq:rank-definition}
+rank(\phi)=
+\begin{cases}
+0 &\text{for atomic }\phi\\
+
+\max(rank(\phi_1),rank(\phi_2)) + 1
+  & \phi := \phi_1\,\square\, \phi_2 \\
+rank(\phi_1) + 1  & \phi := \neg \phi_1
+\end{cases}
+\end{equation}
+
+\end{definition}
+
+Then, we our final revision for the function $\unshunt$ is the
+function$\unshunt^{+}$ with type $PROP \to PROP$
+with a structured recursion,
+
+\begin{equation}
+\unshunt^{+}(\varphi) = \unshunt^{*}(\varphi, rank(\varphi))
+\end{equation}
+
+In the following section, our task will consist of a searching
+appropriate functions like $rank$ to assure the termination of
+our transformation functions like $nnf$.
+
+% ................................................
+
+\subsection{Splitting the goal}
+
+\begin{equation}
+\label{eq:split-definition}
+\mysplit(φ) =
+\begin{cases}
+\unshunt(\mysplit(φ₁)) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂)
+  & φ := φ₁ ∧ φ₂\\
+
+\unshunt(¬ φ₁ ⇒ \mysplit(φ₂))
+  & φ := φ₁ ∨ φ₂\\
+
+\unshunt(φ₁ ⇒ \mysplit(φ₂))
+  & φ := φ₁ ⇒ φ₂\\
+
+\unshunt(φ₁ ⇒ \mysplit(φ₂)) ∧ \unshunt(φ₂ ⇒ \mysplit(φ₁))
+  & φ := φ₁ ⇔ φ₂\\
+
+\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
+  & φ := ¬ (φ₁ ∧ φ₂)\\
+
+\unshunt(\mysplit(¬ φ₁)) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂))
+  & φ := ¬ (φ₁ ∨ φ₂)\\
+
+\unshunt(\mysplit(φ₁)) ∧ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
+  & φ := ¬ (φ₁ ⇒ φ₂)\\
+
+\unshunt(φ₁ ⇒ \mysplit(¬ φ₂)) ∧ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))
+  & φ := ¬ (φ₁ ⇔ φ₂)\\
+
+\unshunt(\mysplit(φ₁)
+  & φ := ¬ ¬ φ₁\\
+
+⊤ & φ := ¬ ⊥\\
+
+⊥ & φ := ¬ ⊤\\
+
+φ &\text{otherwise}
+\end{cases}
+\end{equation}
+
 \end{document}

### 2017-09-11 paper/sections/implementation.tex
[ paper ] implementation added, some proofs added.

--- 2017-09-08 paper/sections/proof-reconstruction.tex
@@
 
-\section{Proof Reconstruction}
-\label{sec:proof-reconstruction}
+\section{Implementation}
+\label{sec:implementation}
 
-\begin{figure}
-\centering
+\subsection{A Brief Review of Agda}
+\label{ssec:agda-definition}
 
-\begin{tikzpicture}[scale=0.9]
-\node[text width=2cm, align=center](problem) at (0,0)
-  {1. CPL \\ Problem.};
+\Agda is an interactive system for constructing proofs and programs,
+based on Martin-L\"{o}f's type theory and extended with records, parametrised
+modules, among other features.
+One of the main strengths of \Agda is its support for writing proofs,
+which we shall call \Agda's proof engine. It consists of: support for
+inductively defined types, including inductive families, and function
+definitions using pattern matching on such types, normalisation during type-
+checking, commands for refining proof terms, coverage checker and termination
+checker.
 
-\node[right = 1.1cm of problem, text width=2cm, align=center]
-  (tptp){2. \TPTP \\ Problem.};
+The inductive approach for representing classical propositional logic
+is better because we benefit from \Agda's proof engine and its Unicode
+support that allows us writing proofs similar as we find in math text books.
 
-\node[right= 1.1cm of tptp, text width=2cm, align=center]
-   (metis) {3. \Metis \\ Prover.};
+In \Agda, we define a proposition formula
+as an inductive type using the keyword \texttt{data} extending the
+its definition in \cite{Altenkirch2015}.  
+The \name{PropFormula} data type stands for propositions
+as we define in section \ref{sec:preliminaries}.
+We include every connective and logic constant as a constructor.
+We also define the constructor for atomic propositions denoted by
+\verb!Var!. This atomic expressions are represented using a natural 
+number $i$ bounded by a size of the universe $n$ for those atomic 
+propositions (in \Agda, we use the data type \verb!Fin! from the 
+standard  library for such a purpose).
 
-\node[right= 1.1cm of metis, text width=2cm, align=center, inner sep=10pt]
-   (tstp) {4. \TSTP \\ Derivation.};
+\begin{verbatim}
+data PropFormula : Set where
+  Var : Fin n → PropFormula
+  ⊤ : PropFormula
+  ⊥ : PropFormula
+  _∧_ _∨_ _⇒_ _⇔_ : (φ ψ : PropFormula) → PropFormula
+  ¬_ : (φ : PropFormula) → PropFormula
+\end{verbatim}
 
-\node[below= 0.5cm of tstp, text width=2cm, align=center, inner sep=10pt]
-  (athena) {5. \Haskell \\ Traslator.};
+\begin{remark}
+The underscores in the above definition denote holes for a function of arity equivalent to the number of such holes.
+\end{remark}
 
-\node[left = 1.1cm of athena, text width=2cm, align=center]
-   (agdafile) {6. \Agda \\ Proof.};
+\begin{remark}
+The type notation
+\begin{verbatim}
+_⇔_ : (φ ψ : PropFormula) → PropFormula
+\end{verbatim}
+is a syntax sugar for the type
+\begin{verbatim}
+PropFormula → PropFormula → PropFormula.
+\end{verbatim}
+\end{remark}
 
-\node[left = 1.1cm of agdafile, text width=2cm, align=center]
-   (agda) {7. Proof Checking.};
+\begin{example}
+Using Unicode translating a proposition from a textbook to \Agda 
+using the above data type is straightforward. 
+\begin{verbatim}
+r : PropFormula
+p = Var (# 0)
+q = Var (# 1)
+r = Var (# 2)
 
-\node[below = 0.5cm of problem, text width=2cm, align=center]
-   (verified) {8.1 Proof \\ Checked.};
-
-\node[below = 0.5cm of verified, text width=2cm, align=center]
-   (failure) {8.2 Failure.};
-
-% node[below] {send to}
-\draw[->, thick] (problem) to
-  % node[below] {\tiny encoding}
-  (tptp);
-\draw[->, thick] (tptp) to
-  % node[below] {\tiny }
-  (metis);
-\draw[->, thick] (metis) to
-  % node[below] {\tiny replies on}
-  (tstp);
-\draw[->, thick] (tstp) to
-  % node[right] {\tiny parsing}
-  (athena);
-\draw[->, thick] (athena) to
-  % node[below] {\tiny traslation}
-  (agdafile);
-\draw[->, thick] (agdafile) to
-  % node[below] {\tiny type-checking}
-  (agda);
-\draw[->, thick] (agda) to (verified);
-\draw[->, thick, gray] (agda) to (failure);
-\end{tikzpicture}
-\caption{Proof reconstruction overview.}
-\label{fig:proof-reconstruction-workflow}
-\end{figure}
-
-The proof reconstruction approach proposed here consists of a series 
-of steps similar to the workflow presented by Sultana in
-\cite{sultana2015}. This process is a translation from a source 
-system to a target system. In our case, the system of origin, the 
-automatic theorem prover, is \Metis; the target system is the proof 
-assistant, \Agda. We choose \Agda, but another proof assistant with 
-support of type theory and features similar like \Agda is valid; our 
-results do not depend on the proof assistant but the support of inductive data types, and termination checking, and type-checking.
-\improvement{Make this statement stronger and clear.}
-
-Following the diagram in Fig.
-\ref{fig:proof-reconstruction-workflow}, the process can begin with 
-a problem in \CPL that we encode in \TPTP format to be sent as the 
-input of the \Metis prover.
-The proof-search algorithms of \Metis in step No. 3 perform a 
-search for a solution; if they success, \Metis 
-replies a derivation in \TSTP format of the proof, else \Metis may 
-no stop running forever or replies the problem is counter feasible.
-
-With such a derivation, we process it with our \Haskell translator 
-tool, \Athena. \Athena parses the \TSTP format, analyze the 
-derivation and generates a representation of the natural deduction 
-proof using a version of a tree data structure (see the properties 
-of this tree in subsection \ref{ssec:metis-proofs}). As a result,
-\Athena generates an \Agda file with such a proof. We have included 
-in this file, imports for \Agda libraries that give the support for 
-the logic~\cite{AgdaProp}, and versions of the \Metis' inference 
-rules~\cite{AgdaMetis}.
-
-Finally, we use the proof assistant in step No. 7 to type-check the 
-proof and verify its correctness. We have only one answer from two 
-possible answers: the type-checking success (i.e., the proof is 
-valid) or not. If the type-check fails, one of the three actors are 
-responsible: \Metis, \Athena, or \Agda. We are responsible for 
-errors committed in the translation from \TSTP to \Agda; lack of the 
-coverage of the \Metis' inference rules, or bad assumptions about 
-them.
-
-In the rest of this section, we provide a formal description using 
-type theory to build definitions and theorems for the functions 
-necessary to emulate the \Metis' inference rules.
+φ : PropFormula
+φ = (¬ r ∨ p) ∧ (¬ r ∨ q)
+\end{verbatim}
+\end{example}
 

### 2017-09-11 paper/sections/introduction.tex
[ paper ] implementation added, some proofs added.

@@
 
-proof-reconstruction is a hard labor since it depends on the
+Proof-reconstruction is a hard labor since it depends on the
 integration of two complex systems. On the one hand, we have the
@@
 \ATPs~\cite{Keller2013}, \cite{Bohme2011}, \cite{Fleury2014} and
-\cite{Kanso2012}). We mention some of these tools in the related work,
-section \ref{sec:related-work}.
+\cite{Kanso2012}). We mention some of these tools in the related 
+work, section \ref{sec:related-work}.
 
@@
 proof assistant \Agda by parsing \TSTP derivations to generate \Agda
-proof-terms. We structure the paper as follows. In section
-\ref{sec:metis-language-and-proofs}, we briefly introduce the \Metis
-prover. In section \ref{sec:proof-reconstruction}, we present our
+proof-terms. We structure the paper as follows. 
+We briefly mention notation and syntax of the classical propositional
+logic in section \ref{sec:preliminaries}.
+In section \ref{sec:metis-language-and-proofs}, we introduce the
+\Metis prover and its deduction system.
+In section \ref{sec:proof-reconstruction}, we present our
 approach to reconstruct proofs deliver by \Metis in type theory.
-In section~\ref{sec:conclusions}, we discuss
-some limitations, advantages, and disadvantages with other similar
-proof-reconstruction tools for ending up with some conclusions and
-the future work. Finally, we list some related works in proof
-reconstruction in section \ref{sec:related-work}.
+We listed some conclusions and future work in section
+\ref{sec:conclusions}. At the end, we list some related works in 
+proof reconstruction in section \ref{sec:related-work}.
+The appendix \textsc{A} shows a complete example of the proof 
+reconstruction workflow.
 

### 2017-09-11 paper/sections/metis-language-and-proofs.tex
[ paper ] implementation added, some proofs added.

@@
 syntax describes a well-defined grammar to handle annotated formulas
-with the following form,
+with the following form.
 
@@
 For instance, let us express the problem
-$p\, \vdash \neg (p \wedge \neg p) \vee (q \vee \neg q)$
+$p\, \vdash \neg (p \wedge \neg p) \vee (q \wedge \neg q)$
 in \TPTP syntax as follows, declaring an \tptpaxiom $p$, and the
@@
 parent formulas. The root is the final derived formula. Such a
-derivation is a list of annotated formulas with the form,
+derivation is a list of annotated formulas with the form.
 
@@
 The \name{source} field is an inference record with the following
-pattern,
+pattern.
 
@@
 \end{bprooftree}
-\caption{The \Metis' refutation tree for $p \vdash p$ from the
+\caption{The \Metis' proof tree for $p \vdash p$ from the
 derivation in Fig.~\ref{fig:metis-proof-tstp}}

### 2017-09-11 paper/sections/preliminaries.tex
[ paper ] implementation added, some proofs added.

@@
 binary logic connectives ($∧, ∨, ⇒, ⇔)$,
-propositional negation $(\neg)$, and logic constants $\bot$
-and $\top$. We use the inductive definition of the set \PROP
+propositional negation $(¬)$, and logic constants $⊥$
+and $⊤$. We use the inductive definition of the set \PROP
 defined in \cite{VanDalen1994} as the mechanism to produce any
@@
 Then, $ϕ_i \in \PROP$ for all $i \in \mathbb{N}$.
-If $(\phi\ \square\ \psi)$ stands for a proposition that use a
-binary connective where is the symbol $\square$; when $\phi, \psi\in
-\PROP$, then $(\phi\ \square\ \psi) \in \PROP$.
-If $\phi \in \PROP$, then $(\neg \phi) \in \PROP$.
-Finally, $\bot, \top \in \PROP$.
+If $(φ\ \square\ ψ)$ stands for a proposition that use a
+binary connective where is the symbol $\square$; when $φ, ψ\in
+\PROP$, then $(φ\ \square\ ψ) \in \PROP$.\change{rewrite this}
+If $φ \in \PROP$, then $(¬ φ) \in \PROP$.
+Finally, $⊥, ⊤ \in \PROP$.
 
 \emph{Derivations.}
-A derivation of $φ$ is a mechanism to obtain the conclusion φ from
+A derivation of $φ$ is a mechanism to obtain the conclusion $φ$ from
 the application of some deduction steps. Such a deduction step has
@@
 in the derivation step is typed using verbatim, that means, it is
-available in our implementation for the CPL (see the syntax module in
-\cite{AgdaProp}) used in the proof reconstruction latter.
+available in our implementation for the \CPL (see the syntax module 
+in \cite{AgdaProp}) used in the proof reconstruction latter.
 
@@
 The symbol $⊢$ is called turnstile.
-If $Γ = ∅$, we write $⊢ φ$, and we say that $φ$ is a theorem
+If $Γ = ∅$, we write $⊢ φ$, and we say that $φ$ is a theorem.
 Then, a theorem, $Γ ⊢ φ$ , means that there is a derivation with
@@
 
+\label{eq:PEM-RAA}
 \[
-\label{eq:PEM-RAA}
 \begin{bprooftree}
-\AxiomC{}
+\AxiomC{\ }
 \RightLabel{\scriptsize\tt PEM}
 \UnaryInfC{Γ ⊢ φ ∨ ¬ φ}
-\end{bprooftree}\qquad
+\end{bprooftree}
+\qquad
 \begin{bprooftree}
@@
 \end{bprooftree}
+\qquad
 \]
@@
 \AxiomC{}
-\RightLabel{\scriptsize\tt assume $\varphi$}
-\UnaryInfC{$\Gamma , \varphi \vdash \varphi$}
+\RightLabel{\scriptsize\tt assume $φ$}
+\UnaryInfC{$Γ , φ ⊢ φ$}
 \end{bprooftree}\quad
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt weaken $\psi$}
-\UnaryInfC{$\Gamma , \psi \vdash \varphi$}
+\AxiomC{$Γ ⊢ φ$}
+\RightLabel{\scriptsize\tt weaken $ψ$}
+\UnaryInfC{$Γ , ψ ⊢ φ$}
 \end{bprooftree}\quad
@@
 \AxiomC{}
-\RightLabel{\scriptsize\tt $\top$-intro}
-\UnaryInfC{$\Gamma \vdash \top$}
+\RightLabel{\scriptsize\tt $⊤$-intro}
+\UnaryInfC{$Γ ⊢ ⊤$}
 \end{bprooftree}\quad
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \bot$}
-\RightLabel{\scriptsize\tt $\bot$-elim $\varphi$}
-\UnaryInfC{$\Gamma \vdash \varphi$}
+\AxiomC{$Γ ⊢ ⊥$}
+\RightLabel{\scriptsize\tt $⊥$-elim $φ$}
+\UnaryInfC{$Γ ⊢ φ$}
 \end{bprooftree}
@@
 \begin{bprooftree}
-\AxiomC{$\Gamma , \varphi \vdash \bot$}
-\RightLabel{\scriptsize\tt $\neg$-intro}
-\UnaryInfC{$\Gamma \vdash \neg \varphi$}
+\AxiomC{$Γ , φ ⊢ ⊥$}
+\RightLabel{\scriptsize\tt $¬$-intro}
+\UnaryInfC{$Γ ⊢ ¬ φ$}
 \end{bprooftree}\quad
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \neg \varphi$}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\neg$-elim}
-\BinaryInfC{$\Gamma \vdash \bot$}
+\AxiomC{$Γ ⊢ ¬ φ$}
+\AxiomC{$Γ ⊢ φ$}
+\RightLabel{\scriptsize\tt $¬$-elim}
+\BinaryInfC{$Γ ⊢ ⊥$}
 \end{bprooftree}\quad
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\AxiomC{$\Gamma \vdash \psi$}
+\AxiomC{$Γ ⊢ φ$}
+\AxiomC{$Γ ⊢ ψ$}
 \RightLabel{\scriptsize\tt $\wedge$-intro}
-\BinaryInfC{$\Gamma \vdash \varphi \wedge \psi$}
+\BinaryInfC{$Γ ⊢ φ \wedge ψ$}
 \end{bprooftree}
@@
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
+\AxiomC{$Γ ⊢ φ \wedge ψ$}
 \RightLabel{\scriptsize\tt $\wedge$-proj$_1$}
-\UnaryInfC{$\Gamma\vdash \varphi$}
+\UnaryInfC{$Γ⊢ φ$}
 \end{bprooftree}\quad
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
+\AxiomC{$Γ ⊢ φ \wedge ψ$}
 \RightLabel{\scriptsize\tt $\wedge$-proj$_2$}
-\UnaryInfC{$\Gamma\vdash \psi$}
+\UnaryInfC{$Γ⊢ ψ$}
 \end{bprooftree}\quad
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\vee$-intro$_1$ $\psi$}
-\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
+\AxiomC{$Γ ⊢ φ$}
+\RightLabel{\scriptsize\tt $\vee$-intro$_1$ $ψ$}
+\UnaryInfC{$Γ ⊢ φ \vee ψ$}
 \end{bprooftree}
@@
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \psi$}
-\RightLabel{\scriptsize\tt $\vee$-intro$_2$ $\varphi$}
-\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
+\AxiomC{$Γ ⊢ ψ$}
+\RightLabel{\scriptsize\tt $\vee$-intro$_2$ $φ$}
+\UnaryInfC{$Γ ⊢ φ \vee ψ$}
 \end{bprooftree}\quad
 \begin{bprooftree}
-\AxiomC{$\Gamma ,\varphi \vdash \gamma $}
-\AxiomC{$\Gamma , \psi  \vdash \gamma$}
+\AxiomC{$Γ ,φ ⊢ \gamma $}
+\AxiomC{$Γ , ψ  ⊢ \gamma$}
 \RightLabel{\scriptsize\tt $\vee$-elim}
-\BinaryInfC{$\Gamma , \varphi \vee \psi \vdash \gamma$}
+\BinaryInfC{$Γ , φ \vee ψ ⊢ \gamma$}
 \end{bprooftree}\quad
 \begin{bprooftree}
-\AxiomC{$\Gamma , \varphi \vdash \psi$}
+\AxiomC{$Γ , φ ⊢ ψ$}
 \RightLabel{\scriptsize\tt $\Rightarrow$-intro}
-\UnaryInfC{$\Gamma \vdash \varphi \Rightarrow \psi$}
+\UnaryInfC{$Γ ⊢ φ \Rightarrow ψ$}
 \end{bprooftree}
@@
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
-\AxiomC{$\Gamma \vdash \varphi$}
+\AxiomC{$Γ ⊢ φ \Rightarrow ψ$}
+\AxiomC{$Γ ⊢ φ$}
 \RightLabel{\scriptsize\tt $\Rightarrow$-elim}
-\BinaryInfC{$\Gamma \vdash \psi$}
+\BinaryInfC{$Γ ⊢ ψ$}
 \end{bprooftree}\quad
 \begin{bprooftree}
-\AxiomC{$\Gamma , \varphi \vdash \psi$}
-\AxiomC{$\Gamma , \psi \vdash \varphi$}
-\RightLabel{\scriptsize\tt $\Leftrightarrow$-intro}
-\BinaryInfC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
+\AxiomC{$Γ , φ ⊢ ψ$}
+\AxiomC{$Γ , ψ ⊢ φ$}
+\RightLabel{\scriptsize\tt $⇔$-intro}
+\BinaryInfC{$Γ ⊢ φ ⇔ ψ$}
 \end{bprooftree}
@@
 \[
-%\scalebox{0.9}{
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
-\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_1$}
-\BinaryInfC{$\Gamma \vdash \psi$}
-\end{bprooftree}\quad
+\AxiomC{$Γ ⊢ φ$}
+\AxiomC{$Γ ⊢ φ ⇔ ψ$}
+\RightLabel{\scriptsize\tt $⇔$-elim$_1$}
+\BinaryInfC{$Γ ⊢ ψ$}
+\end{bprooftree}
+\qquad
 \begin{bprooftree}
-\AxiomC{$\Gamma \vdash \varphi$}
-\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
-\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_2$}
-\BinaryInfC{$\Gamma \vdash \psi$}
+\AxiomC{$Γ ⊢ φ$}
+\AxiomC{$Γ ⊢ φ ⇔ ψ$}
+\RightLabel{\scriptsize\tt $⇔$-elim$_2$}
+\BinaryInfC{$Γ ⊢ ψ$}
 \end{bprooftree}
-%}
 \]
@@
 \emph{Proof Trees.} We use trees to represent derivations and
-natural deduction proofs. In a proof tree, the root is the
-conclusion of the entire derivation. The nodes labeled with
-the name of the inference rules contains the result of applying the
-rule to their parents. The leaves in the tree become the premises,
-not all necessary canceled (see a better discussion on cancellation
-of hypotheses in \cite{VanDalen1994}).
-\improvement{Include a tree of a proof tree.}
+natural deduction proofs (see for instance, the proof tree in a
+\Metis' derivation in Fig.~\ref{fig:metis-example}).
+In a proof tree, the root is the conclusion of the entire 
+derivation. The nodes labeled with the name of the inference rule 
+contains the result of applying that rule to their parents. Lastly, 
+the leaves in the tree become the premises, not all necessary 
+canceled (see a better discussion on cancellation of hypotheses in
+\cite{VanDalen1994}).
+
 \end{document}

### 2017-09-11 paper/sections/proof-reconstruction.tex
[ paper ] implementation added, some proofs added.

@@
 \node[text width=2cm, align=center](problem) at (0,0)
-  {1. CPL \\ Problem.};
+  {1. \CPL \\ Problem.};
 
@@
 \node[below= 0.5cm of tstp, text width=2cm, align=center, inner sep=10pt]
-  (athena) {5. \Haskell \\ Traslator.};
+  (athena) {5. \Haskell \\ Translator.};
 
@@
 \end{tikzpicture}
-\caption{proof-reconstruction overview.}
+\caption{Proof-reconstruction overview.}
 \label{fig:proof-reconstruction-workflow}
@@
 assistant, \Agda. We choose \Agda, but another proof assistant with
-support of type theory and features similar like \Agda is valid; our
-results do not depend on the proof assistant but the support of
-inductive data types, termination checking, and type-checking.
+support of type theory and similar features like \Agda
+(see a description of \Agda in section
+\ref{sec:implementation}) is valid; our results do not depend on 
+the proof assistant but the support of inductive data types, 
+termination checking, and type-checking.
 
@@
 input of the \Metis prover.
-The proof-search algorithms of \Metis in step No. 3 perform a
-search for a solution; if they success, \Metis
-replies a derivation in \TSTP format of the proof, else \Metis may
-no stop running forever or replies the problem is counter feasible.
+The proof-search algorithms of \Metis in step No. 3 intend to find 
+a solution; if they success, \Metis replies a derivation in \TSTP 
+format of the proof, else \Metis may no stop and running forever or 
+replies the problem is counter feasible.
 
@@
 \Athena generates an \Agda file with such a proof. We have included
-in this file, imports for \Agda libraries that give the support for
-the logic~\cite{AgdaProp}, and versions of the \Metis' inference
-rules~\cite{AgdaMetis}.
+in this file, \emph{imports} that call \Agda libraries that give 
+support for the logic~\cite{AgdaProp}, and versions of the \Metis' 
+inference rules~\cite{AgdaMetis}.
 
@@
 proof and verify its correctness. Next, we only have one answer:
-type-checking succeed (i.e., the proof is valid) or type-checking failed.
+type-checking succeed (i.e., the proof is valid) or type-checking 
+failed.
 If the type-check fails, one of the three actors in the process are
@@
 
+\subsection{Recursion Theorems}
+
+\improvement{Convention notation := for equivalence between propositions}
 % \footnote{We use the \Agda standard library's implementation of the List data type.}.
-
-\subsection{A Brief Review of Agda}
-\label{ssec:agda-definition}
-
-\Agda is an interactive system for constructing proofs and programs,
-based on Martin-L\"{o}f's type theory and extended with records, parametrised
-modules, among other features.
-One of the main strengths of \Agda is its support for writing proofs,
-which we shall call \Agda's proof engine. It consists of: support for
-inductively defined types, including inductive families, and function
-definitions using pattern matching on such types, normalisation during type-
-checking, commands for refining proof terms, coverage checker and termination
-checker.
-
-The inductive approach for representing classical propositional logic
-is better because we benefit from \Agda's proof engine and its Unicode
-support that allows us writing proofs similar as we find in math text books.
-
-In \Agda, we define a proposition formula
-as an inductive type using the keyword \texttt{data}.
-The \name{PropFormula} data type stands for propositions,\cite{Altenkirch2015}.
-We include every connective, logic constant as a constructor.
-We also define the constructor for atomic propositions \verb!Var!
-to represent based on a natural number $i$, the atomic proposition
-$p_i$ for a finite universe of them ($i \leq n$), this is $Fin n$ in the
-definition.
-
-\begin{verbatim}
-data PropFormula : Set where
-  Var : Fin n → PropFormula
-  ⊤ : PropFormula
-  ⊥ : PropFormula
-  _∧_ _∨_ _⇒_ _⇔_ : (φ ψ : PropFormula) → PropFormula
-  ¬_ : (φ : PropFormula) → PropFormula
-\end{verbatim}
-
-\begin{remark}
-In the above definition, we defined all connectives, execept negation, as
-a binary connective. In \Agda, we named constructors for those functions
-that inhabit the data type, for example, the boolean connecetives and
-the function for atomic propositions, \verb!Var!, are constructors.
-The underscores in a definition like
-\begin{verbatim}
-_⇔_ : (φ ψ : PropFormula) → PropFormula
-\end{verbatim}
-stands for an argument, and \verb!(φ ψ : PropFormula)! intend for the
-uncurryfied version of the type:
-$$PropFormula → PropFormula → PropFormula$$
-\end{remark}
 
@@
 
-\subsection{Splitting the goal}
+\subsection{Emulation \Metis' Inference Rules}
 
+\emph{Splitting.}
+We take a goal and generate subgoals that all in a conjunction
+prove the goal.
+
+\begin{theorem}[{\tt thm-$\unshunt^{*}$}] $Γ ⊢ \unshunt^{*}(φ, n)$ for $n\in \mathbb{N}$, then $Γ ⊢ φ$.
+\end{theorem}
+\begin{proof} Use induction on the cases defined by the result of
+$\unshunt^{*}$. When $n = 0$, by definition in Eq.
+\ref{eq:unshunt-structured} then $Γ ⊢ φ$.
+For the first case, we prove $Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)$ from
+$Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$.
+Because $n > 0$, using induction on the second argument and the
+theorem $∧⇒$\texttt{-to-}$⇒⇒$ from \cite{AgdaProp}.
+
+\begin{equation*}
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
+\RightLabel{By definition}
+\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
+\RightLabel{\tt thm-$\unshunt^{*}$}
+\UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
+\RightLabel{\tt ∧⇒-to-⇒⇒}
+\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)}
+\end{bprooftree}
+\end{equation*}
+
+The second case proves $Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)$ from
+ $Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ∧ φ₃), n)$ and the
+theorem $⇒∧⇒$\texttt{-to-}$⇒∧$ from \cite{AgdaProp}
+\begin{equation*}
+\scalebox{0.95}{
+$D_1$ := \begin{bprooftree}
+\AxiomC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂, n) ∧ \unshunt^{*}(φ₁ ⇒ φ₃, n)$}
+\RightLabel{\tt ∧-proj₁}
+\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂, n)$}
+\RightLabel{By definition}
+\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂, n-1)$}
+\RightLabel{\tt thm-$\unshunt^{*}$}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
+\end{bprooftree}
+}
+\end{equation*}
+
+\begin{equation*}
+D_2 :=
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂) ∧ \unshunt^{*}(φ₁ ⇒ φ₃)$}
+\RightLabel{\tt ∧-proj₂}
+\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₃, n)$}
+\RightLabel{By definition}
+\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₃, n-1)$}
+\RightLabel{\tt thm-$\unshunt^{*}$}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
+\end{bprooftree}
+\end{equation*}
+
+\begin{equation*}
+\begin{bprooftree}
+\AxiomC{$D_1$}
+\AxiomC{$D_2$}
+\RightLabel{\tt ∧-intro}
+\BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
+\RightLabel{\tt ⇒∧⇒-to-⇒∧}
+\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
+\end{bprooftree}
+\end{equation*}
+\end{proof}
+
+The function \mysplit performs such that strategy and it has the type
+\[ \mysplit : \PROP \to \PROP
+\]
 \begin{equation}
@@
 
+The theorem is the following.
+
+\begin{theorem}[Splitting a Goal] $Γ ⊢ \mysplit(φ) ⇒ φ$
+\end{theorem}
+
+\begin{proof}
+ss
+\end{proof}
+
+The \mysplit function returns a conjunction of the subgoal. From each
+\TSTP derivation, we have information of the subgoals but no how they strictly appear in that conjunction.
+For that reason, with \Athena, we infer the exact order in the conjunction that coincides with the conjunction given by \mysplit.
+
+\begin{theorem} For a list of subgoals $s_0, \cdots, s_1$ with their respective theorem $Γ ⊢ s_i$, such that $\bigwedge_i s_i ⇒ \texttt{goal}$, then $Γ ⊢ \texttt{goal}$ 
+\end{theorem}
+
 \end{document}

### 2017-09-12 paper/sections/metis-language-and-proofs.tex
[ paper ] fixing some typos and text added.

@@
 \begin{verbatim}
-fof(a, axiom, p) .
-fof(goal, conjecture, p) .
-fof(subgoal_0, plain, p, inference (strip, [], [goal])) .
-fof(negate_0_0, plain, ~ p, inference (negate, [], [subgoal_0])) .
+fof(premise, axiom, p).
+fof(goal, conjecture, p).
+fof(subgoal_0, plain, p, inference(strip, [], [goal])).
+fof(negate_0_0, plain, ~ p, inference(negate, [], [subgoal_0])).
 fof(normalize_0_0, plain, ∼ p,
-  inference (canonicalize, [], [negate_0_0])) .
+  inference(canonicalize, [], [negate_0_0])).
 fof(normalize_0_1, plain, p,
-  inference (canonicalize, [], [a])) .
+  inference(canonicalize, [], [premise])).
 fof(normalize_0_2, plain, $false,
-  inference (simplify, [], [normalize_0_0, normalize_0_1]))
+  inference(simplify, [], [normalize_0_0, normalize_0_1]))
 cnf(refute_0_0, plain, $false,
-  inference (canonicalize, [], [normalize_0_2])) .
+  inference(canonicalize, [], [normalize_0_2])).
 \end{verbatim}
@@
 observed in \TSTP derivations, for such a propositional fragment,
-\Metis uses in his deductions steps, six rules where only the
+\Metis uses in its deductions steps, six rules where only the
 \emph{resolve} inference persists from the original list. In the
@@
 inferences, \Metis summarized many essential steps to deduce a
-formula from a list a list of formulas as we see in the following
-example.
+formula from a list of formulas.
 \improvement{Add an example here to show a deduction where \Metis do
 a lot between two steps.}
-That inference' behavior is a drawback since, our approach
+That inference's behavior is a drawback since, our approach
 to reconstruct proofs needs take into account any assumption or
@@
 This is an attempt to fulfill the \Metis's documentation, by
-describing our each rule from our perspective. Later on, in section
+describing each rule from our perspective. Later on, in section
 \ref{sec:proof-reconstruction}, we present a formal description of
@@
 \Metis performs this transformation using its criteria.
+\improvement{We should mention that it was indeed a problem for the
+proof-reconstruction? and refer the section next?}
 
@@
 \]
-\caption{Defintions of \canonicalize inference.}
+\caption{Definitions for conjunction and disjunction simplification
+in the \canonicalize inference.}
 \label{fig:conjunctive-disjunctive-simpl}
@@
 \textit{Simplification.}
-The \simplify rule is inference that performs simplification of
+The \simplify rule is an inference that performs simplification of
 definitions or tautologies over a list of derivations. This rule
@@
 Fig. \ref{fig:conjunctive-disjunctive-simpl} and the resolution
-theorem of \resolve rule.
+theorem of the \resolve rule.
 

### 2017-09-12 paper/sections/proof-reconstruction.tex
[ paper ] fixing some typos and text added.

@@
 assistant, \Agda. We choose \Agda, but another proof assistant with
-support of type theory and similar features like \Agda
+support of Type Theory and similar features like \Agda
 (see a description of \Agda in section
@@
 In the rest of this section, we provide a formal description using
-type theory to build definitions and theorems for the functions
+Type Theory to build definitions and theorems for the functions
 necessary to emulate the \Metis' inference rules.
@@
 
-\subsection{Recursion Theorems}
+\subsection{Rules as Theorems}
 
-\improvement{Convention notation := for equivalence between propositions}
-% \footnote{We use the \Agda standard library's implementation of the List data type.}.
+Main algorithms in \CPL need the propositions in some of their normal
+forms. For instance, from the negative normal form
+(henceforth, \abbre{NNF}), we can derive the conjunctive normal form,
+and the disjunctive normal form as well.
+Therefore, we start giving the definition of \abbre{NNF}, one
+function definition, \name{nnf} and a refinement of it.
+We will use it later for instance in the description of \canonicalize
+rule. The following treatment to this function, \name{nnf},
+applies for other conversion functions and theorems defined in
+\cite{AgdaProp,AgdaMetis}.
+We use the notation convention $:=$ for equivalence between
+propositions. The \PROP inductive data type is defined as usual
+based on the definition from section \ref{sec:preliminaries} and
+implemented in \Agda with \name{PropFormula} in section
+\ref{sec:implementation}.
 
-\begin{definition}(Negative Normal Form (NNF))
-Una forma normal negativa para la formula $\varphi$ es aquella
-en la cual negaciones aparecen solamente en los literales y
-la expresión se encuentra en términos unicamente
-de los operadores booleanos ($\neg$, $\wedge$, $\vee$).
-\end{definition}
+\subsubsection{\CPL Functions}
+\hspace*{5cm}\\[3mm]
+\emph{NNF.}
+A negative normal form for the formula φ is one in which negations
+appear only in the literals and the expression is in terms only of
+the boolean operators (¬, ∧, ∨).
 
-Para transformar una formula $\varphi$ a su forma equivalente NNF,
-aplicamos recursivamente las siguientes ecuaciones que definen
-la función \name{nnf}.
+To transform a formula φ to its equivalent \abbre{NNF} form, we
+apply recursively the following equations. The function type for
+\name{nnf} is $\PROP \to \PROP$.
 
@@
 
-\begin{definition}
-Una funcion recursiva se dice bien estructura, si el tamaño de los argumentos
-con que con esta se define se reducen en tamaño por cada llamada a la
-funcion.
-\end{definition}
+A recursive function is a well-structured recursion, if the size of
+the arguments with which it is defined decrease in size for each
+call to the function in the definition. That guarantee termination
+of the function, and its translation to constructive Type Theory.
 
-De la anterior definincion, sintacticamente la funcion nnf no es recursivamente
-bien estructurado. El problem que no lo sea esta en nuestra traducion
-de este tipo de funciones a la teoria de tipos.
-
-Veamos otros ejemplos de funciones con el mismo problema que utilizaremos mas
-adelante para formalizar la inferencia strip.
+But we need to improve the definition for \name{nnf} in order to have
+a version of a well-structured recursion.
+We show a strategy to achieve that with a smaller example function,
+\unshunt, that we will use forward to formalize the inference
+\name{strip}.
 
@@
 
-Para traducir las funciones en un manera que esten bien definidas,
-utilizamos el metodo propuesto por Ana Bove, el cual basicamente consiste
+To translate the functions in a way that is well defined,
+we used the method proposed by Bove and Capettra in
+\cite{Bove2005}, which basically consists of
 
-una funcion general recursiva $f:\sigma \to \tau$, su formalizacion en
-teoria de tipos consiste en definir un predicado inductivo $Ind$,
-$P:\sigma \to Ind$
+We take a general recursive function $f: \sigma \to \tau$.
+Its formalization in Type Theory will define an inductive
+predicate $Ind$, $ P: \sigma \to Ind$.
 
-En nuestro caso, el conjunto de los numeros servira como nuestro
-conjunto inductivo y como segundo argumento para nueva funcion.
-De manera, que la funcion g estara definida por recursion estructural en
-su segundo termino.
+In our case, the set of natural numbers will serve as our
+inductive set $Ind$ and as second argument for new function.
+Thus, the function $\unshunt$ will be defined by structural
+recursion in his second term.
 
-Para aplicar la tecnica antes mencionada para nuestras funciones,
-veamos su aplicación con la funcion \unshunt porque para las demas,
-seguiremos un camino similar, f con tipo:
+The new proposed $\unshunt^{*}$ has type,
 
 \[
-\unshunt^{*} : PROP \to \mathcal{N} \to PROP
+\unshunt^{*} : PROP \to \mathbb{N} \to PROP.
 \]
@@
 
-Then, we our final revision for the function $\unshunt$ is the
+Then, we our final review for the function $\unshunt$ is the
 function$\unshunt^{+}$ with type $PROP \to PROP$
@@
 In the following section, our task will consist of a searching
-appropriate functions like $rank$ to assure the termination of
-our transformation functions like $nnf$.
+appropriate functions like $rank$ to assure the termination for transformation functions like $nnf$.
 
@@
 \emph{Splitting.}
-We take a goal and generate subgoals that all in a conjunction
-prove the goal.
+To prove a goal, we can prove smaller subgoals and combine their
+proofs to achieve the final target, a proof of the initial goal.
 
@@
 
-The function \mysplit performs such that strategy and it has the type
+The function \mysplit has the type
 \[ \mysplit : \PROP \to \PROP
@@
 
-The theorem is the following.
-
 \begin{theorem}[Splitting a Goal] $Γ ⊢ \mysplit(φ) ⇒ φ$
@@
 \TSTP derivation, we have information of the subgoals but no how they strictly appear in that conjunction.
-For that reason, with \Athena, we infer the exact order in the conjunction that coincides with the conjunction given by \mysplit.
+For that reason, with \Athena, we infer the exact order in the conjunction that coincides with the output by \mysplit.
 
-\begin{theorem} For a list of subgoals $s_0, \cdots, s_1$ with their respective theorem $Γ ⊢ s_i$, such that $\bigwedge_i s_i ⇒ \texttt{goal}$, then $Γ ⊢ \texttt{goal}$ 
+\begin{theorem} For a list of subgoals $s_0, \cdots, s_1$ with their respective theorem $Γ ⊢ s_i$, such that $\bigwedge_i s_i ⇒ \texttt{goal}$, then $Γ ⊢ \texttt{goal}$.
 \end{theorem}

### 2017-09-12 paper/sections/implementation.tex
[ paper ] fixing some typos and text added.

@@
 \Agda is an interactive system for constructing proofs and programs,
-based on Martin-L\"{o}f's type theory and extended with records, parametrised
-modules, among other features.
-One of the main strengths of \Agda is its support for writing proofs,
-which we shall call \Agda's proof engine. It consists of: support for
-inductively defined types, including inductive families, and function
-definitions using pattern matching on such types, normalisation during type-
-checking, commands for refining proof terms, coverage checker and termination
-checker.
+based on Martin-L\"{o}f's type theory and extended with records,
+parametrised modules, among other features. One of the main
+strengths of \Agda is its support for writing proofs, which we shall
+call \Agda's proof engine. It consists of: support for inductively
+defined types, including inductive families, and function
+definitions using pattern matching on such types, normalisation
+during type- checking, commands for refining proof terms, coverage
+checker and termination checker.
 
-The inductive approach for representing classical propositional logic
-is better because we benefit from \Agda's proof engine and its Unicode
-support that allows us writing proofs similar as we find in math text books.
+The inductive approach for representing classical propositional
+logic is better because we benefit from \Agda's proof engine and its
+Unicode support that allows us writing proofs similar as we find in
+math text books.
 
@@
 We also define the constructor for atomic propositions denoted by
-\verb!Var!. This atomic expressions are represented using a natural 
+\verb!Var!. These atomic expressions are represented using a natural
 number $i$ bounded by a size of the universe $n$ for those atomic
@@
 \begin{example}
-Using Unicode translating a proposition from a textbook to \Agda 
-using the above data type is straightforward. 
+\hspace*{5cm}\\[3mm]
 \begin{verbatim}

### 2017-09-12 paper/sections/preliminaries.tex
[ paper ] fixing some typos and text added.

@@
 and $⊤$. We use the inductive definition of the set \PROP
-defined in \cite{VanDalen1994} as the mechanism to produce any
+presented in \cite{VanDalen1994} as the mechanism to produce any
 propositional formula.
 Then, $ϕ_i \in \PROP$ for all $i \in \mathbb{N}$.
-If $(φ\ \square\ ψ)$ stands for a proposition that use a
-binary connective where is the symbol $\square$; when $φ, ψ\in
-\PROP$, then $(φ\ \square\ ψ) \in \PROP$.\change{rewrite this}
+If $φ, ψ\in \PROP$, then $(φ\ \square\ ψ) \in \PROP$,
+where $(φ\ \square\ ψ)$ stands for a proposition that use a
+binary connective in the place for the $\square$ symbol.
 If $φ \in \PROP$, then $(¬ φ) \in \PROP$.
@@
 result: one or more propositions. As we show in the following
-figure, the premises are always above the line, and the conclusions
-are below it. As a notation convention, if the name of a rule used
-in the derivation step is typed using verbatim, that means, it is
-available in our implementation for the \CPL (see the syntax module 
-in \cite{AgdaProp}) used in the proof reconstruction latter.
+figure, the premises are always above the line, the conclusions
+are below it, and the name of the inference or the theorem used is
+on the right the line. As a notation convention, if the name of a
+rule used in the derivation step is typed using verbatim, that
+means, it is available in our implementation (see for instance,
+theorems in \cite{AgdaProp}) used in some derivations latter.
 

### 2017-09-12 paper/sections/proof-reconstruction.tex
[ paper ] fixing some typos and text added.

@@
 \begin{definition}
-El rango $rank(\phi)$ de una proposition $\phi$ es definido como
+Th rank of proposition φ denoted by $rank(\phi)$ is defined by the
+following equation.
 
@@
 \end{equation}
-
 \end{definition}
 
-Then, we our final review for the function $\unshunt$ is the
-function$\unshunt^{+}$ with type $PROP \to PROP$
-with a structured recursion,
+The final review for $\unshunt$ function is the
+$\unshunt^{+}$ function in Eq.~\ref{eq:unshunt-fixed}
+with $PROP \to PROP$ type.
 
 \begin{equation}
+\label{eq:unshunt-fixed}
 \unshunt^{+}(\varphi) = \unshunt^{*}(\varphi, rank(\varphi))
@@
 
-In the following section, our task will consist of a searching
-appropriate functions like $rank$ to assure the termination for transformation functions like $nnf$.
+In the following section, our task will consist of searching
+appropriate functions like $rank$ to assure the termination for
+transformation functions like $nnf$.
 

### 2017-09-12 paper/sections/proof-reconstruction.tex
[ paper ] complexity measure added.

@@
 
-\subsection{Rules as Theorems}
+\subsection{Well-structured Recursion}
+\label{ssec:well-structured recursion}
 
-Main algorithms in \CPL need the propositions in some of their normal
-forms. For instance, from the negative normal form
-(henceforth, \abbre{NNF}), we can derive the conjunctive normal form,
-and the disjunctive normal form as well.
-Therefore, we start giving the definition of \abbre{NNF}, one
-function definition, \name{nnf} and a refinement of it.
-We will use it later for instance in the description of \canonicalize
-rule. The following treatment to this function, \name{nnf},
-applies for other conversion functions and theorems defined in
-\cite{AgdaProp,AgdaMetis}.
-We use the notation convention $:=$ for equivalence between
-propositions. The \PROP inductive data type is defined as usual
-based on the definition from section \ref{sec:preliminaries} and
-implemented in \Agda with \name{PropFormula} in section
-\ref{sec:implementation}.
+To emulate the \Metis' Inference Rules in type theory.
+We encounter many functions involved with termination problems, that
+means, it is not possible to determine effectively if the function
+terminates. That makes impossible to translate in type theory
+directly. For that reason, we show a technique that will help us to fix such a issue and guide us how to proceed later.
 
-\subsubsection{\CPL Functions}
-\hspace*{5cm}\\[3mm]
-\emph{NNF.}
-A negative normal form for the formula φ is one in which negations
-appear only in the literals and the expression is in terms only of
-the boolean operators (¬, ∧, ∨).
+A recursive function is a \emph{well-structured recursion}, if the
+size of the arguments with which it is defined decrease in
+size for each call to the function in the definition.
+A well-structured function terminates and it can be translated
+directly to type theory.
 
-To transform a formula φ to its equivalent \abbre{NNF} form, we
-apply recursively the following equations. The function type for
-\name{nnf} is $\PROP \to \PROP$.
-
-\begin{equation}
-\label{eq:nnf-definition}
-\nnf(φ) =
-\begin{cases}
-\nnf(φ₁) ∧ \nnf(φ₂)
-   & φ := φ₁ ∧ φ₂  \\
-
-\nnf(φ₁) ∨ \nnf(φ₂)
-   & φ := φ₁ ∨ φ₂  \\
-
-\nnf(¬ φ₁ ∨ φ₂)
-   & φ := φ₁ ⇒ φ₂  \\
-
-\nnf(φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁)
-   & φ := φ₁ ⇔ φ₂\\
-
-\nnf(¬ φ₁ ∨ ¬ φ₂)
-   & φ := ¬ (φ₁ ∧ φ₂) \\
-
-\nnf(¬ φ₁ ∧ ¬ φ₂)
-   & φ := ¬ (φ₁ ∨ φ₂) \\
-
-\nnf(φ₁)
-   & φ := ¬ ¬ φ₁     \\
-
-\nnf(¬ (φ₂ ∨ ¬ φ₁))
-   & φ := ¬ (φ₁ ⇒ φ₂)  \\
-
-\nnf(¬ (φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁))
-   & φ := ¬ (φ₁ ⇔ φ₂) \\
-
-⊥  & φ := ¬ ⊤        \\
-
-⊤  & φ := ¬ ⊥        \\
-
-φ  & \text{otherwise}
-\end{cases}
-\end{equation}
-
-A recursive function is a well-structured recursion, if the size of
-the arguments with which it is defined decrease in size for each
-call to the function in the definition. That guarantee termination
-of the function, and its translation to constructive Type Theory.
-
-But we need to improve the definition for \name{nnf} in order to have
-a version of a well-structured recursion.
-We show a strategy to achieve that with a smaller example function,
-\unshunt, that we will use forward to formalize the inference
-\name{strip}.
+Consider the following example from the \strip inference.
 
@@
 \unshunt((φ₁ ∧ φ₂) ⇒ φ₃)
-  & φ := φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+  & φ := φ₁ ⇒ (φ₂ ⇒ φ₃),\\
 
 \unshunt(φ₁ ⇒ φ₂) ∧ \unshunt(φ₁ ⇒ φ₃)
-  & φ := φ₁ ⇒ (φ₂ ∧ φ₃)\\
+  & φ := φ₁ ⇒ (φ₂ ∧ φ₃),\\
 
-φ &\text{otherwise}
+φ &\text{otherwise}.
 \end{cases}
@@
 
-To translate the functions in a way that is well defined,
-we used the method proposed by Bove and Capettra in
-\cite{Bove2005}, which basically consists of
+From the above definition, in the first case of the \unshunt
+function, the size of the argument doesn't really decrease.
+Actually, it maintains with the same size ((φ₁ ∧ φ₂) ⇒ φ₃ and  (φ₁ ⇒
+(φ₂ ⇒ φ₃))). Therefore, a termination checking will fail with \unshunt
+function.
 
-We take a general recursive function $f: \sigma \to \tau$.
-Its formalization in Type Theory will define an inductive
-predicate $Ind$, $ P: \sigma \to Ind$.
+To improve it, we will use the technique proposed by Bove and Capettra in
+\cite{Bove2005}, which in our case basically consists of
+take a general recursive function $f: \sigma \to \tau$.
+and an predicate $P: \sigma \to \abbre{Ind}$, where $\abbre{Ind}$
+is a type with a structure inductive definition.
+Then, we redefine the function as
+$f: \sigma \to \abbre{Ind}\ \to \tau$, and perform the recursion
+using induction on the structure of the \abbre{Ind} type.
 
-In our case, the set of natural numbers will serve as our
-inductive set $Ind$ and as second argument for new function.
-Thus, the function $\unshunt$ will be defined by structural
-recursion in his second term.
+In our case, $\abbre{Ind}$ will be the \abbre{Nat} data type for
+natural numbers with constructors \abbre{zero} and \abbre{suc} defined as usual.
 
-The new proposed $\unshunt^{*}$ has type,
+Thus, we have function $\unshunt : \PROP \to \Nat \to \PROP$ defined by structural recursion in his second term with type as follows,
 
-\[
-\unshunt^{*} : PROP \to \mathbb{N} \to PROP.
-\]
+\begin{align*}
+\label{eq:unshunt-structured}
+\unshunt(φ, \zero) &= φ\\
+\unshunt(φ, \suc(n)) &=
+\begin{cases}
+\unshunt((φ₁ ∧ φ₂) ⇒ φ₃, n)
+  & φ := φ₁ ⇒ (φ₂ ⇒ φ₃),\\
+\unshunt(φ₁ ⇒ φ₂, n) ∧ \unshunt(φ₁ ⇒ φ₃,n)
+  & φ := φ₁ ⇒ (φ₂ ∧ φ₃).
+\end{cases}
+\end{align*}
+
+Finally, we define the complexity measure to handle the second argument for the \unshunt function.
+
+\newcommand{\rank}{\name{rank}}
+
+A \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017} or
+a rank function presented in \cite{VanDalen1994} is a function
+$\PROP \to \Nat$ that indents to associate a natural number for a
+proposition φ. The following function is a complexity measure.
+
+\begin{equation*}
+\label{eq:rank-definition}
+\rank(φ)=
+\begin{cases}
+0 &\text{for atomic }φ, \\
+\rank(φ₁) + c_{¬}  & φ := \neg φ₁, \\
+\max(\rank(φ₁),\rank(φ₂)) + c_{\square}
+  & φ := φ₁\,\square\, φ₂.
+\end{cases}
+\end{equation*}
+where $c_{¬}$ or $c_{\square}$ is a non-negative integer called the
+complexity of the connective.
+
+Nevertheless, we need to define an appropriate complexity measure for the second argument in the $\unshunt$ function, in order to
+expect the same behavior of the original function as it was defined at first in Eq.~\ref{eq:unshunt-definition}.
 
 \begin{equation}
-\label{eq:unshunt-structured}
-\unshunt^{*}(φ, n) =
+\label{eq:rank-definition}
+\unshunt_{cm}(φ)=
 \begin{cases}
-\unshunt^{*}((φ₁ ∧ φ₂) ⇒ φ₃, n-1)
-  & φ := φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-
-\unshunt^{*}(φ₁ ⇒ φ₂, n-1) ∧ \unshunt^{*}(φ₁ ⇒ φ₃,n-1)
-  & φ := φ₁ ⇒ (φ₂ ∧ φ₃)\\
-
-φ & n := 0
+\unshunt_{cm}(φ₃) + 2 & φ := φ₁ ⇒ (φ₂ ⇒ φ₃),\\
+\max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1
+  & φ := φ₁ ⇒ (φ₂ ∧ φ₃),\\
+0 &\text{otherwise.}
 \end{cases}
@@
 
-\begin{definition}
-Th rank of proposition φ denoted by $rank(\phi)$ is defined by the
-following equation.
-
-\begin{equation}
-\label{eq:rank-definition}
-rank(\phi)=
-\begin{cases}
-0 &\text{for atomic }\phi\\
-
-\max(rank(\phi_1),rank(\phi_2)) + 1
-  & \phi := \phi_1\,\square\, \phi_2 \\
-rank(\phi_1) + 1  & \phi := \neg \phi_1
-\end{cases}
-\end{equation}
-\end{definition}
-
-The final review for $\unshunt$ function is the
-$\unshunt^{+}$ function in Eq.~\ref{eq:unshunt-fixed}
-with $PROP \to PROP$ type.
+Then, a curated version of \unshunt is presented in Eq.
+\ref{eq:unshunt-fixed}.
 
@@
 \label{eq:unshunt-fixed}
-\unshunt^{+}(\varphi) = \unshunt^{*}(\varphi, rank(\varphi))
+\unshunt(\varphi) := \unshunt(\varphi, \unshunt_{cm}(\varphi))
 \end{equation}
 
-In the following section, our task will consist of searching
-appropriate functions like $rank$ to assure the termination for
-transformation functions like $nnf$.
+In the following section, we may need define such complexity measure
+functions for termination-checking.
 
@@
 
-\subsection{Emulation \Metis' Inference Rules}
+\subsection{Emulating \Metis' Inference Rules}
+\label{ssec:emulating-inferences}
 
@@
 
-\begin{theorem}[{\tt thm-$\unshunt^{*}$}] $Γ ⊢ \unshunt^{*}(φ, n)$ for $n\in \mathbb{N}$, then $Γ ⊢ φ$.
+\begin{theorem}[{\tt thm-$\unshunt^{*}$}] $Γ ⊢ \unshunt^{*}(φ, n)$
+for $n\in \Nat$, then $Γ ⊢ φ$.
+\label{thm:unshunt}
 \end{theorem}
+
 \begin{proof} Use induction on the cases defined by the result of
@@
 \scalebox{0.95}{
-$D_1$ := \begin{bprooftree}
+$\mathcal{D}_1$ := \begin{bprooftree}
 \AxiomC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂, n) ∧ \unshunt^{*}(φ₁ ⇒ φ₃, n)$}
@@
 \begin{equation*}
-D_2 :=
+\mathcal{D}_2 :=
 \begin{bprooftree}
@@
 \begin{bprooftree}
-\AxiomC{$D_1$}
-\AxiomC{$D_2$}
+\AxiomC{$\mathcal{D}_1$}
+\AxiomC{$\mathcal{D}_2$}
 \RightLabel{\tt ∧-intro}
@@
 
-The function \mysplit has the type
-\[ \mysplit : \PROP \to \PROP
-\]
+\vskip 3mm
+
+From now on, we redefine the function $\unshunt$ with the
+definition of $\unshunt^{+}$ for no overloading the notation forward.
+
+\begin{theorem}[{\tt thm-\unshunt}] $Γ ⊢ \unshunt(φ)$ then $Γ ⊢ φ$.
+\end{theorem}
+\begin{proof} It follows from Thm.~\ref{thm:unshunt} using the
+\rank function as the second argument.
+\end{proof}
+
+The \mysplit function yields a conjunction of subformulas that
+implies the proposition φ, the argument of the function. This
+function has type $\PROP \to \NN \to PROP$, its definition is
+ $\mysplit(φ,0) = φ$, and
+for all$n\in \NN$, $n > 0$,
+
 \begin{equation}
 \label{eq:split-definition}
-\mysplit(φ) =
+\mysplit(φ,n+1) =
 \begin{cases}
-\unshunt(\mysplit(φ₁)) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂)
-  & φ := φ₁ ∧ φ₂\\
+\unshunt(\mysplit(φ₁,n)) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n)
+  & φ := φ₁ ∧ φ₂,\\
 
-\unshunt(¬ φ₁ ⇒ \mysplit(φ₂))
-  & φ := φ₁ ∨ φ₂\\
+\unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n))
+  & φ := φ₁ ∨ φ₂,\\
 
-\unshunt(φ₁ ⇒ \mysplit(φ₂))
-  & φ := φ₁ ⇒ φ₂\\
+\unshunt(φ₁ ⇒ \mysplit(φ₂,n))
+  & φ := φ₁ ⇒ φ₂,\\
 
-\unshunt(φ₁ ⇒ \mysplit(φ₂)) ∧ \unshunt(φ₂ ⇒ \mysplit(φ₁))
-  & φ := φ₁ ⇔ φ₂\\
+\unshunt(φ₁ ⇒ \mysplit(φ₂,n)) ∧ \unshunt(φ₂ ⇒ \mysplit(φ₁,n))
+  & φ := φ₁ ⇔ φ₂,\\
 
-\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
-  & φ := ¬ (φ₁ ∧ φ₂)\\
+\unshunt(φ₁ ⇒ \mysplit(¬ φ₂, n))
+  & φ := ¬ (φ₁ ∧ φ₂),\\
 
-\unshunt(\mysplit(¬ φ₁)) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂))
-  & φ := ¬ (φ₁ ∨ φ₂)\\
+\unshunt(\mysplit(¬ φ₁,n)) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂,n))
+  & φ := ¬ (φ₁ ∨ φ₂),\\
 
-\unshunt(\mysplit(φ₁)) ∧ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
-  & φ := ¬ (φ₁ ⇒ φ₂)\\
+\unshunt(\mysplit(φ₁,n)) ∧ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂,n))
+  & φ := ¬ (φ₁ ⇒ φ₂),\\
 
-\unshunt(φ₁ ⇒ \mysplit(¬ φ₂)) ∧ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))
-  & φ := ¬ (φ₁ ⇔ φ₂)\\
+\unshunt(φ₁ ⇒ \mysplit(¬ φ₂,n)) ∧ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁,n))
+  & φ := ¬ (φ₁ ⇔ φ₂),\\
 
-\unshunt(\mysplit(φ₁)
-  & φ := ¬ ¬ φ₁\\
+\unshunt(\mysplit(φ₁, n))
+  & φ := ¬ ¬ φ₁,\\
 
-⊤ & φ := ¬ ⊥\\
+⊤ & φ := ¬ ⊥,\\
 
-⊥ & φ := ¬ ⊤\\
-
-φ &\text{otherwise}
+⊥ & φ := ¬ ⊤.
 \end{cases}
@@
 
-\begin{theorem}[Splitting a Goal] $Γ ⊢ \mysplit(φ) ⇒ φ$
+\newcommand{\thmsplit}{\name{thm-split}}
+\begin{theorem}[\thmsplit] $Γ ⊢ \mysplit(φ)$ then $Γ ⊢ φ$.
 \end{theorem}
 
-\begin{proof}
-ss
+\begin{proof} We use induction on the structure of the formula
+following the cases in the definition of \mysplit function.
+We proceed to show some cases since the others are proved in a
+similar way.\\[3mm]
+(φ := φ₁ ∧ φ₂)
+\begin{equation*}
+\begin{bprooftree}
+\AxiomC{$\mathcal{D}_1$}
+\UnaryInfC{Γ ⊢ φ₁}
+
+\AxiomC{$\mathcal{D}_1$}
+\UnaryInfC{Γ ⊢ φ₁}
+
+\AxiomC{$Γ ⊢ \mysplit(φ)$}
+\RightLabel{By Def.}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂))$}
+\RightLabel{\tt $∧$-proj$₂$}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂))$}
+\RightLabel{\thmunshunt}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂)$}
+\RightLabel{\tt $⇒$-elim}
+\BinaryInfC{$Γ ⊢ \mysplit(φ₂)$}
+\RightLabel{\thmsplit}
+\UnaryInfC{$Γ ⊢ φ₂$}
+
+\RightLabel{\tt ∧-intro}
+\BinaryInfC{$Γ ⊢ φ₁ ∧ φ₂$}
+\end{bprooftree}
+\end{equation*}
+where
+\begin{equation*}
+\mathcal{D}_1 =
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ \mysplit(φ)$}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂))$}
+\RightLabel{\tt ∧-proj₁}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁)$}
+\RightLabel{\thmunshunt}
+\UnaryInfC{$Γ ⊢ φ₁$}
+\end{bprooftree}
+\end{equation*}
+
+(φ := φ₁ ⇒ φ₂)
+\begin{equation*}
+\begin{bprooftree}
+\AxiomC{}
+\RightLabel{\tt assume φ₁}
+\UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
+\AxiomC{$Γ ⊢ \mysplit(φ)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂))$}
+\RightLabel{\thmunshunt}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂)$}
+\RightLabel{weaken φ₁}
+\UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂)$}
+\RightLabel{\tt ⇒-elim}
+\BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂)$}
+\RightLabel{\thmsplit}
+\UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
+\RightLabel{\tt ⇒-intro}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
+\end{bprooftree}
+\end{equation*}
+
+(φ := ¬ (φ₁ ∨ φ₂))
+\begin{equation*}
+\begin{bprooftree}
+\AxiomC{$\mathcal{D}$}
+\UnaryInfC{$Γ ⊢ ¬ φ₁$}
+
+\AxiomC{$\mathcal{D}$}
+\UnaryInfC{$Γ ⊢ ¬ φ₁$}
+
+\AxiomC{$Γ ⊢ \mysplit(φ)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂))$}
+\RightLabel{\tt ∧-proj₂}
+\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂))$}
+\RightLabel{\thmunshunt}
+\UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂)$}
+\RightLabel{\tt ⇒-elim}
+\BinaryInfC{$Γ ⊢ \mysplit(φ₂)$}
+\RightLabel{\thmsplit}
+\UnaryInfC{$Γ ⊢ ¬ φ₂$}
+\RightLabel{\tt ∧-intro}
+\BinaryInfC{$Γ ⊢ ¬ φ₁ ∧ ¬ φ₂$}
+\RightLabel{\tt ¬∧¬-to-¬∨}
+\UnaryInfC{$Γ ⊢ ¬ (φ₁ ∨ φ₂)$}
+\end{bprooftree}
+\end{equation*}
+where
+\begin{equation*}
+\mathcal{D} =
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ \mysplit(φ, n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
+\RightLabel{\tt ∧-proj₁}
+\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁)$}
+\RightLabel{\thmunshunt}
+\UnaryInfC{$Γ ⊢ ¬ φ₁$}
+\end{bprooftree}
+\end{equation*}
+
+(φ := ¬ (φ₁ ⇔ φ₂))
+\begin{equation*}
+\begin{bprooftree}
+
+% -- right
+
+\AxiomC{$Γ ⊢ \mysplit(φ, n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂)) ∧ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁)) $}
+\RightLabel{\tt ∧-proj₂}
+\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))$}
+\RightLabel{\tt \thmunshunt}
+\UnaryInfC{$Γ ⊢ ¬ φ₂ ⇒ \mysplit(φ₁)$}
+\RightLabel{\tt weaken ¬ φ₂}
+\UnaryInfC{$Γ , ¬ φ₂ ⊢ ¬ φ₂ ⇒ \mysplit(φ₁)$}
+
+% -- right
+
+% -- left
+\AxiomC{}
+\RightLabel{\tt assume (¬ φ₂)}
+\UnaryInfC{$Γ , ¬ φ₂ ⊢ ¬ φ₂$}
+\RightLabel{\tt ⇒-elim}
+
+\BinaryInfC{$Γ , ¬ φ₂ ⊢ \mysplit(φ₁)$}
+\RightLabel{\thmsplit}
+\UnaryInfC{$Γ , ¬ φ₂ ⊢ φ₁ $}
+\RightLabel{\tt ⇒-intro}
+\UnaryInfC{$Γ ⊢ ¬ φ₂ ⇒ φ₁$}
+% -- left
+
+% \RightLabel{\tt ∧-intro}
+% \BinaryInfC{$Γ ⊢ (φ₁ ⇒ ¬ φ₂) ∧ (¬ φ₂ ⇒ φ₁)$}
+% \RightLabel{\tt ⇒¬∧¬⇒-to-¬⇔}
+% \UnaryInfC{$Γ ⊢ ¬ (φ₁ ⇔ φ₂)$}
+\end{bprooftree}
+\end{equation*}
+
 \end{proof}
 
-The \mysplit function returns a conjunction of the subgoal. From each
-\TSTP derivation, we have information of the subgoals but no how they strictly appear in that conjunction.
-For that reason, with \Athena, we infer the exact order in the conjunction that coincides with the output by \mysplit.
+The \mysplit function returns a conjunction of the subgoals.
+From each \TSTP derivation, we actually have information of the
+subgoals but it is not explicit how they appear in the conjunction.
+For that reason, with \Athena, we infer the exact order in the
+conjunction that coincides with the output by \mysplit.
 
-\begin{theorem} For a list of subgoals $s_0, \cdots, s_1$ with their respective theorem $Γ ⊢ s_i$, such that $\bigwedge_i s_i ⇒ \texttt{goal}$, then $Γ ⊢ \texttt{goal}$.
+\begin{theorem} For a list of subgoals $s_0, \cdots, s_1$ with their
+respective theorem $Γ ⊢ s_i$, such that $\bigwedge_i s_i ⇒ \texttt{goal}$, then $Γ ⊢ \texttt{goal}$.
 \end{theorem}

### 2017-09-13 paper/sections/proof-reconstruction.tex
[ paper ] minor changes.
[ paper ] resolve inference init.

@@
 \end{equation*}
+% (φ := ¬ (φ₁ ⇔ φ₂))
+% \begin{equation*}
+% \begin{bprooftree}
 
-(φ := ¬ (φ₁ ⇔ φ₂))
-\begin{equation*}
-\begin{bprooftree}
+% % -- right
 
-% -- right
+% \AxiomC{$Γ ⊢ \mysplit(φ, n)$}
+% \RightLabel{By def.}
+% \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂)) ∧ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁)) $}
+% \RightLabel{\tt ∧-proj₂}
+% \UnaryInfC{$Γ ⊢ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))$}
+% \RightLabel{\tt \thmunshunt}
+% \UnaryInfC{$Γ ⊢ ¬ φ₂ ⇒ \mysplit(φ₁)$}
+% \RightLabel{\tt weaken ¬ φ₂}
+% \UnaryInfC{$Γ , ¬ φ₂ ⊢ ¬ φ₂ ⇒ \mysplit(φ₁)$}
 
-\AxiomC{$Γ ⊢ \mysplit(φ, n)$}
-\RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂)) ∧ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁)) $}
-\RightLabel{\tt ∧-proj₂}
-\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))$}
-\RightLabel{\tt \thmunshunt}
-\UnaryInfC{$Γ ⊢ ¬ φ₂ ⇒ \mysplit(φ₁)$}
-\RightLabel{\tt weaken ¬ φ₂}
-\UnaryInfC{$Γ , ¬ φ₂ ⊢ ¬ φ₂ ⇒ \mysplit(φ₁)$}
+% % -- right
 
-% -- right
+% % -- left
+% \AxiomC{}
+% \RightLabel{\tt assume (¬ φ₂)}
+% \UnaryInfC{$Γ , ¬ φ₂ ⊢ ¬ φ₂$}
+% \RightLabel{\tt ⇒-elim}
 
-% -- left
-\AxiomC{}
-\RightLabel{\tt assume (¬ φ₂)}
-\UnaryInfC{$Γ , ¬ φ₂ ⊢ ¬ φ₂$}
-\RightLabel{\tt ⇒-elim}
+% \BinaryInfC{$Γ , ¬ φ₂ ⊢ \mysplit(φ₁)$}
+% \RightLabel{\thmsplit}
+% \UnaryInfC{$Γ , ¬ φ₂ ⊢ φ₁ $}
+% \RightLabel{\tt ⇒-intro}
+% \UnaryInfC{$Γ ⊢ ¬ φ₂ ⇒ φ₁$}
+% % -- left
 
-\BinaryInfC{$Γ , ¬ φ₂ ⊢ \mysplit(φ₁)$}
-\RightLabel{\thmsplit}
-\UnaryInfC{$Γ , ¬ φ₂ ⊢ φ₁ $}
-\RightLabel{\tt ⇒-intro}
-\UnaryInfC{$Γ ⊢ ¬ φ₂ ⇒ φ₁$}
-% -- left
-
-% \RightLabel{\tt ∧-intro}
-% \BinaryInfC{$Γ ⊢ (φ₁ ⇒ ¬ φ₂) ∧ (¬ φ₂ ⇒ φ₁)$}
-% \RightLabel{\tt ⇒¬∧¬⇒-to-¬⇔}
-% \UnaryInfC{$Γ ⊢ ¬ (φ₁ ⇔ φ₂)$}
-\end{bprooftree}
-\end{equation*}
+% % \RightLabel{\tt ∧-intro}
+% % \BinaryInfC{$Γ ⊢ (φ₁ ⇒ ¬ φ₂) ∧ (¬ φ₂ ⇒ φ₁)$}
+% % \RightLabel{\tt ⇒¬∧¬⇒-to-¬⇔}
+% % \UnaryInfC{$Γ ⊢ ¬ (φ₁ ⇔ φ₂)$}
+% \end{bprooftree}
+% \end{equation*}
 
@@
 
+\emph{Resolve.}
+\newcommand{\thmresolve}{\name{thm-resolve}}
+The \resolve rule is a generalization version for resolution
+in propositional logic since the formulas are not shaped always as
+the theorem expect (see Fig.~\ref{fig:metis-inferences}).
+Since our approach is mere syntactic, in order to apply such a
+theorem, we perform rearrangements inside the formulas to match with
+the pattern expected by the resolution theorem. If this strategy
+fails at some point, we could not check the rest of the proof.
+
+Therefore, the best scenario to apply resolution occurs when the
+literal $l$ and its negation appear in the exact place in the
+formulas as the resolve inference shows.
+
+\begin{figure}
+\[%\scalebox{0.9}{
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ (φ₁ := l ∨ ψ₁)$}
+\AxiomC{$Γ ⊢ (φ₂ := ¬ l ∨ ψ₂)$}
+\RightLabel{\thmresolve}
+\BinaryInfC{$Γ ⊢ \resolve(φ₁, φ₂, l, (ψ₁ ∧ ψ₂))$}
+\UnaryInfC{Γ ⊢ ψ₁ ∨ ψ₂}
+\end{bprooftree}
+%}
+\]
+% \caption{Resolution in \Metis.}
+\label{fig:thm-resolve-best-case}
+\end{figure}
+
+To rearrange the proposition in order to match with a specific
+pattern of a formula, we define the following functions and provide
+its respective theorems in \cite{AgdaMetis}.
+
+\begin{itemize}
+  \item[] \name{reorder-∨}
+  \item[] \name{reorder-∧}
+  \item[] \name{reorder-∧∨}
+\end{itemize}
+
+\begin{equation}
+\resolve((φ₁, φ₂, l, ψ)
+
+\begin{theorem}[\thmresolve] $Γ ⊢ φ₁$, $Γ ⊢ φ₂$,
+then $Γ ⊢ \resolve(φ₁, φ₂, l, ψ)$ where $l$ is a literal,
+and ψ is the expected result.
+\end{theorem}
+
+% \begin{proof}
+% \begin{equation*}
+
+% \end{equation*}
+% \end{proof}
+
+\emph{Clausification.}
+
 \end{document}

### 2017-09-14 paper/sections/proof-reconstruction.tex
[ paper ] thm-split added.

@@
 automatic theorem prover, is \Metis; the target system is the proof
-assistant, \Agda. We choose \Agda, but another proof assistant with
-support of Type Theory and similar features like \Agda
+assistant, \Agda. We choose \Agda, but a proof assistant with
+support of type theory and similar features like \Agda
 (see a description of \Agda in section
-\ref{sec:implementation}) is valid; our results do not depend on
-the proof assistant but the support of inductive data types,
-termination checking, and type-checking.
-
+\ref{sec:implementation}) can be used.
 Following the diagram in Fig.
@@
 In the rest of this section, we provide a formal description using
-Type Theory to build definitions and theorems for the functions
-necessary to emulate the \Metis' inference rules.
+type theory to build definitions and theorems for the functions
+necessary to emulate the \Metis' inference rules. We will write the
+type judgments with ``$a : A$'' to denote that $a$ has type $A$.
+For propositions, we will denote by $φ ≡ ψ$ the syntactic
+equivalence.
 
@@
 
-\subsection{Well-structured Recursion}
+\subsection{Well-Structured Recursion}
 \label{ssec:well-structured recursion}
 
-To emulate the \Metis' Inference Rules in type theory.
-We encounter many functions involved with termination problems, that
-means, it is not possible to determine effectively if the function
-terminates. That makes impossible to translate in type theory
-directly. For that reason, we show a technique that will help us to fix such a issue and guide us how to proceed later.
+In the process to emulate \Metis' inference rules in type theory,
+We encountered many recursive algorithms with termination problems,
+that is,when an algorithm could run forever or we can not guarantee
+that it will stop after some point. Such a problem makes impossible
+to translate the algorithm in type theory directly.
+For that reason, we show a technique that will help us to define
+new algorithms based on the previous ones to solve the problem
+mentioned.
 
@@
 size of the arguments with which it is defined decrease in
-size for each call to the function in the definition.
+size for each call to the function in the definition~\cite{Bove2005}.
 A well-structured function terminates and it can be translated
-directly to type theory.
+directly to type theory~\cite{Bove2002}.
 
-Consider the following example from the \strip inference.
+Let us consider the following example from a inner function
+in the \strip inference.
 
@@
 \unshunt((φ₁ ∧ φ₂) ⇒ φ₃)
-  & φ := φ₁ ⇒ (φ₂ ⇒ φ₃),\\
+  & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
 
 \unshunt(φ₁ ⇒ φ₂) ∧ \unshunt(φ₁ ⇒ φ₃)
-  & φ := φ₁ ⇒ (φ₂ ∧ φ₃),\\
+  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
 
@@
 
-From the above definition, in the first case of the \unshunt
+From the definition above, in the first case of the \unshunt
 function, the size of the argument doesn't really decrease.
-Actually, it maintains with the same size ((φ₁ ∧ φ₂) ⇒ φ₃ and  (φ₁ ⇒
-(φ₂ ⇒ φ₃))). Therefore, a termination checking will fail with \unshunt
-function.
+Actually, it maintains with the same length syntactically
+(i.e., (φ₁ ∧ φ₂) ⇒ φ₃ compared with (φ₁ ⇒ (φ₂ ⇒ φ₃))).
+Therefore, a termination checking will fail with \unshunt function.
 
-To improve it, we will use the technique proposed by Bove and Capettra in
-\cite{Bove2005}, which in our case basically consists of
-take a general recursive function $f: \sigma \to \tau$.
-and an predicate $P: \sigma \to \abbre{Ind}$, where $\abbre{Ind}$
-is a type with a structure inductive definition.
+To improve that definition for terminating, we will use the
+technique proposed by Bove and Capettra in
+\cite{Bove2005}, which in particular with functions that
+transform propositions consists of:
+take a general recursive function $f: \PROP \to \PROP$.
+and a predicate $P: \PROP \to \abbre{Ind}$, where $\abbre{Ind}$
+is a type with a structured inductive definition.
+
 Then, we redefine the function as
-$f: \sigma \to \abbre{Ind}\ \to \tau$, and perform the recursion
+$f: \PROP \to \abbre{Ind}\ \to \PROP$, and perform the recursion
 using induction on the structure of the \abbre{Ind} type.
 
-In our case, $\abbre{Ind}$ will be the \abbre{Nat} data type for
-natural numbers with constructors \abbre{zero} and \abbre{suc} defined as usual.
+In our case, the \abbre{Nat} data type for
+natural numbers will be the $\abbre{Ind}$ type.
+We define \abbre{Nat} as usual (constructors \zero and \suc).
+We also allow common arithmetic operations and numbers represented by
+$0,1,2,\dots$ that stand for $\zero, \suc, \suc(\zero), \dots$.
 
-Thus, we have function $\unshunt : \PROP \to \Nat \to \PROP$ defined by structural recursion in his second term with type as follows,
+Thus, we have a new function
+$\unshunt : \PROP \to \Nat \to \PROP$
+defined by structural recursion in its second argument in
+Eq.~\ref{eq:unshunt-structured}.
 
-\begin{align*}
+\begin{align}
 \label{eq:unshunt-structured}
+\begin{split}
 \unshunt(φ, \zero) &= φ\\
@@
 \unshunt((φ₁ ∧ φ₂) ⇒ φ₃, n)
-  & φ := φ₁ ⇒ (φ₂ ⇒ φ₃),\\
-\unshunt(φ₁ ⇒ φ₂, n) ∧ \unshunt(φ₁ ⇒ φ₃,n)
-  & φ := φ₁ ⇒ (φ₂ ∧ φ₃).
+  & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
+\unshunt(φ₁ ⇒ φ₂, n)  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).\\
+∧\ \unshunt(φ₁ ⇒ φ₃, n)
 \end{cases}
-\end{align*}
+\end{split}
+\end{align}
 
-Finally, we define the complexity measure to handle the second argument for the \unshunt function.
+To feed the second argument of this new function, we will use
+functions. For instance, we opted to use a complexity measure of
+the formula that \unshunt function transforms.
 
@@
 
-A \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017} or
-a rank function presented in \cite{VanDalen1994} is a function
-$\PROP \to \Nat$ that indents to associate a natural number for a
-proposition φ. The following function is a complexity measure.
+A \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
+and presented in \cite{VanDalen1994} as well as \emph{the rank for a
+proposition} is a function with type
+$\PROP \to \Nat$ that assigns a natural number to a
+proposition φ as follows.
 
@@
 0 &\text{for atomic }φ, \\
-\rank(φ₁) + c_{¬}  & φ := \neg φ₁, \\
+\rank(φ₁) + c_{¬}  & φ ≡ \neg φ₁, \\
 \max(\rank(φ₁),\rank(φ₂)) + c_{\square}
-  & φ := φ₁\,\square\, φ₂.
+  & φ ≡ φ₁\,\square\, φ₂.
 \end{cases}
 \end{equation*}
+
 where $c_{¬}$ or $c_{\square}$ is a non-negative integer called the
@@
 
-Nevertheless, we need to define an appropriate complexity measure for the second argument in the $\unshunt$ function, in order to
-expect the same behavior of the original function as it was defined at first in Eq.~\ref{eq:unshunt-definition}.
+We have already solved the terminating problem for the \unshunt
+function in Eq.~\ref{eq:unshunt-structured}, nevertheless we do not
+what natural number should be feed that argument in
+order to maintain the same outputs as the original \unshunt does in
+Eq.~\ref{eq:unshunt-definition}.
+
+Therefore, we define an appropriate complexity measure
+$\unshunt_{cm}: \PROP → \NN$
+for the second argument of the $\unshunt$ function in
+Eq.~\ref{eq:unshunt-rank-definition}.
 
 \begin{equation}
-\label{eq:rank-definition}
+\label{eq:unshunt-rank-definition}
 \unshunt_{cm}(φ)=
 \begin{cases}
-\unshunt_{cm}(φ₃) + 2 & φ := φ₁ ⇒ (φ₂ ⇒ φ₃),\\
+\unshunt_{cm}(φ₃) + 2 & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
 \max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1
-  & φ := φ₁ ⇒ (φ₂ ∧ φ₃),\\
+  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
 0 &\text{otherwise.}
@@
 
-Then, a curated version of \unshunt is presented in Eq.
+Then, a curated version of the \unshunt functions is presented in Eq.
 \ref{eq:unshunt-fixed}.
@@
 \label{eq:unshunt-fixed}
-\unshunt(\varphi) := \unshunt(\varphi, \unshunt_{cm}(\varphi))
+\unshunt(\varphi) := \unshunt(\varphi, \unshunt_{cm}(\varphi)).
 \end{equation}
-
-In the following section, we may need define such complexity measure
-functions for termination-checking.
 
@@
 
-\emph{Splitting.}
-To prove a goal, we can prove smaller subgoals and combine their
-proofs to achieve the final target, a proof of the initial goal.
+\emph{Splitting a goal.}
+The goal of a proof is processed by \Metis to generated new targets,
+\Metis calls these new formulas \emph{subgoals}.
+Then, \Metis proves each subgoal and with that it finishes the proof
+of the goal.
 
-\begin{theorem}[{\tt thm-$\unshunt^{*}$}] $Γ ⊢ \unshunt^{*}(φ, n)$
-for $n\in \Nat$, then $Γ ⊢ φ$.
+Nevertheless, \Metis does not provide neither an explanation of this
+process in its \TSTP derivations nor in its documentation.
+We provide such a evidence that the process of creating subgoals,
+and combining them in a final conjunction proves the original goal.
+
+\newcommand{\thmunshunt}{\tt thm-$\unshunt$}
+\begin{theorem}[\thmunshunt]
 \label{thm:unshunt}
+$Γ ⊢ \unshunt(φ)$, then $Γ ⊢ φ$.
 \end{theorem}
@@
 \begin{proof} Use induction on the cases defined by the result of
-$\unshunt^{*}$. When $n = 0$, by definition in Eq.
-\ref{eq:unshunt-structured} then $Γ ⊢ φ$.
-For the first case, we prove $Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)$ from
-$Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$.
-Because $n > 0$, using induction on the second argument and the
-theorem $∧⇒$\texttt{-to-}$⇒⇒$ from \cite{AgdaProp}.
+$\unshunt$ in Eq.~\ref{eq:unshunt-structured}.
+When $n = 0$, by definition, $Γ ⊢ φ$.
+When $n = 1$, we apply the following theorem presented in
+\cite{AgdaProp}
 
 \begin{equation*}
+\texttt{∧⇒-to-⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
+\end{equation*}
+
+For $n > 1$, we will use induction on the structure of second
+argument.
+
+(φ₁ ⇒ (φ₂ ⇒ φ₃))
+\begin{equation*}
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
-\RightLabel{By definition}
-\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
-\RightLabel{\tt thm-$\unshunt^{*}$}
+\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
+\RightLabel{\tt thm-$\unshunt$}
 \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
 \RightLabel{\tt ∧⇒-to-⇒⇒}
-\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)}
+\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).}
 \end{bprooftree}
@@
 
-The second case proves $Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)$ from
- $Γ ⊢ \unshunt^{*}(φ₁ ⇒ (φ₂ ∧ φ₃), n)$ and the
-theorem $⇒∧⇒$\texttt{-to-}$⇒∧$ from \cite{AgdaProp}
+Second, using the following theorem from \cite{AgdaProp},
+\begin{equation*}
+\texttt{⇒∧-to-⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).
+\end{equation*}
+
+(φ₁ ⇒ (φ₂ ∧ φ₃))
 \begin{equation*}
 \scalebox{0.95}{
-$\mathcal{D}_1$ := \begin{bprooftree}
-\AxiomC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂, n) ∧ \unshunt^{*}(φ₁ ⇒ φ₃, n)$}
+($\mathcal{D}_1$)
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n) ∧ \unshunt(φ₁ ⇒ φ₃, n)$}
 \RightLabel{\tt ∧-proj₁}
-\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂, n)$}
-\RightLabel{By definition}
-\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂, n-1)$}
-\RightLabel{\tt thm-$\unshunt^{*}$}
-\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n-1)$}
+\RightLabel{\tt thm-$\unshunt$}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$,}
 \end{bprooftree}
@@
 \begin{equation*}
-\mathcal{D}_2 :=
+(\mathcal{D}_2)
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₂) ∧ \unshunt^{*}(φ₁ ⇒ φ₃)$}
+\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂) ∧ \unshunt(φ₁ ⇒ φ₃)$}
 \RightLabel{\tt ∧-proj₂}
-\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₃, n)$}
-\RightLabel{By definition}
-\UnaryInfC{$Γ ⊢ \unshunt^{*}(φ₁ ⇒ φ₃, n-1)$}
-\RightLabel{\tt thm-$\unshunt^{*}$}
-\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₃, n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₃, n-1)$}
+\RightLabel{\tt thm-$\unshunt$}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$,}
 \end{bprooftree}
@@
 \RightLabel{\tt ⇒∧⇒-to-⇒∧}
-\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
+\UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).}
 \end{bprooftree}
@@
 
-\vskip 3mm
-
-From now on, we redefine the function $\unshunt$ with the
-definition of $\unshunt^{+}$ for no overloading the notation forward.
-
-\begin{theorem}[{\tt thm-\unshunt}] $Γ ⊢ \unshunt(φ)$ then $Γ ⊢ φ$.
-\end{theorem}
-\begin{proof} It follows from Thm.~\ref{thm:unshunt} using the
-\rank function as the second argument.
-\end{proof}
-
-The \mysplit function yields a conjunction of subformulas that
-implies the proposition φ, the argument of the function. This
-function has type $\PROP \to \NN \to PROP$, its definition is
- $\mysplit(φ,0) = φ$, and
-for all$n\in \NN$, $n > 0$,
+Now, let us consider the \mysplit function that
+yields the conjunction of subgoals from a proposition goal.
 
@@
 \label{eq:split-definition}
-\mysplit(φ,n+1) =
+\mysplit(φ) =
 \begin{cases}
-\unshunt(\mysplit(φ₁,n)) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n)
-  & φ := φ₁ ∧ φ₂,\\
+\unshunt(\mysplit(φ₁))              & φ ≡ φ₁ ∧ φ₂,\\
+∧\ \unshunt(φ₁ ⇒ \mysplit(φ₂))      &\\[2mm]
 
-\unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n))
-  & φ := φ₁ ∨ φ₂,\\
+\unshunt(¬ φ₁ ⇒ \mysplit(φ₂))       & φ ≡ φ₁ ∨ φ₂,\\
 
-\unshunt(φ₁ ⇒ \mysplit(φ₂,n))
-  & φ := φ₁ ⇒ φ₂,\\
+\unshunt(φ₁ ⇒ \mysplit(φ₂))         & φ ≡ φ₁ ⇒ φ₂,\\
 
-\unshunt(φ₁ ⇒ \mysplit(φ₂,n)) ∧ \unshunt(φ₂ ⇒ \mysplit(φ₁,n))
-  & φ := φ₁ ⇔ φ₂,\\
+\unshunt(φ₁ ⇒ \mysplit(φ₂))         & φ ≡ φ₁ ⇔ φ₂,\\
+∧\ \unshunt(φ₂ ⇒ \mysplit(φ₁))      &\\[2mm]
 
-\unshunt(φ₁ ⇒ \mysplit(¬ φ₂, n))
-  & φ := ¬ (φ₁ ∧ φ₂),\\
+\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & φ ≡ ¬ (φ₁ ∧ φ₂),\\
 
-\unshunt(\mysplit(¬ φ₁,n)) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂,n))
-  & φ := ¬ (φ₁ ∨ φ₂),\\
+\unshunt(\mysplit(¬ φ₁))            & φ ≡ ¬ (φ₁ ∨ φ₂),\\
+∧\ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂))  &\\[2mm]
 
-\unshunt(\mysplit(φ₁,n)) ∧ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂,n))
-  & φ := ¬ (φ₁ ⇒ φ₂),\\
+\unshunt(\mysplit(φ₁))              & φ ≡ ¬ (φ₁ ⇒ φ₂),\\
+∧\ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂))    &\\[2mm]
 
-\unshunt(φ₁ ⇒ \mysplit(¬ φ₂,n)) ∧ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁,n))
-  & φ := ¬ (φ₁ ⇔ φ₂),\\
+\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & φ ≡ ¬ (φ₁ ⇔ φ₂),\\
+∧\ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))    &\\[2mm]
 
-\unshunt(\mysplit(φ₁, n))
-  & φ := ¬ ¬ φ₁,\\
-
-⊤ & φ := ¬ ⊥,\\
-
-⊥ & φ := ¬ ⊤.
+\unshunt(\mysplit(φ₁))              & φ ≡ ¬ ¬ φ₁,\\
+⊤                                   & φ ≡ ¬ ⊥,\\
+⊥                                   & φ ≡ ¬ ⊤.
 \end{cases}
 \end{equation}
+
+We reformulate \mysplit function to match with the
+new definition after apply the process described above in
+subsection~\ref{ssec:well-structured recursion}, since
+in the recursion calls of \mysplit in Eq.~\ref{eq:split-definition},
+the negations, $(¬ φ_{1,2})$ raise a terminating problem.
 
@@
 
-\begin{proof} We use induction on the structure of the formula
-following the cases in the definition of \mysplit function.
-We proceed to show some cases since the others are proved in a
-similar way.\\[3mm]
-(φ := φ₁ ∧ φ₂)
+\begin{proof} We now proceed by induction on the structure of the
+formula φ in the definition of Eq.~\ref{eq:split-definition}.
+For a complete proof, we refer the reader to \cite{AgdaMetis}.\\[3mm]
+
+(φ ≡ φ₁ ∧ φ₂)
 \begin{equation*}
@@
 
-\AxiomC{$Γ ⊢ \mysplit(φ)$}
-\RightLabel{By Def.}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂))$}
+\AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
 \RightLabel{\tt $∧$-proj$₂$}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂))$}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
 \RightLabel{\thmunshunt}
-\UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂)$}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
 \RightLabel{\tt $⇒$-elim}
-\BinaryInfC{$Γ ⊢ \mysplit(φ₂)$}
+\BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
 \RightLabel{\thmsplit}
@@
 \RightLabel{\tt ∧-intro}
-\BinaryInfC{$Γ ⊢ φ₁ ∧ φ₂$}
+\BinaryInfC{$Γ ⊢ φ₁ ∧ φ₂$.}
 \end{bprooftree}
 \end{equation*}
-where
+Where,
 \begin{equation*}
-\mathcal{D}_1 =
+(\mathcal{D}_1)\hspace{3mm}
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ \mysplit(φ)$}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂))$}
+\AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
 \RightLabel{\tt ∧-proj₁}
@@
 \RightLabel{\thmunshunt}
-\UnaryInfC{$Γ ⊢ φ₁$}
+\UnaryInfC{$Γ ⊢ φ₁$.}
 \end{bprooftree}
@@
 
-(φ := φ₁ ⇒ φ₂)
+(φ ≡ φ₁ ⇒ φ₂)
 \begin{equation*}
@@
 \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
-\AxiomC{$Γ ⊢ \mysplit(φ)$}
+\AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
 \RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂))$}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
 \RightLabel{\thmunshunt}
-\UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂)$}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
 \RightLabel{weaken φ₁}
-\UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂)$}
+\UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
 \RightLabel{\tt ⇒-elim}
-\BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂)$}
+\BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂,n-1)$}
 \RightLabel{\thmsplit}
@@
 \RightLabel{\tt ⇒-intro}
-\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$.}
 \end{bprooftree}
@@
 
-(φ := ¬ (φ₁ ∨ φ₂))
+(φ ≡ ¬ (φ₁ ∨ φ₂))
 \begin{equation*}
@@
 
-\AxiomC{$Γ ⊢ \mysplit(φ)$}
+\AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
 \RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂))$}
+\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
 \RightLabel{\tt ∧-proj₂}
-\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂))$}
+\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
 \RightLabel{\thmunshunt}
-\UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂)$}
+\UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂,n-1)$}
 \RightLabel{\tt ⇒-elim}
-\BinaryInfC{$Γ ⊢ \mysplit(φ₂)$}
+\BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
 \RightLabel{\thmsplit}
@@
 \RightLabel{\tt ¬∧¬-to-¬∨}
-\UnaryInfC{$Γ ⊢ ¬ (φ₁ ∨ φ₂)$}
+\UnaryInfC{$Γ ⊢ ¬ (φ₁ ∨ φ₂)$.}
 \end{bprooftree}
 \end{equation*}
-where
+
+Where,
+
 \begin{equation*}
-\mathcal{D} =
+(\mathcal{D})
 \begin{bprooftree}
@@
 \RightLabel{\thmunshunt}
-\UnaryInfC{$Γ ⊢ ¬ φ₁$}
+\UnaryInfC{$Γ ⊢ ¬ φ₁$.}
 \end{bprooftree}
 \end{equation*}
-% (φ := ¬ (φ₁ ⇔ φ₂))
-% \begin{equation*}
-% \begin{bprooftree}
-
-% % -- right
-
-% \AxiomC{$Γ ⊢ \mysplit(φ, n)$}
-% \RightLabel{By def.}
-% \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂)) ∧ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁)) $}
-% \RightLabel{\tt ∧-proj₂}
-% \UnaryInfC{$Γ ⊢ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))$}
-% \RightLabel{\tt \thmunshunt}
-% \UnaryInfC{$Γ ⊢ ¬ φ₂ ⇒ \mysplit(φ₁)$}
-% \RightLabel{\tt weaken ¬ φ₂}
-% \UnaryInfC{$Γ , ¬ φ₂ ⊢ ¬ φ₂ ⇒ \mysplit(φ₁)$}
-
-% % -- right
-
-% % -- left
-% \AxiomC{}
-% \RightLabel{\tt assume (¬ φ₂)}
-% \UnaryInfC{$Γ , ¬ φ₂ ⊢ ¬ φ₂$}
-% \RightLabel{\tt ⇒-elim}
-
-% \BinaryInfC{$Γ , ¬ φ₂ ⊢ \mysplit(φ₁)$}
-% \RightLabel{\thmsplit}
-% \UnaryInfC{$Γ , ¬ φ₂ ⊢ φ₁ $}
-% \RightLabel{\tt ⇒-intro}
-% \UnaryInfC{$Γ ⊢ ¬ φ₂ ⇒ φ₁$}
-% % -- left
-
-% % \RightLabel{\tt ∧-intro}
-% % \BinaryInfC{$Γ ⊢ (φ₁ ⇒ ¬ φ₂) ∧ (¬ φ₂ ⇒ φ₁)$}
-% % \RightLabel{\tt ⇒¬∧¬⇒-to-¬⇔}
-% % \UnaryInfC{$Γ ⊢ ¬ (φ₁ ⇔ φ₂)$}
-% \end{bprooftree}
-% \end{equation*}
-
 \end{proof}
 
-The \mysplit function returns a conjunction of the subgoals.
-From each \TSTP derivation, we actually have information of the
-subgoals but it is not explicit how they appear in the conjunction.
-For that reason, with \Athena, we infer the exact order in the
-conjunction that coincides with the output by \mysplit.
+\begin{theorem} If $s_i$ are the subgoals for the goal φ, and $\{ Γ ⊢ s_i \}_{i}$, then $Γ ⊢ φ$.
+\end{theorem}
 
-\begin{theorem} For a list of subgoals $s_0, \cdots, s_1$ with their
-respective theorem $Γ ⊢ s_i$, such that $\bigwedge_i s_i ⇒ \texttt{goal}$, then $Γ ⊢ \texttt{goal}$.
-\end{theorem}
+\begin{proof}
+\begin{equation*}
+\begin{bprooftree}
+\AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i}$}
+\RightLabel{\tt ∧-intro}
+\UnaryInfC{$Γ ⊢ \bigwedge_i s_i$}
+
+\AxiomC{$\mysplit(φ) ≡ \bigwedge_i s_i $}
+\RightLabel{\tt subst}
+\BinaryInfC{$Γ ⊢ \mysplit(φ) $}
+
+\RightLabel{\thmsplit}
+\UnaryInfC{$Γ ⊢ φ$.}
+\end{bprooftree}
+\end{equation*}
+Where,
+\begin{equation*}
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
+\RightLabel{\tt subst}
+\BinaryInfC{$Γ ⊢ ψ$.}
+\end{bprooftree}
+\end{equation*}
+\end{proof}
 
@@
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ (φ₁ := l ∨ ψ₁)$}
-\AxiomC{$Γ ⊢ (φ₂ := ¬ l ∨ ψ₂)$}
+\AxiomC{$Γ ⊢ (φ₁ ≡ l ∨ ψ₁)$}
+\AxiomC{$Γ ⊢ (φ₂ ≡ ¬ l ∨ ψ₂)$}
 \RightLabel{\thmresolve}
@@
 \resolve((φ₁, φ₂, l, ψ)
+\end{equation}
 

### 2017-09-14 paper/sections/implementation.tex
[ paper ] improving minor texts.

@@
 
-In \Agda, we define a proposition formula
-as an inductive type using the keyword \texttt{data} extending the
-its definition in \cite{Altenkirch2015}.
-The \name{PropFormula} data type stands for propositions
-as we define in section \ref{sec:preliminaries}.
+In \Agda, we have defined a proposition formula
+as an inductive type using the keyword \texttt{data} and the name
+\name{PropFormula}.
+We extended the definition for propositions presented in
+\cite{Altenkirch2015} to mathc the definion in section
+\ref{sec:preliminaries}.
 We include every connective and logic constant as a constructor.

### 2017-09-14 paper/sections/proof-reconstruction.tex
[ paper ] improving minor texts.

@@
 
-\begin{theorem} If $s_i$ are the subgoals for the goal φ, and $\{ Γ ⊢ s_i \}_{i}$, then $Γ ⊢ φ$.
+\begin{theorem} If $s_i$ are the subgoals for the goal φ, and
+$\{ Γ ⊢ s_i \}_{i}$, then $Γ ⊢ φ$.
 \end{theorem}
@@
 
-To rearrange the proposition in order to match with a specific
-pattern of a formula, we define the following functions and provide
+To rearrange the propositions in order to match with a specific
+pattern for applying a particular theorem like resolution, we have
+define the following functions and provide
 its respective theorems in \cite{AgdaMetis}.
+These rearrangement functions are mainly inspired in
+\cite{bohme2010}, for their treatment for conjunction and
+disjunction equivalence.
+
+\improvement{provide examples for each of the following functions.}
 
 \begin{itemize}
-  \item[] \name{reorder-∨}
-  \item[] \name{reorder-∧}
-  \item[] \name{reorder-∧∨}
+  \item \name{reorder-∨.} Given two formulas, φ and ψ, both disjunctions, fix the order of the first one by following the syntactically
+  order of the second one. If the process succeed (denote by φ ⤳ ψ),
+  returns the target formula, ψ, otherwise, keep the first one, φ.
+  \begin{align}
+  \begin{split}
+&\name{reorder-∨}\ :\ \PROP \to \PROP \to \PROP\\
+&\name{reorder-∨}(φ, ψ) =
+  \begin{cases}
+  ψ   & φ ⤳ ψ\\
+  ϕ   & \text{otherwise.}
+  \end{cases}
+  \end{split}
+  \end{align}
+
+  \item \name{reorder-∧.} Given two formulas, φ and ψ, both conjunctions, fix the order of the first one by following the order  of the second one.
+  \item \name{reorder-∧∨.} Given two formulas, φ and ψ, both in CNF, fix the order of the first one by following the order  of the second one.
 \end{itemize}

### 2017-09-14 paper/sections/proof-reconstruction.tex
[ paper ] citation using natbib.

@@
 The proof-reconstruction approach proposed here consists of a series
-of steps similar to the workflow presented by Sultana in
+of steps similar to the workflow presented by Sultana et al in
 \cite{sultana2015}. This process is a translation from a source
@@
 input of the \Metis prover.
-The proof-search algorithms of \Metis in step No. 3 intend to find
+The algorithms of \Metis in step~3 intend to find
 a solution; if they success, \Metis replies a derivation in \TSTP
-format of the proof, else \Metis may no stop and running forever or
-replies the problem is counter feasible.
+format of the proof, else the problem is counter feasible.
 
@@
 
-Finally, we use the proof assistant in step No. 7 to type-check the
+Finally, we use the proof assistant in step 7 to type-check the
 proof and verify its correctness. Next, we only have one answer:
@@
 
-\subsection{Well-Structured Recursion}
-\label{ssec:well-structured recursion}
+\subsection{Small Structured Recursion}
+\label{ssec:small-structured-recursion}
 
 In the process to emulate \Metis' inference rules in type theory,
-We encountered many recursive algorithms with termination problems,
+we encountered many recursive algorithms with termination problems,
 that is,when an algorithm could run forever or we can not guarantee
@@
 
-A recursive function is a \emph{well-structured recursion}, if the
+A recursive function is a \emph{small-structured-recursion}, if the
 size of the arguments with which it is defined decrease in
@@
 
-Let us consider the following example from a inner function
+Let us consider the following example from an inner function
 in the \strip inference.
@@
 \label{eq:unshunt-definition}
-\unshunt(φ) =
+\unshunt(φ)_{0} =
 \begin{cases}
-\unshunt((φ₁ ∧ φ₂) ⇒ φ₃)
+\unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃)
   & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
 
-\unshunt(φ₁ ⇒ φ₂) ∧ \unshunt(φ₁ ⇒ φ₃)
+\unshunt_{0}(φ₁ ⇒ φ₂) ∧ \unshunt_{0}(φ₁ ⇒ φ₃)
   & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
@@
 From the definition above, in the first case of the \unshunt
-function, the size of the argument doesn't really decrease.
-Actually, it maintains with the same length syntactically
-(i.e., (φ₁ ∧ φ₂) ⇒ φ₃ compared with (φ₁ ⇒ (φ₂ ⇒ φ₃))).
-Therefore, a termination checking will fail with \unshunt function.
+function, the size of the argument in the recursion,(φ₁ ∧ φ₂) ⇒ φ₃,
+is not structured smaller than the decrease, (φ₁ ⇒ (φ₂ ⇒ φ₃)).
+Therefore, a termination checking will fail with the \unshunt
+function.
 
@@
 Thus, we have a new function
-$\unshunt : \PROP \to \Nat \to \PROP$
+$\unshunt_{1} : \PROP \to \Nat \to \PROP$
 defined by structural recursion in its second argument in
@@
 \begin{split}
-\unshunt(φ, \zero) &= φ\\
-\unshunt(φ, \suc(n)) &=
+\unshunt_{1}(φ, \zero) &= φ\\
+\unshunt_{1}(φ, \suc(n)) &=
 \begin{cases}
-\unshunt((φ₁ ∧ φ₂) ⇒ φ₃, n)
+\unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n)
   & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
-\unshunt(φ₁ ⇒ φ₂, n)  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).\\
-∧\ \unshunt(φ₁ ⇒ φ₃, n)
+\unshunt_{1}(φ₁ ⇒ φ₂, n)  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).\\
+∧\ \unshunt_{1}(φ₁ ⇒ φ₃, n)
 \end{cases}
@@
 functions. For instance, we opted to use a complexity measure of
-the formula that \unshunt function transforms.
+the formula that $\unshunt_{1}$ function transforms.
 
@@
 $\unshunt_{cm}: \PROP → \NN$
-for the second argument of the $\unshunt$ function in
+for the second argument of the $\unshunt_{1}$ function in
 Eq.~\ref{eq:unshunt-rank-definition}.
@@
 
-Then, a curated version of the \unshunt functions is presented in Eq.
+Then, a curated version of the $\unshunt_{0}$ function is presented in Eq.
 \ref{eq:unshunt-fixed}.
@@
 \label{eq:unshunt-fixed}
-\unshunt(\varphi) := \unshunt(\varphi, \unshunt_{cm}(\varphi)).
+\unshunt(\varphi) := \unshunt_{1}(\varphi, \unshunt_{cm}(\varphi)).
 \end{equation}
+\change{changes the name of the functions to avoid different
+functions with the same name.}
 
@@
 new definition after apply the process described above in
-subsection~\ref{ssec:well-structured recursion}, since
+subsection~\ref{ssec:small-structured-recursion}, since
 in the recursion calls of \mysplit in Eq.~\ref{eq:split-definition},

### 2017-09-14 paper/fix-references.sh

@@ -1,3 +1,3 @@
 #!/bin/sh
 
-sed -i -r "/(url|doi)/ s/\{.?(.)\}/\1/g" ref.bib
+sed -i -r "/(url|doi)/ s/\{.?(.)\}/\1/g" ref-mendeley.bib

### 2017-09-15 paper/sections/introduction.tex
[ paper ] cosmetics.

@@
 We briefly mention notation and syntax of the classical propositional
-logic in section \ref{sec:preliminaries}.
+logic in Section \ref{sec:preliminaries}.
 In section \ref{sec:metis-language-and-proofs}, we introduce the
@@
 approach to reconstruct proofs deliver by \Metis in type theory.
-We listed some conclusions and future work in section
+We listed some conclusions and future work in Section
 \ref{sec:conclusions}. At the end, we list some related works in
-proof reconstruction in section \ref{sec:related-work}.
+proof reconstruction in Section \ref{sec:related-work}.
 The appendix \textsc{A} shows a complete example of the proof

### 2017-09-15 paper/sections/proof-reconstruction.tex
[ paper ] cosmetics.

@@
 The proof-reconstruction approach proposed here consists of a series
-of steps similar to the workflow presented by Sultana et al in
+of steps similar to the workflow presented by \citeauthor{sultana2015} in
 \cite{sultana2015}. This process is a translation from a source
@@
 support of type theory and similar features like \Agda
-(see a description of \Agda in section
+(see a description of \Agda in Section
 \ref{sec:implementation}) can be used.
@@
 proof using a version of a tree data structure (see the properties
-of this tree in subsection \ref{ssec:metis-proofs}). As a result,
+of this tree in Subsection \ref{ssec:metis-proofs}). As a result,
 \Athena generates an \Agda file with such a proof. We have included
@@
 
+\change{remove the use of tt for functions. (rank, etc..)}
 \begin{equation}
@@
 
-Then, a curated version of the $\unshunt_{0}$ function is presented in Eq.
-\ref{eq:unshunt-fixed}.
+Then, a curated version of the $\unshunt_{0}$ function is presented
+in Eq.~\ref{eq:unshunt-fixed}.
 

### 2017-09-15 paper/fix-references.sh

@@ -1,3 +1,4 @@
 #!/bin/sh
 
-sed -i -r "/(url|doi)/ s/\{.?(.)\}/\1/g" ref-mendeley.bib
+sed -i -r "/(url|doi)/ s/\{.?(.)\}/\1/g" ref.bib
+sed -i -r "s/journaltitle/journal     /g" ref.bib

### 2017-09-15 paper/sections/conclusions.tex
[ paper ] cosmetics.
[ paper ] removed file field from ref.bib.

@@
 proof-reconstruction tools (see a list of some of them in the
-related work, section \ref{sec:related-work}), we found some issues
+related work, Section \ref{sec:related-work}), we found some issues
 around the reconstruction that show this task is far from trivial.
 Depending  on the systems involved in the translation, some
-difficulties can arise. We listed some of them in section
-\ref{sec:metis-language-and-proofs} and in the section
+difficulties can arise. We listed some of them in Section
+\ref{sec:metis-language-and-proofs} and in Section
 \ref{sec:proof-reconstruction}.

### 2017-09-15 paper/sections/introduction.tex
[ paper ] removed file field from ref.bib.

@@
 logic. These tools are usually classified in at least one of the
-following categories. A \SAT solver (e.g., \name{zChaff}
-\cite{Moskewicz2001} and \name{MiniSat}~\cite{Een2004}) to prove
-unsatisfiability of \CNF formulas, a \abbre{QBF} solver (e.g.,
-\name{GhostQ}~\cite{Klieber2014} and \name{DepQBF}
-\cite{Lonsing2017}) to prove satisfiability and invalidity of
-quantified Boolean formulas, a \SMT solver (e.g \name{CVC4}
-\cite{Barrett2011}, \name{veriT}~\cite{bouton2009}, and \name{Z3}
-\cite{DeMoura2008}) to prove unsatisfiability of formulas from
-first-order logic with theories, and a prover for validity of
-formulas from first-order logic with equality (e.g., \name{E}
-\cite{Schulz:AICOM-2002}, \name{leanCoP}~\cite{Otten2008}, \Metis
-\cite{hurd2003first}, \name{SPASS} ~\cite{Weidenbach2009} and
+following categories.
+A \SAT solver (e.g., \name{zChaff}~\cite{Moskewicz2001} and
+\name{MiniSat}~\cite{Een2004}) to prove unsatisfiability of \CNF
+formulas, a \abbre{QBF} solver (e.g.,
+\name{GhostQ}~\cite{Klieber2014} and
+\name{DepQBF}~\cite{Lonsing2017}) to prove satisfiability and
+invalidity of quantified Boolean formulas, a \SMT solver
+(e.g \name{CVC4}~\cite{Barrett2011},\name{veriT}~\cite{bouton2009},
+and \name{Z3}~\cite{DeMoura2008}) to prove unsatisfiability of
+formulas from first-order logic with theories, and a prover for
+validity of formulas from first-order logic with equality
+(e.g.,\name{E}~\cite{Schulz:AICOM-2002},
+\name{leanCoP}~\cite{Otten2008},
+\Metis~\cite{hurd2003first},
+\name{SPASS}~\cite{Weidenbach2009} and
 \name{Vampire}~\cite{Riazanov1999}), high-order logic (e.g.,
-\name{Leo-II} \cite{Benzmuller2008} and \name{Satallax}
-\cite{Brown2012}) or intuitionistic logic (e.g., \name{ileanCoP}
-\cite{Otten2008}, \name{JProver} \cite{Schmitt2001}, and
+\name{Leo-II}~\cite{Benzmuller2008} and
+\name{Satallax}~\cite{Brown2012}) or intuitionistic logic (e.g.,
+\name{ileanCoP}~\cite{Otten2008},
+\name{JProver}~\cite{Schmitt2001}, and
 \name{Gandalf}~\cite{Tammet1997}), among others. On the other hand,
 we have the proof checkers, interactive theorem provers (henceforth
-\ITP) or proof assistants (e.g., \Agda~\cite{agdateam}, \name{Coq}
-\cite{coqteam}, \name{Isabelle}~\cite{paulson1994isabelle}, and
+\ITP) or proof assistants (e.g., \Agda~\cite{agdateam},
+\name{Coq}~\cite{coqteam},
+\name{Isabelle}~\cite{paulson1994isabelle}, and
 \name{HOL4}~\cite{norrish2007hol}). The \ITP tools provide us the
@@
 service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
-provers were able to deliver proofs (e.g., \name{CVC4}
-\cite{Barrett2011}, \name{SPASS}, and \name{Waldmeister}
-\cite{hillenbrand1997}) and a little bit less replied with a proof
+provers were able to deliver proofs (e.g.,
+\name{CVC4}~\cite{Barrett2011}, \name{SPASS}, and
+\name{Waldmeister}~\cite{hillenbrand1997}) and a little bit less replied with a proof
 in a file format like \TSTP~\cite{sutcliffe2004tstp} (e.g.,
-\name{E}, \Metis, \name{Vampire}, and \name{Z3}), \len{LFSC}
-\cite{Stump2008}, or the \len{SMT-LIB}~\cite{Bohme2011} format.
+\name{E}, \Metis, \name{Vampire}, and \name{Z3}),
+\len{LFSC}~\cite{Stump2008}, or the \len{SMT-LIB}~\cite{Bohme2011} format.
 
@@
 \cite{Kanso2012}). We mention some of these tools in the related
-work, section \ref{sec:related-work}.
+work, Section \ref{sec:related-work}.
 
@@
 logic in Section \ref{sec:preliminaries}.
-In section \ref{sec:metis-language-and-proofs}, we introduce the
+In Section \ref{sec:metis-language-and-proofs}, we introduce the
 \Metis prover and its deduction system.
-In section \ref{sec:proof-reconstruction}, we present our
+In Section \ref{sec:proof-reconstruction}, we present our
 approach to reconstruct proofs deliver by \Metis in type theory.

### 2017-09-15 paper/sections/metis-language-and-proofs.tex
[ paper ] cosmetics.
[ paper ] removed file field from ref.bib.

@@
 This is an attempt to fulfill the \Metis's documentation, by
-describing each rule from our perspective. Later on, in section
+describing each rule from our perspective. Later on, in Section
 \ref{sec:proof-reconstruction}, we present a formal description of
@@
 conjunction of these subgoals implies the goal as we show later in
-subsection~\ref{ssec:emulating-inferences}. Then, a proof of the
+Subsection~\ref{ssec:emulating-inferences}. Then, a proof of the
 goal becomes in smaller proofs, one refutation for each subgoal.

### 2017-09-15 paper/sections/proof-reconstruction.tex
[ paper ] removed file field from ref.bib.

@@
 
-\newcommand{\rank}{\name{rank}}
-
 A \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
@@
 \label{eq:rank-definition}
-\rank(φ)=
+rank(φ)=
 \begin{cases}
 0 &\text{for atomic }φ, \\
-\rank(φ₁) + c_{¬}  & φ ≡ \neg φ₁, \\
-\max(\rank(φ₁),\rank(φ₂)) + c_{\square}
+rank(φ₁) + c_{¬}  & φ ≡ \neg φ₁, \\
+\max{(rank(φ₁),rank(φ₂)} + c_{\square}
   & φ ≡ φ₁\,\square\, φ₂.
@@
 new definition after apply the process described above in
-subsection~\ref{ssec:small-structured-recursion}, since
+Subsection~\ref{ssec:small-structured-recursion}, since
 in the recursion calls of \mysplit in Eq.~\ref{eq:split-definition},
@@
 formula φ in the definition of Eq.~\ref{eq:split-definition}.
-For a complete proof, we refer the reader to \cite{AgdaMetis}.\\[3mm]
+For a complete proof, we refer the reader to~\cite{AgdaMetis}.\\[3mm]
 

### 2017-09-15 paper/sections/related-work.tex
[ paper ] cosmetics.
[ paper ] removed file field from ref.bib.

@@
 \name{Isabelle/HOL} \cite{nipkow2002isabelle}, the specialization of
-\name{Isabelle} for higher-order logic. Sultana, Benzm{\"{u}}ller,
-and Paulson~\cite{Een2004} integrates \name{Leo-II} and
+\name{Isabelle} for higher-order logic.
+\citeauthor{Een2004}~\cite{Een2004} integrates \name{Leo-II} and
 \name{Satallax}, two theorem provers for high-order logic with
@@
 \name{Coq} proof assistant \cite{coqteam} which provides a certified
-checker for proof witness coming from the \SMT solver \name{veriT}
-\cite{bouton2009} and adds a new tactic named verit, that calls
-\name{veriT} on any \name{Coq} goal. In \cite{bezem2002automated},
+checker for proof witness coming from the \SMT solver
+\name{veriT}~\cite{bouton2009} and adds a new tactic named verit,
+that calls \name{veriT} on any \name{Coq} goal.
+In \cite{bezem2002automated},
 given a fixed but arbitrary first-order signature, the authors
@@
 \name{HOL} but with a simpler logic core, the \SMT solver \name{CVC4}
-was integrated, and Kaliszyk and Urban~\cite{kaliszyk2013}
+was integrated, and \citeauthor{kaliszyk2013}~\cite{kaliszyk2013}
 reconstruct proofs from different ATPs with their \name{PRocH} tool,
@@
 \name{Waldmeister} is an automatic theorem prover for unit
-equational logic \cite{hillenbrand1997}. Foster and Struth
-\cite{foster2011integrating} integrate \name{Waldmeister} into \Agda
+equational logic \cite{hillenbrand1997}.
+\citeauthor{foster2011integrating}~\cite{foster2011integrating}
+integrate \name{Waldmeister} into \Agda
 \cite{agdateam}. This integration requires a proof-reconstruction
@@
 % propositional logic using semantics that we do not take into account for the
-% reason we describe later on in section~\ref{sec:conclusions}.
+% reason we describe later on in Section~\ref{sec:conclusions}.
 

### 2017-09-15 paper/fix-references.sh

@@ -2,3 +2,4 @@
 
 sed -i -r "/(url|doi)/ s/\{.?(.)\}/\1/g" ref.bib
 sed -i -r "s/journaltitle/journal     /g" ref.bib
+sed -i -r "/file/d" ref.bib

### 2017-09-15 paper/sections/preliminaries.tex
[ paper ] citation using natbib.
[ travis-ci ] fixed cpphs requirement.

@@
 propositional negation $(¬)$, and logic constants $⊥$
-and $⊤$. We use the inductive definition of the set \PROP
+and $⊤$. We use the inductive definition of the set \Prop
 presented in \cite{VanDalen1994} as the mechanism to produce any
 propositional formula.
-Then, $ϕ_i \in \PROP$ for all $i \in \mathbb{N}$.
-If $φ, ψ\in \PROP$, then $(φ\ \square\ ψ) \in \PROP$,
+Then, $ϕ_i \in \Prop$ for all $i \in \mathbb{N}$.
+If $φ, ψ\in \Prop$, then $(φ\ \square\ ψ) \in \Prop$,
 where $(φ\ \square\ ψ)$ stands for a proposition that use a
 binary connective in the place for the $\square$ symbol.
-If $φ \in \PROP$, then $(¬ φ) \in \PROP$.
-Finally, $⊥, ⊤ \in \PROP$.
+If $φ \in \Prop$, then $(¬ φ) \in \Prop$.
+Finally, $⊥, ⊤ \in \Prop$.
 
@@
 how they can be remove them in the conclusion side of the theorems.
+\change{the size of the text.}
 
@@
 \AxiomC{}
-\RightLabel{\scriptsize\tt assume $φ$}
+\RightLabel{\tt assume $φ$}
 \UnaryInfC{$Γ , φ ⊢ φ$}
@@
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{\scriptsize\tt weaken $ψ$}
+\RightLabel{\tt weaken $ψ$}
 \UnaryInfC{$Γ , ψ ⊢ φ$}
@@
 \AxiomC{}
-\RightLabel{\scriptsize\tt $⊤$-intro}
+\RightLabel{\tt $⊤$-intro}
 \UnaryInfC{$Γ ⊢ ⊤$}
@@
 \AxiomC{$Γ ⊢ ⊥$}
-\RightLabel{\scriptsize\tt $⊥$-elim $φ$}
+\RightLabel{\tt $⊥$-elim $φ$}
 \UnaryInfC{$Γ ⊢ φ$}
@@
 \AxiomC{$Γ , φ ⊢ ⊥$}
-\RightLabel{\scriptsize\tt $¬$-intro}
+\RightLabel{\tt $¬$-intro}
 \UnaryInfC{$Γ ⊢ ¬ φ$}
@@
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{\scriptsize\tt $¬$-elim}
+\RightLabel{\tt $¬$-elim}
 \BinaryInfC{$Γ ⊢ ⊥$}
@@
 \AxiomC{$Γ ⊢ ψ$}
-\RightLabel{\scriptsize\tt $\wedge$-intro}
+\RightLabel{\tt $\wedge$-intro}
 \BinaryInfC{$Γ ⊢ φ \wedge ψ$}
@@
 \AxiomC{$Γ ⊢ φ \wedge ψ$}
-\RightLabel{\scriptsize\tt $\wedge$-proj$_1$}
+\RightLabel{\tt $\wedge$-proj$_1$}
 \UnaryInfC{$Γ⊢ φ$}
@@
 \AxiomC{$Γ ⊢ φ \wedge ψ$}
-\RightLabel{\scriptsize\tt $\wedge$-proj$_2$}
+\RightLabel{\tt $\wedge$-proj$_2$}
 \UnaryInfC{$Γ⊢ ψ$}
@@
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{\scriptsize\tt $\vee$-intro$_1$ $ψ$}
+\RightLabel{\tt $\vee$-intro$_1$ $ψ$}
 \UnaryInfC{$Γ ⊢ φ \vee ψ$}
@@
 \AxiomC{$Γ ⊢ ψ$}
-\RightLabel{\scriptsize\tt $\vee$-intro$_2$ $φ$}
+\RightLabel{\tt $\vee$-intro$_2$ $φ$}
 \UnaryInfC{$Γ ⊢ φ \vee ψ$}
@@
 \AxiomC{$Γ , ψ  ⊢ \gamma$}
-\RightLabel{\scriptsize\tt $\vee$-elim}
+\RightLabel{\tt $\vee$-elim}
 \BinaryInfC{$Γ , φ \vee ψ ⊢ \gamma$}
@@
 \AxiomC{$Γ , φ ⊢ ψ$}
-\RightLabel{\scriptsize\tt $\Rightarrow$-intro}
+\RightLabel{\tt $\Rightarrow$-intro}
 \UnaryInfC{$Γ ⊢ φ \Rightarrow ψ$}
@@
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{\scriptsize\tt $\Rightarrow$-elim}
+\RightLabel{\tt $\Rightarrow$-elim}
 \BinaryInfC{$Γ ⊢ ψ$}
@@
 \AxiomC{$Γ , ψ ⊢ φ$}
-\RightLabel{\scriptsize\tt $⇔$-intro}
+\RightLabel{\tt $⇔$-intro}
 \BinaryInfC{$Γ ⊢ φ ⇔ ψ$}
@@
 \AxiomC{$Γ ⊢ φ ⇔ ψ$}
-\RightLabel{\scriptsize\tt $⇔$-elim$_1$}
+\RightLabel{\tt $⇔$-elim$_1$}
 \BinaryInfC{$Γ ⊢ ψ$}
@@
 \AxiomC{$Γ ⊢ φ ⇔ ψ$}
-\RightLabel{\scriptsize\tt $⇔$-elim$_2$}
+\RightLabel{\tt $⇔$-elim$_2$}
 \BinaryInfC{$Γ ⊢ ψ$}

### 2017-09-15 paper/sections/proof-reconstruction.tex
[ travis-ci ] fixed cpphs requirement.

@@
 transform propositions consists of:
-take a general recursive function $f: \PROP \to \PROP$.
-and a predicate $P: \PROP \to \abbre{Ind}$, where $\abbre{Ind}$
+take a general recursive function $f: \Prop \to \Prop$.
+and a predicate $P: \Prop \to \abbre{Ind}$, where $\abbre{Ind}$
 is a type with a structured inductive definition.
@@
 Then, we redefine the function as
-$f: \PROP \to \abbre{Ind}\ \to \PROP$, and perform the recursion
+$f: \Prop \to \abbre{Ind}\ \to \Prop$, and perform the recursion
 using induction on the structure of the \abbre{Ind} type.
@@
 Thus, we have a new function
-$\unshunt_{1} : \PROP \to \Nat \to \PROP$
+$\unshunt_{1} : \Prop \to \Nat \to \Prop$
 defined by structural recursion in its second argument in
@@
 proposition} is a function with type
-$\PROP \to \Nat$ that assigns a natural number to a
+$\Prop \to \Nat$ that assigns a natural number to a
 proposition φ as follows.
@@
 rank(φ₁) + c_{¬}  & φ ≡ \neg φ₁, \\
-\max{(rank(φ₁),rank(φ₂)} + c_{\square}
+\max{(rank(φ₁),rank(φ₂))} + c_{\square}
   & φ ≡ φ₁\,\square\, φ₂.
@@
 Therefore, we define an appropriate complexity measure
-$\unshunt_{cm}: \PROP → \NN$
+$\unshunt_{cm}: \Prop → \NN$
 for the second argument of the $\unshunt_{1}$ function in
@@
 
-\newcommand{\thmunshunt}{\tt thm-$\unshunt$}
 \begin{theorem}[\thmunshunt]
@@
 
-\newcommand{\thmsplit}{\name{thm-split}}
 \begin{theorem}[\thmsplit] $Γ ⊢ \mysplit(φ)$ then $Γ ⊢ φ$.
@@
 \emph{Resolve.}
-\newcommand{\thmresolve}{\name{thm-resolve}}
+
 The \resolve rule is a generalization version for resolution
@@
   \begin{split}
-&\name{reorder-∨}\ :\ \PROP \to \PROP \to \PROP\\
+&\name{reorder-∨}\ :\ \Prop \to \Prop \to \Prop\\
 &\name{reorder-∨}(φ, ψ) =

### 2017-09-15 paper/sections/proof-reconstruction.tex
[ paper ] remove use of \tt.

@@
 
-\change{remove the use of tt for functions. (rank, etc..)}
 \begin{equation}
@@
 \end{equation}
-\change{changes the name of the functions to avoid different
-functions with the same name.}
 
@@
 
-\begin{proof} Use induction on the cases defined by the result of
-$\unshunt$ in Eq.~\ref{eq:unshunt-structured}.
+\begin{proof} Use induction on the cases defined by the outcome of the $\unshunt$ function in Eq.~\ref{eq:unshunt-structured}.
 When $n = 0$, by definition, $Γ ⊢ φ$.
@@
 \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
-\RightLabel{\tt thm-$\unshunt$}
+\RightLabel{\thmunshunt}
 \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
-\RightLabel{\tt ∧⇒-to-⇒⇒}
+\RightLabel{∧⇒-to-⇒⇒}
 \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).}
@@
 Second, using the following theorem from \cite{AgdaProp},
+
 \begin{equation*}
@@
 \AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n) ∧ \unshunt(φ₁ ⇒ φ₃, n)$}
-\RightLabel{\tt ∧-proj₁}
+\RightLabel{∧-proj₁}
 \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n)$}
@@
 \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n-1)$}
-\RightLabel{\tt thm-$\unshunt$}
+\RightLabel{\thmunshunt}
 \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$,}
@@
 \AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂) ∧ \unshunt(φ₁ ⇒ φ₃)$}
-\RightLabel{\tt ∧-proj₂}
+\RightLabel{∧-proj₂}
 \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₃, n)$}
@@
 \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₃, n-1)$}
-\RightLabel{\tt thm-$\unshunt$}
+\RightLabel{\thmunshunt}
 \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$,}
@@
 \AxiomC{$\mathcal{D}_2$}
-\RightLabel{\tt ∧-intro}
+\RightLabel{∧-intro}
 \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
-\RightLabel{\tt ⇒∧⇒-to-⇒∧}
+\RightLabel{⇒∧⇒-to-⇒∧}
 \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).}
@@
 \UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-\RightLabel{\tt $∧$-proj$₂$}
+\RightLabel{$∧$-proj$₂$}
 \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
@@
 \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-\RightLabel{\tt $⇒$-elim}
+\RightLabel{$⇒$-elim}
 \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
@@
 
-\RightLabel{\tt ∧-intro}
+\RightLabel{∧-intro}
 \BinaryInfC{$Γ ⊢ φ₁ ∧ φ₂$.}
@@
 \UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-\RightLabel{\tt ∧-proj₁}
+\RightLabel{∧-proj₁}
 \UnaryInfC{$Γ ⊢ \unshunt(φ₁)$}
@@
 \AxiomC{}
-\RightLabel{\tt assume φ₁}
+\RightLabel{assume φ₁}
 \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
@@
 \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-\RightLabel{\tt ⇒-elim}
+\RightLabel{⇒-elim}
 \BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂,n-1)$}
@@
 \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
-\RightLabel{\tt ⇒-intro}
+\RightLabel{⇒-intro}
 \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$.}
@@
 \UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
-\RightLabel{\tt ∧-proj₂}
+\RightLabel{∧-proj₂}
 \UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
@@
 \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-\RightLabel{\tt ⇒-elim}
+\RightLabel{⇒-elim}
 \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
@@
 \UnaryInfC{$Γ ⊢ ¬ φ₂$}
-\RightLabel{\tt ∧-intro}
+\RightLabel{∧-intro}
 \BinaryInfC{$Γ ⊢ ¬ φ₁ ∧ ¬ φ₂$}
-\RightLabel{\tt ¬∧¬-to-¬∨}
+\RightLabel{¬∧¬-to-¬∨}
 \UnaryInfC{$Γ ⊢ ¬ (φ₁ ∨ φ₂)$.}
@@
 \UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
-\RightLabel{\tt ∧-proj₁}
+\RightLabel{∧-proj₁}
 \UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁)$}
@@
 \AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i}$}
-\RightLabel{\tt ∧-intro}
+\RightLabel{∧-intro}
 \UnaryInfC{$Γ ⊢ \bigwedge_i s_i$}
@@
 \AxiomC{$\mysplit(φ) ≡ \bigwedge_i s_i $}
-\RightLabel{\tt subst}
+\RightLabel{subst}
 \BinaryInfC{$Γ ⊢ \mysplit(φ) $}
@@
 \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
-\RightLabel{\tt subst}
+\RightLabel{subst}
 \BinaryInfC{$Γ ⊢ ψ$.}

### 2017-09-18 paper/sections/proof-reconstruction.tex
[ paper ] working on structurally smaller arguments.

@@
-% -*- root: main.tex -*-
 \documentclass[../main.tex]{subfiles}
@@
 input of the \Metis prover.
-The algorithms of \Metis in step~3 intend to find
+The algorithms of \Metis in Step~3 intend to find
 a solution; if they success, \Metis replies a derivation in \TSTP
@@
 
-Finally, we use the proof assistant in step 7 to type-check the
-proof and verify its correctness. Next, we only have one answer:
-type-checking succeed (i.e., the proof is valid) or type-checking
-failed.
-If the type-check fails, one of the three actors in the process are
-responsible: \Metis, \Athena, or \Agda. We are responsible for
-errors committed in the translation from \TSTP to \Agda; lack of the
-coverage of the \Metis' inference rules, or bad assumptions about
-them. \improvement{Make this statement stronger and clear.}
+Finally, we use the proof checker in Step~7 to type-check the
+proof-term. If type-checking succeed, the proof from such a \TSTP
+derivation is correct, else if type-checking fails, one of the three
+actors in the process could be the responsible.
+They are \Metis, \Athena, or \Agda.
+
+We are responsible for errors committed in the translation from
+\TSTP to \Agda: bugs in the parsing module, lack of the coverage of
+the \Metis' inference rules since we are emulating them, and last
+but not least, the pretty print of the proof in \Agda code.
 
 In the rest of this section, we provide a formal description using
-type theory to build definitions and theorems for the functions
-necessary to emulate the \Metis' inference rules. We will write the
-type judgments with ``$a : A$'' to denote that $a$ has type $A$.
-For propositions, we will denote by $φ ≡ ψ$ the syntactic
+type theory to build definitions and theorems for functions
+necessary to emulate \Metis' inference rules.
+Some conventions about notations. We will write the
+type judgments with ``$a : A$'' to denote that $a$ has type
+$\abbre{A}$. Types are written using small caps.
+For propositions, we will denote by $φ ≡ ψ$, the syntactic
 equivalence.
@@
 
-\subsection{Small Structured Recursion}
-\label{ssec:small-structured-recursion}
+% section section_name (end)
+\subsection{Structural Recursion}
+\label{ssec:structural-recursion}
 
 In the process to emulate \Metis' inference rules in type theory,
-we encountered many recursive algorithms with termination problems,
-that is,when an algorithm could run forever or we can not guarantee
-that it will stop after some point. Such a problem makes impossible
-to translate the algorithm in type theory directly.
-For that reason, we show a technique that will help us to define
-new algorithms based on the previous ones to solve the problem
-mentioned.
+we encountered that some of \Metis' transformation for propositions in
+the inference rules were given by \emph{general recursion} functions.
+But algorithms based on general recursions can not be translated
+directly in type theory since it is not a guarantee they terminate.
+Then, since a termination checker in type theory recognizes
+\emph{structural recursion functions} as well-founded recursive
+functions, we modify our algorithms in order to follow such a
+definition mostly taken from \citeauthor{Abel2002}~\cite{Abel2002}.
 
-A recursive function is a \emph{small-structured-recursion}, if the
-size of the arguments with which it is defined decrease in
-size for each call to the function in the definition~\cite{Bove2005}.
-A well-structured function terminates and it can be translated
-directly to type theory~\cite{Bove2002}.
+\begin{definition} A recursive function is structurally recursive if
+it calls itself with only \emph{structurally smaller} arguments.
+\end{definition}
 
-Let us consider the following example from an inner function
-in the \strip inference.
+\begin{definition}
+Given an \emph{ordering relation} between $t_1 : T$ and $t_2 : T$,
+we say that $t_1$ is structurally smaller than $t_2$ if and only if,
+USE \cite{Coquand1992} definition.
+\begin{itemize}
+  \item $t_1$ and $t_2$ are different constructor for $T$ type.
+\end{itemize}
+\end{definition}
+
+To convert a general recursion function into a structural recursion
+function, for the sake of simplicity, we will follow a technique
+found mainly in \cite{Coquand1992,Abel2002,Bove2005}.
+It mostly consists of using a \emph{recursor}, an inductive type, to
+perform the \emph{induction} over its structure.
+A type-checker will recognize structurally smaller arguments by using
+the lexicographic order, as an extension of the structural ordering
+by the recursor.
+
+Let us consider the following example to exhibit the procedure
+mentioned above for an inner function in the \strip inference.
 
@@
 \end{equation}
+
+For a more complete treatment of general recursion, and how to
+define well-founded and well-structural recursive functions, we refer
+the reader to Ref.~\cite{Bove2005}, where Bove and Capettra described
+not only general recursion but they also treat mutual recursive
+function, among other kinds.
 
@@
 new definition after apply the process described above in
-Subsection~\ref{ssec:small-structured-recursion}, since
+Subsection~\ref{ssec:structural-recursion}, since
 in the recursion calls of \mysplit in Eq.~\ref{eq:split-definition},
@@
 
-\emph{Resolve.}
-
-The \resolve rule is a generalization version for resolution
-in propositional logic since the formulas are not shaped always as
-the theorem expect (see Fig.~\ref{fig:metis-inferences}).
-Since our approach is mere syntactic, in order to apply such a
-theorem, we perform rearrangements inside the formulas to match with
-the pattern expected by the resolution theorem. If this strategy
-fails at some point, we could not check the rest of the proof.
-
-Therefore, the best scenario to apply resolution occurs when the
-literal $l$ and its negation appear in the exact place in the
-formulas as the resolve inference shows.
-
-\begin{figure}
-\[%\scalebox{0.9}{
-\begin{bprooftree}
-\AxiomC{$Γ ⊢ (φ₁ ≡ l ∨ ψ₁)$}
-\AxiomC{$Γ ⊢ (φ₂ ≡ ¬ l ∨ ψ₂)$}
-\RightLabel{\thmresolve}
-\BinaryInfC{$Γ ⊢ \resolve(φ₁, φ₂, l, (ψ₁ ∧ ψ₂))$}
-\UnaryInfC{Γ ⊢ ψ₁ ∨ ψ₂}
-\end{bprooftree}
-%}
-\]
-% \caption{Resolution in \Metis.}
-\label{fig:thm-resolve-best-case}
-\end{figure}
-
-To rearrange the propositions in order to match with a specific
-pattern for applying a particular theorem like resolution, we have
-define the following functions and provide
-its respective theorems in \cite{AgdaMetis}.
-These rearrangement functions are mainly inspired in
-\cite{bohme2010}, for their treatment for conjunction and
-disjunction equivalence.
-
-\improvement{provide examples for each of the following functions.}
-
-\begin{itemize}
-  \item \name{reorder-∨.} Given two formulas, φ and ψ, both disjunctions, fix the order of the first one by following the syntactically
-  order of the second one. If the process succeed (denote by φ ⤳ ψ),
-  returns the target formula, ψ, otherwise, keep the first one, φ.
-  \begin{align}
-  \begin{split}
-&\name{reorder-∨}\ :\ \Prop \to \Prop \to \Prop\\
-&\name{reorder-∨}(φ, ψ) =
-  \begin{cases}
-  ψ   & φ ⤳ ψ\\
-  ϕ   & \text{otherwise.}
-  \end{cases}
-  \end{split}
-  \end{align}
-
-  \item \name{reorder-∧.} Given two formulas, φ and ψ, both conjunctions, fix the order of the first one by following the order  of the second one.
-  \item \name{reorder-∧∨.} Given two formulas, φ and ψ, both in CNF, fix the order of the first one by following the order  of the second one.
-\end{itemize}
-
-\begin{equation}
-\resolve((φ₁, φ₂, l, ψ)
-\end{equation}
-
-\begin{theorem}[\thmresolve] $Γ ⊢ φ₁$, $Γ ⊢ φ₂$,
-then $Γ ⊢ \resolve(φ₁, φ₂, l, ψ)$ where $l$ is a literal,
-and ψ is the expected result.
-\end{theorem}
-
-% \begin{proof}
-% \begin{equation*}
-
-% \end{equation*}
-% \end{proof}
-
 \emph{Clausification.}

### 2017-09-18 paper/sections/proof-reconstruction.tex
fixed some references: \cite{Bertot2004}.

@@
 Then, since a termination checker in type theory recognizes
-\emph{structural recursion functions} as well-founded recursive
-functions, we modify our algorithms in order to follow such a
-definition mostly taken from \citeauthor{Abel2002}~\cite{Abel2002}.
+\emph{structural recursion functions}, we modify our algorithms appropriately.
 
-\begin{definition} A recursive function is structurally recursive if
-it calls itself with only \emph{structurally smaller} arguments.
-\end{definition}
+Using the concept of \emph{structurally smaller} from
+\citeauthor{Abel2002}~\cite{Abel2002}. We say, a recursive function is
+structurally recursive if it calls itself with only \emph{structurally smaller}
+arguments.
 
-\begin{definition}
-Given an \emph{ordering relation} between $t_1 : T$ and $t_2 : T$,
-we say that $t_1$ is structurally smaller than $t_2$ if and only if,
-USE \cite{Coquand1992} definition.
-\begin{itemize}
-  \item $t_1$ and $t_2$ are different constructor for $T$ type.
-\end{itemize}
-\end{definition}
+To convert a general recursive call into a structurally recursive call, we use
+the \emph{Bounded Recursion} technique presented in \cite{Coquand1992} but others found in
+\cite{Coquand1992,Abel2002,Bove2005} could be used.
 
-To convert a general recursion function into a structural recursion
-function, for the sake of simplicity, we will follow a technique
-found mainly in \cite{Coquand1992,Abel2002,Bove2005}.
-It mostly consists of using a \emph{recursor}, an inductive type, to
-perform the \emph{induction} over its structure.
-A type-checker will recognize structurally smaller arguments by using
-the lexicographic order, as an extension of the structural ordering
-by the recursor.
+The \emph{Bounded Recursion} technique converts a general recursive
+function into a structural recursive function by adding an additional
+argument that handle the times the function can call itself.
 
-Let us consider the following example to exhibit the procedure
+In our case, we add a natural number $n : \Nat$ in the input of the general
+recursive function for such an argument in mostly cases, and perform the
+recursion over the structure of \Nat type. \abbre{Nat} type is the usual
+type with \zero and \suc constructors, and including the common arithmetic
+operations ($+,\,-,\,*$) and representations of $\zero, \suc, \suc(\zero),
+\dots$
+with $0,1,2,\dots$.
+
+Then, the type-checker will
+recognize structurally smaller arguments by using the lexicographic
+order~\cite{Abel2002} for such kind of functions.
+
+In other words, we take a general recursive function $f: \Prop \to \Prop$.
+and we redefine that function as
+$f: \Prop \to \Nat \to \Prop$, and perform the recursion
+using induction on the structure of the \Nat type.
+
+We define
+
+Let us consider the following example to exhibit the technique
 mentioned above for an inner function in the \strip inference.
@@
 \label{eq:unshunt-definition}
-\unshunt(φ)_{0} =
+\unshunt_{0}(φ) =
 \begin{cases}
@@
 
-From the definition above, in the first case of the \unshunt
-function, the size of the argument in the recursion,(φ₁ ∧ φ₂) ⇒ φ₃,
-is not structured smaller than the decrease, (φ₁ ⇒ (φ₂ ⇒ φ₃)).
-Therefore, a termination checking will fail with the \unshunt
-function.
-
-To improve that definition for terminating, we will use the
-technique proposed by Bove and Capettra in
-\cite{Bove2005}, which in particular with functions that
-transform propositions consists of:
-take a general recursive function $f: \Prop \to \Prop$.
-and a predicate $P: \Prop \to \abbre{Ind}$, where $\abbre{Ind}$
-is a type with a structured inductive definition.
-
-Then, we redefine the function as
-$f: \Prop \to \abbre{Ind}\ \to \Prop$, and perform the recursion
-using induction on the structure of the \abbre{Ind} type.
-
-In our case, the \abbre{Nat} data type for
-natural numbers will be the $\abbre{Ind}$ type.
-We define \abbre{Nat} as usual (constructors \zero and \suc).
-We also allow common arithmetic operations and numbers represented by
-$0,1,2,\dots$ that stand for $\zero, \suc, \suc(\zero), \dots$.
+From the definition above, the size of the argument, ((φ₁ ∧ φ₂) ⇒ φ₃),
+is not structurally smaller than the input formula, (φ₁ ⇒ (φ₂ ⇒ φ₃));
+((φ₁ ∧ φ₂) ⇒ φ₃) is not a subformula of (φ₁ ⇒ (φ₂ ⇒ φ₃)).
 

### 2017-09-18 paper/sections/related-work.tex
[ paper ] working on structurally smaller arguments.
fixed some references: \cite{Bertot2004}.

@@
 that calls \name{veriT} on any \name{Coq} goal.
-In \cite{bezem2002automated},
+In \cite{Bezem2002},
 given a fixed but arbitrary first-order signature, the authors

### 2017-09-19 paper/sections/preliminaries.tex
[ paper ] working on structurally smaller arguments.
[ paper ] atp-conjunct added.

@@
 We only postulate the principle of excluded third
-(\abbre{PEM}), $φ ∨ ¬ φ$. From there, we derive the
+(\abbre{PEM}). Assuming \abbre{PEM}, we derive the
 \emph{reductio ad absurdum} rule (\abbre{RAA}) as the
-formulation of the principle of proof by contradiction: a derivation
+formulation of the principle of proof by contradiction, that is, a derivation
 of a contradiction, $⊥$, from the hypothesis $(¬ φ)$, is a
@@
 \AxiomC{}
-\RightLabel{\tt assume $φ$}
+\RightLabel{assume $φ$}
 \UnaryInfC{$Γ , φ ⊢ φ$}
@@
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{\tt weaken $ψ$}
+\RightLabel{weaken $ψ$}
 \UnaryInfC{$Γ , ψ ⊢ φ$}
@@
 \AxiomC{}
-\RightLabel{\tt $⊤$-intro}
+\RightLabel{$⊤$-intro}
 \UnaryInfC{$Γ ⊢ ⊤$}
@@
 \AxiomC{$Γ ⊢ ⊥$}
-\RightLabel{\tt $⊥$-elim $φ$}
+\RightLabel{$⊥$-elim $φ$}
 \UnaryInfC{$Γ ⊢ φ$}
@@
 \AxiomC{$Γ , φ ⊢ ⊥$}
-\RightLabel{\tt $¬$-intro}
+\RightLabel{$¬$-intro}
 \UnaryInfC{$Γ ⊢ ¬ φ$}
@@
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{\tt $¬$-elim}
+\RightLabel{$¬$-elim}
 \BinaryInfC{$Γ ⊢ ⊥$}
@@
 \AxiomC{$Γ ⊢ ψ$}
-\RightLabel{\tt $\wedge$-intro}
+\RightLabel{$\wedge$-intro}
 \BinaryInfC{$Γ ⊢ φ \wedge ψ$}
@@
 \AxiomC{$Γ ⊢ φ \wedge ψ$}
-\RightLabel{\tt $\wedge$-proj$_1$}
+\RightLabel{$\wedge$-proj$_1$}
 \UnaryInfC{$Γ⊢ φ$}
@@
 \AxiomC{$Γ ⊢ φ \wedge ψ$}
-\RightLabel{\tt $\wedge$-proj$_2$}
+\RightLabel{$\wedge$-proj$_2$}
 \UnaryInfC{$Γ⊢ ψ$}
@@
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{\tt $\vee$-intro$_1$ $ψ$}
+\RightLabel{$\vee$-intro$_1$ $ψ$}
 \UnaryInfC{$Γ ⊢ φ \vee ψ$}
@@
 \AxiomC{$Γ ⊢ ψ$}
-\RightLabel{\tt $\vee$-intro$_2$ $φ$}
+\RightLabel{$\vee$-intro$_2$ $φ$}
 \UnaryInfC{$Γ ⊢ φ \vee ψ$}
@@
 \AxiomC{$Γ , ψ  ⊢ \gamma$}
-\RightLabel{\tt $\vee$-elim}
+\RightLabel{$\vee$-elim}
 \BinaryInfC{$Γ , φ \vee ψ ⊢ \gamma$}
@@
 \AxiomC{$Γ , φ ⊢ ψ$}
-\RightLabel{\tt $\Rightarrow$-intro}
+\RightLabel{$\Rightarrow$-intro}
 \UnaryInfC{$Γ ⊢ φ \Rightarrow ψ$}
@@
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{\tt $\Rightarrow$-elim}
+\RightLabel{$\Rightarrow$-elim}
 \BinaryInfC{$Γ ⊢ ψ$}
@@
 \AxiomC{$Γ , ψ ⊢ φ$}
-\RightLabel{\tt $⇔$-intro}
+\RightLabel{$⇔$-intro}
 \BinaryInfC{$Γ ⊢ φ ⇔ ψ$}
@@
 \AxiomC{$Γ ⊢ φ ⇔ ψ$}
-\RightLabel{\tt $⇔$-elim$_1$}
+\RightLabel{$⇔$-elim$_1$}
 \BinaryInfC{$Γ ⊢ ψ$}
@@
 \AxiomC{$Γ ⊢ φ ⇔ ψ$}
-\RightLabel{\tt $⇔$-elim$_2$}
+\RightLabel{$⇔$-elim$_2$}
 \BinaryInfC{$Γ ⊢ ψ$}

### 2017-09-19 paper/sections/proof-reconstruction.tex
[ paper ] atp-conjunct added.

@@
 \end{equation*}
-Where,
-\begin{equation*}
+Where, the $subst$ theorem is,
+\begin{equation}
+\label{eq:substitution-theorem}
 \begin{bprooftree}
@@
 \end{bprooftree}
-\end{equation*}
+\end{equation}
+\end{proof}
+
+\emph{Splitting a conjunct}.
+The \conjunct rule extracts from a conjunction, one of its conjunct.
+To achieve this, we use projections repeatedly until we finally find
+the conjunct required.
+
+\begin{align}
+\begin{split}
+conjunct(φ, ψ) =
+\begin{cases}
+ψ &\text{if }φ ≡ ψ\\
+ψ &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }ψ ≡ conjunct(φ₁, ψ)\\
+ψ &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }ψ ≡ conjunct(φ₂, ψ)\\
+φ &\text{otherwise}
+\end{cases}
+\end{split}
+\end{align}
+
+\begin{theorem}[thm-conjunct]  $Γ ⊢ φ$, and $ψ \in \Prop$, then $Γ ⊢ conjunct(φ, ψ)$.
+\end{theorem}
+
+\begin{proof}
+When φ ≡ ψ, from $Γ ⊢ conjunct(φ, ψ)$ by normalization, we get $Γ ⊢ ψ$.
+By using $subst$ theorem Eq.~\ref{eq:substitution-theorem}, we get the desire conclusion. If the proposition φ is a conjunction, and $ψ ≡ conjunct(φ_{i}, ψ)$
+for some $i = 1,\ 2$, from $Γ ⊢ conjunct(φ, ψ)$ by normalization, we get
+$Γ ⊢ ψ$, but since $conjunct(φ_{i}, ψ) ≡ ψ$; we apply $subst$ theorem again,
+and the theorem follows.
+For the latter case, by using the hypothesis, $Γ ⊢ φ$, the proof is complete.
+
+Note that $conjunct$ function and also its theorem are well defined structural recursions, since φ₁ and φ₂ in the argument from the definition are structurally smaller than φ.
 \end{proof}

### 2017-09-19 paper/sections/proof-reconstruction.tex
[ paper ] minor changes.

@@
 To convert a general recursive call into a structurally recursive call, we use
-the \emph{Bounded Recursion} technique presented in \cite{Coquand1992} but others found in
-\cite{Coquand1992,Abel2002,Bove2005} could be used.
-
-The \emph{Bounded Recursion} technique converts a general recursive
+the \emph{Bounded Recursion} technique presented in \cite{Bertot2004} but
+others found in \cite{Coquand1992,Abel2002,Bove2005} could be used.
+This technique converts a general recursive
 function into a structural recursive function by adding an additional
 argument that handle the times the function can call itself.
+As we show later, we use the complexity of the original function for the new argument in the new function.
 
-In our case, we add a natural number $n : \Nat$ in the input of the general
-recursive function for such an argument in mostly cases, and perform the
-recursion over the structure of \Nat type. \abbre{Nat} type is the usual
-type with \zero and \suc constructors, and including the common arithmetic
-operations ($+,\,-,\,*$) and representations of $\zero, \suc, \suc(\zero),
-\dots$
-with $0,1,2,\dots$.
+For that argument, we add the natural number $n : \Nat$ in the input of the
+general recursive function, and perform the recursion over the structure of
+\Nat type. \abbre{Nat} type is the usual type with \zero and \suc constructors, and including the common arithmetic operations ($+,\,-,\,*$) and
+representations of $\zero, \suc, \suc(\zero), \dots$ with $0,1,2,\dots$.
 

### 2017-09-21 paper/sections/proof-reconstruction.tex
minor changes.

@@
   & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
-0 &\text{otherwise.}
+1 &\text{otherwise.}
 \end{cases}
@@
 the reader to Ref.~\cite{Bove2005}, where Bove and Capettra described
-not only general recursion but they also treat mutual recursive
+not only general recursion, but they also treat mutual recursive
 function, among other kinds.
@@
 process in its \TSTP derivations nor in its documentation.
-We provide such a evidence that the process of creating subgoals,
+We provide such an evidence that the process of creating subgoals,
 and combining them in a final conjunction proves the original goal.

### 2017-09-21 paper/sections/proof-reconstruction.tex
[ paper ] working.

--- 2017-09-19 paper/sections/proof-reconstruction.tex
@@
 system to a target system. In our case, the system of origin, the
-automatic theorem prover, is \Metis; the target system is the proof
+automatic theorem prover, is \Metis; the target system are the proof
 assistant, \Agda. We choose \Agda, but a proof assistant with
@@
 
-\begin{equation}
+\begin{align}
+\begin{split}
 \label{eq:unshunt-definition}
-\unshunt_{0}(φ) =
-\begin{cases}
+&\unshunt_{0}(φ) =\\
+&\hspace{3mm}\begin{cases}
 \unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃)
-  & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
-
+  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
 \unshunt_{0}(φ₁ ⇒ φ₂) ∧ \unshunt_{0}(φ₁ ⇒ φ₃)
-  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
-
-φ &\text{otherwise}.
+  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
+φ &\text{otherwise.}
 \end{cases}
-\end{equation}
+\end{split}
+\end{align}
 
@@
 \begin{split}
-\unshunt_{1}(φ, \zero) &= φ\\
-\unshunt_{1}(φ, \suc(n)) &=
-\begin{cases}
+&\unshunt_{1}(φ, \zero) = φ\\
+&\unshunt_{1}(φ, \suc(n)) =\\
+&\hspace{3mm}\begin{cases}
 \unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n)
-  & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
-\unshunt_{1}(φ₁ ⇒ φ₂, n)  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).\\
-∧\ \unshunt_{1}(φ₁ ⇒ φ₃, n)
+  &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
+\unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ \unshunt_{1}(φ₁ ⇒ φ₃, n) &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
 \end{cases}
@@
 0 &\text{for atomic }φ, \\
-rank(φ₁) + c_{¬}  & φ ≡ \neg φ₁, \\
+rank(φ₁) + c_{¬}  &\text{if } φ ≡ \neg φ₁, \\
 \max{(rank(φ₁),rank(φ₂))} + c_{\square}
-  & φ ≡ φ₁\,\square\, φ₂.
+  &\text{if } φ ≡ φ₁\,\square\, φ₂.
 \end{cases}
@@
 \max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1
-  & φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
+  &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
 0 &\text{otherwise.}
@@
 \Metis calls these new formulas \emph{subgoals}.
-Then, \Metis proves each subgoal and with that it finishes the proof
-of the goal.
+The conjunction of these subgoals is a proposition equivalent to the
+original goal. Then, for each subgoal, in a \Metis' \TSTP derivation
+we find a refutation.
 
-Nevertheless, \Metis does not provide neither an explanation of this
-process in its \TSTP derivations nor in its documentation.
-We provide such a evidence that the process of creating subgoals,
-and combining them in a final conjunction proves the original goal.
+Nevertheless, \Metis does not provide neither an explanation for the user about the process in its \TSTP derivations nor in its documentation.
 
-\begin{theorem}[\thmunshunt]
-\label{thm:unshunt}
+In the following, we show how the $split$ function jointly with Theorem.~\ref{thm:thm-strip} prove the correctness of the process mentioned above.
+First, we need to prove the correctness for the $\unshunt$ function in Eq~\ref{eq:unshunt-fixed}.
+
+\begin{lemma}[\thmunshunt]
+\label{lem:unshunt}
 $Γ ⊢ \unshunt(φ)$, then $Γ ⊢ φ$.
-\end{theorem}
+\end{lemma}
 
@@
 
-Now, let us consider the \mysplit function that
-yields the conjunction of subgoals from a proposition goal.
+Now, let us consider the $split$ function that
+yields the conjunction of subgoals from a proposition goal defined in Eq~\ref{eq:split-definition}.
 
@@
 \label{eq:split-definition}
-\mysplit(φ) =
+% \mysplit(φ) =
 \begin{cases}
-\unshunt(\mysplit(φ₁))              & φ ≡ φ₁ ∧ φ₂,\\
-∧\ \unshunt(φ₁ ⇒ \mysplit(φ₂))      &\\[2mm]
+\unshunt(\mysplit(φ₁)) ∧\ \unshunt(φ₁ ⇒ \mysplit(φ₂))  & \text{if }φ ≡ φ₁ ∧ φ₂,\\
+      &\\[2.5mm]
 
-\unshunt(¬ φ₁ ⇒ \mysplit(φ₂))       & φ ≡ φ₁ ∨ φ₂,\\
+\unshunt(¬ φ₁ ⇒ \mysplit(φ₂))       & \text{if }φ ≡ φ₁ ∨ φ₂,\\[2.5mm]
 
-\unshunt(φ₁ ⇒ \mysplit(φ₂))         & φ ≡ φ₁ ⇒ φ₂,\\
+\unshunt(φ₁ ⇒ \mysplit(φ₂))         & \text{if }φ ≡ φ₁ ⇒ φ₂,\\[2.5mm]
 
-\unshunt(φ₁ ⇒ \mysplit(φ₂))         & φ ≡ φ₁ ⇔ φ₂,\\
-∧\ \unshunt(φ₂ ⇒ \mysplit(φ₁))      &\\[2mm]
+\unshunt(φ₁ ⇒ \mysplit(φ₂))         & \text{if }φ ≡ φ₁ ⇔ φ₂,\\
+∧\ \unshunt(φ₂ ⇒ \mysplit(φ₁))      &\\[2.5mm]
 
-\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & φ ≡ ¬ (φ₁ ∧ φ₂),\\
+\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂),\\[2.5mm]
 
-\unshunt(\mysplit(¬ φ₁))            & φ ≡ ¬ (φ₁ ∨ φ₂),\\
-∧\ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂))  &\\[2mm]
+\unshunt(\mysplit(¬ φ₁))            & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂),\\
+∧\ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂))  &\\[2.5mm]
 
-\unshunt(\mysplit(φ₁))              & φ ≡ ¬ (φ₁ ⇒ φ₂),\\
-∧\ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂))    &\\[2mm]
+\unshunt(\mysplit(φ₁))              & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂),\\
+∧\ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂))    &\\[2.5mm]
 
-\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & φ ≡ ¬ (φ₁ ⇔ φ₂),\\
-∧\ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))    &\\[2mm]
+\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂),\\
+∧\ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))    &\\[2.5mm]
 
-\unshunt(\mysplit(φ₁))              & φ ≡ ¬ ¬ φ₁,\\
-⊤                                   & φ ≡ ¬ ⊥,\\
-⊥                                   & φ ≡ ¬ ⊤.
+\unshunt(\mysplit(φ₁))              & \text{if }φ ≡ ¬ ¬ φ₁,\\
+⊤                                   & \text{if }φ ≡ ¬ ⊥,\\
+⊥                                   & \text{if }φ ≡ ¬ ⊤.
 \end{cases}
@@
 
-We reformulate \mysplit function to match with the
-new definition after apply the process described above in
-Subsection~\ref{ssec:structural-recursion}, since
-in the recursion calls of \mysplit in Eq.~\ref{eq:split-definition},
-the negations, $(¬ φ_{1,2})$ raise a terminating problem.
+The definition above suffers termination problems since it is not
+a structural recursion. Therefore, we have reformulated Def.~\ref{eq:split-definition} to solve such a issue following the technique
+described in Subsection~\ref{ssec:structural-recursion}.
+Here and below, we refer to $split$ as the function after applying
+the process mentioned above.
 
-\begin{theorem}[\thmsplit] $Γ ⊢ \mysplit(φ)$ then $Γ ⊢ φ$.
-\end{theorem}
+\begin{lemma}[\thmsplit] $Γ ⊢ \mysplit(φ)$ then $Γ ⊢ φ$.
+\label{lem:lem-split}
+\end{lemma}
 
@@
 
-(φ ≡ φ₁ ∧ φ₂)
+(φ ≡ φ₁ ∧ φ₂). We get a proof for each conjunct and using the introduction rule for conjunction, the result follows.
+
+\begin{equation*}
+(\mathcal{D})\hspace{3mm}
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+\RightLabel{∧-proj₁}
+\UnaryInfC{$Γ ⊢ \unshunt(φ₁)$}
+\RightLabel{\thmunshunt}
+\UnaryInfC{$Γ ⊢ φ₁$.}
+\end{bprooftree}
+\end{equation*}
+
 \begin{equation*}
 \begin{bprooftree}
-\AxiomC{$\mathcal{D}_1$}
-\UnaryInfC{Γ ⊢ φ₁}
-
-\AxiomC{$\mathcal{D}_1$}
+\AxiomC{$\mathcal{D}$}
 \UnaryInfC{Γ ⊢ φ₁}
@@
 \RightLabel{\thmsplit}
-\UnaryInfC{$Γ ⊢ φ₂$}
-
-\RightLabel{∧-intro}
-\BinaryInfC{$Γ ⊢ φ₁ ∧ φ₂$.}
-\end{bprooftree}
-\end{equation*}
-Where,
-\begin{equation*}
-(\mathcal{D}_1)\hspace{3mm}
-\begin{bprooftree}
-\AxiomC{$Γ ⊢ \mysplit(φ,n)$}
-\RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-\RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁)$}
-\RightLabel{\thmunshunt}
-\UnaryInfC{$Γ ⊢ φ₁$.}
+\UnaryInfC{$Γ ⊢ φ₂.$}
 \end{bprooftree}
@@
 
-(φ ≡ φ₁ ⇒ φ₂)
+\vskip 3mm
+
+(φ ≡ φ₁ ⇒ φ₂).
 \begin{equation*}
@@
 \end{equation*}
+\vskip 3mm
 
-(φ ≡ ¬ (φ₁ ∨ φ₂))
+(φ ≡ ¬ (φ₁ ∨ φ₂)). We show $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$. Using their conjunction by the introduction rule, and De Morgan Law, the results follows.
+
+\begin{equation*}
+(\mathcal{D})\hspace{3mm}
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ \mysplit(φ, n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
+\RightLabel{∧-proj₁}
+\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁)$}
+\RightLabel{\thmunshunt}
+\UnaryInfC{$Γ ⊢ ¬ φ₁$,}
+\end{bprooftree}
+\end{equation*}
+
 \begin{equation*}
 \begin{bprooftree}
-\AxiomC{$\mathcal{D}$}
-\UnaryInfC{$Γ ⊢ ¬ φ₁$}
-
 \AxiomC{$\mathcal{D}$}
@@
 \RightLabel{\thmsplit}
-\UnaryInfC{$Γ ⊢ ¬ φ₂$}
-\RightLabel{∧-intro}
-\BinaryInfC{$Γ ⊢ ¬ φ₁ ∧ ¬ φ₂$}
-\RightLabel{¬∧¬-to-¬∨}
-\UnaryInfC{$Γ ⊢ ¬ (φ₁ ∨ φ₂)$.}
-\end{bprooftree}
-\end{equation*}
-
-Where,
-
-\begin{equation*}
-(\mathcal{D})
-\begin{bprooftree}
-\AxiomC{$Γ ⊢ \mysplit(φ, n)$}
-\RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
-\RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁)$}
-\RightLabel{\thmunshunt}
-\UnaryInfC{$Γ ⊢ ¬ φ₁$.}
+\UnaryInfC{$Γ ⊢ ¬ φ₂.$}
 \end{bprooftree}
@@
 
-\begin{theorem} If $s_i$ are the subgoals for the goal φ, and
+\begin{theorem}[thm-strip]
+\label{thm:thm-strip}
+ If $s_i$ are the subgoals for the goal φ, and
 $\{ Γ ⊢ s_i \}_{i}$, then $Γ ⊢ φ$.
@@
 \begin{cases}
-ψ &\text{if }φ ≡ ψ\\
-ψ &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }ψ ≡ conjunct(φ₁, ψ)\\
-ψ &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }ψ ≡ conjunct(φ₂, ψ)\\
-φ &\text{otherwise}
+  ψ &\text{if }φ ≡ ψ,\\
+  ψ &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₁, ψ)≡ ψ,\\
+  ψ &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₂, ψ)≡ ψ,\\
+  φ &\text{otherwise.}
 \end{cases}
@@
 By using $subst$ theorem Eq.~\ref{eq:substitution-theorem}, we get the desire conclusion. If the proposition φ is a conjunction, and $ψ ≡ conjunct(φ_{i}, ψ)$
-for some $i = 1,\ 2$, from $Γ ⊢ conjunct(φ, ψ)$ by normalization, we get
-$Γ ⊢ ψ$, but since $conjunct(φ_{i}, ψ) ≡ ψ$; we apply $subst$ theorem again,
-and the theorem follows.
-For the latter case, by using the hypothesis, $Γ ⊢ φ$, the proof is complete.
+for some $i = 1,\ 2$, then,
+
+\begin{equation}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
+  \RightLabel{∧-proj$_{i}$}
+  \UnaryInfC{$Γ ⊢ φ_{i}$}
+  \UnaryInfC{$Γ ⊢ conjunct(φ_{i}, ψ)$}
+  \AxiomC{$conjunct(φ_{i}, ψ) ≡ ψ$}
+  \RightLabel{subst}
+  \BinaryInfC{$Γ ⊢ ψ$}
+  \end{bprooftree}
+\end{equation}
+
+Finally, in the latter case, by using the hypothesis, $Γ ⊢ φ$,
+we complete the proof.
 

### 2017-09-22 paper/sections/proof-reconstruction.tex
[ paper ] buildOr added.

@@
   \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ ψ$}
+  \BinaryInfC{$Γ ⊢ ψ$.}
   \end{bprooftree}
@@
 
-Finally, in the latter case, by using the hypothesis, $Γ ⊢ φ$,
-we complete the proof.
-
-Note that $conjunct$ function and also its theorem are well defined structural recursions, since φ₁ and φ₂ in the argument from the definition are structurally smaller than φ.
+The last statement follows by using the hypothesis and the proof is complete.
 \end{proof}
 
-\emph{Clausification.}
+% To deal with nested conjunctions and nested disjunctions, we follow a similar strategy mainly described in \citeauthor{bohme2010}~\cite{bohme2010}.
+
+First, we define the $rconj$ function in Eq.~\ref{eq:rconj-def} to convert conjunctions to be right-associative conjunctions, and in a similar way with disjunctions,
+we define $rdisj$ function, to convert a general disjunction to a be right-associative disjunction.
+
+\begin{equation}
+\label{eq:rconj-def}
+\begin{split}
+&rconj(φ) =\begin{cases}
+ψ₁ ∧ rconj(ψ₂ ∧ φ₂) &\text{if }φ = φ₁ ∧ φ₂\text{, } ψ≡rconj(φ₁),\\
+&\text{and }ψ ≡ ψ₁ ∧ ψ₂,\\[3mm]
+ψ ∧ rconj(φ₂)  &\text{if }φ = φ₁ ∧ φ₂\text{, } ψ≡rconj(φ₁),\\
+φ &\text{otherwise.}
+\end{cases}
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+\label{eq:buildOr}
+buildOr(φ, ψ) =
+\begin{cases}
+ψ &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } buildOr(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2,\\
+ψ &\text{if } φ ≡ ψ,\\
+φ &\text{otherwise.}
+\end{cases}
+\end{split}
+\end{equation}
 

### 2017-09-22 paper/sections/introduction.tex
[ paper ] working on structurally smaller arguments.

@@
 \name{Waldmeister}~\cite{hillenbrand1997}) and a little bit less replied with a proof
-in a file format like \TSTP~\cite{sutcliffe2004tstp} (e.g.,
+in a file format like \TSTP~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006} (e.g.,
 \name{E}, \Metis, \name{Vampire}, and \name{Z3}),

### 2017-09-22 paper/sections/proof-reconstruction.tex
[ paper ] minor changes.

@@
 
-\begin{proof} Use induction on the cases defined by the outcome of the $\unshunt$ function in Eq.~\ref{eq:unshunt-structured}.
+\begin{proof} Use induction on the cases defined by the outcome of the
+$\unshunt$ function in Eq.~\ref{eq:unshunt-structured}.
 When $n = 0$, by definition, $Γ ⊢ φ$.

### 2017-09-22 paper/sections/metis-language-and-proofs.tex
[ paper ] working on structurally smaller arguments.
[ paper ] improving the writing.

@@
-% % -*- root: main.tex -*-
+%
 \documentclass[../main.tex]{subfiles}
@@
 \textit{Output.}~\TSTP language is de facto output standard language
-for derivations of ATPs~\cite{sutcliffe2004tstp}. A \TSTP derivation
+for derivations of ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}. A \TSTP derivation
 is a directed acyclic graph, a proof tree, where each leaf is a
@@
 The \simplify rule is an inference that performs simplification of
-definitions or tautologies over a list of derivations. This rule
+definitions and tautologies. This rule
 transverses a list of formulas by applying different theorems (e.g.,
@@
 
-Moreover, we are not completely sure about the exact behavior for
-all \Metis' inference rules. It is somewhat complicated to grasp it
-completely since the source code is around the 10.000 lines of code.
+Moreover, we are not completely covered every detail in the behavior
+for all \Metis' inference rules. It is somewhat complicated to grasp
+completely the inference rules since the source code is around the
+10.000 lines of code.
 

### 2017-09-22 paper/sections/proof-reconstruction.tex
[ paper ] fixed minors.

@@
 \node[left = 1.1cm of athena, text width=2cm, align=center]
-   (agdafile) {6. \Agda \\ Proof.};
+   (agdafile) {6. Proof-term.};
 
 \node[left = 1.1cm of agdafile, text width=2cm, align=center]
-   (agda) {7. Proof Checking.};
+   (agda) {7. Proof Checker.};
 
@@
 system to a target system. In our case, the system of origin, the
-automatic theorem prover, is \Metis; the target system are the proof
-assistant, \Agda. We choose \Agda, but a proof assistant with
-support of type theory and similar features like \Agda
-(see a description of \Agda in Section
-\ref{sec:implementation}) can be used.
-Following the diagram in Fig.
-\ref{fig:proof-reconstruction-workflow}, the process can begin with
+automatic theorem prover, is \Metis; the target system is a proof
+assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types is valid (see a description of \Agda for its main features in
+Section~\ref{sec:implementation}).
+The overview of the proof-reconstruction is presented in
+Fig.~\ref{fig:proof-reconstruction-workflow}, the process can begin with
 a problem in \CPL that we encode in \TPTP format to be sent as the
 input of the \Metis prover.
-The algorithms of \Metis in Step~3 intend to find
-a solution; if they success, \Metis replies a derivation in \TSTP
-format of the proof, else the problem is counter feasible.
+The algorithms of \Metis in Step~3 find
+a solution if the problem is a theorem, in that case \Metis replies
+with a derivation in \TSTP format of the proof, otherwise the problem is counter feasible.
 
-With such a derivation, we process it with our \Haskell translator
-tool, \Athena~\cite{Athena}.
+With such a derivation, in Step~5, we process the derivation with our \Haskell translator tool, \Athena~\cite{Athena}.
 \Athena parses the \TSTP format, analyze the
 derivation and generates a representation of the natural deduction
-proof using a version of a tree data structure (see the properties
-of this tree in Subsection \ref{ssec:metis-proofs}). As a result,
-\Athena generates an \Agda file with such a proof. We have included
-in this file, \emph{imports} that call \Agda libraries that give
-support for the logic~\cite{AgdaProp}, and versions of the \Metis'
-inference rules~\cite{AgdaMetis}.
+proof using a tree data structure (see the properties
+of this tree in Subsection \ref{ssec:metis-proofs}).
+We perform an analysis of the proof-tree removing redundancies,
+unnecessary steps or unused output from the \TSTP derivation.
+
+As a result,
+\Athena generates an \Agda file with the proof-term. We have included
+in this file, \emph{imports} that call our \Agda libraries that give
+support for CPL presented in~\cite{AgdaProp}, and support for \Metis'
+inference rules implemented in~\cite{AgdaMetis}.
 
 Finally, we use the proof checker in Step~7 to type-check the
-proof-term. If type-checking succeed, the proof from such a \TSTP
-derivation is correct, else if type-checking fails, one of the three
-actors in the process could be the responsible.
-They are \Metis, \Athena, or \Agda.
+proof-term. If type-checking succeed, the \TSTP
+derivation is correct, otherwise when it fails, one of the three
+actors in the process could be the responsible: \Metis, \Athena, or
+\Agda.
 
@@
 \TSTP to \Agda: bugs in the parsing module, lack of the coverage of
-the \Metis' inference rules since we are emulating them, and last
-but not least, the pretty print of the proof in \Agda code.
+\Metis' inference rules, and last but not least, the pretty print of
+the proof in \Agda code.
 
@@
 For propositions, we will denote by $φ ≡ ψ$, the syntactic
-equivalence.
+equivalence. We use the \Prop type for propositions and for theorems,
+the dependent type, $ Γ ⊢ φ$ where $Γ$ has type $\abbre{List} \Prop$ and
+$φ$ has type $\Prop$.
 
@@
 
-In the process to emulate \Metis' inference rules in type theory,
-we encountered that some of \Metis' transformation for propositions in
-the inference rules were given by \emph{general recursion} functions.
+To emulate \Metis' inference rules in type theory,
+we observed that transformations performed by some rules were given by \emph{general recursive} functions.
 But algorithms based on general recursions can not be translated
 directly in type theory since it is not a guarantee they terminate.
-Then, since a termination checker in type theory recognizes
-\emph{structural recursion functions}, we modify our algorithms appropriately.
 
-Using the concept of \emph{structurally smaller} from
-\citeauthor{Abel2002}~\cite{Abel2002}. We say, a recursive function is
-structurally recursive if it calls itself with only \emph{structurally smaller}
+Then, we solve the termination problem by modifying problematic functions
+to be \emph{structural recursive}~\cite{Coquand1992,Abel2002,Bove2005}
+
+We use the same notion of \emph{structurally smaller} from
+\citeauthor{Abel2002}~\cite{Abel2002} to say, a recursive function is
+structurally recursive if it calls itself with only
+\emph{structurally smaller}
 arguments.
 
-To convert a general recursive call into a structurally recursive call, we use
-the \emph{Bounded Recursion} technique presented in \cite{Bertot2004} but
+To convert a general recursive call into a structurally recursive call,
+we use the \emph{Bounded Recursion} technique presented
+in~\cite{Bertot2004} but
 others found in \cite{Coquand1992,Abel2002,Bove2005} could be used.
@@
 function into a structural recursive function by adding an additional
-argument that handle the times the function can call itself.
-As we show later, we use the complexity of the original function for the new argument in the new function.
+argument for the function complexity, the bound for the number of times, the function needs to call itself to get the final result.
 
-For that argument, we add the natural number $n : \Nat$ in the input of the
+Then, we add the natural number $n : \Nat$ in the input of the
 general recursive function, and perform the recursion over the structure of
-\Nat type. \abbre{Nat} type is the usual type with \zero and \suc constructors, and including the common arithmetic operations ($+,\,-,\,*$) and
-representations of $\zero, \suc, \suc(\zero), \dots$ with $0,1,2,\dots$.
+\Nat type.
+\abbre{Nat} type is the usual type for natural numbers with \zero and \suc as their constructors.
+We consider the common arithmetic operations ($+,\,-,\,*$) and numbers $0,1,2,\dots$ as representations of $\zero, \suc, \suc(\zero), \dots$.
 
@@
 using induction on the structure of the \Nat type.
-
-We define
 
@@
 From the definition above, the size of the argument, ((φ₁ ∧ φ₂) ⇒ φ₃),
-is not structurally smaller than the input formula, (φ₁ ⇒ (φ₂ ⇒ φ₃));
-((φ₁ ∧ φ₂) ⇒ φ₃) is not a subformula of (φ₁ ⇒ (φ₂ ⇒ φ₃)).
+is not structurally smaller than the input formula, (φ₁ ⇒ (φ₂ ⇒ φ₃)), since ((φ₁ ∧ φ₂) ⇒ φ₃) is not a subformula of (φ₁ ⇒ (φ₂ ⇒ φ₃)).
 
-Thus, we have a new function
+Thus, we define the function
 $\unshunt_{1} : \Prop \to \Nat \to \Prop$
-defined by structural recursion in its second argument in
+by structural recursion in its second argument in
 Eq.~\ref{eq:unshunt-structured}.
@@
 
-To feed the second argument of this new function, we will use
-functions. For instance, we opted to use a complexity measure of
-the formula that $\unshunt_{1}$ function transforms.
+As we mentioned above, the natural number in the second argument of the function used in Eq.~\ref{eq:unshunt-structured} stands for a complexity measure of the function, in this case $\unshunt_{1}$ function.
 
 A \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
-and presented in \cite{VanDalen1994} as well as \emph{the rank for a
-proposition} is a function with type
-$\Prop \to \Nat$ that assigns a natural number to a
-proposition φ as follows.
+and presented in \cite{VanDalen1994} as \emph{the rank for a
+proposition}, is a function $\Prop \to \Nat$ that assigns a natural number for a proposition φ as follows.
 
@@
 
-We have already solved the terminating problem for the \unshunt
-function in Eq.~\ref{eq:unshunt-structured}, nevertheless we do not
-what natural number should be feed that argument in
-order to maintain the same outputs as the original \unshunt does in
-Eq.~\ref{eq:unshunt-definition}.
+Recall, we want to maintain the same outputs as the original \unshunt does in Eq.~\ref{eq:unshunt-definition} and the complexity measure of it, is a bound for the number of times this function can call itself.
 
 Therefore, we define an appropriate complexity measure
-$\unshunt_{cm}: \Prop → \NN$
-for the second argument of the $\unshunt_{1}$ function in
+$\unshunt_{cm}: \Prop → \NN$ for our $\unshunt_{1}$ function presented in
 Eq.~\ref{eq:unshunt-rank-definition}.
@@
 
-Then, a curated version of the $\unshunt_{0}$ function is presented
+Finally, the curated version of $\unshunt_{0}$ function is presented
 in Eq.~\ref{eq:unshunt-fixed}.
@@
 \emph{Splitting a goal.}
-The goal of a proof is processed by \Metis to generated new targets,
-\Metis calls these new formulas \emph{subgoals}.
+The goal of a problem to be proved by \Metis is processed to generate new
+propositions, the new targets, \Metis calls these formulas
+\emph{subgoals}.
+
 The conjunction of these subgoals is a proposition equivalent to the
-original goal. Then, for each subgoal, in a \Metis' \TSTP derivation
-we find a refutation.
+original goal. Then, we find a refutation for each subgoal in the \Metis' \TSTP derivation.
 
@@
 
-In the following, we show how the $split$ function jointly with Theorem.~\ref{thm:thm-strip} prove the correctness of the process mentioned above.
-First, we need to prove the correctness for the $\unshunt$ function in Eq~\ref{eq:unshunt-fixed}.
+In the following, we show how Theorem.~\ref{thm:thm-strip} proves the correctness of the process mentioned above.
+But first, let prove some lemmas for $\unshunt$ function presented in Eq.~\ref{eq:unshunt-fixed},
+and $split$ function from the definition in Eq.~\ref{eq:split-definition}.
 
@@
 
-\begin{proof} Use induction on the cases defined by the outcome of the
-$\unshunt$ function in Eq.~\ref{eq:unshunt-structured}.
+\begin{proof} Use induction on the cases defined by the outcome of the $\unshunt$ function in Eq.~\ref{eq:unshunt-structured}.
 When $n = 0$, by definition, $Γ ⊢ φ$.
-When $n = 1$, we apply the following theorem presented in
-\cite{AgdaProp}
+When $n = 1$, we apply the following theorem from~\cite{AgdaProp}
 
@@
 
-Now, let us consider the $split$ function that
-yields the conjunction of subgoals from a proposition goal defined in Eq~\ref{eq:split-definition}.
+Now, let us consider the $split$ function presented in
+Eq.~\ref{eq:split-definition} that yields a conjunction of subgoals from a proposition, the goal in \Metis.
 

### 2017-09-25 paper/sections/proof-reconstruction.tex
10:49pm 25/09/2017

--- 2017-09-22 paper/sections/proof-reconstruction.tex
@@
       &\\[2.5mm]
-
 \unshunt(¬ φ₁ ⇒ \mysplit(φ₂))       & \text{if }φ ≡ φ₁ ∨ φ₂,\\[2.5mm]
@@
 \unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂),\\[2.5mm]
-
 \unshunt(\mysplit(¬ φ₁))            & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂),\\
@@
 
-First, we define the $rconj$ function in Eq.~\ref{eq:rconj-def} to convert conjunctions to be right-associative conjunctions, and in a similar way with disjunctions,
-we define $rdisj$ function, to convert a general disjunction to a be right-associative disjunction.
+For the rest of inference rules, we need some transformations useful
+to deal with conjunctions and disjunctions.
+
+First, we define the $rconj$ function in Eq.~\ref{eq:rconj-def} to convert conjunctions to be right-associative conjunctions, and following
+a similar approach we define $rdisj$ function for disjunctions.
 
@@
 
+The following function, buildOr intends to construct a disjunction from another disjunction, specifically, we want to rearrange the order of the disjuncts in a disjunctions, no other propositional shape we treat.
+This approach for rearrangement is inspired on the treatment for nested
+disjunctions in \citeauthor{bohme2010}~\cite{bohme2010}.
+
 \begin{equation}
@@
 
+\subsubsection{Reordering}
+...
+
 \end{document}

### 2017-09-25 paper/sections/proof-reconstruction.tex

--- 2017-09-22 paper/sections/proof-reconstruction.tex
@@
 \end{equation}
+
+The following function, buildOr intends to construct a disjunction from another disjunction, specifically, we want to rearrange the order of the disjuncts in a disjunctions, no other propositional shape we treat.
+This approach for rearrangement is inspired on the treatment for nested
+disjunctions in \citeauthor{bohme2010}~\cite{bohme2010}.
 

### 2017-09-25 paper/sections/proof-reconstruction.tex
[ paper ] reordering formalisation added.

--- 2017-09-22 paper/sections/proof-reconstruction.tex
@@
 
-\emph{Splitting a goal.}
+\subsubsection{Splitting a Goal.}
 The goal of a problem to be proved by \Metis is processed to generate new
@@
 
-% To deal with nested conjunctions and nested disjunctions, we follow a similar strategy mainly described in \citeauthor{bohme2010}~\cite{bohme2010}.
+% ------------------------------------------------------------------------
 
-First, we define the $rconj$ function in Eq.~\ref{eq:rconj-def} to convert conjunctions to be right-associative conjunctions, and in a similar way with disjunctions,
-we define $rdisj$ function, to convert a general disjunction to a be right-associative disjunction.
+\subsubsection{Reordering.}
+
+Syntactically speaking, showing the logic equivalence between two conjunctive normal forms is a matter of rearrangements of the conjunctions
+but also of the inner disjunctions inside the propositions involved.
+
+We provide some useful theorems to perform the following tasks.
+
+\begin{itemize}
+  \item Reorder a disjunction like $φ = φ₁ ∨ φ₂ ∨ \cdots$ to match with another disjunction $ψ = ψ₁ ∨ ψ₂ ∨ \cdots$, when $φ$ is a disjunct of $ψ$.
+  \item Reorder a conjunction of disjuncts (CNF), $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another CNF formula equivalent $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$.
+\end{itemize}
+
+First, we define the $rdisj$ function in Eq.~\ref{eq:rdisj-def} to convert a disjunction to be a right-associative disjunction, and following
+a similar approach we define the $rconj$ function for conjunctions.
+
+\begin{align}
+    \begin{split}
+      \label{eq:rdisj-def}
+      rdisj(φ) =
+      \begin{cases}
+      rdisj(φ₁ ∨ (φ₂ ∨ φ₃)) & \text{if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃, \\
+      φ₁ ∨ rdisj(φ₂)        & \text{if } φ ≡ φ₁ ∨ φ₂, \\
+      φ                     & \text{otherwise.}
+      \end{cases}
+    \end{split}
+\end{align}
+
+\begin{lemma}[lem-rdisj]
+\label{lem:lem-rdisj}
+  $Γ ⊢ φ$ then $Γ ⊢ rdisj(φ)$.
+\end{lemma}
+
+The following function, $build_{∨} : \Prop → \Prop → \Prop$ in Eq.~\ref{eq:build-or}, intends to construct a disjunction from another disjunction, specifically, we want to rearrange the order of the disjuncts in a target disjunction.
+This approach for rearrangement is inspired on the treatment for nested
+disjunctions mainly described in \citeauthor{bohme2010}~\cite{bohme2010}.
 
 \begin{equation}
-\label{eq:rconj-def}
 \begin{split}
-&rconj(φ) =\begin{cases}
-ψ₁ ∧ rconj(ψ₂ ∧ φ₂) &\text{if }φ = φ₁ ∧ φ₂\text{, } ψ≡rconj(φ₁),\\
-&\text{and }ψ ≡ ψ₁ ∧ ψ₂,\\[3mm]
-ψ ∧ rconj(φ₂)  &\text{if }φ = φ₁ ∧ φ₂\text{, } ψ≡rconj(φ₁),\\
+\label{eq:build-or}
+&build_{∨}(φ, ψ) =\\
+&\hspace{3mm}
+\begin{cases}
+ψ &\text{if } φ ≡ ψ,\\
+ψ &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2,\\
 φ &\text{otherwise.}
@@
 
-\begin{equation}
+\begin{lemma}[lem-build-or]
+\label{lem:lem-build-or}
+$Γ ⊢ φ$, and $ψ\in \Prop$ then $Γ ⊢ build_{∨}(φ)$.
+\end{lemma}
+
+The function $factor : \Prop → \Prop$  in Eq.~\ref{eq:factor-definition} is intended to work only for right-associative disjunctions, and reduces a disjunction of the same disjunct (e.g., $factor(φ ∨ (φ ∨ \cdots)) \mapsto\ φ$).
+
+\begin{align}
 \begin{split}
-\label{eq:buildOr}
-buildOr(φ, ψ) =
+  \label{eq:factor-definition}
+  factor(φ) =
   \begin{cases}
-ψ &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } buildOr(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2,\\
-ψ &\text{if } φ ≡ ψ,\\
+    φ₁ & \text{if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ factor(φ₂),\\
+    φ  & \text{otherwise.}
+  \end{cases}
+\end{split}
+\end{align}
+
+\begin{lemma}[lem-factor]
+\label{lem:lem-factor}
+$Γ ⊢ φ$ then $Γ ⊢ factor(φ)$.
+\end{lemma}
+
+Now, with a right-associative proposition,
+$strongBuild_{∨}: \Prop → \Prop → \Prop$ in
+Eq.~\ref{eq:strong-build-or-definition} aims to construct the disjunction
+ψ by using each of disjuncts from the proposition φ. This approach to
+build a disjunction from another is inspired on the description
+\citeauthor{bohme2010}~\cite{bohme2010} to prove equality between nested
+disjunctions.
+
+\begin{align}
+  \begin{split}
+  \label{eq:strong-build-or-definition}
+    &strongBuild_{∨}(φ, ψ) =\\
+    &\hspace{3mm}
+    \begin{cases}
+      factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ))  & φ≡ φ₁ ∨ φ₂,\\
+      build_{∨}(φ, ψ)  & \text{otherwise.}
+    \end{cases}
+  \end{split}
+\end{align}
+
+\begin{lemma}[lem-sbuild-or]
+\label{lem:lem-sbuild-or}
+$Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ strongBuild_{∨}(φ, ψ)$.
+\end{lemma}
+
+Let see the following example of the idea behind $strongBuild_{∨}$
+function; from the disjunction $(r ∨ (q ∨ p))$, we build the disjunction
+$((p ∨ q) ∨ r)$.
+
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{Γ ⊢ q}
+  \RightLabel{∨-intro₂}
+  \UnaryInfC{Γ ⊢ p ∨ q}
+  \RightLabel{∨-intro₁}
+  \UnaryInfC{Γ ⊢ (p ∨ q) ∨ r}
+
+  \AxiomC{Γ ⊢ p}
+  \RightLabel{∨-intro₁}
+  \UnaryInfC{Γ ⊢ p ∨ q}
+  \RightLabel{∨-intro₁}
+  \UnaryInfC{Γ ⊢ (p ∨ q) ∨ r}
+
+  \RightLabel{∨-elim}
+  \BinaryInfC{Γ, q ∨ p ⊢ (p ∨ q) ∨ r}
+  \end{bprooftree}
+\end{equation*}
+
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{Γ ⊢ r}
+  \RightLabel{∨-intro₂}
+  \UnaryInfC{Γ ⊢ (p ∨ q) ∨ r}
+
+  \AxiomC{Γ, q ∨ p ⊢ (p ∨ q) ∨ r}
+
+  \RightLabel{∨-elim}
+  \BinaryInfC{Γ, r ∨ (q ∨ p) ⊢ (p ∨ q) ∨ r}
+
+  \RightLabel{⇒-intro}
+  \UnaryInfC{Γ ⊢ r ∨ (q ∨ p) ⇒ (p ∨ q) ∨ r}
+
+  \end{bprooftree}
+\end{equation*}
+
+\begin{theorem}[thm-reorder$_{∨}$] $Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$, where,
+\begin{equation*}
+  \label{eq:reorder-or}
+  reorder_{∨} (φ, ψ) = strongBuild_{∨}(rdisj(φ), ψ).
+\end{equation*}
+\end{theorem}
+\begin{proof} Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
+\end{proof}
+
+To work with nest conjunctions of disjunctions (CNFs), we define similar
+functions and theorems as we previously did for disjunctions.
+
+\begin{lemma}[lem-reorder$_{∧}$]
+\label{lem:lem-reorder-and}
+$Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder(φ, ψ)$, where,
+\begin{align*}
+    \begin{split}
+      reorder_{∧}(φ, ψ) =
+      \begin{cases}
+        φ &\text{if }φ ≡ ψ, \\
+        ψ₁ ∧ ψ₂ &\text{if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁,\\
+                &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂,\\
+        φ       &\text{if } ψ ≡ ψ₁ ∧ ψ₂,\\
+        conjunct(φ, ψ) &\text{otherwise.}
+      \end{cases}
+    \end{split}
+\end{align*}
+
+\end{lemma}
+
+\begin{lemma}[lem-conjunct$_{∨}$]
+\label{lem:lem-conjunct-or}
+$Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$, where,
+
+\begin{align*}
+\begin{split}
+  \label{eq:conjunct-or-definition}
+  conjunct_{∨}(φ, ψ)=
+  \begin{cases}
+    ψ &\text{if }reorder_{∨}(φ, ψ) ≡ ψ,\\
+    ψ &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) = ψ₁,\\
+      &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂,\\
+    ψ &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₁, ψ) ≡ ψ,\\
+    ψ &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₂, ψ) ≡ ψ,\\
     φ &\text{otherwise.}
@@
 \end{split}
-\end{equation}
+\end{align*}
+
+\end{lemma}
+
+\begin{theorem}[thm-reorder$_{∧∨}$]
+\label{thm:thm-reorder-or-and}
+$Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder_{∧∨}(φ, ψ)$, where,
+
+\begin{align}
+    \begin{split}
+    reorder_{∧∨}(φ, ψ)=
+      \begin{cases}
+        ψ &\text{if } φ≡ψ,\\
+        ψ &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁,\\
+          &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂,\\
+        φ &\text{if }ψ ≡ ψ₁ ∧ ψ₂,\\
+        conjunct_{∨}(φ, ψ) &\text{otherwise.}
+      \end{cases}
+    \end{split}
+\end{align}
+
+\end{theorem}
 

### 2017-09-26 paper/sections/proof-reconstruction.tex
[ paper ] working on resolve rule.

@@
 
-\begin{theorem}[thm-reorder$_{∨}$] $Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$, where,
+\begin{theorem}[thm-reorder$_{∨}$]
+$Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$, where,
 \begin{equation*}
@@
 \end{theorem}
+
 \begin{proof} Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
@@
 \end{align}
-
 \end{theorem}
 
+\subsubsection{Resolve.} The \resolve rule is a generalization version for resolution in propositional logic since the formulas are not shaped always as the theorem expect (see Fig.~\ref{fig:metis-inferences}).
+
+Since our approach is mere syntactic, in order to apply such a
+theorem, we perform rearrangements inside the formulas to match with
+the pattern expected by the resolution theorem.
+
+\begin{lemma}[lem-resolution]
+
+\end{lemma}
+
 \end{document}

### 2017-09-26 paper/sections/proof-reconstruction.tex
[ paper ] resolve, nnf, cnf, clausify theorems added.

--- 2017-09-25 paper/sections/proof-reconstruction.tex
@@
 
-(φ₁ ⇒ (φ₂ ∧ φ₃))
+($φ₁ ⇒ (φ₂ ∧ φ₃)$)
 \begin{equation*}
@@
 
-(φ ≡ φ₁ ∧ φ₂). We get a proof for each conjunct and using the introduction rule for conjunction, the result follows.
+($φ ≡ φ₁ ∧ φ₂$). We get a proof for each conjunct and using the introduction rule for conjunction, the result follows.
 
@@
 
-(φ ≡ φ₁ ⇒ φ₂).
+($φ ≡ φ₁ ⇒ φ₂$).
 \begin{equation*}
@@
 
-\begin{theorem}[thm-conjunct]  $Γ ⊢ φ$, and $ψ \in \Prop$, then $Γ ⊢ conjunct(φ, ψ)$.
+\begin{theorem}[thm-conjunct]
+  \label{thm:thm-conjunct}
+  $Γ ⊢ φ$, and $ψ \in \Prop$ , then $Γ ⊢ conjunct(φ, ψ)$.
 \end{theorem}
@@
 
-\begin{lemma}[lem-build-or]
+\begin{lemma}[lem-build$_{∨}$]
 \label{lem:lem-build-or}
@@
 Now, with a right-associative proposition,
-$strongBuild_{∨}: \Prop → \Prop → \Prop$ in
+$sbuild_{∨}: \Prop → \Prop → \Prop$ in
 Eq.~\ref{eq:strong-build-or-definition} aims to construct the disjunction
@@
   \label{eq:strong-build-or-definition}
-    &strongBuild_{∨}(φ, ψ) =\\
+    &sbuild_{∨}(φ, ψ) =\\
     &\hspace{3mm}
@@
 
-\begin{lemma}[lem-sbuild-or]
+\begin{lemma}[lem-sbuild$_{∨}$]
 \label{lem:lem-sbuild-or}
-$Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ strongBuild_{∨}(φ, ψ)$.
+$Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ sbuild_{∨}(φ, ψ)$.
 \end{lemma}
 
-Let see the following example of the idea behind $strongBuild_{∨}$
+Let see the following example of the idea behind $sbuild_{∨}$
 function; from the disjunction $(r ∨ (q ∨ p))$, we build the disjunction
@@
 
-\begin{theorem}[thm-reorder$_{∨}$] $Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$, where,
+\begin{theorem}[thm-reorder$_{∨}$]
+  \label{thm-reorder-or}
+  $Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$, where,
   \begin{equation*}
     \label{eq:reorder-or}
-  reorder_{∨} (φ, ψ) = strongBuild_{∨}(rdisj(φ), ψ).
+    reorder_{∨} (φ, ψ) = sbuild_{∨}(rdisj(φ), ψ).
   \end{equation*}
 \end{theorem}
+
 \begin{proof} Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
@@
   \end{align*}
-
 \end{lemma}
@@
   $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$, where,
-
   \begin{align*}
@@
     \label{eq:conjunct-or-definition}
-  conjunct_{∨}(φ, ψ)=
+    conjunct_{∨}(φ, ψ) =
     \begin{cases}
@@
 \begin{theorem}[thm-reorder$_{∧∨}$]
-\label{thm:thm-reorder-or-and}
+  \label{thm:thm-reorder-and-or}
+
   $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder_{∧∨}(φ, ψ)$, where,
@@
   \end{align}
-
 \end{theorem}
 
+% --------------------------------------------------------------------
+
+\subsubsection{Resolve} % (fold)
+\label{ssub:resolve}
+
+The \resolve rule is a generalization version for resolution in propositional logic since the formulas are not shaped always as the theorem expect (see Fig.~\ref{fig:metis-inferences}).
+
+Since our approach is mere syntactic, in order to apply such a
+theorem, we perform rearrangements inside the formulas to match with
+the pattern expected by the resolution theorem.
+
+\begin{lemma}[lem-rsol]
+  \label{lem:lem-rsol}
+  $Γ ⊢ φ$ then $Γ ⊢ rsol(φ)$, where,
+  \begin{align*}
+      \begin{split}
+        rsol(φ) =
+        \begin{cases}
+          φ₂ &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄,\\
+          φ₂ ∨ φ₄ &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁,\\
+          φ &\text{otherwise.}
+        \end{cases}
+      \end{split}
+  \end{align*}
+\end{lemma}
+
+\begin{theorem}[thm-resolve]
+  \label{thm:thm-resolve}
+  $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ\in\Prop$ then $Γ ⊢ resolve(φ₁, φ₂, l, ψ)$, where,
+  \begin{equation*}
+    resolve(φ₁, φ₂, l, ψ) =
+      rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨} (φ₂, ¬ l ∨ ψ)).
+  \end{equation*}
+\end{theorem}
+
+\begin{proof}
+\begin{equation*}
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ φ₁$}
+    \RightLabel{thm-reorder$_{∨}$}
+    \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ)$}
+
+    \AxiomC{$Γ ⊢ φ₂$}
+    \RightLabel{thm-reorder$_{∨}$}
+    \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+
+    \RightLabel{∧-intro}
+    \BinaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+    \RightLabel{lem-rsol}
+    \UnaryInfC{$Γ ⊢ rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ))$}
+  \end{bprooftree}
+  \end{equation*}
+\end{proof}
+
+% subsubsection resolve (end)
+% --------------------------------------------------------------------
+
+% --------------------------------------------------------------------
+
+\subsubsection{Normal Forms.} % (fold)
+\label{ssub:normal_forms}
+
+A negative normal form for the formula φ is one in which negations
+appear only in the literals and the expression is in terms only of
+the boolean operators (¬, ∧, ∨).
+
+To transform a formula φ to its equivalent \abbre{NNF} form, we
+apply recursively the following equations. The function type for
+\name{nnf} is $\Prop \to \Prop$.
+
+\begin{lemma}[lem-nnf]
+  \label{lem:lem-nnf}
+  $Γ ⊢ φ$ then $Γ ⊢ nnf(φ)$, where,
+  \begin{align*}
+    \begin{split}
+    \label{eq:nnf-definition}
+    nnf(φ) =
+      \begin{cases}
+      nnf(φ₁) ∧ nnf(φ₂)
+         &\text{if }φ ≡ φ₁ ∧ φ₂, \\
+      nnf(φ₁) ∨ nnf(φ₂)
+         &\text{if }φ ≡ φ₁ ∨ φ₂, \\
+      nnf(¬ φ₁ ∨ φ₂)
+         &\text{if }φ ≡ φ₁ ⇒ φ₂, \\
+      nnf(φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁)
+         &\text{if }φ ≡ φ₁ ⇔ φ₂, \\
+      nnf(¬ φ₁ ∨ ¬ φ₂)
+         &\text{if }φ ≡ ¬ (φ₁ ∧ φ₂), \\
+      nnf(¬ φ₁ ∧ ¬ φ₂)
+         &\text{if }φ ≡ ¬ (φ₁ ∨ φ₂), \\
+      nnf(φ₁)
+         &\text{if }φ ≡ ¬ ¬ φ₁, \\
+      nnf(¬ (φ₂ ∨ ¬ φ₁))
+         &\text{if }φ ≡ ¬ (φ₁ ⇒ φ₂), \\
+      nnf(¬ (φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁))
+         &\text{if }φ ≡ ¬ (φ₁ ⇔ φ₂), \\
+      ⊥  &\text{if }φ ≡ ¬ ⊤, \\
+      ⊤  &\text{if }φ ≡ ¬ ⊥, \\
+      φ  & \text{otherwise}.
+      \end{cases}
+    \end{split}
+  \end{align*}
+\end{lemma}
+
+\begin{lemma}[lem-dist$_{∨}$]
+  \label{lem:lem-dist-or}
+  $Γ ⊢ φ$ then $Γ ⊢ dist_{∨}(φ)$, where,
+  \begin{align*}
+      \begin{split}
+      dist_{∨} =
+        \begin{cases}
+          dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃)
+            &\text{if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃,\\
+          dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃)
+            &\text{if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃),\\
+          φ &\text{otherwise.}
+        \end{cases}
+      \end{split}
+  \end{align*}
+\end{lemma}
+
+\begin{lemma}[lem-dist]
+  \label{lem:lem-dist}
+  $Γ ⊢ φ$ then $Γ ⊢ dist(φ)$, where,
+  \begin{align*}
+      \begin{split}
+      dist =
+        \begin{cases}
+          dist(φ₁) ∧ dist(φ₂)
+            &\text{if }φ ≡ φ₁ ∧ φ₂,\\
+          dist_{∨}(dist(φ₁) ∨ dist(φ₂))
+            &\text{if }φ ≡ φ₁ ∨ φ₂,\\
+          φ &\text{otherwise.}
+        \end{cases}
+      \end{split}
+  \end{align*}
+\end{lemma}
+
+\begin{proof} Sketch. Case when $φ ≡ φ₁ ∨ φ₂$.\\
+For $i = 1, 2$,
+\begin{equation}
+  \begin{bprooftree}
+    \RightLabel{assume}
+    \AxiomC{$Γ, φ_{i} ⊢ φ_{i}$}
+    \RightLabel{lem-dist}
+    \UnaryInfC{$Γ ⊢ dist(φ_{i})$}
+    \RightLabel{∨-intro$_{1,2}$}
+    \UnaryInfC{$Γ, φ_{i} ⊢ dist(φ₁) ∨ dist(φ₂)$}
+    \RightLabel{lem-dist$_{∨}$}
+    \UnaryInfC{$Γ, φ_{i} ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$.}
+    \end{bprooftree}
+\end{equation}
+Then, by using the ∨-elim rule, from the last derivation above we derive
+$Γ, φ₁ ∨ φ₂ ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$, and the lemma follows.
+\end{proof}
+
+\begin{theorem}[thm-cnf]
+\label{thm:thm-cnf}
+  $Γ ⊢ φ$ then $Γ ⊢ cnf(φ)$, where,
+  \begin{equation}
+    cnf(φ) = (dist \circ nnf) (\varphi)
+  \end{equation}
+\end{theorem}
+
+\begin{proof}
+  Composition of the Lemma \ref{lem:lem-dist} and Lemma \ref{lem:lem-nnf}.
+\end{proof}
+% subsubsection normal_forms (end)
+% --------------------------------------------------------------------
+
+% --------------------------------------------------------------------
+
+\subsubsection{Clausification.} % (fold)
+\label{ssub:clausification}
+
+\begin{theorem}[thm-clausify] % (fold)
+\label{thm:thm_clausify}
+  $Γ ⊢ φ$ and $ψ \in\Prop$ then $Γ ⊢ clausify(φ, ψ)$, where,
+  \begin{align}
+      clausify(φ,ψ) =
+      \begin{cases}
+        ψ, &\text{ if }φ≡ψ\\
+        reorder_{∧∨}(cnf(φ), ψ), &\text{otherwise.}
+      \end{cases}
+  \end{align}
+\end{theorem}
+
+\begin{proof} When $φ ≡ ψ$, we use the $subs$ theorem Eq.~\ref{eq:substitution-theorem}. Otherwise, we use Theorem \ref{thm:thm-reorder-and-or} and Theorem \ref{thm:thm-cnf}.
+\end{proof}
+
+% subsubsection clausification (end)
+% --------------------------------------------------------------------
+
 \end{document}

### 2017-09-26 paper/sections/proof-reconstruction.tex
[ paper ] cosmetics for cases equations.

@@
 &\hspace{3mm}\begin{cases}
-\unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃)
-  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
-\unshunt_{0}(φ₁ ⇒ φ₂) ∧ \unshunt_{0}(φ₁ ⇒ φ₃)
-  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
-φ &\text{otherwise.}
+\unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
+  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+\unshunt_{0}(φ₁ ⇒ φ₂) ∧ \unshunt_{0}(φ₁ ⇒ φ₃),
+  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
+φ, &\text{otherwise.}
 \end{cases}
@@
 &\hspace{3mm}\begin{cases}
-\unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n)
-  &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
-\unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ \unshunt_{1}(φ₁ ⇒ φ₃, n) &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
+\unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
+  &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+\unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ \unshunt_{1}(φ₁ ⇒ φ₃, n),
+   &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
 \end{cases}
@@
 \begin{cases}
-0 &\text{for atomic }φ, \\
-rank(φ₁) + c_{¬}  &\text{if } φ ≡ \neg φ₁, \\
-\max{(rank(φ₁),rank(φ₂))} + c_{\square}
+0, &\text{for atomic }φ \\
+rank(φ₁) + c_{¬},  &\text{if } φ ≡ \neg φ₁ \\
+\max{(rank(φ₁),rank(φ₂))} + c_{\square},
   &\text{if } φ ≡ φ₁\,\square\, φ₂.
@@
 \begin{cases}
-\unshunt_{cm}(φ₃) + 2 & φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃),\\
-\max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1
-  &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃),\\
-0 &\text{otherwise.}
+\unshunt_{cm}(φ₃) + 2, &\text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+\max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1,
+  &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
+0, &\text{otherwise.}
 \end{cases}
@@
 \label{eq:split-definition}
-% \mysplit(φ) =
+\mysplit(φ) =
 \begin{cases}
-\unshunt(\mysplit(φ₁)) ∧\ \unshunt(φ₁ ⇒ \mysplit(φ₂))  & \text{if }φ ≡ φ₁ ∧ φ₂,\\
+\unshunt(\mysplit(φ₁)) &\text{if }φ ≡ φ₁ ∧ φ₂\\
+∧\ \unshunt(φ₁ ⇒ \mysplit(φ₂)), &\\[2.5mm]
+\unshunt(¬ φ₁ ⇒ \mysplit(φ₂)),
+  & \text{if }φ ≡ φ₁ ∨ φ₂\\[2.5mm]
+\unshunt(φ₁ ⇒ \mysplit(φ₂)),
+  & \text{if }φ ≡ φ₁ ⇒ φ₂\\[2.5mm]
+\unshunt(φ₁ ⇒ \mysplit(φ₂))
+  & \text{if }φ ≡ φ₁ ⇔ φ₂\\
+∧\ \unshunt(φ₂ ⇒ \mysplit(φ₁)),
   &\\[2.5mm]
-\unshunt(¬ φ₁ ⇒ \mysplit(φ₂))       & \text{if }φ ≡ φ₁ ∨ φ₂,\\[2.5mm]
-
-\unshunt(φ₁ ⇒ \mysplit(φ₂))         & \text{if }φ ≡ φ₁ ⇒ φ₂,\\[2.5mm]
-
-\unshunt(φ₁ ⇒ \mysplit(φ₂))         & \text{if }φ ≡ φ₁ ⇔ φ₂,\\
-∧\ \unshunt(φ₂ ⇒ \mysplit(φ₁))      &\\[2.5mm]
-
-\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂),\\[2.5mm]
-\unshunt(\mysplit(¬ φ₁))            & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂),\\
-∧\ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂))  &\\[2.5mm]
-
-\unshunt(\mysplit(φ₁))              & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂),\\
-∧\ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂))    &\\[2.5mm]
-
-\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))       & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂),\\
-∧\ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁))    &\\[2.5mm]
-
-\unshunt(\mysplit(φ₁))              & \text{if }φ ≡ ¬ ¬ φ₁,\\
-⊤                                   & \text{if }φ ≡ ¬ ⊥,\\
-⊥                                   & \text{if }φ ≡ ¬ ⊤.
+\unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
+  & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂)\\[2.5mm]
+\unshunt(\mysplit(¬ φ₁))
+  & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
+∧\ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂)),
+  &\\[2.5mm]
+\unshunt(\mysplit(φ₁))
+  & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
+∧\ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
+  &\\[2.5mm]
+\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
+  & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
+∧\ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁)),
+  &\\[2.5mm]
+\unshunt(\mysplit(φ₁)),
+  & \text{if }φ ≡ ¬ ¬ φ₁\\
+⊤,
+  & \text{if }φ ≡ ¬ ⊥\\
+⊥,
+  & \text{if }φ ≡ ¬ ⊤.
 \end{cases}
@@
     \begin{cases}
-      ψ &\text{if }φ ≡ ψ,\\
-      ψ &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₁, ψ)≡ ψ,\\
-      ψ &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₂, ψ)≡ ψ,\\
-      φ &\text{otherwise.}
+      ψ, &\text{if }φ ≡ ψ\\
+      ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₁, ψ)≡ ψ\\
+      ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₂, ψ)≡ ψ\\
+      φ, &\text{otherwise.}
     \end{cases}
@@
     \begin{cases}
-    rdisj(φ₁ ∨ (φ₂ ∨ φ₃)) & \text{if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃, \\
-    φ₁ ∨ rdisj(φ₂)        & \text{if } φ ≡ φ₁ ∨ φ₂, \\
-    φ                     & \text{otherwise.}
+    rdisj(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
+    φ₁ ∨ rdisj(φ₂),         & \text{if } φ ≡ φ₁ ∨ φ₂\\
+    φ,                      & \text{otherwise.}
     \end{cases}
@@
   \begin{cases}
-  ψ &\text{if } φ ≡ ψ,\\
-  ψ &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2,\\
-  φ &\text{otherwise.}
+  ψ, &\text{if } φ ≡ ψ\\
+  ψ, &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
+  φ, &\text{otherwise.}
   \end{cases}
@@
   \begin{cases}
-    φ₁ & \text{if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ factor(φ₂),\\
-    φ  & \text{otherwise.}
+    φ₁,  &\text{if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ factor(φ₂)\\
+    φ,   &\text{otherwise.}
   \end{cases}
@@
   \label{eq:strong-build-or-definition}
-    &sbuild_{∨}(φ, ψ) =\\
-    &\hspace{3mm}
+    sbuild_{∨}(φ, ψ) =
     \begin{cases}
-      factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ))  & φ≡ φ₁ ∨ φ₂,\\
-      build_{∨}(φ, ψ)  & \text{otherwise.}
+      factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ)),  &\text{if }φ≡ φ₁ ∨ φ₂\\
+      build_{∨}(φ, ψ),  & \text{otherwise.}
     \end{cases}
@@
         \begin{cases}
-          φ &\text{if }φ ≡ ψ, \\
-          ψ₁ ∧ ψ₂ &\text{if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁,\\
-                  &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂,\\
-          φ       &\text{if } ψ ≡ ψ₁ ∧ ψ₂,\\
+          φ, &\text{if }φ ≡ ψ\\
+          ψ₁ ∧ ψ₂, &\text{if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁\\
+                  &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂\\
+          φ,       &\text{if } ψ ≡ ψ₁ ∧ ψ₂\\
           conjunct(φ, ψ) &\text{otherwise.}
@@
     \begin{cases}
-      ψ &\text{if }reorder_{∨}(φ, ψ) ≡ ψ,\\
-      ψ &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) = ψ₁,\\
-        &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂,\\
-      ψ &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₁, ψ) ≡ ψ,\\
-      ψ &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₂, ψ) ≡ ψ,\\
-      φ &\text{otherwise.}
+      ψ, &\text{if }reorder_{∨}(φ, ψ) ≡ ψ\\
+      ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) = ψ₁\\
+        &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂\\
+      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₁, ψ) ≡ ψ\\
+      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₂, ψ) ≡ ψ\\
+      φ, &\text{otherwise.}
     \end{cases}
@@
         \begin{cases}
-          ψ &\text{if } φ≡ψ,\\
-          ψ &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁,\\
-            &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂,\\
-          φ &\text{if }ψ ≡ ψ₁ ∧ ψ₂,\\
+          ψ, &\text{if } φ≡ψ\\
+          ψ, &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
+             &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
+          φ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂\\
           conjunct_{∨}(φ, ψ) &\text{otherwise.}
@@
 
-\subsubsection{Resolve} % (fold)
+\subsubsection{Resolve}
 \label{ssub:resolve}
@@
         \begin{cases}
-          φ₂ &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄,\\
-          φ₂ ∨ φ₄ &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁,\\
-          φ &\text{otherwise.}
+          φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
+          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
+          φ, &\text{otherwise.}
         \end{cases}
@@
 
-\subsubsection{Normal Forms.} % (fold)
+\subsubsection{Normal Forms.}
 \label{ssub:normal_forms}
@@
       \begin{cases}
-      nnf(φ₁) ∧ nnf(φ₂)
-         &\text{if }φ ≡ φ₁ ∧ φ₂, \\
-      nnf(φ₁) ∨ nnf(φ₂)
-         &\text{if }φ ≡ φ₁ ∨ φ₂, \\
-      nnf(¬ φ₁ ∨ φ₂)
-         &\text{if }φ ≡ φ₁ ⇒ φ₂, \\
-      nnf(φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁)
-         &\text{if }φ ≡ φ₁ ⇔ φ₂, \\
-      nnf(¬ φ₁ ∨ ¬ φ₂)
-         &\text{if }φ ≡ ¬ (φ₁ ∧ φ₂), \\
-      nnf(¬ φ₁ ∧ ¬ φ₂)
-         &\text{if }φ ≡ ¬ (φ₁ ∨ φ₂), \\
-      nnf(φ₁)
-         &\text{if }φ ≡ ¬ ¬ φ₁, \\
-      nnf(¬ (φ₂ ∨ ¬ φ₁))
-         &\text{if }φ ≡ ¬ (φ₁ ⇒ φ₂), \\
-      nnf(¬ (φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁))
-         &\text{if }φ ≡ ¬ (φ₁ ⇔ φ₂), \\
-      ⊥  &\text{if }φ ≡ ¬ ⊤, \\
-      ⊤  &\text{if }φ ≡ ¬ ⊥, \\
-      φ  & \text{otherwise}.
+      nnf(φ₁) ∧ nnf(φ₂),
+         &\text{if }φ ≡ φ₁ ∧ φ₂ \\
+      nnf(φ₁) ∨ nnf(φ₂),
+         &\text{if }φ ≡ φ₁ ∨ φ₂ \\
+      nnf(¬ φ₁ ∨ φ₂),
+         &\text{if }φ ≡ φ₁ ⇒ φ₂ \\
+      nnf(φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁),
+         &\text{if }φ ≡ φ₁ ⇔ φ₂ \\
+      nnf(¬ φ₁ ∨ ¬ φ₂),
+         &\text{if }φ ≡ ¬ (φ₁ ∧ φ₂) \\
+      nnf(¬ φ₁ ∧ ¬ φ₂),
+         &\text{if }φ ≡ ¬ (φ₁ ∨ φ₂) \\
+      nnf(φ₁),
+         &\text{if }φ ≡ ¬ ¬ φ₁ \\
+      nnf(¬ (φ₂ ∨ ¬ φ₁)),
+         &\text{if }φ ≡ ¬ (φ₁ ⇒ φ₂) \\
+      nnf(¬ (φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁)),
+         &\text{if }φ ≡ ¬ (φ₁ ⇔ φ₂) \\
+      ⊥,  &\text{if }φ ≡ ¬ ⊤ \\
+      ⊤,  &\text{if }φ ≡ ¬ ⊥ \\
+      φ,  & \text{otherwise}.
       \end{cases}
@@
         \begin{cases}
-          dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃)
-            &\text{if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃,\\
-          dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃)
-            &\text{if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃),\\
-          φ &\text{otherwise.}
+          dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃),
+            &\text{if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
+          dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃),
+            &\text{if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
+          φ, &\text{otherwise.}
         \end{cases}
@@
         \begin{cases}
-          dist(φ₁) ∧ dist(φ₂)
-            &\text{if }φ ≡ φ₁ ∧ φ₂,\\
-          dist_{∨}(dist(φ₁) ∨ dist(φ₂))
-            &\text{if }φ ≡ φ₁ ∨ φ₂,\\
-          φ &\text{otherwise.}
+          dist(φ₁) ∧ dist(φ₂),
+            &\text{if }φ ≡ φ₁ ∧ φ₂\\
+          dist_{∨}(dist(φ₁) ∨ dist(φ₂)),
+            &\text{if }φ ≡ φ₁ ∨ φ₂\\
+          φ, &\text{otherwise.}
         \end{cases}
@@
 
-\subsubsection{Clausification.} % (fold)
-\label{ssub:clausification}
+\subsubsection{Clausification.}
+\label{ssec:clausification}
 
-\begin{theorem}[thm-clausify] % (fold)
+\begin{theorem}[thm-clausify]
 \label{thm:thm_clausify}

### 2017-09-28 paper/sections/proof-reconstruction.tex
[ paper ] cosmetics for theorems.
[ paper ] normalization, first part, added.

@@
 \begin{split}
-&\unshunt_{1}(φ, \zero) = φ\\
+&\unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\
 &\unshunt_{1}(φ, \suc(n)) =\\
@@
 
-\subsubsection{Resolve}
-\label{ssub:resolve}
+\subsubsection{Resolve.}
+\label{sssec:resolve}
 
@@
 \subsubsection{Normal Forms.}
-\label{ssub:normal_forms}
+\label{sssec:normal_forms}
 
@@
   \begin{equation}
-    cnf(φ) = (dist \circ nnf) (\varphi)
+    cnf(φ) = (dist \circ nnf) (\varphi).
   \end{equation}
@@
 \subsubsection{Clausification.}
-\label{ssec:clausification}
+\label{sssec:clausification}
 
@@
 
+% --------------------------------------------------------------------
+\subsubsection{Normalization.}
+\label{sssec:normalization}
+
+In a disjunction, $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$, we say $ψ ∈_{∨} φ$,
+if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
+Then, we define the $rm_{∨}$ function to remove in a disjunction φ, those propositions ψ repeated in the formula.
+
+\begin{equation*}
+\label{eq:rm-or}
+  rm_{∨}(φ) =
+  \begin{cases}
+    rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂, φ₁ ∈_{∨} φ₂\\
+    φ₁ ∨ rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
+    φ,  &\text{otherwise.}
+  \end{cases}
+\end{equation*}
+
+Since, our goal consists of normalizing prepositions in \abbre{CNF}, we also need to generalize $rm_{∨}$ to work with conjunctions. We define $rm_{∧∨}$ function for that purpose.
+
+\begin{equation*}
+\label{eq:rm-and-or}
+  rm_{∧∨}(φ) =
+  \begin{cases}
+    rm_{∧∨}(φ₁) ∧ rm_{∧∨}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
+    rm_{∨}(rconj(φ)),  &\text{otherwise.}
+  \end{cases}
+\end{equation*}
+
+Now, we have removed redundancies in the disjunctions, we move forward and we remove redundancies at the level of the conjunction of the CNFs by applying the $rm_{∧}$ function, we remove conjunct repeated in the formula.
+We define $ψ ∈_{∧} φ$ similar as we described above for disjunction.
+In a conjunction, $φ = φ₁ ∧ φ₂ ∧ \cdots ∧ φₙ$, we say
+$ψ ∈_{∧} φ$, if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
+
+\begin{equation*}
+\label{eq:rm-and}
+  rm_{∧}(φ) =
+  \begin{cases}
+    rm_{∧}(φ₁) ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂, φ₁ ∈_{∧} φ₂\\
+    φ₁ ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
+    φ,  &\text{otherwise.}
+  \end{cases}
+\end{equation*}
+
+Finally, we remove redundancies in a proposition in its conjunctive normal form, by composing the functions described above in the Eq.~\ref{eq:rm-cnf} for the function $cleanCNF$.
+
+\begin{equation*}
+  \label{eq:rm-cnf}
+  cleanCNF = rm_{∧} ∘ rm_{∧∨} ∘ rconj ∘ cnf.
+\end{equation*}
+
+% subsection normalization (end)
+% --------------------------------------------------------------------
+
 \end{document}

### 2017-09-28 src/Athena/Translation/AgdaFile.hs

@@ -319,7 +319,7 @@ getRefutes dict tstp = map (\tag → fromJust (Map.lookup tag dict)) names
     names = [ "refute-" ++ show n ++ "-" ++ show k | (n,k) <- rootRefutes ]
 
     rootRefutes ∷ [ (Int, Int) ]
-    rootRefutes = [ maximum (filter (\l -> (fst l == r)) refutesID) 
+    rootRefutes = [ maximum (filter (\l -> (fst l == r)) refutesID)
                   | r ← numRefutes ]
 
     extractRefuteId ∷ String → (Int, Int)
@@ -494,7 +494,7 @@ docSteps subgoalN (Root Negate _ [subtree@(Root Strip _ _)]) agdaFile =
 -}
 
 docSteps subgoalN (Root Resolve tag [left, right]) agdaFile =
-  parens $ pretty Resolve <+> getFormulaByTag agdaFile tag <+> pretty literal 
+  parens $ pretty Resolve <+> getFormulaByTag agdaFile tag <+> pretty literal
   <> line <> indent 2
     (docSteps subgoalN left agdaFile <> line <>
       docSteps subgoalN right agdaFile)

### 2017-09-28 paper/sections/metis-language-and-proofs.tex
[ paper ] working on normalization subsubsection.

@@
 For instance, let us express the problem
-$p\, \vdash \neg (p \wedge \neg p) \vee (q \wedge \neg q)$
+$p\, \vdash \neg (p \wedge \neg p) ∨ (q \wedge \neg q)$
 in \TPTP syntax as follows, declaring an \tptpaxiom $p$, and the
@@
   \RightLabel{assume $L$}
-  \UnaryInfC{$L \vee \neg L$}
+  \UnaryInfC{$L ∨ \neg L$}
 \end{bprooftree}
@@
   \RightLabel{equality $L$ $p$ $t$}
-  \UnaryInfC{$\neg (L[p] = t) \vee \neg L \vee L[ p \mapsto t]$}
+  \UnaryInfC{$\neg (L[p] = t) ∨ \neg L ∨ L[ p \mapsto t]$}
 \end{bprooftree}
@@
 \begin{bprooftree}
-  \AxiomC{$L \vee C$}
-  \AxiomC{$\neg L \vee D$}
+  \AxiomC{$L ∨ C$}
+  \AxiomC{$\neg L ∨ D$}
   \RightLabel{resolve $L$}
-  \BinaryInfC{$C \vee D$}
+  \BinaryInfC{$C ∨ D$}
 \end{bprooftree}
@@
 conclusion. The proof graphs have at their root the conclusion
-$\bot$, since \Metis delivers proofs by refutation.
+$⊥$, since \Metis delivers proofs by refutation.
 
@@
   \RightLabel{\footnotesize simplify}
-  \BinaryInfC{$\bot$}
+  \BinaryInfC{$⊥$}
   \RightLabel{\footnotesize canonicalize}
-  \UnaryInfC{$\bot$}
+  \UnaryInfC{$⊥$}
 \end{bprooftree}
@@
   \begin{bprooftree}
-    \AxiomC{$\varphi \wedge \bot$}
-    \UnaryInfC{$\bot$}
+    \AxiomC{$φ ∧ ⊥$}
+    \UnaryInfC{$⊥$}
   \end{bprooftree}
@@
   \begin{bprooftree}
-    \AxiomC{$\varphi \wedge \top$}
-    \UnaryInfC{$\varphi$}
+    \AxiomC{$φ ∧ ⊤$}
+    \UnaryInfC{$φ$}
   \end{bprooftree}
@@
   \begin{bprooftree}
-    \AxiomC{$\varphi \wedge \neg \varphi$}
-    \UnaryInfC{$\bot$}
+    \AxiomC{$φ ∧ ¬ φ$}
+    \UnaryInfC{$⊥$}
   \end{bprooftree}
@@
   \begin{bprooftree}
-    \AxiomC{$\varphi \wedge \varphi$}
-    \UnaryInfC{$\varphi$}
+    \AxiomC{$φ ∧ φ$}
+    \UnaryInfC{$φ$}
   \end{bprooftree}
@@
   \begin{bprooftree}
-    \AxiomC{$\varphi \vee \bot$}
-    \UnaryInfC{$\varphi$}
+    \AxiomC{$φ ∨ ⊥$}
+    \UnaryInfC{$φ$}
   \end{bprooftree}
@@
   \begin{bprooftree}
-    \AxiomC{$\varphi \vee \top$}
-    \UnaryInfC{$\top$}
+    \AxiomC{$φ ∨ ⊤$}
+    \UnaryInfC{$⊤$}
   \end{bprooftree}
@@
   \begin{bprooftree}
-    \AxiomC{$\varphi \vee \neg \varphi$}
-    \UnaryInfC{$\top$}
+    \AxiomC{$φ ∨ ¬ φ$}
+    \UnaryInfC{$⊤$}
   \end{bprooftree}
@@
   \begin{bprooftree}
-    \AxiomC{$\varphi \vee \varphi$}
-    \UnaryInfC{$\varphi$}
+    \AxiomC{$φ ∨ φ$}
+    \UnaryInfC{$φ$}
   \end{bprooftree}
@@
 
-Moreover, we are not completely covered every detail in the behavior
-for all \Metis' inference rules. It is somewhat complicated to grasp
-completely the inference rules since the source code is around the
-10.000 lines of code.
-
 \end{document}

### 2017-09-28 paper/sections/proof-reconstruction.tex
[ paper ] working on normalization subsubsection.

@@
       ψ, &\text{if }reorder_{∨}(φ, ψ) ≡ ψ\\
-      ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) = ψ₁\\
+      ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) ≡ ψ₁\\
         &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂\\
@@
 if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
-Then, we define the $rm_{∨}$ function to remove in a disjunction φ, those propositions ψ repeated in the formula.
+Then, we define the $rm_{∨}$ function to remove in a disjunction φ, those propositions ψ repeated in the formula. The formula $φ$ must be a right-associative disjunction.
 
@@
     rm_{∧∨}(φ₁) ∧ rm_{∧∨}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
-    rm_{∨}(rconj(φ)),  &\text{otherwise.}
+    rm_{∨}(rdisj(φ)),  &\text{otherwise.}
   \end{cases}
@@
 
-Finally, we remove redundancies in a proposition in its conjunctive normal form, by composing the functions described above in the Eq.~\ref{eq:rm-cnf} for the function $cleanCNF$.
-
-\begin{equation*}
-  \label{eq:rm-cnf}
-  cleanCNF = rm_{∧} ∘ rm_{∧∨} ∘ rconj ∘ cnf.
-\end{equation*}
+Finally, we remove redundancies in a proposition assuming that it is given in conjunctive normal form and right-associative, by composing the functions described above in the Eq.~\ref{eq:redun-ast}
+for the function $redun^{*}$.
+
+\begin{equation*}
+  \label{eq:redun-ast}
+  redun^{*} = rm_{∧} ∘ rm_{∧∨}.
+\end{equation*}
+
+Then, performing rearrangements to match with the expected output
+by $redon^{*}$ function.
+
+\begin{equation*}
+  \label{eq:redun}
+  redun(φ) = reorder_{∧∨}(φ, redun^{*}(φ)).
+\end{equation*}
+
+\begin{theorem}[thm-redun]
+  \label{thm:thm_redun}
+  $Γ ⊢ φ$ then $Γ ⊢ redun(φ)$.
+\end{theorem}
+
+\begin{proof}
+Use in Theorem~\ref{thm:thm-reorder-and-or} with $ψ$ equals to
+$redun^{*}(φ)$.
+\end{proof}
 

### 2017-10-01 paper/sections/proof-reconstruction.tex
[ paper ] canonicalize lemmas and theorems.

@@
 Then, we solve the termination problem by modifying problematic functions
-to be \emph{structural recursive}~\cite{Coquand1992,Abel2002,Bove2005}
+to be \emph{structural recursive}~\cite{Coquand1992,Abel2002,Bove2005}.
 
@@
 \label{eq:unshunt-definition}
-&\unshunt_{0}(φ) =\\
+&unshunt_{0}(φ) =\\
 &\hspace{3mm}\begin{cases}
-\unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
+unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
   & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-\unshunt_{0}(φ₁ ⇒ φ₂) ∧ \unshunt_{0}(φ₁ ⇒ φ₃),
+unshunt_{0}(φ₁ ⇒ φ₂) ∧ unshunt_{0}(φ₁ ⇒ φ₃),
   & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
@@
 Thus, we define the function
-$\unshunt_{1} : \Prop \to \Nat \to \Prop$
+$unshunt_{1} : \Prop \to \Nat \to \Prop$
 by structural recursion in its second argument in
@@
 \begin{split}
-&\unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\
-&\unshunt_{1}(φ, \suc(n)) =\\
+&unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\
+&unshunt_{1}(φ, \suc(n)) =\\
 &\hspace{3mm}\begin{cases}
-\unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
+unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
   &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-\unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ \unshunt_{1}(φ₁ ⇒ φ₃, n),
+unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ unshunt_{1}(φ₁ ⇒ φ₃, n),
    &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
@@
 
-As we mentioned above, the natural number in the second argument of the function used in Eq.~\ref{eq:unshunt-structured} stands for a complexity measure of the function, in this case $\unshunt_{1}$ function.
+As we mentioned above, the natural number in the second argument of the
+function used in Eq.~\ref{eq:unshunt-structured} stands for a complexity
+measure of the function, in this case $unshunt_{1}$ function.
 
@@
 and presented in \cite{VanDalen1994} as \emph{the rank for a
-proposition}, is a function $\Prop \to \Nat$ that assigns a natural number for a proposition φ as follows.
+proposition}, is a function $\Prop \to \Nat$ that assigns a natural
+number for a proposition φ as follows.
 
@@
 
-Recall, we want to maintain the same outputs as the original \unshunt does in Eq.~\ref{eq:unshunt-definition} and the complexity measure of it, is a bound for the number of times this function can call itself.
+Recall, we want to maintain the same outputs as the original unshunt
+does in Eq.~\ref{eq:unshunt-definition} and the complexity measure of it,
+is a bound for the number of times this function can call itself.
 
 Therefore, we define an appropriate complexity measure
-$\unshunt_{cm}: \Prop → \NN$ for our $\unshunt_{1}$ function presented in
+$unshunt_{cm}: \Prop → \NN$ for our $unshunt_{1}$ function presented in
 Eq.~\ref{eq:unshunt-rank-definition}.
 
-\begin{equation}
+\begin{align}
+\begin{split}
 \label{eq:unshunt-rank-definition}
-\unshunt_{cm}(φ)=
-\begin{cases}
-\unshunt_{cm}(φ₃) + 2, &\text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-\max(\unshunt_{cm}(φ₂),\unshunt_{cm}(φ₃)) + 1,
+&unshunt_{cm}(φ) =\\
+&\hspace{3mm}
+\begin{cases}
+unshunt_{cm}(φ₃) + 2, &\text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+\max(unshunt_{cm}(φ₂),unshunt_{cm}(φ₃)) + 1,
   &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
@@
 \end{cases}
-\end{equation}
-
-Finally, the curated version of $\unshunt_{0}$ function is presented
+\end{split}
+\end{align}
+
+Finally, the curated version of $unshunt_{0}$ function is presented
 in Eq.~\ref{eq:unshunt-fixed}.
@@
 \label{eq:unshunt-fixed}
-\unshunt(\varphi) := \unshunt_{1}(\varphi, \unshunt_{cm}(\varphi)).
+unshunt(\varphi) := unshunt_{1}(\varphi, unshunt_{cm}(\varphi)).
 \end{equation}
@@
 In the following, we show how Theorem.~\ref{thm:thm-strip} proves the correctness of the process mentioned above.
-But first, let prove some lemmas for $\unshunt$ function presented in Eq.~\ref{eq:unshunt-fixed},
+But first, let prove some lemmas for $unshunt$ function presented in Eq.~\ref{eq:unshunt-fixed},
 and $split$ function from the definition in Eq.~\ref{eq:split-definition}.
 
-\begin{lemma}[\thmunshunt]
+\begin{lemma}[lem-unshunt]
   \label{lem:unshunt}
-  $Γ ⊢ \unshunt(φ)$, then $Γ ⊢ φ$.
+  $Γ ⊢ unshunt(φ)$, then $Γ ⊢ φ$.
 \end{lemma}
@@
 \begin{proof} Use induction on the cases defined by the outcome of the
-$\unshunt$ function in Eq.~\ref{eq:unshunt-structured}.
+$unshunt$ function in Eq.~\ref{eq:unshunt-structured}.
 When $n = 0$, by definition, $Γ ⊢ φ$.
@@
   \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
+  \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
   \RightLabel{By def.}
-  \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
-  \RightLabel{\thmunshunt}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
+  \RightLabel{lem-unshunt}
   \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
@@
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n) ∧ \unshunt(φ₁ ⇒ φ₃, n)$}
+\AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n) ∧ unshunt(φ₁ ⇒ φ₃, n)$}
 \RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n)$}
+\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n)$}
 \RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂, n-1)$}
-\RightLabel{\thmunshunt}
+\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n-1)$}
+\RightLabel{lem-unshunt}
 \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$,}
@@
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₂) ∧ \unshunt(φ₁ ⇒ φ₃)$}
+\AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂) ∧ unshunt(φ₁ ⇒ φ₃)$}
 \RightLabel{∧-proj₂}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₃, n)$}
+\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n)$}
 \RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ φ₃, n-1)$}
-\RightLabel{\thmunshunt}
+\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n-1)$}
+\RightLabel{lem-unshunt}
 \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$,}
@@
 \begin{cases}
-\unshunt(\mysplit(φ₁)) &\text{if }φ ≡ φ₁ ∧ φ₂\\
-∧\ \unshunt(φ₁ ⇒ \mysplit(φ₂)), &\\[2.5mm]
-\unshunt(¬ φ₁ ⇒ \mysplit(φ₂)),
+unshunt(\mysplit(φ₁)) &\text{if }φ ≡ φ₁ ∧ φ₂\\
+∧\ unshunt(φ₁ ⇒ \mysplit(φ₂)), &\\[2.5mm]
+unshunt(¬ φ₁ ⇒ \mysplit(φ₂)),
   & \text{if }φ ≡ φ₁ ∨ φ₂\\[2.5mm]
-\unshunt(φ₁ ⇒ \mysplit(φ₂)),
+unshunt(φ₁ ⇒ \mysplit(φ₂)),
   & \text{if }φ ≡ φ₁ ⇒ φ₂\\[2.5mm]
-\unshunt(φ₁ ⇒ \mysplit(φ₂))
+unshunt(φ₁ ⇒ \mysplit(φ₂))
   & \text{if }φ ≡ φ₁ ⇔ φ₂\\
-∧\ \unshunt(φ₂ ⇒ \mysplit(φ₁)),
+∧\ unshunt(φ₂ ⇒ \mysplit(φ₁)),
   &\\[2.5mm]
-\unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
+unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
   & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂)\\[2.5mm]
-\unshunt(\mysplit(¬ φ₁))
+unshunt(\mysplit(¬ φ₁))
   & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
-∧\ \unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂)),
+∧\ unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂)),
   &\\[2.5mm]
-\unshunt(\mysplit(φ₁))
+unshunt(\mysplit(φ₁))
   & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
-∧\ \unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
+∧\ unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
   &\\[2.5mm]
-\unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
+unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
   & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
-∧\ \unshunt(¬ φ₂ ⇒ \mysplit(φ₁)),
+∧\ unshunt(¬ φ₂ ⇒ \mysplit(φ₁)),
   &\\[2.5mm]
-\unshunt(\mysplit(φ₁)),
+unshunt(\mysplit(φ₁)),
   & \text{if }φ ≡ ¬ ¬ φ₁\\
@@
   \RightLabel{By def.}
-  \UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
   \RightLabel{∧-proj₁}
-  \UnaryInfC{$Γ ⊢ \unshunt(φ₁)$}
-  \RightLabel{\thmunshunt}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁)$}
+  \RightLabel{lem-unshunt}
   \UnaryInfC{$Γ ⊢ φ₁$.}
@@
   \UnaryInfC{Γ ⊢ φ₁}
-
   \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
   \RightLabel{By def.}
-  \UnaryInfC{$Γ ⊢ \unshunt(φ₁) ∧ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
   \RightLabel{$∧$-proj$₂$}
-  \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{\thmunshunt}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \RightLabel{lem-unshunt}
   \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
@@
   \RightLabel{By def.}
-  \UnaryInfC{$Γ ⊢ \unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{\thmunshunt}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \RightLabel{lem-unshunt}
   \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
@@
 \RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
+\UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
 \RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁)$}
-\RightLabel{\thmunshunt}
+\UnaryInfC{$Γ ⊢ unshunt(¬ φ₁)$}
+\RightLabel{lem-unshunt}
 \UnaryInfC{$Γ ⊢ ¬ φ₁$,}
@@
   \RightLabel{By def.}
-  \UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁) ∧ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
   \RightLabel{∧-proj₂}
-  \UnaryInfC{$Γ ⊢ \unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{\thmunshunt}
+  \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \RightLabel{lem-unshunt}
   \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂,n-1)$}
@@
   \begin{bprooftree}
-  \AxiomC{Γ ⊢ q}
+  \AxiomC{$Γ ⊢ q$}
   \RightLabel{∨-intro₂}
-  \UnaryInfC{Γ ⊢ p ∨ q}
+  \UnaryInfC{$Γ ⊢ p ∨ q$}
   \RightLabel{∨-intro₁}
-  \UnaryInfC{Γ ⊢ (p ∨ q) ∨ r}
-
-  \AxiomC{Γ ⊢ p}
+  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
+
+  \AxiomC{$Γ ⊢ p$}
   \RightLabel{∨-intro₁}
-  \UnaryInfC{Γ ⊢ p ∨ q}
+  \UnaryInfC{$Γ ⊢ p ∨ q$}
   \RightLabel{∨-intro₁}
-  \UnaryInfC{Γ ⊢ (p ∨ q) ∨ r}
+  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
 
   \RightLabel{∨-elim}
-  \BinaryInfC{Γ, q ∨ p ⊢ (p ∨ q) ∨ r}
-  \end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{Γ ⊢ r}
+  \BinaryInfC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
+  \end{bprooftree}
+\end{equation*}
+
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⊢ r$}
   \RightLabel{∨-intro₂}
-  \UnaryInfC{Γ ⊢ (p ∨ q) ∨ r}
-
-  \AxiomC{Γ, q ∨ p ⊢ (p ∨ q) ∨ r}
+  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
+
+  \AxiomC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
 
   \RightLabel{∨-elim}
-  \BinaryInfC{Γ, r ∨ (q ∨ p) ⊢ (p ∨ q) ∨ r}
+  \BinaryInfC{$Γ, r ∨ (q ∨ p) ⊢ (p ∨ q) ∨ r$}
 
   \RightLabel{⇒-intro}
-  \UnaryInfC{Γ ⊢ r ∨ (q ∨ p) ⇒ (p ∨ q) ∨ r}
+  \UnaryInfC{$Γ ⊢ r ∨ (q ∨ p) ⇒ (p ∨ q) ∨ r$}
 
@@
 if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
-Then, we define the $rm_{∨}$ function to remove in a disjunction φ, those propositions ψ repeated in the formula. The formula $φ$ must be a right-associative disjunction.
+Then, we define the $rm_{∨}$ function to remove in a right-associative disjunction φ, those propositions ψ repeated in the formula.
 
@@
 
-Now, we have removed redundancies in the disjunctions, we move forward and we remove redundancies at the level of the conjunction of the CNFs by applying the $rm_{∧}$ function, we remove conjunct repeated in the formula.
+Now, we have removed redundancies in the disjunctions, we move forward and we remove redundancies at the level of the conjunction of the CNFs by applying the $rm_{∧}$ function.
 We define $ψ ∈_{∧} φ$ similar as we described above for disjunction.
@@
 % --------------------------------------------------------------------
+\begin{lemma}[lem-rmPEM$_{∨}$]
+  \label{lem:lem-rmPEM-or}
+  \begin{align*}
+  \label{eq:rmPEM-or}
+    \begin{split}
+    rmPEM_{∨}(φ) =
+      \begin{cases}
+        ⊤, &\text{if }φ ≡ ¬ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
+        ⊤, &\text{if}φ ≡ ¬ φ₁ ∨ φ₂,\ rmPEM_{∨}(φ₂) ≡ ⊤\\
+        ¬ φ₁ ∨ rmPEM_{∨}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∨ φ₂\\
+        ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ ¬φ₁ ∈_{∨} φ₂ \\
+        ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ rmPEM_{∨}(φ₂) ≡ ⊤\\
+        φ₁ ∨ rmPEM_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
+        φ, &\text{otherwise.}
+      \end{cases}
+    \end{split}
+  \end{align*}
+\end{lemma}
+
+\begin{lemma}[lem-rmPEM$_{∧∨}$]
+  \label{lem:lem-rmPEM-and-or}
+  \begin{equation*}
+    \label{eq:rmPEM-and-or}
+    rmPEM_{∧∨}(φ) =
+    \begin{cases}
+      rmPEM_{∨}(φ₁) ∧ rmPEM_{∨∧}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
+      rmPEM_{∨}(φ), &\text{otherwise.}
+    \end{cases}
+  \end{equation*}
+\end{lemma}
+
+\begin{lemma}[lem-rmBot$_{∧}$]
+  \label{lem:lem-rmbot-and}
+   $Γ ⊢ φ$ then $Γ ⊢ rmBot_{∧}(φ)$, where,
+  \begin{equation*}
+    \label{eq:rmBot-and}
+    rmBot_{∧}(φ) =
+    \begin{cases}
+      ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
+      ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ rmBot_{∧}(φ₂) ≡ ⊥\\
+      ¬ φ₁ ∧ rmBot_{∧}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∧ φ₂\\
+      ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
+      ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ rmBot_{∧}(φ₂) ≡ ⊥\\
+      φ₁ ∧ rmBot_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
+      φ, &\text{otherwise.}
+    \end{cases}
+  \end{equation*}
+\end{lemma}
+
+\begin{lemma}[lem-canon]
+  \label{lem:lem-canon}
+  \begin{align*}
+  \begin{split}
+  &canon(φ) =\\
+  &\hspace{3mm}
+  \begin{cases}
+      canon(φⱼ), &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊤, i,j = 1,2, i≠j\\
+     ⊥, &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊥, i = 1,2\\
+     canon(φ₁) ∧ canon(φ₂), &\text{if } φ ≡ φ₁ ∧ φ₂\\
+     ⊤, &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊤, i = 1,2\\
+     canon(φⱼ), &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊥,  i,j = 1,2, i≠j\\
+     canon(φ₁) ∨ canon(φ₂), &\text{if } φ ≡ φ₁ ∨ φ₂\\
+     φ &\text{otherwise.}
+    \end{cases}
+  \end{split}
+  \end{align*}
+\end{lemma}
+
+\begin{theorem}[thm-canonicalize] % (fold)
+  \label{thm:thm-canonicalize}
+  $Γ ⊢ φ$ then $Γ ⊢ canonicalize(φ)$, where,
+  \begin{equation*}
+    canonicalize =
+     canon ∘ rmBot_{∧} ∘ rmPEM_{∧∨} ∘ redun ∘ rconj ∘ cnf.
+  \end{equation*}
+\end{theorem}
+
+The \canonicalize rule acts in \Metis' \TSTP derivations in three main cases. First, introducing the
+negation of a subgoal. Second, to simplify an intermediate derivation.
+Third, introducing an axiom or a definition of the.
+To justify the two first cases, we use the Theorem~\ref{thm:thm-canonicalize}. For the last case, we use the Lemma~\ref{lem:lem-nnf}.
+
+% -------------------------------------------------------------------
+\subsubsection{Simplify}
+\label{sssec:simplify}
+
+% subsubsection simplify (end)
+% -------------------------------------------------------------------
 

### 2017-10-02 paper/sections/proof-reconstruction.tex
[ paper ] making some notes.

@@
 proof using a tree data structure (see the properties
-of this tree in Subsection \ref{ssec:metis-proofs}).
+of this tree in Section~\ref{ssec:metis-proofs}).
 We perform an analysis of the proof-tree removing redundancies,
@@
 a structural recursion. Therefore, we have reformulated Def.~\ref{eq:split-definition} to solve such a issue following the technique
-described in Subsection~\ref{ssec:structural-recursion}.
+described in Section~\ref{ssec:structural-recursion}.
 Here and below, we refer to $split$ as the function after applying
@@
 but also of the inner disjunctions inside the propositions involved.
+\improvement{Make clear: we are dealing with CNFs, and prove equivalence between two formulas is equivalent to show two trees are  isomorphic.
+And that problem is NP-hard, and for that, we mostly do brute force.}
 
@@
 
-The following function, $build_{∨} : \Prop → \Prop → \Prop$ in Eq.~\ref{eq:build-or}, intends to construct a disjunction from another disjunction, specifically, we want to rearrange the order of the disjuncts in a target disjunction.
-This approach for rearrangement is inspired on the treatment for nested
-disjunctions mainly described in \citeauthor{bohme2010}~\cite{bohme2010}.
+The following function, $build_{∨} : \Prop → \Prop → \Prop$ in Eq.~\ref{eq:build-or}, intends to construct a disjunction from another disjunction, specifically, we want to rearrange the disjuncts in the source formula to match with the target disjunction for syntactic
+equivalence.
 
@@
 
-Now, with a right-associative proposition,
-$sbuild_{∨}: \Prop → \Prop → \Prop$ in
+Now, with a right-associative disjunction by applying $rdisj$ function to
+a proposition $φ$, $sbuild_{∨}: \Prop → \Prop → \Prop$ in
 Eq.~\ref{eq:strong-build-or-definition} aims to construct the disjunction
-ψ by using each of disjuncts from the proposition φ. This approach to
-build a disjunction from another is inspired on the description
+ψ by using each of its disjuncts from the proposition φ. This approach to
+build a disjunction from another is inspired on the description in
 \citeauthor{bohme2010}~\cite{bohme2010} to prove equality between nested
-disjunctions.
+disjunctions. \change{Make clear this, It's not clear the difference with build-or and sbuild-or.}
 
@@
   $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$, where,
+  \improvement{The first case is not implemented in Agda}
   \begin{align*}
@@
     \begin{cases}
+      ψ, &\text{if }φ ≡ ψ\\
       ψ, &\text{if }reorder_{∨}(φ, ψ) ≡ ψ\\
@@
 
-The \resolve rule is a generalization version for resolution in propositional logic since the formulas are not shaped always as the theorem expect (see Fig.~\ref{fig:metis-inferences}).
+The \resolve rule is a generalization version for resolution in propositional logic since the formulas are not shaped always as the aforementioned theorem expects (see Fig.~\ref{fig:metis-inferences}).
 
@@
 \label{sssec:normal_forms}
-
+\change{Here lacks of an introduction!}
 A negative normal form for the formula φ is one in which negations
@@
       \begin{split}
-      dist_{∨} =
+      dist_{∨}(φ) =
         \begin{cases}
@@
       \begin{split}
-      dist =
+      dist(φ) =
         \begin{cases}
@@
 
-\begin{proof} Sketch. Case when $φ ≡ φ₁ ∨ φ₂$.\\
+\begin{sketchproof}
+Case when $φ ≡ φ₁ ∨ φ₂$.\\
 For $i = 1, 2$,
@@
 $Γ, φ₁ ∨ φ₂ ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$, and the lemma follows.
-\end{proof}
+\end{sketchproof}
 
@@
 
+\improvement{We need here a text, or a comment about what
+is going next.}
+
 % subsection normalization (end)
@@
   \begin{cases}
-      canon(φⱼ), &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊤, i,j = 1,2, i≠j\\
+      canon(φⱼ), &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊤,\\
+                 &\text{for same } i,j = 1,2, i≠j\\
      ⊥, &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊥, i = 1,2\\
@@
      ⊤, &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊤, i = 1,2\\
-     canon(φⱼ), &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊥,  i,j = 1,2, i≠j\\
+     canon(φⱼ), &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊥,\\
+                &\text{for same } i,j = 1,2, i≠j\\
      canon(φ₁) ∨ canon(φ₂), &\text{if } φ ≡ φ₁ ∨ φ₂\\
-     φ &\text{otherwise.}
+     φ, &\text{otherwise.}
     \end{cases}
@@
 
+The \simplify rule is the application of the the lemma showed above,
+but also the following lemmas that intend to reduce a list of derivations,
+a conjunction of their formulas into a one smaller.
+
+\improvement{Missing theorems here.}
+
 % subsubsection simplify (end)

### 2017-10-04 paper/sections/metis-language-and-proofs.tex

@@
   \AxiomC{}
-  \RightLabel{\footnotesize negate}
+  \RightLabel{negate}
   \UnaryInfC{$\neg p$}
-  \RightLabel{\footnotesize strip}
+  \RightLabel{strip}
   \UnaryInfC{$\neg p$}
   \AxiomC{}
-  \RightLabel{\footnotesize axiom}
+  \RightLabel{axiom}
   \UnaryInfC{$p$}
-  \RightLabel{\footnotesize canonicalize}
+  \RightLabel{canonicalize}
   \UnaryInfC{$p$}
-  \RightLabel{\footnotesize simplify}
+  \RightLabel{simplify}
   \BinaryInfC{$⊥$}
-  \RightLabel{\footnotesize canonicalize}
+  \RightLabel{canonicalize}
   \UnaryInfC{$⊥$}
@@
 disjoint cases. This process produces a list of new subgoals, the
-conjunction of these subgoals implies the goal as we show later in
-Subsection~\ref{ssec:emulating-inferences}. Then, a proof of the
+conjunction of these subgoals implies the goal. Then, a proof of the
 goal becomes in smaller proofs, one refutation for each subgoal.
 These subgoals are introduced in the \TSTP derivation with the \strip
-inference rule.
+inference rule. We refer the reader to see Theorem~\ref{thm:thm-strip}.
 
@@
 \Metis performs this transformation using its criteria.
+We refer the reader to see Theorem~\ref{thm:thm-clausify}.
+
 \improvement{We should mention that it was indeed a problem for the
@@
 conjunction and disjunction connectives).
+We refer the reader to see Section~\ref{sssec:normalization} and the
+lemmas and theorems described there.
 
@@
 for the resolve inference).
+We refer the reader to see Theorem~\ref{thm:thm-resolve}.
 
@@
 following \TSTP derivation shows.
+We refer the reader to see Theorem~\ref{thm:thm-conjunct}.
 
@@
 the negation of its subgoal. The \negate rule
-introduces the negation of a subgoal that results
-after applies the \strip inference to the goal.
+assumes the negation of a given subgoal. This rules always
+appears after applies the \strip inference to the goal.
 
@@
 theorem of the \resolve rule.
+We refer the reader to see Section~\ref{sssec:simplify}.
 

### 2017-10-04 paper/sections/preliminaries.tex
[ paper ] minor changes.
[ paper ] preliminaries reviewed.

@@
 propositional formula.
-Then, $ϕ_i \in \Prop$ for all $i \in \mathbb{N}$.
+%Then, $ϕ_i \in \Prop$ for all $i \in \mathbb{N}$.
+$⊥, ⊤ \in \Prop$.
 If $φ, ψ\in \Prop$, then $(φ\ \square\ ψ) \in \Prop$,
-where $(φ\ \square\ ψ)$ stands for a proposition that use a
-binary connective in the place for the $\square$ symbol.
+where $(φ\ \square\ ψ)$ stands for a proposition that use the $\square$ symbol as one of the binary connectives mentioned above.
 If $φ \in \Prop$, then $(¬ φ) \in \Prop$.
-Finally, $⊥, ⊤ \in \Prop$.
 
@@
 the application of some deduction steps. Such a deduction step has
-the form of a set of propositional \emph{premises} that conclude the
-result: one or more propositions. As we show in the following
+the form of a set of propositional \emph{premises} that conclude
+one or more proposition as the conclusion.
+
+As we show in the following
 figure, the premises are always above the line, the conclusions
 are below it, and the name of the inference or the theorem used is
-on the right the line. As a notation convention, if the name of a
-rule used in the derivation step is typed using verbatim, that
-means, it is available in our implementation (see for instance,
-theorems in \cite{AgdaProp}) used in some derivations latter.
+on the left or on the right of the line.
+As a notation convention, if the name of a rule used in the derivation step is typed using verbatim font face, it means, the inference rule belongs to our implementation~\cite{AgdaProp, AgdaMetis} in the Proof Assistant of a inference rule presented
+with a similar name.
 
-\[
+\begin{equation*}
 \label{eq:derivation}
 \begin{bprooftree}
-\AxiomC{φ}
-\AxiomC{ψ}
-\BinaryInfC{φ ∧ ψ}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-\AxiomC{[¬ φ]}
-\noLine
-\UnaryInfC{$\vdots$}
-\noLine
-\UnaryInfC{⊥}
-\RightLabel{\abbre{RAA}}
-\UnaryInfC{φ}
+  \AxiomC{$φ$}
+  \AxiomC{$ψ$}
+  \RightLabel{∧-intro}
+  \BinaryInfC{$φ ∧ ψ$.}
 \end{bprooftree}
-\]
+% \qquad
+% \begin{bprooftree}
+%   \AxiomC{$[¬ φ]$}
+%   \noLine
+%   \UnaryInfC{$\vdots$}
+%   \noLine
+%   \UnaryInfC{$⊥$}
+%   \RightLabel{\abbre{RAA}}
+%   \UnaryInfC{φ}
+% \end{bprooftree}
+\end{equation*}
 
@@
 
+\begin{equation*}
 \label{eq:PEM-RAA}
-\[
 \begin{bprooftree}
-\AxiomC{\ }
-\RightLabel{\scriptsize\tt PEM}
-\UnaryInfC{Γ ⊢ φ ∨ ¬ φ}
+\AxiomC{}
+\RightLabel{PEM}
+\UnaryInfC{$Γ ⊢ φ ∨ ¬ φ$,}
+\end{bprooftree}\qquad
+\begin{bprooftree}
+\AxiomC{$Γ, ¬ φ ⊢ ⊥$}
+\RightLabel{RAA}
+\UnaryInfC{$Γ ⊢ φ$.}
 \end{bprooftree}
-\qquad
-\begin{bprooftree}
-\AxiomC{Γ, ¬ φ ⊢ ⊥}
-\RightLabel{\scriptsize\tt RAA}
-\UnaryInfC{Γ ⊢ φ}
-\end{bprooftree}
-\qquad
-\]
+\end{equation*}
 
 \emph{Natural Deductions.}
-The natural deduction designed by Gentzen \improvement{Cite the work
-by Gentzen.} defines a formal system for derivations that uses a set
+The natural deduction designed by Gerhard Gentzen in 1930s defines a formal system for derivations that uses a set
 of inference rules as the only way to obtain a conclusion.
 We use this system to refer to formal proofs as natural deduction
-proofs and conversely, in the latter.
-We define our inference rules for \CPL in the Fig.
-\ref{fig:CPL-inference-rules}. These rules give us the complete
+proofs and conversely.
+We define the \CPL formal system in the
+Fig.~\ref{fig:CPL-inference-rules}. The rules described in the aforementioned figure give us the complete
 meaning of the connectives; how to introduce them and
 how they can be remove them in the conclusion side of the theorems.
-\change{the size of the text.}
 
@@
 the leaves in the tree become the premises, not all necessary
-canceled (see a better discussion on cancellation of hypotheses in
-\cite{VanDalen1994}).
+canceled (see a better discussion about canceling  hypotheses in proof trees in Section 2.4 in \citeauthor{VanDalen1994}~\cite{VanDalen1994}).
 

### 2017-10-04 paper/sections/proof-reconstruction.tex
[ paper ] preliminaries reviewed.

@@
 by structural recursion in its second argument in
-Eq.~\ref{eq:unshunt-structured}.
+Eq.~(\ref{eq:unshunt-structured}).
 
@@
 As we mentioned above, the natural number in the second argument of the
-function used in Eq.~\ref{eq:unshunt-structured} stands for a complexity
+function used in Eq.~(\ref{eq:unshunt-structured}) stands for a complexity
 measure of the function, in this case $unshunt_{1}$ function.
@@
 Recall, we want to maintain the same outputs as the original unshunt
-does in Eq.~\ref{eq:unshunt-definition} and the complexity measure of it,
+does in Eq.~(\ref{eq:unshunt-definition}) and the complexity measure of it,
 is a bound for the number of times this function can call itself.
@@
 $unshunt_{cm}: \Prop → \NN$ for our $unshunt_{1}$ function presented in
-Eq.~\ref{eq:unshunt-rank-definition}.
+Eq.~(\ref{eq:unshunt-rank-definition}).
 
@@
 Finally, the curated version of $unshunt_{0}$ function is presented
-in Eq.~\ref{eq:unshunt-fixed}.
+in Eq.~(\ref{eq:unshunt-fixed}).
 
@@
 In the following, we show how Theorem.~\ref{thm:thm-strip} proves the correctness of the process mentioned above.
-But first, let prove some lemmas for $unshunt$ function presented in Eq.~\ref{eq:unshunt-fixed},
-and $split$ function from the definition in Eq.~\ref{eq:split-definition}.
+But first, let prove some lemmas for $unshunt$ function presented in Eq.~(\ref{eq:unshunt-fixed}),
+and $split$ function from the definition in Eq.~(\ref{eq:split-definition}).
 
@@
 \begin{proof} Use induction on the cases defined by the outcome of the
-$unshunt$ function in Eq.~\ref{eq:unshunt-structured}.
+$unshunt$ function in Eq.~(\ref{eq:unshunt-structured}).
 When $n = 0$, by definition, $Γ ⊢ φ$.
@@
 Now, let us consider the $split$ function presented in
-Eq.~\ref{eq:split-definition} that yields a conjunction of subgoals from a proposition, the goal in \Metis.
+Eq.~(\ref{eq:split-definition}) that yields a conjunction of subgoals from a proposition, the goal in \Metis.
 
@@
 \begin{proof} We now proceed by induction on the structure of the
-formula φ in the definition of Eq.~\ref{eq:split-definition}.
+formula φ in the definition of Eq.~(\ref{eq:split-definition}).
 For a complete proof, we refer the reader to~\cite{AgdaMetis}.\\[3mm]
@@
 When φ ≡ ψ, from $Γ ⊢ conjunct(φ, ψ)$ by normalization, we get $Γ ⊢ ψ$.
-By using $subst$ theorem Eq.~\ref{eq:substitution-theorem}, we get the desire conclusion. If the proposition φ is a conjunction, and $ψ ≡ conjunct(φ_{i}, ψ)$
+By using $subst$ theorem Eq.~(\ref{eq:substitution-theorem}), we get the desire conclusion. If the proposition φ is a conjunction, and $ψ ≡ conjunct(φ_{i}, ψ)$
 for some $i = 1,\ 2$, then,
@@
 
-First, we define the $rdisj$ function in Eq.~\ref{eq:rdisj-def} to convert a disjunction to be a right-associative disjunction, and following
+First, we define the $rdisj$ function in Eq.~(\ref{eq:rdisj-def}) to convert a disjunction to be a right-associative disjunction, and following
 a similar approach we define the $rconj$ function for conjunctions.
@@
 
-The following function, $build_{∨} : \Prop → \Prop → \Prop$ in Eq.~\ref{eq:build-or}, intends to construct a disjunction from another disjunction, specifically, we want to rearrange the disjuncts in the source formula to match with the target disjunction for syntactic
+The following function, $build_{∨} : \Prop → \Prop → \Prop$ in Eq.~(\ref{eq:build-or}), intends to construct a disjunction from another disjunction, specifically, we want to rearrange the disjuncts in the source formula to match with the target disjunction for syntactic
 equivalence.
@@
 
-The function $factor : \Prop → \Prop$  in Eq.~\ref{eq:factor-definition} is intended to work only for right-associative disjunctions, and reduces a disjunction of the same disjunct (e.g., $factor(φ ∨ (φ ∨ \cdots)) \mapsto\ φ$).
+The function $factor : \Prop → \Prop$  in Eq.~(\ref{eq:factor-definition}) is intended to work only for right-associative disjunctions, and reduces a disjunction of the same disjunct (e.g., $factor(φ ∨ (φ ∨ \cdots)) \mapsto\ φ$).
 
@@
 a proposition $φ$, $sbuild_{∨}: \Prop → \Prop → \Prop$ in
-Eq.~\ref{eq:strong-build-or-definition} aims to construct the disjunction
+Eq.~(\ref{eq:strong-build-or-definition}) aims to construct the disjunction
 ψ by using each of its disjuncts from the proposition φ. This approach to
@@
 \begin{theorem}[thm-clausify]
-\label{thm:thm_clausify}
+\label{thm:thm-clausify}
   $Γ ⊢ φ$ and $ψ \in\Prop$ then $Γ ⊢ clausify(φ, ψ)$, where,
@@
 
-\begin{proof} When $φ ≡ ψ$, we use the $subs$ theorem Eq.~\ref{eq:substitution-theorem}. Otherwise, we use Theorem \ref{thm:thm-reorder-and-or} and Theorem \ref{thm:thm-cnf}.
+\begin{proof} When $φ ≡ ψ$, we use the $subs$ theorem Eq.~(\ref{eq:substitution-theorem}). Otherwise, we use Theorem \ref{thm:thm-reorder-and-or} and Theorem \ref{thm:thm-cnf}.
 \end{proof}
@@
 
-Finally, we remove redundancies in a proposition assuming that it is given in conjunctive normal form and right-associative, by composing the functions described above in the Eq.~\ref{eq:redun-ast}
+Finally, we remove redundancies in a proposition assuming that it is given in conjunctive normal form and right-associative, by composing the functions described above in the Eq.~(\ref{eq:redun-ast})
 for the function $redun^{*}$.

### 2017-10-04 paper/sections/metis-language-and-proofs.tex
[ ref.bib ] added a new one ref.

@@
 In this paper, we ported a subset of the \Metis' inference rules to
-\Agda, the propositional fragmented without equality.
-That allows us to justify step-by-step the proofs delivered in
+\Agda, the propositional fragmented without equality, that allows us to justify step-by-step the proofs delivered in
 \TSTP format generated by the prover \Metis.
@@
 
-This lack of the \Metis' documentation is an important matter for
-us in the proof-reconstruction and certainty for other implementors
+This lack of the \Metis' documentation represents one of the first barriers to build proof-reconstruction tools since some inference rules
+like \canonicalize or \simplify summarize many essential steps to deduce the conclusion, making them hard to justify and emulate
 (see a comment related on the presenting of \name{Sledgehammer}
-in \cite{paulson2007source} and \cite{Farber2015}). We faced
-the ambiguity and lack of clearness of some rules like \canonicalize
-or \simplify.
-For example, we believe by applying these last
-inferences, \Metis summarized many essential steps to deduce a
-formula from a list of formulas.
-\improvement{Add an example here to show a deduction where \Metis do
-a lot between two steps.}
-That inference's behavior is a drawback since, our approach
-to reconstruct proofs needs take into account any assumption or
-consideration as ordering for literals, application of
-simplification theorems, reductions, among other valid
-transformations.
+in \citeauthor{paulson2007source}~\cite{paulson2007source} and \citeauthor{Farber2015}~\cite{Farber2015}).
 
-\unsure{Should I give an Example?}
+Henceforth, one of our main purposes with this document consists of
+giving a response to these rules looking at the \Metis' source code but also reviewing a representative set of solutions generated by
+\Metis for the \CPL collection of \TPTP problems~\cite{Prieto-Cubides2017} including some problem from the \Metis repository itself.
 
-In this part, our main purpose consists of giving a response to
-these rules looking at the \Metis' source code while inspecting a
-representative set of solutions of \CPL problems
-\cite{Prieto-Cubides2017} generated by \Metis.
-This is an attempt to fulfill the \Metis's documentation, by
-describing each rule from our perspective. Later on, in Section
-\ref{sec:proof-reconstruction}, we present a formal description of
-such rules.
+In the following, we briefly describe each \Metis' rule from our perspective, but we present a formal description for each rule in Section \ref{sec:proof-reconstruction}.
 
@@
 \textit{Clausification.} The \clausify rule transforms a
-propositional formula in clausal normal form or \CNF, a conjunction
-of clauses. Where a clause is the disjunction of zero or more
-literals and a literal is an atom (positive literal) or a negation
-of an atom (negative literal). This conversion is not unique, and
-\Metis performs this transformation using its criteria.
+propositional formula in clausal normal form, a conjunction
+of clauses. Where a \emph{clause} is the disjunction of zero or more
+literals and a \emph{literal} is an atom (positive literal) or a
+negation of an atom (negative literal).
+Be aware this kind of conversion between one formula to its clausal normal form is not unique, and \Metis has a customized approach to perform that transformation.
 We refer the reader to see Theorem~\ref{thm:thm-clausify}.
 
-\improvement{We should mention that it was indeed a problem for the
-proof-reconstruction? and refer the section next?}
+\vskip 2mm
 
@@
 
-\textit{Normalization.} \Metis uses the \canonicalize rule to
+\textit{Normalization.}
+Each application of the clausify rule described above is preceded by
+\canonicalize rule. Both rules aim to perform a common task for
+automatic theorem provers, clausification, mainly described on paper
+by \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.
+
+\Metis uses the \canonicalize rule to
 normalize a propositional formula that comes from an axiom or a
@@
 conjunction and disjunction connectives).
-We refer the reader to see Section~\ref{sssec:normalization} and the
+We refer the reader to see Section~\ref{sssec:normalization} for the
 lemmas and theorems described there.

### 2017-10-04 paper/fix-references.sh

@@ -2,5 +2,5 @@
 
 sed -i -r "/(url|doi)/ s/\{.?(.)\}/\1/g" ref-mendeley.bib
 sed -i -r "s/journaltitle/journal     /g" ref-mendeley.bib
+sed -i -r "s/@inbook/@incollection/g" ref-mendeley.bib
 sed -i -r "/file/d" ref-mendeley.bib
-

### 2017-10-04 paper/sections/metis-language-and-proofs.tex
[ paper ] improved proof rules descriptions.

@@
 
-\textit{Normalization.}
-Each application of the clausify rule described above is preceded by
-\canonicalize rule. Both rules aim to perform a common task for
-automatic theorem provers, clausification, mainly described on paper
-by \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.
+\textit{Normalization.} We observed \clausify rule described above is preceded by \canonicalize rule when \Metis introduces at some point of the derivation an axiom or a definition of the problem.
+In that case, both rules aim to perform a common task for
+automatic theorem provers, Clausification, mainly described on paper
+by \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}. When the
+aforementioned case does not occur we argue \canonicalize transforms
+proposition into another one that mainly matches with its negative
+normal form, its conjunctive normal form or its disjunctive normal
+form. In addition, \canonicalize could also perform other tasks like
+removing logic constants (⊥, ⊤), definitions, and tautologies, or even reorder both conjunctions and disjunctions of the proposition.
 
-\Metis uses the \canonicalize rule to
-normalize a propositional formula that comes from an axiom or a
-definition. It often converts each expression in one of its normal
-form: the conjunctive normal form, the negative normal form or the
-disjunctive normal form. Next, this rule simplifies the formula
-with some definitions, applying recursively on the structure's
-formula conjunctions and disjunctions simplifications to remove
-tautologies (see Fig.~\ref{fig:conjunctive-disjunctive-simpl} for a
-list of these theorems. We assume the commutative property for the
-conjunction and disjunction connectives).
-We refer the reader to see Section~\ref{sssec:normalization} for the
-lemmas and theorems described there.
+For instance, assuming the commutative properties for both
+connectives, conjunction and disjunction, and using the theorems
+in Fig.~\ref{fig:conjunctive-disjunctive-simpl}, \canonicalize could
+use them to reduce a proposition to a one smaller by applying
+recursively on the structure of the formula those theorems.
+We refer the reader to see Section~\ref{sssec:normalization} to continue our approach to emulate this rule.
 

### 2017-10-07 paper/sections/acknowledgements.tex
[ paper ] appendix added.
Paper (#36)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

*

@@
-% -*- root: main.tex -*-
-\documentclass[main.tex]{subfiles}
+\documentclass[../main.tex]{subfiles}
 \begin{document}
@@
 We thank Joe Leslie-Hurd for his support with \Metis prover. We also
-acknowledge the work carried out by Alejandro G\'omez-Londo\~no~
-\cite{Gomez-Londono2015} used as the basis code for our \TSTP
+acknowledge the work carried out by Alejandro G\'omez-Londo\~no~\cite{Gomez-Londono2015} used as the basis code for our \TSTP
 parsing module.
-\improvement{We should consider thank Kanso and Anton, to provide us
-their thesis, discussion, and source code to compare with our work?}
+% \improvement{We should consider thank Kanso and Anton, to provide
+% us their thesis, discussion, and source code to compare with our
+% work?}
 

### 2017-10-07 paper/sections/metis-language-and-proofs.tex
Paper (#36)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

* [ paper ] minor changes.

@@
 These subgoals are introduced in the \TSTP derivation with the \strip
-inference rule. We refer the reader to see Theorem~\ref{thm:thm-strip}.
+inference rule. We refer the reader to see Section~\ref{sssec:splitting-goal} for the formalization of \strip rule.
 
@@
 Be aware this kind of conversion between one formula to its clausal normal form is not unique, and \Metis has a customized approach to perform that transformation.
-We refer the reader to see Theorem~\ref{thm:thm-clausify}.
+We refer the reader to see Section~\ref{sssec:clausification} for the formalization of \clausify rule.
 
@@
 % ...................................................................
+\vskip 2mm
 
-\textit{Resolution.} The \resolve rule is the resolution theorem
-showed in Fig.~\ref{fig:metis-inferences}. For its application, we
-need the positive literal for resolution and two derivations to
-deduce the \emph{resolvent}. The positive literal $p$ must occur in
-the formula from the first derivation, and the negative literal must
-occur in the formula from the second derivation (this follows the
-same pattern in \Metis' logic core in Fig.~\ref{fig:metis-inferences}
-for the resolve inference).
-We refer the reader to see Theorem~\ref{thm:thm-resolve}.
+\textit{Resolution.} The \resolve rule incorporates  the resolution theorem showed in Fig.~\ref{fig:metis-inferences} with
+three arguments: a positive literal $l$ to apply the resolution theorem, and two derivations, $\mathcal{D}₁$ and $\mathcal{D}₂$.
+
+The positive literal $l$ must occur in
+the formula from the first derivation $\mathcal{D}₁$, and the
+negative literal must occur in the formula from the second derivation $\mathcal{D}₂$ (see the pattern in \Metis' logic core for the \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}).
+We refer the reader to see Section~\ref{sssec:resolve} for the formalization of the \resolve rule.
 
@@
 following \TSTP derivation shows.
-We refer the reader to see Theorem~\ref{thm:thm-conjunct}.
+We refer the reader to see Theorem~\ref{thm:thm-conjunct}
+in Section~\ref{sssec:splitting-a-conjunct} for its formalization.
 

### 2017-10-07 paper/chars.sh

@@ -1,19 +1,0 @@
-#!/bin/sh
-
-sed -i 's/phat/$\\hat p$/g' main.tex
-sed -i 's/ᵢ/$_i$/g' main.tex
-sed -i 's/≤/$\\leq$/g' main.tex
-sed -i 's/ₙ/$_n$/g' main.tex
-sed -i 's/ρ/$\\rho$/g' main.tex
-sed -i 's/ψ/$\\psi$/g' main.tex
-sed -i 's/σ/$\\sigma$/g' main.tex
-sed -i 's/Γ/$\\Gamma$/g' main.tex
-sed -i 's/η/$\\eta$/g' main.tex
-sed -i 's/ᶜ/$\^c$/g' main.tex
-sed -i 's/φ/$\\phi$/g' main.tex
-sed -i 's/⊨/$\\vDash$/g' main.tex
-sed -i 's/◾/$\\scriptscriptstyle\\blacksquare$/g' main.tex
-sed -i 's/⇛/$\\Rrightarrow$/g' main.tex
-# sed -i 's/\\ensuremath{\\neg }/\\ensuremath{\\Varid{neg}}/g' main.tex
-# sed -i 's/\\ensuremath{\\neg}/\\ensuremath{\\Varid{neg}}/g' main.tex
-# sed -i 's/\\neg/\\Varid{neg}/g' main.tex

### 2017-10-07 paper/fix-references.sh

@@ -1,3 +1,6 @@
 #!/bin/sh
 
-sed -i -r "/(url|doi)/ s/\{.?(.)\}/\1/g" ref.bib
+sed -i -r "/(url|doi)/ s/\{.?(.)\}/\1/g" ref-mendeley.bib
+sed -i -r "s/journaltitle/journal     /g" ref-mendeley.bib
+sed -i -r "s/@inbook/@incollection/g" ref-mendeley.bib
+sed -i -r "/file/d" ref-mendeley.bib

### 2017-10-11 paper/sections/discussion.tex
[ paper ] diagram added.

--- 2017-10-07 paper/sections/metis-language-and-proofs.tex
@@
-%
-\documentclass[../main.tex]{subfiles}
-\begin{document}
-
-% ===================================================================
-
-\section{Metis: Language and Proofs}
-\label{sec:metis-language-and-proofs}
-
-\Metis is an automatic theorem prover written in \len{Standard ML}
-for first-order logic with equality developed by John Hurd
-\cite{hurd2003first}. This prover is suitable for proof
-reconstruction since it provides well-documented proof-objects to
-justify its deduction steps from the basis of only six inference
-rules. There are already some tools that perform proof-reconstruction
-with \Metis, some of these systems are the following.
-
-\name{Isabelle/HOL} incorporated \Metis as a macro-step
-reconstruction tool for explaining proof steps (usually \CNF goals)
-replied from other \ATPs like \name{CVC4}, \name{Vampire}, or
-\name{Z3} (more details in Ref.~\cite{paulson2007source}).
-In \cite{Farber2015}, \Metis was used to provide a tactic for
-\name{HOL Light}; this challenges others like \emph{MESON}
-or the \emph{leanCoP} tactic that reconstructs proofs
-delivered by \name{leanCoP}~\cite{Farber2016}.
-
-In this paper, we ported a subset of the \Metis' inference rules to
-\Agda, the propositional fragmented without equality, that allows us to justify step-by-step the proofs delivered in
-\TSTP format generated by the prover \Metis.
-
-% -------------------------------------------------------------------
-
-\subsection{Input and Output Language}
-\label{ssec:input-and-output-language}
-
-\textit{Input.}~The \TPTP language --which includes the first-order
-form (denoted by \name{fof}) and clause normal form (denoted by
-\name{cnf}) formats~\cite{sutcliffe2009} -- is de facto input
-standard language to encode problems for many \ATPs. The \TPTP
-syntax describes a well-defined grammar to handle annotated formulas
-with the following form.
-
-\begin{verbatim}
-language(name, role, formula).
-\end{verbatim}
-
-The \name{language} can be \name{fof} or \name{cnf}. The \name{name}
-serves to identify the formula within the problem. Each formula
-assumes one \name{role}, this could be an \name{axiom},
-\name{conjecture}, \name{definition}, or a \name{hypothesis}.
-The formulas include Boolean connectives (\verb!&!, \verb!|!,
-\verb!=>!, \verb!<=>!, \verb!~!) and logic constants \verb!$true!
-and \verb!$false!, for the symbols (∧, ∨, ⇒, ⇔, ¬, ⊤, ⊥), respectively.
-
-For instance, let us express the problem
-$p\, \vdash \neg (p \wedge \neg p) ∨ (q \wedge \neg q)$
-in \TPTP syntax as follows, declaring an \tptpaxiom $p$, and the
-expected conclusion, the  \tptpconjecture
-\verb!~ ((p & ~ p) | (q & ~ q))!.
-
-\begin{verbatim}
-fof(h, axiom, p).
-fof(goal, conjecture, ~ ((p & ~ p) | (q & ~ q))).
-\end{verbatim}
-
-\textit{Output.}~\TSTP language is de facto output standard language
-for derivations of ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}. A \TSTP derivation
-is a directed acyclic graph, a proof tree, where each leaf is a
-formula from the \TPTP input. A node is a formula inferred from the
-parent formulas. The root is the final derived formula. Such a
-derivation is a list of annotated formulas with the form.
-
-\begin{verbatim}
-language(name, role, formula, source [,useful info]).
-\end{verbatim}
-
-The \name{source} field is an inference record with the following
-pattern.
-
-\begin{verbatim}
-inference(rule, useful info, parents).
-\end{verbatim}
-
-The \name{rule} stands for the inference name; the other fields are
-supporting arguments or useful information to apply the reasoning
-step, and the list of parents nodes. For instance, in Fig.
-\ref{fig:metis-proof-tstp}, \strip is the name of one of the
-inference with no arguments and only one parent node, the
-\name{goal}.
-
-\begin{figure}
-\begin{verbatim}
-fof(premise, axiom, p).
-fof(goal, conjecture, p).
-fof(subgoal_0, plain, p, inference(strip, [], [goal])).
-fof(negate_0_0, plain, ~ p, inference(negate, [], [subgoal_0])).
-fof(normalize_0_0, plain, ∼ p,
-  inference(canonicalize, [], [negate_0_0])).
-fof(normalize_0_1, plain, p,
-  inference(canonicalize, [], [premise])).
-fof(normalize_0_2, plain, $false,
-  inference(simplify, [], [normalize_0_0, normalize_0_1]))
-cnf(refute_0_0, plain, $false,
-  inference(canonicalize, [], [normalize_0_2])).
-\end{verbatim}
-\caption{The \texttt{Metis}' \texttt{TSTP} derivation for the
-problem $p\vdash p$.}
-\label{fig:metis-proof-tstp}
-\end{figure}
-
-% -------------------------------------------------------------------
-
-\subsection{Proofs}
-\label{ssec:metis-proofs}
-
-A proof-object delivered in a \Metis' proof encodes a natural
-deduction proof. The deduction system uses six inference rules
-\cite{hurd2003first} listed in Fig.~\ref{fig:metis-inferences}.
-With these inference rules as the only valid deduction steps, \Metis
-attempts to prove conjectures by refutation (see. e.g.,
-\emph{falsium} in the last conclusion of the \TSTP derivation in
-Fig.~\ref{fig:metis-example}).
-
-\begin{figure}
-\[
-% \scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{axiom}
-  \UnaryInfC{$C$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{assume $L$}
-  \UnaryInfC{$L ∨ \neg L$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{refl $t$}
-  \UnaryInfC{$t = t$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$C$}
-  \RightLabel{subst $\sigma$}
-  \UnaryInfC{$\sigma\,C$}
-\end{bprooftree}
-\qquad
-% }
-\]
-\[
-% \scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{equality $L$ $p$ $t$}
-  \UnaryInfC{$\neg (L[p] = t) ∨ \neg L ∨ L[ p \mapsto t]$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$L ∨ C$}
-  \AxiomC{$\neg L ∨ D$}
-  \RightLabel{resolve $L$}
-  \BinaryInfC{$C ∨ D$}
-\end{bprooftree}
-% }
-\]
-\caption{Inference rules of the \texttt{Metis} prover.}
-\label{fig:metis-inferences}
-\end{figure}
-
-These proofs are directed acyclic graphs, trees of refutations. Each
-node stands for an application of an inference rule and the leaves
-in the tree represent formulas in the given problem. Each node is
-labeled with a name of the inference rule (e.g., \canonicalize in
-Fig.~\ref{fig:metis-example}). Each edge links a premise with one
-conclusion. The proof graphs have at their root the conclusion
-$⊥$, since \Metis delivers proofs by refutation.
-
-% -------------------------------------------------------------------
-
-\subsection{Proof Rules}
-\label{ssec:proof-rules}
-
 We noted in \TSTP derivations that \Metis does not take into account
@@
 undocumented rules found in \TSTP derivations are: \canonicalize,
-\clausify, \conjunct, \negate, \simplify, and \strip.
+ \conjunct, \negate, \simplify, and \strip.
 
@@
 We refer the reader to see Section~\ref{sssec:simplify}.
-
-\end{document}

### 2017-10-11 paper/sections/metis-language-and-proofs.tex
[ paper ] diagram added.

--- 2017-10-04 paper/sections/metis-language-and-proofs.tex
@@
 
-\section{Metis: Language and Proofs}
-\label{sec:metis-language-and-proofs}
+\subsection{Metis: Language and Proofs}
+\label{ssec:metis-language-and-proofs}
 
@@
 
-\subsection{Input and Output Language}
-\label{ssec:input-and-output-language}
+\subsubsection{Input Language.}
+\label{ssec:input-language}
 
-\textit{Input.}~The \TPTP language --which includes the first-order
+The \TPTP language --which includes the first-order
 form (denoted by \name{fof}) and clause normal form (denoted by
@@
 
-\textit{Output.}~\TSTP language is de facto output standard language
-for derivations of ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}. A \TSTP derivation
-is a directed acyclic graph, a proof tree, where each leaf is a
-formula from the \TPTP input. A node is a formula inferred from the
-parent formulas. The root is the final derived formula. Such a
-derivation is a list of annotated formulas with the form.
+\subsubsection{Output Language.}
+\label{ssec:output-language}
+
+The \TSTP language is de facto output standard language
+for derivations of ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}.
+A \TSTP derivation is a directed acyclic graph, a proof tree,
+where each leaf is a formula from the \TPTP input. A node is a formula
+inferred from the parent formulas. The root is the final derived formula.
+Such a derivation is a list of annotated formulas with the form.
 
@@
 
-\subsection{Proofs}
+\subsubsection{Proofs.}
 \label{ssec:metis-proofs}
@@
 
-\subsection{Proof Rules}
+\subsubsection{Proof Rules.}
 \label{ssec:proof-rules}
 
-We noted in \TSTP derivations that \Metis does not take into account
-some inference rules for the \Metis' official documentation; we
-refer to the \Metis' logic kernel.
-Besides the six \Metis' inference rules from the Fig.
-\ref{fig:metis-inferences}, its proof-objects, the \TSTP
-derivations, exhibit an entirely different set of rules.
+Una demostración de Metis para un problema logica propositional sin igualdad puede incluir en su derivacion \TSTP hasta 6 diferentes reglas de inferencia:
+\canonicalize, \clausify, \conjunct, \negate, \simplify, y \strip.
+Contrastando el codigo fuente de Metis y las reglas de la figura~\ref{fig:metis-inferences}. Podemos observar lo siguiente:
+la regla de inferencia \emph{axiom} aparece por medio  de las reglas:
+\canonicalize, \clausify, \conjunct, and \simplify.
+La regla de inferencia \emph{resolve} aparece con el mismo nombre, \resolve.
+Las ultimas reglas son \strip y \negate que son la representacion de la regla de inferencia \emph{assume}, las cuales sirven para
+introducir en una demostracion la conjectura que se pretende demostrar, a esta conjetura nos referiremos tambien como el goal.
+Toda prueba de un goal, tiene en su derivacion la negacion de dicho goal,
+o de uno o varias proposiciones equivalentes, porque recordemos que
+las pruebas son por refutacion.
 
-For instance, for the propositional logic fragment without equality,
-only three rules are valid from the \Metis' Logic Kernel:
-\emph{assume}, \emph{axiom}, and \emph{resolve}. Nevertheless, as we
-observed in \TSTP derivations, for such a propositional fragment,
-\Metis uses in its deductions steps, six rules where only the
-\emph{resolve} inference persists from the original list. In the
-case of \resolve, it differs from its original version since, in
-\TSTP, this rule has by definition an argument, a literal. The other
-undocumented rules found in \TSTP derivations are: \canonicalize,
-\clausify, \conjunct, \negate, \simplify, and \strip.
-
-\begin{figure}
-\centering
-  \begin{bprooftree}\tt
-    \AxiomC{}
-    \RightLabel{negate}
-    \UnaryInfC{$\neg p$}
-    \RightLabel{strip}
-    \UnaryInfC{$\neg p$}
-    \AxiomC{}
-    \RightLabel{axiom}
-    \UnaryInfC{$p$}
-    \RightLabel{canonicalize}
-    \UnaryInfC{$p$}
-    \RightLabel{simplify}
-    \BinaryInfC{$⊥$}
-    \RightLabel{canonicalize}
-    \UnaryInfC{$⊥$}
-  \end{bprooftree}
-  \caption{The \Metis' proof tree for $p \vdash p$ from the
-  derivation in Fig.~\ref{fig:metis-proof-tstp}}
-  \label{fig:metis-example}
-\end{figure}
-
-This lack of the \Metis' documentation represents one of the first barriers to build proof-reconstruction tools since some inference rules
-like \canonicalize or \simplify summarize many essential steps to deduce the conclusion, making them hard to justify and emulate
-(see a comment related on the presenting of \name{Sledgehammer}
-in \citeauthor{paulson2007source}~\cite{paulson2007source} and \citeauthor{Farber2015}~\cite{Farber2015}).
-
-Henceforth, one of our main purposes with this document consists of
-giving a response to these rules looking at the \Metis' source code but also reviewing a representative set of solutions generated by
-\Metis for the \CPL collection of \TPTP problems~\cite{Prieto-Cubides2017} including some problem from the \Metis repository itself.
-
-In the following, we briefly describe each \Metis' rule from our perspective, but we present a formal description for each rule in Section \ref{sec:proof-reconstruction}.
-
-\vskip 2mm
-
-% ...................................................................
-
-\textit{Splitting}. To prove a goal, \Metis splits the goal into
-disjoint cases. This process produces a list of new subgoals, the
-conjunction of these subgoals implies the goal. Then, a proof of the
-goal becomes in smaller proofs, one refutation for each subgoal.
-These subgoals are introduced in the \TSTP derivation with the \strip
-inference rule. We refer the reader to see Theorem~\ref{thm:thm-strip}.
-
-\begin{verbatim}
-fof(goal, conjecture, p & r & q).
-fof(subgoal_0, plain, p, inference(strip, [], [goal])).
-fof(subgoal_1, plain, p => r, inference(strip, [], [goal])).
-fof(subgoal_2, plain, (p & r) => q, inference(strip, [], [goal])).
-\end{verbatim}
-
-% ...................................................................
-
-\textit{Clausification.} The \clausify rule transforms a
-propositional formula in clausal normal form, a conjunction
-of clauses. Where a \emph{clause} is the disjunction of zero or more
-literals and a \emph{literal} is an atom (positive literal) or a
-negation of an atom (negative literal).
-Be aware this kind of conversion between one formula to its clausal normal form is not unique, and \Metis has a customized approach to perform that transformation.
-We refer the reader to see Theorem~\ref{thm:thm-clausify}.
-
-\vskip 2mm
-
-% ...................................................................
-
-\textit{Normalization.}
-Each application of the clausify rule described above is preceded by
-\canonicalize rule. Both rules aim to perform a common task for
-automatic theorem provers, clausification, mainly described on paper
-by \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.
-
-\Metis uses the \canonicalize rule to
-normalize a propositional formula that comes from an axiom or a
-definition. It often converts each expression in one of its normal
-form: the conjunctive normal form, the negative normal form or the
-disjunctive normal form. Next, this rule simplifies the formula
-with some definitions, applying recursively on the structure's
-formula conjunctions and disjunctions simplifications to remove
-tautologies (see Fig.~\ref{fig:conjunctive-disjunctive-simpl} for a
-list of these theorems. We assume the commutative property for the
-conjunction and disjunction connectives).
-We refer the reader to see Section~\ref{sssec:normalization} for the
-lemmas and theorems described there.
-
-\begin{figure}
-\[%\scalebox{0.9}{
-  \begin{bprooftree}
-    \AxiomC{$φ ∧ ⊥$}
-    \UnaryInfC{$⊥$}
-  \end{bprooftree}
-  \qquad
-  \begin{bprooftree}
-    \AxiomC{$φ ∧ ⊤$}
-    \UnaryInfC{$φ$}
-  \end{bprooftree}
-  \qquad
-  \begin{bprooftree}
-    \AxiomC{$φ ∧ ¬ φ$}
-    \UnaryInfC{$⊥$}
-  \end{bprooftree}
-  \qquad
-  \begin{bprooftree}
-    \AxiomC{$φ ∧ φ$}
-    \UnaryInfC{$φ$}
-  \end{bprooftree}
-%}
-\]
-
-\[%\scalebox{0.9}{
-  \begin{bprooftree}
-    \AxiomC{$φ ∨ ⊥$}
-    \UnaryInfC{$φ$}
-  \end{bprooftree}
-  \qquad
-  \begin{bprooftree}
-    \AxiomC{$φ ∨ ⊤$}
-    \UnaryInfC{$⊤$}
-  \end{bprooftree}
-  \qquad
-  \begin{bprooftree}
-    \AxiomC{$φ ∨ ¬ φ$}
-    \UnaryInfC{$⊤$}
-  \end{bprooftree}
-  \qquad
-  \begin{bprooftree}
-    \AxiomC{$φ ∨ φ$}
-    \UnaryInfC{$φ$}
-  \end{bprooftree}
-%}
-\]
-\caption{Definitions for conjunction and disjunction simplification
-in the \canonicalize inference.}
-\label{fig:conjunctive-disjunctive-simpl}
-\end{figure}
-
-% ...................................................................
-
-\textit{Resolution.} The \resolve rule is the resolution theorem
-showed in Fig.~\ref{fig:metis-inferences}. For its application, we
-need the positive literal for resolution and two derivations to
-deduce the \emph{resolvent}. The positive literal $p$ must occur in
-the formula from the first derivation, and the negative literal must
-occur in the formula from the second derivation (this follows the
-same pattern in \Metis' logic core in Fig.~\ref{fig:metis-inferences}
-for the resolve inference).
-We refer the reader to see Theorem~\ref{thm:thm-resolve}.
-
-\begin{verbatim}
-cnf(refute_0_0, plain, p | q,
-  inference(canonicalize, [], [normalize_0_0])).
-cnf(refute_0_1, plain, ~ p,
-  inference(canonicalize, [], [normalize_0_4])).
-cnf(refute_0_2, plain, q,
-  inference(resolve, [$cnf(p)], [refute_0_0, refute_0_1])).
-\end{verbatim}
-
-% ...................................................................
-
-\textit{Splitting a conjunct.} The \conjunct rule extracts from a
-conjunction one of its conjuncts; it is a generalization of the
-projection rules for the conjunction connective as the
-following \TSTP derivation shows.
-We refer the reader to see Theorem~\ref{thm:thm-conjunct}.
-
-\begin{verbatim}
-fof(normalize_1, plain, p & q & r,
-  inference(canonicalize, [], [x])).
-fof(normalize_2, plain, q,
-  inference(conjunct, [], [normalize_1])).
-\end{verbatim}
-
-\textit{Negate.}
-Each subgoal proof is a refutation, thereby each proof assumes
-the negation of its subgoal. The \negate rule
-assumes the negation of a given subgoal. This rules always
-appears after applies the \strip inference to the goal.
-
-\begin{verbatim}
-fof(subgoal_0, plain, p,
-  inference(strip, [], [goal])).
-fof(negate_0_0, plain, ~ p,
-  inference(negate, [], [subgoal_0])).
-\end{verbatim}
-
-% ...................................................................
-
-\textit{Simplification.}
-The \simplify rule is an inference that performs simplification of
-definitions and tautologies. This rule
-transverses a list of formulas by applying different theorems (e.g.,
-\emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
-syllogism}) including the list of theorems used by \canonicalize in
-Fig. \ref{fig:conjunctive-disjunctive-simpl} and the resolution
-theorem of the \resolve rule.
-We refer the reader to see Section~\ref{sssec:simplify}.
+De esta manera concluimos con una breve descripcion del probador de teoremas Metis.
+En lo siguiente, intentaremos justificar derivación de Metis paso por paso.
+Para esto,estudiamos cada una de las reglas antes mencionadas en más detalle, y para cada una de ellas, proponemos un teorema para emular
+su  razonamiento.
 

### 2017-10-11 paper/sections/proof-reconstruction.tex
improved some references in the text.

--- 2017-10-01 paper/sections/proof-reconstruction.tex
@@
 
-\begin{figure}
-\centering
-
-\begin{tikzpicture}[scale=0.9]
-\node[text width=2cm, align=center](problem) at (0,0)
-  {1. \CPL \\ Problem.};
-
-\node[right = 1.1cm of problem, text width=2cm, align=center]
-  (tptp){2. \TPTP \\ Problem.};
-
-\node[right= 1.1cm of tptp, text width=2cm, align=center]
-   (metis) {3. \Metis \\ Prover.};
-
-\node[right= 1.1cm of metis, text width=2cm, align=center, inner sep=10pt]
-   (tstp) {4. \TSTP \\ Derivation.};
-
-\node[below= 0.5cm of tstp, text width=2cm, align=center, inner sep=10pt]
-  (athena) {5. \Haskell \\ Translator.};
-
-\node[left = 1.1cm of athena, text width=2cm, align=center]
-   (agdafile) {6. Proof-term.};
-
-\node[left = 1.1cm of agdafile, text width=2cm, align=center]
-   (agda) {7. Proof Checker.};
-
-\node[below = 0.5cm of problem, text width=2cm, align=center]
-   (verified) {8.1 Proof \\ Checked.};
-
-\node[below = 0.5cm of verified, text width=2cm, align=center]
-   (failure) {8.2 Failure.};
-
-% node[below] {send to}
-\draw[->, thick] (problem) to
-  % node[below] {\tiny encoding}
-  (tptp);
-\draw[->, thick] (tptp) to
-  % node[below] {\tiny }
-  (metis);
-\draw[->, thick] (metis) to
-  % node[below] {\tiny replies on}
-  (tstp);
-\draw[->, thick] (tstp) to
-  % node[right] {\tiny parsing}
-  (athena);
-\draw[->, thick] (athena) to
-  % node[below] {\tiny traslation}
-  (agdafile);
-\draw[->, thick] (agdafile) to
-  % node[below] {\tiny type-checking}
-  (agda);
-\draw[->, thick] (agda) to (verified);
-\draw[->, thick, gray] (agda) to (failure);
-\end{tikzpicture}
-\caption{Proof-reconstruction overview.}
-\label{fig:proof-reconstruction-workflow}
-\end{figure}
-
-The proof-reconstruction approach proposed here consists of a series
-of steps similar to the workflow presented by \citeauthor{sultana2015} in
-\cite{sultana2015}. This process is a translation from a source
-system to a target system. In our case, the system of origin, the
-automatic theorem prover, is \Metis; the target system is a proof
-assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types is valid (see a description of \Agda for its main features in
-Section~\ref{sec:implementation}).
-The overview of the proof-reconstruction is presented in
-Fig.~\ref{fig:proof-reconstruction-workflow}, the process can begin with
-a problem in \CPL that we encode in \TPTP format to be sent as the
-input of the \Metis prover.
-The algorithms of \Metis in Step~3 find
-a solution if the problem is a theorem, in that case \Metis replies
-with a derivation in \TSTP format of the proof, otherwise the problem is counter feasible.
-
-With such a derivation, in Step~5, we process the derivation with our \Haskell translator tool, \Athena~\cite{Athena}.
-\Athena parses the \TSTP format, analyze the
-derivation and generates a representation of the natural deduction
-proof using a tree data structure (see the properties
-of this tree in Subsection \ref{ssec:metis-proofs}).
-We perform an analysis of the proof-tree removing redundancies,
-unnecessary steps or unused output from the \TSTP derivation.
-
-As a result,
-\Athena generates an \Agda file with the proof-term. We have included
-in this file, \emph{imports} that call our \Agda libraries that give
-support for CPL presented in~\cite{AgdaProp}, and support for \Metis'
-inference rules implemented in~\cite{AgdaMetis}.
-
-Finally, we use the proof checker in Step~7 to type-check the
-proof-term. If type-checking succeed, the \TSTP
-derivation is correct, otherwise when it fails, one of the three
-actors in the process could be the responsible: \Metis, \Athena, or
-\Agda.
-
-We are responsible for errors committed in the translation from
-\TSTP to \Agda: bugs in the parsing module, lack of the coverage of
-\Metis' inference rules, and last but not least, the pretty print of
-the proof in \Agda code.
-
-In the rest of this section, we provide a formal description using
-type theory to build definitions and theorems for functions
-necessary to emulate \Metis' inference rules.
-Some conventions about notations. We will write the
-type judgments with ``$a : A$'' to denote that $a$ has type
-$\abbre{A}$. Types are written using small caps.
-For propositions, we will denote by $φ ≡ ψ$, the syntactic
-equivalence. We use the \Prop type for propositions and for theorems,
-the dependent type, $ Γ ⊢ φ$ where $Γ$ has type $\abbre{List} \Prop$ and
-$φ$ has type $\Prop$.
-
-% ...................................................................
-
-% section section_name (end)
-\subsection{Structural Recursion}
-\label{ssec:structural-recursion}
-
-To emulate \Metis' inference rules in type theory,
-we observed that transformations performed by some rules were given by \emph{general recursive} functions.
-But algorithms based on general recursions can not be translated
-directly in type theory since it is not a guarantee they terminate.
-
-Then, we solve the termination problem by modifying problematic functions
-to be \emph{structural recursive}~\cite{Coquand1992,Abel2002,Bove2005}.
-
-We use the same notion of \emph{structurally smaller} from
-\citeauthor{Abel2002}~\cite{Abel2002} to say, a recursive function is
-structurally recursive if it calls itself with only
-\emph{structurally smaller}
-arguments.
-
-To convert a general recursive call into a structurally recursive call,
-we use the \emph{Bounded Recursion} technique presented
-in~\cite{Bertot2004} but
-others found in \cite{Coquand1992,Abel2002,Bove2005} could be used.
-This technique converts a general recursive
-function into a structural recursive function by adding an additional
-argument for the function complexity, the bound for the number of times, the function needs to call itself to get the final result.
-
-Then, we add the natural number $n : \Nat$ in the input of the
-general recursive function, and perform the recursion over the structure of
-\Nat type.
+\input{sections/diagram.tex}
+
+% The proof-reconstruction approach proposed here consists of a series
+% of steps similar to the workflow presented by \citeauthor{sultana2015} in
+% \cite{sultana2015}. This process is a translation from a source
+% system to a target system. In our case, the system of origin, the
+% automatic theorem prover, is \Metis; the target system is a proof
+% assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types is valid (see a description of \Agda for its main features in
+% Section~\ref{sec:implementation}).
+% The overview of the proof-reconstruction is presented in
+% Fig.~\ref{fig:proof-reconstruction-workflow}, the process can begin with
+% a problem in \CPL that we encode in \TPTP format to be sent as the
+% input of the \Metis prover.
+% The algorithms of \Metis in Step~3 find
+% a solution if the problem is a theorem, in that case \Metis replies
+% with a derivation in \TSTP format of the proof, otherwise the problem is counter feasible.
+
+% With such a derivation, in Step~5, we process the derivation with our \Haskell translator tool, \Athena~\cite{Athena}.
+% \Athena parses the \TSTP format, analyze the
+% derivation and generates a representation of the natural deduction
+% proof using a tree data structure (see the properties
+% of this tree in Section~\ref{ssec:metis-proofs}).
+% We perform an analysis of the proof-tree removing redundancies,
+% unnecessary steps or unused output from the \TSTP derivation.
+
+% As a result,
+% \Athena generates an \Agda file with the proof-term. We have included
+% in this file, \emph{imports} that call our \Agda libraries that give
+% support for CPL presented in~\cite{AgdaProp}, and support for \Metis'
+% inference rules implemented in~\cite{AgdaMetis}.
+
+% Finally, we use the proof checker in Step~7 to type-check the
+% proof-term. If type-checking succeed, the \TSTP
+% derivation is correct, otherwise when it fails, one of the three
+% actors in the process could be the responsible: \Metis, \Athena, or
+% \Agda.
+
+% We are responsible for errors committed in the translation from
+% \TSTP to \Agda: bugs in the parsing module, lack of the coverage of
+% \Metis' inference rules, and last but not least, the pretty print of
+% the proof in \Agda code.
+
+% In the rest of this section, we provide a formal description using
+% type theory to build definitions and theorems for functions
+% necessary to emulate \Metis' inference rules.
+% Some conventions about notations. We will write the
+% type judgments with ``$a : A$'' to denote that $a$ has type
+% $\abbre{A}$. Types are written using small caps.
+% For propositions, we will denote by $φ ≡ ψ$, the syntactic
+% equivalence. We use the \Prop type for propositions and for theorems,
+% the dependent type, $ Γ ⊢ φ$ where $Γ$ has type $\abbre{List} \Prop$ and
+% $φ$ has type $\Prop$.
+
+% % ...................................................................
+
+% % section section_name (end)
+% \subsection{Structural Recursion}
+% \label{ssec:structural-recursion}
+
+% To emulate \Metis' inference rules in type theory,
+% we observed that transformations performed by some rules were given by \emph{general recursive} functions.
+% But algorithms based on general recursions can not be translated
+% directly in type theory since it is not a guarantee they terminate.
+
+% Then, we solve the termination problem by modifying problematic functions
+% to be \emph{structural recursive}~\cite{Coquand1992,Abel2002,Bove2005}.
+
+% We use the same notion of \emph{structurally smaller} from
+% \citeauthor{Abel2002}~\cite{Abel2002} to say, a recursive function is
+% structurally recursive if it calls itself with only
+% \emph{structurally smaller}
+% arguments.
+
+% To convert a general recursive call into a structurally recursive call,
+% we use the \emph{Bounded Recursion} technique presented
+% in~\cite{Bertot2004} but
+% others found in \cite{Coquand1992,Abel2002,Bove2005} could be used.
+% This technique converts a general recursive
+% function into a structural recursive function by adding an additional
+% argument for the function complexity, the bound for the number of times, the function needs to call itself to get the final result.
+
+% Then, we add the natural number $n : \Nat$ in the input of the
+% general recursive function, and perform the recursion over the structure of
+% \Nat type.
 \abbre{Nat} type is the usual type for natural numbers with \zero and \suc as their constructors.
@@
 
-Then, the type-checker will
-recognize structurally smaller arguments by using the lexicographic
-order~\cite{Abel2002} for such kind of functions.
-
-In other words, we take a general recursive function $f: \Prop \to \Prop$.
-and we redefine that function as
-$f: \Prop \to \Nat \to \Prop$, and perform the recursion
-using induction on the structure of the \Nat type.
-
-Let us consider the following example to exhibit the technique
-mentioned above for an inner function in the \strip inference.
-
-\begin{align}
-\begin{split}
-\label{eq:unshunt-definition}
-&unshunt_{0}(φ) =\\
-&\hspace{3mm}\begin{cases}
-unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
-  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-unshunt_{0}(φ₁ ⇒ φ₂) ∧ unshunt_{0}(φ₁ ⇒ φ₃),
-  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
-φ, &\text{otherwise.}
-\end{cases}
-\end{split}
-\end{align}
-
-From the definition above, the size of the argument, ((φ₁ ∧ φ₂) ⇒ φ₃),
-is not structurally smaller than the input formula, (φ₁ ⇒ (φ₂ ⇒ φ₃)), since ((φ₁ ∧ φ₂) ⇒ φ₃) is not a subformula of (φ₁ ⇒ (φ₂ ⇒ φ₃)).
-
-Thus, we define the function
-$unshunt_{1} : \Prop \to \Nat \to \Prop$
-by structural recursion in its second argument in
-Eq.~\ref{eq:unshunt-structured}.
-
-\begin{align}
-\label{eq:unshunt-structured}
-\begin{split}
-&unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\
-&unshunt_{1}(φ, \suc(n)) =\\
-&\hspace{3mm}\begin{cases}
-unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
-  &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ unshunt_{1}(φ₁ ⇒ φ₃, n),
-   &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
-\end{cases}
-\end{split}
-\end{align}
-
-As we mentioned above, the natural number in the second argument of the
-function used in Eq.~\ref{eq:unshunt-structured} stands for a complexity
-measure of the function, in this case $unshunt_{1}$ function.
-
-A \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
-and presented in \cite{VanDalen1994} as \emph{the rank for a
-proposition}, is a function $\Prop \to \Nat$ that assigns a natural
-number for a proposition φ as follows.
-
-\begin{equation*}
-\label{eq:rank-definition}
-rank(φ)=
-\begin{cases}
-0, &\text{for atomic }φ \\
-rank(φ₁) + c_{¬},  &\text{if } φ ≡ \neg φ₁ \\
-\max{(rank(φ₁),rank(φ₂))} + c_{\square},
-  &\text{if } φ ≡ φ₁\,\square\, φ₂.
-\end{cases}
-\end{equation*}
-
-where $c_{¬}$ or $c_{\square}$ is a non-negative integer called the
-complexity of the connective.
-
-Recall, we want to maintain the same outputs as the original unshunt
-does in Eq.~\ref{eq:unshunt-definition} and the complexity measure of it,
-is a bound for the number of times this function can call itself.
-
-Therefore, we define an appropriate complexity measure
-$unshunt_{cm}: \Prop → \NN$ for our $unshunt_{1}$ function presented in
-Eq.~\ref{eq:unshunt-rank-definition}.
-
-\begin{align}
-\begin{split}
-\label{eq:unshunt-rank-definition}
-&unshunt_{cm}(φ) =\\
-&\hspace{3mm}
-\begin{cases}
-unshunt_{cm}(φ₃) + 2, &\text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-\max(unshunt_{cm}(φ₂),unshunt_{cm}(φ₃)) + 1,
-  &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
-0, &\text{otherwise.}
-\end{cases}
-\end{split}
-\end{align}
-
-Finally, the curated version of $unshunt_{0}$ function is presented
-in Eq.~\ref{eq:unshunt-fixed}.
-
-\begin{equation}
-\label{eq:unshunt-fixed}
-unshunt(\varphi) := unshunt_{1}(\varphi, unshunt_{cm}(\varphi)).
-\end{equation}
-
-For a more complete treatment of general recursion, and how to
-define well-founded and well-structural recursive functions, we refer
-the reader to Ref.~\cite{Bove2005}, where Bove and Capettra described
-not only general recursion, but they also treat mutual recursive
-function, among other kinds.
-
-% ................................................
-
-\subsection{Emulating \Metis' Inference Rules}
-\label{ssec:emulating-inferences}
-
-\subsubsection{Splitting a Goal.}
-The goal of a problem to be proved by \Metis is processed to generate new
-propositions, the new targets, \Metis calls these formulas
-\emph{subgoals}.
-
-The conjunction of these subgoals is a proposition equivalent to the
-original goal. Then, we find a refutation for each subgoal in the \Metis' \TSTP derivation.
-
-Nevertheless, \Metis does not provide neither an explanation for the user about the process in its \TSTP derivations nor in its documentation.
-
-In the following, we show how Theorem.~\ref{thm:thm-strip} proves the correctness of the process mentioned above.
-But first, let prove some lemmas for $unshunt$ function presented in Eq.~\ref{eq:unshunt-fixed},
-and $split$ function from the definition in Eq.~\ref{eq:split-definition}.
-
-\begin{lemma}[lem-unshunt]
-  \label{lem:unshunt}
-  $Γ ⊢ unshunt(φ)$, then $Γ ⊢ φ$.
-\end{lemma}
-
-\begin{proof} Use induction on the cases defined by the outcome of the
-$unshunt$ function in Eq.~\ref{eq:unshunt-structured}.
-When $n = 0$, by definition, $Γ ⊢ φ$.
-When $n = 1$, we apply the following theorem from~\cite{AgdaProp}
-
-\begin{equation*}
-\texttt{∧⇒-to-⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
-\end{equation*}
-
-For $n > 1$, we will use induction on the structure of second
-argument.
-
-(φ₁ ⇒ (φ₂ ⇒ φ₃))
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
-  \RightLabel{By def.}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
-  \RightLabel{lem-unshunt}
-  \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
-  \RightLabel{∧⇒-to-⇒⇒}
-  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).}
-  \end{bprooftree}
-\end{equation*}
-
-Second, using the following theorem from \cite{AgdaProp},
-
-\begin{equation*}
-  \texttt{⇒∧-to-⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).
-\end{equation*}
-
-($φ₁ ⇒ (φ₂ ∧ φ₃)$)
-\begin{equation*}
-\scalebox{0.95}{
-($\mathcal{D}_1$)
-\begin{bprooftree}
-\AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n) ∧ unshunt(φ₁ ⇒ φ₃, n)$}
-\RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n)$}
-\RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n-1)$}
-\RightLabel{lem-unshunt}
-\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$,}
-\end{bprooftree}
-}
-\end{equation*}
-
-\begin{equation*}
-(\mathcal{D}_2)
-\begin{bprooftree}
-\AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂) ∧ unshunt(φ₁ ⇒ φ₃)$}
-\RightLabel{∧-proj₂}
-\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n)$}
-\RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n-1)$}
-\RightLabel{lem-unshunt}
-\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$,}
-\end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\mathcal{D}_1$}
-  \AxiomC{$\mathcal{D}_2$}
-  \RightLabel{∧-intro}
-  \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
-  \RightLabel{⇒∧⇒-to-⇒∧}
-  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).}
-  \end{bprooftree}
-\end{equation*}
-\end{proof}
-
-Now, let us consider the $split$ function presented in
-Eq.~\ref{eq:split-definition} that yields a conjunction of subgoals from a proposition, the goal in \Metis.
-
-\begin{equation}
-\label{eq:split-definition}
-\mysplit(φ) =
-\begin{cases}
-unshunt(\mysplit(φ₁)) &\text{if }φ ≡ φ₁ ∧ φ₂\\
-∧\ unshunt(φ₁ ⇒ \mysplit(φ₂)), &\\[2.5mm]
-unshunt(¬ φ₁ ⇒ \mysplit(φ₂)),
-  & \text{if }φ ≡ φ₁ ∨ φ₂\\[2.5mm]
-unshunt(φ₁ ⇒ \mysplit(φ₂)),
-  & \text{if }φ ≡ φ₁ ⇒ φ₂\\[2.5mm]
-unshunt(φ₁ ⇒ \mysplit(φ₂))
-  & \text{if }φ ≡ φ₁ ⇔ φ₂\\
-∧\ unshunt(φ₂ ⇒ \mysplit(φ₁)),
-  &\\[2.5mm]
-unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
-  & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂)\\[2.5mm]
-unshunt(\mysplit(¬ φ₁))
-  & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
-∧\ unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂)),
-  &\\[2.5mm]
-unshunt(\mysplit(φ₁))
-  & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
-∧\ unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
-  &\\[2.5mm]
-unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
-  & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
-∧\ unshunt(¬ φ₂ ⇒ \mysplit(φ₁)),
-  &\\[2.5mm]
-unshunt(\mysplit(φ₁)),
-  & \text{if }φ ≡ ¬ ¬ φ₁\\
-⊤,
-  & \text{if }φ ≡ ¬ ⊥\\
-⊥,
-  & \text{if }φ ≡ ¬ ⊤.
-\end{cases}
-\end{equation}
-
-The definition above suffers termination problems since it is not
-a structural recursion. Therefore, we have reformulated Def.~\ref{eq:split-definition} to solve such a issue following the technique
-described in Subsection~\ref{ssec:structural-recursion}.
-Here and below, we refer to $split$ as the function after applying
-the process mentioned above.
-
-\begin{lemma}[\thmsplit] $Γ ⊢ \mysplit(φ)$ then $Γ ⊢ φ$.
-\label{lem:lem-split}
-\end{lemma}
-
-\begin{proof} We now proceed by induction on the structure of the
-formula φ in the definition of Eq.~\ref{eq:split-definition}.
-For a complete proof, we refer the reader to~\cite{AgdaMetis}.\\[3mm]
-
-($φ ≡ φ₁ ∧ φ₂$). We get a proof for each conjunct and using the introduction rule for conjunction, the result follows.
-
-\begin{equation*}
-(\mathcal{D})\hspace{3mm}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
-  \RightLabel{By def.}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{∧-proj₁}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁)$}
-  \RightLabel{lem-unshunt}
-  \UnaryInfC{$Γ ⊢ φ₁$.}
-  \end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\mathcal{D}$}
-  \UnaryInfC{Γ ⊢ φ₁}
-  \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
-  \RightLabel{By def.}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{$∧$-proj$₂$}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{lem-unshunt}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-  \RightLabel{$⇒$-elim}
-  \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
-  \RightLabel{\thmsplit}
-  \UnaryInfC{$Γ ⊢ φ₂.$}
-  \end{bprooftree}
-\end{equation*}
-
-\vskip 3mm
-
-($φ ≡ φ₁ ⇒ φ₂$).
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{assume φ₁}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
-  \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
-  \RightLabel{By def.}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{lem-unshunt}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-  \RightLabel{weaken φ₁}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-  \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂,n-1)$}
-  \RightLabel{\thmsplit}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
-  \RightLabel{⇒-intro}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$.}
-  \end{bprooftree}
-\end{equation*}
-\vskip 3mm
-
-(φ ≡ ¬ (φ₁ ∨ φ₂)). We show $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$. Using their conjunction by the introduction rule, and De Morgan Law, the results follows.
-
-\begin{equation*}
-(\mathcal{D})\hspace{3mm}
-\begin{bprooftree}
-\AxiomC{$Γ ⊢ \mysplit(φ, n)$}
-\RightLabel{By def.}
-\UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
-\RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ unshunt(¬ φ₁)$}
-\RightLabel{lem-unshunt}
-\UnaryInfC{$Γ ⊢ ¬ φ₁$,}
-\end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\mathcal{D}$}
-  \UnaryInfC{$Γ ⊢ ¬ φ₁$}
-
-  \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
-  \RightLabel{By def.}
-  \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{∧-proj₂}
-  \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{lem-unshunt}
-  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-  \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
-  \RightLabel{\thmsplit}
-  \UnaryInfC{$Γ ⊢ ¬ φ₂.$}
-  \end{bprooftree}
-\end{equation*}
-\end{proof}
-
-\begin{theorem}[thm-strip]
-\label{thm:thm-strip}
- If $s_i$ are the subgoals for the goal φ, and
-$\{ Γ ⊢ s_i \}_{i}$, then $Γ ⊢ φ$.
-\end{theorem}
-
-\begin{proof}
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i}$}
-  \RightLabel{∧-intro}
-  \UnaryInfC{$Γ ⊢ \bigwedge_i s_i$}
-
-  \AxiomC{$\mysplit(φ) ≡ \bigwedge_i s_i $}
-  \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ \mysplit(φ) $}
-
-  \RightLabel{\thmsplit}
-  \UnaryInfC{$Γ ⊢ φ$.}
-\end{bprooftree}
-\end{equation*}
-Where, the $subst$ theorem is,
-\begin{equation}
-  \label{eq:substitution-theorem}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
-  \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ ψ$.}
-  \end{bprooftree}
-\end{equation}
-\end{proof}
-
-\emph{Splitting a conjunct}.
-The \conjunct rule extracts from a conjunction, one of its conjunct.
-To achieve this, we use projections repeatedly until we finally find
-the conjunct required.
-
-\begin{align}
-  \begin{split}
-  conjunct(φ, ψ) =
-    \begin{cases}
-      ψ, &\text{if }φ ≡ ψ\\
-      ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₁, ψ)≡ ψ\\
-      ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₂, ψ)≡ ψ\\
-      φ, &\text{otherwise.}
-    \end{cases}
-  \end{split}
-\end{align}
-
-\begin{theorem}[thm-conjunct]
-  \label{thm:thm-conjunct}
-  $Γ ⊢ φ$, and $ψ \in \Prop$ , then $Γ ⊢ conjunct(φ, ψ)$.
-\end{theorem}
-
-\begin{proof}
-When φ ≡ ψ, from $Γ ⊢ conjunct(φ, ψ)$ by normalization, we get $Γ ⊢ ψ$.
-By using $subst$ theorem Eq.~\ref{eq:substitution-theorem}, we get the desire conclusion. If the proposition φ is a conjunction, and $ψ ≡ conjunct(φ_{i}, ψ)$
-for some $i = 1,\ 2$, then,
-
-\begin{equation}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
-  \RightLabel{∧-proj$_{i}$}
-  \UnaryInfC{$Γ ⊢ φ_{i}$}
-  \UnaryInfC{$Γ ⊢ conjunct(φ_{i}, ψ)$}
-  \AxiomC{$conjunct(φ_{i}, ψ) ≡ ψ$}
-  \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ ψ$.}
-  \end{bprooftree}
-\end{equation}
-
-The last statement follows by using the hypothesis and the proof is complete.
-\end{proof}
-
-% ------------------------------------------------------------------------
-
-\subsubsection{Reordering.}
-
-Syntactically speaking, showing the logic equivalence between two conjunctive normal forms is a matter of rearrangements of the conjunctions
-but also of the inner disjunctions inside the propositions involved.
-
-We provide some useful theorems to perform the following tasks.
-
-\begin{itemize}
-  \item Reorder a disjunction like $φ = φ₁ ∨ φ₂ ∨ \cdots$ to match with another disjunction $ψ = ψ₁ ∨ ψ₂ ∨ \cdots$, when $φ$ is a disjunct of $ψ$.
-  \item Reorder a conjunction of disjuncts (CNF), $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another CNF formula equivalent $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$.
-\end{itemize}
-
-First, we define the $rdisj$ function in Eq.~\ref{eq:rdisj-def} to convert a disjunction to be a right-associative disjunction, and following
-a similar approach we define the $rconj$ function for conjunctions.
-
-\begin{align}
-  \begin{split}
-    \label{eq:rdisj-def}
-    rdisj(φ) =
-    \begin{cases}
-    rdisj(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
-    φ₁ ∨ rdisj(φ₂),         & \text{if } φ ≡ φ₁ ∨ φ₂\\
-    φ,                      & \text{otherwise.}
-    \end{cases}
-  \end{split}
-\end{align}
-
-\begin{lemma}[lem-rdisj]
-\label{lem:lem-rdisj}
-  $Γ ⊢ φ$ then $Γ ⊢ rdisj(φ)$.
-\end{lemma}
-
-The following function, $build_{∨} : \Prop → \Prop → \Prop$ in Eq.~\ref{eq:build-or}, intends to construct a disjunction from another disjunction, specifically, we want to rearrange the order of the disjuncts in a target disjunction.
-This approach for rearrangement is inspired on the treatment for nested
-disjunctions mainly described in \citeauthor{bohme2010}~\cite{bohme2010}.
-
-\begin{equation}
-  \begin{split}
-  \label{eq:build-or}
-  &build_{∨}(φ, ψ) =\\
-  &\hspace{3mm}
-  \begin{cases}
-  ψ, &\text{if } φ ≡ ψ\\
-  ψ, &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
-  φ, &\text{otherwise.}
-  \end{cases}
-  \end{split}
-\end{equation}
-
-\begin{lemma}[lem-build$_{∨}$]
-\label{lem:lem-build-or}
-$Γ ⊢ φ$, and $ψ\in \Prop$ then $Γ ⊢ build_{∨}(φ)$.
-\end{lemma}
-
-The function $factor : \Prop → \Prop$  in Eq.~\ref{eq:factor-definition} is intended to work only for right-associative disjunctions, and reduces a disjunction of the same disjunct (e.g., $factor(φ ∨ (φ ∨ \cdots)) \mapsto\ φ$).
-
-\begin{align}
-\begin{split}
-  \label{eq:factor-definition}
-  factor(φ) =
-  \begin{cases}
-    φ₁,  &\text{if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ factor(φ₂)\\
-    φ,   &\text{otherwise.}
-  \end{cases}
-\end{split}
-\end{align}
-
-\begin{lemma}[lem-factor]
-\label{lem:lem-factor}
-  $Γ ⊢ φ$ then $Γ ⊢ factor(φ)$.
-\end{lemma}
-
-Now, with a right-associative proposition,
-$sbuild_{∨}: \Prop → \Prop → \Prop$ in
-Eq.~\ref{eq:strong-build-or-definition} aims to construct the disjunction
-ψ by using each of disjuncts from the proposition φ. This approach to
-build a disjunction from another is inspired on the description
-\citeauthor{bohme2010}~\cite{bohme2010} to prove equality between nested
-disjunctions.
-
-\begin{align}
-  \begin{split}
-  \label{eq:strong-build-or-definition}
-    sbuild_{∨}(φ, ψ) =
-    \begin{cases}
-      factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ)),  &\text{if }φ≡ φ₁ ∨ φ₂\\
-      build_{∨}(φ, ψ),  & \text{otherwise.}
-    \end{cases}
-  \end{split}
-\end{align}
-
-\begin{lemma}[lem-sbuild$_{∨}$]
-\label{lem:lem-sbuild-or}
-$Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ sbuild_{∨}(φ, ψ)$.
-\end{lemma}
-
-Let see the following example of the idea behind $sbuild_{∨}$
-function; from the disjunction $(r ∨ (q ∨ p))$, we build the disjunction
-$((p ∨ q) ∨ r)$.
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ q$}
-  \RightLabel{∨-intro₂}
-  \UnaryInfC{$Γ ⊢ p ∨ q$}
-  \RightLabel{∨-intro₁}
-  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-  \AxiomC{$Γ ⊢ p$}
-  \RightLabel{∨-intro₁}
-  \UnaryInfC{$Γ ⊢ p ∨ q$}
-  \RightLabel{∨-intro₁}
-  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-  \RightLabel{∨-elim}
-  \BinaryInfC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
-  \end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ r$}
-  \RightLabel{∨-intro₂}
-  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-  \AxiomC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
-
-  \RightLabel{∨-elim}
-  \BinaryInfC{$Γ, r ∨ (q ∨ p) ⊢ (p ∨ q) ∨ r$}
-
-  \RightLabel{⇒-intro}
-  \UnaryInfC{$Γ ⊢ r ∨ (q ∨ p) ⇒ (p ∨ q) ∨ r$}
-
-  \end{bprooftree}
-\end{equation*}
-
-\begin{theorem}[thm-reorder$_{∨}$]
-  \label{thm-reorder-or}
-  $Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$, where,
-  \begin{equation*}
-    \label{eq:reorder-or}
-    reorder_{∨} (φ, ψ) = sbuild_{∨}(rdisj(φ), ψ).
-  \end{equation*}
-\end{theorem}
-
-\begin{proof} Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
-\end{proof}
-
-To work with nest conjunctions of disjunctions (CNFs), we define similar
-functions and theorems as we previously did for disjunctions.
-
-\begin{lemma}[lem-reorder$_{∧}$]
-  \label{lem:lem-reorder-and}
-  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder(φ, ψ)$, where,
-  \begin{align*}
-      \begin{split}
-        reorder_{∧}(φ, ψ) =
-        \begin{cases}
-          φ, &\text{if }φ ≡ ψ\\
-          ψ₁ ∧ ψ₂, &\text{if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁\\
-                  &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂\\
-          φ,       &\text{if } ψ ≡ ψ₁ ∧ ψ₂\\
-          conjunct(φ, ψ) &\text{otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{lemma}[lem-conjunct$_{∨}$]
-  \label{lem:lem-conjunct-or}
-  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$, where,
-  \begin{align*}
-  \begin{split}
-    \label{eq:conjunct-or-definition}
-    conjunct_{∨}(φ, ψ) =
-    \begin{cases}
-      ψ, &\text{if }reorder_{∨}(φ, ψ) ≡ ψ\\
-      ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) ≡ ψ₁\\
-        &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂\\
-      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₁, ψ) ≡ ψ\\
-      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₂, ψ) ≡ ψ\\
-      φ, &\text{otherwise.}
-    \end{cases}
-  \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{theorem}[thm-reorder$_{∧∨}$]
-  \label{thm:thm-reorder-and-or}
-
-  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder_{∧∨}(φ, ψ)$, where,
-
-  \begin{align}
-      \begin{split}
-      reorder_{∧∨}(φ, ψ)=
-        \begin{cases}
-          ψ, &\text{if } φ≡ψ\\
-          ψ, &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
-             &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
-          φ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂\\
-          conjunct_{∨}(φ, ψ) &\text{otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align}
-\end{theorem}
-
-% --------------------------------------------------------------------
-
-\subsubsection{Resolve.}
-\label{sssec:resolve}
-
-The \resolve rule is a generalization version for resolution in propositional logic since the formulas are not shaped always as the theorem expect (see Fig.~\ref{fig:metis-inferences}).
-
-Since our approach is mere syntactic, in order to apply such a
-theorem, we perform rearrangements inside the formulas to match with
-the pattern expected by the resolution theorem.
-
-\begin{lemma}[lem-rsol]
-  \label{lem:lem-rsol}
-  $Γ ⊢ φ$ then $Γ ⊢ rsol(φ)$, where,
-  \begin{align*}
-      \begin{split}
-        rsol(φ) =
-        \begin{cases}
-          φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
-          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
-          φ, &\text{otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{theorem}[thm-resolve]
-  \label{thm:thm-resolve}
-  $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ\in\Prop$ then $Γ ⊢ resolve(φ₁, φ₂, l, ψ)$, where,
-  \begin{equation*}
-    resolve(φ₁, φ₂, l, ψ) =
-      rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨} (φ₂, ¬ l ∨ ψ)).
-  \end{equation*}
-\end{theorem}
-
-\begin{proof}
-\begin{equation*}
-  \begin{bprooftree}
-    \AxiomC{$Γ ⊢ φ₁$}
-    \RightLabel{thm-reorder$_{∨}$}
-    \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ)$}
-
-    \AxiomC{$Γ ⊢ φ₂$}
-    \RightLabel{thm-reorder$_{∨}$}
-    \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
-
-    \RightLabel{∧-intro}
-    \BinaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
-    \RightLabel{lem-rsol}
-    \UnaryInfC{$Γ ⊢ rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ))$}
-  \end{bprooftree}
-  \end{equation*}
-\end{proof}
-
-% subsubsection resolve (end)
-% --------------------------------------------------------------------
-
-% --------------------------------------------------------------------
-
-\subsubsection{Normal Forms.}
-\label{sssec:normal_forms}
-
-A negative normal form for the formula φ is one in which negations
-appear only in the literals and the expression is in terms only of
-the boolean operators (¬, ∧, ∨).
-
-To transform a formula φ to its equivalent \abbre{NNF} form, we
-apply recursively the following equations. The function type for
-\name{nnf} is $\Prop \to \Prop$.
-
-\begin{lemma}[lem-nnf]
-  \label{lem:lem-nnf}
-  $Γ ⊢ φ$ then $Γ ⊢ nnf(φ)$, where,
-  \begin{align*}
-    \begin{split}
-    \label{eq:nnf-definition}
-    nnf(φ) =
-      \begin{cases}
-      nnf(φ₁) ∧ nnf(φ₂),
-         &\text{if }φ ≡ φ₁ ∧ φ₂ \\
-      nnf(φ₁) ∨ nnf(φ₂),
-         &\text{if }φ ≡ φ₁ ∨ φ₂ \\
-      nnf(¬ φ₁ ∨ φ₂),
-         &\text{if }φ ≡ φ₁ ⇒ φ₂ \\
-      nnf(φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁),
-         &\text{if }φ ≡ φ₁ ⇔ φ₂ \\
-      nnf(¬ φ₁ ∨ ¬ φ₂),
-         &\text{if }φ ≡ ¬ (φ₁ ∧ φ₂) \\
-      nnf(¬ φ₁ ∧ ¬ φ₂),
-         &\text{if }φ ≡ ¬ (φ₁ ∨ φ₂) \\
-      nnf(φ₁),
-         &\text{if }φ ≡ ¬ ¬ φ₁ \\
-      nnf(¬ (φ₂ ∨ ¬ φ₁)),
-         &\text{if }φ ≡ ¬ (φ₁ ⇒ φ₂) \\
-      nnf(¬ (φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁)),
-         &\text{if }φ ≡ ¬ (φ₁ ⇔ φ₂) \\
-      ⊥,  &\text{if }φ ≡ ¬ ⊤ \\
-      ⊤,  &\text{if }φ ≡ ¬ ⊥ \\
-      φ,  & \text{otherwise}.
-      \end{cases}
-    \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{lemma}[lem-dist$_{∨}$]
-  \label{lem:lem-dist-or}
-  $Γ ⊢ φ$ then $Γ ⊢ dist_{∨}(φ)$, where,
-  \begin{align*}
-      \begin{split}
-      dist_{∨} =
-        \begin{cases}
-          dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃),
-            &\text{if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
-          dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃),
-            &\text{if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
-          φ, &\text{otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{lemma}[lem-dist]
-  \label{lem:lem-dist}
-  $Γ ⊢ φ$ then $Γ ⊢ dist(φ)$, where,
-  \begin{align*}
-      \begin{split}
-      dist =
-        \begin{cases}
-          dist(φ₁) ∧ dist(φ₂),
-            &\text{if }φ ≡ φ₁ ∧ φ₂\\
-          dist_{∨}(dist(φ₁) ∨ dist(φ₂)),
-            &\text{if }φ ≡ φ₁ ∨ φ₂\\
-          φ, &\text{otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{proof} Sketch. Case when $φ ≡ φ₁ ∨ φ₂$.\\
-For $i = 1, 2$,
-\begin{equation}
-  \begin{bprooftree}
-    \RightLabel{assume}
-    \AxiomC{$Γ, φ_{i} ⊢ φ_{i}$}
-    \RightLabel{lem-dist}
-    \UnaryInfC{$Γ ⊢ dist(φ_{i})$}
-    \RightLabel{∨-intro$_{1,2}$}
-    \UnaryInfC{$Γ, φ_{i} ⊢ dist(φ₁) ∨ dist(φ₂)$}
-    \RightLabel{lem-dist$_{∨}$}
-    \UnaryInfC{$Γ, φ_{i} ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$.}
-    \end{bprooftree}
-\end{equation}
-Then, by using the ∨-elim rule, from the last derivation above we derive
-$Γ, φ₁ ∨ φ₂ ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$, and the lemma follows.
-\end{proof}
-
-\begin{theorem}[thm-cnf]
-\label{thm:thm-cnf}
-  $Γ ⊢ φ$ then $Γ ⊢ cnf(φ)$, where,
-  \begin{equation}
-    cnf(φ) = (dist \circ nnf) (\varphi).
-  \end{equation}
-\end{theorem}
-
-\begin{proof}
-  Composition of the Lemma \ref{lem:lem-dist} and Lemma \ref{lem:lem-nnf}.
-\end{proof}
-% subsubsection normal_forms (end)
-% --------------------------------------------------------------------
-
-% --------------------------------------------------------------------
-
-\subsubsection{Clausification.}
-\label{sssec:clausification}
-
-\begin{theorem}[thm-clausify]
-\label{thm:thm_clausify}
-  $Γ ⊢ φ$ and $ψ \in\Prop$ then $Γ ⊢ clausify(φ, ψ)$, where,
-  \begin{align}
-      clausify(φ,ψ) =
-      \begin{cases}
-        ψ, &\text{ if }φ≡ψ\\
-        reorder_{∧∨}(cnf(φ), ψ), &\text{otherwise.}
-      \end{cases}
-  \end{align}
-\end{theorem}
-
-\begin{proof} When $φ ≡ ψ$, we use the $subs$ theorem Eq.~\ref{eq:substitution-theorem}. Otherwise, we use Theorem \ref{thm:thm-reorder-and-or} and Theorem \ref{thm:thm-cnf}.
-\end{proof}
-
-% subsubsection clausification (end)
-% --------------------------------------------------------------------
-
-% --------------------------------------------------------------------
-\subsubsection{Normalization.}
-\label{sssec:normalization}
-
-In a disjunction, $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$, we say $ψ ∈_{∨} φ$,
-if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
-Then, we define the $rm_{∨}$ function to remove in a right-associative disjunction φ, those propositions ψ repeated in the formula.
-
-\begin{equation*}
-\label{eq:rm-or}
-  rm_{∨}(φ) =
-  \begin{cases}
-    rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂, φ₁ ∈_{∨} φ₂\\
-    φ₁ ∨ rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
-    φ,  &\text{otherwise.}
-  \end{cases}
-\end{equation*}
-
-Since, our goal consists of normalizing prepositions in \abbre{CNF}, we also need to generalize $rm_{∨}$ to work with conjunctions. We define $rm_{∧∨}$ function for that purpose.
-
-\begin{equation*}
-\label{eq:rm-and-or}
-  rm_{∧∨}(φ) =
-  \begin{cases}
-    rm_{∧∨}(φ₁) ∧ rm_{∧∨}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
-    rm_{∨}(rdisj(φ)),  &\text{otherwise.}
-  \end{cases}
-\end{equation*}
-
-Now, we have removed redundancies in the disjunctions, we move forward and we remove redundancies at the level of the conjunction of the CNFs by applying the $rm_{∧}$ function.
+% Then, the type-checker will
+% recognize structurally smaller arguments by using the lexicographic
+% order~\cite{Abel2002} for such kind of functions.
+
+% In other words, we take a general recursive function $f: \Prop \to \Prop$.
+% and we redefine that function as
+% $f: \Prop \to \Nat \to \Prop$, and perform the recursion
+% using induction on the structure of the \Nat type.
+
+% Let us consider the following example to exhibit the technique
+% mentioned above for an inner function in the \strip inference.
+
+% \begin{align}
+% \begin{split}
+% \label{eq:unshunt-definition}
+% &unshunt_{0}(φ) =\\
+% &\hspace{3mm}\begin{cases}
+% unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
+%   & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+% unshunt_{0}(φ₁ ⇒ φ₂) ∧ unshunt_{0}(φ₁ ⇒ φ₃),
+%   & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
+% φ, &\text{otherwise.}
+% \end{cases}
+% \end{split}
+% \end{align}
+
+% From the definition above, the size of the argument, ((φ₁ ∧ φ₂) ⇒ φ₃),
+% is not structurally smaller than the input formula, (φ₁ ⇒ (φ₂ ⇒ φ₃)), since ((φ₁ ∧ φ₂) ⇒ φ₃) is not a subformula of (φ₁ ⇒ (φ₂ ⇒ φ₃)).
+
+% Thus, we define the function
+% $unshunt_{1} : \Prop \to \Nat \to \Prop$
+% by structural recursion in its second argument in
+% Eq.~(\ref{eq:unshunt-structured}).
+
+% \begin{align}
+% \label{eq:unshunt-structured}
+% \begin{split}
+% &unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\
+% &unshunt_{1}(φ, \suc(n)) =\\
+% &\hspace{3mm}\begin{cases}
+% unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
+%   &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+% unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ unshunt_{1}(φ₁ ⇒ φ₃, n),
+%    &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
+% \end{cases}
+% \end{split}
+% \end{align}
+
+% As we mentioned above, the natural number in the second argument of the
+% function used in Eq.~(\ref{eq:unshunt-structured}) stands for a complexity
+% measure of the function, in this case $unshunt_{1}$ function.
+
+% A \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
+% and presented in \cite{VanDalen1994} as \emph{the rank for a
+% proposition}, is a function $\Prop \to \Nat$ that assigns a natural
+% number for a proposition φ as follows.
+
+% \begin{equation*}
+% \label{eq:rank-definition}
+% rank(φ)=
+% \begin{cases}
+% 0, &\text{for atomic }φ \\
+% rank(φ₁) + c_{¬},  &\text{if } φ ≡ \neg φ₁ \\
+% \max{(rank(φ₁),rank(φ₂))} + c_{\square},
+%   &\text{if } φ ≡ φ₁\,\square\, φ₂.
+% \end{cases}
+% \end{equation*}
+
+% where $c_{¬}$ or $c_{\square}$ is a non-negative integer called the
+% complexity of the connective.
+
+% Recall, we want to maintain the same outputs as the original unshunt
+% does in Eq.~(\ref{eq:unshunt-definition}) and the complexity measure of it,
+% is a bound for the number of times this function can call itself.
+
+% Therefore, we define an appropriate complexity measure
+% $unshunt_{cm}: \Prop → \NN$ for our $unshunt_{1}$ function presented in
+% Eq.~(\ref{eq:unshunt-rank-definition}).
+
+% \begin{align}
+% \begin{split}
+% \label{eq:unshunt-rank-definition}
+% &unshunt_{cm}(φ) =\\
+% &\hspace{3mm}
+% \begin{cases}
+% unshunt_{cm}(φ₃) + 2, &\text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+% \max(unshunt_{cm}(φ₂),unshunt_{cm}(φ₃)) + 1,
+%   &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
+% 0, &\text{otherwise.}
+% \end{cases}
+% \end{split}
+% \end{align}
+
+% Finally, the curated version of $unshunt_{0}$ function is presented
+% in Eq.~(\ref{eq:unshunt-fixed}).
+
+% \begin{equation}
+% \label{eq:unshunt-fixed}
+% unshunt(\varphi) := unshunt_{1}(\varphi, unshunt_{cm}(\varphi)).
+% \end{equation}
+
+% For a more complete treatment of general recursion, and how to
+% define well-founded and well-structural recursive functions, we refer
+% the reader to Ref.~\cite{Bove2005}, where Bove and Capettra described
+% not only general recursion, but they also treat mutual recursive
+% function, among other kinds.
+
+% % ................................................
+
+% \subsection{Emulating \Metis' Inference Rules}
+% \label{ssec:emulating-inferences}
+
+% \subsubsection{Splitting a Goal.}
+% \label{sssec:splitting-goal}
+
+% The goal of a problem to be proved by \Metis is processed to generate new
+% propositions, the new targets, \Metis calls these formulas
+% \emph{subgoals}.
+
+% The conjunction of these subgoals is a proposition equivalent to the
+% original goal. Then, we find a refutation for each subgoal in the \Metis' \TSTP derivation.
+
+% Nevertheless, \Metis does not provide neither an explanation for the user about the process in its \TSTP derivations nor in its documentation.
+
+% In the following, we show how Theorem.~\ref{thm:thm-strip} proves the correctness of the process mentioned above.
+But first, let prove some lemmas for $unshunt$ function presented in Eq.~(\ref{eq:unshunt-fixed}),
+% and $split$ function from the definition in Eq.~(\ref{eq:split-definition}).
+
+% \begin{lemma}[lem-unshunt]
+%   \label{lem:unshunt}
+%   $Γ ⊢ unshunt(φ)$, then $Γ ⊢ φ$.
+% \end{lemma}
+
+% \begin{proof} Use induction on the cases defined by the outcome of the
+% $unshunt$ function in Eq.~(\ref{eq:unshunt-structured}).
+% When $n = 0$, by definition, $Γ ⊢ φ$.
+% When $n = 1$, we apply the following theorem from~\cite{AgdaProp}
+
+% \begin{equation*}
+% \texttt{∧⇒-to-⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
+% \end{equation*}
+
+% For $n > 1$, we will use induction on the structure of second
+% argument.
+
+% (φ₁ ⇒ (φ₂ ⇒ φ₃))
+% \begin{equation*}
+%   \begin{bprooftree}
+%   \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
+%   \RightLabel{By def.}
+%   \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
+%   \RightLabel{lem-unshunt}
+%   \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
+%   \RightLabel{∧⇒-to-⇒⇒}
+%   \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).}
+%   \end{bprooftree}
+% \end{equation*}
+
+% Second, using the following theorem from \cite{AgdaProp},
+
+% \begin{equation*}
+%   \texttt{⇒∧-to-⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).
+% \end{equation*}
+
+% ($φ₁ ⇒ (φ₂ ∧ φ₃)$)
+% \begin{equation*}
+% \scalebox{0.95}{
+% ($\mathcal{D}_1$)
+% \begin{bprooftree}
+% \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n) ∧ unshunt(φ₁ ⇒ φ₃, n)$}
+% \RightLabel{∧-proj₁}
+% \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n)$}
+% \RightLabel{By def.}
+% \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n-1)$}
+% \RightLabel{lem-unshunt}
+% \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$,}
+% \end{bprooftree}
+% }
+% \end{equation*}
+
+% \begin{equation*}
+% (\mathcal{D}_2)
+% \begin{bprooftree}
+% \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂) ∧ unshunt(φ₁ ⇒ φ₃)$}
+% \RightLabel{∧-proj₂}
+% \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n)$}
+% \RightLabel{By def.}
+% \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n-1)$}
+% \RightLabel{lem-unshunt}
+% \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$,}
+% \end{bprooftree}
+% \end{equation*}
+
+% \begin{equation*}
+%   \begin{bprooftree}
+%   \AxiomC{$\mathcal{D}_1$}
+%   \AxiomC{$\mathcal{D}_2$}
+%   \RightLabel{∧-intro}
+%   \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
+%   \RightLabel{⇒∧⇒-to-⇒∧}
+%   \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).}
+%   \end{bprooftree}
+% \end{equation*}
+% \end{proof}
+
+% Now, let us consider the $split$ function presented in
+% Eq.~(\ref{eq:split-definition}) that yields a conjunction of subgoals from a proposition, the goal in \Metis.
+
+% \begin{equation}
+% \label{eq:split-definition}
+% \mysplit(φ) =
+% \begin{cases}
+% unshunt(\mysplit(φ₁)) &\text{if }φ ≡ φ₁ ∧ φ₂\\
+% ∧\ unshunt(φ₁ ⇒ \mysplit(φ₂)), &\\[2.5mm]
+% unshunt(¬ φ₁ ⇒ \mysplit(φ₂)),
+%   & \text{if }φ ≡ φ₁ ∨ φ₂\\[2.5mm]
+% unshunt(φ₁ ⇒ \mysplit(φ₂)),
+%   & \text{if }φ ≡ φ₁ ⇒ φ₂\\[2.5mm]
+% unshunt(φ₁ ⇒ \mysplit(φ₂))
+%   & \text{if }φ ≡ φ₁ ⇔ φ₂\\
+% ∧\ unshunt(φ₂ ⇒ \mysplit(φ₁)),
+%   &\\[2.5mm]
+% unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
+%   & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂)\\[2.5mm]
+% unshunt(\mysplit(¬ φ₁))
+%   & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
+% ∧\ unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂)),
+%   &\\[2.5mm]
+% unshunt(\mysplit(φ₁))
+%   & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
+% ∧\ unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
+%   &\\[2.5mm]
+% unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
+%   & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
+% ∧\ unshunt(¬ φ₂ ⇒ \mysplit(φ₁)),
+%   &\\[2.5mm]
+% unshunt(\mysplit(φ₁)),
+%   & \text{if }φ ≡ ¬ ¬ φ₁\\
+% ⊤,
+%   & \text{if }φ ≡ ¬ ⊥\\
+% ⊥,
+%   & \text{if }φ ≡ ¬ ⊤.
+% \end{cases}
+% \end{equation}
+
+% The definition above suffers termination problems since it is not
+% a structural recursion. Therefore, we have reformulated Def.~\ref{eq:split-definition} to solve such a issue following the technique
+% described in Section~\ref{ssec:structural-recursion}.
+% Here and below, we refer to $split$ as the function after applying
+% the process mentioned above.
+
+% \begin{lemma}[\thmsplit] $Γ ⊢ \mysplit(φ)$ then $Γ ⊢ φ$.
+% \label{lem:lem-split}
+% \end{lemma}
+
+% \begin{proof} We now proceed by induction on the structure of the
+% formula φ in the definition of Eq.~(\ref{eq:split-definition}).
+% For a complete proof, we refer the reader to~\cite{AgdaMetis}.\\[3mm]
+
+% ($φ ≡ φ₁ ∧ φ₂$). We get a proof for each conjunct and using the introduction rule for conjunction, the result follows.
+
+% \begin{equation*}
+% (\mathcal{D})\hspace{3mm}
+%   \begin{bprooftree}
+%   \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+%   \RightLabel{By def.}
+%   \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+%   \RightLabel{∧-proj₁}
+%   \UnaryInfC{$Γ ⊢ unshunt(φ₁)$}
+%   \RightLabel{lem-unshunt}
+%   \UnaryInfC{$Γ ⊢ φ₁$.}
+%   \end{bprooftree}
+% \end{equation*}
+
+% \begin{equation*}
+%   \begin{bprooftree}
+%   \AxiomC{$\mathcal{D}$}
+%   \UnaryInfC{Γ ⊢ φ₁}
+%   \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+%   \RightLabel{By def.}
+%   \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+%   \RightLabel{$∧$-proj$₂$}
+%   \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+%   \RightLabel{lem-unshunt}
+%   \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+%   \RightLabel{$⇒$-elim}
+%   \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
+%   \RightLabel{\thmsplit}
+%   \UnaryInfC{$Γ ⊢ φ₂.$}
+%   \end{bprooftree}
+% \end{equation*}
+
+% \vskip 3mm
+
+% ($φ ≡ φ₁ ⇒ φ₂$).
+% \begin{equation*}
+%   \begin{bprooftree}
+%   \AxiomC{}
+%   \RightLabel{assume φ₁}
+%   \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
+%   \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
+%   \RightLabel{By def.}
+%   \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+%   \RightLabel{lem-unshunt}
+%   \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+%   \RightLabel{weaken φ₁}
+%   \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+%   \RightLabel{⇒-elim}
+%   \BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂,n-1)$}
+%   \RightLabel{\thmsplit}
+%   \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
+%   \RightLabel{⇒-intro}
+%   \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$.}
+%   \end{bprooftree}
+% \end{equation*}
+% \vskip 3mm
+
+% (φ ≡ ¬ (φ₁ ∨ φ₂)). We show $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$. Using their conjunction by the introduction rule, and De Morgan Law, the results follows.
+
+% \begin{equation*}
+% (\mathcal{D})\hspace{3mm}
+% \begin{bprooftree}
+% \AxiomC{$Γ ⊢ \mysplit(φ, n)$}
+% \RightLabel{By def.}
+% \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
+% \RightLabel{∧-proj₁}
+% \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁)$}
+% \RightLabel{lem-unshunt}
+% \UnaryInfC{$Γ ⊢ ¬ φ₁$,}
+% \end{bprooftree}
+% \end{equation*}
+
+% \begin{equation*}
+%   \begin{bprooftree}
+%   \AxiomC{$\mathcal{D}$}
+%   \UnaryInfC{$Γ ⊢ ¬ φ₁$}
+
+%   \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
+%   \RightLabel{By def.}
+%   \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
+%   \RightLabel{∧-proj₂}
+%   \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
+%   \RightLabel{lem-unshunt}
+%   \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+%   \RightLabel{⇒-elim}
+%   \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
+%   \RightLabel{\thmsplit}
+%   \UnaryInfC{$Γ ⊢ ¬ φ₂.$}
+%   \end{bprooftree}
+% \end{equation*}
+% \end{proof}
+
+% \begin{theorem}[thm-strip]
+% \label{thm:thm-strip}
+%  If $s_i$ are the subgoals for the goal φ, and
+% $\{ Γ ⊢ s_i \}_{i}$, then $Γ ⊢ φ$.
+% \end{theorem}
+
+% \begin{proof}
+% \begin{equation*}
+%   \begin{bprooftree}
+%   \AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i}$}
+%   \RightLabel{∧-intro}
+%   \UnaryInfC{$Γ ⊢ \bigwedge_i s_i$}
+
+%   \AxiomC{$\mysplit(φ) ≡ \bigwedge_i s_i $}
+%   \RightLabel{subst}
+%   \BinaryInfC{$Γ ⊢ \mysplit(φ) $}
+
+%   \RightLabel{\thmsplit}
+%   \UnaryInfC{$Γ ⊢ φ$.}
+% \end{bprooftree}
+% \end{equation*}
+% Where, the $subst$ theorem is,
+% \begin{equation}
+%   \label{eq:substitution-theorem}
+%   \begin{bprooftree}
+%   \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
+%   \RightLabel{subst}
+%   \BinaryInfC{$Γ ⊢ ψ$.}
+%   \end{bprooftree}
+% \end{equation}
+% \end{proof}
+
+% % -------------------------------------------------------------------
+% \subsubsection{splitting a Conjunct}
+% \label{sssec:splitting-a-conjunct}
+
+% The \conjunct rule extracts from a conjunction, one of its conjunct.
+% To achieve this, we use projections repeatedly until we finally find
+% the conjunct required.
+
+% \begin{align}
+%   \begin{split}
+%   conjunct(φ, ψ) =
+%     \begin{cases}
+%       ψ, &\text{if }φ ≡ ψ\\
+%       ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₁, ψ)≡ ψ\\
+%       ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₂, ψ)≡ ψ\\
+%       φ, &\text{otherwise.}
+%     \end{cases}
+%   \end{split}
+% \end{align}
+
+% \begin{theorem}[thm-conjunct]
+%   \label{thm:thm-conjunct}
+%   $Γ ⊢ φ$, and $ψ \in \Prop$ , then $Γ ⊢ conjunct(φ, ψ)$.
+% \end{theorem}
+
+% \begin{proof}
+% When φ ≡ ψ, from $Γ ⊢ conjunct(φ, ψ)$ by normalization, we get $Γ ⊢ ψ$.
+% By using $subst$ theorem Eq.~(\ref{eq:substitution-theorem}), we get the desire conclusion. If the proposition φ is a conjunction, and $ψ ≡ conjunct(φ_{i}, ψ)$
+% for some $i = 1,\ 2$, then,
+
+% \begin{equation}
+%   \begin{bprooftree}
+%   \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
+%   \RightLabel{∧-proj$_{i}$}
+%   \UnaryInfC{$Γ ⊢ φ_{i}$}
+%   \UnaryInfC{$Γ ⊢ conjunct(φ_{i}, ψ)$}
+%   \AxiomC{$conjunct(φ_{i}, ψ) ≡ ψ$}
+%   \RightLabel{subst}
+%   \BinaryInfC{$Γ ⊢ ψ$.}
+%   \end{bprooftree}
+% \end{equation}
+
+% The last statement follows by using the hypothesis and the proof is complete.
+% \end{proof}
+
+% % subsubsection splitting-a-conjunct (end)
+% % -------------------------------------------------------------------
+
+% % ------------------------------------------------------------------------
+
+% \subsubsection{Reordering.}
+
+% Syntactically speaking, showing the logic equivalence between two conjunctive normal forms is a matter of rearrangements of the conjunctions
+% but also of the inner disjunctions inside the propositions involved.
+% \improvement{Make clear: we are dealing with CNFs, and prove equivalence between two formulas is equivalent to show two trees are  isomorphic.
+% And that problem is NP-hard, and for that, we mostly do brute force.}
+
+% We provide some useful theorems to perform the following tasks.
+
+% \begin{itemize}
+%   \item Reorder a disjunction like $φ = φ₁ ∨ φ₂ ∨ \cdots$ to match with another disjunction $ψ = ψ₁ ∨ ψ₂ ∨ \cdots$, when $φ$ is a disjunct of $ψ$.
+%   \item Reorder a conjunction of disjuncts (CNF), $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another CNF formula equivalent $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$.
+% \end{itemize}
+
+% First, we define the $rdisj$ function in Eq.~(\ref{eq:rdisj-def}) to convert a disjunction to be a right-associative disjunction, and following
+% a similar approach we define the $rconj$ function for conjunctions.
+
+% \begin{align}
+%   \begin{split}
+%     \label{eq:rdisj-def}
+%     rdisj(φ) =
+%     \begin{cases}
+%     rdisj(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
+%     φ₁ ∨ rdisj(φ₂),         & \text{if } φ ≡ φ₁ ∨ φ₂\\
+%     φ,                      & \text{otherwise.}
+%     \end{cases}
+%   \end{split}
+% \end{align}
+
+% \begin{lemma}[lem-rdisj]
+% \label{lem:lem-rdisj}
+%   $Γ ⊢ φ$ then $Γ ⊢ rdisj(φ)$.
+% \end{lemma}
+
+% The following function, $build_{∨} : \Prop → \Prop → \Prop$ in Eq.~(\ref{eq:build-or}), intends to construct a disjunction from another disjunction, specifically, we want to rearrange the disjuncts in the source formula to match with the target disjunction for syntactic
+% equivalence.
+
+% \begin{equation}
+%   \begin{split}
+%   \label{eq:build-or}
+%   &build_{∨}(φ, ψ) =\\
+%   &\hspace{3mm}
+%   \begin{cases}
+%   ψ, &\text{if } φ ≡ ψ\\
+%   ψ, &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
+%   φ, &\text{otherwise.}
+%   \end{cases}
+%   \end{split}
+% \end{equation}
+
+% \begin{lemma}[lem-build$_{∨}$]
+% \label{lem:lem-build-or}
+% $Γ ⊢ φ$, and $ψ\in \Prop$ then $Γ ⊢ build_{∨}(φ)$.
+% \end{lemma}
+
+% The function $factor : \Prop → \Prop$  in Eq.~(\ref{eq:factor-definition}) is intended to work only for right-associative disjunctions, and reduces a disjunction of the same disjunct (e.g., $factor(φ ∨ (φ ∨ \cdots)) \mapsto\ φ$).
+
+% \begin{align}
+% \begin{split}
+%   \label{eq:factor-definition}
+%   factor(φ) =
+%   \begin{cases}
+%     φ₁,  &\text{if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ factor(φ₂)\\
+%     φ,   &\text{otherwise.}
+%   \end{cases}
+% \end{split}
+% \end{align}
+
+% \begin{lemma}[lem-factor]
+% \label{lem:lem-factor}
+%   $Γ ⊢ φ$ then $Γ ⊢ factor(φ)$.
+% \end{lemma}
+
+% Now, with a right-associative disjunction by applying $rdisj$ function to
+% a proposition $φ$, $sbuild_{∨}: \Prop → \Prop → \Prop$ in
+% Eq.~(\ref{eq:strong-build-or-definition}) aims to construct the disjunction
+% ψ by using each of its disjuncts from the proposition φ. This approach to
+% build a disjunction from another is inspired on the description in
+% \citeauthor{bohme2010}~\cite{bohme2010} to prove equality between nested
+% disjunctions. \change{Make clear this, It's not clear the difference with build-or and sbuild-or.}
+
+% \begin{align}
+%   \begin{split}
+%   \label{eq:strong-build-or-definition}
+%     sbuild_{∨}(φ, ψ) =
+%     \begin{cases}
+%       factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ)),  &\text{if }φ≡ φ₁ ∨ φ₂\\
+%       build_{∨}(φ, ψ),  & \text{otherwise.}
+%     \end{cases}
+%   \end{split}
+% \end{align}
+
+% \begin{lemma}[lem-sbuild$_{∨}$]
+% \label{lem:lem-sbuild-or}
+% $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ sbuild_{∨}(φ, ψ)$.
+% \end{lemma}
+
+% Let see the following example of the idea behind $sbuild_{∨}$
+% function; from the disjunction $(r ∨ (q ∨ p))$, we build the disjunction
+% $((p ∨ q) ∨ r)$.
+
+% \begin{equation*}
+%   \begin{bprooftree}
+%   \AxiomC{$Γ ⊢ q$}
+%   \RightLabel{∨-intro₂}
+%   \UnaryInfC{$Γ ⊢ p ∨ q$}
+%   \RightLabel{∨-intro₁}
+%   \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
+
+%   \AxiomC{$Γ ⊢ p$}
+%   \RightLabel{∨-intro₁}
+%   \UnaryInfC{$Γ ⊢ p ∨ q$}
+%   \RightLabel{∨-intro₁}
+%   \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
+
+%   \RightLabel{∨-elim}
+%   \BinaryInfC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
+%   \end{bprooftree}
+% \end{equation*}
+
+% \begin{equation*}
+%   \begin{bprooftree}
+%   \AxiomC{$Γ ⊢ r$}
+%   \RightLabel{∨-intro₂}
+%   \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
+
+%   \AxiomC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
+
+%   \RightLabel{∨-elim}
+%   \BinaryInfC{$Γ, r ∨ (q ∨ p) ⊢ (p ∨ q) ∨ r$}
+
+%   \RightLabel{⇒-intro}
+%   \UnaryInfC{$Γ ⊢ r ∨ (q ∨ p) ⇒ (p ∨ q) ∨ r$}
+
+%   \end{bprooftree}
+% \end{equation*}
+
+% \begin{theorem}[thm-reorder$_{∨}$]
+%   \label{thm-reorder-or}
+%   $Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$, where,
+%   \begin{equation*}
+%     \label{eq:reorder-or}
+%     reorder_{∨} (φ, ψ) = sbuild_{∨}(rdisj(φ), ψ).
+%   \end{equation*}
+% \end{theorem}
+
+% \begin{proof} Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
+% \end{proof}
+
+% To work with nest conjunctions of disjunctions (CNFs), we define similar
+% functions and theorems as we previously did for disjunctions.
+
+% \begin{lemma}[lem-reorder$_{∧}$]
+%   \label{lem:lem-reorder-and}
+%   $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder(φ, ψ)$, where,
+%   \begin{align*}
+%       \begin{split}
+%         reorder_{∧}(φ, ψ) =
+%         \begin{cases}
+%           φ, &\text{if }φ ≡ ψ\\
+%           ψ₁ ∧ ψ₂, &\text{if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁\\
+%                   &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂\\
+%           φ,       &\text{if } ψ ≡ ψ₁ ∧ ψ₂\\
+%           conjunct(φ, ψ) &\text{otherwise.}
+%         \end{cases}
+%       \end{split}
+%   \end{align*}
+% \end{lemma}
+
+% \begin{lemma}[lem-conjunct$_{∨}$]
+%   \label{lem:lem-conjunct-or}
+%   $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$, where,
+%   \improvement{The first case is not implemented in Agda}
+%   \begin{align*}
+%   \begin{split}
+%     \label{eq:conjunct-or-definition}
+%     conjunct_{∨}(φ, ψ) =
+%     \begin{cases}
+%       ψ, &\text{if }φ ≡ ψ\\
+%       ψ, &\text{if }reorder_{∨}(φ, ψ) ≡ ψ\\
+%       ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) ≡ ψ₁\\
+%         &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂\\
+%       ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₁, ψ) ≡ ψ\\
+%       ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₂, ψ) ≡ ψ\\
+%       φ, &\text{otherwise.}
+%     \end{cases}
+%   \end{split}
+%   \end{align*}
+% \end{lemma}
+
+% \begin{theorem}[thm-reorder$_{∧∨}$]
+%   \label{thm:thm-reorder-and-or}
+
+%   $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder_{∧∨}(φ, ψ)$, where,
+
+%   \begin{align}
+%       \begin{split}
+%       reorder_{∧∨}(φ, ψ)=
+%         \begin{cases}
+%           ψ, &\text{if } φ≡ψ\\
+%           ψ, &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
+%              &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
+%           φ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂\\
+%           conjunct_{∨}(φ, ψ) &\text{otherwise.}
+%         \end{cases}
+%       \end{split}
+%   \end{align}
+% \end{theorem}
+
+% % --------------------------------------------------------------------
+
+% \subsubsection{Resolve.}
+% \label{sssec:resolve}
+
+% The \resolve rule is a generalization version for resolution in propositional logic since the formulas are not shaped always as the aforementioned theorem expects (see Fig.~\ref{fig:metis-inferences}).
+
+% Since our approach is mere syntactic, in order to apply such a
+% theorem, we perform rearrangements inside the formulas to match with
+% the pattern expected by the resolution theorem.
+
+% \begin{lemma}[lem-rsol]
+%   \label{lem:lem-rsol}
+%   $Γ ⊢ φ$ then $Γ ⊢ rsol(φ)$, where,
+%   \begin{align*}
+%       \begin{split}
+%         rsol(φ) =
+%         \begin{cases}
+%           φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
+%           φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
+%           φ, &\text{otherwise.}
+%         \end{cases}
+%       \end{split}
+%   \end{align*}
+% \end{lemma}
+
+% \begin{theorem}[thm-resolve]
+%   \label{thm:thm-resolve}
+%   $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ\in\Prop$ then $Γ ⊢ resolve(φ₁, φ₂, l, ψ)$, where,
+%   \begin{equation*}
+%     resolve(φ₁, φ₂, l, ψ) =
+%       rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨} (φ₂, ¬ l ∨ ψ)).
+%   \end{equation*}
+% \end{theorem}
+
+% \begin{proof}
+% \begin{equation*}
+%   \begin{bprooftree}
+%     \AxiomC{$Γ ⊢ φ₁$}
+%     \RightLabel{thm-reorder$_{∨}$}
+%     \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ)$}
+
+%     \AxiomC{$Γ ⊢ φ₂$}
+%     \RightLabel{thm-reorder$_{∨}$}
+%     \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+
+%     \RightLabel{∧-intro}
+%     \BinaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+%     \RightLabel{lem-rsol}
+%     \UnaryInfC{$Γ ⊢ rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ))$}
+%   \end{bprooftree}
+%   \end{equation*}
+% \end{proof}
+
+% % subsubsection resolve (end)
+% % --------------------------------------------------------------------
+
+% % --------------------------------------------------------------------
+
+% \subsubsection{Normal Forms.}
+% \label{sssec:normal_forms}
+% \change{Here lacks of an introduction!}
+% A negative normal form for the formula φ is one in which negations
+% appear only in the literals and the expression is in terms only of
+% the boolean operators (¬, ∧, ∨).
+
+% To transform a formula φ to its equivalent \abbre{NNF} form, we
+% apply recursively the following equations. The function type for
+% \name{nnf} is $\Prop \to \Prop$.
+
+% \begin{lemma}[lem-nnf]
+%   \label{lem:lem-nnf}
+%   $Γ ⊢ φ$ then $Γ ⊢ nnf(φ)$, where,
+%   \begin{align*}
+%     \begin{split}
+%     \label{eq:nnf-definition}
+%     nnf(φ) =
+%       \begin{cases}
+%       nnf(φ₁) ∧ nnf(φ₂),
+%          &\text{if }φ ≡ φ₁ ∧ φ₂ \\
+%       nnf(φ₁) ∨ nnf(φ₂),
+%          &\text{if }φ ≡ φ₁ ∨ φ₂ \\
+%       nnf(¬ φ₁ ∨ φ₂),
+%          &\text{if }φ ≡ φ₁ ⇒ φ₂ \\
+%       nnf(φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁),
+%          &\text{if }φ ≡ φ₁ ⇔ φ₂ \\
+%       nnf(¬ φ₁ ∨ ¬ φ₂),
+%          &\text{if }φ ≡ ¬ (φ₁ ∧ φ₂) \\
+%       nnf(¬ φ₁ ∧ ¬ φ₂),
+%          &\text{if }φ ≡ ¬ (φ₁ ∨ φ₂) \\
+%       nnf(φ₁),
+%          &\text{if }φ ≡ ¬ ¬ φ₁ \\
+%       nnf(¬ (φ₂ ∨ ¬ φ₁)),
+%          &\text{if }φ ≡ ¬ (φ₁ ⇒ φ₂) \\
+%       nnf(¬ (φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁)),
+%          &\text{if }φ ≡ ¬ (φ₁ ⇔ φ₂) \\
+%       ⊥,  &\text{if }φ ≡ ¬ ⊤ \\
+%       ⊤,  &\text{if }φ ≡ ¬ ⊥ \\
+%       φ,  & \text{otherwise}.
+%       \end{cases}
+%     \end{split}
+%   \end{align*}
+% \end{lemma}
+
+% \begin{lemma}[lem-dist$_{∨}$]
+%   \label{lem:lem-dist-or}
+%   $Γ ⊢ φ$ then $Γ ⊢ dist_{∨}(φ)$, where,
+%   \begin{align*}
+%       \begin{split}
+%       dist_{∨}(φ) =
+%         \begin{cases}
+%           dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃),
+%             &\text{if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
+%           dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃),
+%             &\text{if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
+%           φ, &\text{otherwise.}
+%         \end{cases}
+%       \end{split}
+%   \end{align*}
+% \end{lemma}
+
+% \begin{lemma}[lem-dist]
+%   \label{lem:lem-dist}
+%   $Γ ⊢ φ$ then $Γ ⊢ dist(φ)$, where,
+%   \begin{align*}
+%       \begin{split}
+%       dist(φ) =
+%         \begin{cases}
+%           dist(φ₁) ∧ dist(φ₂),
+%             &\text{if }φ ≡ φ₁ ∧ φ₂\\
+%           dist_{∨}(dist(φ₁) ∨ dist(φ₂)),
+%             &\text{if }φ ≡ φ₁ ∨ φ₂\\
+%           φ, &\text{otherwise.}
+%         \end{cases}
+%       \end{split}
+%   \end{align*}
+% \end{lemma}
+
+% \begin{sketchproof}
+% Case when $φ ≡ φ₁ ∨ φ₂$.\\
+% For $i = 1, 2$,
+% \begin{equation}
+%   \begin{bprooftree}
+%     \RightLabel{assume}
+%     \AxiomC{$Γ, φ_{i} ⊢ φ_{i}$}
+%     \RightLabel{lem-dist}
+%     \UnaryInfC{$Γ ⊢ dist(φ_{i})$}
+%     \RightLabel{∨-intro$_{1,2}$}
+%     \UnaryInfC{$Γ, φ_{i} ⊢ dist(φ₁) ∨ dist(φ₂)$}
+%     \RightLabel{lem-dist$_{∨}$}
+%     \UnaryInfC{$Γ, φ_{i} ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$.}
+%     \end{bprooftree}
+% \end{equation}
+% Then, by using the ∨-elim rule, from the last derivation above we derive
+% $Γ, φ₁ ∨ φ₂ ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$, and the lemma follows.
+% \end{sketchproof}
+
+% \begin{theorem}[thm-cnf]
+% \label{thm:thm-cnf}
+%   $Γ ⊢ φ$ then $Γ ⊢ cnf(φ)$, where,
+%   \begin{equation}
+%     cnf(φ) = (dist \circ nnf) (\varphi).
+%   \end{equation}
+% \end{theorem}
+
+% \begin{proof}
+%   Composition of the Lemma \ref{lem:lem-dist} and Lemma \ref{lem:lem-nnf}.
+% \end{proof}
+% % subsubsection normal_forms (end)
+% % --------------------------------------------------------------------
+
+% % --------------------------------------------------------------------
+
+% \subsubsection{Clausification.}
+% \label{sssec:clausification}
+
+% \begin{theorem}[thm-clausify]
+% \label{thm:thm-clausify}
+%   $Γ ⊢ φ$ and $ψ \in\Prop$ then $Γ ⊢ clausify(φ, ψ)$, where,
+%   \begin{align}
+%       clausify(φ,ψ) =
+%       \begin{cases}
+%         ψ, &\text{ if }φ≡ψ\\
+%         reorder_{∧∨}(cnf(φ), ψ), &\text{otherwise.}
+%       \end{cases}
+%   \end{align}
+% \end{theorem}
+
+% \begin{proof} When $φ ≡ ψ$, we use the $subs$ theorem Eq.~(\ref{eq:substitution-theorem}). Otherwise, we use Theorem \ref{thm:thm-reorder-and-or} and Theorem \ref{thm:thm-cnf}.
+% \end{proof}
+
+% % subsubsection clausification (end)
+% % --------------------------------------------------------------------
+
+% % --------------------------------------------------------------------
+% \subsubsection{Normalization.}
+% \label{sssec:normalization}
+
+% In a disjunction, $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$, we say $ψ ∈_{∨} φ$,
+% if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
+% Then, we define the $rm_{∨}$ function to remove in a right-associative disjunction φ, those propositions ψ repeated in the formula.
+
+% \begin{equation*}
+% \label{eq:rm-or}
+%   rm_{∨}(φ) =
+%   \begin{cases}
+%     rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂, φ₁ ∈_{∨} φ₂\\
+%     φ₁ ∨ rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
+%     φ,  &\text{otherwise.}
+%   \end{cases}
+% \end{equation*}
+
+% Since, our goal consists of normalizing prepositions in \abbre{CNF}, we also need to generalize $rm_{∨}$ to work with conjunctions. We define $rm_{∧∨}$ function for that purpose.
+
+% \begin{equation*}
+% \label{eq:rm-and-or}
+%   rm_{∧∨}(φ) =
+%   \begin{cases}
+%     rm_{∧∨}(φ₁) ∧ rm_{∧∨}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
+%     rm_{∨}(rdisj(φ)),  &\text{otherwise.}
+%   \end{cases}
+% \end{equation*}
+
+% Now, we have removed redundancies in the disjunctions, we move forward and we remove redundancies at the level of the conjunction of the CNFs by applying the $rm_{∧}$ function.
 We define $ψ ∈_{∧} φ$ similar as we described above for disjunction.
 In a conjunction, $φ = φ₁ ∧ φ₂ ∧ \cdots ∧ φₙ$, we say
-$ψ ∈_{∧} φ$, if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
-
-\begin{equation*}
-\label{eq:rm-and}
-  rm_{∧}(φ) =
-  \begin{cases}
-    rm_{∧}(φ₁) ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂, φ₁ ∈_{∧} φ₂\\
-    φ₁ ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
-    φ,  &\text{otherwise.}
-  \end{cases}
-\end{equation*}
-
-Finally, we remove redundancies in a proposition assuming that it is given in conjunctive normal form and right-associative, by composing the functions described above in the Eq.~\ref{eq:redun-ast}
-for the function $redun^{*}$.
-
-\begin{equation*}
-  \label{eq:redun-ast}
-  redun^{*} = rm_{∧} ∘ rm_{∧∨}.
-\end{equation*}
-
-Then, performing rearrangements to match with the expected output
-by $redon^{*}$ function.
-
-\begin{equation*}
-  \label{eq:redun}
-  redun(φ) = reorder_{∧∨}(φ, redun^{*}(φ)).
-\end{equation*}
-
-\begin{theorem}[thm-redun]
-  \label{thm:thm_redun}
-  $Γ ⊢ φ$ then $Γ ⊢ redun(φ)$.
-\end{theorem}
-
-\begin{proof}
-Use in Theorem~\ref{thm:thm-reorder-and-or} with $ψ$ equals to
-$redun^{*}(φ)$.
-\end{proof}
-
-% subsection normalization (end)
-% --------------------------------------------------------------------
-\begin{lemma}[lem-rmPEM$_{∨}$]
-  \label{lem:lem-rmPEM-or}
-  \begin{align*}
-  \label{eq:rmPEM-or}
-    \begin{split}
-    rmPEM_{∨}(φ) =
-      \begin{cases}
-        ⊤, &\text{if }φ ≡ ¬ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
-        ⊤, &\text{if}φ ≡ ¬ φ₁ ∨ φ₂,\ rmPEM_{∨}(φ₂) ≡ ⊤\\
-        ¬ φ₁ ∨ rmPEM_{∨}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∨ φ₂\\
-        ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ ¬φ₁ ∈_{∨} φ₂ \\
-        ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ rmPEM_{∨}(φ₂) ≡ ⊤\\
-        φ₁ ∨ rmPEM_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
-        φ, &\text{otherwise.}
-      \end{cases}
-    \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{lemma}[lem-rmPEM$_{∧∨}$]
-  \label{lem:lem-rmPEM-and-or}
-  \begin{equation*}
-    \label{eq:rmPEM-and-or}
-    rmPEM_{∧∨}(φ) =
-    \begin{cases}
-      rmPEM_{∨}(φ₁) ∧ rmPEM_{∨∧}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
-      rmPEM_{∨}(φ), &\text{otherwise.}
-    \end{cases}
-  \end{equation*}
-\end{lemma}
-
-\begin{lemma}[lem-rmBot$_{∧}$]
-  \label{lem:lem-rmbot-and}
-   $Γ ⊢ φ$ then $Γ ⊢ rmBot_{∧}(φ)$, where,
-  \begin{equation*}
-    \label{eq:rmBot-and}
-    rmBot_{∧}(φ) =
-    \begin{cases}
-      ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
-      ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ rmBot_{∧}(φ₂) ≡ ⊥\\
-      ¬ φ₁ ∧ rmBot_{∧}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∧ φ₂\\
-      ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
-      ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ rmBot_{∧}(φ₂) ≡ ⊥\\
-      φ₁ ∧ rmBot_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
-      φ, &\text{otherwise.}
-    \end{cases}
-  \end{equation*}
-\end{lemma}
-
-\begin{lemma}[lem-canon]
-  \label{lem:lem-canon}
-  \begin{align*}
-  \begin{split}
-  &canon(φ) =\\
-  &\hspace{3mm}
-  \begin{cases}
-      canon(φⱼ), &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊤, i,j = 1,2, i≠j\\
-     ⊥, &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊥, i = 1,2\\
-     canon(φ₁) ∧ canon(φ₂), &\text{if } φ ≡ φ₁ ∧ φ₂\\
-     ⊤, &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊤, i = 1,2\\
-     canon(φⱼ), &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊥,  i,j = 1,2, i≠j\\
-     canon(φ₁) ∨ canon(φ₂), &\text{if } φ ≡ φ₁ ∨ φ₂\\
-     φ &\text{otherwise.}
-    \end{cases}
-  \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{theorem}[thm-canonicalize] % (fold)
-  \label{thm:thm-canonicalize}
-  $Γ ⊢ φ$ then $Γ ⊢ canonicalize(φ)$, where,
-  \begin{equation*}
-    canonicalize =
-     canon ∘ rmBot_{∧} ∘ rmPEM_{∧∨} ∘ redun ∘ rconj ∘ cnf.
-  \end{equation*}
-\end{theorem}
-
-The \canonicalize rule acts in \Metis' \TSTP derivations in three main cases. First, introducing the
-negation of a subgoal. Second, to simplify an intermediate derivation.
-Third, introducing an axiom or a definition of the.
-To justify the two first cases, we use the Theorem~\ref{thm:thm-canonicalize}. For the last case, we use the Lemma~\ref{lem:lem-nnf}.
-
-% -------------------------------------------------------------------
-\subsubsection{Simplify}
-\label{sssec:simplify}
-
-% subsubsection simplify (end)
-% -------------------------------------------------------------------
+% $ψ ∈_{∧} φ$, if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
+
+% \begin{equation*}
+% \label{eq:rm-and}
+%   rm_{∧}(φ) =
+%   \begin{cases}
+%     rm_{∧}(φ₁) ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂, φ₁ ∈_{∧} φ₂\\
+%     φ₁ ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
+%     φ,  &\text{otherwise.}
+%   \end{cases}
+% \end{equation*}
+
+% Finally, we remove redundancies in a proposition assuming that it is given in conjunctive normal form and right-associative, by composing the functions described above in the Eq.~(\ref{eq:redun-ast})
+% for the function $redun^{*}$.
+
+% \begin{equation*}
+%   \label{eq:redun-ast}
+%   redun^{*} = rm_{∧} ∘ rm_{∧∨}.
+% \end{equation*}
+
+% Then, performing rearrangements to match with the expected output
+% by $redon^{*}$ function.
+
+% \begin{equation*}
+%   \label{eq:redun}
+%   redun(φ) = reorder_{∧∨}(φ, redun^{*}(φ)).
+% \end{equation*}
+
+% \begin{theorem}[thm-redun]
+%   \label{thm:thm_redun}
+%   $Γ ⊢ φ$ then $Γ ⊢ redun(φ)$.
+% \end{theorem}
+
+% \begin{proof}
+% Use in Theorem~\ref{thm:thm-reorder-and-or} with $ψ$ equals to
+% $redun^{*}(φ)$.
+% \end{proof}
+
+% \improvement{We need here a text, or a comment about what
+% is going next.}
+
+% % subsection normalization (end)
+% % --------------------------------------------------------------------
+% \begin{lemma}[lem-rmPEM$_{∨}$]
+%   \label{lem:lem-rmPEM-or}
+%   \begin{align*}
+%   \label{eq:rmPEM-or}
+%     \begin{split}
+%     rmPEM_{∨}(φ) =
+%       \begin{cases}
+%         ⊤, &\text{if }φ ≡ ¬ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
+%         ⊤, &\text{if}φ ≡ ¬ φ₁ ∨ φ₂,\ rmPEM_{∨}(φ₂) ≡ ⊤\\
+%         ¬ φ₁ ∨ rmPEM_{∨}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∨ φ₂\\
+%         ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ ¬φ₁ ∈_{∨} φ₂ \\
+%         ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ rmPEM_{∨}(φ₂) ≡ ⊤\\
+%         φ₁ ∨ rmPEM_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
+%         φ, &\text{otherwise.}
+%       \end{cases}
+%     \end{split}
+%   \end{align*}
+% \end{lemma}
+
+% \begin{lemma}[lem-rmPEM$_{∧∨}$]
+%   \label{lem:lem-rmPEM-and-or}
+%   \begin{equation*}
+%     \label{eq:rmPEM-and-or}
+%     rmPEM_{∧∨}(φ) =
+%     \begin{cases}
+%       rmPEM_{∨}(φ₁) ∧ rmPEM_{∨∧}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
+%       rmPEM_{∨}(φ), &\text{otherwise.}
+%     \end{cases}
+%   \end{equation*}
+% \end{lemma}
+
+% \begin{lemma}[lem-rmBot$_{∧}$]
+%   \label{lem:lem-rmbot-and}
+%    $Γ ⊢ φ$ then $Γ ⊢ rmBot_{∧}(φ)$, where,
+%   \begin{equation*}
+%     \label{eq:rmBot-and}
+%     rmBot_{∧}(φ) =
+%     \begin{cases}
+%       ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
+%       ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ rmBot_{∧}(φ₂) ≡ ⊥\\
+%       ¬ φ₁ ∧ rmBot_{∧}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∧ φ₂\\
+%       ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
+%       ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ rmBot_{∧}(φ₂) ≡ ⊥\\
+%       φ₁ ∧ rmBot_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
+%       φ, &\text{otherwise.}
+%     \end{cases}
+%   \end{equation*}
+% \end{lemma}
+
+% \begin{lemma}[lem-canon]
+%   \label{lem:lem-canon}
+%   \begin{align*}
+%   \begin{split}
+%   &canon(φ) =\\
+%   &\hspace{3mm}
+%   \begin{cases}
+%       canon(φⱼ), &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊤,\\
+%                  &\text{for same } i,j = 1,2, i≠j\\
+%      ⊥, &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊥, i = 1,2\\
+%      canon(φ₁) ∧ canon(φ₂), &\text{if } φ ≡ φ₁ ∧ φ₂\\
+%      ⊤, &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊤, i = 1,2\\
+%      canon(φⱼ), &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊥,\\
+%                 &\text{for same } i,j = 1,2, i≠j\\
+%      canon(φ₁) ∨ canon(φ₂), &\text{if } φ ≡ φ₁ ∨ φ₂\\
+%      φ, &\text{otherwise.}
+%     \end{cases}
+%   \end{split}
+%   \end{align*}
+% \end{lemma}
+
+% \begin{theorem}[thm-canonicalize] % (fold)
+%   \label{thm:thm-canonicalize}
+%   $Γ ⊢ φ$ then $Γ ⊢ canonicalize(φ)$, where,
+%   \begin{equation*}
+%     canonicalize =
+%      canon ∘ rmBot_{∧} ∘ rmPEM_{∧∨} ∘ redun ∘ rconj ∘ cnf.
+%   \end{equation*}
+% \end{theorem}
+
+% The \canonicalize rule acts in \Metis' \TSTP derivations in three main cases. First, introducing the
+% negation of a subgoal. Second, to simplify an intermediate derivation.
+% Third, introducing an axiom or a definition of the.
+% To justify the two first cases, we use the Theorem~\ref{thm:thm-canonicalize}. For the last case, we use the Lemma~\ref{lem:lem-nnf}.
+
+% % -------------------------------------------------------------------
+% \subsubsection{Simplify}
+% \label{sssec:simplify}
+
+% The \simplify rule is the application of the the lemma showed above,
+% but also the following lemmas that intend to reduce a list of derivations,
+% a conjunction of their formulas into a one smaller.
+
+% \improvement{Missing theorems here.}
+
+% % subsubsection simplify (end)
+% % -------------------------------------------------------------------
 

### 2017-10-11 paper/sections/metis-language-and-proofs.tex
[ paper ] translated the end of the metis subsection.

@@
 
-Una demostración de Metis para un problema logica propositional sin igualdad puede incluir en su derivacion \TSTP hasta 6 diferentes reglas de inferencia:
-\canonicalize, \clausify, \conjunct, \negate, \simplify, y \strip.
-Contrastando el codigo fuente de Metis y las reglas de la figura~\ref{fig:metis-inferences}. Podemos observar lo siguiente:
-la regla de inferencia \emph{axiom} aparece por medio  de las reglas:
-\canonicalize, \clausify, \conjunct, and \simplify.
-La regla de inferencia \emph{resolve} aparece con el mismo nombre, \resolve.
-Las ultimas reglas son \strip y \negate que son la representacion de la regla de inferencia \emph{assume}, las cuales sirven para
-introducir en una demostracion la conjectura que se pretende demostrar, a esta conjetura nos referiremos tambien como el goal.
-Toda prueba de un goal, tiene en su derivacion la negacion de dicho goal,
-o de uno o varias proposiciones equivalentes, porque recordemos que
-las pruebas son por refutacion.
+A proof derivation reply by \Metis for a classic propositional logic
+without equality include in the \TSTP file at least six different inferences rules. These are exactly the same six rules from the
+\Metis's description in Fig.~\ref{fig:metis-inferences}. The aforementioned rules are \canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
+Based on the scope of the problems (CPL) but also from the list of 6 inferences rules described on the \Metis' documentation, only 3 rules can be applied: \emph{axiom}, \emph{assume} and \emph{resolve}.
 
-De esta manera concluimos con una breve descripcion del probador de teoremas Metis.
-En lo siguiente, intentaremos justificar derivación de Metis paso por paso.
-Para esto,estudiamos cada una de las reglas antes mencionadas en más detalle, y para cada una de ellas, proponemos un teorema para emular
-su  razonamiento.
+Comparing these rules with \TSTP derivations but also after looking at the
+\Metis' source code, we speculate to say that for example.
+The \emph{axiom} rule appears by using one the rules: \canonicalize, \clausify, \conjunct, and \simplify. The \emph{resolve} appears using the
+same name with the binary rule \resolve. The \emph{assume} rule is the inference rule \negate to introduce the negation of the conjecture since
+\Metis replies refutation proofs.
+The \strip rule works with the conjecture, also named as the \emph{goal} of the problem.
+This intends for finding a equivalent conjunction of easier or smaller in size propositions, named \emph{subgoals}.
+
+This section briefly describes the \Metis prover for our purposes.
+In the next section, we discuss the proof-reconstruction for \Metis \TSTP derivations. In addition, we show a more detailed discussion around
+the aforementioned proof rules.
 

### 2017-10-11 paper/sections/proof-reconstruction.tex
[ paper ] translated the end of the metis subsection.

@@
 
-% The proof-reconstruction approach proposed here consists of a series
-% of steps similar to the workflow presented by \citeauthor{sultana2015} in
-% \cite{sultana2015}. This process is a translation from a source
-% system to a target system. In our case, the system of origin, the
-% automatic theorem prover, is \Metis; the target system is a proof
-% assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types is valid (see a description of \Agda for its main features in
-% Section~\ref{sec:implementation}).
-% The overview of the proof-reconstruction is presented in
-% Fig.~\ref{fig:proof-reconstruction-workflow}, the process can begin with
-% a problem in \CPL that we encode in \TPTP format to be sent as the
-% input of the \Metis prover.
-% The algorithms of \Metis in Step~3 find
-% a solution if the problem is a theorem, in that case \Metis replies
-% with a derivation in \TSTP format of the proof, otherwise the problem is counter feasible.
+The proof-reconstruction approach proposed here consists of a series
+of steps similar to the workflow presented by \citeauthor{sultana2015} in
+\cite{sultana2015}. This process is a translation from a source
+system to a target system. In our case, the system of origin, the
+automatic theorem prover, is \Metis; the target system is a proof
+assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types is valid (see a description of \Agda for its main features in
+Section~\ref{sec:implementation}).
+The overview of the proof-reconstruction is presented in
+Fig.~\ref{fig:proof-reconstruction-workflow}, the process can begin with
+a problem in \CPL that we encode in \TPTP format to be sent as the
+input of the \Metis prover.
+The algorithms of \Metis in Step~3 find
+a solution if the problem is a theorem, in that case \Metis replies
+with a derivation in \TSTP format of the proof, otherwise the problem is counter feasible.
 

### 2017-10-11 paper/sections/metis-language-and-proofs.tex
[ paper ] fixed the last paragraph on metis' section.

@@
 
-A proof derivation reply by \Metis for a classic propositional logic
-without equality include in the \TSTP file at least six different inferences rules. These are exactly the same six rules from the
-\Metis's description in Fig.~\ref{fig:metis-inferences}. The aforementioned rules are \canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
-Based on the scope of the problems (CPL) but also from the list of 6 inferences rules described on the \Metis' documentation, only 3 rules can be applied: \emph{axiom}, \emph{assume} and \emph{resolve}.
+A \TSTP proof derivation reply by \Metis for a classic propositional logic without equality can includes  at least six different inferences rules.
+These are not exactly the same rules showed in \Metis's description from the Fig.~\ref{fig:metis-inferences}.
+The observed rules are \canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
+Based on the scope of the problems (CPL) but also from the \Metis' documentation, only 3 rules can be applied here: \emph{axiom}, \emph{assume} and \emph{resolve} rule.
 
-Comparing these rules with \TSTP derivations but also after looking at the
-\Metis' source code, we speculate to say that for example.
-The \emph{axiom} rule appears by using one the rules: \canonicalize, \clausify, \conjunct, and \simplify. The \emph{resolve} appears using the
-same name with the binary rule \resolve. The \emph{assume} rule is the inference rule \negate to introduce the negation of the conjecture since
-\Metis replies refutation proofs.
-The \strip rule works with the conjecture, also named as the \emph{goal} of the problem.
-This intends for finding a equivalent conjunction of easier or smaller in size propositions, named \emph{subgoals}.
+Comparing these rules with \TSTP derivations and  after looking at the
+\Metis' source code, we believe the rules in \TSTP derivations comes from the following explanation.
+The \emph{axiom} rule appears by using one the rules: \canonicalize, \clausify, \conjunct, and \simplify. The \emph{resolve} rule appears using the
+same name in the binary resolution rule, \resolve.
+The \emph{assume} rule is the inference rule \negate that introduces the negation of a conjecture, since \Metis replies refutation proofs.
+To end with the rules, we found the \strip rule.
+This one works only for conjectures.
+In \Metis, a conjecture is also named as the \emph{goal} of the problem.
+This rule intends to prove conjuncts from a equivalent conjunction of the goal.
+These conjuncts intends to split the goal into less complex propositions, not necessary smaller.
+These conjuncts are named \emph{subgoals}.
+At the end, a derivation is a proof of the goal, composed by proofs of each of these subgoals.
 
 This section briefly describes the \Metis prover for our purposes.
-In the next section, we discuss the proof-reconstruction for \Metis \TSTP derivations. In addition, we show a more detailed discussion around
+In the next section, we discuss the proof-reconstruction for \Metis' \TSTP derivations. In addition, we show a more detailed discussion around
 the aforementioned proof rules.

### 2017-10-12 paper/sections/metis-language-and-proofs.tex
[ paper ] metis section fixes.

@@
 $p\, \vdash \neg (p \wedge \neg p) ∨ (q \wedge \neg q)$
-in \TPTP syntax as follows, declaring an \tptpaxiom $p$, and the
-expected conclusion, the  \tptpconjecture
-\verb!~ ((p & ~ p) | (q & ~ q))!.
+in \TPTP syntax. We begin by declaring the $p$ axiom using the keyword,
+\verb!axiom!. Later, we include the expected conclusion using the \verb!conjecture! keyword.
 
@@
 \end{verbatim}
+
+This study aimed to address proof-reconstruction for refutation
+proofs. Then, we annotated \abbre{CPL} problems using \verb!fof! formulas.
+\Metis converts \abbre{FOF} formulas to \abbre{CNF} clauses to look for a
+refutation.
 
@@
 % -------------------------------------------------------------------
+
+\subsubsection{Proof Rules.}
+\label{ssec:proof-rules}
+
+Based on the scope of the problems treated in this research (CPL), only three rules from Fig.~\ref{fig:metis-inferences} apply: \emph{axiom}, \emph{assume} and \emph{resolve} rule.
+
+Nonetheless, the \Metis' \TSTP derivations includes other different rules. They are \canonicalize, \clausify, \conjunct, \simplify, \negate, and
+\strip.
+
+Comparing the \Metis' rules by looking at the \Metis' source code, we conclude the following.
+
+When \Metis looks for a refutation to prove a \verb!fof! problem.
+A conjecture, also named as the \emph{goal} of the problem, is stripped into
+subgoals.
+The subgoals are the conjuncts of a general conjunction equivalents to the goal.
+The \Metis' strategy here is Divide and Conquer.
+To prove the goal, it proves independently each subgoal.
+They are less complex or even smaller propositions.
+Then, then conjunction of all subgoal proofs must prove the goal.
+Unfortunately, this last reasoning is not explicit in its \TSTP derivations.
+
+The \emph{axiom} rule appears by using one the rules: \canonicalize, \clausify, \conjunct, and \simplify. The \emph{resolve} rule appears using the
+same name in the binary resolution rule, \resolve.
+The \emph{assume} rule is the inference rule \negate that introduces the negation of a conjecture, since \Metis replies refutation proofs.
+To end with the rules, we found the \strip rule.
+This one works only for conjectures.
+In \Metis, a conjecture is also named as the \emph{goal} of the problem.
+This rule intends to prove conjuncts from a equivalent conjunction of the goal.
+These conjuncts intends to split the goal into less complex propositions, not necessary smaller.
+These conjuncts are named \emph{subgoals}.
+At the end, a derivation is a proof of the goal, composed by proofs of each of these subgoals.
+
+This section briefly describes the \Metis prover for our purposes.
+In the next section, we discuss the proof-reconstruction for \Metis' \TSTP derivations. In addition, we show a more detailed discussion around
+the aforementioned proof rules.
 
@@
 \]
-\caption{Inference rules of the \texttt{Metis} prover.}
+\caption{CNF Inference rules of the \texttt{Metis} prover.}
 \label{fig:metis-inferences}
@@
 
-% -------------------------------------------------------------------
-
-\subsubsection{Proof Rules.}
-\label{ssec:proof-rules}
-
-A \TSTP proof derivation reply by \Metis for a classic propositional logic without equality can includes  at least six different inferences rules.
-These are not exactly the same rules showed in \Metis's description from the Fig.~\ref{fig:metis-inferences}.
-The observed rules are \canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
-Based on the scope of the problems (CPL) but also from the \Metis' documentation, only 3 rules can be applied here: \emph{axiom}, \emph{assume} and \emph{resolve} rule.
-
-Comparing these rules with \TSTP derivations and  after looking at the
-\Metis' source code, we believe the rules in \TSTP derivations comes from the following explanation.
-The \emph{axiom} rule appears by using one the rules: \canonicalize, \clausify, \conjunct, and \simplify. The \emph{resolve} rule appears using the
-same name in the binary resolution rule, \resolve.
-The \emph{assume} rule is the inference rule \negate that introduces the negation of a conjecture, since \Metis replies refutation proofs.
-To end with the rules, we found the \strip rule.
-This one works only for conjectures.
-In \Metis, a conjecture is also named as the \emph{goal} of the problem.
-This rule intends to prove conjuncts from a equivalent conjunction of the goal.
-These conjuncts intends to split the goal into less complex propositions, not necessary smaller.
-These conjuncts are named \emph{subgoals}.
-At the end, a derivation is a proof of the goal, composed by proofs of each of these subgoals.
-
-This section briefly describes the \Metis prover for our purposes.
-In the next section, we discuss the proof-reconstruction for \Metis' \TSTP derivations. In addition, we show a more detailed discussion around
-the aforementioned proof rules.
-
 \end{document}

### 2017-10-12 paper/sections/metis-language-and-proofs.tex
[ paper ] last revision to metis' section.

@@
 \subsubsection{Proof Rules.}
-\label{ssec:proof-rules}
+\label{sssec:proof-rules}
 
-Based on the scope of the problems treated in this research (CPL), only three rules from Fig.~\ref{fig:metis-inferences} apply: \emph{axiom}, \emph{assume} and \emph{resolve} rule.
-
-Nonetheless, the \Metis' \TSTP derivations includes other different rules. They are \canonicalize, \clausify, \conjunct, \simplify, \negate, and
+Since the scope of the problems treated in this research is CPL, from the list of \Metis inference rules in~\ref{fig:metis-inferences}, we found that only three rules apply: \emph{axiom}, \emph{assume} and \emph{resolve} rule.
+Nonetheless, \TSTP derivations replied by \Metis use other rules. They are \canonicalize, \clausify, \conjunct, \simplify, \negate, and
 \strip.
 
-Comparing the \Metis' rules by looking at the \Metis' source code, we conclude the following.
+\Metis looks for a refutation to prove \verb!fof! problems.
+A \verb!fof!
+problem contains the conjecture also named the \emph{goal} in the problem.
+This goal is stripped into subgoals by using the \strip rule.
+The subgoals are the conjuncts in a general conjunction that is equivalent to the aforementioned goal.
+Therefore, to prove the goal, \Metis proves independently each subgoal since they tend to be less complex or even smaller propositions.
+At the end, the conjunction of all subgoal proofs must prove the goal.
+Nevertheless, this last reasoning is not explicit neither in the \TSTP derivations nor in the \Metis' documentation.
+Since \Metis replies refutation proofs, to prove each subgoal, in the \TSTP derivation, the inference rule \negate introduces the negation of such subgoals.
+The \negate rule is a specification of the \emph{assume} rule.
 
-When \Metis looks for a refutation to prove a \verb!fof! problem.
-A conjecture, also named as the \emph{goal} of the problem, is stripped into
-subgoals.
-The subgoals are the conjuncts of a general conjunction equivalents to the goal.
-The \Metis' strategy here is Divide and Conquer.
-To prove the goal, it proves independently each subgoal.
-They are less complex or even smaller propositions.
-Then, then conjunction of all subgoal proofs must prove the goal.
-Unfortunately, this last reasoning is not explicit in its \TSTP derivations.
-
-The \emph{axiom} rule appears by using one the rules: \canonicalize, \clausify, \conjunct, and \simplify. The \emph{resolve} rule appears using the
-same name in the binary resolution rule, \resolve.
-The \emph{assume} rule is the inference rule \negate that introduces the negation of a conjecture, since \Metis replies refutation proofs.
-To end with the rules, we found the \strip rule.
-This one works only for conjectures.
-In \Metis, a conjecture is also named as the \emph{goal} of the problem.
-This rule intends to prove conjuncts from a equivalent conjunction of the goal.
-These conjuncts intends to split the goal into less complex propositions, not necessary smaller.
-These conjuncts are named \emph{subgoals}.
-At the end, a derivation is a proof of the goal, composed by proofs of each of these subgoals.
-
-This section briefly describes the \Metis prover for our purposes.
-In the next section, we discuss the proof-reconstruction for \Metis' \TSTP derivations. In addition, we show a more detailed discussion around
-the aforementioned proof rules.
+Finally, \emph{axiom} rule appears in \TSTP derivation by one of the following rules to in the problem a \verb!fof!
+axiom: \canonicalize, \clausify, \conjunct, or \simplify.
+Then, the last rule remains is \emph{resolve}, it appears by the
+binary rule, \resolve, the version in \Metis of the resolution
+theorem. For a more detailed description of this rules see the Section~\ref{sec:proof-reconsruction}.
 

### 2017-10-12 paper/sections/abstract.tex
added text.
[ paper ] perliminaries added.
Paper (#36)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity m

@@
 In this paper, we describe our approach to reconstruct and verify in
-\Agda, a  proof assistant for type theory, solutions obtained by
-\Metis, an automatic theorem prover, to problems in classical 
+the proof assistant for type theory \Agda, solutions obtained by
+the  automatic theorem prover \Metis to problems in classical
 propositional logic. The translation method consists of justifying
@@
 
-\keywords{proof reconstruction
-\unsure{proof reconstruction or proof-reconstruction},
-\Agda, automatic theorem prover, classical propositional logic, \Metis.}
+\keywords{proof-reconstruction, \Agda, automatic theorem prover,
+classical propositional logic, \Metis.}
 

### 2017-10-12 paper/sections/introduction.tex
[ paper ] diagram added.
[ paper ] fixed athena process description.

@@
 their algorithms and their correctness (see, for example, bugs in
-\ATPs~\cite{Keller2013}, \cite{Bohme2011}, \cite{Fleury2014} and
+\ATPs~\cite{Keller2013,Bohme2011,Fleury2014} and
 \cite{Kanso2012}). We mention some of these tools in the related
@@
 
-In this paper, we describe the integration of \Metis prover with the
-proof assistant \Agda by parsing \TSTP derivations to generate \Agda
-proof-terms. We structure the paper as follows.
-We briefly mention notation and syntax of the classical propositional
-logic in Section \ref{sec:preliminaries}.
-In Section \ref{sec:metis-language-and-proofs}, we introduce the
+In this paper, we ported a subset of the \Metis' inference rules to
+\Agda, the propositional fragmented without equality.
+The formalization of these rules allowed us to justify step-by-step \Metis' \TSTP derivations by translating automatically to \Agda by a proof-reconstruction tool built for this research named \Athena.
+We structure the paper as follows.
+We briefly mention some notation and syntax of the classical propositional logic in Section~\ref{ssec:CPL}.
+In Section~\ref{ssec:metis-language-and-proofs}, we introduce the
 \Metis prover and its deduction system.
-In Section \ref{sec:proof-reconstruction}, we present our
+In Section~\ref{sec:proof-reconstruction}, we present our
 approach to reconstruct proofs deliver by \Metis in type theory.
-We listed some conclusions and future work in Section
-\ref{sec:conclusions}. At the end, we list some related works in
-proof reconstruction in Section \ref{sec:related-work}.
-The appendix \textsc{A} shows a complete example of the proof
-reconstruction workflow.
+We listed some conclusions and future work in
+Section~\ref{sec:conclusions}. Some related works with this paper is presented in Section~\ref{sec:related-work}.
+Finally, we provide a complete example in the appendix \textsc{A} of the proof reconstruction workflow.
 

### 2017-10-12 paper/sections/metis-language-and-proofs.tex
[ paper ] fixed athena process description.

@@
 delivered by \name{leanCoP}~\cite{Farber2016}.
-
-In this paper, we ported a subset of the \Metis' inference rules to
-\Agda, the propositional fragmented without equality, that allows us to justify step-by-step the proofs delivered in
-\TSTP format generated by the prover \Metis.
 
@@
 
+\begin{figure}
+\centering
+  \begin{bprooftree}\tt
+    \AxiomC{}
+    \RightLabel{negate}
+    \UnaryInfC{$\neg p$}
+    \RightLabel{strip}
+    \UnaryInfC{$\neg p$}
+    \AxiomC{}
+    \RightLabel{axiom}
+    \UnaryInfC{$p$}
+    \RightLabel{canonicalize}
+    \UnaryInfC{$p$}
+    \RightLabel{simplify}
+    \BinaryInfC{$⊥$}
+    \RightLabel{canonicalize}
+    \UnaryInfC{$⊥$}
+  \end{bprooftree}
+  \caption{The \Metis' proof tree for $p \vdash p$ from the
+  derivation in Fig.~\ref{fig:metis-proof-tstp}}
+  \label{fig:metis-example}
+\end{figure}
+
 \Metis looks for a refutation to prove \verb!fof! problems.
@@
 binary rule, \resolve, the version in \Metis of the resolution
-theorem. For a more detailed description of this rules see the Section~\ref{sec:proof-reconsruction}.
+theorem. For a more detailed description of this rules see the Section~\ref{sec:proof-reconstruction}.
 
 \subsubsection{Proofs.}
-\label{ssec:metis-proofs}
+\label{sssec:metis-proofs}
 

### 2017-10-12 paper/sections/preliminaries.tex
Paper (#36)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

* [ paper ] minor changes.

@@
 \label{sec:preliminaries}
-
-Before describe the proof reconstruction, we need some definitions
-and some convention notations.
 
@@
 propositional formula.
-%Then, $ϕ_i \in \Prop$ for all $i \in \mathbb{N}$.
-$⊥, ⊤ \in \Prop$.
-If $φ, ψ\in \Prop$, then $(φ\ \square\ ψ) \in \Prop$,
-where $(φ\ \square\ ψ)$ stands for a proposition that use the $\square$ symbol as one of the binary connectives mentioned above.
-If $φ \in \Prop$, then $(¬ φ) \in \Prop$.
+\begin{itemize}
+\item $⊥, ⊤ \in \Prop$.
+\item $ϕ_i \in \Prop$ for all $i \in \mathbb{N}$.
+\item If $φ, ψ\in \Prop$, then $(φ\ \square\ ψ) \in \Prop$,
+where the $\square$ symbol is one of the binary connectives mentioned above.
+\item If $φ \in \Prop$, then $(¬ φ) \in \Prop$.
+\end{itemize}
 
@@
   \AxiomC{$ψ$}
-  \RightLabel{∧-intro}
-  \BinaryInfC{$φ ∧ ψ$.}
+  \RightLabel{∧-intro.}
+  \BinaryInfC{$φ ∧ ψ$}
 \end{bprooftree}
@@
 \AxiomC{}
-\RightLabel{PEM}
-\UnaryInfC{$Γ ⊢ φ ∨ ¬ φ$,}
+\RightLabel{PEM,}
+\UnaryInfC{$Γ ⊢ φ ∨ ¬ φ$}
 \end{bprooftree}\qquad
@@
 \AxiomC{$Γ, ¬ φ ⊢ ⊥$}
-\RightLabel{RAA}
-\UnaryInfC{$Γ ⊢ φ$.}
+\RightLabel{RAA.}
+\UnaryInfC{$Γ ⊢ φ$}
 \end{bprooftree}
@@
 the leaves in the tree become the premises, not all necessary
-canceled (see a better discussion about canceling  hypotheses in proof trees in Section 2.4 in \citeauthor{VanDalen1994}~\cite{VanDalen1994}).
+canceled.
+ % (see a better discussion about canceling  hypotheses in proof trees in Section 2.4 in \citeauthor{VanDalen1994}~\cite{VanDalen1994}).
 

### 2017-10-12 paper/sections/proof-reconstruction.tex
[ paper ] fixed athena process description.

@@
 The overview of the proof-reconstruction is presented in
-Fig.~\ref{fig:proof-reconstruction-workflow}, the process can begin with
-a problem in \CPL that we encode in \TPTP format to be sent as the
-input of the \Metis prover.
-The algorithms of \Metis in Step~3 find
-a solution if the problem is a theorem, in that case \Metis replies
-with a derivation in \TSTP format of the proof, otherwise the problem is counter feasible.
-
-% With such a derivation, in Step~5, we process the derivation with our \Haskell translator tool, \Athena~\cite{Athena}.
-% \Athena parses the \TSTP format, analyze the
-% derivation and generates a representation of the natural deduction
-% proof using a tree data structure (see the properties
-% of this tree in Section~\ref{ssec:metis-proofs}).
-% We perform an analysis of the proof-tree removing redundancies,
-% unnecessary steps or unused output from the \TSTP derivation.
-
-% As a result,
-% \Athena generates an \Agda file with the proof-term. We have included
-% in this file, \emph{imports} that call our \Agda libraries that give
-% support for CPL presented in~\cite{AgdaProp}, and support for \Metis'
-% inference rules implemented in~\cite{AgdaMetis}.
-
-% Finally, we use the proof checker in Step~7 to type-check the
-% proof-term. If type-checking succeed, the \TSTP
-% derivation is correct, otherwise when it fails, one of the three
-% actors in the process could be the responsible: \Metis, \Athena, or
-% \Agda.
+Fig.~\ref{fig:proof-reconstruction-workflow}, the process begin with
+a \TPTP file that encodes a problem in \CPL. We use this file as the
+input of the \Metis prover and if the problem is a theorem, \Metis can reply with a derivation in \TSTP format of the proof.
+
+With the \TSTP  derivation from the Step~2, we process the derivation with the \Athena translator tool~\cite{Athena}.
+\Athena parses the \TSTP format, analyzes the
+derivation and generates a representation of the natural deduction
+proof using a tree data structure (see the properties
+of this tree in Section~\ref{sssec:metis-proofs}).
+We perform an analysis of the proof-tree to remove some
+unnecessary steps that introduce redundancies or unused input for
+\Athena.
+
+As a result of using \Athena, we get an \Agda file, the proof-term. To generate this file, \Athena has used names of functions and theorems from \Agda libraries:
+\texttt{agda-prop}~\cite{AgdaProp}, and \texttt{agda-metis}~\cite{AgdaMetis}.
+
+Finally, we type-check the \Agda proof-term. If type-checking succeed, the \TSTP derivation delivered by \Metis was correct.
+In that case \Agda outputs an interface file.
+Otherwise, when type-checking fails, the failure must be investigated by the user, checking \Metis, \Athena, or even \Agda.
 

### 2017-10-13 paper/sections/acknowledgements.tex
[ paper ] working on section three.

@@
 
-We thank Joe Leslie-Hurd for his support with \Metis prover. We also
-acknowledge the work carried out by Alejandro G\'omez-Londo\~no~\cite{Gomez-Londono2015} used as the basis code for our \TSTP
+We thank Joe Leslie-Hurd for his support with its \Metis prover.
+We also acknowledge the work carried out by Alejandro G\'omez-Londo\~no~\cite{Gomez-Londono2015} used as the basis code for our \TSTP
 parsing module.
-% \improvement{We should consider thank Kanso and Anton, to provide
-% us their thesis, discussion, and source code to compare with our
-% work?}
 
@@
 Andreas Abel and Chalmers University of Goteborg, Sweden for
-inviting us to be part of the \Agda Implementors’ Meeting XXV where
-we presented part of this paper.
+inviting us to be part of the \Agda Implementors’ Meeting XXV.
+We honored to present part of the research in this paper.
 

### 2017-10-13 paper/sections/proof-reconstruction.tex
[ paper ] working on section three.

@@
 
-Finally, we type-check the \Agda proof-term. If type-checking succeed, the \TSTP derivation delivered by \Metis was correct.
+Finally, we type-check the \Agda proof-term. If type-checking
+succeed, the \TSTP derivation delivered by \Metis was correct.
 In that case \Agda outputs an interface file.
-Otherwise, when type-checking fails, the failure must be investigated by the user, checking \Metis, \Athena, or even \Agda.
-
-% We are responsible for errors committed in the translation from
-% \TSTP to \Agda: bugs in the parsing module, lack of the coverage of
-% \Metis' inference rules, and last but not least, the pretty print of
-% the proof in \Agda code.
-
-% In the rest of this section, we provide a formal description using
-% type theory to build definitions and theorems for functions
-% necessary to emulate \Metis' inference rules.
-% Some conventions about notations. We will write the
-% type judgments with ``$a : A$'' to denote that $a$ has type
-% $\abbre{A}$. Types are written using small caps.
-% For propositions, we will denote by $φ ≡ ψ$, the syntactic
-% equivalence. We use the \Prop type for propositions and for theorems,
-% the dependent type, $ Γ ⊢ φ$ where $Γ$ has type $\abbre{List} \Prop$ and
-% $φ$ has type $\Prop$.
-
-% % ...................................................................
-
-% % section section_name (end)
-% \subsection{Structural Recursion}
-% \label{ssec:structural-recursion}
-
-% To emulate \Metis' inference rules in type theory,
-% we observed that transformations performed by some rules were given by \emph{general recursive} functions.
-% But algorithms based on general recursions can not be translated
-% directly in type theory since it is not a guarantee they terminate.
-
-% Then, we solve the termination problem by modifying problematic functions
-% to be \emph{structural recursive}~\cite{Coquand1992,Abel2002,Bove2005}.
-
-% We use the same notion of \emph{structurally smaller} from
-% \citeauthor{Abel2002}~\cite{Abel2002} to say, a recursive function is
-% structurally recursive if it calls itself with only
-% \emph{structurally smaller}
-% arguments.
-
-% To convert a general recursive call into a structurally recursive call,
-% we use the \emph{Bounded Recursion} technique presented
-% in~\cite{Bertot2004} but
-% others found in \cite{Coquand1992,Abel2002,Bove2005} could be used.
-% This technique converts a general recursive
-% function into a structural recursive function by adding an additional
-% argument for the function complexity, the bound for the number of times, the function needs to call itself to get the final result.
-
-% Then, we add the natural number $n : \Nat$ in the input of the
-% general recursive function, and perform the recursion over the structure of
-% \Nat type.
-\abbre{Nat} type is the usual type for natural numbers with \zero and \suc as their constructors.
-We consider the common arithmetic operations ($+,\,-,\,*$) and numbers $0,1,2,\dots$ as representations of $\zero, \suc, \suc(\zero), \dots$.
-
-% Then, the type-checker will
-% recognize structurally smaller arguments by using the lexicographic
-% order~\cite{Abel2002} for such kind of functions.
-
-% In other words, we take a general recursive function $f: \Prop \to \Prop$.
-% and we redefine that function as
-% $f: \Prop \to \Nat \to \Prop$, and perform the recursion
-% using induction on the structure of the \Nat type.
-
-% Let us consider the following example to exhibit the technique
-% mentioned above for an inner function in the \strip inference.
-
-% \begin{align}
-% \begin{split}
-% \label{eq:unshunt-definition}
-% &unshunt_{0}(φ) =\\
-% &\hspace{3mm}\begin{cases}
-% unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
-%   & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-% unshunt_{0}(φ₁ ⇒ φ₂) ∧ unshunt_{0}(φ₁ ⇒ φ₃),
-%   & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
-% φ, &\text{otherwise.}
-% \end{cases}
-% \end{split}
-% \end{align}
-
-% From the definition above, the size of the argument, ((φ₁ ∧ φ₂) ⇒ φ₃),
-% is not structurally smaller than the input formula, (φ₁ ⇒ (φ₂ ⇒ φ₃)), since ((φ₁ ∧ φ₂) ⇒ φ₃) is not a subformula of (φ₁ ⇒ (φ₂ ⇒ φ₃)).
-
-% Thus, we define the function
-% $unshunt_{1} : \Prop \to \Nat \to \Prop$
-% by structural recursion in its second argument in
-% Eq.~(\ref{eq:unshunt-structured}).
-
-% \begin{align}
-% \label{eq:unshunt-structured}
-% \begin{split}
-% &unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\
-% &unshunt_{1}(φ, \suc(n)) =\\
-% &\hspace{3mm}\begin{cases}
-% unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
-%   &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-% unshunt_{1}(φ₁ ⇒ φ₂, n) ∧\ unshunt_{1}(φ₁ ⇒ φ₃, n),
-%    &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
-% \end{cases}
-% \end{split}
-% \end{align}
-
-% As we mentioned above, the natural number in the second argument of the
-% function used in Eq.~(\ref{eq:unshunt-structured}) stands for a complexity
-% measure of the function, in this case $unshunt_{1}$ function.
-
-% A \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
-% and presented in \cite{VanDalen1994} as \emph{the rank for a
-% proposition}, is a function $\Prop \to \Nat$ that assigns a natural
-% number for a proposition φ as follows.
-
-% \begin{equation*}
-% \label{eq:rank-definition}
-% rank(φ)=
-% \begin{cases}
-% 0, &\text{for atomic }φ \\
-% rank(φ₁) + c_{¬},  &\text{if } φ ≡ \neg φ₁ \\
-% \max{(rank(φ₁),rank(φ₂))} + c_{\square},
-%   &\text{if } φ ≡ φ₁\,\square\, φ₂.
-% \end{cases}
-% \end{equation*}
-
-% where $c_{¬}$ or $c_{\square}$ is a non-negative integer called the
-% complexity of the connective.
-
-% Recall, we want to maintain the same outputs as the original unshunt
-% does in Eq.~(\ref{eq:unshunt-definition}) and the complexity measure of it,
-% is a bound for the number of times this function can call itself.
-
-% Therefore, we define an appropriate complexity measure
-% $unshunt_{cm}: \Prop → \NN$ for our $unshunt_{1}$ function presented in
-% Eq.~(\ref{eq:unshunt-rank-definition}).
-
-% \begin{align}
-% \begin{split}
-% \label{eq:unshunt-rank-definition}
-% &unshunt_{cm}(φ) =\\
-% &\hspace{3mm}
-% \begin{cases}
-% unshunt_{cm}(φ₃) + 2, &\text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-% \max(unshunt_{cm}(φ₂),unshunt_{cm}(φ₃)) + 1,
-%   &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
-% 0, &\text{otherwise.}
-% \end{cases}
-% \end{split}
-% \end{align}
-
-% Finally, the curated version of $unshunt_{0}$ function is presented
-% in Eq.~(\ref{eq:unshunt-fixed}).
-
-% \begin{equation}
-% \label{eq:unshunt-fixed}
-% unshunt(\varphi) := unshunt_{1}(\varphi, unshunt_{cm}(\varphi)).
-% \end{equation}
-
-% For a more complete treatment of general recursion, and how to
-% define well-founded and well-structural recursive functions, we refer
-% the reader to Ref.~\cite{Bove2005}, where Bove and Capettra described
-% not only general recursion, but they also treat mutual recursive
-% function, among other kinds.
+Otherwise, when type-checking fails, the failure must be
+investigated by the user, checking for the error in \Metis, \Athena,
+or in \Agda.
+
+In the rest of this section, we provide a formal description using
+type theory to build definitions and theorems for functions
+necessary to emulate \Metis' inference rules. For this description,
+we will write the type judgments with ``$a : A$'' to denote that $a$
+has $\abbre{A}$ type. Types are written using small caps.
+We use \Prop type for propositions and a the dependent type, $Γ ⊢ φ$ for theorems. In the latter type, $Γ$ has $\abbre{List}~\Prop$ type
+and $φ$ has type $\Prop$. $\abbre{List}$ is the usual inductive type
+for lists. Finally, we will denote by $φ ≡ ψ$, the syntactic
+equivalence between propositions.
+
+% ...................................................................
+
+% section section_name (end)
+\subsection{Structural Recursion}
+\label{ssec:structural-recursion}
+
+To emulate \Metis' inference rules in type theory,
+we observed that transformations performed by some rules were given by \emph{general recursive} functions.
+But algorithms based on general recursions can not be translated
+directly in type theory since it is not a guarantee they terminate.
+For that reason, we present in this section, a technique to avoid
+such termination problems by modifying the recursive functions
+to be \emph{structural recursive}.
+% (see \cite{Coquand1992,Abel2002,Bove2005} for more details).
+
+We adopt the notion of \emph{structurally smaller} from
+\citeauthor{Abel2002}~\cite{Abel2002} to say, a recursive function is
+structurally recursive if it calls itself with only
+\emph{structurally smaller}
+arguments.
+
+General recursive calls can be translated into structurally recursive
+calls by using for instance, the \emph{Bounded Recursion} technique
+presented in~\cite{Bertot2004}. For a yet another method, we refer
+the reader to \cite{Coquand1992,Abel2002,Bove2005}.
+The former technique defines a new function based on the original
+recursive function by adding an additional argument to the function.
+The new argument is the \emph{bound}, a natural number given by the
+function complexity. In other words, the added argument will store
+the number of times the function needs to call itself to get the
+expected outcome.
+
+Henceforth, a natural number has \Nat type, and it is defined as
+usual. That is, \zero and \suc are the data constructors and some
+arithmetic operations are defined: ($+,\,-,\,*$). We include syntax
+sugar for $\zero$, $\suc$, $\suc(\zero)$, $\cdots$, with the
+classical representation: $1$, $2$, $\cdots$ as well.
+
+Therefore, for a general recursive function $f: \Prop \to \Prop$
+with termination problems, we states a new function $f^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls must done by
+using induction on the \Nat type structure.
+
+\subsubsection{A practical Example.}
+Let us consider the following example to exhibit the technique
+mentioned above for an inner function present in the emulated version
+of the \strip inference.
+
+\begin{align}
+\begin{split}
+\label{eq:unshunt-definition}
+&unshunt_{0}(φ) =\\
+&\hspace{3mm}\begin{cases}
+unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
+  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+unshunt_{0}(φ₁ ⇒ φ₂) ∧ unshunt_{0}(φ₁ ⇒ φ₃),
+  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
+φ, &\text{otherwise.}
+\end{cases}
+\end{split}
+\end{align}
+
+From the definition above, the size of the argument, ((φ₁ ∧ φ₂) ⇒ φ₃),
+is not structurally smaller than the input formula, (φ₁ ⇒ (φ₂ ⇒ φ₃)),
+since ((φ₁ ∧ φ₂) ⇒ φ₃) is not a subformula of (φ₁ ⇒ (φ₂ ⇒ φ₃)).
+
+Thus, we define the function
+$unshunt_{1} : \Prop \to \Nat \to \Prop$
+by structural recursion in its second argument in
+Eq.~(\ref{eq:unshunt-structured}).
+
+\begin{align}
+\label{eq:unshunt-structured}
+\begin{split}
+&unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\
+&unshunt_{1}(φ, \suc(n)) =\\
+&\hspace{3mm}\begin{cases}
+unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
+  &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\[2mm]
+unshunt_{1}(φ₁ ⇒ φ₂, n)\\
+∧\ unshunt_{1}(φ₁ ⇒ φ₃, n),
+   &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
+\end{cases}
+\end{split}
+\end{align}
+
+As we mentioned above, the natural number in the second argument of
+the function used in Eq.~(\ref{eq:unshunt-structured}) stands for a
+complexity measure of the function, in this case $unshunt_{1}$ function.
+
+Recall, the \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
+and presented in \cite{VanDalen1994} as \emph{the rank for a
+proposition}, is a function $\Prop \to \Nat$ that assigns a natural
+number for a proposition $φ$ like the following $rank$ function.
+The symbols, $c_{¬}$ and $c_{\square}$ is a non-negative integer
+number called the complexity of the connective.
+
+\begin{equation*}
+\label{eq:rank-definition}
+rank(φ)=
+\begin{cases}
+0, &\text{for atomic }φ \\
+rank(φ₁) + c_{¬},  &\text{if } φ ≡ \neg φ₁ \\
+\max{(rank(φ₁),rank(φ₂))} + c_{\square},
+  &\text{if } φ ≡ φ₁\,\square\, φ₂.
+\end{cases}
+\end{equation*}
+
+In the case of the $unshunt_0$ function in
+Eq.~(\ref{eq:unshunt-definition}), we define the complexity function
+$unshunt_{cm}: \Prop → \NN$ for our $unshunt_{1}$
+presented in Eq.~(\ref{eq:unshunt-rank-definition}).
+
+\begin{align}
+\begin{split}
+\label{eq:unshunt-rank-definition}
+&unshunt_{cm}(φ) =\\
+&\hspace{3mm}
+\begin{cases}
+unshunt_{cm}(φ₃) + 2, &\text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+\max(unshunt_{cm}(φ₂),unshunt_{cm}(φ₃)) + 1,
+  &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
+0, &\text{otherwise.}
+\end{cases}
+\end{split}
+\end{align}
+
+Finally, following the technique mentioned, we get a curated version of
+$unshunt_{0}$ function presented in Eq.~(\ref{eq:unshunt-fixed}).
+
+\begin{definition}[unshunt]
+\begin{equation}
+\label{eq:unshunt-fixed}
+unshunt(\varphi) := unshunt_{1}(\varphi, unshunt_{cm}(\varphi)).
+\end{equation}
+\end{definition}
+
+For a more complete treatment of general recursion, and how to
+define well-founded and well-structural recursive functions, we refer
+the reader to Ref.~\cite{Bove2005}, where Bove and Capettra described
+not only general recursion, but they also treat mutual recursive
+function, among other kinds.
 
@@
 
-% \subsection{Emulating \Metis' Inference Rules}
-% \label{ssec:emulating-inferences}
-
-% \subsubsection{Splitting a Goal.}
-% \label{sssec:splitting-goal}
-
-% The goal of a problem to be proved by \Metis is processed to generate new
-% propositions, the new targets, \Metis calls these formulas
-% \emph{subgoals}.
-
-% The conjunction of these subgoals is a proposition equivalent to the
-% original goal. Then, we find a refutation for each subgoal in the \Metis' \TSTP derivation.
-
-% Nevertheless, \Metis does not provide neither an explanation for the user about the process in its \TSTP derivations nor in its documentation.
-
-% In the following, we show how Theorem.~\ref{thm:thm-strip} proves the correctness of the process mentioned above.
-But first, let prove some lemmas for $unshunt$ function presented in Eq.~(\ref{eq:unshunt-fixed}),
-% and $split$ function from the definition in Eq.~(\ref{eq:split-definition}).
-
-% \begin{lemma}[lem-unshunt]
-%   \label{lem:unshunt}
-%   $Γ ⊢ unshunt(φ)$, then $Γ ⊢ φ$.
-% \end{lemma}
-
-% \begin{proof} Use induction on the cases defined by the outcome of the
-% $unshunt$ function in Eq.~(\ref{eq:unshunt-structured}).
-% When $n = 0$, by definition, $Γ ⊢ φ$.
-% When $n = 1$, we apply the following theorem from~\cite{AgdaProp}
-
-% \begin{equation*}
-% \texttt{∧⇒-to-⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
-% \end{equation*}
-
-% For $n > 1$, we will use induction on the structure of second
-% argument.
-
-% (φ₁ ⇒ (φ₂ ⇒ φ₃))
-% \begin{equation*}
-%   \begin{bprooftree}
-%   \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
-%   \RightLabel{By def.}
-%   \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
-%   \RightLabel{lem-unshunt}
-%   \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
-%   \RightLabel{∧⇒-to-⇒⇒}
-%   \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).}
-%   \end{bprooftree}
-% \end{equation*}
-
-% Second, using the following theorem from \cite{AgdaProp},
-
-% \begin{equation*}
-%   \texttt{⇒∧-to-⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).
-% \end{equation*}
-
-% ($φ₁ ⇒ (φ₂ ∧ φ₃)$)
-% \begin{equation*}
-% \scalebox{0.95}{
-% ($\mathcal{D}_1$)
-% \begin{bprooftree}
-% \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n) ∧ unshunt(φ₁ ⇒ φ₃, n)$}
-% \RightLabel{∧-proj₁}
-% \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n)$}
-% \RightLabel{By def.}
-% \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n-1)$}
-% \RightLabel{lem-unshunt}
-% \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$,}
-% \end{bprooftree}
-% }
-% \end{equation*}
-
-% \begin{equation*}
-% (\mathcal{D}_2)
-% \begin{bprooftree}
-% \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂) ∧ unshunt(φ₁ ⇒ φ₃)$}
-% \RightLabel{∧-proj₂}
-% \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n)$}
-% \RightLabel{By def.}
-% \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n-1)$}
-% \RightLabel{lem-unshunt}
-% \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$,}
-% \end{bprooftree}
-% \end{equation*}
-
-% \begin{equation*}
-%   \begin{bprooftree}
-%   \AxiomC{$\mathcal{D}_1$}
-%   \AxiomC{$\mathcal{D}_2$}
-%   \RightLabel{∧-intro}
-%   \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
-%   \RightLabel{⇒∧⇒-to-⇒∧}
-%   \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).}
-%   \end{bprooftree}
-% \end{equation*}
-% \end{proof}
-
-% Now, let us consider the $split$ function presented in
-% Eq.~(\ref{eq:split-definition}) that yields a conjunction of subgoals from a proposition, the goal in \Metis.
-
-% \begin{equation}
-% \label{eq:split-definition}
-% \mysplit(φ) =
-% \begin{cases}
-% unshunt(\mysplit(φ₁)) &\text{if }φ ≡ φ₁ ∧ φ₂\\
-% ∧\ unshunt(φ₁ ⇒ \mysplit(φ₂)), &\\[2.5mm]
-% unshunt(¬ φ₁ ⇒ \mysplit(φ₂)),
-%   & \text{if }φ ≡ φ₁ ∨ φ₂\\[2.5mm]
-% unshunt(φ₁ ⇒ \mysplit(φ₂)),
-%   & \text{if }φ ≡ φ₁ ⇒ φ₂\\[2.5mm]
-% unshunt(φ₁ ⇒ \mysplit(φ₂))
-%   & \text{if }φ ≡ φ₁ ⇔ φ₂\\
-% ∧\ unshunt(φ₂ ⇒ \mysplit(φ₁)),
-%   &\\[2.5mm]
-% unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
-%   & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂)\\[2.5mm]
-% unshunt(\mysplit(¬ φ₁))
-%   & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
-% ∧\ unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂)),
-%   &\\[2.5mm]
-% unshunt(\mysplit(φ₁))
-%   & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
-% ∧\ unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
-%   &\\[2.5mm]
-% unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
-%   & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
-% ∧\ unshunt(¬ φ₂ ⇒ \mysplit(φ₁)),
-%   &\\[2.5mm]
-% unshunt(\mysplit(φ₁)),
-%   & \text{if }φ ≡ ¬ ¬ φ₁\\
-% ⊤,
-%   & \text{if }φ ≡ ¬ ⊥\\
-% ⊥,
-%   & \text{if }φ ≡ ¬ ⊤.
-% \end{cases}
-% \end{equation}
-
-% The definition above suffers termination problems since it is not
-% a structural recursion. Therefore, we have reformulated Def.~\ref{eq:split-definition} to solve such a issue following the technique
-% described in Section~\ref{ssec:structural-recursion}.
-% Here and below, we refer to $split$ as the function after applying
-% the process mentioned above.
-
-% \begin{lemma}[\thmsplit] $Γ ⊢ \mysplit(φ)$ then $Γ ⊢ φ$.
-% \label{lem:lem-split}
-% \end{lemma}
-
-% \begin{proof} We now proceed by induction on the structure of the
-% formula φ in the definition of Eq.~(\ref{eq:split-definition}).
-% For a complete proof, we refer the reader to~\cite{AgdaMetis}.\\[3mm]
-
-% ($φ ≡ φ₁ ∧ φ₂$). We get a proof for each conjunct and using the introduction rule for conjunction, the result follows.
-
-% \begin{equation*}
-% (\mathcal{D})\hspace{3mm}
-%   \begin{bprooftree}
-%   \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
-%   \RightLabel{By def.}
-%   \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-%   \RightLabel{∧-proj₁}
-%   \UnaryInfC{$Γ ⊢ unshunt(φ₁)$}
-%   \RightLabel{lem-unshunt}
-%   \UnaryInfC{$Γ ⊢ φ₁$.}
-%   \end{bprooftree}
-% \end{equation*}
-
-% \begin{equation*}
-%   \begin{bprooftree}
-%   \AxiomC{$\mathcal{D}$}
-%   \UnaryInfC{Γ ⊢ φ₁}
-%   \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
-%   \RightLabel{By def.}
-%   \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-%   \RightLabel{$∧$-proj$₂$}
-%   \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-%   \RightLabel{lem-unshunt}
-%   \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-%   \RightLabel{$⇒$-elim}
-%   \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
-%   \RightLabel{\thmsplit}
-%   \UnaryInfC{$Γ ⊢ φ₂.$}
-%   \end{bprooftree}
-% \end{equation*}
-
-% \vskip 3mm
-
-% ($φ ≡ φ₁ ⇒ φ₂$).
-% \begin{equation*}
-%   \begin{bprooftree}
-%   \AxiomC{}
-%   \RightLabel{assume φ₁}
-%   \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
-%   \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
-%   \RightLabel{By def.}
-%   \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-%   \RightLabel{lem-unshunt}
-%   \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-%   \RightLabel{weaken φ₁}
-%   \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-%   \RightLabel{⇒-elim}
-%   \BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂,n-1)$}
-%   \RightLabel{\thmsplit}
-%   \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
-%   \RightLabel{⇒-intro}
-%   \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$.}
-%   \end{bprooftree}
-% \end{equation*}
-% \vskip 3mm
-
-% (φ ≡ ¬ (φ₁ ∨ φ₂)). We show $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$. Using their conjunction by the introduction rule, and De Morgan Law, the results follows.
-
-% \begin{equation*}
-% (\mathcal{D})\hspace{3mm}
-% \begin{bprooftree}
-% \AxiomC{$Γ ⊢ \mysplit(φ, n)$}
-% \RightLabel{By def.}
-% \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
-% \RightLabel{∧-proj₁}
-% \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁)$}
-% \RightLabel{lem-unshunt}
-% \UnaryInfC{$Γ ⊢ ¬ φ₁$,}
-% \end{bprooftree}
-% \end{equation*}
-
-% \begin{equation*}
-%   \begin{bprooftree}
-%   \AxiomC{$\mathcal{D}$}
-%   \UnaryInfC{$Γ ⊢ ¬ φ₁$}
-
-%   \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
-%   \RightLabel{By def.}
-%   \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
-%   \RightLabel{∧-proj₂}
-%   \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
-%   \RightLabel{lem-unshunt}
-%   \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂,n-1)$}
-%   \RightLabel{⇒-elim}
-%   \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
-%   \RightLabel{\thmsplit}
-%   \UnaryInfC{$Γ ⊢ ¬ φ₂.$}
-%   \end{bprooftree}
-% \end{equation*}
-% \end{proof}
-
-% \begin{theorem}[thm-strip]
-% \label{thm:thm-strip}
-%  If $s_i$ are the subgoals for the goal φ, and
-% $\{ Γ ⊢ s_i \}_{i}$, then $Γ ⊢ φ$.
-% \end{theorem}
-
-% \begin{proof}
-% \begin{equation*}
-%   \begin{bprooftree}
-%   \AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i}$}
-%   \RightLabel{∧-intro}
-%   \UnaryInfC{$Γ ⊢ \bigwedge_i s_i$}
-
-%   \AxiomC{$\mysplit(φ) ≡ \bigwedge_i s_i $}
-%   \RightLabel{subst}
-%   \BinaryInfC{$Γ ⊢ \mysplit(φ) $}
-
-%   \RightLabel{\thmsplit}
-%   \UnaryInfC{$Γ ⊢ φ$.}
-% \end{bprooftree}
-% \end{equation*}
-% Where, the $subst$ theorem is,
-% \begin{equation}
-%   \label{eq:substitution-theorem}
-%   \begin{bprooftree}
-%   \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
-%   \RightLabel{subst}
-%   \BinaryInfC{$Γ ⊢ ψ$.}
-%   \end{bprooftree}
-% \end{equation}
-% \end{proof}
+\subsection{Emulating \Metis' Inference Rules}
+\label{ssec:emulating-inferences}
+
+\subsubsection{Splitting a Goal.}
+\label{sssec:splitting-goal}
+
+ To prove a goal, \Metis splits the goal into
+disjoint cases. This process produces a list of new subgoals, the
+conjunction of these subgoals implies the goal. Then, a proof of the
+goal becomes in smaller proofs, one refutation for each subgoal.
+These subgoals are introduced in the \TSTP derivation with the \strip
+inference rule.
+
+\begin{verbatim}
+fof(goal, conjecture, p & r & q).
+fof(subgoal_0, plain, p, inference(strip, [], [goal])).
+fof(subgoal_1, plain, p => r, inference(strip, [], [goal])).
+fof(subgoal_2, plain, (p & r) => q, inference(strip, [], [goal])).
+\end{verbatim}
+
+In the following, we show how Theorem~\ref{thm:thm-strip} proves the
+correctness of the process mentioned above. But first, let us prove some
+lemmas for $unshunt$ function presented in Eq.~(\ref{eq:unshunt-fixed}),
+and $split$ function from the definition in Eq.~(\ref{eq:split-definition}).
+
+\begin{lemma}[lem-unshunt]
+  \label{lem:unshunt}
+  $Γ ⊢ unshunt(φ)$, then $Γ ⊢ φ$.
+\end{lemma}
+
+\begin{proof} Use induction on the cases defined by the outcome of the
+$unshunt$ function in Eq.~(\ref{eq:unshunt-structured}).
+\begin{itemize}
+	\item When $n = 0$, by definition, $Γ ⊢ φ$.
+	\item When $n = 1$, we apply the following theorem from~\cite{AgdaProp}
+		\begin{equation*}
+		\texttt{∧⇒-to-⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
+		\end{equation*}
+  \item For $n > 1$, we will use induction on the structure of the second
+			  argument.
+
+\begin{itemize}
+\item $(φ₁ ⇒ (φ₂ ⇒ φ₃))$
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
+  \RightLabel{By def.}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
+  \RightLabel{lem-unshunt}
+  \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
+  \RightLabel{∧⇒-to-⇒⇒}
+  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).}
+  \end{bprooftree}
+\end{equation*}
+
+\item $(φ₁ ⇒ (φ₂ ∧ φ₃))$
+\begin{equation*}
+\scalebox{0.95}{
+($\mathcal{D}_1$)
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n) ∧ unshunt(φ₁ ⇒ φ₃, n)$}
+\RightLabel{∧-proj₁}
+\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n-1)$}
+\RightLabel{lem-unshunt}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$,}
+\end{bprooftree}
+}
+\end{equation*}
+
+\begin{equation*}
+(\mathcal{D}_2)
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂) ∧ unshunt(φ₁ ⇒ φ₃)$}
+\RightLabel{∧-proj₂}
+\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n-1)$}
+\RightLabel{lem-unshunt,}
+\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
+\end{bprooftree}
+\end{equation*}
+Finally, using the theorem, \texttt{⇒∧⇒-to-⇒∧} from~\cite{AgdaProp},
+\begin{equation*}
+  \texttt{⇒∧⇒-to-⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).
+\end{equation*}
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$\mathcal{D}_1$}
+  \AxiomC{$\mathcal{D}_2$}
+  \RightLabel{∧-intro}
+  \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
+  \RightLabel{\tt ⇒∧⇒-to-⇒∧.}
+  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
+  \end{bprooftree}
+\end{equation*}
+
+\end{itemize}
+\end{itemize}
+
+\end{proof}
+
+Let us now consider the $split$ function presented in
+Eq.~(\ref{eq:split-definition}) that yields the conjunction of subgoals that implies the goal in a \Metis \TSTP derivation.
+
+\begin{definition}[split]
+\begin{equation}
+\label{eq:split-definition}
+\mysplit(φ) =
+\begin{cases}
+unshunt(\mysplit(φ₁)) &\text{if }φ ≡ φ₁ ∧ φ₂\\
+∧\ unshunt(φ₁ ⇒ \mysplit(φ₂)), &\\[2.5mm]
+unshunt(¬ φ₁ ⇒ \mysplit(φ₂)),
+  & \text{if }φ ≡ φ₁ ∨ φ₂\\[2.5mm]
+unshunt(φ₁ ⇒ \mysplit(φ₂)),
+  & \text{if }φ ≡ φ₁ ⇒ φ₂\\[2.5mm]
+unshunt(φ₁ ⇒ \mysplit(φ₂))
+  & \text{if }φ ≡ φ₁ ⇔ φ₂\\
+∧\ unshunt(φ₂ ⇒ \mysplit(φ₁)),
+  &\\[2.5mm]
+unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
+  & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂)\\[2.5mm]
+unshunt(\mysplit(¬ φ₁))
+  & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
+∧\ unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂)),
+  &\\[2.5mm]
+unshunt(\mysplit(φ₁))
+  & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
+∧\ unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
+  &\\[2.5mm]
+unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
+  & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
+∧\ unshunt(¬ φ₂ ⇒ \mysplit(φ₁)),
+  &\\[2.5mm]
+unshunt(\mysplit(φ₁)),
+  & \text{if }φ ≡ ¬ ¬ φ₁\\
+⊤,
+  & \text{if }φ ≡ ¬ ⊥\\
+⊥,
+  & \text{if }φ ≡ ¬ ⊤.
+\end{cases}
+\end{equation}
+\end{definition}
+
+The definition above suffers termination problems since it is not
+a structural recursion. Therefore, we have reformulated the equation above to solve such a issue following the technique
+described in Section~\ref{ssec:structural-recursion}.
+
+Here and below, we refer to $split$ as the function after applying
+the process mentioned above.
+
+\begin{lemma}[\thmsplit] $Γ ⊢ \mysplit(φ)$ then $Γ ⊢ φ$.
+\label{lem:lem-split}
+\end{lemma}
+
+\begin{proof} We now proceed by induction on the structure of the
+formula φ in the definition of Eq.~(\ref{eq:split-definition}).
+For a complete proof, we refer the reader to~\cite{AgdaMetis}.\\[3mm]
+
+($φ ≡ φ₁ ∧ φ₂$). We get a proof for each conjunct and using the introduction rule for conjunction, the result follows.
+
+\begin{equation*}
+(\mathcal{D})\hspace{3mm}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+  \RightLabel{By def.}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \RightLabel{∧-proj₁}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁)$}
+  \RightLabel{lem-unshunt}
+  \UnaryInfC{$Γ ⊢ φ₁$.}
+  \end{bprooftree}
+\end{equation*}
+
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$\mathcal{D}$}
+  \UnaryInfC{Γ ⊢ φ₁}
+  \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+  \RightLabel{By def.}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \RightLabel{$∧$-proj$₂$}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \RightLabel{lem-unshunt}
+  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+  \RightLabel{$⇒$-elim}
+  \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
+  \RightLabel{\thmsplit}
+  \UnaryInfC{$Γ ⊢ φ₂.$}
+  \end{bprooftree}
+\end{equation*}
+
+\vskip 3mm
+
+($φ ≡ φ₁ ⇒ φ₂$).
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{}
+  \RightLabel{assume φ₁}
+  \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
+  \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
+  \RightLabel{By def.}
+  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \RightLabel{lem-unshunt}
+  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+  \RightLabel{weaken φ₁}
+  \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+  \RightLabel{⇒-elim}
+  \BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂,n-1)$}
+  \RightLabel{\thmsplit}
+  \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
+  \RightLabel{⇒-intro}
+  \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$.}
+  \end{bprooftree}
+\end{equation*}
+\vskip 3mm
+
+(φ ≡ ¬ (φ₁ ∨ φ₂)). We show $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$. Using their conjunction by the introduction rule, and De Morgan Law, the results follows.
+
+\begin{equation*}
+(\mathcal{D})\hspace{3mm}
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ \mysplit(φ, n)$}
+\RightLabel{By def.}
+\UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
+\RightLabel{∧-proj₁}
+\UnaryInfC{$Γ ⊢ unshunt(¬ φ₁)$}
+\RightLabel{lem-unshunt}
+\UnaryInfC{$Γ ⊢ ¬ φ₁$,}
+\end{bprooftree}
+\end{equation*}
+
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$\mathcal{D}$}
+  \UnaryInfC{$Γ ⊢ ¬ φ₁$}
+
+  \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
+  \RightLabel{By def.}
+  \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \RightLabel{∧-proj₂}
+  \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \RightLabel{lem-unshunt}
+  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+  \RightLabel{⇒-elim}
+  \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
+  \RightLabel{\thmsplit}
+  \UnaryInfC{$Γ ⊢ ¬ φ₂.$}
+  \end{bprooftree}
+\end{equation*}
+\end{proof}
+
+\begin{theorem}[thm-strip]
+\label{thm:thm-strip}
+ If $s_i$ are the subgoals for the goal φ, and
+$\{ Γ ⊢ s_i \}_{i}$, then $Γ ⊢ φ$.
+\end{theorem}
+
+\begin{proof}
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i}$}
+  \RightLabel{∧-intro}
+  \UnaryInfC{$Γ ⊢ \bigwedge_i s_i$}
+
+  \AxiomC{$\mysplit(φ) ≡ \bigwedge_i s_i $}
+  \RightLabel{subst}
+  \BinaryInfC{$Γ ⊢ \mysplit(φ) $}
+
+  \RightLabel{\thmsplit}
+  \UnaryInfC{$Γ ⊢ φ$.}
+\end{bprooftree}
+\end{equation*}
+Where, the $subst$ theorem is,
+\begin{equation}
+  \label{eq:substitution-theorem}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
+  \RightLabel{subst}
+  \BinaryInfC{$Γ ⊢ ψ$.}
+  \end{bprooftree}
+\end{equation}
+\end{proof}
 

### 2017-10-13 paper/sections/discussion.tex
[ paper ] reviewed to resolve section.

@@
 These subgoals are introduced in the \TSTP derivation with the \strip
-inference rule. We refer the reader to see Section~\ref{sssec:splitting-goal} for the formalization of \strip rule.
+inference rule. We refer the reader to see Section~\ref{sssec:strip-a-goal} for the formalization of \strip rule.
 
@@
 
-\textit{Resolution.} The \resolve rule incorporates  the resolution theorem showed in Fig.~\ref{fig:metis-inferences} with
-three arguments: a positive literal $l$ to apply the resolution theorem, and two derivations, $\mathcal{D}₁$ and $\mathcal{D}₂$.
+\textit{Resolution.} The \resolve rule incorporates the resolution theorem showed in Fig.~\ref{fig:metis-inferences} for the \TSTP derivations.
+This rule posses three arguments: a positive literal $l$ to apply the resolution theorem, and two derivations, $\mathcal{D}₁$ and $\mathcal{D}₂$.
 
@@
 the formula from the first derivation $\mathcal{D}₁$, and the
-negative literal must occur in the formula from the second derivation $\mathcal{D}₂$ (see the pattern in \Metis' logic core for the \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}).
+negative literal must occur in the formula from the second derivation $\mathcal{D}₂$ (see the pattern in the \emph{resolve} rule).
 We refer the reader to see Section~\ref{sssec:resolve} for the formalization of the \resolve rule.

### 2017-10-13 paper/sections/metis-language-and-proofs.tex
[ paper ] reviewed to resolve section.

@@
 $p\, \vdash \neg (p \wedge \neg p) ∨ (q \wedge \neg q)$
-in \TPTP syntax. We begin by declaring the $p$ axiom using the keyword,
-\verb!axiom!. Later, we include the expected conclusion using the \verb!conjecture! keyword.
+in \TPTP syntax. We begin by declaring the $p$ axiom using the \verb!axiom!
+keyword. Later, we include the expected conclusion using the \verb!conjecture! keyword.
 
@@
 
-% -------------------------------------------------------------------
-
-\subsubsection{Proof Rules.}
-\label{sssec:proof-rules}
-
-Since the scope of the problems treated in this research is CPL, from the list of \Metis inference rules in~\ref{fig:metis-inferences}, we found that only three rules apply: \emph{axiom}, \emph{assume} and \emph{resolve} rule.
-Nonetheless, \TSTP derivations replied by \Metis use other rules. They are \canonicalize, \clausify, \conjunct, \simplify, \negate, and
-\strip.
-
-\begin{figure}
-\centering
-  \begin{bprooftree}\tt
-    \AxiomC{}
-    \RightLabel{negate}
-    \UnaryInfC{$\neg p$}
-    \RightLabel{strip}
-    \UnaryInfC{$\neg p$}
-    \AxiomC{}
-    \RightLabel{axiom}
-    \UnaryInfC{$p$}
-    \RightLabel{canonicalize}
-    \UnaryInfC{$p$}
-    \RightLabel{simplify}
-    \BinaryInfC{$⊥$}
-    \RightLabel{canonicalize}
-    \UnaryInfC{$⊥$}
-  \end{bprooftree}
-  \caption{The \Metis' proof tree for $p \vdash p$ from the
-  derivation in Fig.~\ref{fig:metis-proof-tstp}}
-  \label{fig:metis-example}
-\end{figure}
-
-\Metis looks for a refutation to prove \verb!fof! problems.
-A \verb!fof!
-problem contains the conjecture also named the \emph{goal} in the problem.
-This goal is stripped into subgoals by using the \strip rule.
-The subgoals are the conjuncts in a general conjunction that is equivalent to the aforementioned goal.
-Therefore, to prove the goal, \Metis proves independently each subgoal since they tend to be less complex or even smaller propositions.
-At the end, the conjunction of all subgoal proofs must prove the goal.
-Nevertheless, this last reasoning is not explicit neither in the \TSTP derivations nor in the \Metis' documentation.
-Since \Metis replies refutation proofs, to prove each subgoal, in the \TSTP derivation, the inference rule \negate introduces the negation of such subgoals.
-The \negate rule is a specification of the \emph{assume} rule.
-
-Finally, \emph{axiom} rule appears in \TSTP derivation by one of the following rules to in the problem a \verb!fof!
-axiom: \canonicalize, \clausify, \conjunct, or \simplify.
-Then, the last rule remains is \emph{resolve}, it appears by the
-binary rule, \resolve, the version in \Metis of the resolution
-theorem. For a more detailed description of this rules see the Section~\ref{sec:proof-reconstruction}.
-
-\subsubsection{Proofs.}
-\label{sssec:metis-proofs}
-
-A proof-object delivered in a \Metis' proof encodes a natural
-deduction proof. The deduction system uses six inference rules
-\cite{hurd2003first} listed in Fig.~\ref{fig:metis-inferences}.
-With these inference rules as the only valid deduction steps, \Metis
-attempts to prove conjectures by refutation (see. e.g.,
-\emph{falsium} in the last conclusion of the \TSTP derivation in
-Fig.~\ref{fig:metis-example}).
-
 \begin{figure}
@@
 
+% -------------------------------------------------------------------
+
+\subsubsection{Proof Rules.}
+\label{sssec:proof-rules}
+
+Since the scope of the problems treated in this research is \CPL, from the list of \Metis inference rules in Fig.~\ref{fig:metis-inferences}, we found that only three rules apply: \emph{axiom}, \emph{assume} and \emph{resolve} rule.
+Nonetheless, \TSTP derivations replied by \Metis use other rules. They are \canonicalize, \clausify, \conjunct, \simplify, \negate, and
+\strip.
+
+\Metis looks for a refutation to prove \verb!fof! problems.
+A \verb!fof!
+problem contains the conjecture also named the \emph{goal} in the problem.
+This goal is stripped into subgoals by using the \strip rule.
+The subgoals are the conjuncts in a general conjunction that is equivalent to the aforementioned goal.
+Therefore, to prove the goal, \Metis proves independently each subgoal since they tend to be less complex or even smaller propositions.
+At the end, the conjunction of all subgoal proofs must prove the goal.
+Nevertheless, this last reasoning is not explicit neither in the \TSTP derivations nor in the \Metis' documentation.
+Since \Metis replies refutation proofs, to prove each subgoal, in the \TSTP derivation, the inference rule \negate introduces the negation of such subgoals.
+The \negate rule is a specification of the \emph{assume} rule.
+
+Finally, \emph{axiom} rule appears in \TSTP derivation by one of the following rules to in the problem a \verb!fof!
+axiom: \canonicalize, \clausify, \conjunct, or \simplify.
+Then, the last rule remains is \emph{resolve}, it appears by the
+binary rule, \resolve, the version in \Metis of the resolution
+theorem. For a more detailed description of this rules see the Section~\ref{sec:proof-reconstruction}.
+
+\subsubsection{Proofs.}
+\label{sssec:metis-proofs}
+
+\begin{figure}
+\centering
+  \begin{bprooftree}\tt
+    \AxiomC{}
+    \RightLabel{negate}
+    \UnaryInfC{$\neg p$}
+    \RightLabel{strip}
+    \UnaryInfC{$\neg p$}
+    \AxiomC{}
+    \RightLabel{axiom}
+    \UnaryInfC{$p$}
+    \RightLabel{canonicalize}
+    \UnaryInfC{$p$}
+    \RightLabel{simplify}
+    \BinaryInfC{$⊥$}
+    \RightLabel{canonicalize}
+    \UnaryInfC{$⊥$}
+  \end{bprooftree}
+  \caption{The \Metis' proof tree for $p \vdash p$ from the
+  derivation in Fig.~\ref{fig:metis-proof-tstp}}
+  \label{fig:metis-example}
+\end{figure}
+
+A proof-object delivered in a \Metis' proof encodes a natural
+deduction proof. The deduction system uses six inference rules
+\cite{hurd2003first} listed in Fig.~\ref{fig:metis-inferences}.
+With these inference rules as the only valid deduction steps, \Metis
+attempts to prove conjectures by refutation (see. e.g.,
+\emph{falsium} in the last conclusion of the \TSTP derivation in
+Fig.~\ref{fig:metis-example}).
+
 These proofs are directed acyclic graphs, trees of refutations. Each

### 2017-10-13 paper/sections/proof-reconstruction.tex
[ paper ] reviewed to resolve section.

@@
 
-\subsubsection{Splitting a Goal.}
-\label{sssec:splitting-goal}
+\subsubsection{Strip a Goal.}
+\label{sssec:strip-a-goal}
 
@@
 These subgoals are introduced in the \TSTP derivation with the \strip
-inference rule.
+inference rule as we show with the following excerpt.
 
@@
 
-In the following, we show how Theorem~\ref{thm:thm-strip} proves the
-correctness of the process mentioned above. But first, let us prove some
+To prove the correctness of the process mentioned above, we state
+the Theorem~\ref{thm:thm-strip}. But first, let us prove some
 lemmas for $unshunt$ function presented in Eq.~(\ref{eq:unshunt-fixed}),
@@
   \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
-  \RightLabel{By def.}
+  \RightLabel{axiom}
   \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
@@
   \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
-  \RightLabel{∧⇒-to-⇒⇒}
-  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).}
+  \RightLabel{∧⇒-to-⇒⇒.}
+  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)}
   \end{bprooftree}
@@
     \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n)$}
-\RightLabel{By def.}
+    \RightLabel{axiom}
     \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n-1)$}
-\RightLabel{lem-unshunt}
-\UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$,}
+    \RightLabel{lem-unshunt,}
+    \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
   \end{bprooftree}
@@
     \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n)$}
-\RightLabel{By def.}
+    \RightLabel{axiom}
     \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n-1)$}
-\RightLabel{lem-unshunt,}
+    \RightLabel{lem-unshunt.}
     \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
@@
 \end{equation*}
-Finally, using the theorem, \texttt{⇒∧⇒-to-⇒∧} from~\cite{AgdaProp},
-\begin{equation*}
-  \texttt{⇒∧⇒-to-⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃).
+
+Finally, using the theorem \texttt{⇒∧⇒-to-⇒∧} from~\cite{AgdaProp},
+\begin{equation*}
+  \texttt{⇒∧⇒-to-⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
 \end{equation*}
@@
 \end{itemize}
-
 \end{proof}
@@
 Let us now consider the $split$ function presented in
-Eq.~(\ref{eq:split-definition}) that yields the conjunction of subgoals that implies the goal in a \Metis \TSTP derivation.
+Eq.~(\ref{eq:split-definition}) that yields the conjunction of subgoals that implies the goal of the problem in the \Metis \TSTP derivations.
 
 \begin{definition}[split]
+\label{def:split}
+
 \begin{equation}
@@
 described in Section~\ref{ssec:structural-recursion}.
-
 Here and below, we refer to $split$ as the function after applying
@@
 \begin{proof} We now proceed by induction on the structure of the
-formula φ in the definition of Eq.~(\ref{eq:split-definition}).
+formula $φ$ in the definition of Eq.~(\ref{eq:split-definition}).
 For a complete proof, we refer the reader to~\cite{AgdaMetis}.\\[3mm]
 
-($φ ≡ φ₁ ∧ φ₂$). We get a proof for each conjunct and using the introduction rule for conjunction, the result follows.
+\begin{itemize}
+\item $(φ ≡ φ₁ ∧ φ₂)$. We get a proof for each conjunct and using the introduction rule for conjunction connective, the result follows.
 
@@
   \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
-  \RightLabel{By def.}
+  \RightLabel{axiom}
   \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
@@
   \UnaryInfC{$Γ ⊢ unshunt(φ₁)$}
-  \RightLabel{lem-unshunt}
-  \UnaryInfC{$Γ ⊢ φ₁$.}
+  \RightLabel{lem-unshunt.}
+  \UnaryInfC{$Γ ⊢ φ₁$}
   \end{bprooftree}
@@
   \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
-  \RightLabel{\thmsplit}
-  \UnaryInfC{$Γ ⊢ φ₂.$}
-  \end{bprooftree}
-\end{equation*}
-
-\vskip 3mm
-
-($φ ≡ φ₁ ⇒ φ₂$).
+  \RightLabel{\thmsplit.}
+  \UnaryInfC{$Γ ⊢ φ₂$}
+  \end{bprooftree}
+\end{equation*}
+
+\item $(φ ≡ φ₁ ⇒ φ₂)$
 \begin{equation*}
@@
   \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
-  \RightLabel{By def.}
+  \RightLabel{axiom}
   \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
@@
   \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
-  \RightLabel{⇒-intro}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$.}
-  \end{bprooftree}
-\end{equation*}
-\vskip 3mm
-
-(φ ≡ ¬ (φ₁ ∨ φ₂)). We show $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$. Using their conjunction by the introduction rule, and De Morgan Law, the results follows.
+  \RightLabel{⇒-intro.}
+  \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
+  \end{bprooftree}
+\end{equation*}
+
+\item $(φ ≡ ¬ (φ₁ ∨ φ₂))$. We show that $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
+The result follows by introducing the conjunction and applying after
+De Morgan Law.
 
@@
 \AxiomC{$Γ ⊢ \mysplit(φ, n)$}
-\RightLabel{By def.}
+\RightLabel{axiom}
 \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
@@
 \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁)$}
-\RightLabel{lem-unshunt}
-\UnaryInfC{$Γ ⊢ ¬ φ₁$,}
-\end{bprooftree}
-\end{equation*}
+\RightLabel{lem-unshunt,}
+\UnaryInfC{$Γ ⊢ ¬ φ₁$}
+\end{bprooftree}
+\end{equation*}
+\end{itemize}
+\end{proof}
 
@@
   \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
-  \RightLabel{By def.}
+  \RightLabel{axiom}
   \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
@@
   \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
-  \RightLabel{\thmsplit}
-  \UnaryInfC{$Γ ⊢ ¬ φ₂.$}
-  \end{bprooftree}
-\end{equation*}
-\end{proof}
+  \RightLabel{\thmsplit.}
+  \UnaryInfC{$Γ ⊢ ¬ φ₂$}
+  \end{bprooftree}
+\end{equation*}
+
+\begin{lemma}[subst]
+  \label{lem:subst}
+  Substitution theorem.
+\begin{equation}
+  \label{eq:substitution-theorem}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
+  \RightLabel{subst.}
+  \BinaryInfC{$Γ ⊢ ψ$}
+  \end{bprooftree}
+\end{equation}
+\end{lemma}
 
@@
 \label{thm:thm-strip}
- If $s_i$ are the subgoals for the goal φ, and
+ If $s_i$ are the subgoals of the goal $φ$, and
  $\{ Γ ⊢ s_i \}_{i}$, then $Γ ⊢ φ$.
@@
   \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ \mysplit(φ) $}
-
-  \RightLabel{\thmsplit}
-  \UnaryInfC{$Γ ⊢ φ$.}
-\end{bprooftree}
-\end{equation*}
-Where, the $subst$ theorem is,
+  \BinaryInfC{$Γ ⊢ \mysplit(φ)$}
+  \RightLabel{\thmsplit.}
+  \UnaryInfC{$Γ ⊢ φ$}
+\end{bprooftree}
+\end{equation*}
+\end{proof}
+
+% -------------------------------------------------------------------
+\subsubsection{Splitting a Conjunct.}
+\label{sssec:splitting-a-conjunct}
+
+The \conjunct rule extracts from a
+conjunction one of its conjuncts; it is a generalization of the
+projection rules for the conjunction connective as the
+following \TSTP excerpt shows.
+
+\begin{verbatim}
+fof(normalize_1, plain, p & q & (r | ~ p),
+  inference(canonicalize, [], [x])).
+fof(normalize_2, plain, q,
+  inference(conjunct, [], [normalize_1])).
+fof(normalize_2, plain, (r | ~ p),
+  inference(conjunct, [], [normalize_1])).
+\end{verbatim}
+
+\begin{definition}[conjunct]
+\begin{align}
+  \begin{split}
+  &conjunct : \Prop \to \Prop \to \Prop\\
+  &conjunct(φ, ψ) =\\
+  &\hspace{3mm}
+  \begin{cases}
+      ψ, &\text{if }φ ≡ ψ\\
+      ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }ψ ≡ conjunct(φ₁, ψ)\\
+      ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }ψ ≡ conjunct(φ₂, ψ)\\
+      φ, &\text{otherwise.}
+    \end{cases}
+  \end{split}
+\end{align}
+\end{definition}
+
+\begin{theorem}[thm-conjunct]
+  \label{thm:thm-conjunct}
+  $Γ ⊢ φ$, and $ψ  : \Prop$ , then $Γ ⊢ conjunct(φ, ψ)$.
+\end{theorem}
+~\begin{proof}\hspace{2cm}\\
+\begin{itemize}
+  \item For the case, $φ ≡ ψ$, $Γ ⊢ conjunct(φ, ψ)$ normalizes to $Γ ⊢ ψ$.
+Then, we get the desire conclusion by applying the $subst$ theorem.
+  \item If the proposition $φ$ is a conjunction, and we can get $ψ ≡ conjunct(φ_{i}, ψ)$ for some $i = 1,\ 2$, then,
+
 \begin{equation}
-  \label{eq:substitution-theorem}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
-  \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ ψ$.}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
+  \RightLabel{∧-proj$_{i}$}
+  \UnaryInfC{$Γ ⊢ φ_{i}$}
+  \UnaryInfC{$Γ ⊢ conjunct(φ_{i}, ψ)$}
+  \AxiomC{$ψ ≡ conjunct(φ_{i}, ψ)$}
+  \RightLabel{subst.}
+  \BinaryInfC{$Γ ⊢ ψ$}
   \end{bprooftree}
 \end{equation}
+\item The last case follows trivially by using the same hypothesis.
+\end{itemize}
 \end{proof}
 
-% % -------------------------------------------------------------------
-% \subsubsection{splitting a Conjunct}
-% \label{sssec:splitting-a-conjunct}
-
-% The \conjunct rule extracts from a conjunction, one of its conjunct.
-% To achieve this, we use projections repeatedly until we finally find
-% the conjunct required.
-
-% \begin{align}
-%   \begin{split}
-%   conjunct(φ, ψ) =
-%     \begin{cases}
-%       ψ, &\text{if }φ ≡ ψ\\
-%       ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₁, ψ)≡ ψ\\
-%       ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }conjunct(φ₂, ψ)≡ ψ\\
-%       φ, &\text{otherwise.}
-%     \end{cases}
-%   \end{split}
-% \end{align}
-
-% \begin{theorem}[thm-conjunct]
-%   \label{thm:thm-conjunct}
-%   $Γ ⊢ φ$, and $ψ \in \Prop$ , then $Γ ⊢ conjunct(φ, ψ)$.
-% \end{theorem}
-
-% \begin{proof}
-% When φ ≡ ψ, from $Γ ⊢ conjunct(φ, ψ)$ by normalization, we get $Γ ⊢ ψ$.
-% By using $subst$ theorem Eq.~(\ref{eq:substitution-theorem}), we get the desire conclusion. If the proposition φ is a conjunction, and $ψ ≡ conjunct(φ_{i}, ψ)$
-% for some $i = 1,\ 2$, then,
-
-% \begin{equation}
-%   \begin{bprooftree}
-%   \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
-%   \RightLabel{∧-proj$_{i}$}
-%   \UnaryInfC{$Γ ⊢ φ_{i}$}
-%   \UnaryInfC{$Γ ⊢ conjunct(φ_{i}, ψ)$}
-%   \AxiomC{$conjunct(φ_{i}, ψ) ≡ ψ$}
-%   \RightLabel{subst}
-%   \BinaryInfC{$Γ ⊢ ψ$.}
-%   \end{bprooftree}
-% \end{equation}
-
-% The last statement follows by using the hypothesis and the proof is complete.
-% \end{proof}
-
-% % subsubsection splitting-a-conjunct (end)
-% % -------------------------------------------------------------------
+% subsubsection splitting-a-conjunct (end)
+% -------------------------------------------------------------------
 
@@
 
-% \subsubsection{Reordering.}
-
-% Syntactically speaking, showing the logic equivalence between two conjunctive normal forms is a matter of rearrangements of the conjunctions
-% but also of the inner disjunctions inside the propositions involved.
-% \improvement{Make clear: we are dealing with CNFs, and prove equivalence between two formulas is equivalent to show two trees are  isomorphic.
-% And that problem is NP-hard, and for that, we mostly do brute force.}
-
-% We provide some useful theorems to perform the following tasks.
-
-% \begin{itemize}
-%   \item Reorder a disjunction like $φ = φ₁ ∨ φ₂ ∨ \cdots$ to match with another disjunction $ψ = ψ₁ ∨ ψ₂ ∨ \cdots$, when $φ$ is a disjunct of $ψ$.
-%   \item Reorder a conjunction of disjuncts (CNF), $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another CNF formula equivalent $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$.
-% \end{itemize}
-
-% First, we define the $rdisj$ function in Eq.~(\ref{eq:rdisj-def}) to convert a disjunction to be a right-associative disjunction, and following
-% a similar approach we define the $rconj$ function for conjunctions.
-
-% \begin{align}
-%   \begin{split}
-%     \label{eq:rdisj-def}
-%     rdisj(φ) =
-%     \begin{cases}
-%     rdisj(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
-%     φ₁ ∨ rdisj(φ₂),         & \text{if } φ ≡ φ₁ ∨ φ₂\\
-%     φ,                      & \text{otherwise.}
-%     \end{cases}
-%   \end{split}
-% \end{align}
-
-% \begin{lemma}[lem-rdisj]
-% \label{lem:lem-rdisj}
-%   $Γ ⊢ φ$ then $Γ ⊢ rdisj(φ)$.
-% \end{lemma}
-
-% The following function, $build_{∨} : \Prop → \Prop → \Prop$ in Eq.~(\ref{eq:build-or}), intends to construct a disjunction from another disjunction, specifically, we want to rearrange the disjuncts in the source formula to match with the target disjunction for syntactic
-% equivalence.
-
-% \begin{equation}
-%   \begin{split}
-%   \label{eq:build-or}
-%   &build_{∨}(φ, ψ) =\\
-%   &\hspace{3mm}
-%   \begin{cases}
-%   ψ, &\text{if } φ ≡ ψ\\
-%   ψ, &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
-%   φ, &\text{otherwise.}
-%   \end{cases}
-%   \end{split}
-% \end{equation}
-
-% \begin{lemma}[lem-build$_{∨}$]
-% \label{lem:lem-build-or}
-% $Γ ⊢ φ$, and $ψ\in \Prop$ then $Γ ⊢ build_{∨}(φ)$.
-% \end{lemma}
-
-% The function $factor : \Prop → \Prop$  in Eq.~(\ref{eq:factor-definition}) is intended to work only for right-associative disjunctions, and reduces a disjunction of the same disjunct (e.g., $factor(φ ∨ (φ ∨ \cdots)) \mapsto\ φ$).
-
-% \begin{align}
-% \begin{split}
-%   \label{eq:factor-definition}
-%   factor(φ) =
-%   \begin{cases}
-%     φ₁,  &\text{if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ factor(φ₂)\\
-%     φ,   &\text{otherwise.}
-%   \end{cases}
-% \end{split}
-% \end{align}
-
-% \begin{lemma}[lem-factor]
-% \label{lem:lem-factor}
-%   $Γ ⊢ φ$ then $Γ ⊢ factor(φ)$.
-% \end{lemma}
-
-% Now, with a right-associative disjunction by applying $rdisj$ function to
-% a proposition $φ$, $sbuild_{∨}: \Prop → \Prop → \Prop$ in
-% Eq.~(\ref{eq:strong-build-or-definition}) aims to construct the disjunction
-% ψ by using each of its disjuncts from the proposition φ. This approach to
-% build a disjunction from another is inspired on the description in
-% \citeauthor{bohme2010}~\cite{bohme2010} to prove equality between nested
-% disjunctions. \change{Make clear this, It's not clear the difference with build-or and sbuild-or.}
-
-% \begin{align}
-%   \begin{split}
-%   \label{eq:strong-build-or-definition}
-%     sbuild_{∨}(φ, ψ) =
-%     \begin{cases}
-%       factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ)),  &\text{if }φ≡ φ₁ ∨ φ₂\\
-%       build_{∨}(φ, ψ),  & \text{otherwise.}
-%     \end{cases}
-%   \end{split}
-% \end{align}
-
-% \begin{lemma}[lem-sbuild$_{∨}$]
-% \label{lem:lem-sbuild-or}
-% $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ sbuild_{∨}(φ, ψ)$.
-% \end{lemma}
-
-% Let see the following example of the idea behind $sbuild_{∨}$
-% function; from the disjunction $(r ∨ (q ∨ p))$, we build the disjunction
-% $((p ∨ q) ∨ r)$.
-
-% \begin{equation*}
-%   \begin{bprooftree}
-%   \AxiomC{$Γ ⊢ q$}
-%   \RightLabel{∨-intro₂}
-%   \UnaryInfC{$Γ ⊢ p ∨ q$}
-%   \RightLabel{∨-intro₁}
-%   \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-%   \AxiomC{$Γ ⊢ p$}
-%   \RightLabel{∨-intro₁}
-%   \UnaryInfC{$Γ ⊢ p ∨ q$}
-%   \RightLabel{∨-intro₁}
-%   \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-%   \RightLabel{∨-elim}
-%   \BinaryInfC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
-%   \end{bprooftree}
-% \end{equation*}
-
-% \begin{equation*}
-%   \begin{bprooftree}
-%   \AxiomC{$Γ ⊢ r$}
-%   \RightLabel{∨-intro₂}
-%   \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-%   \AxiomC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
-
-%   \RightLabel{∨-elim}
-%   \BinaryInfC{$Γ, r ∨ (q ∨ p) ⊢ (p ∨ q) ∨ r$}
-
-%   \RightLabel{⇒-intro}
-%   \UnaryInfC{$Γ ⊢ r ∨ (q ∨ p) ⇒ (p ∨ q) ∨ r$}
-
-%   \end{bprooftree}
-% \end{equation*}
-
-% \begin{theorem}[thm-reorder$_{∨}$]
-%   \label{thm-reorder-or}
-%   $Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$, where,
-%   \begin{equation*}
-%     \label{eq:reorder-or}
-%     reorder_{∨} (φ, ψ) = sbuild_{∨}(rdisj(φ), ψ).
-%   \end{equation*}
-% \end{theorem}
-
-% \begin{proof} Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
-% \end{proof}
-
-% To work with nest conjunctions of disjunctions (CNFs), we define similar
-% functions and theorems as we previously did for disjunctions.
-
-% \begin{lemma}[lem-reorder$_{∧}$]
-%   \label{lem:lem-reorder-and}
-%   $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder(φ, ψ)$, where,
-%   \begin{align*}
-%       \begin{split}
-%         reorder_{∧}(φ, ψ) =
-%         \begin{cases}
-%           φ, &\text{if }φ ≡ ψ\\
-%           ψ₁ ∧ ψ₂, &\text{if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁\\
-%                   &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂\\
-%           φ,       &\text{if } ψ ≡ ψ₁ ∧ ψ₂\\
-%           conjunct(φ, ψ) &\text{otherwise.}
-%         \end{cases}
-%       \end{split}
-%   \end{align*}
-% \end{lemma}
-
-% \begin{lemma}[lem-conjunct$_{∨}$]
-%   \label{lem:lem-conjunct-or}
-%   $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$, where,
-%   \improvement{The first case is not implemented in Agda}
-%   \begin{align*}
-%   \begin{split}
-%     \label{eq:conjunct-or-definition}
-%     conjunct_{∨}(φ, ψ) =
-%     \begin{cases}
-%       ψ, &\text{if }φ ≡ ψ\\
-%       ψ, &\text{if }reorder_{∨}(φ, ψ) ≡ ψ\\
-%       ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) ≡ ψ₁\\
-%         &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂\\
-%       ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₁, ψ) ≡ ψ\\
-%       ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₂, ψ) ≡ ψ\\
-%       φ, &\text{otherwise.}
-%     \end{cases}
-%   \end{split}
-%   \end{align*}
-% \end{lemma}
-
-% \begin{theorem}[thm-reorder$_{∧∨}$]
-%   \label{thm:thm-reorder-and-or}
-
-%   $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder_{∧∨}(φ, ψ)$, where,
-
-%   \begin{align}
-%       \begin{split}
-%       reorder_{∧∨}(φ, ψ)=
-%         \begin{cases}
-%           ψ, &\text{if } φ≡ψ\\
-%           ψ, &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
-%              &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
-%           φ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂\\
-%           conjunct_{∨}(φ, ψ) &\text{otherwise.}
-%         \end{cases}
-%       \end{split}
-%   \end{align}
-% \end{theorem}
+\subsubsection{Reordering.}
+Logic equivalence between propositions is a major issue to justify
+prover reasoning steps. Since we left out semantics to treat only the
+syntax aspects of the propositions, our approach shows that equivalence
+by converting propositions to their conjunctive normal forms and showing equivalence by reordering the conjunctions and the inner disjunctions.
+In this section, we provide some theorems to perform such reordering tasks, the goals are the following.
+
+\begin{itemize}
+  \item Reorder the disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots φₙ$ to match with $ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$, when for all $i = 1, \cdots, n$, exists at least one $ψⱼ$ such that $φᵢ ≡ ψⱼ$ for $j = 1, \cdots, n$.
+  \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$ when for all $i = 1, \cdots, n$, exists at least one $ψⱼ$ such that $φᵢ ≡ ψⱼ$ for $j = 1, \cdots, n$.
+\end{itemize}
+
+First, we define the $rdisj$ function in Eq.~(\ref{eq:rdisj-def}) to convert a disjunction in its right-associative form.
+\begin{definition}[rdisj]
+\begin{align}
+  \begin{split}
+    \label{eq:rdisj-def}
+    &rdisj(φ) : \Prop \to \Prop\\
+    &rdisj(φ) =
+    \begin{cases}
+    rdisj(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
+    φ₁ ∨ rdisj(φ₂),         & \text{if } φ ≡ φ₁ ∨ φ₂\\
+    φ,                      & \text{otherwise.}
+    \end{cases}
+  \end{split}
+\end{align}
+\end{definition}
+
+\begin{lemma}[lem-rdisj]
+\label{lem:lem-rdisj}
+  $Γ ⊢ φ$ then $Γ ⊢ rdisj(φ)$.
+\end{lemma}
+Following a similar way to define $rdisj$, we define the $rconj$ function,
+to convert a conjunction into its right-associative form.
+
+The $build_{∨}$ function in Eq.~(\ref{eq:build-or}) function intends to construct a disjunction from another disjunction, specifically, it rearranges the disjuncts in the source formula to match with the target disjunction formula as we described above.
+
+\begin{definition}[build$_{∨}$]
+\begin{equation}
+  \begin{split}
+  \label{eq:build-or}
+  &build_{∨} : \Prop → \Prop → \Prop\\
+  &build_{∨}(φ, ψ) =\\
+  &\hspace{3mm}
+  \begin{cases}
+  ψ, &\text{if } φ ≡ ψ\\
+  ψ, &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
+  φ, &\text{otherwise.}
+  \end{cases}
+  \end{split}
+\end{equation}
+\end{definition}
+
+\begin{lemma}[lem-build$_{∨}$]
+\label{lem:lem-build-or}
+$Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ build_{∨}(φ)$.
+\end{lemma}
+
+From now, we assume all propositions are right-associative unless otherwise stated. The $factor$ function in
+Eq.~(\ref{eq:factor-definition}) intends to simplify a special case of disjunction, the repeated disjuncts (e.g., $factor(φ ∨ φ) \mapsto\ φ$).
+Notice that other cases like $φ ∨ (ψ ∨ φ)$ do no reduce to $(ψ ∨ φ)$.
+
+\begin{definition}[factor]
+\begin{align}
+\begin{split}
+  \label{eq:factor-definition}
+  &factor : \Prop → \Prop\\
+  &factor(φ) =
+  \begin{cases}
+    φ₁,  &\text{if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ factor(φ₂)\\
+    φ,   &\text{otherwise.}
+  \end{cases}
+\end{split}
+\end{align}
+\end{definition}
+
+\begin{lemma}[lem-factor]
+\label{lem:lem-factor}
+  $Γ ⊢ φ$ then $Γ ⊢ factor(φ)$.
+\end{lemma}
+
+To construct a disjunction $ψ$ from another disjunction $φ$, we have used ideas from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove equality between nested disjunctions.
+The result is the
+$sbuild_{∨}$ function that uses every disjunct from the source formula, $φ$, to build up the target disjunction $ψ$.
+
+\begin{definition}[sbuild$_{∨}$]
+\begin{align}
+  \begin{split}
+  \label{eq:strong-build-or-definition}
+    &sbuild_{∨} : \Prop → \Prop → \Prop\\
+    &sbuild_{∨}(φ, ψ) =\\
+    &\hspace{3mm}
+    \begin{cases}
+      factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ)),  &\text{if }φ≡ φ₁ ∨ φ₂\\
+      build_{∨}(φ, ψ),  & \text{otherwise.}
+    \end{cases}
+  \end{split}
+\end{align}
+\end{definition}
+
+\begin{lemma}[lem-sbuild$_{∨}$]
+\label{lem:lem-sbuild-or}
+$Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ sbuild_{∨}(φ, ψ)$.
+\end{lemma}
+
+\begin{example}
+Let see the main idea behind the lem-sbuild$_{∨}$ lemma.
+We will build the disjunction $((p ∨ q) ∨ r)$ from the disjunction
+$(r ∨ (q ∨ p))$.
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⊢ q$}
+  \RightLabel{∨-intro₂}
+  \UnaryInfC{$Γ ⊢ p ∨ q$}
+  \RightLabel{∨-intro₁}
+  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
+
+  \AxiomC{$Γ ⊢ p$}
+  \RightLabel{∨-intro₁}
+  \UnaryInfC{$Γ ⊢ p ∨ q$}
+  \RightLabel{∨-intro₁}
+  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
+
+  \RightLabel{∨-elim}
+  \BinaryInfC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
+  \end{bprooftree}
+\end{equation*}
+
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⊢ r$}
+  \RightLabel{∨-intro₂}
+  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
+
+  \AxiomC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
+
+  \RightLabel{∨-elim}
+  \BinaryInfC{$Γ, r ∨ (q ∨ p) ⊢ (p ∨ q) ∨ r$}
+
+  \RightLabel{⇒-intro}
+  \UnaryInfC{$Γ ⊢ r ∨ (q ∨ p) ⇒ (p ∨ q) ∨ r$}
+
+  \end{bprooftree}
+\end{equation*}
+\end{example}
+
+Notice that using $sbuild_{∨}$ we can build not only a disjunction with the same disjuncts of the source formula but also a complete different formula by adding new disjuncts to the source formula.
+
+\begin{definition}[reorder$_{∨}$]
+\begin{align*}
+    \label{eq:reorder-or}
+    \begin{split}
+    &reorder_{∨} : \Prop \to \Prop \to \Prop\\
+    &reorder_{∨} (φ, ψ) = sbuild_{∨}(rdisj(φ), ψ).
+    \end{split}
+  \end{align*}
+\end{definition}
+
+\begin{theorem}[thm-reorder$_{∨}$]
+  \label{thm-reorder-or}
+  $Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$.
+\end{theorem}
+
+\begin{proof}
+Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
+\end{proof}
+
+We define similar functions and state some theorems as we previously did for disjunctions, but instead, we treat conjunctive normal forms.
+
+\begin{definition}[reorder$_{∧}$]
+  \begin{align*}
+      \begin{split}
+        &reorder : \Prop → \Prop \to Prop\\
+        &reorder_{∧}(φ, ψ) =
+        \begin{cases}
+          φ, &\text{if }φ ≡ ψ\\
+          ψ₁ ∧ ψ₂, &\text{if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁\\
+                  &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂\\
+          φ,       &\text{if } ψ ≡ ψ₁ ∧ ψ₂\\
+          conjunct(φ, ψ), &\text{otherwise.}
+        \end{cases}
+      \end{split}
+  \end{align*}
+\end{definition}
+
+\begin{lemma}[lem-reorder$_{∧}$]
+  \label{lem:lem-reorder-and}
+  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder(φ, ψ)$.
+\end{lemma}
+
+\begin{definition}[conjunct$_{∨}$]
+  \label{eq:conjunct-or-definition}
+\begin{align*}
+  \begin{split}
+    &conjunct_{∨} : \Prop → \Prop \to Prop\\
+    &conjunct_{∨}(φ, ψ) =
+    \begin{cases}
+      ψ, &\text{if }φ ≡ ψ\\
+      ψ, &\text{if }reorder_{∨}(φ, ψ) ≡ ψ\\
+      ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) ≡ ψ₁\\
+        &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂\\
+      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₁, ψ) ≡ ψ\\
+      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₂, ψ) ≡ ψ\\
+      φ, &\text{otherwise.}
+    \end{cases}
+  \end{split}
+  \end{align*}
+\end{definition}
+
+\begin{lemma}[lem-conjunct$_{∨}$]
+  \label{lem:lem-conjunct-or}
+  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$.
+\end{lemma}
+
+\begin{definition}[reorder$_{∧∨}$]
+ \begin{align*}
+      \begin{split}
+      &reorder : \Prop \to \Prop \to \Prop\\
+      &reorder_{∧∨}(φ, ψ)=
+        \begin{cases}
+          ψ, &\text{if } φ≡ψ\\
+          ψ, &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
+             &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
+          φ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂\\
+          conjunct_{∨}(φ, ψ) &\text{otherwise.}
+        \end{cases}
+      \end{split}
+  \end{align*}
+  \end{definition}
+
+\begin{theorem}[thm-reorder$_{∧∨}$]
+  \label{thm:thm-reorder-and-or}
+  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder_{∧∨}(φ, ψ)$.
+\end{theorem}
 
@@
 
-% \subsubsection{Resolve.}
-% \label{sssec:resolve}
-
-% The \resolve rule is a generalization version for resolution in propositional logic since the formulas are not shaped always as the aforementioned theorem expects (see Fig.~\ref{fig:metis-inferences}).
-
-% Since our approach is mere syntactic, in order to apply such a
-% theorem, we perform rearrangements inside the formulas to match with
-% the pattern expected by the resolution theorem.
-
-% \begin{lemma}[lem-rsol]
-%   \label{lem:lem-rsol}
-%   $Γ ⊢ φ$ then $Γ ⊢ rsol(φ)$, where,
-%   \begin{align*}
-%       \begin{split}
-%         rsol(φ) =
-%         \begin{cases}
-%           φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
-%           φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
-%           φ, &\text{otherwise.}
-%         \end{cases}
-%       \end{split}
-%   \end{align*}
-% \end{lemma}
-
-% \begin{theorem}[thm-resolve]
-%   \label{thm:thm-resolve}
-%   $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ\in\Prop$ then $Γ ⊢ resolve(φ₁, φ₂, l, ψ)$, where,
-%   \begin{equation*}
-%     resolve(φ₁, φ₂, l, ψ) =
-%       rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨} (φ₂, ¬ l ∨ ψ)).
-%   \end{equation*}
-% \end{theorem}
-
-% \begin{proof}
-% \begin{equation*}
-%   \begin{bprooftree}
-%     \AxiomC{$Γ ⊢ φ₁$}
-%     \RightLabel{thm-reorder$_{∨}$}
-%     \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ)$}
-
-%     \AxiomC{$Γ ⊢ φ₂$}
-%     \RightLabel{thm-reorder$_{∨}$}
-%     \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
-
-%     \RightLabel{∧-intro}
-%     \BinaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
-%     \RightLabel{lem-rsol}
-%     \UnaryInfC{$Γ ⊢ rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ))$}
-%   \end{bprooftree}
-%   \end{equation*}
-% \end{proof}
-
-% % subsubsection resolve (end)
-% % --------------------------------------------------------------------
+\subsubsection{Resolution.}
+\label{sssec:resolve}
+
+The \resolve rule incorporates the resolution theorem showed in
+Fig.~\ref{fig:metis-inferences} for the \TSTP derivations.
+This rule posses three arguments: a positive literal $l$ to apply the resolution theorem, and two derivations,
+$\mathcal{D}₁$ and $\mathcal{D}₂$.
+The positive literal $l$ must occur in
+the formula from the first derivation $\mathcal{D}₁$, and the
+negative literal must occur in the formula from the second derivation $\mathcal{D}₂$ (see the pattern in the \emph{resolve} rule).
+The following excerpt is an \Metis \TSTP example for the \resolve rule.
+
+\begin{verbatim}
+cnf(refute_0_0, plain, p | q,
+  inference(canonicalize, [], [normalize_0_0])).
+cnf(refute_0_1, plain, ~ p,
+  inference(canonicalize, [], [normalize_0_4])).
+cnf(refute_0_2, plain, q,
+  inference(resolve, [$cnf(p)], [refute_0_0, refute_0_1])).
+\end{verbatim}
+
+To emulate this rule, we perform rearrangements inside the formulas
+involved to match with the pattern expected by the resolution theorem
+described above.
+
+\begin{definition}[rsol]
+\begin{align*}
+      \begin{split}
+        &rsol : \Prop \to \Prop\\
+        &rsol(φ) =
+        \begin{cases}
+          φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
+          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
+          φ, &\text{otherwise.}
+        \end{cases}
+      \end{split}
+  \end{align*}
+\end{definition}
+
+\begin{lemma}[lem-rsol]
+  \label{lem:lem-rsol}
+  $Γ ⊢ φ$ then $Γ ⊢ rsol(φ)$.
+\end{lemma}
+
+\begin{definition}[resolve]
+ \begin{equation*}
+    resolve(φ₁, φ₂, l, ψ) =
+      rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨} (φ₂, ¬ l ∨ ψ)).
+  \end{equation*}
+\end{definition}
+
+\begin{theorem}[thm-resolve]
+  \label{thm:thm-resolve}
+  $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ\in\Prop$ then $Γ ⊢ resolve(φ₁, φ₂, l, ψ)$.
+\end{theorem}
+
+\begin{proof}
+\hspace{3mm}\\
+\begin{itemize}
+ \item
+ \begin{equation*}
+    \begin{bprooftree}
+      \AxiomC{$Γ ⊢ φ₁$}
+      \RightLabel{thm-reorder$_{∨}$.}
+      \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ)$}
+   \end{bprooftree}
+  \end{equation*}
+\item
+ \begin{equation*}
+    \begin{bprooftree}
+      \AxiomC{$Γ ⊢ φ₂$}
+      \RightLabel{thm-reorder$_{∨}$.}
+      \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+   \end{bprooftree}
+  \end{equation*}
+  \item
+  \begin{equation*}
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ)$}
+    \AxiomC{$Γ ⊢ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+    \RightLabel{∧-intro}
+    \BinaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+    \RightLabel{lem-rsol.}
+    \UnaryInfC{$Γ ⊢ rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ))$}
+  \end{bprooftree}
+  \end{equation*}
+\end{itemize}
+\end{proof}
+
+% subsubsection resolve (end)
+% --------------------------------------------------------------------
 

### 2017-10-13 paper/sections/proof-reconstruction.tex
[ paper ] negate rule added.

@@
 % -------------------------------------------------------------------
+
+\subsubsection{Negate.}
+
+Each proof of a subgoal is a refutation, thereby each proof assumes
+the negation of its subgoal. The \negate rule
+assumes the negation of such subgoals. This rules always
+appears after apply the \strip inference to the goal.
+
+\begin{verbatim}
+fof(goal, conjecture, (p & q)).
+fof(subgoal_0, plain, (p), inference(strip, [], [goal])).
+fof(subgoal_1, plain, (p => q), inference(strip, [], [goal])).
+fof(negate_0_0, plain, (~ p), inference(negate, [], [subgoal_0])).
+\end{verbatim}
+
+Then, to emulate this rule, we just introduce the negation
+of the subgoal by using the assume rule from the inferences in
+Fig.~\ref{fig:CPL-inference-rules}.
+
+% -------------------------------------------------------------------
 \subsubsection{Splitting a Conjunct.}
@@
 
-% % ------------------------------------------------------------------------
+% ------------------------------------------------------------------------
 
@@
 
-% \subsubsection{Normal Forms.}
-% \label{sssec:normal_forms}
-% \change{Here lacks of an introduction!}
-% A negative normal form for the formula φ is one in which negations
-% appear only in the literals and the expression is in terms only of
-% the boolean operators (¬, ∧, ∨).
+\subsubsection{Normalization.}
+\label{sssec:normal_forms}
+\change{Here lacks of an introduction!}
+A negative normal form for the formula φ is one in which negations
+appear only in the literals and the expression is in terms only of
+the boolean operators (¬, ∧, ∨).
 

### 2017-10-13 paper/sections/proof-reconstruction.tex
[ paper ] introduction added to emulate rules section.

@@
 has $\abbre{A}$ type. Types are written using small caps.
-We use \Prop type for propositions and a the dependent type, $Γ ⊢ φ$ for theorems. In the latter type, $Γ$ has $\abbre{List}~\Prop$ type
+We use \Prop type for propositions and the dependent type, $Γ ⊢ φ$ for theorems. In the latter type, $Γ$ has $\abbre{List}~\Prop$ type
 and $φ$ has type $\Prop$. $\abbre{List}$ is the usual inductive type
@@
 
-From the definition above, the size of the argument, ((φ₁ ∧ φ₂) ⇒ φ₃),
-is not structurally smaller than the input formula, (φ₁ ⇒ (φ₂ ⇒ φ₃)),
-since ((φ₁ ∧ φ₂) ⇒ φ₃) is not a subformula of (φ₁ ⇒ (φ₂ ⇒ φ₃)).
+From the definition above, the size of the argument, $((φ₁ ∧ φ₂) ⇒ φ₃)$,
+is not structurally smaller than the input formula, $(φ₁ ⇒ (φ₂ ⇒ φ₃))$,
+since $((φ₁ ∧ φ₂) ⇒ φ₃)$ is not a subformula of $(φ₁ ⇒ (φ₂ ⇒ φ₃))$.
 
@@
 Finally, following the technique mentioned, we get a curated version of
-$unshunt_{0}$ function presented in Eq.~(\ref{eq:unshunt-fixed}).
+$unshunt_{0}$ function presented in the following definition.
 
 \begin{definition}[unshunt]
-\begin{equation}
-\label{eq:unshunt-fixed}
-unshunt(\varphi) := unshunt_{1}(\varphi, unshunt_{cm}(\varphi)).
-\end{equation}
+\label{def:unshunt}
+  \begin{align*}
+    \begin{split}
+    &unshunt : \Prop → \Prop\\
+    &unshunt(\varphi) = unshunt_{1}(\varphi, unshunt_{cm}(\varphi)).
+    \end{split}
+  \end{align*}
 \end{definition}
@@
 \label{ssec:emulating-inferences}
+
+We emulate each \Metis inference rule by proving a
+function with the same name, and a theorem that
+proves the soundness of the function.
+The pattern is the following.
+
+\begin{itemize}
+\item \texttt{rule} is the \Metis inference rule.
+\item $rule$ is the emulated version function for \texttt{rule} inference.
+\begin{align*}
+\begin{split}
+&rule : \Prop → \Prop → \Prop\\
+&rule(φ, ψ) =
+  \begin{cases}
+  ψ, &\text{if }rule\text{ built }ψ\text{ by applying valid transformations to }φ\\
+  φ, &\text{otherwise.}
+  \end{cases}
+\end{split}
+\end{align*}
+
+\begin{itemize}
+  \item $φ$ is the \emph{source} formula.
+  \item $ψ$ is the \emph{target} formula.
+\end{itemize}
+\item thm-rule is the theorem, $Γ ⊢ rule(φ, ψ)$, that proves
+the soundness of the $rule$ function.
+\end{itemize}
 
@@
 	\item When $n = 0$, by definition, $Γ ⊢ φ$.
-	\item When $n = 1$, we apply the following theorem from~\cite{AgdaProp}
+	\item When $n = 1$, we apply the following theorem from~\cite{AgdaProp},
 		\begin{equation*}
@@
 \label{eq:split-definition}
-\mysplit(φ) =
+\begin{split}
+&split : \Prop → \Prop\\
+&\mysplit(φ) =
 \begin{cases}
@@
 \end{cases}
+\end{split}
 \end{equation}
@@
 \end{theorem}
-~\begin{proof}\hspace{2cm}\\
+\begin{proof}\hspace{2cm}
 \begin{itemize}
@@
 \end{lemma}
-Following a similar way to define $rdisj$, we define the $rconj$ function,
-to convert a conjunction into its right-associative form.
-
-The $build_{∨}$ function in Eq.~(\ref{eq:build-or}) function intends to construct a disjunction from another disjunction, specifically, it rearranges the disjuncts in the source formula to match with the target disjunction formula as we described above.
+% Following a similar way to define $rdisj$, we define the $rconj$ function,
+% to convert a conjunction into its right-associative form.
+
+The $build_{∨}$ function in Eq.~(\ref{eq:build-or}) intends to construct a disjunction from another disjunction, specifically, this functions will try to rearrange the disjuncts in the source formula to match with the target disjunction formula, similar as we described above.
 
@@
 
-We define similar functions and state some theorems as we previously did for disjunctions, but instead, we treat conjunctive normal forms.
+We define similar functions and state some theorems as we previously did for disjunctions, but instead, we treat only with conjunctive normal forms.
 
@@
 
-\begin{proof}
-\hspace{3mm}\\
+\begin{proof}\hspace{3mm}
 \begin{itemize}
@@
 
-% % --------------------------------------------------------------------
-
-% \subsubsection{Clausification.}
-% \label{sssec:clausification}
-
-% \begin{theorem}[thm-clausify]
-% \label{thm:thm-clausify}
-%   $Γ ⊢ φ$ and $ψ \in\Prop$ then $Γ ⊢ clausify(φ, ψ)$, where,
-%   \begin{align}
-%       clausify(φ,ψ) =
-%       \begin{cases}
-%         ψ, &\text{ if }φ≡ψ\\
-%         reorder_{∧∨}(cnf(φ), ψ), &\text{otherwise.}
-%       \end{cases}
-%   \end{align}
-% \end{theorem}
-
-% \begin{proof} When $φ ≡ ψ$, we use the $subs$ theorem Eq.~(\ref{eq:substitution-theorem}). Otherwise, we use Theorem \ref{thm:thm-reorder-and-or} and Theorem \ref{thm:thm-cnf}.
-% \end{proof}
-
-% % subsubsection clausification (end)
-% % --------------------------------------------------------------------
+% --------------------------------------------------------------------
+
+\subsubsection{Clausification.}
+\label{sssec:clausification}
+
+The \clausify rule transforms a
+propositional formula in its clausal normal form, a conjunction
+of clauses. Where a \emph{clause} is the disjunction of zero or more
+literals and a \emph{literal} is an atom (positive literal) or a
+negation of an atom (negative literal).
+Be aware this kind of conversion between one formula to its clausal normal form is not unique, and \Metis has a customized approach to perform that transformation.
+In the following \Metis \TSTP derivation, we saw a clear example, where
+clausify expands the formula \texttt{normalize\_0\_0} by using distributive
+laws.
+
+\begin{verbatim}
+fof(normalize_0_0, plain, (~ p | (q & r)),
+    inference(canonicalize, [], [a1])).
+fof(normalize_0_1, plain, ((~ p | q) & (~ p | r)),
+    inference(clausify, [], [normalize_0_0])).
+\end{verbatim}
+
+\begin{definition}[clausify]
+  \label{def:clausify}
+ \begin{align*}
+   \begin{split}
+      &clausify : \Prop → \Prop → Prop\\
+      &clausify(φ,ψ) =
+      \begin{cases}
+        ψ, &\text{ if }φ≡ψ\\
+        reorder_{∧∨}(cnf(φ), ψ), &\text{otherwise.}
+      \end{cases}
+      \end{split}
+  \end{align*}
+\end{definition}
+
+\begin{theorem}[thm-clausify]
+\label{thm:thm-clausify}
+  $Γ ⊢ φ$ and $ψ \in\Prop$ then $Γ ⊢ clausify(φ, ψ)$
+\end{theorem}
+
+\begin{proof} When $φ ≡ ψ$, we use the $subs$ theorem Eq.~(\ref{eq:substitution-theorem}). Otherwise, we use Theorem \ref{thm:thm-reorder-and-or} and Theorem \ref{thm:thm-cnf}.
+\end{proof}
+
+% subsubsection clausification (end)
+% --------------------------------------------------------------------
 
@@
 
-% % -------------------------------------------------------------------
-% \subsubsection{Simplify}
-% \label{sssec:simplify}
-
-% The \simplify rule is the application of the the lemma showed above,
-% but also the following lemmas that intend to reduce a list of derivations,
-% a conjunction of their formulas into a one smaller.
-
-% \improvement{Missing theorems here.}
-
-% % subsubsection simplify (end)
-% % -------------------------------------------------------------------
+% -------------------------------------------------------------------
+\subsubsection{Simplify}
+\label{sssec:simplify}
+
+The \simplify rule is an inference that performs simplification of
+definitions and tautologies. This rule
+transverses a list of formulas by applying different theorems (e.g.,
+\emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
+syllogism}) including those theorems for removing redundancies and definitions  from the description of the \canonicalize rule,
+Fig.
+\ref{fig:conjunctive-disjunctive-simpl}.
+This rules also use the resolution as we show in the description of the \resolve rule~\ref{thm:thm-resolve}.
+Let see the following excerpt from a \Metis \TSTP derivation where \simplify appears.
+
+\begin{verbatim}
+fof(normalize_1_0, plain, (~ p & ~ r & q),
+    inference(canonicalize, [], [negate_1_0])).
+fof(normalize_1_1, plain, ((p | q) & (p | r)),
+    inference(canonicalize, [], [a1])).
+fof(normalize_1_2, plain, (p | r),
+    inference(conjunct, [], [normalize_1_1])).
+fof(normalize_1_3, plain, ($false),
+    inference(simplify, [], [normalize_1_0, normalize_1_2])).
+\end{verbatim}
+
+% subsubsection simplify (end)
+% -------------------------------------------------------------------
 

### 2017-10-15 paper/sections/discussion.tex
[ paper ] introduction added to emulate rules section.
[ paper ] first description version for canonicalize.

@@
+In the following, we use the \Bool type for booleans defined as usual as
+well as $not$ function, $and$ function for the boolean conjunction,
+and $if_then_else$ dependent function type.
+
 We noted in \TSTP derivations that \Metis does not take into account
@@
 \textit{Clausification.} The \clausify rule transforms a
-propositional formula in clausal normal form, a conjunction
+propositional formula in its clausal normal form, a conjunction
 of clauses. Where a \emph{clause} is the disjunction of zero or more
@@
 \end{figure}
-
-% ...................................................................
-\vskip 2mm
-
-\textit{Resolution.} The \resolve rule incorporates the resolution theorem showed in Fig.~\ref{fig:metis-inferences} for the \TSTP derivations.
-This rule posses three arguments: a positive literal $l$ to apply the resolution theorem, and two derivations, $\mathcal{D}₁$ and $\mathcal{D}₂$.
-
-The positive literal $l$ must occur in
-the formula from the first derivation $\mathcal{D}₁$, and the
-negative literal must occur in the formula from the second derivation $\mathcal{D}₂$ (see the pattern in the \emph{resolve} rule).
-We refer the reader to see Section~\ref{sssec:resolve} for the formalization of the \resolve rule.
-
-\begin{verbatim}
-cnf(refute_0_0, plain, p | q,
-  inference(canonicalize, [], [normalize_0_0])).
-cnf(refute_0_1, plain, ~ p,
-  inference(canonicalize, [], [normalize_0_4])).
-cnf(refute_0_2, plain, q,
-  inference(resolve, [$cnf(p)], [refute_0_0, refute_0_1])).
-\end{verbatim}
-
-% ...................................................................
-
-\textit{Splitting a conjunct.} The \conjunct rule extracts from a
-conjunction one of its conjuncts; it is a generalization of the
-projection rules for the conjunction connective as the
-following \TSTP derivation shows.
-We refer the reader to see Theorem~\ref{thm:thm-conjunct}
-in Section~\ref{sssec:splitting-a-conjunct} for its formalization.
-
-\begin{verbatim}
-fof(normalize_1, plain, p & q & r,
-  inference(canonicalize, [], [x])).
-fof(normalize_2, plain, q,
-  inference(conjunct, [], [normalize_1])).
-\end{verbatim}
-
-\textit{Negate.}
-Each subgoal proof is a refutation, thereby each proof assumes
-the negation of its subgoal. The \negate rule
-assumes the negation of a given subgoal. This rules always
-appears after applies the \strip inference to the goal.
-
-\begin{verbatim}
-fof(subgoal_0, plain, p,
-  inference(strip, [], [goal])).
-fof(negate_0_0, plain, ~ p,
-  inference(negate, [], [subgoal_0])).
-\end{verbatim}
-
-% ...................................................................
-
-\textit{Simplification.}
-The \simplify rule is an inference that performs simplification of
-definitions and tautologies. This rule
-transverses a list of formulas by applying different theorems (e.g.,
-\emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
-syllogism}) including the list of theorems used by \canonicalize in
-Fig. \ref{fig:conjunctive-disjunctive-simpl} and the resolution
-theorem of the \resolve rule.
-We refer the reader to see Section~\ref{sssec:simplify}.

### 2017-10-15 paper/sections/proof-reconstruction.tex
[ paper ] first description version for canonicalize.

@@
 
-\subsubsection{A practical Example.}
+\subsubsection{A Practical Example.}
 Let us consider the following example to exhibit the technique
@@
 
-We emulate each \Metis inference rule by proving a
+In this section, we emulate each \Metis inference rule by proving a
 function with the same name, and a theorem that
-proves the soundness of the function.
-The pattern is the following.
+proves the soundness of the function. Then, we will find
+the following pattern to present the formalization for
+the \Metis inference rules.
 
 \begin{itemize}
-\item \texttt{rule} is the \Metis inference rule.
-\item $rule$ is the emulated version function for \texttt{rule} inference.
+\item \texttt{rule} is a \Metis inference rule
+\item $rule$ is the emulated version function for
+the \texttt{rule} inference.
 \begin{align*}
@@
 fof(goal, conjecture, p & r & q).
-fof(subgoal_0, plain, p, inference(strip, [], [goal])).
-fof(subgoal_1, plain, p => r, inference(strip, [], [goal])).
-fof(subgoal_2, plain, (p & r) => q, inference(strip, [], [goal])).
+fof(subgoal_0, plain, p,
+    inference(strip, [], [goal])).
+fof(subgoal_1, plain, p => r,
+    inference(strip, [], [goal])).
+fof(subgoal_2, plain, (p & r) => q,
+    inference(strip, [], [goal])).
 \end{verbatim}
@@
 the Theorem~\ref{thm:thm-strip}. But first, let us prove some
-lemmas for $unshunt$ function presented in Eq.~(\ref{eq:unshunt-fixed}),
-and $split$ function from the definition in Eq.~(\ref{eq:split-definition}).
+lemmas for $unshunt$ function presented in Def.~(\ref{def:unshunt}),
+and for $split$ function presented in Eq.~(\ref{eq:split-definition}).
 
@@
 
-\begin{proof} Use induction on the cases defined by the outcome of the
+\begin{sketchproof} Use induction on the cases defined by the outcome of the
 $unshunt$ function in Eq.~(\ref{eq:unshunt-structured}).
 \begin{itemize}
-	\item When $n = 0$, by definition, $Γ ⊢ φ$.
-	\item When $n = 1$, we apply the following theorem from~\cite{AgdaProp},
+	\item If $n = 0$, by definition we conclude $Γ ⊢ φ$.
+	\item If $n = 1$, we apply the following theorem proved in~\cite{AgdaProp},
 		\begin{equation*}
@@
 			  argument.
-
 \begin{itemize}
@@
 \end{equation*}
-
+\item Other cases are proved in a similar way.
 \end{itemize}
 \end{itemize}
-\end{proof}
+\end{sketchproof}
 
@@
 The definition above suffers termination problems since it is not
-a structural recursion. Therefore, we have reformulated the equation above to solve such a issue following the technique
-described in Section~\ref{ssec:structural-recursion}.
-Here and below, we refer to $split$ as the function after applying
-the process mentioned above.
+a structural recursion. Therefore, we have reformulated the equation
+above to solve such a issue following the technique
+described in Section~\ref{ssec:structural-recursion}. We refer to $split$
+as the function after applying the process mentioned above here and below
+unless otherwise stated.
 
@@
 
-\begin{proof} We now proceed by induction on the structure of the
-formula $φ$ in the definition of Eq.~(\ref{eq:split-definition}).
-For a complete proof, we refer the reader to~\cite{AgdaMetis}.\\[3mm]
-
+\begin{sketchproof}
+We now proceed by induction on the structure of the
+formula $φ$ by following the cases defined in
+Eq.~(\ref{eq:split-definition}).
+We present some cases but for a complete proof, we refer the reader to~\cite{AgdaMetis}.
 \begin{itemize}
+\item $(φ ≡ ¬ ¬ φ₁)$
+%Using the double negation equivalence, we conclude.
+\begin{equation*}
+  \begin{bprooftree}
+ \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+  \RightLabel{axiom}
+  \UnaryInfC{$Γ ⊢ unshunt(split(¬¬φ₁,n-1))$}
+  \RightLabel{lem-unshunt}
+  \UnaryInfC{$Γ ⊢split(¬¬φ₁,n-1)$}
+  \RightLabel{\thmsplit}
+  \UnaryInfC{$Γ ⊢ ¬¬φ₁$}
+  \RightLabel{axiom.}
+  \UnaryInfC{$Γ ⊢ φ$}
+  \end{bprooftree}
+\end{equation*}
+
 \item $(φ ≡ φ₁ ∧ φ₂)$. We get a proof for each conjunct and using the introduction rule for conjunction connective, the result follows.
@@
 \end{itemize}
-\end{proof}
+\end{sketchproof}
 
@@
 First, we define the $rdisj$ function in Eq.~(\ref{eq:rdisj-def}) to convert a disjunction in its right-associative form.
+
 \begin{definition}[rdisj]
+\label{def:rdisj}
 \begin{align}
@@
 \label{lem:lem-sbuild-or}
-$Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ sbuild_{∨}(φ, ψ)$.
+$Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ sbuild_{∨}(φ, ψ)$.
 \end{lemma}
@@
   \label{thm-reorder-or}
-  $Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ: \Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$.
 \end{theorem}
@@
   \label{lem:lem-reorder-and}
-  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ reorder(φ, ψ)$.
 \end{lemma}
@@
   \label{lem:lem-conjunct-or}
-  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$.
 \end{lemma}
@@
   \label{thm:thm-reorder-and-or}
-  $Γ ⊢ φ$, and $ψ \in\Prop$ then $Γ ⊢ reorder_{∧∨}(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ reorder_{∧∨}(φ, ψ)$.
 \end{theorem}
@@
   \label{thm:thm-resolve}
-  $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ\in\Prop$ then $Γ ⊢ resolve(φ₁, φ₂, l, ψ)$.
+  $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ: \Prop$ then $Γ ⊢ resolve(φ₁, φ₂, l, ψ)$.
 \end{theorem}
-
-\begin{proof}\hspace{3mm}
-\begin{itemize}
- \item
+\Needspace{3\baselineskip}
+\begin{proof}
  \begin{equation*}
@@
       \AxiomC{$Γ ⊢ φ₁$}
-      \RightLabel{thm-reorder$_{∨}$.}
+      \RightLabel{thm-reorder$_{∨}$,}
       \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ)$}
@@
   \end{equation*}
-\item
+    \vskip 1.5mm
  \begin{equation*}
@@
       \AxiomC{$Γ ⊢ φ₂$}
-      \RightLabel{thm-reorder$_{∨}$.}
+      \RightLabel{thm-reorder$_{∨}$,}
       \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
@@
   \end{equation*}
-  \item
+  \vskip 1.5mm
   \begin{equation*}
@@
   \end{equation*}
+\end{proof}
+
+% subsubsection resolve (end)
+% --------------------------------------------------------------------
+
+% % --------------------------------------------------------------------
+
+\subsubsection{Normalization.}
+\label{sssec:normal_forms}
+In the core of \Metis, we find an important module:
+\texttt{Normalize.sml}.
+This module is the responsible for rules like \canonicalize, \clausify,
+\conjunct or \simplify.
+One of the main purposes of the module consists of adding the axioms to the problem. Into this process, some transformation are carried out by different inference rules.
+For example, the \canonicalize rule can convert a FOF formula to their CNF form.
+In that process, the formula can suffers different transformations by removing redundancies (tautologies or definitions), converting the proposition to its normalized negative normal form, to its conjunctive normal form, or to a specialized normal form.
+
+\begin{definition}[\abbre{NProp}]
+  \NProp is the type for a formula in normalized negative normal form
+  in which negations appear only in the literals and the expression is in terms only of ($⊥$, $⊤$, $¬$, $∧$, $∨$, $⊻$) connectives. The $⊻$ connective is the exclusive disjunction.
+  We define the \NProp type in a similar way as we did for \Prop type.
+\end{definition}
+
+A sequent $Γ ⟝ φ$ represents a theorem where
+$Γ$ is a set of \Prop propositions premises, and $φ : \NProp$ is the
+sequent's conclusion. These theorems have a subset of rules from
+the classical inference rules in Fig.~\ref{fig:CPL-inference-rules}
+that apply for the connectives that coincides with \NProp type.
+
+% φ ⊻ ψ if and only if ¬ (φ ⇔ ψ).
+
+\begin{figure}
+  \[
+    \begin{bprooftree}
+      \AxiomC{$φ ∧ ⊥$}
+      \UnaryInfC{$⊥$}
+    \end{bprooftree}
+    \qquad
+    \begin{bprooftree}
+      \AxiomC{$φ ∧ ⊤$}
+      \UnaryInfC{$φ$}
+    \end{bprooftree}
+    \qquad
+    \begin{bprooftree}
+      \AxiomC{$φ ∧ ¬ φ$}
+      \UnaryInfC{$⊥$}
+    \end{bprooftree}
+    \qquad
+    \begin{bprooftree}
+      \AxiomC{$φ ∧ φ$}
+      \UnaryInfC{$φ$}
+    \end{bprooftree}
+  \]
+
+  \[
+    \begin{bprooftree}
+      \AxiomC{$φ ∨ ⊥$}
+      \UnaryInfC{$φ$}
+    \end{bprooftree}
+    \qquad
+    \begin{bprooftree}
+      \AxiomC{$φ ∨ ⊤$}
+      \UnaryInfC{$⊤$}
+    \end{bprooftree}
+    \qquad
+    \begin{bprooftree}
+      \AxiomC{$φ ∨ ¬ φ$}
+      \UnaryInfC{$⊤$}
+    \end{bprooftree}
+    \qquad
+    \begin{bprooftree}
+      \AxiomC{$φ ∨ φ$}
+      \UnaryInfC{$φ$}
+    \end{bprooftree}
+  \]
+\caption{Some definitions applied to translate a formula into its
+normalized normal form.}
+\label{fig:conjunctive-disjunctive-simpl}
+\end{figure}
+
+% -------------------------------------------------------------------
+\subsubsection{Redundancy.}
+\label{sssec:redundancy}
+
+In this section we provide the functions and theorems to
+remove inside a normalized formula the definitions showed in
+Fig.~\ref{fig:conjunctive-disjunctive-simpl}.
+
+\begin{remark}
+We assume all formulas are in right-associative form in
+the input of the functions by applying a version of $rdisj$ or $rconj$
+functions for normalized propositions (see Def.~\ref{def:rdisj}).
+\end{remark}
+
+In a disjunction, $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$, we say $ψ ∈_{∨} φ$,
+if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
+Note that $ψ ∈_{∨} φ$ can be defined as the equality
+$ψ ≡ conjunct_{∨}(φ, ψ)$.
+
+\begin{definition}[rm$_∨$]
+  \label{def:rm-or}
+  \begin{align*}
+    \begin{split}
+      &rm_{∨} :  \NProp \to \NProp\\
+      &rm_{∨}(φ) =
+      \begin{cases}
+        rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
+        φ₁ ∨ rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
+        φ,  &\text{otherwise.}
+      \end{cases}
+    \end{split}
+  \end{align*}
+\end{definition}
+
+\begin{lemma}[lem-rm$_{∨}$]
+  \label{lem:lem_rm-or}
+  $Γ ⟝ φ$ then $Γ ⟝ rm_{∨}(φ)$.
+\end{lemma}
+
+Now, we have removed redundancies in the disjunctions by applying the
+$rm_{∨}$, we can define a similar function to work with conjunctions.
+
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⟝ φ ∨ φ$}
+  \RightLabel{lem-rm$_∨$,}
+  \UnaryInfC{$Γ ⟝ φ$}
+  \end{bprooftree}
+  \qquad
+  \begin{bprooftree}
+  \AxiomC{$Γ ⟝ φ ∧ φ$}
+  \RightLabel{lem-rm$_∧$.}
+  \UnaryInfC{$Γ ⟝ φ$}
+  \end{bprooftree}
+\end{equation*}
+
+In a conjunction, $φ = φ₁ ∧ φ₂ ∧ \cdots ∧ φₙ$, we say
+$ψ ∈_{∧} φ$, if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
+We define $ψ ∈_{∧} φ$ as the equality $ψ ≡ conjunct(φ, ψ)$.
+
+\begin{definition}[rm$_∧$]
+\label{eq:rm-and}
+  \begin{align*}
+    \begin{split}
+    &rm_{∧} : \NProp \to \NProp\\
+    &rm_{∧}(φ) =
+    \begin{cases}
+      rm_{∧}(φ₂),      &\text{if }φ ≡ φ₁ ∧ φ₂, φ₁ ∈_{∧} φ₂\\
+      φ₁ ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
+      φ,               &\text{otherwise.}
+    \end{cases}
+    \end{split}
+  \end{align*}
+\end{definition}
+
+\begin{lemma}[lem-rm$_{∧}$] % (fold)
+  \label{lem:lem_rm-and}
+  $Γ ⟝ φ$ then $Γ ⟝ rm_{∧}(φ)$.
+\end{lemma}
+
+Continuing with the rest of tautologies from
+Fig.~\ref{fig:conjunctive-disjunctive-simpl}, we define
+$ndisj_{∨}$ function and $ndisj_{∨}$ function that
+take into account the following cases.
+
+\begin{equation*}
+\begin{bprooftree}
+  \AxiomC{$Γ ⟝ φ ∨ ¬~φ$}
+  \RightLabel{lem-ndisj$_{∨}$,}
+  \UnaryInfC{$Γ ⟝ ⊤$}
+\end{bprooftree}
+\begin{bprooftree}
+  \AxiomC{$Γ ⟝ φ ∨ ⊤$}
+  \RightLabel{lem-ndisj$_{∨}$,}
+  \UnaryInfC{$Γ ⟝ ⊤$}
+\end{bprooftree}
+\begin{bprooftree}
+  \AxiomC{$Γ ⟝ φ ∨ ⊥$}
+  \RightLabel{lem-ndisj$_{∨}$.}
+  \UnaryInfC{$Γ ⟝ φ$}
+\end{bprooftree}
+\end{equation*}
+
+\begin{equation*}
+\begin{bprooftree}
+  \AxiomC{$Γ ⟝ φ ∧ ¬~φ$}
+  \RightLabel{lem-ndisj$_{∧}$,}
+  \UnaryInfC{$Γ ⟝ ⊥$}
+\end{bprooftree}
+\begin{bprooftree}
+  \AxiomC{$Γ ⟝ φ ∧ ⊤$}
+  \RightLabel{lem-ndisj$_{∧}$,}
+  \UnaryInfC{$Γ ⟝ φ$}
+\end{bprooftree}
+\begin{bprooftree}
+  \AxiomC{$Γ ⟝ φ ∧ ⊥$}
+  \RightLabel{lem-ndisj$_{∧}$.}
+  \UnaryInfC{$Γ ⟝ ⊥$}
+\end{bprooftree}
+\end{equation*}
+
+\begin{definition}[ndisj$_{∨}$]
+  \label{def:ndisj-or}
+  \begin{align*}
+    \begin{split}
+    &ndisj_{∨} : \NProp \to \NProp\\
+    &ndisj_{∨}(φ) =
+      \begin{cases}
+        ⊤, &\text{if }φ ≡ ¬ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
+        ⊤, &\text{if}φ ≡ ¬ φ₁ ∨ φ₂,\ ndisj_{∨}(φ₂) ≡ ⊤\\
+        ¬ φ₁ ∨ ndisj_{∨}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∨ φ₂\\
+        ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ ¬φ₁ ∈_{∨} φ₂ \\
+        ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ ndisj_{∨}(φ₂) ≡ ⊤\\
+        φ₁ ∨ ndisj_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
+        φ, &\text{otherwise.}
+      \end{cases}
+    \end{split}
+  \end{align*}
+\end{definition}
+
+\begin{lemma}[lem-ndisj$_{∨}$] % (fold)
+  \label{lem:lem_ndisj-or}
+  $Γ ⟝ φ$ then $Γ ⟝ ndisj_{∨}(φ)$.
+\end{lemma}
+
+\begin{definition}[ndisj$_{∧}$]
+  \label{def:ndisj-and}
+  \begin{align*}
+    \begin{split}
+    &ndisj_{∧} : \NProp \to \NProp\\
+    &ndisj_{∧}(φ) =
+      \begin{cases}
+        ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
+        ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ ndisj_{∧}(φ₂) ≡ ⊥\\
+        ¬ φ₁ ∧ ndisj_{∧}(φ₂), &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂\\
+        ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
+        ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ndisj_{∧}(φ₂) ≡ ⊥\\
+        φ₁ ∧ ndisj_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
+        φ, &\text{otherwise.}
+      \end{cases}
+    \end{split}
+  \end{align*}
+\end{definition}
+
+\begin{lemma}[lem-ndisj$_{∧}$] % (fold)
+  \label{lem:lem_ndisj-and}
+  $Γ ⟝ φ$ then $Γ ⟝ ndisj_{∧}(φ)$.
+\end{lemma}
+
+% subsubsection redundancy (end)
+% -------------------------------------------------------------------
+
+We are ready to combine all function defined above in two function
+$canon_{∧}$ for removing redundancies in conjunctions, and
+$canon_{∨}$ for removing redundancies in disjunctions.
+
+\begin{definition}[canon$_{∧}$]
+\label{def:canon-and}
+\begin{align*}
+    \begin{split}
+      &canon_{∧} : \NProp \to \NProp\\
+      &canon_{∧}(φ) =
+        \begin{cases}
+        φⱼ, &\text{if } φ ≡ φ₁ ∧ φ₂,\ φᵢ ≡ ⊤,\text{ for } i,j = 1,2, i≠j\\
+        ⊥, &\text{if } φ ≡ φ₁ ∧ φ₂,\ φᵢ ≡ ⊥,\text{ for } i,j = 1,2\\
+       rm_∧(ndisj_∧(φ)), &\text{if } φ ≡ φ₁ ∧ φ₂\\
+       φ, &\text{otherwise.}
+        \end{cases}
+    \end{split}
+\end{align*}
+\end{definition}
+
+\begin{lemma}[lem-canon$_{∧}$]
+  \label{lem:lem_canon-and}
+  $Γ ⟝ φ$ then $Γ ⟝ canon_{∧}(φ)$.
+\end{lemma}
+
+\begin{definition}[canon$_{∨}$]
+\label{def:canon-or}
+\begin{align*}
+    \begin{split}
+      &canon_{∨} : \NProp \to \NProp\\
+      &canon_{∨}(φ) =
+        \begin{cases}
+        φⱼ, &\text{if } φ ≡ φ₁ ∨ φ₂,\ φᵢ ≡ ⊥,\text{ for } i,j = 1,2, i≠j\\
+        ⊤, &\text{if } φ ≡ φ₁ ∨ φ₂,\ φᵢ ≡ ⊤,\text{ for } i,j = 1,2\\
+        rm_∨(ndisj_∨(φ)), &\text{if } φ ≡ φ₁ ∧ φ₂\\
+        φ, &\text{otherwise.}
+        \end{cases}
+    \end{split}
+\end{align*}
+\end{definition}
+
+\begin{lemma}[lem-canon$_{∨}$]
+  \label{lem:lem_canon-or}
+  $Γ ⟝ φ$ then $Γ ⟝ canon_{∨}(φ)$.
+\end{lemma}
+
+\begin{remark}
+A similar treatment we do to define the $canon_{⊻} : \NProp \to \NProp$
+function that removes redundancies related with the exclusive
+disjunction connective, and to prove its soundness with the respective
+theorem thm-canon$_{⊻}$ in~\cite{AgdaMetis}.
+We left out this description for the brevity of this
+document and refer the interested reader to the implementation
+in~\cite{AgdaMetis}.
+\end{remark}
+
+Finally, we can translate formulas from \Prop to \NProp by defining the
+$nnf₀$ function based on the \Metis'source code. We have taken
+inspiration on the $nnf$ function described in
+\citeauthor{Bezem2002}~\cite{Bezem2002}. Their $nnf$ function translates
+formulas to their classical negative normal form. In the reference, the
+authors avoid a termination problem with a similar function by using as a
+extra argument, the polarity of the formula.
+
+For the polarity of a formula, we use the \abbre{Polarity} type with two
+constructors: $⊕$ to denote positive polarity, and $⊖$ to denote negative
+polarity.
+
+\begin{definition}[nnf₀]
+\label{def:nnf-zero}
+  \begin{align*}
+    \begin{split}
+    &nnf₀ : \abbre{Polarity} \to \Prop \to \NProp\\
+    &nnf₀(⊕, φ) =
+      \begin{cases}
+      canon_{∧}(nnf₀(⊕, φ₁) ∧ nnf₀(⊕, φ₂)), &\text{if }φ ≡ φ₁ ∧ φ₂ \\
+      canon_{∨}(nnf₀(⊕, φ₁) ∨ nnf₀(⊕, φ₂)), &\text{if }φ ≡ φ₁ ∨ φ₂ \\
+      canon_{∨}(nnf₀(⊖, φ₁) ∨ nnf₀(⊕, φ₂)), &\text{if }φ ≡ φ₁ ⇒ φ₂ \\
+      canon_{⊻}(nnf₀(⊖, φ₁) ⊻ nnf₀(⊕, φ₂)), &\text{if }φ ≡ φ₁ ⇔ φ₂ \\
+      nnf₀(⊖, φ₁),                          &\text{if }φ ≡ ¬ φ₁ \\
+      φ,                                    &\text{otherwise.} \\
+      \end{cases}\\
+    &nnf₀(⊖, φ) =
+      \begin{cases}
+      canon_{∨}(nnf₀(⊖, φ₁) ∨ nnf₀(⊖, φ₂)),  &\text{if }φ ≡ φ₁ ∧ φ₂ \\
+      canon_{∧}(nnf₀(⊖, φ₁) ∧ nnf₀(⊖, φ₂)),  &\text{if }φ ≡ φ₁ ∨ φ₂ \\
+      canon_{∧}(nnf₀(⊖, φ₂) ∧ nnf₀(⊖, φ₁)),  &\text{if }φ ≡ φ₁ ⇒ φ₂ \\
+      canon_{⊻}(nnf₀(⊕, φ₁) ⊻ nnf₀(⊕, φ₂)),  &\text{if }φ ≡ φ₁ ⇔ φ₂ \\
+      nnf₀(⊕, φ₁),                           &\text{if }φ ≡ ¬ φ₁ \\
+      ⊥,                                     &\text{if }φ ≡ ⊤ \\
+      ⊤,                                     &\text{if }φ ≡ ⊥ \\
+      φ,                                     &\text{otherwise.} \\
+      \end{cases}
+    \end{split}
+  \end{align*}
+\end{definition}
+
+\begin{lemma}[lem-nnf]
+  \label{lem:lem-nnf}
+  $Γ ⊢ φ$ then $Γ ⟝ nnf(φ)$ where,
+  \begin{align*}
+   \begin{split}
+     &nnf : \NProp \to \NProp\\
+     &nnf(φ) = nnf₀(⊕, φ).
+   \end{split}
+  \end{align*}
+\end{lemma}
+
+\begin{lemma}[lem-dist$_{∨}$]
+  \label{lem:lem-dist-or}
+  $Γ ⟝ φ$ then $Γ ⟝ dist_{∨}(φ)$, where,
+  \begin{align*}
+      \begin{split}
+      dist_{∨}(φ) =
+        \begin{cases}
+          dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃),
+            &\text{if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
+          dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃),
+            &\text{if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
+          φ, &\text{otherwise.}
+        \end{cases}
+      \end{split}
+  \end{align*}
+\end{lemma}
+
+\begin{lemma}[lem-dist]
+  \label{lem:lem-dist}
+  $Γ ⟝ φ$ then $Γ ⟝ dist(φ)$, where,
+  \begin{align*}
+      \begin{split}
+      dist(φ) =
+        \begin{cases}
+          dist(φ₁) ∧ dist(φ₂),
+            &\text{if }φ ≡ φ₁ ∧ φ₂\\
+          dist_{∨}(dist(φ₁) ∨ dist(φ₂)),
+            &\text{if }φ ≡ φ₁ ∨ φ₂\\
+          φ, &\text{otherwise.}
+        \end{cases}
+      \end{split}
+  \end{align*}
+\end{lemma}
+
+\begin{sketchproof} If $φ ≡ φ₁ ∨ φ₂$, we get for $i = 1, 2$,
+\begin{equation*}
+  \begin{bprooftree}
+    \RightLabel{assume}
+    \AxiomC{$Γ, φ_{i} ⊢ φ_{i}$}
+    \RightLabel{lem-dist}
+    \UnaryInfC{$Γ ⊢ dist(φ_{i})$}
+    \RightLabel{∨-intro$_{1,2}$}
+    \UnaryInfC{$Γ, φ_{i} ⊢ dist(φ₁) ∨ dist(φ₂)$}
+    \RightLabel{lem-dist$_{∨}$.}
+    \UnaryInfC{$Γ, φ_{i} ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$}
+    \end{bprooftree}
+\end{equation*}
+Then, by using the ∨-elim rule, from the last derivation above we derive
+$Γ, φ₁ ∨ φ₂ ⟝ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$, and the lemma follows.
+\end{sketchproof}
+
+\begin{definition}[form]
+\begin{align*}
+    \begin{split}
+      &form : \NProp \to \Prop\\
+      &form(φ) =
+      \begin{cases}
+        form(φ₁) ∧ form(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
+        form(φ₁) ∨ form(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂\\
+        form_{⊻}(φ₂),        &\text{ if }φ ≡ φ₁ ⊻ φ₂\\
+        % ⊥, &\text{ if }φ ≡ ⊥\\
+        % ⊤, &\text{ if }φ ≡ ⊤\\
+        φ, &\text{otherwise.}\\
+      \end{cases}
+    \end{split}
+\end{align*}
+\end{definition}
+
+\begin{lemma}[lem-form]
+  \label{lem:lem-form}
+   $Γ ⟝ φ$ then $Γ ⊢ form(φ)$.
+\end{lemma}
+
+\begin{theorem}[thm-cnf]
+\label{thm:thm-cnf}
+  $Γ ⊢ φ$ then $Γ ⊢ cnf(φ)$, where,
+  \begin{align*}
+    \begin{split}
+    &cnf : \NProp \to \NProp\\
+    &cnf = form ∘ dist ∘ nnf.
+    \end{split}
+  \end{align*}
+\end{theorem}
+
+\begin{proof}
+  Composition of the Lemmas \ref{lem:lem-form}, \ref{lem:lem-dist} and \ref{lem:lem-nnf}.
+\end{proof}
+
+Since all transformations performed above come from equivalences
+in classical propositional logic, we can also states the following theorem convenient for the next section.
+
+\begin{theorem}[thm-inv-cnf]
+\label{thm:thm-inv-cnf}
+  $Γ ⊢ cnf(φ)$ then $Γ ⊢ φ$.
+\end{theorem}
+
+% subsubsection normal_forms (end)
+% --------------------------------------------------------------------
+
+% -------------------------------------------------------------------
+\subsubsection{Canonicalize.}
+\label{sssec:canonicalize}
+
+The \canonicalize rule is an overloaded inference rule that performs
+mainly normalization of the proposition input by using theorems
+described in the section above. This rule  can convert a FOF formula in
+clausal form to a CNF clause. \Metis can introduce axioms, and definitions
+by using this rule. Since the nature of this rule consists of dealing with
+CNF clauses, our strategy to justify its reasoning mainly consists of
+testing for equality with normalized negative form of the formula, or a
+reordering of the conjunctive normal form of the source formula that
+matches the conjunctive normal form of the target formula.
+
+\begin{definition}[canonicalize]
+\begin{align*}
+    \begin{split}
+      &canonicalize : \Prop \to \Prop \to \Prop\\
+      &canonicalize(φ, ψ) =
+      \begin{cases}
+        ψ, &\text{if }ψ ≡ φ\\
+        ψ, &\text{if }ψ ≡ form(nnf(φ))\\
+        ψ, &\text{if }cnf(ψ) ≡ reorder_{∧∨}(cnf(φ), cnf(ψ))\\
+        φ, &\text{otherwise.}\\
+      \end{cases}
+    \end{split}
+\end{align*}
+\end{definition}
+
+\begin{theorem}[thm-canonicalize] % (fold)
+  \label{thm:thm-canonicalize}
+  \hspace{4mm}\\
+  $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ canonicalize(φ, ψ)$.
+\end{theorem}
+
+\begin{proof}\hspace{3mm}
+\begin{itemize}
+\item If $φ ≡ ψ$ by substitution theorem we conclude $Γ ⊢ ψ$.
+\item If $ψ ≡ form(nnf(φ))$,
+\begin{equation*}
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ φ$}
+    \RightLabel{lem-nnf}
+    \UnaryInfC{$Γ ⊢₂~nnf(φ)$}
+    \RightLabel{lem-form}
+    \UnaryInfC{$Γ ⊢ form(nnf(φ))$}
+    \AxiomC{$ψ ≡ form(nnf(φ))$}
+    \RightLabel{subst.}
+    \BinaryInfC{$Γ ⊢ ψ$}
+  \end{bprooftree}
+\end{equation*}
+\item If $γ := cnf(ψ) ≡ reorder_{∧∨}(cnf(φ), cnf(ψ))$,
+\begin{equation*}
+  \begin{bprooftree}
+     \AxiomC{$Γ ⊢ φ$}
+     \RightLabel{thm-cnf}
+     \UnaryInfC{$Γ ⊢ cnf(φ)$}
+     \RightLabel{thm-reorder$_{∧∨}$}
+     \UnaryInfC{$Γ ⊢ reorder_{∧∨}(cnf(φ), cnf(ψ))$}
+     \AxiomC{$γ$}
+    \RightLabel{subst}
+    \BinaryInfC{$Γ ⊢ cnf(ψ)$}
+    \RightLabel{thm-inv-cnf.}
+    \UnaryInfC{$Γ ⊢ ψ$}
+  \end{bprooftree}
+\end{equation*}
 \end{itemize}
@@
 
-% subsubsection resolve (end)
-% --------------------------------------------------------------------
-
-% % --------------------------------------------------------------------
-
-\subsubsection{Normalization.}
-\label{sssec:normal_forms}
-\change{Here lacks of an introduction!}
-A negative normal form for the formula φ is one in which negations
-appear only in the literals and the expression is in terms only of
-the boolean operators (¬, ∧, ∨).
-
-% To transform a formula φ to its equivalent \abbre{NNF} form, we
-% apply recursively the following equations. The function type for
-% \name{nnf} is $\Prop \to \Prop$.
-
-% \begin{lemma}[lem-nnf]
-%   \label{lem:lem-nnf}
-%   $Γ ⊢ φ$ then $Γ ⊢ nnf(φ)$, where,
-%   \begin{align*}
-%     \begin{split}
-%     \label{eq:nnf-definition}
-%     nnf(φ) =
-%       \begin{cases}
-%       nnf(φ₁) ∧ nnf(φ₂),
-%          &\text{if }φ ≡ φ₁ ∧ φ₂ \\
-%       nnf(φ₁) ∨ nnf(φ₂),
-%          &\text{if }φ ≡ φ₁ ∨ φ₂ \\
-%       nnf(¬ φ₁ ∨ φ₂),
-%          &\text{if }φ ≡ φ₁ ⇒ φ₂ \\
-%       nnf(φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁),
-%          &\text{if }φ ≡ φ₁ ⇔ φ₂ \\
-%       nnf(¬ φ₁ ∨ ¬ φ₂),
-%          &\text{if }φ ≡ ¬ (φ₁ ∧ φ₂) \\
-%       nnf(¬ φ₁ ∧ ¬ φ₂),
-%          &\text{if }φ ≡ ¬ (φ₁ ∨ φ₂) \\
-%       nnf(φ₁),
-%          &\text{if }φ ≡ ¬ ¬ φ₁ \\
-%       nnf(¬ (φ₂ ∨ ¬ φ₁)),
-%          &\text{if }φ ≡ ¬ (φ₁ ⇒ φ₂) \\
-%       nnf(¬ (φ₁ ⇒ φ₂ ∧ φ₂ ⇒ φ₁)),
-%          &\text{if }φ ≡ ¬ (φ₁ ⇔ φ₂) \\
-%       ⊥,  &\text{if }φ ≡ ¬ ⊤ \\
-%       ⊤,  &\text{if }φ ≡ ¬ ⊥ \\
-%       φ,  & \text{otherwise}.
-%       \end{cases}
-%     \end{split}
-%   \end{align*}
-% \end{lemma}
-
-% \begin{lemma}[lem-dist$_{∨}$]
-%   \label{lem:lem-dist-or}
-%   $Γ ⊢ φ$ then $Γ ⊢ dist_{∨}(φ)$, where,
-%   \begin{align*}
-%       \begin{split}
-%       dist_{∨}(φ) =
-%         \begin{cases}
-%           dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃),
-%             &\text{if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
-%           dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃),
-%             &\text{if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
-%           φ, &\text{otherwise.}
-%         \end{cases}
-%       \end{split}
-%   \end{align*}
-% \end{lemma}
-
-% \begin{lemma}[lem-dist]
-%   \label{lem:lem-dist}
-%   $Γ ⊢ φ$ then $Γ ⊢ dist(φ)$, where,
-%   \begin{align*}
-%       \begin{split}
-%       dist(φ) =
-%         \begin{cases}
-%           dist(φ₁) ∧ dist(φ₂),
-%             &\text{if }φ ≡ φ₁ ∧ φ₂\\
-%           dist_{∨}(dist(φ₁) ∨ dist(φ₂)),
-%             &\text{if }φ ≡ φ₁ ∨ φ₂\\
-%           φ, &\text{otherwise.}
-%         \end{cases}
-%       \end{split}
-%   \end{align*}
-% \end{lemma}
-
-% \begin{sketchproof}
-% Case when $φ ≡ φ₁ ∨ φ₂$.\\
-% For $i = 1, 2$,
-% \begin{equation}
-%   \begin{bprooftree}
-%     \RightLabel{assume}
-%     \AxiomC{$Γ, φ_{i} ⊢ φ_{i}$}
-%     \RightLabel{lem-dist}
-%     \UnaryInfC{$Γ ⊢ dist(φ_{i})$}
-%     \RightLabel{∨-intro$_{1,2}$}
-%     \UnaryInfC{$Γ, φ_{i} ⊢ dist(φ₁) ∨ dist(φ₂)$}
-%     \RightLabel{lem-dist$_{∨}$}
-%     \UnaryInfC{$Γ, φ_{i} ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$.}
-%     \end{bprooftree}
-% \end{equation}
-% Then, by using the ∨-elim rule, from the last derivation above we derive
-% $Γ, φ₁ ∨ φ₂ ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$, and the lemma follows.
-% \end{sketchproof}
-
-% \begin{theorem}[thm-cnf]
-% \label{thm:thm-cnf}
-%   $Γ ⊢ φ$ then $Γ ⊢ cnf(φ)$, where,
-%   \begin{equation}
-%     cnf(φ) = (dist \circ nnf) (\varphi).
-%   \end{equation}
-% \end{theorem}
-
-% \begin{proof}
-%   Composition of the Lemma \ref{lem:lem-dist} and Lemma \ref{lem:lem-nnf}.
-% \end{proof}
-% % subsubsection normal_forms (end)
-% % --------------------------------------------------------------------
+% subsubsection canonicalize (end)
+% -------------------------------------------------------------------
 
@@
 Be aware this kind of conversion between one formula to its clausal normal form is not unique, and \Metis has a customized approach to perform that transformation.
-In the following \Metis \TSTP derivation, we saw a clear example, where
+In the following \Metis \TSTP derivation, we see a clear example, where
 clausify expands the formula \texttt{normalize\_0\_0} by using distributive
@@
 \begin{verbatim}
+fof(a1, axiom, (p => (q & r))).
+...
 fof(normalize_0_0, plain, (~ p | (q & r)),
@@
    \begin{split}
-      &clausify : \Prop → \Prop → Prop\\
+      &clausify : \Prop → \Prop → \Prop\\
       &clausify(φ,ψ) =
@@
 \label{thm:thm-clausify}
-  $Γ ⊢ φ$ and $ψ \in\Prop$ then $Γ ⊢ clausify(φ, ψ)$
+  $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ clausify(φ, ψ)$.
 \end{theorem}
@@
 
+\begin{remark}
+The \clausify rule is always preceded by the application of the
+\canonicalize rule. Both rules perform Clausification that introduces
+into the problem axioms or definitions in the domain of the solution.
+The process is mainly described on paper by \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.
+\end{remark}
+
 % subsubsection clausification (end)
 % --------------------------------------------------------------------
-
-% % --------------------------------------------------------------------
-% \subsubsection{Normalization.}
-% \label{sssec:normalization}
-
-% In a disjunction, $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$, we say $ψ ∈_{∨} φ$,
-% if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
-% Then, we define the $rm_{∨}$ function to remove in a right-associative disjunction φ, those propositions ψ repeated in the formula.
-
-% \begin{equation*}
-% \label{eq:rm-or}
-%   rm_{∨}(φ) =
-%   \begin{cases}
-%     rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂, φ₁ ∈_{∨} φ₂\\
-%     φ₁ ∨ rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
-%     φ,  &\text{otherwise.}
-%   \end{cases}
-% \end{equation*}
-
-% Since, our goal consists of normalizing prepositions in \abbre{CNF}, we also need to generalize $rm_{∨}$ to work with conjunctions. We define $rm_{∧∨}$ function for that purpose.
-
-% \begin{equation*}
-% \label{eq:rm-and-or}
-%   rm_{∧∨}(φ) =
-%   \begin{cases}
-%     rm_{∧∨}(φ₁) ∧ rm_{∧∨}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
-%     rm_{∨}(rdisj(φ)),  &\text{otherwise.}
-%   \end{cases}
-% \end{equation*}
-
-% Now, we have removed redundancies in the disjunctions, we move forward and we remove redundancies at the level of the conjunction of the CNFs by applying the $rm_{∧}$ function.
-We define $ψ ∈_{∧} φ$ similar as we described above for disjunction.
-In a conjunction, $φ = φ₁ ∧ φ₂ ∧ \cdots ∧ φₙ$, we say
-% $ψ ∈_{∧} φ$, if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
-
-% \begin{equation*}
-% \label{eq:rm-and}
-%   rm_{∧}(φ) =
-%   \begin{cases}
-%     rm_{∧}(φ₁) ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂, φ₁ ∈_{∧} φ₂\\
-%     φ₁ ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
-%     φ,  &\text{otherwise.}
-%   \end{cases}
-% \end{equation*}
-
-% Finally, we remove redundancies in a proposition assuming that it is given in conjunctive normal form and right-associative, by composing the functions described above in the Eq.~(\ref{eq:redun-ast})
-% for the function $redun^{*}$.
-
-% \begin{equation*}
-%   \label{eq:redun-ast}
-%   redun^{*} = rm_{∧} ∘ rm_{∧∨}.
-% \end{equation*}
-
-% Then, performing rearrangements to match with the expected output
-% by $redon^{*}$ function.
-
-% \begin{equation*}
-%   \label{eq:redun}
-%   redun(φ) = reorder_{∧∨}(φ, redun^{*}(φ)).
-% \end{equation*}
-
-% \begin{theorem}[thm-redun]
-%   \label{thm:thm_redun}
-%   $Γ ⊢ φ$ then $Γ ⊢ redun(φ)$.
-% \end{theorem}
-
-% \begin{proof}
-% Use in Theorem~\ref{thm:thm-reorder-and-or} with $ψ$ equals to
-% $redun^{*}(φ)$.
-% \end{proof}
-
-% \improvement{We need here a text, or a comment about what
-% is going next.}
-
-% % subsection normalization (end)
-% % --------------------------------------------------------------------
-% \begin{lemma}[lem-rmPEM$_{∨}$]
-%   \label{lem:lem-rmPEM-or}
-%   \begin{align*}
-%   \label{eq:rmPEM-or}
-%     \begin{split}
-%     rmPEM_{∨}(φ) =
-%       \begin{cases}
-%         ⊤, &\text{if }φ ≡ ¬ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
-%         ⊤, &\text{if}φ ≡ ¬ φ₁ ∨ φ₂,\ rmPEM_{∨}(φ₂) ≡ ⊤\\
-%         ¬ φ₁ ∨ rmPEM_{∨}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∨ φ₂\\
-%         ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ ¬φ₁ ∈_{∨} φ₂ \\
-%         ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ rmPEM_{∨}(φ₂) ≡ ⊤\\
-%         φ₁ ∨ rmPEM_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
-%         φ, &\text{otherwise.}
-%       \end{cases}
-%     \end{split}
-%   \end{align*}
-% \end{lemma}
-
-% \begin{lemma}[lem-rmPEM$_{∧∨}$]
-%   \label{lem:lem-rmPEM-and-or}
-%   \begin{equation*}
-%     \label{eq:rmPEM-and-or}
-%     rmPEM_{∧∨}(φ) =
-%     \begin{cases}
-%       rmPEM_{∨}(φ₁) ∧ rmPEM_{∨∧}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
-%       rmPEM_{∨}(φ), &\text{otherwise.}
-%     \end{cases}
-%   \end{equation*}
-% \end{lemma}
-
-% \begin{lemma}[lem-rmBot$_{∧}$]
-%   \label{lem:lem-rmbot-and}
-%    $Γ ⊢ φ$ then $Γ ⊢ rmBot_{∧}(φ)$, where,
-%   \begin{equation*}
-%     \label{eq:rmBot-and}
-%     rmBot_{∧}(φ) =
-%     \begin{cases}
-%       ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
-%       ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ rmBot_{∧}(φ₂) ≡ ⊥\\
-%       ¬ φ₁ ∧ rmBot_{∧}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∧ φ₂\\
-%       ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
-%       ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ rmBot_{∧}(φ₂) ≡ ⊥\\
-%       φ₁ ∧ rmBot_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
-%       φ, &\text{otherwise.}
-%     \end{cases}
-%   \end{equation*}
-% \end{lemma}
 
@@
 %     canonicalize =
-%      canon ∘ rmBot_{∧} ∘ rmPEM_{∧∨} ∘ redun ∘ rconj ∘ cnf.
+%      canon ∘ ndisj_{∧} ∘ ndisj_{∧∨} ∘ redun ∘ rconj ∘ cnf.
 %   \end{equation*}
@@
 % -------------------------------------------------------------------
-\subsubsection{Simplify}
+\subsubsection{Simplify.}
 \label{sssec:simplify}

### 2017-10-16 paper/sections/acknowledgements.tex
[ paper ] describing simplify.

@@
 
-We thank Joe Leslie-Hurd for his support with its \Metis prover.
-We also acknowledge the work carried out by Alejandro G\'omez-Londo\~no~\cite{Gomez-Londono2015} used as the basis code for our \TSTP
-parsing module.
+We thank Joe Leslie-Hurd for his support and comments about \Metis.
+We also acknowledge the work carried out by Alejandro
+G\'omez-Londo\~no~\cite{Gomez-Londono2015} used as the basis
+for our \TSTP parsing module.
 
@@
 inviting us to be part of the \Agda Implementors’ Meeting XXV.
-We honored to present part of the research in this paper.
+We honored to present there part of this research.
 

### 2017-10-16 paper/sections/conclusions.tex
Paper (#36)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

* [ paper ] minor changes.

@@
 
-In this document, we reconstruct proofs
-of propositional logic without equality deliver by \Metis
-successfully.
+We presented a reliable proof-reconstruction of \Metis solutions
+for problems in classical propositional logic without logic.
+The reconstruction approach in this study was designed to use
+only a syntactic treatment of the logic without considering the
+semantics. This aspect represent a difficulty but also an opportunity
+to extend this work towards the support for first-order logic.
+As a first future work, we see the support of \Metis propositional
+fragment with equality.
 
-Despite the fact, our logic domain is more straightforward than
-first-order or high-order logic where there are many
-proof-reconstruction tools (see a list of some of them in the
-related work, Section \ref{sec:related-work}), we found some issues
-around the reconstruction that show this task is far from trivial.
-Depending  on the systems involved in the translation, some
-difficulties can arise. We listed some of them in Section
-\ref{sec:metis-language-and-proofs} and in Section
-\ref{sec:proof-reconstruction}.
+Summarizing, we provided for each \Metis inference rule a theorem that
+emulate the rule deduction. The emulated
+version rules exposed in Section~\ref{ssec:emulating-inferences} admit
+improvements, we left this for future work, particularly, a better
+implementation of \simplify rule.
+Some of the improvements are related with computational efficiency.
+For instance, we use widely functions to check for syntactical equivalence
+between propositions and to reorder propositions to match with another.
+We believe both are expensive tasks and can get help in the analysis
+step inside the translator tool.
 
-For instance, just showing equality between Normal Forms for the
-same formula in the output of the \canonicalize inference and a
-common implementation for this kind of conversion; we observed that
-\Metis performs reordering for each inner expression mainly in the
-presence of negative literals. Another aspect to take into account
-is the \Metis' treatment for conjunctions and disjunction;
-these connectives were treated as right associative and binary
-operators in the \TSTP format but that assumptions is not a standard.
-We had to update the \TSTP parser module introduced in
-\cite{Gomez-Londono2015} to include features like these.
+The proof-reconstruction tool presented in this paper
+is able to translate \Metis derivations in \TSTP format to \Agda proof-terms.
+The development presented in this paper can be extended to support
+other \ATPs for \CPL like \name{EProver} or \name{Z3}.
+This future work can be carried out by following the \name{EProver} inference
+rules described on Kanso' Ph.D. Thesis~\cite{Kanso2012}.
 
-An important matter was how dealing with
-the equality between formulas since, in our approach, we only work
-with the syntactic treatment of the logic without considering the
-semantics.
-One of the main reasons for such a restriction relay on our plans
-further to support first-order logic, where a semantic treatment is
-not viable since it computational complexity.\unsure{Please confirm this.}
-
-Nevertheless, the proof-reconstruction is certainly possible, and
-the verification of solutions of \CPL problems can be carried out
-successful in \Agda. Our tool is able to translate \Metis
-derivations in \TSTP format to deliver \Agda code of the proof,
-\change{Better uses \emph{proof-terms}?}
-and this proof can be type-checked by \Agda.
-
-The source code of our tool can be extended to support
-other \ATPs for \CPL like \name{E}. This work can be carried out
-may following the description in Kanso' Ph.D. Thesis~\cite{Kanso2012}
-for the inference rules of \name{E} or \name{Z3}.
-
-Trying to justify a proof-object of a theorem prover has a
-significant impact, may increase the trustworthiness of the prover
-proving its correctness, or contrary, revealing important issues to
-improve the system. In both cases, there is a benefit for both
-sides, the user of this technology, and their developers.
-
-For instance, while writing this document, we found a soundness bug,
-a bug in the printing out of the \TSTP derivations, and a bug in the
-parsing for \TPTP problem in \Metis. Fortunately, all these bugs
-were fixed quickly by Hurd\footnote{Issues No. 4, No. 2, and the
-commit \name{8a3f11e} from the \Metis' official repository
-\url{https://github.com/gilith/metis}}, and a new version of \Metis
-was released (version 2.3, release 20170810).
-
-% \subsubsection*{Future Work.}
-% \label{ssec:future-work}
+One of the main contribution of this study is
+increasing the trustworthiness of these automatic provers,
+in our case, \Metis. Justify a proof-object of a theorem prover has a real
+significant impact for these automatic tools.
+The reverse engineering task can reveal important issues or bugs
+in many parts of these system (e.g., preprocessing, reasoning, or
+deduction modules). While doing this research, we had the opportunity
+to find some of those kind of bugs\footnote{Issues No.~2, No.~4. and
+commit \name{8a3f11e} in the \Metis' official repository
+\url{https://github.com/gilith/metis}}. Fortunately, all these bugs
+were fixed quickly for release 20170810 by Joe Hurd.
 

### 2017-10-16 paper/sections/proof-reconstruction.tex
[ paper ] describing simplify.

@@
 automatic theorem prover, is \Metis; the target system is a proof
-assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types is valid (see a description of \Agda for its main features in
-Section~\ref{sec:implementation}).
+assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types is valid.
+%  (see a description of \Agda for its main features in
+% Section~\ref{sec:implementation}).
 The overview of the proof-reconstruction is presented in
@@
 
-\subsubsection{A Practical Example.}
+\subsubsection*{A Practical Example.}
 Let us consider the following example to exhibit the technique
@@
 
-\subsubsection{Strip a Goal.}
+\subsubsection{Stripping a Goal.}
 \label{sssec:strip-a-goal}
@@
 
-\subsubsection{Negate.}
+\subsubsection{Negating Subgoals.}
 
@@
 Fig.~\ref{fig:metis-inferences} for the \TSTP derivations.
-This rule posses three arguments: a positive literal $l$ to apply the resolution theorem, and two derivations,
-$\mathcal{D}₁$ and $\mathcal{D}₂$.
+This rule posses three arguments: a positive literal $l$ to apply the
+resolution theorem, and two derivations.
 The positive literal $l$ must occur in
-the formula from the first derivation $\mathcal{D}₁$, and the
-negative literal must occur in the formula from the second derivation $\mathcal{D}₂$ (see the pattern in the \emph{resolve} rule).
-The following excerpt is an \Metis \TSTP example for the \resolve rule.
-
+the formula from the first derivation and the
+negative literal must occur in the formula from the second derivation,
+see the pattern of \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.
+
+% \begin{figure}
+\label{fig:resolve-tstp-example}
 \begin{verbatim}
-cnf(refute_0_0, plain, p | q,
-  inference(canonicalize, [], [normalize_0_0])).
-cnf(refute_0_1, plain, ~ p,
-  inference(canonicalize, [], [normalize_0_4])).
-cnf(refute_0_2, plain, q,
-  inference(resolve, [$cnf(p)], [refute_0_0, refute_0_1])).
+cnf(refute_0_4, plain, (~ r | p | q),
+    inference(canonicalize, [], [normalize_0_5])).
+cnf(refute_0_5, plain, (p | q | r),
+    inference(canonicalize, [], [normalize_0_6])).
+cnf(refute_0_6, plain, (p | q),
+    inference(resolve, [$cnf(r)], [refute_0_5, refute_0_4])).
 \end{verbatim}
+% \caption{Excerpt of a \Metis \TSTP example for the \resolve rule.}
+% \end{figure}
 
@@
 involved to match with the pattern expected by the resolution theorem
-described above.
+described above. We begin by defining a convenient version of
+the binary resolution in Def.~\ref{def:rsol}.
 
 \begin{definition}[rsol]
+\label{def:rsol}
 \begin{align*}
@@
 
+In Def.~\ref{def:resolve}, the emulated rule for $resolve$
+has four arguments. The first three were described
+above. The last one, ψ, represents the expected conclusion in the \Metis
+derivation.
+
 \begin{definition}[resolve]
+\label{def:resolve}
  \begin{equation*}
@@
 \end{proof}
+
+\begin{figure}
+\label{fig:resolve-example}
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$Γ ⊢ ¬ r ∨ p ∨ q$}
+  \AxiomC{$Γ ⊢ p ∨ q ∨ r $}
+  \RightLabel{thm-resolve}
+  \BinaryInfC{$Γ ⊢ resolve(¬ r ∨ p ∨ q, p ∨ q ∨ r, r, p ∨ q)$}
+  \UnaryInfC{$Γ ⊢ p ∨ q$}
+  \end{bprooftree}
+\end{equation*}
+\caption{Example of a resolution in \Metis using
+Thm.~\ref{thm:thm-resolve}.}
+%Application of Thm.~\ref{thm:thm-resolve} for the \TSTP excerpt Fig.~\ref{fig:resolve-tstp-example}.}
+\end{figure}
 
@@
 testing for equality with normalized negative form of the formula, or a
-reordering of the conjunctive normal form of the source formula that
-matches the conjunctive normal form of the target formula.
+reordering of the conjunctive normal form of the source formula to match
+the conjunctive normal form of the target formula.
 
 \begin{definition}[canonicalize]
+\label{def:canonicalize}
 \begin{align*}
@@
 \begin{remark}
-The \clausify rule is always preceded by the application of the
-\canonicalize rule. Both rules perform Clausification that introduces
+The \clausify rule is often preceded by the \canonicalize rule.
+Both rules perform \emph{Clausification} that introduces
 into the problem axioms or definitions in the domain of the solution.
-The process is mainly described on paper by \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.
+The Clausification algorithms is mainly described on paper by
+\citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}. We left for future work
+investigate the consequences of removing $clausify$ inference by
+strengthen $canonicalize$ rule in Def.~\ref{def:canonicalize}
 \end{remark}
@@
 
-% \begin{lemma}[lem-canon]
-%   \label{lem:lem-canon}
-%   \begin{align*}
-%   \begin{split}
-%   &canon(φ) =\\
-%   &\hspace{3mm}
-%   \begin{cases}
-%       canon(φⱼ), &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊤,\\
-%                  &\text{for same } i,j = 1,2, i≠j\\
-%      ⊥, &\text{if } φ ≡ φ₁ ∧ φ₂,\ canon(φᵢ) ≡ ⊥, i = 1,2\\
-%      canon(φ₁) ∧ canon(φ₂), &\text{if } φ ≡ φ₁ ∧ φ₂\\
-%      ⊤, &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊤, i = 1,2\\
-%      canon(φⱼ), &\text{if } φ ≡ φ₁ ∨ φ₂,\ canon(φᵢ) ≡ ⊥,\\
-%                 &\text{for same } i,j = 1,2, i≠j\\
-%      canon(φ₁) ∨ canon(φ₂), &\text{if } φ ≡ φ₁ ∨ φ₂\\
-%      φ, &\text{otherwise.}
-%     \end{cases}
-%   \end{split}
-%   \end{align*}
-% \end{lemma}
-
-% \begin{theorem}[thm-canonicalize] % (fold)
-%   \label{thm:thm-canonicalize}
-%   $Γ ⊢ φ$ then $Γ ⊢ canonicalize(φ)$, where,
-%   \begin{equation*}
-%     canonicalize =
-%      canon ∘ ndisj_{∧} ∘ ndisj_{∧∨} ∘ redun ∘ rconj ∘ cnf.
-%   \end{equation*}
-% \end{theorem}
-
-% The \canonicalize rule acts in \Metis' \TSTP derivations in three main cases. First, introducing the
-% negation of a subgoal. Second, to simplify an intermediate derivation.
-% Third, introducing an axiom or a definition of the.
-% To justify the two first cases, we use the Theorem~\ref{thm:thm-canonicalize}. For the last case, we use the Lemma~\ref{lem:lem-nnf}.
-
 % -------------------------------------------------------------------
-\subsubsection{Simplify.}
+\subsubsection{Simplification.}
 \label{sssec:simplify}
@@
 definitions and tautologies. This rule
-transverses a list of formulas by applying different theorems (e.g.,
-\emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
-syllogism}) including those theorems for removing redundancies and definitions  from the description of the \canonicalize rule,
-Fig.
-\ref{fig:conjunctive-disjunctive-simpl}.
-This rules also use the resolution as we show in the description of the \resolve rule~\ref{thm:thm-resolve}.
-Let see the following excerpt from a \Metis \TSTP derivation where \simplify appears.
-
+transverses a list of inner derivations by applying different theorems
+(e.g., \emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
+syllogism}) to get a contradiction or just simplify the formulas.
+To emulate this rule, we have included theorems
+from \canonicalize rule Section~\ref{sssec:canonicalize} and
+\resolve rule Section~\ref{sssec:resolve}.
+
+\begin{remark}
+Besides the fact, $\List\ \Prop \to \Prop$ is the type that coincides
+with the reading of a \TSTP derivation, we choose a different option.
+In the translation from \TSTP to \Agda, we build a conjunction
+from the list of derivations by introducing binary conjunction
+with $∧$-intro rule. That avoids us to define a new sequent type
+to support \List \Prop type in the conclusion side.
+\end{remark}
+
+\begin{figure}
 \begin{verbatim}
@@
 \end{verbatim}
+\caption{Example of \simplify rule in a \TSTP derivation of \Metis.}
+\end{figure}
+
+\begin{align}
+    \begin{split}
+      &\textit{simpl} : \Prop \to \Prop \to \Prop \to \Prop\\
+      &\textit{simpl}(φ₁, φ₂ ψ) =
+      \begin{cases}
+        ψ, &\text{if }φᵢ ≡ ψ,\text{ for some }i = 1, 2\\
+        ψ, &\text{if }φ₁ ≡ φ₂ ⇒ ψ\\
+      \end{cases}
+    \end{split}
+\end{align}
+
+\begin{theorem}[thm-simplify] % (fold)
+  \label{thm:thm-simplify}
+$\{ Γ ⊢ φᵢ \}$ for $i = 1, \cdots, n$ then
+$Γ ⊢ simplify (\bigwedge_{i=1}^n φ)$.
+\end{theorem}
 

### 2017-10-16 paper/sections/related-work.tex
[ paper ] describing simplify.

@@
 
-% Kanso and Setzer~\cite{kanso2016light} integrate \name{Z3} in \Agda
-% but they also integrate the propositional fragment of the \name{E} prover in
-% \cite{Kanso2012}. They cataloged these two integration as
-% \emph{Oracle and Reflection} and \emph{Oracle and Justification}, respectively.
-% Their integration with the \name{E} prover is the most related work with our
-% approach found at the moment while we write this document. Besides the use
-% of the same \ITP, crucial differences easily arise like decidability of
-% propositional logic using semantics that we do not take into account for the
-% reason we describe later on in Section~\ref{sec:conclusions}.
-
+Kanso and Setzer~\cite{kanso2016light} integrate the propositional fragment of \name{EProver} in \Agda.
+In this work, the authors translate automatically propositional logic problems written in \Agda to \TPTP problems.
+By calling an external wrapper the ATP, this tool gets a \TSTP derivation.
+The tool parses the \name{EProver} derivation and outputs
+\Agda code. After that, we say their proof-reconstruction is almost
+similar as the approach presented in Section~\ref{ssec:workflow}.
+Nevertheless, Kanso and Setzer aim to justify some of the inference rules
+by using propositional semantics instead of just syntactic derivation
+steps.
 \end{document}

### 2017-10-16 paper/sections/proof-reconstruction.tex
[ paper ] fixing missing types, dots.

@@
 has $\abbre{A}$ type. Types are written using small caps.
-We use \Prop type for propositions and the dependent type, $Γ ⊢ φ$ for theorems. In the latter type, $Γ$ has $\abbre{List}~\Prop$ type
+We use \Prop type for propositions and the dependent type, $Γ ⊢ φ$ for
+theorems. In the latter type, $Γ$ has $\abbre{List}~\Prop$ type
 and $φ$ has type $\Prop$. $\abbre{List}$ is the usual inductive type
@@
 To emulate \Metis' inference rules in type theory,
-we observed that transformations performed by some rules were given by \emph{general recursive} functions.
+we observed that transformations performed by some rules were given
+by \emph{general recursive} functions.
 But algorithms based on general recursions can not be translated
@@
 Therefore, for a general recursive function $f: \Prop \to \Prop$
-with termination problems, we states a new function $f^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls must done by
-using induction on the \Nat type structure.
+with termination problems, we states a new function
+$f^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls must be
+done by using induction on the \Nat type structure.
 
@@
 \begin{split}
-&unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\
+&unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\%\hspace{10cm}\\
 &unshunt_{1}(φ, \suc(n)) =\\
@@
 
-In the case of the $unshunt_0$ function in
-Eq.~(\ref{eq:unshunt-definition}), we define the complexity function
-$unshunt_{cm}: \Prop → \NN$ for our $unshunt_{1}$
-presented in Eq.~(\ref{eq:unshunt-rank-definition}).
+We define the $unshunt_{cm}: \Prop → \NN$ function as
+the complexity measure for $unshunt_0$ function.
 
@@
 Finally, following the technique mentioned, we get a curated version of
-$unshunt_{0}$ function presented in the following definition.
+$unshunt_{0}$ function presented in Def.~\ref{def:unshunt}.
 
@@
 the negation of its subgoal. The \negate rule
-assumes the negation of such subgoals. This rules always
-appears after apply the \strip inference to the goal.
+assumes the negation of such subgoals. This rule
+appears after applying the \strip inference to the goal.
 
@@
 The \conjunct rule extracts from a
-conjunction one of its conjuncts; it is a generalization of the
+conjunction one of its conjuncts. This rule is a generalization of the
 projection rules for the conjunction connective as the
-following \TSTP excerpt shows.
+following \TSTP excerpt shows us.
 
@@
   &conjunct : \Prop \to \Prop \to \Prop\\
-  &conjunct(φ, ψ) =\\
-  &\hspace{3mm}
+  &conjunct(φ, ψ) =
     \begin{cases}
         ψ, &\text{if }φ ≡ ψ\\
-      ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }ψ ≡ conjunct(φ₁, ψ)\\
-      ψ, &\text{if }φ ≡ φ₁ ∧ φ₁\text{ and }ψ ≡ conjunct(φ₂, ψ)\\
+        ψ, &\text{if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ conjunct(φ₁, ψ)\\
+        ψ, &\text{if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ conjunct(φ₂, ψ)\\
         φ, &\text{otherwise.}
@@
 syntax aspects of the propositions, our approach shows that equivalence
-by converting propositions to their conjunctive normal forms and showing equivalence by reordering the conjunctions and the inner disjunctions.
-In this section, we provide some theorems to perform such reordering tasks, the goals are the following.
+by converting propositions to their conjunctive normal forms and showing
+equivalence by reordering the conjunctions and the inner disjunctions.
+In this section, we provide some theorems to perform such reordering tasks,
+the goals are the following.
 
 \begin{itemize}
-  \item Reorder the disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots φₙ$ to match with $ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$, when for all $i = 1, \cdots, n$, exists at least one $ψⱼ$ such that $φᵢ ≡ ψⱼ$ for $j = 1, \cdots, n$.
-  \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$ when for all $i = 1, \cdots, n$, exists at least one $ψⱼ$ such that $φᵢ ≡ ψⱼ$ for $j = 1, \cdots, n$.
+  \item Reorder the disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots φₙ$ to match with
+$ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$, when for all $i = 1, \cdots, n$, exists at
+least one $ψⱼ$ such that $φᵢ ≡ ψⱼ$ for $j = 1, \cdots, n$.
+  \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another
+CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$ when for all $i = 1, \cdots, n$, exists at
+least one $ψⱼ$ such that $φᵢ ≡ ψⱼ$ for $j = 1, \cdots, n$.
 \end{itemize}
 
-First, we define the $rdisj$ function in Eq.~(\ref{eq:rdisj-def}) to convert a disjunction in its right-associative form.
+First, we define the $rdisj$ function in Eq.~(\ref{eq:rdisj-def}) to convert
+a disjunction in its right-associative form.
 
@@
 
-The $build_{∨}$ function in Eq.~(\ref{eq:build-or}) intends to construct a disjunction from another disjunction, specifically, this functions will try to rearrange the disjuncts in the source formula to match with the target disjunction formula, similar as we described above.
+The $build_{∨}$ function in Eq.~(\ref{eq:build-or}) intends to construct a
+disjunction from another disjunction, specifically, this functions will try
+to rearrange the disjuncts in the source formula to match with the target
+disjunction formula, similar as we described above.
 
@@
 
-From now, we assume all propositions are right-associative unless otherwise stated. The $factor$ function in
-Eq.~(\ref{eq:factor-definition}) intends to simplify a special case of disjunction, the repeated disjuncts (e.g., $factor(φ ∨ φ) \mapsto\ φ$).
+From now, we assume all propositions are right-associative unless otherwise stated.
+The $factor$ function in Eq.~(\ref{eq:factor-definition}) intends to simplify a
+special case of disjunction, the repeated disjuncts (e.g., $factor(φ ∨ φ) \mapsto\ φ$).
 Notice that other cases like $φ ∨ (ψ ∨ φ)$ do no reduce to $(ψ ∨ φ)$.
@@
 
-To construct a disjunction $ψ$ from another disjunction $φ$, we have used ideas from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove equality between nested disjunctions.
-The result is the
-$sbuild_{∨}$ function that uses every disjunct from the source formula, $φ$, to build up the target disjunction $ψ$.
+To construct a disjunction $ψ$ from another disjunction $φ$, we have used ideas
+from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove equality
+between nested disjunctions. The result is the $sbuild_{∨}$ function that uses
+every disjunct from the source formula, $φ$, to build up the target disjunction $ψ$.
 
@@
       \begin{split}
-        &reorder : \Prop → \Prop \to Prop\\
+        &reorder : \Prop → \Prop \to \Prop\\
         &reorder_{∧}(φ, ψ) =
@@
   \begin{split}
-    &conjunct_{∨} : \Prop → \Prop \to Prop\\
+    &conjunct_{∨} : \Prop → \Prop \to \Prop\\
     &conjunct_{∨}(φ, ψ) =
@@
       ψ, &\text{if }reorder_{∨}(φ, ψ) ≡ ψ\\
-      ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂, conjunct_{∨}(φ, ψ₁) ≡ ψ₁\\
+      ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂,\ conjunct_{∨}(φ, ψ₁) ≡ ψ₁,\\
         &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂\\
-      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₁, ψ) ≡ ψ\\
-      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂, conjunct_{∨}(φ₂, ψ) ≡ ψ\\
+      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂,\ conjunct_{∨}(φ₁, ψ) ≡ ψ\\
+      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂,\ conjunct_{∨}(φ₂, ψ) ≡ ψ\\
       φ, &\text{otherwise.}
@@
           ψ, &\text{if } φ≡ψ\\
-          ψ, &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
+          ψ, &\text{if } ψ ≡ ψ₁ ∧ ψ₂,\ reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
              &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
@@
 \label{def:resolve}
- \begin{equation*}
-    resolve(φ₁, φ₂, l, ψ) =
+ \begin{align*}
+ \begin{split}
+    &resolve : \Prop \to \Prop \to \Prop \to \Prop \to \Prop\\
+    &resolve(φ₁, φ₂, l, ψ) =
       rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨} (φ₂, ¬ l ∨ ψ)).
-  \end{equation*}
+  \end{split}
+  \end{align*}
 \end{definition}
@@
         ⊤, &\text{if }φ ≡ ¬ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
-        ⊤, &\text{if}φ ≡ ¬ φ₁ ∨ φ₂,\ ndisj_{∨}(φ₂) ≡ ⊤\\
+        ⊤, &\text{if }φ ≡ ¬ φ₁ ∨ φ₂,\ ndisj_{∨}(φ₂) ≡ ⊤\\
         ¬ φ₁ ∨ ndisj_{∨}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∨ φ₂\\
@@
       \begin{split}
-      dist_{∨}(φ) =
+      &dist_{∨} : \Prop \to \Prop\\
+      &dist_{∨}(φ) =
         \begin{cases}
@@
       \begin{split}
-      dist(φ) =
+      &dist : \Prop \to \Prop\\
+      &dist(φ) =
         \begin{cases}
@@
 
+%TODO check canonicalize can reduce a conjunction into one smaller.
+\begin{definition}[simpl]
+\label{def:simpl}
 \begin{align}
     \begin{split}
-      &\textit{simpl} : \Prop \to \Prop \to \Prop \to \Prop\\
-      &\textit{simpl}(φ₁, φ₂ ψ) =
-      \begin{cases}
-        ψ, &\text{if }φᵢ ≡ ψ,\text{ for some }i = 1, 2\\
-        ψ, &\text{if }φ₁ ≡ φ₂ ⇒ ψ\\
+      &\textit{simpl} : \Prop → \Prop → \Prop\\
+      &\textit{simpl}(φ₁, φ₂) =
+      \begin{cases}
+        ⊥,  &\text{ if }φᵢ ≡ ⊥,\\
+        γ   &\text{ if }φᵢ ≡ φⱼ ⇒ γ\\
+        γ   &\text{ if }φᵢ ≡ γ ⇒ ¬ φⱼ\\
+        γ   &\text{ if }φᵢ ≡ φⱼ ⇔ γ \\
+        γ   &\text{ if }φᵢ ≡ ¬ φⱼ ∨ γ\\
+        ⊥   &\text{ if }conjunct(φᵢ, ¬ φⱼ)\\
+        ⊥,  &\text{ if }canonicalize(φᵢ, ¬ φⱼ) ≡ ¬ φⱼ\\
+        φ₁, &\text{ otherwise.}\\
       \end{cases}
@@
 \end{align}
+For $i = 1, 2$, $i\neq j$. We assume here some commutative properties for brevity.
+\end{definition}
 

### 2017-10-17 paper/sections/abstract.tex
[ paper ] minor fixies.

@@
 In this paper, we describe our approach to reconstruct and verify in
-the proof assistant for type theory \Agda, solutions obtained by
-the  automatic theorem prover \Metis to problems in classical
-propositional logic. The translation method consists of justifying
+\Agda proof assistant, solutions generated by \Metis prover to problems in classical propositional logic. The translation method consists of justifying
 step-by-step each deduction found in the prover's solution. To carry

### 2017-10-17 paper/sections/conclusions.tex
[ paper ] minor fixies.

@@
 only a syntactic treatment of the logic without considering the
-semantics. This aspect represent a difficulty but also an opportunity
-to extend this work towards the support for first-order logic.
-As a first future work, we see the support of \Metis propositional
-fragment with equality.
+semantics. This aspect represents a difficulty but also an opportunity
+to extend this work towards the support of first-order logic.
+As a future work, we propose extend the proof-reconstruction to
+support the  proposition fragment with equality.
 
@@
 improvements, we left this for future work, particularly, a better
-implementation of \simplify rule.
+coverage of the \simplify rule.
 Some of the improvements are related with computational efficiency.
@@
 \url{https://github.com/gilith/metis}}. Fortunately, all these bugs
-were fixed quickly for release 20170810 by Joe Hurd.
+were fixed quickly by Joe Hurd in 20170810 release .
 

### 2017-10-17 paper/sections/introduction.tex
[ paper ] minor fixies.

@@
 \name{CVC4}~\cite{Barrett2011}, \name{SPASS}, and
-\name{Waldmeister}~\cite{hillenbrand1997}) and a little bit less replied with a proof
-in a file format like \TSTP~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006} (e.g.,
-\name{E}, \Metis, \name{Vampire}, and \name{Z3}),
+\name{Waldmeister}~\cite{hillenbrand1997}) and a little bit less replied with
+a proof
+in a file format like \TSTP~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}
+(e.g., \name{E}, \Metis, \name{Vampire}, and \name{Z3}),
 \len{LFSC}~\cite{Stump2008}, or the \len{SMT-LIB}~\cite{Bohme2011} format.
@@
 \ATPs~\cite{Keller2013,Bohme2011,Fleury2014} and
-\cite{Kanso2012}). We mention some of these tools in the related
-work, Section \ref{sec:related-work}.
+\cite{Kanso2012}).
+We mention some of these tools in Section~\ref{sec:related-work}.
 
 In this paper, we ported a subset of the \Metis' inference rules to
-\Agda, the propositional fragmented without equality.
-The formalization of these rules allowed us to justify step-by-step \Metis' \TSTP derivations by translating automatically to \Agda by a proof-reconstruction tool built for this research named \Athena.
-We structure the paper as follows.
-We briefly mention some notation and syntax of the classical propositional logic in Section~\ref{ssec:CPL}.
+\Agda, the propositional fragmented without equality. The formalization of
+these rules allowed us to justify step-by-step \Metis' \TSTP derivations by
+translating automatically to \Agda by a proof-reconstruction tool built for
+this research named \Athena.
+This paper has been organized in the following way.
+The first section of the paper, Section~\ref{ssec:CPL}, will mention some
+notation and syntax of the classical propositional logic.
 In Section~\ref{ssec:metis-language-and-proofs}, we introduce the
@@
 approach to reconstruct proofs deliver by \Metis in type theory.
-We listed some conclusions and future work in
-Section~\ref{sec:conclusions}. Some related works with this paper is presented in Section~\ref{sec:related-work}.
-Finally, we provide a complete example in the appendix \textsc{A} of the proof reconstruction workflow.
+Section~\ref{sec:conclusions} summarizes the main findings and includes a
+discussion of future work.
+Some related works with this paper is presented in Section~\ref{sec:related-work}.
+Finally, we provide a small example in the appendix \textsc{A} of the
+proof-reconstruction workflow.
 

### 2017-10-17 paper/sections/metis-language-and-proofs.tex
[ paper ] minor fixies.

@@
 rules. There are already some tools that perform proof-reconstruction
-with \Metis, some of these systems are the following.
+with \Metis. Some of these systems are the following.
 
@@
 \name{Z3} (more details in Ref.~\cite{paulson2007source}).
-In \cite{Farber2015}, \Metis was used to provide a tactic for
-\name{HOL Light}; this challenges others like \emph{MESON}
-or the \emph{leanCoP} tactic that reconstructs proofs
-delivered by \name{leanCoP}~\cite{Farber2016}.
+\citeauthor{Farber2015} in \cite{Farber2015} present tactic based on \Metis for
+\name{HOL Light} capable to challenge others tactics like \emph{MESON}
+or the \emph{leanCoP} tactic~\cite{Farber2016}.
 
@@
 in \TPTP syntax. We begin by declaring the $p$ axiom using the \verb!axiom!
-keyword. Later, we include the expected conclusion using the \verb!conjecture! keyword.
+keyword. Later, we include the expected conclusion using the \verb!conjecture!
+keyword.
 
@@
 
-Since the scope of the problems treated in this research is \CPL, from the list of \Metis inference rules in Fig.~\ref{fig:metis-inferences}, we found that only three rules apply: \emph{axiom}, \emph{assume} and \emph{resolve} rule.
-Nonetheless, \TSTP derivations replied by \Metis use other rules. They are \canonicalize, \clausify, \conjunct, \simplify, \negate, and
-\strip.
+Since the scope of the problems treated in this research is \CPL, from the
+list of \Metis inference rules in Fig.~\ref{fig:metis-inferences}, we found
+that only three rules apply: \emph{axiom}, \emph{assume} and \emph{resolve}
+rule.
+Nonetheless, \TSTP derivations replied by \Metis use other rules. They are
+\canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
 
 \Metis looks for a refutation to prove \verb!fof! problems.
-A \verb!fof!
-problem contains the conjecture also named the \emph{goal} in the problem.
-This goal is stripped into subgoals by using the \strip rule.
-The subgoals are the conjuncts in a general conjunction that is equivalent to the aforementioned goal.
-Therefore, to prove the goal, \Metis proves independently each subgoal since they tend to be less complex or even smaller propositions.
-At the end, the conjunction of all subgoal proofs must prove the goal.
-Nevertheless, this last reasoning is not explicit neither in the \TSTP derivations nor in the \Metis' documentation.
-Since \Metis replies refutation proofs, to prove each subgoal, in the \TSTP derivation, the inference rule \negate introduces the negation of such subgoals.
-The \negate rule is a specification of the \emph{assume} rule.
+A \verb!fof! problem contains the conjecture also named the \emph{goal} in the
+problem. This goal is stripped into subgoals by using the \strip rule. The
+subgoals are the conjuncts in a general conjunction that is equivalent to the
+aforementioned goal.
+Therefore, to prove the goal, \Metis proves independently each subgoal since
+they tend to be less complex or even smaller propositions. At the end, the
+conjunction of all subgoal proofs must prove the goal. Nevertheless, this last
+reasoning is not explicit neither in the \TSTP derivations nor in the
+documentation available about \Metis.
+Since \Metis replies refutation proofs, to prove each subgoal, in the \TSTP
+derivation, the inference rule \negate introduces the negation of such
+subgoals. The \negate rule is a specification of the \emph{assume} rule.
 
-Finally, \emph{axiom} rule appears in \TSTP derivation by one of the following rules to in the problem a \verb!fof!
-axiom: \canonicalize, \clausify, \conjunct, or \simplify.
-Then, the last rule remains is \emph{resolve}, it appears by the
-binary rule, \resolve, the version in \Metis of the resolution
+Finally, \emph{axiom} rule appears in \TSTP derivation by one of the following
+rules to in the problem a \verb!fof! axiom: \canonicalize, \clausify,
+\conjunct, or \simplify. Then, the last rule remains is \emph{resolve}, it
+appears by the binary rule, \resolve, the version in \Metis of the resolution
 theorem. For a more detailed description of this rules see the Section~\ref{sec:proof-reconstruction}.
@@
 
-A proof-object delivered in a \Metis' proof encodes a natural
+A proof-object delivered by \Metis encodes a natural
 deduction proof. The deduction system uses six inference rules

### 2017-10-17 paper/sections/preliminaries.tex
[ paper ] reviewed to resolve section.
[ paper ] minor fixies.

@@
 define it as a relation between a set of propositions premises $Γ$,
-and $φ$ as the sequent's conclusion.
+and $φ$ as the conclusion of the sequent.
 The symbol $⊢$ is called turnstile.
@@
 Then, a theorem, $Γ ⊢ φ$ , means that there is a derivation with
-conclusion $φ$ and with all (uncancelled) hypotheses in $Γ$.
+conclusion $φ$ and with all (uncanceled) hypotheses in $Γ$.
 
@@
 \AxiomC{}
-\RightLabel{assume $φ$}
+\RightLabel{assume}
 \UnaryInfC{$Γ , φ ⊢ φ$}
@@
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{weaken $ψ$}
+\RightLabel{weaken}
 \UnaryInfC{$Γ , ψ ⊢ φ$}
@@
 \AxiomC{$Γ ⊢ ⊥$}
-\RightLabel{$⊥$-elim $φ$}
+\RightLabel{$⊥$-elim}
 \UnaryInfC{$Γ ⊢ φ$}
@@
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{$\vee$-intro$_1$ $ψ$}
+\RightLabel{$\vee$-intro$_1$}
 \UnaryInfC{$Γ ⊢ φ \vee ψ$}
@@
 \AxiomC{$Γ ⊢ ψ$}
-\RightLabel{$\vee$-intro$_2$ $φ$}
+\RightLabel{$\vee$-intro$_2$}
 \UnaryInfC{$Γ ⊢ φ \vee ψ$}

### 2017-10-17 paper/sections/proof-reconstruction.tex
[ paper ] minor fixies.

@@
 automatic theorem prover, is \Metis; the target system is a proof
-assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types is valid.
+assistant, \Agda. We choose \Agda, but another proof assistant with the same
+support of type theory and inductive types is valid.
 %  (see a description of \Agda for its main features in
@@
 a \TPTP file that encodes a problem in \CPL. We use this file as the
-input of the \Metis prover and if the problem is a theorem, \Metis can reply with a derivation in \TSTP format of the proof.
-
-With the \TSTP  derivation from the Step~2, we process the derivation with the \Athena translator tool~\cite{Athena}.
+input of the \Metis prover and if the problem is a theorem, \Metis can reply
+with a derivation in \TSTP format of the proof.
+
+With the \TSTP  derivation from the Step~2, we process the derivation with the
+\Athena translator tool~\cite{Athena}.
 \Athena parses the \TSTP format, analyzes the
@@
 
-As a result of using \Athena, we get an \Agda file, the proof-term. To generate this file, \Athena has used names of functions and theorems from \Agda libraries:
+As a result of using \Athena, we get an \Agda file, the proof-term. To
+generate this file, \Athena has used names of functions and theorems from
+\Agda libraries:
 \texttt{agda-prop}~\cite{AgdaProp}, and \texttt{agda-metis}~\cite{AgdaMetis}.
@@
 
-In the rest of this section, we provide a formal description using
-type theory to build definitions and theorems for functions
-necessary to emulate \Metis' inference rules. For this description,
-we will write the type judgments with ``$a : A$'' to denote that $a$
+In the remainder part of this section, a formal description using
+type theory is presented to build definitions and theorems of functions
+necessary to emulate \Metis' inference rules. As notation convention,
+We write the type judgments with ``$a : A$'' to denote that $a$
 has $\abbre{A}$ type. Types are written using small caps.
 We use \Prop type for propositions and the dependent type, $Γ ⊢ φ$ for
-theorems. In the latter type, $Γ$ has $\abbre{List}~\Prop$ type
-and $φ$ has type $\Prop$. $\abbre{List}$ is the usual inductive type
-for lists. Finally, we will denote by $φ ≡ ψ$, the syntactic
-equivalence between propositions.
+theorems where $Γ$ has $\abbre{List}~\Prop$ type, and $φ$ has type $\Prop$.
+$\abbre{List}$ type is the usual inductive type for lists. For syntactical
+equivalence, we write $φ ≡ ψ$ for $φ : \Prop$ and $ψ : \Prop$.
 
@@
 directly in type theory since it is not a guarantee they terminate.
-For that reason, we present in this section, a technique to avoid
-such termination problems by modifying the recursive functions
-to be \emph{structural recursive}.
+For that reason, we follow the technique described
+in~\cite{Bertot2004} to avoid termination problems by modifying the
+recursive
+functions to be \emph{structural recursive}.
 % (see \cite{Coquand1992,Abel2002,Bove2005} for more details).
 
-We adopt the notion of \emph{structurally smaller} from
+This paper adopts the notion of \emph{structurally smaller} from
 \citeauthor{Abel2002}~\cite{Abel2002} to say, a recursive function is
@@
 \begin{align}
-\begin{split}
   \label{eq:unshunt-definition}
+  \begin{split}
+    &unshunt_{0} : \Prop → \Prop\\
     &unshunt_{0}(φ) =\\
@@
     unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
-  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+      & \text{ if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
     unshunt_{0}(φ₁ ⇒ φ₂) ∧ unshunt_{0}(φ₁ ⇒ φ₃),
-  & \text{if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
-φ, &\text{otherwise.}
+      & \text{ if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
+    φ, &\text{ otherwise.}
     \end{cases}
@@
 Thus, we define the function
-$unshunt_{1} : \Prop \to \Nat \to \Prop$
-by structural recursion in its second argument in
+$unshunt_{1}$ by structural recursion in its second argument in
 Eq.~(\ref{eq:unshunt-structured}).
@@
   \begin{split}
+    &unshunt_{1} : \Prop → \Nat \to \Prop\\
     &unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\%\hspace{10cm}\\
@@
     unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
-  &\text{if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\[2mm]
+      &\text{ if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\[2mm]
     unshunt_{1}(φ₁ ⇒ φ₂, n)\\
     ∧\ unshunt_{1}(φ₁ ⇒ φ₃, n),
-   &\text{if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
+       &\text{ if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
   \end{cases}
@@
 
-\begin{equation*}
-\label{eq:rank-definition}
-rank(φ)=
+\begin{align*}
+  \begin{split}
+  % \label{eq:rank-definition}
+    &rank : \Prop → \Nat\\
+    &rank(φ) =
     \begin{cases}
     0, &\text{for atomic }φ \\
-rank(φ₁) + c_{¬},  &\text{if } φ ≡ \neg φ₁ \\
+    rank(φ₁) + c_{¬},  &\text{ if } φ ≡ \neg φ₁ \\
     \max{(rank(φ₁),rank(φ₂))} + c_{\square},
-  &\text{if } φ ≡ φ₁\,\square\, φ₂.
-\end{cases}
-\end{equation*}
+      &\text{ if } φ ≡ φ₁\,\square\, φ₂.
+    \end{cases}
+  \end{split}
+\end{align*}
 
@@
 \begin{align}
-  \begin{split}
   \label{eq:unshunt-rank-definition}
+  \begin{split}
+      &unshunt_{cm} : \Prop → \Nat\\
       &unshunt_{cm}(φ) =\\
@@
         \begin{cases}
-        unshunt_{cm}(φ₃) + 2, &\text{if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+        unshunt_{cm}(φ₃) + 2, &\text{ if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
         \max(unshunt_{cm}(φ₂),unshunt_{cm}(φ₃)) + 1,
-          &\text{if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
-        0, &\text{otherwise.}
+          &\text{ if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
+        0, &\text{ otherwise.}
         \end{cases}
@@
 the following pattern to present the formalization for
-the \Metis inference rules.
+the \Metis inference rules. The function name written in bold print is a \Metis
+inference rule in \TSTP derivation. The same function name written
+in italics refers to the emulated version presents in this section.
+Each emulated version states a theorem to prove the soundness of the rule.
+This theorem is named by using the prefix \emph{thm}
+and the name of the rule.
 
 \begin{itemize}
-\item \texttt{rule} is a \Metis inference rule
+\item \texttt{rule} is a $n$-ary \Metis inference rule
 \item $rule$ is the emulated version function  for
@@
   \begin{split}
-&rule : \Prop → \Prop → \Prop\\
-&rule(φ, ψ) =
-  \begin{cases}
-  ψ, &\text{if }rule\text{ built }ψ\text{ by applying valid transformations to }φ\\
-  φ, &\text{otherwise.}
+    &rule : \Prop → \Prop → \cdots → \Prop\\
+    &rule(φ₁,\cdots, φₙ, ψ) =
+      \begin{cases}
+      ψ, &\text{ if }rule\text{ built }ψ\text{ by applying valid}\\
+         &\text{ transformations or other rules to }φ\\
+      φ, &\text{ otherwise.}
       \end{cases}
@@
 \begin{itemize}
-  \item $φ$ is the \emph{source} formula.
-  \item $ψ$ is the \emph{target} formula.
+  \item $φᵢ$ are \emph{source} formulas from previous deducted derivations.
+  \item $ψ$ is the \emph{target} formula. The excepted result of \texttt{rule}.
 \end{itemize}
-\item thm-rule is the theorem, $Γ ⊢ rule(φ, ψ)$, that proves
-the soundness of the $rule$ function.
 \end{itemize}
@@
 
-To prove the correctness of the process mentioned above, we state
-the Theorem~\ref{thm:thm-strip}. But first, let us prove some
-lemmas for $unshunt$ function presented in Def.~(\ref{def:unshunt}),
-and for $split$ function presented in Eq.~(\ref{eq:split-definition}).
+To prove the correctness of the process mentioned above, first,
+we need to establish some lemmas before introduce our main goal of this part,
+Theorem~\ref{thm:thm-strip}.
 
@@
 
-Let us now consider the $split$ function presented in
-Eq.~(\ref{eq:split-definition}) that yields the conjunction of subgoals that implies the goal of the problem in the \Metis \TSTP derivations.
+Let us now define the $split$ function that yields the conjunction of subgoals that implies the goal of the problem in the \Metis \TSTP derivations.
 
@@
 \label{def:split}
-
-\begin{equation}
-\label{eq:split-definition}
+  \begin{equation*}
     \begin{split}
@@
       \begin{cases}
-unshunt(\mysplit(φ₁)) &\text{if }φ ≡ φ₁ ∧ φ₂\\
+      unshunt(\mysplit(φ₁)) &\text{ if }φ ≡ φ₁ ∧ φ₂\\
       ∧\ unshunt(φ₁ ⇒ \mysplit(φ₂)), &\\[2.5mm]
       unshunt(¬ φ₁ ⇒ \mysplit(φ₂)),
-  & \text{if }φ ≡ φ₁ ∨ φ₂\\[2.5mm]
+        & \text{ if }φ ≡ φ₁ ∨ φ₂\\[2.5mm]
       unshunt(φ₁ ⇒ \mysplit(φ₂)),
-  & \text{if }φ ≡ φ₁ ⇒ φ₂\\[2.5mm]
+        & \text{ if }φ ≡ φ₁ ⇒ φ₂\\[2.5mm]
       unshunt(φ₁ ⇒ \mysplit(φ₂))
-  & \text{if }φ ≡ φ₁ ⇔ φ₂\\
+        & \text{ if }φ ≡ φ₁ ⇔ φ₂\\
       ∧\ unshunt(φ₂ ⇒ \mysplit(φ₁)),
@@
       unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
-  & \text{if }φ ≡ ¬ (φ₁ ∧ φ₂)\\[2.5mm]
+        & \text{ if }φ ≡ ¬ (φ₁ ∧ φ₂)\\[2.5mm]
       unshunt(\mysplit(¬ φ₁))
-  & \text{if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
+        & \text{ if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
       ∧\ unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂)),
@@
       unshunt(\mysplit(φ₁))
-  & \text{if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
+        & \text{ if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
       ∧\ unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
@@
       unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
-  & \text{if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
+        & \text{ if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
       ∧\ unshunt(¬ φ₂ ⇒ \mysplit(φ₁)),
@@
       unshunt(\mysplit(φ₁)),
-  & \text{if }φ ≡ ¬ ¬ φ₁\\
+        & \text{ if }φ ≡ ¬ ¬ φ₁\\
       ⊤,
-  & \text{if }φ ≡ ¬ ⊥\\
+        & \text{ if }φ ≡ ¬ ⊥\\
       ⊥,
-  & \text{if }φ ≡ ¬ ⊤.
-\end{cases}
-\end{split}
-\end{equation}
+        & \text{ if }φ ≡ ¬ ⊤.
+      \end{cases}
+    \end{split}
+  \end{equation*}
 \end{definition}
@@
 a structural recursion. Therefore, we have reformulated the equation
-above to solve such a issue following the technique
+above to solve such an issue following the technique
 described in Section~\ref{ssec:structural-recursion}. We refer to $split$
@@
 \begin{sketchproof}
-We now proceed by induction on the structure of the
-formula $φ$ by following the cases defined in
-Eq.~(\ref{eq:split-definition}).
+The proof is by induction on the structure of the
+formula $φ$ by following the cases in Def.~\ref{def:split}.
 We present some cases but for a complete proof, we refer the reader to~\cite{AgdaMetis}.
@@
 \item $(φ ≡ ¬ ¬ φ₁)$
-%Using the double negation equivalence, we conclude.
 \begin{equation*}
@@
 
+We can now formulate our main result of this part that
+justifies the stripping strategy of \Metis to prove goals.
+
 \begin{theorem}[thm-strip]
 \label{thm:thm-strip}
- If $s_i$ are the subgoals of the goal $φ$, and
- $\{ Γ ⊢ s_i \}_{i}$, then $Γ ⊢ φ$.
+ If $s_i$ are the subgoals of the goal $φ$ for $i=1,\cdots,n$, and
+ $\{ Γ ⊢ s_i \}_{i =1}^n$, then $Γ ⊢ φ$.
 \end{theorem}
@@
   \begin{bprooftree}
-  \AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i}$}
+  \AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i=1}^n$}
   \RightLabel{∧-intro}
-  \UnaryInfC{$Γ ⊢ \bigwedge_i s_i$}
-
-  \AxiomC{$\mysplit(φ) ≡ \bigwedge_i s_i $}
+  \UnaryInfC{$Γ ⊢ \bigwedge_{i=1}^n s_i$}
+
+  \AxiomC{$\mysplit(φ) ≡ \bigwedge_{i=1}^n s_i $}
   \RightLabel{subst}
@@
 Then, to emulate this rule, we just introduce the negation
-of the subgoal by using the assume rule from the inferences in
+of the subgoal by using $assume$ rule from the inferences in
 Fig.~\ref{fig:CPL-inference-rules}.
@@
 % -------------------------------------------------------------------
+
 \subsubsection{Splitting a Conjunct.}
@@
     \begin{cases}
-        ψ, &\text{if }φ ≡ ψ\\
-        ψ, &\text{if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ conjunct(φ₁, ψ)\\
-        ψ, &\text{if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ conjunct(φ₂, ψ)\\
-        φ, &\text{otherwise.}
+        ψ, &\text{ if }φ ≡ ψ\\
+        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ conjunct(φ₁, ψ)\\
+        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ conjunct(φ₂, ψ)\\
+        φ, &\text{ otherwise.}
       \end{cases}
@@
 prover reasoning steps. Since we left out semantics to treat only the
-syntax aspects of the propositions, our approach shows that equivalence
-by converting propositions to their conjunctive normal forms and showing
-equivalence by reordering the conjunctions and the inner disjunctions.
+syntax aspects of the propositions, our approach shows equivalence
+by converting propositions to their conjunctive normal forms.
+But also, reordering the conjunctions and the inner disjunctions into the
+formulas to match them.
 In this section, we provide some theorems to perform such reordering tasks,
@@
 \begin{itemize}
-  \item Reorder the disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots φₙ$ to match with
+  \item Reorder a disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots φₙ$ to match with
 $ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$, when for all $i = 1, \cdots, n$, exists at
@@
 
-First, we define the $rdisj$ function in Eq.~(\ref{eq:rdisj-def}) to convert
+First, we define the $rdisj$ function to convert
 a disjunction in its right-associative form.
+The $rconj$ function converts conjunction to its right-associative form is not
+presented here, but is defined in a similar way (see its implementation
+in~\cite{AgdaMetis}).
 
@@
 \label{def:rdisj}
-\begin{align}
+  \begin{align*}
     \begin{split}
@@
       \begin{cases}
-    rdisj(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
-    φ₁ ∨ rdisj(φ₂),         & \text{if } φ ≡ φ₁ ∨ φ₂\\
-    φ,                      & \text{otherwise.}
-    \end{cases}
-  \end{split}
-\end{align}
+      rdisj(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{ if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
+      φ₁ ∨ rdisj(φ₂),         & \text{ if } φ ≡ φ₁ ∨ φ₂\\
+      φ,                      & \text{ otherwise.}
+      \end{cases}
+    \end{split}
+  \end{align*}
 \end{definition}
@@
 \end{lemma}
-% Following a similar way to define $rdisj$, we define the $rconj$ function,
-% to convert a conjunction into its right-associative form.
 
@@
   \begin{cases}
-  ψ, &\text{if } φ ≡ ψ\\
-  ψ, &\text{if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
-  φ, &\text{otherwise.}
+  ψ, &\text{ if } φ ≡ ψ\\
+  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{, } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
+  φ, &\text{ otherwise.}
   \end{cases}
@@
   \begin{cases}
-    φ₁,  &\text{if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ factor(φ₂)\\
-    φ,   &\text{otherwise.}
+    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{, } φ₁ ≡ factor(φ₂)\\
+    φ,   &\text{ otherwise.}
   \end{cases}
@@
     \begin{cases}
-      factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ)),  &\text{if }φ≡ φ₁ ∨ φ₂\\
-      build_{∨}(φ, ψ),  & \text{otherwise.}
+      factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ)),  &\text{ if }φ≡ φ₁ ∨ φ₂\\
+      build_{∨}(φ, ψ),  & \text{ otherwise.}
     \end{cases}
@@
         \begin{cases}
-          φ, &\text{if }φ ≡ ψ\\
-          ψ₁ ∧ ψ₂, &\text{if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁\\
+          φ, &\text{ if }φ ≡ ψ\\
+          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁\\
                   &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂\\
-          φ,       &\text{if } ψ ≡ ψ₁ ∧ ψ₂\\
-          conjunct(φ, ψ), &\text{otherwise.}
+          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
+          conjunct(φ, ψ), &\text{ otherwise.}
         \end{cases}
@@
     \begin{cases}
-      ψ, &\text{if }φ ≡ ψ\\
-      ψ, &\text{if }reorder_{∨}(φ, ψ) ≡ ψ\\
-      ψ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂,\ conjunct_{∨}(φ, ψ₁) ≡ ψ₁,\\
+      ψ, &\text{ if }φ ≡ ψ\\
+      ψ, &\text{ if }reorder_{∨}(φ, ψ) ≡ ψ\\
+      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ conjunct_{∨}(φ, ψ₁) ≡ ψ₁,\\
         &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂\\
-      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂,\ conjunct_{∨}(φ₁, ψ) ≡ ψ\\
-      ψ, &\text{if }φ ≡ φ₁ ∧ φ₂,\ conjunct_{∨}(φ₂, ψ) ≡ ψ\\
-      φ, &\text{otherwise.}
+      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ conjunct_{∨}(φ₁, ψ) ≡ ψ\\
+      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ conjunct_{∨}(φ₂, ψ) ≡ ψ\\
+      φ, &\text{ otherwise.}
     \end{cases}
@@
         \begin{cases}
-          ψ, &\text{if } φ≡ψ\\
-          ψ, &\text{if } ψ ≡ ψ₁ ∧ ψ₂,\ reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
+          ψ, &\text{ if } φ≡ψ\\
+          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
              &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
-          φ, &\text{if }ψ ≡ ψ₁ ∧ ψ₂\\
-          conjunct_{∨}(φ, ψ) &\text{otherwise.}
+          φ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂\\
+          conjunct_{∨}(φ, ψ) &\text{ otherwise.}
         \end{cases}
@@
           φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
-          φ, &\text{otherwise.}
+          φ, &\text{ otherwise.}
         \end{cases}
@@
 One of the main purposes of the module consists of adding the axioms to the problem. Into this process, some transformation are carried out by different inference rules.
-For example, the \canonicalize rule can convert a FOF formula to their CNF form.
+For example, the \canonicalize rule can convert a first-order form formulas to their clausal normal form.
 In that process, the formula can suffers different transformations by removing redundancies (tautologies or definitions), converting the proposition to its normalized negative normal form, to its conjunctive normal form, or to a specialized normal form.
@@
       \begin{cases}
-        rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
-        φ₁ ∨ rm_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
-        φ,  &\text{otherwise.}
+        rm_{∨}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
+        φ₁ ∨ rm_{∨}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂\\
+        φ,  &\text{ otherwise.}
       \end{cases}
@@
     \begin{cases}
-      rm_{∧}(φ₂),      &\text{if }φ ≡ φ₁ ∧ φ₂, φ₁ ∈_{∧} φ₂\\
-      φ₁ ∧ rm_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
-      φ,               &\text{otherwise.}
+      rm_{∧}(φ₂),      &\text{ if }φ ≡ φ₁ ∧ φ₂, φ₁ ∈_{∧} φ₂\\
+      φ₁ ∧ rm_{∧}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
+      φ,               &\text{ otherwise.}
     \end{cases}
@@
       \begin{cases}
-        ⊤, &\text{if }φ ≡ ¬ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
-        ⊤, &\text{if }φ ≡ ¬ φ₁ ∨ φ₂,\ ndisj_{∨}(φ₂) ≡ ⊤\\
-        ¬ φ₁ ∨ ndisj_{∨}(φ₂), &\text{if }φ ≡ ¬ φ₁ ∨ φ₂\\
-        ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ ¬φ₁ ∈_{∨} φ₂ \\
-        ⊤, &\text{if }φ ≡ φ₁ ∨ φ₂,\ ndisj_{∨}(φ₂) ≡ ⊤\\
-        φ₁ ∨ ndisj_{∨}(φ₂), &\text{if }φ ≡ φ₁ ∨ φ₂\\
-        φ, &\text{otherwise.}
+        ⊤, &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
+        ⊤, &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂,\ ndisj_{∨}(φ₂) ≡ ⊤\\
+        ¬ φ₁ ∨ ndisj_{∨}(φ₂), &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂\\
+        ⊤, &\text{ if }φ ≡ φ₁ ∨ φ₂,\ ¬φ₁ ∈_{∨} φ₂ \\
+        ⊤, &\text{ if }φ ≡ φ₁ ∨ φ₂,\ ndisj_{∨}(φ₂) ≡ ⊤\\
+        φ₁ ∨ ndisj_{∨}(φ₂),  &\text{ if }φ ≡ φ₁ ∨ φ₂\\
+        φ, &\text{ otherwise.}
       \end{cases}
@@
         ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ndisj_{∧}(φ₂) ≡ ⊥\\
-        φ₁ ∧ ndisj_{∧}(φ₂), &\text{if }φ ≡ φ₁ ∧ φ₂\\
-        φ, &\text{otherwise.}
+        φ₁ ∧ ndisj_{∧}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
+        φ, &\text{ otherwise.}
       \end{cases}
@@
         \begin{cases}
-        φⱼ, &\text{if } φ ≡ φ₁ ∧ φ₂,\ φᵢ ≡ ⊤,\text{ for } i,j = 1,2, i≠j\\
-        ⊥, &\text{if } φ ≡ φ₁ ∧ φ₂,\ φᵢ ≡ ⊥,\text{ for } i,j = 1,2\\
-       rm_∧(ndisj_∧(φ)), &\text{if } φ ≡ φ₁ ∧ φ₂\\
-       φ, &\text{otherwise.}
+          φⱼ, &\text{ if } φ ≡ φ₁ ∧ φ₂,\ φᵢ ≡ ⊤,\text{ for } i,j = 1,2, i≠j\\
+          ⊥,  &\text{ if } φ ≡ φ₁ ∧ φ₂,\ φᵢ ≡ ⊥,\text{ for } i,j = 1,2\\
+          rm_∧(ndisj_∧(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
+          φ,                &\text{ otherwise.}
         \end{cases}
@@
         \begin{cases}
-        φⱼ, &\text{if } φ ≡ φ₁ ∨ φ₂,\ φᵢ ≡ ⊥,\text{ for } i,j = 1,2, i≠j\\
-        ⊤, &\text{if } φ ≡ φ₁ ∨ φ₂,\ φᵢ ≡ ⊤,\text{ for } i,j = 1,2\\
-        rm_∨(ndisj_∨(φ)), &\text{if } φ ≡ φ₁ ∧ φ₂\\
-        φ, &\text{otherwise.}
+        φⱼ, &\text{ if } φ ≡ φ₁ ∨ φ₂,\ φᵢ ≡ ⊥,\text{ for } i,j = 1,2, i≠j\\
+        ⊤, &\text{ if } φ ≡ φ₁ ∨ φ₂,\ φᵢ ≡ ⊤,\text{ for } i,j = 1,2\\
+        rm_∨(ndisj_∨(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
+        φ, &\text{ otherwise.}
         \end{cases}
@@
 \begin{remark}
-A similar treatment we do to define the $canon_{⊻} : \NProp \to \NProp$
+A similar treatment defines the $canon_{⊻} : \NProp \to \NProp$
 function that removes redundancies related with the exclusive
-disjunction connective, and to prove its soundness with the respective
-theorem thm-canon$_{⊻}$ in~\cite{AgdaMetis}.
+disjunction connective.
+% Its theorem, thm-canon$_{⊻}$ is presented in~\cite{AgdaMetis}.
 We left out this description for the brevity of this
-document and refer the interested reader to the implementation
-in~\cite{AgdaMetis}.
+document and refer the interested reader to \cite{AgdaMetis} for
+more details.
 \end{remark}
@@
 formulas to their classical negative normal form. In the reference, the
-authors avoid a termination problem with a similar function by using as a
+authors avoid a termination problem with a similar function by using as an
 extra argument, the polarity of the formula.
@@
       \begin{cases}
-      canon_{∧}(nnf₀(⊕, φ₁) ∧ nnf₀(⊕, φ₂)), &\text{if }φ ≡ φ₁ ∧ φ₂ \\
-      canon_{∨}(nnf₀(⊕, φ₁) ∨ nnf₀(⊕, φ₂)), &\text{if }φ ≡ φ₁ ∨ φ₂ \\
-      canon_{∨}(nnf₀(⊖, φ₁) ∨ nnf₀(⊕, φ₂)), &\text{if }φ ≡ φ₁ ⇒ φ₂ \\
-      canon_{⊻}(nnf₀(⊖, φ₁) ⊻ nnf₀(⊕, φ₂)), &\text{if }φ ≡ φ₁ ⇔ φ₂ \\
-      nnf₀(⊖, φ₁),                          &\text{if }φ ≡ ¬ φ₁ \\
-      φ,                                    &\text{otherwise.} \\
+      canon_{∧}(nnf₀(⊕, φ₁) ∧ nnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
+      canon_{∨}(nnf₀(⊕, φ₁) ∨ nnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
+      canon_{∨}(nnf₀(⊖, φ₁) ∨ nnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
+      canon_{⊻}(nnf₀(⊖, φ₁) ⊻ nnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ⇔ φ₂ \\
+      nnf₀(⊖, φ₁),                          &\text{ if }φ ≡ ¬ φ₁ \\
+      φ,                                    &\text{ otherwise.} \\
       \end{cases}\\
@@
       \begin{cases}
-      canon_{∨}(nnf₀(⊖, φ₁) ∨ nnf₀(⊖, φ₂)),  &\text{if }φ ≡ φ₁ ∧ φ₂ \\
-      canon_{∧}(nnf₀(⊖, φ₁) ∧ nnf₀(⊖, φ₂)),  &\text{if }φ ≡ φ₁ ∨ φ₂ \\
-      canon_{∧}(nnf₀(⊖, φ₂) ∧ nnf₀(⊖, φ₁)),  &\text{if }φ ≡ φ₁ ⇒ φ₂ \\
-      canon_{⊻}(nnf₀(⊕, φ₁) ⊻ nnf₀(⊕, φ₂)),  &\text{if }φ ≡ φ₁ ⇔ φ₂ \\
-      nnf₀(⊕, φ₁),                           &\text{if }φ ≡ ¬ φ₁ \\
-      ⊥,                                     &\text{if }φ ≡ ⊤ \\
-      ⊤,                                     &\text{if }φ ≡ ⊥ \\
-      φ,                                     &\text{otherwise.} \\
+      canon_{∨}(nnf₀(⊖, φ₁) ∨ nnf₀(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
+      canon_{∧}(nnf₀(⊖, φ₁) ∧ nnf₀(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
+      canon_{∧}(nnf₀(⊖, φ₂) ∧ nnf₀(⊖, φ₁)),  &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
+      canon_{⊻}(nnf₀(⊕, φ₁) ⊻ nnf₀(⊕, φ₂)),  &\text{ if }φ ≡ φ₁ ⇔ φ₂ \\
+      nnf₀(⊕, φ₁),                           &\text{ if }φ ≡ ¬ φ₁ \\
+      ⊥,                                     &\text{ if }φ ≡ ⊤ \\
+      ⊤,                                     &\text{ if }φ ≡ ⊥ \\
+      φ,                                     &\text{ otherwise.} \\
       \end{cases}
@@
       \begin{cases}
-          dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃),
-            &\text{if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
-          dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃),
-            &\text{if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
-          φ, &\text{otherwise.}
+        dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃), &\text{ if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
+        dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃), &\text{ if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
+        φ,                                     &\text{ otherwise.}
       \end{cases}
@@
           dist(φ₁) ∧ dist(φ₂),
-            &\text{if }φ ≡ φ₁ ∧ φ₂\\
+            &\text{ if }φ ≡ φ₁ ∧ φ₂\\
           dist_{∨}(dist(φ₁) ∨ dist(φ₂)),
-            &\text{if }φ ≡ φ₁ ∨ φ₂\\
-          φ, &\text{otherwise.}
+            &\text{ if }φ ≡ φ₁ ∨ φ₂\\
+          φ, &\text{ otherwise.}
         \end{cases}
@@
         % ⊤, &\text{ if }φ ≡ ⊤\\
-        φ, &\text{otherwise.}\\
+        φ, &\text{ otherwise.}\\
       \end{cases}
@@
 Since all transformations performed above come from equivalences
-in classical propositional logic, we can also states the following theorem convenient for the next section.
+in classical propositional logic, we can also states the following theorem
+convenient for the next section.
 
@@
 mainly normalization of the proposition input by using theorems
-described in the section above. This rule  can convert a FOF formula in
-clausal form to a CNF clause. \Metis can introduce axioms, and definitions
-by using this rule. Since the nature of this rule consists of dealing with
-CNF clauses, our strategy to justify its reasoning mainly consists of
-testing for equality with normalized negative form of the formula, or a
-reordering of the conjunctive normal form of the source formula to match
+described in the section above. Metis can introduce axioms, and definitions
+by using it. This rule can convert a \texttt{fof} %TODO
+formula in clausal form into a CNF clause. Since the nature of this rule
+consists of dealing with CNF clauses, to justify its reasoning, our strategy
+mainly consists of checking the equality of normalized negative form between
+the source and the target formula. If it fails, we try to reorder the
+conjunctive normal form of the source formula to match
 the conjunctive normal form of the target formula.
@@
       \begin{cases}
-        ψ, &\text{if }ψ ≡ φ\\
-        ψ, &\text{if }ψ ≡ form(nnf(φ))\\
-        ψ, &\text{if }cnf(ψ) ≡ reorder_{∧∨}(cnf(φ), cnf(ψ))\\
-        φ, &\text{otherwise.}\\
+        ψ, &\text{ if }ψ ≡ φ\\
+        ψ, &\text{ if }ψ ≡ form(nnf(φ))\\
+        ψ, &\text{ if }cnf(ψ) ≡ reorder_{∧∨}(cnf(φ), cnf(ψ))\\
+        φ, &\text{ otherwise.}\\
       \end{cases}
@@
         ψ, &\text{ if }φ≡ψ\\
-        reorder_{∧∨}(cnf(φ), ψ), &\text{otherwise.}
+        reorder_{∧∨}(cnf(φ), ψ), &\text{ otherwise.}
       \end{cases}
@@
 definitions and tautologies. This rule
-transverses a list of inner derivations by applying different theorems
+transverses a list of previous derivations by applying different theorems
 (e.g., \emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
-syllogism}) to get a contradiction or just simplify the formulas.
-To emulate this rule, we have included theorems
-from \canonicalize rule Section~\ref{sssec:canonicalize} and
-\resolve rule Section~\ref{sssec:resolve}.
+syllogism}) to get a contradiction in the first place, or a smaller
+convenient formula
+
+% To emulate this rule, we use theorems from Section~\ref{sssec:canonicalize},
+% Section~\ref{sssec:conjunct}.
+The following \TSTP excerpt is an example of the \simplify rule.
+
+% \begin{figure}
+\begin{verbatim}
+fof(normalize_0_1, plain, (g | (~ a & k)),
+    inference(conjunct, [], [normalize_0_0])).
+fof(normalize_0_2, plain, (~ g | q),
+    inference(conjunct, [], [normalize_0_0])).
+fof(normalize_0_3, plain, (~ q),
+  inference(conjunct, [], [normalize_0_0])).
+fof(normalize_0_4, plain, (~ g),
+    inference(simplify, [], [normalize_0_2, normalize_0_3])).
+fof(normalize_0_5, plain, (~ k),
+inference(conjunct, [], [normalize_0_0])).
+fof(normalize_0_6, plain, ($false),
+    inference(simplify, [],
+              [normalize_0_1, normalize_0_4, normalize_0_5])).
+\end{verbatim}
+% \caption{Example of \simplify rule in a \TSTP derivation of \Metis.}
+% \end{figure}
+
+%TODO check canonicalize can reduce a conjunction into one smaller.
+\begin{definition}[simplify]
+\label{def:simplify}
+For $i,j = 1, 2$, $i\neq j$ and $γ : \Prop$,
+\begin{align}
+    \begin{split}
+      &\textit{simplify} : \Prop → \Prop → \Prop → \Prop\\
+      &\textit{simplify}(φ₁, φ₂,ψ) =\\
+      &\hspace{4mm}
+      \begin{cases}
+        ψ,          &\text{ if }φᵢ ≡ ψ,\\
+        ⊥,          &\text{ if }φᵢ ≡ ⊥,\\
+        φⱼ,         &\text{ if }φᵢ ≡ ⊤,\\
+        γ,          &\text{ if }φᵢ ≡ φⱼ ⇒ γ\\
+        γ,          &\text{ if }φᵢ ≡ γ ⇒ nnf(¬ φⱼ)\\
+        γ,          &\text{ if }φᵢ ≡ φⱼ ⇔ γ \\
+        nnf(¬ γ),   &\text{ if }φᵢ ≡ nnf(¬ φⱼ) ⇔ γ \\
+        γ,          &\text{ if }φᵢ ≡ nnf(¬ φⱼ) ∨ γ\\
+        ⊥,          &\text{ if } nnf(¬ φⱼ) ≡ conjunct(φᵢ, nnf(¬ φⱼ))\\
+      % φ          &\text{ if }conjunct(nnf(¬ φᵢ), φⱼ) ≡  φⱼ\\
+        ⊥,          &\text{ if } ¬ φⱼ ≡ canonicalize(φᵢ, ¬ φⱼ) \\
+        φ₁,         &\text{ otherwise.}\\
+      \end{cases}%\hspace{10cm}
+    \end{split}
+\end{align}
+\end{definition}
 
@@
 Besides the fact, $\List\ \Prop \to \Prop$ is the type that coincides
-with the reading of a \TSTP derivation, we choose a different option.
-In the translation from \TSTP to \Agda, we build a conjunction
-from the list of derivations by introducing binary conjunction
-with $∧$-intro rule. That avoids us to define a new sequent type
-to support \List \Prop type in the conclusion side.
+with the \simplify rule in \TSTP derivations, we choose a different option.
+In the translation from \TSTP to \Agda, we take the list of derivations
+and use a classical left folding ($foldl$) with $simplify$ and the list with
+$φ₁, φ₂, \cdots, φₙ$. That avoids us to define a new sequent type to
+support \List \Prop type in the conclusion side.
 \end{remark}
-
-\begin{figure}
-\begin{verbatim}
-fof(normalize_1_0, plain, (~ p & ~ r & q),
-    inference(canonicalize, [], [negate_1_0])).
-fof(normalize_1_1, plain, ((p | q) & (p | r)),
-    inference(canonicalize, [], [a1])).
-fof(normalize_1_2, plain, (p | r),
-    inference(conjunct, [], [normalize_1_1])).
-fof(normalize_1_3, plain, ($false),
-    inference(simplify, [], [normalize_1_0, normalize_1_2])).
-\end{verbatim}
-\caption{Example of \simplify rule in a \TSTP derivation of \Metis.}
-\end{figure}
-
-%TODO check canonicalize can reduce a conjunction into one smaller.
-\begin{definition}[simpl]
-\label{def:simpl}
-\begin{align}
-    \begin{split}
-      &\textit{simpl} : \Prop → \Prop → \Prop\\
-      &\textit{simpl}(φ₁, φ₂) =
-      \begin{cases}
-        ⊥,  &\text{ if }φᵢ ≡ ⊥,\\
-        γ   &\text{ if }φᵢ ≡ φⱼ ⇒ γ\\
-        γ   &\text{ if }φᵢ ≡ γ ⇒ ¬ φⱼ\\
-        γ   &\text{ if }φᵢ ≡ φⱼ ⇔ γ \\
-        γ   &\text{ if }φᵢ ≡ ¬ φⱼ ∨ γ\\
-        ⊥   &\text{ if }conjunct(φᵢ, ¬ φⱼ)\\
-        ⊥,  &\text{ if }canonicalize(φᵢ, ¬ φⱼ) ≡ ¬ φⱼ\\
-        φ₁, &\text{ otherwise.}\\
-      \end{cases}
-    \end{split}
-\end{align}
-For $i = 1, 2$, $i\neq j$. We assume here some commutative properties for brevity.
-\end{definition}
 
@@
   \label{thm:thm-simplify}
-$\{ Γ ⊢ φᵢ \}$ for $i = 1, \cdots, n$ then
-$Γ ⊢ simplify (\bigwedge_{i=1}^n φ)$.
+For $i=1,2, \cdots, n$, $Γ ⊢ φᵢ$ and $ψ : \Prop$ then
+if $n > 2$, $Γ ⊢ simplify(γ_{n-2}, φ_{n}, ψ)$ where $γ_{i} = simplify(φ_{i}, φ_{i+1}, ψ)$
+else $Γ ⊢ simplify(φ₁, φ₂, ψ)$.
 \end{theorem}
+
+% \begin{sketchproof}
+% If $Γ ⊢ φᵢ$ for $i=1, \cdots, n$, we prove this theorem by induction on $n$.
+% Let us show one case.
+% \begin{itemize}
+%   \item If $n ==2$ and $(canonicalize(φ₁, ¬ φ₂) ≡ ¬ φ₂)$, we need to prove
+%   $Γ ⊢ simplify(φ₁, φ₂, ψ)$.
+% \begin{equation*}
+%   \begin{bprooftree}
+%     \AxiomC{$Γ ⊢ φ₁$}
+%     \RightLabel{thm-canonicalize}
+%     \UnaryInfC{$Γ ⊢ canonicalize(φ₁, ¬φ₂)$}
+%     \AxiomC{$¬ φ₂ ≡ canonicalize(φ₁, ¬ φ₂)$}
+%     \RightLabel{subst}
+%     \BinaryInfC{$Γ ⊢ ¬ φ₂ $}
+%   \end{bprooftree}
+%   \begin{bprooftree}
+%   \AxiomC{$Γ ⊢ ¬ φ₂ $}
+%   \AxiomC{$Γ ⊢ φ₂$}
+%   \RightLabel{¬-elim}
+%   \BinaryInfC{$Γ ⊢ ⊥$}
+%   \RightLabel{axiom}
+%   \UnaryInfC{$Γ ⊢ simplify(φ₁, φ₂, ψ)$}
+%   \end{bprooftree}
+% \end{equation*}
+
+% \end{itemize}
+% \end{sketchproof}
 

### 2017-10-17 paper/sections/proof-reconstruction.tex
[ paper ] minor changes.

@@
 
-Now, we have removed redundancies in the disjunctions by applying the
-$rm_{∨}$, we can define a similar function to work with conjunctions.
+Now, we have removed redundancies in the disjunctions by applying
+$rm_{∨}$ function, we can define a similar function to work with conjunctions.
 
@@
 mainly normalization of the proposition input by using theorems
-described in the section above. Metis can introduce axioms, and definitions
-by using it. This rule can convert a \texttt{fof} %TODO
-formula in clausal form into a CNF clause. Since the nature of this rule
-consists of dealing with CNF clauses, to justify its reasoning, our strategy
-mainly consists of checking the equality of normalized negative form between
-the source and the target formula. If it fails, we try to reorder the
-conjunctive normal form of the source formula to match
+described in the section above.  It can introduce axioms and definitions
+in the problem. This rule convert a \texttt{fof} %TODO
+formula in clausal form to a \CNF clause but also it perform some
+simplification in the process (removing ⊤ and ⊥ from the formula).
+
+Since this rule mostly consists of dealing with \CNF clauses, to justify its reasoning, our strategy mainly consists of checking the equality of normalized negative form between the source and the target formula.
+If it fails, we try to reorder the conjunctive normal form of the source formula to match with
 the conjunctive normal form of the target formula.
@@
 \end{equation*}
-\item If $γ := cnf(ψ) ≡ reorder_{∧∨}(cnf(φ), cnf(ψ))$,
+\item If $γ = cnf(ψ) ≡ reorder_{∧∨}(cnf(φ), cnf(ψ))$,
 \begin{equation*}
@@
 literals and a \emph{literal} is an atom (positive literal) or a
-negation of an atom (negative literal).
-Be aware this kind of conversion between one formula to its clausal normal form is not unique, and \Metis has a customized approach to perform that transformation.
-In the following \Metis \TSTP derivation, we see a clear example, where
-clausify expands the formula \texttt{normalize\_0\_0} by using distributive
-laws.
+negation of an atom (negative literal). Be aware this kind of conversion
+between one formula to its clausal normal form is not unique, and \Metis has a
+customized approach to perform that transformation. That is the reason we
+perform some reordering for the CNF of the source formula to fulfill this
+issue.
+
+In the following \Metis \TSTP derivation, we see a clear example where
+\clausify expands the formula \texttt{normalize\_0\_0} by using distributive
+laws presented in conjunctive normal form conversion.
 

### 2017-10-17 paper/sections/conclusions.tex
[ paper ] conclusions reviewed.

--- 2017-10-16 paper/sections/conclusions.tex
@@
 
-We presented a reliable proof-reconstruction of \Metis solutions
-for problems in classical propositional logic without logic.
+We presented a reliable proof-reconstruction in type theory of \Metis
+solutions for problems in classical propositional logic without
+equality. As a product of this research, we built a proof-reconstruction tool written in \Haskell. This tool generates
+\Agda proof-terms of \Metis \TSTP derivations. \Agda files
+delivered by the aforementioned tool are supported by the
+formalization in \Agda of the \Metis rules described in
+Section~\ref{ssec:emulating-inferences}.
+
 The reconstruction approach in this study was designed to use
-only a syntactic treatment of the logic without considering the
-semantics. This aspect represent a difficulty but also an opportunity
-to extend this work towards the support for first-order logic.
-As a first future work, we see the support of \Metis propositional
-fragment with equality.
+only syntactical aspects of the logic. This decision was first a
+difficulty since it demands more detailed proof-objects, a
+description of every transformation or deduction step performed by
+the prover, see
+Section~\ref{sssec:normalization} and Section~\ref{sssec:reordering}.
+But, we chose that syntactical treatment as the opportunity
+to extend this work towards the support of first-order logic.
+Recall, satisfiability in first-order logic is undecidable.
 
-Summarizing, we provided for each \Metis inference rule a theorem that
-emulate the rule deduction. The emulated
-version rules exposed in Section~\ref{ssec:emulating-inferences} admit
-improvements, we left this for future work, particularly, a better
-implementation of \simplify rule.
-Some of the improvements are related with computational efficiency.
-For instance, we use widely functions to check for syntactical equivalence
-between propositions and to reorder propositions to match with another.
-We believe both are expensive tasks and can get help in the analysis
-step inside the translator tool.
+As an early future work, we propose to extend the
+proof-reconstruction presented in this paper to support the
+proposition fragment with equality of \Metis.
+Another option is to extend the proof-reconstruction to support other \ATPs for \CPL like \name{EProver} or \name{Z3}.
+This development can be carried out by following the \name{EProver}
+inference rules described on Kanso' Ph.D. Thesis~\cite{Kanso2012}.
 
-The proof-reconstruction tool presented in this paper
-is able to translate \Metis derivations in \TSTP format to \Agda proof-terms.
-The development presented in this paper can be extended to support
-other \ATPs for \CPL like \name{EProver} or \name{Z3}.
-This future work can be carried out by following the \name{EProver} inference
-rules described on Kanso' Ph.D. Thesis~\cite{Kanso2012}.
+Summarizing, we provided for each \Metis inference rule a theorem in
+type theory to emulate the rule reasoning. This approach mainly
+exposed in Section~\ref{ssec:emulating-inferences}
+admits some improvements, we leave it for future work. We concern
+mainly for a better coverage of the \simplify rule.
+Other improvements are related with computational efficiency of
+rules strongly depend on reordering tasks,
+Section~\ref{sssec:reordering}.
+We believe some rules like \canonicalize can get some help from a analysis done in the translator tool.
 
-One of the main contribution of this study is
-increasing the trustworthiness of these automatic provers,
-in our case, \Metis. Justify a proof-object of a theorem prover has a real
-significant impact for these automatic tools.
+One of the main contribution of this study was
+increasing the trustworthiness of the automatic provers,
+in our case, \Metis.
+Justifying a proof-object of a theorem prover
+has a real significant impact for these automatic tools.
 The reverse engineering task can reveal important issues or bugs
 in many parts of these system (e.g., preprocessing, reasoning, or
-deduction modules). While doing this research, we had the opportunity
-to find some of those kind of bugs\footnote{Issues No.~2, No.~4. and
+deduction modules). During this research, we had the opportunity
+to find some of bugs\footnote{Issues No.~2, No.~4. and
 commit \name{8a3f11e} in the \Metis' official repository
-\url{https://github.com/gilith/metis}}. Fortunately, all these bugs
-were fixed quickly for release 20170810 by Joe Hurd.
+\url{https://github.com/gilith/metis}} in \Metis.
+Fortunately, all these problems were fixed quickly by Joe Hurd in
+20170810 release.
 

### 2017-10-17 paper/sections/proof-reconstruction.tex
[ paper ] conclusions reviewed.

@@
 \subsubsection{Reordering.}
+\label{sssec:reordering}
+
 Logic equivalence between propositions is a major issue to justify
@@
 \subsubsection{Normalization.}
-\label{sssec:normal_forms}
-In the core of \Metis, we find an important module:
-\texttt{Normalize.sml}.
-This module is the responsible for rules like \canonicalize, \clausify,
-\conjunct or \simplify.
-One of the main purposes of the module consists of adding the axioms to the problem. Into this process, some transformation are carried out by different inference rules.
-For example, the \canonicalize rule can convert a first-order form formulas to their clausal normal form.
-In that process, the formula can suffers different transformations by removing redundancies (tautologies or definitions), converting the proposition to its normalized negative normal form, to its conjunctive normal form, or to a specialized normal form.
+\label{sssec:normalization}
+The normalization module in \Metis is the responsible for
+\canonicalize, \clausify, \conjunct and \simplify.
+One of the main purposes of the module consists of adding the axioms
+to the problem. In this process, some transformations are carried
+out by convert a \verb!fof! formula to their clausal normal form.
+The process mainly consists of removing redundancies (tautologies or
+definitions) and converting the proposition to its normalized
+negative normal form, conjunctive normal form, or
+definitional normal form.
 
@@
 $Γ$ is a set of \Prop propositions premises, and $φ : \NProp$ is the
-sequent's conclusion. These theorems have a subset of rules from
+conclusion of the theorem. These theorems have a subset of rules from
 the classical inference rules in Fig.~\ref{fig:CPL-inference-rules}
@@
 if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
-Note that $ψ ∈_{∨} φ$ can be defined as the equality
+$ψ ∈_{∨} φ$ is another name for the equality
 $ψ ≡ conjunct_{∨}(φ, ψ)$.
@@
 Now, we have removed redundancies in the disjunctions by applying
-$rm_{∨}$ function, we can define a similar function to work with conjunctions.
+$rm_{∨}$ function, we can define a similar function to work with
+conjunctions, the $rm_{∧}$ function.
 
@@
 
-We are ready to combine all function defined above in two function
-$canon_{∧}$ for removing redundancies in conjunctions, and
-$canon_{∨}$ for removing redundancies in disjunctions.
+We use the functions defined above to remove redundancies in conjunctions with $canon_{∧}$ function, and
+$canon_{∨}$ function to remove redundancies in disjunctions.
 
@@
 
-Finally, we can translate formulas from \Prop to \NProp by defining the
-$nnf₀$ function based on the \Metis'source code. We have taken
+Finally, we can translate formulas from \Prop to \NProp by defining
+the $nnf₀$ function. We have taken
 inspiration on the $nnf$ function described in
-\citeauthor{Bezem2002}~\cite{Bezem2002}. Their $nnf$ function translates
-formulas to their classical negative normal form. In the reference, the
-authors avoid a termination problem with a similar function by using as an
-extra argument, the polarity of the formula.
-
-For the polarity of a formula, we use the \abbre{Polarity} type with two
-constructors: $⊕$ to denote positive polarity, and $⊖$ to denote negative
-polarity.
+\citeauthor{Bezem2002}~\cite{Bezem2002}. Their $nnf$ function
+translates formulas to their classical negative normal form. In the
+reference, the authors avoid a termination problem with a similar
+function by using as an extra argument, the polarity of the formula.
+We follow the same idea in Def.~\ref{def:nnf-zero}.
+Therefore, we need the \abbre{Polarity} type with
+two constructors: $⊕$ to denote positive polarity, and $⊖$ to denote
+negative polarity of the formula.
 
@@
 \end{equation*}
-Then, by using the ∨-elim rule, from the last derivation above we derive
-$Γ, φ₁ ∨ φ₂ ⟝ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$, and the lemma follows.
+Then, by using the ∨-elim rule in the last derivation above, we
+derive $Γ, φ₁ ∨ φ₂ ⟝ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$ and the lemma
+follows.
 \end{sketchproof}
+
+To convert normalized propositions to classical propositions, we
+make the following definition, completing the translation between
+these two types.
 
@@
 
+As a result, we can get a conjunctive normal form by applying the
+following theorem.
+
 \begin{theorem}[thm-cnf]
@@
     \begin{split}
-    &cnf : \NProp \to \NProp\\
+    &cnf : \Prop \to \Prop\\
     &cnf = form ∘ dist ∘ nnf.
@@
 Since all transformations performed above come from equivalences
-in classical propositional logic, we can also states the following theorem
-convenient for the next section.
+in classical propositional logic, we have stated the following theorem with a purpose for the next section.
 
@@
 mainly normalization of the proposition input by using theorems
-described in the section above.  It can introduce axioms and definitions
-in the problem. This rule convert a \texttt{fof} %TODO
+described in the section above.  It can introduce axioms and
+definitions into the problem solution.
+This rule convert a \texttt{fof} %TODO
 formula in clausal form to a \CNF clause but also it perform some
-simplification in the process (removing ⊤ and ⊥ from the formula).
-
-Since this rule mostly consists of dealing with \CNF clauses, to justify its reasoning, our strategy mainly consists of checking the equality of normalized negative form between the source and the target formula.
-If it fails, we try to reorder the conjunctive normal form of the source formula to match with
+simplification in the process (e.g., removing ⊤ and ⊥ in the formula).
+
+Since this rule mostly consists of dealing with \CNF clauses, to
+justify its reasoning, our strategy mainly consists of checking the
+equality of normalized negative form between the source and the
+target formula. If it fails, we try to reorder the conjunctive
+normal form of the source formula to match with
 the conjunctive normal form of the target formula.
@@
 
-\begin{proof} When $φ ≡ ψ$, we use the $subs$ theorem Eq.~(\ref{eq:substitution-theorem}). Otherwise, we use Theorem \ref{thm:thm-reorder-and-or} and Theorem \ref{thm:thm-cnf}.
+\begin{proof} If $φ ≡ ψ$, this lemmas follows after applies $subs$
+lemma. Otherwise, we use Theorem~\ref{thm:thm-reorder-and-or} and Theorem~\ref{thm:thm-cnf}.
 \end{proof}

### 2017-10-17 paper/sections/related-work.tex
[ paper ] conclusions reviewed.

@@
 In this work, the authors translate automatically propositional logic problems written in \Agda to \TPTP problems.
-By calling an external wrapper the ATP, this tool gets a \TSTP derivation.
+By calling an external wrapper of the ATP, this tool gets a \TSTP derivation.
 The tool parses the \name{EProver} derivation and outputs
@@
 Nevertheless, Kanso and Setzer aim to justify some of the inference rules
-by using propositional semantics instead of just syntactic derivation
-steps.
+by using propositional semantics instead of a only syntactic treatment. We showed here a kind of treatment to justify \Metis proof-objects.
 \end{document}

### 2017-10-17 paper/sections/proof-reconstruction.tex
[ paper ] minor fix.

@@
 In this section, we emulate each \Metis inference rule by proving a
-function with the same name, and a theorem that
-proves the soundness of the function. Then, we will find
-the following pattern to present the formalization for
-the \Metis inference rules. The function name written in bold print is a \Metis
-inference rule in \TSTP derivation. The same function name written
-in italics refers to the emulated version presents in this section.
-Each emulated version states a theorem to prove the soundness of the rule.
+function with the same name, and a associated theorem.
+The following pattern is used to present the formalization.
+The function name written in bold print
+is a \Metis inference rule in \TSTP derivations.
+The same function name written in italics refers to its emulated
+version.
+Each emulated rule states a theorem to prove its soundness.
 This theorem is named by using the prefix \emph{thm}
@@
 Besides the fact, $\List\ \Prop \to \Prop$ is the type that coincides
-with the \simplify rule in \TSTP derivations, we choose a different option.
-In the translation from \TSTP to \Agda, we take the list of derivations
-and use a classical left folding ($foldl$) with $simplify$ and the list with
-$φ₁, φ₂, \cdots, φₙ$. That avoids us to define a new sequent type to
+with the \simplify rule in \TSTP derivations, we choose a different
+option. In the translation from \TSTP to \Agda, we take the list of
+derivations and use a classical left folding ($foldl$) with
+$simplify$ function over the list of $φ₁, φ₂, \cdots, φₙ$.
+That avoids us to define a new sequent type to
 support \List \Prop type in the conclusion side.

### 2017-10-17 paper/sections/abstract.tex
[ paper ] abstract reviewed.

@@
 \begin{abstract}
-In this paper, we describe our approach to reconstruct and verify in
-\Agda proof assistant, solutions generated by \Metis prover to problems in classical propositional logic. The translation method consists of justifying
-step-by-step each deduction found in the prover's solution. To carry
-out this plan, we emulate the inference rules of the prover,
-providing a version of them in the proof assistant. Finally, we
-parse the output of the prover, build and analyze the respective
-tree associated with the proof, for ending up with an \Agda code of
-the proof for type-checking.
+In this paper, we describe a syntactical proof-reconstruction
+approach to verify solutions generated by \Metis prover to problems in classical propositional logic without equality.
+To verify these \Metis derivations, we translate them automatically
+to \Agda proof-terms.
+Using the proof-assistant, we were able to type-check the
+formalization approach presented in this work. A formulation about
+the inference rules used by \Metis.
+This allowed us to type-check proof-objects step-by-step.
 
-\keywords{proof-reconstruction, \Agda, automatic theorem prover,
-classical propositional logic, \Metis.}
+\keywords{proof-reconstruction, type theory, \Agda, automatic
+theorem prover, classical propositional logic, \Metis.}
 

### 2017-10-17 paper/sections/conclusions.tex
[ paper ] minor changes.

@@
 delivered by the aforementioned tool are supported by the
-formalization in \Agda of the \Metis rules described in
-Section~\ref{ssec:emulating-inferences}.
+formalization in \Agda~\cite{AgdaProp,AgdaMetis} of the \Metis rules
+described in Section~\ref{ssec:emulating-inferences}.
 
@@
 deduction modules). During this research, we had the opportunity
-to find some of bugs\footnote{Issues No.~2, No.~4. and
-commit \name{8a3f11e} in the \Metis' official repository
+to improve \Metis by reporting some bugs\footnote{Issues No.~2,
+No.~4. and commit \name{8a3f11e} in the \Metis' official repository
 \url{https://github.com/gilith/metis}} in \Metis.

### 2017-10-17 paper/sections/related-work.tex
[ paper ] minor changes.

@@
 
-Kanso and Setzer~\cite{kanso2016light} integrate the propositional fragment of \name{EProver} in \Agda.
-In this work, the authors translate automatically propositional logic problems written in \Agda to \TPTP problems.
-By calling an external wrapper of the ATP, this tool gets a \TSTP derivation.
-The tool parses the \name{EProver} derivation and outputs
-\Agda code. After that, we say their proof-reconstruction is almost
+Kanso and Setzer~\cite{kanso2016light} integrate the propositional
+fragment of \name{EProver} in \Agda. In this work, the authors
+translate automatically propositional logic problems written in \Agda
+to \TPTP problems. By calling an external wrapper of the ATP, this
+tool gets a \TSTP derivation. The tool parses the \name{EProver}
+derivation and outputs \Agda code.
+We able to say their proof-reconstruction is almost
 similar as the approach presented in Section~\ref{ssec:workflow}.
-Nevertheless, Kanso and Setzer aim to justify some of the inference rules
-by using propositional semantics instead of a only syntactic treatment. We showed here a kind of treatment to justify \Metis proof-objects.
+Nevertheless, Kanso and Setzer aim to justify some of the inference
+rules by using propositional semantics instead of an only syntactic
+treatment as we did in this work.
+
 \end{document}

### 2017-10-18 paper/sections/abstract.tex
[ paper ] lots of grammar fixes.

@@
 In this paper, we describe a syntactical proof-reconstruction
-approach to verify solutions generated by \Metis prover to problems in classical propositional logic without equality.
-To verify these \Metis derivations, we translate them automatically
-to \Agda proof-terms.
-Using the proof-assistant, we were able to type-check the
-formalization approach presented in this work. A formulation about
-the inference rules used by \Metis.
-This allowed us to type-check proof-objects step-by-step.
+approach to verify solutions generated by \Metis prover to problems in
+classical propositional logic without equality.
+To verify these \Metis derivations, we developed a tool able to
+such derivations to \Agda proof-terms.
+We formulate in type theory each inference rule found
+in \Metis derivations for the logic domain mentioned above.
+This allowed us to type-check \Metis proof-objects step-by-step
+with an opportunity to extend to other provers and formalisms.
 

### 2017-10-18 paper/sections/conclusions.tex
[ paper ] lots of grammar fixes.

@@
 solutions for problems in classical propositional logic without
-equality. As a product of this research, we built a proof-reconstruction tool written in \Haskell. This tool generates
+equality. As a product of this research, we were able to build a proof-reconstruction tool written in \Haskell. This tool generates
 \Agda proof-terms of \Metis \TSTP derivations. \Agda files
@@
 The reconstruction approach in this study was designed to use
-only syntactical aspects of the logic. This decision was first a
-difficulty since it demands more detailed proof-objects, a
+only syntactical aspects of the logic.
+This decision was in the beginning a drawback
+since it demands more detailed proof-objects, a
 description of every transformation or deduction step performed by
-the prover, see
-Section~\ref{sssec:normalization} and Section~\ref{sssec:reordering}.
-But, we chose that syntactical treatment as the opportunity
+the prover, which is rarely included in the output of these programs,
+see Section~\ref{sssec:normalization} and Section~\ref{sssec:reordering}.
+We chose that syntactical treatment as the opportunity
 to extend this work towards the support of first-order logic.
@@
 This development can be carried out by following the \name{EProver}
-inference rules described on Kanso' Ph.D. Thesis~\cite{Kanso2012}.
+inference rules described on Kanso's Ph.D. Thesis~\cite{Kanso2012}.
 
 Summarizing, we provided for each \Metis inference rule a theorem in
-type theory to emulate the rule reasoning. This approach mainly
-exposed in Section~\ref{ssec:emulating-inferences}
+type theory to emulate the rule reasoning. This approach, mainly
+exposed in Section~\ref{ssec:emulating-inferences},
 admits some improvements, we leave it for future work. We concern
@@
 Section~\ref{sssec:reordering}.
-We believe some rules like \canonicalize can get some help from a analysis done in the translator tool.
+We believe some rules like \canonicalize can get some help from an analysis done in the translator tool.
 
@@
 The reverse engineering task can reveal important issues or bugs
-in many parts of these system (e.g., preprocessing, reasoning, or
+in many parts of these systems (e.g., preprocessing, reasoning, or
 deduction modules). During this research, we had the opportunity
@@
 No.~4. and commit \name{8a3f11e} in the \Metis' official repository
-\url{https://github.com/gilith/metis}} in \Metis.
+\url{https://github.com/gilith/metis}}.
 Fortunately, all these problems were fixed quickly by Joe Hurd in

### 2017-10-18 paper/sections/discussion.tex
[ paper ] lots of grammar fixes.

@@
 refer to the \Metis' logic kernel.
-Besides the six \Metis' inference rules from the Fig.
-\ref{fig:metis-inferences}, its proof-objects, the \TSTP
+Besides the six \Metis' inference rules from
+Fig.~\ref{fig:metis-inferences}, its proof-objects, the \TSTP
 derivations, exhibit an entirely different set of rules.

### 2017-10-18 paper/sections/metis-language-and-proofs.tex
[ paper ] lots of grammar fixes.

@@
 rules. There are already some tools that perform proof-reconstruction
-with \Metis. Some of these systems are the following.
+with \Metis. %Some of these systems are the following.
 
@@
 where each leaf is a formula from the \TPTP input. A node is a formula
-inferred from the parent formulas. The root is the final derived formula.
-Such a derivation is a list of annotated formulas with the form.
+inferred from the parent formulas. The root is the final derived formula,
+such a derivation is a list of annotated formulas with the form.
 
@@
 \Metis looks for a refutation to prove \verb!fof! problems.
-A \verb!fof! problem contains the conjecture also named the \emph{goal} in the
+A \verb!fof! problem contains the conjecture, the \emph{goal}, in the
 problem. This goal is stripped into subgoals by using the \strip rule. The
@@
 Therefore, to prove the goal, \Metis proves independently each subgoal since
-they tend to be less complex or even smaller propositions. At the end, the
+they tend to be less complex or even fewer propositions. At the end, the
 conjunction of all subgoal proofs must prove the goal. Nevertheless, this last
@@
 
-Finally, \emph{axiom} rule appears in \TSTP derivation by one of the following
-rules to in the problem a \verb!fof! axiom: \canonicalize, \clausify,
-\conjunct, or \simplify. Then, the last rule remains is \emph{resolve}, it
+Finally, \emph{axiom} rule appears in \TSTP derivations by using one of the following rules: \canonicalize, \clausify, \conjunct, or \simplify.
+Then, the last rule remains is \emph{resolve}, it
 appears by the binary rule, \resolve, the version in \Metis of the resolution
-theorem. For a more detailed description of this rules see the Section~\ref{sec:proof-reconstruction}.
+theorem. For a more detailed description of this rules see Section~\ref{sec:proof-reconstruction}.
 

### 2017-10-18 paper/sections/preliminaries.tex
[ paper ] lots of grammar fixes.

@@
 the application of some deduction steps. Such a deduction step has
-the form of a set of propositional \emph{premises} that conclude
+the form of a set of propositional \emph{premises} that produces
 one or more proposition as the conclusion.
@@
 on the left or on the right of the line.
-As a notation convention, if the name of a rule used in the derivation step is typed using verbatim font face, it means, the inference rule belongs to our implementation~\cite{AgdaProp, AgdaMetis} in the Proof Assistant of a inference rule presented
+As a notation convention, if the name of a rule used in the derivation step is typed using verbatim font face, it means the inference rule belongs to our implementation~\cite{AgdaProp, AgdaMetis} in the Proof Assistant of a inference rule presented
 with a similar name.
@@
 If $Γ = ∅$, we write $⊢ φ$, and we say that $φ$ is a theorem.
-Then, a theorem, $Γ ⊢ φ$ , means that there is a derivation with
+A theorem, $Γ ⊢ φ$ , means that there is a derivation with
 conclusion $φ$ and with all (uncanceled) hypotheses in $Γ$.
@@
 proofs and conversely.
-We define the \CPL formal system in the
+We define the \CPL formal system in
 Fig.~\ref{fig:CPL-inference-rules}. The rules described in the aforementioned figure give us the complete
@@
 \begin{bprooftree}
-\AxiomC{$Γ ,φ ⊢ \gamma $}
+\AxiomC{$Γ , φ ⊢ \gamma $}
 \AxiomC{$Γ , ψ  ⊢ \gamma$}

### 2017-10-18 paper/sections/proof-reconstruction.tex
[ paper ] minor changes.
[ paper ] lots of grammar fixes.

@@
 
-With the \TSTP  derivation from the Step~2, we process the derivation with the
+With the \TSTP  derivation from Step~2, we process the derivation with the
 \Athena translator tool~\cite{Athena}.
@@
 As a result of using \Athena, we get an \Agda file, the proof-term. To
-generate this file, \Athena has used names of functions and theorems from
+generate this file, \Athena uses names of functions and theorems from
 \Agda libraries:
@@
 
-Finally, we type-check the \Agda proof-term. If type-checking
-succeed, the \TSTP derivation delivered by \Metis was correct.
+Finally, we type-check the \Agda proof-term. If the type-checking
+success, the \TSTP derivation delivered by \Metis is correct.
 In that case \Agda outputs an interface file.
@@
 type theory is presented to build definitions and theorems of functions
-necessary to emulate \Metis' inference rules. As notation convention,
-We write the type judgments with ``$a : A$'' to denote that $a$
+necessary to emulate \Metis' inference rules. As a convention,
+We write the type judgments as ``$a : A$'' to denote that $a$
 has $\abbre{A}$ type. Types are written using small caps.
@@
 To emulate \Metis' inference rules in type theory,
-we observed that transformations performed by some rules were given
+we observed that transformations performed by some rules are given
 by \emph{general recursive} functions.
-But algorithms based on general recursions can not be translated
+Algorithms based on general recursions can not be translated
 directly in type theory since it is not a guarantee they terminate.
@@
 The former technique defines a new function based on the original
-recursive function by adding an additional argument to the function.
+recursive function by adding an argument to the function.
 The new argument is the \emph{bound}, a natural number given by the
@@
 Henceforth, a natural number has \Nat type, and it is defined as
-usual. That is, \zero and \suc are the data constructors and some
-arithmetic operations are defined: ($+,\,-,\,*$). We include syntax
+usual, i.e., \zero and \suc are the data constructors and some
+arithmetic operations are defined: ($+,\ -,\ *$). We include syntax
 sugar for $\zero$, $\suc$, $\suc(\zero)$, $\cdots$, with the
@@
 Therefore, for a general recursive function $f: \Prop \to \Prop$
-with termination problems, we states a new function
+with termination problems, we state a new function
 $f^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls must be
@@
 
-Recall, the \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
+Recall the \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
 and presented in \cite{VanDalen1994} as \emph{the rank for a
@@
 number for a proposition $φ$ like the following $rank$ function.
-The symbols, $c_{¬}$ and $c_{\square}$ is a non-negative integer
-number called the complexity of the connective.
+The symbols $c_{¬}$ and $c_{\square}$ are non-negative integer
+numbers called the complexity of the respective connective.
 
@@
     rank(φ₁) + c_{¬},  &\text{ if } φ ≡ \neg φ₁ \\
-    \max{(rank(φ₁),rank(φ₂))} + c_{\square},
+    \max{(rank(φ₁),\ rank(φ₂))} + c_{\square},
       &\text{ if } φ ≡ φ₁\,\square\, φ₂.
@@
 We define the $unshunt_{cm}: \Prop → \NN$ function as
-the complexity measure for $unshunt_0$ function.
-
-\begin{align}
+the complexity measure for the $unshunt_0$ function.
+
+\begin{align*}
   \label{eq:unshunt-rank-definition}
@@
         unshunt_{cm}(φ₃) + 2, &\text{ if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-        \max(unshunt_{cm}(φ₂),unshunt_{cm}(φ₃)) + 1,
+        \max(unshunt_{cm}(φ₂),\ unshunt_{cm}(φ₃)) + 1,
           &\text{ if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
@@
   \end{split}
-\end{align}
+\end{align*}
 
@@
 not only general recursion, but they also treat mutual recursive
-function, among other kinds.
+function, among others.
 
@@
 version.
-Each emulated rule states a theorem to prove its soundness.
+Each emulated rule states a respective theorem that proves its soundness.
 This theorem is named by using the prefix \emph{thm}
@@
     &rule : \Prop → \Prop → \cdots → \Prop\\
-    &rule(φ₁,\cdots, φₙ, ψ) =
+    &rule(φ₁,\ \cdots, φₙ, ψ) =
       \begin{cases}
@@
 conjunction of these subgoals implies the goal. Then, a proof of the
-goal becomes in smaller proofs, one refutation for each subgoal.
+goal becomes, in smaller proofs, one refutation for each subgoal.
 These subgoals are introduced in the \TSTP derivation with the \strip
@@
 
-To prove the correctness of the process mentioned above, first,
+To prove the correctness of the process mentioned above,
 we need to establish some lemmas before introduce our main goal of this part,
@@
 		\end{equation*}
-  \item For $n > 1$, we will use induction on the structure of the second
+  \item For $n > 1$, we use induction on the structure of the second
 			  argument.
@@
 
-Let us now define the $split$ function that yields the conjunction of subgoals that implies the goal of the problem in the \Metis \TSTP derivations.
+We now define the $split$ function that yields the conjunction of subgoals
+that implies the goal of the problem in the \Metis \TSTP derivations.
 
@@
 
-The definition above suffers termination problems since it is not
+The definition above has termination problems since it is not
 a structural recursion. Therefore, we have reformulated the equation
@@
 \item $(φ ≡ ¬ (φ₁ ∨ φ₂))$. We show that $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
-The result follows by introducing the conjunction and applying after
-De Morgan Law.
+The result follows by introducing the conjunction and applying
+De Morgan Laws.
 
@@
   Substitution theorem.
-\begin{equation}
+\begin{equation*}
   \label{eq:substitution-theorem}
@@
   \end{bprooftree}
-\end{equation}
+\end{equation*}
 \end{lemma}
@@
 \label{thm:thm-strip}
- If $s_i$ are the subgoals of the goal $φ$ for $i=1,\cdots,n$, and
+ If $s_i$ are the subgoals of the goal $φ$ for $i=1,\cdots,n$ and
  $\{ Γ ⊢ s_i \}_{i =1}^n$, then $Γ ⊢ φ$.
@@
 the negation of its subgoal. The \negate rule
-assumes the negation of such subgoals. This rule
+assumes the negation of such subgoals, and
 appears after applying the \strip inference to the goal.
@@
 
-Then, to emulate this rule, we just introduce the negation
+To emulate this rule, we introduce the negation
 of the subgoal by using $assume$ rule from the inferences in
@@
 projection rules for the conjunction connective as the
-following \TSTP excerpt shows us.
+following \TSTP excerpt shows.
 
@@
 \begin{definition}[conjunct]
-\begin{align}
+\begin{align*}
   \begin{split}
@@
   \end{split}
-\end{align}
+\end{align*}
 \end{definition}
@@
 \begin{itemize}
-  \item For the case, $φ ≡ ψ$, $Γ ⊢ conjunct(φ, ψ)$ normalizes to $Γ ⊢ ψ$.
+  \item For the case $φ ≡ ψ$, $Γ ⊢ conjunct(φ, ψ)$ normalizes to $Γ ⊢ ψ$.
 Then, we get the desire conclusion by applying the $subst$ theorem.
@@
 
-\begin{equation}
+\begin{equation*}
   \begin{bprooftree}
@@
   \end{bprooftree}
-\end{equation}
+\end{equation*}
 \item The last case follows trivially by using the same hypothesis.
@@
 syntax aspects of the propositions, our approach shows equivalence
-by converting propositions to their conjunctive normal forms.
-But also, reordering the conjunctions and the inner disjunctions into the
-formulas to match them.
+by converting propositions to their conjunctive normal forms,
+and reordering those and the inner disjunctions  to match them
 In this section, we provide some theorems to perform such reordering tasks,
@@
 \begin{itemize}
-  \item Reorder a disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots φₙ$ to match with
-$ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$, when for all $i = 1, \cdots, n$, exists at
-least one $ψⱼ$ such that $φᵢ ≡ ψⱼ$ for $j = 1, \cdots, n$.
+  \item Reorder a disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$ to match with
+$ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$. For all $i$, there exists at least one $j$ such that $φᵢ ≡ ψⱼ$.
   \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another
-CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$ when for all $i = 1, \cdots, n$, exists at
-least one $ψⱼ$ such that $φᵢ ≡ ψⱼ$ for $j = 1, \cdots, n$.
+CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$. For all $i$, there exists at least one $j$ such that $φᵢ ≡ ψⱼ$.
 \end{itemize}
@@
 a disjunction in its right-associative form.
-The $rconj$ function converts conjunction to its right-associative form is not
-presented here, but is defined in a similar way (see its implementation
+The $rconj$ function that converts conjunction to its right-associative form
+is not presented here, but is defined in a similar way (see its implementation
 in~\cite{AgdaMetis}).
@@
 to rearrange the disjuncts in the source formula to match with the target
-disjunction formula, similar as we described above.
+disjunction formula, similar as we describe above.
 
@@
 
-From now, we assume all propositions are right-associative unless otherwise stated.
+From now, we assume all propositions to be right-associative unless otherwise stated.
 The $factor$ function in Eq.~(\ref{eq:factor-definition}) intends to simplify a
@@
 
-To construct a disjunction $ψ$ from another disjunction $φ$, we have used ideas
+To construct a disjunction $ψ$ from a disjunction $φ$, we have used ideas
 from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove equality
@@
 \begin{definition}[sbuild$_{∨}$]
-\begin{align}
+\begin{align*}
   \begin{split}
@@
 Let see the main idea behind the lem-sbuild$_{∨}$ lemma.
-We will build the disjunction $((p ∨ q) ∨ r)$ from the disjunction
+We build the disjunction $((p ∨ q) ∨ r)$ from the disjunction
 $(r ∨ (q ∨ p))$.
@@
       \begin{split}
-        &reorder : \Prop → \Prop \to \Prop\\
+        &reorder_{∧} : \Prop → \Prop \to \Prop\\
         &reorder_{∧}(φ, ψ) =
@@
   \label{lem:lem-reorder-and}
-  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ reorder(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ reorder_{∧}(φ, ψ)$.
 \end{lemma}
@@
 
-To emulate this rule, we perform rearrangements inside the formulas
-involved to match with the pattern expected by the resolution theorem
+To emulate this rule, we perform a sequence of rearrangements inside the
+formulas involved to match with the pattern expected by the resolution theorem
 described above. We begin by defining a convenient version of
@@
 has four arguments. The first three were described
-above. The last one, ψ, represents the expected conclusion in the \Metis
+above, the last one, ψ, represents the expected conclusion in the \Metis
 derivation.
@@
 
-In this section we provide the functions and theorems to
-remove inside a normalized formula the definitions showed in
+In this section we provide functions and theorems to remove, inside a normalized formula, the definitions showed in
 Fig.~\ref{fig:conjunctive-disjunctive-simpl}.
@@
 $rm_{∨}$ function, we can define a similar function to work with
-conjunctions, the $rm_{∧}$ function.
+conjunctions, i.e., $rm_{∧}$.
 
@@
 Continuing with the rest of tautologies from
-Fig.~\ref{fig:conjunctive-disjunctive-simpl}, we define
+Fig.~\ref{fig:conjunctive-disjunctive-simpl}, we define the
 $ndisj_{∨}$ function and $ndisj_{∨}$ function that
@@
 \begin{remark}
-A similar treatment defines the $canon_{⊻} : \NProp \to \NProp$
-function that removes redundancies related with the exclusive
+A similar treatment defines the $canon_{⊻} : \NProp \to \NProp$.
+This function removes redundancies related with the exclusive
 disjunction connective.
@@
 Finally, we can translate formulas from \Prop to \NProp by defining
-the $nnf₀$ function. We have taken
-inspiration on the $nnf$ function described in
+the $nnf₀$ function. This function is based on the $nnf$ function described in
 \citeauthor{Bezem2002}~\cite{Bezem2002}. Their $nnf$ function
@@
 reference, the authors avoid a termination problem with a similar
-function by using as an extra argument, the polarity of the formula.
+function by using, as an extra argument, the polarity of the formula.
 We follow the same idea in Def.~\ref{def:nnf-zero}.
@@
 
-Since all transformations performed above come from equivalences
-in classical propositional logic, we have stated the following theorem with a purpose for the next section.
+Since all the previous transformations came from  equivalences in  the
+classical propositional logic, the following theorem plays an important role
+in the next section.
 
@@
 
-The \canonicalize rule is an overloaded inference rule that performs
-mainly normalization of the proposition input by using theorems
-described in the section above.  It can introduce axioms and
-definitions into the problem solution.
-This rule convert a \texttt{fof} %TODO
-formula in clausal form to a \CNF clause but also it perform some
-simplification in the process (e.g., removing ⊤ and ⊥ in the formula).
+The \canonicalize rule is an overloaded inference rule which performs
+normalization of the proposition input.
+%This rule can introduce axioms and definitions into the problem solution.
+This rule converts a \texttt{fof} %TODO
+formula in clausal form to a \CNF clause but also it performs some
+simplifications in the process (e.g., removing ⊤ and ⊥ in the formula).
 
@@
 The \clausify rule transforms a
-propositional formula in its clausal normal form, a conjunction
-of clauses. Where a \emph{clause} is the disjunction of zero or more
+propositional formula into its clausal normal form, a conjunction
+of clauses. A \emph{clause} is the disjunction of zero or more
 literals and a \emph{literal} is an atom (positive literal) or a
-negation of an atom (negative literal). Be aware this kind of conversion
+negation of an atom (negative literal).
+It is important to notice that this kind of conversion
 between one formula to its clausal normal form is not unique, and \Metis has a
@@
 
-In the following \Metis \TSTP derivation, we see a clear example where
+In the following \Metis \TSTP derivation, we see an example where
 \clausify expands the formula \texttt{normalize\_0\_0} by using distributive
@@
 
-\begin{proof} If $φ ≡ ψ$, this lemmas follows after applies $subs$
+\begin{proof} If $φ ≡ ψ$, this lemmas follows after applying $subs$
 lemma. Otherwise, we use Theorem~\ref{thm:thm-reorder-and-or} and Theorem~\ref{thm:thm-cnf}.
@@
 \label{def:simplify}
-For $i,j = 1, 2$, $i\neq j$ and $γ : \Prop$,
-\begin{align}
+For $i,\, j = 1, 2$, $i\neq j$ and $γ : \Prop$,
+\begin{align*}
     \begin{split}
       &\textit{simplify} : \Prop → \Prop → \Prop → \Prop\\
-      &\textit{simplify}(φ₁, φ₂,ψ) =\\
+      &\textit{simplify}(φ₁, φ₂, ψ) =\\
       &\hspace{4mm}
       \begin{cases}
-        ψ,          &\text{ if }φᵢ ≡ ψ,\\
-        ⊥,          &\text{ if }φᵢ ≡ ⊥,\\
-        φⱼ,         &\text{ if }φᵢ ≡ ⊤,\\
+        ψ,          &\text{ if }φᵢ ≡ ψ\\
+        ⊥,          &\text{ if }φᵢ ≡ ⊥\\
+        φⱼ,         &\text{ if }φᵢ ≡ ⊤\\
         γ,          &\text{ if }φᵢ ≡ φⱼ ⇒ γ\\
@@
     \end{split}
-\end{align}
+\end{align*}
 \end{definition}
@@
 \begin{remark}
-Besides the fact, $\List\ \Prop \to \Prop$ is the type that coincides
+Besides the fact that $\List\ \Prop \to \Prop$ is the type that coincides
 with the \simplify rule in \TSTP derivations, we choose a different
@@
 derivations and use a classical left folding ($foldl$) with
-$simplify$ function over the list of $φ₁, φ₂, \cdots, φₙ$.
-That avoids us to define a new sequent type to
+$simplify$ function over the list of $φ₁, φ₂, \cdots, φₙ$
+that avoids us to define a new sequent type to
 support \List \Prop type in the conclusion side.
@@
   \label{thm:thm-simplify}
-For $i=1,2, \cdots, n$, $Γ ⊢ φᵢ$ and $ψ : \Prop$ then
+For $i=1,\, 2, \cdots, n$, $Γ ⊢ φᵢ$ and $ψ : \Prop$ then
 if $n > 2$, $Γ ⊢ simplify(γ_{n-2}, φ_{n}, ψ)$ where $γ_{i} = simplify(φ_{i}, φ_{i+1}, ψ)$

### 2017-10-18 paper/sections/related-work.tex
[ paper ] lots of grammar fixes.

@@
 derivation and outputs \Agda code.
-We able to say their proof-reconstruction is almost
+We are able to say their proof-reconstruction is almost
 similar as the approach presented in Section~\ref{ssec:workflow}.
 Nevertheless, Kanso and Setzer aim to justify some of the inference
-rules by using propositional semantics instead of an only syntactic
-treatment as we did in this work.
+rules by using propositional semantics instead of only syntactic
+treatment as shown above.
 

### 2017-10-18 paper/sections/acknowledgements.tex
[ paper ] lots of grammar fixes.

@@
 
-We thank Universidad EAFIT in Medell\'in, Colombia for funding
-support. This project was a product of the Logic and Computation
+I would like to thank to Universidad EAFIT in Medell\'in, Colombia for funding
+support of this research and my master studies.
+This project was a product of the Logic and Computation
 Research Group at Universidad EAFIT.
+My special thanks to Andrés Sicard-Ramiréz for its patience, valuable comments
+during this research, and in general advices and discussions around many
+topics of my interest.
 
-We thank Joe Leslie-Hurd for his support and comments about \Metis.
-We also acknowledge the work carried out by Alejandro
+I thank Joe Leslie-Hurd for his support and comments about \Metis.
+I also acknowledge the work carried out by Alejandro
 G\'omez-Londo\~no~\cite{Gomez-Londono2015} used as the basis
@@
 inviting us to be part of the \Agda Implementors’ Meeting XXV.
-We honored to present there part of this research.
+I was honored to present there part of this research.
 

### 2017-10-18 paper/sections/conclusions.tex
[ paper ] lots of grammar fixes.

--- 2017-10-17 paper/sections/conclusions.tex
@@
 The reconstruction approach in this study was designed to use
-only syntactical aspects of the logic. This decision was first a
-difficulty since it demands more detailed proof-objects, a
+only syntactical aspects of the logic.
+This decision was in the beginning a drawback
+since it demands more detailed proof-objects, a
 description of every transformation or deduction step performed by

### 2017-10-18 paper/sections/introduction.tex
[ paper ] lots of grammar fixes.

@@
 invalidity of quantified Boolean formulas, a \SMT solver
-(e.g \name{CVC4}~\cite{Barrett2011},\name{veriT}~\cite{bouton2009},
+(e.g \name{CVC4}~\cite{Barrett2011}, \name{veriT}~\cite{bouton2009},
 and \name{Z3}~\cite{DeMoura2008}) to prove unsatisfiability of
@@
 validity of formulas from first-order logic with equality
-(e.g.,\name{E}~\cite{Schulz:AICOM-2002},
+(e.g., \name{E}~\cite{Schulz:AICOM-2002},
 \name{leanCoP}~\cite{Otten2008},
@@
 logic framework to check and validate the reply of the \ATPs since
-they allow us to define the formal language for the problems like
+they allow us to define the formal language for the problems i.e.,
 operators, logic variables, axioms, and theorems.
 
-A proof-reconstruction tool provides such an integration translating
-the reply delivered by the prover into the formalism of the proof
-assistant. Because the formalism of the source (the evidence
+A proof-reconstruction tool provides such an integration, translating
+the reply generated by the prover into the formalism of the proof
+assistant. Since the formalism of the source (the evidence
 generated by the \ATP) is not necessarily the same logic in the
-target, the reconstruction turns out in a ``reverse engineering''
+target, the reconstruction turns out to be a ``reverse engineering''
 task. Then, reconstructing a proof involves an in-depth
-understanding of the algorithms in the \ATP and the specification
-logic in the \ITP. To begin with the proof-reconstruction, it is
+understanding of the algorithms in the \ATP and the logic specification
+in the \ITP. To begin with the proof-reconstruction, it is
 necessary to have a proof-object from the \ATP in a consistent
-format to work with, that is, a full script describing step-by-step
+format, that is, a full script describing step-by-step
 with exhaustive details and without ambiguities, the derivation to
@@
 \name{CVC4}~\cite{Barrett2011}, \name{SPASS}, and
-\name{Waldmeister}~\cite{hillenbrand1997}) and a little bit less replied with
+\name{Waldmeister}~\cite{hillenbrand1997}) and fewer replied with
 a proof
@@
 discussion of future work.
-Some related works with this paper is presented in Section~\ref{sec:related-work}.
-Finally, we provide a small example in the appendix \textsc{A} of the
+Some related works to this paper are presented in Section~\ref{sec:related-work}.
+Finally, in appendix \textsc{A}, we provide a small example of the
 proof-reconstruction workflow.

### 2017-10-18 paper/sections/proof-reconstruction.tex
[ paper ] lots of grammar fixes.

@@
 \begin{itemize}
-  \item For the case $φ ≡ ψ$, $Γ ⊢ conjunct(φ, ψ)$ normalizes to $Γ ⊢ ψ$.
+  \item For the case, $φ ≡ ψ$, $Γ ⊢ conjunct(φ, ψ)$ normalizes to $Γ ⊢ ψ$.
 Then, we get the desire conclusion by applying the $subst$ theorem.
@@
   \item Reorder a disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$ to match with
-$ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$. For all $i$, there exists at least one $j$ such that $φᵢ ≡ ψⱼ$.
+$ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$, when for all $i = 1, \cdots, n$, exists at
+least one $ψⱼ$ such that $φᵢ ≡ ψⱼ$ for $j = 1, \cdots, n$.
   \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another
-CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$. For all $i$, there exists at least one $j$ such that $φᵢ ≡ ψⱼ$.
+CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$ when for all $i = 1, \cdots, n$, exists at
+least one $ψⱼ$ such that $φᵢ ≡ ψⱼ$ for $j = 1, \cdots, n$.
 \end{itemize}
@@
 a disjunction in its right-associative form.
-The $rconj$ function that converts conjunction to its right-associative form
-is not presented here, but is defined in a similar way (see its implementation
+The $rconj$ function converts conjunction to its right-associative form is not
+presented here, but is defined in a similar way (see its implementation
 in~\cite{AgdaMetis}).
@@
 to rearrange the disjuncts in the source formula to match with the target
-disjunction formula, similar as we describe above.
+disjunction formula, similar as we described above.
 
@@
 
-From now, we assume all propositions to be right-associative unless otherwise stated.
+From now, we assume all propositions are right-associative unless otherwise stated.
 The $factor$ function in Eq.~(\ref{eq:factor-definition}) intends to simplify a
@@
 
-To construct a disjunction $ψ$ from a disjunction $φ$, we have used ideas
+To construct a disjunction $ψ$ from another disjunction $φ$, we have used ideas
 from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove equality
@@
 Let see the main idea behind the lem-sbuild$_{∨}$ lemma.
-We build the disjunction $((p ∨ q) ∨ r)$ from the disjunction
+We will build the disjunction $((p ∨ q) ∨ r)$ from the disjunction
 $(r ∨ (q ∨ p))$.
@@
       \begin{split}
-        &reorder_{∧} : \Prop → \Prop \to \Prop\\
+        &reorder : \Prop → \Prop \to \Prop\\
         &reorder_{∧}(φ, ψ) =
@@
   \label{lem:lem-reorder-and}
-  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ reorder_{∧}(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ reorder(φ, ψ)$.
 \end{lemma}
@@
 
-To emulate this rule, we perform a sequence of rearrangements inside the
-formulas involved to match with the pattern expected by the resolution theorem
+To emulate this rule, we perform rearrangements inside the formulas
+involved to match with the pattern expected by the resolution theorem
 described above. We begin by defining a convenient version of
@@
 has four arguments. The first three were described
-above, the last one, ψ, represents the expected conclusion in the \Metis
+above. The last one, ψ, represents the expected conclusion in the \Metis
 derivation.
@@
 
-In this section we provide functions and theorems to remove, inside a normalized formula, the definitions showed in
+In this section we provide the functions and theorems to
+remove inside a normalized formula the definitions showed in
 Fig.~\ref{fig:conjunctive-disjunctive-simpl}.
@@
 $rm_{∨}$ function, we can define a similar function to work with
-conjunctions, i.e., $rm_{∧}$.
+conjunctions, the $rm_{∧}$ function.
 
@@
 Continuing with the rest of tautologies from
-Fig.~\ref{fig:conjunctive-disjunctive-simpl}, we define the
+Fig.~\ref{fig:conjunctive-disjunctive-simpl}, we define
 $ndisj_{∨}$ function and $ndisj_{∨}$ function that
@@
 reference, the authors avoid a termination problem with a similar
-function by using, as an extra argument, the polarity of the formula.
+function by using as an extra argument, the polarity of the formula.
 We follow the same idea in Def.~\ref{def:nnf-zero}.
@@
 This rule converts a \texttt{fof} %TODO
-formula in clausal form to a \CNF clause but also it performs some
-simplifications in the process (e.g., removing ⊤ and ⊥ in the formula).
+formula in clausal form to a \CNF clause but also it perform some
+simplification in the process (e.g., removing ⊤ and ⊥ in the formula).
 
@@
 
-In the following \Metis \TSTP derivation, we see an example where
+In the following \Metis \TSTP derivation, we see a clear example where
 \clausify expands the formula \texttt{normalize\_0\_0} by using distributive
@@
 \begin{remark}
-Besides the fact that $\List\ \Prop \to \Prop$ is the type that coincides
+Besides the fact, $\List\ \Prop \to \Prop$ is the type that coincides
 with the \simplify rule in \TSTP derivations, we choose a different
@@
 derivations and use a classical left folding ($foldl$) with
-$simplify$ function over the list of $φ₁, φ₂, \cdots, φₙ$
-that avoids us to define a new sequent type to
+$simplify$ function over the list of $φ₁, φ₂, \cdots, φₙ$.
+That avoids us to define a new sequent type to
 support \List \Prop type in the conclusion side.

### 2017-10-18 paper/sections/acknowledgements.tex

@@
 Research Group at Universidad EAFIT.
-My special thanks to Andrés Sicard-Ramiréz for its patience, valuable comments
-during this research, and in general advices and discussions around many
-topics of my interest.
+My special thanks to Andrés Sicard-Ramiréz to give me the opportunity
+to work on these exciting topics but also for its patience, discussions,
+and very valuable comments during all this research.
 

### 2017-10-18 paper/sections/metis-language-and-proofs.tex
[ paper ] lots of grammar fixes.

@@
 form (denoted by \name{fof}) and clause normal form (denoted by
-\name{cnf}) formats~\cite{sutcliffe2009} -- is de facto input
+\name{cnf}) formats~\cite{sutcliffe2009,Sicard-Ramirez2016} -- is de facto input
 standard language to encode problems for many \ATPs. The \TPTP
@@
 The \TSTP language is de facto output standard language
-for derivations of ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}.
+for derivations of ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006,Sicard-Ramirez2016}.
 A \TSTP derivation is a directed acyclic graph, a proof tree,

### 2017-10-18 paper/sections/related-work.tex

@@
 \label{sec:related-work}
+
+In this section, we present an extended version of the related work description made in the proposal for this research~\cite{Sicard-Ramirez2016}.
 
@@
 \cite{agdateam}. This integration requires a proof-reconstruction
-step, but authors' approach is restricted to pure equational logic
+step, but authors' approach is restricted to pure equation logic
 --also called identity theory~\cite{humberstone2011}-- that is,

### 2017-10-19 paper/sections/abstract.tex
[ paper ] lots of grammar fixes.
[ paper ] working on corrections.

--- 2017-10-17 paper/sections/abstract.tex
@@
 \begin{abstract}
-In this paper, we describe a syntactical proof-reconstruction
-approach to verify solutions generated by \Metis prover to problems in classical propositional logic without equality.
-To verify these \Metis derivations, we translate them automatically
-to \Agda proof-terms.
-Using the proof-assistant, we were able to type-check the
-formalization approach presented in this work. A formulation about
-the inference rules used by \Metis.
-This allowed us to type-check proof-objects step-by-step.
+We describe a syntactical proof-reconstruction
+approach to verify proofs generated by \Metis prover to problems in
+classical propositional logic.
+To verify these \Metis proofs, we developed a tool able to translate
+such derivations to \Agda proof-terms.
+We formulate in type theory each inference rule found
+in \Metis derivations. This allowed us to type-check \Metis proofs
+step-by-step. We leave it for future work,
+the opportunity to extend this work to other provers, proof assistants, and other formalisms.
 
-\keywords{proof-reconstruction, type theory, \Agda, automatic
-theorem prover, classical propositional logic, \Metis.}
+\keywords{proof-reconstruction, type theory,
+automatic theorem prover}
 

### 2017-10-19 paper/sections/introduction.tex
[ paper ] working on corrections.

@@
 
-Proof-reconstruction is a hard labor since it depends on the
-integration of two complex systems. On the one hand, we have the
+Proof-reconstruction is a non-trivial task since it depends on the
+integration of two complex systems.
+
+On the one hand, we have the
 automatic theorem provers (henceforth \ATP) and their specification
@@
 In this paper, we ported a subset of the \Metis' inference rules to
-\Agda, the propositional fragmented without equality. The formalization of
+\Agda, the propositional fragmented. The formalization of
 these rules allowed us to justify step-by-step \Metis' \TSTP derivations by
@@
 This paper has been organized in the following way.
-The first section of the paper, Section~\ref{ssec:CPL}, will mention some
-notation and syntax of the classical propositional logic.
+In Section~\ref{ssec:CPL}, we introduce some
+notation and syntax of propositional logic.
 In Section~\ref{ssec:metis-language-and-proofs}, we introduce the

### 2017-10-19 paper/sections/metis-language-and-proofs.tex
[ paper ] working on corrections.

@@
 
-\Metis is an automatic theorem prover written in \len{Standard ML}
+\Metis is an automatic theorem prover written in \len{ML}
 for first-order logic with equality developed by John Hurd
@@
 step, and the list of parents nodes. For instance, in Fig.
-\ref{fig:metis-proof-tstp}, \strip is the name of one of the
-inference with no arguments and only one parent node, the
+\ref{fig:metis-proof-tstp}, \strip for example is the name of one of the inference with no arguments and only one parent node, the
 \name{goal}.
@@
 \end{verbatim}
-\caption{The \texttt{Metis}' \texttt{TSTP} derivation for the
+\caption{\texttt{Metis}' \texttt{TSTP} derivation for the
 problem $p\vdash p$.}
@@
   \end{bprooftree}
-  \caption{The \Metis' proof tree for $p \vdash p$ from the
-  derivation in Fig.~\ref{fig:metis-proof-tstp}}
+  \caption{\Metis' proof tree for $p \vdash p$. Derivation in Fig.~\ref{fig:metis-proof-tstp}}
   \label{fig:metis-example}
@@
 
-A proof-object delivered by \Metis encodes a natural
+The output of a proof delivered by \Metis encodes a natural
 deduction proof. The deduction system uses six inference rules
@@
 With these inference rules as the only valid deduction steps, \Metis
-attempts to prove conjectures by refutation (see. e.g.,
+attempts to prove conjectures by refutation (e.g.,
 \emph{falsium} in the last conclusion of the \TSTP derivation in

### 2017-10-19 paper/sections/preliminaries.tex
[ paper ] working on corrections.

@@
 \textit{Propositions.}
-We define the classical propositional logic as usual.
+We define the propositional logic as usual.
 A proposition is an expression of indivisible propositional atoms
-(e.g., symbols $φ₀, φ₁, \cdots$),
-binary logic connectives ($∧, ∨, ⇒, ⇔)$,
-propositional negation $(¬)$, and logic constants $⊥$
-and $⊤$. We use the inductive definition of the set \Prop
+(e.g., symbols $φ₀, φ₁, \cdots$), the logic constants:
+$⊥$, $⊤$, the binary connectives ($∧, ∨, ⇒, ⇔)$, and the negation
+$(¬)$. We use the inductive definition of the set \Prop
 presented in \cite{VanDalen1994} as the mechanism to produce any
 propositional formula.
+
 \begin{itemize}
@@
 A derivation of $φ$ is a mechanism to obtain the conclusion $φ$ from
-the application of some deduction steps. Such a deduction step has
+the application of some deduction steps. Such deduction step has
 the form of a set of propositional \emph{premises} that produces
-one or more proposition as the conclusion.
+propositions as the conclusion.
 
-As we show in the following
-figure, the premises are always above the line, the conclusions
-are below it, and the name of the inference or the theorem used is
+As we show in Fig.~\ref{fig:derivation}, the premises are always above the line, the conclusion
+is below it, and the name of the inference or the theorem used is
 on the left or on the right of the line.
-As a notation convention, if the name of a rule used in the derivation step is typed using verbatim font face, it means the inference rule belongs to our implementation~\cite{AgdaProp, AgdaMetis} in the Proof Assistant of a inference rule presented
-with a similar name.
+% As a notation convention, if the name of a rule used in the derivation step is typed using verbatim font face, for example, \verb!resolve!, it means the inference rule belongs to our implementation~\cite{AgdaProp, AgdaMetis} in the Proof Assistant of a inference rule presented
+% with a similar name.
 
+\begin{figure}
+\label{fig:derivation}
 \begin{equation*}
-\label{eq:derivation}
 \begin{bprooftree}
@@
   \AxiomC{$ψ$}
-  \RightLabel{∧-intro.}
+  \RightLabel{∧-intro}
   \BinaryInfC{$φ ∧ ψ$}
 \end{bprooftree}
-% \qquad
-% \begin{bprooftree}
-%   \AxiomC{$[¬ φ]$}
-%   \noLine
-%   \UnaryInfC{$\vdots$}
-%   \noLine
-%   \UnaryInfC{$⊥$}
-%   \RightLabel{\abbre{RAA}}
-%   \UnaryInfC{φ}
-% \end{bprooftree}
 \end{equation*}
-
-\vskip 2mm
+\caption{Derivation example.}
+\end{figure}
 
@@
 
-\caption{Inference rules in classical propositional logic.}
+\[
+\begin{bprooftree}
+\AxiomC{}
+\RightLabel{PEM}
+\UnaryInfC{$Γ ⊢ φ ∨ ¬ φ$}
+\end{bprooftree}\qquad
+\begin{bprooftree}
+\AxiomC{$Γ, ¬ φ ⊢ ⊥$}
+\RightLabel{RAA}
+\UnaryInfC{$Γ ⊢ φ$}
+\end{bprooftree}
+\]
+
+\caption{Inference rules for propositional logic.}
 \label{fig:CPL-inference-rules}

### 2017-10-19 paper/sections/proof-reconstruction.tex
[ paper ] working on corrections.

--- 2017-10-18 paper/sections/proof-reconstruction.tex
@@
 
-The proof-reconstruction approach proposed here consists of a series
+The proof-reconstruction approach proposed consists of a series
 of steps similar to the workflow presented by \citeauthor{sultana2015} in
@@
 automatic theorem prover, is \Metis; the target system is a proof
-assistant, \Agda. We choose \Agda, but another proof assistant with the same
-support of type theory and inductive types is valid.
+assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types can be used.
 %  (see a description of \Agda for its main features in
@@
 The overview of the proof-reconstruction is presented in
-Fig.~\ref{fig:proof-reconstruction-workflow}, the process begin with
+Fig.~\ref{fig:proof-reconstruction-workflow}. The process begin with
 a \TPTP file that encodes a problem in \CPL. We use this file as the
-input of the \Metis prover and if the problem is a theorem, \Metis can reply
-with a derivation in \TSTP format of the proof.
+input of the \Metis prover and if the problem is a theorem, \Metis can reply a derivation in \TSTP format of the proof.
 
@@
 In the remainder part of this section, a formal description using
-type theory is presented to build definitions and theorems of functions
-necessary to emulate \Metis' inference rules. As a convention,
-We write the type judgments as ``$a : A$'' to denote that $a$
-has $\abbre{A}$ type. Types are written using small caps.
+type theory is presented to build definitions and theorems of
+functions necessary to emulate \Metis' inference rules.
+As a convention, we write the type judgments as ``$m : M$'' to denote that $m$ has $\abbre{M}$ type.
+Types are written using small caps.
 We use \Prop type for propositions and the dependent type, $Γ ⊢ φ$ for
@@
 sugar for $\zero$, $\suc$, $\suc(\zero)$, $\cdots$, with the
-classical representation: $1$, $2$, $\cdots$ as well.
+classical representation: $0$, $1$, $2$, $\cdots$ as well.
 
@@
   \item Reorder a disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$ to match with
-$ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$. For all $i$, there exists at least one $j$ such that $φᵢ ≡ ψⱼ$.
+$ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$. For all $i$, there exists at least one $j$ such
+that $φᵢ ≡ ψⱼ$.
   \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another
-CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$. For all $i$, there exists at least one $j$ such that $φᵢ ≡ ψⱼ$.
+CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$. For all $i$, there exists at least one $j$
+such that $φᵢ ≡ ψⱼ$.
 \end{itemize}

### 2017-10-20 paper/sections/proof-reconstruction.tex
[ paper ] function names using \rm.

@@
 
-Therefore, for a general recursive function $f: \Prop \to \Prop$
+Therefore, for a general recursive function $\rm{f}: \Prop \to \Prop$
 with termination problems, we state a new function
-$f^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls must be
+$\rm{f}^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls must be
 done by using induction on the \Nat type structure.
@@
 \begin{align}
-  \label{eq:unshunt-definition}
-  \begin{split}
-    &unshunt_{0} : \Prop → \Prop\\
-    &unshunt_{0}(φ) =\\
+  \label{eq:uh-definition}
+  \begin{split}
+    &\fuh_{0} : \Prop → \Prop\\
+    &\fuh_{0}(φ) =\\
     &\hspace{3mm}\begin{cases}
-    unshunt_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
+    \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
       & \text{ if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-    unshunt_{0}(φ₁ ⇒ φ₂) ∧ unshunt_{0}(φ₁ ⇒ φ₃),
+    \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃),
       & \text{ if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
@@
 Thus, we define the function
-$unshunt_{1}$ by structural recursion in its second argument in
-Eq.~(\ref{eq:unshunt-structured}).
+$uh_{1}$ by structural recursion in its second argument in
+Eq.~(\ref{eq:uh-structured}).
 
 \begin{align}
-  \label{eq:unshunt-structured}
-  \begin{split}
-    &unshunt_{1} : \Prop → \Nat \to \Prop\\
-    &unshunt_{1}(φ, \zero)\hspace{3mm}= φ\\%\hspace{10cm}\\
-    &unshunt_{1}(φ, \suc(n)) =\\
+  \label{eq:uh-structured}
+  \begin{split}
+    &\fuh_{1} : \Prop → \Nat \to \Prop\\
+    &\fuh_{1}(φ, \zero)\hspace{3mm}= φ\\%\hspace{10cm}\\
+    &\fuh_{1}(φ, \suc(n)) =\\
     &\hspace{3mm}\begin{cases}
-    unshunt_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
+    \fuh_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
       &\text{ if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\[2mm]
-    unshunt_{1}(φ₁ ⇒ φ₂, n)\\
-    ∧\ unshunt_{1}(φ₁ ⇒ φ₃, n),
+    \fuh_{1}(φ₁ ⇒ φ₂, n)\\
+    ∧\ \fuh_{1}(φ₁ ⇒ φ₃, n),
        &\text{ if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
@@
 As we mentioned above, the natural number in the second argument of
-the function used in Eq.~(\ref{eq:unshunt-structured}) stands for a
-complexity measure of the function, in this case $unshunt_{1}$ function.
+the function used in Eq.~(\ref{eq:uh-structured}) stands for a
+complexity measure of the function, in this case $uh_{1}$ function.
 
@@
 proposition}, is a function $\Prop \to \Nat$ that assigns a natural
-number for a proposition $φ$ like the following $rank$ function.
+number for a proposition $φ$ like the following $\frank$ function.
 The symbols $c_{¬}$ and $c_{\square}$ are non-negative integer
@@
   % \label{eq:rank-definition}
-    &rank : \Prop → \Nat\\
-    &rank(φ) =
+    &\frank : \Prop → \Nat\\
+    &\frank(φ) =
     \begin{cases}
     0, &\text{for atomic }φ \\
-    rank(φ₁) + c_{¬},  &\text{ if } φ ≡ \neg φ₁ \\
-    \max{(rank(φ₁),\ rank(φ₂))} + c_{\square},
+    \frank(φ₁) + c_{¬},  &\text{ if } φ ≡ \neg φ₁ \\
+    \fmax{(\frank(φ₁),\ \frank(φ₂))} + c_{\square},
       &\text{ if } φ ≡ φ₁\,\square\, φ₂.
@@
 
-We define the $unshunt_{cm}: \Prop → \NN$ function as
-the complexity measure for the $unshunt_0$ function.
-
-\begin{align*}
-  \label{eq:unshunt-rank-definition}
-  \begin{split}
-      &unshunt_{cm} : \Prop → \Nat\\
-      &unshunt_{cm}(φ) =\\
+We define the $\fuh_{cm}: \Prop → \NN$ function as
+the complexity measure for the $\fuh_0$ function.
+
+\begin{align*}
+  \label{eq:uh-rank-definition}
+  \begin{split}
+      &\fuh_{cm} : \Prop → \Nat\\
+      &\fuh_{cm}(φ) =\\
       &\hspace{3mm}
         \begin{cases}
-        unshunt_{cm}(φ₃) + 2, &\text{ if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-        \max(unshunt_{cm}(φ₂),\ unshunt_{cm}(φ₃)) + 1,
+        \fuh_{cm}(φ₃) + 2, &\text{ if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
+        \fmax(\fuh_{cm}(φ₂),\ \fuh_{cm}(φ₃)) + 1,
           &\text{ if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
@@
 Finally, following the technique mentioned, we get a curated version of
-$unshunt_{0}$ function presented in Def.~\ref{def:unshunt}.
-
-\begin{definition}[unshunt]
-  \label{def:unshunt}
-    \begin{align*}
-      \begin{split}
-      &unshunt : \Prop → \Prop\\
-      &unshunt(\varphi) = unshunt_{1}(\varphi, unshunt_{cm}(\varphi)).
+$\fuh_{0}$ function presented in Def.~\ref{def:uh}.
+
+\begin{definition}[uh]
+  \label{def:uh}
+    \begin{align*}
+      \begin{split}
+      &\fuh : \Prop → \Prop\\
+      &\fuh(φ) = \fuh_{1}(φ, \fuh_{cm}(φ)).
       \end{split}
@@
 \item \texttt{rule} is a $n$-ary \Metis inference rule
-\item $rule$ is the emulated version function  for
+\item $\rm{rule}$ is the emulated version function  for
 the \texttt{rule} inference.
@@
   \begin{split}
-    &rule : \Prop → \Prop → \cdots → \Prop\\
-    &rule(φ₁,\ \cdots, φₙ, ψ) =
-      \begin{cases}
-      ψ, &\text{ if }rule\text{ built }ψ\text{ by applying valid}\\
+    &\rm{rule} : \Prop → \Prop → \cdots → \Prop\\
+    &\rm{rule}(φ₁,\ \cdots, φₙ, ψ) =
+      \begin{cases}
+      ψ, &\text{ if }\rm{rule}\text{ built }ψ\text{ by applying valid}\\
          &\text{ transformations or other rules to }φ\\
@@
   \item $φᵢ$ are \emph{source} formulas from previous deducted derivations.
-  \item $ψ$ is the \emph{target} formula. The excepted result of \texttt{rule}.
+  \item $ψ$ is the \emph{target} formula.
+  The excepted result of \texttt{rule}.
 \end{itemize}
 \end{itemize}
+
+% ------------------------------------------------------------------------------
 
@@
 To prove the correctness of the process mentioned above,
-we need to establish some lemmas before introduce our main goal of this part,
-Theorem~\ref{thm:thm-strip}.
-
-\begin{lemma}[lem-unshunt]
-  \label{lem:unshunt}
-  $Γ ⊢ unshunt(φ)$, then $Γ ⊢ φ$.
+we need to establish some lemmas before introduce our main goal of this
+part, Theorem~\ref{thm:thm-strip}.
+
+\begin{lemma}[lem-inv-uh]
+  \label{lem:uh}
+  $Γ ⊢ \fuh(φ)$, then $Γ ⊢ φ$.
 \end{lemma}
@@
 \begin{sketchproof} Use induction on the cases defined by the outcome of the
-$unshunt$ function in Eq.~(\ref{eq:unshunt-structured}).
+$\fuh$ function in Eq.~(\ref{eq:uh-structured}).
 \begin{itemize}
@@
 		\begin{equation*}
-		\texttt{∧⇒-to-⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
+		\texttt{∧⇒\rm{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
 		\end{equation*}
@@
   \begin{bprooftree}
-  \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
+  \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
   \RightLabel{axiom}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
-  \RightLabel{lem-unshunt}
+  \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
+  \RightLabel{lem-inv-uh}
   \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
-  \RightLabel{∧⇒-to-⇒⇒.}
+  \RightLabel{∧⇒\rm{-to-}⇒⇒.}
   \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)}
@@
   \begin{bprooftree}
-    \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n) ∧ unshunt(φ₁ ⇒ φ₃, n)$}
+    \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n) ∧ \fuh(φ₁ ⇒ φ₃, n)$}
     \RightLabel{∧-proj₁}
-    \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n)$}
+    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n)$}
     \RightLabel{axiom}
-    \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂, n-1)$}
-    \RightLabel{lem-unshunt,}
+    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n-1)$}
+    \RightLabel{lem-inv-uh,}
     \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
@@
   \begin{bprooftree}
-    \AxiomC{$Γ ⊢ unshunt(φ₁ ⇒ φ₂) ∧ unshunt(φ₁ ⇒ φ₃)$}
+    \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂) ∧ \fuh(φ₁ ⇒ φ₃)$}
     \RightLabel{∧-proj₂}
-    \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n)$}
+    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₃, n)$}
     \RightLabel{axiom}
-    \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ φ₃, n-1)$}
-    \RightLabel{lem-unshunt.}
+    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₃, n-1)$}
+    \RightLabel{lem-inv-uh.}
     \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
@@
 
-Finally, using the theorem \texttt{⇒∧⇒-to-⇒∧} from~\cite{AgdaProp},
-\begin{equation*}
-  \texttt{⇒∧⇒-to-⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
+Finally, using the theorem \texttt{⇒∧⇒\rm{-to-}⇒∧} from~\cite{AgdaProp},
+\begin{equation*}
+  \texttt{⇒∧⇒\rm{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
 \end{equation*}
@@
   \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
-  \RightLabel{\tt ⇒∧⇒-to-⇒∧.}
+  \RightLabel{\tt ⇒∧⇒\rm{-to-}⇒∧.}
   \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
@@
 
-We now define the $split$ function that yields the conjunction of subgoals
-that implies the goal of the problem in the \Metis \TSTP derivations.
-
-\begin{definition}[split]
-\label{def:split}
-  \begin{equation*}
-    \begin{split}
-    &split : \Prop → \Prop\\
-    &\mysplit(φ) =
-      \begin{cases}
-      unshunt(\mysplit(φ₁)) &\text{ if }φ ≡ φ₁ ∧ φ₂\\
-      ∧\ unshunt(φ₁ ⇒ \mysplit(φ₂)), &\\[2.5mm]
-      unshunt(¬ φ₁ ⇒ \mysplit(φ₂)),
-        & \text{ if }φ ≡ φ₁ ∨ φ₂\\[2.5mm]
-      unshunt(φ₁ ⇒ \mysplit(φ₂)),
-        & \text{ if }φ ≡ φ₁ ⇒ φ₂\\[2.5mm]
-      unshunt(φ₁ ⇒ \mysplit(φ₂))
+We now define the $\fstrip$ function that yields the conjunction of
+subgoals that implies the goal of the problem in the \Metis \TSTP derivations.
+
+\begin{definition}[strip]
+\label{def:strip}
+  \begin{equation*}
+    \begin{split}
+    &\fstrip : \Prop → \Prop\\
+    &\fstrip(φ) =
+      \begin{cases}
+      \fuh(\fstrip(φ₁)) ∧ \fuh(φ₁ ⇒ \fstrip(φ₂)),
+      &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
+      \fuh(¬ φ₁ ⇒ \fstrip(φ₂)),
+        & \text{ if }φ ≡ φ₁ ∨ φ₂\\
+      \fuh(φ₁ ⇒ \fstrip(φ₂)),
+        & \text{ if }φ ≡ φ₁ ⇒ φ₂\\
+      \fuh(φ₁ ⇒ \fstrip(φ₂)) ∧ \fuh(φ₂ ⇒ \fstrip(φ₁)),
         & \text{ if }φ ≡ φ₁ ⇔ φ₂\\
-      ∧\ unshunt(φ₂ ⇒ \mysplit(φ₁)),
-        &\\[2.5mm]
-      unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
-        & \text{ if }φ ≡ ¬ (φ₁ ∧ φ₂)\\[2.5mm]
-      unshunt(\mysplit(¬ φ₁))
+      \fuh(φ₁ ⇒ \fstrip(¬ φ₂)),
+        & \text{ if }φ ≡ ¬ (φ₁ ∧ φ₂)\\
+      \fuh(\fstrip(¬ φ₁)) ∧\ \fuh(¬ φ₁ ⇒ \fstrip(¬ φ₂)),
         & \text{ if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
-      ∧\ unshunt(¬ φ₁ ⇒ \mysplit(¬ φ₂)),
-        &\\[2.5mm]
-      unshunt(\mysplit(φ₁))
+      \fuh(\fstrip(φ₁)) ∧\ \fuh(φ₁ ⇒ \fstrip(¬ φ₂)),
         & \text{ if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
-      ∧\ unshunt(φ₁ ⇒ \mysplit(¬ φ₂)),
-        &\\[2.5mm]
-      unshunt(φ₁ ⇒ \mysplit(¬ φ₂))
+      \fuh(φ₁ ⇒ \fstrip(¬ φ₂)) ∧\ \fuh(¬ φ₂ ⇒ \fstrip(φ₁)),
         & \text{ if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
-      ∧\ unshunt(¬ φ₂ ⇒ \mysplit(φ₁)),
-        &\\[2.5mm]
-      unshunt(\mysplit(φ₁)),
+      \fuh(\fstrip(φ₁)),
         & \text{ if }φ ≡ ¬ ¬ φ₁\\
@@
       ⊥,
-        & \text{ if }φ ≡ ¬ ⊤.
+        & \text{ if }φ ≡ ¬ ⊤.\\
+      φ, &\text{ otherwise}.
       \end{cases}
@@
 above to solve such an issue following the technique
-described in Section~\ref{ssec:structural-recursion}. We refer to $split$
-as the function after applying the process mentioned above here and below
-unless otherwise stated.
-
-\begin{lemma}[\thmsplit] $Γ ⊢ \mysplit(φ)$ then $Γ ⊢ φ$.
-\label{lem:lem-split}
+described in Section~\ref{ssec:structural-recursion}.
+We refer to $\fstrip$ as the function after applying the process mentioned above here and below unless otherwise stated.
+
+\begin{lemma}[lem-inv-strip] $Γ ⊢ \fstrip(φ)$ then $Γ ⊢ φ$.
+\label{lem:lem-inv-strip}
 \end{lemma}
@@
 The proof is by induction on the structure of the
-formula $φ$ by following the cases in Def.~\ref{def:split}.
+formula $φ$ by following the cases in Def.~\ref{def:strip}.
 We present some cases but for a complete proof, we refer the reader to~\cite{AgdaMetis}.
+
 \begin{itemize}
@@
   \begin{bprooftree}
- \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+ \AxiomC{$Γ ⊢ \fstrip(φ,n)$}
   \RightLabel{axiom}
-  \UnaryInfC{$Γ ⊢ unshunt(split(¬¬φ₁,n-1))$}
-  \RightLabel{lem-unshunt}
-  \UnaryInfC{$Γ ⊢split(¬¬φ₁,n-1)$}
-  \RightLabel{\thmsplit}
+  \UnaryInfC{$Γ ⊢ \fuh(\fstrip(¬¬φ₁,n-1))$}
+  \RightLabel{lem-inv-uh}
+  \UnaryInfC{$Γ ⊢ \fstrip(¬¬φ₁,n-1)$}
+  \RightLabel{lem-inv-strip}
   \UnaryInfC{$Γ ⊢ ¬¬φ₁$}
@@
   \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+  \AxiomC{$Γ ⊢ \fstrip(φ,n)$}
   \RightLabel{axiom}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ \fuh(φ₁) ∧ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
   \RightLabel{∧-proj₁}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁)$}
-  \RightLabel{lem-unshunt.}
+  \UnaryInfC{$Γ ⊢ \fuh(φ₁)$}
+  \RightLabel{lem-inv-uh.}
   \UnaryInfC{$Γ ⊢ φ₁$}
@@
   \UnaryInfC{Γ ⊢ φ₁}
-  \AxiomC{$Γ ⊢ \mysplit(φ,n)$}
+  \AxiomC{$Γ ⊢ \fstrip(φ,n)$}
   \RightLabel{axiom}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁) ∧ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ \fuh(φ₁) ∧ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
   \RightLabel{$∧$-proj$₂$}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{lem-unshunt}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+  \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
+  \RightLabel{lem-inv-uh}
+  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip(φ₂,n-1)$}
   \RightLabel{$⇒$-elim}
-  \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
-  \RightLabel{\thmsplit.}
+  \BinaryInfC{$Γ ⊢ \fstrip(φ₂,n-1)$}
+  \RightLabel{lem-inv-strip.}
   \UnaryInfC{$Γ ⊢ φ₂$}
@@
   \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
-  \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
+  \AxiomC{$Γ ⊢ \fstrip(φ,n-1)$}
   \RightLabel{axiom}
-  \UnaryInfC{$Γ ⊢ unshunt(φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{lem-unshunt}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+  \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
+  \RightLabel{lem-inv-uh}
+  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip(φ₂,n-1)$}
   \RightLabel{weaken φ₁}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+  \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \fstrip(φ₂,n-1)$}
   \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ , φ₁ ⊢ \mysplit(φ₂,n-1)$}
-  \RightLabel{\thmsplit}
+  \BinaryInfC{$Γ , φ₁ ⊢ \fstrip(φ₂,n-1)$}
+  \RightLabel{lem-inv-strip}
   \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
@@
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ \mysplit(φ, n)$}
+\AxiomC{$Γ ⊢ \fstrip(φ, n)$}
 \RightLabel{axiom}
-\UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂, n))$}
+\UnaryInfC{$Γ ⊢ \fuh(¬ φ₁) ∧ \fuh(¬ φ₁ ⇒ \fstrip(φ₂, n))$}
 \RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ unshunt(¬ φ₁)$}
-\RightLabel{lem-unshunt,}
+\UnaryInfC{$Γ ⊢ \fuh(¬ φ₁)$}
+\RightLabel{lem-inv-uh,}
 \UnaryInfC{$Γ ⊢ ¬ φ₁$}
@@
 
-  \AxiomC{$Γ ⊢ \mysplit(φ,n-1)$}
+  \AxiomC{$Γ ⊢ \fstrip(φ,n-1)$}
   \RightLabel{axiom}
-  \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁) ∧ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ \fuh(¬ φ₁) ∧ \fuh(¬ φ₁ ⇒ \fstrip(φ₂,n-1))$}
   \RightLabel{∧-proj₂}
-  \UnaryInfC{$Γ ⊢ unshunt(¬ φ₁ ⇒ \mysplit(φ₂,n-1))$}
-  \RightLabel{lem-unshunt}
-  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \mysplit(φ₂,n-1)$}
+  \UnaryInfC{$Γ ⊢ \fuh(¬ φ₁ ⇒ \fstrip(φ₂,n-1))$}
+  \RightLabel{lem-inv-uh}
+  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip(φ₂,n-1)$}
   \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ ⊢ \mysplit(φ₂,n-1)$}
-  \RightLabel{\thmsplit.}
+  \BinaryInfC{$Γ ⊢ \fstrip(φ₂,n-1)$}
+  \RightLabel{lem-inv-strip.}
   \UnaryInfC{$Γ ⊢ ¬ φ₂$}
@@
 
-  \AxiomC{$\mysplit(φ) ≡ \bigwedge_{i=1}^n s_i $}
+  \AxiomC{$\fstrip(φ) ≡ \bigwedge_{i=1}^n s_i $}
   \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ \mysplit(φ)$}
-  \RightLabel{\thmsplit.}
+  \BinaryInfC{$Γ ⊢ \fstrip(φ)$}
+  \RightLabel{lem-inv-strip.}
   \UnaryInfC{$Γ ⊢ φ$}
@@
   \begin{split}
-  &conjunct : \Prop \to \Prop \to \Prop\\
-  &conjunct(φ, ψ) =
+  &\fconjunct : \Prop \to \Prop \to \Prop\\
+  &\fconjunct(φ, ψ) =
     \begin{cases}
         ψ, &\text{ if }φ ≡ ψ\\
-        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ conjunct(φ₁, ψ)\\
-        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ conjunct(φ₂, ψ)\\
+        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ \fconjunct(φ₁, ψ)\\
+        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ \fconjunct(φ₂, ψ)\\
         φ, &\text{ otherwise.}
@@
   \label{thm:thm-conjunct}
-  $Γ ⊢ φ$, and $ψ  : \Prop$ , then $Γ ⊢ conjunct(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ  : \Prop$ , then $Γ ⊢ \fconjunct(φ, ψ)$.
 \end{theorem}
@@
 \begin{itemize}
-  \item For the case $φ ≡ ψ$, $Γ ⊢ conjunct(φ, ψ)$ normalizes to $Γ ⊢ ψ$.
-Then, we get the desire conclusion by applying the $subst$ theorem.
-  \item If the proposition $φ$ is a conjunction, and we can get $ψ ≡ conjunct(φ_{i}, ψ)$ for some $i = 1,\ 2$, then,
+  \item For the case $φ ≡ ψ$, $Γ ⊢ \fconjunct(φ, ψ)$ normalizes to $Γ ⊢ ψ$.
+Then, we get the desire conclusion by applying the $\fsubst$ theorem.
+  \item If the proposition $φ$ is a conjunction, and we can get $ψ ≡ \fconjunct(φ_{i}, ψ)$ for some $i = 1,\ 2$, then,
 
@@
   \UnaryInfC{$Γ ⊢ φ_{i}$}
-  \UnaryInfC{$Γ ⊢ conjunct(φ_{i}, ψ)$}
-  \AxiomC{$ψ ≡ conjunct(φ_{i}, ψ)$}
+  \UnaryInfC{$Γ ⊢ \fconjunct(φ_{i}, ψ)$}
+  \AxiomC{$ψ ≡ \fconjunct(φ_{i}, ψ)$}
   \RightLabel{subst.}
@@
 
-First, we define the $rdisj$ function to convert
+First, we define the $\rm{rdisj}$ function to convert
 a disjunction in its right-associative form.
-The $rconj$ function that converts conjunction to its right-associative form
+The $\rm{rconj}$ function that converts conjunction to its right-associative form
 is not presented here, but is defined in a similar way (see its implementation
@@
     \label{eq:rdisj-def}
-      &rdisj(φ) : \Prop \to \Prop\\
-      &rdisj(φ) =
-      \begin{cases}
-      rdisj(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{ if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
-      φ₁ ∨ rdisj(φ₂),         & \text{ if } φ ≡ φ₁ ∨ φ₂\\
+      &\rm{rdisj}(φ) : \Prop \to \Prop\\
+      &\rm{rdisj}(φ) =
+      \begin{cases}
+      \rm{rdisj}(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{ if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
+      φ₁ ∨ \rm{rdisj}(φ₂),         & \text{ if } φ ≡ φ₁ ∨ φ₂\\
       φ,                      & \text{ otherwise.}
@@
 \label{lem:lem-rdisj}
-  $Γ ⊢ φ$ then $Γ ⊢ rdisj(φ)$.
-\end{lemma}
-
-The $build_{∨}$ function in Eq.~(\ref{eq:build-or}) intends to construct a
-disjunction from another disjunction, specifically, this functions will try
-to rearrange the disjuncts in the source formula to match with the target
-disjunction formula, similar as we describe above.
+  $Γ ⊢ φ$ then $Γ ⊢ \rm{rdisj}(φ)$.
+\end{lemma}
 
 \begin{definition}[build$_{∨}$]
-\begin{equation}
+\begin{equation*}
   \begin{split}
   \label{eq:build-or}
-  &build_{∨} : \Prop → \Prop → \Prop\\
-  &build_{∨}(φ, ψ) =\\
-  &\hspace{3mm}
+  &\rm{build}_{∨} : \Prop → \Prop → \Prop\\
+  &\rm{build}_{∨}(φ, ψ) =%\\
+  % &\hspace{3mm}
   \begin{cases}
   ψ, &\text{ if } φ ≡ ψ\\
-  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{, } build_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
+  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{, } \rm{build}_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
   φ, &\text{ otherwise.}
@@
   \end{split}
-\end{equation}
-\end{definition}
+\end{equation*}
+\end{definition}
+
+The $\rm{build}_{∨}$ function defined above intends to construct a
+disjunction from another disjunction, specifically, this functions will
+try to rearrange the disjuncts in the source formula to match with the
+target disjunction formula, similar as we describe above.
 
@@
 \label{lem:lem-build-or}
-$Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ build_{∨}(φ)$.
-\end{lemma}
-
-From now, we assume all propositions to be right-associative unless otherwise stated.
-The $factor$ function in Eq.~(\ref{eq:factor-definition}) intends to simplify a
-special case of disjunction, the repeated disjuncts (e.g., $factor(φ ∨ φ) \mapsto\ φ$).
+$Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}(φ)$.
+\end{lemma}
+
+From now, we assume all propositions to be right-associative unless
+otherwise stated.
+The $\ffactor$ function in Eq.~(\ref{eq:factor-definition}) intends to
+simplify a special case of disjunction, the repeated disjuncts
+(e.g., $\ffactor(φ ∨ φ) \mapsto\ φ$).
 Notice that other cases like $φ ∨ (ψ ∨ φ)$ do no reduce to $(ψ ∨ φ)$.
@@
   \label{eq:factor-definition}
-  &factor : \Prop → \Prop\\
-  &factor(φ) =
-  \begin{cases}
-    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{, } φ₁ ≡ factor(φ₂)\\
+  &\ffactor : \Prop → \Prop\\
+  &\ffactor(φ) =
+  \begin{cases}
+    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{, } φ₁ ≡ \ffactor(φ₂)\\
     φ,   &\text{ otherwise.}
@@
 \label{lem:lem-factor}
-  $Γ ⊢ φ$ then $Γ ⊢ factor(φ)$.
+  $Γ ⊢ φ$ then $Γ ⊢ \ffactor(φ)$.
 \end{lemma}
@@
 To construct a disjunction $ψ$ from a disjunction $φ$, we have used ideas
-from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove equality
-between nested disjunctions. The result is the $sbuild_{∨}$ function that uses
-every disjunct from the source formula, $φ$, to build up the target disjunction $ψ$.
+from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove
+equality between nested disjunctions.
+The result is the $\rm{sbuild}_{∨}$ function
+that uses every disjunct from the source formula, $φ$, to build up the
+target disjunction $ψ$.
 
@@
   \label{eq:strong-build-or-definition}
-    &sbuild_{∨} : \Prop → \Prop → \Prop\\
-    &sbuild_{∨}(φ, ψ) =\\
-    &\hspace{3mm}
-    \begin{cases}
-      factor(build_{∨}(φ₁, ψ) ∨ build_{∨}(φ₂,ψ)),  &\text{ if }φ≡ φ₁ ∨ φ₂\\
-      build_{∨}(φ, ψ),  & \text{ otherwise.}
+    &\rm{sbuild}_{∨} : \Prop → \Prop → \Prop\\
+    &\rm{sbuild}_{∨}(φ, ψ) =%\\
+    % &\hspace{3mm}
+    \begin{cases}
+      \ffactor(\rm{build}_{∨}(φ₁, ψ) ∨ \rm{build}_{∨}(φ₂,ψ)),
+      &\text{ if }φ≡ φ₁ ∨ φ₂\\
+      \rm{build}_{∨}(φ, ψ),  & \text{ otherwise.}
     \end{cases}
@@
 \label{lem:lem-sbuild-or}
-$Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ sbuild_{∨}(φ, ψ)$.
+$Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}(φ, ψ)$.
 \end{lemma}
@@
 
-Notice that using $sbuild_{∨}$ we can build not only a disjunction with the same disjuncts of the source formula but also a complete different formula by adding new disjuncts to the source formula.
+Notice that using $\rm{sbuild}_{∨}$ we can build not only a disjunction with the same disjuncts of the source formula but also a complete different formula by adding new disjuncts to the source formula.
 
@@
     \begin{split}
-    &reorder_{∨} : \Prop \to \Prop \to \Prop\\
-    &reorder_{∨} (φ, ψ) = sbuild_{∨}(rdisj(φ), ψ).
+    &\rm{reorder}_{∨} : \Prop \to \Prop \to \Prop\\
+    &\rm{reorder}_{∨} (φ, ψ) = \rm{sbuild}_{∨}(rdisj(φ), ψ).
     \end{split}
@@
   \label{thm-reorder-or}
-  $Γ ⊢ φ$, and $ψ: \Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ: \Prop$ then $Γ ⊢ \rm{reorder}_{∨}(φ, ψ)$.
 \end{theorem}
@@
       \begin{split}
-        &reorder_{∧} : \Prop → \Prop \to \Prop\\
-        &reorder_{∧}(φ, ψ) =
+        &\rm{reorder}_{∧} : \Prop → \Prop \to \Prop\\
+        &\rm{reorder}_{∧}(φ, ψ) =
         \begin{cases}
           φ, &\text{ if }φ ≡ ψ\\
-          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }reorder_{∧}(φ, ψ₁) ≡ ψ₁\\
-                  &\text{and }reorder_{∧}(φ, ψ₂)≡ ψ₂\\
+          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\rm{reorder}_{∧}(φ, ψ₁) ≡ ψ₁\\
+                  &\text{and }\rm{reorder}_{∧}(φ, ψ₂)≡ ψ₂\\
           φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
-          conjunct(φ, ψ), &\text{ otherwise.}
+          \rm{conjunct}(φ, ψ), &\text{ otherwise.}
         \end{cases}
@@
   \label{lem:lem-reorder-and}
-  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ reorder_{∧}(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ \rm{reorder}_{∧}(φ, ψ)$.
 \end{lemma}
@@
   \begin{split}
-    &conjunct_{∨} : \Prop → \Prop \to \Prop\\
-    &conjunct_{∨}(φ, ψ) =
+    &\fconjunct_{∨} : \Prop → \Prop \to \Prop\\
+    &\fconjunct_{∨}(φ, ψ) =
     \begin{cases}
       ψ, &\text{ if }φ ≡ ψ\\
-      ψ, &\text{ if }reorder_{∨}(φ, ψ) ≡ ψ\\
-      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ conjunct_{∨}(φ, ψ₁) ≡ ψ₁,\\
-        &\text{and } reorder_{∨}(φ, ψ₂) ≡ ψ₂\\
-      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ conjunct_{∨}(φ₁, ψ) ≡ ψ\\
-      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ conjunct_{∨}(φ₂, ψ) ≡ ψ\\
+      ψ, &\text{ if }\freorder_{∨}(φ, ψ) ≡ ψ\\
+      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ \fconjunct_{∨}(φ, ψ₁) ≡ ψ₁,\\
+        &\text{and } \freorder_{∨}(φ, ψ₂) ≡ ψ₂\\
+      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}(φ₁, ψ) ≡ ψ\\
+      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}(φ₂, ψ) ≡ ψ\\
       φ, &\text{ otherwise.}
@@
   \label{lem:lem-conjunct-or}
-  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ conjunct_{∨}(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}(φ, ψ)$.
 \end{lemma}
@@
       \begin{split}
-      &reorder : \Prop \to \Prop \to \Prop\\
-      &reorder_{∧∨}(φ, ψ)=
+      &\freorder : \Prop \to \Prop \to \Prop\\
+      &\freorder_{∧∨}(φ, ψ)=
         \begin{cases}
           ψ, &\text{ if } φ≡ψ\\
-          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ reorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
-             &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
+          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ \freorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
+             &\text{and }\freorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
           φ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂\\
-          conjunct_{∨}(φ, ψ) &\text{ otherwise.}
+          \fconjunct_{∨}(φ, ψ) &\text{ otherwise.}
         \end{cases}
@@
   \label{thm:thm-reorder-and-or}
-  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ reorder_{∧∨}(φ, ψ)$.
+  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$.
 \end{theorem}
@@
       \begin{split}
-        &rsol : \Prop \to \Prop\\
-        &rsol(φ) =
+        &\rm{rsol} : \Prop \to \Prop\\
+        &\rm{rsol}(φ) =
         \begin{cases}
@@
   \label{lem:lem-rsol}
-  $Γ ⊢ φ$ then $Γ ⊢ rsol(φ)$.
+  $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}(φ)$.
 \end{lemma}
@@
  \begin{split}
-    &resolve : \Prop \to \Prop \to \Prop \to \Prop \to \Prop\\
-    &resolve(φ₁, φ₂, l, ψ) =
-      rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨} (φ₂, ¬ l ∨ ψ)).
+    &\fresolve : \Prop \to \Prop \to \Prop \to \Prop \to \Prop\\
+    &\fresolve(φ₁, φ₂, l, ψ) =
+      \rm{rsol}(\freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨} (φ₂, ¬ l ∨ ψ)).
   \end{split}
@@
   \label{thm:thm-resolve}
-  $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ: \Prop$ then $Γ ⊢ resolve(φ₁, φ₂, l, ψ)$.
+  $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ: \Prop$ then
+  $Γ ⊢ \fresolve(φ₁, φ₂, l, ψ)$.
 \end{theorem}
@@
       \RightLabel{thm-reorder$_{∨}$,}
-      \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ)$}
+      \UnaryInfC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ)$}
    \end{bprooftree}
@@
       \RightLabel{thm-reorder$_{∨}$,}
-      \UnaryInfC{$Γ ⊢ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+      \UnaryInfC{$Γ ⊢ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
    \end{bprooftree}
@@
   \begin{bprooftree}
-    \AxiomC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ)$}
-    \AxiomC{$Γ ⊢ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+    \AxiomC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ)$}
+    \AxiomC{$Γ ⊢ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
     \RightLabel{∧-intro}
-    \BinaryInfC{$Γ ⊢ reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+    \BinaryInfC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
     \RightLabel{lem-rsol.}
-    \UnaryInfC{$Γ ⊢ rsol(reorder_{∨}(φ₁, l ∨ ψ) ∧ reorder_{∨}(φ₂, ¬ l ∨ ψ))$}
+    \UnaryInfC{$Γ ⊢ \rm{rsol}(\freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨}(φ₂, ¬ l ∨ ψ))$}
   \end{bprooftree}
@@
   \RightLabel{thm-resolve}
-  \BinaryInfC{$Γ ⊢ resolve(¬ r ∨ p ∨ q, p ∨ q ∨ r, r, p ∨ q)$}
+  \BinaryInfC{$Γ ⊢ \fresolve(¬ r ∨ p ∨ q, p ∨ q ∨ r, r, p ∨ q)$}
   \UnaryInfC{$Γ ⊢ p ∨ q$}
@@
   \NProp is the type for a formula in normalized negative normal form
-  in which negations appear only in the literals and the expression is in terms only of ($⊥$, $⊤$, $¬$, $∧$, $∨$, $⊻$) connectives. The $⊻$ connective is the exclusive disjunction.
+  in which negations appear only in the literals and the expression is
+  in terms only of ($⊥$, $⊤$, $¬$, $∧$, $∨$, $⊻$) connectives.
+  The $⊻$ connective is the exclusive disjunction.
   We define the \NProp type in a similar way as we did for \Prop type.
@@
 
-In this section we provide functions and theorems to remove, inside a normalized formula, the definitions showed in
+In this section we provide functions and theorems to remove, inside
+a normalized formula, the definitions showed in
 Fig.~\ref{fig:conjunctive-disjunctive-simpl}.
@@
 We assume all formulas are in right-associative form in
-the input of the functions by applying a version of $rdisj$ or $rconj$
+the input of the functions by applying a version of $\rm{rdisj}$ or $\rm{rconj}$
 functions for normalized propositions (see Def.~\ref{def:rdisj}).
@@
 $ψ ∈_{∨} φ$ is another name for the equality
-$ψ ≡ conjunct_{∨}(φ, ψ)$.
+$ψ ≡ \fconjunct_{∨}(φ, ψ)$.
 
@@
     \begin{split}
-      &rm_{∨} :  \NProp \to \NProp\\
-      &rm_{∨}(φ) =
-      \begin{cases}
-        rm_{∨}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
+      &\rm{rm}_{∨} :  \NProp \to \NProp\\
+      &\rm{rm}_{∨}(φ) =
+      \begin{cases}
+        \rm{rm}_{∨}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
         φ₁ ∨ rm_{∨}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂\\
@@
   \label{lem:lem_rm-or}
-  $Γ ⟝ φ$ then $Γ ⟝ rm_{∨}(φ)$.
+  $Γ ⟝ φ$ then $Γ ⟝ \rm{rm}_{∨}(φ)$.
 \end{lemma}
@@
 Now, we have removed redundancies in the disjunctions by applying
-$rm_{∨}$ function, we can define a similar function to work with
-conjunctions, i.e., $rm_{∧}$.
+$\rm{rm}_{∨}$ function, we can define a similar function to work with
+conjunctions, i.e., $\rm{rm}_{∧}$.
 
@@
 $ψ ∈_{∧} φ$, if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
-We define $ψ ∈_{∧} φ$ as the equality $ψ ≡ conjunct(φ, ψ)$.
+We define $ψ ∈_{∧} φ$ as the equality $ψ ≡ \fconjunct(φ, ψ)$.
 
@@
     \begin{split}
-    &rm_{∧} : \NProp \to \NProp\\
-    &rm_{∧}(φ) =
+    &\rm{rm}_{∧} : \NProp \to \NProp\\
+    &\rm{rm}_{∧}(φ) =
     \begin{cases}
@@
   \label{lem:lem_rm-and}
-  $Γ ⟝ φ$ then $Γ ⟝ rm_{∧}(φ)$.
+  $Γ ⟝ φ$ then $Γ ⟝ \rm{rm}_{∧}(φ)$.
 \end{lemma}
@@
 Fig.~\ref{fig:conjunctive-disjunctive-simpl}, we define the
-$ndisj_{∨}$ function and $ndisj_{∨}$ function that
+$\rm{ndisj}_{∨}$ function and $\rm{ndisj}_{∨}$ function that
 take into account the following cases.
@@
     \begin{split}
-    &ndisj_{∨} : \NProp \to \NProp\\
-    &ndisj_{∨}(φ) =
+    &\rm{ndisj}_{∨} : \NProp \to \NProp\\
+    &\rm{ndisj}_{∨}(φ) =
       \begin{cases}
         ⊤, &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
-        ⊤, &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂,\ ndisj_{∨}(φ₂) ≡ ⊤\\
-        ¬ φ₁ ∨ ndisj_{∨}(φ₂), &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂\\
+        ⊤, &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂,\ \rm{ndisj}_{∨}(φ₂) ≡ ⊤\\
+        ¬ φ₁ ∨ \rm{ndisj}_{∨}(φ₂), &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂\\
         ⊤, &\text{ if }φ ≡ φ₁ ∨ φ₂,\ ¬φ₁ ∈_{∨} φ₂ \\
-        ⊤, &\text{ if }φ ≡ φ₁ ∨ φ₂,\ ndisj_{∨}(φ₂) ≡ ⊤\\
-        φ₁ ∨ ndisj_{∨}(φ₂),  &\text{ if }φ ≡ φ₁ ∨ φ₂\\
+        ⊤, &\text{ if }φ ≡ φ₁ ∨ φ₂,\ \rm{ndisj}_{∨}(φ₂) ≡ ⊤\\
+        φ₁ ∨ \rm{ndisj}_{∨}(φ₂),  &\text{ if }φ ≡ φ₁ ∨ φ₂\\
         φ, &\text{ otherwise.}
@@
   \label{lem:lem_ndisj-or}
-  $Γ ⟝ φ$ then $Γ ⟝ ndisj_{∨}(φ)$.
+  $Γ ⟝ φ$ then $Γ ⟝ \rm{ndisj}_{∨}(φ)$.
 \end{lemma}
@@
     \begin{split}
-    &ndisj_{∧} : \NProp \to \NProp\\
-    &ndisj_{∧}(φ) =
+    &\rm{ndisj}_{∧} : \NProp \to \NProp\\
+    &\rm{ndisj}_{∧}(φ) =
       \begin{cases}
         ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
-        ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ ndisj_{∧}(φ₂) ≡ ⊥\\
-        ¬ φ₁ ∧ ndisj_{∧}(φ₂), &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂\\
+        ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ \rm{ndisj}_{∧}(φ₂) ≡ ⊥\\
+        ¬ φ₁ ∧ \rm{ndisj}_{∧}(φ₂), &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂\\
         ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
-        ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ndisj_{∧}(φ₂) ≡ ⊥\\
-        φ₁ ∧ ndisj_{∧}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
+        ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \rm{ndisj}_{∧}(φ₂) ≡ ⊥\\
+        φ₁ ∧ \rm{ndisj}_{∧}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
         φ, &\text{ otherwise.}
@@
   \label{lem:lem_ndisj-and}
-  $Γ ⟝ φ$ then $Γ ⟝ ndisj_{∧}(φ)$.
+  $Γ ⟝ φ$ then $Γ ⟝ \rm{ndisj}_{∧}(φ)$.
 \end{lemma}
@@
 
-We use the functions defined above to remove redundancies in conjunctions with $canon_{∧}$ function, and
-$canon_{∨}$ function to remove redundancies in disjunctions.
+We use the functions defined above to remove redundancies in conjunctions
+with $\rm{canon}_{∧}$ function, and $\rm{canon}_{∨}$ function to remove redundancies
+in disjunctions.
 
@@
     \begin{split}
-      &canon_{∧} : \NProp \to \NProp\\
-      &canon_{∧}(φ) =
+      &\rm{canon}_{∧} : \NProp \to \NProp\\
+      &\rm{canon}_{∧}(φ) =
         \begin{cases}
@@
           ⊥,  &\text{ if } φ ≡ φ₁ ∧ φ₂,\ φᵢ ≡ ⊥,\text{ for } i,j = 1,2\\
-          rm_∧(ndisj_∧(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
+          \rm{rm}_∧(\rm{ndisj}_∧(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
           φ,                &\text{ otherwise.}
@@
   \label{lem:lem_canon-and}
-  $Γ ⟝ φ$ then $Γ ⟝ canon_{∧}(φ)$.
+  $Γ ⟝ φ$ then $Γ ⟝ \rm{canon}_{∧}(φ)$.
 \end{lemma}
@@
     \begin{split}
-      &canon_{∨} : \NProp \to \NProp\\
-      &canon_{∨}(φ) =
+      &\rm{canon}_{∨} : \NProp \to \NProp\\
+      &\rm{canon}_{∨}(φ) =
         \begin{cases}
@@
         ⊤,  &\text{ if } φ ≡ φ₁ ∨ φ₂,\ φᵢ ≡ ⊤,\text{ for } i,j = 1,2\\
-        rm_∨(ndisj_∨(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
+        \rm{rm}_∨(\rm{ndisj}_∨(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
         φ, &\text{ otherwise.}
@@
   \label{lem:lem_canon-or}
-  $Γ ⟝ φ$ then $Γ ⟝ canon_{∨}(φ)$.
+  $Γ ⟝ φ$ then $Γ ⟝ \rm{canon}_{∨}(φ)$.
 \end{lemma}
@@
 \begin{remark}
-A similar treatment defines the $canon_{⊻} : \NProp \to \NProp$.
+A similar treatment defines the $\rm{canon}_{⊻} : \NProp \to \NProp$.
 This function removes redundancies related with the exclusive
@@
 Finally, we can translate formulas from \Prop to \NProp by defining
-the $nnf₀$ function. This function is based on the $nnf$ function described in
-\citeauthor{Bezem2002}~\cite{Bezem2002}. Their $nnf$ function
+the $\rm{nnf}₀$ function. This function is based on the $\rm{nnf}$ function described in
+\citeauthor{Bezem2002}~\cite{Bezem2002}. Their $\rm{nnf}$ function
 translates formulas to their classical negative normal form. In the
@@
     \begin{split}
-    &nnf₀ : \abbre{Polarity} \to \Prop \to \NProp\\
-    &nnf₀(⊕, φ) =
-      \begin{cases}
-      canon_{∧}(nnf₀(⊕, φ₁) ∧ nnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
-      canon_{∨}(nnf₀(⊕, φ₁) ∨ nnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
-      canon_{∨}(nnf₀(⊖, φ₁) ∨ nnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
-      canon_{⊻}(nnf₀(⊖, φ₁) ⊻ nnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ⇔ φ₂ \\
-      nnf₀(⊖, φ₁),                          &\text{ if }φ ≡ ¬ φ₁ \\
+    &\rm{nnf₀} : \abbre{Polarity} \to \Prop \to \NProp\\
+    &\rm{nnf₀}(⊕, φ) =
+      \begin{cases}
+      \rm{canon}_{∧}(\rm{nnf₀}(⊕, φ₁) ∧ \rm{nnf₀}(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
+      \rm{canon}_{∨}(\rm{nnf₀}(⊕, φ₁) ∨ \rm{nnf₀}(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
+      \rm{canon}_{∨}(\rm{nnf₀}(⊖, φ₁) ∨ \rm{nnf₀}(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
+      \rm{canon}_{⊻}(\rm{nnf₀}(⊖, φ₁) ⊻ \rm{nnf₀}(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ⇔ φ₂ \\
+      \rm{nnf₀}(⊖, φ₁),                          &\text{ if }φ ≡ ¬ φ₁ \\
       φ,                                    &\text{ otherwise.} \\
       \end{cases}\\
-    &nnf₀(⊖, φ) =
-      \begin{cases}
-      canon_{∨}(nnf₀(⊖, φ₁) ∨ nnf₀(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
-      canon_{∧}(nnf₀(⊖, φ₁) ∧ nnf₀(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
-      canon_{∧}(nnf₀(⊖, φ₂) ∧ nnf₀(⊖, φ₁)),  &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
-      canon_{⊻}(nnf₀(⊕, φ₁) ⊻ nnf₀(⊕, φ₂)),  &\text{ if }φ ≡ φ₁ ⇔ φ₂ \\
-      nnf₀(⊕, φ₁),                           &\text{ if }φ ≡ ¬ φ₁ \\
+    &\rm{nnf₀}(⊖, φ) =
+      \begin{cases}
+      \rm{canon}_{∨}(\rm{nnf₀}(⊖, φ₁) ∨ \rm{nnf₀}(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
+      \rm{canon}_{∧}(\rm{nnf₀}(⊖, φ₁) ∧ \rm{nnf₀}(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
+      \rm{canon}_{∧}(\rm{nnf₀}(⊖, φ₂) ∧ \rm{nnf₀}(⊖, φ₁)),  &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
+      \rm{canon}_{⊻}(\rm{nnf₀}(⊕, φ₁) ⊻ \rm{nnf₀}(⊕, φ₂)),  &\text{ if }φ ≡ φ₁ ⇔ φ₂ \\
+      \rm{nnf₀}(⊕, φ₁),                           &\text{ if }φ ≡ ¬ φ₁ \\
       ⊥,                                          &\text{ if }φ ≡ ⊤ \\
@@
   \label{lem:lem-nnf}
-  $Γ ⊢ φ$ then $Γ ⟝ nnf(φ)$ where,
-  \begin{align*}
-   \begin{split}
-     &nnf : \NProp \to \NProp\\
-     &nnf(φ) = nnf₀(⊕, φ).
+  $Γ ⊢ φ$ then $Γ ⟝ \rm{nnf}(φ)$ where,
+  \begin{align*}
+   \begin{split}
+     &\rm{nnf} : \NProp \to \NProp\\
+     &\rm{nnf}(φ) = \rm{nnf}₀(⊕, φ).
    \end{split}
@@
   \label{lem:lem-dist-or}
-  $Γ ⟝ φ$ then $Γ ⟝ dist_{∨}(φ)$, where,
-  \begin{align*}
-    \begin{split}
-    &dist_{∨} : \Prop \to \Prop\\
-    &dist_{∨}(φ) =
-      \begin{cases}
-        dist_{∨}(φ₁ ∨ φ₂) ∧ dist_{∨}(φ₂ ∨ φ₃), &\text{ if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
-        dist_{∨}(φ₁ ∨ φ₃) ∧ dist_{∨}(φ₁ ∨ φ₃), &\text{ if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
+  $Γ ⟝ φ$ then $Γ ⟝ \rm{dist}_{∨}(φ)$, where,
+  \begin{align*}
+    \begin{split}
+    &\rm{dist}_{∨} : \Prop \to \Prop\\
+    &\rm{dist}_{∨}(φ) =
+      \begin{cases}
+        \rm{dist}_{∨}(φ₁ ∨ φ₂) ∧ \rm{dist}_{∨}(φ₂ ∨ φ₃), &\text{ if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
+        \rm{dist}_{∨}(φ₁ ∨ φ₃) ∧ \rm{dist}_{∨}(φ₁ ∨ φ₃), &\text{ if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
         φ,                                     &\text{ otherwise.}
@@
   \label{lem:lem-dist}
-  $Γ ⟝ φ$ then $Γ ⟝ dist(φ)$, where,
-  \begin{align*}
-      \begin{split}
-      &dist : \Prop \to \Prop\\
-      &dist(φ) =
-        \begin{cases}
-          dist(φ₁) ∧ dist(φ₂),
+  $Γ ⟝ φ$ then $Γ ⟝ \rm{dist}(φ)$, where,
+  \begin{align*}
+      \begin{split}
+      &\rm{dist} : \Prop \to \Prop\\
+      &\rm{dist}(φ) =
+        \begin{cases}
+          \rm{dist}(φ₁) ∧ \rm{dist}(φ₂),
             &\text{ if }φ ≡ φ₁ ∧ φ₂\\
-          dist_{∨}(dist(φ₁) ∨ dist(φ₂)),
+          \rm{dist}_{∨}(\rm{dist}(φ₁) ∨ \rm{dist}(φ₂)),
             &\text{ if }φ ≡ φ₁ ∨ φ₂\\
@@
     \RightLabel{lem-dist}
-    \UnaryInfC{$Γ ⊢ dist(φ_{i})$}
+    \UnaryInfC{$Γ ⊢ \rm{dist}(φ_{i})$}
     \RightLabel{∨-intro$_{1,2}$}
-    \UnaryInfC{$Γ, φ_{i} ⊢ dist(φ₁) ∨ dist(φ₂)$}
+    \UnaryInfC{$Γ, φ_{i} ⊢ \rm{dist}(φ₁) ∨ \rm{dist}(φ₂)$}
     \RightLabel{lem-dist$_{∨}$.}
-    \UnaryInfC{$Γ, φ_{i} ⊢ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$}
+    \UnaryInfC{$Γ, φ_{i} ⊢ \rm{dist}_{∨}(\rm{dist}(φ₁) ∨ \rm{dist}(φ₂))$}
     \end{bprooftree}
@@
 Then, by using the ∨-elim rule in the last derivation above, we
-derive $Γ, φ₁ ∨ φ₂ ⟝ dist_{∨}(dist(φ₁) ∨ dist(φ₂))$ and the lemma
+derive $Γ, φ₁ ∨ φ₂ ⟝ \rm{dist}_{∨}(\rm{dist}(φ₁) ∨ \rm{dist}(φ₂))$ and the lemma
 follows.
@@
     \begin{split}
-      &form : \NProp \to \Prop\\
-      &form(φ) =
-      \begin{cases}
-        form(φ₁) ∧ form(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
-        form(φ₁) ∨ form(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂\\
-        form_{⊻}(φ₂),        &\text{ if }φ ≡ φ₁ ⊻ φ₂\\
+      &\rm{form} : \NProp \to \Prop\\
+      &\rm{form}(φ) =
+      \begin{cases}
+        \rm{form}(φ₁) ∧ \rm{form}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
+        \rm{form}(φ₁) ∨ \rm{form}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂\\
+        \rm{form}_{⊻}(φ₂),        &\text{ if }φ ≡ φ₁ ⊻ φ₂\\
         % ⊥, &\text{ if }φ ≡ ⊥\\
@@
   \label{lem:lem-form}
-   $Γ ⟝ φ$ then $Γ ⊢ form(φ)$.
+   $Γ ⟝ φ$ then $Γ ⊢ \rm{form}(φ)$.
 \end{lemma}
@@
 \label{thm:thm-cnf}
-  $Γ ⊢ φ$ then $Γ ⊢ cnf(φ)$, where,
-  \begin{align*}
-    \begin{split}
-    &cnf : \Prop \to \Prop\\
-    &cnf = form ∘ dist ∘ nnf.
+  $Γ ⊢ φ$ then $Γ ⊢ \rm{cnf}(φ)$, where,
+  \begin{align*}
+    \begin{split}
+    &\rm{cnf} : \Prop \to \Prop\\
+    &\rm{cnf} = \rm{form} ∘ \rm{dist} ∘ \rm{nnf}.
     \end{split}
@@
 \label{thm:thm-inv-cnf}
-  $Γ ⊢ cnf(φ)$ then $Γ ⊢ φ$.
+  $Γ ⊢ \rm{cnf}(φ)$ then $Γ ⊢ φ$.
 \end{theorem}
@@
     \begin{split}
-      &canonicalize : \Prop \to \Prop \to \Prop\\
-      &canonicalize(φ, ψ) =
+      &\fcanonicalize : \Prop \to \Prop \to \Prop\\
+      &\fcanonicalize(φ, ψ) =
       \begin{cases}
         ψ, &\text{ if }ψ ≡ φ\\
-        ψ, &\text{ if }ψ ≡ form(nnf(φ))\\
-        ψ, &\text{ if }cnf(ψ) ≡ reorder_{∧∨}(cnf(φ), cnf(ψ))\\
+        ψ, &\text{ if }ψ ≡ \fform(\fnnf(φ))\\
+        ψ, &\text{ if }\fcnf(ψ) ≡ \freorder_{∧∨}(\fcnf(φ), \fcnf(ψ))\\
         φ, &\text{ otherwise.}\\
@@
   \hspace{4mm}\\
-  $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ canonicalize(φ, ψ)$.
+  $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fcanonicalize(φ, ψ)$.
 \end{theorem}
@@
 \item If $φ ≡ ψ$ by substitution theorem we conclude $Γ ⊢ ψ$.
-\item If $ψ ≡ form(nnf(φ))$,
+\item If $ψ ≡ \fform(\fnnf(φ))$,
 \begin{equation*}
@@
     \RightLabel{lem-nnf}
-    \UnaryInfC{$Γ ⊢₂~nnf(φ)$}
+    \UnaryInfC{$Γ ⊢₂~\fnnf(φ)$}
     \RightLabel{lem-form}
-    \UnaryInfC{$Γ ⊢ form(nnf(φ))$}
-    \AxiomC{$ψ ≡ form(nnf(φ))$}
+    \UnaryInfC{$Γ ⊢ \fform(\fnnf(φ))$}
+    \AxiomC{$ψ ≡ \fform(\fnnf(φ))$}
     \RightLabel{subst.}
@@
 \end{equation*}
-\item If $γ = cnf(ψ) ≡ reorder_{∧∨}(cnf(φ), cnf(ψ))$,
+\item If $γ = \fcnf(ψ) ≡ \freorder_{∧∨}(\fcnf(φ), \fcnf(ψ))$,
 \begin{equation*}
@@
      \RightLabel{thm-cnf}
-     \UnaryInfC{$Γ ⊢ cnf(φ)$}
+     \UnaryInfC{$Γ ⊢ \fcnf(φ)$}
      \RightLabel{thm-reorder$_{∧∨}$}
-     \UnaryInfC{$Γ ⊢ reorder_{∧∨}(cnf(φ), cnf(ψ))$}
+     \UnaryInfC{$Γ ⊢ \freorder_{∧∨}(\fcnf(φ), \fcnf(ψ))$}
      \AxiomC{$γ$}
     \RightLabel{subst}
-    \BinaryInfC{$Γ ⊢ cnf(ψ)$}
+    \BinaryInfC{$Γ ⊢ \fcnf(ψ)$}
     \RightLabel{thm-inv-cnf.}
@@
    \begin{split}
-      &clausify : \Prop → \Prop → \Prop\\
-      &clausify(φ,ψ) =
+      &\fclausify : \Prop → \Prop → \Prop\\
+      &\fclausify(φ,ψ) =
       \begin{cases}
         ψ, &\text{ if }φ≡ψ\\
-        reorder_{∧∨}(cnf(φ), ψ), &\text{ otherwise.}
+        \freorder_{∧∨}(\fcnf(φ), ψ), &\text{ otherwise.}
       \end{cases}
@@
 \label{thm:thm-clausify}
-  $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ clausify(φ, ψ)$.
+  $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fclausify(φ, ψ)$.
 \end{theorem}
 
-\begin{proof} If $φ ≡ ψ$, this lemmas follows after applying $subs$
+\begin{proof} If $φ ≡ ψ$, this lemmas follows after applying $\fsubst$
 lemma. Otherwise, we use Theorem~\ref{thm:thm-reorder-and-or} and Theorem~\ref{thm:thm-cnf}.
@@
     \begin{split}
-      &\textit{simplify} : \Prop → \Prop → \Prop → \Prop\\
-      &\textit{simplify}(φ₁, φ₂, ψ) =\\
-      &\hspace{4mm}
+      &\fsimplify : \Prop → \Prop → \Prop → \Prop\\
+      &\fsimplify(φ₁, φ₂, ψ) =%\\
+      % &\hspace{4mm}
       \begin{cases}
@@
         γ,          &\text{ if }φᵢ ≡ φⱼ ⇒ γ\\
-        γ,          &\text{ if }φᵢ ≡ γ ⇒ nnf(¬ φⱼ)\\
+        γ,          &\text{ if }φᵢ ≡ γ ⇒ \fnnf(¬ φⱼ)\\
         γ,          &\text{ if }φᵢ ≡ φⱼ ⇔ γ \\
-        nnf(¬ γ),   &\text{ if }φᵢ ≡ nnf(¬ φⱼ) ⇔ γ \\
-        γ,          &\text{ if }φᵢ ≡ nnf(¬ φⱼ) ∨ γ\\
-        ⊥,          &\text{ if } nnf(¬ φⱼ) ≡ conjunct(φᵢ, nnf(¬ φⱼ))\\
-      % φ          &\text{ if }conjunct(nnf(¬ φᵢ), φⱼ) ≡  φⱼ\\
-        ⊥,          &\text{ if } ¬ φⱼ ≡ canonicalize(φᵢ, ¬ φⱼ) \\
+        \fnnf(¬ γ), &\text{ if }φᵢ ≡ \fnnf(¬ φⱼ) ⇔ γ \\
+        γ,          &\text{ if }φᵢ ≡ \fnnf(¬ φⱼ) ∨ γ\\
+        ⊥,          &\text{ if } \fnnf(¬ φⱼ) ≡ \fconjunct(φᵢ, \fnnf(¬ φⱼ))\\
+      % φ          &\text{ if }\fconjunct(nnf(¬ φᵢ), φⱼ) ≡  φⱼ\\
+        ⊥,          &\text{ if } ¬ φⱼ ≡ \fcanonicalize(φᵢ, ¬ φⱼ) \\
         φ₁,         &\text{ otherwise.}\\
@@
 option. In the translation from \TSTP to \Agda, we take the list of
-derivations and use a classical left folding ($foldl$) with
-$simplify$ function over the list of $φ₁, φ₂, \cdots, φₙ$
+derivations and use a classical left folding ($\rm{foldl}$) with
+$\fsimplify$ function over the list of $φ₁, φ₂, \cdots, φₙ$
 that avoids us to define a new sequent type to
@@
 For $i=1,\, 2, \cdots, n$, $Γ ⊢ φᵢ$ and $ψ : \Prop$ then
-if $n > 2$, $Γ ⊢ simplify(γ_{n-2}, φ_{n}, ψ)$ where $γ_{i} = simplify(φ_{i}, φ_{i+1}, ψ)$
-else $Γ ⊢ simplify(φ₁, φ₂, ψ)$.
+if $n > 2$, $Γ ⊢ \fsimplify(γ_{n-2}, φ_{n}, ψ)$ where $γ_{i} = \fsimplify(φ_{i}, φ_{i+1}, ψ)$
+else $Γ ⊢ \fsimplify(φ₁, φ₂, ψ)$.
 \end{theorem}

### 2017-10-20 paper/sections/abstract.tex
[ paper ] restructuring the paper :S.

@@
 We formulate in type theory each inference rule found
-in \Metis derivations. This allowed us to type-check \Metis proofs
+in \Metis derivations. This allowed us to type-check with \Agda, \Metis proofs
 step-by-step. We leave it for future work,
-the opportunity to extend this work to other provers, proof assistants, and other formalisms.
+the opportunity to extend this work to support other provers, proof assistants, and formalisms.
 
-\keywords{proof-reconstruction, type theory,
-automatic theorem prover}
+\keywords{proof-reconstruction, type theory, automatic theorem prover,
+proof-assistant}
 

### 2017-10-20 paper/sections/introduction.tex
[ paper ] restructuring the paper :S.

@@
 Proof-reconstruction is a non-trivial task since it depends on the
-integration of two complex systems.
+integration between two complex systems.
+We work in this study with one integration between an automatic theorem
+prover (henceforth \ATP) and an interactive theorem prover (henceforth
+\ITP).
 
-On the one hand, we have the
-automatic theorem provers (henceforth \ATP) and their specification
-logic. These tools are usually classified in at least one of the
-following categories.
-A \SAT solver (e.g., \name{zChaff}~\cite{Moskewicz2001} and
-\name{MiniSat}~\cite{Een2004}) to prove unsatisfiability of \CNF
-formulas, a \abbre{QBF} solver (e.g.,
-\name{GhostQ}~\cite{Klieber2014} and
-\name{DepQBF}~\cite{Lonsing2017}) to prove satisfiability and
-invalidity of quantified Boolean formulas, a \SMT solver
-(e.g \name{CVC4}~\cite{Barrett2011}, \name{veriT}~\cite{bouton2009},
-and \name{Z3}~\cite{DeMoura2008}) to prove unsatisfiability of
-formulas from first-order logic with theories, and a prover for
-validity of formulas from first-order logic with equality
-(e.g., \name{E}~\cite{Schulz:AICOM-2002},
-\name{leanCoP}~\cite{Otten2008},
-\Metis~\cite{hurd2003first},
-\name{SPASS}~\cite{Weidenbach2009} and
-\name{Vampire}~\cite{Riazanov1999}), high-order logic (e.g.,
-\name{Leo-II}~\cite{Benzmuller2008} and
-\name{Satallax}~\cite{Brown2012}) or intuitionistic logic (e.g.,
-\name{ileanCoP}~\cite{Otten2008},
-\name{JProver}~\cite{Schmitt2001}, and
-\name{Gandalf}~\cite{Tammet1997}), among others. On the other hand,
-we have the proof checkers, interactive theorem provers (henceforth
-\ITP) or proof assistants (e.g., \Agda~\cite{agdateam},
-\name{Coq}~\cite{coqteam},
-\name{Isabelle}~\cite{paulson1994isabelle}, and
-\name{HOL4}~\cite{norrish2007hol}). The \ITP tools provide us the
+The \ITP tools provide us the
 logic framework to check and validate the reply of the \ATPs since
@@
 the reply generated by the prover into the formalism of the proof
-assistant. Since the formalism of the source (the evidence
-generated by the \ATP) is not necessarily the same logic in the
-target, the reconstruction turns out to be a ``reverse engineering''
-task. Then, reconstructing a proof involves an in-depth
+assistant.
+
+% Since the formalism of the source (the evidence
+% generated by the \ATP) is not necessarily the same logic in the
+% target, the reconstruction turns out to be a ``reverse engineering''
+% task.
+
+Then, reconstructing a proof involves an in-depth
 understanding of the algorithms in the \ATP and the logic specification
@@
 
+The program and formalizations in \Agda described in this paper are available
+as \verb!Git! repositories at \verb!Github!:
+
+\begin{itemize}
+  \item The \Athena program to translate \Metis proofs to \Agda code:\\
+  \hfill\url{http://github.com/jonaprieto/athena}.\hfill
+  \item A formal system in \Agda for propositional logic:\\
+  \hfill\url{http://github.com/jonaprieto/agda-prop}.\hfill
+  \item A formalization in \Agda to justify \Metis proofs in propositional
+  logic:\\
+  \hfill\url{http://github.com/jonaprieto/agda-prop}.\hfill
+\end{itemize}
+
 \end{document}

### 2017-10-20 paper/sections/metis-language-and-proofs.tex
[ paper ] restructuring the paper :S.

@@
 \cite{hurd2003first}. This prover is suitable for proof
-reconstruction since it provides well-documented proof-objects to
-justify its deduction steps from the basis of only six inference
-rules. There are already some tools that perform proof-reconstruction
-with \Metis. %Some of these systems are the following.
+reconstruction since it provides well-documented proof-objects
+to justify its deduction steps from the basis of only six inference
+rules.
+In Fig.~\ref{fig:metis-inferences}, we show the three \Metis rules for
+propositional logic.
 
-\name{Isabelle/HOL} incorporated \Metis as a macro-step
-reconstruction tool for explaining proof steps (usually \CNF goals)
-replied from other \ATPs like \name{CVC4}, \name{Vampire}, or
-\name{Z3} (more details in Ref.~\cite{paulson2007source}).
-\citeauthor{Farber2015} in \cite{Farber2015} present tactic based on \Metis for
-\name{HOL Light} capable to challenge others tactics like \emph{MESON}
-or the \emph{leanCoP} tactic~\cite{Farber2016}.
+\begin{figure}
+\begin{equation*}
+  \begin{bprooftree}
+    \AxiomC{}
+    \RightLabel{axiom}
+    \UnaryInfC{$Γ ⊢ φ$}
+  \end{bprooftree}
+  \qquad
+  \begin{bprooftree}
+    \AxiomC{}
+    \RightLabel{assume $L$}
+    \UnaryInfC{$Γ ⊢ φ ∨ ¬ φ$}
+  \end{bprooftree}
+  \end{equation*}
+  \vskip2mm
+  \begin{equation*}
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ l ∨ φ$}
+    \AxiomC{$Γ ⊢ ¬ l ∨ ψ$}
+    \RightLabel{resolve $l$}
+    \BinaryInfC{$Γ ⊢ φ ∨ ψ$}
+  \end{bprooftree}
+\end{equation*}
+\caption{CPL inference rules of the \texttt{Metis} prover.}
+\label{fig:metis-inferences}
+\end{figure}
 
@@
 
-\begin{figure}
-\[
-% \scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{axiom}
-  \UnaryInfC{$C$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{assume $L$}
-  \UnaryInfC{$L ∨ \neg L$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{refl $t$}
-  \UnaryInfC{$t = t$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$C$}
-  \RightLabel{subst $\sigma$}
-  \UnaryInfC{$\sigma\,C$}
-\end{bprooftree}
-\qquad
-% }
-\]
-\[
-% \scalebox{0.9}{
-\begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{equality $L$ $p$ $t$}
-  \UnaryInfC{$\neg (L[p] = t) ∨ \neg L ∨ L[ p \mapsto t]$}
-\end{bprooftree}
-\qquad
-\begin{bprooftree}
-  \AxiomC{$L ∨ C$}
-  \AxiomC{$\neg L ∨ D$}
-  \RightLabel{resolve $L$}
-  \BinaryInfC{$C ∨ D$}
-\end{bprooftree}
-% }
-\]
-\caption{CNF Inference rules of the \texttt{Metis} prover.}
-\label{fig:metis-inferences}
-\end{figure}
-
 % -------------------------------------------------------------------

### 2017-10-20 paper/sections/preliminaries.tex
[ paper ] restructuring the paper :S.

@@
 
-\subsection{Classical Propositional Logic}
+\subsection*{Classical Propositional Logic}
 \label{ssec:CPL}
@@
 
-\emph{Derivations.}
-A derivation of $φ$ is a mechanism to obtain the conclusion $φ$ from
+\emph{Inference Rule.}
+An inference rule is a deduction step of the form of a set of propositional
+\emph{premises} that produces propositions as the conclusion.
+A derivation is a
+
+is a mechanism to obtain the conclusion $φ$ from
 the application of some deduction steps. Such deduction step has
-the form of a set of propositional \emph{premises} that produces
-propositions as the conclusion.
 
@@
 \begin{bprooftree}
-  \AxiomC{$φ$}
-  \AxiomC{$ψ$}
+  \AxiomC{$φ ∧ ψ$}
+  \RightLabel{∧-proj₂}
+  \UnaryInfC{$ψ$}
+  \AxiomC{$φ ∧ ψ$}
+  \RightLabel{∧-proj₁}
+  \UnaryInfC{$φ$}
   \RightLabel{∧-intro}
-  \BinaryInfC{$φ ∧ ψ$}
+  \BinaryInfC{$ψ ∧ φ$}
 \end{bprooftree}
@@
 
-\emph{Postulates.}
-We only postulate the principle of excluded third
-(\abbre{PEM}). Assuming \abbre{PEM}, we derive the
-\emph{reductio ad absurdum} rule (\abbre{RAA}) as the
-formulation of the principle of proof by contradiction, that is, a derivation
-of a contradiction, $⊥$, from the hypothesis $(¬ φ)$, is a
-derivation of $φ$.
+% \emph{Postulates.}
+% We postulate the principle of excluded third
+% (\abbre{PEM}). Assuming \abbre{PEM}, we derive the
+% \emph{reductio ad absurdum} rule (\abbre{RAA}) as the
+% formulation of the principle of proof by contradiction, that is, a derivation
+% of a contradiction, $⊥$, from the hypothesis $(¬ φ)$, is a
+% derivation of $φ$.
 
-\begin{equation*}
-\label{eq:PEM-RAA}
-\begin{bprooftree}
-\AxiomC{}
-\RightLabel{PEM,}
-\UnaryInfC{$Γ ⊢ φ ∨ ¬ φ$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-\AxiomC{$Γ, ¬ φ ⊢ ⊥$}
-\RightLabel{RAA.}
-\UnaryInfC{$Γ ⊢ φ$}
-\end{bprooftree}
-\end{equation*}
+% \begin{equation*}
+% \label{eq:PEM-RAA}
+% \begin{bprooftree}
+% \AxiomC{}
+% \RightLabel{PEM,}
+% \UnaryInfC{$Γ ⊢ φ ∨ ¬ φ$}
+% \end{bprooftree}\qquad
+% \begin{bprooftree}
+% \AxiomC{$Γ, ¬ φ ⊢ ⊥$}
+% \RightLabel{RAA.}
+% \UnaryInfC{$Γ ⊢ φ$}
+% \end{bprooftree}
+% \end{equation*}
 
 \emph{Natural Deductions.}
-The natural deduction designed by Gerhard Gentzen in 1930s defines a formal system for derivations that uses a set
-of inference rules as the only way to obtain a conclusion.
-We use this system to refer to formal proofs as natural deduction
+The natural deduction introduced by Gentzen in 1930s defines a formal system
+for derivations that uses a set of inference rules as the only way to obtain a
+conclusion. We use this system to refer to formal proofs as natural deduction
 proofs and conversely.
-We define the \CPL formal system in
-Fig.~\ref{fig:CPL-inference-rules}. The rules described in the aforementioned figure give us the complete
-meaning of the connectives; how to introduce them and
-how they can be remove them in the conclusion side of the theorems.
+
+In this document, we extend the \CPL formal system
+Fig.~\ref{fig:CPL-inference-rules} described on
+paper~\cite{Altenkirch2015} to include inferences rules for the biconditional
+connective, $PEM$ and $RAA$ postulates, among others.
 
 \begin{figure}
-\[%\scalebox{0.9}{
+\begin{equation*}
   \begin{bprooftree}
@@
   \end{bprooftree}
-%}
-\]
+\end{equation*}
 
-\[%\scalebox{0.9}{
+\begin{equation*}
   \begin{bprooftree}
@@
   \begin{bprooftree}
-\AxiomC{$Γ , φ ⊢ \gamma $}
-\AxiomC{$Γ , ψ  ⊢ \gamma$}
+    \AxiomC{$Γ , φ ⊢ γ $}
+    \AxiomC{$Γ , ψ  ⊢ γ$}
     \RightLabel{$\vee$-elim}
-\BinaryInfC{$Γ , φ \vee ψ ⊢ \gamma$}
+    \BinaryInfC{$Γ , φ \vee ψ ⊢ γ$}
   \end{bprooftree}\quad
@@
   \end{bprooftree}
-%}
-\]
+\end{equation*}
 

### 2017-10-20 paper/sections/introduction.tex
[ paper ] diagram: some fixes.

@@
 notation and syntax of propositional logic.
-In Section~\ref{ssec:metis-language-and-proofs}, we introduce the
+In Section~\ref{sec:metis-language-and-proofs}, we introduce the
 \Metis prover and its deduction system.
@@
 
-The program and formalizations in \Agda described in this paper are available
+The program and formalizations in \Agda mentioned in this paper are available
 as \verb!Git! repositories at \verb!Github!:
@@
 \begin{itemize}
-  \item The \Athena program to translate \Metis proofs to \Agda code:\\
-  \hfill\url{http://github.com/jonaprieto/athena}.\hfill
-  \item A formal system in \Agda for propositional logic:\\
-  \hfill\url{http://github.com/jonaprieto/agda-prop}.\hfill
-  \item A formalization in \Agda to justify \Metis proofs in propositional
-  logic:\\
-  \hfill\url{http://github.com/jonaprieto/agda-prop}.\hfill
+  \item The \Athena program to translate proofs generated by \Metis to \Agda code:
+  \url{http://github.com/jonaprieto/athena}.
+  \item The \verb!agda-prop! library as a formal system in \Agda for propositional logic:
+  \url{http://github.com/jonaprieto/agda-prop}.
+  \item The \verb!agda-metis! library as a formalization in \Agda to justify \Metis proofs in propositional
+  logic:
+  \url{http://github.com/jonaprieto/agda-prop}.
 \end{itemize}

### 2017-10-20 paper/sections/proof-reconstruction.tex
[ paper ] restructuring the paper :S.
[ paper ] diagram: some fixes.

@@
 proof using a tree data structure (see the properties
-of this tree in Section~\ref{sssec:metis-proofs}).
+of this tree in Section~\ref{ssec:metis-proofs}).
 We perform an analysis of the proof-tree to remove some
@@
 These subgoals are introduced in the \TSTP derivation with the \strip
-inference rule as we show with the following excerpt.
+inference rule as we show in the following excerpt.
 
@@
 			  argument.
+\vskip 2mm
 \begin{itemize}
@@
 described in Section~\ref{ssec:structural-recursion}.
-We refer to $\fstrip$ as the function after applying the process mentioned above here and below unless otherwise stated.
+We refer to $\fstrip$ as the function after applying the process mentioned
+above here and below unless otherwise stated.
 

### 2017-10-20 paper/sections/conclusions.tex
[ paper ] .0.

--- 2017-10-18 paper/sections/conclusions.tex
@@
 This decision was in the beginning a drawback
-since it demands more detailed proof-objects, a
+since it demands more detailed proofs, a
 description of every transformation or deduction step performed by
@@
 in our case, \Metis.
-Justifying a proof-object of a theorem prover
+Justifying a proof of a theorem prover
 has a real significant impact for these automatic tools.

### 2017-10-20 paper/sections/discussion.tex
[ paper ] .0.

@@
 Besides the six \Metis' inference rules from
-Fig.~\ref{fig:metis-inferences}, its proof-objects, the \TSTP
+Fig.~\ref{fig:metis-inferences}, its proofs, the \TSTP
 derivations, exhibit an entirely different set of rules.

### 2017-10-20 paper/sections/introduction.tex
[ paper ] .0.

@@
 
-Proof-reconstruction is a non-trivial task since it depends on the
-integration between two complex systems.
-We work in this study with one integration between an automatic theorem
-prover (henceforth \ATP) and an interactive theorem prover (henceforth
-\ITP).
+% Proof-reconstruction is a non-trivial task since it depends on the
+% integration between two complex systems.
+% We describe one proof-reconstruction approach between an automatic theorem
+% prover (henceforth \ATP) and an interactive theorem prover (henceforth
+% \ITP).
 
-The \ITP tools provide us the
-logic framework to check and validate the reply of the \ATPs since
-they allow us to define the formal language for the problems i.e.,
-operators, logic variables, axioms, and theorems.
+% The \ITP tools provide us the
+% logic framework to check and validate the reply of the \ATPs since
+% they allow us to define the formal language for the problems i.e.,
+% operators, logic variables, axioms, and theorems.
 
-A proof-reconstruction tool provides such an integration, translating
-the reply generated by the prover into the formalism of the proof
-assistant.
+% A proof-reconstruction tool provides such an integration, translating
+% the reply generated by the prover into the formalism of the proof
+% assistant.
 
-% Since the formalism of the source (the evidence
-% generated by the \ATP) is not necessarily the same logic in the
-% target, the reconstruction turns out to be a ``reverse engineering''
-% task.
+% % Since the formalism of the source (the evidence
+% % generated by the \ATP) is not necessarily the same logic in the
+% % target, the reconstruction turns out to be a ``reverse engineering''
+% % task.
 
-Then, reconstructing a proof involves an in-depth
-understanding of the algorithms in the \ATP and the logic specification
-in the \ITP. To begin with the proof-reconstruction, it is
-necessary to have a proof-object from the \ATP in a consistent
-format, that is, a full script describing step-by-step
-with exhaustive details and without ambiguities, the derivation to
-get the actual proof.
-For problems in classical propositional logic (henceforth \CPL),
-from a list of at least forty\footnote{\ATPs available from the web
-service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
-provers were able to deliver proofs (e.g.,
-\name{CVC4}~\cite{Barrett2011}, \name{SPASS}, and
-\name{Waldmeister}~\cite{hillenbrand1997}) and fewer replied with
-a proof
-in a file format like \TSTP~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}
-(e.g., \name{E}, \Metis, \name{Vampire}, and \name{Z3}),
-\len{LFSC}~\cite{Stump2008}, or the \len{SMT-LIB}~\cite{Bohme2011} format.
+% Then, reconstructing a proof involves an in-depth
+% understanding of the algorithms in the \ATP and the logic specification
+% in the \ITP. To begin with the proof-reconstruction, it is
+% necessary to have a proof from the \ATP in a consistent
+% format, that is, a full script describing step-by-step
+% with exhaustive details and without ambiguities, the derivation to
+% get the actual proof.
 
-Many approaches have been proposed and some tools have been
-implemented for proof-reconstruction in the last decades. These
-programs are relevant not only because it helps to spread their
-usage but they also increase the confidence of their users about
-their algorithms and their correctness (see, for example, bugs in
-\ATPs~\cite{Keller2013,Bohme2011,Fleury2014} and
-\cite{Kanso2012}).
-We mention some of these tools in Section~\ref{sec:related-work}.
+% For problems in classical propositional logic (henceforth \CPL),
+% from a list of at least forty\footnote{\ATPs available from the web
+% service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
+% provers were able to deliver proofs (e.g.,
+% \name{CVC4}~\cite{Barrett2011}, \name{SPASS}, and
+% \name{Waldmeister}~\cite{hillenbrand1997}) and fewer replied with
+% a proof
+% in a file format like \TSTP~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}
+% (e.g., \name{E}, \Metis, \name{Vampire}, and \name{Z3}),
+% \len{LFSC}~\cite{Stump2008}, or the \len{SMT-LIB}~\cite{Bohme2011} format.
 
-In this paper, we ported a subset of the \Metis' inference rules to
-\Agda, the propositional fragmented. The formalization of
-these rules allowed us to justify step-by-step \Metis' \TSTP derivations by
-translating automatically to \Agda by a proof-reconstruction tool built for
-this research named \Athena.
-This paper has been organized in the following way.
-In Section~\ref{ssec:CPL}, we introduce some
-notation and syntax of propositional logic.
-In Section~\ref{sec:metis-language-and-proofs}, we introduce the
-\Metis prover and its deduction system.
-In Section~\ref{sec:proof-reconstruction}, we present our
-approach to reconstruct proofs deliver by \Metis in type theory.
-Section~\ref{sec:conclusions} summarizes the main findings and includes a
-discussion of future work.
-Some related works to this paper are presented in Section~\ref{sec:related-work}.
-Finally, in appendix \textsc{A}, we provide a small example of the
-proof-reconstruction workflow.
+% Many approaches have been proposed and some tools have been
+% implemented for proof-reconstruction in the last decades. These
+% programs are relevant not only because it helps to spread their
+% usage but they also increase the confidence of their users about
+% their algorithms and their correctness (see, for example, bugs in
+% \ATPs~\cite{Keller2013,Bohme2011,Fleury2014} and
+% \cite{Kanso2012}).
+% We mention some of these tools in Section~\ref{sec:related-work}.
+
+% In this paper, we ported a subset of the \Metis' inference rules to
+% \Agda, the propositional fragmented. The formalization of
+% these rules allowed us to justify step-by-step \Metis' \TSTP derivations by
+% translating automatically to \Agda by a proof-reconstruction tool built for
+% this research named \Athena.
+% This paper has been organized in the following way.
+% In Section~\ref{ssec:CPL}, we introduce some
+% notation and syntax of propositional logic.
+% In Section~\ref{sec:metis-language-and-proofs}, we introduce the
+% \Metis prover and its deduction system.
+% In Section~\ref{sec:proof-reconstruction}, we present our
+% approach to reconstruct proofs deliver by \Metis in type theory.
+% Section~\ref{sec:conclusions} summarizes the main findings and includes a
+% discussion of future work.
+% Some related works to this paper are presented in Section~\ref{sec:related-work}.
+% Finally, in appendix \textsc{A}, we provide a small example of the
+% proof-reconstruction workflow.
 

### 2017-10-20 paper/sections/metis-language-and-proofs.tex
[ paper ] diagram: some fixes.
[ paper ] .0.

@@
 
-\subsection{Metis: Language and Proofs}
-\label{ssec:metis-language-and-proofs}
+\section{Metis: Language and Proofs}
+\label{sec:metis-language-and-proofs}
 
@@
 \cite{hurd2003first}. This prover is suitable for proof
-reconstruction since it provides well-documented proof-objects
+reconstruction since it provides well-documented proofs
 to justify its deduction steps from the basis of only six inference
@@
 
-\subsubsection{Input Language.}
+\subsection{Input Language.}
 \label{ssec:input-language}
@@
 form (denoted by \name{fof}) and clause normal form (denoted by
-\name{cnf}) formats~\cite{sutcliffe2009,Sicard-Ramirez2016} -- is de facto input
-standard language to encode problems for many \ATPs. The \TPTP
-syntax describes a well-defined grammar to handle annotated formulas
-with the following form.
+\name{cnf}) formats~\cite{sutcliffe2009,Sicard-Ramirez2016} -- is the
+input language to encode problems used by \Metis.
+The \TPTP syntax describes a well-defined grammar to handle annotated
+formulas with the following form.
 
@@
 serves to identify the formula within the problem. Each formula
-assumes one \name{role}, this could be an \name{axiom},
+assumes a \name{role}, this could be an \name{axiom},
 \name{conjecture}, \name{definition}, or a \name{hypothesis}.
-The formulas include Boolean connectives (\verb!&!, \verb!|!,
-\verb!=>!, \verb!<=>!, \verb!~!) and logic constants \verb!$true!
+%existen otros
+%----Keywords:    fof cnf thf tff include
+%----Punctuation: ( ) , . [ ] :
+%----Operators:   ! ? ~ & | <=> => <= <~> ~| ~& * +
+%----Predicates:  = != $true $false
+
+%----Top of Page---------------------------------------------------------------
+%----CNF formulae (variables implicitly universally quantified)
+% <cnf_formula>          ::= <disjunction> | (<disjunction>)
+% <disjunction>          ::= <literal> | <disjunction> <vline> <literal>
+% <literal>              ::= <fof_atomic_formula> | ~ <fof_atomic_formula> |
+%                            <fof_infix_unary>
+The formulas include the binary Boolean connectives
+(\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!, \verb!~!) and logic constants \verb!$true!
+% the boolean type ($true and $false)
 and \verb!$false!, for the symbols (∧, ∨, ⇒, ⇔, ¬, ⊤, ⊥), respectively.
@@
 
-\subsubsection{Output Language.}
+\subsection{Output Language.}
 \label{ssec:output-language}
@@
 supporting arguments or useful information to apply the reasoning
-step, and the list of parents nodes. For instance, in Fig.
-\ref{fig:metis-proof-tstp}, \strip for example is the name of one of the inference with no arguments and only one parent node, the
+step, and the list of parents nodes.
+
+\begin{verbatim}
+fof(subgoal_0, plain, p, inference(strip, [], [goal])).
+\end{verbatim}
+
+In the script above, \strip is for example the name of the inference.
+It has no arguments and derives from one parent node with goal name.
 \name{goal}.
+
+% -------------------------------------------------------------------
+
+\subsection{Inference Rules.}
+\label{ssec:metis-inferences-rules}
+
+% \TSTP derivations replied by \Metis use other rules. They are
+% \canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
+
+% \Metis looks for a refutation to prove \verb!fof! problems.
+% A \verb!fof! problem contains the conjecture, the \emph{goal}, in the
+% problem. This goal is stripped into subgoals by using the \strip rule. The
+% subgoals are the conjuncts in a general conjunction that is equivalent to the
+% aforementioned goal.
+% Therefore, to prove the goal, \Metis proves independently each subgoal since
+% they tend to be less complex or even fewer propositions. At the end, the
+% conjunction of all subgoal proofs must prove the goal. Nevertheless, this last
+% reasoning is not explicit neither in the \TSTP derivations nor in the
+% documentation available about \Metis.
+% Since \Metis replies refutation proofs, to prove each subgoal, in the \TSTP
+% derivation, the inference rule \negate introduces the negation of such
+% subgoals. The \negate rule is a specification of the \emph{assume} rule.
+
+Finally, \emph{axiom} rule appears in \TSTP derivations by using one of the following rules: \canonicalize, \clausify, \conjunct, or \simplify.
+Then, the last rule remains is \emph{resolve}, it
+appears by the binary rule, \resolve, the version in \Metis of the resolution
+theorem. For a more detailed description of this rules see Section~\ref{sec:proof-reconstruction}.
+
+\subsection{Proofs.}
+\label{ssec:metis-proofs}
 
@@
 \end{figure}
-
-% -------------------------------------------------------------------
-
-\subsubsection{Proof Rules.}
-\label{sssec:proof-rules}
-
-Since the scope of the problems treated in this research is \CPL, from the
-list of \Metis inference rules in Fig.~\ref{fig:metis-inferences}, we found
-that only three rules apply: \emph{axiom}, \emph{assume} and \emph{resolve}
-rule.
-Nonetheless, \TSTP derivations replied by \Metis use other rules. They are
-\canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
-
-\Metis looks for a refutation to prove \verb!fof! problems.
-A \verb!fof! problem contains the conjecture, the \emph{goal}, in the
-problem. This goal is stripped into subgoals by using the \strip rule. The
-subgoals are the conjuncts in a general conjunction that is equivalent to the
-aforementioned goal.
-Therefore, to prove the goal, \Metis proves independently each subgoal since
-they tend to be less complex or even fewer propositions. At the end, the
-conjunction of all subgoal proofs must prove the goal. Nevertheless, this last
-reasoning is not explicit neither in the \TSTP derivations nor in the
-documentation available about \Metis.
-Since \Metis replies refutation proofs, to prove each subgoal, in the \TSTP
-derivation, the inference rule \negate introduces the negation of such
-subgoals. The \negate rule is a specification of the \emph{assume} rule.
-
-Finally, \emph{axiom} rule appears in \TSTP derivations by using one of the following rules: \canonicalize, \clausify, \conjunct, or \simplify.
-Then, the last rule remains is \emph{resolve}, it
-appears by the binary rule, \resolve, the version in \Metis of the resolution
-theorem. For a more detailed description of this rules see Section~\ref{sec:proof-reconstruction}.
-
-\subsubsection{Proofs.}
-\label{sssec:metis-proofs}
 

### 2017-10-20 paper/sections/proof-reconstruction.tex
[ paper ] .0.

@@
 automatic theorem prover, is \Metis; the target system is a proof
-assistant, \Agda. We choose \Agda, but another proof assistant with the same support of type theory and inductive types can be used.
+assistant, \Agda. We choose \Agda, but another proof assistant with the
+same support of type theory and inductive types can be used.
 %  (see a description of \Agda for its main features in
@@
 a \TPTP file that encodes a problem in \CPL. We use this file as the
-input of the \Metis prover and if the problem is a theorem, \Metis can reply a derivation in \TSTP format of the proof.
+input of the \Metis prover and if the problem is a theorem, \Metis can
+reply a derivation in \TSTP format of the proof.
 
@@
 Finally, we type-check the \Agda proof-term. If the type-checking
-success, the \TSTP derivation delivered by \Metis is correct.
+success, the \TSTP derivation delivered by \Metis is correct
+module \Agda and the formalizations of \Metis inferences.
+
 In that case \Agda outputs an interface file.
@@
 functions necessary to emulate \Metis' inference rules.
-As a convention, we write the type judgments as ``$m : M$'' to denote that $m$ has $\abbre{M}$ type.
+As a convention, we write the type judgments as ``$m : M$'' to denote
+that $m$ has $\abbre{M}$ type.
 Types are written using small caps.
@@
 
-\item $(φ ≡ φ₁ ∧ φ₂)$. We get a proof for each conjunct and using the introduction rule for conjunction connective, the result follows.
+\item $(φ ≡ φ₁ ∧ φ₂)$. We get a proof for each conjunct and using the
+introduction rule for conjunction connective, the result follows.
 
@@
 
-\begin{definition}[build$_{∨}$]
+\begin{definition}[build$_{\boldsymbol{∨}}$]
 \begin{equation*}
@@
 
-\begin{lemma}[lem-build$_{∨}$]
+\begin{lemma}[lem-build$_{\boldsymbol{∨}}$]
 \label{lem:lem-build-or}
@@
 
-\begin{definition}[sbuild$_{∨}$]
+\begin{definition}[sbuild$_{\boldsymbol{∨}}$]
 \begin{align*}
@@
 
-\begin{lemma}[lem-sbuild$_{∨}$]
+\begin{lemma}[lem-sbuild$_{\boldsymbol{∨}}$]
 \label{lem:lem-sbuild-or}
@@
 
-\begin{definition}[reorder$_{∨}$]
+\begin{definition}[reorder$_{\boldsymbol{∨}}$]
 \begin{align*}
@@
 
-\begin{theorem}[thm-reorder$_{∨}$]
+\begin{theorem}[thm-reorder$_{\boldsymbol{∨}}$]
   \label{thm-reorder-or}
@@
 
-\begin{definition}[reorder$_{∧}$]
+\begin{definition}[reorder$_{\boldsymbol{∧}}$]
   \begin{align*}
@@
 
-\begin{lemma}[lem-reorder$_{∧}$]
+\begin{lemma}[lem-reorder$_{\boldsymbol{∧}}$]
   \label{lem:lem-reorder-and}
@@
 
-\begin{definition}[conjunct$_{∨}$]
+\begin{definition}[conjunct$_{\boldsymbol{∨}}$]
   \label{eq:conjunct-or-definition}
@@
 
-\begin{lemma}[lem-conjunct$_{∨}$]
+\begin{lemma}[lem-conjunct$_{\boldsymbol{∨}}$]
   \label{lem:lem-conjunct-or}
@@
 
-\begin{definition}[reorder$_{∧∨}$]
+\begin{definition}[reorder$_{\boldsymbol{∧∨}}$]
  \begin{align*}
@@
 
-\begin{theorem}[thm-reorder$_{∧∨}$]
+\begin{theorem}[thm-reorder$_{\boldsymbol{∧∨}}$]
   \label{thm:thm-reorder-and-or}
@@
   in which negations appear only in the literals and the expression is
-  in terms only of ($⊥$, $⊤$, $¬$, $∧$, $∨$, $⊻$) connectives.
+  in terms only of ($⊥$, $⊤$, $¬$, $∧$, $∨$, $\overline{\vee}$) connectives.
   The $⊻$ connective is the exclusive disjunction.

### 2017-10-21 paper/sections/proof-reconstruction.tex
[ paper ] working on corrections.

@@
 assistant, \Agda. We choose \Agda, but another proof assistant with the
-same support of type theory and inductive types can be used.
+same support of type theory and inductive types could be used.
 %  (see a description of \Agda for its main features in
@@
 input of the \Metis prover and if the problem is a theorem, \Metis can
-reply a derivation in \TSTP format of the proof.
+reply a derivation of the proof in \TSTP format.
 
 With the \TSTP derivation from Step~2, we process the derivation with the
-\Athena translator tool~\cite{Athena}.
+\Athena translator tool.
 \Athena parses the \TSTP format, analyzes the
@@
 of this tree in Section~\ref{ssec:metis-proofs}).
-We perform an analysis of the proof-tree to remove some
-unnecessary steps that introduce redundancies or unused input for
-\Athena.
-
-As a result of using \Athena, we get an \Agda file, the proof-term. To
-generate this file, \Athena uses names of functions and theorems from
-\Agda libraries:
-\texttt{agda-prop}~\cite{AgdaProp}, and \texttt{agda-metis}~\cite{AgdaMetis}.
+In the \Athena analysis, some unnecessary steps that introduce redundancies
+and some unused input is removed from the proof-tree.
+
+As a result of using \Athena, we get an \Agda file of the proof.
+To generate this file, \Athena uses names of functions and theorems from
+our \Agda libraries: \texttt{agda-prop}, and \texttt{agda-metis}.
 
@@
 % section section_name (end)
-\subsection{Structural Recursion}
+\subsection{Structural recursion}
 \label{ssec:structural-recursion}
@@
 structurally recursive if it calls itself with only
-\emph{structurally smaller}
-arguments.
+structurally smaller arguments.
 
@@
 The new argument is the \emph{bound}, a natural number given by the
-function complexity. In other words, the added argument will store
+function complexity. In other words, the added argument will represent
 the number of times the function needs to call itself to get the
-expected outcome.
-
-Henceforth, a natural number has \Nat type, and it is defined as
-usual, i.e., \zero and \suc are the data constructors and some
-arithmetic operations are defined: ($+,\ -,\ *$). We include syntax
-sugar for $\zero$, $\suc$, $\suc(\zero)$, $\cdots$, with the
-classical representation: $0$, $1$, $2$, $\cdots$ as well.
+expected outcome~\cite{Bertot2004}.
+
+The type of natural numbers is called \Nat type, and it is defined as
+usual, i.e., \zero and \suc are the data constructors. We use names
+and symbols of the arithmetic operations as usual.
+We include syntax sugar for $\zero$, $\suc$, $\suc(\zero)$,
+$\cdots$, with the decimal representation: $0$, $1$, $2$, $\cdots$
+as well.
 
@@
 
-\subsubsection*{A Practical Example.}
-Let us consider the following example to exhibit the technique
-mentioned above for an inner function present in the emulated version
-of the \strip inference.
+\subsubsection*{An  example.}
+Let us consider the following example to exhibit the bounded technique
+mentioned above for the \fuh function presented in the version
+proposed of the \Metis \strip inference.
 
@@
   \label{eq:uh-definition}
-  \begin{split}
-    &\fuh_{0} : \Prop → \Prop\\
-    &\fuh_{0}(φ) =\\
-    &\hspace{3mm}\begin{cases}
-    \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃),
-      & \text{ if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-    \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃),
-      & \text{ if }φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
-    φ, &\text{ otherwise.}
-    \end{cases}
-  \end{split}
+    &\fuh_{0} &&: \Prop → \Prop\\
+    &\fuh_{0}\ (φ₁ ⇒ (φ₂ ⇒ φ₃)) &&= \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃)\\
+    &\fuh_{0}\ (φ₁ ⇒ (φ₂ ∧ φ₃)) &&= \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃)\\
+    &\fuh_{0}\ φ &&= φ
 \end{align}
 
-From the definition above, the size of the argument, $((φ₁ ∧ φ₂) ⇒ φ₃)$,
-is not structurally smaller than the input formula, $(φ₁ ⇒ (φ₂ ⇒ φ₃))$,
-since $((φ₁ ∧ φ₂) ⇒ φ₃)$ is not a subformula of $(φ₁ ⇒ (φ₂ ⇒ φ₃))$.
-
-Thus, we define the function
+From the definition above, the size of the argument, $(φ₁ ∧ φ₂) ⇒ φ₃$,
+is not structurally smaller than the input formula, $φ₁ ⇒ (φ₂ ⇒ φ₃)$,
+since $(φ₁ ∧ φ₂) ⇒ φ₃$ is not a subformula of $φ₁ ⇒ (φ₂ ⇒ φ₃)$.
+
+Therefore, we define the function
 $uh_{1}$ by structural recursion in its second argument in
@@
 As we mentioned above, the natural number in the second argument of
-the function used in Eq.~(\ref{eq:uh-structured}) stands for a
-complexity measure of the function, in this case $uh_{1}$ function.
+the function stands for a complexity measure of it.
 
@@
     \begin{cases}
-    0, &\text{for atomic }φ \\
     \frank(φ₁) + c_{¬},  &\text{ if } φ ≡ \neg φ₁ \\
     \fmax{(\frank(φ₁),\ \frank(φ₂))} + c_{\square},
-      &\text{ if } φ ≡ φ₁\,\square\, φ₂.
-    \end{cases}
-  \end{split}
-\end{align*}
-
-We define the $\fuh_{cm}: \Prop → \NN$ function as
+      &\text{ if } φ ≡ φ₁\,\square\, φ₂.\\
+    0, &\text{ otherwise}
+    \end{cases}
+  \end{split}
+\end{align*}
+
+We define the $\fuh_{cm}: \Prop → \Nat$ function as
 the complexity measure for the $\fuh_0$ function.
@@
 \begin{align*}
-  \label{eq:uh-rank-definition}
   \begin{split}
@@
 
-Finally, following the technique mentioned, we get a curated version of
-$\fuh_{0}$ function presented in Def.~\ref{def:uh}.
+Finally, following the technique mentioned, we get a final version of
+$\fuh_{0}$ function presented in Eq.~(\ref{eq:uh}).
 
@@
   \label{def:uh}
-    \begin{align*}
+    \begin{align}
+      \label{eq:uh}
       \begin{split}
@@
       \end{split}
-    \end{align*}
+    \end{align}
 \end{definition}
@@
 define well-founded and well-structural recursive functions, we refer
-the reader to Ref.~\cite{Bove2005}, where Bove and Capettra described
-not only general recursion, but they also treat mutual recursive
-function, among others.
+the reader to \citeauthor{Bove2005}~\cite{Bove2005}.
 
@@
 
-\subsection{Emulating \Metis' Inference Rules}
+\subsection{Emulating \Metis' inference rules}
 \label{ssec:emulating-inferences}
 
-In this section, we emulate each \Metis inference rule by proving a
-function with the same name, and a associated theorem.
+In this section, we emulate each \Metis inference rule with
+function and its respective theorem.
 The following pattern is used to present the formalization.
-The function name written in bold print
+The function name written in bold face
 is a \Metis inference rule in \TSTP derivations.
-The same function name written in italics refers to its emulated
-version.
-Each emulated rule states a respective theorem that proves its soundness.
+The same function name written in roman letters refers to the proposed
+version of the rule.
+Each rule proposed has a respective theorem also written in roman letters
+that proves its soundness.
 This theorem is named by using the prefix \emph{thm}
@@
 
+For example, we know the \verb!conjunct! inference rule is a
+\Metis inference rule since it appears in \TSTP derivations like
+the following excerpt.
+
+\begin{verbatim}
+fof(normalize_1_2, plain, (p | r),
+    inference(conjunct, [], [normalize_1_1])).
+\end{verbatim}
+
+For this inference rule, we proposed the \rm{conjunct} function in
+Def.~\ref{def:conjunct} and we proved the theorem \rm{thm-conjunct}
+in Thm.~\ref{thm:thm-conjunct}. The pattern is the following for
+a binary rule and we extend it for $n$-ary rules in a natural way.
+
 \begin{itemize}
-\item \texttt{rule} is a $n$-ary \Metis inference rule
-\item $\rm{rule}$ is the emulated version function  for
-the \texttt{rule} inference.
-\begin{align*}
-  \begin{split}
-    &\rm{rule} : \Prop → \Prop → \cdots → \Prop\\
-    &\rm{rule}(φ₁,\ \cdots, φₙ, ψ) =
-      \begin{cases}
-      ψ, &\text{ if }\rm{rule}\text{ built }ψ\text{ by applying valid}\\
-         &\text{ transformations or other rules to }φ\\
-      φ, &\text{ otherwise.}
+\item \texttt{rule} is a binary \Metis inference rule.
+\item $\rm{rule}$ is the proposed function for the \texttt{rule} inference.
+\begin{align*}
+  \begin{split}
+    &\rm{rule} : \Prop → \Prop → \Prop\\
+    &\rm{rule}\ φ₁\ φ₂\ ψ\ =
+      \begin{cases}
+      ψ, &\text{if }\rm{rule}\text{ built }ψ\text{ by applying valid transformations}\\
+         &\text{or other rules to }φ₁\text{ and }φ₂\\
+      φ, &\text{otherwise.}
       \end{cases}
@@
   \item $φᵢ$ are \emph{source} formulas from previous deducted derivations.
-  \item $ψ$ is the \emph{target} formula.
-  The excepted result of \texttt{rule}.
+  \item $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
 \end{itemize}
+\item \rm{thm-rule} is the theorem that proves the soundness of the
+$\rm{rule}$ function.
+\begin{equation*}\text{If }Γ ⊢ φ\text{ then }Γ ⊢ rule\ φ.\end{equation*}
+
 \end{itemize}
@@
 
-\subsubsection{Stripping a Goal.}
+\subsubsection{Stripping a goal.}
 \label{sssec:strip-a-goal}
@@
 \begin{verbatim}
-fof(goal, conjecture, p & r & q).
+fof(goal, conjecture, ((p & r) & q)).
 fof(subgoal_0, plain, p,
@@
   \label{lem:uh}
-  $Γ ⊢ \fuh(φ)$, then $Γ ⊢ φ$.
-\end{lemma}
-
-\begin{sketchproof} Use induction on the cases defined by the outcome of the
+  If $Γ ⊢ \fuh\ φ$ then $Γ ⊢ φ$.
+\end{lemma}
+
+\begin{sketchproof}
+Use induction on the cases defined by the outcome of the
 $\fuh$ function in Eq.~(\ref{eq:uh-structured}).
@@
 \begin{itemize}
-\item $(φ₁ ⇒ (φ₂ ⇒ φ₃))$
+
+\item Case $φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)$.
 \begin{equation*}
@@
   \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
-  \RightLabel{axiom}
+  \RightLabel{by def.}
   \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
@@
 
-\item $(φ₁ ⇒ (φ₂ ∧ φ₃))$
+\item Case $φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)$.
 \begin{equation*}
@@
     \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n)$}
-    \RightLabel{axiom}
+    \RightLabel{by def.}
     \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n-1)$}
@@
     \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₃, n)$}
-    \RightLabel{axiom}
+    \RightLabel{by def.}
     \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₃, n-1)$}
@@
 \label{def:strip}
-  \begin{equation*}
-    \begin{split}
-    &\fstrip : \Prop → \Prop\\
-    &\fstrip(φ) =
-      \begin{cases}
-      \fuh(\fstrip(φ₁)) ∧ \fuh(φ₁ ⇒ \fstrip(φ₂)),
-      &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
-      \fuh(¬ φ₁ ⇒ \fstrip(φ₂)),
-        & \text{ if }φ ≡ φ₁ ∨ φ₂\\
-      \fuh(φ₁ ⇒ \fstrip(φ₂)),
-        & \text{ if }φ ≡ φ₁ ⇒ φ₂\\
-      \fuh(φ₁ ⇒ \fstrip(φ₂)) ∧ \fuh(φ₂ ⇒ \fstrip(φ₁)),
-        & \text{ if }φ ≡ φ₁ ⇔ φ₂\\
-      \fuh(φ₁ ⇒ \fstrip(¬ φ₂)),
-        & \text{ if }φ ≡ ¬ (φ₁ ∧ φ₂)\\
-      \fuh(\fstrip(¬ φ₁)) ∧\ \fuh(¬ φ₁ ⇒ \fstrip(¬ φ₂)),
-        & \text{ if }φ ≡ ¬ (φ₁ ∨ φ₂)\\
-      \fuh(\fstrip(φ₁)) ∧\ \fuh(φ₁ ⇒ \fstrip(¬ φ₂)),
-        & \text{ if }φ ≡ ¬ (φ₁ ⇒ φ₂)\\
-      \fuh(φ₁ ⇒ \fstrip(¬ φ₂)) ∧\ \fuh(¬ φ₂ ⇒ \fstrip(φ₁)),
-        & \text{ if }φ ≡ ¬ (φ₁ ⇔ φ₂)\\
-      \fuh(\fstrip(φ₁)),
-        & \text{ if }φ ≡ ¬ ¬ φ₁\\
-      ⊤,
-        & \text{ if }φ ≡ ¬ ⊥\\
-      ⊥,
-        & \text{ if }φ ≡ ¬ ⊤.\\
-      φ, &\text{ otherwise}.
-      \end{cases}
-    \end{split}
-  \end{equation*}
-\end{definition}
-
-The definition above has termination problems since it is not
-a structural recursion. Therefore, we have reformulated the equation
-above to solve such an issue following the technique
-described in Section~\ref{ssec:structural-recursion}.
-We refer to $\fstrip$ as the function after applying the process mentioned
-above here and below unless otherwise stated.
-
-\begin{lemma}[lem-inv-strip] $Γ ⊢ \fstrip(φ)$ then $Γ ⊢ φ$.
+  \begin{align}
+  \label{eq:strip}
+    &\fstrip &&: \Prop → \Nat → \Prop\\
+    &\fstrip\ (φ₁ ∧ φ₂)\ n     &&= \fuh\ (\fstrip\ φ₁) ∧ \fuh\ (φ₁ ⇒ \fstrip\ φ₂)\\
+    &\fstrip\ (φ₁ ∨ φ₂)\ n     &&= \fuh\ (¬ φ₁ ⇒ \fstrip\ φ₂)\\
+    &\fstrip\ (φ₁ ⇒ φ₂)\ n     &&= \fuh\ (φ₁ ⇒ \fstrip\ φ₂)\\
+    &\fstrip\ (φ₁ ⇔ φ₂)\ n     &&= \fuh\ φ₁ ⇒ \fstrip\ φ₂) ∧ \fuh\ φ₂ ⇒ \fstrip φ₁)\\
+    &\fstrip\ (¬ (φ₁ ∧ φ₂))\ n &&= \fuh\ φ₁ ⇒ \fstrip(¬ φ₂))\\
+    &\fstrip\ (¬ (φ₁ ∨ φ₂))\ n &&= \fuh\ \fstrip(¬ φ₁)) ∧\ \fuh ¬ φ₁ ⇒ \fstrip(¬ φ₂))\\
+    &\fstrip\ (¬ (φ₁ ⇒ φ₂))\ n &&= \fuh\ \fstrip(φ₁)) ∧\ \fuh φ₁ ⇒ \fstrip(¬ φ₂))\\
+    &\fstrip\ (¬ (φ₁ ⇔ φ₂))\ n &&= \fuh\ φ₁ ⇒ \fstrip(¬ φ₂)) ∧\ \fuh ¬ φ₂ ⇒ \fstrip(φ₁))\\
+    &\fstrip\ (¬ ¬ φ₁)\ n      &&= \fuh\ \fstrip(φ₁))\\
+    &\fstrip\ (¬ ⊥)\ n         &&= ⊤\\
+    &\fstrip\ (¬ ⊤.)\ n        &&= ⊥\\
+    &\fstrip\ φ\ n             &&= φ
+  \end{align}
+\end{definition}
+
+% The definition above has termination problems since it is not
+% a structural recursion. Therefore, we have reformulated the equation
+% above to solve such an issue following the technique
+% described in Section~\ref{ssec:structural-recursion}.
+% We refer to $\fstrip$ as the function after applying the process mentioned
+% above here and below unless otherwise stated.
+
+\begin{lemma}[lem-inv-strip]
+If $Γ ⊢ \fstrip\ φ$ then $Γ ⊢ φ$.
 \label{lem:lem-inv-strip}
@@
 The proof is by induction on the structure of the
-formula $φ$ by following the cases in Def.~\ref{def:strip}.
+formula~$φ$ by following the cases in Eq.~(\ref{eq:strip}).
 We present some cases but for a complete proof, we refer the reader to~\cite{AgdaMetis}.
@@
 \begin{itemize}
-\item $(φ ≡ ¬ ¬ φ₁)$
-\begin{equation*}
+\item Case $φ ≡ ¬ ¬ φ₁$.
+\begin{equation*}
+  \begin{bprooftree}
+ \AxiomC{$Γ ⊢ \fstrip(¬¬φ₁,n)$}
+  \RightLabel{by def.}
+  \UnaryInfC{$Γ ⊢ \fuh(\fstrip(φ₁,n-1))$}
+  \RightLabel{lem-inv-uh}
+  \UnaryInfC{$Γ ⊢ \fstrip(φ₁,n-1)$}
+  \RightLabel{lem-inv-strip}
+  \UnaryInfC{$Γ ⊢ φ₁$}
+  \end{bprooftree}
+\end{equation*}
+
+\item Case $φ ≡ φ₁ ∧ φ₂$. We get a proof for each conjunct and using the
+introduction rule for conjunction connective, the result follows.
+
+\begin{equation*}
+(\mathcal{D})\hspace{3mm}
   \begin{bprooftree}
   \AxiomC{$Γ ⊢ \fstrip(φ,n)$}
-  \RightLabel{axiom}
-  \UnaryInfC{$Γ ⊢ \fuh(\fstrip(¬¬φ₁,n-1))$}
-  \RightLabel{lem-inv-uh}
-  \UnaryInfC{$Γ ⊢ \fstrip(¬¬φ₁,n-1)$}
-  \RightLabel{lem-inv-strip}
-  \UnaryInfC{$Γ ⊢ ¬¬φ₁$}
-  \RightLabel{axiom.}
-  \UnaryInfC{$Γ ⊢ φ$}
-  \end{bprooftree}
-\end{equation*}
-
-\item $(φ ≡ φ₁ ∧ φ₂)$. We get a proof for each conjunct and using the
-introduction rule for conjunction connective, the result follows.
-
-\begin{equation*}
-(\mathcal{D})\hspace{3mm}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \fstrip(φ,n)$}
-  \RightLabel{axiom}
+  \RightLabel{by def.}
   \UnaryInfC{$Γ ⊢ \fuh(φ₁) ∧ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
@@
   \AxiomC{$Γ ⊢ \fstrip(φ,n)$}
-  \RightLabel{axiom}
+  \RightLabel{by def.}
   \UnaryInfC{$Γ ⊢ \fuh(φ₁) ∧ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
@@
 
-\item $(φ ≡ φ₁ ⇒ φ₂)$
+\item Case $φ ≡ φ₁ ⇒ φ₂$.
 \begin{equation*}
@@
   \AxiomC{$Γ ⊢ \fstrip(φ,n-1)$}
-  \RightLabel{axiom}
+  \RightLabel{by def.}
   \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
@@
 
-\item $(φ ≡ ¬ (φ₁ ∨ φ₂))$. We show that $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
+\item Case $φ ≡ ¬ (φ₁ ∨ φ₂)$. We show that $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
 The result follows by introducing the conjunction and applying
@@
 \AxiomC{$Γ ⊢ \fstrip(φ, n)$}
-\RightLabel{axiom}
+\RightLabel{by def.}
 \UnaryInfC{$Γ ⊢ \fuh(¬ φ₁) ∧ \fuh(¬ φ₁ ⇒ \fstrip(φ₂, n))$}
@@
   \AxiomC{$Γ ⊢ \fstrip(φ,n-1)$}
-  \RightLabel{axiom}
+  \RightLabel{by def.}
   \UnaryInfC{$Γ ⊢ \fuh(¬ φ₁) ∧ \fuh(¬ φ₁ ⇒ \fstrip(φ₂,n-1))$}
@@
 
-We can now formulate our main result of this part that
-justifies the stripping strategy of \Metis to prove goals.
+We can now formulate the result that justifies the stripping strategy
+of \Metis to prove goals.
 
@@
 
-\subsubsection{Negating Subgoals.}
+\subsubsection{Negating subgoals.}
 
@@
 
-\subsubsection{Splitting a Conjunct.}
+\subsubsection{Splitting a conjunct.}
 \label{sssec:splitting-a-conjunct}
@@
 \begin{definition}[conjunct]
+  \label{def:conjunct}
   \begin{align*}
@@
   \label{thm:thm-conjunct}
-  $Γ ⊢ φ$, and $ψ  : \Prop$ , then $Γ ⊢ \fconjunct(φ, ψ)$.
+  If $Γ ⊢ φ$ and $ψ  : \Prop$ then $Γ ⊢ \fconjunct(φ, ψ)$.
 \end{theorem}
@@
 \label{lem:lem-rdisj}
-  $Γ ⊢ φ$ then $Γ ⊢ \rm{rdisj}(φ)$.
+  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rdisj}(φ)$.
 \end{lemma}
@@
 \label{lem:lem-build-or}
-$Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}(φ)$.
+If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}(φ)$.
 \end{lemma}
@@
 \label{lem:lem-sbuild-or}
-$Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}(φ, ψ)$.
+If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}(φ, ψ)$.
 \end{lemma}
@@
 
-Notice that using $\rm{sbuild}_{∨}$ we can build not only a disjunction with the same disjuncts of the source formula but also a complete different formula by adding new disjuncts to the source formula.
+Notice that using $\rm{sbuild}_{∨}$ we can build not only a disjunction
+with the same disjuncts of the source formula but also a complete different
+formula by adding new disjuncts to the source formula.
 
@@
     \begin{split}
-    &\rm{reorder}_{∨} : \Prop \to \Prop \to \Prop\\
-    &\rm{reorder}_{∨} (φ, ψ) = \rm{sbuild}_{∨}(rdisj(φ), ψ).
+    &\freorder_{∨} : \Prop \to \Prop \to \Prop\\
+    &\freorder_{∨} (φ, ψ) = \rm{sbuild}_{∨}(rdisj(φ), ψ).
     \end{split}
@@
   \label{thm-reorder-or}
-  $Γ ⊢ φ$, and $ψ: \Prop$ then $Γ ⊢ \rm{reorder}_{∨}(φ, ψ)$.
+  If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}(φ, ψ)$.
 \end{theorem}
@@
 
-We define similar functions and state some theorems as we previously did for disjunctions, but instead, we treat only with conjunctive normal forms.
+We define similar functions and state some theorems as we previously did
+for disjunctions, but instead, we treat only with conjunctive normal forms.
 
@@
       \begin{split}
-        &\rm{reorder}_{∧} : \Prop → \Prop \to \Prop\\
-        &\rm{reorder}_{∧}(φ, ψ) =
+        &\freorder_{∧} : \Prop → \Prop \to \Prop\\
+        &\freorder_{∧}(φ, ψ) =
         \begin{cases}
           φ, &\text{ if }φ ≡ ψ\\
-          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\rm{reorder}_{∧}(φ, ψ₁) ≡ ψ₁\\
-                  &\text{and }\rm{reorder}_{∧}(φ, ψ₂)≡ ψ₂\\
+          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\freorder_{∧}(φ, ψ₁) ≡ ψ₁\\
+                  &\text{and }\freorder_{∧}(φ, ψ₂)≡ ψ₂\\
           φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
-          \rm{conjunct}(φ, ψ), &\text{ otherwise.}
+          \fconjunct(φ, ψ), &\text{ otherwise.}
         \end{cases}
@@
   \label{lem:lem-reorder-and}
-  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ \rm{reorder}_{∧}(φ, ψ)$.
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}(φ, ψ)$.
 \end{lemma}
@@
   \label{lem:lem-conjunct-or}
-  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}(φ, ψ)$.
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}(φ, ψ)$.
 \end{lemma}
@@
   \label{thm:thm-reorder-and-or}
-  $Γ ⊢ φ$, and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$.
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$.
 \end{theorem}
@@
   \label{lem:lem-rsol}
-  $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}(φ)$.
+  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}(φ)$.
 \end{lemma}
@@
   \label{thm:thm-resolve}
-  $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ: \Prop$ then
+  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ : \Prop$ then
   $Γ ⊢ \fresolve(φ₁, φ₂, l, ψ)$.
@@
   in which negations appear only in the literals and the expression is
-  in terms only of ($⊥$, $⊤$, $¬$, $∧$, $∨$, $\overline{\vee}$) connectives.
-  The $⊻$ connective is the exclusive disjunction.
+  in terms only of ($⊥$, $⊤$, $¬$, $∧$, $∨$) connectives.
   We define the \NProp type in a similar way as we did for \Prop type.
@@
     \begin{bprooftree}
-      \AxiomC{$φ ∧ ⊥$}
-      \UnaryInfC{$⊥$}
+      \AxiomC{$Γ ⊢ φ ∧ ⊥$}
+      \UnaryInfC{$Γ ⊢ ⊥$}
     \end{bprooftree}
@@
     \begin{bprooftree}
-      \AxiomC{$φ ∧ ⊤$}
-      \UnaryInfC{$φ$}
+      \AxiomC{$Γ ⊢ φ ∧ ⊤$}
+      \UnaryInfC{$Γ ⊢ φ$}
     \end{bprooftree}
@@
     \begin{bprooftree}
-      \AxiomC{$φ ∧ ¬ φ$}
-      \UnaryInfC{$⊥$}
+      \AxiomC{$Γ ⊢ φ ∧ ¬ φ$}
+      \UnaryInfC{$Γ ⊢ ⊥$}
     \end{bprooftree}
@@
     \begin{bprooftree}
-      \AxiomC{$φ ∧ φ$}
-      \UnaryInfC{$φ$}
+      \AxiomC{$Γ ⊢ φ ∧ φ$}
+      \UnaryInfC{$Γ ⊢ φ$}
     \end{bprooftree}
@@
     \begin{bprooftree}
-      \AxiomC{$φ ∨ ⊥$}
-      \UnaryInfC{$φ$}
+      \AxiomC{$Γ ⊢ φ ∨ ⊥$}
+      \UnaryInfC{$Γ ⊢ φ$}
     \end{bprooftree}
@@
     \begin{bprooftree}
-      \AxiomC{$φ ∨ ⊤$}
-      \UnaryInfC{$⊤$}
+      \AxiomC{$Γ ⊢ φ ∨ ⊤$}
+      \UnaryInfC{$Γ ⊢ ⊤$}
     \end{bprooftree}
@@
     \begin{bprooftree}
-      \AxiomC{$φ ∨ ¬ φ$}
-      \UnaryInfC{$⊤$}
+      \AxiomC{$Γ ⊢ φ ∨ ¬ φ$}
+      \UnaryInfC{$Γ ⊢ ⊤$}
     \end{bprooftree}
@@
     \begin{bprooftree}
-      \AxiomC{$φ ∨ φ$}
-      \UnaryInfC{$φ$}
+      \AxiomC{$Γ ⊢ φ ∨ φ$}
+      \UnaryInfC{$Γ ⊢ φ$}
     \end{bprooftree}
@@
     \begin{split}
-      &\rm{rm}_{∨} :  \NProp \to \NProp\\
-      &\rm{rm}_{∨}(φ) =
-      \begin{cases}
-        \rm{rm}_{∨}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
+      &\frm_{∨} :  \NProp \to \NProp\\
+      &\frm_{∨}(φ) =
+      \begin{cases}
+        \frm_{∨}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
         φ₁ ∨ rm_{∨}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂\\
@@
   \label{lem:lem_rm-or}
-  $Γ ⟝ φ$ then $Γ ⟝ \rm{rm}_{∨}(φ)$.
+  If $Γ ⟝ φ$ then $Γ ⟝ \frm_{∨}(φ)$.
 \end{lemma}
@@
 Now, we have removed redundancies in the disjunctions by applying
-$\rm{rm}_{∨}$ function, we can define a similar function to work with
-conjunctions, i.e., $\rm{rm}_{∧}$.
+$\frm_{∨}$ function, we can define a similar function to work with
+conjunctions, i.e., $\frm_{∧}$.
 
@@
     \begin{split}
-    &\rm{rm}_{∧} : \NProp \to \NProp\\
-    &\rm{rm}_{∧}(φ) =
+    &\frm_{∧} : \NProp \to \NProp\\
+    &\frm_{∧}(φ) =
     \begin{cases}
@@
   \label{lem:lem_rm-and}
-  $Γ ⟝ φ$ then $Γ ⟝ \rm{rm}_{∧}(φ)$.
+  If $Γ ⟝ φ$ then $Γ ⟝ \frm_{∧}(φ)$.
 \end{lemma}
@@
   \label{lem:lem_ndisj-or}
-  $Γ ⟝ φ$ then $Γ ⟝ \rm{ndisj}_{∨}(φ)$.
+  If $Γ ⟝ φ$ then $Γ ⟝ \rm{ndisj}_{∨}(φ)$.
 \end{lemma}
@@
   \label{lem:lem_ndisj-and}
-  $Γ ⟝ φ$ then $Γ ⟝ \rm{ndisj}_{∧}(φ)$.
+  If $Γ ⟝ φ$ then $Γ ⟝ \rm{ndisj}_{∧}(φ)$.
 \end{lemma}
@@
 We use the functions defined above to remove redundancies in conjunctions
-with $\rm{canon}_{∧}$ function, and $\rm{canon}_{∨}$ function to remove redundancies
+with $\fcanon_{∧}$ function, and $\fcanon_{∨}$ function to remove redundancies
 in disjunctions.
@@
     \begin{split}
-      &\rm{canon}_{∧} : \NProp \to \NProp\\
-      &\rm{canon}_{∧}(φ) =
+      &\fcanon_{∧} : \NProp \to \NProp\\
+      &\fcanon_{∧}(φ) =
         \begin{cases}
@@
           ⊥,  &\text{ if } φ ≡ φ₁ ∧ φ₂,\ φᵢ ≡ ⊥,\text{ for } i,j = 1,2\\
-          \rm{rm}_∧(\rm{ndisj}_∧(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
+          \frm_∧(\rm{ndisj}_∧(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
           φ,                &\text{ otherwise.}
@@
   \label{lem:lem_canon-and}
-  $Γ ⟝ φ$ then $Γ ⟝ \rm{canon}_{∧}(φ)$.
+  If $Γ ⟝ φ$ then $Γ ⟝ \fcanon_{∧}(φ)$.
 \end{lemma}
@@
     \begin{split}
-      &\rm{canon}_{∨} : \NProp \to \NProp\\
-      &\rm{canon}_{∨}(φ) =
+      &\fcanon_{∨} : \NProp \to \NProp\\
+      &\fcanon_{∨}(φ) =
         \begin{cases}
@@
         ⊤,  &\text{ if } φ ≡ φ₁ ∨ φ₂,\ φᵢ ≡ ⊤,\text{ for } i,j = 1,2\\
-        \rm{rm}_∨(\rm{ndisj}_∨(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
+        \frm_∨(\rm{ndisj}_∨(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
         φ, &\text{ otherwise.}
@@
   \label{lem:lem_canon-or}
-  $Γ ⟝ φ$ then $Γ ⟝ \rm{canon}_{∨}(φ)$.
-\end{lemma}
-
-\begin{remark}
-A similar treatment defines the $\rm{canon}_{⊻} : \NProp \to \NProp$.
-This function removes redundancies related with the exclusive
-disjunction connective.
-% Its theorem, thm-canon$_{⊻}$ is presented in~\cite{AgdaMetis}.
-We left out this description for the brevity of this
-document and refer the interested reader to \cite{AgdaMetis} for
-more details.
-\end{remark}
+  If $Γ ⟝ φ$ then $Γ ⟝ \fcanon_{∨}(φ)$.
+\end{lemma}
+
+% \begin{remark}
+% A similar treatment defines the $\fcanon_{⊻} : \NProp \to \NProp$.
+% This function removes redundancies related with the exclusive
+% disjunction connective.
+% % Its theorem, thm-canon$_{⊻}$ is presented in~\cite{AgdaMetis}.
+% We left out this description for the brevity of this
+% document and refer the interested reader to \cite{AgdaMetis} for
+% more details.
+% \end{remark}
 
 Finally, we can translate formulas from \Prop to \NProp by defining
-the $\rm{nnf}₀$ function. This function is based on the $\rm{nnf}$ function described in
-\citeauthor{Bezem2002}~\cite{Bezem2002}. Their $\rm{nnf}$ function
+the $\fnnf₀$ function. This function is based on the $\fnnf$ function described in
+\citeauthor{Bezem2002}~\cite{Bezem2002}. Their $\fnnf$ function
 translates formulas to their classical negative normal form. In the
@@
     \begin{split}
-    &\rm{nnf₀} : \abbre{Polarity} \to \Prop \to \NProp\\
-    &\rm{nnf₀}(⊕, φ) =
-      \begin{cases}
-      \rm{canon}_{∧}(\rm{nnf₀}(⊕, φ₁) ∧ \rm{nnf₀}(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
-      \rm{canon}_{∨}(\rm{nnf₀}(⊕, φ₁) ∨ \rm{nnf₀}(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
-      \rm{canon}_{∨}(\rm{nnf₀}(⊖, φ₁) ∨ \rm{nnf₀}(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
-      \rm{canon}_{⊻}(\rm{nnf₀}(⊖, φ₁) ⊻ \rm{nnf₀}(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ⇔ φ₂ \\
-      \rm{nnf₀}(⊖, φ₁),                          &\text{ if }φ ≡ ¬ φ₁ \\
+    &\fnnf₀ : \abbre{Polarity} \to \Prop \to \NProp\\
+    &\fnnf₀(⊕, φ) =
+      \begin{cases}
+      \fcanon_{∧}(\fnnf₀(⊕, φ₁) ∧ \fnnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
+      \fcanon_{∨}(\fnnf₀(⊕, φ₁) ∨ \fnnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
+      \fcanon_{∨}(\fnnf₀(⊖, φ₁) ∨ \fnnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
+      \fnnf₀(⊖, φ₁),                              &\text{ if }φ ≡ ¬ φ₁ \\
       φ,                                          &\text{ otherwise.} \\
       \end{cases}\\
-    &\rm{nnf₀}(⊖, φ) =
-      \begin{cases}
-      \rm{canon}_{∨}(\rm{nnf₀}(⊖, φ₁) ∨ \rm{nnf₀}(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
-      \rm{canon}_{∧}(\rm{nnf₀}(⊖, φ₁) ∧ \rm{nnf₀}(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
-      \rm{canon}_{∧}(\rm{nnf₀}(⊖, φ₂) ∧ \rm{nnf₀}(⊖, φ₁)),  &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
-      \rm{canon}_{⊻}(\rm{nnf₀}(⊕, φ₁) ⊻ \rm{nnf₀}(⊕, φ₂)),  &\text{ if }φ ≡ φ₁ ⇔ φ₂ \\
-      \rm{nnf₀}(⊕, φ₁),                           &\text{ if }φ ≡ ¬ φ₁ \\
+    &\fnnf₀(⊖, φ) =
+      \begin{cases}
+      \fcanon_{∨}(\fnnf₀(⊖, φ₁) ∨ \fnnf₀(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
+      \fcanon_{∧}(\fnnf₀(⊖, φ₁) ∧ \fnnf₀(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
+      \fcanon_{∧}(\fnnf₀(⊖, φ₂) ∧ \fnnf₀(⊖, φ₁)),  &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
+      \fnnf₀(⊕, φ₁),                               &\text{ if }φ ≡ ¬ φ₁ \\
       ⊥,                                           &\text{ if }φ ≡ ⊤ \\
@@
   \label{lem:lem-nnf}
-  $Γ ⊢ φ$ then $Γ ⟝ \rm{nnf}(φ)$ where,
-  \begin{align*}
-   \begin{split}
-     &\rm{nnf} : \NProp \to \NProp\\
-     &\rm{nnf}(φ) = \rm{nnf}₀(⊕, φ).
+  If $Γ ⊢ φ$ then $Γ ⟝ \fnnf(φ)$ where,
+  \begin{align*}
+   \begin{split}
+     &\fnnf : \NProp \to \NProp\\
+     &\fnnf(φ) = \fnnf₀(⊕, φ).
    \end{split}
@@
   \label{lem:lem-dist-or}
-  $Γ ⟝ φ$ then $Γ ⟝ \rm{dist}_{∨}(φ)$, where,
-  \begin{align*}
-    \begin{split}
-    &\rm{dist}_{∨} : \Prop \to \Prop\\
-    &\rm{dist}_{∨}(φ) =
-      \begin{cases}
-        \rm{dist}_{∨}(φ₁ ∨ φ₂) ∧ \rm{dist}_{∨}(φ₂ ∨ φ₃), &\text{ if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
-        \rm{dist}_{∨}(φ₁ ∨ φ₃) ∧ \rm{dist}_{∨}(φ₁ ∨ φ₃), &\text{ if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
+  $Γ ⟝ φ$ then $Γ ⟝ \fdist_{∨}(φ)$, where,
+  \begin{align*}
+    \begin{split}
+    &\fdist_{∨} : \Prop \to \Prop\\
+    &\fdist_{∨}(φ) =
+      \begin{cases}
+        \fdist_{∨}(φ₁ ∨ φ₂) ∧ \fdist_{∨}(φ₂ ∨ φ₃), &\text{ if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
+        \fdist_{∨}(φ₁ ∨ φ₃) ∧ \fdist_{∨}(φ₁ ∨ φ₃), &\text{ if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
         φ,                                     &\text{ otherwise.}
@@
   \label{lem:lem-dist}
-  $Γ ⟝ φ$ then $Γ ⟝ \rm{dist}(φ)$, where,
-  \begin{align*}
-      \begin{split}
-      &\rm{dist} : \Prop \to \Prop\\
-      &\rm{dist}(φ) =
-        \begin{cases}
-          \rm{dist}(φ₁) ∧ \rm{dist}(φ₂),
+  $Γ ⟝ φ$ then $Γ ⟝ \fdist(φ)$, where,
+  \begin{align*}
+      \begin{split}
+      &\fdist : \Prop \to \Prop\\
+      &\fdist(φ) =
+        \begin{cases}
+          \fdist(φ₁) ∧ \fdist(φ₂),
             &\text{ if }φ ≡ φ₁ ∧ φ₂\\
-          \rm{dist}_{∨}(\rm{dist}(φ₁) ∨ \rm{dist}(φ₂)),
+          \fdist_{∨}(\fdist(φ₁) ∨ \fdist(φ₂)),
             &\text{ if }φ ≡ φ₁ ∨ φ₂\\
@@
     \RightLabel{lem-dist}
-    \UnaryInfC{$Γ ⊢ \rm{dist}(φ_{i})$}
+    \UnaryInfC{$Γ ⊢ \fdist(φ_{i})$}
     \RightLabel{∨-intro$_{1,2}$}
-    \UnaryInfC{$Γ, φ_{i} ⊢ \rm{dist}(φ₁) ∨ \rm{dist}(φ₂)$}
+    \UnaryInfC{$Γ, φ_{i} ⊢ \fdist(φ₁) ∨ \fdist(φ₂)$}
     \RightLabel{lem-dist$_{∨}$.}
-    \UnaryInfC{$Γ, φ_{i} ⊢ \rm{dist}_{∨}(\rm{dist}(φ₁) ∨ \rm{dist}(φ₂))$}
+    \UnaryInfC{$Γ, φ_{i} ⊢ \fdist_{∨}(\fdist(φ₁) ∨ \fdist(φ₂))$}
     \end{bprooftree}
@@
 Then, by using the ∨-elim rule in the last derivation above, we
-derive $Γ, φ₁ ∨ φ₂ ⟝ \rm{dist}_{∨}(\rm{dist}(φ₁) ∨ \rm{dist}(φ₂))$ and the lemma
+derive $Γ, φ₁ ∨ φ₂ ⟝ \fdist_{∨}(\fdist(φ₁) ∨ \fdist(φ₂))$ and the lemma
 follows.
@@
         \rm{form}_{⊻}(φ₂),        &\text{ if }φ ≡ φ₁ ⊻ φ₂\\
-        % ⊥, &\text{ if }φ ≡ ⊥\\
-        % ⊤, &\text{ if }φ ≡ ⊤\\
         φ, &\text{ otherwise.}\\
@@
   \label{lem:lem-form}
-   $Γ ⟝ φ$ then $Γ ⊢ \rm{form}(φ)$.
+   If $Γ ⟝ φ$ then $Γ ⊢ \rm{form}(φ)$.
 \end{lemma}
@@
 \label{thm:thm-cnf}
-  $Γ ⊢ φ$ then $Γ ⊢ \rm{cnf}(φ)$, where,
+  If $Γ ⊢ φ$ then $Γ ⊢ \rm{cnf}(φ)$, where,
   \begin{align*}
@@
     &\rm{cnf} : \Prop \to \Prop\\
-    &\rm{cnf} = \rm{form} ∘ \rm{dist} ∘ \rm{nnf}.
+    &\rm{cnf} = \rm{form} ∘ \fdist ∘ \fnnf.
     \end{split}
@@
 \begin{proof}
-  Composition of the Lemmas \ref{lem:lem-form}, \ref{lem:lem-dist} and \ref{lem:lem-nnf}.
+  Composition of the Lemmas \ref{lem:lem-form}, \ref{lem:lem-dist}
+  and \ref{lem:lem-nnf}.
 \end{proof}
@@
 \label{thm:thm-inv-cnf}
-  $Γ ⊢ \rm{cnf}(φ)$ then $Γ ⊢ φ$.
+  If $Γ ⊢ \rm{cnf}(φ)$ then $Γ ⊢ φ$.
 \end{theorem}
@@
 normalization of the proposition input.
-%This rule can introduce axioms and definitions into the problem solution.
 This rule converts a \texttt{fof} %TODO
@@
   \hspace{4mm}\\
-  $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fcanonicalize(φ, ψ)$.
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fcanonicalize(φ, ψ)$.
 \end{theorem}
@@
 \end{equation*}
+
 \item If $γ = \fcnf(ψ) ≡ \freorder_{∧∨}(\fcnf(φ), \fcnf(ψ))$,
@@
 % -------------------------------------------------------------------
-
-% --------------------------------------------------------------------
 
@@
         γ,          &\text{ if }φᵢ ≡ γ ⇒ \fnnf(¬ φⱼ)\\
-        γ,          &\text{ if }φᵢ ≡ φⱼ ⇔ γ \\
-        \fnnf(¬ γ), &\text{ if }φᵢ ≡ \fnnf(¬ φⱼ) ⇔ γ \\
         γ,          &\text{ if }φᵢ ≡ \fnnf(¬ φⱼ) ∨ γ\\
@@
 %   \BinaryInfC{$Γ ⊢ ⊥$}
-%   \RightLabel{axiom}
+%   \RightLabel{by def.}
 %   \UnaryInfC{$Γ ⊢ simplify(φ₁, φ₂, ψ)$}

### 2017-10-21 paper/sections/metis-language-and-proofs.tex
[ paper ] working on corrections.
[ paper ] putting some order...

@@
 to justify its deduction steps from the basis of only six inference
-rules.
-In Fig.~\ref{fig:metis-inferences}, we show the three \Metis rules for
-propositional logic.
+rules. In Fig.~\ref{fig:metis-inferences}, we show the three \Metis
+rules for propositional logic.
 
@@
 
-\subsection{Input Language.}
+\subsection{Input language}
 \label{ssec:input-language}
@@
 \name{conjecture}, \name{definition}, or a \name{hypothesis}.
-%existen otros
-%----Keywords:    fof cnf thf tff include
-%----Punctuation: ( ) , . [ ] :
-%----Operators:   ! ? ~ & | <=> => <= <~> ~| ~& * +
-%----Predicates:  = != $true $false
-
-%----Top of Page---------------------------------------------------------------
-%----CNF formulae (variables implicitly universally quantified)
-% <cnf_formula>          ::= <disjunction> | (<disjunction>)
-% <disjunction>          ::= <literal> | <disjunction> <vline> <literal>
-% <literal>              ::= <fof_atomic_formula> | ~ <fof_atomic_formula> |
-%                            <fof_infix_unary>
-The formulas include the binary Boolean connectives
-(\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!, \verb!~!) and logic constants \verb!$true!
-% the boolean type ($true and $false)
-and \verb!$false!, for the symbols (∧, ∨, ⇒, ⇔, ¬, ⊤, ⊥), respectively.
+The formulas include the binary connectives
+(\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!, \verb!~!)
+and the constants \verb!$true!, and \verb!$false!.
 
@@
 
-This study aimed to address proof-reconstruction for refutation
-proofs. Then, we annotated \abbre{CPL} problems using \verb!fof! formulas.
-\Metis converts \abbre{FOF} formulas to \abbre{CNF} clauses to look for a
-refutation.
-
-\subsection{Output Language.}
+\subsection{Output language}
 \label{ssec:output-language}
 
-The \TSTP language is de facto output standard language
-for derivations of ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006,Sicard-Ramirez2016}.
+The \TSTP language is an output language for derivations of
+ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006,Sicard-Ramirez2016}.
 A \TSTP derivation is a directed acyclic graph, a proof tree,
@@
 inferred from the parent formulas. The root is the final derived formula,
-such a derivation is a list of annotated formulas with the form.
+such a derivation is a list of annotated formulas with the following form.
 
@@
 
-The \name{rule} stands for the inference name; the other fields are
-supporting arguments or useful information to apply the reasoning
-step, and the list of parents nodes.
+The \name{rule} in the line above stands for the inference name;
+the other fields are supporting arguments or useful information to
+apply the reasoning step, and list the parents nodes.
 
@@
 In the script above, \strip is for example the name of the inference.
-It has no arguments and derives from one parent node with goal name.
-\name{goal}.
+It has no arguments and derives from one parent node named goal. The
+result of this inference when it applies to the \verb!goal! formula is
+\verb!p!.
 
@@
 
-\subsection{Inference Rules.}
+\subsection{Inference rules}
 \label{ssec:metis-inferences-rules}
@@
 
-Finally, \emph{axiom} rule appears in \TSTP derivations by using one of the following rules: \canonicalize, \clausify, \conjunct, or \simplify.
-Then, the last rule remains is \emph{resolve}, it
-appears by the binary rule, \resolve, the version in \Metis of the resolution
-theorem. For a more detailed description of this rules see Section~\ref{sec:proof-reconstruction}.
+% Finally, \emph{axiom} rule appears in \TSTP derivations by using one of the following rules: \canonicalize, \clausify, \conjunct, or \simplify.
+% Then, the last rule remains is \emph{resolve}, it
+% appears by the binary rule, \resolve, the version in \Metis of the resolution
+% theorem. For a more detailed description of this rules see Section~\ref{sec:proof-reconstruction}.
 
-\subsection{Proofs.}
+\subsection{Proofs}
 \label{ssec:metis-proofs}
@@
 
-\begin{figure}
+The output of a proof delivered by \Metis encodes a natural
+deduction proof (see a complete proof in Fig.~\ref{fig:metis-proof-tstp}.
+The deduction system uses six inference rules \cite{hurd2003first}.
+With these inference rules as the only valid deduction steps, \Metis
+attempts to prove conjectures by refutation (e.g.,
+\emph{falsium} in the last conclusion in the \TSTP derivation
+Fig.~\ref{fig:metis-proof-tstp}).
+
+These proofs are directed acyclic graphs, trees of refutations
+(see the proof tree of the \TSTP derivation showed above in
+Fig.~\ref{fig:metis-proof-tstp}).
+Each node stands for an application of an inference rule and the leaves
+in the tree represent formulas in the given problem. Each node is
+labeled with a name of the inference rule (e.g., \canonicalize).
+Each edge links a premise with one conclusion.
+The proof graphs have at their root the conclusion
+$⊥$, since \Metis delivers proofs by refutation.
+
+\begin{figure}[!ht]
 \centering
@@
   \end{bprooftree}
-  \caption{\Metis' proof tree for $p \vdash p$. Derivation in Fig.~\ref{fig:metis-proof-tstp}}
+  \caption{Proof tree for the \Metis derivation in
+  Fig.~\ref{fig:metis-proof-tstp}}.
   \label{fig:metis-example}
@@
 
-The output of a proof delivered by \Metis encodes a natural
-deduction proof. The deduction system uses six inference rules
-\cite{hurd2003first} listed in Fig.~\ref{fig:metis-inferences}.
-With these inference rules as the only valid deduction steps, \Metis
-attempts to prove conjectures by refutation (e.g.,
-\emph{falsium} in the last conclusion of the \TSTP derivation in
-Fig.~\ref{fig:metis-example}).
-
-These proofs are directed acyclic graphs, trees of refutations. Each
-node stands for an application of an inference rule and the leaves
-in the tree represent formulas in the given problem. Each node is
-labeled with a name of the inference rule (e.g., \canonicalize in
-Fig.~\ref{fig:metis-example}). Each edge links a premise with one
-conclusion. The proof graphs have at their root the conclusion
-$⊥$, since \Metis delivers proofs by refutation.
-
 \end{document}

### 2017-10-21 paper/sections/proof-reconstruction.tex
[ paper ] putting some order...

@@
 success, the \TSTP derivation delivered by \Metis is correct
-module \Agda and the formalizations of \Metis inferences.
-
+module \Agda and the proposed formalizations for the
+propositional logic and the \Metis inferences.
 In that case \Agda outputs an interface file.
+
 Otherwise, when type-checking fails, the failure must be
-investigated by the user, checking for the error in \Metis, \Athena,
-or in \Agda.
+investigated by the user looking at the error in the \TSTP derivation by \Metis,
+in the translation by \Athena,in the \Agda formalisations mentioned above or
+even in the type-checker, \Agda..
 
@@
 Therefore, for a general recursive function $\rm{f}: \Prop \to \Prop$
-with termination problems, we state a new function
+with termination problems, we formulate a new function
 $\rm{f}^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls must be
@@
 Let us consider the following example to exhibit the bounded technique
-mentioned above for the \fuh function presented in the version
-proposed of the \Metis \strip inference.
+mentioned above for the \fuh function presented in the proposed version
+for the \Metis \strip inference.
 
@@
 Therefore, we define the function
-$uh_{1}$ by structural recursion in its second argument in
+$\fuh_{1}$ by structural recursion in its second argument in
 Eq.~(\ref{eq:uh-structured}).

### 2017-10-21 paper/sections/proof-reconstruction.tex
'.

@@
 and some unused input is removed from the proof-tree.
-
-As a result of using \Athena, we get an \Agda file of the proof.
-To generate this file, \Athena uses names of functions and theorems from
-our \Agda libraries: \texttt{agda-prop}, and \texttt{agda-metis}.
+As result, we get from \Athena an \Agda file of the proof
+with names of functions and theorems from
+the \Agda libraries that accompany this article:
+\texttt{agda-prop} and \texttt{agda-metis}.
 
@@
 In that case \Agda outputs an interface file.
-
 Otherwise, when type-checking fails, the failure must be
-investigated by the user looking at the error in the \TSTP derivation by \Metis,
-in the translation by \Athena,in the \Agda formalisations mentioned above or
-even in the type-checker, \Agda..
+investigated by the user looking at the error in the \TSTP derivation
+by \Metis, in the translation by \Athena, in the \Agda formalizations
+mentioned above or even in the type-checker~\Agda.
 
@@
 The type of natural numbers is called \Nat type, and it is defined as
-usual, i.e., \zero and \suc are the data constructors. We use names
+usual, \ie \zero and \suc are the data constructors. We use names
 and symbols of the arithmetic operations as usual.
@@
 
-In this section, we emulate each \Metis inference rule with
+In this section, we emulate each \Metis inference rule with a
 function and its respective theorem.
 The following pattern is used to present the formalization.
-The function name written in bold face
+The function name written in bold font
 is a \Metis inference rule in \TSTP derivations.
@@
 $\rm{rule}$ function.
-\begin{equation*}\text{If }Γ ⊢ φ\text{ then }Γ ⊢ rule\ φ.\end{equation*}
+\begin{equation*}\text{If }Γ ⊢ φ\text{ then }Γ ⊢ \rm{rule}\ φ.\end{equation*}
 
@@
 \label{def:strip}
-  \begin{align}
 \label{eq:strip}
-    &\fstrip &&: \Prop → \Nat → \Prop\\
-    &\fstrip\ (φ₁ ∧ φ₂)\ n     &&= \fuh\ (\fstrip\ φ₁) ∧ \fuh\ (φ₁ ⇒ \fstrip\ φ₂)\\
-    &\fstrip\ (φ₁ ∨ φ₂)\ n     &&= \fuh\ (¬ φ₁ ⇒ \fstrip\ φ₂)\\
-    &\fstrip\ (φ₁ ⇒ φ₂)\ n     &&= \fuh\ (φ₁ ⇒ \fstrip\ φ₂)\\
-    &\fstrip\ (φ₁ ⇔ φ₂)\ n     &&= \fuh\ φ₁ ⇒ \fstrip\ φ₂) ∧ \fuh\ φ₂ ⇒ \fstrip φ₁)\\
-    &\fstrip\ (¬ (φ₁ ∧ φ₂))\ n &&= \fuh\ φ₁ ⇒ \fstrip(¬ φ₂))\\
-    &\fstrip\ (¬ (φ₁ ∨ φ₂))\ n &&= \fuh\ \fstrip(¬ φ₁)) ∧\ \fuh ¬ φ₁ ⇒ \fstrip(¬ φ₂))\\
-    &\fstrip\ (¬ (φ₁ ⇒ φ₂))\ n &&= \fuh\ \fstrip(φ₁)) ∧\ \fuh φ₁ ⇒ \fstrip(¬ φ₂))\\
-    &\fstrip\ (¬ (φ₁ ⇔ φ₂))\ n &&= \fuh\ φ₁ ⇒ \fstrip(¬ φ₂)) ∧\ \fuh ¬ φ₂ ⇒ \fstrip(φ₁))\\
-    &\fstrip\ (¬ ¬ φ₁)\ n      &&= \fuh\ \fstrip(φ₁))\\
-    &\fstrip\ (¬ ⊥)\ n         &&= ⊤\\
-    &\fstrip\ (¬ ⊤.)\ n        &&= ⊥\\
-    &\fstrip\ φ\ n             &&= φ
-  \end{align}
+
+\begin{equation}
+\begin{aligned}
+&\hspace{.495mm}\fstrip : \Prop → \Nat → \Prop\\
+&\begin{array}{lll}
+\fstrip &(φ₁ ∧ φ₂)     ~(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
+\fstrip &(φ₁ ∨ φ₂)     ~(\suc~n) &= \fuh~(¬ φ₁ ⇒ \fstrip~φ₂~n)\\
+\fstrip &(φ₁ ⇒ φ₂)     ~(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
+\fstrip &(¬ (φ₁ ∧ φ₂)) ~(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~¬ φ₂~n)\\
+\fstrip &(¬ (φ₁ ∨ φ₂)) ~(\suc~n) &= \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh (¬ φ₁ ⇒ \fstrip~¬ φ₂~n)\\
+\fstrip &(¬ (φ₁ ⇒ φ₂)) ~(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh (φ₁ ⇒ \fstrip~¬ φ₂~n)\\
+\fstrip &(¬ ¬ φ₁)      ~(\suc~n) &= \fuh~(\fstrip~φ₁~n)\\
+\fstrip &(¬ ⊥)         ~(\suc~n) &= ⊤\\
+\fstrip &(¬ ⊤)         ~(\suc~n) &= ⊥\\
+\fstrip &φ             ~n &= φ
+\end{array}
+\end{aligned}
+\end{equation}
 \end{definition}
@@
 \begin{lemma}[lem-inv-strip]
-If $Γ ⊢ \fstrip\ φ$ then $Γ ⊢ φ$.
+If $Γ ⊢ \fstrip~φ$ then $Γ ⊢ φ$.
 \label{lem:lem-inv-strip}
@@
   \begin{bprooftree}
- \AxiomC{$Γ ⊢ \fstrip(¬¬φ₁,n)$}
+ \AxiomC{$Γ ⊢ \fstrip~(¬¬φ₁)~(\suc~n)$}
   \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh(\fstrip(φ₁,n-1))$}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
   \RightLabel{lem-inv-uh}
-  \UnaryInfC{$Γ ⊢ \fstrip(φ₁,n-1)$}
+  \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
   \RightLabel{lem-inv-strip}
@@
   \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \fstrip(φ,n)$}
+  \AxiomC{$Γ ⊢ \fstrip~(φ₁ ∧ φ₂)~(\suc~n)$}
   \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh(φ₁) ∧ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
   \RightLabel{∧-proj₁}
-  \UnaryInfC{$Γ ⊢ \fuh(φ₁)$}
-  \RightLabel{lem-inv-uh.}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
+  \RightLabel{lem-inv-uh}
+  \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
+  \RightLabel{lem-inv-strip}
   \UnaryInfC{$Γ ⊢ φ₁$}
@@
   \UnaryInfC{Γ ⊢ φ₁}
-  \AxiomC{$Γ ⊢ \fstrip(φ,n)$}
+  \AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
   \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh(φ₁) ∧ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
   \RightLabel{$∧$-proj$₂$}
-  \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
   \RightLabel{lem-inv-uh}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip(φ₂,n-1)$}
+  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
   \RightLabel{$⇒$-elim}
-  \BinaryInfC{$Γ ⊢ \fstrip(φ₂,n-1)$}
+  \BinaryInfC{$Γ ⊢ \fstrip~φ₂~n$}
   \RightLabel{lem-inv-strip.}
@@
   \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
-  \AxiomC{$Γ ⊢ \fstrip(φ,n-1)$}
+  \AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
   \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ \fstrip(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
   \RightLabel{lem-inv-uh}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip(φ₂,n-1)$}
+  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
   \RightLabel{weaken φ₁}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \fstrip(φ₂,n-1)$}
+  \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
   \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ , φ₁ ⊢ \fstrip(φ₂,n-1)$}
+  \BinaryInfC{$Γ , φ₁ ⊢ \fstrip~φ₂~n$}
   \RightLabel{lem-inv-strip}
@@
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ \fstrip(φ, n)$}
+\AxiomC{$Γ ⊢ \fstrip~φ, n)$}
 \RightLabel{by def.}
-\UnaryInfC{$Γ ⊢ \fuh(¬ φ₁) ∧ \fuh(¬ φ₁ ⇒ \fstrip(φ₂, n))$}
+\UnaryInfC{$Γ ⊢ \fuh(¬ φ₁) ∧ \fuh(¬ φ₁ ⇒ \fstrip~φ₂, n))$}
 \RightLabel{∧-proj₁}
@@
   \UnaryInfC{$Γ ⊢ ¬ φ₁$}
-
-  \AxiomC{$Γ ⊢ \fstrip(φ,n-1)$}
+  \AxiomC{$Γ ⊢ \fstrip~φ,n-1)$}
   \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh(¬ φ₁) ∧ \fuh(¬ φ₁ ⇒ \fstrip(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ \fuh(¬ φ₁) ∧ \fuh(¬ φ₁ ⇒ \fstrip~φ₂,n-1))$}
   \RightLabel{∧-proj₂}
-  \UnaryInfC{$Γ ⊢ \fuh(¬ φ₁ ⇒ \fstrip(φ₂,n-1))$}
+  \UnaryInfC{$Γ ⊢ \fuh(¬ φ₁ ⇒ \fstrip~φ₂,n-1))$}
   \RightLabel{lem-inv-uh}
-  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip(φ₂,n-1)$}
+  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip~φ₂,n-1)$}
   \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ ⊢ \fstrip(φ₂,n-1)$}
+  \BinaryInfC{$Γ ⊢ \fstrip~φ₂,n-1)$}
   \RightLabel{lem-inv-strip.}
@@
 
-  \AxiomC{$\fstrip(φ) ≡ \bigwedge_{i=1}^n s_i $}
+  \AxiomC{$\fstrip~φ) ≡ \bigwedge_{i=1}^n s_i $}
   \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ \fstrip(φ)$}
+  \BinaryInfC{$Γ ⊢ \fstrip~φ)$}
   \RightLabel{lem-inv-strip.}
@@
 
-In Def.~\ref{def:resolve}, the emulated rule for $resolve$
+In Def.~\ref{def:resolve}, the proposed rule for $resolve$
 has four arguments. The first three were described
@@
 
-% φ ⊻ ψ if and only if ¬ (φ ⇔ ψ).
-
 \begin{figure}
@@
 $\frm_{∨}$ function, we can define a similar function to work with
-conjunctions, i.e., $\frm_{∧}$.
+conjunctions, \ie, $\frm_{∧}$.
 
@@
   \label{lem:lem-nnf}
-  If $Γ ⊢ φ$ then $Γ ⟝ \fnnf(φ)$ where,
+  If $Γ ⊢ φ$ then $Γ ⟝ \fnnf~φ$ where,
   \begin{align*}
@@
      &\fnnf : \NProp \to \NProp\\
-     &\fnnf(φ) = \fnnf₀(⊕, φ).
+     &\fnnf~φ = \fnnf₀(⊕, φ).
    \end{split}
@@
         ψ, &\text{ if }ψ ≡ φ\\
-        ψ, &\text{ if }ψ ≡ \fform(\fnnf(φ))\\
-        ψ, &\text{ if }\fcnf(ψ) ≡ \freorder_{∧∨}(\fcnf(φ), \fcnf(ψ))\\
+        ψ, &\text{ if }ψ ≡ \fform(\fnnf~φ)\\
+        ψ, &\text{ if }\fcnf~ψ ≡ \freorder_{∧∨}(\fcnf~φ, \fcnf~ψ)\\
         φ, &\text{ otherwise.}\\
@@
 \item If $φ ≡ ψ$ by substitution theorem we conclude $Γ ⊢ ψ$.
-\item If $ψ ≡ \fform(\fnnf(φ))$,
+\item If $ψ ≡ \fform(\fnnf~φ)$,
 \begin{equation*}
@@
     \RightLabel{lem-nnf}
-    \UnaryInfC{$Γ ⊢₂~\fnnf(φ)$}
+    \UnaryInfC{$Γ ⊢₂~\fnnf~φ$}
     \RightLabel{lem-form}
-    \UnaryInfC{$Γ ⊢ \fform(\fnnf(φ))$}
-    \AxiomC{$ψ ≡ \fform(\fnnf(φ))$}
+    \UnaryInfC{$Γ ⊢ \fform(\fnnf~φ)$}
+    \AxiomC{$ψ ≡ \fform(\fnnf~φ)$}
     \RightLabel{subst.}
@@
 
-\item If $γ = \fcnf(ψ) ≡ \freorder_{∧∨}(\fcnf(φ), \fcnf(ψ))$,
+\item If $γ = \fcnf~ψ ≡ \freorder_{∧∨}~(\fcnf~φ)~(\fcnf~ψ)$,
   \begin{equation*}
@@
       \RightLabel{thm-cnf}
-      \UnaryInfC{$Γ ⊢ \fcnf(φ)$}
+      \UnaryInfC{$Γ ⊢ \fcnf~φ$}
       \RightLabel{thm-reorder$_{∧∨}$}
-      \UnaryInfC{$Γ ⊢ \freorder_{∧∨}(\fcnf(φ), \fcnf(ψ))$}
+      \UnaryInfC{$Γ ⊢ \freorder_{∧∨}(\fcnf~φ, \fcnf~ψ)$}
       \AxiomC{$γ$}
       \RightLabel{subst}
-      \BinaryInfC{$Γ ⊢ \fcnf(ψ)$}
+      \BinaryInfC{$Γ ⊢ \fcnf~ψ$}
       \RightLabel{thm-inv-cnf.}
@@
       &\fclausify : \Prop → \Prop → \Prop\\
-      &\fclausify(φ,ψ) =
+      &\fclausify~φ~ψ =
       \begin{cases}
         ψ, &\text{ if }φ≡ψ\\
-        \freorder_{∧∨}(\fcnf(φ), ψ), &\text{ otherwise.}
+        \freorder_{∧∨}~(\fcnf~φ~ψ), &\text{ otherwise.}
       \end{cases}
@@
 \label{thm:thm-clausify}
-  $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fclausify(φ, ψ)$.
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fclausify~φ~ψ$.
 \end{theorem}

### 2017-10-22 paper/sections/proof-reconstruction.tex
[ paper ] fixing proofs.
[ paper ] rules in distinct files.

@@
 
-\subsubsection{Stripping a goal.}
-\label{sssec:strip-a-goal}
+\subfile{sections/proof-reconstruction/strip.tex}
+\subfile{sections/proof-reconstruction/negate.tex}
+\subfile{sections/proof-reconstruction/resolve.tex}
+\subfile{sections/proof-reconstruction/canonicalize.tex}
+\subfile{sections/proof-reconstruction/conjunct.tex}
+\subfile{sections/proof-reconstruction/clausify.tex}
+\subfile{sections/proof-reconstruction/simplify.tex}
 
-To prove a goal, \Metis splits the goal into
-disjoint cases. This process produces a list of new subgoals, the
-conjunction of these subgoals implies the goal. Then, a proof of the
-goal becomes, in smaller proofs, one refutation for each subgoal.
-These subgoals are introduced in the \TSTP derivation with the \strip
-inference rule as we show in the following excerpt.
-
-\begin{verbatim}
-fof(goal, conjecture, ((p & r) & q)).
-fof(subgoal_0, plain, p,
-    inference(strip, [], [goal])).
-fof(subgoal_1, plain, p => r,
-    inference(strip, [], [goal])).
-fof(subgoal_2, plain, (p & r) => q,
-    inference(strip, [], [goal])).
-\end{verbatim}
-
-To prove the correctness of the process mentioned above,
-we need to establish some lemmas before introduce our main goal of this
-part, Theorem~\ref{thm:thm-strip}.
-
-\begin{lemma}[lem-inv-uh]
-  \label{lem:uh}
-  If $Γ ⊢ \fuh\ φ$ then $Γ ⊢ φ$.
-\end{lemma}
-
-\begin{sketchproof}
-Use induction on the cases defined by the outcome of the
-$\fuh$ function in Eq.~(\ref{eq:uh-structured}).
-\begin{itemize}
-	\item If $n = 0$, by definition we conclude $Γ ⊢ φ$.
-	\item If $n = 1$, we apply the following theorem proved in~\cite{AgdaProp},
-		\begin{equation*}
-		\texttt{∧⇒\rm{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
-		\end{equation*}
-  \item For $n > 1$, we use induction on the structure of the second
-			  argument.
-\vskip 2mm
-\begin{itemize}
-
-\item Case $φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)$.
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
-  \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
-  \RightLabel{lem-inv-uh}
-  \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
-  \RightLabel{∧⇒\rm{-to-}⇒⇒.}
-  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)}
-  \end{bprooftree}
-\end{equation*}
-
-\item Case $φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)$.
-\begin{equation*}
-  \scalebox{0.95}{
-  ($\mathcal{D}_1$)
-  \begin{bprooftree}
-    \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n) ∧ \fuh(φ₁ ⇒ φ₃, n)$}
-    \RightLabel{∧-proj₁}
-    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n)$}
-    \RightLabel{by def.}
-    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n-1)$}
-    \RightLabel{lem-inv-uh,}
-    \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
-  \end{bprooftree}
-  }
-\end{equation*}
-
-\begin{equation*}
-  (\mathcal{D}_2)
-  \begin{bprooftree}
-    \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂) ∧ \fuh(φ₁ ⇒ φ₃)$}
-    \RightLabel{∧-proj₂}
-    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₃, n)$}
-    \RightLabel{by def.}
-    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₃, n-1)$}
-    \RightLabel{lem-inv-uh.}
-    \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
-    \end{bprooftree}
-\end{equation*}
-
-Finally, using the theorem \texttt{⇒∧⇒\rm{-to-}⇒∧} from~\cite{AgdaProp},
-\begin{equation*}
-  \texttt{⇒∧⇒\rm{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
-\end{equation*}
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\mathcal{D}_1$}
-  \AxiomC{$\mathcal{D}_2$}
-  \RightLabel{∧-intro}
-  \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
-  \RightLabel{\tt ⇒∧⇒\rm{-to-}⇒∧.}
-  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
-  \end{bprooftree}
-\end{equation*}
-\item Other cases are proved in a similar way.
-\end{itemize}
-\end{itemize}
-\end{sketchproof}
-
-We now define the $\fstrip$ function that yields the conjunction of
-subgoals that implies the goal of the problem in the \Metis \TSTP derivations.
-
-\begin{definition}[strip]
-\label{def:strip}
-\label{eq:strip}
-
-\begin{equation}
-\begin{aligned}
-&\hspace{.495mm}\fstrip : \Prop → \Nat → \Prop\\
-&\begin{array}{lll}
-\fstrip &(φ₁ ∧ φ₂)     ~(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
-\fstrip &(φ₁ ∨ φ₂)     ~(\suc~n) &= \fuh~(¬ φ₁ ⇒ \fstrip~φ₂~n)\\
-\fstrip &(φ₁ ⇒ φ₂)     ~(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
-\fstrip &(¬ (φ₁ ∧ φ₂)) ~(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~¬ φ₂~n)\\
-\fstrip &(¬ (φ₁ ∨ φ₂)) ~(\suc~n) &= \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh (¬ φ₁ ⇒ \fstrip~¬ φ₂~n)\\
-\fstrip &(¬ (φ₁ ⇒ φ₂)) ~(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh (φ₁ ⇒ \fstrip~¬ φ₂~n)\\
-\fstrip &(¬ ¬ φ₁)      ~(\suc~n) &= \fuh~(\fstrip~φ₁~n)\\
-\fstrip &(¬ ⊥)         ~(\suc~n) &= ⊤\\
-\fstrip &(¬ ⊤)         ~(\suc~n) &= ⊥\\
-\fstrip &φ             ~n &= φ
-\end{array}
-\end{aligned}
-\end{equation}
-\end{definition}
-
-% The definition above has termination problems since it is not
-% a structural recursion. Therefore, we have reformulated the equation
-% above to solve such an issue following the technique
-% described in Section~\ref{ssec:structural-recursion}.
-% We refer to $\fstrip$ as the function after applying the process mentioned
-% above here and below unless otherwise stated.
-
-\begin{lemma}[lem-inv-strip]
-If $Γ ⊢ \fstrip~φ$ then $Γ ⊢ φ$.
-\label{lem:lem-inv-strip}
-\end{lemma}
-
-\begin{sketchproof}
-The proof is by induction on the structure of the
-formula~$φ$ by following the cases in Eq.~(\ref{eq:strip}).
-We present some cases but for a complete proof, we refer the reader to~\cite{AgdaMetis}.
-
-\begin{itemize}
-\item Case $φ ≡ ¬ ¬ φ₁$.
-\begin{equation*}
-  \begin{bprooftree}
- \AxiomC{$Γ ⊢ \fstrip~(¬¬φ₁)~(\suc~n)$}
-  \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
-  \RightLabel{lem-inv-uh}
-  \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
-  \RightLabel{lem-inv-strip}
-  \UnaryInfC{$Γ ⊢ φ₁$}
-  \end{bprooftree}
-\end{equation*}
-
-\item Case $φ ≡ φ₁ ∧ φ₂$. We get a proof for each conjunct and using the
-introduction rule for conjunction connective, the result follows.
-
-\begin{equation*}
-(\mathcal{D})\hspace{3mm}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \fstrip~(φ₁ ∧ φ₂)~(\suc~n)$}
-  \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
-  \RightLabel{∧-proj₁}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
-  \RightLabel{lem-inv-uh}
-  \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
-  \RightLabel{lem-inv-strip}
-  \UnaryInfC{$Γ ⊢ φ₁$}
-    \end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\mathcal{D}$}
-  \UnaryInfC{Γ ⊢ φ₁}
-  \AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
-  \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
-  \RightLabel{$∧$-proj$₂$}
-  \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
-  \RightLabel{lem-inv-uh}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
-  \RightLabel{$⇒$-elim}
-  \BinaryInfC{$Γ ⊢ \fstrip~φ₂~n$}
-  \RightLabel{lem-inv-strip.}
-  \UnaryInfC{$Γ ⊢ φ₂$}
-  \end{bprooftree}
-\end{equation*}
-
-\item Case $φ ≡ φ₁ ⇒ φ₂$.
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{assume φ₁}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
-  \AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
-  \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
-  \RightLabel{lem-inv-uh}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
-  \RightLabel{weaken φ₁}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
-  \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ , φ₁ ⊢ \fstrip~φ₂~n$}
-  \RightLabel{lem-inv-strip}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
-  \RightLabel{⇒-intro.}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
-  \end{bprooftree}
-\end{equation*}
-
-\item Case $φ ≡ ¬ (φ₁ ∨ φ₂)$. We show that $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
-The result follows by introducing the conjunction and applying
-De Morgan Laws.
-
-\begin{equation*}
-(\mathcal{D})\hspace{3mm}
-\begin{bprooftree}
-\AxiomC{$Γ ⊢ \fstrip~φ, n)$}
-\RightLabel{by def.}
-\UnaryInfC{$Γ ⊢ \fuh(¬ φ₁) ∧ \fuh(¬ φ₁ ⇒ \fstrip~φ₂, n))$}
-\RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ \fuh(¬ φ₁)$}
-\RightLabel{lem-inv-uh,}
-\UnaryInfC{$Γ ⊢ ¬ φ₁$}
-\end{bprooftree}
-\end{equation*}
-\end{itemize}
-\end{sketchproof}
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\mathcal{D}$}
-  \UnaryInfC{$Γ ⊢ ¬ φ₁$}
-  \AxiomC{$Γ ⊢ \fstrip~φ,n-1)$}
-  \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh(¬ φ₁) ∧ \fuh(¬ φ₁ ⇒ \fstrip~φ₂,n-1))$}
-  \RightLabel{∧-proj₂}
-  \UnaryInfC{$Γ ⊢ \fuh(¬ φ₁ ⇒ \fstrip~φ₂,n-1))$}
-  \RightLabel{lem-inv-uh}
-  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip~φ₂,n-1)$}
-  \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ ⊢ \fstrip~φ₂,n-1)$}
-  \RightLabel{lem-inv-strip.}
-  \UnaryInfC{$Γ ⊢ ¬ φ₂$}
-  \end{bprooftree}
-\end{equation*}
-
-\begin{lemma}[subst]
-  \label{lem:subst}
-  Substitution theorem.
-\begin{equation*}
-  \label{eq:substitution-theorem}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
-  \RightLabel{subst.}
-  \BinaryInfC{$Γ ⊢ ψ$}
-  \end{bprooftree}
-\end{equation*}
-\end{lemma}
-
-We can now formulate the result that justifies the stripping strategy
-of \Metis to prove goals.
-
-\begin{theorem}[thm-strip]
-\label{thm:thm-strip}
- If $s_i$ are the subgoals of the goal $φ$ for $i=1,\cdots,n$ and
- $\{ Γ ⊢ s_i \}_{i =1}^n$, then $Γ ⊢ φ$.
-\end{theorem}
-
-\begin{proof}
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i=1}^n$}
-  \RightLabel{∧-intro}
-  \UnaryInfC{$Γ ⊢ \bigwedge_{i=1}^n s_i$}
-
-  \AxiomC{$\fstrip~φ) ≡ \bigwedge_{i=1}^n s_i $}
-  \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ \fstrip~φ)$}
-  \RightLabel{lem-inv-strip.}
-  \UnaryInfC{$Γ ⊢ φ$}
-\end{bprooftree}
-\end{equation*}
-\end{proof}
-
-% -------------------------------------------------------------------
-
-\subsubsection{Negating subgoals.}
-
-Each proof of a subgoal is a refutation, thereby each proof assumes
-the negation of its subgoal. The \negate rule
-assumes the negation of such subgoals, and
-appears after applying the \strip inference to the goal.
-
-\begin{verbatim}
-fof(goal, conjecture, (p & q)).
-fof(subgoal_0, plain, (p), inference(strip, [], [goal])).
-fof(subgoal_1, plain, (p => q), inference(strip, [], [goal])).
-fof(negate_0_0, plain, (~ p), inference(negate, [], [subgoal_0])).
-\end{verbatim}
-
-To emulate this rule, we introduce the negation
-of the subgoal by using $assume$ rule from the inferences in
-Fig.~\ref{fig:CPL-inference-rules}.
-
-% -------------------------------------------------------------------
-
-\subsubsection{Splitting a conjunct.}
-\label{sssec:splitting-a-conjunct}
-
-The \conjunct rule extracts from a
-conjunction one of its conjuncts. This rule is a generalization of the
-projection rules for the conjunction connective as the
-following \TSTP excerpt shows.
-
-\begin{verbatim}
-fof(normalize_1, plain, p & q & (r | ~ p),
-  inference(canonicalize, [], [x])).
-fof(normalize_2, plain, q,
-  inference(conjunct, [], [normalize_1])).
-fof(normalize_2, plain, (r | ~ p),
-  inference(conjunct, [], [normalize_1])).
-\end{verbatim}
-
-\begin{definition}[conjunct]
-  \label{def:conjunct}
-  \begin{align*}
-    \begin{split}
-    &\fconjunct : \Prop \to \Prop \to \Prop\\
-    &\fconjunct(φ, ψ) =
-      \begin{cases}
-          ψ, &\text{ if }φ ≡ ψ\\
-          ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ \fconjunct(φ₁, ψ)\\
-          ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ \fconjunct(φ₂, ψ)\\
-          φ, &\text{ otherwise.}
-        \end{cases}
-    \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{theorem}[thm-conjunct]
-  \label{thm:thm-conjunct}
-  If $Γ ⊢ φ$ and $ψ  : \Prop$ then $Γ ⊢ \fconjunct(φ, ψ)$.
-\end{theorem}
-\begin{proof}\hspace{2cm}
-\begin{itemize}
-  \item For the case $φ ≡ ψ$, $Γ ⊢ \fconjunct(φ, ψ)$ normalizes to $Γ ⊢ ψ$.
-Then, we get the desire conclusion by applying the $\fsubst$ theorem.
-  \item If the proposition $φ$ is a conjunction, and we can get $ψ ≡ \fconjunct(φ_{i}, ψ)$ for some $i = 1,\ 2$, then,
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
-  \RightLabel{∧-proj$_{i}$}
-  \UnaryInfC{$Γ ⊢ φ_{i}$}
-  \UnaryInfC{$Γ ⊢ \fconjunct(φ_{i}, ψ)$}
-  \AxiomC{$ψ ≡ \fconjunct(φ_{i}, ψ)$}
-  \RightLabel{subst.}
-  \BinaryInfC{$Γ ⊢ ψ$}
-  \end{bprooftree}
-\end{equation*}
-\item The last case follows trivially by using the same hypothesis.
-\end{itemize}
-\end{proof}
-
-% subsubsection splitting-a-conjunct (end)
-% -------------------------------------------------------------------
-
-% ------------------------------------------------------------------------
-
-\subsubsection{Reordering.}
-\label{sssec:reordering}
-
-Logic equivalence between propositions is a major issue to justify
-prover reasoning steps. Since we left out semantics to treat only the
-syntax aspects of the propositions, our approach shows equivalence
-by converting propositions to their conjunctive normal forms,
-and reordering those and the inner disjunctions  to match them
-In this section, we provide some theorems to perform such reordering tasks,
-the goals are the following.
-
-\begin{itemize}
-  \item Reorder a disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$ to match with
-$ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$. For all $i$, there exists at least one $j$ such
-that $φᵢ ≡ ψⱼ$.
-  \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another
-CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$. For all $i$, there exists at least one $j$
-such that $φᵢ ≡ ψⱼ$.
-\end{itemize}
-
-First, we define the $\rm{rdisj}$ function to convert
-a disjunction in its right-associative form.
-The $\rm{rconj}$ function that converts conjunction to its right-associative form
-is not presented here, but is defined in a similar way (see its implementation
-in~\cite{AgdaMetis}).
-
-\begin{definition}[rdisj]
-\label{def:rdisj}
-  \begin{align*}
-    \begin{split}
-    \label{eq:rdisj-def}
-      &\rm{rdisj}(φ) : \Prop \to \Prop\\
-      &\rm{rdisj}(φ) =
-      \begin{cases}
-      \rm{rdisj}(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{ if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
-      φ₁ ∨ \rm{rdisj}(φ₂),         & \text{ if } φ ≡ φ₁ ∨ φ₂\\
-      φ,                      & \text{ otherwise.}
-      \end{cases}
-    \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{lemma}[lem-rdisj]
-\label{lem:lem-rdisj}
-  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rdisj}(φ)$.
-\end{lemma}
-
-\begin{definition}[build$_{\boldsymbol{∨}}$]
-\begin{equation*}
-  \begin{split}
-  \label{eq:build-or}
-  &\rm{build}_{∨} : \Prop → \Prop → \Prop\\
-  &\rm{build}_{∨}(φ, ψ) =%\\
-  % &\hspace{3mm}
-  \begin{cases}
-  ψ, &\text{ if } φ ≡ ψ\\
-  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{, } \rm{build}_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
-  φ, &\text{ otherwise.}
-  \end{cases}
-  \end{split}
-\end{equation*}
-\end{definition}
-
-The $\rm{build}_{∨}$ function defined above intends to construct a
-disjunction from another disjunction, specifically, this functions will
-try to rearrange the disjuncts in the source formula to match with the
-target disjunction formula, similar as we describe above.
-
-\begin{lemma}[lem-build$_{\boldsymbol{∨}}$]
-\label{lem:lem-build-or}
-If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}(φ)$.
-\end{lemma}
-
-From now, we assume all propositions to be right-associative unless
-otherwise stated.
-The $\ffactor$ function in Eq.~(\ref{eq:factor-definition}) intends to
-simplify a special case of disjunction, the repeated disjuncts
-(e.g., $\ffactor(φ ∨ φ) \mapsto\ φ$).
-Notice that other cases like $φ ∨ (ψ ∨ φ)$ do no reduce to $(ψ ∨ φ)$.
-
-\begin{definition}[factor]
-\begin{align}
-\begin{split}
-  \label{eq:factor-definition}
-  &\ffactor : \Prop → \Prop\\
-  &\ffactor(φ) =
-  \begin{cases}
-    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{, } φ₁ ≡ \ffactor(φ₂)\\
-    φ,   &\text{ otherwise.}
-  \end{cases}
-\end{split}
-\end{align}
-\end{definition}
-
-\begin{lemma}[lem-factor]
-\label{lem:lem-factor}
-  $Γ ⊢ φ$ then $Γ ⊢ \ffactor(φ)$.
-\end{lemma}
-
-To construct a disjunction $ψ$ from a disjunction $φ$, we have used ideas
-from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove
-equality between nested disjunctions.
-The result is the $\rm{sbuild}_{∨}$ function
-that uses every disjunct from the source formula, $φ$, to build up the
-target disjunction $ψ$.
-
-\begin{definition}[sbuild$_{\boldsymbol{∨}}$]
-\begin{align*}
-  \begin{split}
-  \label{eq:strong-build-or-definition}
-    &\rm{sbuild}_{∨} : \Prop → \Prop → \Prop\\
-    &\rm{sbuild}_{∨}(φ, ψ) =%\\
-    % &\hspace{3mm}
-    \begin{cases}
-      \ffactor(\rm{build}_{∨}(φ₁, ψ) ∨ \rm{build}_{∨}(φ₂,ψ)),
-      &\text{ if }φ≡ φ₁ ∨ φ₂\\
-      \rm{build}_{∨}(φ, ψ),  & \text{ otherwise.}
-    \end{cases}
-  \end{split}
-\end{align*}
-\end{definition}
-
-\begin{lemma}[lem-sbuild$_{\boldsymbol{∨}}$]
-\label{lem:lem-sbuild-or}
-If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}(φ, ψ)$.
-\end{lemma}
-
-\begin{example}
-Let see the main idea behind the lem-sbuild$_{∨}$ lemma.
-We build the disjunction $((p ∨ q) ∨ r)$ from the disjunction
-$(r ∨ (q ∨ p))$.
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ q$}
-  \RightLabel{∨-intro₂}
-  \UnaryInfC{$Γ ⊢ p ∨ q$}
-  \RightLabel{∨-intro₁}
-  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-  \AxiomC{$Γ ⊢ p$}
-  \RightLabel{∨-intro₁}
-  \UnaryInfC{$Γ ⊢ p ∨ q$}
-  \RightLabel{∨-intro₁}
-  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-  \RightLabel{∨-elim}
-  \BinaryInfC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
-  \end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ r$}
-  \RightLabel{∨-intro₂}
-  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-  \AxiomC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
-
-  \RightLabel{∨-elim}
-  \BinaryInfC{$Γ, r ∨ (q ∨ p) ⊢ (p ∨ q) ∨ r$}
-
-  \RightLabel{⇒-intro}
-  \UnaryInfC{$Γ ⊢ r ∨ (q ∨ p) ⇒ (p ∨ q) ∨ r$}
-
-  \end{bprooftree}
-\end{equation*}
-\end{example}
-
-Notice that using $\rm{sbuild}_{∨}$ we can build not only a disjunction
-with the same disjuncts of the source formula but also a complete different
-formula by adding new disjuncts to the source formula.
-
-\begin{definition}[reorder$_{\boldsymbol{∨}}$]
-\begin{align*}
-    \label{eq:reorder-or}
-    \begin{split}
-    &\freorder_{∨} : \Prop \to \Prop \to \Prop\\
-    &\freorder_{∨} (φ, ψ) = \rm{sbuild}_{∨}(rdisj(φ), ψ).
-    \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{theorem}[thm-reorder$_{\boldsymbol{∨}}$]
-  \label{thm-reorder-or}
-  If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}(φ, ψ)$.
-\end{theorem}
-
-\begin{proof}
-Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
-\end{proof}
-
-We define similar functions and state some theorems as we previously did
-for disjunctions, but instead, we treat only with conjunctive normal forms.
-
-\begin{definition}[reorder$_{\boldsymbol{∧}}$]
-  \begin{align*}
-      \begin{split}
-        &\freorder_{∧} : \Prop → \Prop \to \Prop\\
-        &\freorder_{∧}(φ, ψ) =
-        \begin{cases}
-          φ, &\text{ if }φ ≡ ψ\\
-          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\freorder_{∧}(φ, ψ₁) ≡ ψ₁\\
-                  &\text{and }\freorder_{∧}(φ, ψ₂)≡ ψ₂\\
-          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
-          \fconjunct(φ, ψ), &\text{ otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{lemma}[lem-reorder$_{\boldsymbol{∧}}$]
-  \label{lem:lem-reorder-and}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}(φ, ψ)$.
-\end{lemma}
-
-\begin{definition}[conjunct$_{\boldsymbol{∨}}$]
-  \label{eq:conjunct-or-definition}
-\begin{align*}
-  \begin{split}
-    &\fconjunct_{∨} : \Prop → \Prop \to \Prop\\
-    &\fconjunct_{∨}(φ, ψ) =
-    \begin{cases}
-      ψ, &\text{ if }φ ≡ ψ\\
-      ψ, &\text{ if }\freorder_{∨}(φ, ψ) ≡ ψ\\
-      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ \fconjunct_{∨}(φ, ψ₁) ≡ ψ₁,\\
-        &\text{and } \freorder_{∨}(φ, ψ₂) ≡ ψ₂\\
-      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}(φ₁, ψ) ≡ ψ\\
-      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}(φ₂, ψ) ≡ ψ\\
-      φ, &\text{ otherwise.}
-    \end{cases}
-  \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{lemma}[lem-conjunct$_{\boldsymbol{∨}}$]
-  \label{lem:lem-conjunct-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}(φ, ψ)$.
-\end{lemma}
-
-\begin{definition}[reorder$_{\boldsymbol{∧∨}}$]
- \begin{align*}
-      \begin{split}
-      &\freorder : \Prop \to \Prop \to \Prop\\
-      &\freorder_{∧∨}(φ, ψ)=
-        \begin{cases}
-          ψ, &\text{ if } φ≡ψ\\
-          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ \freorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
-             &\text{and }\freorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
-          φ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂\\
-          \fconjunct_{∨}(φ, ψ) &\text{ otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align*}
-  \end{definition}
-
-\begin{theorem}[thm-reorder$_{\boldsymbol{∧∨}}$]
-  \label{thm:thm-reorder-and-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$.
-\end{theorem}
-
-% % --------------------------------------------------------------------
-
-\subsubsection{Resolution.}
-\label{sssec:resolve}
-
-The \resolve rule incorporates the resolution theorem showed in
-Fig.~\ref{fig:metis-inferences} for the \TSTP derivations.
-This rule posses three arguments: a positive literal $l$ to apply the
-resolution theorem, and two derivations.
-The positive literal $l$ must occur in
-the formula from the first derivation and the
-negative literal must occur in the formula from the second derivation,
-see the pattern of \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.
-
-% \begin{figure}
-\label{fig:resolve-tstp-example}
-\begin{verbatim}
-cnf(refute_0_4, plain, (~ r | p | q),
-    inference(canonicalize, [], [normalize_0_5])).
-cnf(refute_0_5, plain, (p | q | r),
-    inference(canonicalize, [], [normalize_0_6])).
-cnf(refute_0_6, plain, (p | q),
-    inference(resolve, [$cnf(r)], [refute_0_5, refute_0_4])).
-\end{verbatim}
-% \caption{Excerpt of a \Metis \TSTP example for the \resolve rule.}
-% \end{figure}
-
-To emulate this rule, we perform a sequence of rearrangements inside the
-formulas involved to match with the pattern expected by the resolution theorem
-described above. We begin by defining a convenient version of
-the binary resolution in Def.~\ref{def:rsol}.
-
-\begin{definition}[rsol]
-\label{def:rsol}
-\begin{align*}
-      \begin{split}
-        &\rm{rsol} : \Prop \to \Prop\\
-        &\rm{rsol}(φ) =
-        \begin{cases}
-          φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
-          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
-          φ, &\text{ otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{lemma}[lem-rsol]
-  \label{lem:lem-rsol}
-  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}(φ)$.
-\end{lemma}
-
-In Def.~\ref{def:resolve}, the proposed rule for $resolve$
-has four arguments. The first three were described
-above, the last one, ψ, represents the expected conclusion in the \Metis
-derivation.
-
-\begin{definition}[resolve]
-\label{def:resolve}
- \begin{align*}
- \begin{split}
-    &\fresolve : \Prop \to \Prop \to \Prop \to \Prop \to \Prop\\
-    &\fresolve(φ₁, φ₂, l, ψ) =
-      \rm{rsol}(\freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨} (φ₂, ¬ l ∨ ψ)).
-  \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{theorem}[thm-resolve]
-  \label{thm:thm-resolve}
-  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ : \Prop$ then
-  $Γ ⊢ \fresolve(φ₁, φ₂, l, ψ)$.
-\end{theorem}
-\Needspace{3\baselineskip}
-\begin{proof}
- \begin{equation*}
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ₁$}
-      \RightLabel{thm-reorder$_{∨}$,}
-      \UnaryInfC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ)$}
-   \end{bprooftree}
-  \end{equation*}
-    \vskip 1.5mm
- \begin{equation*}
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ₂$}
-      \RightLabel{thm-reorder$_{∨}$,}
-      \UnaryInfC{$Γ ⊢ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
-   \end{bprooftree}
-  \end{equation*}
-  \vskip 1.5mm
-  \begin{equation*}
-  \begin{bprooftree}
-    \AxiomC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ)$}
-    \AxiomC{$Γ ⊢ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
-    \RightLabel{∧-intro}
-    \BinaryInfC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
-    \RightLabel{lem-rsol.}
-    \UnaryInfC{$Γ ⊢ \rm{rsol}(\freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨}(φ₂, ¬ l ∨ ψ))$}
-  \end{bprooftree}
-  \end{equation*}
-\end{proof}
-
-\begin{figure}
-\label{fig:resolve-example}
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ ¬ r ∨ p ∨ q$}
-  \AxiomC{$Γ ⊢ p ∨ q ∨ r $}
-  \RightLabel{thm-resolve}
-  \BinaryInfC{$Γ ⊢ \fresolve(¬ r ∨ p ∨ q, p ∨ q ∨ r, r, p ∨ q)$}
-  \UnaryInfC{$Γ ⊢ p ∨ q$}
-  \end{bprooftree}
-\end{equation*}
-\caption{Example of a resolution in \Metis using
-Thm.~\ref{thm:thm-resolve}.}
-%Application of Thm.~\ref{thm:thm-resolve} for the \TSTP excerpt Fig.~\ref{fig:resolve-tstp-example}.}
-\end{figure}
-
-% subsubsection resolve (end)
-% --------------------------------------------------------------------
-
-% % --------------------------------------------------------------------
-
-\subsubsection{Normalization.}
-\label{sssec:normalization}
-The normalization module in \Metis is the responsible for
-\canonicalize, \clausify, \conjunct and \simplify.
-One of the main purposes of the module consists of adding the axioms
-to the problem. In this process, some transformations are carried
-out by convert a \verb!fof! formula to their clausal normal form.
-The process mainly consists of removing redundancies (tautologies or
-definitions) and converting the proposition to its normalized
-negative normal form, conjunctive normal form, or
-definitional normal form.
-
-\begin{definition}[\abbre{NProp}]
-  \NProp is the type for a formula in normalized negative normal form
-  in which negations appear only in the literals and the expression is
-  in terms only of ($⊥$, $⊤$, $¬$, $∧$, $∨$) connectives.
-  We define the \NProp type in a similar way as we did for \Prop type.
-\end{definition}
-
-A sequent $Γ ⟝ φ$ represents a theorem where
-$Γ$ is a set of \Prop propositions premises, and $φ : \NProp$ is the
-conclusion of the theorem. These theorems have a subset of rules from
-the classical inference rules in Fig.~\ref{fig:CPL-inference-rules}
-that apply for the connectives that coincides with \NProp type.
-
-\begin{figure}
-  \[
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ ∧ ⊥$}
-      \UnaryInfC{$Γ ⊢ ⊥$}
-    \end{bprooftree}
-    \qquad
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ ∧ ⊤$}
-      \UnaryInfC{$Γ ⊢ φ$}
-    \end{bprooftree}
-    \qquad
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ ∧ ¬ φ$}
-      \UnaryInfC{$Γ ⊢ ⊥$}
-    \end{bprooftree}
-    \qquad
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ ∧ φ$}
-      \UnaryInfC{$Γ ⊢ φ$}
-    \end{bprooftree}
-  \]
-
-  \[
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ ∨ ⊥$}
-      \UnaryInfC{$Γ ⊢ φ$}
-    \end{bprooftree}
-    \qquad
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ ∨ ⊤$}
-      \UnaryInfC{$Γ ⊢ ⊤$}
-    \end{bprooftree}
-    \qquad
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ ∨ ¬ φ$}
-      \UnaryInfC{$Γ ⊢ ⊤$}
-    \end{bprooftree}
-    \qquad
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ ∨ φ$}
-      \UnaryInfC{$Γ ⊢ φ$}
-    \end{bprooftree}
-  \]
-\caption{Some definitions applied to translate a formula into its
-normalized normal form.}
-\label{fig:conjunctive-disjunctive-simpl}
-\end{figure}
-
-% -------------------------------------------------------------------
-\subsubsection{Redundancy.}
-\label{sssec:redundancy}
-
-In this section we provide functions and theorems to remove, inside
-a normalized formula, the definitions showed in
-Fig.~\ref{fig:conjunctive-disjunctive-simpl}.
-
-\begin{remark}
-We assume all formulas are in right-associative form in
-the input of the functions by applying a version of $\rm{rdisj}$ or $\rm{rconj}$
-functions for normalized propositions (see Def.~\ref{def:rdisj}).
-\end{remark}
-
-In a disjunction, $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$, we say $ψ ∈_{∨} φ$,
-if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
-$ψ ∈_{∨} φ$ is another name for the equality
-$ψ ≡ \fconjunct_{∨}(φ, ψ)$.
-
-\begin{definition}[rm$_∨$]
-  \label{def:rm-or}
-  \begin{align*}
-    \begin{split}
-      &\frm_{∨} :  \NProp \to \NProp\\
-      &\frm_{∨}(φ) =
-      \begin{cases}
-        \frm_{∨}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
-        φ₁ ∨ rm_{∨}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂\\
-        φ,  &\text{ otherwise.}
-      \end{cases}
-    \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{lemma}[lem-rm$_{∨}$]
-  \label{lem:lem_rm-or}
-  If $Γ ⟝ φ$ then $Γ ⟝ \frm_{∨}(φ)$.
-\end{lemma}
-
-Now, we have removed redundancies in the disjunctions by applying
-$\frm_{∨}$ function, we can define a similar function to work with
-conjunctions, \ie, $\frm_{∧}$.
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∨ φ$}
-  \RightLabel{lem-rm$_∨$,}
-  \UnaryInfC{$Γ ⟝ φ$}
-  \end{bprooftree}
-  \qquad
-  \begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∧ φ$}
-  \RightLabel{lem-rm$_∧$.}
-  \UnaryInfC{$Γ ⟝ φ$}
-  \end{bprooftree}
-\end{equation*}
-
-In a conjunction, $φ = φ₁ ∧ φ₂ ∧ \cdots ∧ φₙ$, we say
-$ψ ∈_{∧} φ$, if there is some $i = 1, \cdots, n$ such that $ψ = φᵢ$.
-We define $ψ ∈_{∧} φ$ as the equality $ψ ≡ \fconjunct(φ, ψ)$.
-
-\begin{definition}[rm$_∧$]
-\label{eq:rm-and}
-  \begin{align*}
-    \begin{split}
-    &\frm_{∧} : \NProp \to \NProp\\
-    &\frm_{∧}(φ) =
-    \begin{cases}
-      rm_{∧}(φ₂),      &\text{ if }φ ≡ φ₁ ∧ φ₂, φ₁ ∈_{∧} φ₂\\
-      φ₁ ∧ rm_{∧}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
-      φ,               &\text{ otherwise.}
-    \end{cases}
-    \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{lemma}[lem-rm$_{∧}$] % (fold)
-  \label{lem:lem_rm-and}
-  If $Γ ⟝ φ$ then $Γ ⟝ \frm_{∧}(φ)$.
-\end{lemma}
-
-Continuing with the rest of tautologies from
-Fig.~\ref{fig:conjunctive-disjunctive-simpl}, we define the
-$\rm{ndisj}_{∨}$ function and $\rm{ndisj}_{∨}$ function that
-take into account the following cases.
-
-\begin{equation*}
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∨ ¬~φ$}
-  \RightLabel{lem-ndisj$_{∨}$,}
-  \UnaryInfC{$Γ ⟝ ⊤$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∨ ⊤$}
-  \RightLabel{lem-ndisj$_{∨}$,}
-  \UnaryInfC{$Γ ⟝ ⊤$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∨ ⊥$}
-  \RightLabel{lem-ndisj$_{∨}$.}
-  \UnaryInfC{$Γ ⟝ φ$}
-\end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∧ ¬~φ$}
-  \RightLabel{lem-ndisj$_{∧}$,}
-  \UnaryInfC{$Γ ⟝ ⊥$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∧ ⊤$}
-  \RightLabel{lem-ndisj$_{∧}$,}
-  \UnaryInfC{$Γ ⟝ φ$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∧ ⊥$}
-  \RightLabel{lem-ndisj$_{∧}$.}
-  \UnaryInfC{$Γ ⟝ ⊥$}
-\end{bprooftree}
-\end{equation*}
-
-\begin{definition}[ndisj$_{∨}$]
-  \label{def:ndisj-or}
-  \begin{align*}
-    \begin{split}
-    &\rm{ndisj}_{∨} : \NProp \to \NProp\\
-    &\rm{ndisj}_{∨}(φ) =
-      \begin{cases}
-        ⊤, &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂,\ φ₁ ∈_{∨} φ₂\\
-        ⊤, &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂,\ \rm{ndisj}_{∨}(φ₂) ≡ ⊤\\
-        ¬ φ₁ ∨ \rm{ndisj}_{∨}(φ₂), &\text{ if }φ ≡ ¬ φ₁ ∨ φ₂\\
-        ⊤, &\text{ if }φ ≡ φ₁ ∨ φ₂,\ ¬φ₁ ∈_{∨} φ₂ \\
-        ⊤, &\text{ if }φ ≡ φ₁ ∨ φ₂,\ \rm{ndisj}_{∨}(φ₂) ≡ ⊤\\
-        φ₁ ∨ \rm{ndisj}_{∨}(φ₂),  &\text{ if }φ ≡ φ₁ ∨ φ₂\\
-        φ, &\text{ otherwise.}
-      \end{cases}
-    \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{lemma}[lem-ndisj$_{∨}$] % (fold)
-  \label{lem:lem_ndisj-or}
-  If $Γ ⟝ φ$ then $Γ ⟝ \rm{ndisj}_{∨}(φ)$.
-\end{lemma}
-
-\begin{definition}[ndisj$_{∧}$]
-  \label{def:ndisj-and}
-  \begin{align*}
-    \begin{split}
-    &\rm{ndisj}_{∧} : \NProp \to \NProp\\
-    &\rm{ndisj}_{∧}(φ) =
-      \begin{cases}
-        ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
-        ⊥, &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂,\ \rm{ndisj}_{∧}(φ₂) ≡ ⊥\\
-        ¬ φ₁ ∧ \rm{ndisj}_{∧}(φ₂), &\text{ if }φ ≡ ¬ φ₁ ∧ φ₂\\
-        ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ φ₁ ∈_{∧} φ₂\\
-        ⊥, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \rm{ndisj}_{∧}(φ₂) ≡ ⊥\\
-        φ₁ ∧ \rm{ndisj}_{∧}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
-        φ, &\text{ otherwise.}
-      \end{cases}
-    \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{lemma}[lem-ndisj$_{∧}$] % (fold)
-  \label{lem:lem_ndisj-and}
-  If $Γ ⟝ φ$ then $Γ ⟝ \rm{ndisj}_{∧}(φ)$.
-\end{lemma}
-
-% subsubsection redundancy (end)
-% -------------------------------------------------------------------
-
-We use the functions defined above to remove redundancies in conjunctions
-with $\fcanon_{∧}$ function, and $\fcanon_{∨}$ function to remove redundancies
-in disjunctions.
-
-\begin{definition}[canon$_{∧}$]
-\label{def:canon-and}
-\begin{align*}
-    \begin{split}
-      &\fcanon_{∧} : \NProp \to \NProp\\
-      &\fcanon_{∧}(φ) =
-        \begin{cases}
-          φⱼ, &\text{ if } φ ≡ φ₁ ∧ φ₂,\ φᵢ ≡ ⊤,\text{ for } i,j = 1,2, i≠j\\
-          ⊥,  &\text{ if } φ ≡ φ₁ ∧ φ₂,\ φᵢ ≡ ⊥,\text{ for } i,j = 1,2\\
-          \frm_∧(\rm{ndisj}_∧(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
-          φ,                &\text{ otherwise.}
-        \end{cases}
-    \end{split}
-\end{align*}
-\end{definition}
-
-\begin{lemma}[lem-canon$_{∧}$]
-  \label{lem:lem_canon-and}
-  If $Γ ⟝ φ$ then $Γ ⟝ \fcanon_{∧}(φ)$.
-\end{lemma}
-
-\begin{definition}[canon$_{∨}$]
-\label{def:canon-or}
-\begin{align*}
-    \begin{split}
-      &\fcanon_{∨} : \NProp \to \NProp\\
-      &\fcanon_{∨}(φ) =
-        \begin{cases}
-        φⱼ, &\text{ if } φ ≡ φ₁ ∨ φ₂,\ φᵢ ≡ ⊥,\text{ for } i,j = 1,2, i≠j\\
-        ⊤,  &\text{ if } φ ≡ φ₁ ∨ φ₂,\ φᵢ ≡ ⊤,\text{ for } i,j = 1,2\\
-        \frm_∨(\rm{ndisj}_∨(φ)), &\text{ if } φ ≡ φ₁ ∧ φ₂\\
-        φ, &\text{ otherwise.}
-        \end{cases}
-    \end{split}
-\end{align*}
-\end{definition}
-
-\begin{lemma}[lem-canon$_{∨}$]
-  \label{lem:lem_canon-or}
-  If $Γ ⟝ φ$ then $Γ ⟝ \fcanon_{∨}(φ)$.
-\end{lemma}
-
-% \begin{remark}
-% A similar treatment defines the $\fcanon_{⊻} : \NProp \to \NProp$.
-% This function removes redundancies related with the exclusive
-% disjunction connective.
-% % Its theorem, thm-canon$_{⊻}$ is presented in~\cite{AgdaMetis}.
-% We left out this description for the brevity of this
-% document and refer the interested reader to \cite{AgdaMetis} for
-% more details.
-% \end{remark}
-
-Finally, we can translate formulas from \Prop to \NProp by defining
-the $\fnnf₀$ function. This function is based on the $\fnnf$ function described in
-\citeauthor{Bezem2002}~\cite{Bezem2002}. Their $\fnnf$ function
-translates formulas to their classical negative normal form. In the
-reference, the authors avoid a termination problem with a similar
-function by using, as an extra argument, the polarity of the formula.
-We follow the same idea in Def.~\ref{def:nnf-zero}.
-Therefore, we need the \abbre{Polarity} type with
-two constructors: $⊕$ to denote positive polarity, and $⊖$ to denote
-negative polarity of the formula.
-
-\begin{definition}[nnf₀]
-\label{def:nnf-zero}
-  \begin{align*}
-    \begin{split}
-    &\fnnf₀ : \abbre{Polarity} \to \Prop \to \NProp\\
-    &\fnnf₀(⊕, φ) =
-      \begin{cases}
-      \fcanon_{∧}(\fnnf₀(⊕, φ₁) ∧ \fnnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
-      \fcanon_{∨}(\fnnf₀(⊕, φ₁) ∨ \fnnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
-      \fcanon_{∨}(\fnnf₀(⊖, φ₁) ∨ \fnnf₀(⊕, φ₂)), &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
-      \fnnf₀(⊖, φ₁),                              &\text{ if }φ ≡ ¬ φ₁ \\
-      φ,                                          &\text{ otherwise.} \\
-      \end{cases}\\
-    &\fnnf₀(⊖, φ) =
-      \begin{cases}
-      \fcanon_{∨}(\fnnf₀(⊖, φ₁) ∨ \fnnf₀(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∧ φ₂ \\
-      \fcanon_{∧}(\fnnf₀(⊖, φ₁) ∧ \fnnf₀(⊖, φ₂)),  &\text{ if }φ ≡ φ₁ ∨ φ₂ \\
-      \fcanon_{∧}(\fnnf₀(⊖, φ₂) ∧ \fnnf₀(⊖, φ₁)),  &\text{ if }φ ≡ φ₁ ⇒ φ₂ \\
-      \fnnf₀(⊕, φ₁),                               &\text{ if }φ ≡ ¬ φ₁ \\
-      ⊥,                                           &\text{ if }φ ≡ ⊤ \\
-      ⊤,                                           &\text{ if }φ ≡ ⊥ \\
-      φ,                                           &\text{ otherwise.} \\
-      \end{cases}
-    \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{lemma}[lem-nnf]
-  \label{lem:lem-nnf}
-  If $Γ ⊢ φ$ then $Γ ⟝ \fnnf~φ$ where,
-  \begin{align*}
-   \begin{split}
-     &\fnnf : \NProp \to \NProp\\
-     &\fnnf~φ = \fnnf₀(⊕, φ).
-   \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{lemma}[lem-dist$_{∨}$]
-  \label{lem:lem-dist-or}
-  $Γ ⟝ φ$ then $Γ ⟝ \fdist_{∨}(φ)$, where,
-  \begin{align*}
-    \begin{split}
-    &\fdist_{∨} : \Prop \to \Prop\\
-    &\fdist_{∨}(φ) =
-      \begin{cases}
-        \fdist_{∨}(φ₁ ∨ φ₂) ∧ \fdist_{∨}(φ₂ ∨ φ₃), &\text{ if }φ ≡ (φ₁ ∧ φ₂) ∨ φ₃\\
-        \fdist_{∨}(φ₁ ∨ φ₃) ∧ \fdist_{∨}(φ₁ ∨ φ₃), &\text{ if }φ ≡ φ₁ ∨ (φ₂ ∧ φ₃)\\
-        φ,                                     &\text{ otherwise.}
-      \end{cases}
-    \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{lemma}[lem-dist]
-  \label{lem:lem-dist}
-  $Γ ⟝ φ$ then $Γ ⟝ \fdist(φ)$, where,
-  \begin{align*}
-      \begin{split}
-      &\fdist : \Prop \to \Prop\\
-      &\fdist(φ) =
-        \begin{cases}
-          \fdist(φ₁) ∧ \fdist(φ₂),
-            &\text{ if }φ ≡ φ₁ ∧ φ₂\\
-          \fdist_{∨}(\fdist(φ₁) ∨ \fdist(φ₂)),
-            &\text{ if }φ ≡ φ₁ ∨ φ₂\\
-          φ, &\text{ otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align*}
-\end{lemma}
-
-\begin{sketchproof} If $φ ≡ φ₁ ∨ φ₂$, we get for $i = 1, 2$,
-\begin{equation*}
-  \begin{bprooftree}
-    \RightLabel{assume}
-    \AxiomC{$Γ, φ_{i} ⊢ φ_{i}$}
-    \RightLabel{lem-dist}
-    \UnaryInfC{$Γ ⊢ \fdist(φ_{i})$}
-    \RightLabel{∨-intro$_{1,2}$}
-    \UnaryInfC{$Γ, φ_{i} ⊢ \fdist(φ₁) ∨ \fdist(φ₂)$}
-    \RightLabel{lem-dist$_{∨}$.}
-    \UnaryInfC{$Γ, φ_{i} ⊢ \fdist_{∨}(\fdist(φ₁) ∨ \fdist(φ₂))$}
-    \end{bprooftree}
-\end{equation*}
-Then, by using the ∨-elim rule in the last derivation above, we
-derive $Γ, φ₁ ∨ φ₂ ⟝ \fdist_{∨}(\fdist(φ₁) ∨ \fdist(φ₂))$ and the lemma
-follows.
-\end{sketchproof}
-
-To convert normalized propositions to classical propositions, we
-make the following definition, completing the translation between
-these two types.
-
-\begin{definition}[form]
-\begin{align*}
-    \begin{split}
-      &\rm{form} : \NProp \to \Prop\\
-      &\rm{form}(φ) =
-      \begin{cases}
-        \rm{form}(φ₁) ∧ \rm{form}(φ₂), &\text{ if }φ ≡ φ₁ ∧ φ₂\\
-        \rm{form}(φ₁) ∨ \rm{form}(φ₂), &\text{ if }φ ≡ φ₁ ∨ φ₂\\
-        \rm{form}_{⊻}(φ₂),        &\text{ if }φ ≡ φ₁ ⊻ φ₂\\
-        φ, &\text{ otherwise.}\\
-      \end{cases}
-    \end{split}
-\end{align*}
-\end{definition}
-
-\begin{lemma}[lem-form]
-  \label{lem:lem-form}
-   If $Γ ⟝ φ$ then $Γ ⊢ \rm{form}(φ)$.
-\end{lemma}
-
-As a result, we can get a conjunctive normal form by applying the
-following theorem.
-
-\begin{theorem}[thm-cnf]
-\label{thm:thm-cnf}
-  If $Γ ⊢ φ$ then $Γ ⊢ \rm{cnf}(φ)$, where,
-  \begin{align*}
-    \begin{split}
-    &\rm{cnf} : \Prop \to \Prop\\
-    &\rm{cnf} = \rm{form} ∘ \fdist ∘ \fnnf.
-    \end{split}
-  \end{align*}
-\end{theorem}
-
-\begin{proof}
-  Composition of the Lemmas \ref{lem:lem-form}, \ref{lem:lem-dist}
-  and \ref{lem:lem-nnf}.
-\end{proof}
-
-Since all the previous transformations came from  equivalences in  the
-classical propositional logic, the following theorem plays an important role
-in the next section.
-
-\begin{theorem}[thm-inv-cnf]
-\label{thm:thm-inv-cnf}
-  If $Γ ⊢ \rm{cnf}(φ)$ then $Γ ⊢ φ$.
-\end{theorem}
-
-% subsubsection normal_forms (end)
-% --------------------------------------------------------------------
-
-% -------------------------------------------------------------------
-\subsubsection{Canonicalize.}
-\label{sssec:canonicalize}
-
-The \canonicalize rule is an overloaded inference rule which performs
-normalization of the proposition input.
-This rule converts a \texttt{fof} %TODO
-formula in clausal form to a \CNF clause but also it performs some
-simplifications in the process (e.g., removing ⊤ and ⊥ in the formula).
-
-Since this rule mostly consists of dealing with \CNF clauses, to
-justify its reasoning, our strategy mainly consists of checking the
-equality of normalized negative form between the source and the
-target formula. If it fails, we try to reorder the conjunctive
-normal form of the source formula to match with
-the conjunctive normal form of the target formula.
-
-\begin{definition}[canonicalize]
-  \label{def:canonicalize}
-  \begin{align*}
-    \begin{split}
-      &\fcanonicalize : \Prop \to \Prop \to \Prop\\
-      &\fcanonicalize(φ, ψ) =
-      \begin{cases}
-        ψ, &\text{ if }ψ ≡ φ\\
-        ψ, &\text{ if }ψ ≡ \fform(\fnnf~φ)\\
-        ψ, &\text{ if }\fcnf~ψ ≡ \freorder_{∧∨}(\fcnf~φ, \fcnf~ψ)\\
-        φ, &\text{ otherwise.}\\
-      \end{cases}
-    \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{theorem}[thm-canonicalize] % (fold)
-  \label{thm:thm-canonicalize}
-  \hspace{4mm}\\
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fcanonicalize(φ, ψ)$.
-\end{theorem}
-
-\begin{proof}\hspace{3mm}
-\begin{itemize}
-\item If $φ ≡ ψ$ by substitution theorem we conclude $Γ ⊢ ψ$.
-\item If $ψ ≡ \fform(\fnnf~φ)$,
-\begin{equation*}
-  \begin{bprooftree}
-    \AxiomC{$Γ ⊢ φ$}
-    \RightLabel{lem-nnf}
-    \UnaryInfC{$Γ ⊢₂~\fnnf~φ$}
-    \RightLabel{lem-form}
-    \UnaryInfC{$Γ ⊢ \fform(\fnnf~φ)$}
-    \AxiomC{$ψ ≡ \fform(\fnnf~φ)$}
-    \RightLabel{subst.}
-    \BinaryInfC{$Γ ⊢ ψ$}
-  \end{bprooftree}
-\end{equation*}
-
-\item If $γ = \fcnf~ψ ≡ \freorder_{∧∨}~(\fcnf~φ)~(\fcnf~ψ)$,
-  \begin{equation*}
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ$}
-      \RightLabel{thm-cnf}
-      \UnaryInfC{$Γ ⊢ \fcnf~φ$}
-      \RightLabel{thm-reorder$_{∧∨}$}
-      \UnaryInfC{$Γ ⊢ \freorder_{∧∨}(\fcnf~φ, \fcnf~ψ)$}
-      \AxiomC{$γ$}
-      \RightLabel{subst}
-      \BinaryInfC{$Γ ⊢ \fcnf~ψ$}
-      \RightLabel{thm-inv-cnf.}
-      \UnaryInfC{$Γ ⊢ ψ$}
-    \end{bprooftree}
-  \end{equation*}
-\end{itemize}
-\end{proof}
-
-% subsubsection canonicalize (end)
-% -------------------------------------------------------------------
-
-\subsubsection{Clausification.}
-\label{sssec:clausification}
-
-The \clausify rule transforms a
-propositional formula into its clausal normal form, a conjunction
-of clauses. A \emph{clause} is the disjunction of zero or more
-literals and a \emph{literal} is an atom (positive literal) or a
-negation of an atom (negative literal).
-It is important to notice that this kind of conversion
-between one formula to its clausal normal form is not unique, and \Metis has a
-customized approach to perform that transformation. That is the reason we
-perform some reordering for the CNF of the source formula to fulfill this
-issue.
-
-In the following \Metis \TSTP derivation, we see an example where
-\clausify expands the formula \texttt{normalize\_0\_0} by using distributive
-laws presented in conjunctive normal form conversion.
-
-\begin{verbatim}
-fof(a1, axiom, (p => (q & r))).
-...
-fof(normalize_0_0, plain, (~ p | (q & r)),
-    inference(canonicalize, [], [a1])).
-fof(normalize_0_1, plain, ((~ p | q) & (~ p | r)),
-    inference(clausify, [], [normalize_0_0])).
-\end{verbatim}
-
-\begin{definition}[clausify]
-  \label{def:clausify}
- \begin{align*}
-   \begin{split}
-      &\fclausify : \Prop → \Prop → \Prop\\
-      &\fclausify~φ~ψ =
-      \begin{cases}
-        ψ, &\text{ if }φ≡ψ\\
-        \freorder_{∧∨}~(\fcnf~φ~ψ), &\text{ otherwise.}
-      \end{cases}
-      \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{theorem}[thm-clausify]
-\label{thm:thm-clausify}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fclausify~φ~ψ$.
-\end{theorem}
-
-\begin{proof} If $φ ≡ ψ$, this lemmas follows after applying $\fsubst$
-lemma. Otherwise, we use Theorem~\ref{thm:thm-reorder-and-or} and Theorem~\ref{thm:thm-cnf}.
-\end{proof}
-
-\begin{remark}
-The \clausify rule is often preceded by the \canonicalize rule.
-Both rules perform \emph{Clausification} that introduces
-into the problem axioms or definitions in the domain of the solution.
-The Clausification algorithms is mainly described on paper by
-\citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}. We left for future work
-investigate the consequences of removing $clausify$ inference by
-strengthen $canonicalize$ rule in Def.~\ref{def:canonicalize}
-\end{remark}
-
-% subsubsection clausification (end)
-% --------------------------------------------------------------------
-
-% -------------------------------------------------------------------
-\subsubsection{Simplification.}
-\label{sssec:simplify}
-
-The \simplify rule is an inference that performs simplification of
-definitions and tautologies. This rule
-transverses a list of previous derivations by applying different theorems
-(e.g., \emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
-syllogism}) to get a contradiction in the first place, or a smaller
-convenient formula
-
-% To emulate this rule, we use theorems from Section~\ref{sssec:canonicalize},
-% Section~\ref{sssec:conjunct}.
-The following \TSTP excerpt is an example of the \simplify rule.
-
-% \begin{figure}
-\begin{verbatim}
-fof(normalize_0_1, plain, (g | (~ a & k)),
-    inference(conjunct, [], [normalize_0_0])).
-fof(normalize_0_2, plain, (~ g | q),
-    inference(conjunct, [], [normalize_0_0])).
-fof(normalize_0_3, plain, (~ q),
-  inference(conjunct, [], [normalize_0_0])).
-fof(normalize_0_4, plain, (~ g),
-    inference(simplify, [], [normalize_0_2, normalize_0_3])).
-fof(normalize_0_5, plain, (~ k),
-inference(conjunct, [], [normalize_0_0])).
-fof(normalize_0_6, plain, ($false),
-    inference(simplify, [],
-              [normalize_0_1, normalize_0_4, normalize_0_5])).
-\end{verbatim}
-% \caption{Example of \simplify rule in a \TSTP derivation of \Metis.}
-% \end{figure}
-
-%TODO check canonicalize can reduce a conjunction into one smaller.
-\begin{definition}[simplify]
-\label{def:simplify}
-For $i,\, j = 1, 2$, $i\neq j$ and $γ : \Prop$,
-\begin{align*}
-    \begin{split}
-      &\fsimplify : \Prop → \Prop → \Prop → \Prop\\
-      &\fsimplify(φ₁, φ₂, ψ) =%\\
-      % &\hspace{4mm}
-      \begin{cases}
-        ψ,          &\text{ if }φᵢ ≡ ψ\\
-        ⊥,          &\text{ if }φᵢ ≡ ⊥\\
-        φⱼ,         &\text{ if }φᵢ ≡ ⊤\\
-        γ,          &\text{ if }φᵢ ≡ φⱼ ⇒ γ\\
-        γ,          &\text{ if }φᵢ ≡ γ ⇒ \fnnf(¬ φⱼ)\\
-        γ,          &\text{ if }φᵢ ≡ \fnnf(¬ φⱼ) ∨ γ\\
-        ⊥,          &\text{ if } \fnnf(¬ φⱼ) ≡ \fconjunct(φᵢ, \fnnf(¬ φⱼ))\\
-      % φ          &\text{ if }\fconjunct(nnf(¬ φᵢ), φⱼ) ≡  φⱼ\\
-        ⊥,          &\text{ if } ¬ φⱼ ≡ \fcanonicalize(φᵢ, ¬ φⱼ) \\
-        φ₁,         &\text{ otherwise.}\\
-      \end{cases}%\hspace{10cm}
-    \end{split}
-\end{align*}
-\end{definition}
-
-\begin{remark}
-Besides the fact that $\List\ \Prop \to \Prop$ is the type that coincides
-with the \simplify rule in \TSTP derivations, we choose a different
-option. In the translation from \TSTP to \Agda, we take the list of
-derivations and use a classical left folding ($\rm{foldl}$) with
-$\fsimplify$ function over the list of $φ₁, φ₂, \cdots, φₙ$
-that avoids us to define a new sequent type to
-support \List \Prop type in the conclusion side.
-\end{remark}
-
-\begin{theorem}[thm-simplify] % (fold)
-  \label{thm:thm-simplify}
-For $i=1,\, 2, \cdots, n$, $Γ ⊢ φᵢ$ and $ψ : \Prop$ then
-if $n > 2$, $Γ ⊢ \fsimplify(γ_{n-2}, φ_{n}, ψ)$ where $γ_{i} = \fsimplify(φ_{i}, φ_{i+1}, ψ)$
-else $Γ ⊢ \fsimplify(φ₁, φ₂, ψ)$.
-\end{theorem}
-
-% \begin{sketchproof}
-% If $Γ ⊢ φᵢ$ for $i=1, \cdots, n$, we prove this theorem by induction on $n$.
-% Let us show one case.
-% \begin{itemize}
-%   \item If $n ==2$ and $(canonicalize(φ₁, ¬ φ₂) ≡ ¬ φ₂)$, we need to prove
-%   $Γ ⊢ simplify(φ₁, φ₂, ψ)$.
-% \begin{equation*}
-%   \begin{bprooftree}
-%     \AxiomC{$Γ ⊢ φ₁$}
-%     \RightLabel{thm-canonicalize}
-%     \UnaryInfC{$Γ ⊢ canonicalize(φ₁, ¬φ₂)$}
-%     \AxiomC{$¬ φ₂ ≡ canonicalize(φ₁, ¬ φ₂)$}
-%     \RightLabel{subst}
-%     \BinaryInfC{$Γ ⊢ ¬ φ₂ $}
-%   \end{bprooftree}
-%   \begin{bprooftree}
-%   \AxiomC{$Γ ⊢ ¬ φ₂ $}
-%   \AxiomC{$Γ ⊢ φ₂$}
-%   \RightLabel{¬-elim}
-%   \BinaryInfC{$Γ ⊢ ⊥$}
-%   \RightLabel{by def.}
-%   \UnaryInfC{$Γ ⊢ simplify(φ₁, φ₂, ψ)$}
-%   \end{bprooftree}
-% \end{equation*}
-
-% \end{itemize}
-% \end{sketchproof}
-
-% subsubsection simplify (end)
-% -------------------------------------------------------------------
+% ------------------------------------------------------------------------------
 

### 2017-10-22 paper/sections/proof-reconstruction/clausify.tex
[ paper ] rules in distinct files.

\documentclass[../../main.tex]{subfiles}
\begin{document}

\subsubsection{Clausification.}
\label{sssec:clausification}

The \clausify rule transforms a
propositional formula into its clausal normal form, a conjunction
of clauses. A \emph{clause} is the disjunction of zero or more
literals and a \emph{literal} is an atom (positive literal) or a
negation of an atom (negative literal).
It is important to notice that this kind of conversion
between one formula to its clausal normal form is not unique, and \Metis has a
customized approach to perform that transformation. That is the reason we
perform some reordering for the CNF of the source formula to fulfill this
issue.

In the following \Metis \TSTP derivation, we see an example where
\clausify expands the formula \texttt{normalize\_0\_0} by using distributive
laws presented in conjunctive normal form conversion.

\begin{verbatim}
fof(a1, axiom, (p => (q & r))).
...
fof(normalize_0_0, plain, (~ p | (q & r)),
    inference(canonicalize, [], [a1])).
fof(normalize_0_1, plain, ((~ p | q) & (~ p | r)),
    inference(clausify, [], [normalize_0_0])).
\end{verbatim}

\begin{definition}[clausify]
  \label{def:clausify}
 \begin{align*}
   \begin{split}
      &\fclausify : \Prop → \Prop → \Prop\\
      &\fclausify~φ~ψ =
      \begin{cases}
        ψ, &\text{ if }φ≡ψ\\
        \freorder_{∧∨}~(\fcnf~φ~ψ), &\text{ otherwise.}
      \end{cases}
      \end{split}
  \end{align*}
\end{definition}

\begin{theorem}[thm-clausify]
\label{thm:thm-clausify}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fclausify~φ~ψ$.
\end{theorem}

\begin{proof} If $φ ≡ ψ$, this lemmas follows after applying $\fsubst$
lemma. Otherwise, we use Theorem~\ref{thm:thm-reorder-and-or} and Theorem~\ref{thm:thm-cnf}.
\end{proof}

\begin{remark}
The \clausify rule is often preceded by the \canonicalize rule.
Both rules perform \emph{Clausification} that introduces
into the problem axioms or definitions in the domain of the solution.
The Clausification algorithms is mainly described on paper by
\citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}. We left for future work
investigate the consequences of removing $clausify$ inference by
strengthen $canonicalize$ rule in Def.~\ref{def:canonicalize}
\end{remark}

\end{document}

### 2017-10-22 paper/sections/proof-reconstruction/conjunct.tex
[ paper ] rules in distinct files.

\documentclass[../../main.tex]{subfiles}
\begin{document}

\subsubsection{Splitting a conjunct.}
\label{sssec:splitting-a-conjunct}

The \conjunct rule extracts from a
conjunction one of its conjuncts. This rule is a generalization of the
projection rules for the conjunction connective as the
following \TSTP excerpt shows.

\begin{verbatim}
fof(normalize_1, plain, p & q & (r | ~ p),
  inference(canonicalize, [], [x])).
fof(normalize_2, plain, q,
  inference(conjunct, [], [normalize_1])).
fof(normalize_2, plain, (r | ~ p),
  inference(conjunct, [], [normalize_1])).
\end{verbatim}

\begin{definition}[conjunct]
  \label{def:conjunct}
  \begin{align*}
    \begin{split}
    &\fconjunct : \Prop \to \Prop \to \Prop\\
    &\fconjunct(φ, ψ) =
      \begin{cases}
          ψ, &\text{ if }φ ≡ ψ\\
          ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ \fconjunct(φ₁, ψ)\\
          ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ \fconjunct(φ₂, ψ)\\
          φ, &\text{ otherwise.}
        \end{cases}
    \end{split}
  \end{align*}
\end{definition}

\begin{theorem}[thm-conjunct]
  \label{thm:thm-conjunct}
  If $Γ ⊢ φ$ and $ψ  : \Prop$ then $Γ ⊢ \fconjunct(φ, ψ)$.
\end{theorem}
\begin{proof}\hspace{2cm}
\begin{itemize}
  \item For the case $φ ≡ ψ$, $Γ ⊢ \fconjunct(φ, ψ)$ normalizes to $Γ ⊢ ψ$.
Then, we get the desire conclusion by applying the $\fsubst$ theorem.
  \item If the proposition $φ$ is a conjunction, and we can get $ψ ≡ \fconjunct(φ_{i}, ψ)$ for some $i = 1,\ 2$, then,

\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
  \RightLabel{∧-proj$_{i}$}
  \UnaryInfC{$Γ ⊢ φ_{i}$}
  \UnaryInfC{$Γ ⊢ \fconjunct(φ_{i}, ψ)$}
  \AxiomC{$ψ ≡ \fconjunct(φ_{i}, ψ)$}
  \RightLabel{subst.}
  \BinaryInfC{$Γ ⊢ ψ$}
  \end{bprooftree}
\end{equation*}
\item The last case follows trivially by using the same hypothesis.
\end{itemize}
\end{proof}
\end{document}

### 2017-10-22 paper/sections/proof-reconstruction/negate.tex
[ paper ] rules in distinct files.

\documentclass[../../main.tex]{subfiles}
\begin{document}

\subsubsection{Negating subgoals.}
\label{sssec:negate}

Each proof of a subgoal is a refutation, thereby each proof assumes
the negation of its subgoal. The \negate rule
assumes the negation of such subgoals, and
appears after applying the \strip inference to the goal.

\begin{verbatim}
fof(goal, conjecture, (p & q)).
fof(subgoal_0, plain, (p), inference(strip, [], [goal])).
fof(subgoal_1, plain, (p => q), inference(strip, [], [goal])).
fof(negate_0_0, plain, (~ p), inference(negate, [], [subgoal_0])).
\end{verbatim}

To emulate this rule, we introduce the negation
of the subgoal by using $assume$ rule from the inferences in
Fig.~\ref{fig:CPL-inference-rules}.

\end{document}

### 2017-10-22 paper/sections/proof-reconstruction/resolve.tex
[ paper ] rules in distinct files.

\documentclass[../../main.tex]{subfiles}
\begin{document}

\subsubsection{Resolution.}
\label{sssec:resolve}

Logic equivalence between propositions is a major issue to justify
prover reasoning steps. Since we left out semantics to treat only the
syntax aspects of the propositions, our approach shows equivalence
by converting propositions to their conjunctive normal forms,
and reordering those and the inner disjunctions  to match them
In this section, we provide some theorems to perform such reordering tasks,
the goals are the following.

\begin{itemize}
  \item Reorder a disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$ to match with
$ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$. For all $i$, there exists at least one $j$ such
that $φᵢ ≡ ψⱼ$.
  \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another
CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$. For all $i$, there exists at least one $j$
such that $φᵢ ≡ ψⱼ$.
\end{itemize}

First, we define the $\rm{rdisj}$ function to convert
a disjunction in its right-associative form.
The $\rm{rconj}$ function that converts conjunction to its right-associative form
is not presented here, but is defined in a similar way (see its implementation
in~\cite{AgdaMetis}).

\begin{definition}[rdisj]
\label{def:rdisj}
  \begin{align*}
    \begin{split}
    \label{eq:rdisj-def}
      &\rm{rdisj}(φ) : \Prop \to \Prop\\
      &\rm{rdisj}(φ) =
      \begin{cases}
      \rm{rdisj}(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{ if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
      φ₁ ∨ \rm{rdisj}(φ₂),         & \text{ if } φ ≡ φ₁ ∨ φ₂\\
      φ,                      & \text{ otherwise.}
      \end{cases}
    \end{split}
  \end{align*}
\end{definition}

\begin{lemma}[lem-rdisj]
\label{lem:lem-rdisj}
  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rdisj}(φ)$.
\end{lemma}

\begin{definition}[build$_{\boldsymbol{∨}}$]
\begin{equation*}
  \begin{split}
  \label{eq:build-or}
  &\rm{build}_{∨} : \Prop → \Prop → \Prop\\
  &\rm{build}_{∨}(φ, ψ) =%\\
  % &\hspace{3mm}
  \begin{cases}
  ψ, &\text{ if } φ ≡ ψ\\
  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{, } \rm{build}_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
  φ, &\text{ otherwise.}
  \end{cases}
  \end{split}
\end{equation*}
\end{definition}

The $\rm{build}_{∨}$ function defined above intends to construct a
disjunction from another disjunction, specifically, this functions will
try to rearrange the disjuncts in the source formula to match with the
target disjunction formula, similar as we describe above.

\begin{lemma}[lem-build$_{\boldsymbol{∨}}$]
\label{lem:lem-build-or}
If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}(φ)$.
\end{lemma}

From now, we assume all propositions to be right-associative unless
otherwise stated.
The $\ffactor$ function in Eq.~(\ref{eq:factor-definition}) intends to
simplify a special case of disjunction, the repeated disjuncts
(e.g., $\ffactor(φ ∨ φ) \mapsto\ φ$).
Notice that other cases like $φ ∨ (ψ ∨ φ)$ do no reduce to $(ψ ∨ φ)$.

\begin{definition}[factor]
\begin{align}
\begin{split}
  \label{eq:factor-definition}
  &\ffactor : \Prop → \Prop\\
  &\ffactor(φ) =
  \begin{cases}
    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{, } φ₁ ≡ \ffactor(φ₂)\\
    φ,   &\text{ otherwise.}
  \end{cases}
\end{split}
\end{align}
\end{definition}

\begin{lemma}[lem-factor]
\label{lem:lem-factor}
  $Γ ⊢ φ$ then $Γ ⊢ \ffactor(φ)$.
\end{lemma}

To construct a disjunction $ψ$ from a disjunction $φ$, we have used ideas
from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove
equality between nested disjunctions.
The result is the $\rm{sbuild}_{∨}$ function
that uses every disjunct from the source formula, $φ$, to build up the
target disjunction $ψ$.

\begin{definition}[sbuild$_{\boldsymbol{∨}}$]
\begin{align*}
  \begin{split}
  \label{eq:strong-build-or-definition}
    &\rm{sbuild}_{∨} : \Prop → \Prop → \Prop\\
    &\rm{sbuild}_{∨}(φ, ψ) =%\\
    % &\hspace{3mm}
    \begin{cases}
      \ffactor(\rm{build}_{∨}(φ₁, ψ) ∨ \rm{build}_{∨}(φ₂,ψ)),
      &\text{ if }φ≡ φ₁ ∨ φ₂\\
      \rm{build}_{∨}(φ, ψ),  & \text{ otherwise.}
    \end{cases}
  \end{split}
\end{align*}
\end{definition}

\begin{lemma}[lem-sbuild$_{\boldsymbol{∨}}$]
\label{lem:lem-sbuild-or}
If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}(φ, ψ)$.
\end{lemma}

\begin{example}
Let see the main idea behind the lem-sbuild$_{∨}$ lemma.
We build the disjunction $((p ∨ q) ∨ r)$ from the disjunction
$(r ∨ (q ∨ p))$.
\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$Γ ⊢ q$}
  \RightLabel{∨-intro₂}
  \UnaryInfC{$Γ ⊢ p ∨ q$}
  \RightLabel{∨-intro₁}
  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}

  \AxiomC{$Γ ⊢ p$}
  \RightLabel{∨-intro₁}
  \UnaryInfC{$Γ ⊢ p ∨ q$}
  \RightLabel{∨-intro₁}
  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}

  \RightLabel{∨-elim}
  \BinaryInfC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
  \end{bprooftree}
\end{equation*}

\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$Γ ⊢ r$}
  \RightLabel{∨-intro₂}
  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}

  \AxiomC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}

  \RightLabel{∨-elim}
  \BinaryInfC{$Γ, r ∨ (q ∨ p) ⊢ (p ∨ q) ∨ r$}

  \RightLabel{⇒-intro}
  \UnaryInfC{$Γ ⊢ r ∨ (q ∨ p) ⇒ (p ∨ q) ∨ r$}

  \end{bprooftree}
\end{equation*}
\end{example}

Notice that using $\rm{sbuild}_{∨}$ we can build not only a disjunction
with the same disjuncts of the source formula but also a complete different
formula by adding new disjuncts to the source formula.

\begin{definition}[reorder$_{\boldsymbol{∨}}$]
\begin{align*}
    \label{eq:reorder-or}
    \begin{split}
    &\freorder_{∨} : \Prop \to \Prop \to \Prop\\
    &\freorder_{∨} (φ, ψ) = \rm{sbuild}_{∨}(rdisj(φ), ψ).
    \end{split}
  \end{align*}
\end{definition}

\begin{theorem}[thm-reorder$_{\boldsymbol{∨}}$]
  \label{thm-reorder-or}
  If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}(φ, ψ)$.
\end{theorem}

\begin{proof}
Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
\end{proof}

We define similar functions and state some theorems as we previously did
for disjunctions, but instead, we treat only with conjunctive normal forms.

\begin{definition}[reorder$_{\boldsymbol{∧}}$]
  \begin{align*}
      \begin{split}
        &\freorder_{∧} : \Prop → \Prop \to \Prop\\
        &\freorder_{∧}(φ, ψ) =
        \begin{cases}
          φ, &\text{ if }φ ≡ ψ\\
          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\freorder_{∧}(φ, ψ₁) ≡ ψ₁\\
                  &\text{and }\freorder_{∧}(φ, ψ₂)≡ ψ₂\\
          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct(φ, ψ), &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{definition}

\begin{lemma}[lem-reorder$_{\boldsymbol{∧}}$]
  \label{lem:lem-reorder-and}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}(φ, ψ)$.
\end{lemma}

\begin{definition}[conjunct$_{\boldsymbol{∨}}$]
  \label{eq:conjunct-or-definition}
\begin{align*}
  \begin{split}
    &\fconjunct_{∨} : \Prop → \Prop \to \Prop\\
    &\fconjunct_{∨}(φ, ψ) =
    \begin{cases}
      ψ, &\text{ if }φ ≡ ψ\\
      ψ, &\text{ if }\freorder_{∨}(φ, ψ) ≡ ψ\\
      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ \fconjunct_{∨}(φ, ψ₁) ≡ ψ₁,\\
        &\text{and } \freorder_{∨}(φ, ψ₂) ≡ ψ₂\\
      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}(φ₁, ψ) ≡ ψ\\
      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}(φ₂, ψ) ≡ ψ\\
      φ, &\text{ otherwise.}
    \end{cases}
  \end{split}
  \end{align*}
\end{definition}

\begin{lemma}[lem-conjunct$_{\boldsymbol{∨}}$]
  \label{lem:lem-conjunct-or}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}(φ, ψ)$.
\end{lemma}

\begin{definition}[reorder$_{\boldsymbol{∧∨}}$]
 \begin{align*}
      \begin{split}
      &\freorder : \Prop \to \Prop \to \Prop\\
      &\freorder_{∧∨}(φ, ψ)=
        \begin{cases}
          ψ, &\text{ if } φ≡ψ\\
          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ \freorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
             &\text{and }\freorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
          φ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct_{∨}(φ, ψ) &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
  \end{definition}

\begin{theorem}[thm-reorder$_{\boldsymbol{∧∨}}$]
  \label{thm:thm-reorder-and-or}
  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$.
\end{theorem}

The \resolve rule incorporates the resolution theorem showed in
Fig.~\ref{fig:metis-inferences} for the \TSTP derivations.
This rule posses three arguments: a positive literal $l$ to apply the
resolution theorem, and two derivations.
The positive literal $l$ must occur in
the formula from the first derivation and the
negative literal must occur in the formula from the second derivation,
see the pattern of \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.

% \begin{figure}
\label{fig:resolve-tstp-example}
\begin{verbatim}
cnf(refute_0_4, plain, (~ r | p | q),
    inference(canonicalize, [], [normalize_0_5])).
cnf(refute_0_5, plain, (p | q | r),
    inference(canonicalize, [], [normalize_0_6])).
cnf(refute_0_6, plain, (p | q),
    inference(resolve, [$cnf(r)], [refute_0_5, refute_0_4])).
\end{verbatim}
% \caption{Excerpt of a \Metis \TSTP example for the \resolve rule.}
% \end{figure}

To emulate this rule, we perform a sequence of rearrangements inside the
formulas involved to match with the pattern expected by the resolution theorem
described above. We begin by defining a convenient version of
the binary resolution in Def.~\ref{def:rsol}.

\begin{definition}[rsol]
\label{def:rsol}
\begin{align*}
      \begin{split}
        &\rm{rsol} : \Prop \to \Prop\\
        &\rm{rsol}(φ) =
        \begin{cases}
          φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
          φ, &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align*}
\end{definition}

\begin{lemma}[lem-rsol]
  \label{lem:lem-rsol}
  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}(φ)$.
\end{lemma}

In Def.~\ref{def:resolve}, the proposed rule for $resolve$
has four arguments. The first three were described
above, the last one, ψ, represents the expected conclusion in the \Metis
derivation.

\begin{definition}[resolve]
\label{def:resolve}
 \begin{align*}
 \begin{split}
    &\fresolve : \Prop \to \Prop \to \Prop \to \Prop \to \Prop\\
    &\fresolve(φ₁, φ₂, l, ψ) =
      \rm{rsol}(\freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨} (φ₂, ¬ l ∨ ψ)).
  \end{split}
  \end{align*}
\end{definition}

\begin{theorem}[thm-resolve]
  \label{thm:thm-resolve}
  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ : \Prop$ then
  $Γ ⊢ \fresolve(φ₁, φ₂, l, ψ)$.
\end{theorem}
\Needspace{3\baselineskip}
\begin{proof}
 \begin{equation*}
    \begin{bprooftree}
      \AxiomC{$Γ ⊢ φ₁$}
      \RightLabel{thm-reorder$_{∨}$,}
      \UnaryInfC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ)$}
   \end{bprooftree}
  \end{equation*}
    \vskip 1.5mm
 \begin{equation*}
    \begin{bprooftree}
      \AxiomC{$Γ ⊢ φ₂$}
      \RightLabel{thm-reorder$_{∨}$,}
      \UnaryInfC{$Γ ⊢ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
   \end{bprooftree}
  \end{equation*}
  \vskip 1.5mm
  \begin{equation*}
  \begin{bprooftree}
    \AxiomC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ)$}
    \AxiomC{$Γ ⊢ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
    \RightLabel{∧-intro}
    \BinaryInfC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
    \RightLabel{lem-rsol.}
    \UnaryInfC{$Γ ⊢ \rm{rsol}(\freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨}(φ₂, ¬ l ∨ ψ))$}
  \end{bprooftree}
  \end{equation*}
\end{proof}

\begin{figure}
\label{fig:resolve-example}
\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$Γ ⊢ ¬ r ∨ p ∨ q$}
  \AxiomC{$Γ ⊢ p ∨ q ∨ r $}
  \RightLabel{thm-resolve}
  \BinaryInfC{$Γ ⊢ \fresolve(¬ r ∨ p ∨ q, p ∨ q ∨ r, r, p ∨ q)$}
  \UnaryInfC{$Γ ⊢ p ∨ q$}
  \end{bprooftree}
\end{equation*}
\caption{Example of a resolution in \Metis using
Thm.~\ref{thm:thm-resolve}.}
%Application of Thm.~\ref{thm:thm-resolve} for the \TSTP excerpt Fig.~\ref{fig:resolve-tstp-example}.}
\end{figure}

\end{document}

### 2017-10-22 paper/sections/proof-reconstruction/strip.tex
[ paper ] rules in distinct files.

\documentclass[../../main.tex]{subfiles}
\begin{document}

\subsubsection{Stripping a goal.}
\label{sssec:strip-a-goal}

To prove a goal, \Metis splits the goal into
disjoint cases. This process produces a list of new subgoals, the
conjunction of these subgoals implies the goal. Then, a proof of the
goal becomes, in smaller proofs, one refutation for each subgoal.
These subgoals are introduced in the \TSTP derivation with the \strip
inference rule as we show in the following excerpt.

\begin{verbatim}
fof(goal, conjecture, ((p & r) & q)).
fof(subgoal_0, plain, p,
    inference(strip, [], [goal])).
fof(subgoal_1, plain, p => r,
    inference(strip, [], [goal])).
fof(subgoal_2, plain, (p & r) => q,
    inference(strip, [], [goal])).
\end{verbatim}

To prove the correctness of the process mentioned above,
we need to establish some lemmas before introduce our main goal of this
part, Theorem~\ref{thm:thm-strip}.

\begin{lemma}[lem-inv-uh]
  \label{lem:uh}
  If $Γ ⊢ \fuh\ φ$ then $Γ ⊢ φ$.
\end{lemma}

\begin{sketchproof}
Use induction on the cases defined by the outcome of the
$\fuh$ function in Eq.~(\ref{eq:uh-structured}).
\begin{itemize}
  \item If $n = 0$, by definition we conclude $Γ ⊢ φ$.
  \item If $n = 1$, we apply the following theorem proved in~\cite{AgdaProp},
    \begin{equation*}
    \texttt{∧⇒\rm{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
    \end{equation*}
  \item For $n > 1$, we use induction on the structure of the second
        argument.
\vskip 2mm
\begin{itemize}

\item Case $φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)$.
\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
  \RightLabel{by def.}
  \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
  \RightLabel{lem-inv-uh}
  \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
  \RightLabel{∧⇒\rm{-to-}⇒⇒.}
  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)}
  \end{bprooftree}
\end{equation*}

\item Case $φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)$.
\begin{equation*}
  \scalebox{0.95}{
  ($\mathcal{D}_1$)
  \begin{bprooftree}
    \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n) ∧ \fuh(φ₁ ⇒ φ₃, n)$}
    \RightLabel{∧-proj₁}
    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n)$}
    \RightLabel{by def.}
    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n-1)$}
    \RightLabel{lem-inv-uh,}
    \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
  \end{bprooftree}
  }
\end{equation*}

\begin{equation*}
  (\mathcal{D}_2)
  \begin{bprooftree}
    \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂) ∧ \fuh(φ₁ ⇒ φ₃)$}
    \RightLabel{∧-proj₂}
    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₃, n)$}
    \RightLabel{by def.}
    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₃, n-1)$}
    \RightLabel{lem-inv-uh.}
    \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
    \end{bprooftree}
\end{equation*}

Finally, using the theorem \texttt{⇒∧⇒\rm{-to-}⇒∧} from~\cite{AgdaProp},
\begin{equation*}
  \texttt{⇒∧⇒\rm{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
\end{equation*}
\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$\mathcal{D}_1$}
  \AxiomC{$\mathcal{D}_2$}
  \RightLabel{∧-intro}
  \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
  \RightLabel{\tt ⇒∧⇒\rm{-to-}⇒∧.}
  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
  \end{bprooftree}
\end{equation*}
\item Other cases are proved in a similar way.
\end{itemize}
\end{itemize}
\end{sketchproof}

We now define the $\fstrip$ function that yields the conjunction of
subgoals that implies the goal of the problem in the \Metis \TSTP derivations.

\begin{definition}[strip]
\label{def:strip}
\label{eq:strip}

\begin{equation}
\begin{aligned}
&\hspace{.495mm}\fstrip : \Prop → \Nat → \Prop\\
&\begin{array}{lll}
\fstrip &(φ₁ ∧ φ₂)     ~(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
\fstrip &(φ₁ ∨ φ₂)     ~(\suc~n) &= \fuh~(¬ φ₁ ⇒ \fstrip~φ₂~n)\\
\fstrip &(φ₁ ⇒ φ₂)     ~(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
\fstrip &(¬ (φ₁ ∧ φ₂)) ~(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~¬ φ₂~n)\\
\fstrip &(¬ (φ₁ ∨ φ₂)) ~(\suc~n) &= \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)\\
\fstrip &(¬ (φ₁ ⇒ φ₂)) ~(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~¬ φ₂~n)\\
\fstrip &(¬ ¬ φ₁)      ~(\suc~n) &= \fuh~(\fstrip~φ₁~n)\\
\fstrip &(¬ ⊥)         ~(\suc~n) &= ⊤\\
\fstrip &(¬ ⊤)         ~(\suc~n) &= ⊥\\
\fstrip &φ             ~n &= φ
\end{array}
\end{aligned}
\end{equation}
\end{definition}

% The definition above has termination problems since it is not
% a structural recursion. Therefore, we have reformulated the equation
% above to solve such an issue following the technique
% described in Section~\ref{ssec:structural-recursion}.
% We refer to $\fstrip$ as the function after applying the process mentioned
% above here and below unless otherwise stated.

\begin{lemma}[lem-inv-strip]
If $Γ ⊢ \fstrip~φ$ then $Γ ⊢ φ$.
\label{lem:lem-inv-strip}
\end{lemma}

\begin{sketchproof}
The proof is by induction on the structure of the
formula~$φ$ by following the cases in Eq.~(\ref{eq:strip}).
We present some cases but for a complete proof, we refer the reader to~\cite{AgdaMetis}.

\begin{itemize}
\item Case $φ ≡ ¬ ¬ φ₁$.
\begin{equation*}
  \begin{bprooftree}
 \AxiomC{$Γ ⊢ \fstrip~(¬¬φ₁)~(\suc~n)$}
  \RightLabel{by def.}
  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
  \RightLabel{lem-inv-uh}
  \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
  \RightLabel{lem-inv-strip}
  \UnaryInfC{$Γ ⊢ φ₁$}
  \end{bprooftree}
\end{equation*}

\item Case $φ ≡ φ₁ ∧ φ₂$. We get a proof for each conjunct and using the
introduction rule for conjunction connective, the result follows.

\begin{equation*}
(\mathcal{D})\hspace{3mm}
  \begin{bprooftree}
  \AxiomC{$Γ ⊢ \fstrip~(φ₁ ∧ φ₂)~(\suc~n)$}
  \RightLabel{by def.}
  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
  \RightLabel{∧-proj₁}
  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
  \RightLabel{lem-inv-uh}
  \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
  \RightLabel{lem-inv-strip}
  \UnaryInfC{$Γ ⊢ φ₁$}
    \end{bprooftree}
\end{equation*}

\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$\mathcal{D}$}
  \UnaryInfC{Γ ⊢ φ₁}
  \AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
  \RightLabel{by def.}
  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
  \RightLabel{$∧$-proj$₂$}
  \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
  \RightLabel{lem-inv-uh}
  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
  \RightLabel{$⇒$-elim}
  \BinaryInfC{$Γ ⊢ \fstrip~φ₂~n$}
  \RightLabel{lem-inv-strip.}
  \UnaryInfC{$Γ ⊢ φ₂$}
  \end{bprooftree}
\end{equation*}

\item Case $φ ≡ φ₁ ⇒ φ₂$.
\begin{equation*}
  \begin{bprooftree}
  \AxiomC{}
  \RightLabel{assume φ₁}
  \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
  \AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
  \RightLabel{by def.}
  \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
  \RightLabel{lem-inv-uh}
  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
  \RightLabel{weaken φ₁}
  \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
  \RightLabel{⇒-elim}
  \BinaryInfC{$Γ , φ₁ ⊢ \fstrip~φ₂~n$}
  \RightLabel{lem-inv-strip}
  \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
  \RightLabel{⇒-intro.}
  \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
  \end{bprooftree}
\end{equation*}

\item Case $φ ≡ ¬ (φ₁ ∨ φ₂)$. We show that $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
The result follows by introducing the conjunction and applying
De Morgan Laws.

\begin{equation*}
(\mathcal{D})\hspace{3mm}
\begin{bprooftree}
\AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
\RightLabel{by def.}
\UnaryInfC{$Γ ⊢ \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)$}
\RightLabel{∧-proj₁}
\UnaryInfC{$Γ ⊢ \fuh~(\fstrip~¬ φ₁~n)$}
\RightLabel{lem-inv-uh,}
\UnaryInfC{$Γ ⊢ \fstrip~¬ φ₁~n$}
\RightLabel{lem-inv-strip}
  \UnaryInfC{$Γ ⊢ ¬φ₁$}
\end{bprooftree}
\end{equation*}
\end{itemize}
\end{sketchproof}

\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$\mathcal{D}$}
  \UnaryInfC{$Γ ⊢ ¬ φ₁$}
  \AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
  \RightLabel{by def.}
  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)$}
  \RightLabel{∧-proj₂}
  \UnaryInfC{$Γ ⊢ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)$}
  \RightLabel{lem-inv-uh}
  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip~¬ φ₂~n$}
  \RightLabel{⇒-elim}
  \BinaryInfC{$Γ ⊢ \fstrip~¬ φ₂~n$}
  \RightLabel{lem-inv-strip.}
  \UnaryInfC{$Γ ⊢ ¬ φ₂$}
  \end{bprooftree}
\end{equation*}

\begin{lemma}[subst]
  \label{lem:subst}
  Substitution theorem.
\begin{equation*}
  \label{eq:substitution-theorem}
  \begin{bprooftree}
  \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
  \RightLabel{subst.}
  \BinaryInfC{$Γ ⊢ ψ$}
  \end{bprooftree}
\end{equation*}
\end{lemma}

We can now formulate the result that justifies the stripping strategy
of \Metis to prove goals.

\begin{theorem}[thm-strip]
\label{thm:thm-strip}
 If $s_i$ are the subgoals of the goal $φ$ for $i=1,\cdots,n$ and
 $\{ Γ ⊢ s_i \}_{i =1}^n$, then $Γ ⊢ φ$.
\end{theorem}

\begin{proof}
\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i=1}^n$}
  \RightLabel{∧-intro}
  \UnaryInfC{$Γ ⊢ \bigwedge_{i=1}^n s_i$}

  \AxiomC{$\fstrip~φ) ≡ \bigwedge_{i=1}^n s_i $}
  \RightLabel{subst}
  \BinaryInfC{$Γ ⊢ \fstrip~φ)$}
  \RightLabel{lem-inv-strip.}
  \UnaryInfC{$Γ ⊢ φ$}
\end{bprooftree}
\end{equation*}
\end{proof}

% -------------------------------------------------------------------

\end{document}

### 2017-10-22 paper/sections/proof-reconstruction.tex
[ paper ] roman in theorems.

@@
 theorems where $Γ$ has $\abbre{List}~\Prop$ type, and $φ$ has type $\Prop$.
-$\abbre{List}$ type is the usual inductive type for lists. For syntactical
-equivalence, we write $φ ≡ ψ$ for $φ : \Prop$ and $ψ : \Prop$.
+$\abbre{List}$ type is the usual inductive type for lists.
+For syntactical equivalence, we write the equality as $φ ≡ ψ$
+for $φ : \Prop$ and $ψ : \Prop$.
 
@@
 
-To emulate \Metis' inference rules in type theory,
-we observed that transformations performed by some rules are given
-by \emph{general recursive} functions.
-Algorithms based on general recursions can not be translated
-directly in type theory since it is not a guarantee they terminate.
-For that reason, we follow the technique described
-in~\cite{Bertot2004} to avoid termination problems by modifying the
-recursive
-functions to be \emph{structural recursive}.
+To emulate \Metis' inference rules in type theory, we observed that
+transformations performed by some rules are given by \emph{general recursive}
+functions. Algorithms based on general recursions can not be translated
+directly in type theory since it is not a guarantee they terminate. For that
+reason, we follow the technique described in~\cite{Bertot2004} to avoid
+termination problems by modifying the recursive functions to be
+\emph{structural recursive}.
 % (see \cite{Coquand1992,Abel2002,Bove2005} for more details).

### 2017-10-22 paper/main.tex
added text.
[ paper ] perliminaries added.
[ paper ] implementation added, some proofs added.
[ paper ] fixing some typos and text added.
[ paper ] complexity measure added.
[ paper ] thm-split added.
[ paper ] improving minor texts.
[ paper ] Added temporally `hyperref` package.
[ paper ] citation using natbib.
[ travis-ci ] fixed cpphs requirement.
[ paper ] working.
[ paper ] cosmetics for cases equations.
[ paper ] normalization, first part, added.
[ paper ] canonicalize lemmas and theorems.
[ paper ] metis section fixes.
[ paper ] fixed athena process description.
[ paper ] first descript

@@
-\documentclass[runningheads, a4paper]{llncs}
+\documentclass[
+    envcountsect    %% In order to provide the usual behaviour expected
+                    %% from \newtheorem
+  , runningheads
+  ]{llncs}
+
+\spnewtheorem{mainth}[theorem]{Main Theorem}{\bfseries}{\rmfamily}
+
+\usepackage[numbers]{natbib}
+
 \usepackage{subfiles}
+
+\usepackage{needspace}  %% https://tex.stackexchange.com/questions/28203/
+                        %% thmtools-how-to-prevent-pagebreak-between-theorem-
+                        %% and-proof
 
@@
 \usepackage{array}
+
 \usepackage{bussproofs}
@@
   {\DisplayProof\egroup}
+
 \def\extraVskip{3pt}
@@
 \usepackage[title]{appendix}
+
+\usepackage{hyphenat}
+\hyphenation{proof-re-cons-truc-tion proof-ob-ject}
 
@@
 \usetikzlibrary{calc}
+\usetikzlibrary{shapes}
 \usepackage{rotating}
@@
 \usepackage{comment}
-\usepackage{url}
-\usepackage{amsmath}
+\usepackage[hyphens]{url}
+\usepackage{bm}
+
 \usepackage{amssymb}
 \usepackage{amsmath}
+
+\let\proof\relax      %% https://tex.stackexchange.com/questions/43835/
+\let\endproof\relax   %% conflict-between-amsthm-and-some-other-package
+\usepackage{amsthm}
+
+\newenvironment{sketchproof}{%
+  \renewcommand{\proofname}{Sketch of the Proof}\proof}{\endproof}
+\renewcommand\qedsymbol{$\blacksquare$}
+
 %\usepackage{stmaryrd} %new symbol font for tcs
@@
 
+% -------------------------------------------------------------------
+% Unicode Characters.
+% -------------------------------------------------------------------
+
 \usepackage{textcomp}
 \usepackage[verbose]{newunicodechar}
+
+\newunicodechar{¬}{\ensuremath{\neg}\;}
+\newunicodechar{Γ}{\ensuremath{\Gamma}}
+\newunicodechar{γ}{\ensuremath{\gamma}}
+\newunicodechar{φ}{\ensuremath{\varphi}}
+\newunicodechar{ψ}{\ensuremath{\psi}}
+\newunicodechar{ϕ}{\ensuremath{\varphi}}
+\newunicodechar{ᵢ}{\ensuremath{{}_{i}}}
+\newunicodechar{₀}{\ensuremath{{}_{0}}}
+\newunicodechar{₁}{\ensuremath{{}_{1}}}
+\newunicodechar{₂}{\ensuremath{{}_{2}}}
+\newunicodechar{₃}{\ensuremath{{}_{3}}}
+\newunicodechar{₄}{\ensuremath{{}_{4}}}
+\newunicodechar{₅}{\ensuremath{{}_{5}}}
+\newunicodechar{₆}{\ensuremath{{}_{6}}}
+\newunicodechar{₇}{\ensuremath{{}_{7}}}
+\newunicodechar{₈}{\ensuremath{{}_{8}}}
+\newunicodechar{₉}{\ensuremath{{}_{9}}}
+\newunicodechar{ₙ}{\ensuremath{{}_{n}}}
+\newunicodechar{→}{\ensuremath{\rightarrow}}
+\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
+\newunicodechar{⇔}{\ensuremath{\Leftrightarrow}}
+\newunicodechar{∅}{\ensuremath{\emptyset}}
+\newunicodechar{∈}{\ensuremath{\in}}
+\newunicodechar{∘}{\ensuremath{\circ}}
 \newunicodechar{∧}{\ensuremath{\wedge}}
 \newunicodechar{∨}{\ensuremath{\vee}}
-\newunicodechar{¬}{\ensuremath{\neg}}
-\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
-\newunicodechar{⇔}{\ensuremath{\Leftrightarrow}}
 \newunicodechar{∼}{\ensuremath{\sim}}
-\newunicodechar{₀}{\ensuremath{{}_{0}}}
-\newunicodechar{₁}{\ensuremath{{}_{1}}}
-\newunicodechar{₃}{\ensuremath{{}_{2}}}
-\newunicodechar{₄}{\ensuremath{{}_{3}}}
-\newunicodechar{₅}{\ensuremath{{}_{4}}}
-\newunicodechar{₆}{\ensuremath{{}_{5}}}
-\newunicodechar{₇}{\ensuremath{{}_{6}}}
-\newunicodechar{₈}{\ensuremath{{}_{7}}}
-\newunicodechar{₉}{\ensuremath{{}_{8}}}
-\newunicodechar{∅}{\ensuremath{\emptyset}}
+\newunicodechar{≠}{\ensuremath{\neq}}
+\newunicodechar{≡}{\ensuremath{\equiv}}
+\newunicodechar{⊕}{\ensuremath{\oplus}}
+\newunicodechar{⊖}{\ensuremath{\ominus}}
 \newunicodechar{⊢}{\ensuremath{\vdash}}
+\newunicodechar{⊤}{\ensuremath{\top}}
 \newunicodechar{⊥}{\ensuremath{\bot}}
-\newunicodechar{Γ}{\ensuremath{\Gamma}}
+\newunicodechar{⊻}{\ensuremath{\veebar}}
+\newunicodechar{⟝}{\ensuremath{\vdash_{2}}}
+\newunicodechar{ⱼ}{\ensuremath{{}_{j}}}
 
-%\DeclareUnicodeCharacter{00A0}{~}
+% -------------------------------------------------------------------
+% Verbatim.
+% -------------------------------------------------------------------
 
@@
 % -------------------------------------------------------------------
+
 \usepackage{xspace}
@@
 \newcommand{\abbre}[1]{\textsc{#1}\xspace}
+\newcommand{\ATPs}{\abbre{ATPs}}
 \newcommand{\ATP}{\abbre{ATP}}
-\newcommand{\ATPs}{\abbre{ATPs}}
+\newcommand{\Bool}{\abbre{Bool}}
+\newcommand{\CNF}{\abbre{CNF}}
+\newcommand{\CPL}{\abbre{CPL}}
+\newcommand{\ITP}{\abbre{ITP}}
+\newcommand{\ITPs}{\abbre{ITPs}}
+\newcommand{\List}{\abbre{List}}
+\newcommand{\NProp}{\abbre{NProp}}
+\newcommand{\Nat}{\abbre{Nat}}
+\newcommand{\Prop}{\abbre{Prop}}
 \newcommand{\SAT}{\abbre{SAT}}
 \newcommand{\SMT}{\abbre{SMT}}
-\newcommand{\ITP}{\abbre{ITP}}
-\newcommand{\CPL}{\abbre{CPL}}
-\newcommand{\CNF}{\abbre{CNF}}
 
@@
 
+\newcommand{\zero}{\rm{zero}\xspace}
+\newcommand{\suc}{\rm{succ}\xspace}
+
+\newcommand{\nnf}{\name{nnf}}
+
 \newcommand{\prg}[1]{\texttt{#1}\xspace}
 \newcommand{\Agda}{\prg{Agda}}
-\newcommand{\Metis}{\prg{Metis}}
 \newcommand{\Athena}{\prg{Athena}}
 \newcommand{\IsabelleHOL}{\prg{IsabelleHOL}}
+\newcommand{\Metis}{\prg{Metis}}
 
@@
 \newcommand{\TSTP}{\len{TSTP}}
+
+\newcommand{\NN}{\ensuremath{\mathbb{N}}}
+
+\newcommand{\fun}[1]{\rm{#1}\xspace}
+\newcommand{\fbuild}{\fun{build}}
+\newcommand{\fcanon}{\fun{canon}}
+\newcommand{\fcnf}{\fun{cnf}}
+\newcommand{\fdist}{\fun{dist}}
+\newcommand{\ffactor}{\fun{factor}}
+\newcommand{\fform}{\fun{form}}
+\newcommand{\fmax}{\fun{max}}
+\newcommand{\fndisj}{\fun{ndisj}}
+\newcommand{\fnnf}{\fun{nnf}}
+\newcommand{\frank}{\fun{rank}}
+\newcommand{\frconj}{\fun{rconj}}
+\newcommand{\frdisj}{\fun{rdisj}}
+\newcommand{\freorder}{\fun{reorder}}
+\newcommand{\frm}{\fun{rm}}
+\newcommand{\fsbuild}{\fun{sbuild}}
+\newcommand{\fsubst}{\fun{subst}}
+\newcommand{\fuh}{\fun{uh}}
+\newcommand{\tunshunt}{\fun{thm-uh}}
+
+\newcommand{\fstrip}{\fun{strip}}
+\newcommand{\tstrip}{\fun{thm-strip}}
+
+\newcommand{\fcanonicalize}{\fun{canonicalize}}
+\newcommand{\tcanonicalize}{\fun{thm-canonicalize}}
+
+\newcommand{\fconjunct}{\fun{conjunct}}
+\newcommand{\tconjunct}{\fun{thm-conjunct}}
+
+\newcommand{\fresolve}{\fun{resolve}}
+\newcommand{\tresolve}{\fun{thm-resolve}}
+
+\newcommand{\fclausify}{\fun{clausify}}
+\newcommand{\tclausify}{\fun{thm-clausify}}
+
+\newcommand{\fsimplify}{\fun{simplify}}
+\newcommand{\tsimplify}{\fun{thm-simplify}}
+
+\newcommand{\fnegate}{\fun{negate}}
+\newcommand{\tnegate}{\fun{thm-negate}}
+
+% latin etc. abbrev
+\newcommand{\abbrev}[1]{#1} % alternative: \emph{#1}
+\newcommand{\cf}{\abbrev{cf.}\ }
+\newcommand{\eg}{\abbrev{e.\,g.}}
+\newcommand{\Eg}{\abbrev{E.\,g.}}
+\newcommand{\ie}{\abbrev{i.\,e.}}
+\newcommand{\Ie}{\abbrev{I.\,e.}}
+\newcommand{\etal}{\abbrev{et.\,al.}}
+\newcommand{\wwlog}{w.\,l.\,o.\,g.} % \wlog is ``write into log file''
+\newcommand{\Wlog}{W.\,l.\,o.\,g.}
+\newcommand{\wrt}{w.\,r.\,t.}
 
@@
 
+% -------------------------------------------------------------------
+% Hyperef.
+% -------------------------------------------------------------------
+
+\usepackage{hyperref}
+
 \begin{document}
@@
 
-\title{Towards Proof-Reconstruction of Problems
-in Classical Propositional Logic}
-
-\titlerunning{Proof-Reconstruction in Classical
-Propositional Logic}
-
+\title{Proof-Reconstruction in Type Theory for Propositional Logic}
 \author{Jonathan Prieto-Cubides%
-\and Andr\'es Sicard-Ram\'irez}
+%\and Andr\'es Sicard-Ram\'irez
+}
 %
-\authorrunning{Proof-Reconstruction in Classical Propositional Logic}
 
@@
 Universidad EAFIT, Medell\'in, Colombia\\
-\email{\{jprieto9,asr\}@eafit.edu.co}}
+\email{jprieto9@eafit.edu.co}}
 
@@
 
-\listoftodos[Notes]
+% \listoftodos[Notes]
 
@@
 \subfile{sections/abstract.tex}
+% \tableofcontents
 \subfile{sections/introduction.tex}
+% \subfile{sections/preliminaries.tex}
 \subfile{sections/metis-language-and-proofs.tex}
 \subfile{sections/proof-reconstruction.tex}
+% \subfile{sections/implementation.tex}
+\subfile{sections/related-work.tex}
 \subfile{sections/conclusions.tex}
-\subfile{sections/related-work.tex}
 \subfile{sections/acknowledgements.tex}
 
-\bibliographystyle{splncs03}
+\bibliographystyle{plainnat}
 \bibliography{ref}

### 2017-10-22 paper/sections/acknowledgements.tex
Last changes in the Paper (#37)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

* [ pape

@@
 
-Last but not least, we thankfully acknowledge
+Last but not least, I thankfully acknowledge
 Andreas Abel and Chalmers University of Goteborg, Sweden for
-inviting us to be part of the \Agda Implementors’ Meeting XXV.
+inviting me to be part of the \Agda Implementors’ Meeting XXV.
 I was honored to present there part of this research.

### 2017-10-22 paper/sections/related-work.tex
Last changes in the Paper (#37)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

* [ pape

@@
 In this section, we present an extended version of the related work description made in the proposal for this research~\cite{Sicard-Ramirez2016}.
+
+% On the one hand, we have the
+% automatic theorem provers (henceforth \ATP) and their specification
+% logic. These tools are usually classified in at least one of the
+% following categories.
+% A \SAT solver (e.g., \name{zChaff}~\cite{Moskewicz2001} and
+% \name{MiniSat}~\cite{Een2004}) to prove unsatisfiability of \CNF
+% formulas, a \abbre{QBF} solver (e.g.,
+% \name{GhostQ}~\cite{Klieber2014} and
+% \name{DepQBF}~\cite{Lonsing2017}) to prove satisfiability and
+% invalidity of quantified Boolean formulas, a \SMT solver
+% (e.g \name{CVC4}~\cite{Barrett2011}, \name{veriT}~\cite{bouton2009},
+% and \name{Z3}~\cite{DeMoura2008}) to prove unsatisfiability of
+% formulas from first-order logic with theories, and a prover for
+% validity of formulas from first-order logic with equality
+% (e.g., \name{E}~\cite{Schulz:AICOM-2002},
+% \name{leanCoP}~\cite{Otten2008},
+% \Metis~\cite{hurd2003first},
+% \name{SPASS}~\cite{Weidenbach2009} and
+% \name{Vampire}~\cite{Riazanov1999}), high-order logic (e.g.,
+% \name{Leo-II}~\cite{Benzmuller2008} and
+% \name{Satallax}~\cite{Brown2012}) or intuitionistic logic (e.g.,
+% \name{ileanCoP}~\cite{Otten2008},
+% \name{JProver}~\cite{Schmitt2001}, and
+% \name{Gandalf}~\cite{Tammet1997}), among others. On the other hand,
+% we have the proof checkers, interactive theorem provers (henceforth
+% \ITP) or proof assistants (e.g., \Agda~\cite{agdateam},
+% \name{Coq}~\cite{coqteam},
+% \name{Isabelle}~\cite{paulson1994isabelle}, and
+% \name{HOL4}~\cite{norrish2007hol}).
+
+\name{Isabelle/HOL} incorporated \Metis as a macro-step
+reconstruction tool for explaining proof steps (usually \CNF goals)
+replied from other \ATPs like \name{CVC4}, \name{Vampire}, or
+\name{Z3} (more details in Ref.~\cite{paulson2007source}).
+\citeauthor{Farber2015} in \cite{Farber2015} present tactic based on \Metis for
+\name{HOL Light} capable to challenge others tactics like \emph{MESON}
+or the \emph{leanCoP} tactic~\cite{Farber2016}.
 

### 2017-10-22 paper/sections/proof-reconstruction.tex
[ paper ] table added.

@@
 
-\subsubsection*{An  example.}
+\begin{example}
+\label{ex:structural-recursion}
+
 Let us consider the following example to exhibit the bounded technique
@@
 
+\end{example}
+
 For a more complete treatment of general recursion, and how to
@@
 
+\begin{table}[!ht]
+  \begin{center}
+  {\renewcommand{\arraystretch}{1.6}%
+    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}
+    \hline
+    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
+    \texttt{canonicalize}
+      &Normalization of the formula
+      &Thm.~\ref{thm:canonicalizeThm}
+    \\
+    \texttt{clausify}
+      &Performs clausification
+      &Thm.~\ref{thm:clausifyThm}
+    \\
+    \hyperlink{atp-conjunct}{\texttt{conjunct}}
+      &Takes a formula from a conjunction
+      &Thm.~\ref{thm:conjunctThm}
+    \\
+    \texttt{negate}
+      &Negate the formula
+      &Thm.~\ref{thm:negateThm}
+    \\
+    \texttt{resolve}
+      &A general form of the resolution theorem
+      &Thm.~\ref{thm:resolveThm}
+    \\
+    \texttt{simplify}
+      &Simplify definitions and theorems
+      &Thm.~\ref{thm:simplifyThm}
+    \\
+    \texttt{strip}
+      &Strip a goal into subgoals
+      &Thm.~\ref{thm:stripThm}
+    \\[1ex]
+    \hline
+    \end{tabular}}
+  \end{center}
+\label{tab:agda-metis-table}
+\end{table}
 % ------------------------------------------------------------------------------

### 2017-10-22 paper/sections/proof-reconstruction.tex
[ paper ] last changes.

@@
 
-\begin{align}
-  \label{eq:uh-definition}
-    &\fuh_{0} &&: \Prop → \Prop\\
-    &\fuh_{0}\ (φ₁ ⇒ (φ₂ ⇒ φ₃)) &&= \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃)\\
-    &\fuh_{0}\ (φ₁ ⇒ (φ₂ ∧ φ₃)) &&= \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃)\\
-    &\fuh_{0}\ φ &&= φ
-\end{align}
+% \begin{functiondef}{$\fuh_{0}$ : \Prop → \Prop}
+%   \label{eq:uh-definition}
+
+% \begin{array}
+%     &\fuh_{0} &&: \Prop → \Prop\\
+%     &\fuh_{0}\ (φ₁ ⇒ (φ₂ ⇒ φ₃)) &&= \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃)\\
+%     &\fuh_{0}\ (φ₁ ⇒ (φ₂ ∧ φ₃)) &&= \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃)\\
+%     &\fuh_{0}\ φ &&= φ
+% \end{array}
+
+% \end{functiondef}
 
@@
       &Normalization of the formula
-      &Thm.~\ref{thm:canonicalizeThm}
+      &Thm.~\ref{thm:canonicalize}
     \\
@@
       &Performs clausification
-      &Thm.~\ref{thm:clausifyThm}
+      &Thm.~\ref{thm:clausify}
     \\
@@
       &Takes a formula from a conjunction
-      &Thm.~\ref{thm:conjunctThm}
+      &Thm.~\ref{thm:conjunct}
     \\
@@
       &Negate the formula
-      &Thm.~\ref{thm:negateThm}
+      &Thm.~\ref{thm:negate}
     \\
@@
       &A general form of the resolution theorem
-      &Thm.~\ref{thm:resolveThm}
+      &Thm.~\ref{thm:resolve}
     \\
@@
       &Simplify definitions and theorems
-      &Thm.~\ref{thm:simplifyThm}
+      &Thm.~\ref{thm:simplify}
     \\
@@
       &Strip a goal into subgoals
-      &Thm.~\ref{thm:stripThm}
+      &Thm.~\ref{thm:strip}
     \\[1ex]
@@
 \end{table}
-% ------------------------------------------------------------------------------
+
+% -----------------------------------------------------------------------------
 
 \subfile{sections/proof-reconstruction/strip.tex}
-\subfile{sections/proof-reconstruction/negate.tex}
-\subfile{sections/proof-reconstruction/resolve.tex}
-\subfile{sections/proof-reconstruction/canonicalize.tex}
-\subfile{sections/proof-reconstruction/conjunct.tex}
-\subfile{sections/proof-reconstruction/clausify.tex}
-\subfile{sections/proof-reconstruction/simplify.tex}
+% \subfile{sections/proof-reconstruction/negate.tex}
+% \subfile{sections/proof-reconstruction/resolve.tex}
+% \subfile{sections/proof-reconstruction/canonicalize.tex}
+% \subfile{sections/proof-reconstruction/conjunct.tex}
+% \subfile{sections/proof-reconstruction/clausify.tex}
+% \subfile{sections/proof-reconstruction/simplify.tex}
 
-% ------------------------------------------------------------------------------
+%------------------------------------------------------------------------------
 

### 2017-10-22 paper/sections/proof-reconstruction.tex
changes definitions
[ paper ] last changes.

@@
 
-% \begin{functiondef}{$\fuh_{0}$ : \Prop → \Prop}
-%   \label{eq:uh-definition}
-
-% \begin{array}
-%     &\fuh_{0} &&: \Prop → \Prop\\
-%     &\fuh_{0}\ (φ₁ ⇒ (φ₂ ⇒ φ₃)) &&= \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃)\\
-%     &\fuh_{0}\ (φ₁ ⇒ (φ₂ ∧ φ₃)) &&= \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃)\\
-%     &\fuh_{0}\ φ &&= φ
-% \end{array}
-
-% \end{functiondef}
+\begin{equation*}
+\label{eq:uh-definition}
+\begin{aligned}
+&\hspace{.495mm}\fuh_{0} : \Prop → \Prop\\
+&\begin{array}{lll}
+  \fuh_{0} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃)\\
+  \fuh_{0} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃)\\
+  \fuh_{0} &φ                &= φ
+\end{array}
+\end{aligned}
+\end{equation*}
 
@@
 
-\begin{align}
+\begin{equation}
 \label{eq:uh-structured}
-  \begin{split}
-    &\fuh_{1} : \Prop → \Nat \to \Prop\\
-    &\fuh_{1}(φ, \zero)\hspace{3mm}= φ\\%\hspace{10cm}\\
-    &\fuh_{1}(φ, \suc(n)) =\\
-    &\hspace{3mm}\begin{cases}
-    \fuh_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
-      &\text{ if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\[2mm]
-    \fuh_{1}(φ₁ ⇒ φ₂, n)\\
-    ∧\ \fuh_{1}(φ₁ ⇒ φ₃, n),
-       &\text{ if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
-  \end{cases}
-  \end{split}
-\end{align}
+\begin{aligned}
+&\hspace{.495mm} \fuh_{1} : \Prop → \Nat \to \Prop\\
+&\begin{array}{llll}
+\fuh_{1} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &(\suc~n) &= \fuh_{1}~((φ₁ ∧ φ₂) ⇒ φ₃)~n\\
+\fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
+\fuh_{1} &φ &\xspace\emph{n} &= φ
+\end{array}
+\end{aligned}
+\end{equation}
 
@@
 
-\begin{align*}
-  \begin{split}
+\begin{equation}
 % \label{eq:rank-definition}
-    &\frank : \Prop → \Nat\\
-    &\frank(φ) =
-    \begin{cases}
-    \frank(φ₁) + c_{¬},  &\text{ if } φ ≡ \neg φ₁ \\
-    \fmax{(\frank(φ₁),\ \frank(φ₂))} + c_{\square},
-      &\text{ if } φ ≡ φ₁\,\square\, φ₂.\\
-    0, &\text{ otherwise}
-    \end{cases}
-  \end{split}
-\end{align*}
+\begin{aligned}
+&\hspace{.495mm}\frank : \Prop → \Nat\\
+&\begin{array}{llll}
+\frank~(¬~φ)           &= \frank~φ₁~+~c_{¬}\\
+\frank~(φ₁~\square~φ₂) &= \fmax~(\frank~φ₁)~(\frank~φ₂) + c_{\square}\\
+\frank~φ               &= 0
+\end{array}
+\end{aligned}
+\end{equation}
 
@@
 
-\begin{align*}
-  \begin{split}
-      &\fuh_{cm} : \Prop → \Nat\\
-      &\fuh_{cm}(φ) =\\
-      &\hspace{3mm}
-        \begin{cases}
-        \fuh_{cm}(φ₃) + 2, &\text{ if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
-        \fmax(\fuh_{cm}(φ₂),\ \fuh_{cm}(φ₃)) + 1,
-          &\text{ if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
-        0, &\text{ otherwise.}
-        \end{cases}
-  \end{split}
-\end{align*}
+\begin{equation*}
+% \label{eq:rank-definition}
+\begin{aligned}
+&\hspace{.495mm}\fuh_{cm} : \Prop → \Nat\\
+&\begin{array}{llll}
+\fuh_{cm}~(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{cm}(φ₃) + 2\\
+\fuh_{cm}~(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fmax~(\fuh_{cm}~φ₂)~(\fuh_{cm}~φ₃) + 1\\
+\fuh_{cm}~φ                &= 0
+\end{array}
+\end{aligned}
+\end{equation*}
 
@@
 
-\begin{definition}[uh]
-  \label{def:uh}
 \begin{align}
@@
 \end{align}
-\end{definition}
 

### 2017-10-22 paper/sections/proof-reconstruction.tex
[ paper ] strip proof.

@@
 \fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
-\fuh_{1} &φ &\xspace\emph{n} &= φ
+\fuh_{1} &φ &\xspace\text{n} &= φ
 \end{array}
@@
 that proves its soundness.
-This theorem is named by using the prefix \emph{thm}
-and the name of the rule.
 
@@
 For this inference rule, we proposed the \rm{conjunct} function in
-Def.~\ref{def:conjunct} and we proved the theorem \rm{thm-conjunct}
-in Thm.~\ref{thm:thm-conjunct}. The pattern is the following for
+Def.~\ref{def:conjunct} and we proved Thm.~\ref{thm:thm-conjunct}. The pattern is the following for
 a binary rule and we extend it for $n$-ary rules in a natural way.
@@
 \end{itemize}
-\item \rm{thm-rule} is the theorem that proves the soundness of the
-$\rm{rule}$ function.
+\item The theorem that proves the soundness of the
+$\rm{rule}$ function looks like
 \begin{equation*}\text{If }Γ ⊢ φ\text{ then }Γ ⊢ \rm{rule}\ φ.\end{equation*}

### 2017-10-22 paper/sections/proof-reconstruction/strip.tex
[ paper ] table added.
[ paper ] strip proof.

@@
 
-\begin{lemma}[lem-inv-uh]
-  \label{lem:uh}
+\begin{mainlemma}
+  \label{lem:inv-uh-lem}
   If $Γ ⊢ \fuh\ φ$ then $Γ ⊢ φ$.
-\end{lemma}
+\end{mainlemma}
 
@@
   \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ (φ₂ ⇒ φ₃), n)$}
+  \AxiomC{$Γ ⊢ \fuh~(φ₁ ⇒ (φ₂ ⇒ φ₃))~(\suc~n)$}
   \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ (φ₂ ⇒ φ₃), n-1)$}
-  \RightLabel{lem-inv-uh}
+  \UnaryInfC{$Γ ⊢ \fuh~((φ₁ ∧ φ₂) ⇒ φ₃)~n$}
+  \RightLabel{by hip.}
   \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
-  \RightLabel{∧⇒\rm{-to-}⇒⇒.}
+  \RightLabel{∧⇒\rm{-to-}⇒⇒}
   \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)}
@@
   \begin{bprooftree}
-    \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n) ∧ \fuh(φ₁ ⇒ φ₃, n)$}
+    \AxiomC{$Γ ⊢ \fuh~(φ₁ ⇒ φ₂)~n ∧ \fuh~(φ₁ ⇒ φ₃)~n$}
     \RightLabel{∧-proj₁}
-    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n)$}
-    \RightLabel{by def.}
-    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂, n-1)$}
-    \RightLabel{lem-inv-uh,}
+    \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ φ₂)~n$}
+    \RightLabel{by hip.}
     \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
@@
   \begin{bprooftree}
-    \AxiomC{$Γ ⊢ \fuh(φ₁ ⇒ φ₂) ∧ \fuh(φ₁ ⇒ φ₃)$}
+    \AxiomC{$Γ ⊢ \fuh~(φ₁ ⇒ φ₂)~n ∧ \fuh~(φ₁ ⇒ φ₃)~n$}
     \RightLabel{∧-proj₂}
-    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₃, n)$}
-    \RightLabel{by def.}
-    \UnaryInfC{$Γ ⊢ \fuh(φ₁ ⇒ φ₃, n-1)$}
-    \RightLabel{lem-inv-uh.}
+    \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ φ₃)~n$}
+    \RightLabel{by hip.}
     \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
@@
   \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
-  \RightLabel{\tt ⇒∧⇒\rm{-to-}⇒∧.}
+  \RightLabel{\tt ⇒∧⇒\rm{-to-}⇒∧}
   \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
@@
 
-We now define the $\fstrip$ function that yields the conjunction of
-subgoals that implies the goal of the problem in the \Metis \TSTP derivations.
-
-\begin{definition}[strip]
-\label{def:strip}
-\label{eq:strip}
+We now define the $\fstrip$ function in Eq.~\ref{eq:strip-unfixed} that
+yields the conjunction of subgoals that implies the goal of the problem in
+the \Metis \TSTP derivations.
 
 \begin{equation}
+\label{eq:strip-unfixed}
+\begin{aligned}
+&\hspace{.495mm}\fstrip : \Prop → \Nat → \Prop\\
+&\begin{array}{lll}
+\fstrip &(φ₁ ∧ φ₂)     &= \fuh~(\fstrip~φ₁) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂)\\
+\fstrip &(φ₁ ∨ φ₂)     &= \fuh~(¬ φ₁ ⇒ \fstrip~φ₂)\\
+\fstrip &(φ₁ ⇒ φ₂)     &= \fuh~(φ₁ ⇒ \fstrip~φ₂)\\
+\fstrip &(¬ (φ₁ ∧ φ₂)) &= \fuh~(φ₁ ⇒ \fstrip~¬ φ₂)\\
+\fstrip &(¬ (φ₁ ∨ φ₂)) &= \fuh~(\fstrip~¬ φ₁) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂)\\
+\fstrip &(¬ (φ₁ ⇒ φ₂)) &= \fuh~(\fstrip~φ₁) ∧ \fuh~(φ₁ ⇒ \fstrip~¬ φ₂)\\
+\fstrip &(¬ ¬ φ₁)      &= \fuh~(\fstrip~φ₁)\\
+\fstrip &(¬ ⊥)         &= ⊤\\
+\fstrip &(¬ ⊤)         &= ⊥\\
+\fstrip &φ             &= φ
+\end{array}
+\end{aligned}
+\end{equation}
+
+The function defined above has termination problems since it is not
+a structural recursion. Therefore, we have reformulated it in
+Eq.~\ref{eq:strip-fixed} in order to solve such an issue following
+the technique described in Section~\ref{ssec:structural-recursion}.
+
+\begin{equation}
+\label{eq:strip-fixed}
 \begin{aligned}
@@
 \fstrip &(¬ ⊤)         ~(\suc~n) &= ⊥\\
-\fstrip &φ             ~n &= φ
+\fstrip &φ             ~\emph{n} &= φ
 \end{array}
@@
 \end{equation}
-\end{definition}
 
-% The definition above has termination problems since it is not
-% a structural recursion. Therefore, we have reformulated the equation
-% above to solve such an issue following the technique
-% described in Section~\ref{ssec:structural-recursion}.
-% We refer to $\fstrip$ as the function after applying the process mentioned
-% above here and below unless otherwise stated.
-
-\begin{lemma}[lem-inv-strip]
-If $Γ ⊢ \fstrip~φ$ then $Γ ⊢ φ$.
+\begin{mainlemma}
 \label{lem:lem-inv-strip}
-\end{lemma}
+Let $n : \Nat$ the complexity measure of the strip function in
+Eq.~\ref{eq:strip-unfixed}.
+If $Γ ⊢ \fstrip~φ~n$ then $Γ ⊢ φ$.
+\end{mainlemma}
 
@@
   \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
-  \RightLabel{lem-inv-uh}
+  \RightLabel{lemma~\ref{lem:inv-uh-lem}}
   \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
-  \RightLabel{lem-inv-strip}
+  \RightLabel{by hip.}
   \UnaryInfC{$Γ ⊢ φ₁$}
@@
   \UnaryInfC{Γ ⊢ φ₁}
-  \AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
+  \AxiomC{$Γ ⊢ \fstrip~(φ₁ ∧ φ₂)~(\suc~n)$}
   \RightLabel{by def.}
@@
   \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
-  \RightLabel{lem-inv-uh}
+  \RightLabel{lemma~\ref{lem:inv-uh-lem}}
   \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
@@
   \BinaryInfC{$Γ ⊢ \fstrip~φ₂~n$}
-  \RightLabel{lem-inv-strip.}
+  \RightLabel{by hip.}
   \UnaryInfC{$Γ ⊢ φ₂$}
@@
   \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
-  \AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
+  \AxiomC{$Γ ⊢ \fstrip~(φ₁ ⇒ φ₂)~(\suc~n)$}
   \RightLabel{by def.}
   \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
-  \RightLabel{lem-inv-uh}
+  \RightLabel{lemma~\ref{lem:inv-uh-lem}}
   \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
@@
   \BinaryInfC{$Γ , φ₁ ⊢ \fstrip~φ₂~n$}
-  \RightLabel{lem-inv-strip}
+  \RightLabel{by hip}
   \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
-  \RightLabel{⇒-intro.}
+  \RightLabel{⇒-intro}
   \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
@@
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
+\AxiomC{$Γ ⊢ \fstrip~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
 \RightLabel{by def.}
@@
 \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~¬ φ₁~n)$}
-\RightLabel{lem-inv-uh,}
+\RightLabel{lemma~\ref{lem:inv-uh-lem}}
 \UnaryInfC{$Γ ⊢ \fstrip~¬ φ₁~n$}
-\RightLabel{lem-inv-strip}
+\RightLabel{by hip.}
   \UnaryInfC{$Γ ⊢ ¬φ₁$}
@@
   \UnaryInfC{$Γ ⊢ ¬ φ₁$}
-  \AxiomC{$Γ ⊢ \fstrip~(φ)~(\suc~n)$}
+  \AxiomC{$Γ ⊢ \fstrip~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
   \RightLabel{by def.}
@@
   \UnaryInfC{$Γ ⊢ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)$}
-  \RightLabel{lem-inv-uh}
+  \RightLabel{lemma~\ref{lem:inv-uh-lem}}
   \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip~¬ φ₂~n$}
@@
   \BinaryInfC{$Γ ⊢ \fstrip~¬ φ₂~n$}
-  \RightLabel{lem-inv-strip.}
+  \RightLabel{by hip.}
   \UnaryInfC{$Γ ⊢ ¬ φ₂$}
@@
 \end{equation*}
+\TheEnd
 
-\begin{lemma}[subst]
+\begin{mainlemma}[subst]
   \label{lem:subst}
@@
   \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
-  \RightLabel{subst.}
+  \RightLabel{subst}
   \BinaryInfC{$Γ ⊢ ψ$}
@@
 \end{equation*}
-\end{lemma}
+\end{mainlemma}
 
@@
 of \Metis to prove goals.
+For the sake of brevity, we state the following theorem for the
+\strip function when the goal has only two subgoals. In other cases, we extend the theorem in the natural way.
 
-\begin{theorem}[thm-strip]
+\begin{mainth}
 \label{thm:thm-strip}
- If $s_i$ are the subgoals of the goal $φ$ for $i=1,\cdots,n$ and
- $\{ Γ ⊢ s_i \}_{i =1}^n$, then $Γ ⊢ φ$.
-\end{theorem}
+ If $s_1$ and $s_2$ are the subgoals of the goal $φ$, $Γ ⊢ s_1$, and
+$Γ ⊢ s_2$ then $Γ ⊢ φ$.
+\end{mainth}
 
@@
   \begin{bprooftree}
-  \AxiomC{$\left\{ Γ ⊢ s_i \right\}_{i=1}^n$}
+  \AxiomC{$ Γ ⊢ s_1 $}
+  \AxiomC{$ Γ ⊢ s_2 $}
   \RightLabel{∧-intro}
-  \UnaryInfC{$Γ ⊢ \bigwedge_{i=1}^n s_i$}
-
-  \AxiomC{$\fstrip~φ) ≡ \bigwedge_{i=1}^n s_i $}
+  \BinaryInfC{$Γ ⊢ s_1\wedge s_2$}
+  \AxiomC{$\fstrip~φ~n ≡ s_1\wedge s_2 $}
   \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ \fstrip~φ)$}
-  \RightLabel{lem-inv-strip.}
+  \BinaryInfC{$Γ ⊢ \fstrip~φ~n$}
+  \RightLabel{lemma~\ref{lem:lem-inv-strip}}
   \UnaryInfC{$Γ ⊢ φ$}
@@
 \end{equation*}
+\TheEnd
 \end{proof}

### 2017-10-22 paper/sections/metis-language-and-proofs.tex
[ paper ] conjunct reviewed.

@@
 assumes a \name{role}, this could be an \name{axiom},
-\name{conjecture}, \name{definition}, or a \name{hypothesis}.
+\name{conjecture}, \name{definition}, \name{plain} or a \name{hypothesis}.
 The formulas include the binary connectives
@@
 in \TPTP syntax. We begin by declaring the $p$ axiom using the \verb!axiom!
-keyword. Later, we include the expected conclusion using the \verb!conjecture!
-keyword.
+keyword. Later, we include the expected conclusion using the
+\verb!conjecture! keyword.
 
@@
 fof(goal, conjecture, p).
-fof(subgoal_0, plain, p, inference(strip, [], [goal])).
-fof(negate_0_0, plain, ~ p, inference(negate, [], [subgoal_0])).
+fof(subgoal_0, plain, p, inf(strip, [], [goal])).
+fof(negate_0_0, plain, ~ p, inf(negate, [], [subgoal_0])).
 fof(normalize_0_0, plain, ∼ p,
-  inference(canonicalize, [], [negate_0_0])).
+  inf(canonicalize, [], [negate_0_0])).
 fof(normalize_0_1, plain, p,
-  inference(canonicalize, [], [premise])).
+  inf(canonicalize, [], [premise])).
 fof(normalize_0_2, plain, $false,
-  inference(simplify, [], [normalize_0_0, normalize_0_1]))
+  inf(simplify, [], [normalize_0_0, normalize_0_1]))
 cnf(refute_0_0, plain, $false,
-  inference(canonicalize, [], [normalize_0_2])).
+  inf(canonicalize, [], [normalize_0_2])).
 \end{verbatim}
@@
 
+\begin{remark}
+In order to keep as short as possible the \Metis derivations 
+for increasing the readability, we have simplified the \TSTP
+syntax and \Metis derivations (see a simplification in Fig.~\ref{fig:simplified-tstp}).
+For instance in \TSTP derivations, we use \verb!inf! instead of \verb!inference!. If the role of the formula is \verb!plain!, we omit it.
+We shorten names generated automatically by \Metis, \eg,
+\verb!sg0! instead of \verb!subgoal_0! or \verb!norm0_0!
+insead of \verb!normalize_0_0!.
+Finally, if the inference rule does not need arguments except its parent nodes, we remove the field for useful information.
+A simplified version of the \texttt{TSTP} derivation of Fig.~\ref{fig:metis-proof-tstp} is the following.
+
+\begin{verbatim}
+fof(premise, axiom, p).
+fof(goal, conjecture, p).
+fof(sg0, p, inf(strip, [goal])).
+fof(neg0, ~ p, inf(negate, [sg0])).
+fof(norm0, ∼ p, inf(canonicalize, [neg0])).
+fof(norm1, p, inf(canonicalize, [premise])).
+fof(norm2, $false, inf(simplify, [norm0, norm1]))
+cnf(refute0, $false, inf(canonicalize, [norm2])).
+\end{verbatim}
+
+\end{remark}
+
 \end{document}

### 2017-10-22 paper/sections/proof-reconstruction/conjunct.tex
[ paper ] table added.
[ paper ] conjunct reviewed.

@@
 \begin{verbatim}
-fof(normalize_1, plain, p & q & (r | ~ p),
-  inference(canonicalize, [], [x])).
-fof(normalize_2, plain, q,
-  inference(conjunct, [], [normalize_1])).
-fof(normalize_2, plain, (r | ~ p),
-  inference(conjunct, [], [normalize_1])).
+fof(p1, p & q & (r | ~ p), inf(canonicalize, [x])).
+fof(p2, q, inf(conjunct, [p1])).
+fof(p3, (r | ~ p), inf(conjunct, [p1])).
 \end{verbatim}
 
-\begin{definition}[conjunct]
-  \label{def:conjunct}
-  \begin{align*}
-    \begin{split}
-    &\fconjunct : \Prop \to \Prop \to \Prop\\
-    &\fconjunct(φ, ψ) =
+\begin{mainth}
+  \label{thm:conjunct}
+  If $Γ ⊢ φ$ and $ψ  : \Prop$ then $Γ ⊢ \fconjunct~φ~ψ$, where,
+  \begin{equation*}
+  % \label{eq:rank-definition}
+  \begin{aligned}
+  &\hspace{.495mm}\fconjunct : \Prop \to \Prop \to \Prop\\
+  &\begin{array}{llll}
+  \fconjunct~φ~ψ &=
         \begin{cases}
             ψ, &\text{ if }φ ≡ ψ\\
-          ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ \fconjunct(φ₁, ψ)\\
-          ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ , }ψ ≡ \fconjunct(φ₂, ψ)\\
+            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }\fconjunct(φ₁, ψ) ≡ ψ  \\
+            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }\fconjunct(φ₂, ψ) ≡ ψ  \\
             φ, &\text{ otherwise.}
           \end{cases}
-    \end{split}
-  \end{align*}
-\end{definition}
+  \end{array}
+  \end{aligned}
+  \end{equation*}
+\end{mainth}
 
-\begin{theorem}[thm-conjunct]
-  \label{thm:thm-conjunct}
-  If $Γ ⊢ φ$ and $ψ  : \Prop$ then $Γ ⊢ \fconjunct(φ, ψ)$.
-\end{theorem}
-\begin{proof}\hspace{2cm}
-\begin{itemize}
-  \item For the case $φ ≡ ψ$, $Γ ⊢ \fconjunct(φ, ψ)$ normalizes to $Γ ⊢ ψ$.
-Then, we get the desire conclusion by applying the $\fsubst$ theorem.
-  \item If the proposition $φ$ is a conjunction, and we can get $ψ ≡ \fconjunct(φ_{i}, ψ)$ for some $i = 1,\ 2$, then,
+\begin{proof}\hspace{2cm}\\
+Case $φ ≡ ψ$. $Γ ⊢ \fconjunct~φ~ψ$ normalizes to $Γ ⊢ ψ$.
+Then, we get the desire conclusion by applying the $\fsubst$ theorem.\\[2mm]
+Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct(φ_{i}, ψ)$ for some $i = 1,\ 2$, then,
 
@@
   \UnaryInfC{$Γ ⊢ φ_{i}$}
+  \RightLabel{by hyp.}
   \UnaryInfC{$Γ ⊢ \fconjunct(φ_{i}, ψ)$}
   \AxiomC{$ψ ≡ \fconjunct(φ_{i}, ψ)$}
-  \RightLabel{subst.}
+  \RightLabel{subst}
   \BinaryInfC{$Γ ⊢ ψ$}
@@
 \end{equation*}
-\item The last case follows trivially by using the same hypothesis.
-\end{itemize}
+Otherwise, the last case follows trivially.
 \end{proof}
+
 \end{document}

### 2017-10-22 paper/sections/proof-reconstruction/negate.tex
[ paper ] removed HEAD.
[ paper ] conjunct reviewed.

@@
 Each proof of a subgoal is a refutation, thereby each proof assumes
-the negation of its subgoal. The \negate rule
-assumes the negation of such subgoals, and
-appears after applying the \strip inference to the goal.
+the negation of its subgoal.
+The \negate rule assumes the negation of such subgoals. Then, this rules
+is always derived from a strip inference application as we can see in 
+the following \TSTP excerpt.
 
 \begin{verbatim}
-fof(goal, conjecture, (p & q)).
-fof(subgoal_0, plain, (p), inference(strip, [], [goal])).
-fof(subgoal_1, plain, (p => q), inference(strip, [], [goal])).
-fof(negate_0_0, plain, (~ p), inference(negate, [], [subgoal_0])).
+fof(sg0, (~ p => q), inf(strip, [goal])).
+fof(neg0, ~ (~ p => q), inf(negate, [sg0])).
 \end{verbatim}
 
-To emulate this rule, we introduce the negation
+To emulate this rule, we only need to introduce the negation
 of the subgoal by using $assume$ rule from the inferences in

### 2017-10-22 paper/sections/proof-reconstruction/strip.tex
[ paper ] conjunct reviewed.

@@
 \begin{verbatim}
-fof(goal, conjecture, ((p & r) & q)).
-fof(subgoal_0, plain, p,
-    inference(strip, [], [goal])).
-fof(subgoal_1, plain, p => r,
-    inference(strip, [], [goal])).
-fof(subgoal_2, plain, (p & r) => q,
-    inference(strip, [], [goal])).
+fof(goal, conjecture, (p & r) & q)).
+fof(sg0, p, inf(strip, [goal])).
+fof(sg1, p => r, inf(strip, [goal])).
+fof(sg2, (p & r) => q, inf(strip, [goal])).
 \end{verbatim}
@@
 Let $n : \Nat$ the complexity measure of the strip function in
-Eq.~\ref{eq:strip-unfixed}.
+Eq.~(\ref{eq:strip-unfixed}).
 If $Γ ⊢ \fstrip~φ~n$ then $Γ ⊢ φ$.
@@
 The proof is by induction on the structure of the
-formula~$φ$ by following the cases in Eq.~(\ref{eq:strip}).
-We present some cases but for a complete proof, we refer the reader to~\cite{AgdaMetis}.
+formula~$φ$ by following the cases in Eq.~(\ref{eq:strip-fixed}).
+We present a straightforward case with double negation, a case with
+conjunction connective, and last, the case with a negated disjunction.
+We refer the reader to~\cite{AgdaMetis} for the complete proof in \Agda.
 
-\begin{itemize}
-\item Case $φ ≡ ¬ ¬ φ₁$.
+Case $φ ≡ ¬ ¬ φ₁$.
 \begin{equation*}
@@
 
-\item Case $φ ≡ φ₁ ∧ φ₂$. We get a proof for each conjunct and using the
-introduction rule for conjunction connective, the result follows.
+Case $φ ≡ φ₁ ∧ φ₂$. We get a proof for each conjunct and using the
+introduction rule for conjunction connective, the expected result follows.
 
@@
 
-\item Case $φ ≡ φ₁ ⇒ φ₂$.
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{}
-  \RightLabel{assume φ₁}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₁$}
-  \AxiomC{$Γ ⊢ \fstrip~(φ₁ ⇒ φ₂)~(\suc~n)$}
-  \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
-  \RightLabel{lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
-  \RightLabel{weaken φ₁}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
-  \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ , φ₁ ⊢ \fstrip~φ₂~n$}
-  \RightLabel{by hip}
-  \UnaryInfC{$Γ , φ₁ ⊢ φ₂$}
-  \RightLabel{⇒-intro}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
-  \end{bprooftree}
-\end{equation*}
-
-\item Case $φ ≡ ¬ (φ₁ ∨ φ₂)$. We show that $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
-The result follows by introducing the conjunction and applying
-De Morgan Laws.
+Case $φ ≡ ¬ (φ₁ ∨ φ₂)$. We show the theorems $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
+With the conjunction of $¬ φ₁$ and $¬ φ₂$ by applying De Morgan Law, the result follows.
 
@@
 \end{equation*}
-\end{itemize}
-\end{sketchproof}
-
 \begin{equation*}
@@
 \end{equation*}
-\TheEnd
+\end{sketchproof} % the proof continue...
 
@@
 For the sake of brevity, we state the following theorem for the
-\strip function when the goal has only two subgoals. In other cases, we extend the theorem in the natural way.
+\strip function when the goal has only two subgoals. In other cases, we extend that theorem in the natural way.
 
 \begin{mainth}
-\label{thm:thm-strip}
- If $s_1$ and $s_2$ are the subgoals of the goal $φ$, $Γ ⊢ s_1$, and
-$Γ ⊢ s_2$ then $Γ ⊢ φ$.
+\label{thm:strip}
+If $s_1$ and $s_2$ are the subgoals of the goal $φ$, that is,
+$\fstrip~φ~n~≡~s_1\wedge~s_2$.
+If $Γ ⊢ s_1$ and $Γ ⊢ s_2$ then $Γ ⊢ φ$.
 \end{mainth}
@@
 \end{equation*}
-\TheEnd
 \end{proof}

### 2017-10-22 paper/sections/conclusions.tex
[ paper ] clausify added.

@@
 solutions for problems in classical propositional logic without
-equality. As a product of this research, we were able to build a proof-reconstruction tool written in \Haskell. This tool generates
+equality. As a product of this research, we were able to build a
+proof-reconstruction tool written in \Haskell. This tool generates
 \Agda proof-terms of \Metis \TSTP derivations. \Agda files
@@
 proposition fragment with equality of \Metis.
-Another option is to extend the proof-reconstruction to support other \ATPs for \CPL like \name{EProver} or \name{Z3}.
+Another option is to extend the proof-reconstruction to support other \ATPs
+for \CPL like \name{EProver} or \name{Z3}.
 This development can be carried out by following the \name{EProver}
@@
 exposed in Section~\ref{ssec:emulating-inferences},
-admits some improvements, we leave it for future work. We concern
-mainly for a better coverage of the \simplify rule.
+admits some improvements that we leave it for future work.
+
+For instance, we can investigate the consequences of removing $clausify$ inference by strengthen $canonicalize$ rule in Thm.~\ref{thm:canonicalize}
+The \simplify rule is still lacking of some coverage since it is fairly complex, many cases could be omitted.
 Other improvements are related with computational efficiency of

### 2017-10-22 paper/sections/proof-reconstruction/clausify.tex
[ paper ] roman in theorems.
[ paper ] table added.
[ paper ] clausify added.

@@
 negation of an atom (negative literal).
-It is important to notice that this kind of conversion
-between one formula to its clausal normal form is not unique, and \Metis has a
-customized approach to perform that transformation. That is the reason we
-perform some reordering for the CNF of the source formula to fulfill this
-issue.
+It is important to notice that this kind of conversion between one formula 
+to its clausal normal form is not unique, and \Metis has a customized 
+approach to perform that transformation. That is the reason we perform some 
+reordering for the \CNF of the source formula to fulfill this issue.
 
 In the following \Metis \TSTP derivation, we see an example where
-\clausify expands the formula \texttt{normalize\_0\_0} by using distributive
+\clausify expands the formula \texttt{norm0} by using distributive
 laws presented in conjunctive normal form conversion.
@@
 \begin{verbatim}
-fof(a1, axiom, (p => (q & r))).
+fof(a1, axiom, p => (q & r)).
 ...
-fof(normalize_0_0, plain, (~ p | (q & r)),
-    inference(canonicalize, [], [a1])).
-fof(normalize_0_1, plain, ((~ p | q) & (~ p | r)),
-    inference(clausify, [], [normalize_0_0])).
+fof(norm0, (~ p | (q & r)), inf(canonicalize, [a1])).
+fof(norm1, ((~ p | q) & (~ p | r)), inf(clausify, [norm0])).
+...
 \end{verbatim}
 
-\begin{definition}[clausify]
-  \label{def:clausify}
- \begin{align*}
-   \begin{split}
-      &\fclausify : \Prop → \Prop → \Prop\\
-      &\fclausify~φ~ψ =
+\begin{mainth}
+\label{thm:clausify}
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fclausify~φ~ψ$, where,
+
+  \begin{equation*}
+  \begin{aligned}
+  &\hspace{.495mm}\fclausify : \Prop → \Prop → \Prop\\
+  &\begin{array}{llll}
+  \fclausify~φ~ψ &=
          \begin{cases}
@@
       \end{cases}
-      \end{split}
-  \end{align*}
-\end{definition}
+  \end{array}
+  \end{aligned}
+  \end{equation*}
+\end{mainth}
 
-\begin{theorem}[thm-clausify]
-\label{thm:thm-clausify}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fclausify~φ~ψ$.
-\end{theorem}
-
-\begin{proof} If $φ ≡ ψ$, this lemmas follows after applying $\fsubst$
-lemma. Otherwise, we use Theorem~\ref{thm:thm-reorder-and-or} and Theorem~\ref{thm:thm-cnf}.
+\begin{proof}
+If $φ ≡ ψ$, $Γ ⊢ \fclausify~φ~ψ$ normalizes to $Γ ⊢ ψ$. The conclusion follows by applying the $\fsubst$ lemma.\\[2mm]
+Otherwise, we use Theorem~\ref{thm:thm-reorder-and-or} and Theorem~\ref{thm:thm-cnf}.
 \end{proof}
@@
 into the problem axioms or definitions in the domain of the solution.
-The Clausification algorithms is mainly described on paper by
-\citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}. We left for future work
-investigate the consequences of removing $clausify$ inference by
-strengthen $canonicalize$ rule in Def.~\ref{def:canonicalize}
+The clausification algorithms is mainly described on paper by
+\citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.
 \end{remark}

### 2017-10-22 paper/sections/proof-reconstruction.tex
[ paper ] conjunct reviewed.
[ paper ] clausify added.
[ paper ] simplify and its example added.
[ paper ] final comment.

@@
 For syntactical equivalence, we write the equality as $φ ≡ ψ$
-for $φ : \Prop$ and $ψ : \Prop$.
+for $φ : \Prop$ and $ψ : \Prop$. For this equality, we assume the
+reflexivity, symmetry and transitivity property.
 
@@
     \\
-    \texttt{negate}
-      &Negate the formula
-      &Thm.~\ref{thm:negate}
-    \\
+    % \texttt{negate}
+    %   &Negate the formula
+    %   &Thm.~\ref{thm:negate}
+    % \\
     \texttt{resolve}
@@
 \subfile{sections/proof-reconstruction/strip.tex}
-% \subfile{sections/proof-reconstruction/negate.tex}
+\subfile{sections/proof-reconstruction/negate.tex}
+\subfile{sections/proof-reconstruction/conjunct.tex}
 % \subfile{sections/proof-reconstruction/resolve.tex}
 % \subfile{sections/proof-reconstruction/canonicalize.tex}
-% \subfile{sections/proof-reconstruction/conjunct.tex}
-% \subfile{sections/proof-reconstruction/clausify.tex}
-% \subfile{sections/proof-reconstruction/simplify.tex}
+\subfile{sections/proof-reconstruction/clausify.tex}
+\subfile{sections/proof-reconstruction/simplify.tex}
 
@@
 
+Now, we have finished the formalization of every inference rule in 
+a \Metis proof, we are able to justify step-by-step any proof
+for a problem in propositional logic. 
+For instance, we tested successfully the translation by \Athena jointly with 
+the \Agda formalizations of the rules mentioned above with more than eighty representative theorems in propositional logic.
+An interested reader can test the problems~\cite{Prieto-Cubides2017} in the \Athena tool repository~\cite{Athena}.
+
 \end{document}

### 2017-10-22 paper/sections/conclusions.tex
[ paper ] simplify and its example added.
[ paper ] related work.

@@
 
+We are able to say that Kansos~\cite{Kanso2012} proof-reconstruction is 
+similar to the approach presented in Section~\ref{ssec:workflow}.
+Nevertheless, the authors aim to justify some of the inference
+rules by using propositional semantics. We instead perform only a syntactic
+analysis of the derivations.
+
 Summarizing, we provided for each \Metis inference rule a theorem in

### 2017-10-22 paper/sections/related-work.tex
[ paper ] related work.

--- 2017-10-18 paper/sections/related-work.tex
@@
 
-\name{Sledgehammer} is a tool for \name{Isabelle} proof assistant
-\cite{paulson1994isabelle} that provides a full integration of
-automatic theorem provers including \ATPs (see, for example,
-\cite{meng2006automation}, \cite{blanchette2013extending} and
-\cite{Fleury2014}) and \SMT solvers (see, for instance,
-\cite{hurlin07practical}, \cite{bohme2010},
-\cite{blanchette2013extending}, and \cite{Fleury2014}) with
-\name{Isabelle/HOL} \cite{nipkow2002isabelle}, the specialization of
+There are many proof-reconstruction tools nowadays.
+Let us mention a list of some representative tools mainly based on the description by \citeauthor{Sicard-Ramirez2016}~\cite{Sicard-Ramirez2016}.
+
+The \name{Isabelle} proof assistant has the \name{Sledgehammer} tool.
+This program provides a full integration between
+automatic theorem provers~\cite{meng2006automation,blanchette2013extending,Fleury2014,hurlin07practical,bohme2010,blanchette2013extending} and
+\name{Isabelle/HOL}~\cite{nipkow2002isabelle}, the specialization of
 \name{Isabelle} for higher-order logic.
-\citeauthor{Een2004}~\cite{Een2004} integrates \name{Leo-II} and
-\name{Satallax}, two theorem provers for high-order logic with
-\name{Isabelle/HOL} proposing a modular proof-reconstruction work
-flow.
+A modular proof-reconstruction workflow is presented jointly with
+the full integration of \name{Leo-II} and \name{Satallax} provers with \name{
+Isabelle/HOL} in \citeauthor{Een2004}~\cite{Een2004}.
 
@@
 Hurd~\cite{Hurd1999} integrates the first-order resolution prover
-\name{Gandalf} with \name{HOL}~\cite{norrish2007hol}, a high-order
-theorem prover, following an \abbre{LCF} model implementing the
-tactic \verb!GANDALF_TAC!. For \name{HOL Light}, a version of
+\name{Gandalf} with the high-order
+theorem prover \name{HOL}~\cite{norrish2007hol}. Hurd implements the
+tactic \verb!GANDALF_TAC! following an \abbre{LCF} model to reconstruct
+\name{Gandalf} proofs. For \name{HOL Light}, a version of
 \name{HOL} but with a simpler logic core, the \SMT solver \name{CVC4}
-was integrated, and \citeauthor{kaliszyk2013}~\cite{kaliszyk2013}
-reconstruct proofs from different ATPs with their \name{PRocH} tool,
-replaying the detailed inference steps from the ATPs with internal
+was integrated. \citeauthor{kaliszyk2013}~\cite{kaliszyk2013}
+reconstruct proofs from different ATPs with the \name{PRocH} tool by
+replaying detailed inference steps from the ATPs with internal
 inference methods implemented in \name{HOL Light}.
 
-% Taken from: % Färber, M., & Kaliszyk, C. (2015). Metis-based
-% Paramodulation Tactic for HOL
-
-% Light. In GCAI 2015. Global Conference on Artificial Intelligence
-% Metis-based
-
-% (Vol. 36, pp. 127–136).
-
-% HOL(y)Hammer [KU15] is an automated deduction framework for HOL4 and
-% HOL Light.
-
-% Given a conjecture, it attempts to find suitable premises, then
-% calls external ATPs such as E[Sch13], Vampire [KV13], or Z3 [dMB08],
-% and attempts to reconstruct the proof using the premises used by the
-% ATP. To reconstruct proofs, it uses tactics such as MESON,
-% simplification, and a few other decision procedures, however, these
-% are sometimes not p owerful enough to reconstruct proofs found by
-% the external ATPs.
-
-\name{Waldmeister} is an automatic theorem prover for unit
-equational logic \cite{hillenbrand1997}.
-\citeauthor{foster2011integrating}~\cite{foster2011integrating}
-integrate \name{Waldmeister} into \Agda
-\cite{agdateam}. This integration requires a proof-reconstruction
-step, but authors' approach is restricted to pure equational logic
---also called identity theory~\cite{humberstone2011}-- that is,
-first-order logic with equality but no other predicate symbols and
-no functions symbols~\cite{appel1959}.
-
-Kanso and Setzer~\cite{kanso2016light} integrate the propositional
-fragment of \name{EProver} in \Agda. In this work, the authors
+For the proof assistant \Agda, we found two proof-reconstruction tools.
+First, the integration with the \name{Waldmeister}~\cite{hillenbrand1997} prover by \citeauthor{foster2011integrating}~\cite{foster2011integrating}.
+A prover for pure equational logic, i.e.
+first-order logic with equality but no other predicate symbols and no functions symbols.
+Second, Kanso and Setzer in~\cite{kanso2016light} integrate the propositional
+fragment of the \name{EProver}. The tool presented by the authors
 translate automatically propositional logic problems written in \Agda
@@
 derivation and outputs \Agda code.
-We are able to say their proof-reconstruction is almost
-similar as the approach presented in Section~\ref{ssec:workflow}.
-Nevertheless, Kanso and Setzer aim to justify some of the inference
-rules by using propositional semantics instead of only syntactic
-treatment as shown above.
 

### 2017-10-22 paper/sections/conclusions.tex
[ paper ] conclusions added.

--- 2017-10-20 paper/sections/conclusions.tex
@@
 
-We presented a reliable proof-reconstruction in type theory of \Metis
-solutions for problems in classical propositional logic without
-equality. As a product of this research, we were able to build a proof-reconstruction tool written in \Haskell. This tool generates
-\Agda proof-terms of \Metis \TSTP derivations. \Agda files
-delivered by the aforementioned tool are supported by the
-formalization in \Agda~\cite{AgdaProp,AgdaMetis} of the \Metis rules
-described in Section~\ref{ssec:emulating-inferences}.
+We presented a reliable proof-reconstruction in type theory
+for the propositional fragment of the \Metis prover.
+
+We built a proof-reconstruction tool written in \Haskell
+to generate \Agda proof-terms of \Metis \TSTP derivations.
+\Agda files delivered by the translator contain call to theorems from the
+\Agda formalizations of \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
 
@@
 the prover, which is rarely included in the output of these programs,
-see Section~\ref{sssec:normalization} and Section~\ref{sssec:reordering}.
+see Section~\ref{ssec:emulating-inferences}.
 We chose that syntactical treatment as the opportunity
@@
 
+Besides the fact, Kansos~\cite{Kanso2012} proof-reconstruction is
+similar to the approach presented in Section~\ref{ssec:workflow},
+the authors aim to justify some of the inference
+rules by using propositional semantics. We instead perform only a syntactic analysis of the derivations as we mentioned above.
+
 Summarizing, we provided for each \Metis inference rule a theorem in
-type theory to emulate the rule reasoning. This approach, mainly
-exposed in Section~\ref{ssec:emulating-inferences},
-admits some improvements, we leave it for future work. We concern
-mainly for a better coverage of the \simplify rule.
+type theory to emulate the rule reasoning. Our approach is mainly
+exposed in Section~\ref{ssec:emulating-inferences}.
+We detect some improvements for our approach that we leave it for future
+work.
+For instance, we can investigate the consequences of removing \clausify
+inference by strengthen \canonicalize rule in Thm.~\ref{thm:canonicalize}
+The \simplify rule is still lacking of some coverage since it is fairly complex, many cases could be omitted.
 Other improvements are related with computational efficiency of
@@
 One of the main contribution of this study was
-increasing the trustworthiness of the automatic provers,
-in our case, \Metis.
-Justifying a proof of a theorem prover
+increasing the trustworthiness of the automatic prover \Metis.
+Justifying a proof by a theorem prover
 has a real significant impact for these automatic tools.

### 2017-10-22 paper/sections/proof-reconstruction/resolve.tex
[ paper ] table added.
[ paper ] removed HEAD.
[ paper ] fixing lemmas.

@@
 by converting propositions to their conjunctive normal forms,
-and reordering those and the inner disjunctions  to match them
+and reordering those and the inner disjunctions to match them.
 In this section, we provide some theorems to perform such reordering tasks,
@@
 The $\rm{rconj}$ function that converts conjunction to its right-associative form
-is not presented here, but is defined in a similar way (see its implementation
+is not presented here, but is defined in a similar way (see its definition
 in~\cite{AgdaMetis}).
@@
 
-\begin{lemma}[lem-rdisj]
+\begin{mainlemma}[lem-rdisj]
 \label{lem:lem-rdisj}
   If $Γ ⊢ φ$ then $Γ ⊢ \rm{rdisj}(φ)$.
-\end{lemma}
+\end{mainlemma}
 
@@
 
-\begin{lemma}[lem-build$_{\boldsymbol{∨}}$]
+\begin{mainlemma}[lem-build$_{\boldsymbol{∨}}$]
 \label{lem:lem-build-or}
 If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}(φ)$.
-\end{lemma}
+\end{mainlemma}
 
@@
 
-\begin{lemma}[lem-factor]
+\begin{mainlemma}[lem-factor]
 \label{lem:lem-factor}
   $Γ ⊢ φ$ then $Γ ⊢ \ffactor(φ)$.
-\end{lemma}
+\end{mainlemma}
 
@@
 
-\begin{lemma}[lem-sbuild$_{\boldsymbol{∨}}$]
+\begin{mainlemma}[lem-sbuild$_{\boldsymbol{∨}}$]
 \label{lem:lem-sbuild-or}
 If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}(φ, ψ)$.
-\end{lemma}
+\end{mainlemma}
 
@@
 
-\begin{theorem}[thm-reorder$_{\boldsymbol{∨}}$]
+\begin{mainth}[thm-reorder$_{\boldsymbol{∨}}$]
   \label{thm-reorder-or}
   If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}(φ, ψ)$.
-\end{theorem}
+\end{mainth}
 
@@
 
-\begin{lemma}[lem-reorder$_{\boldsymbol{∧}}$]
+\begin{mainlemma}[lem-reorder$_{\boldsymbol{∧}}$]
   \label{lem:lem-reorder-and}
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}(φ, ψ)$.
-\end{lemma}
+\end{mainlemma}
 
@@
 
-\begin{lemma}[lem-conjunct$_{\boldsymbol{∨}}$]
+\begin{mainlemma}[lem-conjunct$_{\boldsymbol{∨}}$]
   \label{lem:lem-conjunct-or}
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}(φ, ψ)$.
-\end{lemma}
+\end{mainlemma}
 
@@
 
-\begin{theorem}[thm-reorder$_{\boldsymbol{∧∨}}$]
+\begin{mainth}[thm-reorder$_{\boldsymbol{∧∨}}$]
   \label{thm:thm-reorder-and-or}
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$.
-\end{theorem}
+\end{mainth}
 
@@
 
-\begin{lemma}[lem-rsol]
+\begin{mainlemma}[lem-rsol]
   \label{lem:lem-rsol}
   If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}(φ)$.
-\end{lemma}
+\end{mainlemma}
 
@@
 
-\begin{theorem}[thm-resolve]
+\begin{mainth}[thm-resolve]
   \label{thm:thm-resolve}
@@
   $Γ ⊢ \fresolve(φ₁, φ₂, l, ψ)$.
-\end{theorem}
+\end{mainth}
+
 \Needspace{3\baselineskip}

### 2017-10-22 paper/sections/proof-reconstruction/resolve.tex
[ paper ] working on resolve.

@@
 and reordering those and the inner disjunctions to match them.
-In this section, we provide some theorems to perform such reordering tasks,
-the goals are the following.
+Below, we provide some lemmas to perform such reordering tasks,
+we omit the proofs but they can found in~\cite{AgdaMetis}.
 
-\begin{itemize}
-  \item Reorder a disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$ to match with
-$ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$. For all $i$, there exists at least one $j$ such
-that $φᵢ ≡ ψⱼ$.
-  \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another
-CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$. For all $i$, there exists at least one $j$
-such that $φᵢ ≡ ψⱼ$.
-\end{itemize}
+% \begin{itemize}
+%   \item Reorder a disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$ to match with
+% $ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$. For all $i$, there exists at least one $j$ such
+% that $φᵢ ≡ ψⱼ$.
+%   \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another
+% CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$. For all $i$, there exists at least one $j$
+% such that $φᵢ ≡ ψⱼ$.
+% \end{itemize}
 
-First, we define the $\rm{rdisj}$ function to convert
-a disjunction in its right-associative form.
-The $\rm{rconj}$ function that converts conjunction to its right-associative form
-is not presented here, but is defined in a similar way (see its definition
-in~\cite{AgdaMetis}).
+First, we define \rm{rassoc}$_{⬓}$ function in Eq.~(\ref{def:right-square})
+to convert a disjunctions or a conjunction into its right-associative form.
+We use $\rm{rassoc}_{∧}$ to convert conjunctions and $\rm{rassoc}_{∨}$ for
+disjunctions.
 
-\begin{definition}[rdisj]
-\label{def:rdisj}
-  \begin{align*}
-    \begin{split}
-    \label{eq:rdisj-def}
-      &\rm{rdisj}(φ) : \Prop \to \Prop\\
-      &\rm{rdisj}(φ) =
-      \begin{cases}
-      \rm{rdisj}(φ₁ ∨ (φ₂ ∨ φ₃)),  & \text{ if } φ ≡ (φ₁ ∨ φ₂) ∨ φ₃\\
-      φ₁ ∨ \rm{rdisj}(φ₂),         & \text{ if } φ ≡ φ₁ ∨ φ₂\\
-      φ,                      & \text{ otherwise.}
-      \end{cases}
-    \end{split}
-  \end{align*}
-\end{definition}
+\begin{equation}
+\label{def:right-square}
+  \begin{aligned}
+    &\hspace{.495mm}\rm{rassoc}_{⬓} : \Prop \to \Prop\\
+    &\begin{array}{lll}
+    \rm{rassoc}_{⬓} &((φ₁ ⬓ φ₂) ⬓ φ₃) &= \rm{rassoc}_{⬓}~(φ₁~⬓~(φ₂ ⬓ φ₃))\\
+    \rm{rassoc}_{⬓} &(φ₁ ⬓ φ₂)        &= φ₁~∨~\rm{rassoc}_{⬓}~φ₂\\
+    \rm{rassoc}_{⬓} &φ                &= φ
+    \end{array}
+  \end{aligned}
+\end{equation}
 
-\begin{mainlemma}[lem-rdisj]
-\label{lem:lem-rdisj}
-  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rdisj}(φ)$.
+\begin{example}\hspace{5mm}\\
+\begin{enumerate}
+\item $\rm{rassoc}_{∨}~(((p ∨ ((q ∨ r) ∨ s)) ∨ t) = p ∨ (q ∨ (r ∨ (s ∨ t)))$.
+\item $\rm{rassoc}_{∧}~((((p ∧ q) ∧ r) ∧ s) ∧ t) = p ∧ (q ∧ (r ∧ (s ∧ t)))$.
+\end{enumerate}
+\end{example}
+
+\begin{remark}
+In \TPTP syntax, the formulas are in left-associative form by default.
+Despite of that convention, \Metis understands a formula to be in right-associative form by default. As we mentioned above, this is a matter to take into account for
+the proof-reconstruction. We opted to work as far as possible with right-associative formulas in~\cite{AgdaMetis}.
+\end{remark}
+
+\begin{mainlemma}
+\label{lem:lem-rassoc}
+  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rassoc}_{⬓}~φ$.
 \end{mainlemma}
 
-\begin{definition}[build$_{\boldsymbol{∨}}$]
 \begin{equation*}
@@
 \end{equation*}
-\end{definition}
 
@@
 \label{lem:lem-build-or}
-If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}(φ)$.
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}~φ~ψ$.
 \end{mainlemma}
@@
 otherwise stated.
-The $\ffactor$ function in Eq.~(\ref{eq:factor-definition}) intends to
-simplify a special case of disjunction, the repeated disjuncts
-(e.g., $\ffactor(φ ∨ φ) \mapsto\ φ$).
-Notice that other cases like $φ ∨ (ψ ∨ φ)$ do no reduce to $(ψ ∨ φ)$.
+The $\ffactor$ function in Eq.~(\ref{eq:factor-definition})
+simplifies a special case of disjunction, the repeated disjuncts
+(e.g., $\ffactor(φ ∨ φ) = φ$).
+Notice that other cases like $φ ∨ (ψ ∨ φ)$ do no reduce to $ψ ∨ φ$.
 
-\begin{definition}[factor]
 \begin{align}
@@
   \begin{cases}
-    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{, } φ₁ ≡ \ffactor(φ₂)\\
+    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ \ffactor(φ₂)\\
     φ,   &\text{ otherwise.}
@@
 equality between nested disjunctions.
-The result is the $\rm{sbuild}_{∨}$ function
+We define the $\rm{sbuild}_{∨}$ function in
+Eq.~(\ref{eq:strong-build-or-definition}).
 that uses every disjunct from the source formula, $φ$, to build up the
@@
 
-\begin{definition}[sbuild$_{\boldsymbol{∨}}$]
-\begin{align*}
+\begin{align}
   \begin{split}
@@
   \end{split}
-\end{align*}
-\end{definition}
+\end{align}
 
-\begin{mainlemma}[lem-sbuild$_{\boldsymbol{∨}}$]
+\begin{mainlemma}
 \label{lem:lem-sbuild-or}
@@
 
-\begin{definition}[reorder$_{\boldsymbol{∨}}$]
+\begin{mainth}[thm-reorder$_{\boldsymbol{∨}}$]
+  \label{thm-reorder-or}
+  If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}~φ~ψ~$, where,
   \begin{align*}
@@
     &\freorder_{∨} : \Prop \to \Prop \to \Prop\\
-    &\freorder_{∨} (φ, ψ) = \rm{sbuild}_{∨}(rdisj(φ), ψ).
+    &\freorder_{∨}~φ~ψ~= \rm{sbuild}_{∨}~(rassoc_{∨}~φ)~ψ.
     \end{split}
   \end{align*}
-\end{definition}
-
-\begin{mainth}[thm-reorder$_{\boldsymbol{∨}}$]
-  \label{thm-reorder-or}
-  If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}(φ, ψ)$.
 \end{mainth}
@@
 \begin{proof}
-Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
+Use Lemma~\ref{lem:lem-rassoc} and Lemma~\ref{lem:lem-sbuild-or}.
 \end{proof}
@@
 \begin{mainth}[thm-reorder$_{\boldsymbol{∧∨}}$]
-  \label{thm:thm-reorder-and-or}
+  \label{thm:reorder-and-or}
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$.
@@
 \begin{mainth}[thm-resolve]
-  \label{thm:thm-resolve}
+  \label{thm:resolve}
   If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ : \Prop$ then
@@
 \caption{Example of a resolution in \Metis using
-Thm.~\ref{thm:thm-resolve}.}
-%Application of Thm.~\ref{thm:thm-resolve} for the \TSTP excerpt Fig.~\ref{fig:resolve-tstp-example}.}
+Thm.~\ref{thm:resolve}.}
+%Application of Thm.~\ref{thm:resolve} for the \TSTP excerpt Fig.~\ref{fig:resolve-tstp-example}.}
 \end{figure}

### 2017-10-22 paper/sections/proof-reconstruction/conjunct.tex
[ paper ] clausify added.
last changes.

@@
             ψ, &\text{ if }φ ≡ ψ\\
-            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }\fconjunct(φ₁, ψ) ≡ ψ  \\
-            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }\fconjunct(φ₂, ψ) ≡ ψ  \\
+            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }\fconjunct~φ₁~ψ ≡ ψ  \\
+            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }\fconjunct~φ₂~ψ ≡ ψ  \\
             φ, &\text{ otherwise.}
@@
 Case $φ ≡ ψ$. $Γ ⊢ \fconjunct~φ~ψ$ normalizes to $Γ ⊢ ψ$.
-Then, we get the desire conclusion by applying the $\fsubst$ theorem.\\[2mm]
-Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct(φ_{i}, ψ)$ for some $i = 1,\ 2$, then,
+Then, we get the desire conclusion by applying the $\fsubst$ lemma.\\[2mm]
+Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct~φ_{i}~ψ$ for some $i = 1,\ 2$, then,
 
@@
   \RightLabel{by hyp.}
-  \UnaryInfC{$Γ ⊢ \fconjunct(φ_{i}, ψ)$}
-  \AxiomC{$ψ ≡ \fconjunct(φ_{i}, ψ)$}
+  \UnaryInfC{$Γ ⊢ \fconjunct~φ_{i}~ψ$}
+  \AxiomC{$ψ ≡ \fconjunct~φ_{i}~ψ$}
   \RightLabel{subst}

### 2017-10-22 paper/sections/proof-reconstruction/resolve.tex
last changes.

@@
 \begin{mainlemma}
-\label{lem:lem-rassoc}
+\label{lem:rassoc}
   If $Γ ⊢ φ$ then $Γ ⊢ \rm{rassoc}_{⬓}~φ$.
@@
 \begin{equation*}
-  \begin{split}
  \label{eq:build-or}
-  &\rm{build}_{∨} : \Prop → \Prop → \Prop\\
-  &\rm{build}_{∨}(φ, ψ) =%\\
-  % &\hspace{3mm}
+  \begin{aligned}
+  &\hspace{.495mm}\rm{build}_{∨} : \Prop → \Prop → \Prop\\
+  &\begin{array}{llll}
+    \rm{build}_{∨}&ψ~ψ &= ψ\\
+    \rm{build}_{∨}&(φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{1} ≡ ψ_{1}\\
+    \rm{build}_{∨}&(φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{2} ≡ ψ_{2}\\
+    \rm{build}_{∨}&φ~ψ&=φ&\text{ otherwise.}
+   \end{array}
+  \end{aligned}
+\end{equation*}
+
+\begin{equation}
+  \label{eq:ndisj-or}
+  \begin{aligned}
+  &\hspace{.495mm}\rm{ndisj}_{∨} : \NProp \to \NProp\\
+  &\begin{array}{lll}
+    \rm{ndisj}_{∨} &(¬ φ₁ ∨ φ₂) &=
         \begin{cases}
-  ψ, &\text{ if } φ ≡ ψ\\
-  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{, } \rm{build}_{∨}(φ, ψ_{i}) ≡ ψ_{i}\text{ for some }i=1, 2\\
-  φ, &\text{ otherwise.}
-  \end{cases}
-  \end{split}
-\end{equation*}
+         ⊤, &\text{ if } φ₁ ∈_{∨} φ₂\\
+         ⊤, &\text{ if } \rm{ndisj}_{∨}~φ₂≡ ⊤\\
+         ¬ φ₁ ∨ \rm{ndisj}_{∨}~φ₂, &\text{ otherwise.}
+        \end{cases}\\
+
+  \rm{ndisj}_{∨} &(φ₁ ∨ φ₂)&=
+        \begin{cases}
+         ⊤, &\,\,\,\,\,\,\text{ if } ¬φ₁ ∈_{∨} φ₂ \\
+         ⊤, &\,\,\,\,\,\,\text{ if } \rm{ndisj}_{∨}(φ₂) ≡ ⊤\\
+         φ₁ ∨ \rm{ndisj}_{∨}~φ₂, &\,\,\,\,\,\,\text{ otherwise.}
+        \end{cases}\\
+    \rm{ndisj}_{∨}&φ &=φ
+    \end{array}
+  \end{aligned}
+\end{equation}
 
@@
 \begin{mainlemma}[lem-build$_{\boldsymbol{∨}}$]
-\label{lem:lem-build-or}
+\label{lem:build-or}
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}~φ~ψ$.
@@
 \begin{mainlemma}[lem-factor]
-\label{lem:lem-factor}
+\label{lem:factor}
   $Γ ⊢ φ$ then $Γ ⊢ \ffactor(φ)$.
@@
 \begin{mainlemma}
-\label{lem:lem-sbuild-or}
+\label{lem:sbuild-or}
 If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}(φ, ψ)$.
@@
 
-\begin{mainth}[thm-reorder$_{\boldsymbol{∨}}$]
-  \label{thm-reorder-or}
+\begin{mainlemma}
+  \label{lem:reorder-or}
   If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}~φ~ψ~$, where,
@@
   \end{align*}
-\end{mainth}
+\end{mainlemma}
 
 \begin{proof}
-Use Lemma~\ref{lem:lem-rassoc} and Lemma~\ref{lem:lem-sbuild-or}.
+Use Lemma~\ref{lem:rassoc} and Lemma~\ref{lem:sbuild-or}.
 \end{proof}
@@
 
-\begin{mainlemma}[lem-reorder$_{\boldsymbol{∧}}$]
-  \label{lem:lem-reorder-and}
+\begin{mainlemma}
+  \label{lem:reorder-and}
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}(φ, ψ)$.
@@
 
-\begin{mainlemma}[lem-conjunct$_{\boldsymbol{∨}}$]
-  \label{lem:lem-conjunct-or}
+\begin{mainlemma}
+  \label{lem:conjunct-or}
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}(φ, ψ)$.
@@
 
-\begin{definition}[reorder$_{\boldsymbol{∧∨}}$]
+\begin{mainlemma}
+  \label{lem:reorder-and-or}
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$, where
    \begin{align*}
@@
       &\freorder : \Prop \to \Prop \to \Prop\\
-      &\freorder_{∧∨}(φ, ψ)=
+      &\freorder_{∧∨}~φ~ψ~=
         \begin{cases}
           ψ, &\text{ if } φ≡ψ\\
-          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ \freorder_{∧∨}(φ,ψ₁) ≡ ψ₁\\
-             &\text{and }\freorder_{∧∨}(φ, ψ₂) ≡ ψ₂\\
+          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁~\\
+             &\text{and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂~\\
           φ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂\\
-          \fconjunct_{∨}(φ, ψ) &\text{ otherwise.}
+          \fconjunct_{∨}~φ~ψ~ &\text{ otherwise.}
         \end{cases}
@@
   \end{align*}
-  \end{definition}
-
-\begin{mainth}[thm-reorder$_{\boldsymbol{∧∨}}$]
-  \label{thm:reorder-and-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$.
-\end{mainth}
+\end{mainlemma}
 
@@
 described above. We begin by defining a convenient version of
-the binary resolution in Def.~\ref{def:rsol}.
+the binary resolution in Def.~\ref{eq:rsol}.
 
-\begin{definition}[rsol]
-\label{def:rsol}
-\begin{align*}
-      \begin{split}
-        &\rm{rsol} : \Prop \to \Prop\\
-        &\rm{rsol}(φ) =
-        \begin{cases}
-          φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
-          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
-          φ, &\text{ otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align*}
-\end{definition}
+% \begin{equation}
+% \label{eq:rsol}
+% \begin{aligned}
+% &\rm{rsol} : \Prop \to \Prop\\
+%       \begin{split}
+%         &\rm{rsol} : \Prop \to \Prop\\
+%         &\rm{rsol}~φ =
+%         \begin{cases}
+%           φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
+%           φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
+%           φ, &\text{ otherwise.}
+%         \end{cases}
+%       \end{split}
+%   \end{align*}
+% \end{definition}
 
-\begin{mainlemma}[lem-rsol]
-  \label{lem:lem-rsol}
-  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}(φ)$.
+\begin{mainlemma}
+  \label{lem:rsol}
+  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}~φ$.
 \end{mainlemma}
@@
 
-\begin{definition}[resolve]
-\label{def:resolve}
- \begin{align*}
+\begin{mainth}
+  \label{thm:resolve}
+  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l : \Prop$, and $ψ : \Prop$ then
+  $Γ ⊢ \fresolve~φ₁~φ₂~l~ψ$, where,
+  \begin{equation}
   \begin{split}
+  \label{eq:resolve}
     &\fresolve : \Prop \to \Prop \to \Prop \to \Prop \to \Prop\\
-    &\fresolve(φ₁, φ₂, l, ψ) =
-      \rm{rsol}(\freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨} (φ₂, ¬ l ∨ ψ)).
+    &\fresolve~φ₁~φ₂~l~ψ =
+      \rm{rsol}~(\freorder_{∨}~φ₁~(l ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ l ∨ ψ)).
   \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{mainth}[thm-resolve]
-  \label{thm:resolve}
-  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l$, and $ψ : \Prop$ then
-  $Γ ⊢ \fresolve(φ₁, φ₂, l, ψ)$.
+  \end{equation}
 \end{mainth}
@@
     \AxiomC{$Γ ⊢ φ₁$}
-      \RightLabel{thm-reorder$_{∨}$,}
-      \UnaryInfC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ)$}
-   \end{bprooftree}
-  \end{equation*}
-    \vskip 1.5mm
- \begin{equation*}
-    \begin{bprooftree}
+    \RightLabel{Lemma~\ref{lem:reorder-and-or}}
+    \UnaryInfC{$Γ ⊢ \freorder_{∨}~φ₁~(l ∨ ψ)$}
+    \RightLabel{Lemma~\ref{lem:reorder-and-or}}
     \AxiomC{$Γ ⊢ φ₂$}
-      \RightLabel{thm-reorder$_{∨}$,}
-      \UnaryInfC{$Γ ⊢ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
-   \end{bprooftree}
-  \end{equation*}
-  \vskip 1.5mm
-  \begin{equation*}
-  \begin{bprooftree}
-    \AxiomC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ)$}
-    \AxiomC{$Γ ⊢ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
+    \UnaryInfC{$Γ ⊢ \freorder_{∨}~φ₂~(¬ l ∨ ψ)$}
     \RightLabel{∧-intro}
-    \BinaryInfC{$Γ ⊢ \freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨}(φ₂, ¬ l ∨ ψ)$}
-    \RightLabel{lem-rsol.}
-    \UnaryInfC{$Γ ⊢ \rm{rsol}(\freorder_{∨}(φ₁, l ∨ ψ) ∧ \freorder_{∨}(φ₂, ¬ l ∨ ψ))$}
+    \BinaryInfC{$Γ ⊢ \freorder_{∨}~φ₁~(l ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ l ∨ ψ)$}
+    \RightLabel{Lemma~\ref{lem:rsol}}
+    \UnaryInfC{$Γ ⊢ \rm{rsol}~(\freorder_{∨}~φ₁~(l ∨ ψ) ∧
+     \freorder_{∨}~φ₂~(¬ l ∨ ψ))$}
+    \RightLabel{by (\ref{eq:resolve})}
+    \UnaryInfC{$Γ ⊢ \fresolve~φ₁~φ₂~l~ψ$}
   \end{bprooftree}
@@
 
-\begin{figure}
-\label{fig:resolve-example}
+\begin{example}COMPLETAR ESTE EJEMPLO AL FINAL
 \begin{equation*}
@@
   \AxiomC{$Γ ⊢ p ∨ q ∨ r $}
-  \RightLabel{thm-resolve}
-  \BinaryInfC{$Γ ⊢ \fresolve(¬ r ∨ p ∨ q, p ∨ q ∨ r, r, p ∨ q)$}
+  \RightLabel{Theorem \ref{thm:resolve}}
+  \BinaryInfC{$Γ ⊢ \fresolve~(¬ r ∨ p ∨ q)~(p ∨ q ∨ r)~r~(p ∨ q)$}
   \UnaryInfC{$Γ ⊢ p ∨ q$}
@@
 \end{equation*}
-\caption{Example of a resolution in \Metis using
-Thm.~\ref{thm:resolve}.}
-%Application of Thm.~\ref{thm:resolve} for the \TSTP excerpt Fig.~\ref{fig:resolve-tstp-example}.}
-\end{figure}
+\end{example}
 

### 2017-10-22 paper/sections/proof-reconstruction/strip.tex
[ paper ] minor fixes.
[ paper ] fixing lemmas.
last changes.

@@
 
-We now define the $\fstrip$ function in Eq.~\ref{eq:strip-unfixed} that
+We now define the $\fstrip_0$ function in Eq.~\ref{eq:strip-unfixed} that
 yields the conjunction of subgoals that implies the goal of the problem in
@@
 \begin{aligned}
-&\hspace{.495mm}\fstrip : \Prop → \Nat → \Prop\\
+&\hspace{.495mm}\fstrip_0 : \Prop → \Nat → \Prop\\
 &\begin{array}{lll}
-\fstrip &(φ₁ ∧ φ₂)     &= \fuh~(\fstrip~φ₁) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂)\\
-\fstrip &(φ₁ ∨ φ₂)     &= \fuh~(¬ φ₁ ⇒ \fstrip~φ₂)\\
-\fstrip &(φ₁ ⇒ φ₂)     &= \fuh~(φ₁ ⇒ \fstrip~φ₂)\\
-\fstrip &(¬ (φ₁ ∧ φ₂)) &= \fuh~(φ₁ ⇒ \fstrip~¬ φ₂)\\
-\fstrip &(¬ (φ₁ ∨ φ₂)) &= \fuh~(\fstrip~¬ φ₁) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂)\\
-\fstrip &(¬ (φ₁ ⇒ φ₂)) &= \fuh~(\fstrip~φ₁) ∧ \fuh~(φ₁ ⇒ \fstrip~¬ φ₂)\\
-\fstrip &(¬ ¬ φ₁)      &= \fuh~(\fstrip~φ₁)\\
-\fstrip &(¬ ⊥)         &= ⊤\\
-\fstrip &(¬ ⊤)         &= ⊥\\
-\fstrip &φ             &= φ
+\fstrip_0 &(φ₁ ∧ φ₂)     &= \fuh~(\fstrip_0~φ₁) ∧ \fuh~(φ₁ ⇒ \fstrip_0~φ₂)\\
+\fstrip_0 &(φ₁ ∨ φ₂)     &= \fuh~(¬ φ₁ ⇒ \fstrip_0~φ₂)\\
+\fstrip_0 &(φ₁ ⇒ φ₂)     &= \fuh~(φ₁ ⇒ \fstrip_0~φ₂)\\
+\fstrip_0 &(¬ (φ₁ ∧ φ₂)) &= \fuh~(φ₁ ⇒ \fstrip_0~¬ φ₂)\\
+\fstrip_0 &(¬ (φ₁ ∨ φ₂)) &= \fuh~(\fstrip_0~¬ φ₁) ∧ \fuh~(¬ φ₁ ⇒ \fstrip_0~¬ φ₂)\\
+\fstrip_0 &(¬ (φ₁ ⇒ φ₂)) &= \fuh~(\fstrip_0~φ₁) ∧ \fuh~(φ₁ ⇒ \fstrip_0~¬ φ₂)\\
+\fstrip_0 &(¬ ¬ φ₁)      &= \fuh~(\fstrip_0~φ₁)\\
+\fstrip_0 &(¬ ⊥)         &= ⊤\\
+\fstrip_0 &(¬ ⊤)         &= ⊥\\
+\fstrip_0 &φ             &= φ
 \end{array}
@@
 
+%  1137  git add .
+%  1138  git commit -am "[ paper ] strip proof."
+%  1139  git pull origin paper
+%  1140  git push origin paper
 \begin{equation}
@@
 \fstrip &(¬ ⊤)         ~(\suc~n) &= ⊥\\
-\fstrip &φ             ~\emph{n} &= φ
+\fstrip &φ             ~\text{n} &= φ
 \end{array}
@@
 \label{lem:lem-inv-strip}
-Let $n : \Nat$ the complexity measure of the strip function in
+Let $\text{n} : \Nat$ the complexity measure of the strip function in
 Eq.~(\ref{eq:strip-unfixed}).
@@
   \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
-  \RightLabel{lemma~\ref{lem:inv-uh-lem}}
+  \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
   \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
@@
   \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
-  \RightLabel{lemma~\ref{lem:inv-uh-lem}}
+  \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
   \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
@@
 \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~¬ φ₁~n)$}
-\RightLabel{lemma~\ref{lem:inv-uh-lem}}
+\RightLabel{Lemma~\ref{lem:inv-uh-lem}}
 \UnaryInfC{$Γ ⊢ \fstrip~¬ φ₁~n$}
@@
   \UnaryInfC{$Γ ⊢ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)$}
-  \RightLabel{lemma~\ref{lem:inv-uh-lem}}
+  \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
   \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip~¬ φ₂~n$}
@@
   \BinaryInfC{$Γ ⊢ \fstrip~φ~n$}
-  \RightLabel{lemma~\ref{lem:lem-inv-strip}}
+  \RightLabel{Lemma~\ref{lem:lem-inv-strip}}
   \UnaryInfC{$Γ ⊢ φ$}

### 2017-10-23 paper/sections/proof-reconstruction/resolve.tex
last changes in subsections.

@@
     \rm{build}_{∨}&ψ~ψ &= ψ\\
-    \rm{build}_{∨}&(φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{1} ≡ ψ_{1}\\
-    \rm{build}_{∨}&(φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{2} ≡ ψ_{2}\\
+    \rm{build}_{∨}&φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{1} ≡ ψ_{1}\\
+    \rm{build}_{∨}&φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{2} ≡ ψ_{2}\\
     \rm{build}_{∨}&φ~ψ&=φ&\text{ otherwise.}
@@
 
-\begin{mainlemma}[lem-build$_{\boldsymbol{∨}}$]
+\begin{mainlemma}
 \label{lem:build-or}
@@
 
-\begin{align}
-\begin{split}
+\begin{mainlemma}
+\label{lem:factor}
+  $Γ ⊢ φ$ then $Γ ⊢ \ffactor~φ$, where, 
+  \begin{equation}
   \label{eq:factor-definition}
-  &\ffactor : \Prop → \Prop\\
-  &\ffactor(φ) =
-  \begin{cases}
-    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ \ffactor(φ₂)\\
-    φ,   &\text{ otherwise.}
-  \end{cases}
-\end{split}
-\end{align}
-
-\begin{mainlemma}[lem-factor]
-\label{lem:factor}
-  $Γ ⊢ φ$ then $Γ ⊢ \ffactor(φ)$.
+   \begin{aligned}
+   &\hspace{.495mm}\ffactor : \Prop → \Prop\\
+    &\begin{array}{llll}
+     \ffactor&(φ₁ ∨ φ₂) &=φ₁,  &\text{ if } φ₁ ≡ \ffactor~φ₂\\
+     \ffactor&φ &= φ, &\text{ otherwise.}
+  \end{array}
+\end{aligned}
+\end{equation}
 \end{mainlemma}
@@
 We define the $\rm{sbuild}_{∨}$ function in
-Eq.~(\ref{eq:strong-build-or-definition}).
+Eq.~(\ref{eq:strong-build-or}).
 that uses every disjunct from the source formula, $φ$, to build up the
@@
 
-\begin{align}
-  \begin{split}
-  \label{eq:strong-build-or-definition}
-    &\rm{sbuild}_{∨} : \Prop → \Prop → \Prop\\
-    &\rm{sbuild}_{∨}(φ, ψ) =%\\
-    % &\hspace{3mm}
-    \begin{cases}
-      \ffactor(\rm{build}_{∨}(φ₁, ψ) ∨ \rm{build}_{∨}(φ₂,ψ)),
-      &\text{ if }φ≡ φ₁ ∨ φ₂\\
-      \rm{build}_{∨}(φ, ψ),  & \text{ otherwise.}
-    \end{cases}
-  \end{split}
-\end{align}
-
 \begin{mainlemma}
 \label{lem:sbuild-or}
-If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}(φ, ψ)$.
+If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}~φ~ψ$, where, 
+\begin{equation}
+\label{eq:strong-build-or}
+ \begin{aligned}
+     &\hspace{.495mm}\rm{sbuild}_{∨} : \Prop → \Prop → \Prop\\
+    &\begin{array}{llll}
+    \rm{sbuild}_{∨}&(φ₁ ∨ φ₂)~ψ &=\ffactor(\rm{build}_{∨}~φ₁~ψ ∨ \rm{build}_{∨}~φ₂~ψ)&\\
+    \rm{build}_{∨}&φ~ψ &= \rm{build}_{∨}~φ~ψ& \text{ otherwise.}
+     \end{array}
+\end{aligned}
+\end{equation}
 \end{mainlemma}
@@
         &\freorder_{∧} : \Prop → \Prop \to \Prop\\
-        &\freorder_{∧}(φ, ψ) =
+        &\freorder_{∧}~φ~ψ =
         \begin{cases}
           φ, &\text{ if }φ ≡ ψ\\
-          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\freorder_{∧}(φ, ψ₁) ≡ ψ₁\\
-                  &\text{and }\freorder_{∧}(φ, ψ₂)≡ ψ₂\\
+          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\freorder_{∧}~φ~ψ₁ ≡ ψ₁\\
+                  &\text{and }\freorder_{∧}~φ~ψ₂≡ ψ₂\\
           φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
-          \fconjunct(φ, ψ), &\text{ otherwise.}
+          \fconjunct~φ~ψ, &\text{ otherwise.}
         \end{cases}
@@
   \label{lem:reorder-and}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}(φ, ψ)$.
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}~φ~ψ$.
 \end{mainlemma}
@@
     &\fconjunct_{∨} : \Prop → \Prop \to \Prop\\
-    &\fconjunct_{∨}(φ, ψ) =
+    &\fconjunct_{∨}~φ~ψ =
     \begin{cases}
       ψ, &\text{ if }φ ≡ ψ\\
-      ψ, &\text{ if }\freorder_{∨}(φ, ψ) ≡ ψ\\
-      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ \fconjunct_{∨}(φ, ψ₁) ≡ ψ₁,\\
-        &\text{and } \freorder_{∨}(φ, ψ₂) ≡ ψ₂\\
-      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}(φ₁, ψ) ≡ ψ\\
-      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}(φ₂, ψ) ≡ ψ\\
+      ψ, &\text{ if }\freorder_{∨}~φ~ψ ≡ ψ\\
+      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ \fconjunct_{∨}~φ~ψ₁ ≡ ψ₁,\\
+        &\text{and } \freorder_{∨}~φ~ψ₂ ≡ ψ₂\\
+      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}~φ₁~ψ ≡ ψ\\
+      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}~φ₂~ψ ≡ ψ\\
       φ, &\text{ otherwise.}
@@
   \label{lem:conjunct-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}(φ, ψ)$.
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}~φ~ψ$.
 \end{mainlemma}
@@
   \label{lem:reorder-and-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}(φ, ψ)$, where
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$, where
    \begin{align*}
       \begin{split}
-      &\freorder : \Prop \to \Prop \to \Prop\\
+      &\freorder_{∧∨} : \Prop \to \Prop \to \Prop\\
       &\freorder_{∧∨}~φ~ψ~=

### 2017-10-23 paper/sections/proof-reconstruction.tex
[ paper ] fixing lemmas.
[ paper ] working on resolve.
[ paper ] diagram fixed.

@@
 \label{sec:proof-reconstruction}
+
+MISSING TEXT
 
@@
 a \TPTP file that encodes a problem in \CPL. We use this file as the
-input of the \Metis prover and if the problem is a theorem, \Metis can
+input of the \Metis prover. If the problem is a theorem, \Metis
 reply a derivation of the proof in \TSTP format.
@@
 by \Metis, in the translation by \Athena, in the \Agda formalizations
-mentioned above or even in the type-checker~\Agda.
+mentioned above or in the type-checker~\Agda.
 
@@
 functions necessary to emulate \Metis' inference rules.
-As a convention, we write the type judgments as ``$m : M$'' to denote
+
+\begin{notation}
+We write the type judgments as $m : \abbre{M}$ to denote
 that $m$ has $\abbre{M}$ type.
 Types are written using small caps.
-We use \Prop type for propositions and the dependent type, $Γ ⊢ φ$ for
-theorems where $Γ$ has $\abbre{List}~\Prop$ type, and $φ$ has type $\Prop$.
+We use \Prop for the type of propositions and the dependent type, $Γ ⊢ φ$ for
+theorems where $Γ : \List~\Prop$ and $φ : \Prop$.
 $\abbre{List}$ type is the usual inductive type for lists.
 For syntactical equivalence, we write the equality as $φ ≡ ψ$
-for $φ : \Prop$ and $ψ : \Prop$. For this equality, we assume the
-reflexivity, symmetry and transitivity property.
-
+for $φ,~ψ : \Prop$. For this equality, we assume the
+reflexivity, symmetry and transitivity properties.
+\end{notation}
 % ...................................................................
@@
 
-To emulate \Metis' inference rules in type theory, we observed that
-transformations performed by some rules are given by \emph{general recursive}
-functions. Algorithms based on general recursions can not be translated
+To reconstruct \Metis' inference rules in type theory, we observed that
+transformations performed by some rules are implemented by \emph{general
+recursive} functions.
+Algorithms based on general recursions can not be translated
 directly in type theory since it is not a guarantee they terminate. For that
@@
 
-General recursive calls can be translated into structurally recursive
-calls by using for instance, the \emph{Bounded Recursion} technique
-presented in~\cite{Bertot2004}. For a yet another method, we refer
+General recursive functions can be translated into structurally recursive
+functions by using for instance, the \emph{Bounded Recursion} technique
+presented in~\cite{Bertot2004}. For a yet another methods, we refer
 the reader to \cite{Coquand1992,Abel2002,Bove2005}.
-The former technique defines a new function based on the original
-recursive function by adding an argument to the function.
+The bounded technique defines a new structural recursive function based on
+the general recursive function by adding an argument to the function.
 The new argument is the \emph{bound}, a natural number given by the
@@
 
-The type of natural numbers is called \Nat type, and it is defined as
-usual, \ie \zero and \suc are the data constructors. We use names
+\begin{notation}
+The type of natural numbers is called \Nat, and it is defined as
+usual, where \zero and \suc are its data constructors. We use names
 and symbols of the arithmetic operations as usual.
@@
 as well.
+\end{notation}
 
-Therefore, for a general recursive function $\rm{f}: \Prop \to \Prop$
-with termination problems, we formulate a new function
-$\rm{f}^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls must be
-done by using induction on the \Nat type structure.
+Therefore, one approach to guarantee a structural recursive function based on
+a general recursive function $\rm{f}: \Prop \to \Prop$ is to formulate a new function $\rm{f}^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls are done on smaller arguments.
 
@@
 Let us consider the following example to exhibit the bounded technique
-mentioned above for the \fuh function presented in the proposed version
-for the \Metis \strip inference.
+mentioned above for the \fuh function. this function is used for reconstructing
+the \Metis \strip inference rule in Section~\ref{sssec:strip-a-goal}.
 
-\begin{equation*}
+\begin{equation}
 \label{eq:uh-definition}
@@
 &\begin{array}{lll}
-  \fuh_{0} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃)\\
-  \fuh_{0} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃)\\
+  \fuh_{0} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{0}~((φ₁ ∧ φ₂) ⇒ φ₃)\\
+  \fuh_{0} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fuh_{0}~(φ₁ ⇒ φ₂) ∧ \fuh_{0}~(φ₁ ⇒ φ₃)\\
   \fuh_{0} &φ                &= φ
@@
 \end{aligned}
-\end{equation*}
+\end{equation}
 
-From the definition above, the size of the argument, $(φ₁ ∧ φ₂) ⇒ φ₃$,
-is not structurally smaller than the input formula, $φ₁ ⇒ (φ₂ ⇒ φ₃)$,
-since $(φ₁ ∧ φ₂) ⇒ φ₃$ is not a subformula of $φ₁ ⇒ (φ₂ ⇒ φ₃)$.
-
-Therefore, we define the function
-$\fuh_{1}$ by structural recursion in its second argument in
-Eq.~(\ref{eq:uh-structured}).
-
+In (\ref{eq:uh-definition}), the first two equation show
+call on arguments no structurally smaller.
+For instance, on the first call, $φ ≡ (φ₁ ∧ φ₂) ⇒ φ₃$, the recursion
+calls on the  $φ₁ ⇒ (φ₂ ⇒ φ₃)$ argument.
+But this argument is not a subformula for φ.
+Therefore, one way to translate $\fuh_{0}$ in (\ref{eq:uh-definition}) to type
+theory is to define the a new function using the bounded technique.
 \begin{equation}
@@
 \begin{equation*}
-% \label{eq:rank-definition}
   \begin{aligned}
@@
     &\begin{array}{llll}
-\fuh_{cm}~(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{cm}(φ₃) + 2\\
+    \fuh_{cm}~(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{cm}~φ₃ + 2\\
     \fuh_{cm}~(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fmax~(\fuh_{cm}~φ₂)~(\fuh_{cm}~φ₃) + 1\\
@@
 
-Finally, following the technique mentioned, we get a final version of
-$\fuh_{0}$ function presented in Eq.~(\ref{eq:uh}).
+Following the technique mentioned above, we get the structural recursive definition of $\fuh_{0}$ function presented in ~(\ref{eq:uh}).
 
@@
   &\fuh : \Prop → \Prop\\
-  &\fuh(φ) = \fuh_{1}(φ, \fuh_{cm}(φ)).
+  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
   \end{split}
@@
 
-\subsection{Emulating \Metis' inference rules}
+\subsection{Reconstructing \Metis' inference rules}
 \label{ssec:emulating-inferences}
 
-In this section, we emulate each \Metis inference rule with a
-function and its respective theorem.
-The following pattern is used to present the formalization.
-The function name written in bold font
-is a \Metis inference rule in \TSTP derivations.
+In this section, we reconstruct each \Metis inference rule.
+We present a function and a theorem for each rule.
+
+\begin{notation}
+The function name written in bold font is a \Metis inference rule.
 The same function name written in roman letters refers to the proposed
@@
 that proves its soundness.
+\end{notation}
+
+The following pattern is used to present the reconstruction.
 
@@
 \begin{verbatim}
-fof(normalize_1_2, plain, (p | r),
-    inference(conjunct, [], [normalize_1_1])).
+fof(norm1, (p | r), inf(conjunct, [norma1])).
 \end{verbatim}
 
-For this inference rule, we proposed the \rm{conjunct} function in
-Def.~\ref{def:conjunct} and we proved Thm.~\ref{thm:thm-conjunct}. The pattern is the following for
+For this inference rule, we the \rm{conjunct} function in~(\ref{def:conjunct}) and we proved Theorem~\ref{thm:thm-conjunct}. The pattern is the following for
 a binary rule and we extend it for $n$-ary rules in a natural way.
@@
 \begin{itemize}
-\item \texttt{rule} is a binary \Metis inference rule.
-\item $\rm{rule}$ is the proposed function for the \texttt{rule} inference.
+\item \conjunct is a binary \Metis inference rule.
+\item $\rm{conjunct}$ is the type theory function for the \texttt{rule} inference.
 \begin{align*}
   \begin{split}
-    &\rm{rule} : \Prop → \Prop → \Prop\\
-    &\rm{rule}\ φ₁\ φ₂\ ψ\ =
+    &\rm{conjunct} : \Prop → \Prop → \Prop\\
+    &\rm{conjunct}\ φ₁\ φ₂\ ψ\ =
       \begin{cases}
-      ψ, &\text{if }\rm{rule}\text{ built }ψ\text{ by applying valid transformations}\\
+      ψ, &\text{if }\rm{conjunct}\text{ built }ψ\text{ by applying valid transformations}\\
          &\text{or other rules to }φ₁\text{ and }φ₂\\
@@
 \item The theorem that proves the soundness of the
-$\rm{rule}$ function looks like
-\begin{equation*}\text{If }Γ ⊢ φ\text{ then }Γ ⊢ \rm{rule}\ φ.\end{equation*}
-
+$\rm{conjunct}$ function would be
+\begin{equation*}\text{If }Γ ⊢ φ\text{ then }Γ ⊢ \rm{conjunct}\ φ.\end{equation*}
 \end{itemize}
@@
 \begin{table}[!ht]
+\label{tab:agda-metis-table}
+\caption{Presentation of \Metis inference rules in type theory.}
   \begin{center}
@@
       &Normalization of the formula
-      &Thm.~\ref{thm:canonicalize}
+      &Theorem~\ref{thm:canonicalize}
     \\
@@
       &Performs clausification
-      &Thm.~\ref{thm:clausify}
+      &Theorem~\ref{thm:clausify}
     \\
@@
       &Takes a formula from a conjunction
-      &Thm.~\ref{thm:conjunct}
+      &Theorem~\ref{thm:conjunct}
     \\
@@
     %   &Negate the formula
-    %   &Thm.~\ref{thm:negate}
+    %   &Theorem~\ref{thm:negate}
     % \\
@@
       &A general form of the resolution theorem
-      &Thm.~\ref{thm:resolve}
+      &Theorem~\ref{thm:resolve}
     \\
@@
       &Simplify definitions and theorems
-      &Thm.~\ref{thm:simplify}
+      &Theorem~\ref{thm:simplify}
     \\
@@
       &Strip a goal into subgoals
-      &Thm.~\ref{thm:strip}
+      &Theorem~\ref{thm:strip}
     \\[1ex]
@@
   \end{center}
-\label{tab:agda-metis-table}
 \end{table}
+
+MISSING TEXT
 
@@
 \subfile{sections/proof-reconstruction/conjunct.tex}
-% \subfile{sections/proof-reconstruction/resolve.tex}
-% \subfile{sections/proof-reconstruction/canonicalize.tex}
+\subfile{sections/proof-reconstruction/resolve.tex}
+\subfile{sections/proof-reconstruction/canonicalize.tex}
 \subfile{sections/proof-reconstruction/clausify.tex}
@@
 For instance, we tested successfully the translation by \Athena jointly with
-the \Agda formalizations of the rules mentioned above with more than eighty representative theorems in propositional logic.
-An interested reader can test the problems~\cite{Prieto-Cubides2017} in the \Athena tool repository~\cite{Athena}.
+the \Agda formalizations of the rules mentioned above with more than eighty
+representative theorems in propositional logic. An interested reader can test
+the problems~\cite{Prieto-Cubides2017} in the \Athena tool
+repository~\cite{Athena}.
 

### 2017-10-23 paper/sections/proof-reconstruction/resolve.tex
[ paper ] Eq removed.

@@
 
-First, we define \rm{rassoc}$_{⬓}$ function in Eq.~(\ref{def:right-square})
+First, we define \rm{rassoc}$_{⬓}$ function in~(\ref{def:right-square})
 to convert a disjunctions or a conjunction into its right-associative form.
@@
 otherwise stated.
-The $\ffactor$ function in Eq.~(\ref{eq:factor-definition})
+The $\ffactor$ function in~(\ref{eq:factor-definition})
 simplifies a special case of disjunction, the repeated disjuncts
-(e.g., $\ffactor(φ ∨ φ) = φ$).
+(\eg, $\ffactor(φ ∨ φ) = φ$).
 Notice that other cases like $φ ∨ (ψ ∨ φ)$ do no reduce to $ψ ∨ φ$.
@@
 equality between nested disjunctions.
-We define the $\rm{sbuild}_{∨}$ function in
-Eq.~(\ref{eq:strong-build-or}).
+We define the $\rm{sbuild}_{∨}$ function in~(\ref{eq:strong-build-or}).
 that uses every disjunct from the source formula, $φ$, to build up the

### 2017-10-23 paper/sections/proof-reconstruction/strip.tex
[ paper ] Eq removed.

@@
 we need to establish some lemmas before introduce our main goal of this
-part, Theorem~\ref{thm:thm-strip}.
+part, Theorem~\ref{thm:strip}.
 
@@
 Use induction on the cases defined by the outcome of the
-$\fuh$ function in Eq.~(\ref{eq:uh-structured}).
+$\fuh$ function in~(\ref{eq:uh-structured}).
 \begin{itemize}
@@
 
-We now define the $\fstrip_0$ function in Eq.~\ref{eq:strip-unfixed} that
+We now define the $\fstripp$ function in~(\ref{eq:strip-unfixed}) that
 yields the conjunction of subgoals that implies the goal of the problem in
@@
 \begin{aligned}
-&\hspace{.495mm}\fstrip_0 : \Prop → \Nat → \Prop\\
+&\hspace{.495mm}\fstripp : \Prop → \Prop\\
 &\begin{array}{lll}
-\fstrip_0 &(φ₁ ∧ φ₂)     &= \fuh~(\fstrip_0~φ₁) ∧ \fuh~(φ₁ ⇒ \fstrip_0~φ₂)\\
-\fstrip_0 &(φ₁ ∨ φ₂)     &= \fuh~(¬ φ₁ ⇒ \fstrip_0~φ₂)\\
-\fstrip_0 &(φ₁ ⇒ φ₂)     &= \fuh~(φ₁ ⇒ \fstrip_0~φ₂)\\
-\fstrip_0 &(¬ (φ₁ ∧ φ₂)) &= \fuh~(φ₁ ⇒ \fstrip_0~¬ φ₂)\\
-\fstrip_0 &(¬ (φ₁ ∨ φ₂)) &= \fuh~(\fstrip_0~¬ φ₁) ∧ \fuh~(¬ φ₁ ⇒ \fstrip_0~¬ φ₂)\\
-\fstrip_0 &(¬ (φ₁ ⇒ φ₂)) &= \fuh~(\fstrip_0~φ₁) ∧ \fuh~(φ₁ ⇒ \fstrip_0~¬ φ₂)\\
-\fstrip_0 &(¬ ¬ φ₁)      &= \fuh~(\fstrip_0~φ₁)\\
-\fstrip_0 &(¬ ⊥)         &= ⊤\\
-\fstrip_0 &(¬ ⊤)         &= ⊥\\
-\fstrip_0 &φ             &= φ
+\fstripp &(φ₁ ∧ φ₂)     &= \fuh~(\fstripp~φ₁) ∧ \fuh~(φ₁ ⇒ \fstripp~φ₂)\\
+\fstripp &(φ₁ ∨ φ₂)     &= \fuh~(¬ φ₁ ⇒ \fstripp~φ₂)\\
+\fstripp &(φ₁ ⇒ φ₂)     &= \fuh~(φ₁ ⇒ \fstripp~φ₂)\\
+\fstripp &(¬ (φ₁ ∧ φ₂)) &= \fuh~(φ₁ ⇒ \fstripp~¬ φ₂)\\
+\fstripp &(¬ (φ₁ ∨ φ₂)) &= \fuh~(\fstripp~¬ φ₁) ∧ \fuh~(¬ φ₁ ⇒ \fstripp~¬ φ₂)\\
+\fstripp &(¬ (φ₁ ⇒ φ₂)) &= \fuh~(\fstripp~φ₁) ∧ \fuh~(φ₁ ⇒ \fstripp~¬ φ₂)\\
+\fstripp &(¬ ¬ φ₁)      &= \fuh~(\fstripp~φ₁)\\
+\fstripp &(¬ ⊥)         &= ⊤\\
+\fstripp &(¬ ⊤)         &= ⊥\\
+\fstripp &φ             &= φ
 \end{array}
@@
 The function defined above has termination problems since it is not
-a structural recursion. Therefore, we have reformulated it in
-Eq.~\ref{eq:strip-fixed} in order to solve such an issue following
+a structural recursion. Therefore, we have reformulated it
+in~(\ref{eq:strip-fixed}) in order to solve such an issue following
 the technique described in Section~\ref{ssec:structural-recursion}.
@@
 \label{lem:lem-inv-strip}
-Let $\text{n} : \Nat$ the complexity measure of the strip function in
-Eq.~(\ref{eq:strip-unfixed}).
+Let $\text{n} : \Nat$ the complexity measure of the strip function
+in~(\ref{eq:strip-unfixed}).
 If $Γ ⊢ \fstrip~φ~n$ then $Γ ⊢ φ$.
@@
 The proof is by induction on the structure of the
-formula~$φ$ by following the cases in Eq.~(\ref{eq:strip-fixed}).
+formula~$φ$ by following the cases in~(\ref{eq:strip-fixed}).
 We present a straightforward case with double negation, a case with

### 2017-10-23 paper/sections/proof-reconstruction/resolve.tex
resolve fixing

@@
 
-\begin{definition}[reorder$_{\boldsymbol{∧}}$]
+\begin{mainlemma}
+  \label{lem:reorder-and}
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}~φ~ψ$, where, 
     \begin{align*}
@@
           φ, &\text{ if }φ ≡ ψ\\
-          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }\freorder_{∧}~φ~ψ₁ ≡ ψ₁\\
-                  &\text{and }\freorder_{∧}~φ~ψ₂≡ ψ₂\\
+          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }ψ₁ ≡ \freorder_{∧}~φ~ψ₁ \\
+                  &\text{and }ψ₂ ≡ \freorder_{∧}~φ~ψ₂\\
           φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
@@
   \end{align*}
-\end{definition}
-
-\begin{mainlemma}
-  \label{lem:reorder-and}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}~φ~ψ$.
 \end{mainlemma}

### 2017-10-23 paper/sections/proof-reconstruction/strip.tex
[ paper ] last changes.

@@
   \label{lem:inv-uh-lem}
-  If $Γ ⊢ \fuh\ φ$ then $Γ ⊢ φ$.
+Let $\text{n} : \Nat$ be the complexity measure of the \rm{\fuh₀} function
+in~(\ref{eq:strip-unfixed}).
+If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$.
 \end{mainlemma}
 
-\begin{sketchproof}
+\begin{proof}
 Use induction on the cases defined by the outcome of the
@@
 \end{itemize}
-\end{sketchproof}
+\end{proof}
 
@@
 &\hspace{.495mm}\fstrip : \Prop → \Nat → \Prop\\
-&\begin{array}{lll}
-\fstrip &(φ₁ ∧ φ₂)     ~(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
-\fstrip &(φ₁ ∨ φ₂)     ~(\suc~n) &= \fuh~(¬ φ₁ ⇒ \fstrip~φ₂~n)\\
-\fstrip &(φ₁ ⇒ φ₂)     ~(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
-\fstrip &(¬ (φ₁ ∧ φ₂)) ~(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~¬ φ₂~n)\\
-\fstrip &(¬ (φ₁ ∨ φ₂)) ~(\suc~n) &= \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)\\
-\fstrip &(¬ (φ₁ ⇒ φ₂)) ~(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~¬ φ₂~n)\\
-\fstrip &(¬ ¬ φ₁)      ~(\suc~n) &= \fuh~(\fstrip~φ₁~n)\\
-\fstrip &(¬ ⊥)         ~(\suc~n) &= ⊤\\
-\fstrip &(¬ ⊤)         ~(\suc~n) &= ⊥\\
-\fstrip &φ             ~\text{n} &= φ
+&\begin{array}{llll}
+\fstrip &(φ₁ ∧ φ₂)     &(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
+\fstrip &(φ₁ ∨ φ₂)     &(\suc~n) &= \fuh~(¬ φ₁ ⇒ \fstrip~φ₂~n)\\
+\fstrip &(φ₁ ⇒ φ₂)     &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
+\fstrip &(¬ (φ₁ ∧ φ₂)) &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~¬ φ₂~n)\\
+\fstrip &(¬ (φ₁ ∨ φ₂)) &(\suc~n) &= \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)\\
+\fstrip &(¬ (φ₁ ⇒ φ₂)) &(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~¬ φ₂~n)\\
+\fstrip &(¬ ¬ φ₁)      &(\suc~n) &= \fuh~(\fstrip~φ₁~n)\\
+\fstrip &(¬ ⊥)         &(\suc~n) &= ⊤\\
+\fstrip &(¬ ⊤)         &(\suc~n) &= ⊥\\
+\fstrip &φ             &\text{n} &= φ
 \end{array}
@@
 \label{lem:lem-inv-strip}
-Let $\text{n} : \Nat$ the complexity measure of the strip function
+Let $\text{n} : \Nat$ be the complexity measure of the strip function
 in~(\ref{eq:strip-unfixed}).
@@
 
-\begin{sketchproof}
+\begin{proof}
 The proof is by induction on the structure of the
@@
 
-Case $φ ≡ ¬ ¬ φ₁$.
+$\bullet$~Case $φ ≡ ¬ ¬ φ₁$.
 \begin{equation*}
@@
  \AxiomC{$Γ ⊢ \fstrip~(¬¬φ₁)~(\suc~n)$}
-  \RightLabel{by def.}
+  \RightLabel{by~(\ref{eq:uh-fixed})}
   \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
@@
 
-Case $φ ≡ φ₁ ∧ φ₂$. We get a proof for each conjunct and using the
+$\bullet$~Case $φ ≡ φ₁ ∧ φ₂$. We get a proof for each conjunct and using the
 introduction rule for conjunction connective, the expected result follows.
@@
   \AxiomC{$Γ ⊢ \fstrip~(φ₁ ∧ φ₂)~(\suc~n)$}
-  \RightLabel{by def.}
+  \RightLabel{by~(\ref{eq:strip-fixed})}
   \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
@@
 
-Case $φ ≡ ¬ (φ₁ ∨ φ₂)$. We show the theorems $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
-With the conjunction of $¬ φ₁$ and $¬ φ₂$ by applying De Morgan Law, the result follows.
+$\bullet$~Case $φ ≡ ¬ (φ₁ ∨ φ₂)$.
+We show the theorems $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
+With the conjunction of $¬ φ₁$ and $¬ φ₂$ by applying De Morgan Law, the
+result follows.
 
@@
 \AxiomC{$Γ ⊢ \fstrip~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
-\RightLabel{by def.}
+\RightLabel{by~(\ref{eq:strip-fixed})}
 \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)$}
@@
   \AxiomC{$Γ ⊢ \fstrip~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
-  \RightLabel{by def.}
+  \RightLabel{by~(\ref{eq:strip-fixed})}
   \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)$}
@@
 \end{equation*}
-\end{sketchproof} % the proof continue...
+\end{proof} % the proof continue...
+
+MISSING TEXT
 
@@
 For the sake of brevity, we state the following theorem for the
-\strip function when the goal has only two subgoals. In other cases, we extend that theorem in the natural way.
+\strip function when the goal has only two subgoals. In other cases,
+we extend that theorem in the natural way.
 
@@
 If $s_1$ and $s_2$ are the subgoals of the goal $φ$, that is,
-$\fstrip~φ~n~≡~s_1\wedge~s_2$.
-If $Γ ⊢ s_1$ and $Γ ⊢ s_2$ then $Γ ⊢ φ$.
+$\fstrip~φ~n~≡~s_1\wedge~s_2$, if $Γ ⊢ s_1$ and $Γ ⊢ s_2$ then $Γ ⊢ φ$.
 \end{mainth}

### 2017-10-23 paper/sections/conclusions.tex
[ paper ] lots of changes.

@@
 
-We built a proof-reconstruction tool written in \Haskell
-to generate \Agda proof-terms of \Metis \TSTP derivations.
-\Agda files delivered by the translator contain call to theorems from the
-\Agda formalizations of \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
+We built \Athena translator tool written in \Haskell
+to generate \Agda proof-terms of \Metis derivations.
+\Agda files delivered by this translator imports
+\Agda formalizations of the \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
 
@@
 see Section~\ref{ssec:emulating-inferences}.
-We chose that syntactical treatment as the opportunity
-to extend this work towards the support of first-order logic.
+Nevertheless, we chose that syntactical treatment instead of using
+semantics to extend this work towards the support of first-order logic.
 Recall, satisfiability in first-order logic is undecidable.
@@
 
-Besides the fact, Kansos~\cite{Kanso2012} proof-reconstruction is
-similar to the approach presented in Section~\ref{ssec:workflow},
-the authors aim to justify some of the inference
-rules by using propositional semantics. We instead perform only a syntactic analysis of the derivations as we mentioned above.
+In \Agda, we found the proof-reconstruction proposed by \citeauthor{Kanso2012}
+in~\cite{Kanso2012,kanso2016light}. The author present an approach similar to
+the reasoning presented in Section~\ref{ssec:workflow}.
+Nonetheless, his approach includes semantics reasoning that as we mentioned
+above differs completely from our proof-reconstructing propose.
 
@@
 exposed in Section~\ref{ssec:emulating-inferences}.
-We detect some improvements for our approach that we leave it for future
+We identify some improvements for our approach that we leave it for future
 work.
@@
 inference by strengthen \canonicalize rule in Thm.~\ref{thm:canonicalize}
-The \simplify rule is still lacking of some coverage since it is fairly complex, many cases could be omitted.
+The \simplify rule is still lacking of some coverage since it is fairly complex its \Metis source code, and many cases could be omitted.
 Other improvements are related with computational efficiency of
-rules strongly depend on reordering tasks,
+rules that strongly depend on reordering tasks,
 Section~\ref{sssec:reordering}.
-We believe some rules like \canonicalize can get some help from an analysis done in the translator tool.
+We believe some rules like \canonicalize can get some help by
+performing an analysis with \Athena.
 
@@
 has a real significant impact for these automatic tools.
-The reverse engineering task can reveal important issues or bugs
+The reverse engineering task to understand the prover reasoning
+can reveal important issues or bugs
 in many parts of these systems (e.g., preprocessing, reasoning, or
@@
 Fortunately, all these problems were fixed quickly by Joe Hurd in
-20170810 release.
+the \Metis 20170810 release.
 

### 2017-10-23 paper/sections/metis-language-and-proofs.tex
[ paper ] lots of changes.

@@
 assumes a \name{role}, this could be an \name{axiom},
-\name{conjecture}, \name{definition}, \name{plain} or a \name{hypothesis}.
+\name{conjecture}, \name{definition}, \name{plain} or an \name{hypothesis}.
 The formulas include the binary connectives
-(\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!, \verb!~!)
+(\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!), negation (\verb!~!),
 and the constants \verb!$true!, and \verb!$false!.

### 2017-10-23 paper/sections/proof-reconstruction/conjunct.tex
[ paper ] lots of changes.

@@
 following \TSTP excerpt shows.
+In the first formula \verb!p1!, \verb!p & q & (r | ~ p)!, is a left-associative conjunction.
+\conjunct extracts \verb!q!
+from the \verb!p1!
+conjunction by using twice left projection (∧-proj₁).
 
@@
             ψ, &\text{ if }φ ≡ ψ\\
-            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }\fconjunct~φ₁~ψ ≡ ψ  \\
-            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }\fconjunct~φ₂~ψ ≡ ψ  \\
+            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }ψ ≡ \fconjunct~φ₁~ψ  \\
+            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }ψ ≡ \fconjunct~φ₂~ψ  \\
             φ, &\text{ otherwise.}
@@
 \begin{proof}\hspace{2cm}\\
-Case $φ ≡ ψ$. $Γ ⊢ \fconjunct~φ~ψ$ normalizes to $Γ ⊢ ψ$.
-Then, we get the desire conclusion by applying the $\fsubst$ lemma.\\[2mm]
-Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct~φ_{i}~ψ$ for some $i = 1,\ 2$, then,
+\begin{itemize}
+\item[$\bullet$] Case $φ ≡ ψ$. $Γ ⊢ \fconjunct~φ~ψ$ normalizes to $Γ ⊢ ψ$.
+Then, we get the desire conclusion by applying the $\fsubst$ lemma.
+\item[$\bullet$] Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct~φ_{i}~ψ$ for some $i = 1,\ 2$, then,
 
@@
 \end{equation*}
-Otherwise, the last case follows trivially.
+\item[$\bullet$] Otherwise, the last case follows trivially.
+\end{itemize}
 \end{proof}

### 2017-10-23 paper/sections/related-work.tex
[ paper ] lots of changes.

@@
 
-There are many proof-reconstruction tools nowadays.
-Let us mention a list of some representative tools mainly based on the description by \citeauthor{Sicard-Ramirez2016}~\cite{Sicard-Ramirez2016}.
+Let us mention a list of some representative of such tools mainly based on the
+description by \citeauthor{Sicard-Ramirez2016}~\cite{Sicard-Ramirez2016}.
 
@@
 A modular proof-reconstruction workflow is presented jointly with
-the full integration of \name{Leo-II} and \name{Satallax} provers with \name{
-Isabelle/HOL} in \citeauthor{Een2004}~\cite{Een2004}.
+the full integration of \name{Leo-II} and \name{Satallax} provers with
+\name{Isabelle/HOL} in \citeauthor{Een2004}~\cite{Een2004}.
 
@@
 \name{Gandalf} with the high-order
-theorem prover \name{HOL}~\cite{norrish2007hol}. Hurd implements the
-tactic \verb!GANDALF_TAC! following an \abbre{LCF} model to reconstruct
-\name{Gandalf} proofs. For \name{HOL Light}, a version of
+theorem prover \name{HOL}~\cite{norrish2007hol}.
+Its \verb!GANDALF_TAC! tactic is able to reconstruct \name{Gandalf} proofs
+by using a \abbre{LCF} model. For \name{HOL Light}, a version of
 \name{HOL} but with a simpler logic core, the \SMT solver \name{CVC4}
 was integrated. \citeauthor{kaliszyk2013}~\cite{kaliszyk2013}
-reconstruct proofs from different ATPs with the \name{PRocH} tool by
-replaying detailed inference steps from the ATPs with internal
+reconstruct proofs from different \ATPs with the \name{PRocH} tool by
+replaying detailed inference steps from the \ATPs with internal
 inference methods implemented in \name{HOL Light}.
@@
 For the proof assistant \Agda, we found two proof-reconstruction tools.
-First, the integration with the \name{Waldmeister}~\cite{hillenbrand1997} prover by \citeauthor{foster2011integrating}~\cite{foster2011integrating}.
+First, the integration with the \name{Waldmeister}~\cite{hillenbrand1997}
+prover by \citeauthor{foster2011integrating}~\cite{foster2011integrating}.
 A prover for pure equational logic, i.e.
-first-order logic with equality but no other predicate symbols and no functions symbols.
+first-order logic with equality but no other predicate symbols and no
+functions symbols.
 Second, Kanso and Setzer in~\cite{kanso2016light} integrate the propositional
@@
 translate automatically propositional logic problems written in \Agda
-to \TPTP problems. By calling an external wrapper of the ATP, this
+to \TPTP problems. By calling an external wrapper of the \ATP, this
 tool gets a \TSTP derivation. The tool parses the \name{EProver}

### 2017-10-23 paper/sections/proof-reconstruction/clausify.tex
[ paper ] Eq removed.
ruu

@@
 \clausify expands the formula \texttt{norm0} by using distributive
-laws presented in conjunctive normal form conversion.
+laws included in the conjunctive normal form conversion.
 
@@
 ...
-fof(norm0, (~ p | (q & r)), inf(canonicalize, [a1])).
-fof(norm1, ((~ p | q) & (~ p | r)), inf(clausify, [norm0])).
+fof(norm0, ~ p | (q & r), inf(canonicalize, [a1])).
+fof(norm1, (~ p | q) & (~ p | r), inf(clausify, [norm0])).
 ...
@@
 \begin{proof}
-If $φ ≡ ψ$, $Γ ⊢ \fclausify~φ~ψ$ normalizes to $Γ ⊢ ψ$. The conclusion follows by applying the $\fsubst$ lemma.\\[2mm]
-Otherwise, we use Theorem~\ref{thm:thm-reorder-and-or} and Theorem~\ref{thm:thm-cnf}.
+If $φ ≡ ψ$, $Γ ⊢ \fclausify~φ~ψ$ normalizes to $Γ ⊢ ψ$. The conclusion follows by applying the $\fsubst$ lemma. Otherwise, we use Theorem~\ref{lem:reorder-and-or} and Theorem~\ref{lem:cnf}.
 \end{proof}
@@
 \begin{remark}
-The \clausify rule is often preceded by the \canonicalize rule.
+The \clausify rule is often preceded by \canonicalize.
 Both rules perform \emph{Clausification} that introduces
-into the problem axioms or definitions in the domain of the solution.
+into the problem axioms and definitions in the domain of the solution.
 The clausification algorithms is mainly described on paper by

### 2017-10-23 paper/sections/proof-reconstruction/resolve.tex
ruu

@@
     \rm{build}_{∨}&ψ~ψ &= ψ\\
-    \rm{build}_{∨}&φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{1} ≡ ψ_{1}\\
-    \rm{build}_{∨}&φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if }\rm{build}_{∨}~φ~ψ_{2} ≡ ψ_{2}\\
+    \rm{build}_{∨}&φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if } ψ_{1} ≡ \rm{build}_{∨}~φ~ψ_{1}\\
+    \rm{build}_{∨}&φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if } ψ_{2} ≡\rm{build}_{∨}~φ~ψ_{2}\\
     \rm{build}_{∨}&φ~ψ&=φ&\text{ otherwise.}
@@
      &\hspace{.495mm}\rm{sbuild}_{∨} : \Prop → \Prop → \Prop\\
-    &\begin{array}{llll}
-    \rm{sbuild}_{∨}&(φ₁ ∨ φ₂)~ψ &=\ffactor(\rm{build}_{∨}~φ₁~ψ ∨ \rm{build}_{∨}~φ₂~ψ)&\\
-    \rm{build}_{∨}&φ~ψ &= \rm{build}_{∨}~φ~ψ& \text{ otherwise.}
+    &\begin{array}{lll}
+    \rm{sbuild}_{∨}&(φ₁ ∨ φ₂)~ψ &=\ffactor(\rm{build}_{∨}~φ₁~ψ ∨ \rm{build}_{∨}~φ₂~ψ)\\
+    \rm{build}_{∨}&φ~ψ &= \rm{build}_{∨}~φ~ψ
      \end{array}
@@
           ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }ψ₁ ≡ \freorder_{∧}~φ~ψ₁ \\
-                  &\text{and }ψ₂ ≡ \freorder_{∧}~φ~ψ₂\\
+                  &\text{and } ψ₂ ≡ \freorder_{∧}~φ~ψ₂\\
           φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
@@
 
-\begin{definition}[conjunct$_{\boldsymbol{∨}}$]
+\begin{mainlemma}
+  \label{lem:conjunct-or}
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}~φ~ψ$, where, 
+  \begin{equation*}
 \label{eq:conjunct-or-definition}
-\begin{align*}
   \begin{split}
@@
       ψ, &\text{ if }φ ≡ ψ\\
-      ψ, &\text{ if }\freorder_{∨}~φ~ψ ≡ ψ\\
-      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ \fconjunct_{∨}~φ~ψ₁ ≡ ψ₁,\\
-        &\text{and } \freorder_{∨}~φ~ψ₂ ≡ ψ₂\\
-      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}~φ₁~ψ ≡ ψ\\
-      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ \fconjunct_{∨}~φ₂~ψ ≡ ψ\\
+      ψ, &\text{ if } ψ ≡ \freorder_{∨}~φ~ψ\\
+      ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \fconjunct_{∨}~φ~ψ₁,\\
+        &\text{and } ψ₂ ≡ \freorder_{∨}~φ~ψ₂\\
+      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunct_{∨}~φ₁~ψ \\
+      ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunct_{∨}~φ₂~ψ \\
       φ, &\text{ otherwise.}
@@
   \end{split}
-  \end{align*}
-\end{definition}
-
-\begin{mainlemma}
-  \label{lem:conjunct-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}~φ~ψ$.
+  \end{equation*}
 \end{mainlemma}
@@
   \label{lem:reorder-and-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$, where
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$, where,
    \begin{align*}
@@
       &\freorder_{∧∨} : \Prop \to \Prop \to \Prop\\
-      &\freorder_{∧∨}~φ~ψ~=
+      &\freorder_{∧∨}~φ~ψ=
         \begin{cases}
-          ψ, &\text{ if } φ≡ψ\\
-          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁~\\
-             &\text{and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂~\\
-          φ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂\\
-          \fconjunct_{∨}~φ~ψ~ &\text{ otherwise.}
+          ψ, &\text{ if } φ ≡ ψ\\
+          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁\\
+             &\text{and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂\\
+          φ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
+          \fconjunct_{∨}~φ~ψ &\text{ otherwise.}
         \end{cases}

### 2017-10-23 paper/sections/proof-reconstruction/strip.tex
ruu

@@
   \label{lem:inv-uh-lem}
-Let $\text{n} : \Nat$ be the complexity measure of the \rm{\fuh₀} function
-in~(\ref{eq:strip-unfixed}).
+Let $\text{n} : \Nat$ be the complexity measure of the $\fuh_0$ function
+in~(\ref{eq:uh-structured}).
 If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$.
@@
 \begin{proof}
-Use induction on the cases defined by the outcome of the
-$\fuh$ function in~(\ref{eq:uh-structured}).
+The proof is by induction on the cases defined by the outcome of the
+$\fuh_{1}$ function in~(\ref{eq:uh-structured}).
 \begin{itemize}
@@
   \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \fuh~(φ₁ ⇒ (φ₂ ⇒ φ₃))~(\suc~n)$}
-  \RightLabel{by def.}
-  \UnaryInfC{$Γ ⊢ \fuh~((φ₁ ∧ φ₂) ⇒ φ₃)~n$}
+  \AxiomC{$Γ ⊢ \fuh_1~(φ₁ ⇒ (φ₂ ⇒ φ₃))~(\suc~n)$}
+  \RightLabel{by~(\ref{eq:uh-structured})}
+  \UnaryInfC{$Γ ⊢ \fuh_1~((φ₁ ∧ φ₂) ⇒ φ₃)~n$}
   \RightLabel{by hip.}
@@
   \begin{bprooftree}
-    \AxiomC{$Γ ⊢ \fuh~(φ₁ ⇒ φ₂)~n ∧ \fuh~(φ₁ ⇒ φ₃)~n$}
+    \AxiomC{$Γ ⊢ \fuh_1~(φ₁ ⇒ (φ₂ ∧ φ₃))~(\suc~n)$}
+    \RightLabel{by~(\ref{eq:uh-structured})}
+    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n ∧ \fuh_1~(φ₁ ⇒ φ₃)~n$}
     \RightLabel{∧-proj₁}
-    \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ φ₂)~n$}
+    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n$}
     \RightLabel{by hip.}
@@
   \begin{bprooftree}
-    \AxiomC{$Γ ⊢ \fuh~(φ₁ ⇒ φ₂)~n ∧ \fuh~(φ₁ ⇒ φ₃)~n$}
+    \AxiomC{$Γ ⊢ \fuh_1~(φ₁ ⇒ (φ₂ ∧ φ₃))~(\suc~n)$}
+    \RightLabel{by~(\ref{eq:uh-structured})}
+    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n ∧ \fuh_1~(φ₁ ⇒ φ₃)~n$}
     \RightLabel{∧-proj₂}
-    \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ φ₃)~n$}
+    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₃)~n$}
     \RightLabel{by hip.}
@@
 
-Finally, using the theorem \texttt{⇒∧⇒\rm{-to-}⇒∧} from~\cite{AgdaProp},
+Now, using the theorem \texttt{⇒∧⇒\rm{-to-}⇒∧} from~\cite{AgdaProp},
 \begin{equation*}
@@
 
-The function defined above has termination problems since it is not
-a structural recursion. Therefore, we have reformulated it
-in~(\ref{eq:strip-fixed}) in order to solve such an issue following
-the technique described in Section~\ref{ssec:structural-recursion}.
+The function defined above is not a structural recursion function.
+Therefore, we have reformulated it in~(\ref{eq:strip-fixed}) in order to solve such an issue following the technique described in Section~\ref{ssec:structural-recursion}.
 
@@
  \AxiomC{$Γ ⊢ \fstrip~(¬¬φ₁)~(\suc~n)$}
-  \RightLabel{by~(\ref{eq:uh-fixed})}
+  \RightLabel{by~(\ref{eq:strip-fixed})}
   \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}

### 2017-10-23 paper/sections/limitations-type-theory.tex
[ paper ] lots of changes.

--- 2017-10-23 paper/sections/proof-reconstruction.tex
@@
 
-% ===================================================================
-
-\section{Proof-Reconstruction}
-\label{sec:proof-reconstruction}
+\section{Limitations of Type Theory}
+\label{sec:limitations-type-theory}
 
 MISSING TEXT
-
-\subsection{Workflow}
-\label{ssec:workflow}
-
-\input{sections/diagram.tex}
-
-The proof-reconstruction approach proposed consists of a series
-of steps similar to the workflow presented by \citeauthor{sultana2015} in
-\cite{sultana2015}. This process is a translation from a source
-system to a target system. In our case, the system of origin, the
-automatic theorem prover, is \Metis; the target system is a proof
-assistant, \Agda. We choose \Agda, but another proof assistant with the
-same support of type theory and inductive types could be used.
-%  (see a description of \Agda for its main features in
-% Section~\ref{sec:implementation}).
-The overview of the proof-reconstruction is presented in
-Fig.~\ref{fig:proof-reconstruction-workflow}. The process begin with
-a \TPTP file that encodes a problem in \CPL. We use this file as the
-input of the \Metis prover. If the problem is a theorem, \Metis
-reply a derivation of the proof in \TSTP format.
-
-With the \TSTP derivation from Step~2, we process the derivation with the
-\Athena translator tool.
-\Athena parses the \TSTP format, analyzes the
-derivation and generates a representation of the natural deduction
-proof using a tree data structure (see the properties
-of this tree in Section~\ref{ssec:metis-proofs}).
-In the \Athena analysis, some unnecessary steps that introduce redundancies
-and some unused input is removed from the proof-tree.
-As result, we get from \Athena an \Agda file of the proof
-with names of functions and theorems from
-the \Agda libraries that accompany this article:
-\texttt{agda-prop} and \texttt{agda-metis}.
-
-Finally, we type-check the \Agda proof-term. If the type-checking
-success, the \TSTP derivation delivered by \Metis is correct
-module \Agda and the proposed formalizations for the
-propositional logic and the \Metis inferences.
-In that case \Agda outputs an interface file.
-Otherwise, when type-checking fails, the failure must be
-investigated by the user looking at the error in the \TSTP derivation
-by \Metis, in the translation by \Athena, in the \Agda formalizations
-mentioned above or in the type-checker~\Agda.
-
-In the remainder part of this section, a formal description using
-type theory is presented to build definitions and theorems of
-functions necessary to emulate \Metis' inference rules.
 
@@
 % section section_name (end)
-\subsection{Structural recursion}
+\subsection{Terminating functions}
 \label{ssec:structural-recursion}
@@
 
-\begin{example}
+\begin{myexample}
 \label{ex:structural-recursion}
@@
 theory is to define the a new function using the bounded technique.
+
 \begin{equation}
@@
 
-\end{example}
+\end{myexample}
 
@@
 
-% % ................................................
+\subsection{Intuitionistic logic}
+\label{ssec:intuitionistic-logc}
 
-\subsection{Reconstructing \Metis' inference rules}
-\label{ssec:emulating-inferences}
-
-In this section, we reconstruct each \Metis inference rule.
-We present a function and a theorem for each rule.
-
-\begin{notation}
-The function name written in bold font is a \Metis inference rule.
-The same function name written in roman letters refers to the proposed
-version of the rule.
-Each rule proposed has a respective theorem also written in roman letters
-that proves its soundness.
-\end{notation}
-
-The following pattern is used to present the reconstruction.
-
-For example, we know the \verb!conjunct! inference rule is a
-\Metis inference rule since it appears in \TSTP derivations like
-the following excerpt.
-
-\begin{verbatim}
-fof(norm1, (p | r), inf(conjunct, [norma1])).
-\end{verbatim}
-
-For this inference rule, we the \rm{conjunct} function in~(\ref{def:conjunct}) and we proved Theorem~\ref{thm:thm-conjunct}. The pattern is the following for
-a binary rule and we extend it for $n$-ary rules in a natural way.
-
-\begin{itemize}
-\item \conjunct is a binary \Metis inference rule.
-\item $\rm{conjunct}$ is the type theory function for the \texttt{rule} inference.
-\begin{align*}
-  \begin{split}
-    &\rm{conjunct} : \Prop → \Prop → \Prop\\
-    &\rm{conjunct}\ φ₁\ φ₂\ ψ\ =
-      \begin{cases}
-      ψ, &\text{if }\rm{conjunct}\text{ built }ψ\text{ by applying valid transformations}\\
-         &\text{or other rules to }φ₁\text{ and }φ₂\\
-      φ, &\text{otherwise.}
-      \end{cases}
-  \end{split}
-\end{align*}
-
-\begin{itemize}
-  \item $φᵢ$ are \emph{source} formulas from previous deducted derivations.
-  \item $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
-\end{itemize}
-\item The theorem that proves the soundness of the
-$\rm{conjunct}$ function would be
-\begin{equation*}\text{If }Γ ⊢ φ\text{ then }Γ ⊢ \rm{conjunct}\ φ.\end{equation*}
-\end{itemize}
-
-\begin{table}[!ht]
-\label{tab:agda-metis-table}
-\caption{Presentation of \Metis inference rules in type theory.}
-  \begin{center}
-  {\renewcommand{\arraystretch}{1.6}%
-    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}
-    \hline
-    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
-    \texttt{canonicalize}
-      &Normalization of the formula
-      &Theorem~\ref{thm:canonicalize}
-    \\
-    \texttt{clausify}
-      &Performs clausification
-      &Theorem~\ref{thm:clausify}
-    \\
-    \hyperlink{atp-conjunct}{\texttt{conjunct}}
-      &Takes a formula from a conjunction
-      &Theorem~\ref{thm:conjunct}
-    \\
-    % \texttt{negate}
-    %   &Negate the formula
-    %   &Theorem~\ref{thm:negate}
-    % \\
-    \texttt{resolve}
-      &A general form of the resolution theorem
-      &Theorem~\ref{thm:resolve}
-    \\
-    \texttt{simplify}
-      &Simplify definitions and theorems
-      &Theorem~\ref{thm:simplify}
-    \\
-    \texttt{strip}
-      &Strip a goal into subgoals
-      &Theorem~\ref{thm:strip}
-    \\[1ex]
-    \hline
-    \end{tabular}}
-  \end{center}
-\end{table}
-
-MISSING TEXT
-
-% -----------------------------------------------------------------------------
-
-\subfile{sections/proof-reconstruction/strip.tex}
-\subfile{sections/proof-reconstruction/negate.tex}
-\subfile{sections/proof-reconstruction/conjunct.tex}
-\subfile{sections/proof-reconstruction/resolve.tex}
-\subfile{sections/proof-reconstruction/canonicalize.tex}
-\subfile{sections/proof-reconstruction/clausify.tex}
-\subfile{sections/proof-reconstruction/simplify.tex}
-
-%------------------------------------------------------------------------------
-
-Now, we have finished the formalization of every inference rule in
-a \Metis proof, we are able to justify step-by-step any proof
-for a problem in propositional logic.
-For instance, we tested successfully the translation by \Athena jointly with
-the \Agda formalizations of the rules mentioned above with more than eighty
-representative theorems in propositional logic. An interested reader can test
-the problems~\cite{Prieto-Cubides2017} in the \Athena tool
-repository~\cite{Athena}.
+...
 

### 2017-10-23 paper/sections/metis-language-and-proofs.tex
[ paper ] lots of changes.

--- 2017-10-21 paper/sections/metis-language-and-proofs.tex
@@
 
-The \TPTP language --which includes the first-order
-form (denoted by \name{fof}) and clause normal form (denoted by
-\name{cnf}) formats~\cite{sutcliffe2009,Sicard-Ramirez2016} -- is the
-input language to encode problems used by \Metis.
+The \TPTP language is the input language to encode problems used by \Metis.
+It includes the first-order form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf}) formats~\cite{sutcliffe2009,Sicard-Ramirez2016}.
 The \TPTP syntax describes a well-defined grammar to handle annotated
-formulas with the following form.
+formulas with the following form:
 
@@
 
-The \name{language} can be \name{fof} or \name{cnf}. The \name{name}
+Where the \name{language} can be \name{fof} or \name{cnf}. The \name{name}
 serves to identify the formula within the problem. Each formula
 assumes a \name{role}, this could be an \name{axiom},
-\name{conjecture}, \name{definition}, or a \name{hypothesis}.
-The formulas include the binary connectives
-(\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!, \verb!~!)
-and the constants \verb!$true!, and \verb!$false!.
+\name{conjecture}, \name{definition}, \name{plain} or an \name{hypothesis}.
+The formulas include the constants \verb!$true!, negation unary operator (\verb!~!), and the binary connectives (\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!),
 
+\begin{myexample}
 For instance, let us express the problem
@@
   \end{verbatim}
+
+\end{myexample}
 
@@
 
-The \name{source} field is an inference record with the following
-pattern.
+Where the \name{source} field is an inference record with the following
+pattern:
 
@@
 
+\begin{myexample}
+
 \begin{verbatim}
@@
 In the script above, \strip is for example the name of the inference.
-It has no arguments and derives from one parent node named goal. The
+It has no arguments and derives from one parent node named  \verb!goal!. The
 result of this inference when it applies to the \verb!goal! formula is
 \verb!p!.
+
+\end{myexample}
+
+We adopt a customized \TSTP syntax to keep as short as possible the \Metis derivations for increasing the readability in this paper.
+
+\begin{myexample}
+
+Let us consider the following \TSTP derivation using
+the customized \TSTP syntax. Note that we remove for example
+empty fields in the inference information, the \verb!role! field if it is
+\verb!plain! and shorten names as long as possible.
+
+\begin{verbatim}
+fof(premise, axiom, p).
+fof(goal, conjecture, p).
+fof(sg0, p, inf(strip, [goal])).
+fof(neg0, ~ p, inf(negate, [sg0])).
+fof(norm0, ∼ p, inf(canonicalize, [neg0])).
+fof(norm1, p, inf(canonicalize, [premise])).
+fof(norm2, $false, inf(simplify, [norm0, norm1]))
+cnf(refute0, $false, inf(canonicalize, [norm2])).
+\end{verbatim}
+
+\end{myexample}
 
@@
 
-% \TSTP derivations replied by \Metis use other rules. They are
+% \TSTP derivations replied by \Metis use the following rules:
 % \canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
@@
 
+\begin{table}[!ht]
+\label{tab:agda-metis-table}
+\caption{Presentation of \Metis inference rules in type theory.}
+  \begin{center}
+  {\renewcommand{\arraystretch}{1.6}%
+    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}
+    \hline
+    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
+    \texttt{canonicalize}
+      &Normalization of the formula
+      &Theorem~\ref{thm:canonicalize}
+    \\
+    \texttt{clausify}
+      &Performs clausification
+      &Theorem~\ref{thm:clausify}
+    \\
+    \hyperlink{atp-conjunct}{\texttt{conjunct}}
+      &Takes a formula from a conjunction
+      &Theorem~\ref{thm:conjunct}
+    \\
+    % \texttt{negate}
+    %   &Negate the formula
+    %   &Theorem~\ref{thm:negate}
+    % \\
+    \texttt{resolve}
+      &A general form of the resolution theorem
+      &Theorem~\ref{thm:resolve}
+    \\
+    \texttt{simplify}
+      &Simplify definitions and theorems
+      &Theorem~\ref{thm:simplify}
+    \\
+    \texttt{strip}
+      &Strip a goal into subgoals
+      &Theorem~\ref{thm:strip}
+    \\[1ex]
+    \hline
+    \end{tabular}}
+  \end{center}
+\end{table}
+
 \subsection{Proofs}
@@
 
-\begin{figure}
-\begin{verbatim}
-fof(premise, axiom, p).
-fof(goal, conjecture, p).
-fof(subgoal_0, plain, p, inference(strip, [], [goal])).
-fof(negate_0_0, plain, ~ p, inference(negate, [], [subgoal_0])).
-fof(normalize_0_0, plain, ∼ p,
-  inference(canonicalize, [], [negate_0_0])).
-fof(normalize_0_1, plain, p,
-  inference(canonicalize, [], [premise])).
-fof(normalize_0_2, plain, $false,
-  inference(simplify, [], [normalize_0_0, normalize_0_1]))
-cnf(refute_0_0, plain, $false,
-  inference(canonicalize, [], [normalize_0_2])).
-\end{verbatim}
-\caption{\texttt{Metis}' \texttt{TSTP} derivation for the
-problem $p\vdash p$.}
-\label{fig:metis-proof-tstp}
-\end{figure}
-
-The output of a proof delivered by \Metis encodes a natural
-deduction proof (see a complete proof in Fig.~\ref{fig:metis-proof-tstp}.
-The deduction system uses six inference rules \cite{hurd2003first}.
+A proof delivered by \Metis encodes a natural
+deduction proof (see a complete proof in Fig.~\ref{fig:metis-proof-tstp}).
 With these inference rules as the only valid deduction steps, \Metis
-attempts to prove conjectures by refutation (e.g.,
-\emph{falsium} in the last conclusion in the \TSTP derivation
-Fig.~\ref{fig:metis-proof-tstp}).
+attempts to prove conjectures by refutation (\eg,
+\emph{falsium} in the root of the \TSTP derivation
+in Fig.~\ref{fig:metis-proof-tstp}).
 
@@
   \end{bprooftree}
-  \caption{Proof tree for the \Metis derivation in
-  Fig.~\ref{fig:metis-proof-tstp}}.
+  \caption{A \Metis proof tree.}
   \label{fig:metis-example}

### 2017-10-23 paper/sections/notes/implementation.tex
[ paper ] lots of changes.

--- 2017-09-14 paper/sections/implementation.tex
@@
 We extended the definition for propositions presented in
-\cite{Altenkirch2015} to mathc the definion in section
+\cite{Altenkirch2015} to mathc the definion in Section
 \ref{sec:preliminaries}.
@@
 
-\begin{remark}
+\begin{myremark}
 The underscores in the above definition denote holes for a function of arity equivalent to the number of such holes.
-\end{remark}
+\end{myremark}
 
-\begin{remark}
+\begin{myremark}
 The type notation
@@
 \end{verbatim}
-\end{remark}
+\end{myremark}
 
-\begin{example}
+\begin{myexample}
 \hspace*{5cm}\\[3mm]
@@
 \end{verbatim}
-\end{example}
+\end{myexample}
 

### 2017-10-23 paper/sections/proof-reconstruction.tex
[ paper ] Eq removed.
[ paper ] last changes.
[ paper ] lots of changes.

@@
 
-MISSING TEXT
-
-\subsection{Workflow}
-\label{ssec:workflow}
-
-\input{sections/diagram.tex}
-
 The proof-reconstruction approach proposed consists of a series
@@
 same support of type theory and inductive types could be used.
+
+\subsection{Workflow}
+\label{ssec:workflow}
+
+\input{sections/diagram.tex}
 %  (see a description of \Agda for its main features in
@@
 
-\begin{notation}
-We write the type judgments as $m : \abbre{M}$ to denote
-that $m$ has $\abbre{M}$ type.
-Types are written using small caps.
-We use \Prop for the type of propositions and the dependent type, $Γ ⊢ φ$ for
-theorems where $Γ : \List~\Prop$ and $φ : \Prop$.
-$\abbre{List}$ type is the usual inductive type for lists.
-For syntactical equivalence, we write the equality as $φ ≡ ψ$
-for $φ,~ψ : \Prop$. For this equality, we assume the
-reflexivity, symmetry and transitivity properties.
-\end{notation}
-% ...................................................................
-
-% section section_name (end)
-\subsection{Structural recursion}
-\label{ssec:structural-recursion}
-
-To reconstruct \Metis' inference rules in type theory, we observed that
-transformations performed by some rules are implemented by \emph{general
-recursive} functions.
-Algorithms based on general recursions can not be translated
-directly in type theory since it is not a guarantee they terminate. For that
-reason, we follow the technique described in~\cite{Bertot2004} to avoid
-termination problems by modifying the recursive functions to be
-\emph{structural recursive}.
-% (see \cite{Coquand1992,Abel2002,Bove2005} for more details).
-
-This paper adopts the notion of \emph{structurally smaller} from
-\citeauthor{Abel2002}~\cite{Abel2002} to say, a recursive function is
-structurally recursive if it calls itself with only
-structurally smaller arguments.
-
-General recursive functions can be translated into structurally recursive
-functions by using for instance, the \emph{Bounded Recursion} technique
-presented in~\cite{Bertot2004}. For a yet another methods, we refer
-the reader to \cite{Coquand1992,Abel2002,Bove2005}.
-The bounded technique defines a new structural recursive function based on
-the general recursive function by adding an argument to the function.
-The new argument is the \emph{bound}, a natural number given by the
-function complexity. In other words, the added argument will represent
-the number of times the function needs to call itself to get the
-expected outcome~\cite{Bertot2004}.
-
-\begin{notation}
-The type of natural numbers is called \Nat, and it is defined as
-usual, where \zero and \suc are its data constructors. We use names
-and symbols of the arithmetic operations as usual.
-We include syntax sugar for $\zero$, $\suc$, $\suc(\zero)$,
-$\cdots$, with the decimal representation: $0$, $1$, $2$, $\cdots$
-as well.
-\end{notation}
-
-Therefore, one approach to guarantee a structural recursive function based on
-a general recursive function $\rm{f}: \Prop \to \Prop$ is to formulate a new function $\rm{f}^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls are done on smaller arguments.
-
-\begin{example}
-\label{ex:structural-recursion}
-
-Let us consider the following example to exhibit the bounded technique
-mentioned above for the \fuh function. this function is used for reconstructing
-the \Metis \strip inference rule in Section~\ref{sssec:strip-a-goal}.
-
-\begin{equation}
-\label{eq:uh-definition}
-\begin{aligned}
-&\hspace{.495mm}\fuh_{0} : \Prop → \Prop\\
-&\begin{array}{lll}
-  \fuh_{0} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{0}~((φ₁ ∧ φ₂) ⇒ φ₃)\\
-  \fuh_{0} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fuh_{0}~(φ₁ ⇒ φ₂) ∧ \fuh_{0}~(φ₁ ⇒ φ₃)\\
-  \fuh_{0} &φ                &= φ
-\end{array}
-\end{aligned}
-\end{equation}
-
-In (\ref{eq:uh-definition}), the first two equation show
-call on arguments no structurally smaller.
-For instance, on the first call, $φ ≡ (φ₁ ∧ φ₂) ⇒ φ₃$, the recursion
-calls on the  $φ₁ ⇒ (φ₂ ⇒ φ₃)$ argument.
-But this argument is not a subformula for φ.
-Therefore, one way to translate $\fuh_{0}$ in (\ref{eq:uh-definition}) to type
-theory is to define the a new function using the bounded technique.
-\begin{equation}
-\label{eq:uh-structured}
-\begin{aligned}
-&\hspace{.495mm} \fuh_{1} : \Prop → \Nat \to \Prop\\
-&\begin{array}{llll}
-\fuh_{1} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &(\suc~n) &= \fuh_{1}~((φ₁ ∧ φ₂) ⇒ φ₃)~n\\
-\fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
-\fuh_{1} &φ &\xspace\text{n} &= φ
-\end{array}
-\end{aligned}
-\end{equation}
-
-As we mentioned above, the natural number in the second argument of
-the function stands for a complexity measure of it.
-
-Recall the \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
-and presented in \cite{VanDalen1994} as \emph{the rank for a
-proposition}, is a function $\Prop \to \Nat$ that assigns a natural
-number for a proposition $φ$ like the following $\frank$ function.
-The symbols $c_{¬}$ and $c_{\square}$ are non-negative integer
-numbers called the complexity of the respective connective.
-
-\begin{equation}
-% \label{eq:rank-definition}
-\begin{aligned}
-&\hspace{.495mm}\frank : \Prop → \Nat\\
-&\begin{array}{llll}
-\frank~(¬~φ)           &= \frank~φ₁~+~c_{¬}\\
-\frank~(φ₁~\square~φ₂) &= \fmax~(\frank~φ₁)~(\frank~φ₂) + c_{\square}\\
-\frank~φ               &= 0
-\end{array}
-\end{aligned}
-\end{equation}
-
-We define the $\fuh_{cm}: \Prop → \Nat$ function as
-the complexity measure for the $\fuh_0$ function.
-
-\begin{equation*}
-  \begin{aligned}
-    &\hspace{.495mm}\fuh_{cm} : \Prop → \Nat\\
-    &\begin{array}{llll}
-    \fuh_{cm}~(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{cm}~φ₃ + 2\\
-    \fuh_{cm}~(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fmax~(\fuh_{cm}~φ₂)~(\fuh_{cm}~φ₃) + 1\\
-    \fuh_{cm}~φ                &= 0
-    \end{array}
-  \end{aligned}
-\end{equation*}
-
-Following the technique mentioned above, we get the structural recursive definition of $\fuh_{0}$ function presented in ~(\ref{eq:uh}).
-
-\begin{align}
-  \label{eq:uh}
-  \begin{split}
-  &\fuh : \Prop → \Prop\\
-  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
-  \end{split}
-\end{align}
-
-\end{example}
-
-For a more complete treatment of general recursion, and how to
-define well-founded and well-structural recursive functions, we refer
-the reader to \citeauthor{Bove2005}~\cite{Bove2005}.
-
 % % ................................................
@@
 
-In this section, we reconstruct each \Metis inference rule.
-We present a function and a theorem for each rule.
+In this section, we reconstruct each \Metis inference rule with a
+function and its respective theorem. We present a pattern of the
+formal description for these rules.
 
@@
 
-The following pattern is used to present the reconstruction.
-
-For example, we know the \verb!conjunct! inference rule is a
-\Metis inference rule since it appears in \TSTP derivations like
-the following excerpt.
+\begin{myexample}
+\Metis has a inference rule named conjunct.
+Since that rule appears in \TSTP derivations like in the following excerpt.
+We refer to this rule writing \conjunct.
 
 \begin{verbatim}
-fof(norm1, (p | r), inf(conjunct, [norma1])).
+fof(p3, (r | ~ p), inf(conjunct, [p1])).
 \end{verbatim}
 
-For this inference rule, we the \rm{conjunct} function in~(\ref{def:conjunct}) and we proved Theorem~\ref{thm:thm-conjunct}. The pattern is the following for
-a binary rule and we extend it for $n$-ary rules in a natural way.
+The pattern of the formalization for this rule is the following.
+For \conjunct rule, we define in type theory a function using the same name,
+conjunct, but written using roman font to distinguish from the original.
+The \fconjunct function has the following pattern:
+
+ \begin{equation*}
+  \begin{aligned}
+  &\hspace{.495mm}\fconjunct : \Prop → \Prop → \Prop\\
+  &\begin{array}{ll}
+  \fconjunct~φ~ψ\ &=
+      \begin{cases}
+      ψ, &\text{if }\fconjunct \text{ built }ψ\text{ by applying valid}\\
+         &\text{transformations or other rules to }φ\\
+      φ, &\text{otherwise.}
+      \end{cases}
+  \end{array}
+  \end{aligned}
+  \end{equation*}
 
 \begin{itemize}
-\item \conjunct is a binary \Metis inference rule.
-\item $\rm{conjunct}$ is the type theory function for the \texttt{rule} inference.
-\begin{align*}
-  \begin{split}
-    &\rm{conjunct} : \Prop → \Prop → \Prop\\
-    &\rm{conjunct}\ φ₁\ φ₂\ ψ\ =
-      \begin{cases}
-      ψ, &\text{if }\rm{conjunct}\text{ built }ψ\text{ by applying valid transformations}\\
-         &\text{or other rules to }φ₁\text{ and }φ₂\\
-      φ, &\text{otherwise.}
-      \end{cases}
-  \end{split}
-\end{align*}
-
-\begin{itemize}
-  \item $φᵢ$ are \emph{source} formulas from previous deducted derivations.
-  \item $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
-\end{itemize}
-\item The theorem that proves the soundness of the
-$\rm{conjunct}$ function would be
-\begin{equation*}\text{If }Γ ⊢ φ\text{ then }Γ ⊢ \rm{conjunct}\ φ.\end{equation*}
+  \item[$\bullet$] $φ$ is the \emph{source} formula from a previous deducted derivation.
+  \item[$\bullet$] $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
 \end{itemize}
 
-\begin{table}[!ht]
-\label{tab:agda-metis-table}
-\caption{Presentation of \Metis inference rules in type theory.}
-  \begin{center}
-  {\renewcommand{\arraystretch}{1.6}%
-    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}
-    \hline
-    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
-    \texttt{canonicalize}
-      &Normalization of the formula
-      &Theorem~\ref{thm:canonicalize}
-    \\
-    \texttt{clausify}
-      &Performs clausification
-      &Theorem~\ref{thm:clausify}
-    \\
-    \hyperlink{atp-conjunct}{\texttt{conjunct}}
-      &Takes a formula from a conjunction
-      &Theorem~\ref{thm:conjunct}
-    \\
-    % \texttt{negate}
-    %   &Negate the formula
-    %   &Theorem~\ref{thm:negate}
-    % \\
-    \texttt{resolve}
-      &A general form of the resolution theorem
-      &Theorem~\ref{thm:resolve}
-    \\
-    \texttt{simplify}
-      &Simplify definitions and theorems
-      &Theorem~\ref{thm:simplify}
-    \\
-    \texttt{strip}
-      &Strip a goal into subgoals
-      &Theorem~\ref{thm:strip}
-    \\[1ex]
-    \hline
-    \end{tabular}}
-  \end{center}
-\end{table}
+To justify all transformations done by \fconjunct, we prove its soundness
+with a theorem. This theorem would be
 
-MISSING TEXT
+\begin{equation*}
+\text{If }Γ ⊢ φ\text{ then }Γ ⊢ \fconjunct~φ~ψ.
+\end{equation*}
+
+\end{myexample}
+
+The remainder of this section will be devoted to present a formal description
+in type theory of each rule presented in Table~\ref{tab:agda-metis-table} using
+the pattern present in the example above.
 

### 2017-10-23 paper/sections/proof-reconstruction/negate.tex
[ paper ] lots of changes.

@@
 The \negate rule assumes the negation of such subgoals. Then, this rules
-is always derived from a strip inference application as we can see in 
+is always derived from a \strip inference application as we can see in
 the following \TSTP excerpt.
+
+\begin{myexample}
+\negate is a rule that only puts the negation symbol
+in front of the formula to assume it.
 
@@
 
+\end{myexample}
+
 To emulate this rule, we only need to introduce the negation
-of the subgoal by using $assume$ rule from the inferences in
-Fig.~\ref{fig:CPL-inference-rules}.
+of the subgoal by using $assume$ rule.
 

### 2017-10-23 paper/sections/proof-reconstruction/resolve.tex
[ paper ] lots of changes.

@@
 
-First, we define \rm{rassoc}$_{⬓}$ function in~(\ref{def:right-square})
-to convert a disjunctions or a conjunction into its right-associative form.
-We use $\rm{rassoc}_{∧}$ to convert conjunctions and $\rm{rassoc}_{∨}$ for
+First, we define \fassoc$_{⬓}$ function in~(\ref{def:right-square})
+to convert a disjunction or a conjunction into its right-associative form.
+The square symbol can be the conjunction symbol or the disjunction symbol.
+We use $\fassoc_{∧}$ to convert conjunctions and $\fassoc_{∨}$ for
 disjunctions.
@@
   \begin{aligned}
-    &\hspace{.495mm}\rm{rassoc}_{⬓} : \Prop \to \Prop\\
+    &\hspace{.495mm}\fassoc_{⬓} : \Prop \to \Prop\\
     &\begin{array}{lll}
-    \rm{rassoc}_{⬓} &((φ₁ ⬓ φ₂) ⬓ φ₃) &= \rm{rassoc}_{⬓}~(φ₁~⬓~(φ₂ ⬓ φ₃))\\
-    \rm{rassoc}_{⬓} &(φ₁ ⬓ φ₂)        &= φ₁~∨~\rm{rassoc}_{⬓}~φ₂\\
-    \rm{rassoc}_{⬓} &φ                &= φ
+    \fassoc_{⬓} &((φ₁~⬓~φ₂)~⬓~φ₃) &= \fassoc_{⬓}~(φ₁~⬓~(φ₂~⬓~φ₃))\\
+    \fassoc_{⬓} &(φ₁~⬓~φ₂)        &= φ₁~∨~\fassoc_{⬓}~φ₂\\
+    \fassoc_{⬓} &φ                &= φ
     \end{array}
@@
 
-\begin{example}\hspace{5mm}\\
+\begin{myexample}\hspace{10cm}
 \begin{enumerate}
-\item $\rm{rassoc}_{∨}~(((p ∨ ((q ∨ r) ∨ s)) ∨ t) = p ∨ (q ∨ (r ∨ (s ∨ t)))$.
-\item $\rm{rassoc}_{∧}~((((p ∧ q) ∧ r) ∧ s) ∧ t) = p ∧ (q ∧ (r ∧ (s ∧ t)))$.
+\item $\fassoc_{∨}~(((p ∨ ((q ∨ r) ∨ s)) ∨ t) = p ∨ (q ∨ (r ∨ (s ∨ t)))$.
+\item $\fassoc_{∧}~((((p ∧ q) ∧ r) ∧ s) ∧ t) = p ∧ (q ∧ (r ∧ (s ∧ t)))$.
 \end{enumerate}
-\end{example}
-
-\begin{remark}
-In \TPTP syntax, the formulas are in left-associative form by default.
-Despite of that convention, \Metis understands a formula to be in right-associative form by default. As we mentioned above, this is a matter to take into account for
-the proof-reconstruction. We opted to work as far as possible with right-associative formulas in~\cite{AgdaMetis}.
-\end{remark}
+\end{myexample}
 
@@
 \label{lem:rassoc}
-  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rassoc}_{⬓}~φ$.
+  If $Γ ⊢ φ$ then $Γ ⊢ \fassoc_{⬓}~φ$.
 \end{mainlemma}
 
-\begin{equation*}
- \label{eq:build-or}
-  \begin{aligned}
-  &\hspace{.495mm}\rm{build}_{∨} : \Prop → \Prop → \Prop\\
-  &\begin{array}{llll}
-    \rm{build}_{∨}&ψ~ψ &= ψ\\
-    \rm{build}_{∨}&φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if } ψ_{1} ≡ \rm{build}_{∨}~φ~ψ_{1}\\
-    \rm{build}_{∨}&φ~(ψ₁ ∨ ψ₂)&=ψ &\text{ if } ψ_{2} ≡\rm{build}_{∨}~φ~ψ_{2}\\
-    \rm{build}_{∨}&φ~ψ&=φ&\text{ otherwise.}
-   \end{array}
-  \end{aligned}
-\end{equation*}
+\begin{myremark}
+In \TPTP syntax, the formulas are in left-associative form by default.
+Despite of that convention, \Metis understands a formula to be in right-associative form by default. This is a matter to take into account for the proof-reconstruction.
+\end{myremark}
 
-\begin{equation}
-  \label{eq:ndisj-or}
-  \begin{aligned}
-  &\hspace{.495mm}\rm{ndisj}_{∨} : \NProp \to \NProp\\
-  &\begin{array}{lll}
-    \rm{ndisj}_{∨} &(¬ φ₁ ∨ φ₂) &=
-        \begin{cases}
-         ⊤, &\text{ if } φ₁ ∈_{∨} φ₂\\
-         ⊤, &\text{ if } \rm{ndisj}_{∨}~φ₂≡ ⊤\\
-         ¬ φ₁ ∨ \rm{ndisj}_{∨}~φ₂, &\text{ otherwise.}
-        \end{cases}\\
-
-  \rm{ndisj}_{∨} &(φ₁ ∨ φ₂)&=
-        \begin{cases}
-         ⊤, &\,\,\,\,\,\,\text{ if } ¬φ₁ ∈_{∨} φ₂ \\
-         ⊤, &\,\,\,\,\,\,\text{ if } \rm{ndisj}_{∨}(φ₂) ≡ ⊤\\
-         φ₁ ∨ \rm{ndisj}_{∨}~φ₂, &\,\,\,\,\,\,\text{ otherwise.}
-        \end{cases}\\
-    \rm{ndisj}_{∨}&φ &=φ
-    \end{array}
-  \end{aligned}
-\end{equation}
-
-The $\rm{build}_{∨}$ function defined above intends to construct a
-disjunction from another disjunction, specifically, this functions will
-try to rearrange the disjuncts in the source formula to match with the
-target disjunction formula, similar as we describe above.
+The $\fbuild_{∨}$ function defined in~(\ref{eq:build-or})
+intends to construct a disjunction from another disjunction, specifically,
+this functions will try to rearrange the disjuncts in the source formula to
+match with the target disjunction formula.
 
@@
 \label{lem:build-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{build}_{∨}~φ~ψ$.
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fbuild_{∨}~φ~ψ$, where,
+\begin{equation*}
+  \begin{split}
+  \label{eq:build-or}
+  &\fbuild_{∨} : \Prop → \Prop → \Prop\\
+  &\fbuild_{∨}~φ~ψ~ =%\\
+  % &\hspace{3mm}
+  \begin{cases}
+  ψ, &\text{ if } φ ≡ ψ\\
+  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{, } ψᵢ ≡ \fbuild_{∨}~φ~ψᵢ\text{ for some }i=1, 2\\
+  φ, &\text{ otherwise.}
+  \end{cases}
+  \end{split}
+\end{equation*}
 \end{mainlemma}
@@
 \label{lem:factor}
-  $Γ ⊢ φ$ then $Γ ⊢ \ffactor~φ$, where,
+ If $Γ ⊢ φ$ then $Γ ⊢ \ffactor~φ$, where,
+\begin{align}
+\begin{split}
+  \label{eq:factor-definition}
+  &\ffactor : \Prop → \Prop\\
+  &\ffactor~φ~ =
+  \begin{cases}
+    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ \ffactor~φ₂\\
+    φ,   &\text{ otherwise.}
+  \end{cases}
+\end{split}
+\end{align}
+\end{mainlemma}
+
+To construct a disjunction $ψ$ from a disjunction $φ$, we have used ideas
+from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove
+equality between nested disjunctions.
+We define the $\fsbuild_{∨}$ function in~(\ref{eq:strong-build-or}).
+that uses every disjunct from the source formula, $φ$, to build up the
+target disjunction $ψ$.
+
+\begin{mainlemma}
+\label{lem:sbuild-or}
+If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fsbuild_{∨}~φ~ψ$, where,
 \begin{equation}
-  \label{eq:factor-definition}
+\label{eq:strong-build-or}
  \begin{aligned}
-   &\hspace{.495mm}\ffactor : \Prop → \Prop\\
-    &\begin{array}{llll}
-     \ffactor&(φ₁ ∨ φ₂) &=φ₁,  &\text{ if } φ₁ ≡ \ffactor~φ₂\\
-     \ffactor&φ &= φ, &\text{ otherwise.}
+     &\hspace{.495mm}\fsbuild_{∨} : \Prop → \Prop → \Prop\\
+    &\begin{array}{lll}
+    \fsbuild_{∨}&(φ₁ ∨ φ₂)~ψ &=\ffactor~(\fbuild_{∨}~φ₁~ψ ∨ \fbuild_{∨}~φ₂~ψ)\\
+    \fsbuild_{∨}&φ~ψ &= \fbuild_{∨}~φ~ψ
      \end{array}
@@
 
-To construct a disjunction $ψ$ from a disjunction $φ$, we have used ideas
-from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove
-equality between nested disjunctions.
-We define the $\rm{sbuild}_{∨}$ function in~(\ref{eq:strong-build-or}).
-that uses every disjunct from the source formula, $φ$, to build up the
-target disjunction $ψ$.
-
-\begin{mainlemma}
-\label{lem:sbuild-or}
-If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \rm{sbuild}_{∨}~φ~ψ$, where,
-\begin{equation}
-\label{eq:strong-build-or}
- \begin{aligned}
-     &\hspace{.495mm}\rm{sbuild}_{∨} : \Prop → \Prop → \Prop\\
-    &\begin{array}{lll}
-    \rm{sbuild}_{∨}&(φ₁ ∨ φ₂)~ψ &=\ffactor(\rm{build}_{∨}~φ₁~ψ ∨ \rm{build}_{∨}~φ₂~ψ)\\
-    \rm{build}_{∨}&φ~ψ &= \rm{build}_{∨}~φ~ψ
-     \end{array}
-\end{aligned}
-\end{equation}
-\end{mainlemma}
-
-\begin{example}
-Let see the main idea behind the lem-sbuild$_{∨}$ lemma.
-We build the disjunction $((p ∨ q) ∨ r)$ from the disjunction
-$(r ∨ (q ∨ p))$.
+\begin{myexample}
+We build the disjunction $(p ∨ q) ∨ r$ from the disjunction
+$r ∨ (q ∨ p)$ based on the idea of the Lemma~\ref{lem:sbuild-or}.
 \begin{equation*}
@@
 \end{equation*}
-\end{example}
+\end{myexample}
 
-Notice that using $\rm{sbuild}_{∨}$ we can build not only a disjunction
+\begin{myremark}
+Notice that using $\fsbuild_{∨}$ we can build not only a disjunction
 with the same disjuncts of the source formula but also a complete different
-formula by adding new disjuncts to the source formula.
+disjunction by adding new disjuncts to the source formula.
+\end{myremark}
+
+The following lemma tries to reorder nested disjunctions
+by forcing the formula to be in right-associative form in order to
+apply Lemma~\ref{lem:sbuild-or}.
 
@@
   If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}~φ~ψ~$, where,
-  \begin{align*}
+  \begin{align}
+    \begin{split}
     \label{eq:reorder-or}
-    \begin{split}
     &\freorder_{∨} : \Prop \to \Prop \to \Prop\\
-    &\freorder_{∨}~φ~ψ~= \rm{sbuild}_{∨}~(rassoc_{∨}~φ)~ψ.
+    &\freorder_{∨}~φ~ψ~= \fsbuild_{∨}~(\fassoc_{∨}~φ)~ψ.
     \end{split}
-  \end{align*}
+  \end{align}
 \end{mainlemma}
@@
 
-We define similar functions and state some theorems as we previously did
-for disjunctions, but instead, we treat only with conjunctive normal forms.
+Now, we define function to work with nested conjunctions. This will
+help us in the end of this section to reorder conjunctive normal forms.
+For instance, the $\freorder_{∧}$ function in~(\ref{eq:reorder-and}),
+reorders nested conjunctions.
 
@@
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}~φ~ψ$, where,
-    \begin{align*}
+    \begin{align}
       \begin{split}
+      \label{eq:reorder-and}
         &\freorder_{∧} : \Prop → \Prop \to \Prop\\
@@
           ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }ψ₁ ≡ \freorder_{∧}~φ~ψ₁ \\
-                  &\text{and } ψ₂ ≡ \freorder_{∧}~φ~ψ₂\\
+                   &\text{ and } ψ₂ ≡ \freorder_{∧}~φ~ψ₂\\
           φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
@@
       \end{split}
-  \end{align*}
+  \end{align}
 \end{mainlemma}
+
+\begin{myexample}\hspace{10cm}
+\begin{enumerate}
+  \item $\freorder_{∧}~(p ∧ q ∧ r)~(r ∧ q ∧ p)~=~(r ∧ q ∧ p).$
+  \item $\freorder_{∧}~(p ∧ q ∧ r)~(r ∧ r ∧ p)~=~(r ∧ q ∧ p).$
+  \item $\freorder_{∧}~(p ∧ q ∧ r)~(k ∧ q ∧ p)~=~(p ∧ q ∧ r).$
+  \item $\freorder_{∧}~((p ∨ q) ∧ r)~(r ∧ (q ∨ p))~=~((p ∨ q) ∧ r).$
+\end{enumerate}
+\end{myexample}
+
+In the last example, Item~4, we could not build the conjunction
+$r ∧ (q ∨ p)$ since $p ∨ q$ is not syntactical equal to $q ∨ p$.
+We solve this issue in the Lemma~\ref{lem:reorder-and-or} by
+using the $\fconjunct_{∨}$ function defined in~(\ref{eq:conjunct-or}).
 
@@
   \begin{equation*}
-\label{eq:conjunct-or-definition}
     \begin{split}
+    \label{eq:conjunct-or}
       &\fconjunct_{∨} : \Prop → \Prop \to \Prop\\
@@
         ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \fconjunct_{∨}~φ~ψ₁,\\
-        &\text{and } ψ₂ ≡ \freorder_{∨}~φ~ψ₂\\
+           &\text{ and } ψ₂ ≡ \freorder_{∨}~φ~ψ₂\\
         ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunct_{∨}~φ₁~ψ \\
@@
 
+Now, we are able to reorder conjunctive normal forms using
+$\freorder_{∧∨}$ function defined in (\ref{eq:reorder-and-or})
+that unifies the previous lemma showed above.
+
 \begin{mainlemma}
@@
       \begin{split}
+      \label{eq:reorder-and-or}
       &\freorder_{∧∨} : \Prop \to \Prop \to \Prop\\
@@
 
-The \resolve rule incorporates the resolution theorem showed in
-Fig.~\ref{fig:metis-inferences} for the \TSTP derivations.
-This rule posses three arguments: a positive literal $l$ to apply the
-resolution theorem, and two derivations.
+Now, we are in a position to reconstruct \resolve rule. This is the
+first application of the Lemma \ref{lem:reorder-and-or}.
+The \resolve rule is a generalization of the resolution theorem showed in
+Fig.~\ref{fig:metis-inferences} in the \TSTP derivations.
+This rule has three arguments: a positive literal $l$ to apply the
+resolution theorem and two derivations.
 The positive literal $l$ must occur in
 the formula from the first derivation and the
-negative literal must occur in the formula from the second derivation,
+negative literal $¬ l$ must occur in the formula from the second derivation,
 see the pattern of \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.
 
-% \begin{figure}
-\label{fig:resolve-tstp-example}
+\begin{myexample}\hspace{10cm}
 \begin{verbatim}
-cnf(refute_0_4, plain, (~ r | p | q),
-    inference(canonicalize, [], [normalize_0_5])).
-cnf(refute_0_5, plain, (p | q | r),
-    inference(canonicalize, [], [normalize_0_6])).
-cnf(refute_0_6, plain, (p | q),
-    inference(resolve, [$cnf(r)], [refute_0_5, refute_0_4])).
+cnf(ref4, (~ r | p | q), inf(canonicalize, [norm5])).
+cnf(ref5, (p | q | r), inf(canonicalize, [norm6])).
+cnf(ref6, (p | q), inf(resolve, [$cnf(r)], [ref5, ref4])).
 \end{verbatim}
-% \caption{Excerpt of a \Metis \TSTP example for the \resolve rule.}
-% \end{figure}
+In the excerpt above, we apply resolution for the first two formulas,
+$¬ r ∨ p ∨ q$ and $p ∨ q ∨ r$. The last line tells us the literal mentioned
+for resolution is $r$. Syntactically speaking,
+we can not derive neither the conclusion $p ∨ q$ in \verb!ref6! nor apply the resolution theorem with \verb!ref4! and \verb!ref5! since the formulas does not fit the pattern required.
 
-To emulate this rule, we perform a sequence of rearrangements inside the
+If the scenario would have other like replacing \verb!ref5! by
+\begin{verbatim}
+cnf(ref5, (r | p | q), inf(canonicalize, [norm6])).
+\end{verbatim}
+We have could derive $(p ∨ q) ∨ (p ∨ q)$ but again, that is not the expected result.
+\end{myexample}
+
+Therefore, we perform a sequence of rearrangements inside the
 formulas involved to match with the pattern expected by the resolution theorem
-described above. We begin by defining a convenient version of
-the binary resolution in Def.~\ref{eq:rsol}.
-
-% \begin{equation}
-% \label{eq:rsol}
-% \begin{aligned}
-% &\rm{rsol} : \Prop \to \Prop\\
-%       \begin{split}
-%         &\rm{rsol} : \Prop \to \Prop\\
-%         &\rm{rsol}~φ =
-%         \begin{cases}
-%           φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁, φ₂ ≡ φ₄\\
-%           φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (φ₃ ∨ φ₄), φ₃ ≡ ¬ φ₁\\
-%           φ, &\text{ otherwise.}
-%         \end{cases}
-%       \end{split}
-%   \end{align*}
-% \end{definition}
+described in Fig.~\ref{fig:metis-inferences}. Using reordering after
+applying a convenient version of the resolution theorem defined
+in~(\ref{eq:rsol}) we get the expect result.
 
@@
   \label{lem:rsol}
-  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}~φ$.
+  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}~φ$, where,
+  \begin{equation}
+    \label{eq:rsol}
+    \begin{aligned}
+    &\rm{rsol} : \Prop \to \Prop\\
+    &\begin{array}{ll}
+      \rm{rsol}~φ &=
+        \begin{cases}
+          φ₂, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (¬φ₁ ∨ φ₂)\\
+          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (¬φ₁ ∨ φ₄)\\\
+          φ, &\text{ otherwise.}
+        \end{cases}
+      \end{array}
+      \end{aligned}
+\end{equation}
 \end{mainlemma}
-
-In Def.~\ref{def:resolve}, the proposed rule for $resolve$
-has four arguments. The first three were described
-above, the last one, ψ, represents the expected conclusion in the \Metis
-derivation.
 
@@
 
-\begin{example}COMPLETAR ESTE EJEMPLO AL FINAL
+\begin{myexample}
+Continuing with the problem presented in the example above,
+we can use Theorem \ref{thm:resolve} to derive $Γ ⊢ p ∨ q$.
+Let be $φ₁ ≡ p ∨ q ∨ r$ and $φ₂ ≡ ¬ r ∨ p ∨ q$.
+
 \begin{equation*}
   \begin{bprooftree}
+  \AxiomC{$Γ ⊢ p ∨ q ∨ r $}
   \AxiomC{$Γ ⊢ ¬ r ∨ p ∨ q$}
-  \AxiomC{$Γ ⊢ p ∨ q ∨ r $}
   \RightLabel{Theorem \ref{thm:resolve}}
-  \BinaryInfC{$Γ ⊢ \fresolve~(¬ r ∨ p ∨ q)~(p ∨ q ∨ r)~r~(p ∨ q)$}
+  \BinaryInfC{$Γ ⊢ \fresolve~(p ∨ q ∨ r)~(¬ r ∨ p ∨ q)~r~(p ∨ q)$}
+  \RightLabel{by (\ref{eq:resolve})}
+  \UnaryInfC{$Γ ⊢ \rm{rsol}~(\freorder_{∨}~φ₁~(r ∨ (p ∨ q))~∧~\freorder_{∨}~φ₂~(¬ r ∨ (p ∨ q))$}
+  \RightLabel{by (\ref{eq:reorder-or})}
+  \UnaryInfC{$Γ ⊢ \rm{rsol}~((r ∨ (p ∨ q)) ∧ (¬ r ∨ (p ∨ q)))$}
+  \RightLabel{by (\ref{eq:rsol})}
   \UnaryInfC{$Γ ⊢ p ∨ q$}
@@
 \end{equation*}
-\end{example}
+\end{myexample}
 

### 2017-10-23 paper/sections/proof-reconstruction/strip.tex
[ paper ] lots of changes.

@@
 goal becomes, in smaller proofs, one refutation for each subgoal.
-These subgoals are introduced in the \TSTP derivation with the \strip
-inference rule as we show in the following excerpt.
+
+\begin{myexample}
+The subgoals mentioned above are introduced in the \TSTP derivation
+with the \strip inference rule.
 
@@
 
-To prove the correctness of the process mentioned above,
-we need to establish some lemmas before introduce our main goal of this
-part, Theorem~\ref{thm:strip}.
+In the script above, the conjecture $(p ∧ r) ∧ q$ is stripped in
+tree subgoals: $p$, $p ⇒ r$ and $(p ∧ r) ⇒ q$.
+
+\begin{equation}
+\label{eq:strip-example}
+(p ∧ (p ⇒ r) ∧ ((p ∧ r) ⇒ q)) ⇒ ((p ∧ r) ∧ q)
+\end{equation}
+
+In (\ref{eq:strip-example}), by proving each subgoal from left to right in the right conjunction,
+we get a proof for the conjecture by using the elimination of the implication .
+\end{myexample}
+
+We prove the correctness of the process mentioned above in
+Theorem~\ref{thm:strip}. To show that theorem, we need to prove
+Lemma~\ref{lem:inv-uh-lem} and Lemma~\ref{lem:lem-inv-strip}.
 
@@
 \begin{itemize}
-  \item If $n = 0$, by definition we conclude $Γ ⊢ φ$.
+  \item If $n = 0$, by definition in~(\ref{eq:uh-structured})
+        we conclude $Γ ⊢ φ$.
   \item If $n = 1$, we apply the following theorem proved in~\cite{AgdaProp},
@@
   \UnaryInfC{$Γ ⊢ \fuh_1~((φ₁ ∧ φ₂) ⇒ φ₃)~n$}
-  \RightLabel{by hip.}
+  \RightLabel{by hyp.}
   \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
@@
     \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n$}
-    \RightLabel{by hip.}
+    \RightLabel{by hyp.}
     \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
@@
     \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₃)~n$}
-    \RightLabel{by hip.}
+    \RightLabel{by hyp.}
     \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
@@
 \label{lem:lem-inv-strip}
-Let $\text{n} : \Nat$ be the complexity measure of the strip function
-in~(\ref{eq:strip-unfixed}).
+Let $\text{n} : \Nat$ be the complexity measure of the strip function defined
+in~(\ref{eq:strip-fixed}).
 If $Γ ⊢ \fstrip~φ~n$ then $Γ ⊢ φ$.
@@
   \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
-  \RightLabel{by hip.}
+  \RightLabel{by hyp.}
   \UnaryInfC{$Γ ⊢ φ₁$}
@@
   \BinaryInfC{$Γ ⊢ \fstrip~φ₂~n$}
-  \RightLabel{by hip.}
+  \RightLabel{by hyp.}
   \UnaryInfC{$Γ ⊢ φ₂$}
@@
 \UnaryInfC{$Γ ⊢ \fstrip~¬ φ₁~n$}
-\RightLabel{by hip.}
+\RightLabel{by hyp.}
   \UnaryInfC{$Γ ⊢ ¬φ₁$}
@@
   \BinaryInfC{$Γ ⊢ \fstrip~¬ φ₂~n$}
-  \RightLabel{by hip.}
+  \RightLabel{by hyp.}
   \UnaryInfC{$Γ ⊢ ¬ φ₂$}
@@
 
-MISSING TEXT
+The following theorem is convenient to substitute equals by equals in
+a theorem. Recall the equality is symmetric and transitive as well.
+We use such properties without any mention.
 

### 2017-10-23 paper/sections/limitations-type-theory.tex
[ paper ] last changes.

@@
 
-MISSING TEXT
+AGREGAR TEXTO INTRODUCTORIO
 
@@
 Therefore, one approach to guarantee a structural recursive function based on
-a general recursive function $\rm{f}: \Prop \to \Prop$ is to formulate a new function $\rm{f}^{*} : \Prop \to \Nat \to \Prop$ where all recursive calls are done on smaller arguments.
+a general recursive function $\rm{f}:~\Prop~\to~\Prop$ is to formulate a new function $\rm{f}^{*}~:~\Prop~\to~\Nat~\to~\Prop$ where all of its recursive calls are done on smaller arguments.
 
@@
 Let us consider the following example to exhibit the bounded technique
-mentioned above for the \fuh function. this function is used for reconstructing
+mentioned above for the \fuh function. This function is used for reconstructing
 the \Metis \strip inference rule in Section~\ref{sssec:strip-a-goal}.
@@
 
-In (\ref{eq:uh-definition}), the first two equation show
+In (\ref{eq:uh-definition}), the first two equation
 call on arguments no structurally smaller.
 For instance, on the first call, $φ ≡ (φ₁ ∧ φ₂) ⇒ φ₃$, the recursion
-calls on the  $φ₁ ⇒ (φ₂ ⇒ φ₃)$ argument.
-But this argument is not a subformula for φ.
-Therefore, one way to translate $\fuh_{0}$ in (\ref{eq:uh-definition}) to type
-theory is to define the a new function using the bounded technique.
+calls on the  $φ₁ ⇒ (φ₂ ⇒ φ₃)$ argument that is not a subformula of φ.
+Therefore, one way to translate $\fuh_{0}$ to type
+theory is to define a new function using a bounded recursion.
 
@@
 
-As we mentioned above, the natural number in the second argument of
-the function stands for a complexity measure of it.
+We bounded the recursion calls in~(\ref{eq:uh-structured}) with \Nat type argument. This natural number represents the complexity measure of $\fuh_{0}$
+function.
 
@@
 
-...
+AGREGAR TEXTO
 

### 2017-10-23 paper/sections/metis-language-and-proofs.tex
[ paper ] last changes.

@@
 Let us consider the following \TSTP derivation using
-the customized \TSTP syntax. Note that we remove for example
-empty fields in the inference information, the \verb!role! field if it is
-\verb!plain! and shorten names as long as possible.
+the customized \TSTP syntax. Note that we remove
+empty fields in the inference information, we shorten names as long as possible, and we delete the \verb!role! field when the role is
+\verb!plain!.
 
@@
 \label{ssec:metis-inferences-rules}
+
+AGREGAR EL TEXTO
 
@@
 \label{tab:agda-metis-table}
-\caption{Presentation of \Metis inference rules in type theory.}
+\caption{\Metis inference rules in type theory.}
   \begin{center}

### 2017-10-23 paper/sections/proof-reconstruction/resolve.tex
[ paper ] last changes.

@@
           ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁\\
-             &\text{and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂\\
+             &\text{ and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂\\
           φ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\

### 2017-10-23 paper/sections/proof-reconstruction/strip.tex
[ paper ] fixed subgoal description.

@@
 
-In (\ref{eq:strip-example}), by proving each subgoal from left to right in the right conjunction,
-we get a proof for the conjecture by using the elimination of the implication .
+\Metis proves each subgoal in the same order above from left to right
+in (\ref{eq:strip-example}).
+Besides the fact \Metis does not explicit in \TSTP derivation
+how it uses the proofs of subgoals, we know using the elimination
+of the implication, we get the proof of the conjecture.
 \end{myexample}
@@
 Let $\text{n} : \Nat$ be the complexity measure of the $\fuh_0$ function
-in~(\ref{eq:uh-structured}).
-If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$.
+in~(\ref{eq:uh-definition}).
+If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$, where $\fuh₁$ is the function defined
+in (\ref{eq:uh-structured}).
 \end{mainlemma}
@@
 The proof is by induction on the cases defined by the outcome of the
-$\fuh_{1}$ function in~(\ref{eq:uh-structured}).
+$\fuh_{1}$ function.
 \begin{itemize}

### 2017-10-23 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed rm funnctions and example added.

@@
 syntax aspects of the propositions, our approach shows equivalence
-by converting propositions to their conjunctive normal forms,
+by converting propositions to their conjunctive normal form,
 and reordering those and the inner disjunctions to match them.
@@
 
-% \begin{itemize}
-%   \item Reorder a disjunction $φ = φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$ to match with
-% $ψ = ψ₁ ∨ ψ₂ ∨ \cdots ∨ ψₙ$. For all $i$, there exists at least one $j$ such
-% that $φᵢ ≡ ψⱼ$.
-%   \item Reorder a CNF formula, $φ = φ₁ ∧ φ₂ ∧ \cdots$, to match with another
-% CNF formula $ψ = ψ₁ ∧ ψ₂ ∧ \cdots$. For all $i$, there exists at least one $j$
-% such that $φᵢ ≡ ψⱼ$.
-% \end{itemize}
-
-First, we define \fassoc$_{⬓}$ function in~(\ref{def:right-square})
+First, we define \fassoc$_{⬓}$ function in~(\ref{eq:fassoc})
 to convert a disjunction or a conjunction into its right-associative form.
@@
 \begin{equation}
-\label{def:right-square}
+\label{eq:fassoc}
   \begin{aligned}
@@
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fbuild_{∨}~φ~ψ$, where,
-\begin{equation*}
+\begin{equation}
   \begin{split}
@@
   \end{split}
-\end{equation*}
+\end{equation}
 \end{mainlemma}
@@
 simplifies a special case of disjunction, the repeated disjuncts
-(\eg, $\ffactor(φ ∨ φ) = φ$).
-Notice that other cases like $φ ∨ (ψ ∨ φ)$ do no reduce to $ψ ∨ φ$.
+(\eg, $\ffactor~(φ ∨ φ)~=~φ$).
+Notice that other cases like $φ~∨~(ψ~∨~φ)$ do no reduce to $ψ~∨~φ$.
 

### 2017-10-23 paper/sections/proof-reconstruction/clausify.tex
[ paper ] lots of changes.
[ paper ] fixed conjunct example.

@@
 
-In the following \Metis \TSTP derivation, we see an example where
-\clausify expands the formula \texttt{norm0} by using distributive
-laws included in the conjunctive normal form conversion.
+\begin{myexample}
+In the following \Metis \TSTP derivation, we see how
+\clausify expands the\texttt{norm0} formula to get \texttt{norm1} formula
+by using distributive laws included in the conjunctive normal form conversion.
 
@@
 \end{verbatim}
+
+\end{myexample}
 
@@
 
-\begin{remark}
+\begin{myremark}
 The \clausify rule is often preceded by \canonicalize.
@@
 \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.
-\end{remark}
+\end{myremark}
 

### 2017-10-23 paper/sections/proof-reconstruction/conjunct.tex
[ paper ] lots of changes.
[ paper ] fixed conjunct example.

@@
 following \TSTP excerpt shows.
-In the first formula \verb!p1!, \verb!p & q & (r | ~ p)!, is a left-associative conjunction.
-\conjunct extracts \verb!q!
-from the \verb!p1!
-conjunction by using twice left projection (∧-proj₁).
+
+\begin{myexample}\hspace{10cm}
 
@@
 \end{verbatim}
+
+In the first formula, \verb!p & q & (r | ~ p)!, we find a left-associative
+conjunction named \verb!p1!.
+\conjunct extracts \verb!q! from the \verb!p1! using a left
+projection (∧-proj₁) follow by a right projection (∧-proj₂).
+\conjunct extracts \verb!r | ~ p! by using right projection
+on \verb!p1!.
+\end{myexample}
 
@@
 
-\begin{proof}\hspace{2cm}\\
+\begin{proof}\hspace{10cm}
 \begin{itemize}

### 2017-10-23 paper/sections/metis-language-and-proofs.tex
[ paper ] fixed minor typos.

@@
 
+\begin{remark}
+We address proof-reconstruction in this paper for refutation proofs.
+We annotate \abbre{CPL} problems using \verb!fof! formulas that
+\Metis converts to \abbre{CNF} clauses to look for a refutation.
+\end{remark}
+
 \subsection{Output language}
@@
 
+\subsection{Proofs}
+\label{ssec:metis-proofs}
+
+A proof delivered by \Metis encodes a natural
+deduction proof.
+With these inference rules as the only valid deduction steps, \Metis
+attempts to prove conjectures by refutation (\eg,
+\emph{falsium} in the root of the \TSTP derivation).
+
+These proofs are directed acyclic graphs, trees of refutations
+Each node stands for an application of an inference rule and the leaves
+in the tree represent formulas in the given problem. Each node is
+labeled with a name of the inference rule (\eg, \canonicalize).
+Each edge links a premise with one conclusion.
+The proof graphs have at their root the conclusion
+$⊥$, since \Metis delivers proofs by refutation.
+
+\begin{figure}[!ht]
+\centering
+  \begin{bprooftree}\tt
+    \AxiomC{}
+    \RightLabel{negate}
+    \UnaryInfC{$\neg p$}
+    \RightLabel{strip}
+    \UnaryInfC{$\neg p$}
+    \AxiomC{}
+    \RightLabel{axiom}
+    \UnaryInfC{$p$}
+    \RightLabel{canonicalize}
+    \UnaryInfC{$p$}
+    \RightLabel{simplify}
+    \BinaryInfC{$⊥$}
+    \RightLabel{canonicalize}
+    \UnaryInfC{$⊥$}
+  \end{bprooftree}
+  \caption{A \Metis proof tree.}
+  \label{fig:metis-example}
+\end{figure}
+
 \subsection{Inference rules}
@@
 
-AGREGAR EL TEXTO
-
-% \TSTP derivations replied by \Metis use the following rules:
-% \canonicalize, \clausify, \conjunct, \simplify, \negate, and \strip.
+In the following table we present the list of inference rules used
+by \Metis in its \TSTP derivations for propositional logic.
 
@@
 
-\subsection{Proofs}
-\label{ssec:metis-proofs}
-
-A proof delivered by \Metis encodes a natural
-deduction proof (see a complete proof in Fig.~\ref{fig:metis-proof-tstp}).
-With these inference rules as the only valid deduction steps, \Metis
-attempts to prove conjectures by refutation (\eg,
-\emph{falsium} in the root of the \TSTP derivation
-in Fig.~\ref{fig:metis-proof-tstp}).
-
-These proofs are directed acyclic graphs, trees of refutations
-(see the proof tree of the \TSTP derivation showed above in
-Fig.~\ref{fig:metis-proof-tstp}).
-Each node stands for an application of an inference rule and the leaves
-in the tree represent formulas in the given problem. Each node is
-labeled with a name of the inference rule (e.g., \canonicalize).
-Each edge links a premise with one conclusion.
-The proof graphs have at their root the conclusion
-$⊥$, since \Metis delivers proofs by refutation.
-
-\begin{figure}[!ht]
-\centering
-  \begin{bprooftree}\tt
-    \AxiomC{}
-    \RightLabel{negate}
-    \UnaryInfC{$\neg p$}
-    \RightLabel{strip}
-    \UnaryInfC{$\neg p$}
-    \AxiomC{}
-    \RightLabel{axiom}
-    \UnaryInfC{$p$}
-    \RightLabel{canonicalize}
-    \UnaryInfC{$p$}
-    \RightLabel{simplify}
-    \BinaryInfC{$⊥$}
-    \RightLabel{canonicalize}
-    \UnaryInfC{$⊥$}
-  \end{bprooftree}
-  \caption{A \Metis proof tree.}
-  \label{fig:metis-example}
-\end{figure}
-
 \end{document}

### 2017-10-23 paper/sections/proof-reconstruction/strip.tex
[ paper ] fixed rm funnctions and example added.
[ paper ] fixed minor typos.

@@
 yields the conjunction of subgoals that implies the goal of the problem in
-the \Metis \TSTP derivations.
+the \Metis \TSTP derivations. Its definition is based on the source code
+of \Metis for the strip goal functions.
 
@@
 
-The function defined above is not a structural recursion function.
-Therefore, we have reformulated it in~(\ref{eq:strip-fixed}) in order to solve such an issue following the technique described in Section~\ref{ssec:structural-recursion}.
+The function defined above is not a structural recursion function. Therefore, we have reformulated it in~(\ref{eq:strip-fixed}) in order to solve such an issue following the technique described in
+Section~\ref{ssec:structural-recursion}.
 
@@
 %  1140  git push origin paper
+
 \begin{equation}
@@
 \label{thm:strip}
+Let $\text{n} : \Nat$ be the complexity measure of the strip function defined
+in~(\ref{eq:strip-fixed}).
 If $s_1$ and $s_2$ are the subgoals of the goal $φ$, that is,
-$\fstrip~φ~n~≡~s_1\wedge~s_2$, if $Γ ⊢ s_1$ and $Γ ⊢ s_2$ then $Γ ⊢ φ$.
+$$\fstrip~φ~n~≡~s_1∧~s_2,$$
+if $Γ ⊢ s_1$ and $Γ ⊢ s_2$ then $Γ ⊢ φ$.
 \end{mainth}

### 2017-10-24 paper/sections/metis-language-and-proofs.tex
[ paper ] fixing last suggestions.

@@
 \label{tab:agda-metis-table}
-\caption{\Metis inference rules in type theory.}
+\caption{\Metis inference rules.}
   \begin{center}
@@
       &Normalization of the formula
-      &Theorem~\ref{thm:canonicalize}
+      &\ref{thm:canonicalize}
     \\
@@
       &Performs clausification
-      &Theorem~\ref{thm:clausify}
+      &\ref{thm:clausify}
     \\
@@
       &Takes a formula from a conjunction
-      &Theorem~\ref{thm:conjunct}
+      &\ref{thm:conjunct}
     \\
@@
     %   &Negate the formula
-    %   &Theorem~\ref{thm:negate}
+    %   &\ref{thm:negate}
     % \\
@@
       &A general form of the resolution theorem
-      &Theorem~\ref{thm:resolve}
+      &\ref{thm:resolve}
     \\
@@
       &Simplify definitions and theorems
-      &Theorem~\ref{thm:simplify}
+      &\ref{thm:simplify}
     \\
@@
       &Strip a goal into subgoals
-      &Theorem~\ref{thm:strip}
+      &\ref{thm:strip}
     \\[1ex]

### 2017-10-24 paper/sections/proof-reconstruction/strip.tex
[ paper ] fixing last suggestions.

@@
 \begin{myexample}
-The subgoals mentioned above are introduced in the \TSTP derivation
+The subgoals associated to a goal are introduced in the \TSTP derivation
 with the \strip inference rule.
@@
 
-In the script above, the conjecture $(p ∧ r) ∧ q$ is stripped in
+In this example, the conjecture \verb!(p & r) & q! is stripped into
 tree subgoals: $p$, $p ⇒ r$ and $(p ∧ r) ⇒ q$.
@@
 
-We prove the correctness of the process mentioned above in
+We prove the correctness of the \strip inference rule in
 Theorem~\ref{thm:strip}. To show that theorem, we need to prove
@@
   \UnaryInfC{$Γ ⊢ \fuh_1~((φ₁ ∧ φ₂) ⇒ φ₃)~n$}
-  \RightLabel{by hyp.}
+  \RightLabel{by~ind.~hyp.}
   \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
@@
     \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n$}
-    \RightLabel{by hyp.}
+    \RightLabel{by~ind.~hyp.}
     \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
@@
     \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₃)~n$}
-    \RightLabel{by hyp.}
+    \RightLabel{by~ind.~hyp.}
     \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
@@
 
-We now define the $\fstripp$ function in~(\ref{eq:strip-unfixed}) that
-yields the conjunction of subgoals that implies the goal of the problem in
-the \Metis \TSTP derivations. Its definition is based on the source code
-of \Metis for the strip goal functions.
+The function that yields the conjunction of subgoals that implies the goal of
+the problem in the \Metis \TSTP derivations is not a structurally recursive
+function.  We present that function in (\ref{eq:strip-fixed}) after applying
+the bounded technique described in Section~\ref{ssec:structural-recursion}.
+We based the definition of this function based on the \Metis source code.
 
@@
   \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
-  \RightLabel{by hyp.}
+  \RightLabel{by~ind.~hyp.}
   \UnaryInfC{$Γ ⊢ φ₁$}
@@
   \BinaryInfC{$Γ ⊢ \fstrip~φ₂~n$}
-  \RightLabel{by hyp.}
+  \RightLabel{by~ind.~hyp.}
   \UnaryInfC{$Γ ⊢ φ₂$}
@@
 \UnaryInfC{$Γ ⊢ \fstrip~¬ φ₁~n$}
-\RightLabel{by hyp.}
+\RightLabel{by~ind.~hyp.}
   \UnaryInfC{$Γ ⊢ ¬φ₁$}
@@
   \BinaryInfC{$Γ ⊢ \fstrip~¬ φ₂~n$}
-  \RightLabel{by hyp.}
+  \RightLabel{by~ind.~hyp.}
   \UnaryInfC{$Γ ⊢ ¬ φ₂$}
@@
 The following theorem is convenient to substitute equals by equals in
-a theorem. Recall the equality is symmetric and transitive as well.
+a theorem. Recall the equality ≡ is symmetric and transitive as well.
 We use such properties without any mention.
@@
 For the sake of brevity, we state the following theorem for the
-\strip function when the goal has only two subgoals. In other cases,
-we extend that theorem in the natural way.
+\strip function when the goal has two subgoals. In other cases,
+we extend the theorem in the natural way.
 
@@
 in~(\ref{eq:strip-fixed}).
-If $s_1$ and $s_2$ are the subgoals of the goal $φ$, that is,
-$$\fstrip~φ~n~≡~s_1∧~s_2,$$
-if $Γ ⊢ s_1$ and $Γ ⊢ s_2$ then $Γ ⊢ φ$.
+Let $s₁$ and $s₂$ be the subgoals of the goal $φ$, that is,
+$$\fstrip~φ~n~≡~s₁∧~s₂.$$
+If $Γ ⊢ s₁$ and $Γ ⊢ s₂$ then $Γ ⊢ φ$.
 \end{mainth}
@@
 
+Since \Metis proves by refutation,
+to prove each subgoal, \Metis assumes the negation of it
+using the \negate rule. Then, this rule is always derived from a \strip
+inference application as we can see in the following \TSTP excerpt.
+
+\begin{verbatim}
+fof(goal, conjecture, (p & r & q)).
+fof(subgoal_0, p, inf(strip,[goal])).
+fof(subgoal_1, p => r, inf(strip,[goal])).
+fof(subgoal_2, (p & r) => q, inf(strip,[goal])).
+fof(negate_0_0, ~ p, inf(negate,[subgoal_0])).
+...
+fof(negate_1_0, ~ (p => r), inf(negate,[subgoal_1])).
+...
+fof(negate_2_0, ~ ((p & r) => q), inf(negate,[subgoal_2])).
+\end{verbatim}
+
 \end{document}

### 2017-10-24 paper/sections/proof-reconstruction/strip.tex
[ paper ] canon ==> simplify-and simplify-or.

@@
 the problem in the \Metis \TSTP derivations is not a structurally recursive
-function.  We present that function in (\ref{eq:strip-fixed}) after applying
+function.  We present its structural recursive function
+in~(\ref{eq:strip-fixed}) after applying
 the bounded technique described in Section~\ref{ssec:structural-recursion}.
@@
 \begin{equation}
-\label{eq:strip-unfixed}
+\label{eq:strip-fixed}
 \begin{aligned}
-&\hspace{.495mm}\fstripp : \Prop → \Prop\\
-&\begin{array}{lll}
-\fstripp &(φ₁ ∧ φ₂)     &= \fuh~(\fstripp~φ₁) ∧ \fuh~(φ₁ ⇒ \fstripp~φ₂)\\
-\fstripp &(φ₁ ∨ φ₂)     &= \fuh~(¬ φ₁ ⇒ \fstripp~φ₂)\\
-\fstripp &(φ₁ ⇒ φ₂)     &= \fuh~(φ₁ ⇒ \fstripp~φ₂)\\
-\fstripp &(¬ (φ₁ ∧ φ₂)) &= \fuh~(φ₁ ⇒ \fstripp~¬ φ₂)\\
-\fstripp &(¬ (φ₁ ∨ φ₂)) &= \fuh~(\fstripp~¬ φ₁) ∧ \fuh~(¬ φ₁ ⇒ \fstripp~¬ φ₂)\\
-\fstripp &(¬ (φ₁ ⇒ φ₂)) &= \fuh~(\fstripp~φ₁) ∧ \fuh~(φ₁ ⇒ \fstripp~¬ φ₂)\\
-\fstripp &(¬ ¬ φ₁)      &= \fuh~(\fstripp~φ₁)\\
-\fstripp &(¬ ⊥)         &= ⊤\\
-\fstripp &(¬ ⊤)         &= ⊥\\
-\fstripp &φ             &= φ
+&\hspace{.495mm}\fstrip₁ : \Prop → \Nat → \Prop\\
+&\begin{array}{llll}
+\fstrip₁ &(φ₁ ∧ φ₂)     &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)\\
+\fstrip₁ &(φ₁ ∨ φ₂)     &(\suc~n) &= \fuh~(¬ φ₁ ⇒ \fstrip₁~φ₂~n)\\
+\fstrip₁ &(φ₁ ⇒ φ₂)     &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)\\
+\fstrip₁ &(¬ (φ₁ ∧ φ₂)) &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip₁~¬ φ₂~n)\\
+\fstrip₁ &(¬ (φ₁ ∨ φ₂)) &(\suc~n) &= \fuh~(\fstrip₁~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~¬ φ₂~n)\\
+\fstrip₁ &(¬ (φ₁ ⇒ φ₂)) &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~¬ φ₂~n)\\
+\fstrip₁ &(¬ ¬ φ₁)      &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n)\\
+\fstrip₁ &(¬ ⊥)         &(\suc~n) &= ⊤\\
+\fstrip₁ &(¬ ⊤)         &(\suc~n) &= ⊥\\
+\fstrip₁ &φ             &\text{n} &= φ
 \end{array}
@@
 
-The function defined above is not a structural recursion function. Therefore, we have reformulated it in~(\ref{eq:strip-fixed}) in order to solve such an issue following the technique described in
-Section~\ref{ssec:structural-recursion}.
+In a similar way as we define $\fuh_{cm}$ in (\ref{eq:uh-complexity}) we define
+$\fstrip_{cm}$ as the complexity measure for $\fstrip₀$ function. As excepted,
+the \fstrip function is defined as follows.
 
-%  1137  git add .
-%  1138  git commit -am "[ paper ] strip proof."
-%  1139  git pull origin paper
-%  1140  git push origin paper
-
-\begin{equation}
-\label{eq:strip-fixed}
-\begin{aligned}
-&\hspace{.495mm}\fstrip : \Prop → \Nat → \Prop\\
-&\begin{array}{llll}
-\fstrip &(φ₁ ∧ φ₂)     &(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
-\fstrip &(φ₁ ∨ φ₂)     &(\suc~n) &= \fuh~(¬ φ₁ ⇒ \fstrip~φ₂~n)\\
-\fstrip &(φ₁ ⇒ φ₂)     &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~φ₂~n)\\
-\fstrip &(¬ (φ₁ ∧ φ₂)) &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip~¬ φ₂~n)\\
-\fstrip &(¬ (φ₁ ∨ φ₂)) &(\suc~n) &= \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)\\
-\fstrip &(¬ (φ₁ ⇒ φ₂)) &(\suc~n) &= \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~¬ φ₂~n)\\
-\fstrip &(¬ ¬ φ₁)      &(\suc~n) &= \fuh~(\fstrip~φ₁~n)\\
-\fstrip &(¬ ⊥)         &(\suc~n) &= ⊤\\
-\fstrip &(¬ ⊤)         &(\suc~n) &= ⊥\\
-\fstrip &φ             &\text{n} &= φ
-\end{array}
-\end{aligned}
-\end{equation}
+\begin{align}
+  \label{eq:strip}
+  \begin{split}
+  &\fstrip : \Prop → \Prop\\
+  &\fstrip~φ~ = \fstrip_{1}~φ~(\fstrip_{cm}~φ).
+  \end{split}
+\end{align}
 
@@
 \label{lem:lem-inv-strip}
-Let $\text{n} : \Nat$ be the complexity measure of the strip function defined
+Let $\text{n} : \Nat$ be the complexity measure of the \fstrip function defined
 in~(\ref{eq:strip-fixed}).
-If $Γ ⊢ \fstrip~φ~n$ then $Γ ⊢ φ$.
+If $Γ ⊢ \fstrip₁~φ~n$ then $Γ ⊢ φ$.
 \end{mainlemma}
@@
   \begin{bprooftree}
- \AxiomC{$Γ ⊢ \fstrip~(¬¬φ₁)~(\suc~n)$}
+ \AxiomC{$Γ ⊢ \fstrip₁~(¬¬φ₁)~(\suc~n)$}
   \RightLabel{by~(\ref{eq:strip-fixed})}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~φ₁~n)$}
   \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
+  \UnaryInfC{$Γ ⊢ \fstrip₁~φ₁~n$}
   \RightLabel{by~ind.~hyp.}
@@
   \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \fstrip~(φ₁ ∧ φ₂)~(\suc~n)$}
+  \AxiomC{$Γ ⊢ \fstrip₁~(φ₁ ∧ φ₂)~(\suc~n)$}
   \RightLabel{by~(\ref{eq:strip-fixed})}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)$}
   \RightLabel{∧-proj₁}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~φ₁~n)$}
   \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ \fstrip~φ₁~n$}
+  \UnaryInfC{$Γ ⊢ \fstrip₁~φ₁~n$}
   \RightLabel{by~ind.~hyp.}
@@
   \UnaryInfC{Γ ⊢ φ₁}
-  \AxiomC{$Γ ⊢ \fstrip~(φ₁ ∧ φ₂)~(\suc~n)$}
+  \AxiomC{$Γ ⊢ \fstrip₁~(φ₁ ∧ φ₂)~(\suc~n)$}
   \RightLabel{by~(\ref{eq:strip-fixed})}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)$}
   \RightLabel{$∧$-proj$₂$}
-  \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip~φ₂~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)$}
   \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip~φ₂~n$}
+  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip₁~φ₂~n$}
   \RightLabel{$⇒$-elim}
-  \BinaryInfC{$Γ ⊢ \fstrip~φ₂~n$}
+  \BinaryInfC{$Γ ⊢ \fstrip₁~φ₂~n$}
   \RightLabel{by~ind.~hyp.}
@@
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ \fstrip~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
+\AxiomC{$Γ ⊢ \fstrip₁~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
 \RightLabel{by~(\ref{eq:strip-fixed})}
-\UnaryInfC{$Γ ⊢ \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)$}
+\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~¬ φ₂~n)$}
 \RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ \fuh~(\fstrip~¬ φ₁~n)$}
+\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~¬ φ₁~n)$}
 \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-\UnaryInfC{$Γ ⊢ \fstrip~¬ φ₁~n$}
+\UnaryInfC{$Γ ⊢ \fstrip₁~¬ φ₁~n$}
 \RightLabel{by~ind.~hyp.}
@@
   \UnaryInfC{$Γ ⊢ ¬ φ₁$}
-  \AxiomC{$Γ ⊢ \fstrip~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
+  \AxiomC{$Γ ⊢ \fstrip₁~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
   \RightLabel{by~(\ref{eq:strip-fixed})}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~¬ φ₂~n)$}
   \RightLabel{∧-proj₂}
-  \UnaryInfC{$Γ ⊢ \fuh~(¬ φ₁ ⇒ \fstrip~¬ φ₂~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~(¬ φ₁ ⇒ \fstrip₁~¬ φ₂~n)$}
   \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip~¬ φ₂~n$}
+  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip₁~¬ φ₂~n$}
   \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ ⊢ \fstrip~¬ φ₂~n$}
+  \BinaryInfC{$Γ ⊢ \fstrip₁~¬ φ₂~n$}
   \RightLabel{by~ind.~hyp.}
@@
 
-Since \Metis proves by refutation,
+Since \Metis proves a conjecture by refutation,
 to prove each subgoal, \Metis assumes the negation of it
-using the \negate rule. Then, this rule is always derived from a \strip
-inference application as we can see in the following \TSTP excerpt.
+using the \negate rule. Then, the \negate rule is
+always derived from a \strip inference application.
+
+\begin{myexample}
+In the following \TSTP derivation, the three subgoal are
+introduced by the \negate rule.
 
@@
 fof(goal, conjecture, (p & r & q)).
-fof(subgoal_0, p, inf(strip,[goal])).
-fof(subgoal_1, p => r, inf(strip,[goal])).
-fof(subgoal_2, (p & r) => q, inf(strip,[goal])).
-fof(negate_0_0, ~ p, inf(negate,[subgoal_0])).
+fof(sg0, p, inf(strip,[goal])).
+fof(sg1, p => r, inf(strip,[goal])).
+fof(sg2, (p & r) => q, inf(strip,[goal])).
+fof(neg0, ~ p, inf(negate,[sg0])).
 ...
-fof(negate_1_0, ~ (p => r), inf(negate,[subgoal_1])).
+fof(neg1, ~ (p => r), inf(negate,[sg1])).
 ...
-fof(negate_2_0, ~ ((p & r) => q), inf(negate,[subgoal_2])).
+fof(neg2, ~ ((p & r) => q), inf(negate,[sg2])).
 \end{verbatim}
+\end{myexample}
 

### 2017-10-24 paper/sections/proof-reconstruction.tex
[ paper ] fixing last suggestions.
[ paper ] fixing refs.

@@
 
-In this section, we reconstruct each \Metis inference rule with a
+In this section, we reconstruct each \Metis inference rule
+in Table~\ref{tab:agda-metis-table} with a
 function and its respective theorem. We present a pattern of the
@@
 \Metis has a inference rule named conjunct.
-Since that rule appears in \TSTP derivations like in the following excerpt.
 We refer to this rule writing \conjunct.
@@
 \subfile{sections/proof-reconstruction/strip.tex}
-\subfile{sections/proof-reconstruction/negate.tex}
 \subfile{sections/proof-reconstruction/conjunct.tex}

### 2017-10-24 paper/sections/conclusions-and-future-work.tex
[ paper ] reorder conclusions with future work.

--- 2017-10-23 paper/sections/conclusions.tex
@@
 
-\section{Conclusions}
+\section{Conclusions and Future Work}
 \label{sec:conclusions}
@@
 We presented a reliable proof-reconstruction in type theory
-for the propositional fragment of the \Metis prover.
+for the propositional fragment of the \Metis prover. We provided for
+each \Metis inference rule a formal description in type theory.
+This formalizations is mainly exposed in
+Section~\ref{ssec:emulating-inferences}.
 
-We built \Athena translator tool written in \Haskell
-to generate \Agda proof-terms of \Metis derivations.
+We built the \Athena translator tool written in \Haskell
+that generates \Agda proof-terms of \Metis derivations.
 \Agda files delivered by this translator imports
 \Agda formalizations of the \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
+We tested successful using this tool and \Agda as we
+described in Section~\ref{sec:proof-reconstruction} over a subset of
+propositional problems from~\cite{Prieto-Cubides2017}.
 
@@
 semantics to extend this work towards the support of first-order logic.
-Recall, satisfiability in first-order logic is undecidable.
+Recall satisfiability in first-order logic is undecidable.
 
-As an early future work, we propose to extend the
-proof-reconstruction presented in this paper to support the
-proposition fragment with equality of \Metis.
-Another option is to extend the proof-reconstruction to support other \ATPs for \CPL like \name{EProver} or \name{Z3}.
-This development can be carried out by following the \name{EProver}
-inference rules described on Kanso's Ph.D. Thesis~\cite{Kanso2012}.
-
-In \Agda, we found the proof-reconstruction proposed by \citeauthor{Kanso2012}
-in~\cite{Kanso2012,kanso2016light}. The author present an approach similar to
-the reasoning presented in Section~\ref{ssec:workflow}.
-Nonetheless, his approach includes semantics reasoning that as we mentioned
-above differs completely from our proof-reconstructing propose.
-
-Summarizing, we provided for each \Metis inference rule a theorem in
-type theory to emulate the rule reasoning. Our approach is mainly
-exposed in Section~\ref{ssec:emulating-inferences}.
-We identify some improvements for our approach that we leave it for future
-work.
-For instance, we can investigate the consequences of removing \clausify
-inference by strengthen \canonicalize rule in Thm.~\ref{thm:canonicalize}
-The \simplify rule is still lacking of some coverage since it is fairly complex its \Metis source code, and many cases could be omitted.
-Other improvements are related with computational efficiency of
-rules that strongly depend on reordering tasks,
-Section~\ref{sssec:reordering}.
-We believe some rules like \canonicalize can get some help by
-performing an analysis with \Athena.
-
+Summarizing,
 One of the main contribution of this study was
@@
 deduction modules). During this research, we had the opportunity
-to improve \Metis by reporting some bugs\footnote{Issues No.~2,
+to contribute to \Metis by reporting some bugs\footnote{Issues No.~2,
 No.~4. and commit \name{8a3f11e} in the \Metis' official repository
@@
 
+\subsection*{Future work}
+
+As an early future work, we propose to extend the
+proof-reconstruction presented in this paper to support the
+proposition fragment with equality of \Metis.
+Another option is to extend the proof-reconstruction to support other \ATPs for \CPL like \name{EProver} or \name{Z3}.
+This development can be carried out by following the \name{EProver}
+inference rules described on Kanso's Ph.D. thesis~\cite{Kanso2012}.
+
+We identify some improvements for our approach in
+Section~\ref{ssec:emulating-inferences}.
+For instance, we can investigate the consequences of removing \clausify
+inference by strengthen \canonicalize rule in Theorem~\ref{thm:canonicalize}
+The \simplify rule is still lacking of some coverage since it is fairly
+complex in its implementation in the \Metis source code,
+and many cases could be omitted.
+Other improvements are related with computational efficiency of
+rules that strongly depend on reordering tasks,
+Section~\ref{sssec:resolve}.
+We believe some rules like \canonicalize can get some help by
+performing an analysis with \Athena.
+
 \end{document}

### 2017-10-24 paper/sections/related-work.tex
[ paper ] reorder conclusions with future work.

@@
 \label{sec:related-work}
+
+In \Agda, we found the proof-reconstruction proposed by \citeauthor{Kanso2012}
+in~\cite{Kanso2012,kanso2016light}. The author present an approach similar to
+the reasoning presented in Section~\ref{ssec:workflow}.
+Nonetheless, his approach includes semantics reasoning that as we mentioned
+above differs completely from our proof-reconstructing propose.
 

### 2017-10-24 paper/sections/acknowledgements.tex
[ paper ] future work.

@@
 
-I would like to thank to Universidad EAFIT in Medell\'in, Colombia for funding
-support of this research and my master studies.
+Research on this paper was fully supported by Universidad EAFIT in Medellín,
+Colombia. I would like to thank for this funding and its support for
+my master studies.
 This project was a product of the Logic and Computation
@@
 G\'omez-Londo\~no~\cite{Gomez-Londono2015} used as the basis
-for our \TSTP parsing module.
+for our \TSTP parsing module in~\cite{Athena}.
 
@@
 inviting me to be part of the \Agda Implementors’ Meeting XXV.
-I was honored to present there part of this research.
+I was honored to present part of this research in the meeting.
 

### 2017-10-24 paper/sections/conclusions-and-future-work.tex
[ paper ] future work.

@@
 Nevertheless, we chose that syntactical treatment instead of using
-semantics to extend this work towards the support of first-order logic.
-Recall satisfiability in first-order logic is undecidable.
+semantics to extend this work towards the support of first-order logic
+or other non-classical logics.
+For predicative logic, recall satisfiability is undecidable and
+its syntactical aspect plays a important role to reconstruct proofs.
 
-Summarizing,
 One of the main contribution of this study was
@@
 
-As an early future work, we propose to extend the
-proof-reconstruction presented in this paper to support the
-proposition fragment with equality of \Metis.
-Another option is to extend the proof-reconstruction to support other \ATPs for \CPL like \name{EProver} or \name{Z3}.
+Further research  directions include, but are not limited to:
+
+\begin{itemize}
+\item extend the proof-reconstruction presented in this paper to
+  \begin{itemize}
+    \item support the proposition fragment with equality of \Metis.
+    \item support other \ATPs for \CPL like \name{EProver} or \name{Z3}.
+    \item support \Metis first order proofs.
 This development can be carried out by following the \name{EProver}
 inference rules described on Kanso's Ph.D. thesis~\cite{Kanso2012}.
+  \end{itemize}
+\item contrasts the use of a shallow embedding instead
+of the deep embedding implemented in~\cite{AgdaProp}.
+\item improve some functions in Section~\ref{ssec:emulating-inferences}
+\begin{itemize}
+  \item by investigating the consequences of removing \clausify
+inference by strengthen \canonicalize rule in Theorem~\ref{thm:canonicalize}
+  \item by increasing the coverage of the \simplify rule. Since is fairly
+complex its implementation in the \Metis source code, some cases could be omitted in Section~\ref{sssec:simplify}.
+\end{itemize}
 
-We identify some improvements for our approach in
-Section~\ref{ssec:emulating-inferences}.
-For instance, we can investigate the consequences of removing \clausify
-inference by strengthen \canonicalize rule in Theorem~\ref{thm:canonicalize}
-The \simplify rule is still lacking of some coverage since it is fairly
-complex in its implementation in the \Metis source code,
-and many cases could be omitted.
-Other improvements are related with computational efficiency of
-rules that strongly depend on reordering tasks,
-Section~\ref{sssec:resolve}.
-We believe some rules like \canonicalize can get some help by
-performing an analysis with \Athena.
+% For instance, we can
 
+% and many cases could be omitted.
+% Other improvements are related with computational efficiency of
+% rules that strongly depend on reordering tasks,
+% Section~\ref{sssec:resolve}.
+% We believe some rules like \canonicalize can get some help by
+% performing an analysis with \Athena.
+\end{itemize}
 \end{document}

### 2017-10-24 paper/sections/introduction.tex
'.
[ paper ] last changes.
[ paper ] some messages added.
[ paper ] none inspiration .. :S

@@
 
-\section{Introduction}
+\section{Introduction (ESCRIBIENDO)}
 \label{sec:introduction}
 
-% Proof-reconstruction is a non-trivial task since it depends on the
-% integration between two complex systems.
-% We describe one proof-reconstruction approach between an automatic theorem
-% prover (henceforth \ATP) and an interactive theorem prover (henceforth
+disciplina
+en el tiempo
+hilighting an import
+
+The main challenge faced of reconstrucing proofs
+
+the main disadavantage of X
+
+One of the main obstacles to reconstruct proofs generated by
+automatic provers consists of ...
+
+However,
+
+The performance of X is limited by ...
+
+synopsys
+
+Previous studies have reported proof-reconstruction for
+
+Existing research recognizes the critical role by ...
+
+What we known about X is largely based on ....
+
+Few published studied have examined the role of
+
+focus on a full description of the inference rules in the ATP logic.
+
+No previous studies has given sufficient considerations to ...
+
+This paper describes the design and implementation of X...
+
+This study provides new insights into the automatic reasoning of \Metis prover.
+Understanding the link between the ATP and ITP will help xxxx
+
+The reader should bear in mind that the study is based on
+reverse engineering.
+
+DECIR QUE ES NOVEDOSO EN AGDA Y Q NO ESTA HECHO EN TEORIA DE TIPOS
+SYNTATICA VS SEMANTICA.
+APPLICACIONES
+
+% We describe how to reconstruct proofs delivered by an automatic theorem prover
+% (henceforth \ATP)
+% and an interactive theorem prover (henceforth
 % \ITP).
 
-% The \ITP tools provide us the
-% logic framework to check and validate the reply of the \ATPs since
-% they allow us to define the formal language for the problems i.e.,
-% operators, logic variables, axioms, and theorems.
+% One way to reconstruct proofs of \ATPs consists of using an \ITP.
+% An \ITP system provide us the logic framework to check and validate
+% the reply of the \ATPs since they allow us to define the formal language
+ % for the problems \ie, operators, logic variables, axioms, and theorems.
+
+% This task is non-trivial since it depends on the
+% integration between two complex systems.
 
@@
 
-% Many approaches have been proposed and some tools have been
-% implemented for proof-reconstruction in the last decades. These
+ These
 % programs are relevant not only because it helps to spread their
@@
 
-% In this paper, we ported a subset of the \Metis' inference rules to
-% \Agda, the propositional fragmented. The formalization of
-% these rules allowed us to justify step-by-step \Metis' \TSTP derivations by
-% translating automatically to \Agda by a proof-reconstruction tool built for
-% this research named \Athena.
-% This paper has been organized in the following way.
-% In Section~\ref{ssec:CPL}, we introduce some
-% notation and syntax of propositional logic.
-% In Section~\ref{sec:metis-language-and-proofs}, we introduce the
-% \Metis prover and its deduction system.
-% In Section~\ref{sec:proof-reconstruction}, we present our
-% approach to reconstruct proofs deliver by \Metis in type theory.
-% Section~\ref{sec:conclusions} summarizes the main findings and includes a
-% discussion of future work.
-% Some related works to this paper are presented in Section~\ref{sec:related-work}.
+The recontruction of  proof can play an important role in addressing a issue
+of ...
+Moreover, verification is fast becoming a key instrument in automatic reasoning.
+
+The type theory provides a useful account of how ...
+
+No previous study has investigated to reconstruct proofs using a syntactical approach
+in \Agda for any \ATPs.
+
+In this paper, we ported a subset of the \Metis inference rules to
+\Agda, the propositional fragmented. The formalization of
+these rules allowed us to justify step-by-step \Metis derivations by
+translating automatically to \Agda by a the \Athena tool.
+
+This paper has been organized in the following way.
+We mention in Section~\ref{sec:limitations-type-theory}
+some limitations of the proof-reconstruction from the type theory
+point of view. In Section~\ref{sec:metis-language-and-proofs}, we introduce the
+\Metis prover and its deduction system.
+In Section~\ref{sec:proof-reconstruction}, we show our
+approach to reconstruct proofs deliver by \Metis.
+Related work is described in Section~\ref{sec:related-work}.
+Section~\ref{sec:conclusions} summarizes the main findings and suggest future work.
+
 % Finally, in appendix \textsc{A}, we provide a small example of the

### 2017-10-24 paper/sections/metis-language-and-proofs.tex
[ paper ] fixing refs.
[ paper ] none inspiration .. :S

@@
 
+We note a lack of clarity in defining the differences between the rules used in \TSTP derivations and the rules described on the documentation in
+the Metis description~\cite{hurd2003first}.
+These rules are not the same as we expected from the Fig.~\ref{fig:metis-inferences}.
+
+AGREGAR el sitio de metis official.!!
+
 % \Metis looks for a refutation to prove \verb!fof! problems.
@@
 \begin{table}[!ht]
-\label{tab:agda-metis-table}
+
 \caption{\Metis inference rules.}
@@
   {\renewcommand{\arraystretch}{1.6}%
+    \label{tab:agda-metis-table}
     \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}

### 2017-10-24 paper/sections/proof-reconstruction/strip.tex
[ paper ] none inspiration .. :S

@@
 in (\ref{eq:strip-example}).
-Besides the fact \Metis does not explicit in \TSTP derivation
-how it uses the proofs of subgoals, we know using the elimination
-of the implication, we get the proof of the conjecture.
+So far, very little attention has been paid to the role of \strip rule.
+in \TSTP derivation since \Metis does not make explicit the way
+it uses the subgoals to prove the conjecture.
 \end{myexample}

### 2017-10-24 paper/sections/introduction.tex
[ paper ] some text added.

@@
 
-disciplina
-en el tiempo
-hilighting an import
+% During the last decades, the research field of automated reasoning has been experimenting a growth in the development of new methods, tools, and systems.
+One of the major achievements of this field are the automatic
+% theorem provers (henceforth ATPs).
 
-The main challenge faced of reconstrucing proofs
+% At the beginning in its development, the main goal was prove automatically
+% problems in different logics (\eg, first-order logic, high-order logic).
+% Nowadays, they continuing extending its support, performance and precision
+% in their deductive methods. To guarantee the validity of their methods,
+% many ATPs has been opted to include proofs in their output.
+% Nevertheless, it has been argued that some of their deductions are not
+% valid even in delivering a proof. One of the reason to say that is
+% the discover of bugs in ATPs that outputs unsound proofs.
 
-the main disadavantage of X
+% This problem to verify proofs delivered by ATPs is a non-trivial task
+% and involves an in-depth understanding of the algorithms in the \ATP.
 
-One of the main obstacles to reconstruct proofs generated by
-automatic provers consists of ...
+% The proof-reconstruction problem aim to solve this issue.
+% One way to address this problem is using another major system in this field, the proof assistants.
 
-However,
+% A proof-reconstruction tool using this approach will try to verify the proof delivered by the ATP using the proof assistant.
 
-The performance of X is limited by ...
+% In this paper, we purpose one of such proof-reconstruction tools.
+% Our approach describes the design and implementation to reconstruct
+% proofs of the \Metis prover into a proof assistant for type theory like
+% \Agda. We use type theory to guarantee that proofs of the \ATP are valid.
 
-synopsys
+% To begin with the proof-reconstruction, it is
+% necessary to have a proof from the \ATP in a consistent
+% format, that is, a full script describing step-by-step
+% with exhaustive details and without ambiguities, the derivation to
+% get the that proof. But this is a strong requirement and its the main obstacle we found with \Metis proofs.
+% The reader should bear in mind that the study is based on
+% reverse engineering about \Metis.
 
-Previous studies have reported proof-reconstruction for
+% The main disadvantage of X
 
-Existing research recognizes the critical role by ...
+% One of the main obstacles to reconstruct proof generated by this tools
+% are their
 
-What we known about X is largely based on ....
+% One of the main obstacles to reconstruct proofs generated by
+% automatic provers consists of ...
 
-Few published studied have examined the role of
+% However,
 
-focus on a full description of the inference rules in the ATP logic.
+% The performance of X is limited by ...
 
-No previous studies has given sufficient considerations to ...
+% synopsys
 
-This paper describes the design and implementation of X...
+% Previous studies have reported proof-reconstruction for
 
-This study provides new insights into the automatic reasoning of \Metis prover.
-Understanding the link between the ATP and ITP will help xxxx
+% Existing research recognizes the critical role by ...
 
-The reader should bear in mind that the study is based on
-reverse engineering.
+% What we known about X is largely based on ....
 
-DECIR QUE ES NOVEDOSO EN AGDA Y Q NO ESTA HECHO EN TEORIA DE TIPOS
-SYNTATICA VS SEMANTICA.
-APPLICACIONES
+% Few published studied have examined the role of
+
+% focus on a full description of the inference rules in the ATP logic.
+
+% No previous studies has given sufficient considerations to ...
+
+% This paper describes the design and implementation of X...
+
+% This study provides new insights into the automatic reasoning of \Metis prover.
+% Understanding the link between the ATP and ITP will help xxxx
+
+% DECIR QUE ES NOVEDOSO EN AGDA Y Q NO ESTA HECHO EN TEORIA DE TIPOS
+% SYNTATICA VS SEMANTICA.
+% APPLICACIONES
 
@@
 
-The recontruction of  proof can play an important role in addressing a issue
-of ...
-Moreover, verification is fast becoming a key instrument in automatic reasoning.
+% The recontruction of  proof can play an important role in addressing a issue
+% of ...
+% Moreover, verification is fast becoming a key instrument in automatic reasoning.
 
-The type theory provides a useful account of how ...
+% The type theory provides a useful account of how ...
 
-No previous study has investigated to reconstruct proofs using a syntactical approach
-in \Agda for any \ATPs.
+% No previous study has investigated to reconstruct proofs using a syntactical approach
+% in \Agda for any \ATPs.
 

### 2017-10-24 paper/sections/conclusions-and-future-work.tex
[ paper ] none inspiration .. :S
[ paper ] two first paragraphs in the introduction.

@@
     \item support the proposition fragment with equality of \Metis.
-    \item support other \ATPs for \CPL like \name{EProver} or \name{Z3}.
+    \item support other \ATPs for propositional logic like \name{EProver} or \name{Z3}.This development can be carried out by following the \name{EProver}
+description on Kanso's Ph.D. thesis~\cite{Kanso2012}.
     \item support \Metis first order proofs.
-This development can be carried out by following the \name{EProver}
-inference rules described on Kanso's Ph.D. thesis~\cite{Kanso2012}.
+
   \end{itemize}
-\item contrasts the use of a shallow embedding instead
-of the deep embedding implemented in~\cite{AgdaProp}.
+\item contrasts a shallow embedding instead
+of the deep embedding implemented in~\cite{AgdaProp} to reconstruct proofs.
 \item improve some functions in Section~\ref{ssec:emulating-inferences}

### 2017-10-24 paper/sections/introduction.tex
[ paper ] two first paragraphs in the introduction.

@@
 
-% During the last decades, the research field of automated reasoning has been experimenting a growth in the development of new methods, tools, and systems.
+Reconstructing and verifying proofs delivered by automatic theorem provers
+(henceforth ATP) are non-trivial tasks.
+In the last decades, \ATPs is fast becoming a key instrument in 
+different disciplines (\eg verifying cryptographic protocols for information security) and researchers have shown an increased interest to prove the validity of the deduction algorithms.
+One reason to say that are the bugs found in many ATPs.
+For that reason, in order to give confidence to the user of these systems,
+many ATPs has started to include in their outputs, the proofs of the
+conclusion. However, existing research recognizes that in many cases these proofs encode non-trivial reasoning
+hard to reconstruct them and therefore to verify them.
+
+Hence proof-reconstructing becomes a reverse engineering task
+in which the source, the proof, and its quality play an important role.
+To begin with the proof-reconstruction, it is necessary to have
+the proof of the \ATP in a consistent format, that is, a full script 
+describing step-by-step with exhaustive details and without ambiguities, the 
+derivation to get the actual proof.  
+For classical propositional logic (henceforth \CPL), from a list of at least forty\footnote{\ATPs 
+available from the web
+service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
+provers were able to deliver proofs and fewer like \name{EProver} or \Metis 
+replied the proof in an admissible file format.
+
+-----
+
+% One approach to address the problem mentioned above
+% consists of use a proof assistant as the proof checker.
+% In this direction, we describe the usage of a proof assistant in type theory
+% to reconstruct proofs delivered by \Metis prover.
+
+% To guarantee the validity of their methods,
+% many ATPs has been opted to include proofs in their output.
+
+% The problem address in this paper concern about justifying such proofs.
+
+% One approach to address  these tasks could be use a proof assistant
+% to verify the reply of the ATP.
+
+% % During the last decades, the research field of automated reasoning has been experimenting a growth in the development of new methods, tools, and systems.
 One of the major achievements of this field are the automatic
-% theorem provers (henceforth ATPs).
+% % theorem provers (henceforth ATPs).
 
@@
 % Nowadays, they continuing extending its support, performance and precision
-% in their deductive methods. To guarantee the validity of their methods,
-% many ATPs has been opted to include proofs in their output.
+% in their deductive methods.
+
 % Nevertheless, it has been argued that some of their deductions are not
-% valid even in delivering a proof. One of the reason to say that is
-% the discover of bugs in ATPs that outputs unsound proofs.
+% valid even in delivering a proof.
 
@@
 % and involves an in-depth understanding of the algorithms in the \ATP.
+% The proof-reconstruction is a non-trivial problem.
 
-% The proof-reconstruction problem aim to solve this issue.
+% The proof-reconstruction is a non-trivial task since it depends on the
+% integration between two complex systems.
+
+% The proof-reconstruction problem aims to solve this issue.
 % One way to address this problem is using another major system in this field, the proof assistants.
@@
 % \Agda. We use type theory to guarantee that proofs of the \ATP are valid.
-
-% To begin with the proof-reconstruction, it is
-% necessary to have a proof from the \ATP in a consistent
-% format, that is, a full script describing step-by-step
-% with exhaustive details and without ambiguities, the derivation to
-% get the that proof. But this is a strong requirement and its the main obstacle we found with \Metis proofs.
-% The reader should bear in mind that the study is based on
-% reverse engineering about \Metis.
 
@@
 
-% This task is non-trivial since it depends on the
-% integration between two complex systems.
-
 % A proof-reconstruction tool provides such an integration, translating
@@
 
-% % Since the formalism of the source (the evidence
-% % generated by the \ATP) is not necessarily the same logic in the
-% % target, the reconstruction turns out to be a ``reverse engineering''
-% % task.
+% Since the formalism of the source (the evidence
+% generated by the \ATP) is not necessarily the same logic in the
+% target, the reconstruction turns out to be a ``reverse engineering''
+% task.
 
@@
 
- These
+%  These
 % programs are relevant not only because it helps to spread their

### 2017-10-24 paper/sections/introduction.tex
[ paper ] add the third paragraph in the introduction.

@@
 
------
-
-% One approach to address the problem mentioned above
-% consists of use a proof assistant as the proof checker.
-% In this direction, we describe the usage of a proof assistant in type theory
-% to reconstruct proofs delivered by \Metis prover.
+One approach to address the proof-reconstruction 
+is integrating the \ATP, the \emph{source} system, with a proof assistant, the \emph{target} system.
+The target system becomes in the proof checker.   
+Previous studies have reported proof-reconstruction using proof assistant for classical logic where the development is at a mature stage.
+In contrast, we choose a proof assistant for type theory
+where proof verification becomes a type-checking task of the
+proof-term following the Curry-Howard isomorphism.
 
@@
 
-% Previous studies have reported proof-reconstruction for
+%
 

### 2017-10-24 paper/sections/introduction.tex
[ paper ] added the fourth paragraph in the introduction.

@@
 different disciplines (\eg verifying cryptographic protocols for information security) and researchers have shown an increased interest to prove the validity of the deduction algorithms.
-One reason to say that are the bugs found in many ATPs.
+One reason to say that is the bugs found in many ATPs~\cite{Keller2013,Bohme2011,Fleury2014}.
 For that reason, in order to give confidence to the user of these systems,
@@
 One approach to address the proof-reconstruction 
-is integrating the \ATP, the \emph{source} system, with a proof assistant, the \emph{target} system.
-The target system becomes in the proof checker.   
-Previous studies have reported proof-reconstruction using proof assistant for classical logic where the development is at a mature stage.
+is integrating the \ATP, the \emph{source} system, with a proof assistant, the 
+\emph{target} system.
+The target system becomes in the proof checker. These proof assistants allow 
+us to define the formal language used in the proofs, \ie, operators, logic 
+variables, axioms, and theorems. A proof-reconstruction tool provides such an
+integration, translating the replied generated by the prover into the formalism of the proof assistant.
+
+Previous studies have reported proof-reconstruction using proof assistants for classical logic where the development is at a mature stage.
 In contrast, we choose a proof assistant for type theory
-where proof verification becomes a type-checking task of the
-proof-term following the Curry-Howard isomorphism.
+where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.
+Then, the proof-reconstruction generates such proof-terms by reconstructing the proof replied by the \ATP.
+However, some limitations arises by using type theory as we describe in Section~\ref{sec:limitations-type-theory}.
 
-% To guarantee the validity of their methods,
-% many ATPs has been opted to include proofs in their output.
-
-% The problem address in this paper concern about justifying such proofs.
-
-% One approach to address  these tasks could be use a proof assistant
-% to verify the reply of the ATP.
-
-% % During the last decades, the research field of automated reasoning has been experimenting a growth in the development of new methods, tools, and systems.
-One of the major achievements of this field are the automatic
-% % theorem provers (henceforth ATPs).
-
-% At the beginning in its development, the main goal was prove automatically
-% problems in different logics (\eg, first-order logic, high-order logic).
-% Nowadays, they continuing extending its support, performance and precision
-% in their deductive methods.
-
-% Nevertheless, it has been argued that some of their deductions are not
-% valid even in delivering a proof.
-
-% This problem to verify proofs delivered by ATPs is a non-trivial task
-% and involves an in-depth understanding of the algorithms in the \ATP.
-% The proof-reconstruction is a non-trivial problem.
-
-% The proof-reconstruction is a non-trivial task since it depends on the
-% integration between two complex systems.
+In this paper, we describe how to reconstruct proofs in type theory
+replied by \Metis Prover\footnote{v2.3 release 2017102}.
+We ported the subset of the \Metis inference rules for the propositional 
+fragment using a syntactical treatment of that logic. The \Metis reasoning was formalized in \Agda~\cite{AgdaProp,AgdaMetis}. 
+to reconstruct \Metis proofs, we built a proof-reconstruction tool named
+\Athena~\cite{Athena} that is able to generate \Agda\footnote{v2.5.3} proof-terms for \Metis derivations.
+We have avoided the use of propositions meanings towards a future work to support other formalisms.
+% but also to contrast the deep embedding using to write propositions in \Agda 
+% with a shallow embedding.
 
@@
 % An \ITP system provide us the logic framework to check and validate
-% the reply of the \ATPs since they allow us to define the formal language
-%  for the problems \ie, operators, logic variables, axioms, and theorems.
+% the reply of the \ATPs since
 
@@
 % assistant.
-
-% Since the formalism of the source (the evidence
-% generated by the \ATP) is not necessarily the same logic in the
-% target, the reconstruction turns out to be a ``reverse engineering''
-% task.
 
@@
 
-% The recontruction of  proof can play an important role in addressing a issue
-% of ...
-% Moreover, verification is fast becoming a key instrument in automatic reasoning.
+In this paper,
 
-% The type theory provides a useful account of how ...
-
-% No previous study has investigated to reconstruct proofs using a syntactical approach
-% in \Agda for any \ATPs.
-
-In this paper, we ported a subset of the \Metis inference rules to
-\Agda, the propositional fragmented. The formalization of
-these rules allowed us to justify step-by-step \Metis derivations by
-translating automatically to \Agda by a the \Athena tool.
+The formalization of these rules allow us to justify step-by-step \Metis derivations. We implemented this formalization in \Agda and we built
+a translator tool, \Athena, to generate automatically the proof-terms
+from \Metis proofs.
 

### 2017-10-24 paper/sections/introduction.tex
[ paper ] fixed some text in intro.

@@
 
-\section{Introduction (ESCRIBIENDO)}
+\section{Introduction}
 \label{sec:introduction}
@@
 In the last decades, \ATPs is fast becoming a key instrument in 
-different disciplines (\eg verifying cryptographic protocols for information security) and researchers have shown an increased interest to prove the validity of the deduction algorithms.
+different disciplines (\eg~verifying cryptographic protocols for information security) and researchers have shown an increased interest to prove the validity of their deduction algorithms.
 One reason to say that is the bugs found in many ATPs~\cite{Keller2013,Bohme2011,Fleury2014}.
 For that reason, in order to give confidence to the user of these systems,
-many ATPs has started to include in their outputs, the proofs of the
-conclusion. However, existing research recognizes that in many cases these proofs encode non-trivial reasoning
-hard to reconstruct them and therefore to verify them.
+many ATPs has started to include in their outputs, the proof of their
+conclusions. However, existing research recognizes that in many cases these proofs encode non-trivial reasoning
+hard to reconstruct and therefore hard to verify. The proof-reconstruction
+address this problem and becomes in some cases a reverse engineering of the
+prover reasoning.
 
-Hence proof-reconstructing becomes a reverse engineering task
-in which the source, the proof, and its quality play an important role.
-To begin with the proof-reconstruction, it is necessary to have
-the proof of the \ATP in a consistent format, that is, a full script 
-describing step-by-step with exhaustive details and without ambiguities, the 
-derivation to get the actual proof.  
-For classical propositional logic (henceforth \CPL), from a list of at least forty\footnote{\ATPs 
+Therefore, the proof replied by the prover and its quality play an important role for proof-reconstruction. To verify such a proof, it is necessary to have
+it in a consistent format, that is, a full script 
+describing step-by-step with exhaustive details and without ambiguities, the derivation to get the proof.
+For classical propositional logic (henceforth \CPL) from a list of at least forty\footnote{\ATPs 
 available from the web
@@
 Previous studies have reported proof-reconstruction using proof assistants for classical logic where the development is at a mature stage.
-In contrast, we choose a proof assistant for type theory
+Even though we choose a proof assistant for type theory
 where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.

### 2017-10-24 paper/sections/introduction.tex
[ paper ] fixing intro.

@@
 where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.
-Then, the proof-reconstruction generates such proof-terms by reconstructing the proof replied by the \ATP.
-However, some limitations arises by using type theory as we describe in Section~\ref{sec:limitations-type-theory}.
+Therefore the proof-reconstruction tool generates proof-terms by reconstructing the proof using the formalization
+the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:limitations-type-theory}.
 
 In this paper, we describe how to reconstruct proofs in type theory
-replied by \Metis Prover\footnote{v2.3 release 2017102}.
+replied by \Metis prover\footnote{v2.3 release 2017102}.
 We ported the subset of the \Metis inference rules for the propositional 
-fragment using a syntactical treatment of that logic. The \Metis reasoning was formalized in \Agda~\cite{AgdaProp,AgdaMetis}. 
-to reconstruct \Metis proofs, we built a proof-reconstruction tool named
-\Athena~\cite{Athena} that is able to generate \Agda\footnote{v2.5.3} proof-terms for \Metis derivations.
-We have avoided the use of propositions meanings towards a future work to support other formalisms.
-% but also to contrast the deep embedding using to write propositions in \Agda 
-% with a shallow embedding.
-
-% The proof-reconstruction problem aims to solve this issue.
-% One way to address this problem is using another major system in this field, the proof assistants.
-
-% A proof-reconstruction tool using this approach will try to verify the proof delivered by the ATP using the proof assistant.
-
-% In this paper, we purpose one of such proof-reconstruction tools.
-% Our approach describes the design and implementation to reconstruct
-% proofs of the \Metis prover into a proof assistant for type theory like
-% \Agda. We use type theory to guarantee that proofs of the \ATP are valid.
-
-% The main disadvantage of X
-
-% One of the main obstacles to reconstruct proof generated by this tools
-% are their
-
-% One of the main obstacles to reconstruct proofs generated by
-% automatic provers consists of ...
-
-% However,
-
-% The performance of X is limited by ...
-
-% synopsys
-
-%
-
-% Existing research recognizes the critical role by ...
-
-% What we known about X is largely based on ....
-
-% Few published studied have examined the role of
-
-% focus on a full description of the inference rules in the ATP logic.
-
-% No previous studies has given sufficient considerations to ...
-
-% This paper describes the design and implementation of X...
-
-% This study provides new insights into the automatic reasoning of \Metis prover.
-% Understanding the link between the ATP and ITP will help xxxx
-
-% DECIR QUE ES NOVEDOSO EN AGDA Y Q NO ESTA HECHO EN TEORIA DE TIPOS
-% SYNTATICA VS SEMANTICA.
-% APPLICACIONES
-
-% We describe how to reconstruct proofs delivered by an automatic theorem prover
-% (henceforth \ATP)
-% and an interactive theorem prover (henceforth
-% \ITP).
-
-% One way to reconstruct proofs of \ATPs consists of using an \ITP.
-% An \ITP system provide us the logic framework to check and validate
-% the reply of the \ATPs since
-
-% A proof-reconstruction tool provides such an integration, translating
-% the reply generated by the prover into the formalism of the proof
-% assistant.
-
-% Then, reconstructing a proof involves an in-depth
-% understanding of the algorithms in the \ATP and the logic specification
-% in the \ITP. To begin with the proof-reconstruction, it is
-% necessary to have a proof from the \ATP in a consistent
-% format, that is, a full script describing step-by-step
-% with exhaustive details and without ambiguities, the derivation to
-% get the actual proof.
-
-% For problems in classical propositional logic (henceforth \CPL),
-% from a list of at least forty\footnote{\ATPs available from the web
-% service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
-% provers were able to deliver proofs (e.g.,
-% \name{CVC4}~\cite{Barrett2011}, \name{SPASS}, and
-% \name{Waldmeister}~\cite{hillenbrand1997}) and fewer replied with
-% a proof
-% in a file format like \TSTP~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}
-% (e.g., \name{E}, \Metis, \name{Vampire}, and \name{Z3}),
-% \len{LFSC}~\cite{Stump2008}, or the \len{SMT-LIB}~\cite{Bohme2011} format.
-
-%  These
-% programs are relevant not only because it helps to spread their
-% usage but they also increase the confidence of their users about
-% their algorithms and their correctness (see, for example, bugs in
-% \ATPs~\cite{Keller2013,Bohme2011,Fleury2014} and
-% \cite{Kanso2012}).
-% We mention some of these tools in Section~\ref{sec:related-work}.
-
-In this paper,
-
-The formalization of these rules allow us to justify step-by-step \Metis derivations. We implemented this formalization in \Agda and we built
-a translator tool, \Athena, to generate automatically the proof-terms
-from \Metis proofs.
+fragment using a syntactical treatment of the logic.
+The \Metis reasoning was formalized in \Agda in~\cite{AgdaProp,AgdaMetis}.
+We built a proof-reconstruction tool named \Athena~\cite{Athena} that is able to generate \Agda\footnote{v2.5.3} proof-terms for \Metis derivations.
+We have avoided the use of propositions meanings towards a future work to support other logics
+but also contrast the usage of a deep embedding of the logic with
+a shallow embedding.
 
 This paper has been organized in the following way.
-We mention in Section~\ref{sec:limitations-type-theory}
-some limitations of the proof-reconstruction from the type theory
-point of view. In Section~\ref{sec:metis-language-and-proofs}, we introduce the
+In Section~\ref{sec:limitations-type-theory} some limitations of type theory
+are discussed for proof-reconstruction point view.
+In Section~\ref{sec:metis-language-and-proofs}, we introduce the
 \Metis prover and its deduction system.
@@
 Related work is described in Section~\ref{sec:related-work}.
-Section~\ref{sec:conclusions} summarizes the main findings and suggest future work.
+Main findings and suggestion for future work is presented Section~\ref{sec:conclusions}.
 

### 2017-10-24 paper/sections/related-work.tex
[ paper ] none inspiration .. :S
[ paper ] related work, first review.

--- 2017-10-23 paper/sections/related-work.tex
@@
 
-Let us mention a list of some representative of such tools mainly based on the
-description by \citeauthor{Sicard-Ramirez2016}~\cite{Sicard-Ramirez2016}.
+% EJEMPLOS DE RECONSTRUCTION DE PRUEBAS USANDO IPTS EN TEORIA DE TIPOS PARA
+% ATPS.
+
+% AGDA
+% COQ
+
+% Otros: HOL
+
+Many approaches have been proposed for proof-reconstruction and some tools have been
+implemented in the last decades.
+
+In type theory, for \Agda and  for the same propositional fragmented used in this paper,
+we found the proof-reconstruction proposed by \citeauthor{Kanso2012}
+in~\cite{Kanso2012,kanso2016light}. The author present an approach similar to
+the reasoning presented in Section~\ref{ssec:workflow}.
+Nonetheless, his approach includes semantics reasoning that as we mentioned
+in the introduction differs completely from our proof-reconstruction approach.
+
+In \Agda but with another logic, \citeauthor{foster2011integrating}~\cite{foster2011integrating}
+describe the proof-reconstruction for \name{Waldmeister}~\cite{hillenbrand1997}
+prover to pure equational logic, \ie,
+first-order logic with equality but no other predicate symbols and no
+functions symbols.
+
+In \name{Coq}~\cite{coqteam}, and proof assistant for type theory like \Agda, 
+we found the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a
+certified checker for proof witness coming from the \SMT solver
+\name{veriT}~\cite{bouton2009} and adds a new tactic named verit,
+that calls \name{veriT} on any \name{Coq} goal.
+Also for \name{Coq}, 
+given a fixed but arbitrary first-order signature,
+\citeauthor{Bezem2002} in \cite{Bezem2002}
+transform a proof produced by the first-order automatic theorem
+prover \name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof
+term.
+
+We found many successful attemps using proof assistant for classical logic
+instead of type theory.
+Let us mention some representative of such tools. This descriptions is
+mainly based on~\citeauthor{Sicard-Ramirez2016}~\cite{Sicard-Ramirez2016}.
 
@@
 This program provides a full integration between
-automatic theorem provers~\cite{meng2006automation,blanchette2013extending,Fleury2014,hurlin07practical,bohme2010,blanchette2013extending} and
+automatic theorem provers~\cite{blanchette2013extending,Fleury2014,bohme2010} and
 \name{Isabelle/HOL}~\cite{nipkow2002isabelle}, the specialization of
@@
 \name{Isabelle/HOL} in \citeauthor{Een2004}~\cite{Een2004}.
-
-\name{SMTCoq}~\cite{armand2011,Ekici2017} is a tool for the
-\name{Coq} proof assistant \cite{coqteam} which provides a certified
-checker for proof witness coming from the \SMT solver
-\name{veriT}~\cite{bouton2009} and adds a new tactic named verit,
-that calls \name{veriT} on any \name{Coq} goal.
-In \cite{Bezem2002},
-given a fixed but arbitrary first-order signature, the authors
-transform a proof produced by the first-order automatic theorem
-prover \name{Bliksem} \cite{deNivelle2003} in a \name{Coq} proof
-term.
 
@@
 
-For the proof assistant \Agda, we found two proof-reconstruction tools.
-First, the integration with the \name{Waldmeister}~\cite{hillenbrand1997}
-prover by \citeauthor{foster2011integrating}~\cite{foster2011integrating}.
-A prover for pure equational logic, i.e.
-first-order logic with equality but no other predicate symbols and no
-functions symbols.
-Second, Kanso and Setzer in~\cite{kanso2016light} integrate the propositional
-fragment of the \name{EProver}. The tool presented by the authors
-translate automatically propositional logic problems written in \Agda
-to \TPTP problems. By calling an external wrapper of the \ATP, this
-tool gets a \TSTP derivation. The tool parses the \name{EProver}
-derivation and outputs \Agda code.
-
 \end{document}

### 2017-10-24 paper/sections/limitations-type-theory.tex
[ paper ] some messages added.
[ paper ] canon ==> simplify-and simplify-or.
[ paper ] none inspiration .. :S
[ paper ] minor fixes.
[ paper ] addind some text to section 2.

@@
 
-AGREGAR TEXTO INTRODUCTORIO
+% In Section~\label{ssec:structural-recursion},
+% we describe how this observation is an issue from the type theory point of
+% view. In Section~\ref{ssec:intuitionistic-logic} we mention
+% the use intuitionistic-logic and its limitation.
 
@@
 \end{notation}
+
 % ...................................................................
@@
 recursive} functions.
+
 Algorithms based on general recursions can not be translated
@@
 
-\begin{equation*}
+\begin{equation}
+  \label{eq:uh-complexity}
   \begin{aligned}
@@
   \end{aligned}
-\end{equation*}
+\end{equation}
 
@@
 
-\subsection{Intuitionistic logic}
-\label{ssec:intuitionistic-logc}
+\subsection{Intuitionistic logic (ESCRIBIENDO)}
+\label{ssec:intuitionistic-logic}
 
-AGREGAR TEXTO
+We follow the same approach presented in~\cite{Altenkirch2015} to work with propositional
+logic in type theory. Therefore, we include
+in the constructors for theorems, structural rules and formation rules of 
+all connectives in Fig.~\ref{fig:CPL-inference-rules}.
+
+Since we pretend to reconstruct proofs replied by \Metis, and \Metis works
+in classical logic,  we have included as an axiom, the 
+principle of excluded third (\abbre{PEM}).
+
+Assuming \abbre{PEM}, we can justify refutation proofs.
+We derive the \emph{reductio ad absurdum} rule (\abbre{RAA}) as the
+formulation of the principle of proof by contradiction, that is, a derivation
+of a contradiction, $⊥$, from the hypothesis $(¬ φ)$, is a
+derivation of $φ$.
+
+\begin{figure}
+\begin{equation*}
+  \begin{bprooftree}
+    \AxiomC{}
+    \RightLabel{assume}
+    \UnaryInfC{$Γ , φ ⊢ φ$}
+  \end{bprooftree}\quad
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ φ$}
+    \RightLabel{weaken}
+    \UnaryInfC{$Γ , ψ ⊢ φ$}
+  \end{bprooftree}\quad
+  \begin{bprooftree}
+    \AxiomC{}
+    \RightLabel{$⊤$-intro}
+    \UnaryInfC{$Γ ⊢ ⊤$}
+  \end{bprooftree}\quad
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ ⊥$}
+    \RightLabel{$⊥$-elim}
+    \UnaryInfC{$Γ ⊢ φ$}
+  \end{bprooftree}
+\end{equation*}
+
+\begin{equation*}
+  \begin{bprooftree}
+    \AxiomC{$Γ , φ ⊢ ⊥$}
+    \RightLabel{$¬$-intro}
+    \UnaryInfC{$Γ ⊢ ¬ φ$}
+  \end{bprooftree}\quad
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ ¬ φ$}
+    \AxiomC{$Γ ⊢ φ$}
+    \RightLabel{$¬$-elim}
+    \BinaryInfC{$Γ ⊢ ⊥$}
+  \end{bprooftree}\quad
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ φ$}
+    \AxiomC{$Γ ⊢ ψ$}
+    \RightLabel{$\wedge$-intro}
+    \BinaryInfC{$Γ ⊢ φ \wedge ψ$}
+  \end{bprooftree}
+\end{equation*}
+
+\begin{equation*}
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ φ \wedge ψ$}
+    \RightLabel{$\wedge$-proj$_1$}
+    \UnaryInfC{$Γ⊢ φ$}
+  \end{bprooftree}\quad
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ φ \wedge ψ$}
+    \RightLabel{$\wedge$-proj$_2$}
+    \UnaryInfC{$Γ⊢ ψ$}
+  \end{bprooftree}\quad
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ φ$}
+    \RightLabel{$\vee$-intro$_1$}
+    \UnaryInfC{$Γ ⊢ φ \vee ψ$}
+  \end{bprooftree}
+\end{equation*}
+
+\begin{equation*}
+  \begin{bprooftree}
+    \AxiomC{$Γ ⊢ ψ$}
+    \RightLabel{$\vee$-intro$_2$}
+    \UnaryInfC{$Γ ⊢ φ \vee ψ$}
+  \end{bprooftree}\quad
+  \begin{bprooftree}
+    \AxiomC{$Γ , φ ⊢ γ $}
+    \AxiomC{$Γ , ψ  ⊢ γ$}
+    \RightLabel{$\vee$-elim}
+    \BinaryInfC{$Γ , φ \vee ψ ⊢ γ$}
+  \end{bprooftree}\quad
+  \begin{bprooftree}
+    \AxiomC{$Γ , φ ⊢ ψ$}
+    \RightLabel{$\Rightarrow$-intro}
+    \UnaryInfC{$Γ ⊢ φ \Rightarrow ψ$}
+  \end{bprooftree}
+\end{equation*}
+
+\[
+%\scalebox{0.9}{
+\begin{bprooftree}
+\AxiomC{$Γ ⊢ φ \Rightarrow ψ$}
+\AxiomC{$Γ ⊢ φ$}
+\RightLabel{$\Rightarrow$-elim}
+\BinaryInfC{$Γ ⊢ ψ$}
+\end{bprooftree}\qquad
+\begin{bprooftree}
+\AxiomC{}
+\RightLabel{PEM}
+\UnaryInfC{$Γ ⊢ φ ∨ ¬ φ$}
+\end{bprooftree}
+\]
+
+% \[
+% \qquad
+% \begin{bprooftree}
+% \AxiomC{$Γ, ¬ φ ⊢ ⊥$}
+% \RightLabel{RAA}
+% \UnaryInfC{$Γ ⊢ φ$}
+% \end{bprooftree}
+% \]
+
+\caption{Inference rules for propositional logic.}
+\label{fig:CPL-inference-rules}
+\end{figure}
 

### 2017-10-25 paper/sections/metis-language-and-proofs.tex
Fixed citation.
Fixed citations.

@@
 
-\Metis is an automatic theorem prover written in \len{ML}
-for first-order logic with equality developed by John Hurd
-\cite{hurd2003first}. This prover is suitable for proof
-reconstruction since it provides well-documented proofs
-to justify its deduction steps from the basis of only six inference
-rules. In Fig.~\ref{fig:metis-inferences}, we show the three \Metis
-rules for propositional logic.
+\Metis is an automatic theorem prover written in \len{ML} for
+first-order logic with equality developed by
+\citeauthor{hurd2003first}~\cite{hurd2003first}. This prover is
+suitable for proof reconstruction since it provides well-documented
+proofs to justify its deduction steps from the basis of only six
+inference rules. In Fig.~\ref{fig:metis-inferences}, we show the three
+\Metis rules for propositional logic.
 

### 2017-10-25 paper/main.tex
[ paper ] table added.
[ paper ] related work added.
[ paper ] removed HEAD.
[ paper ] last changes.
[ paper ] strip proof.
[ paper ] conjunct reviewed.
[ paper ] fixing lemmas.
[ paper ] working on resolve.
[ paper ] diagram fixed.
[ paper ] Eq removed.
[ paper ] lots of changes.
[ paper ] canon ==> simplify-and simplify-or.
[ paper ] reorder conclusions with future work.
[ bib ] Switched to biblatex.
[ bib ] Removed quotes from the titles.

@@
   , runningheads
+  % , fleqn           %% all equations in the document left aligned
   ]{llncs}
 
-\spnewtheorem{mainth}[theorem]{Main Theorem}{\bfseries}{\rmfamily}
+% \setlength{\mathindent}{1cm}
 
-\usepackage[numbers]{natbib}
+\spnewtheorem{mainth}{Theorem}[section]{\bfseries}{\rmfamily}
+\spnewtheorem{mainlemma}{Lemma}[section]{\bfseries}{\rmfamily}
+\spnewtheorem*{notation}{Notation}{\it}{\rmfamily}
+\spnewtheorem*{myremark}{Remark}{\it}{\rmfamily}
+\spnewtheorem*{myexample}{Example}{\it}{\rmfamily}
 
@@
 \usepackage[utf8]{inputenc}
-\usepackage{ucs}
 \usepackage{autofe}
@@
   \renewcommand{\proofname}{Sketch of the Proof}\proof}{\endproof}
+
 \renewcommand\qedsymbol{$\blacksquare$}
@@
 \newunicodechar{⊥}{\ensuremath{\bot}}
+\newunicodechar{⬓}{\ensuremath{\square}}
 \newunicodechar{⊻}{\ensuremath{\veebar}}
@@
 \newcommand{\fun}[1]{\rm{#1}\xspace}
+\newcommand{\fassoc}{\fun{assoc}}
 \newcommand{\fbuild}{\fun{build}}
-\newcommand{\fcanon}{\fun{canon}}
+\newcommand{\fcanon}{\fun{simplify}}
 \newcommand{\fcnf}{\fun{cnf}}
@@
 \newcommand{\fndisj}{\fun{ndisj}}
+\newcommand{\fnnfp}{\fun{nnf}₀}
 \newcommand{\fnnf}{\fun{nnf}}
+\newcommand{\fpolarity}{\fun{polarity}}
 \newcommand{\frank}{\fun{rank}}
@@
 \newcommand{\fsbuild}{\fun{sbuild}}
+\newcommand{\fstripp}{\fun{strip}\prime}
+\newcommand{\fstrip}{\fun{strip}}
 \newcommand{\fsubst}{\fun{subst}}
@@
 \newcommand{\tunshunt}{\fun{thm-uh}}
-
-\newcommand{\fstrip}{\fun{strip}}
-\newcommand{\tstrip}{\fun{thm-strip}}
 
@@
 \newcommand{\wrt}{w.\,r.\,t.}
+\newcommand{\TheEnd}{\\\hspace*{0.975\textwidth}$\blacksquare$}
+
+% -------------------------------------------------------------------
+% Rest.
+% -------------------------------------------------------------------
 
@@
 % -------------------------------------------------------------------
+% biblatex.
+% -------------------------------------------------------------------
+
+\usepackage[%
+backend=biber,
+% bibstyle=authoryear,%
+% citestyle=authoryear-comp,%
+% giveninits=false,%%
+% maxcitenames=4,%
+]{biblatex}
+\usepackage{csquotes}
+
+\addbibresource{ref.bib}
+
+% Remove the quotes from the title.
+\DeclareFieldFormat
+  [article,%
+  incollection,%
+  inproceedings,%
+  thesis,% works for mastersthesis and phdthesis
+  unpublished,%
+  ]{title}{#1}
+
+% -------------------------------------------------------------------
 % Hyperef.
@@
 
-\title{Proof-Reconstruction in Type Theory for Propositional Logic}
+\title{Reconstructing Propositional Proofs in Type Theory}
+% \title{Proof-Reconstruction in Type Theory for Propositional Logic}
 \author{Jonathan Prieto-Cubides%
@@
 \subfile{sections/introduction.tex}
-% \subfile{sections/preliminaries.tex}
+\subfile{sections/limitations-type-theory.tex}
 \subfile{sections/metis-language-and-proofs.tex}
@@
 \subfile{sections/related-work.tex}
-\subfile{sections/conclusions.tex}
+\subfile{sections/conclusions-and-future-work.tex}
 \subfile{sections/acknowledgements.tex}
 
-\bibliographystyle{plainnat}
-\bibliography{ref}
+\printbibliography
 \addcontentsline{toc}{section}{References}
 
-\newpage
-\subfile{sections/appendices.tex}
+% \newpage
+% \subfile{sections/appendices.tex}
 

### 2017-10-25 paper/sections/metis-language-and-proofs.tex
minor fixed.

@@
 \name{conjecture}, \name{definition}, \name{plain} or an \name{hypothesis}.
-The formulas include the constants \verb!$true!, negation unary operator (\verb!~!), and the binary connectives (\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!),
+The formulas include the constants \verb!$true!
+and \verb!$false!, negation unary operator (\verb!~!), and the binary connectives (\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!) to represent $⊤, ⊥, ¬, ∧, ∨, ⇒, ⇔$ respectively.
 
@@
 For instance, let us express the problem
-$p\, \vdash \neg (p \wedge \neg p) ∨ (q \wedge \neg q)$
+$p\, ⊢ ¬  (p ∧ ¬ p) ∨ (q ∧ ¬ q)$
 in \TPTP syntax. We begin by declaring the $p$ axiom using the \verb!axiom!
@@
 the customized \TSTP syntax. Note that we remove
-empty fields in the inference information, we shorten names as long as possible, and we delete the \verb!role! field when the role is
-\verb!plain!.
+empty fields in the inference information, we shorten names as long as possible, we delete the \verb!role! field when the role is
+\verb!plain! and we use the math symbols to express the formulas.
 
@@
 fof(sg0, p, inf(strip, [goal])).
-fof(neg0, ~ p, inf(negate, [sg0])).
-fof(norm0, ∼ p, inf(canonicalize, [neg0])).
+fof(neg0, ¬ p, inf(negate, [sg0])).
+fof(norm0, ¬ p, inf(canonicalize, [neg0])).
 fof(norm1, p, inf(canonicalize, [premise])).
-fof(norm2, $false, inf(simplify, [norm0, norm1]))
-cnf(refute0, $false, inf(canonicalize, [norm2])).
+fof(norm2, ⊥, inf(simplify, [norm0, norm1]))
+cnf(refute0, ⊥, inf(canonicalize, [norm2])).
 \end{verbatim}
@@
     \label{tab:agda-metis-table}
-    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}
+    \begin{tabular}{|@{\hspace{2mm}}c@{\hspace{2mm}}l@{\hspace{3mm}}l@{\hspace{3mm}}|}
     \hline
-    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
-    \texttt{canonicalize}
+    \textbf{Theorem} & \textbf{Purpose} &\textbf{\Metis rule}\\ \hline
+
+       \ref{thm:strip}
+      &Strip a goal into subgoals
+      &\texttt{strip}    \\[1ex]
+
+       \ref{thm:conjunct}
+      &Takes a formula from a conjunction
+      &\texttt{conjunct}    \\
+
+       \ref{thm:resolve}
+      &A general form of the resolution theorem
+      &\texttt{resolve}    \\
+
+       \ref{thm:clausify}
+      &Performs clausification
+      &\texttt{clausify}    \\
+
+       \ref{thm:canonicalize}
       &Normalization of the formula
-      &\ref{thm:canonicalize}
-    \\
-    \texttt{clausify}
-      &Performs clausification
-      &\ref{thm:clausify}
-    \\
-    \hyperlink{atp-conjunct}{\texttt{conjunct}}
-      &Takes a formula from a conjunction
-      &\ref{thm:conjunct}
-    \\
-    % \texttt{negate}
-    %   &Negate the formula
-    %   &\ref{thm:negate}
-    % \\
-    \texttt{resolve}
-      &A general form of the resolution theorem
-      &\ref{thm:resolve}
-    \\
-    \texttt{simplify}
+      &\texttt{canonicalize}    \\
+
+       \ref{thm:simplify}
       &Simplify definitions and theorems
-      &\ref{thm:simplify}
-    \\
-    \texttt{strip}
-      &Strip a goal into subgoals
-      &\ref{thm:strip}
-    \\[1ex]
+      &\texttt{simplify}    \\
+
     \hline

### 2017-10-25 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed minor typos.
[ paper ] fixing last suggestions.
minor fixed.

@@
 prover reasoning steps. Since we left out semantics to treat only the
-syntax aspects of the propositions, our approach shows equivalence
+syntax aspects of propositional logic, our approach shows logic equivalence
 by converting propositions to their conjunctive normal form,
 and reordering those and the inner disjunctions to match them.
-Below, we provide some lemmas to perform such reordering tasks,
-we omit the proofs but they can found in~\cite{AgdaMetis}.
+Below, we provide Lemma~\ref{lem:reorder-or}, Lemma~\ref{lem:reorder-and}, Lemma~\ref{lem:reorder-and-or} to perform such reordering tasks,
+the omitted proofs can be found in~\cite{AgdaMetis}.
 
@@
 to convert a disjunction or a conjunction into its right-associative form.
-The square symbol can be the conjunction symbol or the disjunction symbol.
+The square symbol (⬓) can be the conjunction symbol or the disjunction symbol.
 We use $\fassoc_{∧}$ to convert conjunctions and $\fassoc_{∨}$ for
@@
 \end{equation}
-
-\begin{myexample}\hspace{10cm}
-\begin{enumerate}
-\item $\fassoc_{∨}~(((p ∨ ((q ∨ r) ∨ s)) ∨ t) = p ∨ (q ∨ (r ∨ (s ∨ t)))$.
-\item $\fassoc_{∧}~((((p ∧ q) ∧ r) ∧ s) ∧ t) = p ∧ (q ∧ (r ∧ (s ∧ t)))$.
-\end{enumerate}
-\end{myexample}
 
@@
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$, where,
-   \begin{align*}
+   \begin{align}
       \begin{split}
@@
       \end{split}
-  \end{align*}
+  \end{align}
 \end{mainlemma}
@@
 
-\begin{myexample}\hspace{10cm}
+\begin{myexamplenum}\hspace{10cm}
+\label{ex:resolve-tstp}
 \begin{verbatim}
@@
 We have could derive $(p ∨ q) ∨ (p ∨ q)$ but again, that is not the expected result.
-\end{myexample}
+\end{myexamplenum}
 
@@
 \begin{myexample}
-Continuing with the problem presented in the example above,
+Continuing with the problem presented in the Example~\ref{ex:resolve-tstp},
 we can use Theorem \ref{thm:resolve} to derive $Γ ⊢ p ∨ q$.

### 2017-10-25 paper/sections/proof-reconstruction/strip.tex
minor fixed.

@@
 \begin{verbatim}
-fof(goal, conjecture, (p & r) & q)).
+fof(goal, conjecture, (p ∧ r) ∧ q)).
 fof(sg0, p, inf(strip, [goal])).
-fof(sg1, p => r, inf(strip, [goal])).
-fof(sg2, (p & r) => q, inf(strip, [goal])).
+fof(sg1, p ⇒ r, inf(strip, [goal])).
+fof(sg2, (p ∧ r) ⇒ q, inf(strip, [goal])).
 \end{verbatim}
@@
         we conclude $Γ ⊢ φ$.
-  \item If $n = 1$, we apply the following theorem proved in~\cite{AgdaProp},
-    \begin{equation*}
-    \texttt{∧⇒\rm{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
-    \end{equation*}
-  \item For $n > 1$, we use induction on the structure of the second
+  \item For $n \geq 1$, we use induction on the structure of the second
         argument.
@@
 \begin{itemize}
-
 \item Case $φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)$.
@@
   \end{bprooftree}
+\end{equation*}
+using the following theorem proved in~\cite{AgdaProp},
+  \begin{equation*}
+  \texttt{∧⇒\rm{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
   \end{equation*}
@@
 
-The function that yields the conjunction of subgoals that implies the goal of
-the problem in the \Metis \TSTP derivations is not a structurally recursive
-function.  We present its structural recursive function
+The \fstrip₀ function yields the conjunction of subgoals that implies the goal of the problem in the \Metis \TSTP derivations but is not a structurally recursive
+function.  Instead, we present its structural recursive version
 in~(\ref{eq:strip-fixed}) after applying
 the bounded technique described in Section~\ref{ssec:structural-recursion}.
-We based the definition of this function based on the \Metis source code.
+We based on the definition of this function from the \Metis source code.
 
@@
 In a similar way as we define $\fuh_{cm}$ in (\ref{eq:uh-complexity}) we define
-$\fstrip_{cm}$ as the complexity measure for $\fstrip₀$ function. As excepted,
+$\fstrip_{cm}$ as the complexity measure for $\fstrip₀$ function. As expected,
 the \fstrip function is defined as follows.
@@
 The proof is by induction on the structure of the
-formula~$φ$ by following the cases in~(\ref{eq:strip-fixed}).
+formula~$φ$ by following the equations in~(\ref{eq:strip-fixed}).
 We present a straightforward case with double negation, a case with
@@
 
-$\bullet$~Case $φ ≡ φ₁ ∧ φ₂$. We get a proof for each conjunct and using the
-introduction rule for conjunction connective, the expected result follows.
+$\bullet$~Case $φ ≡ φ₁ ∧ φ₂$. We prove $Γ ⊢ φ₁$ and $Γ ⊢ φ₂$. Using the
+introduction rule for conjunction, the expected result follows.
 
@@
 to prove each subgoal, \Metis assumes the negation of it
-using the \negate rule. Then, the \negate rule is
-always derived from a \strip inference application.
+by using the \negate rule after the \strip inference application
+that introduce such a subgoal.
 
 \begin{myexample}
-In the following \TSTP derivation, the three subgoal are
-introduced by the \negate rule.
+In the following \TSTP derivation, note that the three subgoals
+\verb!sg0!, \verb!sg1! and \verb!sg2! are assumed by the \negate
+rule in \verb!neg0!, \verb!neg1! and  \verb!neg2! respectively.
 
 \begin{verbatim}
-fof(goal, conjecture, (p & r & q)).
+fof(goal, conjecture, (p ∧ r ∧ q)).
 fof(sg0, p, inf(strip,[goal])).
-fof(sg1, p => r, inf(strip,[goal])).
-fof(sg2, (p & r) => q, inf(strip,[goal])).
-fof(neg0, ~ p, inf(negate,[sg0])).
+fof(sg1, p ⇒ r, inf(strip,[goal])).
+fof(sg2, (p ∧ r) ⇒ q, inf(strip,[goal])).
+fof(neg0, ¬ p, inf(negate,[sg0])).
 ...
-fof(neg1, ~ (p => r), inf(negate,[sg1])).
+fof(neg1, ¬ (p ⇒ r), inf(negate,[sg1])).
 ...
-fof(neg2, ~ ((p & r) => q), inf(negate,[sg2])).
+fof(neg2, ¬ ((p ∧ r) ⇒ q), inf(negate,[sg2])).
 \end{verbatim}

### 2017-10-25 paper/sections/acknowledgements.tex
more fixes.

@@
 Andreas Abel and Chalmers University of Goteborg, Sweden for
-inviting me to be part of the \Agda Implementors’ Meeting XXV.
-I was honored to present part of this research in the meeting.
+inviting me to be part of the \Agda Implementors’ Meeting XXV
+where I presented part of this research in the meeting.
 

### 2017-10-25 paper/sections/proof-reconstruction/resolve.tex
more fixes.

@@
 In \TPTP syntax, the formulas are in left-associative form by default.
-Despite of that convention, \Metis understands a formula to be in right-associative form by default. This is a matter to take into account for the proof-reconstruction.
+Despite of that convention, \Metis assumes the formulas to be in
+right-associative form by default. This is a matter to take into account for
+the proof-reconstruction.
 \end{myremark}
@@
 \label{lem:build-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fbuild_{∨}~φ~ψ$, where,
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fbuild_{∨}~φ~ψ$ where,
 \begin{equation}
@@
   ψ, &\text{ if } φ ≡ ψ\\
-  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{, } ψᵢ ≡ \fbuild_{∨}~φ~ψᵢ\text{ for some }i=1, 2\\
+  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } ψᵢ ≡ \fbuild_{∨}~φ~ψᵢ\text{ for some }i=1, 2\\
   φ, &\text{ otherwise.}
@@
 otherwise stated.
+
 The $\ffactor$ function in~(\ref{eq:factor-definition})
@@
 \label{lem:factor}
- If $Γ ⊢ φ$ then $Γ ⊢ \ffactor~φ$, where,
+ If $Γ ⊢ φ$ then $Γ ⊢ \ffactor~φ$ where,
 \begin{align}
@@
 equality between nested disjunctions.
-We define the $\fsbuild_{∨}$ function in~(\ref{eq:strong-build-or}).
+We define the $\fsbuild_{∨}$ function in~(\ref{eq:strong-build-or})
 that uses every disjunct from the source formula, $φ$, to build up the
@@
 \label{lem:sbuild-or}
-If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fsbuild_{∨}~φ~ψ$, where,
+If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fsbuild_{∨}~φ~ψ$ where,
 \begin{equation}
@@
 We build the disjunction $(p ∨ q) ∨ r$ from the disjunction
-$r ∨ (q ∨ p)$ based on the idea of the Lemma~\ref{lem:sbuild-or}.
+$r ∨ (q ∨ p)$ using Lemma~\ref{lem:sbuild-or}.
 \begin{equation*}
+(\mathcal{D})\hspace{3mm}
   \begin{bprooftree}
@@
 
-  \AxiomC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
+  \AxiomC{$\mathcal{D}$}
+  \UnaryInfC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
 
@@
   \label{lem:reorder-or}
-  If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}~φ~ψ~$, where,
+  If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}~φ~ψ~$ where,
   \begin{align}
@@
   \label{lem:reorder-and}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}~φ~ψ$, where,
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}~φ~ψ$ where,
     \begin{align}
@@
 
-\begin{myexample}\hspace{10cm}
-\begin{enumerate}
-  \item $\freorder_{∧}~(p ∧ q ∧ r)~(r ∧ q ∧ p)~=~(r ∧ q ∧ p).$
-  \item $\freorder_{∧}~(p ∧ q ∧ r)~(r ∧ r ∧ p)~=~(r ∧ q ∧ p).$
-  \item $\freorder_{∧}~(p ∧ q ∧ r)~(k ∧ q ∧ p)~=~(p ∧ q ∧ r).$
-  \item $\freorder_{∧}~((p ∨ q) ∧ r)~(r ∧ (q ∨ p))~=~((p ∨ q) ∧ r).$
-\end{enumerate}
+\begin{myexample}
+\begin{equation}
+\label{ex:reorder-example}
+\begin{aligned}
+\begin{array}{llll}
+  \freorder_{∧} &(p ∧ q ∧ r)   &(r ∧ q ∧ p)     ~&=~(r ∧ q ∧ p),\\
+  \freorder_{∧} &(p ∧ q ∧ r)   &(r ∧ r ∧ p)     ~&=~(r ∧ q ∧ p),\\
+  \freorder_{∧} &(p ∧ q ∧ r)   &(k ∧ q ∧ p)     ~&=~(p ∧ q ∧ r),\\
+  \freorder_{∧} &((p ∨ q) ∧ r) &((r ∧ (q ∨ p)) ~&=~((p ∨ q) ∧ r).
+\end{array}
+\end{aligned}
+\end{equation}
 \end{myexample}
 
-In the last example, Item~4, we could not build the conjunction
+In the last example in (\ref{ex:reorder-example}), we could not build the conjunction
 $r ∧ (q ∨ p)$ since $p ∨ q$ is not syntactical equal to $q ∨ p$.
@@
   \label{lem:conjunct-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}~φ~ψ$, where,
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}~φ~ψ$ where,
   \begin{equation*}
@@
 
-Now, we are able to reorder conjunctive normal forms using
+We are able now to reorder conjunctive normal forms using the
 $\freorder_{∧∨}$ function defined in (\ref{eq:reorder-and-or})
-that unifies the previous lemma showed above.
+by using the previous lemma.
 
@@
   \label{lem:reorder-and-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$, where,
+  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$ where,
    \begin{align}
@@
 
-Now, we are in a position to reconstruct \resolve rule. This is the
+Now, we are ready to reconstruct the \resolve rule. This is the
 first application of the Lemma \ref{lem:reorder-and-or}.
-The \resolve rule is a generalization of the resolution theorem showed in
-Fig.~\ref{fig:metis-inferences} in the \TSTP derivations.
-This rule has three arguments: a positive literal $l$ to apply the
+The \resolve rule is a generalization of the resolution theorem.
+This rule has three arguments: a positive literal $ℓ$to apply the
 resolution theorem and two derivations.
-The positive literal $l$ must occur in
+Recall a\emph{literal} is an atom (positive literal) or a negation
+of an atom (negative literal).
+The positive literal $ℓ$ must occur in
 the formula from the first derivation and the
-negative literal $¬ l$ must occur in the formula from the second derivation,
+negative literal $¬ ℓ$ must occur in the formula from the second derivation,
 see the pattern of \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.
@@
 \begin{verbatim}
-cnf(ref4, (~ r | p | q), inf(canonicalize, [norm5])).
-cnf(ref5, (p | q | r), inf(canonicalize, [norm6])).
-cnf(ref6, (p | q), inf(resolve, [$cnf(r)], [ref5, ref4])).
+cnf(ref4, (¬ r ∨ p ∨ q), inf(canonicalize, [norm5])).
+cnf(ref5, (p ∨ q ∨ r), inf(canonicalize, [norm6])).
+cnf(ref6, (p ∨ q), inf(resolve, r, [ref5, ref4])).
 \end{verbatim}
-In the excerpt above, we apply resolution for the first two formulas,
-$¬ r ∨ p ∨ q$ and $p ∨ q ∨ r$. The last line tells us the literal mentioned
+In the excerpt above, we apply resolution to the first two formulas,
+$¬ r ∨ p ∨ q$ and $p ∨ q ∨ r$. The last line tells us the literal used
 for resolution is $r$. Syntactically speaking,
-we can not derive neither the conclusion $p ∨ q$ in \verb!ref6! nor apply the resolution theorem with \verb!ref4! and \verb!ref5! since the formulas does not fit the pattern required.
+we can not derive neither the conclusion $p ∨ q$ in \verb!ref6! nor apply the resolution theorem with \verb!ref4! and \verb!ref5! since the formulas do not fit the pattern required.
 
@@
 \begin{verbatim}
-cnf(ref5, (r | p | q), inf(canonicalize, [norm6])).
+cnf(ref5, (r ∨ p ∨ q), inf(canonicalize, [norm6])).
 \end{verbatim}
-We have could derive $(p ∨ q) ∨ (p ∨ q)$ but again, that is not the expected result.
+The \resolve rule have could derive $(p ∨ q) ∨ (p ∨ q)$, but again, that is not the expected result.
 \end{myexamplenum}
@@
 described in Fig.~\ref{fig:metis-inferences}. Using reordering after
-applying a convenient version of the resolution theorem defined
+applying a customized version of the resolution theorem defined
 in~(\ref{eq:rsol}) we get the expect result.
@@
   \label{lem:rsol}
-  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}~φ$, where,
+  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}~φ$ where,
   \begin{equation}
@@
   \label{thm:resolve}
-  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, a literal $l : \Prop$, and $ψ : \Prop$ then
-  $Γ ⊢ \fresolve~φ₁~φ₂~l~ψ$, where,
+  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, let $ℓ$ be a literal $ℓ : \Prop$, and $ψ : \Prop$ then
+  $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$ where,
   \begin{equation}
@@
     &\fresolve : \Prop \to \Prop \to \Prop \to \Prop \to \Prop\\
-    &\fresolve~φ₁~φ₂~l~ψ =
-      \rm{rsol}~(\freorder_{∨}~φ₁~(l ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ l ∨ ψ)).
+    &\fresolve~φ₁~φ₂~ℓ~ψ =
+      \rm{rsol}~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)).
   \end{split}
@@
     \RightLabel{Lemma~\ref{lem:reorder-and-or}}
-    \UnaryInfC{$Γ ⊢ \freorder_{∨}~φ₁~(l ∨ ψ)$}
+    \UnaryInfC{$Γ ⊢ \freorder_{∨}~φ₁~(ℓ ∨ ψ)$}
     \RightLabel{Lemma~\ref{lem:reorder-and-or}}
     \AxiomC{$Γ ⊢ φ₂$}
-    \UnaryInfC{$Γ ⊢ \freorder_{∨}~φ₂~(¬ l ∨ ψ)$}
+    \UnaryInfC{$Γ ⊢ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)$}
     \RightLabel{∧-intro}
-    \BinaryInfC{$Γ ⊢ \freorder_{∨}~φ₁~(l ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ l ∨ ψ)$}
+    \BinaryInfC{$Γ ⊢ \freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)$}
     \RightLabel{Lemma~\ref{lem:rsol}}
-    \UnaryInfC{$Γ ⊢ \rm{rsol}~(\freorder_{∨}~φ₁~(l ∨ ψ) ∧
-     \freorder_{∨}~φ₂~(¬ l ∨ ψ))$}
+    \UnaryInfC{$Γ ⊢ \rm{rsol}~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧
+     \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ))$}
     \RightLabel{by (\ref{eq:resolve})}
-    \UnaryInfC{$Γ ⊢ \fresolve~φ₁~φ₂~l~ψ$}
+    \UnaryInfC{$Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$}
   \end{bprooftree}
@@
 \begin{myexample}
-Continuing with the problem presented in the Example~\ref{ex:resolve-tstp},
+Continuing with the problem presented in Example~\ref{ex:resolve-tstp},
 we can use Theorem \ref{thm:resolve} to derive $Γ ⊢ p ∨ q$.

### 2017-10-25 paper/sections/proof-reconstruction/resolve.tex
more fixes.

@@
 $r ∧ (q ∨ p)$ since $p ∨ q$ is not syntactical equal to $q ∨ p$.
-We solve this issue in the Lemma~\ref{lem:reorder-and-or} by
+We solve this issue in Lemma~\ref{lem:reorder-and-or} by
 using the $\fconjunct_{∨}$ function defined in~(\ref{eq:conjunct-or}).
@@
   If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}~φ~ψ$ where,
-  \begin{equation*}
+  \begin{equation}
     \begin{split}
@@
     \end{split}
-  \end{equation*}
+  \end{equation}
 \end{mainlemma}
@@
 Now, we are ready to reconstruct the \resolve rule. This is the
-first application of the Lemma \ref{lem:reorder-and-or}.
+first application of Lemma \ref{lem:reorder-and-or}.
 The \resolve rule is a generalization of the resolution theorem.

### 2017-10-25 paper/sections/proof-reconstruction/strip.tex
more fixes.

@@
 
-In this example, the conjecture \verb!(p & r) & q! is stripped into
-tree subgoals: $p$, $p ⇒ r$ and $(p ∧ r) ⇒ q$.
+In this example, the conjecture \$(p ∧ r) ∧ q$ is stripped into
+tree subgoals: \$p$, \$p ⇒ r$ and \$(p ∧ r) ⇒ q$.
 
@@
 \fstrip₁ &(φ₁ ⇒ φ₂)     &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)\\
-\fstrip₁ &(¬ (φ₁ ∧ φ₂)) &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip₁~¬ φ₂~n)\\
-\fstrip₁ &(¬ (φ₁ ∨ φ₂)) &(\suc~n) &= \fuh~(\fstrip₁~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~¬ φ₂~n)\\
-\fstrip₁ &(¬ (φ₁ ⇒ φ₂)) &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~¬ φ₂~n)\\
+\fstrip₁ &(¬ (φ₁ ∧ φ₂)) &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)\\
+\fstrip₁ &(¬ (φ₁ ∨ φ₂)) &(\suc~n) &= \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)\\
+\fstrip₁ &(¬ (φ₁ ⇒ φ₂)) &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)\\
 \fstrip₁ &(¬ ¬ φ₁)      &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n)\\
@@
 
-$\bullet$~Case $φ ≡ φ₁ ∧ φ₂$. We prove $Γ ⊢ φ₁$ and $Γ ⊢ φ₂$. Using the
-introduction rule for conjunction, the expected result follows.
+$\bullet$~Case $φ ≡ φ₁ ∧ φ₂$. We prove $Γ ⊢ φ₁$ and $Γ ⊢ φ₂$.
+From the conjunction of φ₁ and φ₂, the expected result follows.
 
@@
 $\bullet$~Case $φ ≡ ¬ (φ₁ ∨ φ₂)$.
-We show the theorems $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
-With the conjunction of $¬ φ₁$ and $¬ φ₂$ by applying De Morgan Law, the
-result follows.
+We prove $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
+From the conjunction of $¬ φ₁$ and $¬ φ₂$ by applying De Morgan Law
+and the result follows.
 
@@
 \RightLabel{by~(\ref{eq:strip-fixed})}
-\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~¬ φ₂~n)$}
+\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)$}
 \RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~¬ φ₁~n)$}
+\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n)$}
 \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-\UnaryInfC{$Γ ⊢ \fstrip₁~¬ φ₁~n$}
+\UnaryInfC{$Γ ⊢ \fstrip₁~(¬ φ₁)~n$}
 \RightLabel{by~ind.~hyp.}
@@
   \RightLabel{by~(\ref{eq:strip-fixed})}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~¬ φ₁~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~¬ φ₂~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)$}
   \RightLabel{∧-proj₂}
-  \UnaryInfC{$Γ ⊢ \fuh~(¬ φ₁ ⇒ \fstrip₁~¬ φ₂~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~(¬ φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)$}
   \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip₁~¬ φ₂~n$}
+  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip₁~(¬ φ₂)~n$}
   \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ ⊢ \fstrip₁~¬ φ₂~n$}
+  \BinaryInfC{$Γ ⊢ \fstrip₁~(¬ φ₂)~n$}
   \RightLabel{by~ind.~hyp.}
@@
 The following theorem is convenient to substitute equals by equals in
-a theorem. Recall the equality ≡ is symmetric and transitive as well.
-We use such properties without any mention.
+a theorem. Recall the equality (≡) is symmetric and transitive as well.
+We use these properties without any mention.
 

### 2017-10-25 paper/sections/proof-reconstruction/clausify.tex
more fixes.
strip equations.

@@
 of clauses. A \emph{clause} is the disjunction of zero or more
-literals and a \emph{literal} is an atom (positive literal) or a
-negation of an atom (negative literal).
+literals.
 It is important to notice that this kind of conversion between one formula
@@
 \begin{verbatim}
-fof(a1, axiom, p => (q & r)).
+fof(a1, axiom, p ⇒ (q ∧ r)).
 ...
-fof(norm0, ~ p | (q & r), inf(canonicalize, [a1])).
-fof(norm1, (~ p | q) & (~ p | r), inf(clausify, [norm0])).
+fof(norm0, ¬ p ∨ (q ∧ r), inf(canonicalize, [a1])).
+fof(norm1, (¬ p ∨ q) ∧ (¬ p ∨ r), inf(clausify, [norm0])).
 ...
@@
 \begin{proof}
-If $φ ≡ ψ$, $Γ ⊢ \fclausify~φ~ψ$ normalizes to $Γ ⊢ ψ$. The conclusion follows by applying the $\fsubst$ lemma. Otherwise, we use Theorem~\ref{lem:reorder-and-or} and Theorem~\ref{lem:cnf}.
+If $φ ≡ ψ$, $Γ ⊢ \fclausify~φ~ψ$ normalizes to $Γ ⊢ ψ$. The conclusion follows by applying the $\fsubst$ lemma. Otherwise, we use Lemma~\ref{lem:reorder-and-or} and Lemma~\ref{lem:cnf}.
 \end{proof}

### 2017-10-25 paper/sections/metis-language-and-proofs.tex
typo fixed.

@@
       &Strip a goal into subgoals
-      &\texttt{strip}    \\[1ex]
+      &\texttt{strip}
+      \\
 
@@
       &Takes a formula from a conjunction
-      &\texttt{conjunct}    \\
+      &\texttt{conjunct}
+      \\
 
@@
       &A general form of the resolution theorem
-      &\texttt{resolve}    \\
+      &\texttt{resolve}
+      \\
 
@@
       &Performs clausification
-      &\texttt{clausify}    \\
+      &\texttt{clausify}
+      \\
 
@@
       &Normalization of the formula
-      &\texttt{canonicalize}    \\
+      &\texttt{canonicalize}
+      \\
 
@@
       &Simplify definitions and theorems
-      &\texttt{simplify}    \\
+      &\texttt{simplify}
+      \\[1ex]
 

### 2017-10-25 paper/sections/proof-reconstruction/strip.tex
strip equations.
typo fixed.

@@
 
-In this example, the conjecture \$(p ∧ r) ∧ q$ is stripped into
-tree subgoals: \$p$, \$p ⇒ r$ and \$(p ∧ r) ⇒ q$.
+In this example, the conjecture $(p ∧ r) ∧ q$ is stripped into
+tree subgoals: $p$, $p ⇒ r$ and $(p ∧ r) ⇒ q$.
 
@@
 
-Now, using the theorem \texttt{⇒∧⇒\rm{-to-}⇒∧} from~\cite{AgdaProp},
+Now, using \texttt{⇒∧⇒\rm{-to-}⇒∧} theorem from~\cite{AgdaProp},
 \begin{equation*}
@@
 \fstrip₁ &(φ₁ ∧ φ₂)     &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)\\
-\fstrip₁ &(φ₁ ∨ φ₂)     &(\suc~n) &= \fuh~(¬ φ₁ ⇒ \fstrip₁~φ₂~n)\\
+\fstrip₁ &(φ₁ ∨ φ₂)     &(\suc~n) &= \fuh~((¬ φ₁) ⇒ \fstrip₁~φ₂~n)\\
 \fstrip₁ &(φ₁ ⇒ φ₂)     &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)\\
 \fstrip₁ &(¬ (φ₁ ∧ φ₂)) &(\suc~n) &= \fuh~(φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)\\
-\fstrip₁ &(¬ (φ₁ ∨ φ₂)) &(\suc~n) &= \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)\\
+\fstrip₁ &(¬ (φ₁ ∨ φ₂)) &(\suc~n) &= \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~((¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n)\\
 \fstrip₁ &(¬ (φ₁ ⇒ φ₂)) &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)\\
@@
 
-In a similar way as we define $\fuh_{cm}$ in (\ref{eq:uh-complexity}) we define
+In a similar way as we define $\fuh_{cm}$ in (\ref{eq:uh-complexity}), we define
 $\fstrip_{cm}$ as the complexity measure for $\fstrip₀$ function. As expected,
@@
 \RightLabel{by~(\ref{eq:strip-fixed})}
-\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)$}
+\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~((¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n)$}
 \RightLabel{∧-proj₁}
@@
   \RightLabel{by~(\ref{eq:strip-fixed})}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~(¬ φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~((¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n)$}
   \RightLabel{∧-proj₂}
-  \UnaryInfC{$Γ ⊢ \fuh~(¬ φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)$}
+  \UnaryInfC{$Γ ⊢ \fuh~((¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n)$}
   \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ ¬ φ₁ ⇒ \fstrip₁~(¬ φ₂)~n$}
+  \UnaryInfC{$Γ ⊢ (¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n$}
   \RightLabel{⇒-elim}

### 2017-10-25 paper/sections/conclusions-and-future-work.tex
[ paper ] add the third paragraph in the introduction.
[ paper ] using sans serif.

--- 2017-10-24 paper/sections/conclusions-and-future-work.tex
@@
     \item support the proposition fragment with equality of \Metis.
-    \item support other \ATPs for \CPL like \name{EProver} or \name{Z3}.
-    \item support \Metis first order proofs.
-This development can be carried out by following the \name{EProver}
-inference rules described on Kanso's Ph.D. thesis~\cite{Kanso2012}.
+    \item support other \ATPs for propositional logic like \name{EProver} or \name{Z3}. This development can be carried out by following the \name{EProver}
+description on Kanso's Ph.D. thesis~\cite{Kanso2012}.
+    \item support \Metis first-order proofs.
+
   \end{itemize}
-\item contrasts the use of a shallow embedding instead
-of the deep embedding implemented in~\cite{AgdaProp}.
+\item use a shallow embedding instead the deep embedding implemented in~\cite{AgdaProp} to reconstruct proofs.
 \item improve some functions in Section~\ref{ssec:emulating-inferences}

### 2017-10-25 paper/sections/proof-reconstruction/strip.tex
[ paper ] using sans serif.

@@
   \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
-  \RightLabel{∧⇒\rm{-to-}⇒⇒}
+  \RightLabel{∧⇒\textsf{-to-}⇒⇒}
   \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)}
@@
   \begin{equation*}
-  \texttt{∧⇒\rm{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
+  \texttt{∧⇒\textsf{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
   \end{equation*}
@@
 
-Now, using \texttt{⇒∧⇒\rm{-to-}⇒∧} theorem from~\cite{AgdaProp},
+Now, using \texttt{⇒∧⇒\textsf{-to-}⇒∧} theorem from~\cite{AgdaProp},
 \begin{equation*}
-  \texttt{⇒∧⇒\rm{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
+  \texttt{⇒∧⇒\textsf{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
 \end{equation*}
@@
   \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
-  \RightLabel{\tt ⇒∧⇒\rm{-to-}⇒∧}
+  \RightLabel{\tt ⇒∧⇒\textsf{-to-}⇒∧}
   \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
@@
 \fstrip₁ &(¬ ⊤)         &(\suc~n) &= ⊥\\
-\fstrip₁ &φ             &\text{n} &= φ
+\fstrip₁ &φ             &n        &= φ
 \end{array}
@@
   \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \fstrip₁~(φ₁ ∧ φ₂)~(\suc~n)$}
+  \AxiomC{$Γ ⊢ \fstrip₁~(φ₁ ∧ φ₂)~(\suc\,\textit{n})$}
   \RightLabel{by~(\ref{eq:strip-fixed})}
@@
 
-\begin{mainlemma}[subst]
+\begin{mainlemma}
   \label{lem:subst}
@@
   \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
-  \RightLabel{subst}
+  \RightLabel{\fsubst}
   \BinaryInfC{$Γ ⊢ ψ$}
@@
 Let $s₁$ and $s₂$ be the subgoals of the goal $φ$, that is,
-$$\fstrip~φ~n~≡~s₁∧~s₂.$$
+$$\fstrip₁~φ~n~≡~s₁∧~s₂.$$
 If $Γ ⊢ s₁$ and $Γ ⊢ s₂$ then $Γ ⊢ φ$.
@@
   \BinaryInfC{$Γ ⊢ s_1\wedge s_2$}
-  \AxiomC{$\fstrip~φ~n ≡ s_1\wedge s_2 $}
-  \RightLabel{subst}
-  \BinaryInfC{$Γ ⊢ \fstrip~φ~n$}
+  \AxiomC{$\fstrip₁~φ~n ≡ s_1\wedge s_2 $}
+  \RightLabel{\fsubst}
+  \BinaryInfC{$Γ ⊢ \fstrip₁~φ~n$}
   \RightLabel{Lemma~\ref{lem:lem-inv-strip}}

### 2017-10-26 paper/sections/conclusions-and-future-work.tex
[ paper ] fixed some typos.

@@
 can reveal important issues or bugs
-in many parts of these systems (e.g., preprocessing, reasoning, or
+in many parts of these systems (\eg, preprocessing, reasoning, or
 deduction modules). During this research, we had the opportunity
@@
 \url{https://github.com/gilith/metis}}.
-Fortunately, all these problems were fixed quickly by Joe Hurd in
-the \Metis 20170810 release.
+Fortunately, all these problems were fixed quickly by
+\citeauthor{hurd2003first} in the \Metis 20170810 release.
 
@@
     \item support \Metis first-order proofs.
+  \end{itemize}
 
-  \end{itemize}
-\item use a shallow embedding instead the deep embedding implemented in~\cite{AgdaProp} to reconstruct proofs.
+\item use a shallow embedding instead the deep embedding
+implemented in~\cite{AgdaProp} to reconstruct proofs.
 \item improve some functions in Section~\ref{ssec:emulating-inferences}

### 2017-10-26 paper/sections/metis-language-and-proofs.tex
removed ugly message.
[ paper ] fixed some typos.

@@
 
-\begin{myexample}
+\begin{myexamplenum}
+\label{fig:metis-example-tree}
 
@@
 
-\end{myexample}
+\end{myexamplenum}
 
@@
   \end{bprooftree}
-  \caption{A \Metis proof tree.}
+  \caption{\Metis proof tree of derivation in Example~\ref{fig:metis-example-tree}.}
   \label{fig:metis-example}
@@
 These rules are not the same as we expected from the Fig.~\ref{fig:metis-inferences}.
-
-AGREGAR el sitio de metis official.!!
 
@@
     \label{tab:agda-metis-table}
-    \begin{tabular}{|@{\hspace{2mm}}c@{\hspace{2mm}}l@{\hspace{3mm}}l@{\hspace{3mm}}|}
+    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}c@{\hspace{2mm}}|}
     \hline
-    \textbf{Theorem} & \textbf{Purpose} &\textbf{\Metis rule}\\ \hline
+    \textbf{\Metis rule name} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
 
-       \ref{thm:strip}
-      &Strip a goal into subgoals
+      Strip a goal into subgoals
       &\texttt{strip}
+      &\ref{thm:strip}
       \\
 
-       \ref{thm:conjunct}
-      &Takes a formula from a conjunction
+      Takes a formula from a conjunction
       &\texttt{conjunct}
+      &\ref{thm:conjunct}
       \\
 
-       \ref{thm:resolve}
-      &A general form of the resolution theorem
+      A general form of the resolution theorem
       &\texttt{resolve}
+      &\ref{thm:resolve}
       \\
 
-       \ref{thm:clausify}
-      &Performs clausification
+      Performs clausification
       &\texttt{clausify}
+      &\ref{thm:clausify}
       \\
 
-       \ref{thm:canonicalize}
-      &Normalization of the formula
+      Normalization of the formula
       &\texttt{canonicalize}
+      &\ref{thm:canonicalize}
       \\
 
-       \ref{thm:simplify}
-      &Simplify definitions and theorems
+      Simplify definitions and theorems
       &\texttt{simplify}
+      &\ref{thm:simplify}
       \\[1ex]
-
     \hline

### 2017-10-26 paper/sections/proof-reconstruction/resolve.tex
[ paper ] using sans serif.
[ paper ] fixed some typos.

@@
 The \resolve rule is a generalization of the resolution theorem.
-This rule has three arguments: a positive literal $ℓ$to apply the
+This rule has three arguments: a positive literal $ℓ$ to apply the
 resolution theorem and two derivations.
-Recall a\emph{literal} is an atom (positive literal) or a negation
+Recall a \emph{literal} is an atom (positive literal) or a negation
 of an atom (negative literal).
@@
   \label{lem:rsol}
-  If $Γ ⊢ φ$ then $Γ ⊢ \rm{rsol}~φ$ where,
+  If $Γ ⊢ φ$ then $Γ ⊢ \frsol~φ$ where,
   \begin{equation}
@@
     \begin{aligned}
-    &\rm{rsol} : \Prop \to \Prop\\
+    &\frsol : \Prop \to \Prop\\
     &\begin{array}{ll}
-      \rm{rsol}~φ &=
+      \frsol~φ &=
         \begin{cases}
@@
     &\fresolve~φ₁~φ₂~ℓ~ψ =
-      \rm{rsol}~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)).
+      \frsol~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)).
   \end{split}
@@
     \RightLabel{Lemma~\ref{lem:rsol}}
-    \UnaryInfC{$Γ ⊢ \rm{rsol}~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧
+    \UnaryInfC{$Γ ⊢ \frsol~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧
      \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ))$}
@@
   \RightLabel{by (\ref{eq:resolve})}
-  \UnaryInfC{$Γ ⊢ \rm{rsol}~(\freorder_{∨}~φ₁~(r ∨ (p ∨ q))~∧~\freorder_{∨}~φ₂~(¬ r ∨ (p ∨ q))$}
+  \UnaryInfC{$Γ ⊢ \frsol~(\freorder_{∨}~φ₁~(r ∨ (p ∨ q))~∧~\freorder_{∨}~φ₂~(¬ r ∨ (p ∨ q))$}
   \RightLabel{by (\ref{eq:reorder-or})}
-  \UnaryInfC{$Γ ⊢ \rm{rsol}~((r ∨ (p ∨ q)) ∧ (¬ r ∨ (p ∨ q)))$}
+  \UnaryInfC{$Γ ⊢ \frsol~((r ∨ (p ∨ q)) ∧ (¬ r ∨ (p ∨ q)))$}
   \RightLabel{by (\ref{eq:rsol})}

### 2017-10-26 paper/sections/related-work.tex
[ paper ] minor fixes.
Fixed citations.
[ paper ] fixed some typos.

@@
 
-% EJEMPLOS DE RECONSTRUCTION DE PRUEBAS USANDO IPTS EN TEORIA DE TIPOS PARA
-% ATPS.
-
-% AGDA
-% COQ
-
-% Otros: HOL
-
-Many approaches have been proposed for proof-reconstruction and some tools have been
-implemented in the last decades.
+Many approaches have been proposed for proof-reconstruction and some tools have been implemented in the last decades.
 
@@
 
-We found many successful attemps using proof assistant for classical logic
+There are some successful attempts using proof assistants for classical logic
 instead of type theory.
@@
 
-Hurd~\cite{Hurd1999} integrates the first-order resolution prover
-\name{Gandalf} with the high-order
-theorem prover \name{HOL}~\cite{norrish2007hol}.
+\citeauthor{Hurd1999}~\cite{Hurd1999} integrates the first-order resolution
+prover \name{Gandalf} with the high-order theorem prover
+\name{HOL}~\cite{norrish2007hol}.
 Its \verb!GANDALF_TAC! tactic is able to reconstruct \name{Gandalf} proofs

### 2017-10-26 paper/sections/proof-reconstruction.tex
strip equations.
[ paper ] minor changes.

@@
 type theory is presented to build definitions and theorems of
-functions necessary to emulate \Metis' inference rules.
+functions necessary to reconstruct \Metis' inference rules.
 
@@
 \begin{verbatim}
-fof(p3, (r | ~ p), inf(conjunct, [p1])).
+fof(p3, (r ∨ ¬ p), inf(conjunct, [p1])).
 \end{verbatim}

### 2017-10-26 paper/sections/proof-reconstruction.tex
[ paper ] bullet symbol.

@@
 type theory is presented to build definitions and theorems of
-functions necessary to reconstruct \Metis' inference rules.
+functions necessary to reconstruct \Metis inference rules.
 
@@
 
-\subsection{Reconstructing \Metis' inference rules}
+\subsection{Reconstructing \Metis inference rules}
 \label{ssec:emulating-inferences}
@@
 \begin{notation}
-The function name written in bold font is a \Metis inference rule.
-The same function name written in roman letters refers to the proposed
-version of the rule.
-Each rule proposed has a respective theorem also written in roman letters
-that proves its soundness.
+The function name written in \texttt{typewriter} font refers to
+a \Metis inference rule.
+The same function name written using \textsf{sans serif} refers to the proposed
+version of the rule implemented in \cite{AgdaProp,AgdaMetis}.
 \end{notation}
@@
 \begin{itemize}
-  \item[$\bullet$] $φ$ is the \emph{source} formula from a previous deducted derivation.
-  \item[$\bullet$] $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
+  \item[∙] $φ$ is the \emph{source} formula from a previous deducted derivation.
+  \item[∙] $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
 \end{itemize}

### 2017-10-26 paper/sections/limitations-type-theory.tex
minor fixed.
[ paper ] using sans serif.
Fixed typos.

@@
 and symbols of the arithmetic operations as usual.
-We include syntax sugar for $\zero$, $\suc$, $\suc(\zero)$,
+We include syntax sugar for $\zero$, $\suc$, $\suc~\zero$,
 $\cdots$, with the decimal representation: $0$, $1$, $2$, $\cdots$
@@
 \fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
-\fuh_{1} &φ &\xspace\text{n} &= φ
+\fuh_{1} &φ &n &= φ
 \end{array}
@@
 
-Following the technique mentioned above, we get the structural recursive definition of $\fuh_{0}$ function presented in ~(\ref{eq:uh}).
+Following the technique mentioned above, we get the structural
+recursive definition of the $\fuh_{0}$ function presented in~(\ref{eq:uh}).
 

### 2017-10-26 paper/sections/limitations-type-theory.tex
Using `\eqref`.

@@
 
-In (\ref{eq:uh-definition}), the first two equation
+In~\eqref{eq:uh-definition}, the first two equation
 call on arguments no structurally smaller.
@@
 
-We bounded the recursion calls in~(\ref{eq:uh-structured}) with \Nat type argument. This natural number represents the complexity measure of $\fuh_{0}$
+We bounded the recursion calls in~\eqref{eq:uh-structured} with \Nat type argument. This natural number represents the complexity measure of $\fuh_{0}$
 function.
@@
 Following the technique mentioned above, we get the structural
-recursive definition of the $\fuh_{0}$ function presented in~(\ref{eq:uh}).
+recursive definition of the $\fuh_{0}$ function presented
+in~\eqref{eq:uh}.
 

### 2017-10-26 paper/sections/proof-reconstruction/resolve.tex
Using `\eqref`.

@@
 
-First, we define \fassoc$_{⬓}$ function in~(\ref{eq:fassoc})
+First, we define \fassoc$_{⬓}$ function in~\eqref{eq:fassoc}
 to convert a disjunction or a conjunction into its right-associative form.
@@
 
-The $\fbuild_{∨}$ function defined in~(\ref{eq:build-or})
+The $\fbuild_{∨}$ function defined in~\eqref{eq:build-or}
 intends to construct a disjunction from another disjunction, specifically,
@@
 
-The $\ffactor$ function in~(\ref{eq:factor-definition})
+The $\ffactor$ function in~\eqref{eq:factor-definition}
 simplifies a special case of disjunction, the repeated disjuncts
@@
 equality between nested disjunctions.
-We define the $\fsbuild_{∨}$ function in~(\ref{eq:strong-build-or})
+We define the $\fsbuild_{∨}$ function in~\eqref{eq:strong-build-or}
 that uses every disjunct from the source formula, $φ$, to build up the
@@
 help us in the end of this section to reorder conjunctive normal forms.
-For instance, the $\freorder_{∧}$ function in~(\ref{eq:reorder-and}),
+For instance, the $\freorder_{∧}$ function in~\eqref{eq:reorder-and},
 reorders nested conjunctions.
@@
 
-In the last example in (\ref{ex:reorder-example}), we could not build the conjunction
+In the last example in~\eqref{ex:reorder-example}, we could not build the conjunction
 $r ∧ (q ∨ p)$ since $p ∨ q$ is not syntactical equal to $q ∨ p$.
 We solve this issue in Lemma~\ref{lem:reorder-and-or} by
-using the $\fconjunct_{∨}$ function defined in~(\ref{eq:conjunct-or}).
+using the $\fconjunct_{∨}$ function defined in~\eqref{eq:conjunct-or}.
 
@@
 We are able now to reorder conjunctive normal forms using the
-$\freorder_{∧∨}$ function defined in (\ref{eq:reorder-and-or})
+$\freorder_{∧∨}$ function defined in~\eqref{eq:reorder-and-or}
 by using the previous lemma.
@@
 applying a customized version of the resolution theorem defined
-in~(\ref{eq:rsol}) we get the expect result.
+in~\eqref{eq:rsol} we get the expect result.
 

### 2017-10-26 paper/sections/proof-reconstruction/strip.tex
[ paper ] bullet symbol.
Using `\eqref`.

@@
 \Metis proves each subgoal in the same order above from left to right
-in (\ref{eq:strip-example}).
+in~\ref{eq:strip-example}.
 So far, very little attention has been paid to the role of \strip rule.
@@
 Let $\text{n} : \Nat$ be the complexity measure of the $\fuh_0$ function
-in~(\ref{eq:uh-definition}).
+in~\eqref{eq:uh-definition}.
 If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$, where $\fuh₁$ is the function defined
-in (\ref{eq:uh-structured}).
+in~\eqref{eq:uh-structured}.
 \end{mainlemma}
@@
 \begin{itemize}
-  \item If $n = 0$, by definition in~(\ref{eq:uh-structured})
+  \item If $n = 0$, by definition in~\eqref{eq:uh-structured}
         we conclude $Γ ⊢ φ$.
@@
 function.  Instead, we present its structural recursive version
-in~(\ref{eq:strip-fixed}) after applying
+in~\eqref{eq:strip-fixed} after applying
 the bounded technique described in Section~\ref{ssec:structural-recursion}.
@@
 
-In a similar way as we define $\fuh_{cm}$ in (\ref{eq:uh-complexity}), we define
+In a similar way as we define $\fuh_{cm}$ in~\eqref{eq:uh-complexity}, we define
 $\fstrip_{cm}$ as the complexity measure for $\fstrip₀$ function. As expected,
@@
 Let $\text{n} : \Nat$ be the complexity measure of the \fstrip function defined
-in~(\ref{eq:strip-fixed}).
+in~\eqref{eq:strip-fixed}.
 If $Γ ⊢ \fstrip₁~φ~n$ then $Γ ⊢ φ$.
@@
 The proof is by induction on the structure of the
-formula~$φ$ by following the equations in~(\ref{eq:strip-fixed}).
+formula~$φ$ by following the equations in~\eqref{eq:strip-fixed}.
 We present a straightforward case with double negation, a case with
@@
 
-$\bullet$~Case $φ ≡ ¬ ¬ φ₁$.
+∙~Case $φ ≡ ¬ ¬ φ₁$.
 \begin{equation*}
@@
 
-$\bullet$~Case $φ ≡ φ₁ ∧ φ₂$. We prove $Γ ⊢ φ₁$ and $Γ ⊢ φ₂$.
+∙~Case $φ ≡ φ₁ ∧ φ₂$. We prove $Γ ⊢ φ₁$ and $Γ ⊢ φ₂$.
 From the conjunction of φ₁ and φ₂, the expected result follows.
@@
 
-$\bullet$~Case $φ ≡ ¬ (φ₁ ∨ φ₂)$.
+∙~Case $φ ≡ ¬ (φ₁ ∨ φ₂)$.
 We prove $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
@@
 Let $\text{n} : \Nat$ be the complexity measure of the strip function defined
-in~(\ref{eq:strip-fixed}).
+in~\eqref{eq:strip-fixed}.
 Let $s₁$ and $s₂$ be the subgoals of the goal $φ$, that is,

### 2017-10-26 paper/sections/introduction.tex
[ paper ] fixed some corrections.

@@
 
-Reconstructing and verifying proofs delivered by automatic theorem provers
-(henceforth ATP) are non-trivial tasks.
-In the last decades, \ATPs is fast becoming a key instrument in 
-different disciplines (\eg~verifying cryptographic protocols for information security) and researchers have shown an increased interest to prove the validity of their deduction algorithms.
-One reason to say that is the bugs found in many ATPs~\cite{Keller2013,Bohme2011,Fleury2014}.
+An automatic theorem provers (henceforth \ATP) is a tool that intends to prove
+conjectures based on assumptions and hypothesis in a logic specification.
+Verifying proofs generated by \ATPs are non-trivial tasks.
+In the last decades, \ATPs are fast becoming a key instrument in
+different disciplines and real applications (\eg, verifying railway interlocking systems in~\cite{Kanso2012}).
+Therefore, researchers from academy and industry have shown an increased interest to prove the validity of their deduction algorithms.
+
+See for instance bugs found in ATPs in~\cite{Keller2013,Bohme2011,Fleury2014}.
 For that reason, in order to give confidence to the user of these systems,
-many ATPs has started to include in their outputs, the proof of their
+many ATPs have started to include in their outputs, a witness of their
 conclusions. However, existing research recognizes that in many cases these proofs encode non-trivial reasoning
 hard to reconstruct and therefore hard to verify. The proof-reconstruction
-address this problem and becomes in some cases a reverse engineering of the
-prover reasoning.
+address this problem.
+It becomes in mostly cases a reverse engineering to justify the prover reasoning.
+That happen when the reconstruction is made by another and not by
+the developers of the \ATP.
 
-Therefore, the proof replied by the prover and its quality play an important role for proof-reconstruction. To verify such a proof, it is necessary to have
+Therefore, the proof generated by the prover and its presentation play an important role for proof-reconstruction. To verify such a proof, it is necessary to have
 it in a consistent format, that is, a full script
@@
 service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
-provers were able to deliver proofs and fewer like \name{EProver} or \Metis 
-replied the proof in an admissible file format.
+provers were able to output proofs.
 
 One approach to address the proof-reconstruction
-is integrating the \ATP, the \emph{source} system, with a proof assistant, the 
+is integrating the \ATP, the \emph{source} system, with a proof-assistant, the
 \emph{target} system.
-The target system becomes in the proof checker. These proof assistants allow 
+The target system becomes in the proof checker. These proof-assistants allow
 us to define the formal language used in the proofs, \ie, operators, logic
 variables, axioms, and theorems. A proof-reconstruction tool provides such an
-integration, translating the replied generated by the prover into the formalism of the proof assistant.
+integration, translating the replied generated by the prover into the formalism of the proof-assistant.
 
-Previous studies have reported proof-reconstruction using proof assistants for classical logic where the development is at a mature stage.
-Even though we choose a proof assistant for type theory
-where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.
-Therefore the proof-reconstruction tool generates proof-terms by reconstructing the proof using the formalization
-the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:limitations-type-theory}.
+Previous studies have reported proof-reconstruction using proof-assistants
+based on classical logic where the development is at a
+mature stage~\cite{paulson2010three,hurlin07practical,kaliszyk2013}.
+
+Another approaches has been proposed for proof-reconstructing using
+the formalism of type theory.
+The reader can review~\cite{Bezem2002,armand2011,Ekici2017,kanso2016light}.
 
 In this paper, we describe how to reconstruct proofs in type theory
-replied by \Metis prover\footnote{v2.3 release 2017102}.
+generated by the \Metis prover\footnote{v2.3 release 2017102}~\cite{hurd2003first}.
 We ported the subset of the \Metis inference rules for the propositional
-fragment using a syntactical treatment of the logic.
-The \Metis reasoning was formalized in \Agda in~\cite{AgdaProp,AgdaMetis}.
-We built a proof-reconstruction tool named \Athena~\cite{Athena} that is able to generate \Agda\footnote{v2.5.3} proof-terms for \Metis derivations.
-We have avoided the use of propositions meanings towards a future work to support other logics
-but also contrast the usage of a deep embedding of the logic with
-a shallow embedding.
+fragment using a syntactical treatment of the logic. The \Metis reasoning was
+formalized in \Agda~\cite{agdateam} in~\cite{AgdaProp,AgdaMetis}. We built a
+proof-reconstruction tool named \Athena~\cite{Athena} written in \Haskell
+that is able to generate \Agda proof-terms for \Metis derivations.
 
@@
 In Section~\ref{sec:limitations-type-theory} some limitations of type theory
-are discussed for proof-reconstruction point view.
+are discussed from proof-reconstruction point view.
 In Section~\ref{sec:metis-language-and-proofs}, we introduce the
-\Metis prover and its deduction system.
-In Section~\ref{sec:proof-reconstruction}, we show our
-approach to reconstruct proofs deliver by \Metis.
+\Metis prover.
+In Section~\ref{sec:proof-reconstruction} we show our
+approach to reconstruct \Metis proofs.
 Related work is described in Section~\ref{sec:related-work}.
-Main findings and suggestion for future work is presented Section~\ref{sec:conclusions}.
+Conclusions and suggestions for future work are  presented in
+Section~\ref{sec:conclusions}.
 
@@
 
-The program and formalizations in \Agda mentioned in this paper are available
+The program and formalizations in \Agda and \Haskell mentioned in this paper are available
 as \verb!Git! repositories at \verb!Github!:
@@
 \begin{itemize}
-  \item The \Athena program to translate proofs generated by \Metis to \Agda code:
+  \item The \Athena program that translates proofs generated by \Metis to \Agda:
   \url{http://github.com/jonaprieto/athena}.
-  \item The \verb!agda-prop! library as a formal system in \Agda for propositional logic:
+  \item The \verb!agda-prop! library as a formalization in \Agda for propositional logic:
   \url{http://github.com/jonaprieto/agda-prop}.
-  \item The \verb!agda-metis! library as a formalization in \Agda to justify \Metis proofs in propositional
+  \item The \verb!agda-metis! library as a formalization in \Agda to justify \Metis proofs of propositional
   logic:

### 2017-10-26 paper/sections/limitations-type-theory.tex
[ paper ] fixed some corrections.

@@
 
-% In Section~\label{ssec:structural-recursion},
-% we describe how this observation is an issue from the type theory point of
-% view. In Section~\ref{ssec:intuitionistic-logic} we mention
-% the use intuitionistic-logic and its limitation.
+Even though we choose a proof-assistant for type theory
+where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.
+
+Therefore the proof-reconstruction tool generates proof-terms by reconstructing the proof using the formalization
+the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:limitations-type-theory}.
 
@@
 
-Since we pretend to reconstruct proofs replied by \Metis, and \Metis works
+Since we pretend to reconstruct proofs generated by \Metis, and \Metis works
 in classical logic,  we have included as an axiom, the

### 2017-10-26 paper/sections/metis-language-and-proofs.tex
[ paper ] fixed some corrections.

@@
 
-A proof delivered by \Metis encodes a natural
+A proof generated by \Metis encodes a natural
 deduction proof.
@@
 The proof graphs have at their root the conclusion
-$⊥$, since \Metis delivers proofs by refutation.
+$⊥$, since \Metis proofs are refutations.
 

### 2017-10-26 paper/sections/proof-reconstruction.tex
[ paper ] fixed some corrections.

@@
 Finally, we type-check the \Agda proof-term. If the type-checking
-success, the \TSTP derivation delivered by \Metis is correct
+success, the \TSTP derivation generated by \Metis is correct
 module \Agda and the proposed formalizations for the

### 2017-10-26 paper/sections/related-work.tex
[ bib ] Updated HOL reference.
[ paper ] fixed some corrections.

@@
 the reasoning presented in Section~\ref{ssec:workflow}.
-Nonetheless, his approach includes semantics reasoning that as we mentioned
-in the introduction differs completely from our proof-reconstruction approach.
+Nonetheless, his approach includes semantics reasoning. We have avoided the
+use of propositions meanings towards a future work to support other logics but
+also contrast the usage of a deep embedding of the logic with a shallow
+embedding.
 
@@
 prover \name{Gandalf} with the high-order theorem prover
-\name{HOL}~\cite{norrish2007hol}.
+\name{HOL}~\cite{norrish2017hol}.
 Its \verb!GANDALF_TAC! tactic is able to reconstruct \name{Gandalf} proofs

### 2017-10-26 paper/sections/introduction.tex
[ paper ] added some corrections.

@@
 
-An automatic theorem provers (henceforth \ATP) is a tool that intends to prove
+An automatic theorem prover (henceforth \ATP) is a tool that intends to prove
 conjectures based on assumptions and hypothesis in a logic specification.
@@
 In the last decades, \ATPs are fast becoming a key instrument in
-different disciplines and real applications (\eg, verifying railway interlocking systems in~\cite{Kanso2012}).
-Therefore, researchers from academy and industry have shown an increased interest to prove the validity of their deduction algorithms.
+different disciplines and real applications (\eg, verifying railway
+interlocking systems in~\cite{Kanso2012}).
+Therefore, researchers from academy and industry have shown an increased
+interest to prove the validity of their deduction algorithms since
+some bugs have been found in these
+tools~\cite{Keller2013,Bohme2011,Fleury2014}.
 
-See for instance bugs found in ATPs in~\cite{Keller2013,Bohme2011,Fleury2014}.
-For that reason, in order to give confidence to the user of these systems,
-many ATPs have started to include in their outputs, a witness of their
-conclusions. However, existing research recognizes that in many cases these proofs encode non-trivial reasoning
-hard to reconstruct and therefore hard to verify. The proof-reconstruction
-address this problem.
+For that reason, in order to give confidence to the \ATP users,
+many of these system have started to include in their outputs the derivations, witnesses, of their conclusions.
+However, existing research recognizes that in many cases these proofs encode
+non-trivial reasoning
+hard to reconstruct and therefore hard to verify~\cite{paulson2007source,Keller2013}.
+
+The proof-reconstruction address this problem.
 It becomes in mostly cases a reverse engineering to justify the prover reasoning.
-That happen when the reconstruction is made by another and not by
-the developers of the \ATP.
+That happen when the reconstruction is made by another and not by the developers of the \ATP.
 
-Therefore, the proof generated by the prover and its presentation play an important role for proof-reconstruction. To verify such a proof, it is necessary to have
-it in a consistent format, that is, a full script
-describing step-by-step with exhaustive details and without ambiguities, the derivation to get the proof.
-For classical propositional logic (henceforth \CPL) from a list of at least forty\footnote{\ATPs
-available from the web
-service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
-provers were able to output proofs.
+Therefore, the proof generated by the prover and its presentation play an
+important role for proof-reconstruction. To verify such a proof, it is
+necessary to have it in a consistent format, that is, a full script describing
+step-by-step with exhaustive details and without ambiguities, the derivation
+to get the proof. For classical propositional logic (henceforth \CPL) from a
+list of at least forty\footnote{\ATPs available from the web service
+\name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few provers were able to
+output proofs.
 
-One approach to address the proof-reconstruction
-is integrating the \ATP, the \emph{source} system, with a proof-assistant, the
-\emph{target} system.
-The target system becomes in the proof checker. These proof-assistants allow
-us to define the formal language used in the proofs, \ie, operators, logic
-variables, axioms, and theorems. A proof-reconstruction tool provides such an
-integration, translating the replied generated by the prover into the formalism of the proof-assistant.
+One approach to address the proof-reconstruction problem is integrating the
+\ATP, the \emph{source} system, with a proof-assistant, the \emph{target}
+system. The target system is the proof checker in charge to  verify the prover reasoning.
+These proof-assistants allow us to define the formal
+language used in the proofs, \ie, operators, logic variables, axioms, and
+theorems. A proof-reconstruction tool provides such an integration,
+translating the replied generated by the prover into the formalism of the
+proof-assistant.
 

### 2017-10-26 paper/sections/limitations-type-theory.tex
[ paper ] added some corrections.

@@
 \begin{notation}
+Types are written using small caps.
 We write the type judgments as $m : \abbre{M}$ to denote
 that $m$ has $\abbre{M}$ type.
-Types are written using small caps.
 We use \Prop for the type of propositions and the dependent type, $Γ ⊢ φ$ for
@@
 
-Algorithms based on general recursions can not be translated
+Algorithms based on general recursion can not be translated
 directly in type theory since it is not a guarantee they terminate. For that
@@
 
-General recursive functions can be translated into structurally recursive
-functions by using for instance, the \emph{Bounded Recursion} technique
-presented in~\cite{Bertot2004}. For a yet another methods, we refer
+General recursive functions can be rewrote into structurally recursive
+functions by using for instance, the \emph{bounded recursion} technique.
+For a yet another methods, we refer
 the reader to \cite{Coquand1992,Abel2002,Bove2005}.
@@
 
-In~\eqref{eq:uh-definition}, the first two equation
+In~\eqref{eq:uh-definition}, the first two equations
 call on arguments no structurally smaller.
@@
 
-We bounded the recursion calls in~\eqref{eq:uh-structured} with \Nat type argument. This natural number represents the complexity measure of $\fuh_{0}$
+We bounded the recursion calls in~\eqref{eq:uh-structured} with a \Nat argument. This natural number represents the complexity measure of $\fuh_{0}$
 function.
 
-Recall the \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
+The \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
 and presented in \cite{VanDalen1994} as \emph{the rank for a
 proposition}, is a function $\Prop \to \Nat$ that assigns a natural
-number for a proposition $φ$ like the following $\frank$ function.
+number to a formula like we do with the following $\frank$ function.
 The symbols $c_{¬}$ and $c_{\square}$ are non-negative integer

### 2017-10-26 paper/sections/metis-language-and-proofs.tex
[ paper ] added some corrections.

@@
 \end{equation*}
-\caption{CPL inference rules of the \texttt{Metis} prover.}
+\caption{Inference rules of the \texttt{Metis} prover.}
 \label{fig:metis-inferences}
@@
 
-      Strip a goal into subgoals
-      &\texttt{strip}
+      \texttt{strip}
+      &Strip a goal into subgoals
       &\ref{thm:strip}
@@
 
-      Takes a formula from a conjunction
-      &\texttt{conjunct}
+      \texttt{conjunct}
+      &Takes a formula from a conjunction
       &\ref{thm:conjunct}
@@
 
-      A general form of the resolution theorem
-      &\texttt{resolve}
+      \texttt{resolve}
+      &A general form of the resolution theorem
       &\ref{thm:resolve}
@@
 
-      Performs clausification
-      &\texttt{clausify}
+      \texttt{clausify}
+      &Performs clausification
       &\ref{thm:clausify}
@@
 
-      Normalization of the formula
-      &\texttt{canonicalize}
+      \texttt{canonicalize}
+      &Normalization of the formula
       &\ref{thm:canonicalize}
@@
 
-      Simplify definitions and theorems
-      &\texttt{simplify}
+      \texttt{simplify}
+      &Simplify definitions and theorems
       &\ref{thm:simplify}

### 2017-10-26 paper/sections/related-work.tex
[ paper ] added some corrections.

@@
 
-In type theory, for \Agda and  for the same propositional fragmented used in this paper,
-we found the proof-reconstruction proposed by \citeauthor{Kanso2012}
-in~\cite{Kanso2012,kanso2016light}. The author present an approach similar to
+For type theory using \Agda and for the same propositional fragmented used in this paper, we found the proof-reconstruction proposed by \citeauthor{Kanso2012} in~\cite{Kanso2012,kanso2016light}.
+The author present an approach similar to
 the reasoning presented in Section~\ref{ssec:workflow}.

### 2017-10-26 paper/sections/metis-language-and-proofs.tex
[ paper ] lots of changes.

@@
 
-\Metis is an automatic theorem prover written in \len{ML} for
-first-order logic with equality developed by
-\citeauthor{hurd2003first}~\cite{hurd2003first}. This prover is
-suitable for proof reconstruction since it provides well-documented
-proofs to justify its deduction steps from the basis of only six
-inference rules. In Fig.~\ref{fig:metis-inferences}, we show the three
-\Metis rules for propositional logic.
+\Metis is an automatic theorem prover for first-order logic with equality developed by
+ \citeauthor{hurd2003first}~\cite{hurd2003first}.
+This prover is suitable for proof reconstruction since it provides well-documented proofs to justify its deduction steps from the basis of only six inference rules.
+In Fig.~\ref{fig:metis-inferences}, we show the three \Metis rules for propositional logic.
 
@@
     \hline
-    \textbf{\Metis rule name} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
+    \textbf{\Metis Rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
 

### 2017-10-26 paper/sections/proof-reconstruction.tex
[ paper ] lots of changes.

@@
 The proof-reconstruction approach proposed consists of a series
-of steps similar to the workflow presented by \citeauthor{sultana2015} in
-\cite{sultana2015}. This process is a translation from a source
+of steps similar to the workflow presented by
+\citeauthor{sultana2015}~\cite{sultana2015}.
+This process is a translation from a source
 system to a target system. In our case, the system of origin, the
@@
 
-Now, we have finished the formalization of every inference rule in
+We have finished the formalization of every inference rule in
 a \Metis proof, we are able to justify step-by-step any proof

### 2017-10-26 paper/sections/proof-reconstruction/clausify.tex
[ paper ] added some corrections.
[ paper ] lots of changes.

@@
 The \clausify rule transforms a
-propositional formula into its clausal normal form, a conjunction
-of clauses. A \emph{clause} is the disjunction of zero or more
-literals.
+propositional formula into its clausal normal form.
 It is important to notice that this kind of conversion between one formula
@@
 \begin{myexample}
-In the following \Metis \TSTP derivation, we see how
-\clausify expands the\texttt{norm0} formula to get \texttt{norm1} formula
-by using distributive laws included in the conjunctive normal form conversion.
+In the following \TSTP derivation by \Metis, we see how
+\clausify transform the \texttt{norm0} formula to get \texttt{norm1} formula.
 
 \begin{verbatim}
-fof(a1, axiom, p ⇒ (q ∧ r)).
-...
-fof(norm0, ¬ p ∨ (q ∧ r), inf(canonicalize, [a1])).
+fof(norm0, ¬ p ∨ (q ∧ r) ...
 fof(norm1, (¬ p ∨ q) ∧ (¬ p ∨ r), inf(clausify, [norm0])).
-...
 \end{verbatim}
@@
 \begin{myremark}
-The \clausify rule is often preceded by \canonicalize.
+The \clausify rule is often preceded by the \canonicalize rule.
 Both rules perform \emph{Clausification} that introduces
 into the problem axioms and definitions in the domain of the solution.
-The clausification algorithms is mainly described on paper by
+The clausification is widely described by
 \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.

### 2017-10-26 paper/sections/introduction.tex
Improved introduction.

@@
 
-An automatic theorem prover (henceforth \ATP) is a tool that intends to prove
-conjectures based on assumptions and hypothesis in a logic specification.
-Verifying proofs generated by \ATPs are non-trivial tasks.
-In the last decades, \ATPs are fast becoming a key instrument in
-different disciplines and real applications (\eg, verifying railway
-interlocking systems in~\cite{Kanso2012}).
-Therefore, researchers from academy and industry have shown an increased
-interest to prove the validity of their deduction algorithms since
-some bugs have been found in these
-tools~\cite{Keller2013,Bohme2011,Fleury2014}.
+An automatic theorem prover (henceforth \ATP) is a program that
+intends to prove conjectures from axioms and inference rules of some
+logical system. In the last decades, \ATPs are fast becoming a key
+instrument in different disciplines and real applications (\eg,
+verifying railway interlocking systems~\cite{Kanso2012}). Since some
+bugs have been found in these programs (see, for example,
+\cite{Keller2013,Bohme2011,Fleury2014}), researchers and users from
+academy and industry have shown an increased interest to
+\emph{formally} prove the validity of \ATPs' results.
 
-For that reason, in order to give confidence to the \ATP users,
-many of these system have started to include in their outputs the derivations, witnesses, of their conclusions.
-However, existing research recognizes that in many cases these proofs encode
-non-trivial reasoning
-hard to reconstruct and therefore hard to verify~\cite{paulson2007source,Keller2013}.
+In order to give confidence to the \ATP users, many of these system
+have started to include in their outputs the full derivations
+associated to the proved theorems. However, existing research
+recognizes that in many cases these proofs encode non-trivial
+reasoning hard to reconstruct and therefore hard to
+verify~\cite{paulson2007source,Keller2013}.
 
-The proof-reconstruction address this problem.
-It becomes in mostly cases a reverse engineering to justify the prover reasoning.
-That happen when the reconstruction is made by another and not by the developers of the \ATP.
+Proof-reconstruction address this problem. It becomes in mostly cases
+a reverse engineering task to verify the prover reasoning. That
+usually happen when the reconstruction is made by another and not by
+the developers of the \ATP. The presentation of the proofs generated
+by the prover play an important role in proof-reconstruction. To
+verify such a proof, it is convenient to have it in a consistent
+format, that is, a full script describing step-by-step with exhaustive
+details and without ambiguities, the derivation to get the proof. For
+classical propositional logic (henceforth \CPL) from a list of at
+least forty \ATPs---available from the Web service \name{SystemOnTPTP}
+of the TPTP World---just few of them show their proofs.
 
-Therefore, the proof generated by the prover and its presentation play an
-important role for proof-reconstruction. To verify such a proof, it is
-necessary to have it in a consistent format, that is, a full script describing
-step-by-step with exhaustive details and without ambiguities, the derivation
-to get the proof. For classical propositional logic (henceforth \CPL) from a
-list of at least forty\footnote{\ATPs available from the web service
-\name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few provers were able to
-output proofs.
+One approach to address the proof-reconstruction problem is
+integrating the \ATP, the \emph{source} system, with a
+proof-assistant, the \emph{target} system. The target system is the
+proof \emph{checker} in charge to verify the source system reasoning.
+These proof-assistants allow us to formalize the logical system used
+in the proofs, \ie, logical constants, axioms, inference rules, and
+theorems. A proof-reconstruction tool provides such an integration,
+translating the derivation generated by the prover into the formalism
+of the proof-assistant.
 
-One approach to address the proof-reconstruction problem is integrating the
-\ATP, the \emph{source} system, with a proof-assistant, the \emph{target}
-system. The target system is the proof checker in charge to  verify the prover reasoning.
-These proof-assistants allow us to define the formal
-language used in the proofs, \ie, operators, logic variables, axioms, and
-theorems. A proof-reconstruction tool provides such an integration,
-translating the replied generated by the prover into the formalism of the
-proof-assistant.
+Previous studies have reported proof-reconstruction using
+proof-assistants based on higher-order logic where the development is
+at a mature
+stage~\cite{paulson2010three,hurlin07practical,kaliszyk2013}. Another
+approaches has been proposed for proof-reconstructing using type
+theory~\cite{Bezem2002,armand2011,Ekici2017,kanso2016light}.
 
-Previous studies have reported proof-reconstruction using proof-assistants
-based on classical logic where the development is at a
-mature stage~\cite{paulson2010three,hurlin07practical,kaliszyk2013}.
-
-Another approaches has been proposed for proof-reconstructing using
-the formalism of type theory.
-The reader can review~\cite{Bezem2002,armand2011,Ekici2017,kanso2016light}.
-
-In this paper, we describe how to reconstruct proofs in type theory
-generated by the \Metis prover\footnote{v2.3 release 2017102}~\cite{hurd2003first}.
-We ported the subset of the \Metis inference rules for the propositional
-fragment using a syntactical treatment of the logic. The \Metis reasoning was
-formalized in \Agda~\cite{agdateam} in~\cite{AgdaProp,AgdaMetis}. We built a
-proof-reconstruction tool named \Athena~\cite{Athena} written in \Haskell
-that is able to generate \Agda proof-terms for \Metis derivations.
+We describe a formal reconstruction of proofs generated by the \Metis
+prover~\cite{hurd2003first}---our source system---in type theory. We
+formalize the subset of the \Metis inference rules for the
+propositional logic fragment using a syntactical treatment of the
+logic. The \Metis reasoning was formalized in
+\Agda~\cite{agdateam}---our target system---in two
+libraries~\cite{AgdaProp,AgdaMetis} and we implemented a
+proof-reconstruction tool named \Athena~\cite{Athena} written in
+\Haskell that is able to generate \Agda proof-terms for \Metis
+derivations.
 
@@
 
-The program and formalizations in \Agda and \Haskell mentioned in this paper are available
-as \verb!Git! repositories at \verb!Github!:
+The source codes accompanying this paper (programs, libraries, and
+examples) are available as repositories at \verb!GitHub!:
 
@@
   \url{http://github.com/jonaprieto/athena}.
-  \item The \verb!agda-prop! library as a formalization in \Agda for propositional logic:
+  \item The \verb!agda-prop! library as a formalization in \Agda for
+    classical propositional logic:
   \url{http://github.com/jonaprieto/agda-prop}.
-  \item The \verb!agda-metis! library as a formalization in \Agda to justify \Metis proofs of propositional
-  logic:
+\item The \verb!agda-metis! library as a formalization in \Agda to
+  justify \Metis proofs of classical propositional logic:
   \url{http://github.com/jonaprieto/agda-prop}.
@@
 
+The proof-reconstruction was carried on for \Metis~v2.3
+release~2017102, and the accompanying source code was tested with
+\Agda~v2.3, \Agda standard library~v0.14 and \prg{GHC}~v.8.2.1.
+
 \end{document}

### 2017-10-26 paper/sections/proof-reconstruction.tex
[ paper ] lots of changes.

@@
 version of the rule implemented in \cite{AgdaProp,AgdaMetis}.
+We use \Source and \Target as synonyms of \Prop type in the
+function type to refer that \Source is the type of the input formula in
+the function also called the \emph{source} formula in the inference rule and
+\Target is the type of the expected formula also called \emph{target} formula after using the rule with the source formula.
 \end{notation}
@@
   \begin{aligned}
-  &\hspace{.495mm}\fconjunct : \Prop → \Prop → \Prop\\
+  &\hspace{.495mm}\fconjunct : \Source → \Target → \Prop\\
   &\begin{array}{ll}
@@
 \begin{itemize}
-  \item[∙] $φ$ is the \emph{source} formula from a previous deducted derivation.
-  \item[∙] $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
+  \item[∙] $φ$ is the source formula from a previous deducted derivation.
+  \item[∙] $ψ$ is the target formula. The expected result of \texttt{rule}.
 \end{itemize}

### 2017-10-26 paper/sections/proof-reconstruction/resolve.tex
[ paper ] lots of changes.

@@
 We solve this issue in Lemma~\ref{lem:reorder-and-or} by
-using the $\fconjunct_{∨}$ function defined in~\eqref{eq:conjunct-or}.
+using the $\fconjunctor$ function defined in~\eqref{eq:conjunct-or}.
+This purpose of this function consists of extract a disjunction from
+a conjunction, but without matter the order atoms in the disjunction.
 
@@
   \label{lem:conjunct-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fconjunct_{∨}~φ~ψ$ where,
+  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fconjunctor~φ~ψ$ where,
   \begin{equation}
@@
     \label{eq:conjunct-or}
-      &\fconjunct_{∨} : \Prop → \Prop \to \Prop\\
-      &\fconjunct_{∨}~φ~ψ =
+      &\fconjunctor : \Source → \Target \to \Prop\\
+      &\fconjunctor~φ~ψ =
       \begin{cases}
@@
         ψ, &\text{ if } ψ ≡ \freorder_{∨}~φ~ψ\\
-        ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \fconjunct_{∨}~φ~ψ₁,\\
+        ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \fconjunctor~φ~ψ₁,\\
            &\text{ and } ψ₂ ≡ \freorder_{∨}~φ~ψ₂\\
-        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunct_{∨}~φ₁~ψ \\
-        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunct_{∨}~φ₂~ψ \\
+        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunctor~φ₁~ψ \\
+        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunctor~φ₂~ψ \\
         φ, &\text{ otherwise.}
@@
   \label{lem:reorder-and-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$ where,
+  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$ where,
    \begin{align}
@@
       \label{eq:reorder-and-or}
-      &\freorder_{∧∨} : \Prop \to \Prop \to \Prop\\
+      &\freorder_{∧∨} : \Source \to \Target \to \Prop\\
       &\freorder_{∧∨}~φ~ψ=
@@
           φ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
-          \fconjunct_{∨}~φ~ψ &\text{ otherwise.}
+          \fconjunctor~φ~ψ &\text{ otherwise.}
         \end{cases}
@@
 of an atom (negative literal).
+
+\begin{myremark}
+We use \Lit as synonym of \Prop type to refer literals.
+\end{myremark}
+
 The positive literal $ℓ$ must occur in
@@
   \label{thm:resolve}
-  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, let $ℓ$ be a literal $ℓ : \Prop$, and $ψ : \Prop$ then
+  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, let $ℓ$ be a literal $ℓ : \Lit$, and $ψ : \Target$ then
   $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$ where,
@@
   \label{eq:resolve}
-    &\fresolve : \Prop \to \Prop \to \Prop \to \Prop \to \Prop\\
+    &\fresolve : \Source \to \Source \to \Lit \to \Target \to \Prop\\
     &\fresolve~φ₁~φ₂~ℓ~ψ =

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
Fixed figure.
[ paper ] lots of many changes.

@@
 
-\Metis is an automatic theorem prover for first-order logic with equality developed by
- \citeauthor{hurd2003first}~\cite{hurd2003first}.
+\Metis is an automatic theorem prover for first-order logic with equality
+developed by  \citeauthor{hurd2003first}~\cite{hurd2003first}.
 This prover is suitable for proof reconstruction since it provides well-documented proofs to justify its deduction steps from the basis of only six inference rules.
@@
     \AxiomC{}
-    \RightLabel{assume $L$}
+    \RightLabel{assume $φ$}
     \UnaryInfC{$Γ ⊢ φ ∨ ¬ φ$}
@@
 \end{equation*}
-\caption{Inference rules of the \texttt{Metis} prover.}
+\caption{Propositional logic inference rules of the \texttt{Metis} prover.}
 \label{fig:metis-inferences}
@@
 
-\begin{remark}
+\begin{myremark}
 We address proof-reconstruction in this paper for refutation proofs.
@@
 \Metis converts to \abbre{CNF} clauses to look for a refutation.
-\end{remark}
+\end{myremark}
 
@@
 
-\begin{myexample}
+\begin{myexample}\hspace{10cmm}\\
 
@@
 
-In the script above, \strip is for example the name of the inference.
+In the script above, \strip is the name of the inference.
 It has no arguments and derives from one parent node named  \verb!goal!. The
@@
 
-We adopt a customized \TSTP syntax to keep as short as possible the \Metis derivations for increasing the readability in this paper.
+\begin{notation}
+
+We adopt a customized \TSTP syntax to keep as short as possible the \Metis
+derivations for increasing the readability in this paper.
 
@@
 empty fields in the inference information, we shorten names as long as possible, we delete the \verb!role! field when the role is
-\verb!plain! and we use the math symbols to express the formulas.
+\verb!plain! and we use the ⊤, ⊥, ¬, ∧, ∨, ⇒, ⇔ symbols to express the formulas.
 
@@
 \end{myexamplenum}
+\end{notation}
 
@@
 deduction proof.
-With these inference rules as the only valid deduction steps, \Metis
+With the inference rules in Fig.~\ref{tab:agda-metis-table}
+as the only valid deduction steps, \Metis
 attempts to prove conjectures by refutation (\eg,

### 2017-10-27 paper/sections/proof-reconstruction.tex
[ paper ] lots of many changes.

@@
 The remainder of this section will be devoted to present a formal description
-in type theory of each rule presented in Table~\ref{tab:agda-metis-table} using
-the pattern present in the example above.
+in type theory of each rule presented in the same order in Table~\ref{tab:agda-metis-table} using the pattern present in the example above.
 

### 2017-10-27 paper/sections/proof-reconstruction/clausify.tex
[ paper ] lots of changes.
[ paper ] lots of many changes.

@@
 
-The \clausify rule transforms a
-propositional formula into its clausal normal form.
+The \clausify rule transforms a formula into its clausal normal form.
 It is important to notice that this kind of conversion between one formula
@@
 \label{thm:clausify}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fclausify~φ~ψ$, where,
+  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fclausify~φ~ψ$, where,
 
@@
   \begin{aligned}
-  &\hspace{.495mm}\fclausify : \Prop → \Prop → \Prop\\
+  &\hspace{.495mm}\fclausify : \Source → \Target → \Prop\\
   &\begin{array}{llll}

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] lots of many changes.

@@
 \label{lem:build-or}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fbuild_{∨}~φ~ψ$ where,
+  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fbuild_{∨}~φ~ψ$ where,
 \begin{equation}
@@
   \label{eq:build-or}
-  &\fbuild_{∨} : \Prop → \Prop → \Prop\\
+  &\fbuild_{∨} : \Source → \Target → \Prop\\
   &\fbuild_{∨}~φ~ψ~ =%\\
@@
 \label{lem:sbuild-or}
-If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \fsbuild_{∨}~φ~ψ$ where,
+If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fsbuild_{∨}~φ~ψ$ where,
 \begin{equation}
@@
  \begin{aligned}
-     &\hspace{.495mm}\fsbuild_{∨} : \Prop → \Prop → \Prop\\
+     &\hspace{.495mm}\fsbuild_{∨} : \Source → \Target → \Prop\\
     &\begin{array}{lll}
@@
   \label{lem:reorder-or}
-  If $Γ ⊢ φ$ and $ψ: \Prop$ then $Γ ⊢ \freorder_{∨}~φ~ψ~$ where,
+  If $Γ ⊢ φ$ and $ψ: \Target$ then $Γ ⊢ \freorder_{∨}~φ~ψ~$ where,
   \begin{align}
@@
     \label{eq:reorder-or}
-    &\freorder_{∨} : \Prop \to \Prop \to \Prop\\
+    &\freorder_{∨} : \Source \to \Target \to \Prop\\
     &\freorder_{∨}~φ~ψ~= \fsbuild_{∨}~(\fassoc_{∨}~φ)~ψ.
@@
   \label{lem:reorder-and}
-  If $Γ ⊢ φ$ and $ψ : \Prop$ then $Γ ⊢ \freorder_{∧}~φ~ψ$ where,
+  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \freorder_{∧}~φ~ψ$ where,
     \begin{align}
@@
       \label{eq:reorder-and}
-        &\freorder_{∧} : \Prop → \Prop \to \Prop\\
+        &\freorder_{∧} : \Source \to \Target \to \Prop\\
         &\freorder_{∧}~φ~ψ =

### 2017-10-27 paper/sections/conclusions-and-future-work.tex
[ paper ] fixed some corrections.
Fixed typo.
Cosmetic changes.

@@
 that generates \Agda proof-terms of \Metis derivations.
-\Agda files delivered by this translator imports
+\Agda files generated by this translator imports
 \Agda formalizations of the \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
@@
 
-One of the main contribution of this study was
-increasing the trustworthiness of the automatic prover \Metis.
-Justifying a proof by a theorem prover
-has a real significant impact for these automatic tools.
-The reverse engineering task to understand the prover reasoning
-can reveal important issues or bugs
-in many parts of these systems (\eg, preprocessing, reasoning, or
-deduction modules). During this research, we had the opportunity
-to contribute to \Metis by reporting some bugs\footnote{Issues No.~2,
-No.~4. and commit \name{8a3f11e} in the \Metis' official repository
-\url{https://github.com/gilith/metis}}.
+One of the main contribution of this study was increasing the
+trustworthiness of the automatic prover \Metis.  Justifying a proof by
+a theorem prover has a real significant impact for these automatic
+tools.  The reverse engineering task to understand the prover
+reasoning can reveal important issues or bugs in many parts of these
+systems (\eg, preprocessing, reasoning, or deduction modules). During
+this research, we had the opportunity to contribute to \Metis by
+reporting some bugs---see Issues No.~2, No.~4. and commit
+\name{8a3f11e} in \Metis' official
+repository.\footnote{\url{https://github.com/gilith/metis}.}
 Fortunately, all these problems were fixed quickly by
-\citeauthor{hurd2003first} in the \Metis 20170810 release.
+\citeauthor{hurd2003first} in \Metis~2.3 (release~20170822).
 

### 2017-10-27 paper/sections/conclusions-and-future-work.tex
[ paper ] lots of changes.

--- 2017-10-26 paper/sections/conclusions-and-future-work.tex
@@
 that generates \Agda proof-terms of \Metis derivations.
-\Agda files delivered by this translator imports
+\Agda files generated by this translator imports
 \Agda formalizations of the \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
-We tested successful using this tool and \Agda as we
-described in Section~\ref{sec:proof-reconstruction} over a subset of
-propositional problems from~\cite{Prieto-Cubides2017}.
+% We tested successful using this tool and \Agda as we
+% described in Section~\ref{sec:proof-reconstruction} over a subset of
+% propositional problems from~\cite{Prieto-Cubides2017}.
 
@@
 \begin{itemize}
-  \item by investigating the consequences of removing \clausify
-inference by strengthen \canonicalize rule in Theorem~\ref{thm:canonicalize}
+  \item by investigating the consequences of removing the \clausify
+inference rule by the \canonicalize rule.
   \item by increasing the coverage of the \simplify rule. Since is fairly

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
Cosmetic changes.
[ paper ] lots of changes.

@@
 The \TPTP language is the input language to encode problems used by \Metis.
-It includes the first-order form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf}) formats~\cite{sutcliffe2009,Sicard-Ramirez2016}.
+It includes the first-order form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf}) formats~\cite{sutcliffe2009}.
 The \TPTP syntax describes a well-defined grammar to handle annotated
@@
 \begin{verbatim}
-language(name, role, formula).
+  language(name, role, formula).,
 \end{verbatim}
 
-Where the \name{language} can be \name{fof} or \name{cnf}. The \name{name}
+where the \name{language} can be \name{fof} or \name{cnf}. The \name{name}
 serves to identify the formula within the problem. Each formula
@@
 \name{conjecture}, \name{definition}, \name{plain} or an \name{hypothesis}.
-The formulas include the constants \verb!$true!
-and \verb!$false!, negation unary operator (\verb!~!), and the binary connectives (\verb!&!, \verb!|!, \verb!=>!, \verb!<=>!) to represent $⊤, ⊥, ¬, ∧, ∨, ⇒, ⇔$ respectively.
+The formulas include the constants \verb!$true! and \verb!$false!, negation
+unary operator (\verb!~!), and the binary connectives (\verb!&!, \verb!|!,
+\verb!=>!, \verb!<=>!) to represent $⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$,
+and $⇔$ respectively.
 
@@
 The \TSTP language is an output language for derivations of
-ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006,Sicard-Ramirez2016}.
+ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}.
 A \TSTP derivation is a directed acyclic graph, a proof tree,
@@
 inferred from the parent formulas. The root is the final derived formula,
-such a derivation is a list of annotated formulas with the following form.
+such a derivation is a list of annotated formulas with the following form:
 
@@
 
-Where the \name{source} field is an inference record with the following
+where the \name{source} field is an inference record with the following
 pattern:
@@
 
-\begin{myexample}\hspace{10cmm}\\
+\begin{myexample}
+
+In the script below, \strip is the name of the inference.
+It has no arguments and derives from one parent node named  \verb!goal!. The
+result of this inference when it applies to the \verb!goal! formula is
+\verb!p!.
 
@@
 \end{verbatim}
-
-In the script above, \strip is the name of the inference.
-It has no arguments and derives from one parent node named  \verb!goal!. The
-result of this inference when it applies to the \verb!goal! formula is
-\verb!p!.
-
 \end{myexample}

### 2017-10-27 paper/sections/proof-reconstruction/conjunct.tex
[ paper ] fixing last suggestions.
[ paper ] canon ==> simplify-and simplify-or.
minor fixed.
more fixes.
[ paper ] using sans serif.
[ paper ] bullet symbol.
[ paper ] lots of changes.
Cosmetic changes.

@@
 \begin{verbatim}
-fof(p1, p & q & (r | ~ p), inf(canonicalize, [x])).
+  fof(p1, p ∧ q ∧ (r ∨ ¬ p), inf(canonicalize, [x])).
   fof(p2, q, inf(conjunct, [p1])).
-fof(p3, (r | ~ p), inf(conjunct, [p1])).
+  fof(p3, (r ∨ ¬ p), inf(conjunct, [p1])).
 \end{verbatim}
 
-In the first formula, \verb!p & q & (r | ~ p)!, we find a left-associative
+In the first formula, $p ∧ q ∧ (r ∨ ¬ p)$, we find a left-associative
 conjunction named \verb!p1!.
-\conjunct extracts \verb!q! from the \verb!p1! using a left
+The \conjunct rule extracts $q$ from the \verb!p1! using a left
 projection (∧-proj₁) follow by a right projection (∧-proj₂).
-\conjunct extracts \verb!r | ~ p! by using right projection
+After, the \conjunct rule extracts $r ∨ ¬ p$ by using a right projection
 on \verb!p1!.
@@
   \label{thm:conjunct}
-  If $Γ ⊢ φ$ and $ψ  : \Prop$ then $Γ ⊢ \fconjunct~φ~ψ$, where,
+  If $Γ ⊢ φ$ and $ψ  : \Target$ then $Γ ⊢ \fconjunct~φ~ψ$ where,
   \begin{equation*}
@@
   \begin{aligned}
-  &\hspace{.495mm}\fconjunct : \Prop \to \Prop \to \Prop\\
+  &\hspace{.495mm}\fconjunct : \Source \to \Target \to \Prop\\
   &\begin{array}{llll}
@@
 \begin{itemize}
-\item[$\bullet$] Case $φ ≡ ψ$. $Γ ⊢ \fconjunct~φ~ψ$ normalizes to $Γ ⊢ ψ$.
+\item[∙] Case $φ ≡ ψ$. $Γ ⊢ \fconjunct~φ~ψ$ normalizes to $Γ ⊢ ψ$.
 Then, we get the desire conclusion by applying the $\fsubst$ lemma.
-\item[$\bullet$] Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct~φ_{i}~ψ$ for some $i = 1,\ 2$, then,
+\item[∙] Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct~φ_{i}~ψ$ for some $i = 1,\ 2$, then,
 
@@
   \UnaryInfC{$Γ ⊢ φ_{i}$}
-  \RightLabel{by hyp.}
+  \RightLabel{by~ind.~hyp.}
   \UnaryInfC{$Γ ⊢ \fconjunct~φ_{i}~ψ$}
   \AxiomC{$ψ ≡ \fconjunct~φ_{i}~ψ$}
-  \RightLabel{subst}
+  \RightLabel{\fsubst}
   \BinaryInfC{$Γ ⊢ ψ$}
@@
 \end{equation*}
-\item[$\bullet$] Otherwise, the last case follows trivially.
+\item[∙] Otherwise, the last case follows from the hypothesis.
 \end{itemize}

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
Cosmetic changes.
[ paper ] lots of changes.

@@
 using the $\fconjunctor$ function defined in~\eqref{eq:conjunct-or}.
-This purpose of this function consists of extract a disjunction from
-a conjunction, but without matter the order atoms in the disjunction.
+The purpose of this function consists of extracting a disjunction from
+a conjunction, but without matter the order of inner disjunction.
 
@@
 
-\begin{myremark}
+\begin{notation}
 We use \Lit as synonym of \Prop type to refer literals.
-\end{myremark}
+\end{notation}
 
@@
 we can use Theorem \ref{thm:resolve} to derive $Γ ⊢ p ∨ q$.
-Let be $φ₁ ≡ p ∨ q ∨ r$ and $φ₂ ≡ ¬ r ∨ p ∨ q$.
+% Let be $φ₁ ≡ p ∨ q ∨ r$ and $φ₂ ≡ ¬ r ∨ p ∨ q$.
 
@@
   \RightLabel{by (\ref{eq:resolve})}
-  \UnaryInfC{$Γ ⊢ \frsol~(\freorder_{∨}~φ₁~(r ∨ (p ∨ q))~∧~\freorder_{∨}~φ₂~(¬ r ∨ (p ∨ q))$}
+  \UnaryInfC{$Γ ⊢ \frsol~(\freorder_{∨}~(p ∨ q ∨ r)~(r ∨ (p ∨ q))~∧~\freorder_{∨}~(¬ r ∨ p ∨ q)~(¬ r ∨ (p ∨ q))$}
   \RightLabel{by (\ref{eq:reorder-or})}

### 2017-10-27 paper/sections/proof-reconstruction/strip.tex
Cosmetic changes.
[ paper ] lots of changes.

@@
 
-The \fstrip₀ function yields the conjunction of subgoals that implies the goal of the problem in the \Metis \TSTP derivations but is not a structurally recursive
+The $\fstrip₀$ function yields the conjunction of subgoals that implies the goal of the problem in the \Metis \TSTP derivations but is not a structurally recursive
 function.  Instead, we present its structural recursive version
@@
 \fstrip₁ &(¬ (φ₁ ⇒ φ₂)) &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~(¬ φ₂)~n)\\
-\fstrip₁ &(¬ ¬ φ₁)      &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n)\\
+\fstrip₁ &(¬ (¬ φ₁))      &(\suc~n) &= \fuh~(\fstrip₁~φ₁~n)\\
 \fstrip₁ &(¬ ⊥)         &(\suc~n) &= ⊤\\
@@
 In a similar way as we define $\fuh_{cm}$ in~\eqref{eq:uh-complexity}, we define
-$\fstrip_{cm}$ as the complexity measure for $\fstrip₀$ function. As expected,
-the \fstrip function is defined as follows.
+$\fstrip_{cm}$ as the complexity measure for the $\fstrip₀$ function.
+Then we define the \fstrip function is defined as follows.
 
@@
 in~\eqref{eq:strip-fixed}.
-If $Γ ⊢ \fstrip₁~φ~n$ then $Γ ⊢ φ$.
+If $Γ~⊢~\fstrip₁~φ~n$ then $Γ~⊢~φ$.
 \end{mainlemma}
@@
 
-∙~Case $φ ≡ ¬ ¬ φ₁$.
+∙~Case $φ ≡ ¬ (¬ φ₁) $.
 \begin{equation*}
   \begin{bprooftree}
- \AxiomC{$Γ ⊢ \fstrip₁~(¬¬φ₁)~(\suc~n)$}
+ \AxiomC{$Γ ⊢ \fstrip₁~(¬(¬φ₁))~(\suc~n)$}
   \RightLabel{by~(\ref{eq:strip-fixed})}

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] lots of changes.

--- 2017-10-26 paper/sections/limitations-type-theory.tex
@@
 
-\section{Limitations of Type Theory}
-\label{sec:limitations-type-theory}
+\section{Type Theory}
+\label{sec:type-theory}
+
+Type theory is a formalism [TODO]
 
@@
 Therefore the proof-reconstruction tool generates proof-terms by reconstructing the proof using the formalization
-the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:limitations-type-theory}.
+the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:type-theory}.
 
@@
 The bounded technique defines a new structural recursive function based on
-the general recursive function by adding an argument to the function.
+the general recursive function by adding an argument.
 The new argument is the \emph{bound}, a natural number given by the
@@
 the number of times the function needs to call itself to get the
-expected outcome~\cite{Bertot2004}.
+expected outcome.
 
@@
 The type of natural numbers is called \Nat, and it is defined as
-usual, where \zero and \suc are its data constructors. We use names
-and symbols of the arithmetic operations as usual.
+usual, where $\zero$ and $\suc$ are its data constructors. We use names
+and symbols for the arithmetic operations as usual ($+$, $-$, $*$).
 We include syntax sugar for $\zero$, $\suc$, $\suc~\zero$,
@@
 
-Therefore, one approach to guarantee a structural recursive function based on
-a general recursive function $\rm{f}:~\Prop~\to~\Prop$ is to formulate a new function $\rm{f}^{*}~:~\Prop~\to~\Nat~\to~\Prop$ where all of its recursive calls are done on smaller arguments.
+Hence, one approach to define a structural recursive function based on
+a general recursive function $\rm{f}:~\Prop~\to~\Prop$ is to formulate a new
+function $\rm{f}^{*}~:~\Prop~\to~\Nat~\to~\Prop$ where all of its recursive
+calls are done on smaller arguments.
 
@@
 
-Let us consider the following example to exhibit the bounded technique
-mentioned above for the \fuh function. This function is used for reconstructing
-the \Metis \strip inference rule in Section~\ref{sssec:strip-a-goal}.
+Let us consider the following example to show the bounded recursion technique
+for the \fuh function. This function is used for reconstructing
+a \Metis inference rule in Section~\ref{sssec:strip-a-goal}.
 
@@
   \begin{bprooftree}
-    \AxiomC{}
+    \AxiomC{\,}
     \RightLabel{assume}
@@
   \begin{bprooftree}
-    \AxiomC{}
+    \AxiomC{\,}
     \RightLabel{$⊤$-intro}
@@
 \begin{bprooftree}
-\AxiomC{}
+\AxiomC{\,}
 \RightLabel{PEM}

### 2017-10-27 paper/sections/conclusions-and-future-work.tex

--- 2017-10-27 paper/sections/conclusions-and-future-work.tex
@@
 \Agda formalizations of the \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
-We tested successful using this tool and \Agda as we
-described in Section~\ref{sec:proof-reconstruction} over a subset of
-propositional problems from~\cite{Prieto-Cubides2017}.
+% We tested successful using this tool and \Agda as we
+% described in Section~\ref{sec:proof-reconstruction} over a subset of
+% propositional problems from~\cite{Prieto-Cubides2017}.
 

### 2017-10-27 paper/sections/introduction.tex
Fixed Agda version.
Cosmetic changes.
[ paper ] lots of changes.

@@
 This paper has been organized in the following way.
-In Section~\ref{sec:limitations-type-theory} some limitations of type theory
+In Section~\ref{sec:type-theory} some limitations of type theory
 are discussed from proof-reconstruction point view.
@@
 
-The proof-reconstruction was carried on for \Metis~v2.3
-release~2017102, and the accompanying source code was tested with
-\Agda~v2.3, \Agda standard library~v0.14 and \prg{GHC}~v.8.2.1.
+The proof-reconstruction was carried on for \Metis~2.3
+(release~20170822), and the accompanying source code was tested with
+\Agda~2.5.3, \Agda standard library~0.14 and \prg{GHC}~8.2.1.
 

### 2017-10-27 paper/sections/proof-reconstruction/conjunct.tex
Added punctuation symbols.

@@
 \begin{verbatim}
-  fof(p1, p ∧ q ∧ (r ∨ ¬ p), inf(canonicalize, [x])).
+  fof(p1, p & q & (r | ~ p), inf(canonicalize, [x])).
   fof(p2, q, inf(conjunct, [p1])).
-  fof(p3, (r ∨ ¬ p), inf(conjunct, [p1])).
+  fof(p3, (r | ~ p), inf(conjunct, [p1])).
 \end{verbatim}
 
-In the first formula, $p ∧ q ∧ (r ∨ ¬ p)$, we find a left-associative
+In the first formula, \verb!p & q & (r | ~ p)!, we find a left-associative
 conjunction named \verb!p1!.
-The \conjunct rule extracts $q$ from the \verb!p1! using a left
+The \conjunct rule extracts \verb!q! from the \verb!p1! using a left
 projection (∧-proj₁) follow by a right projection (∧-proj₂).
-After, the \conjunct rule extracts $r ∨ ¬ p$ by using a right projection
+After, the \conjunct rule extracts \verb!r | ~ p! by using a right projection
 on \verb!p1!.
@@
         \begin{cases}
-            ψ, &\text{ if }φ ≡ ψ\\
-            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }ψ ≡ \fconjunct~φ₁~ψ  \\
-            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }ψ ≡ \fconjunct~φ₂~ψ  \\
+            ψ, &\text{ if }φ ≡ ψ;\\
+            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }ψ ≡ \fconjunct~φ₁~ψ;\\
+            ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂\text{ and }ψ ≡ \fconjunct~φ₂~ψ;\\
             φ, &\text{ otherwise.}

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
Added punctuation symbols.

--- 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
@@
     \fassoc_{⬓} &(φ₁~⬓~φ₂)        &= φ₁~∨~\fassoc_{⬓}~φ₂\\
-    \fassoc_{⬓} &φ                &= φ
+    \fassoc_{⬓} &φ                &= φ.
     \end{array}
@@
   \begin{cases}
-  ψ, &\text{ if } φ ≡ ψ\\
-  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } ψᵢ ≡ \fbuild_{∨}~φ~ψᵢ\text{ for some }i=1, 2\\
+  ψ, &\text{ if } φ ≡ ψ;\\
+  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } ψᵢ ≡ \fbuild_{∨}~φ~ψᵢ\text{ for some }i=1, 2;\\
   φ, &\text{ otherwise.}
@@
   \begin{cases}
-    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ \ffactor~φ₂\\
+    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ \ffactor~φ₂;\\
     φ,   &\text{ otherwise.}
@@
     \fsbuild_{∨}&(φ₁ ∨ φ₂)~ψ &=\ffactor~(\fbuild_{∨}~φ₁~ψ ∨ \fbuild_{∨}~φ₂~ψ)\\
-    \fsbuild_{∨}&φ~ψ &= \fbuild_{∨}~φ~ψ
+    \fsbuild_{∨}&φ~ψ &= \fbuild_{∨}~φ~ψ.
      \end{array}
@@
         \begin{cases}
-          φ, &\text{ if }φ ≡ ψ\\
-          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }ψ₁ ≡ \freorder_{∧}~φ~ψ₁ \\
-                   &\text{ and } ψ₂ ≡ \freorder_{∧}~φ~ψ₂\\
+          φ, &\text{ if }φ ≡ ψ;\\
+          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }ψ₁ ≡ \freorder_{∧}~φ~ψ₁;\\
+                   &\text{ and } ψ₂ ≡ \freorder_{∧}~φ~ψ₂;\\
           φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
@@
       \begin{cases}
-        ψ, &\text{ if }φ ≡ ψ\\
-        ψ, &\text{ if } ψ ≡ \freorder_{∨}~φ~ψ\\
+        ψ, &\text{ if }φ ≡ ψ;\\
+        ψ, &\text{ if } ψ ≡ \freorder_{∨}~φ~ψ;\\
         ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \fconjunctor~φ~ψ₁,\\
-           &\text{ and } ψ₂ ≡ \freorder_{∨}~φ~ψ₂\\
-        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunctor~φ₁~ψ \\
-        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunctor~φ₂~ψ \\
+           &\text{ and } ψ₂ ≡ \freorder_{∨}~φ~ψ₂;\\
+        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunctor~φ₁~ψ;\\
+        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunctor~φ₂~ψ;\\
         φ, &\text{ otherwise.}
@@
         \begin{cases}
-          ψ, &\text{ if } φ ≡ ψ\\
+          ψ, &\text{ if } φ ≡ ψ;\\
           ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁\\
-             &\text{ and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂\\
-          φ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
-          \fconjunctor~φ~ψ &\text{ otherwise.}
+             &\text{ and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂;\\
+          φ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂;\\
+          \fconjunctor~φ~ψ, &\text{ otherwise.}
         \end{cases}
@@
         \begin{cases}
-          φ₂,      &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (¬φ₁ ∨ φ₂)\\
-          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (¬φ₁ ∨ φ₄)\\\
+          φ₂,      &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (¬φ₁ ∨ φ₂);\\
+          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (¬φ₁ ∨ φ₄);\\\
           φ, &\text{ otherwise.}

### 2017-10-27 paper/sections/proof-reconstruction.tex
Cosmetic changes.
[ paper ] more corrections.

--- 2017-10-26 paper/sections/proof-reconstruction.tex
@@
 \begin{notation}
-The function name written in \texttt{typewriter} font refers to
-a \Metis inference rule.
-The same function name written using \textsf{sans serif} refers to the proposed
-version of the rule implemented in \cite{AgdaProp,AgdaMetis}.
+
+The function name written in \texttt{typewriter} font refers to a \Metis
+inference rule. The same function name written using \textsf{sans serif} font
+refers to our proposed version to reconstruct the rule and implemented
+in~\cite{AgdaMetis}. We use \Source and \Target as synonyms of \Prop type to
+describe in the function type the role of the arguments.
+
 \end{notation}
@@
 
-The pattern of the formalization for this rule is the following.
-For \conjunct rule, we define in type theory a function using the same name,
-conjunct, but written using roman font to distinguish from the original.
-The \fconjunct function has the following pattern:
+The pattern of the formalization for this rule is the following. For the
+\conjunct rule, we define in type theory a function using the same name,
+\fconjunct, but written using \textsf{san serif} font to distinguish from the
+original. The \fconjunct function has the following pattern:
 
@@
       ψ, &\text{if }\fconjunct \text{ built }ψ\text{ by applying valid}\\
-         &\text{transformations or other rules to }φ\\
+         &\text{transformations or other rules to }φ;\\
       φ, &\text{otherwise.}
@@
 \begin{itemize}
-  \item[∙] $φ$ is the \emph{source} formula from a previous deducted derivation.
-  \item[∙] $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
+  \item[∙] $φ : \Source$ is the \emph{source} formula from a previous deducted derivation.
+  \item[∙] $ψ : \Target$ is the \emph{target} formula. The expected result of the \fconjunct rule.
 \end{itemize}
 
-To justify all transformations done by \fconjunct, we prove its soundness
-with a theorem. This theorem would be
+To justify all transformations done by the \fconjunct rule, we prove its
+soundness with a theorem. This theorem would be
 
 \begin{equation*}
-\text{If }Γ ⊢ φ\text{ then }Γ ⊢ \fconjunct~φ~ψ.
+\text{If }Γ ⊢ φ\text{ and }ψ : \Target \text{ then }Γ ⊢ \fconjunct~φ~ψ.
 \end{equation*}
@@
 The remainder of this section will be devoted to present a formal description
-in type theory of each rule presented in Table~\ref{tab:agda-metis-table} using
-the pattern present in the example above.
+in type theory of each rule presented in Table~\ref{tab:agda-metis-table} using the pattern present in the example above.
+We follow the same order to present the rules as the table shows.
 

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
[ paper ] more corrections.

@@
 % ===================================================================
+
+% \begin{myremark}
+% We address proof-reconstruction in this paper for refutation proofs.
+% We annotate \abbre{CPL} problems using \verb!fof! formulas that
+% \Metis converts to \abbre{CNF} clauses to look for a refutation.
+% \end{myremark}
 
@@
 
-\begin{myremark}
-We address proof-reconstruction in this paper for refutation proofs.
-We annotate \abbre{CPL} problems using \verb!fof! formulas that
-\Metis converts to \abbre{CNF} clauses to look for a refutation.
-\end{myremark}
-
 \subsection{Output language}
@@
 Let us consider the following \TSTP derivation using
-the customized \TSTP syntax. Note that we remove
-empty fields in the inference information, we shorten names as long as possible, we delete the \verb!role! field when the role is
-\verb!plain! and we use the ⊤, ⊥, ¬, ∧, ∨, ⇒, ⇔ symbols to express the formulas.
+the customized \TSTP syntax (see the original \TSTP derivation and customizations in Appendix~\ref{app:tstp-syntax}).
 
@@
 
-In the following table we present the list of inference rules used
-by \Metis in its \TSTP derivations for propositional logic.
+In the following table we present the list of inference rules used by \Metis in
+the \TSTP derivations for propositional logic and reconstructed in
+Section~\ref{sec:proof-reconstruction} . The reader may notice that the
+inference rules presented in Fig~\ref{fig:metis-inferences} diverge from the
+rules in Table~\ref{tab:agda-metis-table}. However, the former rules are
+implemented by the rules in the latter. For instance, as far as we know, in
+\TSTP derivations, \canonicalize, \clausify, \conjunct, and \simplify, are all
+rules that represent the \emph{axiom} rule in the \Metis rules.
 
-We note a lack of clarity in defining the differences between the rules used in \TSTP derivations and the rules described on the documentation in
-the Metis description~\cite{hurd2003first}.
-These rules are not the same as we expected from the Fig.~\ref{fig:metis-inferences}.
+In the aforementioned table, we first present
+the \strip inference rule since it is the rule that appears first after each
+conjecture. The other rules are sorted mainly follow their level of complexity
+of their definitions and the formalization presented in
+Section~\ref{ssec:emulating-inferences}. Some inference rules depends the
+formalizations of other rules. For instance, the \simplify rule and the
+\clausify rule  need functions
+developed for the \canonicalize rule. The \canonicalize rule needs functions
+developed in the \resolve section. But the \resolve rule depends on the
+\conjunct rule.
+
+% We note a lack of clarity in defining the differences between the rules used in \TSTP derivations and the rules described on the documentation in
+% the Metis description~\cite{hurd2003first}.
+% These rules are not the same as we expected from the Fig.~\ref{fig:metis-inferences}.
 

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
[ paper ] metis rules improved.

@@
 
-In the following table we present the list of inference rules used by \Metis in
-the \TSTP derivations for propositional logic and reconstructed in
-Section~\ref{sec:proof-reconstruction} . The reader may notice that the
+We present the list of inference rules used by \Metis in
+the \TSTP derivations for propositional logic
+in Table~\ref{tab:agda-metis-table}.
+We reconstruct these rules in Section~\ref{sec:proof-reconstruction}.
+The reader may notice that the
 inference rules presented in Fig~\ref{fig:metis-inferences} diverge from the
-rules in Table~\ref{tab:agda-metis-table}. However, the former rules are
-implemented by the rules in the latter. For instance, as far as we know, in
+rules in aforementioned table. However, the former rules are
+implemented by the latter rules. For instance, as far as we know, in
 \TSTP derivations, \canonicalize, \clausify, \conjunct, and \simplify, are all
-rules that represent the \emph{axiom} rule in the \Metis rules.
+rules that represent the \emph{axiom} rule by \Metis.
 
-In the aforementioned table, we first present
-the \strip inference rule since it is the rule that appears first after each
-conjecture. The other rules are sorted mainly follow their level of complexity
-of their definitions and the formalization presented in
+We first present the \strip inference rule since it is the rule that appears
+first after each conjecture. The other rules are sorted mainly follow their
+level of complexity of their definitions and the formalization presented in
 Section~\ref{ssec:emulating-inferences}. Some inference rules depends the
 formalizations of other rules. For instance, the \simplify rule and the
-\clausify rule  need functions
-developed for the \canonicalize rule. The \canonicalize rule needs functions
-developed in the \resolve section. But the \resolve rule depends on the
-\conjunct rule.
+\clausify rule  need functions developed for the \canonicalize rule. The
+\canonicalize rule needs functions developed in the \resolve section. But the
+\resolve rule depends on the \conjunct rule.
 

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] more corrections.
[ paper ] added strip reference to the appendix.

@@
 
-Type theory is a formalism [TODO]
+% Type theory is a formalism [TODO]
 
-Even though we choose a proof-assistant for type theory
-where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.
+% Even though we choose a proof-assistant for type theory
+% where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.
 
-Therefore the proof-reconstruction tool generates proof-terms by reconstructing the proof using the formalization
-the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:type-theory}.
+% Therefore the proof-reconstruction tool generates proof-terms by reconstructing the proof using the formalization
+% the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:type-theory}.
 
@@
   \fuh_{0} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fuh_{0}~(φ₁ ⇒ φ₂) ∧ \fuh_{0}~(φ₁ ⇒ φ₃)\\
-  \fuh_{0} &φ                &= φ
+  \fuh_{0} &φ                &= φ.
 \end{array}
@@
 \fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
-\fuh_{1} &φ &n &= φ
+\fuh_{1} &φ &n &= φ.
 \end{array}
@@
 \frank~(φ₁~\square~φ₂) &= \fmax~(\frank~φ₁)~(\frank~φ₂) + c_{\square}\\
-\frank~φ               &= 0
+\frank~φ               &= 0.
 \end{array}
@@
     \fuh_{cm}~(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fmax~(\fuh_{cm}~φ₂)~(\fuh_{cm}~φ₃) + 1\\
-    \fuh_{cm}~φ                &= 0
+    \fuh_{cm}~φ                &= 0.
     \end{array}
@@
 
-\subsection{Intuitionistic logic (ESCRIBIENDO)}
+\subsection{Intuitionistic logic}
 \label{ssec:intuitionistic-logic}
 
-We follow the same approach presented in~\cite{Altenkirch2015} to work with propositional
-logic in type theory. Therefore, we include
-in the constructors for theorems, structural rules and formation rules of
-all connectives in Fig.~\ref{fig:CPL-inference-rules}.
+We follow the same approach presented in~\cite{Altenkirch2015} to work with
+propositional logic in type theory. Therefore, we include in the constructors
+for theorems, structural rules and formation rules of all connectives in
+Fig.~\ref{fig:CPL-inference-rules}.
 

### 2017-10-27 paper/sections/proof-reconstruction/clausify.tex
Cosmetic changes.
[ paper ] lots of changes.
Added punctuation symbols.
Numbered all the examples.

@@
 
-\begin{myexample}
+\begin{myexamplenum}
 In the following \TSTP derivation by \Metis, we see how
@@
          \begin{cases}
-        ψ, &\text{ if }φ≡ψ\\
+        ψ, &\text{ if }φ≡ψ;\\
         \freorder_{∧∨}~(\fcnf~φ~ψ), &\text{ otherwise.}
@@
 
-\begin{myremark}
-The \clausify rule is often preceded by the \canonicalize rule.
-Both rules perform \emph{Clausification} that introduces
-into the problem axioms and definitions in the domain of the solution.
-The clausification is widely described by
-\citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.
-\end{myremark}
-
 \end{document}

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] more corrections.
Numbered all the examples.

@@
 
-\begin{myexample}
+\begin{myexamplenum}
 We build the disjunction $(p ∨ q) ∨ r$ from the disjunction
@@
 \end{equation*}
-\end{myexample}
+\end{myexamplenum}
 
@@
 
-\begin{myexample}
+\begin{myexamplenum}
 \begin{equation}
@@
 \end{equation}
-\end{myexample}
+\end{myexamplenum}
 
@@
 resolution theorem and two derivations.
-Recall a \emph{literal} is an atom (positive literal) or a negation
+
+\begin{definition}
+A \emph{literal} is an atom (positive literal) or a negation
 of an atom (negative literal).
+\end{definition}
 
@@
 
-\begin{myexample}
+\begin{myexamplenum}
 Continuing with the problem presented in Example~\ref{ex:resolve-tstp},

### 2017-10-27 paper/sections/proof-reconstruction/strip.tex
Added punctuation symbols.
[ paper ] more corrections.
[ paper ] added strip reference to the appendix.
Numbered all the examples.

@@
 
-\begin{myexample}
+\begin{myexamplenum}
 The subgoals associated to a goal are introduced in the \TSTP derivation
@@
 \label{eq:strip-example}
-(p ∧ (p ⇒ r) ∧ ((p ∧ r) ⇒ q)) ⇒ ((p ∧ r) ∧ q)
+(p ∧ (p ⇒ r) ∧ ((p ∧ r) ⇒ q)) ⇒ ((p ∧ r) ∧ q).
 \end{equation}
@@
 \Metis proves each subgoal in the same order above from left to right
-in~\ref{eq:strip-example}.
+in~\eqref{eq:strip-example}.
 So far, very little attention has been paid to the role of \strip rule.
@@
 it uses the subgoals to prove the conjecture.
-\end{myexample}
+\end{myexamplenum}
 
@@
 \begin{equation*}
-  \scalebox{0.95}{
-  ($\mathcal{D}_1$)
+  (\mathcal{D}_1)
   \begin{bprooftree}
@@
   \end{bprooftree}
-  }
 \end{equation*}
@@
 \fstrip₁ &(¬ ⊤)         &(\suc~n) &= ⊥\\
-\fstrip₁ &φ             &n        &= φ
+\fstrip₁ &φ             &n        &= φ.
 \end{array}
@@
 \end{equation*}
+∙~  Other cases are proved in a similar way, see Appendix~\ref{app:strip-proof-case}.
+
 \end{proof} % the proof continue...
@@
 
-\begin{myexample}
+\begin{myexamplenum}
 In the following \TSTP derivation, note that the three subgoals
@@
 \end{verbatim}
-\end{myexample}
+\end{myexamplenum}
 

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
Numbered all the examples.
Cosmetics.
[ paper ] fixed a typo.

@@
 
-\begin{myexample}
+\begin{myexamplenum}
 For instance, let us express the problem
@@
 
-\begin{myexample}
+\begin{myexamplenum}
 
@@
 level of complexity of their definitions and the formalization presented in
-Section~\ref{ssec:emulating-inferences}. Some inference rules depends the
+Section~\ref{ssec:emulating-inferences}. Some inference rules depend on the
 formalizations of other rules. For instance, the \simplify rule and the
-\clausify rule  need functions developed for the \canonicalize rule. The
-\canonicalize rule needs functions developed in the \resolve section. But the
+\clausify rule need theorems developed for the \canonicalize rule. The
+\canonicalize rule needs theorems developed in the \resolve section. But the
 \resolve rule depends on the \conjunct rule.
-
-% We note a lack of clarity in defining the differences between the rules used in \TSTP derivations and the rules described on the documentation in
-% the Metis description~\cite{hurd2003first}.
-% These rules are not the same as we expected from the Fig.~\ref{fig:metis-inferences}.
 
@@
 
-% Finally, \emph{axiom} rule appears in \TSTP derivations by using one of the following rules: \canonicalize, \clausify, \conjunct, or \simplify.
-% Then, the last rule remains is \emph{resolve}, it
-% appears by the binary rule, \resolve, the version in \Metis of the resolution
-% theorem. For a more detailed description of this rules see Section~\ref{sec:proof-reconstruction}.
-
 \begin{table}[!ht]
@@
     \hline
-    \textbf{\Metis Rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
+    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem number}\\ \hline
 

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
[ paper ] fixed another typo.
[ paper ] metis-intro improved.

@@
 \Metis is an automatic theorem prover for first-order logic with equality
-developed by  \citeauthor{hurd2003first}~\cite{hurd2003first}.
-This prover is suitable for proof reconstruction since it provides well-documented proofs to justify its deduction steps from the basis of only six inference rules.
-In Fig.~\ref{fig:metis-inferences}, we show the three \Metis rules for propositional logic.
+developed by  \citeauthor{hurd2003first}~\cite{hurd2003first}. This prover is
+suitable for proof-reconstruction since it provides well-documented proofs to
+justify its deduction steps from the basis of only six inference rules for
+first-order logic (see, for example, \cite{paulson2007source,Farber2015}). For
+the propositional fragment, \Metis has three inference rules,
+see Fig.~\ref{fig:metis-inferences}.
 
@@
 \TSTP derivations, \canonicalize, \clausify, \conjunct, and \simplify, are all
-rules that represent the \emph{axiom} rule by \Metis.
+the rules that represent the \emph{axiom} rule by \Metis.
 

### 2017-10-27 paper/sections/type-theory.tex
Numbered all the examples.
[ paper ]  type-theory introduction.

@@
 
-% Type theory is a formalism [TODO]
+Type theory is another formalism for the foundation of mathematics, and it has become in a key instrument to study logic and proof theory.
+It was proposed in 1902 to avoid the Russell's paradox and it follows
+the same philosophy of constructive mathematics where the witness of
+a statement is \emph{everything}. In that direction, we could say
+the main actors in type theory are the statements and their proofs.
+The \emph{types} are theorems and their \emph{terms} are the proofs.
 
-% Even though we choose a proof-assistant for type theory
-% where proof verification becomes a type-checking task of the proof-term following the Curry-Howard isomorphism.
+Since it is a formal system, in type theory, we have a syntax and a set of derivation rules.
+These rules enables us to get certain kind of conclusions that we call \emph{judgments}.
+A judgment is a statement that says a
+term has certain type.
+
+\begin{notation}
+Types are written using small caps.
+We write the type judgments as $m : \abbre{M}$ to denote
+that $m$ has $\abbre{M}$ type.
+\end{notation}
+
+With the derivation rules we produce derivation trees inside
+the judgments. These trees represent proofs of theorems.
+We use such level of expressiveness for the reconstructed proofs
+from the \ATPs.
+
+% Since type theory can be seen as typed lambda calculus with dependent products,
+% compute terms is basically $\beta$-reductions.
+% And we
+
+We choose a proof-assistant for type theory
+because of the verification of proofs is type-checking, that is,
+given a type of the theorem and the proof-term, verify that term
+effectively has the type of the theorem.
+Therefore, by following the Curry-Howard correspondence,
 
@@
 \begin{notation}
-Types are written using small caps.
-We write the type judgments as $m : \abbre{M}$ to denote
-that $m$ has $\abbre{M}$ type.
 We use \Prop for the type of propositions and the dependent type, $Γ ⊢ φ$ for
@@
 
-\begin{myexample}
+\begin{myexamplenum}
 \label{ex:structural-recursion}

### 2017-10-27 paper/sections/introduction.tex

@@
 These proof-assistants allow us to formalize the logical system used
-in the proofs, \ie, logical constants, axioms, inference rules, and
-theorems. A proof-reconstruction tool provides such an integration,
-translating the derivation generated by the prover into the formalism
-of the proof-assistant.
+in the proofs, \ie, logical constants, axioms, inference rules,
+hypotheses, and theorems. A proof-reconstruction tool provides such an
+integration, translating the derivation generated by the prover into
+the formalism of the proof-assistant.
 

### 2017-10-27 paper/sections/introduction.tex
Added reference for type theory.

@@
 We describe a formal reconstruction of proofs generated by the \Metis
-prover~\cite{hurd2003first}---our source system---in type theory. We
+prover~\cite{hurd2003first}---our source system---in Martin-Löf type
+theory~\cite{Nordstrom-Petersson-Smith-1990}. We
 formalize the subset of the \Metis inference rules for the

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] fixed typo.
Cosmetic changes.

@@
 We use such level of expressiveness for the reconstructed proofs
-from the \ATPs.
+of the \ATPs.
 
@@
 
-This paper adopts the notion of \emph{structurally smaller} from
-\citeauthor{Abel2002}~\cite{Abel2002} to say, a recursive function is
-structurally recursive if it calls itself with only
-structurally smaller arguments.
+This paper adopts the notion of \emph{structurally smaller}
+from~\cite{Abel2002}, that is, a recursive function is structurally
+recursive if it calls itself with only structurally smaller arguments.
 
@@
 
-Following the technique mentioned above, we get the structural
-recursive definition of the $\fuh_{0}$ function presented
-in~\eqref{eq:uh}.
-
-\begin{align}
+Following the technique mentioned above, we define the
+function~$\fuh$, the structural
+recursive definition of the function~$\fuh_{0}$.
+\begin{align*}
   \label{eq:uh}
@@
 
-For a more complete treatment of general recursion, and how to
-define well-founded and well-structural recursive functions, we refer
-the reader to \citeauthor{Bove2005}~\cite{Bove2005}.
+For a more complete treatment of general recursion, and how to define
+well-founded and well-structural recursive functions, we refer the
+reader to~\cite{Bove2005}.
 

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] additions in introductio to type theory.

--- 2017-10-27 paper/sections/type-theory.tex
@@
 the main actors in type theory are the statements and their proofs.
-The \emph{types} are theorems and their \emph{terms} are the proofs.
+By following the Curry-Howard correspondence, we say
+\emph{types} are theorems and their \emph{terms} are their proofs.
 
-Since it is a formal system, in type theory, we have a syntax and a set of derivation rules.
-These rules enables us to get certain kind of conclusions that we call \emph{judgments}.
-A judgment is a statement that says a
-term has certain type.
+Since the type theory is formal system, we have a syntax and a set of
+derivation rules. These rules enables us to derive a kind of conclusions called
+\emph{judgments}. A judgment is another way a term has certain type.
 
@@
 
-With the derivation rules we produce derivation trees inside
-the judgments. These trees represent proofs of theorems.
-We use such level of expressiveness for the reconstructed proofs
-from the \ATPs.
-
-% Since type theory can be seen as typed lambda calculus with dependent products,
-% compute terms is basically $\beta$-reductions.
-% And we
-
-We choose a proof-assistant for type theory
-because of the verification of proofs is type-checking, that is,
-given a type of the theorem and the proof-term, verify that term
-effectively has the type of the theorem.
-Therefore, by following the Curry-Howard correspondence,
-
-% Therefore the proof-reconstruction tool generates proof-terms by reconstructing the proof using the formalization
-% the prover in type theory. However, this approach suffers from some limitations of type theory as we describe in Section~\ref{sec:type-theory}.
+We produce derivation trees inside the judgments using the derivation rules. The task to verify if a proof proves a certain theorem becomes in verify if the
+derivation tree of the proof has the type of the theorem. This process is known
+as type-checking. This feature of type theory allow us to verify a proof
+generated by \ATPs by reconstructing its proof-term to type-check the proof.
+However, type theory has some limitations for proof-reconstruction as we
+describe in the following section.
 

### 2017-10-27 paper/sections/conclusions-and-future-work.tex

--- 2017-10-27 paper/sections/conclusions-and-future-work.tex
@@
 
-One of the main contribution of this study was
-increasing the trustworthiness of the automatic prover \Metis.
-Justifying a proof by a theorem prover
-has a real significant impact for these automatic tools.
-The reverse engineering task to understand the prover reasoning
-can reveal important issues or bugs
-in many parts of these systems (\eg, preprocessing, reasoning, or
-deduction modules). During this research, we had the opportunity
-to contribute to \Metis by reporting some bugs\footnote{Issues No.~2,
-No.~4. and commit \name{8a3f11e} in the \Metis' official repository
-\url{https://github.com/gilith/metis}}.
-Fortunately, all these problems were fixed quickly by
-\citeauthor{hurd2003first} in the \Metis 20170810 release.
+One of the main contribution of this study was increasing the
+trustworthiness of the automatic prover \Metis.  Justifying a proof by
+a theorem prover has a real significant impact for these automatic
+tools.  The reverse engineering task to understand the prover
+reasoning can reveal important issues or bugs in many parts of these
+systems (\eg, preprocessing, reasoning, or deduction modules). During
+this research, we had the opportunity to contribute to \Metis by
+reporting some bugs---see Issues No.~2, No.~4, and commit
+\name{8a3f11e} in \Metis' official
+repository.\footnote{\url{https://github.com/gilith/metis}.}
+Fortunately, all these problems were fixed quickly by Hurd in
+\Metis~2.3 (release~20170822).
 

### 2017-10-27 paper/sections/metis-language-and-proofs.tex

@@
 
-\Metis is an automatic theorem prover for first-order logic with equality
-developed by  \citeauthor{hurd2003first}~\cite{hurd2003first}. This prover is
-suitable for proof-reconstruction since it provides well-documented proofs to
-justify its deduction steps from the basis of only six inference rules for
-first-order logic (see, for example, \cite{paulson2007source,Farber2015}). For
-the propositional fragment, \Metis has three inference rules,
-see Fig.~\ref{fig:metis-inferences}.
+\Metis is an automatic theorem prover for first-order logic with
+equality developed by Hurd~\cite{hurd2003first}. This prover is
+suitable for proof-reconstruction since it provides well-documented
+proofs to justify its deduction steps from the basis of only six
+inference rules for first-order logic (see, for example,
+\cite{paulson2007source,Farber2015}). For the propositional fragment,
+\Metis has three inference rules, see Fig.~\ref{fig:metis-inferences}.
 

### 2017-10-27 paper/sections/notes/discussion.tex
Cosmetic changes.

--- 2017-10-20 paper/sections/discussion.tex
@@
 
-This lack of the \Metis' documentation represents one of the first barriers to build proof-reconstruction tools since some inference rules
-like \canonicalize or \simplify summarize many essential steps to deduce the conclusion, making them hard to justify and emulate
-(see a comment related on the presenting of \name{Sledgehammer}
-in \citeauthor{paulson2007source}~\cite{paulson2007source} and \citeauthor{Farber2015}~\cite{Farber2015}).
+This lack of the \Metis' documentation represents one of the first
+barriers to build proof-reconstruction tools since some inference
+rules like \canonicalize or \simplify summarize many essential steps
+to deduce the conclusion, making them hard to justify and emulate (see
+a comment related on the presenting of \name{Sledgehammer}
+in~\cite{paulson2007source} and ~\cite{Farber2015}).
 
@@
 
-\textit{Normalization.} We observed \clausify rule described above is preceded by \canonicalize rule when \Metis introduces at some point of the derivation an axiom or a definition of the problem.
-In that case, both rules aim to perform a common task for
-automatic theorem provers, Clausification, mainly described on paper
-by \citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}. When the
+\textit{Normalization.} We observed \clausify rule described above is
+preceded by \canonicalize rule when \Metis introduces at some point of
+the derivation an axiom or a definition of the problem. In that case,
+both rules aim to perform a common task for automatic theorem provers,
+Clausification, mainly described on~\cite{Sutcliffe1996}. When the
 aforementioned case does not occur we argue \canonicalize transforms
@@
 form. In addition, \canonicalize could also perform other tasks like
-removing logic constants (⊥, ⊤), definitions, and tautologies, or even reorder both conjunctions and disjunctions of the proposition.
+removing logic constants (⊥, ⊤), definitions, and tautologies, or even
+reorder both conjunctions and disjunctions of the proposition.
 

### 2017-10-27 paper/sections/proof-reconstruction.tex
Numbered all the examples.

@@
 
-The proof-reconstruction approach proposed consists of a series
-of steps similar to the workflow presented by
-\citeauthor{sultana2015}~\cite{sultana2015}.
-This process is a translation from a source
-system to a target system. In our case, the system of origin, the
-automatic theorem prover, is \Metis; the target system is a proof
-assistant, \Agda. We choose \Agda, but another proof assistant with the
-same support of type theory and inductive types could be used.
+The proof-reconstruction approach proposed consists of a series of
+steps similar to the workflow presented~\cite{sultana2015}.  This
+process is a translation from a source system to a target system. In
+our case, the system of origin, the automatic theorem prover, is
+\Metis; the target system is a proof assistant, \Agda. We choose
+\Agda, but another proof assistant with the same support of type
+theory and inductive types could be used.
 
@@
 
-\begin{myexample}
+\begin{myexamplenum}
 \Metis has a inference rule named conjunct.

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex

@@
 
-To construct a disjunction $ψ$ from a disjunction $φ$, we have used ideas
-from the description in \citeauthor{bohme2010}~\cite{bohme2010} to prove
-equality between nested disjunctions.
-We define the $\fsbuild_{∨}$ function in~\eqref{eq:strong-build-or}
-that uses every disjunct from the source formula, $φ$, to build up the
-target disjunction $ψ$.
+To construct a disjunction~$ψ$ from a disjunction~$φ$, we have used
+ideas from the description in~\cite{bohme2010} to prove equality
+between nested disjunctions.  We define the $\fsbuild_{∨}$ function
+in~\eqref{eq:strong-build-or} that uses every disjunct from the source
+formula, $φ$, to build up the target disjunction $ψ$.
 

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] type theory section.

@@
 describe in the following section.
-
-\begin{notation}
-We use \Prop for the type of propositions and the dependent type, $Γ ⊢ φ$ for
-theorems where $Γ : \List~\Prop$ and $φ : \Prop$.
-$\abbre{List}$ type is the usual inductive type for lists.
-For syntactical equivalence, we write the equality as $φ ≡ ψ$
-for $φ,~ψ : \Prop$. For this equality, we assume the
-reflexivity, symmetry and transitivity properties.
-\end{notation}
 
@@
 \begin{notation}
+
+We use \Prop for the type of propositions.
+For syntactical equivalence, we write the equality as $φ ≡ ψ$
+for $φ,~ψ : \Prop$. For this equality, we assume the
+reflexivity, symmetry and transitivity properties.
+
+\end{notation}
+
+\begin{notation}
+
 The type of natural numbers is called \Nat, and it is defined as
@@
 as well.
+
 \end{notation}
@@
 Fig.~\ref{fig:CPL-inference-rules}.
+
+\begin{notation}
+We write theorems as the family of dependent types, $Γ ⊢ φ$ where
+the turnstile symbol (⊢) represents the syntactical consequence relation
+between a set of premises, $Γ : \List~\Prop$ and a conclusion $φ : \Prop$.
+$\abbre{List}$ type is the usual inductive type for lists.
+\end{notation}
 

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] fixed typo.
[ paper ] type theory introcution improved.

@@
 
-Type theory is another formalism for the foundation of mathematics, and it has become in a key instrument to study logic and proof theory.
+Type theory is another formalism for the foundation of mathematics, and it has became in a key instrument to study logic and proof theory.
 It was proposed in 1902 to avoid the Russell's paradox and it follows
@@
 
-Since the type theory is formal system, we have a syntax and a set of
+Since type theory is a formal system, we have a syntax and a set of
 derivation rules. These rules enables us to derive a kind of conclusions called
-\emph{judgments}. A judgment is another way a term has certain type.
+\emph{judgments}. A judgment is another way to say a term has certain type.
 
@@
 
-We produce derivation trees inside the judgments using the derivation rules. The task to verify if a proof proves a certain theorem becomes in verify if the
-derivation tree of the proof has the type of the theorem. This process is known
-as type-checking. This feature of type theory allow us to verify a proof
-generated by \ATPs by reconstructing its proof-term to type-check the proof.
-However, type theory has some limitations for proof-reconstruction as we
-describe in the following section.
+We produce derivation trees inside the judgments using the derivation rules.
+Since type theory can be seen as typed lambda calculus with dependent products,
+evaluation of lambda terms also called \emph{normalization} of the proofs-terms, are reductions using the system inference rules.
+
+Therefore, the task to verify a proof that proves a certain theorem is
+translated to verify if the associated tree of the proof has the correspondent
+type of the theorem. This process is known as \emph{type-checking}. This feature
+of type theory allow us to verify a proof generated by \ATPs by reconstructing
+its proof-term to type- check the proof. However, type theory has some
+limitations for proof- reconstruction as we describe in the following section.
 

### 2017-10-27 paper/sections/proof-reconstruction.tex
Cosmetic changes.

@@
 
-In this section, we reconstruct each \Metis inference rule
-in Table~\ref{tab:agda-metis-table} with a
-function and its respective theorem. We present a pattern of the
-formal description for these rules.
+In this section, we reconstruct each \Metis inference rule in
+Table~\ref{tab:agda-metis-table} via a function and its respective
+theorem. We present a pattern of the formal description for these
+rules in Example~\ref{ex:inference-rule-pattern}.
 
 \begin{notation}
-
-The function name written in \texttt{typewriter} font refers to a \Metis
-inference rule. The same function name written using \textsf{sans serif} font
-refers to our proposed version to reconstruct the rule and implemented
-in~\cite{AgdaMetis}. We use \Source and \Target as synonyms of \Prop type to
-describe in the function type the role of the arguments.
-
+  The function name written in \texttt{typewriter} font refers to a
+  \Metis inference rule. The same function name written using
+  \textsf{sans serif} font refers to our formalized version to
+  reconstruct the rule and implemented in~\cite{AgdaMetis}. We use
+  \Source and \Target as synonyms of the \Prop type to describe in the
+  function types the role of the arguments.
 \end{notation}
@@
 \begin{myexamplenum}
-\Metis has a inference rule named conjunct.
-We refer to this rule writing \conjunct.
-
-\begin{verbatim}
-  fof(p3, (r ∨ ¬ p), inf(conjunct, [p1])).
-\end{verbatim}
-
-The pattern of the formalization for this rule is the following. For the
-\conjunct rule, we define in type theory a function using the same name,
-\fconjunct, but written using \textsf{san serif} font to distinguish from the
-original. The \fconjunct function has the following pattern:
-
+\label{ex:inference-rule-pattern}
+\Metis has a inference rule named \conjunct. We reconstruct this
+inference rule as follow. We define in \Agda the function
+\fconjunct which has the following pattern:
 \begin{equation*}
@@
          &\text{transformations or other rules to }φ;\\
-      φ, &\text{otherwise.}
+      φ, &\text{otherwise;}
       \end{cases}
@@
 
-\begin{itemize}
-  \item[∙] $φ : \Source$ is the \emph{source} formula from a previous deducted derivation.
-  \item[∙] $ψ : \Target$ is the \emph{target} formula. The expected result of the \fconjunct rule.
-\end{itemize}
-
-To justify all transformations done by the \fconjunct rule, we prove its
-soundness with a theorem. This theorem would be
-
+To justify all transformations done by the \fconjunct rule, we prove
+its soundness with a theorem. This theorem would be
 \begin{equation*}
-\text{If }Γ ⊢ φ\text{ and }ψ : \Target \text{ then }Γ ⊢ \fconjunct~φ~ψ.
+  \text{If }Γ ⊢ φ \text{ then }Γ ⊢ \fconjunct~φ~ψ, \text{ where } ψ : \Target.
 \end{equation*}
-
 \end{myexamplenum}
 
-The remainder of this section will be devoted to present a formal description
-in type theory of each rule presented in Table~\ref{tab:agda-metis-table} using the pattern present in the example above.
-We follow the same order to present the rules as the table shows.
+The remainder of this section will be devoted to present a formal
+description in type theory of each rule presented in
+Table~\ref{tab:agda-metis-table} using the pattern present in the
+example above.  We follow the same order to present the rules as the
+table shows.
 

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] type theory section additions.

@@
 translated to verify if the associated tree of the proof has the correspondent
-type of the theorem. This process is known as \emph{type-checking}. This feature
+type of the theorem. We know this process as \emph{type-checking}. This feature
 of type theory allow us to verify a proof generated by \ATPs by reconstructing
-its proof-term to type- check the proof. However, type theory has some
-limitations for proof- reconstruction as we describe in the following section.
+its proof-term to type-check the proof. For such a purpose, we use a proof
+assistant in type theory like \Agda to delegate this task.  However, this
+approach has some weak points discussed in~\cite{Bezem2002}. Some limitations
+from the type theory point of view for proof-reconstruction is described in the
+following section.
 
@@
 
-We follow the same approach presented in~\cite{Altenkirch2015} to work with
-propositional logic in type theory. Therefore, we include in the constructors
-for theorems, structural rules and formation rules of all connectives in
-Fig.~\ref{fig:CPL-inference-rules}.
+To reconstruct proofs generated by \Metis, we have formalized in type
+theory the propositional logic (we briefly describe classical propositional logic in Appendix~\ref{app:CPL}).
+
+To accomplish that formalization, the reader must take into account,
+type theory and intuitionistic logic are based on the same basis of
+the spirit of constructive mathematics. Therefore, proving propositions
+demands a construction of the proof but in classical logic, they may
+no exist and some proofs are proved by refutation. That is, using
+a non-constructive method.
+
+Therefore, to reconstruct \Metis derivations, we included as an axiom, the
+principle of excluded third (\abbre{PEM}) since \Metis proves by refutation.
+Assuming \abbre{PEM}, we can justify refutation proofs by deriving from it the
+\emph{reductio ad absurdum} rule (\abbre{RAA}). The \abbrev{RAA} rule is the
+formulation of the principle of proof by contradiction, that is, a derivation of
+a contradiction, $⊥$, from the hypothesis $(¬ φ)$, is a derivation of $φ$.
 
@@
 
-Since we pretend to reconstruct proofs generated by \Metis, and \Metis works
-in classical logic,  we have included as an axiom, the
-principle of excluded third (\abbre{PEM}).
-
-Assuming \abbre{PEM}, we can justify refutation proofs.
-We derive the \emph{reductio ad absurdum} rule (\abbre{RAA}) as the
-formulation of the principle of proof by contradiction, that is, a derivation
-of a contradiction, $⊥$, from the hypothesis $(¬ φ)$, is a
-derivation of $φ$.
+We implemented in~\cite{AgdaProp} the syntactical consequence relation in a
+similar way as it was presented in~\cite{Altenkirch2015}. For that reason, we
+have included structural rules like \emph{weaken} and formation rules for
+connectives as the constructors for new theorems in
+Fig.~\ref{fig:CPL-inference-rules}.
 

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
Fixed table.

@@
 formulas with the following form:
-
 \begin{verbatim}
@@
 \end{verbatim}
-
-where the \name{language} can be \name{fof} or \name{cnf}. The \name{name}
-serves to identify the formula within the problem. Each formula
-assumes a \name{role}, this could be an \name{axiom},
-\name{conjecture}, \name{definition}, \name{plain} or an \name{hypothesis}.
-The formulas include the constants \verb!$true! and \verb!$false!, negation
-unary operator (\verb!~!), and the binary connectives (\verb!&!, \verb!|!,
-\verb!=>!, \verb!<=>!) to represent $⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$,
-and $⇔$ respectively.
+where the \name{language} can be \name{fof} or \name{cnf}. The
+\name{name} serves to identify the formula within the problem. Each
+formula assumes a \name{role}, this could be an \name{axiom},
+\name{conjecture}, \name{definition}, \name{plain} or an
+\name{hypothesis}.  The formulas include the constants
+\verb!$true! and \verb!$false!, the negation unary operator~\verb!~!,
+and the binary connectives \verb!&!, \verb!|!, \verb!=>!, and
+\verb!<=>! to represent $⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$, and $⇔$
+respectively.
 
@@
   For instance, let us express the problem
-$p\, ⊢ ¬  (p ∧ ¬ p) ∨ (q ∧ ¬ q)$
-in \TPTP syntax. We begin by declaring the $p$ axiom using the \verb!axiom!
-keyword. Later, we include the expected conclusion using the
-\verb!conjecture! keyword.
-
+  $p\, ⊢ ¬ (p ∧ ¬ p) ∨ (q ∧ ¬ q)$ in \TPTP syntax. We begin by
+  declaring the $p$ axiom using the \verb!axiom!  keyword. Next, we
+  include the expected conclusion using the \verb!conjecture! keyword.
 \begin{verbatim}
@@
 \end{verbatim}
-
 \end{myexamplenum}
@@
 
+      \texttt{canonicalize}
+      &Normalization of the formula
+      &\ref{thm:canonicalize}
+      \\
+
       \texttt{clausify}
@@
       &\ref{thm:clausify}
-      \\
-
-      \texttt{canonicalize}
-      &Normalization of the formula
-      &\ref{thm:canonicalize}
       \\

### 2017-10-27 paper/sections/type-theory.tex
Cosmetic changes.

@@
 the main actors in type theory are the statements and their proofs.
-By following the Curry-Howard correspondence, we say
+By following the Curry-Howard correspondence (see, for example,~\cite{Wadler-2015}), we say
 \emph{types} are theorems and their \emph{terms} are their proofs.
@@
 \begin{notation}
-Types are written using small caps.
-We write the type judgments as $m : \abbre{M}$ to denote
-that $m$ has $\abbre{M}$ type.
+  Types are written using \abbre{small caps}.  We write the type
+  judgments as $m : \abbre{m}$ to denote that~$m$ is of
+  type~$\abbre{m}$.
 \end{notation}

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] addtions in type theory.

@@
 
-To reconstruct proofs generated by \Metis, we have formalized in type
-theory the propositional logic (we briefly describe classical propositional logic in Appendix~\ref{app:CPL}).
+Type theory and intuitionistic logic are accompanying theories since they are
+based on the same basis of constructive mathematics. Proving propositions in
+these theories demands a witness construction for the proof. Nonetheless,
+classical logic does not always have constructive proofs and some of its proofs
+are proved by non-constructive methods like refutation.
 
-To accomplish that formalization, the reader must take into account,
-type theory and intuitionistic logic are based on the same basis of
-the spirit of constructive mathematics. Therefore, proving propositions
-demands a construction of the proof but in classical logic, they may
-no exist and some proofs are proved by refutation. That is, using
-a non-constructive method.
-
-Therefore, to reconstruct \Metis derivations, we included as an axiom, the
-principle of excluded third (\abbre{PEM}) since \Metis proves by refutation.
-Assuming \abbre{PEM}, we can justify refutation proofs by deriving from it the
-\emph{reductio ad absurdum} rule (\abbre{RAA}). The \abbrev{RAA} rule is the
-formulation of the principle of proof by contradiction, that is, a derivation of
-a contradiction, $⊥$, from the hypothesis $(¬ φ)$, is a derivation of $φ$.
+To reconstruct proofs generated by \Metis, we have formalized in type theory the classical propositional logic.
+A  briefly description of it is presented in Appendix~\ref{app:CPL}. In this
+formalization, we assume the principle of excluded third (\abbre{PEM}) as the
+only axiom since \Metis is a prover for classical logic. Assuming \abbre{PEM},
+we can justify refutation proofs by deriving from it the \emph{reductio ad
+absurdum} rule (\abbre{RAA}). The \abbrev{RAA} rule is the formulation of the
+principle of proof by contradiction, that is, a derivation of a contradiction,
+$⊥$, from the hypothesis $(¬ φ)$, is a derivation of $φ$.
 
 \begin{notation}
-We write theorems as the family of dependent types, $Γ ⊢ φ$ where
+We write theorems in \CPL as the family of dependent types, $Γ ⊢ φ$ where
 the turnstile symbol (⊢) represents the syntactical consequence relation
@@
 similar way as it was presented in~\cite{Altenkirch2015}. For that reason, we
-have included structural rules like \emph{weaken} and formation rules for
-connectives as the constructors for new theorems in
-Fig.~\ref{fig:CPL-inference-rules}.
+have included structural rules like \emph{weaken}, formation and elimination
+rules for connectives and the PEM axiom as the constructors of the theorem type
+in Fig.~\ref{fig:CPL-inference-rules}.
 

### 2017-10-27 paper/sections/type-theory.tex
Cosmetic changes.

@@
 
-We produce derivation trees inside the judgments using the derivation rules.
-Since type theory can be seen as typed lambda calculus with dependent products,
-evaluation of lambda terms also called \emph{normalization} of the proofs-terms, are reductions using the system inference rules.
+We produce derivation trees inside the judgments using the derivation
+rules.  Since type theory can be seen as typed $λ$-calculus with
+dependent products, evaluation of $λ$-terms also called
+\emph{normalization} of the proof-terms, are reductions using the
+system inference rules.
 
 Therefore, the task to verify a proof that proves a certain theorem is
-translated to verify if the associated tree of the proof has the correspondent
-type of the theorem. We know this process as \emph{type-checking}. This feature
-of type theory allow us to verify a proof generated by \ATPs by reconstructing
-its proof-term to type-check the proof. For such a purpose, we use a proof
-assistant in type theory like \Agda to delegate this task.  However, this
-approach has some weak points discussed in~\cite{Bezem2002}. Some limitations
-from the type theory point of view for proof-reconstruction is described in the
-following section.
+translated to verify if the associated tree of the proof has the
+correspondent type of the theorem. We know this process as
+\emph{type-checking}. This feature of type theory allow us to verify a
+proof generated by an \ATP by reconstructing its proof-term to
+type-check the proof. For such a purpose, we use a proof assistant in
+type theory like \Agda to delegate this task.  However, this approach
+has some weak points discussed in~\cite{Bezem2002}. Some limitations
+from the type theory point of view for proof-reconstruction is
+described in the following sections.
 

### 2017-10-27 paper/sections/related-work.tex
[ paper ] refactoring in relate-work.

--- 2017-10-26 paper/sections/related-work.tex
@@
 
-Many approaches have been proposed for proof-reconstruction and some tools have been implemented in the last decades.
+Many approaches have been proposed for proof-reconstruction and some tools have
+been implemented in the last decades. We first mention some tools in type
+theory and later we listed some proof-reconstruction tools for classical logic.
 
-In type theory, for \Agda and  for the same propositional fragmented used in this paper,
-we found the proof-reconstruction proposed by \citeauthor{Kanso2012}
-in~\cite{Kanso2012,kanso2016light}. The author present an approach similar to
-the reasoning presented in Section~\ref{ssec:workflow}.
-Nonetheless, his approach includes semantics reasoning that as we mentioned
-in the introduction differs completely from our proof-reconstruction approach.
+\citeauthor{Kanso2012} in~\cite{Kanso2012,kanso2016light} presents a proof-
+reconstruction in \Agda for propositional logic. Its tool support proof-
+reconstruction for \name{EProver} and \name{Z3} ATPs following a similar work-
+flow as we presented in Section~\ref{ssec:workflow}. Nonetheless, his approach
+employs semantics for logic equivalences. We have avoided the use of
+propositions meanings towards a future work to support other logics where a
+syntactical approach plays an important role~(for an example of such logics, we
+refer the reader to \cite{Agudelo-Agudelo2017}).
+\citeauthor{foster2011integrating}~\cite{foster2011integrating} describe  the
+proof-reconstruction in \Agda for \name{Waldmeister}~\cite{hillenbrand1997}, a
+prover for pure equational logic. As far as we know, no other proof-
+reconstruction has been carried out in \Agda and with \Metis prover.
 
-In \Agda but with another logic, \citeauthor{foster2011integrating}~\cite{foster2011integrating}
-describe the proof-reconstruction for \name{Waldmeister}~\cite{hillenbrand1997}
-prover to pure equational logic, \ie,
-first-order logic with equality but no other predicate symbols and no
-functions symbols.
-
-In \name{Coq}~\cite{coqteam}, and proof assistant for type theory like \Agda,
+Another important proof-assistant in type theory is \name{Coq}~\cite{coqteam}.
 we found the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a
 certified checker for proof witness coming from the \SMT solver
-\name{veriT}~\cite{bouton2009} and adds a new tactic named verit,
-that calls \name{veriT} on any \name{Coq} goal.
-Also for \name{Coq},
-given a fixed but arbitrary first-order signature,
-\citeauthor{Bezem2002} in \cite{Bezem2002}
-transform a proof produced by the first-order automatic theorem
-prover \name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof
-term.
+\name{veriT}~\cite{bouton2009} and adds a new tactic named verit, that calls
+\name{veriT} on any \name{Coq} goal. Also for \name{Coq}, given a fixed but
+arbitrary first-order signature, \citeauthor{Bezem2002} in \cite{Bezem2002}
+transform a proof produced by the first-order automatic theorem prover
+\name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof term.
 

### 2017-10-27 paper/sections/type-theory.tex

@@
 
-Type theory and intuitionistic logic are accompanying theories since they are
-based on the same basis of constructive mathematics. Proving propositions in
-these theories demands a witness construction for the proof. Nonetheless,
-classical logic does not always have constructive proofs and some of its proofs
-are proved by non-constructive methods like refutation.
+Type theory and intuitionistic logic are accompanying theories since
+they are based on the same basis of constructive mathematics. Proving
+propositions in these theories demands a witness construction for the
+proof. Nonetheless, classical logic does not always have constructive
+proofs and some of its proofs are proved by non-constructive methods
+like refutation.
 
-To reconstruct proofs generated by \Metis, we have formalized in type theory the classical propositional logic.
-A  briefly description of it is presented in Appendix~\ref{app:CPL}. In this
-formalization, we assume the principle of excluded third (\abbre{PEM}) as the
-only axiom since \Metis is a prover for classical logic. Assuming \abbre{PEM},
-we can justify refutation proofs by deriving from it the \emph{reductio ad
-absurdum} rule (\abbre{RAA}). The \abbrev{RAA} rule is the formulation of the
-principle of proof by contradiction, that is, a derivation of a contradiction,
-$⊥$, from the hypothesis $(¬ φ)$, is a derivation of $φ$.
+To reconstruct proofs generated by \Metis, we have formalized in type
+theory the classical propositional logic.  A briefly description of it
+is presented in Appendix~\ref{app:CPL}. In this formalization, we
+assume the principle of excluded third (henceforth \abbre{PEM}) as the
+only axiom since \Metis is a prover for classical logic. Assuming
+\abbre{PEM}, we can justify refutation proofs by deriving from it the
+\emph{reductio ad absurdum} rule (henceforth \abbre{RAA}). The
+\abbrev{RAA} rule is the formulation of the principle of proof by
+contradiction, that is, a derivation of a contradiction,~$⊥$, from the
+hypothesis~$¬ φ$, is a derivation of~$φ$.
 
 \begin{notation}
-We write theorems in \CPL as the family of dependent types, $Γ ⊢ φ$ where
-the turnstile symbol (⊢) represents the syntactical consequence relation
-between a set of premises, $Γ : \List~\Prop$ and a conclusion $φ : \Prop$.
-$\abbre{List}$ type is the usual inductive type for lists.
+  The $\abbre{List}$ type is the usual inductive and parametric type
+  for lists. We formalise theorems in \CPL by an inductive family
+  $\_⊢\_$ indexed by a list of propositions and a proposition, that
+  is, $Γ ⊢ φ$ represents the syntactical consequence relation between
+  a list of premises, $Γ : \List~\Prop$ and a conclusion $φ : \Prop$.
 \end{notation}

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
[ paper ] minor fixes.

@@
 formulas with the following form:
+
 \begin{verbatim}
@@
 \end{verbatim}
+
 where the \name{language} can be \name{fof} or \name{cnf}. The
@@
 \name{hypothesis}.  The formulas include the constants
-\verb!$true! and \verb!$false!, the negation unary operator~\verb!~!,
+\verb!$true! and \verb!$false!, the negation unary operator~(\verb!~!),
 and the binary connectives \verb!&!, \verb!|!, \verb!=>!, and
-\verb!<=>! to represent $⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$, and $⇔$
+(\verb!<=>!) to represent ($⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$), and ($⇔$)
 respectively.
@@
   include the expected conclusion using the \verb!conjecture! keyword.
+
 \begin{verbatim}
@@
 \end{verbatim}
+
 \end{myexamplenum}
@@
 \begin{verbatim}
-  language(name, role, formula, source [,useful info]).
+  language(name, role, formula, source [,useful info]).,
 \end{verbatim}
@@
 We adopt a customized \TSTP syntax to keep as short as possible the \Metis
-derivations for increasing the readability in this paper.
+derivations for increasing the readability of this paper.
 

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] removed CPL.
[ paper ] minor fixes.

@@
 
-To reconstruct proofs generated by \Metis, we have formalized in type
-theory the classical propositional logic.  A briefly description of it
-is presented in Appendix~\ref{app:CPL}. In this formalization, we
-assume the principle of excluded third (henceforth \abbre{PEM}) as the
-only axiom since \Metis is a prover for classical logic. Assuming
-\abbre{PEM}, we can justify refutation proofs by deriving from it the
-\emph{reductio ad absurdum} rule (henceforth \abbre{RAA}). The
-\abbrev{RAA} rule is the formulation of the principle of proof by
-contradiction, that is, a derivation of a contradiction,~$⊥$, from the
-hypothesis~$¬ φ$, is a derivation of~$φ$.
+To reconstruct proofs generated by \Metis, we have formalized in type theory the
+classical propositional logic in~\cite{AgdaProp}.  A briefly description of it
+is presented in \cite{VanDalen1994}. In this formalization, we assume the
+principle of excluded third (henceforth \abbre{PEM}) as the only axiom since
+\Metis is a prover for classical logic. Assuming \abbre{PEM}, we can justify
+refutation proofs by deriving from it the \emph{reductio ad absurdum} rule
+(henceforth \abbre{RAA}). The \abbrev{RAA} rule is the formulation of the
+principle of proof by contradiction, that is, a derivation of a
+contradiction,~$⊥$, from the hypothesis~$¬ φ$, is a derivation of~$φ$.
 
@@
 have included structural rules like \emph{weaken}, formation and elimination
-rules for connectives and the PEM axiom as the constructors of the theorem type
+rules for connectives and the PEM axiom as the valid inference rules
 in Fig.~\ref{fig:CPL-inference-rules}.

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
fixed typos.

@@
 as the only valid deduction steps, \Metis
-attempts to prove conjectures by refutation (\eg,
+attempts to prove conjectures by refutation (\ie,
 \emph{falsium} in the root of the \TSTP derivation).
@@
 
-We present the list of inference rules used by \Metis in
-the \TSTP derivations for propositional logic
-in Table~\ref{tab:agda-metis-table}.
-We reconstruct these rules in Section~\ref{sec:proof-reconstruction}.
-The reader may notice that the
-inference rules presented in Fig~\ref{fig:metis-inferences} diverge from the
-rules in aforementioned table. However, the former rules are
-implemented by the latter rules. For instance, as far as we know, in
-\TSTP derivations, \canonicalize, \clausify, \conjunct, and \simplify, are all
-the rules that represent the \emph{axiom} rule by \Metis.
+We present the list of inference rules used by \Metis in the \TSTP derivations
+for propositional logic in Table~\ref{tab:agda-metis-table}. We reconstruct
+these rules in Section~\ref{sec:proof-reconstruction}. The reader may notice
+that the inference rules presented in Fig~\ref{fig:metis-inferences} diverge
+from the rules in aforementioned table. The former rules are implemented by the
+latter rules in the \TSTP derivations.
+For instance, as far as we know, in \TSTP
+derivations,  the \emph{axiom} rule is implemented by the rules
+\canonicalize, \clausify, \conjunct, and \simplify.
 

### 2017-10-27 paper/sections/proof-reconstruction.tex
fixed typos.

@@
 The overview of the proof-reconstruction is presented in
-Fig.~\ref{fig:proof-reconstruction-workflow}. The process begin with
+Fig.~\ref{fig:proof-reconstruction-workflow}. The process begins with
 a \TPTP file that encodes a problem in \CPL. We use this file as the
 input of the \Metis prover. If the problem is a theorem, \Metis
-reply a derivation of the proof in \TSTP format.
+generates a derivation of the proof in \TSTP format.
 
@@
 In the \Athena analysis, some unnecessary steps that introduce redundancies
-and some unused input is removed from the proof-tree.
+and some unused input are removed from the proof-tree.
 As result, we get from \Athena an \Agda file of the proof
@@
 module \Agda and the proposed formalizations for the
-propositional logic and the \Metis inferences.
+propositional logic and for the \Metis reasoning.
 In that case \Agda outputs an interface file.

### 2017-10-27 paper/sections/type-theory.tex
fixed typos.

@@
 
-To reconstruct \Metis' inference rules in type theory, we observed that
+To reconstruct \Metis inference rules in type theory, we observed that
 transformations performed by some rules are implemented by \emph{general

### 2017-10-27 paper/sections/proof-reconstruction/strip.tex
Cosmetic changes.
[ paper ] fixed typo.

@@
 in~\eqref{eq:strip-example}.
-So far, very little attention has been paid to the role of \strip rule.
+So far, very little attention has been paid to the role of the \strip rule
 in \TSTP derivation since \Metis does not make explicit the way
@@
 We based on the definition of this function from the \Metis source code.
-
 \begin{equation}
@@
 Then we define the \fstrip function is defined as follows.
-
 \begin{align}

### 2017-10-27 paper/sections/proof-reconstruction/strip.tex
[ paper ] fixed typo.

--- 2017-10-27 paper/sections/proof-reconstruction/strip.tex
@@
 in~\eqref{eq:strip-example}.
-So far, very little attention has been paid to the role of \strip rule.
-in \TSTP derivation since \Metis does not make explicit the way
+So far, very little attention has been paid to the role of the \strip rule
+in \TSTP derivations since \Metis does not make explicit the way
 it uses the subgoals to prove the conjecture.

### 2017-10-27 paper/sections/introduction.tex
Added URL for SystemOnTPTP.

@@
 least forty \ATPs---available from the Web service \name{SystemOnTPTP}
-of the TPTP World---just few of them show their proofs.
+of the TPTP
+World\footnote{\url{http://www.cs.miami.edu/~tptp/}.}---just few of
+them show their proofs.
 

### 2017-10-27 paper/sections/proof-reconstruction/strip.tex
[ paper ] fixed typo.

@@
 in~\eqref{eq:uh-definition}.
-If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$, where $\fuh₁$ is the function defined
+If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$ where $\fuh₁$ is the function defined
 in~\eqref{eq:uh-structured}.
@@
         we conclude $Γ ⊢ φ$.
-  \item For $n \geq 1$, we use induction on the structure of the second
+  \item For $n \geq 1$, we use induction on the structure of the first
         argument.

### 2017-10-27 paper/sections/proof-reconstruction/strip.tex
[ paper ] fixed typo in strip.

@@
 
-The $\fstrip₀$ function yields the conjunction of subgoals that implies the goal of the problem in the \Metis \TSTP derivations but is not a structurally recursive
-function.  Instead, we present its structural recursive version
-in~\eqref{eq:strip-fixed} after applying
-the bounded technique described in Section~\ref{ssec:structural-recursion}.
-We based on the definition of this function from the \Metis source code.
+The $\fstrip₀$ function yields the conjunction of subgoals that implies the
+goal of the problem in the \Metis \TSTP derivations but is not a structurally
+recursive function.  Instead, we present its structural recursive version
+in~\eqref{eq:strip-fixed}, the $\fstrip₁$ function after applying the bounded
+technique described in Section~\ref{ssec:structural-recursion}. We define the
+$\fstrip₁$ function based on the definition from the \Metis source code.
+
 \begin{equation}

### 2017-10-27 paper/sections/introduction.tex
Fixed typo.
Cosmetic changes.

@@
 
-This paper has been organized in the following way.
-In Section~\ref{sec:type-theory} some limitations of type theory
-are discussed from proof-reconstruction point view.
-In Section~\ref{sec:metis-language-and-proofs}, we introduce the
-\Metis prover.
-In Section~\ref{sec:proof-reconstruction} we show our
-approach to reconstruct \Metis proofs.
-Related work is described in Section~\ref{sec:related-work}.
-Conclusions and suggestions for future work are  presented in
-Section~\ref{sec:conclusions}.
+This paper has been organized in the following way.  In
+Section~\ref{sec:type-theory}, some limitations of type theory are
+discussed from proof-reconstruction point view.  In
+Section~\ref{sec:metis-language-and-proofs}, we introduce the \Metis
+prover.  In Section~\ref{sec:proof-reconstruction}, we show our
+approach to reconstruct \Metis proofs.  Related work is described in
+Section~\ref{sec:related-work}.  Conclusions and suggestions for
+future work are presented in Section~\ref{sec:conclusions}.
 
@@
 The source codes accompanying this paper (programs, libraries, and
-examples) are available as repositories at \verb!GitHub!:
-
+examples) are available at \verb!GitHub!:
 \begin{itemize}
@@
 \end{itemize}
-
 The proof-reconstruction was carried on for \Metis~2.3
-(release~20170822), and the accompanying source code was tested with
-\Agda~2.5.3, \Agda standard library~0.14 and \prg{GHC}~8.2.1.
-
+(release~20170822), and the programs and libraries were tested with
+\Agda~2.5.3, \Agda standard library~0.14, and \prg{GHC}~8.2.1.
 \end{document}

### 2017-10-27 paper/sections/type-theory.tex
Cosmetic changes.

@@
   Types are written using \abbre{small caps}.  We write the type
-  judgments as $m : \abbre{m}$ to denote that~$m$ is of
-  type~$\abbre{m}$.
+  judgments as $a : \abbre{a}$ to denote that~$a$ is of
+  type~$\abbre{a}$.
 \end{notation}
@@
 rules.  Since type theory can be seen as typed $λ$-calculus with
-dependent products, evaluation of $λ$-terms also called
+dependent function types, evaluation of $λ$-terms also called
 \emph{normalization} of the proof-terms, are reductions using the
-system inference rules.
-
-Therefore, the task to verify a proof that proves a certain theorem is
-translated to verify if the associated tree of the proof has the
-correspondent type of the theorem. We know this process as
-\emph{type-checking}. This feature of type theory allow us to verify a
-proof generated by an \ATP by reconstructing its proof-term to
-type-check the proof. For such a purpose, we use a proof assistant in
-type theory like \Agda to delegate this task.  However, this approach
-has some weak points discussed in~\cite{Bezem2002}. Some limitations
-from the type theory point of view for proof-reconstruction is
-described in the following sections.
+system inference rules. Therefore, the task to verify a proof that
+proves a certain theorem is translated to verify if the associated
+tree of the proof has the correspondent type of the theorem. We know
+this process as \emph{type-checking}. This feature of type theory
+allow us to verify a proof generated by an \ATP by reconstructing its
+proof-term to type-check the proof. For such a purpose, we use a proof
+assistant in type theory like \Agda to delegate this task.  However,
+this approach has some weak points discussed in~\cite{Bezem2002}. Some
+limitations from the type theory point of view for
+proof-reconstruction is described in the following sections.
 

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
Cosmetic changes.
[ paper ] fixed typos in resolve.

@@
 
-First, we define \fassoc$_{⬓}$ function in~\eqref{eq:fassoc}
+First, we define the \fassoc$_{⬓}$ function in~\eqref{eq:fassoc}
 to convert a disjunction or a conjunction into its right-associative form.
@@
 intends to construct a disjunction from another disjunction, specifically,
-this functions will try to rearrange the disjuncts in the source formula to
+this function will try to rearrange the disjuncts in the source formula to
 match with the target disjunction formula.
@@
   \label{thm:resolve}
-  If $Γ ⊢ φ₁$, $Γ ⊢ φ₂$, let $ℓ$ be a literal $ℓ : \Lit$, and $ψ : \Target$ then
-  $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$ where,
+  Let $ℓ$ be a literal, $ℓ : \Lit$, and $ψ : \Target$. If $Γ ⊢ φ₁$ and
+  $Γ ⊢ φ₂$ then $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$, where
   \begin{equation}

### 2017-10-27 paper/sections/type-theory.tex
Cosmetic changes.

@@
   Types are written using \abbre{small caps}.  We write the type
-  judgments as $a : \abbre{a}$ to denote that~$a$ is of
+  judgments as $a : \abbre{a}$ to denote that the term~$a$ is of
   type~$\abbre{a}$.
@@
 \begin{notation}
-
-We use \Prop for the type of propositions.
-For syntactical equivalence, we write the equality as $φ ≡ ψ$
-for $φ,~ψ : \Prop$. For this equality, we assume the
-reflexivity, symmetry and transitivity properties.
-
-\end{notation}
-
-\begin{notation}
-
-The type of natural numbers is called \Nat, and it is defined as
-usual, where $\zero$ and $\suc$ are its data constructors. We use names
-and symbols for the arithmetic operations as usual ($+$, $-$, $*$).
-We include syntax sugar for $\zero$, $\suc$, $\suc~\zero$,
-$\cdots$, with the decimal representation: $0$, $1$, $2$, $\cdots$
-as well.
-
+  We use \Prop for the type of propositions.  For syntactical
+  equivalence, we write the equality as $φ ≡ ψ$ for $φ,~ψ :
+  \Prop$. For this equality, we assume the reflexivity, symmetry and
+  transitivity properties. The type of natural numbers is called \Nat,
+  and it is defined as usual, where $\zero$ and $\suc$ are its data
+  constructors. We use names and symbols for the arithmetic operations
+  as usual ($+$, $-$, $*$).  We use syntax sugar for $\zero$, $\suc$,
+  $\suc~\zero$, $\dots$, with the decimal representation~$0$, $1$,
+  $2$, $\dots$ as well.
 \end{notation}

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed typos in resolve.

@@
 
-From now, we assume all propositions to be right-associative unless
+From now on, we assume all propositions to be right-associative unless
 otherwise stated.
@@
 Notice that other cases like $φ~∨~(ψ~∨~φ)$ do no reduce to $ψ~∨~φ$.
+We use this function in Lemma~\ref{lem:sbuild-or}.
 
@@
 with the same disjuncts of the source formula but also a complete different
-disjunction by adding new disjuncts to the source formula.
+disjunction by adding new disjuncts to the source formula
+via introduction rules for disjunctions.
 \end{myremark}
 
-The following lemma tries to reorder nested disjunctions
+The following lemma aims to reorder nested disjunctions
 by forcing the formula to be in right-associative form in order to
@@
 
-Now, we define function to work with nested conjunctions. This will
-help us in the end of this section to reorder conjunctive normal forms.
-For instance, the $\freorder_{∧}$ function in~\eqref{eq:reorder-and},
-reorders nested conjunctions.
+Now, we define the $\freorder_{∧}$ function in~\eqref{eq:reorder-and} to
+reorder nested conjunctions. This will help us in the end of this section to
+reorder conjunctive normal forms. For instance,
 

### 2017-10-27 paper/sections/type-theory.tex
Cosmetic changes.

@@
 
-To reconstruct proofs generated by \Metis, we have formalized in type theory the
-classical propositional logic in~\cite{AgdaProp}.  A briefly description of it
-is presented in \cite{VanDalen1994}. In this formalization, we assume the
-principle of excluded third (henceforth \abbre{PEM}) as the only axiom since
-\Metis is a prover for classical logic. Assuming \abbre{PEM}, we can justify
-refutation proofs by deriving from it the \emph{reductio ad absurdum} rule
-(henceforth \abbre{RAA}). The \abbrev{RAA} rule is the formulation of the
-principle of proof by contradiction, that is, a derivation of a
+To reconstruct proofs generated by \Metis, we have formalized in type
+theory the classical propositional logic in~\cite{AgdaProp}.  A
+briefly description of it is presented in \cite{VanDalen1994}. In this
+formalization, we have to assume the principle of excluded third
+(henceforth \abbre{PEM}) as an axiom since \Metis is a prover for
+classical logic. Assuming \abbre{PEM}, we can justify refutation
+proofs by deriving from it the \emph{reductio ad absurdum} rule
+(henceforth \abbre{RAA}). The \abbrev{RAA} rule is the formulation of
+the principle of proof by contradiction, that is, a derivation of a
 contradiction,~$⊥$, from the hypothesis~$¬ φ$, is a derivation of~$φ$.
@@
   The $\abbre{List}$ type is the usual inductive and parametric type
-  for lists. We formalise theorems in \CPL by an inductive family
-  $\_⊢\_$ indexed by a list of propositions and a proposition, that
-  is, $Γ ⊢ φ$ represents the syntactical consequence relation between
-  a list of premises, $Γ : \List~\Prop$ and a conclusion $φ : \Prop$.
+  for lists.
 \end{notation}
 
-We implemented in~\cite{AgdaProp} the syntactical consequence relation in a
-similar way as it was presented in~\cite{Altenkirch2015}. For that reason, we
-have included structural rules like \emph{weaken}, formation and elimination
-rules for connectives and the PEM axiom as the valid inference rules
-in Fig.~\ref{fig:CPL-inference-rules}.
+We formalise the syntactical consequence relation of \CPL by an
+inductive family $\_⊢\_$ with two indexes, a set of propositions (the
+premises) and a proposition (the conclusion), that is, $Γ ⊢ φ$
+represents that there is derivation with conclusion $φ : \Prop$ from
+the set of premises $Γ : \List~\Prop$. We implemented
+in~\cite{AgdaProp} the syntactical consequence relation in a similar
+way as it was presented in~\cite{Altenkirch2015}. For that reason, we
+have included structural rules like \emph{weaken}, formation and
+elimination rules for connectives and the PEM axiom as the valid
+inference rules in Fig.~\ref{fig:CPL-inference-rules}.
 

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed typos in resolve.

@@
 reorder nested conjunctions. This will help us in the end of this section to
-reorder conjunctive normal forms. For instance,
+reorder conjunctive normal forms.
 
@@
 The purpose of this function consists of extracting a disjunction from
-a conjunction, but without matter the order of inner disjunction.
+a conjunction, but without matter the order of the inner disjunctions.
 
@@
 
-Now, we are ready to reconstruct the \resolve rule. This is the
-first application of Lemma \ref{lem:reorder-and-or}.
+Now, we are ready to reconstruct the \resolve rule using
+Lemma~\ref{lem:reorder-and-or}.
 The \resolve rule is a generalization of the resolution theorem.

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed typos in resolve.

@@
 negative literal $¬ ℓ$ must occur in the formula from the second derivation,
-see the pattern of \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.
+see the pattern of the \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.
 

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed typos in resolve.

@@
 
-\begin{definition}
+\begin{mydefinition}
 A \emph{literal} is an atom (positive literal) or a negation
 of an atom (negative literal).
-\end{definition}
+\end{mydefinition}
 
@@
 Therefore, we perform a sequence of rearrangements inside the
-formulas involved to match with the pattern expected by the resolution theorem
-described in Fig.~\ref{fig:metis-inferences}. Using reordering after
+involved formulas to match with the expected pattern by the
+\emph{resolve} inference rule in Fig.~\ref{fig:metis-inferences}.
+
+Using reordering after
 applying a customized version of the resolution theorem defined

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed typos in resolve.
[ paper ] fixed typos in canonicalize.
Cosmetic changes.

@@
 
-The positive literal $ℓ$ must occur in
-the formula from the first derivation and the
-negative literal $¬ ℓ$ must occur in the formula from the second derivation,
-see the pattern of the \emph{resolve} rule in Fig.~\ref{fig:metis-inferences}.
+The positive literal~$ℓ$ must occur in the formula from the first
+derivation and the negative literal~$¬ ℓ$ must occur in the formula
+from the second derivation, see the pattern of the \emph{resolve} rule
+in Fig.~\ref{fig:metis-inferences}.
 
@@
 applying a customized version of the resolution theorem defined
-in~\eqref{eq:rsol} we get the expect result.
+in~\eqref{eq:rsol} we get the expected result.
 
@@
   Let $ℓ$ be a literal, $ℓ : \Lit$, and $ψ : \Target$. If $Γ ⊢ φ₁$ and
-  $Γ ⊢ φ₂$ then $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$, where
+  $Γ ⊢ φ₂$ then $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$ where,
   \begin{equation}

### 2017-10-27 paper/sections/proof-reconstruction/resolve.tex
Cosmetic changes.

@@
 \label{lem:build-or}
-  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fbuild_{∨}~φ~ψ$ where,
+  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fbuild_{∨}~φ~ψ$, where
 \begin{equation}
@@
 \label{lem:factor}
- If $Γ ⊢ φ$ then $Γ ⊢ \ffactor~φ$ where,
+ If $Γ ⊢ φ$ then $Γ ⊢ \ffactor~φ$, where
 \begin{align}
@@
 \label{lem:sbuild-or}
-If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fsbuild_{∨}~φ~ψ$ where,
+If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fsbuild_{∨}~φ~ψ$, where
 \begin{equation}
@@
   \label{lem:reorder-or}
-  If $Γ ⊢ φ$ and $ψ: \Target$ then $Γ ⊢ \freorder_{∨}~φ~ψ~$ where,
+  If $Γ ⊢ φ$ and $ψ: \Target$ then $Γ ⊢ \freorder_{∨}~φ~ψ~$, where
   \begin{align}
@@
   \label{lem:reorder-and}
-  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \freorder_{∧}~φ~ψ$ where,
+  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \freorder_{∧}~φ~ψ$, where
     \begin{align}
@@
   \label{lem:conjunct-or}
-  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fconjunctor~φ~ψ$ where,
+  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fconjunctor~φ~ψ$, where
   \begin{equation}
@@
   \label{lem:reorder-and-or}
-  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$ where,
+  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$, where
    \begin{align}
@@
   \label{lem:rsol}
-  If $Γ ⊢ φ$ then $Γ ⊢ \frsol~φ$ where,
+  If $Γ ⊢ φ$ then $Γ ⊢ \frsol~φ$, where
   \begin{equation}
@@
   Let $ℓ$ be a literal, $ℓ : \Lit$, and $ψ : \Target$. If $Γ ⊢ φ₁$ and
-  $Γ ⊢ φ₂$ then $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$ where,
+  $Γ ⊢ φ₂$ then $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$, where
   \begin{equation}

### 2017-10-27 paper/sections/related-work.tex
[ paper ] fixed related work.

@@
 
-\citeauthor{Kanso2012} in~\cite{Kanso2012,kanso2016light} presents a proof-
-reconstruction in \Agda for propositional logic. Its tool support proof-
-reconstruction for \name{EProver} and \name{Z3} ATPs following a similar work-
-flow as we presented in Section~\ref{ssec:workflow}. Nonetheless, his approach
+\citeauthor{Kanso2012} in~\cite{Kanso2012,kanso2016light} presents a
+proof-reconstruction in \Agda for propositional logic. Its tool support
+proof-reconstruction for \name{EProver} and \name{Z3} ATPs following a similar work-flow as we presented in Section~\ref{ssec:workflow}.
+Nonetheless, its approach
 employs semantics for logic equivalences. We have avoided the use of

### 2017-10-27 paper/sections/related-work.tex
[ paper ] fixed related work.

@@
 proof-reconstruction in \Agda for \name{Waldmeister}~\cite{hillenbrand1997}, a
-prover for pure equational logic. As far as we know, no other proof-
-reconstruction has been carried out in \Agda and with \Metis prover.
+prover for pure equational logic. As far as we know, no other
+proof-reconstruction has been carried out neither in \Agda nor with \Metis prover.
 
 Another important proof-assistant in type theory is \name{Coq}~\cite{coqteam}.
-we found the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a
+We found the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a
 certified checker for proof witness coming from the \SMT solver

### 2017-10-27 paper/sections/conclusions-and-future-work.tex
[ paper ] fixed a typo.
[ paper ] fixed conclusions.

@@
 for the propositional fragment of the \Metis prover. We provided for
-each \Metis inference rule a formal description in type theory.
-This formalizations is mainly exposed in
+each \Metis inference rule a formal description in type theory
+following a syntactical approach.
+This formalizations are mainly exposed in
 Section~\ref{ssec:emulating-inferences}.

### 2017-10-27 paper/sections/conclusions-and-future-work.tex
[ paper ] fixed conclusions.

@@
 For predicative logic, recall satisfiability is undecidable and
-its syntactical aspect plays a important role to reconstruct proofs.
+its syntactical aspect plays an important role to reconstruct proofs.
 
@@
 a theorem prover has a real significant impact for these automatic
-tools.  The reverse engineering task to understand the prover
+tools.  The reverse engineering task to grasp the prover
 reasoning can reveal important issues or bugs in many parts of these

### 2017-10-27 paper/sections/abstract.tex
Last changes in the Paper (#37)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

* [ pape

@@
 
-% ===================================================================
-
 \begin{abstract}
-We describe a syntactical proof-reconstruction
-approach to verify proofs generated by \Metis prover to problems in
-classical propositional logic.
-To verify these \Metis proofs, we developed a tool able to translate
-such derivations to \Agda proof-terms.
-We formulate in type theory each inference rule found
-in \Metis derivations. This allowed us to type-check with \Agda, \Metis proofs
-step-by-step. We leave it for future work,
-the opportunity to extend this work to support other provers, proof assistants, and formalisms.
+We describe a syntactical proof-reconstruction approach to verify proofs
+generated by \Metis prover to problems in classical propositional logic.
+To verify these \Metis proofs, we developed a tool able to translate such
+derivations to \Agda proof-terms. We formalise in type theory each inference
+rule found in \Metis derivations. This allowed us to type-check with \Agda,
+\Metis proofs step-by-step. We leave it for future work, the opportunity to
+extend this work to support other provers, proof-assistants, and formalisms.
 
@@
 proof-assistant}
-
 \end{abstract}

### 2017-10-27 paper/sections/proof-reconstruction.tex
[ paper ] proof-assistant and proof-term.

@@
 our case, the system of origin, the automatic theorem prover, is
-\Metis; the target system is a proof assistant, \Agda. We choose
-\Agda, but another proof assistant with the same support of type
+\Metis; the target system is a proof-assistant, \Agda. We choose
+\Agda, but another proof-assistant with the same support of type
 theory and inductive types could be used.

### 2017-10-27 paper/sections/related-work.tex
[ paper ] proof-assistant and proof-term.

@@
 transform a proof produced by the first-order automatic theorem prover
-\name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof term.
+\name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof-term.
 
-There are some successful attempts using proof assistants for classical logic
+There are some successful attempts using proof-assistants for classical logic
 instead of type theory.
@@
 
-The \name{Isabelle} proof assistant has the \name{Sledgehammer} tool.
+The \name{Isabelle} proof-assistant has the \name{Sledgehammer} tool.
 This program provides a full integration between

### 2017-10-30 paper/sections/proof-reconstruction/resolve.tex
[ paper ] reorder-and-or missing comma.

@@
           ψ, &\text{ if } φ ≡ ψ;\\
-          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁\\
+          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁,\\
              &\text{ and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂;\\

### 2017-10-30 src/Data/TSTP/Rule.hs
thm-rule ==> rule-thm in agda proofs.

@@ -36,11 +36,11 @@ data Rule = Canonicalize
           deriving (Eq, Ord, Read, Show)
 
 instance Pretty Rule where
-  pretty Canonicalize = pretty "thm" <> hypen <> pretty "canonicalize"
-  pretty Clausify     = pretty "thm" <> hypen <> pretty "clausify"
-  pretty Conjunct     = pretty "thm" <> hypen <> pretty "conjunct"
-  pretty Negate       = pretty "thm" <> hypen <> pretty "negate"
-  pretty Resolve      = pretty "thm" <> hypen <> pretty "resolve"
-  pretty Simplify     = pretty "thm" <> hypen <> pretty "simplify"
-  pretty Strip        = pretty "thm" <> hypen <> pretty "strip"
+  pretty Canonicalize = pretty (pretty "canonicalize-thm")
+  pretty Clausify     = pretty (pretty "clausify-thm")
+  pretty Conjunct     = pretty (pretty "conjunct-thm")
+  pretty Negate       = pretty (pretty "negate-thm")
+  pretty Resolve      = pretty (pretty "resolve-thm")
+  pretty Simplify     = pretty (pretty "simplify-thm")
+  pretty Strip        = pretty (pretty "strip-thm")
   pretty _            = error "Rule no supported yet"

### 2017-10-30 src/Athena/Translation/AgdaFile.hs
[ AgdaFile ] supporting renaming in Agda-Metis.

@@ -371,7 +371,7 @@ docProofGoal agdaFile =
        <+> pretty "Γ ⊢ " <> (pretty (fileConjecture agdaFile)) <> line
   <> pretty "proof" <+> equals <> line
   <> indent 2 (pretty "⇒-elim" <> line)
-  <> indent 2 (pretty "thm-strip" <> line <> nestedproofs) <> line
+  <> indent 2 (pretty Strip <> line <> nestedproofs) <> line
     where
       nestedproofs :: Doc
       nestedproofs =
@@ -452,13 +452,8 @@ docSteps subgoalN (Leaf _ axiom) agdaFile =
 ------------------------------------------------------------------------------
 
 docSteps subgoalN (Root Canonicalize tag [subtree]) agdaFile =
-  parens (canonicalizeThm <+> getFormulaByTag agdaFile tag <> line
+  parens (pretty Canonicalize <+> getFormulaByTag agdaFile tag <> line
     <> indent 2 (docSteps subgoalN subtree agdaFile))
-  where
-    canonicalizeThm ∷ Doc
-    canonicalizeThm = case subtree of
-      (Leaf _ axiom ) → pretty "thm-canonicalize-axiom"
-      _               → pretty "thm-canonicalize"
 
 ------------------------------------------------------------------------------
 -- Clausify.

### 2017-10-30 src/Athena/Translation/AgdaFile.hs
[ agda-metis ] updated to latest.

@@ -398,9 +398,7 @@ docSteps _ (Leaf Conjecture conjecture) _ = pretty conjecture
 docSteps subgoalN (Leaf _ axiom) agdaFile =
   parens (prettyWeaken <> line
     <> indent 2
-       prettyAssume)
-      -- (parens (pretty "--" <+> getFormulaByTag agdaFile axiom <> line
-      --   <> prettyAssume)))
+      (parens prettyAssume))
   where
 
     dict ∷ ProofMap

### 2017-10-31 paper/sections/type-theory.tex
[ paper ] some fixes in type-theory section.

@@
 
-We produce derivation trees inside the judgments using the derivation
-rules.  Since type theory can be seen as typed $λ$-calculus with
-dependent function types, evaluation of $λ$-terms also called
-\emph{normalization} of the proof-terms, are reductions using the
-system inference rules. Therefore, the task to verify a proof that
-proves a certain theorem is translated to verify if the associated
-tree of the proof has the correspondent type of the theorem. We know
-this process as \emph{type-checking}. This feature of type theory
-allow us to verify a proof generated by an \ATP by reconstructing its
-proof-term to type-check the proof. For such a purpose, we use a proof
-assistant in type theory like \Agda to delegate this task.  However,
-this approach has some weak points discussed in~\cite{Bezem2002}. Some
-limitations from the type theory point of view for
-proof-reconstruction is described in the following sections.
+We produce derivation trees inside the judgments using the derivation rules.
+Since type theory can be seen as typed $λ$-calculus with dependent function
+types, evaluation of $λ$-terms also called \emph{normalization} of the proof-
+terms, are reductions using the system inference rules. Therefore, the task to
+verify a proof that proves a certain theorem is translated to verify if the
+associated tree of the proof has the correspondent type of the theorem. We know
+this process as \emph{type-checking}. This feature of type theory allow us to
+verify a proof generated by an \ATP by reconstructing its proof-term to type-
+check the proof. For such a purpose, we use a proof assistant based on type
+theory like \Agda to delegate this task.
+% However, this approach has some weak points discussed in~\cite{Bezem2002}.
+Some limitations from the type theory
+point of view for proof-reconstruction is described in the following sections.
 
@@
 
-Algorithms based on general recursion can not be translated
-directly in type theory since it is not a guarantee they terminate. For that
-reason, we follow the technique described in~\cite{Bertot2004} to avoid
-termination problems by modifying the recursive functions to be
-\emph{structural recursive}.
-% (see \cite{Coquand1992,Abel2002,Bove2005} for more details).
+Functions defined by a general recursion can not be directly translated in type
+theory since it is not a guarantee they terminate. For that reason, we follow
+the technique described in~\cite{Bertot2004} to avoid termination problems by
+modifying the recursive functions to be \emph{structural recursive}. % (see
+\cite{Coquand1992,Abel2002,Bove2005} for more details).
 
@@
   We use \Prop for the type of propositions.  For syntactical
-  equivalence, we write the equality as $φ ≡ ψ$ for $φ,~ψ :
+  equivalence, we write the equality as $φ ≡ ψ$, for $φ,~ψ :
   \Prop$. For this equality, we assume the reflexivity, symmetry and
@@
   constructors. We use names and symbols for the arithmetic operations
-  as usual ($+$, $-$, $*$).  We use syntax sugar for $\zero$, $\suc$,
+  as usual (\eg, $+$, $-$, $*$).  We use syntax sugar for $\zero$, $\suc$,
   $\suc~\zero$, $\dots$, with the decimal representation~$0$, $1$,
@@
 
-Hence, one approach to define a structural recursive function based on
-a general recursive function $\rm{f}:~\Prop~\to~\Prop$ is to formulate a new
-function $\rm{f}^{*}~:~\Prop~\to~\Nat~\to~\Prop$ where all of its recursive
-calls are done on smaller arguments.
+Hence, one approach to define a structural recursive function based on a general
+recursive function $\rm{f}:~\abbre{a}~\to~\abbre{b}$ is to formulate a new
+function $\rm{f}^{*}~:~\abbre{a}~\to~\Nat~\to~\abbre{b}$ where all of its
+recursive calls are done on smaller arguments.
 
@@
 
-We bounded the recursion calls in~\eqref{eq:uh-structured} with a \Nat argument. This natural number represents the complexity measure of $\fuh_{0}$
-function.
+We bounded the recursion calls of the $\fuh_{0}$ function using its
+\emph{complexity measure}.
 
-The \emph{complexity measure} defined in \cite{Agudelo-Agudelo2017}
-and presented in \cite{VanDalen1994} as \emph{the rank for a
-proposition}, is a function $\Prop \to \Nat$ that assigns a natural
-number to a formula like we do with the following $\frank$ function.
-The symbols $c_{¬}$ and $c_{\square}$ are non-negative integer
-numbers called the complexity of the respective connective.
+The complexity measure of a function is the number of steps
+the function takes to finish. Since the functions defined for formulas
+are based on the formula structure, we assign a complexity measure for each
+of these cases in the formula structure. We refer the reader to~\cite{VanDalen1994,Agudelo-Agudelo2017} for more details about this kind of function.
 
-\begin{equation}
-% \label{eq:rank-definition}
-\begin{aligned}
-&\hspace{.495mm}\frank : \Prop → \Nat\\
-&\begin{array}{llll}
-\frank~(¬~φ)           &= \frank~φ₁~+~c_{¬}\\
-\frank~(φ₁~\square~φ₂) &= \fmax~(\frank~φ₁)~(\frank~φ₂) + c_{\square}\\
-\frank~φ               &= 0.
-\end{array}
-\end{aligned}
-\end{equation}
-
-We define the $\fuh_{cm}: \Prop → \Nat$ function as
+In our case, we define the $\fuh_{cm}: \Prop → \Nat$ function as
 the complexity measure for the $\fuh_0$ function.

### 2017-10-31 paper/sections/introduction.tex
[ paper ] minor fixes/ .

@@
 stage~\cite{paulson2010three,hurlin07practical,kaliszyk2013}. Another
-approaches has been proposed for proof-reconstructing using type
-theory~\cite{Bezem2002,armand2011,Ekici2017,kanso2016light}.
+approaches has been proposed for proof-reconstructing based on type
+theory~\cite{Bezem2002,kanso2016light,Keller2013}.
 
@@
 formalize the subset of the \Metis inference rules for the
-propositional logic fragment using a syntactical treatment of the
-logic. The \Metis reasoning was formalized in
+propositional logic fragment using a syntactical treatment.
+The \Metis reasoning was formalized in
 \Agda~\cite{agdateam}---our target system---in two
@@
 
-The source codes accompanying this paper (programs, libraries, and
-examples) are available at \verb!GitHub!:
+The source code accompanying this paper (programs, libraries, and
+examples) is available at \verb!GitHub!:
 \begin{itemize}

### 2017-10-31 paper/sections/type-theory.tex
[ paper ] minor fixes/ .

@@
 
-Type theory is another formalism for the foundation of mathematics, and it has became in a key instrument to study logic and proof theory.
-It was proposed in 1902 to avoid the Russell's paradox and it follows
+Type theory is a formalism for the foundation of mathematics, and it has became in a key instrument to study logic and proof theory.
+It was proposed in 1902 to avoid Russell's paradox and it follows
 the same philosophy of constructive mathematics where the witness of
@@
 derivation rules. These rules enables us to derive a kind of conclusions called
-\emph{judgments}. A judgment is another way to say a term has certain type.
+\emph{judgments}. A judgment is another way to say that a term has a certain type.
 
@@
 
-To reconstruct \Metis inference rules in type theory, we observed that
-transformations performed by some rules are implemented by \emph{general
-recursive} functions.
+To reconstruct \Metis inference rules in type theory, we observed that some
+rules or their inner functions are implemented by \emph{general recursive}
+functions.
 

### 2017-11-14 paper/sections/abstract.tex
minor fixes.
[ paper ] minor change in the abstract.

@@
 \begin{abstract}
+
 We describe a syntactical proof-reconstruction approach to verify proofs
-generated by \Metis prover to problems in classical propositional logic.
-To verify these \Metis proofs, we developed a tool able to translate such
-derivations to \Agda proof-terms. We formalise in type theory each inference
-rule found in \Metis derivations. This allowed us to type-check with \Agda,
-\Metis proofs step-by-step. We leave it for future work, the opportunity to
-extend this work to support other provers, proof-assistants, and formalisms.
+generated by \Metis prover to problems in classical propositional logic. To
+verify \Metis proofs, we developed a tool and two Agda libraries able to
+translate such derivations to \Agda proof-terms. We formalise in type theory
+each inference rule found in the \Metis derivations. This allowed us to type-
+check with \Agda, \Metis proofs step-by-step.
+
+% We leave it for future work, the opportunity to
+% extend this work to support other provers, proof-assistants, and formalisms.
 

### 2017-11-14 paper/sections/introduction.tex

@@
 approaches has been proposed for proof-reconstructing based on type
-theory~\cite{Bezem2002,kanso2016light,Keller2013}.
+theory in~\cite{Bezem2002,kanso2016light,Keller2013}.
 
@@
 \end{itemize}
-The proof-reconstruction was carried on for \Metis~2.3
-(release~20170822), and the programs and libraries were tested with
-\Agda~2.5.3, \Agda standard library~0.14, and \prg{GHC}~8.2.1.
+
+We carried out proof-reconstruction for \Metis~2.3
+(release~20170822). The \Athena program was tested with \prg{GHC}~8.2.1.
+The \verb!agda-prop! and \verb!agda-metis! libraries were tested with
+\Agda~2.5.3 and \Agda standard library~0.14.
+
 \end{document}

### 2017-11-14 paper/sections/proof-reconstruction/strip.tex
[ paper ] fixed typo in strip.

@@
 
-In a similar way as we define $\fuh_{cm}$ in~\eqref{eq:uh-complexity}, we define
-$\fstrip_{cm}$ as the complexity measure for the $\fstrip₀$ function.
-Then we define the \fstrip function is defined as follows.
+In a similar way as we define $\fuh_{cm}$ in~\eqref{eq:uh-complexity}, we
+define $\fstrip_{cm}$ as the complexity measure for the $\fstrip₀$ function.
+Then we define the \fstrip function as follows in~\ref{eq:strip}.
+
 \begin{align}
@@
 formula~$φ$ by following the equations in~\eqref{eq:strip-fixed}.
-We present a straightforward case with double negation, a case with
-conjunction connective, and last, the case with a negated disjunction.
+We present a straightforward case with double negation, the case for
+conjunctions, and last, the case for a negated disjunction.
 We refer the reader to~\cite{AgdaMetis} for the complete proof in \Agda.

### 2017-11-15 src/Athena/Options.hs
Some changes to improve the performance (#44)
* Working on issue #31.

* added docTag to handle axioms.

@@ -11,6 +11,7 @@ module Athena.Options
     , optHelp
     , optInputFile
     , optOutputFile
+    , optScriptMode
     , optVersion
     )
   , printUsage
@@ -40,6 +41,7 @@ data Options = Options
   , optHelp       ∷ Bool
   , optInputFile  ∷ Maybe FilePath
   , optOutputFile ∷ Maybe FilePath
+  , optScriptMode ∷ Bool
   , optVersion    ∷ Bool
   }
 
@@ -49,6 +51,7 @@ defaultOptions = Options
   , optHelp       = False
   , optInputFile  = Nothing
   , optOutputFile = Nothing
+  , optScriptMode = False
   , optVersion    = False
   }
 
@@ -76,6 +79,9 @@ outputFileOpt file opts =
 versionOpt ∷ OM
 versionOpt opts = Right opts { optVersion = True }
 
+scriptModeOpt ∷ OM
+scriptModeOpt opts = Right opts { optScriptMode = True }
+
 -- | Description of the command-line 'Options'.
 options ∷ [OptDescr OM]
 options =
@@ -83,6 +89,8 @@ options =
       ""
   , Option ['h'] ["help"] (NoArg helpOpt)
       "Prints help message"
+  , Option []    ["script"] (NoArg scriptModeOpt)
+      "Script mode for printing the proof."
   , Option []    ["version"] (NoArg versionOpt)
       "Show version number"
   ]

### 2017-11-15 src/Athena/Translation/AgdaFile.hs

@@ -8,14 +8,16 @@ module Athena.Translation.AgdaFile
    (
    AgdaFile
       ( AgdaFile
-      , fileVariables
       , fileAxioms
       , fileConjecture
       , fileDict
       , fileName
       , filePremises
+      , fileScriptMode
       , fileSubgoals
+      , fileTags
       , fileTrees
+      , fileVariables
       )
    , docAxioms
    , docConjecture
@@ -53,6 +55,7 @@ import Athena.Utils.PrettyPrint
   , equals
   , hashtag
   , hypenline
+  , hypenlineQED
   , indent
   , int
   , lbracket
@@ -73,6 +76,7 @@ import Data.Proof
 import Data.List                ( isPrefixOf, nub)
 import Data.Maybe               ( fromJust )
 import qualified Data.Map as Map
+import qualified Data.Set as Set
 
 import Data.TSTP
   ( F ( name, role, formula, source )
@@ -108,7 +112,9 @@ data AgdaFile = AgdaFile
   , fileDict       ∷ ProofMap
   , fileName       ∷ FilePath
   , filePremises   ∷ [F]
+  , fileScriptMode ∷ Bool
   , fileSubgoals   ∷ [F]
+  , fileTags       ∷ Set.Set String
   , fileTrees      ∷ [ProofTree]
   , fileVariables  ∷ [V]
   }
@@ -178,9 +184,11 @@ docModule filename =
 docImports ∷ Int → Doc
 docImports n =
        hypenline
-   <@> pretty "open import ATP.Metis" <+> int n <+> pretty "public" <> line
-   <>  pretty "open import Data.PropFormula" <+> int n <+> pretty "public"
-   <> line <@> hypenline
+   <@> pretty "open import ATP.Metis" <+> int n <+> pretty "public"
+   <> line
+   <> pretty "open import Data.PropFormula" <+> int n <+> pretty "public"
+   <> line
+   <@> hypenline
 
 ------------------------------------------------------------------------------
 -- Variables.
@@ -215,7 +223,7 @@ docVars vars =
 
 definition ∷ F → Doc
 definition fm =
-     pretty fm <+> colon  <+> pretty "PropFormula"   <> line
+     pretty fm <+> colon  <+> pretty "PropFormula" <> line
   <> pretty fm <+> equals <+> pretty formulaF <> line
   where
     formulaF ∷ Formula
@@ -278,6 +286,7 @@ docConjecture ∷ F → Doc
 docConjecture fm =
[…]

### 2017-11-15 src/Athena/Translation/AgdaFile.hs
[ AgdaFile ] Simplify rule: fixed left folding.

@@ -721,35 +721,21 @@ docSteps subgoalN (Root Resolve tag [left, right]) agdaFile =
 ------------------------------------------------------------------------------
 
 docSteps subgoalN (Root Simplify tag nodes) agdaFile =
-  simplification
-  where
-    smode ∷ Bool
-    smode = fileScriptMode agdaFile
-
-    rNodes ∷ [ProofTree]
-    rNodes = case nodes of
-      []    → []
-      [x]   → [x]
-      [x,y] → [x,y]
-      xs    → reverse xs
-
-    simplification ∷ Doc
-    simplification =
-      foldr
-        (\node y →
-          parens $
-            vsep
-              [ pretty Simplify <+> getFormulaByTag agdaFile tag
-              , indent 2
-                  (vsep
-                    [ y
-                    , docSteps subgoalN node agdaFile
-                    ]
-                   )
-               ]
-        )
-        (docSteps subgoalN (last rNodes) agdaFile)
-        (init rNodes)
+  foldl
+    (\x node →
+      parens $
+        vsep
+          [ pretty Simplify <+> getFormulaByTag agdaFile tag
+          , indent 2
+              (vsep
+                [ x
+                , docSteps subgoalN node agdaFile
+                ]
+               )
+           ]
+    )
+    (docSteps subgoalN (head nodes) agdaFile)
+    (tail nodes)
 
 ------------------------------------------------------------------------------
 -- Strip.

### 2017-11-16 paper/sections/proof-reconstruction/clausify.tex
Cosmetic changes.
[ paper ] clausify: fixed parenthesis.
[ paper ] clausify: removed CNF abbrev.
[ slides ] lots of changes.

@@
 to its clausal normal form is not unique, and \Metis has a customized
-approach to perform that transformation. That is the reason we perform some
-reordering for the \CNF of the source formula to fulfill this issue.
+approach to perform that transformation. Hence, we perform a
+reordering of the conjunctive normal form for the source formula.
 
@@
 In the following \TSTP derivation by \Metis, we see how
-\clausify transform the \texttt{norm0} formula to get \texttt{norm1} formula.
+\clausify transforms the \texttt{norm0} formula to get \texttt{norm1} formula.
 
@@
 \label{thm:clausify}
-  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fclausify~φ~ψ$, where,
-
+   Let $ψ : \Target$. If $Γ ⊢ φ$ then $Γ ⊢ \fclausify~φ~ψ$, where
   \begin{equation*}
@@
         ψ, &\text{ if }φ≡ψ;\\
-        \freorder_{∧∨}~(\fcnf~φ~ψ), &\text{ otherwise.}
+        \freorder_{∧∨}~(\fcnf~φ)~ψ, &\text{ otherwise.}
       \end{cases}

### 2017-11-16 slides/Jonathan-Proof-Reconstruction.tex
[ slides ] fixing compilation.
minor changes.
fixed slides
[ Slides ] preparing new ones.
[ slides ] lots of changes.
[ slides ] last changes.

@@
 \definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
+\definecolor{background}{RGB}{1,0,102}
 \definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
+\definecolor{bline}{RGB}{255, 255, 255}
 \definecolor{blue(munsell)}{rgb}{0.0, 0.5, 0.69}
@@
 \definecolor{cadet}{rgb}{0.33, 0.41, 0.47}
+\definecolor{decoration}{RGB}{10,164,216}
+\definecolor{fontc}{RGB}{255, 255, 255}
+\definecolor{logo}{RGB}{1,0,102}
 
@@
 \setbeamerfont{frametitle}{size=\small,series=\bfseries}
-\setbeamercolor{frametitle}{fg=white,bg=plum}
+\setbeamercolor{frametitle}{fg=white,bg=blue}
 
 \setbeamerfont{framesubtitle}{size=\normalfont\scriptsize}
-\setbeamercolor{framesubtitle}{fg=white, bg=plum!80!black}
+\setbeamercolor{framesubtitle}{fg=white, bg=blue!80!black}
 
@@
 
-,
+% --------------------------------------------------------------------------
+% Listings
+% --------------------------------------------------------------------------
+
+\usepackage{minted}
+\setminted[cagda]{
+  bgcolor   = aliceblue
+, fontsize  = \footnotesize
+, frame     = none
+% , framerule = 0.4pt
+% , framesep  = 0pt
+, style     = cagda
+}
 
@@
 \vfill
+\end{frame}
+
+\begin{frame}
+
 \end{frame}
@@
 \begin{minted}{cagda}
-data Prop : Set where
+data PropFormula : Set where
   Var : Fin n → Prop

### 2017-11-17 paper/sections/type-theory.tex
[ paper ] some corrections added.

@@
 the main actors in type theory are the statements and their proofs.
-By following the Curry-Howard correspondence (see, for example,~\cite{Wadler-2015}), we say
-\emph{types} are theorems and their \emph{terms} are their proofs.
+By following the Curry-Howard correspondence (see, for example,~\cite{Wadler-2015}), types as propositions.
+A proposition corresponds to a type, and a proof of that propositions
+corresponds to the term of that proof (henceforth proof-term).
+%\emph{types} are theorems and their \emph{terms} are their proofs.
 
@@
 types, evaluation of $λ$-terms also called \emph{normalization} of the proof-
-terms, are reductions using the system inference rules. Therefore, the task to
-verify a proof that proves a certain theorem is translated to verify if the
-associated tree of the proof has the correspondent type of the theorem. We know
+terms, are reductions using the system inference rules.
+
+Therefore, the
+proof verification task becomes in type theory as verifying that the proof-term has the correspondent type of the theorem. We know
 this process as \emph{type-checking}. This feature of type theory allow us to
@@
 the technique described in~\cite{Bertot2004} to avoid termination problems by
-modifying the recursive functions to be \emph{structural recursive}. % (see
+modifying the recursive functions to be \emph{structurally recursive}. % (see
 \cite{Coquand1992,Abel2002,Bove2005} for more details).
@@
 \begin{notation}
-  We use \Prop for the type of propositions.  For syntactical
-  equivalence, we write the equality as $φ ≡ ψ$, for $φ,~ψ :
+  We use \Prop for the type of propositions.
+  We write the equality as $φ ≡ ψ$, for $φ,~ψ :
   \Prop$. For this equality, we assume the reflexivity, symmetry and
-  transitivity properties. The type of natural numbers is called \Nat,
+  transitivity properties.
+  We say $\varphi$ and $\psi$ are Two propositions are syntactically equivalent if there is a derivation from $\varphi$ to $\psi$ and
+  a derivation from $\psi$ to $\varphi$.
+   The type of natural numbers is called \Nat,
   and it is defined as usual, where $\zero$ and $\suc$ are its data
@@
 call on arguments no structurally smaller.
-For instance, on the first call, $φ ≡ (φ₁ ∧ φ₂) ⇒ φ₃$, the recursion
-calls on the  $φ₁ ⇒ (φ₂ ⇒ φ₃)$ argument that is not a subformula of φ.
+For instance, in the first equation,
+$$\fuh_{0} (φ₁ ⇒ (φ₂ ⇒ φ₃)) = \fuh_{0}~((φ₁ ∧ φ₂) ⇒ φ₃),$$
+the function $\fuh_{0}$ calls on the  $(φ₁ ∧ φ₂) ⇒ φ₃$ argument in the right-hand side but this formula is not a subformula of $φ₁ ⇒ (φ₂ ⇒ φ₃)$.
 Therefore, one way to translate $\fuh_{0}$ to type
@@
 proof. Nonetheless, classical logic does not always have constructive
-proofs and some of its proofs are proved by non-constructive methods
-like refutation.
+proofs since some of the proofs are stated by refutation.
 
@@
 briefly description of it is presented in \cite{VanDalen1994}. In this
-formalization, we have to assume the principle of excluded third
+formalization, we have to assume the principle of excluded middle
 (henceforth \abbre{PEM}) as an axiom since \Metis is a prover for

### 2017-11-20 paper/sections/abstract.tex
[ paper ] lots of changes.

@@
 
-We describe a syntactical proof-reconstruction approach to verify proofs
-generated by \Metis prover to problems in classical propositional logic. To
-verify \Metis proofs, we developed a tool and two Agda libraries able to
-translate such derivations to \Agda proof-terms. We formalise in type theory
-each inference rule found in the \Metis derivations. This allowed us to type-
-check with \Agda, \Metis proofs step-by-step.
-
-% We leave it for future work, the opportunity to
-% extend this work to support other provers, proof-assistants, and formalisms.
+We describe a syntactical proof-reconstruction approach to verify derivations
+generated by \Metis prover to theorems in classical propositional logic. To
+verify such derivations, we formalise in type theory each inference rule
+of the \Metis reasoning. We developed a tool jointly with two \Agda libraries
+to translate \Metis derivations to \Agda proof-terms.
+These developments allowed us to type-check with \Agda, \Metis proofs
+step-by-step.
 

### 2017-11-20 paper/sections/introduction.tex
This closes #40
[ paper ] lots of changes.

@@
 instrument in different disciplines and real applications (\eg,
-verifying railway interlocking systems~\cite{Kanso2012}). Since some
-bugs have been found in these programs (see, for example,
-\cite{Keller2013,Bohme2011,Fleury2014}), researchers and users from
-academy and industry have shown an increased interest to
+verifying a railway interlocking system, an operating-system kernel,
+or a pseudo-random number generator for cryptography). Since some
+programming errors have been found in these programs (see, for
+example, \cite{Keller2013,Bohme2011,Fleury2014}), researchers and
+users from academy and industry have shown an increased interest to
 \emph{formally} prove the validity of \ATPs' results.
@@
 
-Proof-reconstruction address this problem. It becomes in mostly cases
-a reverse engineering task to verify the prover reasoning. That
-usually happen when the reconstruction is made by another and not by
+Proof-reconstruction addresses this problem. It becomes in mostly
+cases a reverse engineering task to verify the prover reasoning. That
+usually happens when the reconstruction is made by another and not by
 the developers of the \ATP. The presentation of the proofs generated
-by the prover play an important role in proof-reconstruction. To
+by the prover plays an important role in proof-reconstruction. To
 verify such a proof, it is convenient to have it in a consistent
-format, that is, a full script describing step-by-step with exhaustive
-details and without ambiguities, the derivation to get the proof. For
+format, that is, a full script describing the derivation step-by-step
+with  exhaustive details and without ambiguities. For example, for
 classical propositional logic (henceforth \CPL) from a list of at
-least forty \ATPs---available from the Web service \name{SystemOnTPTP}
-of the TPTP
-World\footnote{\url{http://www.cs.miami.edu/~tptp/}.}---just few of
+least forty \ATPs---available from the Web service
+\name{SystemOnTPTP} of the TPTP World\footnote{\url{http://www.cs.miami.edu/~tptp/}.}---just few of
 them show their proofs.
@@
 One approach to address the proof-reconstruction problem is
-integrating the \ATP, the \emph{source} system, with a
-proof-assistant, the \emph{target} system. The target system is the
-proof \emph{checker} in charge to verify the source system reasoning.
+justifying each inference rule of the \emph{source} system, the \ATP,
+with a proof-assistant, the \emph{target} system. The target system
+is the proof \emph{checker} in charge to verify the source system
+reasoning.
 These proof-assistants allow us to formalize the logical system used
 in the proofs, \ie, logical constants, axioms, inference rules,
-hypotheses, and theorems. A proof-reconstruction tool provides such an
-integration, translating the derivation generated by the prover into
-the formalism of the proof-assistant.
+hypotheses, and theorems. A proof-reconstruction tool provides such
+an integration, translating the derivation generated by the prover
+into the formalism of the proof-assistant.
 
-Previous studies have reported proof-reconstruction using
-proof-assistants based on higher-order logic where the development is
-at a mature
-stage~\cite{paulson2010three,hurlin07practical,kaliszyk2013}. Another
-approaches has been proposed for proof-reconstructing based on type
-theory in~\cite{Bezem2002,kanso2016light,Keller2013}.
+Previous studies have reported proof-reconstruction using proof-
+assistants based on higher-order logic where the development is at a
+mature stage~\cite{paulson2010three,hurlin07practical,kaliszyk2013}.
+Another approaches has been proposed for proof-reconstructing based
+on type theory in~\cite{Bezem2002,kanso2016light,Keller2013}.
 
@@
 
-% Finally, in appendix \textsc{A}, we provide a small example of the
-% proof-reconstruction workflow.
-
 The source code accompanying this paper (programs, libraries, and
 examples) is available at \verb!GitHub!:
+
 \begin{itemize}
-  \item The \Athena program that translates proofs generated by \Metis to \Agda:
-  \url{http://github.com/jonaprieto/athena}.
+  \item The \Athena program that translates proofs generated by \Metis
+  to \Agda code: \url{http://github.com/jonaprieto/athena}.
+
   \item The \verb!agda-prop! library as a formalization in \Agda for
@@
   \url{http://github.com/jonaprieto/agda-prop}.
+
   \item The \verb!agda-metis! library as a formalization in \Agda to
@@
   \url{http://github.com/jonaprieto/agda-prop}.
+
 \end{itemize}
 
-We carried out proof-reconstruction for \Metis~2.3
-(release~20170822). The \Athena program was tested with \prg{GHC}~8.2.1.
-The \verb!agda-prop! and \verb!agda-metis! libraries were tested with
+The proof-reconstruction tool \Athena was tested with \prg{GHC}~8.2.1.
+Both libraries, \verb!agda-prop! and \verb!agda-metis! were tested with
 \Agda~2.5.3 and \Agda standard library~0.14.
+\Athena jointly with \verb!agda-prop! and \verb!agda-metis! are able to reconstruct propositional proofs of \Metis~2.3 (release~20171021).
 

### 2017-11-20 paper/sections/metis-language-and-proofs.tex
[ paper ] fixed typos in metis descrp..
[ paper ] lots of changes.

@@
   \begin{bprooftree}
-    \AxiomC{$Γ ⊢ l ∨ φ$}
-    \AxiomC{$Γ ⊢ ¬ l ∨ ψ$}
-    \RightLabel{resolve $l$}
+    \AxiomC{$Γ ⊢ ℓ ∨ φ$}
+    \AxiomC{$Γ ⊢ ¬ ℓ ∨ ψ$}
+    \RightLabel{resolve $ℓ$}
     \BinaryInfC{$Γ ⊢ φ ∨ ψ$}
@@
 It includes the first-order form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf}) formats~\cite{sutcliffe2009}.
-The \TPTP syntax describes a well-defined grammar to handle annotated
+The \TPTP syntax\footnote{See the complete grammar
+at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} describes a well-defined grammar to handle annotated
 formulas with the following form:
@@
 \name{conjecture}, \name{definition}, \name{plain} or an
-\name{hypothesis}.  The formulas include the constants
-\verb!$true! and \verb!$false!, the negation unary operator~(\verb!~!),
-and the binary connectives \verb!&!, \verb!|!, \verb!=>!, and
-(\verb!<=>!) to represent ($⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$), and ($⇔$)
-respectively.
+\name{hypothesis}.
+
+The formulas include the constants
+\verb!$true! and \verb!$false!, the negation unary
+operator~(\verb!~!), and the binary connectives
+(\verb!&!, \verb!|!, \verb!=>!) to represent
+($⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$) respectively.
 
@@
 
-We adopt a customized \TSTP syntax to keep as short as possible the \Metis
-derivations for increasing the readability of this paper.
+We adopt a customized \TSTP syntax to keep as short as possible the
+\Metis derivations for increasing the readability of this paper.
 
@@
   fof(goal, conjecture, p).
-  fof(sg0, p, inf(strip, [goal])).
-  fof(neg0, ¬ p, inf(negate, [sg0])).
-  fof(norm0, ¬ p, inf(canonicalize, [neg0])).
-  fof(norm1, p, inf(canonicalize, [premise])).
-  fof(norm2, ⊥, inf(simplify, [norm0, norm1]))
-  cnf(refute0, ⊥, inf(canonicalize, [norm2])).
+  fof(s₀, p, inf(strip, goal)).
+  fof(neg₀, ¬ p, inf(negate, s₀)).
+  fof(n₀, ¬ p, inf(canonicalize, neg₀)).
+  fof(n₁, p, inf(canonicalize, premise)).
+  fof(n₂, ⊥, inf(simplify, [n₀, n₁]))
+  cnf(r₀, ⊥, inf(canonicalize, n₂)).
 \end{verbatim}
@@
 A proof generated by \Metis encodes a natural
-deduction proof.
-With the inference rules in Fig.~\ref{tab:agda-metis-table}
+deduction proof, Fig.~\ref{fig:metis-example} is an example of such kind of proof. With the inference rules in
+Fig.~\ref{tab:agda-metis-table}
 as the only valid deduction steps, \Metis

### 2017-11-20 paper/sections/proof-reconstruction.tex
Updating the paper in master for the visibility. (#42)
* [ paper ] Eq removed.

* resolve fixing

* [ paper ] last changes.

* [ paper ] lots of changes.

* ruu

* ppp

* [ paper ] lots of changes.

* [ paper ] last changes.

* [ paper ] some messages added.

* [ paper ] fixed subgoal description.

* [ paper ] fixed rm funnctions and example added.

* [ paper ] fixed normalized formula description.

* [ paper ] canon-and fixed.

* [ paper ] fixed form function text description.

* [ paper ] fixed canoncialize theorem.

* [ paper ] fixed conjunct example.

* [ paper ] fixed minor typos.

* [ pa

@@
 \label{ex:inference-rule-pattern}
-\Metis has a inference rule named \conjunct. We reconstruct this
-inference rule as follow. We define in \Agda the function
-\fconjunct which has the following pattern:
+Let \texttt{metisRule} be a \Metis inference rule. To reconstruct this rule,
+we define the function \fun{metisRule} in type theory that follows the pattern:
+
 \begin{equation*}
   \begin{aligned}
-  &\hspace{.495mm}\fconjunct : \Source → \Target → \Prop\\
+  &\hspace{.495mm}\fun{metisRule} : \Source → \Target → \Prop\\
   &\begin{array}{ll}
-  \fconjunct~φ~ψ\ &=
+  \fun{metisRule}~φ~ψ\ &=
       \begin{cases}
-      ψ, &\text{if }\fconjunct \text{ built }ψ\text{ by applying valid}\\
-         &\text{transformations or other rules to }φ;\\
+      ψ, &\text{if the conclusion}ψ\text{ can be}\text{ derived by applying certain inference}\\
+         &\text{rules to the premise }φ;\\
       φ, &\text{otherwise;}
@@
 
-To justify all transformations done by the \fconjunct rule, we prove
-its soundness with a theorem. This theorem would be
+To justify all transformations done by the \fun{metisRule} rule, we prove
+its soundness with a theorem like the following:
+
 \begin{equation*}
-  \text{If }Γ ⊢ φ \text{ then }Γ ⊢ \fconjunct~φ~ψ, \text{ where } ψ : \Target.
+  \text{If }Γ ⊢ φ \text{ then }Γ ⊢ \fun{metisRule}~φ~ψ, \text{ where } ψ : \Target.
 \end{equation*}
+
 \end{myexamplenum}

### 2017-11-20 paper/sections/proof-reconstruction/clausify.tex
[ paper ] some corrections added.
[ paper ] lots of changes.

@@
 
-\subsubsection{Clausification.}
+\subsubsection{Clausify.}
 \label{sssec:clausification}
 
-The \clausify rule transforms a formula into its clausal normal form.
-It is important to notice that this kind of conversion between one formula
-to its clausal normal form is not unique, and \Metis has a customized
-approach to perform that transformation. Hence, we perform a
-reordering of the conjunctive normal form for the source formula.
+The \clausify rule is another alternative way to transform a formula
+into its clausal normal form but without any simplification since
+remember this conversion is taking into account by the \canonicalize
+rule. It is important to notice that this kind of conversion between
+one formula to its clausal normal form is not unique, and \Metis has
+a customized approach to perform that transformation. Hence, we
+perform a reordering of the conjunctive normal form for the source
+formula.
 
@@
 In the following \TSTP derivation by \Metis, we see how
-\clausify transforms the \texttt{norm0} formula to get \texttt{norm1} formula.
+\clausify transforms the \texttt{n₀} formula to get \texttt{n₁} formula.
 
 \begin{verbatim}
-  fof(norm0, ¬ p ∨ (q ∧ r) ...
-  fof(norm1, (¬ p ∨ q) ∧ (¬ p ∨ r), inf(clausify, [norm0])).
+  fof(n₀, ¬ p ∨ (q ∧ r) ...
+  fof(n₁, (¬ p ∨ q) ∧ (¬ p ∨ r), inf(clausify, n₀)).
 \end{verbatim}

### 2017-11-20 paper/sections/proof-reconstruction/resolve.tex
[ paper ] lots of changes.

@@
 
-\subsubsection{Resolution.}
+\subsubsection{Resolve.}
 \label{sssec:resolve}
@@
 prover reasoning steps. Since we left out semantics to treat only the
-syntax aspects of propositional logic, our approach shows logic equivalence
-by converting propositions to their conjunctive normal form,
-and reordering those and the inner disjunctions to match them.
-Below, we provide Lemma~\ref{lem:reorder-or}, Lemma~\ref{lem:reorder-and}, Lemma~\ref{lem:reorder-and-or} to perform such reordering tasks,
-the omitted proofs can be found in~\cite{AgdaMetis}.
+syntax aspects of propositional logic, our approach shows logic
+equivalence by converting propositions to their conjunctive normal
+form, and reordering those and the inner disjunctions to match them.
+Below, we provide Lemma~\ref{lem:reorder-or},
+Lemma~\ref{lem:reorder-and}, Lemma~\ref{lem:reorder-and-or} to perform such reordering tasks, the omitted proofs can be found
+in~\cite{AgdaMetis}.
 
-First, we define the \fassoc$_{⬓}$ function in~\eqref{eq:fassoc}
-to convert a disjunction or a conjunction into its right-associative form.
-The square symbol (⬓) can be the conjunction symbol or the disjunction symbol.
-We use $\fassoc_{∧}$ to convert conjunctions and $\fassoc_{∨}$ for
-disjunctions.
+First, we define the \fassoc$_{⬓}$ function in~\eqref{eq:fassoc} to
+convert a disjunction or a conjunction into its right-associative
+form. The square symbol (⬓) can be the conjunction symbol or the
+disjunction symbol. We use $\fassoc_{∧}$ to convert conjunctions and
+$\fassoc_{∨}$ for disjunctions.
 
@@
     \fassoc_{⬓} &((φ₁~⬓~φ₂)~⬓~φ₃) &= \fassoc_{⬓}~(φ₁~⬓~(φ₂~⬓~φ₃))\\
-    \fassoc_{⬓} &(φ₁~⬓~φ₂)        &= φ₁~∨~\fassoc_{⬓}~φ₂\\
+    \fassoc_{⬓} &(φ₁~⬓~φ₂)        &= φ₁~⬓~\fassoc_{⬓}~φ₂\\
     \fassoc_{⬓} &φ                &= φ.
@@
 \begin{myremark}
-In \TPTP syntax, the formulas are in left-associative form by default.
-Despite of that convention, \Metis assumes the formulas to be in
-right-associative form by default. This is a matter to take into account for
-the proof-reconstruction.
+
+In \TPTP syntax, the formulas are in left-associative form by
+default. Despite of that convention, \Metis assumes the formulas to
+be in right-associative form by default. This is a matter to take
+into account for the proof-reconstruction.
+
 \end{myremark}
 
-The $\fbuild_{∨}$ function defined in~\eqref{eq:build-or}
-intends to construct a disjunction from another disjunction, specifically,
-this function will try to rearrange the disjuncts in the source formula to
+The $\fbuild_{∨}$ function defined in~\eqref{eq:build-or} intends to
+construct a disjunction from another disjunction, specifically, this
+function will try to rearrange the disjuncts in the source formula to
 match with the target disjunction formula.
@@
 
-From now on, we assume all propositions to be right-associative unless
-otherwise stated.
+From now on, we assume all propositions to be right-associative
+unless otherwise stated.
 
@@
 (\eg, $\ffactor~(φ ∨ φ)~=~φ$).
-Notice that other cases like $φ~∨~(ψ~∨~φ)$ do no reduce to $ψ~∨~φ$.
+Notice that other cases like $φ~∨~(ψ~∨~φ)$ do not reduce to $ψ~∨~φ$.
 We use this function in Lemma~\ref{lem:sbuild-or}.
@@
 \begin{myremark}
+
 Notice that using $\fsbuild_{∨}$ we can build not only a disjunction
-with the same disjuncts of the source formula but also a complete different
-disjunction by adding new disjuncts to the source formula
+with the same disjuncts of the source formula but also a complete
+different disjunction by adding new disjuncts to the source formula
 via introduction rules for disjunctions.
+
 \end{myremark}
@@
 
-Now, we define the $\freorder_{∧}$ function in~\eqref{eq:reorder-and} to
-reorder nested conjunctions. This will help us in the end of this section to
-reorder conjunctive normal forms.
+Now, we define the $\freorder_{∧}$ function in~\eqref{eq:reorder-and}
+to reorder nested conjunctions. This will help us in the end of this
+section to reorder conjunctive normal forms.
 
@@
 
-In the last example in~\eqref{ex:reorder-example}, we could not build the conjunction
-$r ∧ (q ∨ p)$ since $p ∨ q$ is not syntactical equal to $q ∨ p$.
-We solve this issue in Lemma~\ref{lem:reorder-and-or} by
+In the last example in~\eqref{ex:reorder-example}, we could not build
+the conjunction $r ∧ (q ∨ p)$ since $p ∨ q$ is not syntactical equal
+to $q ∨ p$. We solve this issue in Lemma~\ref{lem:reorder-and-or} by
 using the $\fconjunctor$ function defined in~\eqref{eq:conjunct-or}.
-The purpose of this function consists of extracting a disjunction from
-a conjunction, but without matter the order of the inner disjunctions.
+The purpose of this function consists of extracting a disjunction
+from a conjunction, but without matter the order of the inner disjunctions.
 
@@
 derivation and the negative literal~$¬ ℓ$ must occur in the formula
-from the second derivation, see the pattern of the \emph{resolve} rule
-in Fig.~\ref{fig:metis-inferences}.
+from the second derivation, see the pattern of the \emph{resolve}
+rule in Fig.~\ref{fig:metis-inferences}.
 
@@
 \begin{verbatim}
-  cnf(ref4, (¬ r ∨ p ∨ q), inf(canonicalize, [norm5])).
-  cnf(ref5, (p ∨ q ∨ r), inf(canonicalize, [norm6])).
-  cnf(ref6, (p ∨ q), inf(resolve, r, [ref5, ref4])).
+  cnf(r₄, (¬ r ∨ p ∨ q), ...
+  cnf(r₅, (p ∨ q ∨ r), ...
+  cnf(r₆, (p ∨ q), inf(resolve, r, [r₅, r₄])).
 \end{verbatim}
+
 In the excerpt above, we apply resolution to the first two formulas,
-$¬ r ∨ p ∨ q$ and $p ∨ q ∨ r$. The last line tells us the literal used
-for resolution is $r$. Syntactically speaking,
-we can not derive neither the conclusion $p ∨ q$ in \verb!ref6! nor apply the resolution theorem with \verb!ref4! and \verb!ref5! since the formulas do not fit the pattern required.
+$¬ r ∨ p ∨ q$ and $p ∨ q ∨ r$.
+The last line tells us the literal used
+for resolution is $r$. Syntactically speaking, we can not derive
+neither the conclusion $p ∨ q$ in \verb!r₆! nor apply the resolution
+theorem with \verb!r₄! and \verb!r₅! since the formulas do not fit
+the pattern required.
 
-If the scenario would have other like replacing \verb!ref5! by
+If the scenario would have other like replacing \verb!r₅! by
 \begin{verbatim}
-  cnf(ref5, (r ∨ p ∨ q), inf(canonicalize, [norm6])).
+  cnf(r₅, (r ∨ p ∨ q), ...
 \end{verbatim}
@@
 
-Using reordering after
-applying a customized version of the resolution theorem defined
-in~\eqref{eq:rsol} we get the expected result.
+Using reordering after applying a customized version of the
+resolution theorem defined in~\eqref{eq:rsol} we get the expected
+result.
 
@@
 \begin{myexamplenum}
-Continuing with the problem presented in Example~\ref{ex:resolve-tstp},
-we can use Theorem \ref{thm:resolve} to derive $Γ ⊢ p ∨ q$.
-% Let be $φ₁ ≡ p ∨ q ∨ r$ and $φ₂ ≡ ¬ r ∨ p ∨ q$.
+
+Continuing with the problem presented in
+Example~\ref{ex:resolve-tstp}, we can use Theorem \ref{thm:resolve} to derive $Γ ⊢ p ∨ q$.
 

### 2017-11-20 paper/sections/proof-reconstruction/strip.tex
[ paper ] lots of changes.

@@
 
-\subsubsection{Stripping a goal.}
+\subsubsection{Strip.}
 \label{sssec:strip-a-goal}
@@
   fof(goal, conjecture, (p ∧ r) ∧ q)).
-  fof(sg0, p, inf(strip, [goal])).
-  fof(sg1, p ⇒ r, inf(strip, [goal])).
-  fof(sg2, (p ∧ r) ⇒ q, inf(strip, [goal])).
+  fof(s₁, p, inf(strip, goal)).
+  fof(s₂, p ⇒ r, inf(strip, goal)).
+  fof(s₃, (p ∧ r) ⇒ q, inf(strip, goal)).
 \end{verbatim}
@@
 
-In a similar way as we define $\fuh_{cm}$ in~\eqref{eq:uh-complexity}, we
-define $\fstrip_{cm}$ as the complexity measure for the $\fstrip₀$ function.
+In a similar way as we define $\fuh_{cm}$
+in~\eqref{eq:uh-complexity}, we
+define the $\fstrip_{cm}$ function in Appendix~\ref{app:strip-cm} as the complexity measure for the $\fstrip₀$ function.
 Then we define the \fstrip function as follows in~\ref{eq:strip}.
@@
 in~\eqref{eq:strip-fixed}.
-Let $s₁$ and $s₂$ be the subgoals of the goal $φ$, that is,
-$$\fstrip₁~φ~n~≡~s₁∧~s₂.$$
-If $Γ ⊢ s₁$ and $Γ ⊢ s₂$ then $Γ ⊢ φ$.
+Let $s₂$ and $s₃$ be the subgoals of the goal $φ$, that is,
+$$\fstrip₁~φ~n~≡~s₂∧~s₃.$$
+If $Γ ⊢ s₂$ and $Γ ⊢ s₃$ then $Γ ⊢ φ$.
 \end{mainth}
@@
 In the following \TSTP derivation, note that the three subgoals
-\verb!sg0!, \verb!sg1! and \verb!sg2! are assumed by the \negate
-rule in \verb!neg0!, \verb!neg1! and  \verb!neg2! respectively.
+\verb!s₁!, \verb!s₂! and \verb!s₃! are assumed by the \negate
+rule in \verb!neg₁!, \verb!neg₂! and  \verb!neg₃! respectively.
 
@@
   fof(goal, conjecture, (p ∧ r ∧ q)).
-  fof(sg0, p, inf(strip,[goal])).
-  fof(sg1, p ⇒ r, inf(strip,[goal])).
-  fof(sg2, (p ∧ r) ⇒ q, inf(strip,[goal])).
-  fof(neg0, ¬ p, inf(negate,[sg0])).
+  fof(s₁, p, inf(strip, goal)).
+  fof(s₂, p ⇒ r, inf(strip, goal)).
+  fof(s₃, (p ∧ r) ⇒ q, inf(strip, goal)).
+  fof(neg₁, ¬ p, inf(negate, s₁)).
   ...
-  fof(neg1, ¬ (p ⇒ r), inf(negate,[sg1])).
+  fof(neg₂, ¬ (p ⇒ r), inf(negate, s₂)).
   ...
-  fof(neg2, ¬ ((p ∧ r) ⇒ q), inf(negate,[sg2])).
+  fof(neg₃, ¬ ((p ∧ r) ⇒ q), inf(negate, s₃)).
 \end{verbatim}

### 2017-11-20 paper/sections/type-theory.tex
[ paper ] lots of changes.

@@
 
-Type theory is a formalism for the foundation of mathematics, and it has became in a key instrument to study logic and proof theory.
-It was proposed in 1902 to avoid Russell's paradox and it follows
-the same philosophy of constructive mathematics where the witness of
-a statement is \emph{everything}. In that direction, we could say
-the main actors in type theory are the statements and their proofs.
-By following the Curry-Howard correspondence (see, for example,~\cite{Wadler-2015}), types as propositions.
-A proposition corresponds to a type, and a proof of that propositions
-corresponds to the term of that proof (henceforth proof-term).
-%\emph{types} are theorems and their \emph{terms} are their proofs.
+% It was proposed in 1902 to avoid Russell's paradox --- (bettter mention BHK)
+Type theory is a formalism for the foundation of mathematics,
+it has became in a key instrument to study logic and proof theory
+that follows the same basis of constructive mathematics where the witness of a statement is \emph{everything}.
+In that direction, we could say the main actors in type theory are the statements and their proofs.
 
+By following the Curry-Howard correspondence (see, for
+example,~\cite{Wadler-2015}), types are propositions. The inhabitants
+of that types, the \emph{terms}, are proofs of that propositions.
 Since type theory is a formal system, we have a syntax and a set of
-derivation rules. These rules enables us to derive a kind of conclusions called
-\emph{judgments}. A judgment is another way to say that a term has a certain type.
+derivation rules. These rules enables us to derive a kind of
+conclusions called \emph{judgments}. A judgment is another way to say
+that a term has a certain type.
 
@@
 
-We produce derivation trees inside the judgments using the derivation rules.
-Since type theory can be seen as typed $λ$-calculus with dependent function
-types, evaluation of $λ$-terms also called \emph{normalization} of the proof-
-terms, are reductions using the system inference rules.
+We produce derivation trees inside the judgments using the derivation
+rules. Since type theory can be seen as typed $λ$-calculus with
+dependent function types, evaluation of $λ$-terms also called
+\emph{normalization} of the proof- terms, are reductions using the
+system inference rules.
 
-Therefore, the
-proof verification task becomes in type theory as verifying that the proof-term has the correspondent type of the theorem. We know
-this process as \emph{type-checking}. This feature of type theory allow us to
-verify a proof generated by an \ATP by reconstructing its proof-term to type-
-check the proof. For such a purpose, we use a proof assistant based on type
-theory like \Agda to delegate this task.
-% However, this approach has some weak points discussed in~\cite{Bezem2002}.
-Some limitations from the type theory
-point of view for proof-reconstruction is described in the following sections.
+Therefore, the proof verification task becomes in type theory as
+verifying that the proof-term has the correspondent type of the
+theorem. We know this process as \emph{type-checking}.
+This feature of type theory allow us to verify a proof generated by an \ATP by reconstructing its proof-term to type-check the proof. For such a
+purpose, we use a proof assistant based on type theory like \Agda to
+delegate this task. % However, this approach has some weak points
+discussed in~\cite{Bezem2002}. Some limitations from the type theory
+point of view for proof-reconstruction is described in the following
+sections.
 
@@
 
-To reconstruct \Metis inference rules in type theory, we observed that some
-rules or their inner functions are implemented by \emph{general recursive}
-functions.
+To reconstruct \Metis inference rules in type theory, we observed
+that some rules or their inner functions are implemented by \emph{
+general recursive} functions.
 
-Functions defined by a general recursion can not be directly translated in type
-theory since it is not a guarantee they terminate. For that reason, we follow
-the technique described in~\cite{Bertot2004} to avoid termination problems by
-modifying the recursive functions to be \emph{structurally recursive}. % (see
-\cite{Coquand1992,Abel2002,Bove2005} for more details).
+Functions defined by a general recursion can not be directly
+translated in type theory since it is not a guarantee they terminate.
+For that reason, we follow the technique described
+in~\cite{Bertot2004} to avoid termination problems by modifying the
+recursive functions to be \emph{structurally recursive}.
 
-This paper adopts the notion of \emph{structurally smaller}
-from~\cite{Abel2002}, that is, a recursive function is structurally
-recursive if it calls itself with only structurally smaller arguments.
+A recursive function is structurally recursive if it calls itself
+with only structurally smaller arguments~\cite{Abel2002}.
+General recursive functions can be rewrote into structurally
+recursive functions by  using for instance, the \emph{bounded
+recursion} technique. For a yet another methods, we refer the reader
+to \cite{Coquand1992,Abel2002,Bove2005}.
 
-General recursive functions can be rewrote into structurally recursive
-functions by using for instance, the \emph{bounded recursion} technique.
-For a yet another methods, we refer
-the reader to \cite{Coquand1992,Abel2002,Bove2005}.
-The bounded technique defines a new structural recursive function based on
-the general recursive function by adding an argument.
-The new argument is the \emph{bound}, a natural number given by the
-function complexity. In other words, the added argument will represent
-the number of times the function needs to call itself to get the
-expected outcome.
+The bounded technique defines a new structural recursive function
+based on the general recursive function by adding an argument. The
+new argument is the \emph{bound}, a natural number given by the
+function complexity.
+In other words, the added argument will represent the number of times
+the function needs to call itself to get the expected outcome.
 
@@
   We use \Prop for the type of propositions.
-  We write the equality as $φ ≡ ψ$, for $φ,~ψ :
+  A proposition is an expression of indivisible propositional variables (\eg, symbols $φ₀, φ₁, \cdots$), the logic constants:
+  $⊥$, $⊤$, the binary connectives ($∧, ∨, ⇒, ⇔)$, and the negation
+  $(\neg)$.
+  We write the equality using the symbol (≡) as $φ ≡ ψ$, for $φ,~ψ :
   \Prop$. For this equality, we assume the reflexivity, symmetry and
   transitivity properties.
-  We say $\varphi$ and $\psi$ are Two propositions are syntactically equivalent if there is a derivation from $\varphi$ to $\psi$ and
-  a derivation from $\psi$ to $\varphi$.
+  % We say $φ$ and $ψ$ are syntactically equivalent if there is a derivation from $φ$ to $ψ$ and
+  % a derivation from $ψ$ to $φ$.
   The type of natural numbers is called \Nat,
@@
 
-Hence, one approach to define a structural recursive function based on a general
-recursive function $\rm{f}:~\abbre{a}~\to~\abbre{b}$ is to formulate a new
-function $\rm{f}^{*}~:~\abbre{a}~\to~\Nat~\to~\abbre{b}$ where all of its
-recursive calls are done on smaller arguments.
+Hence, one approach to define a structural recursive function based
+on a general
+recursive function $\rm{f}:\,\abbre{a}~\to~\abbre{b}$ is to
+formulate a new
+function $\rm{f}^{*}:\,\abbre{a}~\to~\Nat~\to~\abbre{b}$ where all
+of its recursive calls are done on smaller arguments.
+
+\begin{notation}
+We define some functions by pattern-matching on \Prop or \Nat.
+\end{notation}
 
@@
 
-Let us consider the following example to show the bounded recursion technique
-for the \fuh function. This function is used for reconstructing
-a \Metis inference rule in Section~\ref{sssec:strip-a-goal}.
+Let us consider the following example to show the bounded recursion
+technique for defining the \fuh function. This function is used for
+reconstructing a \Metis inference rule in
+Section~\ref{sssec:strip-a-goal}.
 
@@
 
-The complexity measure of a function is the number of steps
-the function takes to finish. Since the functions defined for formulas
-are based on the formula structure, we assign a complexity measure for each
-of these cases in the formula structure. We refer the reader to~\cite{VanDalen1994,Agudelo-Agudelo2017} for more details about this kind of function.
+The complexity measure of a function is the number of steps the
+function takes to finish. Since the $\fuh_{0}$ function is recursive,
+we can define its complexity measure by defining a recursive function
+instead of a closed formula for such a number. However, this function
+must to be structurally recursive as well and can be defined by
+following the pattern-matching cases of its definition.
 
-In our case, we define the $\fuh_{cm}: \Prop → \Nat$ function as
-the complexity measure for the $\fuh_0$ function.
+Therefore, we define in~\eqref{eq:uh-complexity} the complexity
+measure function of $\fuh_{0}$ by assigning the number of steps to
+finish for each pattern-matching case.
+We have used the complexity measure definition for a formula defined in~\cite{Agudelo-Agudelo2017} to define other complexity measures
+in this paper.
 
@@
 
-For a more complete treatment of general recursion, and how to define
-well-founded and well-structural recursive functions, we refer the
-reader to~\cite{Bove2005}.
+% For a more complete treatment of general recursion, and how to define
+% well-founded and well-structural recursive functions, we refer the
+% reader to~\cite{Bove2005}.
 
@@
 Type theory and intuitionistic logic are accompanying theories since
-they are based on the same basis of constructive mathematics. Proving
-propositions in these theories demands a witness construction for the
-proof. Nonetheless, classical logic does not always have constructive
-proofs since some of the proofs are stated by refutation.
+they are based on the same philosophical basis of constructive
+mathematics. Proving propositions in these theories demands a witness
+construction for the proof. Nonetheless, classical logic does not
+always have constructive proofs since some of the proofs are stated
+by refutation.
 
@@
 theory the classical propositional logic in~\cite{AgdaProp}.  A
-briefly description of it is presented in \cite{VanDalen1994}. In this
-formalization, we have to assume the principle of excluded middle
-(henceforth \abbre{PEM}) as an axiom since \Metis is a prover for
-classical logic. Assuming \abbre{PEM}, we can justify refutation
+briefly description of it is presented in \cite{VanDalen1994}.
+In this formalization, we have to assume the principle of excluded
+middle (henceforth \abbre{PEM}) as an axiom since \Metis is a prover
+for classical logic. Assuming \abbre{PEM}, we can justify refutation
 proofs by deriving from it the \emph{reductio ad absurdum} rule
@@
 the principle of proof by contradiction, that is, a derivation of a
-contradiction,~$⊥$, from the hypothesis~$¬ φ$, is a derivation of~$φ$.
+contradiction,~$⊥$, from the hypothesis~$¬ φ$, is a derivation
+of~$φ$.
 
@@
     \AxiomC{$Γ , φ ⊢ ψ$}
-    \RightLabel{$\Rightarrow$-intro}
-    \UnaryInfC{$Γ ⊢ φ \Rightarrow ψ$}
+    \RightLabel{$⇒$-intro}
+    \UnaryInfC{$Γ ⊢ φ ⇒ ψ$}
   \end{bprooftree}
@@
 \begin{bprooftree}
-\AxiomC{$Γ ⊢ φ \Rightarrow ψ$}
+\AxiomC{$Γ ⊢ φ ⇒ ψ$}
 \AxiomC{$Γ ⊢ φ$}
-\RightLabel{$\Rightarrow$-elim}
+\RightLabel{$⇒$-elim}
 \BinaryInfC{$Γ ⊢ ψ$}

### 2017-11-21 paper/sections/metis-language-and-proofs.tex
[ paper ] fixed some typos related with nnf.

@@
 It includes the first-order form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf}) formats~\cite{sutcliffe2009}.
-The \TPTP syntax\footnote{See the complete grammar
+The \TPTP syntax\footnote{See the complete syntax grammar
 at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} describes a well-defined grammar to handle annotated

### 2017-11-21 paper/sections/proof-reconstruction.tex
[ paper ] fixed some typos related with nnf.

@@
 \label{ex:inference-rule-pattern}
-Let \texttt{metisRule} be a \Metis inference rule. To reconstruct this rule,
-we define the function \fun{metisRule} in type theory that follows the pattern:
+Let \texttt{metisRule} be a \Metis inference rule. To reconstruct
+this rule, we define the function \fun{metisRule} in type theory
+that follows the pattern:
 
@@
       \begin{cases}
-      ψ, &\text{if the conclusion}ψ\text{ can be}\text{ derived by applying certain inference}\\
+      ψ, &\text{if the conclusion }ψ\text{ can be}\text{ derived by applying certain inference}\\
          &\text{rules to the premise }φ;\\
@@
 
-To justify all transformations done by the \fun{metisRule} rule, we prove
-its soundness with a theorem like the following:
+To justify all transformations done by the \fun{metisRule} rule, we
+prove its soundness with a theorem like the following:
 
@@
 
-% -----------------------------------------------------------------------------
+% ------------------------------------------------------------------
 
@@
 
-%------------------------------------------------------------------------------
+% -------------------------------------------------------------------
 
@@
 for a problem in propositional logic.
-For instance, we tested successfully the translation by \Athena jointly with
-the \Agda formalizations of the rules mentioned above with more than eighty
-representative theorems in propositional logic. An interested reader can test
-the problems~\cite{Prieto-Cubides2017} in the \Athena tool
+For instance, we tested successfully the translation by \Athena
+jointly with the \Agda formalizations of the rules mentioned above
+with more than eighty representative theorems in propositional
+logic. An interested reader can test the
+problems~\cite{Prieto-Cubides2017} in the \Athena tool
 repository~\cite{Athena}.

### 2017-11-21 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed some typos related with nnf.

@@
                    &\text{ and } ψ₂ ≡ \freorder_{∧}~φ~ψ₂;\\
-          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
+          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂;\\
           \fconjunct~φ~ψ, &\text{ otherwise.}
@@
 \begin{verbatim}
-  cnf(r₄, (¬ r ∨ p ∨ q), ...
-  cnf(r₅, (p ∨ q ∨ r), ...
-  cnf(r₆, (p ∨ q), inf(resolve, r, [r₅, r₄])).
+  cnf(r₄, ¬ r ∨ p ∨ q, ...
+  cnf(r₅, p ∨ q ∨ r, ...
+  cnf(r₆, p ∨ q, inf(resolve, r, [r₅, r₄])).
 \end{verbatim}
@@
 \begin{verbatim}
-  cnf(r₅, (r ∨ p ∨ q), ...
+  cnf(r₅, r ∨ p ∨ q, ...
 \end{verbatim}

### 2017-11-21 paper/sections/conclusions-and-future-work.tex
[ paper ] lots of changes.
[ paper ] lots of fixes and additions.

@@
 
-We presented a reliable proof-reconstruction in type theory
-for the propositional fragment of the \Metis prover. We provided for
-each \Metis inference rule a formal description in type theory
-following a syntactical approach.
-This formalizations are mainly exposed in
+We presented a proof-reconstruction approach in type theory for the
+propositional fragment of the \Metis prover. We provided for each
+\Metis inference rule a formal description in type theory following a
+syntactical approach. This formalizations are mainly exposed in
 Section~\ref{ssec:emulating-inferences}.
@@
 Nevertheless, we chose that syntactical treatment instead of using
-semantics to extend this work towards the support of first-order logic
-or other non-classical logics.
-For predicative logic, recall satisfiability is undecidable and
+semantics to extend this work towards the support of first-order
+logic or other non-classical logics.
+For first-order logic, recall satisfiability is undecidable and
 its syntactical aspect plays an important role to reconstruct proofs.
@@
   \begin{itemize}
-    \item support the proposition fragment with equality of \Metis.
+    \item support \Metis inference rules with equality (\eg, equality).
     \item support other \ATPs for propositional logic like \name{EProver} or \name{Z3}. This development can be carried out by following the \name{EProver}
@@
 
-\item use a shallow embedding instead the deep embedding
-implemented in~\cite{AgdaProp} to reconstruct proofs.
+% \item use a shallow embedding instead the deep embedding
+% implemented in~\cite{AgdaProp} to reconstruct proofs.
 \item improve some functions in Section~\ref{ssec:emulating-inferences}

### 2017-11-21 paper/sections/proof-reconstruction/clausify.tex
[ paper ] lots of fixes and additions.

@@
 
-The \clausify rule is another alternative way to transform a formula
-into its clausal normal form but without any simplification since
-remember this conversion is taking into account by the \canonicalize
-rule. It is important to notice that this kind of conversion between
-one formula to its clausal normal form is not unique, and \Metis has
-a customized approach to perform that transformation. Hence, we
-perform a reordering of the conjunctive normal form for the source
-formula.
+The \clausify rule is an alternative rule to transform a formula into
+its clausal normal form but without performing simplifications with
+tautologies or definitions. Recall, this kind of conversion was
+addressed by the \canonicalize rule. It is important to notice that
+this kind of conversions between one formula to its clausal normal
+form are not unique, and \Metis has customized approaches to perform
+that transformations. Therefore, we perform a reordering of the
+conjunctive normal form given by the $\fcnf$ function defined in
+Lemma~\ref{lem:cnf} with the $\freorder_{∧∨}$ function from
+Lemma~\ref{lem:reorder-and-or} to the input formula of the rule.
 

### 2017-11-21 paper/sections/proof-reconstruction/resolve.tex
[ paper ] lots of fixes and additions.

@@
 
-First, we define the \fassoc$_{⬓}$ function in~\eqref{eq:fassoc} to
+First, we define the $\fassoc_{⬓}$ function in~\eqref{eq:fassoc} to
 convert a disjunction or a conjunction into its right-associative
@@
 Now, we are ready to reconstruct the \resolve rule using
-Lemma~\ref{lem:reorder-and-or}.
-The \resolve rule is a generalization of the resolution theorem.
-This rule has three arguments: a positive literal $ℓ$ to apply the
-resolution theorem and two derivations.
+Lemma~\ref{lem:reorder-and-or}. As we see in the following, the
+\resolve rule is the \Metis version of the resolution theorem. This
+rule takes into account, two propositions that contain a positive
+literal $ℓ$ and its negation $¬ ℓ$ respectively. Then, it produces the
+\emph{resolvent}, a disjunction of two propositions: the first
+proposition after removing the literal $ℓ$ and the second proposition
+after removing its negation $¬ ℓ$.
 
 \begin{mydefinition}
-A \emph{literal} is an atom (positive literal) or a negation
-of an atom (negative literal).
+
+A \emph{literal} is an propositional variable (positive literal) or a
+negation of an propositional variable (negative literal).
+
 \end{mydefinition}
@@
         \begin{cases}
-          φ₂,      &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (¬φ₁ ∨ φ₂);\\
-          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∨ (¬φ₁ ∨ φ₄);\\\
+          φ₂,      &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∧ (¬ φ₁ ∨ φ₂);\\
+          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∧ (¬ φ₁ ∨ φ₄);\\\
           φ, &\text{ otherwise.}

### 2017-11-21 src/Athena/TSTP.hs
Support ⊃ symbol instead of ⇒.

@@ -37,7 +37,7 @@ import Data.TSTP.F
 --     F { name = "a2", role = Axiom, formula = b, source = NoSource},
 --     F { name = "a3"
 --       , role = Axiom
---       , formula = ( a ∧ b ⇒ z )
+--       , formula = ( a ∧ b ⊃ z )
 --       , source = NoSource
 --       },
 --     ...

### 2017-11-21 src/Athena/Translation/AgdaFile.hs

@@ -421,7 +421,7 @@ docProofGoal agdaFile =
      pretty "proof" <+> colon
        <+> pretty "Γ ⊢ " <> (pretty (fileConjecture agdaFile)) <> line
   <> pretty "proof" <+> equals <> line
-  <> indent 2 (pretty "⇒-elim" <> line)
+  <> indent 2 (pretty "⊃-elim" <> line)
   <> indent 2 (pretty Strip <> line <> nestedproofs) <> line
   <> hypenlineQED
     where

### 2017-11-21 src/Data/TSTP/BinOp.hs

@@ -24,7 +24,7 @@ import Athena.Utils.PrettyPrint ( Pretty(pretty) )
 
 -- | Binary formula connectives.
 data BinOp = (:<=>:)  -- ^ ⇔ /Equivalence/
-           | (:=>:)   -- ^ ⇒ /Implication/
+           | (:=>:)   -- ^ ⊃ /Implication/
            | (:<=:)   -- ^ ⇐ /Reverse Implication/
            | (:&:)    -- ^ ∧ /AND/
            | (:|:)    -- ^ ∨ /OR/
@@ -35,7 +35,7 @@ data BinOp = (:<=>:)  -- ^ ⇔ /Equivalence/
 
 instance Pretty BinOp where
   pretty (:<=>:) = pretty "⇔"
-  pretty (:=>:)  = pretty "⇒"
+  pretty (:=>:)  = pretty "⊃"
   pretty (:<=:)  = pretty "⇐"
   pretty (:&:)   = pretty "∧"
   pretty (:|:)   = pretty "∨"

### 2017-11-21 paper/sections/introduction.tex
[ paper ] proof by derivation.

@@
 prover.  In Section~\ref{sec:proof-reconstruction}, we show our
-approach to reconstruct \Metis proofs.  Related work is described in
+approach to reconstruct \Metis derivations.  Related work is described in
 Section~\ref{sec:related-work}.  Conclusions and suggestions for
@@
   \item The \verb!agda-metis! library as a formalization in \Agda to
-  justify \Metis proofs of classical propositional logic:
+  justify \Metis derivations of classical propositional logic:
   \url{http://github.com/jonaprieto/agda-prop}.

### 2017-11-21 paper/sections/metis-language-and-proofs.tex
[ paper ] proof by derivation.

@@
 The proof graphs have at their root the conclusion
-$⊥$, since \Metis proofs are refutations.
+$⊥$, since \Metis derivations are refutations.
 
@@
   \end{bprooftree}
-  \caption{\Metis proof tree of derivation in Example~\ref{fig:metis-example-tree}.}
+  \caption{\Metis derivation tree of derivation in Example~\ref{fig:metis-example-tree}.}
   \label{fig:metis-example}

### 2017-11-21 paper/sections/introduction.tex
[ paper ] minor changes.

@@
 
-In order to give confidence to the \ATP users, many of these system
+In order to give confidence to the \ATP users, many of these systems
 have started to include in their outputs the full derivations
@@
 
-Previous studies have reported proof-reconstruction using proof-
-assistants based on higher-order logic where the development is at a
-mature stage~\cite{paulson2010three,hurlin07practical,kaliszyk2013}.
+Previous studies have reported proof-reconstruction using
+proof-assistants based on higher-order logic where the development is at a mature
+stage~\cite{paulson2010three,hurlin07practical,kaliszyk2013}.
 Another approaches has been proposed for proof-reconstructing based
@@
 \Haskell that is able to generate \Agda proof-terms for \Metis
-derivations.
+derivations. During writing this document, our formalization helps to report two programming errors in \Metis.
+A bug\footnote{Issue No.\,2 at \url{https://github.com/gilith/metis/issue/4}} in the printing of the derivation and a soundness bug\footnote{Issue No.\,4 at \url{https://github.com/gilith/metis/issue/4}} in the stripping of the goal.
 
@@
 Section~\ref{sec:type-theory}, some limitations of type theory are
-discussed from proof-reconstruction point view.  In
+discussed from our proof-reconstruction point of view.  In
 Section~\ref{sec:metis-language-and-proofs}, we introduce the \Metis
@@
 \Athena jointly with \verb!agda-prop! and \verb!agda-metis! are able to reconstruct propositional proofs of \Metis~2.3 (release~20171021).
+We successfully reconstruct around eighty theorems in classical propositional logic from the \TPTP
+collection~\cite{Prieto-Cubides2017}.
 

### 2017-11-21 paper/sections/metis-language-and-proofs.tex
[ paper ] minor changes.

@@
 \begin{verbatim}
-  language(name, role, formula, source [,useful info]).,
+  language(name, role, formula, source [,useful info]).
 \end{verbatim}
 
-where the \name{source} field is an inference record with the following
+The \name{source} field is an inference record with the following
 pattern:
@@
 
-\subsection{Proofs}
+\subsection{\Metis Derivations}
 \label{ssec:metis-proofs}
 
-A proof generated by \Metis encodes a natural
+A derivation generated by \Metis encodes a natural
 deduction proof, Fig.~\ref{fig:metis-example} is an example of such kind of proof. With the inference rules in
@@
 
-These proofs are directed acyclic graphs, trees of refutations
-Each node stands for an application of an inference rule and the leaves
-in the tree represent formulas in the given problem. Each node is
-labeled with a name of the inference rule (\eg, \canonicalize).
+These derivations are directed acyclic graphs, trees of refutations.
+Each node stands for an application of an inference rule and the leaves in the tree represent formulas in the given problem.
+Each node is labeled with a name of the inference rule
+(\eg, \canonicalize).
 Each edge links a premise with one conclusion.
@@
   \end{bprooftree}
-  \caption{\Metis derivation tree of derivation in Example~\ref{fig:metis-example-tree}.}
+  \caption{\Metis derivation tree of Example~\ref{fig:metis-example-tree}.}
   \label{fig:metis-example}

### 2017-11-21 paper/sections/type-theory.tex
[ paper ] minor changes.

@@
 By following the Curry-Howard correspondence (see, for
-example,~\cite{Wadler-2015}), types are propositions. The inhabitants
-of that types, the \emph{terms}, are proofs of that propositions.
+example,~\cite{Wadler-2015}), we say \emph{types} are \emph{}propositions}.
+Inhabitant types are theorems and their proofs we called their terms.
+
 Since type theory is a formal system, we have a syntax and a set of

### 2017-11-21 paper/sections/introduction.tex
[ paper ] minor changes.

@@
 \Athena jointly with \verb!agda-prop! and \verb!agda-metis! are able to reconstruct propositional proofs of \Metis~2.3 (release~20171021).
-We successfully reconstruct around eighty theorems in classical propositional logic from the \TPTP
-collection~\cite{Prieto-Cubides2017}.
+We successfully reconstruct around eighty theorems in classical propositional
+logic from the \TPTP collection~\cite{Prieto-Cubides2017} to test
+the developments and the formalization presented in this research.
 

### 2017-11-21 paper/sections/type-theory.tex
[ paper ] minor changes.

--- 2017-11-20 paper/sections/type-theory.tex
@@
 By following the Curry-Howard correspondence (see, for
-example,~\cite{Wadler-2015}), types are propositions. The inhabitants
-of that types, the \emph{terms}, are proofs of that propositions.
+example,~\cite{Wadler-2015}), a formula corresponds to a \emph{type},
+and one proof of that formula is a \emph{term} of the correspondent type.
+Therefore, inhabitants types are such formulas with proofs, that is, theorems.
+
 Since type theory is a formal system, we have a syntax and a set of
@@
 conclusions called \emph{judgments}. A judgment is another way to say
-that a term has a certain type.
+that a term has a certain type. Each term has associated a derivation,
+we refer to this derivation as proof-terms.
 
@@
 dependent function types, evaluation of $λ$-terms also called
-\emph{normalization} of the proof- terms, are reductions using the
+\emph{normalization} of the proof-terms, are reductions using the
 system inference rules.
@@
 To reconstruct \Metis inference rules in type theory, we observed
-that some rules or their inner functions are implemented by \emph{
-general recursive} functions.
+that some rules or their inner functions are implemented by
+\emph{general recursive} functions.
 
@@
 General recursive functions can be rewrote into structurally
-recursive functions by  using for instance, the \emph{bounded
-recursion} technique. For a yet another methods, we refer the reader
-to \cite{Coquand1992,Abel2002,Bove2005}.
+recursive functions by  using for instance, the
+\emph{bounded recursion} technique. For a yet another methods, we refer the
+reader to \cite{Coquand1992,Abel2002,Bove2005}.
 

### 2017-11-23 paper/sections/introduction.tex
First version of the document - November 22, 2017 (#51)
* [ paper ] two first paragraphs in the introduction.

* [ bib] Fixed warning.

(Warning--empty publisher in Bertot2004).

* [ bib ] Fixed warning.

(Warning--empty booktitle in Bove2005).

* [ bib ] Fixed warning.

(Warning--empty booktitle in Een2004).

* [ bib ] Fixed warning.

(Warning--empty journal in Altenkirch2015).

* [ bib ] Fixed warning.

(Warning--empty year in deNivelle2003).

* [ paper ] add the third paragraph in the introduction.

* [ paper ] added the fourth paragraph in the introduction.

* [ paper
] fixed some text in

@@
 
-In order to give confidence to the \ATP users, many of these systems
+In order to give confidence to the \ATP users many of these systems
 have started to include in their outputs the full derivations
 associated to the proved theorems. However, existing research
-recognizes that in many cases these proofs encode non-trivial
+recognizes that in many cases these derivations encode non-trivial
 reasoning hard to reconstruct and therefore hard to
@@
 
-Proof-reconstruction addresses this problem. It becomes in mostly
-cases a reverse engineering task to verify the prover reasoning. That
-usually happens when the reconstruction is made by another and not by
-the developers of the \ATP. The presentation of the proofs generated
-by the prover plays an important role in proof-reconstruction. To
-verify such a proof, it is convenient to have it in a consistent
-format, that is, a full script describing the derivation step-by-step
-with  exhaustive details and without ambiguities. For example, for
-classical propositional logic (henceforth \CPL) from a list of at
-least forty \ATPs---available from the Web service
+Proof-reconstruction addresses this problem. Since many \ATPs are
+poor-documented, this problem becomes in mostly cases a reverse
+engineering task to verify the prover reasoning. The usual is the
+reconstruction is made by another and not by the developers of the
+\ATP. Therefore, the presentation of the derivations generated by the
+prover plays an important role in proof-reconstruction.
+
+To verify such automatically generated derivation by the prover,
+it is convenient to have them in a
+consistent format, that is, a full script describing the derivation
+step-by-step with  exhaustive details and without ambiguities. For
+example, for classical propositional logic (henceforth \CPL) from a
+list of at least forty \ATPs---available from the Web service
 \name{SystemOnTPTP} of the TPTP World\footnote{\url{http://www.cs.miami.edu/~tptp/}.}---just few of
@@
 One approach to address the proof-reconstruction problem is
-justifying each inference rule of the \emph{source} system, the \ATP,
-with a proof-assistant, the \emph{target} system. The target system
-is the proof \emph{checker} in charge to verify the source system
-reasoning.
+proving each deduction of the prover, the \emph{source} system,
+with a formalization of the prover reasoning in a proof-assistant, the \emph{target} system. The target system is the
+proof \emph{checker} in charge to verify the source system reasoning
+for each derivation.
 These proof-assistants allow us to formalize the logical system used
 in the proofs, \ie, logical constants, axioms, inference rules,
-hypotheses, and theorems. A proof-reconstruction tool provides such
-an integration, translating the derivation generated by the prover
-into the formalism of the proof-assistant.
+hypotheses, and theorems.
+A proof-reconstruction tool provides such an
+integration, translating the derivation generated by the prover into
+the formalism of the proof-assistant.
 
@@
 derivations. During writing this document, our formalization helps to report two programming errors in \Metis.
-A bug\footnote{Issue No.\,2 at \url{https://github.com/gilith/metis/issue/4}} in the printing of the derivation and a soundness bug\footnote{Issue No.\,4 at \url{https://github.com/gilith/metis/issue/4}} in the stripping of the goal.
+A bug\footnote{Issue No.\,2 at \url{https://github.com/gilith/metis/issues/2}} in the printing of the derivation and a soundness bug\footnote{Issue No.\,4 at \url{https://github.com/gilith/metis/issues/4}} in the stripping of the goal.
 

### 2017-11-23 paper/sections/proof-reconstruction.tex
First version of the document - November 22, 2017 (#51)
* [ paper ] two first paragraphs in the introduction.

* [ bib] Fixed warning.

(Warning--empty publisher in Bertot2004).

* [ bib ] Fixed warning.

(Warning--empty booktitle in Bove2005).

* [ bib ] Fixed warning.

(Warning--empty booktitle in Een2004).

* [ bib ] Fixed warning.

(Warning--empty journal in Altenkirch2015).

* [ bib ] Fixed warning.

(Warning--empty year in deNivelle2003).

* [ paper ] add the third paragraph in the introduction.

* [ paper ] added the fourth paragraph in the introduction.

* [ paper
] fixed some text in

@@
 We have finished the formalization of every inference rule in
-a \Metis proof, we are able to justify step-by-step any proof
+a \Metis derivation, we are able to justify step-by-step any proof
 for a problem in propositional logic.

### 2017-11-23 paper/sections/proof-reconstruction/strip.tex
First version of the document - November 22, 2017 (#51)
* [ paper ] two first paragraphs in the introduction.

* [ bib] Fixed warning.

(Warning--empty publisher in Bertot2004).

* [ bib ] Fixed warning.

(Warning--empty booktitle in Bove2005).

* [ bib ] Fixed warning.

(Warning--empty booktitle in Een2004).

* [ bib ] Fixed warning.

(Warning--empty journal in Altenkirch2015).

* [ bib ] Fixed warning.

(Warning--empty year in deNivelle2003).

* [ paper ] add the third paragraph in the introduction.

* [ paper ] added the fourth paragraph in the introduction.

* [ paper
] fixed some text in

@@
 
-The $\fstrip₀$ function yields the conjunction of subgoals that implies the
-goal of the problem in the \Metis \TSTP derivations but is not a structurally
-recursive function.  Instead, we present its structural recursive version
-in~\eqref{eq:strip-fixed}, the $\fstrip₁$ function after applying the bounded
-technique described in Section~\ref{ssec:structural-recursion}. We define the
-$\fstrip₁$ function based on the definition from the \Metis source code.
+The $\fstrip₀$ function defined in~\eqref{eq:strip-zero} yields the
+conjunction of subgoals that implies the goal of the problem in the
+\Metis \TSTP derivations. Nonetheless, this function is not a
+structurally recursive function (see more details in
+Appendix~\ref{app:strip-cm}).
+Therefore, we present the $\fstrip₁$ function
+in~\eqref{eq:strip-fixed} as the structurally recursive version
+of the $\fstrip₀$ function by applying the
+bounded technique described in
+Section~\ref{ssec:structural-recursion}.
+We define the $\fstrip₁$ function based on the reading of the \Metis source code.
 
@@
 \begin{verbatim}
-  fof(goal, conjecture, (p ∧ r ∧ q)).
+  fof(goal, conjecture, p ∧ r ∧ q).
   fof(s₁, p, inf(strip, goal)).

### 2017-11-23 paper/sections/type-theory.tex
First version of the document - November 22, 2017 (#51)
* [ paper ] two first paragraphs in the introduction.

* [ bib] Fixed warning.

(Warning--empty publisher in Bertot2004).

* [ bib ] Fixed warning.

(Warning--empty booktitle in Bove2005).

* [ bib ] Fixed warning.

(Warning--empty booktitle in Een2004).

* [ bib ] Fixed warning.

(Warning--empty journal in Altenkirch2015).

* [ bib ] Fixed warning.

(Warning--empty year in deNivelle2003).

* [ paper ] add the third paragraph in the introduction.

* [ paper ] added the fourth paragraph in the introduction.

* [ paper
] fixed some text in

@@
 example,~\cite{Wadler-2015}), a formula corresponds to a \emph{type},
-and one proof of that formula is a \emph{term} of the correspondent type.
-Therefore, inhabitants types are such formulas with proofs, that is, theorems.
+and one proof of that formula is a \emph{term} of the correspondent
+type. Therefore, inhabitants types are such formulas with proofs, they are theorems.
 
@@
 dependent function types, evaluation of $λ$-terms also called
-\emph{normalization} of the proof-terms, are reductions using the
-system inference rules.
+\emph{normalization} of the proof-terms, is a process of reductions with the system inference rules.
 
@@
 This feature of type theory allow us to verify a proof generated by an \ATP by reconstructing its proof-term to type-check the proof. For such a
-purpose, we use a proof assistant based on type theory like \Agda to
+purpose, we use a proof-assistant based on type theory like \Agda to
 delegate this task. % However, this approach has some weak points

### 2017-11-23 src/Athena/Translation/AgdaFile.hs
[ AgdaFile ] comments to seperate the comments.

@@ -369,13 +369,10 @@ subgoalName n = pretty "subgoal" <> (pretty . stdName . show) n
 
 docProof ∷ AgdaFile → Doc
 docProof agdaFile =
-     hypenline
-  <> comment (pretty "Proof" <> dot)
-  <> hypenline
-  <@> vsep
-       [ docProofSubgoals agdaFile
-       , docProofGoal agdaFile
-       ]
+  vsep
+    [ docProofSubgoals agdaFile
+    , docProofGoal agdaFile
+    ]
 
 docProofSubgoals ∷ AgdaFile → Doc
 docProofSubgoals agdaFile =
@@ -389,9 +386,13 @@ docProofSubgoals agdaFile =
 
 docProofSubgoal ∷ Int → ProofTree → AgdaFile → Doc
 docProofSubgoal n tree agdaFile =
-     proof
+     hypenline
+  <> comment (pretty "Proof of subgoal"<> (pretty . stdName . show) n <> dot)
+  <> hypenline
   <> line
-  <> hypenlineQED
+  <> proof
+  <> line
+  -- <> hypenlineQED
   where
     pName ∷  Doc
     pName = pretty "proof" <> (pretty . stdName . show) n
@@ -418,12 +419,16 @@ docProofSubgoal n tree agdaFile =
 
 docProofGoal ∷ AgdaFile → Doc
 docProofGoal agdaFile =
-     pretty "proof" <+> colon
+     hypenline
+  <> comment (pretty "Proof of the goal.")
+  <> hypenline
+  <> line
+  <> pretty "proof" <+> colon
        <+> pretty "Γ ⊢ " <> (pretty (fileConjecture agdaFile)) <> line
   <> pretty "proof" <+> equals <> line
   <> indent 2 (pretty "⊃-elim" <> line)
   <> indent 2 (pretty Strip <> line <> nestedproofs) <> line
-  <> hypenlineQED
+  -- <> hypenlineQED
     where
       nestedproofs ∷ Doc
       nestedproofs =

### 2017-11-24 paper/sections/type-theory.tex
[ paper ] fixed typos.

@@
 \begin{notation}
-  Types are written using \abbre{small caps}.  We write the type
-  judgments as $a : \abbre{a}$ to denote that the term~$a$ is of
-  type~$\abbre{a}$.
+
+  We write the type judgments as $a : \type{A}$ to denote that the
+  term~$a$ is of type~$\type{A}$.
+
 \end{notation}
@@
   A proposition is an expression of indivisible propositional variables (\eg, symbols $φ₀, φ₁, \cdots$), the logic constants:
-  $⊥$, $⊤$, the binary connectives ($∧, ∨, ⇒, ⇔)$, and the negation
+  $⊥$, $⊤$, the binary connectives ($∧, ∨, ⇒)$, and the negation
   $(\neg)$.
-  We write the equality using the symbol (≡) as $φ ≡ ψ$, for $φ,~ψ :
+  We write the syntactical equality using the symbol (≡) as $φ ≡ ψ$, for $φ,~ψ :
   \Prop$. For this equality, we assume the reflexivity, symmetry and
@@
 on a general
-recursive function $\rm{f}:\,\abbre{a}~\to~\abbre{b}$ is to
+recursive function $\rm{f}:\,\type{A}~\to~\type{B}$ is to
 formulate a new
-function $\rm{f}^{*}:\,\abbre{a}~\to~\Nat~\to~\abbre{b}$ where all
+function $\rm{f}^{*}:\,\type{A}~\to~\Nat~\to~\type{B}$ where all
 of its recursive calls are done on smaller arguments.

### 2017-11-29 paper/sections/type-theory.tex
[ paper ] added a reference for general recursion.

@@
 that some rules or their inner functions are implemented by
-\emph{general recursive} functions.
+\emph{general recursive} functions (see a definition of these functions in~\cite{Bove2002}.
 
@@
 \begin{aligned}
-&\hspace{.495mm} \fuh_{1} : \Prop → \Nat \to \Prop\\
+&\hspace{.495mm} \fuh_{1} : \Prop → \Nat → \Prop\\
 &\begin{array}{llll}
@@
 We formalise the syntactical consequence relation of \CPL by an
-inductive family $\_⊢\_$ with two indexes, a set of propositions (the
+inductive family \verb!_⊢_! with two indexes, a set of propositions (the
 premises) and a proposition (the conclusion), that is, $Γ ⊢ φ$

### 2017-12-06 paper/sections/proof-reconstruction.tex
[ README ] Fixed a typo.
[ paper ] fixed intro in proof-reconstruction section.

@@
 
-The proof-reconstruction approach proposed consists of a series of
-steps similar to the workflow presented~\cite{sultana2015}.  This
-process is a translation from a source system to a target system. In
-our case, the system of origin, the automatic theorem prover, is
+In this section, we describe one approach to reconstruct
+propositional proofs. This reconstruction is a translation
+process from a source system to the target system.
+In our case, the system of origin, the automatic theorem prover, is
 \Metis; the target system is a proof-assistant, \Agda. We choose
@@
 \input{sections/diagram.tex}
-%  (see a description of \Agda for its main features in
-% Section~\ref{sec:implementation}).
-The overview of the proof-reconstruction is presented in
-Fig.~\ref{fig:proof-reconstruction-workflow}. The process begins with
-a \TPTP file that encodes a problem in \CPL. We use this file as the
-input of the \Metis prover. If the problem is a theorem, \Metis
-generates a derivation of the proof in \TSTP format.
+The overview of the proof-reconstruction is presented as a workflow
+in Fig.~\ref{fig:proof-reconstruction-workflow}. This workflow
+follow the same basis of the proposed workflow presented
+in~\cite{sultana2015}.
+
+The process begins with a \TPTP file that encodes a problem in \CPL.
+We use this file as the input of the \Metis prover. If the problem is
+a theorem, \Metis generates a derivation of the proof in \TSTP
+format.
 

### 2017-12-06 paper/sections/proof-reconstruction.tex
[ paper ] more spacing in metis table/strip rule begins section.

@@
 
-% % ................................................
+% ...................................................................
 
@@
 In this section, we reconstruct each \Metis inference rule in
-Table~\ref{tab:agda-metis-table} via a function and its respective
-theorem. We present a pattern of the formal description for these
-rules in Example~\ref{ex:inference-rule-pattern}.
+Table~\ref{tab:agda-metis-table}.
+We begin describing the reconstruction of the \strip inference rule
+since this rule  is the only one that closely follows the \Metis
+source code. For the other rules, we present a pattern of the formal
+description for these rules in
+Example~\ref{ex:inference-rule-pattern} to reconstruct such rules.
 
@@
   The function name written in \texttt{typewriter} font refers to a
-  \Metis inference rule. The same function name written using
+  \Metis inference rule in the \TSTP derivations. The same function
+  name written using
   \textsf{sans serif} font refers to our formalized version to
-  reconstruct the rule and implemented in~\cite{AgdaMetis}. We use
-  \Source and \Target as synonyms of the \Prop type to describe in the
-  function types the role of the arguments.
+  reconstruct the rule and formally implemented in~\cite{AgdaMetis}.
+  To increase the readability of our formal descriptions in
+  functions and theorems, we adopt
+  the convention to use \Source and \Target as synonyms of the \Prop
+  type. The \Source type in the reconstructed rule definition refers
+  to the argument in the \TSTP derivations, \ie the input formula of
+  the inference rule. A formula of \Target type refers to the
+  expected result of the rule found in the \TSTP derivation.
 \end{notation}
+
+\subfile{sections/proof-reconstruction/strip.tex}
 
@@
 % ------------------------------------------------------------------
+% Rules that follow the pattern:
 
-\subfile{sections/proof-reconstruction/strip.tex}
 \subfile{sections/proof-reconstruction/conjunct.tex}

### 2017-12-06 paper/sections/proof-reconstruction.tex
[ paper ] formalization pattern with some fixes.

@@
 
+As we mention in the beginning of this section, to reconstruct
+the \Metis inference rules, we use the following pattern in
+the formalization.
+
 \begin{myexamplenum}
@@
 \begin{equation*}
-  \text{If }Γ ⊢ φ \text{ then }Γ ⊢ \fun{metisRule}~φ~ψ, \text{ where } ψ : \Target.
+  \text{If }Γ ⊢ φ \text{ then }Γ ⊢ \fun{metisRule}~φ~ψ\enspace.
 \end{equation*}
@@
 The remainder of this section will be devoted to present a formal
-description in type theory of each rule presented in
-Table~\ref{tab:agda-metis-table} using the pattern present in the
+description in type theory of remaining \Metis rules presented in
+Table~\ref{tab:agda-metis-table} using the pattern presented in the
 example above. We follow the same order to present the rules as the

### 2017-12-17 paper/sections/type-theory.tex
[ README ] Fixed a typo.
[ paper ] minor fixes in type theory section.

@@
 that some rules or their inner functions are implemented by
-\emph{general recursive} functions (see a definition of these functions in~\cite{Bove2002}.
+\emph{general recursive} functions (see a definition of these functions in~\cite{Bove2002}).
 
@@
   $⊥$, $⊤$, the binary connectives ($∧, ∨, ⇒)$, and the negation
-  $(\neg)$.
+  $(\neg)$. We use the inductive definition for propositions presented in~\cite{VanDalen1994}.
+
   We write the syntactical equality using the symbol (≡) as $φ ≡ ψ$, for $φ,~ψ :
@@
 \begin{notation}
-We define some functions by pattern-matching on \Prop or \Nat.
+In the latter definitions and theorems, we  use a common notation in
+type theory, pattern-matching~\cite{Coquand1992} to define by cases
+on the inductive definition of types.
+
+We adopt pattern-matching to define some functions.
+These pattern-matching definitions follow the inductive definitions
+of the type.
 \end{notation}

### 2017-12-17 paper/sections/type-theory.tex
fixed some spacing issues.

@@
   We use \Prop for the type of propositions.
-  A proposition is an expression of indivisible propositional variables (\eg, symbols $φ₀, φ₁, \cdots$), the logic constants:
+  A proposition is an expression of indivisible propositional variables (\eg, symbols $φ₀, φ₁, \cdots$), and the logic constants:
   $⊥$, $⊤$, the binary connectives ($∧, ∨, ⇒)$, and the negation
@@
 
-  We write the syntactical equality using the symbol (≡) as $φ ≡ ψ$, for $φ,~ψ :
-  \Prop$. For this equality, we assume the reflexivity, symmetry and
+  We write the syntactical equality between two propositions φ and ψ using the symbol (≡) as $φ ≡ ψ$. For this equality, we assume the reflexivity, symmetry and
   transitivity properties.
-  % We say $φ$ and $ψ$ are syntactically equivalent if there is a derivation from $φ$ to $ψ$ and
-  % a derivation from $ψ$ to $φ$.
+
   The type of natural numbers is called \Nat,
-  and it is defined as usual, where $\zero$ and $\suc$ are its data
-  constructors. We use names and symbols for the arithmetic operations
-  as usual (\eg, $+$, $-$, $*$).  We use syntax sugar for $\zero$, $\suc$,
+  and it is defined as usual, \ie, $\zero$ and $\suc$ are its data
+  constructors. We use names and symbols for the arithmetic
+  operations as usual (\eg, $+$, $-$, $*$).
+  We use syntax sugar for $\zero$, $\suc$,
   $\suc~\zero$, $\dots$, with the decimal representation~$0$, $1$,
@@
 on a general
-recursive function $\rm{f}:\,\type{A}~\to~\type{B}$ is to
+recursive function $f₀ : \type{A} \to \type{B}$ is to
 formulate a new
-function $\rm{f}^{*}:\,\type{A}~\to~\Nat~\to~\type{B}$ where all
+function $f₁ : \type{A} \to \Nat \to \type{B}$ where all
 of its recursive calls are done on smaller arguments.

### 2017-12-17 paper/sections/type-theory.tex
added footer to review paper.

@@
 
-In~\eqref{eq:uh-definition}, the first two equations
-call on arguments no structurally smaller.
-For instance, in the first equation,
-$$\fuh_{0} (φ₁ ⇒ (φ₂ ⇒ φ₃)) = \fuh_{0}~((φ₁ ∧ φ₂) ⇒ φ₃),$$
-the function $\fuh_{0}$ calls on the  $(φ₁ ∧ φ₂) ⇒ φ₃$ argument in the right-hand side but this formula is not a subformula of $φ₁ ⇒ (φ₂ ⇒ φ₃)$.
+In~\eqref{eq:uh-definition} is a definition no structurally recursive.
+
+% TODO
+% , the first two equations
+% call on arguments no structurally smaller.
+% For instance, in the first equation,
+% $$\fuh_{0} (φ₁ ⇒ (φ₂ ⇒ φ₃)) = \fuh_{0}~((φ₁ ∧ φ₂) ⇒ φ₃),$$
+% the function $\fuh_{0}$ calls on the argument $(φ₁ ∧ φ₂) ⇒ φ₃$ argument. However, this formula is not a subformula of $φ₁ ⇒ (φ₂ ⇒ φ₃)$.
+
 Therefore, one way to translate $\fuh_{0}$ to type
@@
 finish for each pattern-matching case.
+
+% In this particular case,
+% as we can see by the definition of the $\fuh_{0}$ function, the pattern-matching cases depend on the formula structure for implications.
+For example, when φ ≡ in the consequent when the input formula is an implication.
+For example, when the input formula
+% is an implication like φ₁ ⇒ (φ₂ ∧ φ₃) then, the recursive calls
+% are using only the consequent φ₂ ∧ φ₃, otherwise, if φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃) based on the cases of the function definition, we only need
+% to take care of φ₃.
+
 We have used the complexity measure definition for a formula defined in~\cite{Agudelo-Agudelo2017} to define other complexity measures
@@
 
-We formalise the syntactical consequence relation of \CPL by an
+We formalize the syntactical consequence relation of \CPL by an
 inductive family \verb!_⊢_! with two indexes, a set of propositions (the

### 2017-12-18 paper/sections/proof-reconstruction.tex
lots of changes.

@@
 since this rule  is the only one that closely follows the \Metis
-source code. For the other rules, we present a pattern of the formal
-description for these rules in
-Example~\ref{ex:inference-rule-pattern} to reconstruct such rules.
+source code.
+
+To reconstruct the other rules, we use for their formalization
+a pattern in their description and definition,
+see Example~\ref{ex:inference-rule-pattern}.
 
@@
   type. The \Source type in the reconstructed rule definition refers
-  to the argument in the \TSTP derivations, \ie the input formula of
+  to the argument in the \TSTP derivation, \ie the input formula of
   the inference rule. A formula of \Target type refers to the
@@
 
-As we mention in the beginning of this section, to reconstruct
+Now, as we mention in the beginning of this section, to reconstruct
 the \Metis inference rules, we use the following pattern in

### 2017-12-18 paper/sections/proof-reconstruction/resolve.tex
[ paper ] added a reference for general recursion.
lots of changes.

@@
 function will try to rearrange the disjuncts in the source formula to
-match with the target disjunction formula.
+be the target disjunction formula.
 
@@
 between nested disjunctions.  We define the $\fsbuild_{∨}$ function
-in~\eqref{eq:strong-build-or} that uses every disjunct from the source
-formula, $φ$, to build up the target disjunction $ψ$.
+in~\eqref{eq:strong-build-or} that uses every disjunct from the
+source formula, $φ$, to build up the target disjunction $ψ$.
 
@@
 $r ∨ (q ∨ p)$ using Lemma~\ref{lem:sbuild-or}.
+
 \begin{equation*}
@@
           φ₂,      &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∧ (¬ φ₁ ∨ φ₂);\\
-          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∧ (¬ φ₁ ∨ φ₄);\\\
+          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∧ (¬ φ₁ ∨ φ₄);\\
           φ, &\text{ otherwise.}

### 2017-12-18 paper/sections/proof-reconstruction/strip.tex
[ paper ] formalization pattern with some fixes.
lots of changes.

@@
 
-To prove a goal, \Metis splits the goal into
-disjoint cases. This process produces a list of new subgoals, the
-conjunction of these subgoals implies the goal. Then, a proof of the
-goal becomes, in smaller proofs, one refutation for each subgoal.
+To prove a goal, \Metis splits the goal into disjoint cases. This
+process produces a list of new subgoals, the conjunction of these
+subgoals implies the goal. Then, a proof of the goal becomes into a
+set of smaller proofs, one refutation for each subgoal.
 
 \begin{myexamplenum}
-The subgoals associated to a goal are introduced in the \TSTP derivation
-with the \strip inference rule.
+
+The subgoals associated to a goal are introduced
+in the \TSTP derivation with the \strip inference rule.
 
@@
 \label{eq:strip-example}
-(p ∧ (p ⇒ r) ∧ ((p ∧ r) ⇒ q)) ⇒ ((p ∧ r) ∧ q).
+(p ∧ (p ⇒ r) ∧ ((p ∧ r) ⇒ q)) ⇒ ((p ∧ r) ∧ q)\enspace.
 \end{equation}
@@
   \begin{equation*}
-  \texttt{∧⇒\textsf{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
+  \texttt{∧⇒\textsf{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)\enspace.
   \end{equation*}
@@
 \begin{equation*}
-  \texttt{⇒∧⇒\textsf{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
+  \texttt{⇒∧⇒\textsf{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)\enspace,
 \end{equation*}
@@
 in~\eqref{eq:uh-complexity}, we
-define the $\fstrip_{cm}$ function in Appendix~\ref{app:strip-cm} as the complexity measure for the $\fstrip₀$ function.
-Then we define the \fstrip function as follows in~\ref{eq:strip}.
+define the $\fstrip_{cm}$ function in Appendix~\ref{app:strip-cm} as
+the complexity measure for the $\fstrip₀$ function.
+We define the \fstrip function as follows in~\ref{eq:strip}.
 
@@
 \label{thm:strip}
-Let $\text{n} : \Nat$ be the complexity measure of the strip function defined
-in~\eqref{eq:strip-fixed}.
+Let $\text{n} : \Nat$ be the complexity measure of the strip function defined in Appendix~\ref{app:strip-cm}~\eqref{eq:strip-cm}.
 Let $s₂$ and $s₃$ be the subgoals of the goal $φ$, that is,
-$$\fstrip₁~φ~n~≡~s₂∧~s₃.$$
+$$\fstrip₁~φ~n~≡~s₂∧~s₃\enspace.$$
 If $Γ ⊢ s₂$ and $Γ ⊢ s₃$ then $Γ ⊢ φ$.

### 2017-12-19 paper/sections/proof-reconstruction/clausify.tex
removed redundacies and definitions.

@@
 
-The \clausify rule is an alternative rule to transform a formula into
-its clausal normal form but without performing simplifications with
-tautologies or definitions. Recall, this kind of conversion was
+The \clausify rule is a rule that transforms a formula into
+its clausal normal form but without performing simplifications of
+tautologies. Recall, this kind of conversion was already
 addressed by the \canonicalize rule. It is important to notice that

### 2017-12-19 paper/sections/proof-reconstruction/strip.tex
removed redundacies and definitions.

@@
 \label{eq:strip-example}
-(p ∧ (p ⇒ r) ∧ ((p ∧ r) ⇒ q)) ⇒ ((p ∧ r) ∧ q)\enspace.
+(p ∧ (p ⇒ r) ∧ ((p ∧ r) ⇒ q)) ⇒ ((p ∧ r) ∧ q).
 \end{equation}
@@
   \begin{equation*}
-  \texttt{∧⇒\textsf{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)\enspace.
+  \texttt{∧⇒\textsf{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
   \end{equation*}
@@
 \begin{equation*}
-  \texttt{⇒∧⇒\textsf{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)\enspace,
+  \texttt{⇒∧⇒\textsf{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
 \end{equation*}
@@
 Let $s₂$ and $s₃$ be the subgoals of the goal $φ$, that is,
-$$\fstrip₁~φ~n~≡~s₂∧~s₃\enspace.$$
+$$\fstrip₁~φ~n~≡~s₂∧~s₃.$$
 If $Γ ⊢ s₂$ and $Γ ⊢ s₃$ then $Γ ⊢ φ$.

### 2017-12-19 paper/sections/type-theory.tex
removed redundacies and definitions.

@@
   We use \Prop for the type of propositions.
-  A proposition is an expression of indivisible propositional variables (\eg, symbols $φ₀, φ₁, \cdots$), and the logic constants:
+  A proposition is an expression of indivisible propositional variables (\eg, symbols $φ₀, φ₁, \dots$), and the logic constants:
   $⊥$, $⊤$, the binary connectives ($∧, ∨, ⇒)$, and the negation

### 2017-12-22 paper/sections/proof-reconstruction/resolve.tex
Paper (#59) : this closes #57, #56, #55, #58
* [ paper ] fixed intro in proof-reconstruction section.

* [ paper ] more spacing in metis table/strip rule begins section.

* [ paper ] formalization pattern with some fixes.

* [ paper ] minor fixes in type theory section.

* fixed some spacing issues.

* added footer to review paper.

* lots of changes.

* fixes for canonicalize section.

* minor fixes.

* minor fixes.

* removed redundacies and definitions.

* hypenation of Medellín.

* more info in some references.

* fixed some DOIs.

* minor fixes.

* [ paper ] diagram fixed.

* [ paper ] re

@@
 form, and reordering those and the inner disjunctions to match them.
+
+\begin{mydefinition}
+
+A \emph{literal} is an propositional variable (positive literal) or a
+negation of an propositional variable (negative literal).
+
+\end{mydefinition}
+
+\begin{notation}
+We use \Lit as synonym of \Prop type to refer literals.
+\end{notation}
+
+\begin{mydefinition}
+
+The \emph{negative normal form} of a formula is the logical
+equivalent version of it in which negations appear only in the
+literals and the formula does not contain any implications.
+
+\end{mydefinition}
+
+\begin{mydefinition}
+
+The \emph{conjunctive normal form} of a formula also called clausal
+normal form is the logical equivalent version expressed as a
+conjunction of clauses where a \emph{clause} is the disjunction of
+zero or more literals.
+
+\end{mydefinition}
+
 Below, we provide Lemma~\ref{lem:reorder-or},
@@
 
-\begin{mydefinition}
-
-A \emph{literal} is an propositional variable (positive literal) or a
-negation of an propositional variable (negative literal).
-
-\end{mydefinition}
-
-\begin{notation}
-We use \Lit as synonym of \Prop type to refer literals.
-\end{notation}
-
 The positive literal~$ℓ$ must occur in the formula from the first
@@
   Let $ℓ$ be a literal, $ℓ : \Lit$, and $ψ : \Target$. If $Γ ⊢ φ₁$ and
-  $Γ ⊢ φ₂$ then $Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$, where
+  $Γ~⊢~φ₂$ then $Γ~⊢~\fresolve~φ₁~φ₂~ℓ~ψ$, where
   \begin{equation}
@@
 Continuing with the problem presented in
-Example~\ref{ex:resolve-tstp}, we can use Theorem \ref{thm:resolve} to derive $Γ ⊢ p ∨ q$.
+Example~\ref{ex:resolve-tstp}, we can use Theorem \ref{thm:resolve} to derive $Γ~⊢~p~∨~q$.
 

### 2018-01-03 pubs/thesis/sections/acknowledgements.tex
[ paper ] Renamed directory.

--- 2017-10-25 paper/sections/acknowledgements.tex
@@
 Last but not least, I thankfully acknowledge
-Andreas Abel and Chalmers University of Goteborg, Sweden for
+Andreas Abel and Chalmers University of Technology at Goteborg, Sweden for
 inviting me to be part of the \Agda Implementors’ Meeting XXV

### 2018-01-03 pubs/thesis/sections/introduction.tex
[ paper ] Renamed directory.

--- 2017-11-23 paper/sections/introduction.tex
@@
 verifying a railway interlocking system, an operating-system kernel,
-or a pseudo-random number generator for cryptography). Since some
+or a pseudo-random number generator). Since some
 programming errors have been found in these programs (see, for

### 2018-01-03 pubs/thesis/sections/notes/discussion.tex
[ paper ] Renamed directory.

--- 2017-10-27 paper/sections/notes/discussion.tex
@@
   fof(goal, conjecture, p & r & q).
-  fof(subgoal_0, plain, p, inference(strip, [], [goal])).
-  fof(subgoal_1, plain, p => r, inference(strip, [], [goal])).
-  fof(subgoal_2, plain, (p & r) => q, inference(strip, [], [goal])).
+  fof(subgoal_0, plain, p, inference(strip, [], goal)).
+  fof(subgoal_1, plain, p => r, inference(strip, [], goal)).
+  fof(subgoal_2, plain, (p & r) => q, inference(strip, [], goal)).
 \end{verbatim}

### 2018-01-03 pubs/thesis/sections/notes/implementation.tex
[ paper ] Renamed directory.

--- 2017-10-23 paper/sections/notes/implementation.tex
@@
 definitions using pattern matching on such types, normalisation
-during type- checking, commands for refining proof terms, coverage
+during type- checking, commands for refining proof-terms, coverage
 checker and termination checker.
@@
 
-\begin{myexample}
+\begin{myexamplenum}
 \hspace*{5cm}\\[3mm]

### 2018-01-03 pubs/thesis/sections/proof-reconstruction/conjunct.tex
[ paper ] Renamed directory.

--- 2017-10-27 paper/sections/proof-reconstruction/conjunct.tex
@@
 
-\subsubsection{Splitting a conjunct.}
+\subsubsection{Conjunct.}
 \label{sssec:splitting-a-conjunct}
 
-The \conjunct rule extracts from a
-conjunction one of its conjuncts. This rule is a generalization of the
-projection rules for the conjunction connective as the
-following \TSTP excerpt shows.
+The \conjunct rule extracts from a conjunction one of its conjuncts.
+This rule is a generalization of the projection rules for the
+conjunction connective as the following \TSTP excerpt shows.
 
-\begin{myexample}\hspace{10cm}
+\begin{myexamplenum}\hspace{10cm}
 
 \begin{verbatim}
-  fof(p1, p ∧ q ∧ (r ∨ ¬ p), inf(canonicalize, [x])).
-  fof(p2, q, inf(conjunct, [p1])).
-  fof(p3, (r ∨ ¬ p), inf(conjunct, [p1])).
+  fof(p₁, p ∧ q ∧ (r ∨ ¬ p), ...
+  fof(p₂, q, inf(conjunct, p₁)).
+  fof(p₃, r ∨ ¬ p, inf(conjunct, p₁)).
 \end{verbatim}
@@
 In the first formula, $p ∧ q ∧ (r ∨ ¬ p)$, we find a left-associative
-conjunction named \verb!p1!.
-The \conjunct rule extracts $q$ from the \verb!p1! using a left
-projection (∧-proj₁) follow by a right projection (∧-proj₂).
-After, the \conjunct rule extracts $r ∨ ¬ p$ by using a right projection
-on \verb!p1!.
-\end{myexample}
+conjunction named \verb!p₁!. The \conjunct rule extracts $q$ from the
+\verb!p₁! using a left projection (∧-proj₁) follow by a right
+projection (∧-proj₂). After, the \conjunct rule extracts $r ∨ ¬ p$ by
+using a right projection on \verb!p₁!.
+
+\end{myexamplenum}
 
@@
   \label{thm:conjunct}
-  If $Γ ⊢ φ$ and $ψ  : \Target$ then $Γ ⊢ \fconjunct~φ~ψ$ where,
+  Let $ψ : \Target$. If $Γ ⊢ φ$ then $Γ ⊢ \fconjunct~φ~ψ$, where
   \begin{equation*}

### 2018-01-03 pubs/thesis/sections/type-theory.tex
[ paper ] Renamed directory.

--- 2017-12-19 paper/sections/type-theory.tex
@@
 discussed in~\cite{Bezem2002}. Some limitations from the type theory
-point of view for proof-reconstruction is described in the following
-sections.
+point of view for proof-reconstruction is described in
+Section~\ref{ssec:structural-recursion} and
+Section~\ref{ssec:intuitionistic-logic}.
 
@@
 In the latter definitions and theorems, we  use a common notation in
-type theory, pattern-matching~\cite{Coquand1992} to define by cases
-on the inductive definition of types.
-
-We adopt pattern-matching to define some functions.
-These pattern-matching definitions follow the inductive definitions
-of the type.
+type theory, pattern-matching~\cite{Coquand1992} to define functions by cases on the inductive definition for the type of the arguments.
 \end{notation}
@@
 
-In~\eqref{eq:uh-definition} is a definition no structurally recursive.
+In~\eqref{eq:uh-definition}, the first two equations in the $\fuh_{0}$ function definition are no structurally recursive.
+Note that the formula used in the recursive calls are not subformulas
+of the formula in the function argument.
 
@@
 
-Therefore, one way to translate $\fuh_{0}$ to type
+Therefore, one way to define $\fuh_{0}$ in type
 theory is to define a new function using a bounded recursion.
@@
 
-\caption{Inference rules for propositional logic.}
+\caption{Inference rules for classical propositional logic.}
 \label{fig:CPL-inference-rules}

### 2018-01-03 pubs/itp-2018/sections/abstract.tex
ITP 2018: Initial commit.

--- 2017-11-20 paper/sections/abstract.tex
@@
 
-We describe a syntactical proof-reconstruction approach to verify derivations
-generated by \Metis prover to theorems in classical propositional logic. To
-verify such derivations, we formalise in type theory each inference rule
-of the \Metis reasoning. We developed a tool jointly with two \Agda libraries
-to translate \Metis derivations to \Agda proof-terms.
-These developments allowed us to type-check with \Agda, \Metis proofs
-step-by-step.
+We describe a syntactical proof-reconstruction approach to verify
+derivations generated by \Metis prover to theorems in classical
+propositional logic. To verify such derivations, we formalize in type
+theory each inference rule of the \Metis reasoning. We developed a
+tool jointly with two \Agda libraries to translate \Metis derivations
+to \Agda proof-terms. These developments allowed us to type-check
+with \Agda, \Metis derivations step-by-step.
 

### 2018-01-03 pubs/itp-2018/sections/acknowledgements.tex
ITP 2018: Initial commit.

\documentclass[../main.tex]{subfiles}
\begin{document}

% ===================================================================

\subsubsection*{Acknowledgments.}
The first author would like to thank to Universidad EAFIT for funding
and supporting his master studies. He thankfully acknowledge Andreas
Abel and Chalmers University of Technology at Goteborg, Sweden for
inviting him to be part of the \Agda Implementors’ Meeting XXV where
he presented part of this research. We thank Joe Leslie-Hurd for his
support and comments about \Metis.  We also acknowledge the work
carried out by Alejandro G\'omez-Londo\~no~\cite{Gomez-Londono2015}
used as the basis for our \TSTP parsing module in~\cite{Athena}. This
research was fully supported by Universidad EAFIT (grant
\#~690-000088).

\end{document}

### 2018-01-03 pubs/itp-2018/fix-references.sh

@@ -1,0 +1,6 @@
+#!/bin/sh
+
+sed -i -r "/(url|doi)/ s/\{.?(.)\}/\1/g" ref-mendeley.bib
+sed -i -r "s/journaltitle/journal     /g" ref-mendeley.bib
+sed -i -r "s/@inbook/@incollection/g" ref-mendeley.bib
+sed -i -r "/file/d" ref-mendeley.bib

### 2018-01-25 pubs/itp-2018/sections/abstract.tex
[ itp-2018 ] Abstract and title submitted.

--- 2017-11-20 paper/sections/abstract.tex
@@
 \begin{abstract}
+  We describe a syntactical proof-reconstruction approach to verify
+  derivations generated by the automatic theorem prover \Metis for
+  classical propositional logic theorems. To verify these derivations,
+  we use \Agda, a proof assistant for dependent type theory. We
+  formalise in \Agda each inference rule of \Metis reasoning, that is,
+  we transform \Metis derivations into \Agda proof-terms. In a future
+  full-fledged integration of \Agda with off-the-shelf automatic
+  theorem provers, proof-reconstruction shall be a necessary
+  component.
 
-We describe a syntactical proof-reconstruction approach to verify derivations
-generated by \Metis prover to theorems in classical propositional logic. To
-verify such derivations, we formalise in type theory each inference rule
-of the \Metis reasoning. We developed a tool jointly with two \Agda libraries
-to translate \Metis derivations to \Agda proof-terms.
-These developments allowed us to type-check with \Agda, \Metis proofs
-step-by-step.
-
-\keywords{proof-reconstruction, type theory, automatic theorem prover,
-proof-assistant}
+  \keywords{proof-reconstruction, automatic theorem provers,
+    proof-assistants, Agda, Metis}
 \end{abstract}

### 2018-02-23 pubs/itp-2018/sections/introduction.tex
Tested with GHC 8.2.2.
[ paper ] removed many examples and extra content.

--- 2018-01-03 pubs/thesis/sections/introduction.tex
@@
 proving each deduction of the prover, the \emph{source} system,
-with a formalization of the prover reasoning in a proof-assistant, the \emph{target} system. The target system is the
+with a formalization of the prover reasoning in a proof-assistant, the
+\emph{target} system. The target system is the
 proof \emph{checker} in charge to verify the source system reasoning
@@
 \Haskell that is able to generate \Agda proof-terms for \Metis
-derivations. During writing this document, our formalization helps to report two programming errors in \Metis.
-A bug\footnote{Issue No.\,2 at \url{https://github.com/gilith/metis/issues/2}} in the printing of the derivation and a soundness bug\footnote{Issue No.\,4 at \url{https://github.com/gilith/metis/issues/4}} in the stripping of the goal.
+derivations. During writing this document, our formalization helps to report
+two programming errors in \Metis.
+A bug\footnote{Issue No.\,2 at \url{https://github.com/gilith/metis/issues/2}}
+in the printing of the derivation and a soundness
+bug\footnote{Issue No.\,4 at \url{https://github.com/gilith/metis/issues/4}} in the stripping of the goal.
 
@@
 
-The proof-reconstruction tool \Athena was tested with \prg{GHC}~8.2.1.
+The proof-reconstruction tool \Athena was tested with \prg{GHC}~8.2.2.
 Both libraries, \verb!agda-prop! and \verb!agda-metis! were tested with
 \Agda~2.5.3 and \Agda standard library~0.14.
-\Athena jointly with \verb!agda-prop! and \verb!agda-metis! are able to reconstruct propositional proofs of \Metis~2.3 (release~20171021).
+\Athena jointly with \verb!agda-prop! and \verb!agda-metis! are able
+to reconstruct propositional proofs of \Metis~2.3 (release~20171021).
 We successfully reconstruct around eighty theorems in classical propositional

### 2018-02-23 pubs/itp-2018/sections/metis-language-and-proofs.tex
ITP 2018: Initial commit.
[ paper ] removed many examples and extra content.

--- 2017-11-21 paper/sections/metis-language-and-proofs.tex
@@
     \AxiomC{}
-    \RightLabel{axiom}
-    \UnaryInfC{$Γ ⊢ φ$}
+    \RightLabel{axiom~$φ₁,\cdots,φₙ$}
+    \UnaryInfC{$Γ ⊢ φ₁ ∨ \cdots ∨ φₙ$}
   \end{bprooftree}
@@
 The \TPTP language is the input language to encode problems used by \Metis.
-It includes the first-order form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf}) formats~\cite{sutcliffe2009}.
+It includes the first-order form (denoted by \name{fof}) and clause normal
+form (denoted by \name{cnf}) formats~\cite{sutcliffe2009}.
 The \TPTP syntax\footnote{See the complete syntax grammar
-at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} describes a well-defined grammar to handle annotated
-formulas with the following form:
+at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} describes a
+well-defined grammar to handle annotated formulas with the following form:
 
@@
 ($⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$) respectively.
-
-\begin{myexamplenum}
-  For instance, let us express the problem
-  $p\, ⊢ ¬ (p ∧ ¬ p) ∨ (q ∧ ¬ q)$ in \TPTP syntax. We begin by
-  declaring the $p$ axiom using the \verb!axiom!  keyword. Next, we
-  include the expected conclusion using the \verb!conjecture! keyword.
-
-\begin{verbatim}
-  fof(h, axiom, p).
-  fof(goal, conjecture, ~ ((p & ~ p) | (q & ~ q))).
-\end{verbatim}
-
-\end{myexamplenum}
 
@@
 
-\begin{myexamplenum}
-
-In the script below, \strip is the name of the inference.
-It has no arguments and derives from one parent node named  \verb!goal!. The
-result of this inference when it applies to the \verb!goal! formula is
-\verb!p!.
-
-\begin{verbatim}
-  fof(subgoal_0, plain, p, inference(strip, [], [goal])).
-\end{verbatim}
-\end{myexamplenum}
-
 \begin{notation}
@@
 Let us consider the following \TSTP derivation using
-the customized \TSTP syntax (see the original \TSTP derivation and customizations in Appendix~\ref{app:tstp-syntax}).
+the customized \TSTP syntax (see the original \TSTP derivation and
+customizations in Appendix~\ref{app:tstp-syntax}).
 
@@
   fof(goal, conjecture, p).
-  fof(s₀, p, inf(strip, goal)).
+  fof(s₀, inf(strip, goal)).
   fof(neg₀, ¬ p, inf(negate, s₀)).
@@
 
-\subsection{\Metis Derivations}
+\subsection{Derivations}
 \label{ssec:metis-proofs}
@@
 A derivation generated by \Metis encodes a natural
-deduction proof, Fig.~\ref{fig:metis-example} is an example of such kind of proof. With the inference rules in
+deduction proof. With the inference rules in
 Fig.~\ref{tab:agda-metis-table}
@@
 These derivations are directed acyclic graphs, trees of refutations.
-Each node stands for an application of an inference rule and the leaves in the tree represent formulas in the given problem.
-Each node is labeled with a name of the inference rule
-(\eg, \canonicalize).
-Each edge links a premise with one conclusion.
-The proof graphs have at their root the conclusion
-$⊥$, since \Metis derivations are refutations.
-
-\begin{figure}[!ht]
-\centering
-  \begin{bprooftree}\tt
-    \AxiomC{}
-    \RightLabel{negate}
-    \UnaryInfC{$\neg p$}
-    \RightLabel{strip}
-    \UnaryInfC{$\neg p$}
-    \AxiomC{}
-    \RightLabel{axiom}
-    \UnaryInfC{$p$}
-    \RightLabel{canonicalize}
-    \UnaryInfC{$p$}
-    \RightLabel{simplify}
-    \BinaryInfC{$⊥$}
-    \RightLabel{canonicalize}
-    \UnaryInfC{$⊥$}
-  \end{bprooftree}
-  \caption{\Metis derivation tree of Example~\ref{fig:metis-example-tree}.}
-  \label{fig:metis-example}
-\end{figure}
+Each node stands for an application of an inference rule and the
+leaves in the tree represent formulas in the given problem. Each node
+is labeled with a name of the inference rule (\eg, \canonicalize).
+Each edge links a premise with one conclusion. The proof graphs have
+at their root the conclusion $⊥$, since \Metis derivations are
+refutations.
 
@@
 \clausify rule need theorems developed for the \canonicalize rule. The
-\canonicalize rule needs theorems developed in the \resolve section. But the
-\resolve rule depends on the \conjunct rule.
+\canonicalize rule needs theorems developed in the \resolve formalization,
+and \resolve depends on the \conjunct rule.
 
@@
     \label{tab:agda-metis-table}
-    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}c@{\hspace{2mm}}|}
+    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{4mm}}l@{\hspace{2mm}}c@{\hspace{2mm}}|}
     \hline
-    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem number}\\ \hline
+    \textbf{Rule} & \textbf{Purpose} &\textbf{Theorem number}\\ \hline
 

### 2018-02-23 pubs/itp-2018/sections/proof-reconstruction/canonicalize.tex
[ paper ] removed many examples and extra content.

\documentclass[../../main.tex]{subfiles}
\begin{document}

\subsubsection{Canonicalize.}
\label{sssec:canonicalize}

The \canonicalize rule is an inference that transforms a formula to
its negative normal form or its conjunctive normal form depending on
the role that the formula plays in the problem.
This rule jointly with the \clausify rule perform the so-called
\emph{clausification} process mainly described
in~\cite{Sutcliffe1996}.

The \canonicalize rule also removes inside of the formula
the tautologies listed in~Fig.~\ref{fig:redundancies}.

\begin{figure}
  \[
    \begin{bprooftree}
      \AxiomC{$Γ ⟝ φ ∨ ⊥$}
      \UnaryInfC{$Γ ⟝ φ$}
    \end{bprooftree}
    \qquad
    \begin{bprooftree}
      \AxiomC{$Γ ⟝ φ ∨ ⊤$}
      \UnaryInfC{$Γ ⟝ ⊤$}
    \end{bprooftree}
    \qquad
    \begin{bprooftree}
      \AxiomC{$Γ ⟝ φ ∨ ¬ φ$}
      \UnaryInfC{$Γ ⟝ ⊤$}
    \end{bprooftree}
    \qquad
    \begin{bprooftree}
      \AxiomC{$Γ ⟝ φ ∨ φ$}
      \UnaryInfC{$Γ ⟝ φ$}
    \end{bprooftree}
  \]

  \[
    \begin{bprooftree}
      \AxiomC{$Γ ⟝ φ ∧ ⊥$}
      \UnaryInfC{$Γ ⟝ ⊥$}
    \end{bprooftree}
    \qquad
    \begin{bprooftree}
      \AxiomC{$Γ ⟝ φ ∧ ⊤$}
      \UnaryInfC{$Γ ⟝ φ$}
    \end{bprooftree}
    \qquad
    \begin{bprooftree}
      \AxiomC{$Γ ⟝ φ ∧ φ$}
      \UnaryInfC{$Γ ⟝ φ$}
    \end{bprooftree}
    \qquad
    \begin{bprooftree}
      \AxiomC{$Γ ⟝ φ ∧ ¬ φ$}
      \UnaryInfC{$Γ ⟝ ⊥$}
    \end{bprooftree}
  \]
  \caption{Theorems to remove inside of a formula by the
  \canonicalize rule.}
\label{fig:redundancies}
\end{figure}

The \canonicalize rule is used by \Metis to introduce the subgoals in
their refutation proofs but also helps to simplify formulas at
intermediate steps in the derivations. As far as we know, the
\canonicalize rule implements a conjunctive normal form conversion
with simplifications of tautologies. Otherwise, when
an axiom, definition or hypothesis is needed to prove some goal, this
rule gets the negative normal form of the formula.

To reconstruct the \canonicalize rule, we adapted some ideas from the
\Metis source code. The presentation of this reconstruction is as
follows. We firstly describe functions to remove tautologies inside
of the formula. After, we present the negative normal form conversion
in~Lemma~\ref{lem:nnf} and the conjunctive normal form in
Lemma~\ref{lem:cnf}. At the end of this section, we state
Theorem~\ref{thm:canonicalize} to reconstruct the \canonicalize rule.

\begin{notation}
In a disjunction, $φ ≡ φ₁ ∨ φ₂ ∨ \cdots ∨ φₙ$, we say $ψ ∈_{∨} φ$,
if there is some $i = 1, \cdots, n$ such that $ψ ≡ φᵢ$.
Note that $ψ ∈_{∨} φ$ is another representation for the equality
$ψ ≡ \freorder_{∨}~φ~ψ$.
\end{notation}

In right-associative disjunctions we remove the tautologies
in Fig.~\ref{fig:or-redundancies} using Lemma~\ref{lem:canon-or}.
We assume the formulas to be right-associative unless otherwise
stated.

\begin{figure}
\begin{equation*}
\begin{bprooftree}
  \AxiomC{$Γ ⟝ φ ∨ ⊥$}
  \UnaryInfC{$Γ ⟝ φ$}
\end{bprooftree}\qquad
\begin{bprooftree}
  \AxiomC{$Γ ⟝ φ ∨ ⊤$}
  \UnaryInfC{$Γ ⟝ ⊤$}
\end{bprooftree}\qquad
\begin{bprooftree}
  \AxiomC{$Γ ⟝ φ ∨ φ$}
  \UnaryInfC{$Γ ⟝ φ$}
\end{bprooftree}
\begin{bprooftree}
  \AxiomC{$Γ ⟝ φ ∨ ¬~φ$}
  \UnaryInfC{$Γ ⟝ ⊤$}
\end{bprooftree}\qquad
\end{equation*}
\caption{Theorems to remove inside of a disjunction by
the \canonicalize rule.}
\label{fig:or-redundancies}
\end{figure}

\begin{mainlemma}
  \label{lem:canon-or}

  Let $φ : \Prop$ be a right-associative formula. If $Γ~⟝~φ$
  then $Γ~⟝~\fcanon_{∨}~φ$, where

\begin{equation}
\label{eq:canon-or}
\begin{aligned}
 &\hspace{.495mm}\fcanon_{∨} : \NProp \to \NProp\\
 &\begin{array}{lll}
   \fcanon_{∨} &(⊥ ∨ φ)     &= \fcanon_{∨}~φ \\
   \fcanon_{∨} &(φ ∨ ⊥)     &= \fcanon_{∨}~φ \\
   \fcanon_{∨} &(⊤ ∨ φ)     &= ⊤\\
   \fcanon_{∨} &(φ ∨ ⊤)     &= ⊤\\
   % \fcanon_{∨} &(¬ φ₁ ∨ φ₂) &=
   %      \begin{cases}
   %       \fcanon_{∨}~φ₂,        &\text{ if } ¬ φ₁ ∈_{∨} φ₂;\\
   %       ⊤,                     &\text{ if } φ₁ ∈_{∨} φ₂;\\
   %       ⊤,                     &\text{ if } \fcanon_{∨}~φ₂≡ ⊤;\\
   %       ¬ φ₁,                  &\text{ if } \fcanon_{∨}~φ₂≡ ⊥;\\
   %       ¬ φ₁ ∨ \fcanon_{∨}~φ₂, &\text{ otherwise.}
   %      \end{cases}\\
   \fcanon_{∨} &(φ₁ ∨ φ₂)   &=
    \begin{cases}
     ⊤,                     & \text{ if } φ₁ ≡ ¬ ψ \text{ for some }ψ : \Prop \text{ and } ψ ∈_{∨} φ₂;\\
     ⊤,                     & \text{ if } (¬ φ₁) ∈_{∨} φ₂;\\
     \fcanon_{∨}~φ₂,        & \text{ if } φ₁ ∈_{∨} φ₂;\\
     ⊤,                     & \text{ if } \fcanon_{∨}~φ₂~ ≡ ⊤;\\
     φ₁,                    & \text{ if } \fcanon_{∨}~φ₂~ ≡ ⊥;\\
     φ₁ ∨ \fcanon_{∨}~φ₂,   & \text{ otherwise.}
    \end{cases}\\
   \fcanon_{∨} &φ           &= φ.
  \end{array}
\end{aligned}
\end{equation}
\end{mainlemma}

Now, we have removed tautologies in disjunctions by applying the
$\fcanon_{∨}$ function. In a similar way, we define the $\fcanon_{∧}$
function to work with conjunctions.

\begin{notation}
In a conjunction, $φ ≡ φ₁ ∧ φ₂ ∧ \cdots ∧ φₙ$, we say
$ψ ∈_{∧} φ$, if there is some $i = 1, \cdots, n$ such that $ψ ≡ φᵢ$.
Note that $ψ ∈_{∧} φ$ is another representation of
the equality $ψ ≡ \fconjunct~φ~ψ$.
\end{notation}

In right-associative conjunctions we remove the tautologies
in Fig.~\ref{fig:and-redundancies} using Lemma~\ref{lem:canon-and}.

\begin{figure}
\begin{equation*}
\begin{bprooftree}
  \AxiomC{$Γ ⟝ φ ∧ ⊤$}
  \UnaryInfC{$Γ ⟝ φ$}
\end{bprooftree}\qquad
\begin{bprooftree}
  \AxiomC{$Γ ⟝ φ ∧ ⊥$}
  \UnaryInfC{$Γ ⟝ ⊥$}
\end{bprooftree}\qquad
\begin{bprooftree}
  \AxiomC{$Γ ⟝ φ ∧ φ$}
  \UnaryInfC{$Γ ⟝ φ$}
\end{bprooftree}\qquad
\begin{bprooftree}
  \AxiomC{$Γ ⟝ φ ∧ ¬~φ$}
  \UnaryInfC{$Γ ⟝ ⊥$}
\end{bprooftree}
\end{equation*}
\caption{Conjunction tautologies.}
\label{fig:and-redundancies}
\end{figure}

\begin{mainlemma}
  \label{lem:canon-and}

  Let $φ : \Prop$ be a right-associative formula. If $Γ~⟝~φ$
  then $Γ~⟝~\fcanon_{∧}~φ$, where

  \begin{equation}
   \label{eq:canon-and}
    \begin{aligned}
     &\hspace{.495mm}\fcanon_{∧} : \NProp \to \NProp\\
      &\begin{array}{lll}
        \fcanon_{∧} &(⊥ ∧ φ)     &= ⊥  \\
        \fcanon_{∧} &(φ ∧ ⊥)     &= ⊥  \\
        \fcanon_{∧} &(⊤ ∧ φ)     &= \fcanon_{∧}~φ \\
        \fcanon_{∧} &(φ ∧ ⊤)     &= \fcanon_{∧}~φ \\
        % \fcanon_{∧} &(¬ φ₁ ∧ φ₂) &=
        %   \begin{cases}
        %     ⊥,                     &\text{ if } φ₁ ∈_{∧} φ₂;\\
        %     \fcanon_{∧}~φ₂,        &\text{ if } ¬ φ₁ ∈_{∧} φ₂;\\
        %     ⊥,                     &\text{ if } \fcanon_{∧}~φ₂~≡ ⊥;\\
        %      \fcanon_{∧}~φ₂,       &\text{ if } \fcanon_{∧}~φ₂~≡ ⊤;\\
        %     ¬ φ₁ ∧ \fcanon_{∧}~φ₂, &\text{ otherwise.}
        %   \end{cases}\\
        \fcanon_{∧} &(φ₁ ∧ φ₂) &=
          \begin{cases}
            ⊥,                   & \text{ if } φ₁ ≡ ¬ ψ \text{ for some }ψ : \Prop \text{ and } ψ ∈_{∧} φ₂;\\
            ⊥,                   & \text{ if } (¬ φ₁) ∈_{∧} φ₂;\\
            \fcanon_{∧}~φ₂,      & \text{ if } φ₁ ∈_{∧} φ₂;\\
            φ₁,                  & \text{ if } \fcanon_{∧}~φ₂~≡ ⊤;\\
            ⊥,                   & \text{ if } \fcanon_{∧}~φ₂~≡ ⊥;\\
            φ₁ ∧ \fcanon_{∧}~φ₂, &\text{ otherwise.}
          \end{cases}\\
        \fcanon_{∧} &φ         &= φ.
       \end{array}
    \end{aligned}
    \end{equation}
\end{mainlemma}

Now, we are ready to define the negative normal form of a formula with
simplifications by applying to it the $\fnnf$ function defined in
Lemma~\ref{lem:nnf} (see more details in Appendix~\ref{app:polarity-for-propositions}).
This definition is mainly based on the \Metis
source code to normalize formulas. To define such a function in type
theory we used bounded recursion as we describe in
Section~\ref{ssec:structural-recursion}.

\begin{equation}
\label{eq:nnf}
\begin{aligned}
&\hspace{.495mm}\fnnf_{1} : \Prop \to \Nat \to \Prop\\
&\begin{array}{llll}
\fnnf_{1} &(φ₁ ∧ φ₂)     &(\suc~n) &= \fcanon_{∧}~(\fassoc_{∧}~(\fnnf_{1}~φ₁~n ∧ \fnnf_{1}~φ₂~n))\\
\fnnf_{1} &(φ₁ ∨ φ₂)     &(\suc~n) &= \fcanon_{∨}~(\fassoc_{∨}~(\fnnf_{1}~φ₁~n ∨ \fnnf_{1}~φ₂~n))\\
\fnnf_{1} &(φ₁ ⇒ φ₂)     &(\suc~n) &= \fcanon_{∨}~(\fassoc_{∨}~(\fnnf_{1}~((¬ φ₁) ∨ φ₂)~n))\\
\fnnf_{1} &(¬ (φ₁ ∧ φ₂)) &(\suc~n) &= \fcanon_{∨}~(\fassoc_{∨}~(\fnnf_{1}~((¬ φ₁) ∨ (¬ φ₂))~n))\\
\fnnf_{1} &(¬ (φ₁ ∨ φ₂)) &(\suc~n) &= \fcanon_{∧}~(\fassoc_{∧}~(\fnnf_{1}~((¬ φ₁) ∧ (¬ φ₂))~n))\\
\fnnf_{1} &(¬ (φ₁ ⇒ φ₂)) &(\suc~n) &= \fcanon_{∧}~(\fassoc_{∧}~(\fnnf_{1}~((¬ φ₂) ∧ φ₁)~n))\\
\fnnf_{1} &(¬ (¬ φ))     &(\suc~n) &= \fnnf_{1}~φ₁~n\\
\fnnf_{1} &(¬ ⊤)         &(\suc~n) &= ⊥\\
\fnnf_{1} &(¬ ⊥)         &(\suc~n) &= ⊤\\
\fnnf_{1} &φ             &\zero    &= φ
\end{array}
\end{aligned}
\end{equation}

\begin{mainlemma}
  \label{lem:nnf}
  If $Γ ⊢ φ$ then $Γ ⟝ \fnnf~φ$, where
  \begin{align*}
   \begin{split}
     &\fnnf : \NProp \to \NProp\\
     &\fnnf~φ = \fnnf_{1}~φ~(\fnnf_{cm}~φ).
   \end{split}
  \end{align*}
  The $\fnnf_{cm}$  complexity measure function
  is defined in Appendix~\ref{app:polarity-for-propositions}.
\end{mainlemma}

To get the conjunctive normal form, we make sure the formula is a
conjunction of disjunctions. For such a purpose, we use distributive laws in
Lemma~\ref{lem:dist} to get that form after applying the $\fnnf$ function.

\begin{mainlemma}
  \label{lem:dist}
  $Γ ⟝ φ$ then $Γ ⟝ \fdist~φ$, where
  \begin{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fdist : \NProp \to \NProp\\
  &\begin{array}{lll}
    \fdist &(φ₁ ∧ φ₂) &= \fdist~φ₁ ∧ \fdist~φ₂\\
    \fdist &(φ₁ ∨ φ₂) &= \fdist_{∨}~(\fdist~φ₁ ∨ \fdist~φ₂)\\
    \fdist &φ         &= φ
   \end{array}\\
  \text{and}\\
  &\hspace{.495mm}\fdist_{∨} : \NProp \to \NProp\\
  &\begin{array}{lll}
    \fdist_{∨}&((φ₁ ∧ φ₂) ∨ φ₃) &= \fdist_{∨}~(φ₁ ∨ φ₂) ∧ \fdist_{∨}~(φ₂ ∨ φ₃)\\
    \fdist_{∨}&(φ₁ ∨ (φ₂ ∧ φ₃)) &= \fdist_{∨}~(φ₁ ∨ φ₂) ∧ \fdist_{∨}~(φ₁ ∨ φ₃)\\
    \fdist_{∨}&φ &= φ.
    \end{array}
   \end{aligned}
  \end{equation*}
\end{mainlemma}

We get the conjunctive normal form by applying
the $\fnnf$ function follow by the $\fdist$ function.

\begin{mainlemma}
\label{lem:cnf}
  If $Γ ⊢ φ$ then $Γ ⊢ \fcnf~φ$, where
  \begin{align*}
    \begin{split}
    &\fcnf : \Prop \to \Prop\\
    &\fcnf~φ = \fdist~(\fnnf~φ).
    \end{split}
  \end{align*}
\end{mainlemma}

\begin{proof}
  Composition of Lemma~\ref{lem:dist} and Lemma~\ref{lem:nnf}.
\end{proof}

Since all the transformations in Lemma~\ref{lem:nnf} and
Lemma~\ref{lem:dist} came from logical equivalences in propositional
logic, we state the following lemmas used in the reconstruction of the \simplify rule in Lemma~\ref{lem:reduce-literal} and in
Theorem~\ref{thm:canonicalize} for the \canonicalize rule.
\begin{mainlemma}
\label{lem:nnf-inv}
  If $Γ ⊢ \fnnf~φ$ then $Γ ⊢ φ$.
\end{mainlemma}

\begin{mainlemma}
\label{lem:cnf-inv}
  If $Γ ⊢ \fcnf~φ$ then $Γ ⊢ φ$.
\end{mainlemma}

Now, we are ready to reconstruct the \fcanonicalize rule. This inference rule
defined in \eqref{eq:canonicalize} performs normalization for a proposition.
That is, depending on the role of the formula in the problem, it converts that
formula to its negative normal form or its conjunctive normal form. In both
cases, \canonicalize simplifies the formula by removing tautologies inside of
it as we widely described above for theorems in Fig.~\ref{fig:redundancies}.

Based on the \Metis source code, when the formula plays the axiom or
definition role, the \canonicalize rule transforms the source formula
to its negative normal form. Otherwise, this rule converts the
formula to a simplified conjunctive normal form.

Since this rule mostly consists of dealing with clauses, to
reconstruct this rule, our strategy mainly consists of checking the
equality of negative normal form between the source and the target
formula. If it fails, we try to reorder the conjunctive normal form
of the source formula to match with the conjunctive normal form of
the target formula. It definition is as follows.

\begin{mainth} % (fold)
  \label{thm:canonicalize}
   Let $ψ : \Target$. If $Γ ⊢ φ$ then $Γ~⊢~\fcanonicalize~φ~ψ$, where
  \begin{equation}
  \label{eq:canonicalize}
  \begin{aligned}
  &\hspace{.495mm}\fcanonicalize : \Source \to \Target \to \Prop\\
  &\fcanonicalize~φ~ψ = \begin{cases}
        ψ, &\text{ if  } ψ ≡ φ;\\
        ψ, &\text{ if  } ψ ≡ \fnnf~φ;\\
        ψ, &\text{ if  } \fcnf~ψ≡ \freorder_{∧∨}~(\fcnf~φ)~(\fcnf~ψ);\\
        φ, &\text{ otherwise. }
        \end{cases}
   \end{aligned}
  \end{equation}
\end{mainth}

\begin{proof}\hspace{3mm}
\begin{itemize}
\item[∙] Case $φ ≡ ψ$. By substitution theorem we conclude $Γ ⊢ ψ$.
\item[∙] Case $ψ ≡ \fnnf~φ$.
\begin{equation*}
  \begin{bprooftree}
    \AxiomC{$Γ ⊢ φ$}
    \RightLabel{Lemma~\ref{lem:nnf}}
    \UnaryInfC{$Γ ⊢~\fnnf~φ$}
    \AxiomC{$ψ ≡ \fnnf~φ$}
    \RightLabel{\fsubst}
    \BinaryInfC{$Γ ⊢ ψ$}
  \end{bprooftree}
\end{equation*}

\item[∙] Case $\fcnf~ψ ≡ \freorder_{∧∨}~(\fcnf~φ)~(\fcnf~ψ)$.
  \begin{equation*}
    \begin{bprooftree}
      \AxiomC{$Γ ⊢ φ$}
      \RightLabel{Lemma~\ref{lem:cnf}}
      \UnaryInfC{$Γ ⊢ \fcnf~φ$}
      \RightLabel{Lemma~\ref{lem:reorder-and-or}}
      \UnaryInfC{$Γ ⊢ \freorder_{∧∨}~(\fcnf~φ)~(\fcnf~ψ)$}
      \AxiomC{$\fcnf~ψ~≡~\freorder_{∧∨}~(\fcnf~φ)~(\fcnf~ψ)$}
      \RightLabel{\fsubst}
      \BinaryInfC{$Γ ⊢ \fcnf~ψ$}
      \RightLabel{Lemma~\ref{lem:cnf-inv}}
      \UnaryInfC{$Γ ⊢ ψ$}
    \end{bprooftree}
  \end{equation*}
\end{itemize}
\end{proof}

\end{document}

### 2018-02-23 pubs/itp-2018/sections/proof-reconstruction/resolve.tex
[ paper ] removed many examples and extra content.

--- 2017-12-22 paper/sections/proof-reconstruction/resolve.tex
@@
 \end{mydefinition}
-
-Below, we provide Lemma~\ref{lem:reorder-or},
-Lemma~\ref{lem:reorder-and}, Lemma~\ref{lem:reorder-and-or} to perform such reordering tasks, the omitted proofs can be found
-in~\cite{AgdaMetis}.
-
-First, we define the $\fassoc_{⬓}$ function in~\eqref{eq:fassoc} to
-convert a disjunction or a conjunction into its right-associative
-form. The square symbol (⬓) can be the conjunction symbol or the
-disjunction symbol. We use $\fassoc_{∧}$ to convert conjunctions and
-$\fassoc_{∨}$ for disjunctions.
-
-\begin{equation}
-\label{eq:fassoc}
-  \begin{aligned}
-    &\hspace{.495mm}\fassoc_{⬓} : \Prop \to \Prop\\
-    &\begin{array}{lll}
-    \fassoc_{⬓} &((φ₁~⬓~φ₂)~⬓~φ₃) &= \fassoc_{⬓}~(φ₁~⬓~(φ₂~⬓~φ₃))\\
-    \fassoc_{⬓} &(φ₁~⬓~φ₂)        &= φ₁~⬓~\fassoc_{⬓}~φ₂\\
-    \fassoc_{⬓} &φ                &= φ.
-    \end{array}
-  \end{aligned}
-\end{equation}
-
-\begin{mainlemma}
-\label{lem:rassoc}
-  If $Γ ⊢ φ$ then $Γ ⊢ \fassoc_{⬓}~φ$.
-\end{mainlemma}
-
-\begin{myremark}
-
-In \TPTP syntax, the formulas are in left-associative form by
-default. Despite of that convention, \Metis assumes the formulas to
-be in right-associative form by default. This is a matter to take
-into account for the proof-reconstruction.
-
-\end{myremark}
-
-The $\fbuild_{∨}$ function defined in~\eqref{eq:build-or} intends to
-construct a disjunction from another disjunction, specifically, this
-function will try to rearrange the disjuncts in the source formula to
-be the target disjunction formula.
-
-\begin{mainlemma}
-\label{lem:build-or}
-  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fbuild_{∨}~φ~ψ$, where
-\begin{equation}
-  \begin{split}
-  \label{eq:build-or}
-  &\fbuild_{∨} : \Source → \Target → \Prop\\
-  &\fbuild_{∨}~φ~ψ~ =%\\
-  % &\hspace{3mm}
-  \begin{cases}
-  ψ, &\text{ if } φ ≡ ψ;\\
-  ψ, &\text{ if } ψ ≡ ψ₁ ∨ ψ₂\text{ and } ψᵢ ≡ \fbuild_{∨}~φ~ψᵢ\text{ for some }i=1, 2;\\
-  φ, &\text{ otherwise.}
-  \end{cases}
-  \end{split}
-\end{equation}
-\end{mainlemma}
-
-From now on, we assume all propositions to be right-associative
-unless otherwise stated.
-
-The $\ffactor$ function in~\eqref{eq:factor-definition}
-simplifies a special case of disjunction, the repeated disjuncts
-(\eg, $\ffactor~(φ ∨ φ)~=~φ$).
-Notice that other cases like $φ~∨~(ψ~∨~φ)$ do not reduce to $ψ~∨~φ$.
-We use this function in Lemma~\ref{lem:sbuild-or}.
-
-\begin{mainlemma}
-\label{lem:factor}
- If $Γ ⊢ φ$ then $Γ ⊢ \ffactor~φ$, where
-\begin{align}
-\begin{split}
-  \label{eq:factor-definition}
-  &\ffactor : \Prop → \Prop\\
-  &\ffactor~φ~ =
-  \begin{cases}
-    φ₁,  &\text{ if }φ ≡ φ₁ ∨ φ₂ \text{ and } φ₁ ≡ \ffactor~φ₂;\\
-    φ,   &\text{ otherwise.}
-  \end{cases}
-\end{split}
-\end{align}
-\end{mainlemma}
-
-To construct a disjunction~$ψ$ from a disjunction~$φ$, we have used
-ideas from the description in~\cite{bohme2010} to prove equality
-between nested disjunctions.  We define the $\fsbuild_{∨}$ function
-in~\eqref{eq:strong-build-or} that uses every disjunct from the
-source formula, $φ$, to build up the target disjunction $ψ$.
-
-\begin{mainlemma}
-\label{lem:sbuild-or}
-If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fsbuild_{∨}~φ~ψ$, where
-\begin{equation}
-\label{eq:strong-build-or}
- \begin{aligned}
-     &\hspace{.495mm}\fsbuild_{∨} : \Source → \Target → \Prop\\
-    &\begin{array}{lll}
-    \fsbuild_{∨}&(φ₁ ∨ φ₂)~ψ &=\ffactor~(\fbuild_{∨}~φ₁~ψ ∨ \fbuild_{∨}~φ₂~ψ)\\
-    \fsbuild_{∨}&φ~ψ &= \fbuild_{∨}~φ~ψ.
-     \end{array}
-\end{aligned}
-\end{equation}
-\end{mainlemma}
-
-\begin{myexamplenum}
-We build the disjunction $(p ∨ q) ∨ r$ from the disjunction
-$r ∨ (q ∨ p)$ using Lemma~\ref{lem:sbuild-or}.
-
-\begin{equation*}
-(\mathcal{D})\hspace{3mm}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ q$}
-  \RightLabel{∨-intro₂}
-  \UnaryInfC{$Γ ⊢ p ∨ q$}
-  \RightLabel{∨-intro₁}
-  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-  \AxiomC{$Γ ⊢ p$}
-  \RightLabel{∨-intro₁}
-  \UnaryInfC{$Γ ⊢ p ∨ q$}
-  \RightLabel{∨-intro₁}
-  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-  \RightLabel{∨-elim}
-  \BinaryInfC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
-  \end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ r$}
-  \RightLabel{∨-intro₂}
-  \UnaryInfC{$Γ ⊢ (p ∨ q) ∨ r$}
-
-  \AxiomC{$\mathcal{D}$}
-  \UnaryInfC{$Γ, q ∨ p ⊢ (p ∨ q) ∨ r$}
-
-  \RightLabel{∨-elim}
-  \BinaryInfC{$Γ, r ∨ (q ∨ p) ⊢ (p ∨ q) ∨ r$}
-
-  \RightLabel{⇒-intro}
-  \UnaryInfC{$Γ ⊢ r ∨ (q ∨ p) ⇒ (p ∨ q) ∨ r$}
-
-  \end{bprooftree}
-\end{equation*}
-\end{myexamplenum}
-
-\begin{myremark}
-
-Notice that using $\fsbuild_{∨}$ we can build not only a disjunction
-with the same disjuncts of the source formula but also a complete
-different disjunction by adding new disjuncts to the source formula
-via introduction rules for disjunctions.
-
-\end{myremark}
-
-The following lemma aims to reorder nested disjunctions
-by forcing the formula to be in right-associative form in order to
-apply Lemma~\ref{lem:sbuild-or}.
-
-\begin{mainlemma}
-  \label{lem:reorder-or}
-  If $Γ ⊢ φ$ and $ψ: \Target$ then $Γ ⊢ \freorder_{∨}~φ~ψ~$, where
-  \begin{align}
-    \begin{split}
-    \label{eq:reorder-or}
-    &\freorder_{∨} : \Source \to \Target \to \Prop\\
-    &\freorder_{∨}~φ~ψ~= \fsbuild_{∨}~(\fassoc_{∨}~φ)~ψ.
-    \end{split}
-  \end{align}
-\end{mainlemma}
-
-\begin{proof}
-Use Lemma~\ref{lem:rassoc} and Lemma~\ref{lem:sbuild-or}.
-\end{proof}
-
-Now, we define the $\freorder_{∧}$ function in~\eqref{eq:reorder-and}
-to reorder nested conjunctions. This will help us in the end of this
-section to reorder conjunctive normal forms.
-
-\begin{mainlemma}
-  \label{lem:reorder-and}
-  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \freorder_{∧}~φ~ψ$, where
-    \begin{align}
-      \begin{split}
-      \label{eq:reorder-and}
-        &\freorder_{∧} : \Source \to \Target \to \Prop\\
-        &\freorder_{∧}~φ~ψ =
-        \begin{cases}
-          φ, &\text{ if }φ ≡ ψ;\\
-          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }ψ₁ ≡ \freorder_{∧}~φ~ψ₁;\\
-                   &\text{ and } ψ₂ ≡ \freorder_{∧}~φ~ψ₂;\\
-          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂;\\
-          \fconjunct~φ~ψ, &\text{ otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align}
-\end{mainlemma}
-
-\begin{myexamplenum}
-\begin{equation}
-\label{ex:reorder-example}
-\begin{aligned}
-\begin{array}{llll}
-  \freorder_{∧} &(p ∧ q ∧ r)   &(r ∧ q ∧ p)     ~&=~(r ∧ q ∧ p),\\
-  \freorder_{∧} &(p ∧ q ∧ r)   &(r ∧ r ∧ p)     ~&=~(r ∧ q ∧ p),\\
-  \freorder_{∧} &(p ∧ q ∧ r)   &(k ∧ q ∧ p)     ~&=~(p ∧ q ∧ r),\\
-  \freorder_{∧} &((p ∨ q) ∧ r) &((r ∧ (q ∨ p)) ~&=~((p ∨ q) ∧ r).
-\end{array}
-\end{aligned}
-\end{equation}
-\end{myexamplenum}
-
-In the last example in~\eqref{ex:reorder-example}, we could not build
-the conjunction $r ∧ (q ∨ p)$ since $p ∨ q$ is not syntactical equal
-to $q ∨ p$. We solve this issue in Lemma~\ref{lem:reorder-and-or} by
-using the $\fconjunctor$ function defined in~\eqref{eq:conjunct-or}.
-The purpose of this function consists of extracting a disjunction
-from a conjunction, but without matter the order of the inner disjunctions.
-
-\begin{mainlemma}
-  \label{lem:conjunct-or}
-  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \fconjunctor~φ~ψ$, where
-  \begin{equation}
-    \begin{split}
-    \label{eq:conjunct-or}
-      &\fconjunctor : \Source → \Target \to \Prop\\
-      &\fconjunctor~φ~ψ =
-      \begin{cases}
-        ψ, &\text{ if }φ ≡ ψ;\\
-        ψ, &\text{ if } ψ ≡ \freorder_{∨}~φ~ψ;\\
-        ψ, &\text{ if }ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \fconjunctor~φ~ψ₁,\\
-           &\text{ and } ψ₂ ≡ \freorder_{∨}~φ~ψ₂;\\
-        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunctor~φ₁~ψ;\\
-        ψ, &\text{ if }φ ≡ φ₁ ∧ φ₂,\ ψ ≡ \fconjunctor~φ₂~ψ;\\
-        φ, &\text{ otherwise.}
-      \end{cases}
-    \end{split}
-  \end{equation}
-\end{mainlemma}
-
-We are able now to reorder conjunctive normal forms using the
-$\freorder_{∧∨}$ function defined in~\eqref{eq:reorder-and-or}
-by using the previous lemma.
-
-\begin{mainlemma}
-  \label{lem:reorder-and-or}
-  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \freorder_{∧∨}~φ~ψ$, where
-   \begin{align}
-      \begin{split}
-      \label{eq:reorder-and-or}
-      &\freorder_{∧∨} : \Source \to \Target \to \Prop\\
-      &\freorder_{∧∨}~φ~ψ=
-        \begin{cases}
-          ψ, &\text{ if } φ ≡ ψ;\\
-          ψ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂,\ ψ₁ ≡ \freorder_{∧∨}~φ~ψ₁,\\
-             &\text{ and } ψ₂ ≡ \freorder_{∧∨}~φ~ψ₂;\\
-          φ, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂;\\
-          \fconjunctor~φ~ψ, &\text{ otherwise.}
-        \end{cases}
-      \end{split}
-  \end{align}
-\end{mainlemma}
-
-Now, we are ready to reconstruct the \resolve rule using
-Lemma~\ref{lem:reorder-and-or}. As we see in the following, the
-\resolve rule is the \Metis version of the resolution theorem. This
-rule takes into account, two propositions that contain a positive
-literal $ℓ$ and its negation $¬ ℓ$ respectively. Then, it produces the
-\emph{resolvent}, a disjunction of two propositions: the first
-proposition after removing the literal $ℓ$ and the second proposition
-after removing its negation $¬ ℓ$.
-
-The positive literal~$ℓ$ must occur in the formula from the first
-derivation and the negative literal~$¬ ℓ$ must occur in the formula
-from the second derivation, see the pattern of the \emph{resolve}
-rule in Fig.~\ref{fig:metis-inferences}.
 
@@
 
-\begin{myexamplenum}
-
-Continuing with the problem presented in
-Example~\ref{ex:resolve-tstp}, we can use Theorem \ref{thm:resolve} to derive $Γ~⊢~p~∨~q$.
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ p ∨ q ∨ r $}
-  \AxiomC{$Γ ⊢ ¬ r ∨ p ∨ q$}
-  \RightLabel{Theorem \ref{thm:resolve}}
-  \BinaryInfC{$Γ ⊢ \fresolve~(p ∨ q ∨ r)~(¬ r ∨ p ∨ q)~r~(p ∨ q)$}
-  \RightLabel{by (\ref{eq:resolve})}
-  \UnaryInfC{$Γ ⊢ \frsol~(\freorder_{∨}~(p ∨ q ∨ r)~(r ∨ (p ∨ q))~∧~\freorder_{∨}~(¬ r ∨ p ∨ q)~(¬ r ∨ (p ∨ q))$}
-  \RightLabel{by (\ref{eq:reorder-or})}
-  \UnaryInfC{$Γ ⊢ \frsol~((r ∨ (p ∨ q)) ∧ (¬ r ∨ (p ∨ q)))$}
-  \RightLabel{by (\ref{eq:rsol})}
-  \UnaryInfC{$Γ ⊢ p ∨ q$}
-  \end{bprooftree}
-\end{equation*}
-\end{myexamplenum}
-
 \end{document}

### 2018-02-23 pubs/itp-2018/sections/proof-reconstruction/simplify.tex
[ paper ] removed many examples and extra content.

\documentclass[../../main.tex]{subfiles}
\begin{document}

\subsubsection{Simplify.}
\label{sssec:simplify}

The \simplify rule is an inference that performs simplification of
tautologies in a list of derivations. This rule simplifies such a list
by transversing the list while applying Lemma~\ref{lem:canon-or},
Lemma~\ref{lem:canon-and}, among others theorems presented in the following.
The goal of this rule despites simplifying the list of derivations to a
new formula (often smaller than its input formulas), consists of finding
a contradiction.

We observe based on the analysis of different cases in the \TSTP
derivations that \simplify can be modeled by a function with three
arguments: two source formulas and the target formula.

Since the main purpose of the \simplify rule is simplification of
formulas, we have defined the $\freduce$ function to help removing
the negation of a given literal $ℓ$ from a input formula.

\begin{equation}
\label{def:remove-literal}
  \begin{aligned}
  &\hspace{.495mm}\freduce : \Prop → \Lit → \Prop\hspace*{3.5cm}\\
  &\begin{array}{lll}
\freduce &(φ₁~∧~φ₂) &ℓ~= \fsimplify_{∧}~(\freduce~φ₁~ℓ~∧~\freduce~φ₂~ℓ)\\
\freduce &(φ₁~∨~φ₂) &ℓ~= \fsimplify_{∨}~(\freduce~φ₁~ℓ~∨~\freduce~φ₂~ℓ)\\[2mm]
\freduce &φ &ℓ~=\begin{cases}
  ⊥,  &\text{ if }φ\text{ is a literal and }ℓ ≡ \fnnf(¬ φ);\\
  φ,  &\text{ otherwise.}
  \end{cases}
   \end{array}
  \end{aligned}
\end{equation}

\begin{mainlemma}
\label{lem:reduce-literal}
Let $ℓ$ be a literal and $φ : \Prop$. If $Γ ⊢ φ$ and $Γ ⊢ ℓ$ then
$Γ~⊢~\freduce~φ~ℓ$.
\end{mainlemma}

\begin{proof} This proof is by induction on the structure of $φ$.\\

∙~Case $φ ≡ φ₁ ∨ φ₂$.

\begin{center}
\begin{scprooftree}{1}
\AxiomC{$Γ , φ₁ ⊢ φ₁$}
\AxiomC{$Γ ⊢ ℓ$}
\RightLabel{weaken}
\UnaryInfC{$Γ , φ₁ ⊢ ℓ$}
\RightLabel{by~ind.~hyp.}
\BinaryInfC{$Γ , φ₁ ⊢ \freduce~φ₁~ℓ$}
\RightLabel{∨-intro₁}
\UnaryInfC{$Γ , φ₁ ⊢ \freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ$}
%
\AxiomC{$Γ , φ₂ ⊢ φ₂$}
\AxiomC{$Γ ⊢ ℓ$}
\RightLabel{weaken}
\UnaryInfC{$Γ , φ₂ ⊢ ℓ$}
\RightLabel{by~ind.~hyp.}
\BinaryInfC{$Γ , φ₂ ⊢ \freduce~φ₂~ℓ$}
\RightLabel{∨-intro₂}
\UnaryInfC{$Γ , φ₂ ⊢ \freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ$}
\LeftLabel{$(\mathcal{D})$\hspace{3mm}}
\RightLabel{∨-elim}
\BinaryInfC{$Γ , φ₁ ∨ φ₂ ⊢ \freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ$}
\RightLabel{⇒-intro}
\UnaryInfC{$Γ ⊢  φ₁ ∨ φ₂ ⇒ (\freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ)$}
\end{scprooftree}
\end{center}
\medskip

\def\defaultHypSeparation{\hskip.4in}
\begin{center}
\begin{scprooftree}{1}
\AxiomC{$\mathcal{D}$}
\RightLabel{⇒-elim}
\AxiomC{$Γ ⊢ φ₁ ∨ φ₂$}
\BinaryInfC{$Γ ⊢ \freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ$}
\RightLabel{Lemma~\ref{lem:canon-or}}
\UnaryInfC{$Γ ⊢ \fsimplify_{∨}~(\freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ)$}
\end{scprooftree}
\end{center}

\def\defaultHypSeparation{\hskip.2in}

∙ Otherwise use the same hypothesis $Γ ⊢ φ$.
\end{proof}

The \fsimplify function is defined in~\eqref{eq:simplify}. If some
input formula is equal to the target formula, we derive that formula.
If some formula is $⊥$, we derive the target formula by using the
⊥-elim inference rule.
Otherwise, we proceed by cases on the structure of the formula.
For example, when the second source formula is a literal, we
use the $\freduce$ function and Lemma~\ref{lem:reduce-literal}.

\begin{equation}
\label{eq:simplify}
  \begin{aligned}
  &\hspace{.495mm}\fsimplify : \Source → \Source → \Target → \Prop \hspace*{3.5cm}\\
  &\begin{array}{l}
  \fsimplify~φ₁~φ₂~ψ~=\\
  \hspace{3mm}\begin{cases}
  ψ, &\text{ if }φᵢ ≡ ⊥\text{ for some }i = 1, 2;\\
  ψ, &\text{ if }φᵢ ≡ ψ\text{ for some }i = 1, 2;\\
  \fsimplify_{∧}~(\fsimplify~φ₁~φ₂₁~ψ)~φ₂₂~ψ,
  &\text{ if }φ₂ ≡ φ₂₁ ∧ φ₂₂;\\
   \fsimplify_{∨}~(\fsimplify~φ₁~φ₂₁~ψ~∨~\fsimplify~φ₁~φ₂₂~ψ)
  &\text{ if }φ₂ ≡ φ₂₁ ∨ φ₂₂;\\
  \freduce~φ₁~φ₂, &\text{ if }φ₂\text{ is a literal};\\
  φ₁,  &\text{ otherwise.}
  \end{cases}
  \end{array}
  \end{aligned}
\end{equation}

\begin{mainlemma}
  \label{lem:binary-simplify}
  Let $ψ : \Target$. If $Γ ⊢ φ₁$ and $Γ ⊢ φ₂$ then
  $Γ ⊢ \fsimplify~φ₁~φ₂~ψ$.
\end{mainlemma}

\begin{proof}
This proof is by induction on the structure of $φ$. \\

∙~Case $φ₂ ≡ φ₂₁ ∨ φ₂₂$.

\def\defaultHypSeparation{\hskip.2in}

\begin{center}
\begin{scprooftree}{1}
\AxiomC{$Γ ⊢ φ₁$}
\RightLabel{weaken}
\UnaryInfC{$Γ , φ₂₁ ⊢ φ₁$}
\AxiomC{$Γ , φ₂₁ ⊢ φ₂₁$}
\RightLabel{by~ind.~hyp.}
\BinaryInfC{$Γ , φ₂₁ ⊢ \fsimplify~φ₁~φ₂₁~ψ$}
\LeftLabel{$(\mathcal{D}_{1})$\hspace{5mm}}
\RightLabel{∨-intro₁}
\UnaryInfC{$Γ , φ₂₁ ⊢ \fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₁~φ₂₁~ψ$}
\end{scprooftree}
\end{center}
\medskip
\begin{center}
\begin{scprooftree}{1}
\AxiomC{$Γ ⊢ φ₁$}
\RightLabel{weaken}
\UnaryInfC{$Γ , φ₂₂ ⊢ φ₁$}
\AxiomC{$Γ , φ₂₂ ⊢ φ₂₂$}
\RightLabel{by~ind.~hyp.}
\BinaryInfC{$Γ , φ₂₂ ⊢ \fsimplify~φ₁~φ₂₂~ψ$}
\LeftLabel{$(\mathcal{D}_{2})$\hspace{5mm}}
\RightLabel{∨-intro₂}
\UnaryInfC{$Γ , φ₂₂ ⊢ \fsimplify~φ₁~φ₂₂~ψ ∨ \fsimplify~φ₁~φ₂₂~ψ$}
\end{scprooftree}
\end{center}
\medskip
\begin{center}
\begin{scprooftree}{1}
\AxiomC{$\mathcal{D}_{1}$}
% \UnaryInfC{$Γ , φ₂₁ ⊢ \fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₁~φ₂₁~ψ$}
\AxiomC{$\mathcal{D}_{2}$}
% \UnaryInfC{$Γ , φ₂₂ ⊢ \fsimplify~φ₁~φ₂₂~ψ ∨ \fsimplify~φ₁~φ₂₂~ψ$}
\RightLabel{∨-elim}
\BinaryInfC{$Γ , φ₂₁ ∨ φ₂₂ ⊢ \fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₁~φ₂₂~ψ$}
\RightLabel{⇒-intro}
\LeftLabel{$(\mathcal{D}_{3})$\hspace{5mm}}
\UnaryInfC{$Γ ⊢  φ₂₁ ∨ φ₂₂ ⇒ (\fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₁~φ₂₂~ψ)$}
\end{scprooftree}
\end{center}

\medskip
\begin{center}
\begin{scprooftree}{1}
\AxiomC{$\mathcal{D}_{3}$}
\UnaryInfC{$Γ ⊢  φ₂₁ ∨ φ₂₂ ⇒ (\fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₁~φ₂₂~ψ)$}
\RightLabel{⇒-elim}
\AxiomC{$Γ ⊢ φ₂₁ ∨ φ₂₂$}
\BinaryInfC{$Γ ⊢ \fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₂~φ₂₂~ψ$}
\RightLabel{Lemma~\ref{lem:canon-or}}
\UnaryInfC{$Γ ⊢ \fsimplify_{∨}~(\fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₂~φ₂₂~ψ)$}
\end{scprooftree}
\end{center}
\medskip

∙~Case $φ₂$ is a literal. Use Lemma~\ref{lem:reduce-literal} with $φ = φ₁$ and
$ℓ = φ₂$.
\end{proof}

\begin{mainth}
  \label{thm:simplify}
  Let $ψ : \Target$. Let $φᵢ : \Source$ such that $Γ ⊢ φᵢ$ for
  $i = 1, \cdots, n$ and $n \geq 2$.
  Then $Γ ⊢ \fsimplify~γ_{n-1}~φ_{n}~ψ$ where
  $γ₁ = φ₁$, and $γᵢ ≡ \fsimplify~γ_{i-1}~φᵢ~ψ$.
\end{mainth}

\begin{proof} We prove this theorem by induction on $n$.\\
∙~Case $n = 2$. Use Lemma~\ref{lem:binary-simplify}.\\
∙~Case $n > 2$. Suppose this theorem is valid for $n$, that is,
for $i = 1, \cdots, n$, $Γ ⊢ \fsimplify~γ_{n-1}~φ_{n}~ψ$. Let us prove it for $n+1$.\\

\begin{equation*}
\begin{bprooftree}
\AxiomC{$Γ ⊢ \fsimplify~γ_{n-1}~φ_{n}~ψ$}
\AxiomC{$γ_{n} ≡ \fsimplify~γ_{n-1}~φ_{n}~ψ$}
\RightLabel{subst}
\BinaryInfC{$Γ ⊢ γ_{n}$}
\AxiomC{$Γ ⊢ φ_{n+1}$}
\RightLabel{by~ind.~hyp.}
\BinaryInfC{$Γ ⊢ \fsimplify~γ_{n}~φ_{n+1}~ψ$}
\end{bprooftree}
\end{equation*}
\end{proof}

\begin{myremark}

Besides the fact that $\List~\Prop~\to~\Prop$ is the type that mostly
fit with the \simplify rule, we choose a different option. In the
translation from \TSTP to \Agda, we take the list of derivations and
we apply the rule by using a left folding (the \verb!foldl! function
in functional programming) with the $\fsimplify$ function over the
list of $φ₁, φ₂, \cdots, φₙ$. This design decision avoids us to define a new theorem
type to support \List~\Prop type in the premise side.
\end{myremark}

\begin{myexamplenum}
Let us review the following \TSTP excerpt where \simplify was used twice.

\begin{verbatim}
  fof(n₀, (¬ p ∨ q) ∧ ¬ r ∧ ¬ q ∧ (p ∨ (¬ s ∨ r)), ...
  fof(n₁, p ∨ (¬ s ∨ r), inf(conjunct, n₀)).
  fof(n₂, ¬ p ∨ q, inf(conjunct, n₀)).
  fof(n₃, ¬ q, inf(conjunct, n₀)).
  fof(n₄, ¬ p, inf(simplify, [n₂, n₃])).
  fof(n₅, ¬ r, inf(conjunct, n₀)).
  fof(n₆, ⊥, inf(simplify, [n₁, n₄, n₅])).
\end{verbatim}

\begin{enumerate}
\item The \simplify rule derives $¬ p$ in \verb!n₄!
from \verb!n₂! and \verb!n₃! derivations.

$$\fsimplify~(¬ p ∨ q)~(¬ q)~(¬ p) = ¬ p.$$
% \begin{verbatim}
% fof(norm2, ¬ p ∨ q, inf(conjunct, [norm0])).
% fof(norm3, ¬ q, inf(conjunct, [norm0])).
% fof(norm4, ¬ p, inf(simplify, [norm2, norm3])).
% \end{verbatim}
\item We use Theorem~\ref{thm:simplify} to derive ⊥ in \verb!n₆!, the
following is a proof.

\begin{equation*}
\begin{bprooftree}
\AxiomC{$Γ ⊢ p ∨ (¬ s ∧ r)$}
\AxiomC{$Γ ⊢ ¬ p$}
\RightLabel{Theorem~\ref{thm:simplify}}
\BinaryInfC{$Γ ⊢ ¬ s ∧ r$}
\AxiomC{$Γ ⊢ ¬ r$}
\RightLabel{Theorem~\ref{thm:simplify}}
\BinaryInfC{$Γ ⊢ ⊥$}
\end{bprooftree}
\end{equation*}

% \begin{verbatim}
% fof(n1, g ∨ (¬ s ∧ r), inf(conjunct, [n0])).
% fof(n4, ¬ p, inf(simplify, [n2, n3])).
% fof(n5, ¬ r, inf(conjunct, [n0])).
% fof(n6, ⊥, inf(simplify, [n1, n4, n5])).
% \end{verbatim}
\end{enumerate}
\end{myexamplenum}

% subsubsection simplify (end)
% -------------------------------------------------------------------

\end{document}

### 2018-02-23 pubs/itp-2018/sections/proof-reconstruction/strip.tex
[ paper ] removed many examples and extra content.

--- 2017-12-19 paper/sections/proof-reconstruction/strip.tex
@@
 \begin{itemize}
-\item Case $φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)$.
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \fuh_1~(φ₁ ⇒ (φ₂ ⇒ φ₃))~(\suc~n)$}
-  \RightLabel{by~(\ref{eq:uh-structured})}
-  \UnaryInfC{$Γ ⊢ \fuh_1~((φ₁ ∧ φ₂) ⇒ φ₃)~n$}
-  \RightLabel{by~ind.~hyp.}
-  \UnaryInfC{Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃}
-  \RightLabel{∧⇒\textsf{-to-}⇒⇒}
-  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃)}
-  \end{bprooftree}
-\end{equation*}
-using the following theorem proved in~\cite{AgdaProp},
-  \begin{equation*}
-  \texttt{∧⇒\textsf{-to-}⇒⇒}\ :\  Γ ⊢ (φ₁ ∧ φ₂) ⇒ φ₃ → Γ ⊢ φ₁ ⇒ (φ₂ ⇒ φ₃).
-  \end{equation*}
-
 \item Case $φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)$.
@@
 
-∙~Case $φ ≡ ¬ (¬ φ₁) $.
-\begin{equation*}
-  \begin{bprooftree}
- \AxiomC{$Γ ⊢ \fstrip₁~(¬(¬φ₁))~(\suc~n)$}
-  \RightLabel{by~(\ref{eq:strip-fixed})}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~φ₁~n)$}
-  \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ \fstrip₁~φ₁~n$}
-  \RightLabel{by~ind.~hyp.}
-  \UnaryInfC{$Γ ⊢ φ₁$}
-  \end{bprooftree}
-\end{equation*}
-
-∙~Case $φ ≡ φ₁ ∧ φ₂$. We prove $Γ ⊢ φ₁$ and $Γ ⊢ φ₂$.
-From the conjunction of φ₁ and φ₂, the expected result follows.
-
-\begin{equation*}
-(\mathcal{D})\hspace{3mm}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ \fstrip₁~(φ₁ ∧ φ₂)~(\suc\,\textit{n})$}
-  \RightLabel{by~(\ref{eq:strip-fixed})}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)$}
-  \RightLabel{∧-proj₁}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~φ₁~n)$}
-  \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ \fstrip₁~φ₁~n$}
-  \RightLabel{by~ind.~hyp.}
-  \UnaryInfC{$Γ ⊢ φ₁$}
-    \end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\mathcal{D}$}
-  \UnaryInfC{Γ ⊢ φ₁}
-  \AxiomC{$Γ ⊢ \fstrip₁~(φ₁ ∧ φ₂)~(\suc~n)$}
-  \RightLabel{by~(\ref{eq:strip-fixed})}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~φ₁~n) ∧ \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)$}
-  \RightLabel{$∧$-proj$₂$}
-  \UnaryInfC{$Γ ⊢ \fuh~(φ₁ ⇒ \fstrip₁~φ₂~n)$}
-  \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ φ₁ ⇒ \fstrip₁~φ₂~n$}
-  \RightLabel{$⇒$-elim}
-  \BinaryInfC{$Γ ⊢ \fstrip₁~φ₂~n$}
-  \RightLabel{by~ind.~hyp.}
-  \UnaryInfC{$Γ ⊢ φ₂$}
-  \end{bprooftree}
-\end{equation*}
-
 ∙~Case $φ ≡ ¬ (φ₁ ∨ φ₂)$.
@@
 by using the \negate rule after the \strip inference application
-that introduce such a subgoal.
-
-\begin{myexamplenum}
-In the following \TSTP derivation, note that the three subgoals
-\verb!s₁!, \verb!s₂! and \verb!s₃! are assumed by the \negate
-rule in \verb!neg₁!, \verb!neg₂! and  \verb!neg₃! respectively.
-
-\begin{verbatim}
-  fof(goal, conjecture, p ∧ r ∧ q).
-  fof(s₁, p, inf(strip, goal)).
-  fof(s₂, p ⇒ r, inf(strip, goal)).
-  fof(s₃, (p ∧ r) ⇒ q, inf(strip, goal)).
-  fof(neg₁, ¬ p, inf(negate, s₁)).
-  ...
-  fof(neg₂, ¬ (p ⇒ r), inf(negate, s₂)).
-  ...
-  fof(neg₃, ¬ ((p ∧ r) ⇒ q), inf(negate, s₃)).
-\end{verbatim}
-\end{myexamplenum}
+that introduces such a subgoal.
 

### 2018-02-23 pubs/itp-2018/sections/proof-reconstruction/strip.tex
[ paper ] all proofs have been removed.

@@
 \end{mainlemma}
-
-\begin{proof}
-The proof is by induction on the cases defined by the outcome of the
-$\fuh_{1}$ function.
-\begin{itemize}
-  \item If $n = 0$, by definition in~\eqref{eq:uh-structured}
-        we conclude $Γ ⊢ φ$.
-  \item For $n \geq 1$, we use induction on the structure of the first
-        argument.
-\vskip 2mm
-\begin{itemize}
-\item Case $φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)$.
-\begin{equation*}
-  (\mathcal{D}_1)
-  \begin{bprooftree}
-    \AxiomC{$Γ ⊢ \fuh_1~(φ₁ ⇒ (φ₂ ∧ φ₃))~(\suc~n)$}
-    \RightLabel{by~(\ref{eq:uh-structured})}
-    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n ∧ \fuh_1~(φ₁ ⇒ φ₃)~n$}
-    \RightLabel{∧-proj₁}
-    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n$}
-    \RightLabel{by~ind.~hyp.}
-    \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₂$}
-  \end{bprooftree}
-\end{equation*}
-
-\begin{equation*}
-  (\mathcal{D}_2)
-  \begin{bprooftree}
-    \AxiomC{$Γ ⊢ \fuh_1~(φ₁ ⇒ (φ₂ ∧ φ₃))~(\suc~n)$}
-    \RightLabel{by~(\ref{eq:uh-structured})}
-    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₂)~n ∧ \fuh_1~(φ₁ ⇒ φ₃)~n$}
-    \RightLabel{∧-proj₂}
-    \UnaryInfC{$Γ ⊢ \fuh_1~(φ₁ ⇒ φ₃)~n$}
-    \RightLabel{by~ind.~hyp.}
-    \UnaryInfC{$Γ ⊢ φ₁ ⇒ φ₃$}
-    \end{bprooftree}
-\end{equation*}
-
-Now, using \texttt{⇒∧⇒\textsf{-to-}⇒∧} theorem from~\cite{AgdaProp},
-\begin{equation*}
-  \texttt{⇒∧⇒\textsf{-to-}⇒∧}\ :\ Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃) → Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃),
-\end{equation*}
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\mathcal{D}_1$}
-  \AxiomC{$\mathcal{D}_2$}
-  \RightLabel{∧-intro}
-  \BinaryInfC{$Γ ⊢ (φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$}
-  \RightLabel{\tt ⇒∧⇒\textsf{-to-}⇒∧}
-  \UnaryInfC{Γ ⊢ φ₁ ⇒ (φ₂ ∧ φ₃)}
-  \end{bprooftree}
-\end{equation*}
-\item Other cases are proved in a similar way.
-\end{itemize}
-\end{itemize}
-\end{proof}
 
@@
 
-\begin{proof}
-The proof is by induction on the structure of the
-formula~$φ$ by following the equations in~\eqref{eq:strip-fixed}.
-We present a straightforward case with double negation, the case for
-conjunctions, and last, the case for a negated disjunction.
-We refer the reader to~\cite{AgdaMetis} for the complete proof in \Agda.
-
-∙~Case $φ ≡ ¬ (φ₁ ∨ φ₂)$.
-We prove $Γ ⊢ ¬ φ₁$ and $Γ ⊢ ¬ φ₂$.
-From the conjunction of $¬ φ₁$ and $¬ φ₂$ by applying De Morgan Law
-and the result follows.
-
-\begin{equation*}
-(\mathcal{D})\hspace{3mm}
-\begin{bprooftree}
-\AxiomC{$Γ ⊢ \fstrip₁~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
-\RightLabel{by~(\ref{eq:strip-fixed})}
-\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~((¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n)$}
-\RightLabel{∧-proj₁}
-\UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n)$}
-\RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-\UnaryInfC{$Γ ⊢ \fstrip₁~(¬ φ₁)~n$}
-\RightLabel{by~ind.~hyp.}
-  \UnaryInfC{$Γ ⊢ ¬φ₁$}
-\end{bprooftree}
-\end{equation*}
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$\mathcal{D}$}
-  \UnaryInfC{$Γ ⊢ ¬ φ₁$}
-  \AxiomC{$Γ ⊢ \fstrip₁~(¬ (φ₁ ∨ φ₂))~(\suc~n)$}
-  \RightLabel{by~(\ref{eq:strip-fixed})}
-  \UnaryInfC{$Γ ⊢ \fuh~(\fstrip₁~(¬ φ₁)~n) ∧ \fuh~((¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n)$}
-  \RightLabel{∧-proj₂}
-  \UnaryInfC{$Γ ⊢ \fuh~((¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n)$}
-  \RightLabel{Lemma~\ref{lem:inv-uh-lem}}
-  \UnaryInfC{$Γ ⊢ (¬ φ₁) ⇒ \fstrip₁~(¬ φ₂)~n$}
-  \RightLabel{⇒-elim}
-  \BinaryInfC{$Γ ⊢ \fstrip₁~(¬ φ₂)~n$}
-  \RightLabel{by~ind.~hyp.}
-  \UnaryInfC{$Γ ⊢ ¬ φ₂$}
-  \end{bprooftree}
-\end{equation*}
-∙~  Other cases are proved in a similar way, see Appendix~\ref{app:strip-proof-case}.
-
-\end{proof} % the proof continue...
-
 The following theorem is convenient to substitute equals by equals in
@@
 \end{mainth}
-
-\begin{proof}
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$ Γ ⊢ s_1 $}
-  \AxiomC{$ Γ ⊢ s_2 $}
-  \RightLabel{∧-intro}
-  \BinaryInfC{$Γ ⊢ s_1\wedge s_2$}
-  \AxiomC{$\fstrip₁~φ~n ≡ s_1\wedge s_2 $}
-  \RightLabel{\fsubst}
-  \BinaryInfC{$Γ ⊢ \fstrip₁~φ~n$}
-  \RightLabel{Lemma~\ref{lem:lem-inv-strip}}
-  \UnaryInfC{$Γ ⊢ φ$}
-\end{bprooftree}
-\end{equation*}
-\end{proof}
-
 % -------------------------------------------------------------------

### 2018-03-13 pubs/itp-2018/sections/metis-language-and-proofs.tex
Complete first revision to section about Metis

@@
 
-\section{Metis: Language and Proofs}
+\section{Metis Prover}
 \label{sec:metis-language-and-proofs}
@@
 \end{equation*}
-\caption{Propositional logic inference rules of the \texttt{Metis} prover.}
+\caption{\Metis inference rules for propositional logic.}
 \label{fig:metis-inferences}
@@
 The \TPTP syntax\footnote{See the complete syntax grammar
-at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} describes a
-well-defined grammar to handle annotated formulas with the following form:
+at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} is a
+well-defined grammar to handle annotated formulas with the form:
+\begin{verbatim}
+  language(name, role, formula).
+\end{verbatim}
+where the \name{language} can be \name{fof} or \name{cnf} and the \name{name} serves
+to identify the formula within the problem. Each
+annotated formula also assumes a \name{role}. Some roles frequently used are \name{axiom},
+\name{conjecture}, \name{definition}, \name{plain} and \name{hypothesis} but the reader
+can find the full list in~\cite{sutcliffe2009}.
 
-\begin{verbatim}
-  language(name, role, formula).,
-\end{verbatim}
-
-where the \name{language} can be \name{fof} or \name{cnf}. The
-\name{name} serves to identify the formula within the problem. Each
-formula assumes a \name{role}, this could be an \name{axiom},
-\name{conjecture}, \name{definition}, \name{plain} or an
-\name{hypothesis}.
-
-The formulas include the constants
-\verb!$true! and \verb!$false!, the negation unary
+On the other hand, the well-written formulas can include 
+the constants \verb!$true! and \verb!$false!, the negation unary
 operator~(\verb!~!), and the binary connectives
@@
 ($⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$) respectively.
+Finally, to refer us to propositional variables,
+we can just write a word using letters and numbers.
+%http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html#atomic_word
 
@@
 
-The \TSTP language is an output language for derivations of
-ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}.
-A \TSTP derivation is a directed acyclic graph, a proof tree,
-where each leaf is a formula from the \TPTP input. A node is a formula
-inferred from the parent formulas. The root is the final derived formula,
-such a derivation is a list of annotated formulas with the following form:
+The \TSTP language is an output language for derivations used by 
+\Metis and other ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}.
+A \TSTP  derivation generated by \Metis encodes a natural
+deduction proof using only as valid deduction steps the inference rules
+in Fig.~\ref{tab:agda-metis-table}. 
+These derivations are directed acyclic graphs, trees of refutations.
+Each node stands for an application of an inference rule to the formulas
+in the parent nodes. The leaves in the tree represent formulas in the given
+\TPTP input. Each node is labeled with a name of its inference rule (\eg, \canonicalize).
+Each edge in the tree links a premise with one conclusion.
+
+Since \Metis attempts to prove conjectures by refutation, and the root
+is the final derived formula in these proof trees,  we have at their
+roots the conclusion $⊥$. Such derivations are a list of annotated
+formulas with the form:
 
@@
 
-The \name{source} field is an inference record with the following
-pattern:
+The new field regarding the \TPTP syntax is the \name{source} field
+that mainly intends to record the inference rule of the deduction step.
+This field has the following pattern:
 
@@
 
-The \name{rule} in the line above stands for the inference name;
-the other fields are supporting arguments or useful information to
-apply the reasoning step, and list the parents nodes.
+We have the \name{rule} field with the inference name, another field
+including supporting arguments to apply the reasoning step, and the
+last one field with a list its parents nodes.
 
-\begin{notation}
-
-We adopt a customized \TSTP syntax to keep as short as possible the
-\Metis derivations for increasing the readability of this paper.
+For increasing the readability of this paper, we are not presenting
+these \TSTP derivations using the above description. Instead of it, we
+have adopted a customized \TSTP syntax to keep as short as possible
+the \Metis derivations. For instance,  we shortened some keywords,
+removed unnecessary arguments, and replaced some symbols. The list of
+all customizations is in Appendix~\ref{app:tstp-syntax}.
 
@@
 
-Let us consider the following \TSTP derivation using
-the customized \TSTP syntax (see the original \TSTP derivation and
-customizations in Appendix~\ref{app:tstp-syntax}).
+Let us consider the following \TSTP derivation generated by \Metis after using
+the customized \TSTP syntax proposed for the theorem:
 
+\begin{equation}
+(p \Rightarrow q) \wedge (q \Rightarrow p) ⊢ (p \vee q) \Rightarrow (p \wedge q).
+\end{equation}
+
+% this tstp example should be used to explain the reconstruction.
 \begin{verbatim}
-  fof(premise, axiom, p).
-  fof(goal, conjecture, p).
-  fof(s₀, inf(strip, goal)).
-  fof(neg₀, ¬ p, inf(negate, s₀)).
-  fof(n₀, ¬ p, inf(canonicalize, neg₀)).
-  fof(n₁, p, inf(canonicalize, premise)).
-  fof(n₂, ⊥, inf(simplify, [n₀, n₁]))
-  cnf(r₀, ⊥, inf(canonicalize, n₂)).
+  fof(premise, axiom, (p ⇒ q) ∧ (q ⇒ p)).
+  fof(goal, conjecture, (p ∨ q) ⇒ (p ∧ q)).
+  fof(s₀, (p ∨ q) ⇒ p, inf(strip, goal)).
+  fof(s₁, ((p ∨ q) ∧ p) ⇒ q, inf(strip, goal)).
+  fof(neg₀, ¬ ((p ∨ q) ⇒ p), inf(negate, s₀)).
+  fof(n₀₀, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).
+  fof(n₀₁, ¬ q ∨ p, inf(conjunct, n₀₀)).
+  fof(n₀₂, ¬ p ∧ (p ∨ q), inf(canonicalize, neg₀)).
+  fof(n₀₃, p ∨ q, inf(conjunct, n₀₂)).
+  fof(n₀₄, ¬ p, inf(conjunct, n₀₂)).
+  fof(n₀₅, q, inf(simplify, [n₀₃, n₀₄])).
+  cnf(r₀₀, ¬ q ∨ p, inf(canonicalize, n₀₁)).
+  cnf(r₀₁, q, inf(canonicalize, n₀₅)).
+  cnf(r₀₂, p, inf(resolve, q, [r₀₁, r₀₀])).
+  cnf(r₀₃, ¬ p, inf(canonicalize, n₀₄)).
+  cnf(r₀₄, ⊥, inf(resolve, p, [r₀₂, r₀₃])).
+  fof(neg₁, ¬ ((p ∨ q) ∧ p) ⇒ q), inf(negate, s₁)).
+  fof(n₁₀, ¬ q ∧ p ∧ (p ∨ q), inf(canonicalize, neg₁)).
+  fof(n₁₁, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).
+  fof(n₁₂, ¬ p ∨ q, inf(conjunct, n₁₁)).
+  fof(n₁₃, ⊥, inf(simplify,[n₁₀, n₁₂])).
+  cnf(r₁₀, ⊥, inf(canonicalize, n₁₃)).
 \end{verbatim}
@@
 \end{myexamplenum}
-\end{notation}
 
 % -------------------------------------------------------------------
-
-\subsection{Derivations}
-\label{ssec:metis-proofs}
-
-A derivation generated by \Metis encodes a natural
-deduction proof. With the inference rules in
-Fig.~\ref{tab:agda-metis-table}
-as the only valid deduction steps, \Metis
-attempts to prove conjectures by refutation (\ie,
-\emph{falsium} in the root of the \TSTP derivation).
-
-These derivations are directed acyclic graphs, trees of refutations.
-Each node stands for an application of an inference rule and the
-leaves in the tree represent formulas in the given problem. Each node
-is labeled with a name of the inference rule (\eg, \canonicalize).
-Each edge links a premise with one conclusion. The proof graphs have
-at their root the conclusion $⊥$, since \Metis derivations are
-refutations.
 
@@
 
-We first present the \strip inference rule since it is the rule that appears
-first after each conjecture. The other rules are sorted mainly follow their
+We first present the reconstruction of the \strip inference rule and its
+description since it is the rule that appears
+first after each conjecture in \TSTP derivations. The other rules are sorted mainly follow their
 level of complexity of their definitions and the formalization presented in

### 2018-03-14 pubs/itp-2018/sections/proof-reconstruction.tex
ITP 2018: Initial commit.
Review section 4.2

--- 2017-12-18 paper/sections/proof-reconstruction.tex
@@
 
-In this section, we describe one approach to reconstruct
+In this section, we describe our approach to reconstruct
 propositional proofs. This reconstruction is a translation
@@
 
-With the \TSTP derivation from Step~2, we process the derivation with the
+With a \TSTP derivation file, we process the derivation with the
 \Athena translator tool.
@@
 since this rule  is the only one that closely follows the \Metis
-source code.
-
-To reconstruct the other rules, we use for their formalization
-a pattern in their description and definition,
-see Example~\ref{ex:inference-rule-pattern}.
+source code. To reconstruct the other rules, we use a pattern for their
+formalization showed in Example~\ref{ex:inference-rule-pattern}.
 
@@
   reconstruct the rule and formally implemented in~\cite{AgdaMetis}.
-  To increase the readability of our formal descriptions in
-  functions and theorems, we adopt
-  the convention to use \Source and \Target as synonyms of the \Prop
+  To increase the readability for functions and theorems, we use
+  the convention \Source and \Target as synonyms of the \Prop
   type. The \Source type in the reconstructed rule definition refers
@@
 \begin{equation*}
-  \text{If }Γ ⊢ φ \text{ then }Γ ⊢ \fun{metisRule}~φ~ψ\enspace.
+  \text{If }Γ ⊢ φ \text{ then }Γ ⊢ \fun{metisRule}~φ~ψ.
 \end{equation*}

### 2018-03-14 pubs/itp-2018/sections/proof-reconstruction.tex
Review introduction Section 4

@@
 
-In this section, we describe our approach to reconstruct
-propositional proofs. This reconstruction is a translation
-process from a source system to the target system.
-In our case, the system of origin, the automatic theorem prover, is
-\Metis; the target system is a proof-assistant, \Agda. We choose
-\Agda, but another proof-assistant with the same support of type
-theory and inductive types could be used.
+In this section, we describe our approach to reconstruct proofs from
+\CPL derivations generated by \Metis. This reconstruction consists of
+a translation from a source system (\Metis) to the target system
+(\Agda). The system of origin is the automatic theorem prover and the
+target system is the proof-assistant. We choose \Agda but another
+proof-assistant with the same support of type theory and inductive
+types could be used \eg \Coq.
 

### 2018-03-27 pubs/itp-2018/sections/metis-language-and-proofs.tex
Improve many parts in the text.
Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

@@
 annotated formula also assumes a \name{role}. Some roles frequently used are \name{axiom},
-\name{conjecture}, \name{definition}, \name{plain} and \name{hypothesis} but the reader
-can find the full list in~\cite{sutcliffe2009}.
+\name{conjecture}, \name{definition}, \name{plain} and \name{hypothesis}. The reader
+can find the complete list in~\cite{sutcliffe2009}.
 
-On the other hand, the well-written formulas can include 
+In the last field of the annotated formula we found the \texttt{formula},
+a well-written expression using the
 the constants \verb!$true! and \verb!$false!, the negation unary
 operator~(\verb!~!), and the binary connectives
-(\verb!&!, \verb!|!, \verb!=>!) to represent
+(\verb!&!, \verb!|!, \verb!=>!) that represent
 ($⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$) respectively.
-Finally, to refer us to propositional variables,
-we can just write a word using letters and numbers.
+To refer us to propositional variables, we can use words composing by letters and numbers.
 %http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html#atomic_word
@@
 that mainly intends to record the inference rule of the deduction step.
-This field has the following pattern:
+This field has the pattern
 
@@
 
-We have the \name{rule} field with the inference name, another field
-including supporting arguments to apply the reasoning step, and the
-last one field with a list its parents nodes.
+where the \name{rule} is the inference name, the next field
+includes supporting arguments to apply the reasoning step, and the
+last field is a list of the parents nodes.
 
@@
 the \Metis derivations. For instance,  we shortened some keywords,
-removed unnecessary arguments, and replaced some symbols. The list of
-all customizations is in Appendix~\ref{app:tstp-syntax}.
+removed unnecessary arguments, and replaced some symbols.
+The complete description of these customizations are showed in Appendix~\ref{app:tstp-syntax}.
 
@@
 \label{fig:metis-example-tree}
-
-Let us consider the following \TSTP derivation generated by \Metis after using
-the customized \TSTP syntax proposed for the theorem:
+We show in Fig.~\ref{complete-metis-example} the customized version
+of the \Metis derivation of the theorem~\eqref{eq:complete-example-problem}.
+This derivation will be used in Section~\ref{sec:proof-reconstruction} to
+present the proof-reconstruction process.
 
 \begin{equation}
-(p \Rightarrow q) \wedge (q \Rightarrow p) ⊢ (p \vee q) \Rightarrow (p \wedge q).
+\label{eq:complete-example-problem}
+(p \Rightarrow q) \wedge (q \Rightarrow p) ⊢ (p \vee q) \Rightarrow (p \wedge q)
 \end{equation}
 
-% this tstp example should be used to explain the reconstruction.
-\begin{verbatim}
-  fof(premise, axiom, (p ⇒ q) ∧ (q ⇒ p)).
-  fof(goal, conjecture, (p ∨ q) ⇒ (p ∧ q)).
-  fof(s₀, (p ∨ q) ⇒ p, inf(strip, goal)).
-  fof(s₁, ((p ∨ q) ∧ p) ⇒ q, inf(strip, goal)).
-  fof(neg₀, ¬ ((p ∨ q) ⇒ p), inf(negate, s₀)).
-  fof(n₀₀, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).
-  fof(n₀₁, ¬ q ∨ p, inf(conjunct, n₀₀)).
-  fof(n₀₂, ¬ p ∧ (p ∨ q), inf(canonicalize, neg₀)).
-  fof(n₀₃, p ∨ q, inf(conjunct, n₀₂)).
-  fof(n₀₄, ¬ p, inf(conjunct, n₀₂)).
-  fof(n₀₅, q, inf(simplify, [n₀₃, n₀₄])).
-  cnf(r₀₀, ¬ q ∨ p, inf(canonicalize, n₀₁)).
-  cnf(r₀₁, q, inf(canonicalize, n₀₅)).
-  cnf(r₀₂, p, inf(resolve, q, [r₀₁, r₀₀])).
-  cnf(r₀₃, ¬ p, inf(canonicalize, n₀₄)).
-  cnf(r₀₄, ⊥, inf(resolve, p, [r₀₂, r₀₃])).
-  fof(neg₁, ¬ ((p ∨ q) ∧ p) ⇒ q), inf(negate, s₁)).
-  fof(n₁₀, ¬ q ∧ p ∧ (p ∨ q), inf(canonicalize, neg₁)).
-  fof(n₁₁, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).
-  fof(n₁₂, ¬ p ∨ q, inf(conjunct, n₁₁)).
-  fof(n₁₃, ⊥, inf(simplify,[n₁₀, n₁₂])).
-  cnf(r₁₀, ⊥, inf(canonicalize, n₁₃)).
-\end{verbatim}
+\begin{figure}
+\begin{Verbatim}[commandchars=\\\{\}, numbers=left,xleftmargin=5mm]
+fof(premise, axiom, (p ⇒ q) ∧ (q ⇒ p)).  \label{line1}
+fof(goal, conjecture, (p ∨ q) ⇒ (p ∧ q)).  \label{line2}
+fof(s₀, (p ∨ q) ⇒ p, inf(strip, goal)).  \label{line3}
+fof(s₁, ((p ∨ q) ∧ p) ⇒ q, inf(strip, goal)).  \label{line4}
+fof(neg₀, ¬ ((p ∨ q) ⇒ p), inf(negate, s₀)).  \label{line5}
+fof(n₀₀, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).  \label{line6}
+fof(n₀₁, ¬ q ∨ p, inf(conjunct, n₀₀)).  \label{line7}
+fof(n₀₂, ¬ p ∧ (p ∨ q), inf(canonicalize, neg₀)).  \label{line8}
+fof(n₀₃, p ∨ q, inf(conjunct, n₀₂)).  \label{line9}
+fof(n₀₄, ¬ p, inf(conjunct, n₀₂)).  \label{line10}
+fof(n₀₅, q, inf(simplify, [n₀₃, n₀₄])).  \label{line11}
+cnf(r₀₀, ¬ q ∨ p, inf(canonicalize, n₀₁)).  \label{line12}
+cnf(r₀₁, q, inf(canonicalize, n₀₅)).  \label{line13}
+cnf(r₀₂, p, inf(resolve, q, [r₀₁, r₀₀])).  \label{line14}
+cnf(r₀₃, ¬ p, inf(canonicalize, n₀₄)).  \label{line15}
+cnf(r₀₄, ⊥, inf(resolve, p, [r₀₂, r₀₃])).  \label{line16}
+fof(neg₁, ¬ ((p ∨ q) ∧ p) ⇒ q, inf(negate, s₁)).  \label{line17}
+fof(n₁₀, ¬ q ∧ p ∧ (p ∨ q), inf(canonicalize, neg₁)).  \label{line18}
+fof(n₁₁, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).  \label{line19}
+fof(n₁₂, ¬ p ∨ q, inf(conjunct, n₁₁)).  \label{line20}
+fof(n₁₃, ⊥, inf(simplify,[n₁₀, n₁₂])).  \label{line21}
+cnf(r₁₀, ⊥, inf(canonicalize, n₁₃)).  \label{line22}
+\end{Verbatim}
+\caption{Customized \Metis \TSTP derivation of the theorem in~\eqref{eq:complete-example-problem}.}
+\label{complete-metis-example}
+\end{figure}
 
@@
 for propositional logic in Table~\ref{tab:agda-metis-table}. We reconstruct
-these rules in Section~\ref{sec:proof-reconstruction}. The reader may notice
-that the inference rules presented in Fig~\ref{fig:metis-inferences} diverge
-from the rules in aforementioned table. The former rules are implemented by the
-latter rules in the \TSTP derivations.
-For instance, as far as we know, in \TSTP
-derivations,  the \emph{axiom} rule is implemented by the rules
+these rules in Section~\ref{sec:proof-reconstruction} following the same order
+of this table.
+
+In this table, \strip is the first inference rule since is the first
+one in appearing in the \TSTP derivations. The other rules are sorted
+by a mix between their level of complexity of their main purpose and
+their dependency with the reconstruction of other rules. For
+instance, the \simplify rule and the \clausify rule need theorems
+developed for the reconstruction of the \canonicalize rule. The
+\canonicalize rule depends on the \resolve reconstruction which
+depends on the reconstruction of the \conjunct rule.
+
+An alert reader could also notice that the inference rules presented in
+Fig.~\ref{fig:metis-inferences} diverge from the rules in
+aforementioned table. The former rules are implemented by the latter
+rules in the \TSTP derivations. For instance, as far as we know, in
+\TSTP derivations,  the \emph{axiom} rule is implemented by the rules
 \canonicalize, \clausify, \conjunct, and \simplify.
-
-We first present the reconstruction of the \strip inference rule and its
-description since it is the rule that appears
-first after each conjecture in \TSTP derivations. The other rules are sorted mainly follow their
-level of complexity of their definitions and the formalization presented in
-Section~\ref{ssec:emulating-inferences}. Some inference rules depend on the
-formalizations of other rules. For instance, the \simplify rule and the
-\clausify rule need theorems developed for the \canonicalize rule. The
-\canonicalize rule needs theorems developed in the \resolve formalization,
-and \resolve depends on the \conjunct rule.
 

### 2018-03-27 pubs/itp-2018/sections/proof-reconstruction.tex
Improve many parts in the text.
Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

@@
 \CPL derivations generated by \Metis. This reconstruction consists of
-a translation from a source system (\Metis) to the target system
-(\Agda). The system of origin is the automatic theorem prover and the
-target system is the proof-assistant. We choose \Agda but another
-proof-assistant with the same support of type theory and inductive
-types could be used \eg \Coq.
+a translation from a source system to the target system. The system of
+origin is the automatic theorem prover \Metis and the target system is
+the proof-assistant \Agda. We choose \Agda but another proof-assistant
+with the same support of type theory and inductive types could be used
+(\eg \Coq).
 
@@
 \input{sections/diagram.tex}
-The overview of the proof-reconstruction is presented as a workflow
-in Fig.~\ref{fig:proof-reconstruction-workflow}. This workflow
-follow the same basis of the proposed workflow presented
-in~\cite{sultana2015}.
+The overview of the proof-reconstruction is presented as the workflow
+in Fig.~\ref{fig:proof-reconstruction-workflow} following the same
+basis of the proposed workflow presented in~\cite{sultana2015}.
 
-The process begins with a \TPTP file that encodes a problem in \CPL.
-We use this file as the input of the \Metis prover. If the problem is
-a theorem, \Metis generates a derivation of the proof in \TSTP
-format.
-
-With a \TSTP derivation file, we process the derivation with the
-\Athena translator tool.
-\Athena parses the \TSTP format, analyzes the
+The process begins with a \TPTP file that encodes a \CPL conjecture.
+Then, we use the \Metis prover to generate a derivation of the proof
+in \TSTP format in case the \CPL conjecture corresponds to a theorem.
+If so, the process continues. The next step is in charge of the
+\Athena translator tool that generates an \Agda file.
+Athena first parses the \TSTP file, then analyzes its
 derivation and generates a representation of the natural deduction
-proof using a tree data structure (see the properties
-of this tree in Section~\ref{ssec:metis-proofs}).
-In the \Athena analysis, some unnecessary steps that introduce redundancies
-and some unused input are removed from the proof-tree.
-As result, we get from \Athena an \Agda file of the proof
-with names of functions and theorems from
-the \Agda libraries that accompany this article:
+proof. In the \Athena analysis, some unnecessary steps are removed
+mainly because of they introduce redundancies or they do not appear in
+the proof-tree. The Agda file genereted by \Athena uses names of functions
+and theorems from the \Agda libraries that accompany this article:
 \texttt{agda-prop} and \texttt{agda-metis}.
 
-Finally, we type-check the \Agda proof-term. If the type-checking
-success, the \TSTP derivation generated by \Metis is correct
-module \Agda and the proposed formalizations for the
-propositional logic and for the \Metis reasoning.
-In that case \Agda outputs an interface file.
-Otherwise, when type-checking fails, the failure must be
-investigated by the user looking at the error in the \TSTP derivation
-by \Metis, in the translation by \Athena, in the \Agda formalizations
-mentioned above or in the type-checker~\Agda.
+Finally, we type-check the proof-terms of the \Agda file.
+If this type-checking success, the \TSTP derivation generated by \Metis will be
+\emph{correct} module the \Agda correctness and the completeness of the
+proposed formalisation and \Agda will output an interface file.
 
-In the remainder part of this section, a formal description using
-type theory is presented to build definitions and theorems of
-functions necessary to reconstruct \Metis inference rules.
+Otherwise, when the type-checking fails, the failure must be
+investigated by the user. The possible causes can be due to
+a \emph{completeness} issue in our \Agda libraries for the \Metis reasoning
+but also in a translation bug in \Athena. We have also consider
+errors due to some failure in the type-checker~\Agda,
+soundness bugs in the \Metis prover.
+
+In the remainder part of this section, we present a formal description
+of definitions and theorems necessary to reconstruct \Metis inference
+rules. Through this description, we refer to the lines in the \Metis
+derivation presented in Fig.~\ref{complete-metis-example} of the
+theorem in \eqref{eq:complete-example-problem} to show each rule.
 

### 2018-04-03 pubs/itp-2018/sections/proof-reconstruction.tex
[ Sec4 ] example of the strip inference.

@@
 \input{sections/diagram.tex}
-The overview of the proof-reconstruction is presented as the workflow
+The overview of the proof-reconstruction is presented as a workflow
 in Fig.~\ref{fig:proof-reconstruction-workflow} following the same
@@
 The process begins with a \TPTP file that encodes a \CPL conjecture.
-Then, we use the \Metis prover to generate a derivation of the proof
-in \TSTP format in case the \CPL conjecture corresponds to a theorem.
+Then, we use the \Metis prover to generate in \TSTP format a derivation
+of the proof in case the \CPL conjecture corresponds to a theorem.
 If so, the process continues. The next step is in charge of the
@@
 derivation and generates a representation of the natural deduction
-proof. In the \Athena analysis, some unnecessary steps are removed
-mainly because of they introduce redundancies or they do not appear in
-the proof-tree. The Agda file genereted by \Athena uses names of functions
+proof. In the analysis, some unnecessary steps read from the \TSTP derivation
+are taken into account in the final proof-tree mainly because some introduce redundancies
+or they do not contribute in the proof.
+The Agda file genereted by \Athena uses names of functions
 and theorems from the \Agda libraries that accompany this article:
@@
 
-Finally, we type-check the proof-terms of the \Agda file.
-If this type-checking success, the \TSTP derivation generated by \Metis will be
-\emph{correct} module the \Agda correctness and the completeness of the
-proposed formalisation and \Agda will output an interface file.
-
-Otherwise, when the type-checking fails, the failure must be
-investigated by the user. The possible causes can be due to
-a \emph{completeness} issue in our \Agda libraries for the \Metis reasoning
-but also in a translation bug in \Athena. We have also consider
-errors due to some failure in the type-checker~\Agda,
+Using \Agda as the proof-checker, we type-check the proof-terms of the
+\Agda file previous generated. If this type-checking success, the
+\TSTP derivation generated by \Metis will be \emph{correct} module the
+\Agda correctness and the proposed formalisation.
+In such a case, \Agda will output an interface file. Otherwise, when
+the type-checking fails, the failure must be investigated by the user.
+The possible causes can be due to many factors: a
+\emph{completeness} issue in our \Agda libraries for the \Metis
+reasoning, a translation bug in \Athena, errors in \Agda, printing or
 soundness bugs in the \Metis prover.
@@
 
-In this section, we reconstruct each \Metis inference rule in
+In this section, we reconstruct each \Metis inference rule from
 Table~\ref{tab:agda-metis-table}.
@@
 since this rule  is the only one that closely follows the \Metis
-source code. To reconstruct the other rules, we use a pattern for their
-formalization showed in Example~\ref{ex:inference-rule-pattern}.
+source code. To reconstruct the other rules, we follow a pattern showed
+in Example~\ref{ex:inference-rule-pattern}.
 

### 2018-04-03 pubs/itp-2018/sections/proof-reconstruction/strip.tex
[ Sec4 ] example of the strip inference.

@@
 \begin{myexamplenum}
-
-The subgoals associated to a goal are introduced
-in the \TSTP derivation with the \strip inference rule.
-
-\begin{verbatim}
-  fof(goal, conjecture, (p ∧ r) ∧ q)).
-  fof(s₁, p, inf(strip, goal)).
-  fof(s₂, p ⇒ r, inf(strip, goal)).
-  fof(s₃, (p ∧ r) ⇒ q, inf(strip, goal)).
-\end{verbatim}
-
-In this example, the conjecture $(p ∧ r) ∧ q$ is stripped into
-tree subgoals: $p$, $p ⇒ r$ and $(p ∧ r) ⇒ q$.
-
-\begin{equation}
-\label{eq:strip-example}
-(p ∧ (p ⇒ r) ∧ ((p ∧ r) ⇒ q)) ⇒ ((p ∧ r) ∧ q).
-\end{equation}
-
-\Metis proves each subgoal in the same order above from left to right
-in~\eqref{eq:strip-example}.
-So far, very little attention has been paid to the role of the \strip rule
-in \TSTP derivations since \Metis does not make explicit the way
-it uses the subgoals to prove the conjecture.
+In Fig.~\ref{complete-metis-example}, we can see how
+the subgoals associated to a goal are introduced
+in the \TSTP derivation line \ref{line3} with the \strip inference rule.
+The conjecture in line \ref{line2}, $(p ∨ q) ⇒ (p ∧ q)$,
+is stripped into two subgoals (line~\ref{line4} and \ref{line5}):
+$(p ∨ q) ⇒ p$ and $((p ∨ q) ∧ p) ⇒ q$.
+\Metis proves each subgoal separately following the same order as
+they appeared in the \TSTP derivation.
 \end{myexamplenum}
 
-We prove the correctness of the \strip inference rule in
-Theorem~\ref{thm:strip}. To show that theorem, we need to prove
-Lemma~\ref{lem:inv-uh-lem} and Lemma~\ref{lem:lem-inv-strip}.
+Unluckily, \Metis does not make explicit the way it uses the subgoals
+to prove the goal by the time this document is written. Thus we show the
+explicit description of this stripping process in the correctness of
+the \strip inference rule in Theorem~\ref{thm:strip}. We first need
+to prove Lemma~\ref{lem:inv-uh-lem} and Lemma~\ref{lem:lem-inv-strip}.
 

### 2018-04-03 pubs/itp-2018/sections/proof-reconstruction/strip.tex
First attempt introducting uh in strip sec.

@@
 
-Unluckily, \Metis does not make explicit the way it uses the subgoals
-to prove the goal by the time this document is written. Thus we show the
-explicit description of this stripping process in the correctness of
-the \strip inference rule in Theorem~\ref{thm:strip}. We first need
-to prove Lemma~\ref{lem:inv-uh-lem} and Lemma~\ref{lem:lem-inv-strip}.
+Unluckily, \Metis does not make explicit in the \TSTP derivation
+the way it uses the subgoals to prove the goal. We show that way
+in the correctness of the \strip inference rule in Theorem~\ref{thm:strip}.
+To show that, we first need to prove Lemma~\ref{lem:inv-uh-lem} and
+Lemma~\ref{lem:lem-inv-strip}.
 
@@
   \label{lem:inv-uh-lem}
-Let $\text{n} : \Nat$ be the complexity measure of the $\fuh_0$ function
-in~\eqref{eq:uh-definition}.
-If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$ where $\fuh₁$ is the function defined
-in~\eqref{eq:uh-structured}.
+Let $\text{n} : \Nat$. If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$ where
+
+\begin{equation}
+\label{eq:uh-structured}
+\begin{aligned}
+&\hspace{.495mm} \fuh_{1} : \Prop → \Nat → \Prop\\
+&\begin{array}{llll}
+\fuh_{1} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &(\suc~n) &= \fuh_{1}~((φ₁ ∧ φ₂) ⇒ φ₃)~n\\
+\fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
+\fuh_{1} &φ &n &= φ.
+\end{array}
+\end{aligned}
+\end{equation}
 \end{mainlemma}
+
+To keep simpler the coming definitions, we use instead of $\fuh_{1}$ function
+a unary function defined in~\eqref{eq:uh}.
+
+\begin{align*}
+  \label{eq:uh}
+  \begin{split}
+  &\fuh : \Prop → \Prop\\
+  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
+  \end{split}
+\end{align*}
+Using the $\fuh_{cm}$ function defined in~\eqref{eq:uh-complexity}.
+
+\begin{equation}
+  \label{eq:uh-complexity}
+  \begin{aligned}
+    &\hspace{.495mm}\fuh_{cm} : \Prop → \Nat\\
+    &\begin{array}{llll}
+    \fuh_{cm}~(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{cm}~φ₃ + 2\\
+    \fuh_{cm}~(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fmax~(\fuh_{cm}~φ₂)~(\fuh_{cm}~φ₃) + 1\\
+    \fuh_{cm}~φ                &= 0.
+    \end{array}
+  \end{aligned}
+\end{equation}
 

### 2018-04-03 pubs/itp-2018/sections/acknowledgements.tex
[ pubs ] preparation of the paper (#60)
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

* [ Sec4 ] example of the s

@@
 \subsubsection*{Acknowledgments.}
+
 The first author would like to thank to Universidad EAFIT for funding
@@
 he presented part of this research. We thank Joe Leslie-Hurd for his
-support and comments about \Metis.  We also acknowledge the work
-carried out by Alejandro G\'omez-Londo\~no~\cite{Gomez-Londono2015}
-used as the basis for our \TSTP parsing module in~\cite{Athena}. This
-research was fully supported by Universidad EAFIT (grant
-\#~690-000088).
+support and comments about \Metis.  This research was fully supported
+by Universidad EAFIT (grant \#~690-000088).
 

### 2018-04-03 pubs/itp-2018/sections/conclusions-and-future-work.tex
[ pubs ] preparation of the paper (#60)
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

* [ Sec4 ] example of the s

--- 2017-11-21 paper/sections/conclusions-and-future-work.tex
@@
 
-\section{Conclusions and Future Work}
+\section{Conclusions}
 \label{sec:conclusions}
@@
 \Metis~2.3 (release~20170822).
-
-\subsection*{Future work}
-
-Further research directions include, but are not limited to:
-
-\begin{itemize}
-\item extend the proof-reconstruction presented in this paper to
-  \begin{itemize}
-    \item support \Metis inference rules with equality (\eg, equality).
-    \item support other \ATPs for propositional logic like \name{EProver} or \name{Z3}. This development can be carried out by following the \name{EProver}
-description on Kanso's Ph.D. thesis~\cite{Kanso2012}.
-    \item support \Metis first-order proofs.
-  \end{itemize}
-
-% \item use a shallow embedding instead the deep embedding
-% implemented in~\cite{AgdaProp} to reconstruct proofs.
-\item improve some functions in Section~\ref{ssec:emulating-inferences}
-\begin{itemize}
-  \item by investigating the consequences of removing the \clausify
-inference rule by the \canonicalize rule.
-  \item by increasing the coverage of the \simplify rule. Since is fairly
-complex its implementation in the \Metis source code, some cases could be omitted in Section~\ref{sssec:simplify}.
-\end{itemize}
-
-% For instance, we can
-
-% and many cases could be omitted.
-% Other improvements are related with computational efficiency of
-% rules that strongly depend on reordering tasks,
-% Section~\ref{sssec:resolve}.
-% We believe some rules like \canonicalize can get some help by
-% performing an analysis with \Athena.
-\end{itemize}
 \end{document}

### 2018-04-03 pubs/itp-2018/sections/metis-language-and-proofs.tex
[ pubs ] preparation of the paper (#60)
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

* [ Sec4 ] example of the s

@@
 The \TPTP syntax\footnote{See the complete syntax grammar
-at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} is a
+at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}.} is a
 well-defined grammar to handle annotated formulas with the form:

### 2018-04-03 pubs/itp-2018/sections/proof-reconstruction/simplify.tex
[ pubs ] preparation of the paper (#60)
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

* [ Sec4 ] example of the s

@@
 
-\begin{proof} This proof is by induction on the structure of $φ$.\\
-
-∙~Case $φ ≡ φ₁ ∨ φ₂$.
-
-\begin{center}
-\begin{scprooftree}{1}
-\AxiomC{$Γ , φ₁ ⊢ φ₁$}
-\AxiomC{$Γ ⊢ ℓ$}
-\RightLabel{weaken}
-\UnaryInfC{$Γ , φ₁ ⊢ ℓ$}
-\RightLabel{by~ind.~hyp.}
-\BinaryInfC{$Γ , φ₁ ⊢ \freduce~φ₁~ℓ$}
-\RightLabel{∨-intro₁}
-\UnaryInfC{$Γ , φ₁ ⊢ \freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ$}
-%
-\AxiomC{$Γ , φ₂ ⊢ φ₂$}
-\AxiomC{$Γ ⊢ ℓ$}
-\RightLabel{weaken}
-\UnaryInfC{$Γ , φ₂ ⊢ ℓ$}
-\RightLabel{by~ind.~hyp.}
-\BinaryInfC{$Γ , φ₂ ⊢ \freduce~φ₂~ℓ$}
-\RightLabel{∨-intro₂}
-\UnaryInfC{$Γ , φ₂ ⊢ \freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ$}
-\LeftLabel{$(\mathcal{D})$\hspace{3mm}}
-\RightLabel{∨-elim}
-\BinaryInfC{$Γ , φ₁ ∨ φ₂ ⊢ \freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ$}
-\RightLabel{⇒-intro}
-\UnaryInfC{$Γ ⊢  φ₁ ∨ φ₂ ⇒ (\freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ)$}
-\end{scprooftree}
-\end{center}
-\medskip
-
-\def\defaultHypSeparation{\hskip.4in}
-\begin{center}
-\begin{scprooftree}{1}
-\AxiomC{$\mathcal{D}$}
-\RightLabel{⇒-elim}
-\AxiomC{$Γ ⊢ φ₁ ∨ φ₂$}
-\BinaryInfC{$Γ ⊢ \freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ$}
-\RightLabel{Lemma~\ref{lem:canon-or}}
-\UnaryInfC{$Γ ⊢ \fsimplify_{∨}~(\freduce~φ₁~ℓ ∨ \freduce~φ₂~ℓ)$}
-\end{scprooftree}
-\end{center}
-
-\def\defaultHypSeparation{\hskip.2in}
-
-∙ Otherwise use the same hypothesis $Γ ⊢ φ$.
-\end{proof}
-
 The \fsimplify function is defined in~\eqref{eq:simplify}. If some
@@
 
-\begin{proof}
-This proof is by induction on the structure of $φ$. \\
-
-∙~Case $φ₂ ≡ φ₂₁ ∨ φ₂₂$.
-
-\def\defaultHypSeparation{\hskip.2in}
-
-\begin{center}
-\begin{scprooftree}{1}
-\AxiomC{$Γ ⊢ φ₁$}
-\RightLabel{weaken}
-\UnaryInfC{$Γ , φ₂₁ ⊢ φ₁$}
-\AxiomC{$Γ , φ₂₁ ⊢ φ₂₁$}
-\RightLabel{by~ind.~hyp.}
-\BinaryInfC{$Γ , φ₂₁ ⊢ \fsimplify~φ₁~φ₂₁~ψ$}
-\LeftLabel{$(\mathcal{D}_{1})$\hspace{5mm}}
-\RightLabel{∨-intro₁}
-\UnaryInfC{$Γ , φ₂₁ ⊢ \fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₁~φ₂₁~ψ$}
-\end{scprooftree}
-\end{center}
-\medskip
-\begin{center}
-\begin{scprooftree}{1}
-\AxiomC{$Γ ⊢ φ₁$}
-\RightLabel{weaken}
-\UnaryInfC{$Γ , φ₂₂ ⊢ φ₁$}
-\AxiomC{$Γ , φ₂₂ ⊢ φ₂₂$}
-\RightLabel{by~ind.~hyp.}
-\BinaryInfC{$Γ , φ₂₂ ⊢ \fsimplify~φ₁~φ₂₂~ψ$}
-\LeftLabel{$(\mathcal{D}_{2})$\hspace{5mm}}
-\RightLabel{∨-intro₂}
-\UnaryInfC{$Γ , φ₂₂ ⊢ \fsimplify~φ₁~φ₂₂~ψ ∨ \fsimplify~φ₁~φ₂₂~ψ$}
-\end{scprooftree}
-\end{center}
-\medskip
-\begin{center}
-\begin{scprooftree}{1}
-\AxiomC{$\mathcal{D}_{1}$}
-% \UnaryInfC{$Γ , φ₂₁ ⊢ \fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₁~φ₂₁~ψ$}
-\AxiomC{$\mathcal{D}_{2}$}
-% \UnaryInfC{$Γ , φ₂₂ ⊢ \fsimplify~φ₁~φ₂₂~ψ ∨ \fsimplify~φ₁~φ₂₂~ψ$}
-\RightLabel{∨-elim}
-\BinaryInfC{$Γ , φ₂₁ ∨ φ₂₂ ⊢ \fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₁~φ₂₂~ψ$}
-\RightLabel{⇒-intro}
-\LeftLabel{$(\mathcal{D}_{3})$\hspace{5mm}}
-\UnaryInfC{$Γ ⊢  φ₂₁ ∨ φ₂₂ ⇒ (\fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₁~φ₂₂~ψ)$}
-\end{scprooftree}
-\end{center}
-
-\medskip
-\begin{center}
-\begin{scprooftree}{1}
-\AxiomC{$\mathcal{D}_{3}$}
-\UnaryInfC{$Γ ⊢  φ₂₁ ∨ φ₂₂ ⇒ (\fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₁~φ₂₂~ψ)$}
-\RightLabel{⇒-elim}
-\AxiomC{$Γ ⊢ φ₂₁ ∨ φ₂₂$}
-\BinaryInfC{$Γ ⊢ \fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₂~φ₂₂~ψ$}
-\RightLabel{Lemma~\ref{lem:canon-or}}
-\UnaryInfC{$Γ ⊢ \fsimplify_{∨}~(\fsimplify~φ₁~φ₂₁~ψ ∨ \fsimplify~φ₂~φ₂₂~ψ)$}
-\end{scprooftree}
-\end{center}
-\medskip
-
-∙~Case $φ₂$ is a literal. Use Lemma~\ref{lem:reduce-literal} with $φ = φ₁$ and
-$ℓ = φ₂$.
-\end{proof}
-
 \begin{mainth}
@@
 \end{mainth}
-
-\begin{proof} We prove this theorem by induction on $n$.\\
-∙~Case $n = 2$. Use Lemma~\ref{lem:binary-simplify}.\\
-∙~Case $n > 2$. Suppose this theorem is valid for $n$, that is,
-for $i = 1, \cdots, n$, $Γ ⊢ \fsimplify~γ_{n-1}~φ_{n}~ψ$. Let us prove it for $n+1$.\\
-
-\begin{equation*}
-\begin{bprooftree}
-\AxiomC{$Γ ⊢ \fsimplify~γ_{n-1}~φ_{n}~ψ$}
-\AxiomC{$γ_{n} ≡ \fsimplify~γ_{n-1}~φ_{n}~ψ$}
-\RightLabel{subst}
-\BinaryInfC{$Γ ⊢ γ_{n}$}
-\AxiomC{$Γ ⊢ φ_{n+1}$}
-\RightLabel{by~ind.~hyp.}
-\BinaryInfC{$Γ ⊢ \fsimplify~γ_{n}~φ_{n+1}~ψ$}
-\end{bprooftree}
-\end{equation*}
-\end{proof}
 

### 2018-04-05 pubs/itp-2018/sections/proof-reconstruction.tex
[ ref.bib ] Add the master thesis reference to introduce uh function.
Added a mention to the master thesis to skip all the proofs.

@@
 
+We skip all the proofs in the following sections to keep the length of
+this document. Nevertheless, these proofs and other intermediate
+results are presented in~\cite{Prieto-Cubides2017a}. We remind the
+reader the formalisation~\cite{AgdaMetis,AgdaProp} contains also these
+proofs type-checked by \Agda.
+
 \begin{notation}
@@
 The remainder of this section will be devoted to present a formal
-description in type theory of remaining \Metis rules presented in
+description in type theory of the remaining \Metis rules presented in
 Table~\ref{tab:agda-metis-table} using the pattern presented in the

### 2018-04-05 pubs/itp-2018/sections/proof-reconstruction/strip.tex
[ ref.bib ] Add the master thesis reference to introduce uh function.
Added a mention to the master thesis to skip all the proofs.

@@
 in the correctness of the \strip inference rule in Theorem~\ref{thm:strip}.
-To show that, we first need to prove Lemma~\ref{lem:inv-uh-lem} and
+To show that, we first need to state Lemma~\ref{lem:inv-uh-lem} and
 Lemma~\ref{lem:lem-inv-strip}.
@@
   \label{lem:inv-uh-lem}
-Let $\text{n} : \Nat$. If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$ where
+If $Γ ⊢ \fuh~φ$ then $Γ ⊢ φ$ where
+\begin{align}
+  \label{eq:uh}
+  \begin{split}
+  &\fuh : \Prop → \Prop\\
+  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
+  \end{split}
+\end{align}
+\end{mainlemma}
+
+In~\cite{Prieto-Cubides2017a}, we make a complete treatment for
+terminating functions including the analysis of the function $\fuh$
+showed in~\eqref{eq:uh}. The goal of this function comes from the
+defintion of $\fuh_{1}$ function in~\eqref{eq:uh-structured}. It consists of
+contracting a formula $φ₁ ⇒ (φ₂ ⇒ φ₃)$ to $(φ₁ ∧ φ₂) ⇒ φ₃$, and expanding a
+formula $φ₁ ⇒ (φ₂ ∧ φ₃)$ to $(φ₁ ⇒ φ₂) ∧ (φ₁ ⇒ φ₃)$.
 
@@
 \end{equation}
-\end{mainlemma}
-
-To keep simpler the coming definitions, we use instead of $\fuh_{1}$ function
-a unary function defined in~\eqref{eq:uh}.
-
-\begin{align*}
-  \label{eq:uh}
-  \begin{split}
-  &\fuh : \Prop → \Prop\\
-  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
-  \end{split}
-\end{align*}
-Using the $\fuh_{cm}$ function defined in~\eqref{eq:uh-complexity}.
+The remining function is $\fuh_{cm}$. This functions outputs the complexity
+measure for the $\fuh_{1}$ function (see more details in Section 2.1
+in~\cite{Prieto-Cubides2017a}).
 

### 2018-06-18 pubs/itp-2018/sections/proof-reconstruction.tex
Workflow reviewed

--- 2018-04-03 pubs/itp-2018/sections/proof-reconstruction.tex
@@
-\documentclass[../main.tex]{subfiles}
+\documentclass[../itp-2018.tex]{subfiles}
 \begin{document}
@@
 
-The process begins with a \TPTP file that encodes a \CPL conjecture.
-Then, we use the \Metis prover to generate in \TSTP format a derivation
-of the proof in case the \CPL conjecture corresponds to a theorem.
-If so, the process continues. The next step is in charge of the
-\Athena translator tool that generates an \Agda file.
-Athena first parses the \TSTP file, then analyzes its
-derivation and generates a representation of the natural deduction
-proof. In the analysis, some unnecessary steps read from the \TSTP derivation
-are taken into account in the final proof-tree mainly because some introduce redundancies
-or they do not contribute in the proof.
-The Agda file genereted by \Athena uses names of functions
-and theorems from the \Agda libraries that accompany this article:
-\texttt{agda-prop} and \texttt{agda-metis}.
+The process begins assuming that the user posses a \TPTP valid file that encodes
+a \CPL conjecture. If this conjecture is a theorem, by means of \Metis, we
+obtain a derivation in \TSTP format of a proof for this conjecture. Now, we use
+the \Athena tool to generate the \Agda file that corresponds to the proof-term
+for such \TSTP derivation. \Athena parses and prunes the proof-tree of the \TSTP
+derivation by removing some redundancies and steps that do not contribute in the
+proof. After this translation process, we end up with a proof-term  in the \Agda
+file of the natural deduction proof. This \Agda file will make calls to theorems
+and lemmas from the \Agda libraries, \texttt{agda-prop} (classical propositional
+logic) and \texttt{agda-metis} (propositional reasoning for \Metis derivations).
 
-Using \Agda as the proof-checker, we type-check the proof-terms of the
-\Agda file previous generated. If this type-checking success, the
-\TSTP derivation generated by \Metis will be \emph{correct} module the
-\Agda correctness and the proposed formalisation.
-In such a case, \Agda will output an interface file. Otherwise, when
-the type-checking fails, the failure must be investigated by the user.
-The possible causes can be due to many factors: a
-\emph{completeness} issue in our \Agda libraries for the \Metis
-reasoning, a translation bug in \Athena, errors in \Agda, printing or
-soundness bugs in the \Metis prover.
+Using \Agda as the proof-checker, we type-check the proof-terms of the \Agda
+file previous generated. If this type-checking success, the \TSTP derivation
+generated by \Metis will be \emph{correct} module the \Agda correctness and the
+proposed formalisation. In such a case, \Agda will output an interface file.
+Otherwise, \Agda will report where the type-checking fails, if it is the case,
+the failure must be investigated by the user. The possible causes can be due to
+many factors: \emph{completeness} issues in our \Agda libraries for the \Metis
+reasoning, bugs in the translation by \Athena, bugs in \Agda, printing errors
+of the \TSTP derivation by \Metis or soundness bugs in the \Metis
+reasoning.
 
-In the remainder part of this section, we present a formal description
-of definitions and theorems necessary to reconstruct \Metis inference
-rules. Through this description, we refer to the lines in the \Metis
-derivation presented in Fig.~\ref{complete-metis-example} of the
-theorem in \eqref{eq:complete-example-problem} to show each rule.
+In the remainder part of this section, we present a formal description of
+definitions and theorems necessary to reconstruct \Metis inference rules.
+Through this description, we refer to the lines in the \Metis derivation
+presented in Fig.~\ref{complete-metis-example} of the theorem in
+\eqref{eq:complete-example-problem} to show examples of each rule.
 

### 2018-06-18 pubs/itp-2018/sections/proof-reconstruction/strip.tex
Introduction of the strip part reviewed

--- 2018-04-03 pubs/itp-2018/sections/proof-reconstruction/strip.tex
@@
 
-Unluckily, \Metis does not make explicit in the \TSTP derivation
-the way it uses the subgoals to prove the goal. We show that way
-in the correctness of the \strip inference rule in Theorem~\ref{thm:strip}.
-To show that, we first need to prove Lemma~\ref{lem:inv-uh-lem} and
-Lemma~\ref{lem:lem-inv-strip}.
+\begin{remark}
+\Metis does not make explicit in the \TSTP derivation the way it uses the
+subgoals to prove the goal. We show this approach in the correctness of the
+\strip inference rule in Theorem~\ref{thm:strip}. To show this theorem, we prove
+Lemma~\ref{lem:inv-uh-lem} and  Lemma~\ref{lem:lem-inv-strip}. In the former, we
+introduce the auxiliary function $\fuh_1$ to define the $\fuh$ function used to
+define the $\fstrip_1$ function in the latter.
+\end{remark}
 
@@
 
-To keep simpler the coming definitions, we use instead of $\fuh_{1}$ function
-a unary function defined in~\eqref{eq:uh}.
-
-\begin{align*}
-  \label{eq:uh}
-  \begin{split}
-  &\fuh : \Prop → \Prop\\
-  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
-  \end{split}
-\end{align*}
-Using the $\fuh_{cm}$ function defined in~\eqref{eq:uh-complexity}.
+The second argument in the $\fuh_1$ function is a natural number that constrains
+the number of recursive calls. To provide such a number given a formula
+$\varphi$, we call the $\fuh_{cm}$ function defined in~\eqref{eq:uh-complexity}.
+This function finds what we call the \emph{function complexity} of the function
+$\fuh_1$. For the convenience in the following descriptions, we use the
+function $\fuh : \Prop → \Prop$ for $\varphi \mapsto \fuh_{1}~φ~(\fuh_{cm}~φ)$.
 
@@
 \end{equation}
+
+% \begin{align}
+%   \label{eq:uh}
+%   \begin{split}
+%   &\fuh : \Prop → \Prop\\
+%   &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
+%   \end{split}
+% \end{align}
+
+% == CONTINUAR DESDE AQUI
 

### 2018-06-20 pubs/itp-2018/sections/proof-reconstruction.tex
[ strip ] first finished draft of its description

@@
 for such \TSTP derivation. \Athena parses and prunes the proof-tree of the \TSTP
-derivation by removing some redundancies and steps that do not contribute in the
-proof. After this translation process, we end up with a proof-term  in the \Agda
-file of the natural deduction proof. This \Agda file will make calls to theorems
-and lemmas from the \Agda libraries, \texttt{agda-prop} (classical propositional
-logic) and \texttt{agda-metis} (propositional reasoning for \Metis derivations).
+derivation by removing some redundancies and steps that do not contribute to
+prove the conjecture. When the translation process finishes, we end up with a
+proof-term in an \Agda file with the natural deduction proof. In this file, we
+make calls to theorems and lemmas in the \Agda libraries, \texttt{agda-prop}
+(classical propositional logic) and \texttt{agda-metis} (propositional reasoning
+for \Metis derivations).
 
@@
 proposed formalisation. In such a case, \Agda will output an interface file.
-Otherwise, \Agda will report where the type-checking fails, if it is the case,
-the failure must be investigated by the user. The possible causes can be due to
-many factors: \emph{completeness} issues in our \Agda libraries for the \Metis
-reasoning, bugs in the translation by \Athena, bugs in \Agda, printing errors
-of the \TSTP derivation by \Metis or soundness bugs in the \Metis
-reasoning.
+Otherwise, \Agda will report where the type-checking fails, if so, the failure
+must be investigated by the user. The possible causes can be due to many
+factors: \emph{completeness} issues in our \Agda libraries for the \Metis
+reasoning, bugs in the translation by \Athena, bugs in \Agda, printing errors of
+the \TSTP derivation by \Metis or soundness bugs in the \Metis reasoning.
 

### 2018-06-20 pubs/itp-2018/sections/proof-reconstruction/strip.tex
[ strip ] first finished draft of its description

@@
 
-To prove a goal, \Metis splits the goal into disjoint cases. This
-process produces a list of new subgoals, the conjunction of these
-subgoals implies the goal. Then, a proof of the goal becomes into a
-set of smaller proofs, one refutation for each subgoal.
+To prove a goal, \Metis splits the goal into disjoint cases. This process
+produces a list of new subgoals, the conjunction of these subgoals implies the
+goal. Then, a proof of the goal becomes into a set of smaller proofs, one
+refutation for each subgoal.
 
@@
 Lemma~\ref{lem:inv-uh-lem} and  Lemma~\ref{lem:lem-inv-strip}. In the former, we
-introduce the auxiliary function $\fuh_1$ to define the $\fuh$ function used to
-define the $\fstrip_1$ function in the latter.
+introduce the auxiliary function $\fuh_1$ to define the $\fuh$ function used in
+in the latter in the definition of the $\fstrip$ function.
 \end{remark}
@@
   \label{lem:inv-uh-lem}
-Let $\text{n} : \Nat$. If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$ where
+Let be $\text{n} : \Nat$. If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$ where
 
@@
 $\varphi$, we call the $\fuh_{cm}$ function defined in~\eqref{eq:uh-complexity}.
-This function finds what we call the \emph{function complexity} of the function
-$\fuh_1$. For the convenience in the following descriptions, we use the
+This function finds what we call the \emph{complexity measure} of the function
+$\fuh_1$. For the convenience in the following descriptions, we have the
 function $\fuh : \Prop → \Prop$ for $\varphi \mapsto \fuh_{1}~φ~(\fuh_{cm}~φ)$.
-
 \begin{equation}
@@
 \end{equation}
+Now, we define the $\fstrip$ function in \eqref{eq:strip} in a similar way as we
+did above for the $\fuh$ function. We have a definition of the $\fstrip₁$ function
+in~\eqref{eq:strip-fixed} and a complexity measure denoted by $\fstrip_{cm}$
+and defined in~\cite{Prieto-Cubides2017a}.
+% \vspace*{-5mm}
+\begin{align}
+  \label{eq:strip}
+  \begin{split}
+  &\fstrip : \Prop → \Prop\\
+  &\fstrip~φ~ = \fstrip₁~φ~(\fstrip_{cm}~φ).
+  \end{split}
+\end{align}
 
-% \begin{align}
-%   \label{eq:uh}
-%   \begin{split}
-%   &\fuh : \Prop → \Prop\\
-%   &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
-%   \end{split}
-% \end{align}
-
-% == CONTINUAR DESDE AQUI
-
-The $\fstrip₀$ function defined in~\eqref{eq:strip-zero} yields the
-conjunction of subgoals that implies the goal of the problem in the
-\Metis \TSTP derivations. Nonetheless, this function is not a
-structurally recursive function (see more details in
-Appendix~\ref{app:strip-cm}).
-Therefore, we present the $\fstrip₁$ function
-in~\eqref{eq:strip-fixed} as the structurally recursive version
-of the $\fstrip₀$ function by applying the
-bounded technique described in
-Section~\ref{ssec:structural-recursion}.
-We define the $\fstrip₁$ function based on the reading of the \Metis source code.
+The $\fstrip$ function yields the conjunction of subgoals that implies the goal
+of the problem in the \Metis \TSTP derivations. Its definition comes mainly from
+the reading of the \Metis source code and its \TSTP derivations.
 
@@
 
-In a similar way as we define $\fuh_{cm}$
-in~\eqref{eq:uh-complexity}, we
-define the $\fstrip_{cm}$ function in Appendix~\ref{app:strip-cm} as
-the complexity measure for the $\fstrip₀$ function.
-We define the \fstrip function as follows in~\ref{eq:strip}.
-
-\begin{align}
-  \label{eq:strip}
-  \begin{split}
-  &\fstrip : \Prop → \Prop\\
-  &\fstrip~φ~ = \fstrip_{1}~φ~(\fstrip_{cm}~φ).
-  \end{split}
-\end{align}
-
 \begin{mainlemma}
 \label{lem:lem-inv-strip}
-Let $\text{n} : \Nat$ be the complexity measure of the \fstrip function defined
-in~\eqref{eq:strip-fixed}.
-If $Γ~⊢~\fstrip₁~φ~n$ then $Γ~⊢~φ$.
+Let $n : \Nat$. If $Γ~⊢~\fstrip₁~φ~n$ then $Γ~⊢~φ$.
 \end{mainlemma}
 
-The following theorem is convenient to substitute equals by equals in
-a theorem. Recall the equality (≡) is symmetric and transitive as well.
-We use these properties without any mention.
+The following lemma is convenient to substitute equals by equals in a theorem.
+Recall the equality (≡) is symmetric and transitive, and we use these properties
+without any mention.
 
-\begin{mainlemma}
+\begin{mainlemma}[\fsubst]
   \label{lem:subst}
-  Substitution theorem.
-\begin{equation*}
-  \label{eq:substitution-theorem}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
-  \RightLabel{\fsubst}
-  \BinaryInfC{$Γ ⊢ ψ$}
-  \end{bprooftree}
-\end{equation*}
+  If $Γ ⊢ φ$ and $ψ ≡ φ$ then $Γ ⊢ ψ$.
+% \begin{equation*}
+%   \label{eq:substitution-theorem}
+%   \begin{bprooftree}
+%   \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
+%   \RightLabel{\fsubst}
+%   \BinaryInfC{$Γ ⊢ ψ$}
+%   \end{bprooftree}
+% \end{equation*}
 \end{mainlemma}
 
-We can now formulate the result that justifies the stripping strategy
-of \Metis to prove goals.
-For the sake of brevity, we state the following theorem for the
-\strip function when the goal has two subgoals. In other cases,
-we extend the theorem in the natural way.
+We can now formulate the result that justifies the stripping strategy of \Metis
+to prove goals. For the sake of brevity, we state the following theorem for the
+\strip function when the goal has two subgoals. In other cases, we extend the
+theorem in the natural way.
 
@@
 \label{thm:strip}
-Let $\text{n} : \Nat$ be the complexity measure of the strip function defined in Appendix~\ref{app:strip-cm}~\eqref{eq:strip-cm}.
-Let $s₂$ and $s₃$ be the subgoals of the goal $φ$, that is,
-$$\fstrip₁~φ~n~≡~s₂∧~s₃.$$
+Let $s_1$ and $s_2$ be the subgoals of the goal $φ$, that is,
+$\fstrip~\varphi≡~s_{1}∧~s_{2}$.
+% $\fstrip₁~φ~n~≡~s₂∧~s₃$ where $\text{n} : \Nat$ is the complexity measure $\fstrip_{cm}$.
 If $Γ ⊢ s₂$ and $Γ ⊢ s₃$ then $Γ ⊢ φ$.
 \end{mainth}
+\begin{proof}
+\begin{equation*}
+  \begin{bprooftree}
+  \AxiomC{$ Γ ⊢ s_1 $}
+  \AxiomC{$ Γ ⊢ s_2 $}
+  \RightLabel{∧-intro}
+  \BinaryInfC{$Γ ⊢ s_1\wedge s_2$}
+  \AxiomC{$\fstrip~φ ≡ s_1\wedge s_2 $}
+  \RightLabel{By def.~\eqref{eq:strip}}
+  \UnaryInfC{$\fstrip₁~φ~(\fstrip_{cm}~\varphi) ≡ s_1\wedge s_2 $}
+  \RightLabel{\fsubst}
+  \BinaryInfC{$Γ ⊢ \fstrip₁~φ~n$}
+  \RightLabel{Lemma~\ref{lem:lem-inv-strip}}
+  \UnaryInfC{$Γ ⊢ φ$}
+\end{bprooftree}
+\end{equation*}
+\end{proof}
+
 % -------------------------------------------------------------------
 
-Since \Metis proves a conjecture by refutation,
-to prove each subgoal, \Metis assumes the negation of it
-by using the \negate rule after the \strip inference application
-that introduces such a subgoal.
+\begin{remark}
+
+The user of \Metis will probably note another rule in the derivations related
+with these subgoals, the \negate rule. Since \Metis proves a conjecture by
+refutation, to prove a subgoal, \Metis assumes its negation with the \negate
+rule. This negation ocurrs always after the application of the \strip rule which
+as we mentioned before it is the rule that introduces each subgoal.
+
+\end{remark}
 

### 2018-06-20 pubs/itp-2018/sections/proof-reconstruction.tex
[ strip ] first finished draft of its description

@@
 \input{sections/diagram.tex}
+
 The overview of the proof-reconstruction is presented as a workflow
@@
 \begin{notation}
-  The function name written in \texttt{typewriter} font refers to a
-  \Metis inference rule in the \TSTP derivations. The same function
-  name written using
-  \textsf{sans serif} font refers to our formalized version to
-  reconstruct the rule and formally implemented in~\cite{AgdaMetis}.
-  To increase the readability for functions and theorems, we use
-  the convention \Source and \Target as synonyms of the \Prop
-  type. The \Source type in the reconstructed rule definition refers
-  to the argument in the \TSTP derivation, \ie the input formula of
-  the inference rule. A formula of \Target type refers to the
+
+  The function name written in \texttt{typewriter} font refers to a \Metis
+  inference rule in the \TSTP derivations. The same function name written using
+  \textsf{sans serif} font refers to our formalized version to reconstruct the
+  rule and formally implemented in~\cite{AgdaMetis}. To increase the readability
+  for functions and theorems, we use the convention \Source and \Target as
+  synonyms of the \Prop type. The \Source type in the reconstructed rule
+  definition refers to the argument in the \TSTP derivation, \ie the input
+  formula of the inference rule. A formula of \Target type refers to the
   expected result of the rule found in the \TSTP derivation.
+
 \end{notation}
 
+% -----------------------------------------------------------------------------
+% -- Strip Rule --
+% -----------------------------------------------------------------------------
 \subfile{sections/proof-reconstruction/strip.tex}
+% -----------------------------------------------------------------------------
 
-Now, as we mention in the beginning of this section, to reconstruct
-the \Metis inference rules, we use the following pattern in
-the formalization.
+The remainder of this section will be devoted to present a formal description in
+type theory of the remaining \Metis rules presented in
+Table~\ref{tab:agda-metis-table} using the pattern presented in
+Example~\ref{ex:inference-rule-pattern}. We follow the same order to present the
+rules as the table shows.
 
@@
 \label{ex:inference-rule-pattern}
-Let \texttt{metisRule} be a \Metis inference rule. To reconstruct
-this rule, we define the function \fun{metisRule} in type theory
-that follows the pattern:
+Let \texttt{metisRule} be a \Metis inference rule in the \TSTP derivations.
+To reconstruct this \texttt{metisRule}, we define in the type theory
+a function preserving the name of the original rule. This function should follow
+the following pattern.
 
@@
 
-To justify all transformations done by the \fun{metisRule} rule, we
-prove its soundness with a theorem like the following:
+To justify that all transformations performed by the \fun{metisRule} rule are correct, we
+will provide a theorem to show its soundness that says:
 
@@
 \end{myexamplenum}
-
-The remainder of this section will be devoted to present a formal
-description in type theory of the remaining \Metis rules presented in
-Table~\ref{tab:agda-metis-table} using the pattern presented in the
-example above. We follow the same order to present the rules as the
-table shows.
 

### 2018-06-20 pubs/itp-2018/sections/proof-reconstruction/conjunct.tex
[ paper ] all proofs have been removed.
First review to the conjunct fule text

--- 2018-01-03 pubs/thesis/sections/proof-reconstruction/conjunct.tex
@@
 This rule is a generalization of the projection rules for the
-conjunction connective as the following \TSTP excerpt shows.
+conjunction connective.
+See in  as the following \TSTP excerpt shows.
 
-\begin{myexamplenum}\hspace{10cm}
+\begin{myexamplenum}
 
-\begin{verbatim}
-  fof(p₁, p ∧ q ∧ (r ∨ ¬ p), ...
-  fof(p₂, q, inf(conjunct, p₁)).
-  fof(p₃, r ∨ ¬ p, inf(conjunct, p₁)).
-\end{verbatim}
-
-In the first formula, $p ∧ q ∧ (r ∨ ¬ p)$, we find a left-associative
-conjunction named \verb!p₁!. The \conjunct rule extracts $q$ from the
-\verb!p₁! using a left projection (∧-proj₁) follow by a right
-projection (∧-proj₂). After, the \conjunct rule extracts $r ∨ ¬ p$ by
-using a right projection on \verb!p₁!.
+In Fig.~\ref{complete-metis-example}, we see in line~\ref{line20} how we get $ ¬
+p ∨ q$ from the formula in line~\ref{line19}, $(¬ p ∨ q) ∧ (¬ q ∨ p)$, by means
+of the \conjunct rule, that in this case acts as a left projection (∧-proj₁).
 
@@
 
-\begin{proof}\hspace{10cm}
-\begin{itemize}
-\item[∙] Case $φ ≡ ψ$. $Γ ⊢ \fconjunct~φ~ψ$ normalizes to $Γ ⊢ ψ$.
-Then, we get the desire conclusion by applying the $\fsubst$ lemma.
-\item[∙] Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct~φ_{i}~ψ$ for some $i = 1,\ 2$, then,
-
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
-  \RightLabel{∧-proj$_{i}$}
-  \UnaryInfC{$Γ ⊢ φ_{i}$}
-  \RightLabel{by~ind.~hyp.}
-  \UnaryInfC{$Γ ⊢ \fconjunct~φ_{i}~ψ$}
-  \AxiomC{$ψ ≡ \fconjunct~φ_{i}~ψ$}
-  \RightLabel{\fsubst}
-  \BinaryInfC{$Γ ⊢ ψ$}
-  \end{bprooftree}
-\end{equation*}
-\item[∙] Otherwise, the last case follows from the hypothesis.
-\end{itemize}
-\end{proof}
-
 \end{document}

### 2018-06-20 pubs/itp-2018/sections/proof-reconstruction/strip.tex
minor changes

@@
 
-The following lemma is convenient to substitute equals by equals in a theorem.
-Recall the equality (≡) is symmetric and transitive, and we use these properties
-without any mention.
+The following lemma is convenient to substitute in a theorem equals by equals in
+the conclusion of the sequent. Recall the equality (≡) is symmetric and
+transitive, and we use these properties without any mention.
 
@@
 with these subgoals, the \negate rule. Since \Metis proves a conjecture by
-refutation, to prove a subgoal, \Metis assumes its negation with the \negate
-rule. This negation ocurrs always after the application of the \strip rule which
-as we mentioned before it is the rule that introduces each subgoal.
+refutation, to prove a subgoal, \Metis assumes its negation using the \negate
+rule. This rule always ocurrs in the \TSTP derivation after the application of
+the \strip rule that introduces the subgoal.
 

### 2018-06-22 pubs/itp-2018/sections/proof-reconstruction/resolve.tex
[ pubs ] preparation of the paper (#60)
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

* [ Sec4 ] example of the s

@@
 
-\subsubsection{Resolve.}
-\label{sssec:resolve}
-
-Logic equivalence between propositions is a major issue to justify
-prover reasoning steps. Since we left out semantics to treat only the
-syntax aspects of propositional logic, our approach shows logic
-equivalence by converting propositions to their conjunctive normal
-form, and reordering those and the inner disjunctions to match them.
+% -- TODO algun texto aqui?
 
@@
 
-A \emph{literal} is an propositional variable (positive literal) or a
-negation of an propositional variable (negative literal).
+A \emph{literal} is a propositional variable (positive literal) or a
+negation of a propositional variable (negative literal).
 
@@
 \begin{notation}
-We use \Lit as synonym of \Prop type to refer literals.
+\Lit is a synonym of \Prop to refer to literals.
 \end{notation}
@@
 zero or more literals.
-
 \end{mydefinition}
 
-\begin{myexamplenum}\hspace{10cm}
-\label{ex:resolve-tstp}
-\begin{verbatim}
-  cnf(r₄, ¬ r ∨ p ∨ q, ...
-  cnf(r₅, p ∨ q ∨ r, ...
-  cnf(r₆, p ∨ q, inf(resolve, r, [r₅, r₄])).
-\end{verbatim}
+% ----------------------------------------------------------------------------
+% -- RESOLVE --
+% ----------------------------------------------------------------------------
 
-In the excerpt above, we apply resolution to the first two formulas,
-$¬ r ∨ p ∨ q$ and $p ∨ q ∨ r$.
-The last line tells us the literal used
-for resolution is $r$. Syntactically speaking, we can not derive
-neither the conclusion $p ∨ q$ in \verb!r₆! nor apply the resolution
-theorem with \verb!r₄! and \verb!r₅! since the formulas do not fit
-the pattern required.
+\subsubsection{Resolve.}
+\label{sssec:resolve}
 
-If the scenario would have other like replacing \verb!r₅! by
-\begin{verbatim}
-  cnf(r₅, r ∨ p ∨ q, ...
-\end{verbatim}
-The \resolve rule have could derive $(p ∨ q) ∨ (p ∨ q)$, but again, that is not the expected result.
-\end{myexamplenum}
+The \resolve inference rule in combination with the \simplify rule is  the
+resolution theorem for propositional logic that we found in the \Metis \TSTP
+derivations (see this rule in~Fig.~\ref{fig:metis-inferences}). In particular,
+to reconstruct the \resolve rule following the pattern in
+Example~\ref{ex:inference-rule-pattern}, it is necessary to have a mechanism to
+test for logic equivalence between propositions. The challenge is because of we
+left out the semantics to treat only the syntax aspects of the propositional
+formulas, therefore we have to manipulate in somehow the formulas to see if they
+are logically equivalent.
 
-Therefore, we perform a sequence of rearrangements inside the
-involved formulas to match with the expected pattern by the
-\emph{resolve} inference rule in Fig.~\ref{fig:metis-inferences}.
+Our approach to address this issue mainly consists of checking for syntactical
+equality between the formulas. Firstly by converting them to their conjunctive
+normal and secondly, by performing reordering of the inner formulas of the
+resulting normal forms in the first conversion when they were not equal.
+
+In~\cite{Prieto-Cubides2017a}, we make a description of the complete machinery
+we use for that purpose. For instance, we define functions of the type ($\Source
+\to  \Target \to \Prop$) like $\freorder_{∨}$ to fix the order of a disjunction
+(premise) given by the order in the literals of another disjunction (conclusion)
+if it is possible. Following the same way, we define for conjunctions the
+function $\freorder_{\wedge}$ and for conjunctive normal forms the function
+$\freorder_{\wedge\vee}$.
 
@@
 
-\Needspace{3\baselineskip}
-\begin{proof}
-  \begin{equation*}
-  \begin{bprooftree}
-    \AxiomC{$Γ ⊢ φ₁$}
-    \RightLabel{Lemma~\ref{lem:reorder-and-or}}
-    \UnaryInfC{$Γ ⊢ \freorder_{∨}~φ₁~(ℓ ∨ ψ)$}
-    \RightLabel{Lemma~\ref{lem:reorder-and-or}}
-    \AxiomC{$Γ ⊢ φ₂$}
-    \UnaryInfC{$Γ ⊢ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)$}
-    \RightLabel{∧-intro}
-    \BinaryInfC{$Γ ⊢ \freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)$}
-    \RightLabel{Lemma~\ref{lem:rsol}}
-    \UnaryInfC{$Γ ⊢ \frsol~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧
-     \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ))$}
-    \RightLabel{by (\ref{eq:resolve})}
-    \UnaryInfC{$Γ ⊢ \fresolve~φ₁~φ₂~ℓ~ψ$}
-  \end{bprooftree}
-  \end{equation*}
-\end{proof}
-
 \end{document}

### 2018-06-25 pubs/itp-2018/sections/metis-language-and-proofs.tex
Attempt to realocate the resolve rule after simplify

@@
 
-For increasing the readability of this paper, we are not presenting
-these \TSTP derivations using the above description. Instead of it, we
-have adopted a customized \TSTP syntax to keep as short as possible
-the \Metis derivations. For instance,  we shortened some keywords,
-removed unnecessary arguments, and replaced some symbols.
-The complete description of these customizations are showed in Appendix~\ref{app:tstp-syntax}.
+For increasing the readability of this paper, we are not presenting these \TSTP
+derivations using the above description. Instead of it, we have adopted a
+customized \TSTP syntax to keep as short as possible the \Metis derivations. For
+instance,  we shortened some keywords, removed unnecessary arguments, and
+replaced some symbols. The complete description of these customizations are
+showed in Appendix~\ref{app:tstp-syntax}.
 
@@
       \texttt{conjunct}
-      &Takes a formula from a conjunction
+      &Take a formula from a conjunction
       &\ref{thm:conjunct}
@@
 
-      \texttt{resolve}
-      &A general form of the resolution theorem
-      &\ref{thm:resolve}
-      \\
-
       \texttt{canonicalize}
-      &Normalization of the formula
+      &Normalize a formula
       &\ref{thm:canonicalize}
@@
       \texttt{clausify}
-      &Performs clausification
+      &Perform clausification
       &\ref{thm:clausify}
@@
       &\ref{thm:simplify}
+      \\
+
+      \texttt{resolve}
+      &Apply one form of the resolution theorem
+      &\ref{thm:resolve}
       \\[1ex]
+
     \hline

### 2018-06-25 pubs/itp-2018/sections/proof-reconstruction.tex
Attempt to realocate the resolve rule after simplify

@@
 \subfile{sections/proof-reconstruction/conjunct.tex}
-\subfile{sections/proof-reconstruction/resolve.tex}
 \subfile{sections/proof-reconstruction/canonicalize.tex}
@@
 \subfile{sections/proof-reconstruction/simplify.tex}
+\subfile{sections/proof-reconstruction/resolve.tex}
 
@@
 
-We have finished the formalization of every inference rule in
-a \Metis derivation, we are able to justify step-by-step any proof
-for a problem in propositional logic.
-For instance, we tested successfully the translation by \Athena
-jointly with the \Agda formalizations of the rules mentioned above
-with more than eighty representative theorems in propositional
-logic. An interested reader can test the
-problems~\cite{Prieto-Cubides2017} in the \Athena tool
-repository~\cite{Athena}.
+We have finished the formalization of every inference rule in a \Metis
+derivation, we are able to justify step-by-step any proof for a problem in
+propositional logic. For instance, we tested successfully the translation by
+\Athena jointly with the \Agda formalizations of the rules mentioned above with
+more than eighty representative theorems in propositional logic. An interested
+reader can reproduce the testing of all problems from \cite{Prieto-Cubides2017}
+with the sources in the \Athena tool repository~\cite{Athena}.
 

### 2018-06-25 pubs/itp-2018/sections/proof-reconstruction/canonicalize.tex
[ paper ] all proofs have been removed.
Attempt to realocate the resolve rule after simplify

@@
 \begin{document}
+
+% ----------------------------------------------------------------------------
+% -- Preliminars --
+% ----------------------------------------------------------------------------
+
+\begin{mydefinition}
+
+A \emph{literal} is a propositional variable (positive literal) or a
+negation of a propositional variable (negative literal).
+
+\end{mydefinition}
+
+\begin{notation}
+\Lit is a synonym of \Prop to refer to literals.
+\end{notation}
+
+\begin{mydefinition}
+
+The \emph{negative normal form} of a formula is the logical
+equivalent version of it in which negations appear only in the
+literals and the formula does not contain any implications.
+
+\end{mydefinition}
+
+\begin{mydefinition}
+
+The \emph{conjunctive normal form} of a formula also called clausal
+normal form is the logical equivalent version expressed as a
+conjunction of clauses where a \emph{clause} is the disjunction of
+zero or more literals.
+\end{mydefinition}
+
+\begin{remark} The proof-reconstruction we are exposing needs a mechanism to
+test logic equivalence between propositions in some cases. This task is not
+trivial since we left out the semantics to treat only the syntax aspects of the
+propositional formulas, and therefore we have to manipulate in somehow the
+formulas to see if they are logically equivalent.
+
+We address this challenge by converting the formulas to their conjunctive
+normal. We check if their normal forms are equal and if they are not, we try to
+reorder the first formula to match with the second one to fulfill the
+syntactical equality. In~\cite{Prieto-Cubides2017a}, we make a description of a
+set of functions and lemmas for such a purpose. For instance, we define
+functions of ($\Source \to  \Target \to \Prop$) type following the pattern in
+Example~\ref{ex:inference-rule-pattern} like the $\freorder_{∨}$ function. This
+function try to fix the order of a \emph{premise} disjunction given by following
+the order about the \emph{conclusion} disjunction, the target. Similarly, we
+define the function $\freorder_{\wedge}$ for conjunctions and the function
+$\freorder_{\wedge\vee}$ for conjunctive normal forms.
+
+\end{remark}
+
+% ----------------------------------------------------------------------------
+% -- CANONICALIZE --
+% ----------------------------------------------------------------------------
 
@@
 
-The \canonicalize rule also removes inside of the formula
-the tautologies listed in~Fig.~\ref{fig:redundancies}.
-
 \begin{figure}
   \[
+    \text{Disjunction:}
     \begin{bprooftree}
@@
   \[
+    \text{Conjunction:}
     \begin{bprooftree}
@@
 
-The \canonicalize rule is used by \Metis to introduce the subgoals in
-their refutation proofs but also helps to simplify formulas at
-intermediate steps in the derivations. As far as we know, the
-\canonicalize rule implements a conjunctive normal form conversion
-with simplifications of tautologies. Otherwise, when
-an axiom, definition or hypothesis is needed to prove some goal, this
-rule gets the negative normal form of the formula.
+The \canonicalize rule is mainly used by \Metis to introduce the negation of a
+subgoal in its refutation proof. When the input formula is an axiom, definition
+or hypothesis introduced in the \TPTP file of the problem, the \canonicalize
+rule returns its negative normal form. In the remaining cases, as far as we
+know, \Metis uses the \canonicalize rule to performs a sort of simplifications
+to remove the tautologies listed in~Fig.~\ref{fig:redundancies} in the
+conjunctive normal form of the input formula.
 
-To reconstruct the \canonicalize rule, we adapted some ideas from the
-\Metis source code. The presentation of this reconstruction is as
-follows. We firstly describe functions to remove tautologies inside
-of the formula. After, we present the negative normal form conversion
-in~Lemma~\ref{lem:nnf} and the conjunctive normal form in
-Lemma~\ref{lem:cnf}. At the end of this section, we state
-Theorem~\ref{thm:canonicalize} to reconstruct the \canonicalize rule.
+To reconstruct this rule, we guide its prensentation as follows. In
+Lemma~\ref{lem:simplify-or} and Lemma~\ref{lem:simplify-and}, we show how to
+simplify in disjunctions and conjunctions, respectively. The negative normal form
+is stated in~Lemma~\ref{lem:nnf} and the conjunctive normal form in
+Lemma~\ref{lem:cnf}. Finally, the reconstruction of the \canonicalize rule is
+stated in Theorem~\ref{thm:canonicalize}.
+
+% ----------------------------------------------------------------------------
+% -- Simplify-Or --
+% ----------------------------------------------------------------------------
 
@@
 $ψ ≡ \freorder_{∨}~φ~ψ$.
+We assume all disjunctions to be right-associative unless otherwise
+stated.
 \end{notation}
 
-In right-associative disjunctions we remove the tautologies
-in Fig.~\ref{fig:or-redundancies} using Lemma~\ref{lem:canon-or}.
-We assume the formulas to be right-associative unless otherwise
-stated.
-
-\begin{figure}
-\begin{equation*}
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∨ ⊥$}
-  \UnaryInfC{$Γ ⟝ φ$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∨ ⊤$}
-  \UnaryInfC{$Γ ⟝ ⊤$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∨ φ$}
-  \UnaryInfC{$Γ ⟝ φ$}
-\end{bprooftree}
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∨ ¬~φ$}
-  \UnaryInfC{$Γ ⟝ ⊤$}
-\end{bprooftree}\qquad
-\end{equation*}
-\caption{Theorems to remove inside of a disjunction by
-the \canonicalize rule.}
-\label{fig:or-redundancies}
-\end{figure}
-
 \begin{mainlemma}
-  \label{lem:canon-or}
-
-  Let $φ : \Prop$ be a right-associative formula. If $Γ~⟝~φ$
-  then $Γ~⟝~\fcanon_{∨}~φ$, where
+  \label{lem:simplify-or}
+  %Let $φ : \Prop$ be a right-associative formula.
+  If $Γ~⟝~φ$ then $Γ~⟝~\fcanon_{∨}~φ$, where
 
@@
    \fcanon_{∨} &(φ ∨ ⊤)     &= ⊤\\
-   % \fcanon_{∨} &(¬ φ₁ ∨ φ₂) &=
-   %      \begin{cases}
-   %       \fcanon_{∨}~φ₂,        &\text{ if } ¬ φ₁ ∈_{∨} φ₂;\\
-   %       ⊤,                     &\text{ if } φ₁ ∈_{∨} φ₂;\\
-   %       ⊤,                     &\text{ if } \fcanon_{∨}~φ₂≡ ⊤;\\
-   %       ¬ φ₁,                  &\text{ if } \fcanon_{∨}~φ₂≡ ⊥;\\
-   %       ¬ φ₁ ∨ \fcanon_{∨}~φ₂, &\text{ otherwise.}
-   %      \end{cases}\\
    \fcanon_{∨} &(φ₁ ∨ φ₂)   &=
@@
 
-Now, we have removed tautologies in disjunctions by applying the
-$\fcanon_{∨}$ function. In a similar way, we define the $\fcanon_{∧}$
-function to work with conjunctions.
+% ----------------------------------------------------------------------------
+% -- Simplify-and --
+% ----------------------------------------------------------------------------
+
+Now, we have removed tautologies in disjunctions by applying the $\fcanon_{∨}$
+function, we formulate in a similar way, the $\fcanon_{∧}$ function to simplify
+tautologies about conjunctions.
 
@@
 the equality $ψ ≡ \fconjunct~φ~ψ$.
+We assume all conjunctions to be right-associative unless otherwise
+stated.
 \end{notation}
 
-In right-associative conjunctions we remove the tautologies
-in Fig.~\ref{fig:and-redundancies} using Lemma~\ref{lem:canon-and}.
-
-\begin{figure}
-\begin{equation*}
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∧ ⊤$}
-  \UnaryInfC{$Γ ⟝ φ$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∧ ⊥$}
-  \UnaryInfC{$Γ ⟝ ⊥$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∧ φ$}
-  \UnaryInfC{$Γ ⟝ φ$}
-\end{bprooftree}\qquad
-\begin{bprooftree}
-  \AxiomC{$Γ ⟝ φ ∧ ¬~φ$}
-  \UnaryInfC{$Γ ⟝ ⊥$}
-\end{bprooftree}
-\end{equation*}
-\caption{Conjunction tautologies.}
-\label{fig:and-redundancies}
-\end{figure}
-
 \begin{mainlemma}
-  \label{lem:canon-and}
-
-  Let $φ : \Prop$ be a right-associative formula. If $Γ~⟝~φ$
-  then $Γ~⟝~\fcanon_{∧}~φ$, where
+  \label{lem:simplify-and}
+  %Let $φ : \Prop$ be a right-associative formula.
+  If $Γ~⟝~φ$ then $Γ~⟝~\fcanon_{∧}~φ$, where
 
   \begin{equation}
-   \label{eq:canon-and}
+   \label{eq:simplify-and}
     \begin{aligned}
@@
         \fcanon_{∧} &(φ ∧ ⊤)     &= \fcanon_{∧}~φ \\
-        % \fcanon_{∧} &(¬ φ₁ ∧ φ₂) &=
-        %   \begin{cases}
-        %     ⊥,                     &\text{ if } φ₁ ∈_{∧} φ₂;\\
-        %     \fcanon_{∧}~φ₂,        &\text{ if } ¬ φ₁ ∈_{∧} φ₂;\\
-        %     ⊥,                     &\text{ if } \fcanon_{∧}~φ₂~≡ ⊥;\\
-        %      \fcanon_{∧}~φ₂,       &\text{ if } \fcanon_{∧}~φ₂~≡ ⊤;\\
-        %     ¬ φ₁ ∧ \fcanon_{∧}~φ₂, &\text{ otherwise.}
-        %   \end{cases}\\
         \fcanon_{∧} &(φ₁ ∧ φ₂) &=
@@
 
-Now, we are ready to define the negative normal form of a formula with
-simplifications by applying to it the $\fnnf$ function defined in
-Lemma~\ref{lem:nnf} (see more details in Appendix~\ref{app:polarity-for-propositions}).
-This definition is mainly based on the \Metis
-source code to normalize formulas. To define such a function in type
-theory we used bounded recursion as we describe in
-Section~\ref{ssec:structural-recursion}.
+Using the functions $\fcanon_{∨}$ and $\fcanon_{∧}$ we can define our function for
+the negative normal form present in \Metis, we once again formulate this version
+based on the \Metis source code to \emph{normalize} formulas. We use bounded
+recursion to define the function $\fnnf_{1}$ in~\eqref{eq:nnf}.
+
+% ----------------------------------------------------------------------------
+% -- NNF --
+% ----------------------------------------------------------------------------
 
@@
 
+The function $\fnnf$ in~\eqref{eq:fnnf} is defined similarly as the \fstrip
+function in~\eqref{eq:strip}, the complexity measure function $\fnnf_{cm}$ is
+defined in Appendix in~\cite{Prieto-Cubides2017a}.
+
+\begin{align}
+  \label{eq:fnnf}
+ \begin{split}
+   &\fnnf : \NProp \to \NProp\\
+   &\fnnf~φ = \fnnf_{1}~φ~(\fnnf_{cm} \varphi).
+ \end{split}
+\end{align}
+
 \begin{mainlemma}
   \label{lem:nnf}
-  If $Γ ⊢ φ$ then $Γ ⟝ \fnnf~φ$, where
-  \begin{align*}
-   \begin{split}
-     &\fnnf : \NProp \to \NProp\\
-     &\fnnf~φ = \fnnf_{1}~φ~(\fnnf_{cm}~φ).
-   \end{split}
-  \end{align*}
-  The $\fnnf_{cm}$  complexity measure function
-  is defined in Appendix~\ref{app:polarity-for-propositions}.
+  If $Γ ⊢ φ$ then $Γ ⟝ \fnnf~φ$.
 \end{mainlemma}
+
+%%%
+%%% TODO: 2018-06-25 17:14
+%%%
 
@@
 \end{mainlemma}
-
-\begin{proof}
-  Composition of Lemma~\ref{lem:dist} and Lemma~\ref{lem:nnf}.
-\end{proof}
 
@@
 
-\begin{proof}\hspace{3mm}
-\begin{itemize}
-\item[∙] Case $φ ≡ ψ$. By substitution theorem we conclude $Γ ⊢ ψ$.
-\item[∙] Case $ψ ≡ \fnnf~φ$.
-\begin{equation*}
-  \begin{bprooftree}
-    \AxiomC{$Γ ⊢ φ$}
-    \RightLabel{Lemma~\ref{lem:nnf}}
-    \UnaryInfC{$Γ ⊢~\fnnf~φ$}
-    \AxiomC{$ψ ≡ \fnnf~φ$}
-    \RightLabel{\fsubst}
-    \BinaryInfC{$Γ ⊢ ψ$}
-  \end{bprooftree}
-\end{equation*}
-
-\item[∙] Case $\fcnf~ψ ≡ \freorder_{∧∨}~(\fcnf~φ)~(\fcnf~ψ)$.
-  \begin{equation*}
-    \begin{bprooftree}
-      \AxiomC{$Γ ⊢ φ$}
-      \RightLabel{Lemma~\ref{lem:cnf}}
-      \UnaryInfC{$Γ ⊢ \fcnf~φ$}
-      \RightLabel{Lemma~\ref{lem:reorder-and-or}}
-      \UnaryInfC{$Γ ⊢ \freorder_{∧∨}~(\fcnf~φ)~(\fcnf~ψ)$}
-      \AxiomC{$\fcnf~ψ~≡~\freorder_{∧∨}~(\fcnf~φ)~(\fcnf~ψ)$}
-      \RightLabel{\fsubst}
-      \BinaryInfC{$Γ ⊢ \fcnf~ψ$}
-      \RightLabel{Lemma~\ref{lem:cnf-inv}}
-      \UnaryInfC{$Γ ⊢ ψ$}
-    \end{bprooftree}
-  \end{equation*}
-\end{itemize}
-\end{proof}
-
 \end{document}

### 2018-06-25 pubs/itp-2018/sections/proof-reconstruction/resolve.tex
Attempt to realocate the resolve rule after simplify

@@
 \begin{document}
-
-% -- TODO algun texto aqui?
-
-\begin{mydefinition}
-
-A \emph{literal} is a propositional variable (positive literal) or a
-negation of a propositional variable (negative literal).
-
-\end{mydefinition}
-
-\begin{notation}
-\Lit is a synonym of \Prop to refer to literals.
-\end{notation}
-
-\begin{mydefinition}
-
-The \emph{negative normal form} of a formula is the logical
-equivalent version of it in which negations appear only in the
-literals and the formula does not contain any implications.
-
-\end{mydefinition}
-
-\begin{mydefinition}
-
-The \emph{conjunctive normal form} of a formula also called clausal
-normal form is the logical equivalent version expressed as a
-conjunction of clauses where a \emph{clause} is the disjunction of
-zero or more literals.
-\end{mydefinition}
 
@@
 
-The \resolve inference rule in combination with the \simplify rule is  the
-resolution theorem for propositional logic that we found in the \Metis \TSTP
-derivations (see this rule in~Fig.~\ref{fig:metis-inferences}). In particular,
-to reconstruct the \resolve rule following the pattern in
-Example~\ref{ex:inference-rule-pattern}, it is necessary to have a mechanism to
-test for logic equivalence between propositions. The challenge is because of we
-left out the semantics to treat only the syntax aspects of the propositional
-formulas, therefore we have to manipulate in somehow the formulas to see if they
-are logically equivalent.
+The \resolve inference rule in combination with the \simplify rule are the
+responsable rules to perform resolution. The \fresolve rules is a particular
+version of the resolution theorem for propositional logic \TSTP derivations (see
+this rule in~Fig.~\ref{fig:metis-inferences}).
 
-Our approach to address this issue mainly consists of checking for syntactical
-equality between the formulas. Firstly by converting them to their conjunctive
-normal and secondly, by performing reordering of the inner formulas of the
-resulting normal forms in the first conversion when they were not equal.
+\begin{example} In the \TSTP derivation in
+Fig.~\ref{eq:complete-example-problem}, there are two ocurrences in
+line~\ref{line14} and line~\ref{line16}~of the \resolve rule. This rule has two
+inputs: the \emph{resolvent}, a literal denoted by ℓ in~Fig.\ref{fig:metis-inferences},
+and a list of two formulas. \end{example}
 
-In~\cite{Prieto-Cubides2017a}, we make a description of the complete machinery
-we use for that purpose. For instance, we define functions of the type ($\Source
-\to  \Target \to \Prop$) like $\freorder_{∨}$ to fix the order of a disjunction
-(premise) given by the order in the literals of another disjunction (conclusion)
-if it is possible. Following the same way, we define for conjunctions the
-function $\freorder_{\wedge}$ and for conjunctive normal forms the function
-$\freorder_{\wedge\vee}$.
-
-Using reordering after applying a customized version of the
-resolution theorem defined in~\eqref{eq:rsol} we get the expected
-result.
-
-\begin{mainlemma}
-  \label{lem:rsol}
-  If $Γ ⊢ φ$ then $Γ ⊢ \frsol~φ$, where
-  \begin{equation}
-    \label{eq:rsol}
-    \begin{aligned}
-    &\frsol : \Prop \to \Prop\\
-    &\begin{array}{ll}
-      \frsol~φ &=
-        \begin{cases}
-          φ₂,      &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∧ (¬ φ₁ ∨ φ₂);\\
-          φ₂ ∨ φ₄, &\text{ if }φ ≡ (φ₁ ∨ φ₂) ∧ (¬ φ₁ ∨ φ₄);\\
-          φ, &\text{ otherwise.}
-        \end{cases}
-      \end{array}
-      \end{aligned}
-\end{equation}
-\end{mainlemma}
+In~\cite{Prieto-Cubides2017a}, we describe our first attempt to reconstruct this
+rule that performs reordering of formulas jointly with the application of a
+customized version of the resolution theorem to reconstruct the rule. We propose
+an alternative definition formulated as a particular case
+of the \fsimplify rule. We do this after seeing the behavior
+of this rule in the \TSTP derivations from a more practical point of view for
+the type-checking.
 
@@
     &\fresolve : \Source \to \Source \to \Lit \to \Target \to \Prop\\
-    &\fresolve~φ₁~φ₂~ℓ~ψ =
-      \frsol~(\freorder_{∨}~φ₁~(ℓ ∨ ψ) ∧ \freorder_{∨}~φ₂~(¬ ℓ ∨ ψ)).
+    &\fresolve~φ₁~φ₂~ℓ~ψ~=~\fsimplify~(φ₁ ∧ φ₂)~(¬ ℓ ∨ ℓ)~ψ
   \end{split}
@@
 
+%% maybe we want to show this easy proof.
+% \begin{proof}
+%   \begin{equation*}
+%   \begin{bprooftree}
+%     \AxiomC{$Γ ⊢ φ₁$}
+%     \AxiomC{$Γ ⊢ φ₂$}
+%     \RightLabel{∧-intro}
+%     \BinaryInfC{$Γ ⊢~\varphi_1~\wedge~\varphi_2$}
+%     \AxiomC{\abbre{PEM}~$\ell$}
+%     \RightLabel{Theorem~\ref{thm:simplify}.}
+%     \BinaryInfC{$\Gamma\vdash~\fsimplify~~(φ₁ ∧ φ₂)~(¬ ℓ ∨ ℓ)~ψ$}
+%   \end{bprooftree}
+%   \end{equation*}
+% \end{proof}
+
 \end{document}

### 2018-06-25 pubs/itp-2018/sections/metis-language-and-proofs.tex
Add the current output from athena for the article's problem

@@
 
-\begin{figure}
-\begin{Verbatim}[commandchars=\\\{\}, numbers=left,xleftmargin=5mm]
-fof(premise, axiom, (p ⇒ q) ∧ (q ⇒ p)).  \label{line1}
-fof(goal, conjecture, (p ∨ q) ⇒ (p ∧ q)).  \label{line2}
-fof(s₀, (p ∨ q) ⇒ p, inf(strip, goal)).  \label{line3}
-fof(s₁, ((p ∨ q) ∧ p) ⇒ q, inf(strip, goal)).  \label{line4}
-fof(neg₀, ¬ ((p ∨ q) ⇒ p), inf(negate, s₀)).  \label{line5}
-fof(n₀₀, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).  \label{line6}
-fof(n₀₁, ¬ q ∨ p, inf(conjunct, n₀₀)).  \label{line7}
-fof(n₀₂, ¬ p ∧ (p ∨ q), inf(canonicalize, neg₀)).  \label{line8}
-fof(n₀₃, p ∨ q, inf(conjunct, n₀₂)).  \label{line9}
-fof(n₀₄, ¬ p, inf(conjunct, n₀₂)).  \label{line10}
-fof(n₀₅, q, inf(simplify, [n₀₃, n₀₄])).  \label{line11}
-cnf(r₀₀, ¬ q ∨ p, inf(canonicalize, n₀₁)).  \label{line12}
-cnf(r₀₁, q, inf(canonicalize, n₀₅)).  \label{line13}
-cnf(r₀₂, p, inf(resolve, q, [r₀₁, r₀₀])).  \label{line14}
-cnf(r₀₃, ¬ p, inf(canonicalize, n₀₄)).  \label{line15}
-cnf(r₀₄, ⊥, inf(resolve, p, [r₀₂, r₀₃])).  \label{line16}
-fof(neg₁, ¬ ((p ∨ q) ∧ p) ⇒ q, inf(negate, s₁)).  \label{line17}
-fof(n₁₀, ¬ q ∧ p ∧ (p ∨ q), inf(canonicalize, neg₁)).  \label{line18}
-fof(n₁₁, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).  \label{line19}
-fof(n₁₂, ¬ p ∨ q, inf(conjunct, n₁₁)).  \label{line20}
-fof(n₁₃, ⊥, inf(simplify,[n₁₀, n₁₂])).  \label{line21}
-cnf(r₁₀, ⊥, inf(canonicalize, n₁₃)).  \label{line22}
-\end{Verbatim}
-\caption{Customized \Metis \TSTP derivation of the theorem in~\eqref{eq:complete-example-problem}.}
-\label{complete-metis-example}
-\end{figure}
+\input{sections/data/problem.tstp.tex}
 

### 2018-06-26 pubs/itp-2018/sections/proof-reconstruction/canonicalize.tex
Nice box color for equations about functions

@@
 % ----------------------------------------------------------------------------
+
+Before continuing with the remaining rules, let us mention the normal forms we
+are using for propositions and one comment about their pertinence in the
+reconstruction process.
 
@@
 function try to fix the order of a \emph{premise} disjunction given by following
-the order about the \emph{conclusion} disjunction, the target. Similarly, we
+the order of the \emph{conclusion} disjunction. Similarly, we
 define the function $\freorder_{\wedge}$ for conjunctions and the function
@@
 
-\begin{equation}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
   \label{eq:canon-or}
@@
   \end{aligned}
-\end{equation}
+\end{empheq}
+
 \end{mainlemma}
@@
 
-  \begin{equation}
+  \begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
    \label{eq:simplify-and}
@@
     \end{aligned}
-    \end{equation}
+    \end{empheq}
 \end{mainlemma}
@@
 
-\begin{equation}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
   \label{eq:nnf}
@@
   \end{aligned}
-\end{equation}
+\end{empheq}
 
@@
 
-\begin{align}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{align}
   \label{eq:fnnf}
@@
  \end{split}
-\end{align}
+\end{empheq}
 
@@
   $Γ ⟝ φ$ then $Γ ⟝ \fdist~φ$, where
-  \begin{equation*}
+  \begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation*}
   \begin{aligned}
@@
     \fdist &φ         &= φ
-   \end{array}\\
-  \text{and}\\
+   \end{array}
+   \end{aligned}
+  \end{empheq}
+and
+  \begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation*}
+  \begin{aligned}
   &\hspace{.495mm}\fdist_{∨} : \NProp \to \NProp\\
@@
    \end{aligned}
-  \end{equation*}
+ \end{empheq}
 \end{mainlemma}
@@
   If $Γ ⊢ φ$ then $Γ ⊢ \fcnf~φ$, where
-  \begin{align*}
+  \begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{align*}
     \begin{split}
@@
     \end{split}
-  \end{align*}
+  \end{empheq}
 \end{mainlemma}
@@
    Let $ψ : \Target$. If $Γ ⊢ φ$ then $Γ~⊢~\fcanonicalize~φ~ψ$, where
-  \begin{equation}
+  \begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
     \label{eq:canonicalize}
@@
      \end{aligned}
-  \end{equation}
+ \end{empheq}
 \end{mainth}

### 2018-06-26 pubs/itp-2018/sections/proof-reconstruction/strip.tex
Attempt to realocate the resolve rule after simplify
Nice box color for equations about functions

@@
 
-\begin{equation}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
   \label{eq:uh-structured}
@@
   \end{aligned}
-\end{equation}
+\end{empheq}
 \end{mainlemma}
@@
 function $\fuh : \Prop → \Prop$ for $\varphi \mapsto \fuh_{1}~φ~(\fuh_{cm}~φ)$.
-\begin{equation}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
   \label{eq:uh-complexity}
@@
   \end{aligned}
-\end{equation}
+\end{empheq}
+
 Now, we define the $\fstrip$ function in \eqref{eq:strip} in a similar way as we
@@
 % \vspace*{-5mm}
-\begin{align}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{align}
   \label{eq:strip}
@@
   \end{split}
-\end{align}
+\end{empheq}
 
@@
 
-\begin{equation}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
   \label{eq:strip-fixed}
@@
   If $Γ ⊢ φ$ and $ψ ≡ φ$ then $Γ ⊢ ψ$.
-% \begin{equation*}
-%   \label{eq:substitution-theorem}
-%   \begin{bprooftree}
-%   \AxiomC{$Γ ⊢ φ$}   \AxiomC{$ψ ≡ φ$}
-%   \RightLabel{\fsubst}
-%   \BinaryInfC{$Γ ⊢ ψ$}
-%   \end{bprooftree}
-% \end{equation*}
 \end{mainlemma}
@@
 \end{mainth}
-\begin{proof}
-\begin{equation*}
-  \begin{bprooftree}
-  \AxiomC{$ Γ ⊢ s_1 $}
-  \AxiomC{$ Γ ⊢ s_2 $}
-  \RightLabel{∧-intro}
-  \BinaryInfC{$Γ ⊢ s_1\wedge s_2$}
-  \AxiomC{$\fstrip~φ ≡ s_1\wedge s_2 $}
-  \RightLabel{By def.~\eqref{eq:strip}}
-  \UnaryInfC{$\fstrip₁~φ~(\fstrip_{cm}~\varphi) ≡ s_1\wedge s_2 $}
-  \RightLabel{\fsubst}
-  \BinaryInfC{$Γ ⊢ \fstrip₁~φ~n$}
-  \RightLabel{Lemma~\ref{lem:lem-inv-strip}}
-  \UnaryInfC{$Γ ⊢ φ$}
-\end{bprooftree}
-\end{equation*}
-\end{proof}
+% % No creo que sea necesario presentar las demostraciones
+% \begin{proof}
+% \begin{equation*}
+%   \begin{bprooftree}
+%   \AxiomC{$ Γ ⊢ s_1 $}
+%   \AxiomC{$ Γ ⊢ s_2 $}
+%   \RightLabel{∧-intro}
+%   \BinaryInfC{$Γ ⊢ s_1\wedge s_2$}
+%   \AxiomC{$\fstrip~φ ≡ s_1\wedge s_2 $}
+%   \RightLabel{By def.~\eqref{eq:strip}}
+%   \UnaryInfC{$\fstrip₁~φ~(\fstrip_{cm}~\varphi) ≡ s_1\wedge s_2 $}
+%   \RightLabel{\fsubst}
+%   \BinaryInfC{$Γ ⊢ \fstrip₁~φ~n$}
+%   \RightLabel{Lemma~\ref{lem:lem-inv-strip}}
+%   \UnaryInfC{$Γ ⊢ φ$}
+% \end{bprooftree}
+% \end{equation*}
+% \end{proof}
 
@@
 rule. This rule always ocurrs in the \TSTP derivation after the application of
-the \strip rule that introduces the subgoal.
+the \strip rule per each subgoal.
 

### 2018-06-26 pubs/itp-2018/sections/proof-reconstruction/canonicalize.tex
first complete review of the section 4

@@
 defined in \eqref{eq:canonicalize} performs normalization for a proposition.
-That is, depending on the role of the formula in the problem, it converts that
+That is, depending on the role of the formula in the problem, it converts the
 formula to its negative normal form or its conjunctive normal form. In both
-cases, \canonicalize simplifies the formula by removing tautologies inside of
-it as we widely described above for theorems in Fig.~\ref{fig:redundancies}.
-
-Based on the \Metis source code, when the formula plays the axiom or
-definition role, the \canonicalize rule transforms the source formula
-to its negative normal form. Otherwise, this rule converts the
-formula to a simplified conjunctive normal form.
-
-Since this rule mostly consists of dealing with clauses, to
-reconstruct this rule, our strategy mainly consists of checking the
-equality of negative normal form between the source and the target
-formula. If it fails, we try to reorder the conjunctive normal form
-of the source formula to match with the conjunctive normal form of
-the target formula. It definition is as follows.
+cases, the \canonicalize rule simplifies the formula by removing tautologies
+inside of it.
 

### 2018-06-26 pubs/itp-2018/sections/proof-reconstruction/clausify.tex
[ paper ] removed many examples and extra content.
[ pubs ] preparation of the paper (#60)
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp

--- 2017-12-19 paper/sections/proof-reconstruction/clausify.tex
@@
 
-The \clausify rule is a rule that transforms a formula into
-its clausal normal form but without performing simplifications of
-tautologies. Recall, this kind of conversion was already
-addressed by the \canonicalize rule. It is important to notice that
-this kind of conversions between one formula to its clausal normal
-form are not unique, and \Metis has customized approaches to perform
-that transformations. Therefore, we perform a reordering of the
-conjunctive normal form given by the $\fcnf$ function defined in
-Lemma~\ref{lem:cnf} with the $\freorder_{∧∨}$ function from
-Lemma~\ref{lem:reorder-and-or} to the input formula of the rule.
+The \clausify rule is a rule that transforms a formula into its clausal normal
+form but without performing simplifications of tautologies. Recall, this kind of
+conversion was already addressed by the \canonicalize rule. It is important to
+notice that this kind of conversions between one formula to its clausal normal
+form are not unique, and \Metis has customized approaches to perform such
+transformations.
 
-\begin{myexamplenum}
-In the following \TSTP derivation by \Metis, we see how
-\clausify transforms the \texttt{n₀} formula to get \texttt{n₁} formula.
+To address the reconstruction of this rule, we perform a
+reordering of the conjunctive normal form given by the $\fcnf$ function defined
+in Lemma~\ref{lem:cnf} with the aforementioned function  $\freorder_{∧∨}$ to the
+input formula of the rule.
+
+\begin{myexamplenum} In the following \TSTP derivation by \Metis, the \clausify
+rule transforms the \texttt{n₀} formula to get the \texttt{n₁} formula, that is
+just the application of the distribution laws.
 
@@
    Let $ψ : \Target$. If $Γ ⊢ φ$ then $Γ ⊢ \fclausify~φ~ψ$, where
-  \begin{equation*}
+  \begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation*}
   \begin{aligned}
@@
   \end{aligned}
-  \end{equation*}
+  \end{empheq}
 \end{mainth}
 
-\begin{proof}
-If $φ ≡ ψ$, $Γ ⊢ \fclausify~φ~ψ$ normalizes to $Γ ⊢ ψ$. The conclusion follows by applying the $\fsubst$ lemma. Otherwise, we use Lemma~\ref{lem:reorder-and-or} and Lemma~\ref{lem:cnf}.
-\end{proof}
-
 \end{document}

### 2018-06-26 pubs/itp-2018/sections/proof-reconstruction/simplify.tex
Nice box color for equations about functions
first complete review of the section 4

@@
 
-The \simplify rule is an inference that performs simplification of
-tautologies in a list of derivations. This rule simplifies such a list
-by transversing the list while applying Lemma~\ref{lem:canon-or},
-Lemma~\ref{lem:canon-and}, among others theorems presented in the following.
-The goal of this rule despites simplifying the list of derivations to a
-new formula (often smaller than its input formulas), consists of finding
-a contradiction.
+The \simplify rule is an inference that performs simplification of tautologies
+in a list of derivations. This rule simplifies such a list by transversing the
+list while applying Lemma~\ref{lem:simplify-or}, Lemma~\ref{lem:simplify-and},
+among others theorems presented in the following description. The goal of this
+rule despites simplifying the list of derivations to a new formula (often
+smaller than its input formulas), consists of finding a contradiction.
 
@@
 
-Since the main purpose of the \simplify rule is simplification of
-formulas, we have defined the $\freduce$ function to help removing
-the negation of a given literal $ℓ$ from a input formula.
+Since the main purpose of the \simplify rule is to simplify formulas to get
+$⊥$, we have defined the $\freduce$ function to help removing the negation
+of a given literal $ℓ$ from a input formula.
 
-\begin{equation}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
 \label{def:remove-literal}
@@
 input formula is equal to the target formula, we derive that formula.
-If some formula is $⊥$, we derive the target formula by using the
+If any formula is $⊥$, we derive the target formula by using the
 ⊥-elim inference rule.
@@
 
-\begin{equation}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
 \label{eq:simplify}

### 2018-06-27 pubs/itp-2018/sections/proof-reconstruction/canonicalize.tex
First attempt to remove complexity measure in sec4

@@
 rule returns its negative normal form. In the remaining cases, as far as we
-know, \Metis uses the \canonicalize rule to performs a sort of simplifications
-to remove the tautologies listed in~Fig.~\ref{fig:redundancies} in the
+know, \Metis uses the \canonicalize rule to perform a sort of simplifications
+to remove the tautologies listed in~Fig.~\ref{fig:redundancies} from the
 conjunctive normal form of the input formula.
@@
   \begin{aligned}
-    &\hspace{.495mm}\fnnf_{1} : \Prop \to \Nat \to \Prop\\
+    &\hspace{.495mm}\fnnf_{1} : \Prop \to \Bound \to \Prop\\
     &\begin{array}{llll}
@@
 The function $\fnnf$ in~\eqref{eq:fnnf} is defined similarly as the \fstrip
-function in~\eqref{eq:strip}, the complexity measure function $\fnnf_{cm}$ is
-defined in Appendix in~\cite{Prieto-Cubides2017a}.
+function in~\eqref{eq:strip} with a function $\fnnf_{cm}$ that finds a bound
+for its recursive calls (See its definition in Appendix in~\cite{Prieto-Cubides2017a}).
 

### 2018-06-27 pubs/itp-2018/sections/proof-reconstruction/strip.tex
First attempt to remove complexity measure in sec4

@@
 
+\begin{notation}
+$\Bound$ is a synonym for $\Nat$ type to refer to a natural number that constrains
+the number of recursive calls for the function that use it in its type.
+\end{notation}
+
 \begin{mainlemma}
   \label{lem:inv-uh-lem}
-Let be $\text{n} : \Nat$. If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$ where
+Let be $n : \Bound$. If $Γ ⊢ \fuh₁~φ~n$ then $Γ ⊢ φ$ where
 
@@
   \begin{aligned}
-  &\hspace{.495mm} \fuh_{1} : \Prop → \Nat → \Prop\\
+  &\hspace{.495mm} \fuh_{1} : \Prop → \Bound → \Prop\\
   &\begin{array}{llll}
@@
 
-The second argument in the $\fuh_1$ function is a natural number that constrains
-the number of recursive calls. To provide such a number given a formula
+To provide such a number given a formula
 $\varphi$, we call the $\fuh_{cm}$ function defined in~\eqref{eq:uh-complexity}.
-This function finds what we call the \emph{complexity measure} of the function
-$\fuh_1$. For the convenience in the following descriptions, we have the
+For the convenience in the following descriptions, we have the
 function $\fuh : \Prop → \Prop$ for $\varphi \mapsto \fuh_{1}~φ~(\fuh_{cm}~φ)$.
+
 \begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
@@
   \begin{aligned}
-    &\hspace{.495mm}\fuh_{cm} : \Prop → \Nat\\
+    &\hspace{.495mm}\fuh_{cm} : \Prop → \Bound\\
     &\begin{array}{llll}
@@
 did above for the $\fuh$ function. We have a definition of the $\fstrip₁$ function
-in~\eqref{eq:strip-fixed} and a complexity measure denoted by $\fstrip_{cm}$
-and defined in~\cite{Prieto-Cubides2017a}.
+in~\eqref{eq:strip-fixed} and a function to find its bound for its recursive calls
+by $\fstrip_{cm}$ defined in~\cite{Prieto-Cubides2017a}.
 % \vspace*{-5mm}
@@
 of the problem in the \Metis \TSTP derivations. Its definition comes mainly from
-the reading of the \Metis source code and its \TSTP derivations.
+the reading of the \Metis source code and some examples from \TSTP derivations.
 
@@
   \begin{aligned}
-  &\hspace{.495mm}\fstrip₁ : \Prop → \Nat → \Prop\\
+  &\hspace{.495mm}\fstrip₁ : \Prop → \Bound → \Prop\\
   &\begin{array}{llll}
@@
 \label{lem:lem-inv-strip}
-Let $n : \Nat$. If $Γ~⊢~\fstrip₁~φ~n$ then $Γ~⊢~φ$.
+Let $n : \Bound$. If $Γ~⊢~\fstrip₁~φ~n$ then $Γ~⊢~φ$.
 \end{mainlemma}
@@
 % $\fstrip₁~φ~n~≡~s₂∧~s₃$ where $\text{n} : \Nat$ is the complexity measure $\fstrip_{cm}$.
-If $Γ ⊢ s₂$ and $Γ ⊢ s₃$ then $Γ ⊢ φ$.
+If $Γ ⊢ s_{1}$ and $Γ ⊢ s_{2}$ then $Γ ⊢ φ$.
 \end{mainth}
+
 % % No creo que sea necesario presentar las demostraciones
@@
 refutation, to prove a subgoal, \Metis assumes its negation using the \negate
-rule. This rule always ocurrs in the \TSTP derivation after the application of
-the \strip rule per each subgoal.
+rule. We will find this rule always after the \strip rule per each subgoal in the
+\TSTP derivation.
 

### 2018-06-29 pubs/itp-2018/sections/proof-reconstruction/canonicalize.tex
Fixies of the day

@@
        φ₁,                    & \text{ if } \fcanon_{∨}~φ₂~ ≡ ⊥;\\
-       φ₁ ∨ \fcanon_{∨}~φ₂,   & \text{ otherwise.}
+       φ₁ ∨ \fcanon_{∨}~φ₂,   & \text{ otherwise,}
       \end{cases}\\
@@
             ⊥,                   & \text{ if } \fcanon_{∧}~φ₂~≡ ⊥;\\
-            φ₁ ∧ \fcanon_{∧}~φ₂, &\text{ otherwise.}
+            φ₁ ∧ \fcanon_{∧}~φ₂, &\text{ otherwise,}
           \end{cases}\\
@@
 
-Using the functions $\fcanon_{∨}$ and $\fcanon_{∧}$ we can define our function for
-the negative normal form present in \Metis, we once again formulate this version
-based on the \Metis source code to \emph{normalize} formulas. We use bounded
-recursion to define the function $\fnnf_{1}$ in~\eqref{eq:nnf}.
+Using the functions $\fcanon_{∨}$ and $\fcanon_{∧}$ we formulate the functions
+that finds the normal form based on the \Metis source code used to
+\emph{normalize} formulas. We use bounded recursion to define the function
+$\fnnf_{1}$ in~\eqref{eq:nnf}.
 
@@
     \fnnf_{1} &(¬ ⊥)         &(\suc~n) &= ⊤\\
-    \fnnf_{1} &φ             &\zero    &= φ
+    \fnnf_{1} &φ             &\zero    &= φ.
     \end{array}
@@
 
-The function $\fnnf$ in~\eqref{eq:fnnf} is defined similarly as the \fstrip
-function in~\eqref{eq:strip} with a function $\fnnf_{cm}$ that finds a bound
-for its recursive calls (See its definition in Appendix in~\cite{Prieto-Cubides2017a}).
+The function $\fnnf$ in~\eqref{eq:fnnf} is defined by using the function $\fnnf_{cm}$ encharges to find
+the bound for the recursive calls of the $\fnnf_{1}$ function. The interested reader can find the complete
+definition from Appendix in~\cite{Prieto-Cubides2017a}, we do not include it for the seek of brevity.
 

### 2018-06-29 pubs/itp-2018/sections/proof-reconstruction/resolve.tex
Nice box color for equations about functions
Fixies of the day

@@
 The \resolve inference rule in combination with the \simplify rule are the
-responsable rules to perform resolution. The \fresolve rules is a particular
-version of the resolution theorem for propositional logic \TSTP derivations (see
-this rule in~Fig.~\ref{fig:metis-inferences}).
+responsable rules to perform resolution, in particular, the \resolve rule is is
+the version of the resolution theorem showed in~Fig.~\ref{fig:metis-inferences}.
 
@@
 line~\ref{line14} and line~\ref{line16}~of the \resolve rule. This rule has two
-inputs: the \emph{resolvent}, a literal denoted by ℓ in~Fig.\ref{fig:metis-inferences},
-and a list of two formulas. \end{example}
+inputs in the following order: the \emph{resolvent} which is the literal denoted
+by ℓ in~Fig.~\ref{fig:metis-inferences} and a list formed by two formulas to
+resolve. \end{example}
 
@@
 rule that performs reordering of formulas jointly with the application of a
-customized version of the resolution theorem to reconstruct the rule. We propose
-an alternative definition formulated as a particular case
-of the \fsimplify rule. We do this after seeing the behavior
-of this rule in the \TSTP derivations from a more practical point of view for
-the type-checking.
+customized version of the resolution theorem to reconstruct the rule.
+Unfortunately, that approach suffers of an exponential computational cost for
+each searching by reordering the formulas. This time, we propose an alternative
+formulation to reconstruct this rule as a particular case of the \fsimplify rule.
+This observation was taken from the \TSTP derivations in order to improve
+the timing of the type-checking. Futher improvements are future work.
 
@@
   $Γ~⊢~φ₂$ then $Γ~⊢~\fresolve~φ₁~φ₂~ℓ~ψ$, where
-  \begin{equation}
+  \begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
   \begin{split}
@@
     &\fresolve : \Source \to \Source \to \Lit \to \Target \to \Prop\\
-    &\fresolve~φ₁~φ₂~ℓ~ψ~=~\fsimplify~(φ₁ ∧ φ₂)~(¬ ℓ ∨ ℓ)~ψ
+    &\fresolve~φ₁~φ₂~ℓ~ψ~=~\fsimplify~(φ₁ ∧ φ₂)~(¬ ℓ ∨ ℓ)~ψ.
   \end{split}
-  \end{equation}
+  \end{empheq}
 \end{mainth}

### 2018-06-30 pubs/itp-2018/sections/acknowledgements.tex
Attempt to realocate the resolve rule after simplify
First review of related work

@@
 
-The first author would like to thank to Universidad EAFIT for funding
-and supporting his master studies. He thankfully acknowledge Andreas
-Abel and Chalmers University of Technology at Goteborg, Sweden for
-inviting him to be part of the \Agda Implementors’ Meeting XXV where
-he presented part of this research. We thank Joe Leslie-Hurd for his
-support and comments about \Metis.  This research was fully supported
-by Universidad EAFIT (grant \#~690-000088).
+The authors would like to thank to Universidad EAFIT for funding and supporting
+this publication (grant \#~690-000088). We thank Joe Leslie-Hurd for his support
+and comments about \Metis.
 

### 2018-06-30 pubs/itp-2018/sections/conclusions-and-future-work.tex
First review of related work

@@
 \Metis inference rule a formal description in type theory following a
-syntactical approach. This formalizations are mainly exposed in
+syntactical approach. These formalizations are mainly exposed in
 Section~\ref{ssec:emulating-inferences}.
@@
 that generates \Agda proof-terms of \Metis derivations.
-\Agda files generated by this translator imports
+\Agda files generated by this translator calls theorems from our
 \Agda formalizations of the \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
-% We tested successful using this tool and \Agda as we
-% described in Section~\ref{sec:proof-reconstruction} over a subset of
-% propositional problems from~\cite{Prieto-Cubides2017}.
+
+% This
+% approach differs from our proof-reconstruction since we left out completely the
+% use of propositions meanings towards a future work to support other logics where
+% a syntactical approach plays an important role~(we refere the reader to
+% \cite{Agudelo-Agudelo2017} for some examples)
 
@@
 only syntactical aspects of the logic.
-This decision was in the beginning a drawback
+This decision was at the beginning a drawback
 since it demands more detailed proofs, a
@@
 
-One of the main contribution of this study was increasing the
+This study increased the
 trustworthiness of the automatic prover \Metis. Justifying a proof by

### 2018-07-25 pubs/itp-2018/sections/conclusions-and-future-work.tex
(#66) Merging revisions of the paper
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

* [ Sec4 ] example of the stri

@@
 We presented a proof-reconstruction approach in type theory for the
-propositional fragment of the \Metis prover. We provided for each
-\Metis inference rule a formal description in type theory following a
-syntactical approach. These formalizations are mainly exposed in
-Section~\ref{ssec:emulating-inferences}.
-
-We built the \Athena translator tool written in \Haskell
-that generates \Agda proof-terms of \Metis derivations.
-\Agda files generated by this translator calls theorems from our
-\Agda formalizations of the \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
+propositional fragment of the \Metis prover. In
+Section~\ref{ssec:emulating-inferences}, we provided for each \Metis inference
+rule a formal description in type theory following a syntactical approach
+type-checked in the proof-assistant \Agda in~\cite{AgdaProp,AgdaMetis}. With
+this formalization, we were able to type-check \Agda proof-terms for
+\TSTP derivations generated by \Metis. The \Agda proof-terms were generated by
+the \Athena translator~\cite{Athena}, a tool written in \Haskell.
 
@@
 
-The reconstruction approach in this study was designed to use
-only syntactical aspects of the logic.
-This decision was at the beginning a drawback
-since it demands more detailed proofs, a
-description of every transformation or deduction step performed by
-the prover, which is rarely included in the output of these programs,
-see Section~\ref{ssec:emulating-inferences}.
-Nevertheless, we chose that syntactical treatment instead of using
-semantics to extend this work towards the support of first-order
-logic or other non-classical logics.
-For first-order logic, recall satisfiability is undecidable and
-its syntactical aspect plays an important role to reconstruct proofs.
+Our approach to reconstruct the proofs for \Metis \TSTP derivations only used
+syntactical aspects of the logic. We chose that syntactical treatment instead of
+using semantics to extend this work towards the support of first-order logic or
+other non-classical logics. For instance, let us recall that
+for first-order logic, satisfiability is undecidable and its syntactical aspect
+plays an important role to reconstruct its proofs.
 
-This study increased the
-trustworthiness of the automatic prover \Metis. Justifying a proof by
-a theorem prover has a real significant impact for these automatic
-tools.  The reverse engineering task to grasp the prover
-reasoning can reveal important issues or bugs in many parts of these
-systems (\eg, preprocessing, reasoning, or deduction modules). During
-this research, we had the opportunity to contribute to \Metis by
-reporting some bugs---see Issues No.~2, No.~4, and commit
-\name{8a3f11e} in \Metis' official
-repository.\footnote{\url{https://github.com/gilith/metis}.}
-Fortunately, all these problems were fixed quickly by Hurd in
-\Metis~2.3 (release~20170822).
+Lastly, we strongly believe that by justifying proofs by theorem provers, we
+help to increase their trustworthiness. In this work, we increased the
+trustworthiness for the automatic prover \Metis. The reverse engineering to
+grasp the reasoning of a theorem prover can help to reveal issues in these
+systems maybe unkwon even for their own developers. During this research, we had
+the opportunity to contribute to \Metis by reporting some bugs---see Issues
+No.~2, No.~4, and commit \name{8a3f11e} in \Metis' official
+repository.\footnote{\url{https://github.com/gilith/metis}.} Fortunately, all
+these problems were fixed quickly by Hurd in \Metis~2.3 (release~20170822).
 \end{document}

### 2018-07-25 pubs/itp-2018/sections/proof-reconstruction.tex
Add the current output from athena for the article's problem
Nice box color for equations about functions
First attempt to remove complexity measure in sec4
(#66) Merging revisions of the paper
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict a

--- 2018-06-20 pubs/itp-2018/sections/proof-reconstruction.tex
@@
 \label{ex:inference-rule-pattern}
-Let \texttt{metisRule} be a \Metis inference rule in the \TSTP derivations.
-To reconstruct this \texttt{metisRule}, we define in the type theory
-a function preserving the name of the original rule. This function should follow
-the following pattern.
 
-\begin{equation*}
+Let \texttt{metisRule} be a \Metis inference rule in the \TSTP derivations. To
+reconstruct this \texttt{metisRule}, we define in the type theory a function
+preserving the name of the original rule. This function should follow the
+following pattern.
+
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation*}
   \begin{aligned}
@@
          &\text{rules to the premise }φ;\\
-      φ, &\text{otherwise;}
+      φ, &\text{otherwise.}
       \end{cases}
@@
   \end{aligned}
-\end{equation*}
+\end{empheq}
 
-To justify that all transformations performed by the \fun{metisRule} rule are correct, we
-will provide a theorem to show its soundness that says:
+To justify that all transformations performed by the \fun{metisRule} rule are
+correct, we will provide a theorem to show its soundness that says:
 
@@
 
-We have finished the formalization of every inference rule in
-a \Metis derivation, we are able to justify step-by-step any proof
-for a problem in propositional logic.
-For instance, we tested successfully the translation by \Athena
-jointly with the \Agda formalizations of the rules mentioned above
-with more than eighty representative theorems in propositional
-logic. An interested reader can test the
-problems~\cite{Prieto-Cubides2017} in the \Athena tool
-repository~\cite{Athena}.
+The above theorem finishes the formalization of the \Metis inference rules. At
+this point, we are able to justify step-by-step any proof in propositional logic
+generated by \Metis. Actually, we tested successfully the translation by \Athena
+jointly with the \Agda formalizations of this section against  more than eighty
+representative theorems in propositional logic. The interested reader can
+reproduce the testing of all problems from~\cite{Prieto-Cubides2017} with the
+sources of the \Athena tool repository~\cite{Athena}.
+
+%% -- TODO : Yo creo que aqui deberia ir el output de Athena...
 

### 2018-07-25 pubs/itp-2018/sections/proof-reconstruction/strip.tex
(#66) Merging revisions of the paper
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

* [ Sec4 ] example of the stri

@@
 $\Bound$ is a synonym for $\Nat$ type to refer to a natural number that constrains
-the number of recursive calls for the function that use it in its type.
+the number of recursive calls done by a function. We use this type mostly in
+the type of the function.
 \end{notation}

### 2018-07-25 pubs/itp-2018/sections/related-work.tex
(#66) Merging revisions of the paper
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

* [ Sec4 ] example of the stri

--- 2017-10-27 paper/sections/related-work.tex
@@
 
-\citeauthor{Kanso2012} in~\cite{Kanso2012,kanso2016light} presents a
-proof-reconstruction in \Agda for propositional logic. Its tool support
-proof-reconstruction for \name{EProver} and \name{Z3} ATPs following a similar work-flow as we presented in Section~\ref{ssec:workflow}.
-Nonetheless, its approach
-employs semantics for logic equivalences. We have avoided the use of
-propositions meanings towards a future work to support other logics where a
-syntactical approach plays an important role~(for an example of such logics, we
-refer the reader to \cite{Agudelo-Agudelo2017}).
-\citeauthor{foster2011integrating}~\cite{foster2011integrating} describe  the
-proof-reconstruction in \Agda for \name{Waldmeister}~\cite{hillenbrand1997}, a
-prover for pure equational logic. As far as we know, no other
-proof-reconstruction has been carried out neither in \Agda nor with \Metis prover.
+\citeauthor{Kanso2012} in~\cite{Kanso2012,kanso2016light} shows a
+proof-reconstruction in \Agda using semantics for logic equivalences for
+derivations in propositional logic generated by \name{EProver} and \name{Z3}. In
+\cite{foster2011integrating}~\citeauthor{foster2011integrating}~describe another
+proof-reconstruction in \Agda but for pure equational logic of derivations
+generated by \name{Waldmeister}~\cite{hillenbrand1997}. No other
+proof-reconstruction has been carried out neither in \Agda nor with \Metis
+prover as far as we know.
 
-Another important proof-assistant in type theory is \name{Coq}~\cite{coqteam}.
-We found the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a
-certified checker for proof witness coming from the \SMT solver
+In \name{Coq}~\cite{coqteam}, other proof-assistant closes to \Agda, we found
+the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a certified
+checker for proof witness coming from the \SMT solver
 \name{veriT}~\cite{bouton2009} and adds a new tactic named verit, that calls
-\name{veriT} on any \name{Coq} goal. Also for \name{Coq}, given a fixed but
-arbitrary first-order signature, \citeauthor{Bezem2002} in \cite{Bezem2002}
+\name{veriT} on any \name{Coq} goal. \citeauthor{Bezem2002} in~\cite{Bezem2002}
 transform a proof produced by the first-order automatic theorem prover
-\name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof-term.
+\name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof-term given a fixed but
+arbitrary first-order signature.
 
-There are some successful attempts using proof-assistants for classical logic
-instead of type theory.
-Let us mention some representative of such tools. This descriptions is
-mainly based on~\citeauthor{Sicard-Ramirez2016}~\cite{Sicard-Ramirez2016}.
+There are other successful attempts to reconstruct proofs from \ATPs but
+using proof-assistants for classical logic instead of type theory.
+Let us mention some representative tools.
 

### 2019-07-08 src/Athena/Translation/Core.hs
[ AgdaFile ] Output cosmetics

@@ -65,13 +65,13 @@ mainCore ∷ Options → IO ()
 mainCore opts = do
 
   when (optDebug opts) $
-    putStrLn ("tstp proof: " ++ show (optInputFile opts))
+    putStrLn ("TSTP proof: " ++ show (optInputFile opts))
 
   tstp ∷ [F] ← parseFile . fromJust $ optInputFile opts
 
   let conj ∷ F
       conj = fromMaybe
-        (error "Couldn't find a conjecture, or it was not unique")
+        (error "[!] Athena works only with one conjecture. ")
         (getConjeture tstp)
 
   let rulesMap ∷ ProofMap

### 2019-07-08 src/Athena/Translation/AgdaFile.hs
Fixed compilation for GHC 8.6.5  (#67)
* [ AgdaFile ] Output cosmetics

* [ Makefile ] Tested with GHC 8.6.5, Agda v2.6.0.1, Std-lib v1.1

* [ .cabal ] Fixed for GHC 8.6.5

@@ -160,7 +160,7 @@ docHeader opts = do
   version ∷ String ← progNameVersion
   return
      (  hypenline
-     <> comment (pretty version <> dot)
+     <> comment (pretty "File automatically generated by" <+> pretty version <> dot)
      <> comment (pretty "TSTP file:" <+> pretty (optInputFile opts) <> dot)
      <> hypenline <> line
      )
@@ -387,7 +387,7 @@ docProofSubgoals agdaFile =
 docProofSubgoal ∷ Int → ProofTree → AgdaFile → Doc
 docProofSubgoal n tree agdaFile =
      hypenline
-  <> comment (pretty "Proof of subgoal"<> (pretty . stdName . show) n <> dot)
+  <> comment (pretty "Proof of the subgoal"<> (pretty . stdName . show) n <> dot)
   <> hypenline
   <> line
   <> proof

### 2019-07-08 pubs/paper/sections/proof-reconstruction/resolve.tex
Renamed folder itp-2018 to paper

--- 2018-06-29 pubs/itp-2018/sections/proof-reconstruction/resolve.tex
@@
 Unfortunately, that approach suffers of an exponential computational cost for
-each searching by reordering the formulas. This time, we propose an alternative
-formulation to reconstruct this rule as a particular case of the \fsimplify rule.
-This observation was taken from the \TSTP derivations in order to improve
-the timing of the type-checking. Futher improvements are future work.
+each searching to reorder the formulas. Therefore, we propose
+in~\label{eq:resolve} an alternative formulation to reconstruct this rule by
+using the \fsimplify rule. This observation was taken from the \TSTP derivations
+and we check that improves significantly the timing of the type-checking.
 

### 2019-07-08 slides/Jonathan-Proof-Reconstruction-AIM.tex
[ slides ] AIM version backup.
[ slides ] fixed compilation

--- 2017-08-14 slides/Jonathan-Proof-Reconstruction.tex
@@
     \node[fill=plum,text=white, hyperlink node = reconstruction]
-      (go) at (0,0) {\tiny Go Back};
+      (go) at (0,0) {\tiny back};
   \end{tikzpicture}}
@@
 \usecolortheme{default}
-\usefonttheme{serif}
+% \usefonttheme{serif}
 
@@
   \hbox{%
+  % \begin{beamercolorbox}
+  %   [wd=.8\paperwidth,ht=2.3ex,dp=1ex,left]{headFoot}%
+  %   \hspace*{2ex}\textbf\insertshorttitle\hspace*{2mm}|
+  %   \hspace*{2mm}\textbf\insertshortauthor
+  % \end{beamercolorbox}%
   \begin{beamercolorbox}
-    [wd=.8\paperwidth,ht=2.3ex,dp=1ex,left]{headFoot}%
-    \hspace*{2ex}\textbf\insertshorttitle\hspace*{2mm}|
-    \hspace*{2mm}\textbf\insertshortauthor
-  \end{beamercolorbox}%
-  \begin{beamercolorbox}
-    [wd=.2\paperwidth,ht=2.3ex,dp=1ex,right]{headFoot}%
+    [wd=\paperwidth,ht=2.4ex,dp=1ex,right]{headFoot}%
     \insertframenumber{}/\inserttotalframenumber\hspace*{2ex}
@@
 }
+
+% \setbeamertemplate{footline}{
+%   \leavevmode%
+%   \hbox{%
+%   \begin{beamercolorbox}
+%     [wd=.8\paperwidth,ht=2.3ex,dp=1ex,left]{headFoot}%
+%     \hspace*{2ex}\textbf\insertshorttitle\hspace*{2mm}|
+%     \hspace*{2mm}\textbf\insertshortauthor
+%   \end{beamercolorbox}%
+%   \begin{beamercolorbox}
+%     [wd=.2\paperwidth,ht=2.3ex,dp=1ex,right]{headFoot}%
+%     \insertframenumber{}/\inserttotalframenumber\hspace*{2ex}
+%   \end{beamercolorbox}}%
+%   \vskip 0pt%
+% }
 
@@
 \usefonttheme{professionalfonts}
-\usefonttheme{serif}
+% \usefonttheme{serif}
+
 \usepackage{fontspec}
@@
 
-\newfontfamily\djvu[ExternalLocation=fonts/
-  , BoldFont=DejaVuSansMono-Bold.ttf
-  , BoldItalicFont=DejaVuSansMono-BoldOblique.ttf
-  , ItalicFont=DejaVuSansMono-Oblique.ttf
-  ]{DejaVuSansMono.ttf}
-
-\setmonofont[ExternalLocation=fonts/
-, BoldFont=DejaVuSansMono-Bold.ttf
-, BoldItalicFont=DejaVuSansMono-BoldOblique.ttf
-, ItalicFont=DejaVuSansMono-Oblique.ttf
-]{DejaVuSansMono.ttf}
-
-\setmathfont[ExternalLocation=fonts/
-  ]{DejaVuMathTeXGyre.ttf}
-\newfontfamily\mathfont{fonts/DejaVuMathTeXGyre.ttf}
-
-\setmainfont[ExternalLocation=fonts/
-  , BoldFont=SourceSansPro-Semibold.otf
-  , BoldItalicFont=SourceSansPro-SemiboldIt.otf
-  , ItalicFont=SourceSansPro-It.otf
-  ]{SourceSansPro-Regular.otf}
-
-\newfontfamily\sourcecode[ExternalLocation=fonts/
-  , BoldFont=SourceCodePro-Semibold.ttf
-  , BoldItalicFont=SourceCodePro-SemiboldIt.ttf
-  , ItalicFont=SourceCodePro-It.ttf
-  ]{SourceCodePro-Regular.ttf}
-
-,
+\usepackage{minted}
 
@@
 \newsavebox\agdapragma
+
+\renewcommand*\rmdefault{cmr}
+
+% -------------------------------------------------------------------
+% New commands
+% -------------------------------------------------------------------
+
+\usepackage{textcomp}
+\usepackage[verbose]{newunicodechar}
+
+\newunicodechar{¬}{\ensuremath{\neg}\;}
+\newunicodechar{Γ}{\ensuremath{\Gamma}}
+\newunicodechar{γ}{\ensuremath{\gamma}}
+\newunicodechar{φ}{\ensuremath{\varphi}}
+\newunicodechar{ψ}{\ensuremath{\psi}}
+\newunicodechar{ϕ}{\ensuremath{\varphi}}
+\newunicodechar{ᵢ}{\ensuremath{{}_{i}}}
+\newunicodechar{₀}{\ensuremath{{}_{0}}}
+\newunicodechar{₁}{\ensuremath{{}_{1}}}
+\newunicodechar{₂}{\ensuremath{{}_{2}}}
+\newunicodechar{₃}{\ensuremath{{}_{3}}}
+\newunicodechar{₄}{\ensuremath{{}_{4}}}
+\newunicodechar{₅}{\ensuremath{{}_{5}}}
+\newunicodechar{₆}{\ensuremath{{}_{6}}}
+\newunicodechar{₇}{\ensuremath{{}_{7}}}
+\newunicodechar{₈}{\ensuremath{{}_{8}}}
+\newunicodechar{₉}{\ensuremath{{}_{9}}}
+\newunicodechar{ₙ}{\ensuremath{{}_{n}}}
+\newunicodechar{ₘ}{\ensuremath{{}_{m}}}
+\newunicodechar{ℓ}{\ensuremath{\ell}}
+\newunicodechar{→}{\ensuremath{\rightarrow}}
+\newunicodechar{⇒}{\ensuremath{\supset}}
+\newunicodechar{⊃}{\ensuremath{\supset}}
+\newunicodechar{⇔}{\ensuremath{\Leftrightarrow}}
+\newunicodechar{∅}{\ensuremath{\emptyset}}
+\newunicodechar{∈}{\ensuremath{\in}}
+\newunicodechar{∀}{\ensuremath{\forall}}
+\newunicodechar{∘}{\ensuremath{\circ}}
+\newunicodechar{∙}{\ensuremath{\bullet}}
+\newunicodechar{∧}{\ensuremath{\wedge}}
+\newunicodechar{∨}{\ensuremath{\vee}}
+\newunicodechar{∼}{\ensuremath{\sim}}
+\newunicodechar{≠}{\ensuremath{\neq}}
+\newunicodechar{≡}{\ensuremath{\equiv}}
+\newunicodechar{⊕}{\ensuremath{\oplus}}
+\newunicodechar{⊖}{\ensuremath{\ominus}}
+\newunicodechar{⊢}{\ensuremath{⊢}}
+\newunicodechar{⊤}{\ensuremath{\top}}
+\newunicodechar{⊥}{\ensuremath{\bot}}
+\newunicodechar{⊻}{\ensuremath{\veebar}}
+\newunicodechar{⟝}{\ensuremath{⊢}}
+\newunicodechar{⬓}{\ensuremath{\square}}
+\newunicodechar{ⱼ}{\ensuremath{{}_{j}}}
+\newunicodechar{λ}{\ensuremath{\lambda}}
+
+\usepackage{xspace}
+
+\newcommand{\abbre}[1]{\textsc{#1}\xspace}
+\newcommand{\ATPs}{\abbre{ATPs}}
+\newcommand{\ATP}{\abbre{ATP}}
+\newcommand{\Bool}{\abbre{Bool}}
+\newcommand{\CNF}{\abbre{CNF}}
+\newcommand{\CPL}{\abbre{CPL}}
+\newcommand{\ITP}{\abbre{ITP}}
+\newcommand{\ITPs}{\abbre{ITPs}}
+\newcommand{\List}{\abbre{List}}
+\newcommand{\SAT}{\abbre{SAT}}
+\newcommand{\SMT}{\abbre{SMT}}
+
+\newcommand{\name}[1]{\texttt{#1}\xspace}
+\newcommand{\canonicalize}{\name{canonicalize}}
+\newcommand{\clausify}{\name{clausify}}
+\newcommand{\conjunct}{\name{conjunct}}
+\newcommand{\negate}{\name{negate}}
+\newcommand{\resolve}{\name{resolve}}
+\newcommand{\simplify}{\name{simplify}}
+\newcommand{\strip}{\name{strip}}
+\newcommand{\tptpaxiom}{\name{axiom}}
+\newcommand{\tptpconjecture}{\name{conjecture}}
+
+\newcommand{\nnf}{\name{nnf}}
+
+\newcommand{\prg}[1]{\texttt{#1}\xspace}
+\newcommand{\Agda}{\prg{Agda}}
+\newcommand{\Athena}{\prg{Athena}}
+\newcommand{\IsabelleHOL}{\prg{IsabelleHOL}}
+\newcommand{\Metis}{\prg{Metis}}
+
+\newcommand{\len}[1]{\texttt{#1}\xspace}
+\newcommand{\Haskell}{\len{Haskell}}
+\newcommand{\TPTP}{\len{TPTP}}
+\newcommand{\TSTP}{\len{TSTP}}
+
+% -- Type notation.
+\newcommand{\type}[1]{ {\fontseries{sb}\selectfont \textsf{#1}} \xspace}
+\newcommand{\NProp}{\type{Prop}}
+\newcommand{\Nat}{\type{Nat}}
+\newcommand{\Prop}{\type{Prop}}
+\newcommand{\Source}{\type{Premise}}
+\newcommand{\Target}{\type{Conclusion}}
+\newcommand{\Lit}{\type{Lit}}
+% --
+
+\newcommand{\NN}{\ensuremath{\mathbb{N}}}
+\newcommand{\fun}[1]{ {\fontseries{sb}\selectfont \textsf{#1}} \xspace}
+
+\newcommand{\zero}{\fun{zero}}
+\newcommand{\suc}{\fun{succ}}
+\newcommand{\fassoc}{\fun{assoc}}
+\newcommand{\fbuild}{\fun{build}}
+\newcommand{\fcanonicalize}{\fun{canonicalize}}
+\newcommand{\fcanon}{\fun{simplify}}
+\newcommand{\fclausify}{\fun{clausify}}
+\newcommand{\fcnf}{\fun{cnf}}
+\newcommand{\fconjunctor}{\fun{disj}}
+\newcommand{\fconjunct}{\fun{conjunct}}
+\newcommand{\fdist}{\fun{dist}}
+\newcommand{\ffactor}{\fun{factor}}
+\newcommand{\fform}{\fun{form}}
+\newcommand{\fmax}{\fun{max}}
+\newcommand{\fndisj}{\fun{ndisj}}
+\newcommand{\fnegate}{\fun{negate}}
+\newcommand{\fnnfp}{\fun{nnf}₀}
+\newcommand{\fnnf}{\fun{nnf}}
+\newcommand{\fpolarity}{\fun{polarity}}
+\newcommand{\frank}{\fun{rank}}
+\newcommand{\frconj}{\fun{rconj}}
+\newcommand{\frdisj}{\fun{rdisj}}
+\newcommand{\freorder}{\fun{reorder}}
+\newcommand{\fresolve}{\fun{resolve}}
+\newcommand{\frm}{\fun{rm}}
+\newcommand{\frsol}{\fun{rsol}}
+\newcommand{\fsbuild}{\fun{sbuild}}
+\newcommand{\fsimplify}{\fun{simplify}}
+\newcommand{\fstripp}{\fun{strip}\prime}
+\newcommand{\fstrip}{\fun{strip}}
+\newcommand{\fsubst}{\fun{subst}}
+\newcommand{\fuh}{\fun{uh}}
+
+% latin etc. abbrev
+\newcommand{\abbrev}[1]{#1} % alternative: \emph{#1}
+\newcommand{\cf}{\abbrev{cf.}\ }
+\newcommand{\eg}{\abbrev{e.\,g.}}
+\newcommand{\Eg}{\abbrev{E.\,g.}}
+\newcommand{\ie}{\abbrev{i.\,e.}}
+\newcommand{\Ie}{\abbrev{I.\,e.}}
+\newcommand{\etal}{\abbrev{et.\,al.}}
+\newcommand{\wwlog}{w.\,l.\,o.\,g.} % \wlog is ``write into log file''
+\newcommand{\Wlog}{W.\,l.\,o.\,g.}
+\newcommand{\wrt}{w.\,r.\,t.}
+\newcommand{\TheEnd}{\\\hspace*{0.975\textwidth}$\blacksquare$}
 
@@
    \begin{center}
-\begin{tptp}
+
+\begin{verbatim}
 language(name, role, formula).
-\end{tptp}
+\end{verbatim}
+
     \end{center}
@@
   \item $p ⊢ p$
-\begin{tptp}
+\begin{verbatim}
 fof(myaxiom, axiom, p).
 fof(goal, conjecture, p).
-\end{tptp}
+\end{verbatim}
 
   \item $⊢ ¬ (p ∧ ¬ p) ∨ (q ∧ ¬ q)$
-\begin{tptp}
+\begin{verbatim}
 fof(goal, conjecture, ~ ((p & ~ p) | (q & ~ q))).
-\end{tptp}
+\end{verbatim}
   \end{itemize}
@@
   {\footnotesize
-\begin{tptp}
+\begin{verbatim}
 language(name, role, formula, source [,useful info]).
-\end{tptp}}
+\end{verbatim}}
 \end{center}
@@
 {\footnotesize
-\begin{tptp}
+\begin{verbatim}
 inference(rule, useful info, parents).
-\end{tptp}
+\end{verbatim}
 }
@@
   \item Proof found by \texttt{Metis} for the problem $p ⊢ p$
-{\small
-\begin{tptp}
+
+{\footnotesize
+\begin{verbatim}
 $ metis --show proof problem.tptp
@@
     inference(canonicalize, [], [normalize_0_2])).
-\end{tptp}
+\end{verbatim}
 }
@@
 
-Is a \texttt{Haskell} program
+Is a \texttt{agda} program
 that translates proofs given by \texttt{Metis}
@@
 
-\begin{minted}{cagda}
+\begin{minted}{agda}
 data Prop : Set where
@@
   \vspace*{1mm}
-\begin{minted}{cagda}
+\begin{minted}{agda}
 data _⊢_ : (Γ : Ctxt)(φ : Prop) → Set
@@
 
-\begin{minted}{cagda}
+\begin{minted}{agda}
 assume, axiom, weaken, ⊤-intro, ⊥-elim, ¬-intro,
@@
   \vspace*{1mm}
-\begin{minted}{cagda}
+\begin{minted}{agda}
 ⇔-equiv, ⇔-assoc, ⇔-comm, ⇒-⇔-¬∨, ⇔-¬-to-¬,
@@
 
-\begin{minted}{cagda}
+{\footnotesize
+\begin{minted}{agda}
 data ConjView : Prop → Set where
@@
 ... | true  = path ∷ʳ pick
-... | false with conj-view φ
+... | false 
+    with conj-view φ
 ...    | other _ = []
@@
 \end{minted}
-
+}
 \end{frame}
@@
 \vfill
-\begin{minted}{cagda}
+{\footnotesize
+\begin{minted}{agda}
 conjunct : Prop → Prop → Prop
@@
 \end{minted}
+}
 \vfill
@@
   \item In \texttt{TPTP} format
-\begin{tptp}
+\begin{verbatim}
 $ cat problem.tptp
@@
 fof(goal, conjecture, q & p).
-\end{tptp}
+\end{verbatim}
   \item How to use Athena with your problem
 
-\begin{tptp}
+\begin{verbatim}
 $ metis --show proof problem.tptp > problem.tstp
@@
 $ agda problem.tstp
-\end{tptp}
+\end{verbatim}
 \end{itemize}
@@
 \begin{frame}[fragile, allowframebreaks]{\texttt{TSTP} Derivation given by \texttt{Metis}}
-\begin{tptp}
+
+\begin{verbatim}
 fof(a, axiom, p & q).
@@
     inference(canonicalize, [], [normalize_1_4])).
-\end{tptp}
+\end{verbatim}
 \end{frame}
@@
 \vfill
-\begin{minted}{cagda}
+\begin{minted}{agda}
 p, q, a, goal, subgoal₀, subgoal₁ : Prop
@@
 \vfill
-\begin{minted}{cagda}
+{\footnotesize
+\begin{minted}{agda}
 a : Prop
@@
 \vfill
-\begin{minted}{cagda}
+{\footnotesize
+\begin{minted}{agda}
 subgoal₁ : Prop
@@
 \vfill
-\begin{minted}{cagda}
+{\footnotesize
+\begin{minted}{agda}
 -- Premise.
@@
 % {}
-\begin{tptp}
+{\footnotesize 
+\begin{verbatim}
 $ cat problem.tptp
@@
   ((p <=> q) <=> r) <=> (p <=> (q <=> r))).
-\end{tptp}
-\begin{tptp}
+\end{verbatim}
+}
+
+{\footnotesize
+\begin{verbatim}
 $ metis --show proof problem.tptp
@@
 ...
-\end{tptp}
+\end{verbatim}
+}
 \end{frame}
@@
 \only<1>{
-\inputminted{cagda}{Or.agda}
+\inputminted{agda}{Or.agda}
 \begin{tikzpicture}[overlay, remember picture, scale=0.5]
@@
     \node[fill=plum,text=white, hyperlink node = metis]
-      (go) at (0,0) {\tiny Go Back};
+      (go) at (0,0) {\tiny back};
   \end{tikzpicture}

### 2019-07-09 pubs/paper/sections/02-introduction.tex
Many revisions and fixes.

--- 2018-02-23 pubs/itp-2018/sections/introduction.tex
@@
-\documentclass[../main.tex]{subfiles}
+\documentclass[../paper.tex]{subfiles}
 \begin{document}
@@
 intends to prove conjectures from axioms and inference rules of some
-logical system. In the last decades, \ATPs are fast becoming a key
-instrument in different disciplines and real applications (\eg,
-verifying a railway interlocking system, an operating-system kernel,
-or a pseudo-random number generator). Since some
-programming errors have been found in these programs (see, for
-example, \cite{Keller2013,Bohme2011,Fleury2014}), researchers and
-users from academy and industry have shown an increased interest to
-\emph{formally} prove the validity of \ATPs' results.
+logical system. In the last decades, \ATPs are quickly becoming a key
+instrument in many disciplines and real applications (\eg, verifying a
+railway interlocking system, an operating-system kernel, or a
+pseudo-random number generator). Since some programming errors have
+been found in these programs (see, for example,
+\cite{Keller2013,Bohme2011,Fleury2014}), researchers and users from
+academia and industry have shown an increased interest in
+\emph{formally} proving the validity of \ATPs' results.
 
-In order to give confidence to the \ATP users many of these systems
-have started to include in their outputs the full derivations
+In order to give confidence to the users of the \ATP, many of these
+systems have started to include in their outputs the full derivations
 associated to the proved theorems. However, existing research
@@
 Proof-reconstruction addresses this problem. Since many \ATPs are
-poor-documented, this problem becomes in mostly cases a reverse
-engineering task to verify the prover reasoning. The usual is the
+poor-documented, this problem becomes a reverse
+engineering task to verify the prover reasoning. Usually, is the
 reconstruction is made by another and not by the developers of the
@@
 
-To verify such automatically generated derivation by the prover,
-it is convenient to have them in a
-consistent format, that is, a full script describing the derivation
-step-by-step with  exhaustive details and without ambiguities. For
-example, for classical propositional logic (henceforth \CPL) from a
-list of at least forty \ATPs---available from the Web service
-\name{SystemOnTPTP} of the TPTP World\footnote{\url{http://www.cs.miami.edu/~tptp/}.}---just few of
-them show their proofs.
+To verify such automatically generated derivations by the prover, it
+is convenient to have them in a consistent format, that is, a full
+script describing the derivation step-by-step with  exhaustive details
+and without ambiguities. For example, from a list of at least forty
+\ATPs for classical propositional logic (henceforth \CPL) ---available
+from the Web service \name{SystemOnTPTP} of the TPTP
+World\footnote{\url{http://www.cs.miami.edu/~tptp/}.}--- just few of
+them show proofs when they find the conjecture of the problem is a 
+theorem.
 
@@
 \emph{target} system. The target system is the
-proof \emph{checker} in charge to verify the source system reasoning
+\emph{proof-checker} in charge of verifying the source system reasoning
 for each derivation.
@@
 prover~\cite{hurd2003first}---our source system---in Martin-Löf type
-theory~\cite{Nordstrom-Petersson-Smith-1990}. We
-formalize the subset of the \Metis inference rules for the
-propositional logic fragment using a syntactical treatment.
-The \Metis reasoning was formalized in
-\Agda~\cite{agdateam}---our target system---in two
-libraries~\cite{AgdaProp,AgdaMetis} and we implemented a
-proof-reconstruction tool named \Athena~\cite{Athena} written in
+theory~\cite{Nordstrom-Petersson-Smith-1990}. To do so, we only  take
+into account the syntax rather than the semantics of the subset of the
+\Metis inference rules for the propositional logic fragment. The
+\Metis reasoning was formalized in \Agda~\cite{agdateam}---our target
+system---in two libraries~\cite{AgdaProp,AgdaMetis} and we implemented
+a proof-reconstruction tool named \Athena~\cite{Athena} written in
 \Haskell that is able to generate \Agda proof-terms for \Metis
-derivations. During writing this document, our formalization helps to report
-two programming errors in \Metis.
-A bug\footnote{Issue No.\,2 at \url{https://github.com/gilith/metis/issues/2}}
-in the printing of the derivation and a soundness
-bug\footnote{Issue No.\,4 at \url{https://github.com/gilith/metis/issues/4}} in the stripping of the goal.
+derivations.  In the course of this work, we uncovered and reported
+two programming errors in the ATP \Metis: a bug\footnote{Issue No.\,2
+at \url{https://github.com/gilith/metis/issues/2}} in the printing of
+the derivation and a soundness bug\footnote{Issue No.\,4 at
+\url{https://github.com/gilith/metis/issues/4}} in the stripping of
+the goal.
 
-This paper has been organized in the following way.  In
+This paper is organized in the following way: in
 Section~\ref{sec:type-theory}, some limitations of type theory are
@@
 prover.  In Section~\ref{sec:proof-reconstruction}, we show our
-approach to reconstruct \Metis derivations.  Related work is described in
-Section~\ref{sec:related-work}.  Conclusions and suggestions for
+approach to reconstruct \Metis derivations.  Related work is described
+in Section~\ref{sec:related-work}.  Conclusions and suggestions for
 future work are presented in Section~\ref{sec:conclusions}.
@@
 
-The proof-reconstruction tool \Athena was tested with \prg{GHC}~8.2.2.
-Both libraries, \verb!agda-prop! and \verb!agda-metis! were tested with
-\Agda~2.5.3 and \Agda standard library~0.14.
-\Athena jointly with \verb!agda-prop! and \verb!agda-metis! are able
-to reconstruct propositional proofs of \Metis~2.3 (release~20171021).
-We successfully reconstruct around eighty theorems in classical propositional
-logic from the \TPTP collection~\cite{Prieto-Cubides2017} to test
-the developments and the formalization presented in this research.
+The proof-reconstruction tool \Athena was tested with
+\prg{GHC}~v8.6.5. Both libraries, \verb!agda-prop! and
+\verb!agda-metis! were tested with \Agda~v2.6.0.1 and \Agda standard
+library~v1.1. \Athena jointly with \verb!agda-prop! and
+\verb!agda-metis! are able to reconstruct propositional proofs of
+\Metis~v2.4.20180810. We successfully reconstructed eighty theorems in
+classical propositional logic from the \TPTP
+collection~\cite{Prieto-Cubides2017} to test the developments and the
+formalization presented in this research.
 

### 2019-07-09 pubs/paper/sections/03-type-theory.tex
Many revisions and fixes.

--- 2018-01-03 pubs/thesis/sections/type-theory.tex
@@
 
-% It was proposed in 1902 to avoid Russell's paradox --- (bettter mention BHK)
-Type theory is a formalism for the foundation of mathematics,
-it has became in a key instrument to study logic and proof theory
-that follows the same basis of constructive mathematics where the witness of a statement is \emph{everything}.
-In that direction, we could say the main actors in type theory are the statements and their proofs.
+Type theory is a formalism for the foundation of mathematics. It has
+become a key instrument to study logic and proof theory, and follows
+the same basis of constructive mathematics where the witnesses of a
+statement, the proofs, have a fundamental role as same as their
+statement.
 
-By following the Curry-Howard correspondence (see, for
+Following the Curry-Howard correspondence (see, for
 example,~\cite{Wadler-2015}), a formula corresponds to a \emph{type},
 and one proof of that formula is a \emph{term} of the correspondent
-type. Therefore, inhabitants types are such formulas with proofs, they are theorems.
+type. Therefore, inhabited types are such formulas with proofs, they
+are theorems.
 
-Since type theory is a formal system, we have a syntax and a set of
-derivation rules. These rules enables us to derive a kind of
-conclusions called \emph{judgments}. A judgment is another way to say
-that a term has a certain type. Each term has associated a derivation,
-we refer to this derivation as proof-terms.
+Type theory is a formal system with a syntax and a set of derivation
+rules. These rules enables us to derive conclusions called
+\emph{judgments} which can be seen as derivation
+trees~\cite{Bezem2002}.  Each term has associated a derivation and we
+refer to these derivations as \emph{proof-terms}.
 
@@
 
-  We write the type judgments as $a : \type{A}$ to denote that the
+  We write the typing judgments as $a : \type{A}$ to denote that the
   term~$a$ is of type~$\type{A}$.
@@
 
-We produce derivation trees inside the judgments using the derivation
-rules. Since type theory can be seen as typed $λ$-calculus with
+Type theory can be seen as typed $λ$-calculus with
 dependent function types, evaluation of $λ$-terms also called
-\emph{normalization} of the proof-terms, is a process of reductions with the system inference rules.
+\emph{normalization} of the proof-terms, is a process of reductions
+with the system inference rules. Therefore, the proof verification
+task becomes in type theory as verifying that the proof-term has the
+correspondent type of the theorem. We refer to this process as
+\emph{type-checking}.
 
-Therefore, the proof verification task becomes in type theory as
-verifying that the proof-term has the correspondent type of the
-theorem. We know this process as \emph{type-checking}.
-This feature of type theory allow us to verify a proof generated by an \ATP by reconstructing its proof-term to type-check the proof. For such a
-purpose, we use a proof-assistant based on type theory like \Agda to
-delegate this task. % However, this approach has some weak points
-discussed in~\cite{Bezem2002}. Some limitations from the type theory
-point of view for proof-reconstruction is described in
-Section~\ref{ssec:structural-recursion} and
+This feature of type theory allow us to verify a proof generated by an
+\ATP by reconstructing its proof-term to type-check the proof. For
+such a purpose, we use a proof-assistant based on type theory, \Agda,
+to delegate this task as in~\cite{Bezem2002}. Some limitations
+of the type theory point-of-view for proof-reconstruction is described
+in Section~\ref{ssec:structural-recursion} and
 Section~\ref{ssec:intuitionistic-logic}.
@@
 
-To reconstruct \Metis inference rules in type theory, we observed
-that some rules or their inner functions are implemented by
-\emph{general recursive} functions (see a definition of these functions in~\cite{Bove2002}).
+To reconstruct \Metis inference rules in type theory, we observed that
+some rules or their inner functions are implemented by \emph{general
+recursive} functions (see the definition of these functions
+in~\cite{Bove2002}).
 
 Functions defined by a general recursion can not be directly
-translated in type theory since it is not a guarantee they terminate.
+translated in type theory since it is not guaranteed that they terminate.
 For that reason, we follow the technique described
@@
 
-A recursive function is structurally recursive if it calls itself
-with only structurally smaller arguments~\cite{Abel2002}.
-General recursive functions can be rewrote into structurally
-recursive functions by  using for instance, the
-\emph{bounded recursion} technique. For a yet another methods, we refer the
-reader to \cite{Coquand1992,Abel2002,Bove2005}.
+A recursive function is structurally recursive if it calls itself with
+only structurally smaller arguments~\cite{Abel2002}. General recursive
+functions can sometimes be rewritten into structurally recursive
+functions by  using for instance, the \emph{bounded recursion}
+technique or other methods as in \cite{Coquand1992,Abel2002,Bove2005}.
 
-The bounded technique defines a new structural recursive function
+The bounded recursion technique defines a new structural recursive function
 based on the general recursive function by adding an argument. The
@@
 \begin{notation}
-  We use \Prop for the type of propositions.
-  A proposition is an expression of indivisible propositional variables (\eg, symbols $φ₀, φ₁, \dots$), and the logic constants:
-  $⊥$, $⊤$, the binary connectives ($∧, ∨, ⇒)$, and the negation
-  $(\neg)$. We use the inductive definition for propositions presented in~\cite{VanDalen1994}.
 
-  We write the syntactical equality between two propositions φ and ψ using the symbol (≡) as $φ ≡ ψ$. For this equality, we assume the reflexivity, symmetry and
-  transitivity properties.
+We define \Prop for the type of propositions. A proposition is an
+expression of indivisible propositional variables (\eg, symbols $φ₀,
+φ₁, \dots$), and the logic constants: $⊥$, $⊤$, the binary connectives
+($∧, ∨, ⇒)$, and the negation $(\neg)$. We use the inductive
+definition for propositions presented in~\cite{VanDalen1994}. The
+syntactical equality between two propositions φ and ψ is written using
+the symbol (≡) as $φ ≡ ψ$. This equality between propositions is
+precisely the Identity type $\mathsf{Id}_{\Prop}(φ, ψ)$ in Martin-Löf
+type theory. Therefore, it holds the reflexivity, symmetry and
+transitivity property for equality. The type of natural numbers is
+called \Nat, and it is defined as usual, \ie, $\zero$ and $\suc$ are
+its data constructors. We use names and symbols for the arithmetic
+operations as usual (\eg, $+$, $-$, $*$). We use syntax sugar for
+$\zero$, $\suc$, $\suc~\zero$, $\dots$, with the decimal
+representation~$0$, $1$, $2$, $\dots$ as well.
 
-  The type of natural numbers is called \Nat,
-  and it is defined as usual, \ie, $\zero$ and $\suc$ are its data
-  constructors. We use names and symbols for the arithmetic
-  operations as usual (\eg, $+$, $-$, $*$).
-  We use syntax sugar for $\zero$, $\suc$,
-  $\suc~\zero$, $\dots$, with the decimal representation~$0$, $1$,
-  $2$, $\dots$ as well.
 \end{notation}
 
-Hence, one approach to define a structural recursive function based
-on a general
-recursive function $f₀ : \type{A} \to \type{B}$ is to
-formulate a new
-function $f₁ : \type{A} \to \Nat \to \type{B}$ where all
-of its recursive calls are done on smaller arguments.
+Hence, one approach to define a structural recursive function based on
+a general recursive function $f₀ : \type{A} \to \type{B}$ is to
+formulate a new function $f₁ : \type{A} \to \Nat \to \type{B}$ where
+all of its recursive calls are done with \emph{smaller} values on its
+second argument~\cite{Abel2002}.
 
@@
 In the latter definitions and theorems, we  use a common notation in
-type theory, pattern-matching~\cite{Coquand1992} to define functions by cases on the inductive definition for the type of the arguments.
+type theory, pattern-matching~\cite{Coquand1992} to define functions by
+cases on the inductive definition for the type of the arguments.
 \end{notation}
@@
 
-\begin{equation}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation}
   \label{eq:uh-definition}
@@
   \end{aligned}
-\end{equation}
+  \end{empheq}
 
-In~\eqref{eq:uh-definition}, the first two equations in the $\fuh_{0}$ function definition are no structurally recursive.
-Note that the formula used in the recursive calls are not subformulas
-of the formula in the function argument.
-
-% TODO
-% , the first two equations
-% call on arguments no structurally smaller.
-% For instance, in the first equation,
-% $$\fuh_{0} (φ₁ ⇒ (φ₂ ⇒ φ₃)) = \fuh_{0}~((φ₁ ∧ φ₂) ⇒ φ₃),$$
-% the function $\fuh_{0}$ calls on the argument $(φ₁ ∧ φ₂) ⇒ φ₃$ argument. However, this formula is not a subformula of $φ₁ ⇒ (φ₂ ⇒ φ₃)$.
-
-Therefore, one way to define $\fuh_{0}$ in type
+In~\eqref{eq:uh-definition}, the first two equations in the $\fuh_{0}$
+function definition are not structurally recursive. As a consequence,
+we could not use this function in \Agda which would report a
+non-terminating error. This happens because the formula used in the
+recursive calls are not subformulas of the input formula in the
+function argument. Therefore, one way to define $\fuh_{0}$ in type
 theory is to define a new function using a bounded recursion.
 
-\begin{equation}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation*}
 \label{eq:uh-structured}
@@
   \end{aligned}
-\end{equation}
+\end{empheq}
 
 We bounded the recursion calls of the $\fuh_{0}$ function using its
-\emph{complexity measure}.
-
-The complexity measure of a function is the number of steps the
-function takes to finish. Since the $\fuh_{0}$ function is recursive,
-we can define its complexity measure by defining a recursive function
-instead of a closed formula for such a number. However, this function
-must to be structurally recursive as well and can be defined by
-following the pattern-matching cases of its definition.
-
-Therefore, we define in~\eqref{eq:uh-complexity} the complexity
-measure function of $\fuh_{0}$ by assigning the number of steps to
-finish for each pattern-matching case.
+\emph{complexity measure}. We refer to the complexity measure of a
+function as the number of steps the function takes to finish. Since
+the $\fuh_{0}$ function is recursive, we can define its complexity
+measure by defining a recursive function instead of a closed formula
+for such a number. However, this function must to be structurally
+recursive as well, and it can be defined by following the
+pattern-matching cases of its definition. Thus,  the complexity
+measure of the $\fuh_{0}$ function can be defined as follows.
 
@@
 
-We have used the complexity measure definition for a formula defined in~\cite{Agudelo-Agudelo2017} to define other complexity measures
-in this paper.
+% We have used the complexity measure definition for a formula defined
+% in~\cite{Agudelo-Agudelo2017} to define other complexity measures in
+% this paper.
 
-\begin{equation}
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation*}
   \label{eq:uh-complexity}
@@
   \end{aligned}
-\end{equation}
+\end{empheq}
 
-Following the technique mentioned above, we define the
-function~$\fuh$, the structural
-recursive definition of the function~$\fuh_{0}$.
-\begin{align*}
+Finally, we are able to define the $\fuh$ function which is the
+structural recursive definition of the function~$\fuh_{0}$ also
+suitable to use in \Agda.
+
+\begin{empheq}[box=\fcolorbox{bocolor}{bgcolor}]{equation*}
+ \begin{aligned}
   \label{eq:uh}
   \begin{split}
-  &\fuh : \Prop → \Prop\\
+  &\hspace{.495mm}\fuh_{cm} : \Prop → \Prop\\
   &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
   \end{split}
-\end{align*}
+\end{aligned}
+\end{empheq}
 
 \end{myexamplenum}
-
-% For a more complete treatment of general recursion, and how to define
-% well-founded and well-structural recursive functions, we refer the
-% reader to~\cite{Bove2005}.
 
@@
 
-Type theory and intuitionistic logic are accompanying theories since
-they are based on the same philosophical basis of constructive
-mathematics. Proving propositions in these theories demands a witness
-construction for the proof. Nonetheless, classical logic does not
-always have constructive proofs since some of the proofs are stated
-by refutation.
+Type theory is foundation for constructive mathematics, and its
+internal language is the intuitionistic logic. Proving propositions in
+this theory demands a witness construction for the proof.
+Traditionally, for example in classical logic, a witness is not always
+needed as we can prove arguments by contraction, named \emph{reductio
+ad absurdum}.
 
@@
 theory the classical propositional logic in~\cite{AgdaProp}.  A
-briefly description of it is presented in \cite{VanDalen1994}.
-In this formalization, we have to assume the principle of excluded
-middle (henceforth \abbre{PEM}) as an axiom since \Metis is a prover
-for classical logic. Assuming \abbre{PEM}, we can justify refutation
+briefly description of it is presented in \cite{VanDalen1994}. In this
+formalization, we have to assume the principle of excluded middle
+(henceforth \abbre{PEM}) as an axiom since \Metis is a prover for
+classical logic. Assuming \abbre{PEM}, we can justify refutation
 proofs by deriving from it the \emph{reductio ad absurdum} rule
@@
 the principle of proof by contradiction, that is, a derivation of a
-contradiction,~$⊥$, from the hypothesis~$¬ φ$, is a derivation
-of~$φ$.
+contradiction,~$⊥$, from the hypothesis~$¬ φ$, is a derivation of~$φ$.
 
@@
 We formalize the syntactical consequence relation of \CPL by an
-inductive family \verb!_⊢_! with two indexes, a set of propositions (the
-premises) and a proposition (the conclusion), that is, $Γ ⊢ φ$
+inductive family \verb!_⊢_! with two indexes, a set of propositions
+(the premises) and a proposition (the conclusion), that is, $Γ ⊢ φ$
 represents that there is derivation with conclusion $φ : \Prop$ from
@@
 way as it was presented in~\cite{Altenkirch2015}. For that reason, we
-have included structural rules like \emph{weaken}, formation and
-elimination rules for connectives and the PEM axiom as the valid
-inference rules in Fig.~\ref{fig:CPL-inference-rules}.
+have included in Fig.~\ref{fig:CPL-inference-rules} the valid
+inference rules: structural rules like \emph{weaken}, formation and
+elimination rules of the logical connectives and to reason
+classically, we add the \abbre{PEM} axiom.
 

### 2019-07-09 pubs/paper/sections/04-metis-language-and-proofs.tex
Many revisions and fixes.

--- 2018-06-25 pubs/itp-2018/sections/metis-language-and-proofs.tex
@@
 %
-\documentclass[../main.tex]{subfiles}
+\documentclass[../paper.tex]{subfiles}
 \begin{document}
@@
 A \TSTP  derivation generated by \Metis encodes a natural
-deduction proof using only as valid deduction steps the inference rules
+deduction proof using as valid deduction steps the inference rules
 in Fig.~\ref{tab:agda-metis-table}.

### 2019-07-10 pubs/paper/sections/01-abstract.tex
PR (#68)
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

* [ Sec4 ] example of the strip inference.

* First attemp

\documentclass[../paper.tex]{subfiles}
\begin{document}

\begin{abstract}

  We describe a syntactical proof-reconstruction approach to verifying
  derivations generated by the automatic theorem prover \Metis for
  classical, propositional logic. To verify the derivations, we use
  \Agda, a proof assistant for dependent type theory. We formalise in
  \Agda each inference rule of \Metis reasoning, that is, we transform
  \Metis derivations into \Agda proof-terms. In a future full-fledged
  integration of \Agda with off-the-shelf automatic theorem provers,
  proof-reconstruction shall be a necessary component.

  \keywords{~proof-reconstruction, automatic theorem provers,
    proof-assistants, Agda, Metis}
\end{abstract}

\end{document}

### 2019-07-10 pubs/paper/sections/data/problem.tstp.tex
PR (#68)
* [ paper ] removed many examples and extra content.

* [ paper ] all proofs have been removed.

* Complete first revision to section about Metis

* Review section 4.2

* Review introduction Section 4

* Improve many parts in the text.

Metis section improves in the tptp description.
The example tstp derivation was added with line
numbers.
The explanation of the workflow has changed to
be more explict and also improved for readability.
Remove the numbers in the diagram.
Appendix updated removing the tstp of the small example.

* [ Sec4 ] example of the strip inference.

* First attemp

\begin{figure}
\begin{Verbatim}[commandchars=\\\{\}, numbers=left,xleftmargin=5mm]
fof(premise, axiom, (p ⇒ q) ∧ (q ⇒ p)).  \label{line1}
fof(goal, conjecture, (p ∨ q) ⇒ (p ∧ q)).  \label{line2}
fof(s₀, (p ∨ q) ⇒ p, inf(strip, goal)).  \label{line3}
fof(s₁, ((p ∨ q) ∧ p) ⇒ q, inf(strip, goal)).  \label{line4}
fof(neg₀, ¬ ((p ∨ q) ⇒ p), inf(negate, s₀)).  \label{line5}
fof(n₀₀, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).  \label{line6}
fof(n₀₁, ¬ q ∨ p, inf(conjunct, n₀₀)).  \label{line7}
fof(n₀₂, ¬ p ∧ (p ∨ q), inf(canonicalize, neg₀)).  \label{line8}
fof(n₀₃, p ∨ q, inf(conjunct, n₀₂)).  \label{line9}
fof(n₀₄, ¬ p, inf(conjunct, n₀₂)).  \label{line10}
fof(n₀₅, q, inf(simplify, [n₀₃, n₀₄])).  \label{line11}
cnf(r₀₀, ¬ q ∨ p, inf(canonicalize, n₀₁)).  \label{line12}
cnf(r₀₁, q, inf(canonicalize, n₀₅)).  \label{line13}
cnf(r₀₂, p, inf(resolve, q, [r₀₁, r₀₀])).  \label{line14}
cnf(r₀₃, ¬ p, inf(canonicalize, n₀₄)).  \label{line15}
cnf(r₀₄, ⊥, inf(resolve, p, [r₀₂, r₀₃])).  \label{line16}
fof(neg₁, ¬ ((p ∨ q) ∧ p) ⇒ q, inf(negate, s₁)).  \label{line17}
fof(n₁₀, ¬ q ∧ p ∧ (p ∨ q), inf(canonicalize, neg₁)).  \label{line18}
fof(n₁₁, (¬ p ∨ q) ∧ (¬ q ∨ p), inf(canonicalize, premise)).  \label{line19}
fof(n₁₂, ¬ p ∨ q, inf(conjunct, n₁₁)).  \label{line20}
fof(n₁₃, ⊥, inf(simplify,[n₁₀, n₁₂])).  \label{line21}
cnf(r₁₀, ⊥, inf(canonicalize, n₁₃)).  \label{line22}
\end{Verbatim}
\caption{Customized \Metis \TSTP derivation of the theorem in~\eqref{eq:complete-example-problem}.}
\label{complete-metis-example}
\end{figure}
